### 2019-04-29 template.Rmd
added newest version and templates

---
output:
  bookdown::pdf_document2:
    toc: false
    keep_tex: false
    fig_caption: yes
title: "Title"
author: Author
bibliography: "references.bib"
csl: apa.csl # by default: Chicago style
header-includes:
- \usepackage{float}
- \usepackage{multirow}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.lp="fig:")

# install.packages("tinytex", repos = "https://cloud.r-project.org" ) if debug needed?

# library(namelibrary) for the R library

# http://rmarkdown.rstudio.com
# echo = TRUE <- makes all next cmds appear

```

# PARAGRAPH NAME

@paolillo2019 and [@clark1991]

```{r chunk1, echo=FALSE, message=FALSE, warning=FALSE, include=TRUE}
#echo=TRUE: the code appears in document
#include=TRUE: the output appears in document

```

```{r chunk2, out.widh = '100%', fig.aign='center', fig.cap="CAPTION", include=FALSE}
# knitr::include_graphics("name.pdf")
```

# References

### 2019-05-01 paper_notes.Rmd
added paper cancelled pics

--- 2019-04-29 template.Rmd
@@
 - \usepackage{multirow}
+- \usepackage{xcolor} 
 ---
@@
 ```
-
+\newcommand{\rocco}[1]{\textcolor{red}{{Rocco:}#1}} <!-- command to appear in pdf -->
+<!-- command not to appear in pdf -->
 # PARAGRAPH NAME

### 2019-05-03 paper_notes.Rmd
writing

@@
 ```
-\newcommand{\rocco}[1]{\textcolor{red}{{Rocco:}#1}} <!-- command to appear in pdf -->
+\newcommand{\rocco}[1]{\textcolor{red}{{Rocco:}#1}} <!-- <- this is a command to appear in pdf -->
 <!-- command not to appear in pdf -->
-# PARAGRAPH NAME
 
-@paolillo2019 and [@clark1991]
+# Introduction and Questions
+
+@zhang2004residential cites and refers to @schelling1978micromotives for his prominent influence on threshold and tipping model, still then elaborates on a model based on random utility with single-peaked function and $\beta$.
+How much can a rational model which uses peak of utility and probability of choice be considered to rely on Schelling's threshold model?\
+What is the relation between random utility models and threshold models?
 

### 2019-05-03 paper_notes.Rmd
check history

@@
 @zhang2004residential cites and refers to @schelling1978micromotives for his prominent influence on threshold and tipping model, still then elaborates on a model based on random utility with single-peaked function and $\beta$.
-How much can a rational model which uses peak of utility and probability of choice be considered to rely on Schelling's threshold model?\
+How much can a rational model which uses peak of utility and probability of choice be considered to rely on Schelling's threshold model?
 What is the relation between random utility models and threshold models?

### 2019-05-03 paper_notes.Rmd
ok
progress writing and clarification

--- 2019-05-01 paper_notes.Rmd
@@
 ```
-\newcommand{\rocco}[1]{\textcolor{red}{{Rocco:}#1}} <!-- command to appear in pdf -->
+\newcommand{\rocco}[1]{\textcolor{red}{{Rocco:}#1}} <!-- <- this is a command to appear in pdf -->
 <!-- command not to appear in pdf -->
-# PARAGRAPH NAME
 
-@paolillo2019 and [@clark1991]
+# Introduction and Questions
+
+@zhang2004 cites and refers to @schelling1978 for his prominent influence on threshold and tipping model, still then elaborates on a model based on random utility with single-peaked function and $\beta$.
+How much can a rational model which uses peak of utility and probability of choice be considered to rely on Schelling's threshold model?\
+What is the relation between random utility models and threshold models?\
+\
+
+- @zhang2004 assumes an entire world, not empty patches, so that $utility = 1$ at 50% is because $4/8$ of agents are of similar ethnicity (plus the peak function).
+To replicate his model there should be not empty space.
+@bruch2006 models with $15%$ empty patches.
+Should our world have not empty patches, so to maximize utility?
+This can allow also to test density effects on satisfaction and not bias on concentration calculation.
+
+## Component of probability of the choice
+
+- Object of choice: neighborhood
+- Choice: relocate to a neighborhood
+- Utility: payoff one is likely to accept to make the choice, i.e. to relocate to one neighborhood (which implies to stay on the same neighborhood). In @zhang2004 it is made up of:
+  - deterministic component $U$: how much people desire/value one preference  in order to make the choice, e.g.
+degree of ethnic concentration (e.g.
+max utility = 1 at 100% similars).
+@zhang2004 uses a single-peaked function (vs maximization).
+  - random term $\epsilon$ that refers to other characteristics of the option, i.e.
+the neighborhood, that influence the payoff to choose the neighborhood although not related to the deterministic component.
+In regression models  this is the random  error terms.
+Random utility models in abm recreate with the exponential function, so that not always the best option according to the deterministic component is taken.
+- Probability of the choice: $\beta u (.) + \epsilon$\
+$\beta$ is a parameter indicating how much the random term is important modeled as a positive constant.
+The lower is \$beta\, the higher is random term $\epsilon$, i.e.
+other random characteristics, are relevant to choose one neighborhood.
+The higher is $\beta$, the lower will be the importance of random term $\epsilon$ and higher the importance of deterministic utility component to make a choice, i.e.
+moving to the neighborhood.
+\
+
+# Aim of the paper
+
+- The conceptual difference between $u$ and  $\beta$ should be $u$: what is the ideal point (payoff) to make the choice and $\beta$ how important is that component to people to make a choice.
+The paper could focus on the interplay between different utility functions at ethnic group level and the individual importance for each of them.
+This would allow to test how segregation can emerge from the interplay of different homophily preferences.
+  - The model could be initialized with correlations from data, as Andreas suggested, plus literature (e.g. right-wing and anti-diversity/migrant attitude)
+- Given the interplay of homophily preferences, to compare the difference between threshold models and random utility models with single peaked function.
+It makes sense to consider $\beta$ would apply equally to threshold models and single-peaked function, as well as the inclusion of randomness in a pure Schelling-type model.
+Check @bruch2006 who should have had similar  interest.
+  - This aim/study would make a straight connection with the ACS paper and its conclusion
+
+<!-- read @Brock2001, @Brock1997 -->
 

### 2019-05-05 paper_notes.Rmd
Update paper_notes.Rmd

@@
 \
+- Given the existence of an ideal payoff to make a choice $u$, why should someone give more importance to that dimension over the other, that is, why should $\beta$ vary among individuals?
+An answer in @esser2010 is social, educational, economic capital.
+For instance:
+  - The lower an agent speaks a language, the higher for ethnic homophily would be  $\beta_{ethnic}$;
+  - the higher is social mobility intention, the higher the wealth (socio-economic status) of the neighborhood would be \beta_{status}$
+  - the higher the need to associate with people sharing the same values of local community (receiving context in Esser [@esser2010] (e.g. political orientations, norm beliefs...), the higher 
+- Seemingly, @zhang2004 describes $\epsilon$ as other characteristics of the option which affects the actual choice of that option (i.e.
+neighborhood).
+Esser's [@esser2010] definition of costs of the choice can be taken into consideration, as costs of moving to the neighborhood.
 
@@
   - This aim/study would make a straight connection with the ACS paper and its conclusion
+- The model can address the question why $\beta$, the importance of one characteristic of the neighborhood, would change depending on the needs (characteristics) of the individuals (households)
+- The model can address the question of how costs interact with needs and preferences (economic capital) of individuals.
+  - Both points above (need $\rightarrow$ change in $\beta$) and costs of relocation can be linked to @esser2010 focus on capital theory.
+Relative group size and ethnic boundary making in @esser2010 are supposed to influence probability to make a choice.
+As linking to the ACS paper, they realize into relative group size and symbolic boundary making through homophily preferences.
+  This would foster the linkage Schelling-Esser of the general project agenda.
+- The formula $\beta u (.) + \epsilon$\ should become somthing like $\N_{e} U_{e} + \N_{v} U_{v} + \N_{s} U_{s} - C$ where $\N: need$, $\C: cost$ and $e,v,s$ the ethnic, value and socio-economic status dimension.
+
+# Limits
+
+- Both $\u$ and $\beta$ can vary across individuals, but the model would explode in its complexity
+- Even if we consider households as agents who make a choice, the decision to relocate/where to live can be the product of negotiation of people in that household. Too complicated to be included
 

### 2019-05-05 paper_notes.Rmd
written local

--- 2019-05-03 paper_notes.Rmd
@@
 \
+- Given the existence of an ideal payoff to make a choice $u$, why should someone give more importance to that dimension over the other, that is, why should $\beta$ vary among individuals?
+An answer in @esser2010 is social, educational, economic capital.
+For instance:
+  - The lower an agent speaks a language, the higher for ethnic homophily would be  $\beta_{ethnic}$;
+  - the higher is social mobility intention, the higher the wealth (socio-economic status) of the neighborhood would be $\beta_{status}$
+  - the higher the need to associate with people sharing the same values of local community (receiving context in Esser [@esser2010] (e.g. political orientations, norm beliefs...), the higher 
+- Seemingly, @zhang2004 describes $\epsilon$ as other characteristics of the option which affects the actual choice of that option (i.e.
+neighborhood).
+Esser's [@esser2010] definition of costs of the choice can be taken into consideration, as costs of moving to the neighborhood.
 
@@
 
+- The model can address the question why $\beta$, the importance of one characteristic of the neighborhood, would change depending on the needs (characteristics) of the individuals (households)
+- The model can address the question of how costs interact with needs and preferences (economic capital) of individuals.
+  - Both points above (need $\rightarrow$ change in $\beta$) and costs of relocation can be linked to @esser2010 focus on capital theory.
+Relative group size and ethnic boundary making in @esser2010 are supposed to influence probability to make a choice.
+As linking to the ACS paper, they realize into relative group size and symbolic boundary making through homophily preferences.
+  This would foster the linkage Schelling-Esser of the general project agenda.
+- The formula $\beta u (.) + \epsilon$ should become somthing like $$N_{e} U_{e} + N_{v} U_{v} + N_{s} U_{s} - C$$ where $N$ =  needs, $C$ = costs and $e,v,s$ the ethnic, value and socio-economic status dimension.
+
+# Limits
+
+- Both $u$ and $\beta$ can vary across individuals, but the model would explode in its complexity
+- Even if we consider households as agents who make a choice, the decision to relocate can be the product of negotiation of people in that household. Too complicated to be included
+
+Test, ignore
 <!-- read @Brock2001, @Brock1997 -->

### 2019-05-05 paper_notes.Rmd
Update paper_notes.Rmd

@@
   - This aim/study would make a straight connection with the ACS paper and its conclusion
-
 - The model can address the question why $\beta$, the importance of one characteristic of the neighborhood, would change depending on the needs (characteristics) of the individuals (households)
@@
   This would foster the linkage Schelling-Esser of the general project agenda.
+- As in the Schelling's model [@schelling1969;@schelling1971], there is not question on why preferences for similar exist.
+While in the ACS paper we extended the model by including different dimensions of similarity.
+Extension to rational models as this would benefit understanding of different homophily preferences through their explicative reasons.
+
 - The formula $\beta u (.) + \epsilon$ should become somthing like $$N_{e} U_{e} + N_{v} U_{v} + N_{s} U_{s} - C$$ where $N$ =  needs, $C$ = costs and $e,v,s$ the ethnic, value and socio-economic status dimension.
@@
 
-Test, ignore
 <!-- read @Brock2001, @Brock1997 -->
 
-```{r chunk1, echo=FALSE, message=FALSE, warning=FALSE, include=TRUE}
-#echo=TRUE: the code appears in document
-#include=TRUE: the output appears in document
-
-```
-
-```{r chunk2, out.widh = '100%', fig.aign='center', fig.cap="CAPTION", include=FALSE}
-# knitr::include_graphics("name.pdf")
-```
-
 # References

### 2019-05-05 paper_notes.Rmd
Update paper_notes.Rmd

@@
   - the higher the need to associate with people sharing the same values of local community (receiving context in Esser [@esser2010] (e.g. political orientations, norm beliefs...), the higher 
-- Seemingly, @zhang2004 describes $\epsilon$ as other characteristics of the option which affects the actual choice of that option (i.e.
-neighborhood).
-Esser's [@esser2010] definition of costs of the choice can be taken into consideration, as costs of moving to the neighborhood.
+- Costs of relocation can be included as costs that hinder relocation despite high probability to choose.
+This can be one application of  @esser2010's definition of costs as limit to the investment on the receving context option (although in the ethnic population, but it can be extended).
+In @esser2010 costs is loosely derived from social, economic and cultural capital milieu, e.g.
+risk of social exclusion from in-group, but economic costs of relocation can be one simple implementation now.
 
@@
 
-- The formula $\beta u (.) + \epsilon$ should become somthing like $$N_{e} U_{e} + N_{v} U_{v} + N_{s} U_{s} - C$$ where $N$ =  needs, $C$ = costs and $e,v,s$ the ethnic, value and socio-economic status dimension.
+- The formula $\beta u (.) + \epsilon$ should become something like $$N_{e} U_{e} + N_{v} U_{v} + N_{s} U_{s} - C$$ where $N$ =  needs, $C$ = costs and $e,v,s$ the ethnic, value and socio-economic status dimension.
+The random term $\epsilon$ is implemented through the exponential function.
 

### 2019-05-06 paper_notes.Rmd
added ses, behavior to do

@@
 
+# Model
+
+- Notes: at the moment the distribution of values or ses is at the ethnic group level, it is not nested.
+E.g.
+it would be possible to extend with distribution of tolerant/intolerants within high ses class and independent distribution of tolerant/intolerant within low ses class.
+I think this would allow to better address the correlation between the dimensions at a more realistic rate, but increase the number of parameter.
+
+- A way to reduce the number of parameters and make the model more realistic might be to have $u$ changing as function of the identification agents hold for the three categories (value, ethnicity and ses), changing the category to a gradient $-1 ...+1$, e.g.:
+  - value: extreme right-wing $\longleftrightarrow$ extreme leftwing, or pro loval norms $\longleftrightarrow$ vs local norms
+  - ses: extrem low $\longleftrightarrow$ extreme high
+  - ethnicity: dychotomous group 1 vs group 2
+People who recognize as extremely leftwing or extremely rightwing might be more likely to attribute higher value to $\beta_{v}$ than people who are on the average position.
+Other dynamics that might be associated can be different homophily/heterophily behavior:
+  - people at the lowest continuum for socio-economic status might be willing to move to richer neighborhoods (i.e.
+heterophily behavior) than people higher in the scale who would relocate to neighborhoods with similar status (i.e.
+homophily)
+  - inter-relation between identification and homophily preferences: if values is considered as tolerance towards diversity as in the ACS paper, people at the middle position should not care about ethnicity, those at the extreme intolerant position devalue the neighborhood, thus increasing the ethnic homophily preference.
+A way could be considering as similar those who fall into a $+0.10\backslash0.10$ range.
+The slope of utility including M can be derived by the position of the agent along the continuum, starting from 0.5 for those in the average position.
+E.g.
+0 value would have a threshold of 0.5 and progressively losing it.
+An extreme agent at 1, with utility 100% of those considered as similar, the same for $-1$ with $u = 1$ at 100% similar (extremely liberal agents).
+Also less than $50%$ would mean others not similar, including extreme ones would be in the neighborhood.
+
 # Limits

### 2019-05-07 paper_notes.Rmd
checked function

@@
 
+The function below works with the modelization of utility.
+In @zhang2004, it is assumed people have a preference for mixed neighborhood ($u=1$  at 50%), depending on number of agents in neighborhood.
+As formulated now, the number of desired agents $n$ is substituted with the desired fraction.
+The first 3 steps compares to @zhang2004 results, Z = 1 and M = 0.6 the last one is to test with a neighborhood of 6 patches.
+With $m=0$, utility is constant once the ideal payoff is reached as in a threshold model, with $m=1$, symmetrical peaked function results To edit in table
+
+```{r testing function, echo=FALSE}
+
+f <- function(P,Z,M,x,n){
+  if (x/n  <= P){U <- ((x/n)/P)}
+  else {U <- (2*Z-M) + (((M-Z)*(x/n))/P)}
+  round(U,digits = 3)
+ # print(U)
+}
+
+f0m <- f(0.5,1,0.6,0,8)
+f1m <- f(0.5,1,0.6,1,8)
+f2m <- f(0.5,1,0.6,2,8)
+f3m <- f(0.5,1,0.6,3,8)
+f4m <- f(0.5,1,0.6,4,8)
+f5m <- f(0.5,1,0.6,5,8)
+f6m <- f(0.5,1,0.6,6,8)
+f7m <- f(0.5,1,0.6,7,8)
+f8m <- f(0.5,1,0.6,8,8)
+
+utilitym <- c(f0m,f1m,f2m,f3m,f4m,f5m,f6m,f7m,f8m)
+concentrationm <- c(0:8)
+
+f0vn <- f(0.5,1,0.6,0,4)
+f1vn <- f(0.5,1,0.6,1,4)
+f2vn <- f(0.5,1,0.6,2,4)
+f3vn <- f(0.5,1,0.6,3,4)
+f4vn <- f(0.5,1,0.6,4,4)
+
+utilityvn <- c(f0vn,f1vn,f2vn,f3vn,f4vn)
+concentrationvn <- c(0:4)
+
+f0r2 <- f(0.5,1,0.6,0,12)
+f1r2 <- f(0.5,1,0.6,1,12)
+f2r2 <- f(0.5,1,0.6,2,12)
+f3r2 <- f(0.5,1,0.6,3,12)
+f4r2 <- f(0.5,1,0.6,4,12)
+f5r2 <- f(0.5,1,0.6,5,12)
+f6r2 <- f(0.5,1,0.6,6,12)
+f7r2 <- f(0.5,1,0.6,7,12)
+f8r2 <- f(0.5,1,0.6,8,12)
+f9r2 <- f(0.5,1,0.6,9,12)
+f10r2 <- f(0.5,1,0.6,10,12)
+f11r2 <- f(0.5,1,0.6,11,12)
+f12r2 <- f(0.5,1,0.6,12,12)
+
+utilityr2 <- c(f0r2,f1r2,f2r2,f3r2,f4r2,f5r2,f6r2,f7r2,f8r2,f9r2,f10r2,f11r2,f12r2)
+concentrationr2 <- c(0:12)
+
+f0t6 <- f(0.5,1,0.6,0,6)
+f1t6 <- f(0.5,1,0.6,1,6)
+f2t6 <- f(0.5,1,0.6,2,6)
+f3t6 <- f(0.5,1,0.6,3,6)
+f4t6 <- f(0.5,1,0.6,4,6)
+f5t6 <- f(0.5,1,0.6,5,6)
+f6t6 <- f(0.5,1,0.6,6,6)
+
+utilityt6 <- c(f0t6,f1t6,f2t6,f3t6,f4t6,f5t6,f6t6)
+concentrationt6 <- c(0:6)
+
+print(utilityvn)
+plot(concentrationvn,utilityvn)
+
+print(utilitym)
+plot(concentrationm,utilitym)
+
+print(utilityr2)
+plot(concentrationr2,utilityr2)
+
+print(utilityt6)
+plot(concentrationt6,utilityt6)
+
+```
+
 # Limits

### 2019-05-07 paper_notes.Rmd
simplified formulae

--- 2019-05-06 paper_notes.Rmd
@@
 - \usepackage{xcolor} 
+- \usepackage{amsmath}
 ---
@@
 
+The function below works with the modelization of utility.
+In @zhang2004, it is assumed people have a preference for mixed neighborhood ($u=1$  at 50%), depending on number of agents in neighborhood.
+As formulated now, the number of desired agents $n$ is substituted with the desired concentration.
+
+$$
+U=
+\begin{cases}
+\frac{x}{np}, & \text{if} \ x \leq np, \\
+(2Z-M)+\frac{(M-Z)x}{p}, & otherwise
+\end{cases}
+$$
+
+Assuming $Z=1$ as peak of utility at desired fraction $P$, then the equation becomes:
+
+$$
+U=
+\begin{cases}
+\frac{x}{np}, & \text{if} \ x \leq np, \\
+(2-M)+\frac{(M-1)x}{p}, & otherwise
+\end{cases}
+$$
+
+The first 3 steps compares to @zhang2004 results, Z = 1 and M = 0.6 the last one is to test with a neighborhood of 6 patches.
+With $m=0$, utility is constant once the ideal payoff is reached as in a threshold model, with $m=1$, symmetrical peaked function results.
+To edit in table
+^[Not managed to implement Flache's formula on slides, either not understood correctly what it would translate on my formula: p = n number of agents; f = P desired concentration.]
+
+```{r testing function, echo=FALSE}
+
+f <- function(p,M,x,n){
+  if (x  <= (n*p)){U <- (x/(n*p))}
+  else {U <- (2-M) + (((M-1)*x)/(n*p))}
+  round(U,digits = 3)
+ # print(U)
+}
+
+f0m <- f(0.5,0.6,0,8)
+f1m <- f(0.5,0.6,1,8)
+f2m <- f(0.5,0.6,2,8)
+f3m <- f(0.5,0.6,3,8)
+f4m <- f(0.5,0.6,4,8)
+f5m <- f(0.5,0.6,5,8)
+f6m <- f(0.5,0.6,6,8)
+f7m <- f(0.5,0.6,7,8)
+f8m <- f(0.5,0.6,8,8)
+
+utilitym <- c(f0m,f1m,f2m,f3m,f4m,f5m,f6m,f7m,f8m)
+concentrationm <- c(0:8)
+
+f0vn <- f(0.5,0.6,0,4)
+f1vn <- f(0.5,0.6,1,4)
+f2vn <- f(0.5,0.6,2,4)
+f3vn <- f(0.5,0.6,3,4)
+f4vn <- f(0.5,0.6,4,4)
+
+utilityvn <- c(f0vn,f1vn,f2vn,f3vn,f4vn)
+concentrationvn <- c(0:4)
+
+f0r2 <- f(0.5,0.6,0,12)
+f1r2 <- f(0.5,0.6,1,12)
+f2r2 <- f(0.5,0.6,2,12)
+f3r2 <- f(0.5,0.6,3,12)
+f4r2 <- f(0.5,0.6,4,12)
+f5r2 <- f(0.5,0.6,5,12)
+f6r2 <- f(0.5,0.6,6,12)
+f7r2 <- f(0.5,0.6,7,12)
+f8r2 <- f(0.5,0.6,8,12)
+f9r2 <- f(0.5,0.6,9,12)
+f10r2 <- f(0.5,0.6,10,12)
+f11r2 <- f(0.5,0.6,11,12)
+f12r2 <- f(0.5,0.6,12,12)
+
+utilityr2 <- c(f0r2,f1r2,f2r2,f3r2,f4r2,f5r2,f6r2,f7r2,f8r2,f9r2,f10r2,f11r2,f12r2)
+concentrationr2 <- c(0:12)
+
+f0t6 <- f(0.5,0.6,0,6)
+f1t6 <- f(0.5,0.6,1,6)
+f2t6 <- f(0.5,0.6,2,6)
+f3t6 <- f(0.5,0.6,3,6)
+f4t6 <- f(0.5,0.6,4,6)
+f5t6 <- f(0.5,0.6,5,6)
+f6t6 <- f(0.5,0.6,6,6)
+
+utilityt6 <- c(f0t6,f1t6,f2t6,f3t6,f4t6,f5t6,f6t6)
+concentrationt6 <- c(0:6)
+
+print(utilityvn)
+plot(concentrationvn,utilityvn)
+
+print(utilitym)
+plot(concentrationm,utilitym)
+
+print(utilityr2)
+plot(concentrationr2,utilityr2)
+
+print(utilityt6)
+plot(concentrationt6,utilityt6)
+
+```
+
 # Limits

### 2019-05-09 paper_notes.Rmd
tested utility to check

@@
 \frac{x}{np}, & \text{if} \ x \leq np, \\
-(2Z-M)+\frac{(M-Z)x}{p}, & otherwise
+(2Z-M)+\frac{(M-Z)x}{np}, & otherwise
 \end{cases}
@@
 \frac{x}{np}, & \text{if} \ x \leq np, \\
-(2-M)+\frac{(M-1)x}{p}, & otherwise
+(2-M)+\frac{(M-1)x}{np}, & otherwise
 \end{cases}
@@
 
-The first 3 steps compares to @zhang2004 results, Z = 1 and M = 0.6 the last one is to test with a neighborhood of 6 patches.
+The first 3 steps compares to @zhang2004 results, Z = 1 and M = 0.6 the last one is to test with a neighborhood of 8 patches.
 With $m=0$, utility is constant once the ideal payoff is reached as in a threshold model, with $m=1$, symmetrical peaked function results.
 To edit in table
-^[Not managed to implement Flache's formula on slides, either not understood correctly what it would translate on my formula: p = n number of agents; f = P desired concentration.]
+^[Not managed to implement Flache's formula on slides, either not understood correctly what it would translate on my formula: p = n number of agents; f = P desired concentration.]\
+* With p = 0.2 the right-side of peaked function goes below 0, in sum conditions as p = 0.8 and p = 0.3 utility is approximated above .9 but does not reach 1.
 
@@
   if (x  <= (n*p)){U <- (x/(n*p))}
-  else {U <- (2-M) + (((M-1)*x)/(n*p))}
+  else {U <- M + ((1-(x/n))*(1-M))/(1-p)}
+ # else {U <- (2-M) + (((M-1)*x)/(n*p))} M + ((1-(x/n))*(1-M))/(1-p)}
   round(U,digits = 3)
@@
 
-f0t6 <- f(0.5,0.6,0,6)
-f1t6 <- f(0.5,0.6,1,6)
-f2t6 <- f(0.5,0.6,2,6)
-f3t6 <- f(0.5,0.6,3,6)
-f4t6 <- f(0.5,0.6,4,6)
-f5t6 <- f(0.5,0.6,5,6)
-f6t6 <- f(0.5,0.6,6,6)
+f0t8 <- f(0.5,0.6,0,8)
+f1t8 <- f(0.5,0.6,1,8)
+f2t8 <- f(0.5,0.6,2,8)
+f3t8 <- f(0.5,0.6,3,8)
+f4t8 <- f(0.5,0.6,4,8)
+f5t8 <- f(0.5,0.6,5,8)
+f6t8 <- f(0.5,0.6,6,8)
+f7t8 <- f(0.5,0.6,7,8)
+f8t8 <- f(0.5,0.6,8,8)
 
-utilityt6 <- c(f0t6,f1t6,f2t6,f3t6,f4t6,f5t6,f6t6)
-concentrationt6 <- c(0:6)
+utilityt8 <- c(f0t8,f1t8,f2t8,f3t8,f4t8,f5t8,f6t8,f7t8)
+concentrationt8 <- c(0:7)
 
@@
 
-print(utilityt6)
-plot(concentrationt6,utilityt6)
+print(utilityt8)
+plot(concentrationt8,utilityt8)
 

### 2019-05-10 paper_notes.Rmd
finalized simulation, check

@@
 
+Test for $utility = 1$, utility = 0 means that agents want $0%$ similars in their neighbborhood, thus neighborhoods with not any similar one will have max utility and literally decreasing for neighborhoods with more similar ones.
+With $\beta = 0$, agents don't care about the composition of the neighborhood, so that both current location and alternative patch have prob.
+equal to zero, selecting alternative or current one randomly, sometimes relocating.
+Increasing $\beta$, the utility attributed to the patch due to neighborhood composition is multiplied times $\beta$, meaning those neighborhoods less inhabited by similar ones will higher probability to be chosen, thus increasing integration.
+It is not agents don't care, but agents care that similar ones are not there.
+See if this is related to @bruch2006's error cited by @van2009
+
 ```{r testing function, echo=FALSE}
@@
 
-f0t8 <- f(0.5,0.6,0,8)
-f1t8 <- f(0.5,0.6,1,8)
-f2t8 <- f(0.5,0.6,2,8)
-f3t8 <- f(0.5,0.6,3,8)
-f4t8 <- f(0.5,0.6,4,8)
-f5t8 <- f(0.5,0.6,5,8)
-f6t8 <- f(0.5,0.6,6,8)
-f7t8 <- f(0.5,0.6,7,8)
-f8t8 <- f(0.5,0.6,8,8)
+f0t8 <- f(0,0.6,0,8)
+f1t8 <- f(0,0.6,1,8)
+f2t8 <- f(0,0.6,2,8)
+f3t8 <- f(0,0.6,3,8)
+f4t8 <- f(0,0.6,4,8)
+f5t8 <- f(0,0.6,5,8)
+f6t8 <- f(0,0.6,6,8)
+f7t8 <- f(0,0.6,7,8)
+f8t8 <- f(0,0.6,8,8)
 

### 2019-05-17 paper_notes.Rmd
utility 0 empty patches

--- 2019-05-09 paper_notes.Rmd
@@
     toc: false
-    keep_tex: false
+ #   keep_tex: false
     fig_caption: yes
-title: "Title"
-author: Author
+title: "Paper notes"
+author: Rocco Paolillo
 bibliography: "references.bib"
-csl: apa.csl # by default: Chicago style
+# csl: apa.csl # by default: Chicago style
 header-includes:
@@
 knitr::opts_chunk$set(echo = TRUE, fig.lp="fig:")
+
+f <- function(p,M,x,n){
+  if (x  <= (n*p)){U <- (x/(n*p))}
+  else {U <- M + ((1-(x/n))*(1-M))/(1-p)}
+ # else {U <- (2-M) + (((M-1)*x)/(n*p))} M + ((1-(x/n))*(1-M))/(1-p)}
+  round(U,digits = 3)
+ # print(U)
+}
 
@@
 
-# Introduction and Questions
-
-@zhang2004 cites and refers to @schelling1978 for his prominent influence on threshold and tipping model, still then elaborates on a model based on random utility with single-peaked function and $\beta$.
-How much can a rational model which uses peak of utility and probability of choice be considered to rely on Schelling's threshold model?\
-What is the relation between random utility models and threshold models?\
-\
-
-- @zhang2004 assumes an entire world, not empty patches, so that $utility = 1$ at 50% is because $4/8$ of agents are of similar ethnicity (plus the peak function).
-To replicate his model there should be not empty space.
-@bruch2006 models with $15%$ empty patches.
-Should our world have not empty patches, so to maximize utility?
-This can allow also to test density effects on satisfaction and not bias on concentration calculation.
-
-## Component of probability of the choice
+# Component of probability of the choice
 
@@
 - Choice: relocate to a neighborhood
-- Utility: payoff one is likely to accept to make the choice, i.e. to relocate to one neighborhood (which implies to stay on the same neighborhood). In @zhang2004 it is made up of:
-  - deterministic component $U$: how much people desire/value one preference  in order to make the choice, e.g.
+- Utility: payoff one is likely to accept to make the choice, i.e. to relocate to one neighborhood (or stay on current one). In @zhang2004 it is made up of:
+  - deterministic component $U$: how much people desire/value one preference  in order to make the choice as ideal payoff, e.g.
 degree of ethnic concentration (e.g.
@@
   - random term $\epsilon$ that refers to other characteristics of the option, i.e.
-the neighborhood, that influence the payoff to choose the neighborhood although not related to the deterministic component.
+the neighborhood, that influence the choice but independent of utility payoff.
 In regression models  this is the random  error terms.
-Random utility models in abm recreate with the exponential function, so that not always the best option according to the deterministic component is taken.
-- Probability of the choice: $\beta u (.) + \epsilon$\
-$\beta$ is a parameter indicating how much the random term is important modeled as a positive constant.
-The lower is \$beta\, the higher is random term $\epsilon$, i.e.
+Random utility models in abm recreate with the exponential function, so that not always the best option according to the deterministic component $U$ is chosen.
+- Probability of the choice: $\beta u (.) + \epsilon$\, which is conceptually different but related to payoff $u$
+  - $\beta$ is a parameter indicating how much the characteristic of the option is important in the probability to make a choice, or the random term $\epsilon$.
+It is modeled as a positive constant: the lower is $\beta$, the higher is random term $\epsilon$, i.e.
 other random characteristics, are relevant to choose one neighborhood.
@@
 \
-- Given the existence of an ideal payoff to make a choice $u$, why should someone give more importance to that dimension over the other, that is, why should $\beta$ vary among individuals?
-An answer in @esser2010 is social, educational, economic capital.
-For instance:
-  - The lower an agent speaks a language, the higher for ethnic homophily would be  $\beta_{ethnic}$;
-  - the higher is social mobility intention, the higher the wealth (socio-economic status) of the neighborhood would be $\beta_{status}$
-  - the higher the need to associate with people sharing the same values of local community (receiving context in Esser [@esser2010] (e.g. political orientations, norm beliefs...), the higher 
-- Costs of relocation can be included as costs that hinder relocation despite high probability to choose.
-This can be one application of  @esser2010's definition of costs as limit to the investment on the receving context option (although in the ethnic population, but it can be extended).
-In @esser2010 costs is loosely derived from social, economic and cultural capital milieu, e.g.
-risk of social exclusion from in-group, but economic costs of relocation can be one simple implementation now.
 
@@
 
-- The conceptual difference between $u$ and  $\beta$ should be $u$: what is the ideal point (payoff) to make the choice and $\beta$ how important is that component to people to make a choice.
-The paper could focus on the interplay between different utility functions at ethnic group level and the individual importance for each of them.
-This would allow to test how segregation can emerge from the interplay of different homophily preferences.
-  - The model could be initialized with correlations from data, as Andreas suggested, plus literature (e.g. right-wing and anti-diversity/migrant attitude)
-- Given the interplay of homophily preferences, to compare the difference between threshold models and random utility models with single peaked function.
-It makes sense to consider $\beta$ would apply equally to threshold models and single-peaked function, as well as the inclusion of randomness in a pure Schelling-type model.
-Check @bruch2006 who should have had similar  interest.
-  - This aim/study would make a straight connection with the ACS paper and its conclusion
-- The model can address the question why $\beta$, the importance of one characteristic of the neighborhood, would change depending on the needs (characteristics) of the individuals (households)
-- The model can address the question of how costs interact with needs and preferences (economic capital) of individuals.
-  - Both points above (need $\rightarrow$ change in $\beta$) and costs of relocation can be linked to @esser2010 focus on capital theory.
-Relative group size and ethnic boundary making in @esser2010 are supposed to influence probability to make a choice.
-As linking to the ACS paper, they realize into relative group size and symbolic boundary making through homophily preferences.
-  This would foster the linkage Schelling-Esser of the general project agenda.
-- As in the Schelling's model [@schelling1969;@schelling1971], there is not question on why preferences for similar exist.
-While in the ACS paper we extended the model by including different dimensions of similarity.
-Extension to rational models as this would benefit understanding of different homophily preferences through their explicative reasons.
+- Independent of the ideal payoff $u$ people have for one characteristic of the neighborhood, my question is why someone should give more importance to that characteristic over the others, that is:
+\par
+why should $\beta$ vary among individuals?
+\par
+An answer in @esser2010 is social, educational, economic capital and how it translates into the investment of people into receiving context/ethnic context and his general suggestion. For instance:
+  - The lower an agent speaks a language, the higher the need for aggregating with co-ethnics would be, so to increase $\beta_{ethnic}$ independently of what is the ideal payoff for ethnic composition of the neighborhood;
+  - the higher is social mobility intention either as investment or value in the own community, the higher the wealth (socio-economic status) of the neighborhood would be $\beta_{status}$
+  - the higher the need to associate with people sharing the same values of local community (receiving context in Esser [@esser2010] (e.g.
+political orientations, norm beliefs...) even as strategy for crossing ethnic boundaries [@wimmer2013], the higher the composition of value-orientation would become with increase of $\beta_{value}$
+- Costs of relocation can be included as costs that hinder relocation despite the choice.
+This can be one application of  @esser2010's definition of costs as limit to the investment on the receving context option.
+In @esser2010 costs is loosely derived from social, economic and cultural capital milieu and are basically conceptualized upon the concrete choice actors (i.e.
+migrants) want to engage in, costs of relocation can be one of many.
 
-- The formula $\beta u (.) + \epsilon$ should become something like $$N_{e} U_{e} + N_{v} U_{v} + N_{s} U_{s} - C$$ where $N$ =  needs, $C$ = costs and $e,v,s$ the ethnic, value and socio-economic status dimension.
+- In the ACS paper [@paolillo2018] we focused on the interplay of different homophily preferences in Schelling's threshold model and diffent type of segregation that emerge.
+With this direction the next paper could link to the ACS paper [@paolillo2018] by:
+  * addressing the reason why people would have preference for one characteristic over the other
+  * what's the effect of people holding different preferences at same grades, while in the ACS they were exclusive tolerant: value, intolerant: ethnicity
+  * extension to the random utility model as in @zhang2004 would distinguish between the ideal payoff $u$ for a characteristic and how important is that characteristic to people $\beta$
+  * an additional point to random utility models would be to link $\beta$ to needs and resources of people as in @esser2010. This has some advantages to me:
+    - relative group size and ethnic boundary making in @esser2010 are supposed to influence probability to make a choice.In the ACS paper we included symbolic boundaries through the definition of similarity and relative group size, now we would include the overall frame of the model with need $\rightarrow$ change in $\beta$) and costs of relocation
+    - as in the original Schelling [@schelling1969;@schelling1971] and other literature, homophily *per se* is a mechanism which describes the aggregation dynamics, but it does not provide causal mechanism on why people should aggregate based on one dimension over the others.
+This frame of the paper could fill this point
+    - foster the linkage between @esser2010's speculation and Schelling's model, so to benefit the long term agenda of the project
+    - deeper definition of utility frame and rational choice, linking to the literature in abm and concretisize @esser2010's model itself, which was elaborated as a summa of general and abstract rational choice
+
+- Linking $\beta$ to needs and including costs, $\beta u (.) + \epsilon$ should become something like $$N_{e} U_{e} + N_{v} U_{v} + N_{s} U_{s} - C$$ where $N$ =  needs, $C$ = costs and $e,v,s$ the ethnic, value and socio-economic status dimension.
 The random term $\epsilon$ is implemented through the exponential function.
 
-# Model
+# Notes on the model
 
-- Notes: at the moment the distribution of values or ses is at the ethnic group level, it is not nested.
-E.g.
-it would be possible to extend with distribution of tolerant/intolerants within high ses class and independent distribution of tolerant/intolerant within low ses class.
-I think this would allow to better address the correlation between the dimensions at a more realistic rate, but increase the number of parameter.
+- Now agents' characteristics of ethnicity, value and ses are nested.
+I think it would be worth to have a change in $u$ and $\beta$ for any intersection, but with risk to increase the number of parameters.
+The simplest solution I found so far was to link it to the value-orientation of agents as in the ACS paper [@paolillo2018].
 
-- A way to reduce the number of parameters and make the model more realistic might be to have $u$ changing as function of the identification agents hold for the three categories (value, ethnicity and ses), changing the category to a gradient $-1 ...+1$, e.g.:
-  - value: extreme right-wing $\longleftrightarrow$ extreme leftwing, or pro loval norms $\longleftrightarrow$ vs local norms
+- A way to reduce the number of parameters and make the model more realistic might be to have $u$ changing as function of the identification agents hold for the three categories (value, ethnicity and ses), changing the categories to a gradient $-1 ...+1$, e.g.:
+  - value: extreme right-wing $\longleftrightarrow$ extreme leftwing, or pro local norms $\longleftrightarrow$ vs local norms.
   - ses: extrem low $\longleftrightarrow$ extreme high
   - ethnicity: dychotomous group 1 vs group 2
-People who recognize as extremely leftwing or extremely rightwing might be more likely to attribute higher value to $\beta_{v}$ than people who are on the average position.
-Other dynamics that might be associated can be different homophily/heterophily behavior:
-  - people at the lowest continuum for socio-economic status might be willing to move to richer neighborhoods (i.e.
-heterophily behavior) than people higher in the scale who would relocate to neighborhoods with similar status (i.e.
-homophily)
-  - inter-relation between identification and homophily preferences: if values is considered as tolerance towards diversity as in the ACS paper, people at the middle position should not care about ethnicity, those at the extreme intolerant position devalue the neighborhood, thus increasing the ethnic homophily preference.
-A way could be considering as similar those who fall into a $+0.10\backslash0.10$ range.
-The slope of utility including M can be derived by the position of the agent along the continuum, starting from 0.5 for those in the average position.
-E.g.
-0 value would have a threshold of 0.5 and progressively losing it.
-An extreme agent at 1, with utility 100% of those considered as similar, the same for $-1$ with $u = 1$ at 100% similar (extremely liberal agents).
-Also less than $50%$ would mean others not similar, including extreme ones would be in the neighborhood.
+This way would maybe allow to explore more with fewer parameters: 
+  - ideal payoff function $u$ as in the single-peaked function could derive from how people positionate along the continuum, as well combination of different homophily preferences.
+Assuming value as tolerance towards diversity, people extremely conservative would likely want in their neighborhood people both of the same ethnic group, but also of the same value orientation.
+People in the middler positions would care less about the value-orientation of others (as in the current ACS paper)
+  - the model would be relaxated which would justify the single-peaked function, linking $u$ to  shift in $M$ and affect the right slope: people who aim at 100% similar neighborhood would be more likely to choose a 90% similar neighborhood than 30%, as well as people aiming at a mixed 50% neighborhood would be more likely to choose a 60% of similar, as in Zhang [@zhang2004]
+  - different and more realistic scenarios, and examples in literature could be compared [@van2012] or what data show.
+This supports  the aim of the abm/project to clarify how different scenarios of integration/segregation are possible in an unified model and theory building
 
-The function below works with the modelization of utility.
-In @zhang2004, it is assumed people have a preference for mixed neighborhood ($u=1$  at 50%), depending on number of agents in neighborhood.
-As formulated now, the number of desired agents $n$ is substituted with the desired concentration.
+I implemented in the model the single-peaked funcition as in @zhang2004 since I think it allows to explore more articulated scenarios. I think it would be worth to question about as above.
 
@@
 
-Assuming $Z=1$ as peak of utility at desired fraction $P$, then the equation becomes:
+Assuming $Z=1$ as peak of utility at desired fraction $P$, then the equation becomes as follow.
+This is how I implemented  for the three utilities (ethnicity, value, ses).
+Did not understand to be honest how the second equation @zhang2004 (otherwise) is reduced to the one used  in Andreas Flache's slides and Sage's model (how 2Z-M disappears).
+I adapted their equation, but I  understand it and it works as I tested.
 
@@
 \frac{x}{np}, & \text{if} \ x \leq np, \\
-(2-M)+\frac{(M-1)x}{np}, & otherwise
+M+\frac{(1-(x/n))*(1-M)}{(1-p)}, & otherwise
 \end{cases}
 $$
+\
 
-The first 3 steps compares to @zhang2004 results, Z = 1 and M = 0.6 the last one is to test with a neighborhood of 8 patches.
-With $m=0$, utility is constant once the ideal payoff is reached as in a threshold model, with $m=1$, symmetrical peaked function results.
-To edit in table
-^[Not managed to implement Flache's formula on slides, either not understood correctly what it would translate on my formula: p = n number of agents; f = P desired concentration.]\
-* With p = 0.2 the right-side of peaked function goes below 0, in sum conditions as p = 0.8 and p = 0.3 utility is approximated above .9 but does not reach 1.
+where
+M = constant for the right slope \
+x = number of similar ones in Moore neighborhood \
+n = number of agents in the Moore neighborhod $\rightarrow$ x/n: fraction similars \
+p = desired concentration \
 
-```{r testing function, echo=FALSE}
+Fig. \ref{fig:moore} replicates @zhang2004 for desired fraction $p=0.5$ in an 8 patches Moore neighborhood, $Z=1$ and $M=0.6$.\
+Fig  \ref{fig:sechneg} shows how the function will not change for the same proportion within a different number of patches occupied in the neighborhood, here with occupied patches equal to 6.\
+Fig. \ref{fig:emmeone} shows how for M=1 utility becomes constant once the ideal payoff is reached, kind similar to threshold models\
+Fig. \ref{fig:emmezero} shows how for M=0 the right slope is symmetrical with left one.
 
-f <- function(p,M,x,n){
-  if (x  <= (n*p)){U <- (x/(n*p))}
-  else {U <- M + ((1-(x/n))*(1-M))/(1-p)}
- # else {U <- (2-M) + (((M-1)*x)/(n*p))} M + ((1-(x/n))*(1-M))/(1-p)}
-  round(U,digits = 3)
- # print(U)
-}
+Fig.
+\ref{fig:utzero} shows the condition where desired concentration $p=0$ in a 8 patches neighborhoood, with $M=0.6$, which means agents actively do not want any similar in the neighborhood.
+This means that although utility = 1 at 0 is not possible, the function becomes linear decreasing.\
+Fig.
+\ref{fig:integr} shows how this translates in the  model with $\beta=100$.
+Seems to me it increases stable integration, and it is not an error: as @zhang2004 describes, with $\beta=0$ agents just move randomly, with equal chance to move to alternative patch or stay in neighborhood.
+Here with $\beta=100$ the characteristic of the neighborhood is relevant to them, although the payoff is 0 and $\beta * u=0$, correct I think conceptually and as the stable patterns of emerged segregations and average utility show.
+To check if this can be related to @bruch2006's error cited by @van2009
+
+```{r moore, echo=FALSE, fig.cap="utility in Moore 8 patches; desired fraction 50%, M=0.6, Z=1"}
 
@@
 
-utilitym <- c(f0m,f1m,f2m,f3m,f4m,f5m,f6m,f7m,f8m)
+utility_Moore <- c(f0m,f1m,f2m,f3m,f4m,f5m,f6m,f7m,f8m)
 concentrationm <- c(0:8)
+
+# print(utilitym)
+plot(concentrationm,utility_Moore)
+```
+
+```{r sechneg, echo=FALSE, fig.cap="utility in Moore 6 patches; desired fraction 50%, M=0.6, Z=1"}
+
+f0t6 <- f(0.5,0.6,0,6)
+f1t6 <- f(0.5,0.6,1,6)
+f2t6<- f(0.5,0.6,2,6)
+f3t6 <- f(0.5,0.6,3,6)
+f4t6 <- f(0.5,0.6,4,6)
+f5t6 <- f(0.5,0.6,5,6)
+f6t6 <- f(0.5,0.6,6,6)
+
+utilityt6 <- c(f0t6,f1t6,f2t6,f3t6,f4t6,f5t6,f6t6)
+concentrationt6 <- c(0:6)
+
+# print(utilityt8)
+plot(concentrationt6,utilityt6)
+
+```
+
+```{r emmeone, echo=FALSE, fig.cap="utility in Moore 8 patches; desired fraction 50%, M=1, Z=1"}
+
+f0m <- f(0.5,1,0,8)
+f1m <- f(0.5,1,1,8)
+f2m <- f(0.5,1,2,8)
+f3m <- f(0.5,1,3,8)
+f4m <- f(0.5,1,4,8)
+f5m <- f(0.5,1,5,8)
+f6m <- f(0.5,1,6,8)
+f7m <- f(0.5,1,7,8)
+f8m <- f(0.5,1,8,8)
+
+utility_Moore <- c(f0m,f1m,f2m,f3m,f4m,f5m,f6m,f7m,f8m)
+concentrationm <- c(0:8)
+
+# print(utilitym)
+plot(concentrationm,utility_Moore)
+```
+
+```{r emmezero, echo=FALSE, fig.cap="utility in Moore 8 patches; desired fraction 50%, M=0, Z=1"}
+
+f0m <- f(0.5,0,0,8)
+f1m <- f(0.5,0,1,8)
+f2m <- f(0.5,0,2,8)
+f3m <- f(0.5,0,3,8)
+f4m <- f(0.5,0,4,8)
+f5m <- f(0.5,0,5,8)
+f6m <- f(0.5,0,6,8)
+f7m <- f(0.5,0,7,8)
+f8m <- f(0.5,0,8,8)
+
+utility_Moore <- c(f0m,f1m,f2m,f3m,f4m,f5m,f6m,f7m,f8m)
+concentrationm <- c(0:8)
+
+# print(utilitym)
+plot(concentrationm,utility_Moore)
+```
+
+```{r vn, echo=FALSE, include=FALSE, fig.cap="utility in Von Neumann 4 patches; desired fraction 50%, M=0.6, Z=1"}
 
@@
 concentrationvn <- c(0:4)
+
+#print(utilityvn)
+plot(concentrationvn,utilityvn)
+
+```
+
+```{r R2,include=FALSE, echo=FALSE, fig.cap="utility in R2 12 patches; desired fraction 50%, M=0.6, Z=1"}
 
@@
 
-f0t8 <- f(0.5,0.6,0,8)
-f1t8 <- f(0.5,0.6,1,8)
-f2t8 <- f(0.5,0.6,2,8)
-f3t8 <- f(0.5,0.6,3,8)
-f4t8 <- f(0.5,0.6,4,8)
-f5t8 <- f(0.5,0.6,5,8)
-f6t8 <- f(0.5,0.6,6,8)
-f7t8 <- f(0.5,0.6,7,8)
-f8t8 <- f(0.5,0.6,8,8)
-
-utilityt8 <- c(f0t8,f1t8,f2t8,f3t8,f4t8,f5t8,f6t8,f7t8)
-concentrationt8 <- c(0:7)
-
-print(utilityvn)
-plot(concentrationvn,utilityvn)
-
-print(utilitym)
-plot(concentrationm,utilitym)
-
-print(utilityr2)
+#print(utilityr2)
 plot(concentrationr2,utilityr2)
 
-print(utilityt8)
+```
+
+```{r utzero, echo=FALSE, fig.cap="Results with desired fraction p = 0 in Moore neighborhood 8 patches, M=0.6 and Z=1"}
+
+f0t8 <- f(0,0.6,0,8)
+f1t8 <- f(0,0.6,1,8)
+f2t8 <- f(0,0.6,2,8)
+f3t8 <- f(0,0.6,3,8)
+f4t8 <- f(0,0.6,4,8)
+f5t8 <- f(0,0.6,5,8)
+f6t8 <- f(0,0.6,6,8)
+f7t8 <- f(0,0.6,7,8)
+f8t8 <- f(0,0.6,8,8)
+
+utilityt8 <- c(f0t8,f1t8,f2t8,f3t8,f4t8,f5t8,f6t8,f7t8,f8t8)
+concentrationt8 <- c(0:8)
+
+# print(utilityt8)
 plot(concentrationt8,utilityt8)
@@
 
-# Limits
+```{r integr, fig.pos='h' , out.widh = '100%', fig.aign='center', fig.cap="Even subgroups ethnicityXvalueXses (12,5% of population each), utility = 0, beta = 100, M = 0.6", echo=FALSE, include=TRUE}
 
-- Both $u$ and $\beta$ can vary across individuals, but the model would explode in its complexity
-- Even if we consider households as agents who make a choice, the decision to relocate can be the product of negotiation of people in that household. Too complicated to be included
+knitr::include_graphics("C:/Users/rocpa/OneDrive/Desktop/upload/integration_0.jpg")
+
+```
+
+# Doubts
+
+* It is still not very clear to me what you can get out of a regression model for what concerns utility.
+Some material I am reading describes dependent variable y as the probability to choose option x, and assumes this to be expression of the term utility quantified in beta coefficient times variable(characteristic) for each characteristic.
+But following @zhang2004, utility of the option made per se would be already the product of $\beta$ probability of choice * $u$ ideal payoff.
+I do not understand if it is possible to disentangle the two components from a regression, although intuitive cases come to mind (e.g.
+finding negative correlation between costs in @esser2010 and probability of choice).
+@borghans2015 use the deviance of betas related to difference within groups, which I understand how to connect to multinomial choice as differences in choice due to characteristics of people, but it is not to my doubt.
+It is how to disentangle utility in empirical terms which is not very clear to me, and how the modeling choice can be related to empirical data, or if I am overthinking on it.
+In  any case I would need to study more.
+
+* Some models as @zhang2004 and @bruch2006 put random utility models within Schelling's framework.
+As I understand so far there  are different components that collapse as multinomial choice, single-peaked function etc.
+In general they seems to me to fit within utility perspective, but it is not clear to me how much these utility models conceptually fit in @schelling1969 threshold model they cite or are innerly different.
+In my understanding a threshold model would not care about the left-slope of a single-peaked function, and utility would be constant as @bruch2006 also describes.
+There would be not consideration of (random) probabilities but prob = 1 once threshold is guaranteed, despite adding randomness, and not assessment of different options, as in the white flight.
+I think there is a difference conceptually and it should be marked.
+I also wonder how much a threshold model and utility models would differ when compared with empirical data and how they could be compared, which many abm paper do not focus on.
+I would like to study this as well, would make sense considering the ACS paper is a threshold model and now shifting to utility, but I think it would be beyond this paper.
+In general for my PhD I have to wite a paper of my onw.
 

### 2019-07-24 paper_notes.Rmd
uti 0, to simplify
Add files via upload

@@
 
-f <- function(p,M,x,n){
-  if (x  <= (n*p)){U <- (x/(n*p))}
-  else {U <- M + ((1-(x/n))*(1-M))/(1-p)}
+library(Hmisc)
+
+#old
+# f <- function(p,M,x,n){
+#  if (x  <= (n*p)){U <- (x/(n*p))}
+#  else {U <- M + ((1-(x/n))*(1-M))/(1-p)}
  # else {U <- (2-M) + (((M-1)*x)/(n*p))} M + ((1-(x/n))*(1-M))/(1-p)}
-  round(U,digits = 3)
- # print(U)
-}
+#  round(U,digits = 3)
+# }
+
+#f_dist <- function(o,ot,M,i,S){
+#  if (abs(o-ot) < i) {
+#    U <- (abs(o-ot)/i) * S
+#    }else if (abs(o-ot) > i){
+#      U <- M + ((1-abs(o-ot))*(1-M))/(1-i)
+#    }else{
+#        U <- 1}
+#  round(U,digits = 3)
+#  }
+
+#f_val <- function(o,ot,M,i,S){
+# if (round(abs(o-ot), digits=2) >= i) {
+#    U <- 1
+#  }else {
+#      U <- # (1 - (1-(abs(o-ot))/i) * S)
+#         1 -  (M + ((1-(1-abs(o-ot)))/(1-M))/(1-(1-i)))
+#       1 - (M + ((1-(1-abs(o-ot)))*(1-M))/(1-(1-i)))
+#    }
+#  round(U,digits = 3)
+#  }
+
+#f_val_repr <- function(sim,M,i,S){
+#  if (sim <= i) {
+#    U <- sim/i * S
+#     }else if (sim > i){
+# U <- M + ((1-sim)*(1-M))/(1-i)
+#    }else{
+#         U <- 1}
+#   round(U,digits = 3)
+#   }
 
@@
 ```
+
+```{r value_similarity, echo=FALSE, }
+
+f_val <- function(o,ot,M,i,S){
+  if (round(abs(o-ot), digits=2) <= i) {
+    U <- 1
+    }else{
+      U <- (M + ((1-(round(abs(o-ot), digits=2)))*(1-M))/(1-i)) * S
+    }
+  round(U,digits = 2)
+  }
+
+i <- 0.2
+S  <- 1
+M <- 0
+
+#  f_dist <- (o,ot,M,i,S)
+
+for (o in seq (0.0,1.0, by = 0.1)){
+
+fv0d2 <- f_val(o,0,M,i,S)
+fv1d2 <- f_val(o,0.1,M,i,S)
+fv2d2 <- f_val(o,0.2,M,i,S)
+fv3d2 <- f_val(o,0.3,M,i,S)
+fv4d2 <- f_val(o,0.4,M,i,S)
+fv5d2 <- f_val(o,0.5,M,i,S)
+fv6d2 <- f_val(o,0.6,M,i,S)
+fv7d2 <- f_val(o,0.7,M,i,S)
+fv8d2 <- f_val(o,0.8,M,i,S)
+fv9d2 <- f_val(o,0.9,M,i,S)
+fv10d2 <- f_val(o,1.0,M,i,S)
+
+value_mean_neighborhood <- seq(0.0, 1.0, by = 0.1)
+Utility_V <- c(fv0d2,fv1d2,fv2d2,fv3d2,fv4d2,fv5d2,fv6d2,fv7d2,fv8d2,fv9d2,fv10d2)
+name <- paste0("Ethnic weight i = ", o,";distance desired i = ",i,"; M = ",M,"; S = ",S)
+
+plot(value_mean_neighborhood,Utility_V, xlab = "Mean ethnic weight neighborhood j", ylab = "Value Utility",  main = "Value Utility for neighborhood j of agent i",  sub = name)
+
+report <- paste0("M = ",M," ??? S = ",S," ??? Ethnic weight i = ",o, " ??? desired distance i = ",i," ??? Mean ethnic weight j = ", seq(0.0, 1.0, by = 0.1), " ??? Utility ij = ", Utility_V)
+
+print(report)
+
+}
+
+```
+
 \newcommand{\rocco}[1]{\textcolor{red}{{Rocco:}#1}} <!-- <- this is a command to appear in pdf -->
 <!-- command not to appear in pdf -->
+
+```{ethnic utility, moore neighborhood}
+
+f_eth <- function(p,M,x,n,S){
+  if (x  < (n*p)){
+    U <- (x / (n*p)) * S
+    }else if (x > (n*p)){
+      U <- M + ((1-(x/n))*(1-M))/(1-p)
+    }else{
+        U <- 1}
+  round(U,digits = 2)
+}
+
+# f2 <- function(p,M,x,n,S)
+
+p = 0.5
+M = 1
+S = 1
+
+f0m <- f_eth(p,M,0,8,S)
+f1m <- f_eth(p,M,1,8,S)
+f2m <- f_eth(p,M,2,8,S)
+f3m <- f_eth(p,M,3,8,S)
+f4m <- f_eth(p,M,4,8,S)
+f5m <- f_eth(p,M,5,8,S)
+f6m <- f_eth(p,M,6,8,S)
+f7m <- f_eth(p,M,7,8,S)
+f8m <- f_eth(p,M,8,8,S)
+
+ethnic_concentration_neighborhood <- seq(0.0, 0.8, length.out = 9)
+Utility_E <- c(f0m,f1m,f2m,f3m,f4m,f5m,f6m,f7m,f8m)
+
+# print(utilitym)
+print(c("Ethnic Utility",Utility_E)) 
+plot(ethnic_concentration_neighborhood,Utility_E,title("Ethnic Utility"))
+
+```
+
+```{r testing logistic}
+
+prob <- function(l,s,t,d,p,q){1 / (1 + exp(-l*(s-t)) + exp(-d*(p-q)))}
+
+prob1 <- prob(100,300,100,1,100,100)
+plot(prob1)
+```
 
@@
 
-```{r moore, echo=FALSE, fig.cap="utility in Moore 8 patches; desired fraction 50%, M=0.6, Z=1"}
-
-f0m <- f(0.5,0.6,0,8)
-f1m <- f(0.5,0.6,1,8)
-f2m <- f(0.5,0.6,2,8)
-f3m <- f(0.5,0.6,3,8)
-f4m <- f(0.5,0.6,4,8)
-f5m <- f(0.5,0.6,5,8)
-f6m <- f(0.5,0.6,6,8)
-f7m <- f(0.5,0.6,7,8)
-f8m <- f(0.5,0.6,8,8)
-
-utility_Moore <- c(f0m,f1m,f2m,f3m,f4m,f5m,f6m,f7m,f8m)
-concentrationm <- c(0:8)
-
-# print(utilitym)
-plot(concentrationm,utility_Moore)
-```
-
 ```{r sechneg, echo=FALSE, fig.cap="utility in Moore 6 patches; desired fraction 50%, M=0.6, Z=1"}
 
-f0t6 <- f(0.5,0.6,0,6)
-f1t6 <- f(0.5,0.6,1,6)
-f2t6<- f(0.5,0.6,2,6)
-f3t6 <- f(0.5,0.6,3,6)
-f4t6 <- f(0.5,0.6,4,6)
-f5t6 <- f(0.5,0.6,5,6)
-f6t6 <- f(0.5,0.6,6,6)
+# f0t6 <- f(0.5,0.6,0,6)
+# f1t6 <- f(0.5,0.6,1,6)
+# f2t6<- f(0.5,0.6,2,6)
+# f3t6 <- f(0.5,0.6,3,6)
+# f4t6 <- f(0.5,0.6,4,6)
+# f5t6 <- f(0.5,0.6,5,6)
+# f6t6 <- f(0.5,0.6,6,6)
 
-utilityt6 <- c(f0t6,f1t6,f2t6,f3t6,f4t6,f5t6,f6t6)
-concentrationt6 <- c(0:6)
+# utilityt6 <- c(f0t6,f1t6,f2t6,f3t6,f4t6,f5t6,f6t6)
+# concentrationt6 <- c(0:6)
 
 # print(utilityt8)
-plot(concentrationt6,utilityt6)
+# plot(concentrationt6,utilityt6)
 
@@
 
-f0m <- f(0.5,1,0,8)
-f1m <- f(0.5,1,1,8)
-f2m <- f(0.5,1,2,8)
-f3m <- f(0.5,1,3,8)
-f4m <- f(0.5,1,4,8)
-f5m <- f(0.5,1,5,8)
-f6m <- f(0.5,1,6,8)
-f7m <- f(0.5,1,7,8)
-f8m <- f(0.5,1,8,8)
+# f0m <- f(0.5,1,0,8)
+# f1m <- f(0.5,1,1,8)
+# f2m <- f(0.5,1,2,8)
+# f3m <- f(0.5,1,3,8)
+# f4m <- f(0.5,1,4,8)
+# f5m <- f(0.5,1,5,8)
+# f6m <- f(0.5,1,6,8)
+# f7m <- f(0.5,1,7,8)
+# f8m <- f(0.5,1,8,8)
 
-utility_Moore <- c(f0m,f1m,f2m,f3m,f4m,f5m,f6m,f7m,f8m)
-concentrationm <- c(0:8)
+# utility_Moore <- c(f0m,f1m,f2m,f3m,f4m,f5m,f6m,f7m,f8m)
+# concentrationm <- c(0:8)
 
 # print(utilitym)
-plot(concentrationm,utility_Moore)
+# plot(concentrationm,utility_Moore)
 ```
@@
 
-f0m <- f(0.5,0,0,8)
-f1m <- f(0.5,0,1,8)
-f2m <- f(0.5,0,2,8)
-f3m <- f(0.5,0,3,8)
-f4m <- f(0.5,0,4,8)
-f5m <- f(0.5,0,5,8)
-f6m <- f(0.5,0,6,8)
-f7m <- f(0.5,0,7,8)
-f8m <- f(0.5,0,8,8)
+# f0m <- f(0.5,0,0,8)
+# f1m <- f(0.5,0,1,8)
+# f2m <- f(0.5,0,2,8)
+# f3m <- f(0.5,0,3,8)
+# f4m <- f(0.5,0,4,8)
+# f5m <- f(0.5,0,5,8)
+# f6m <- f(0.5,0,6,8)
+# f7m <- f(0.5,0,7,8)
+# f8m <- f(0.5,0,8,8)
 
-utility_Moore <- c(f0m,f1m,f2m,f3m,f4m,f5m,f6m,f7m,f8m)
-concentrationm <- c(0:8)
+# utility_Moore <- c(f0m,f1m,f2m,f3m,f4m,f5m,f6m,f7m,f8m)
+# concentrationm <- c(0:8)
 
 # print(utilitym)
-plot(concentrationm,utility_Moore)
+# plot(concentrationm,utility_Moore)
 ```
@@
 
-```{r integr, fig.pos='h' , out.widh = '100%', fig.aign='center', fig.cap="Even subgroups ethnicityXvalueXses (12,5% of population each), utility = 0, beta = 100, M = 0.6", echo=FALSE, include=TRUE}
-
-knitr::include_graphics("C:/Users/rocpa/OneDrive/Desktop/upload/integration_0.jpg")
-
-```
-
 # Doubts

### 2019-08-05 paper_notes.Rmd
Add files via upload

@@
 
-#old
-# f <- function(p,M,x,n){
-#  if (x  <= (n*p)){U <- (x/(n*p))}
-#  else {U <- M + ((1-(x/n))*(1-M))/(1-p)}
- # else {U <- (2-M) + (((M-1)*x)/(n*p))} M + ((1-(x/n))*(1-M))/(1-p)}
-#  round(U,digits = 3)
-# }
+# v_w <- 1 - e_w
 
-#f_dist <- function(o,ot,M,i,S){
-#  if (abs(o-ot) < i) {
-#    U <- (abs(o-ot)/i) * S
-#    }else if (abs(o-ot) > i){
-#      U <- M + ((1-abs(o-ot))*(1-M))/(1-i)
-#    }else{
-#        U <- 1}
-#  round(U,digits = 3)
-#  }
+f_eth <- function(i_e,M,x,n,S){
+  if (x > n){
+    U <- NA}else{
+  if (x < round(n*i_e,digits = 2)){
+   U <- (x / round((n*i_e),digits = 2)) * S
+    }else if (x > round((n*i_e),digits = 2)){
+      U <- M + ((1- round((x/n),digits = 2))*(1-M))/(1-i_e)
+    }else{
+        U <- 1}
+  round(U,digits = 2)
+    }
+}
 
-#f_val <- function(o,ot,M,i,S){
-# if (round(abs(o-ot), digits=2) >= i) {
-#    U <- 1
-#  }else {
-#      U <- # (1 - (1-(abs(o-ot))/i) * S)
-#         1 -  (M + ((1-(1-abs(o-ot)))/(1-M))/(1-(1-i)))
-#       1 - (M + ((1-(1-abs(o-ot)))*(1-M))/(1-(1-i)))
-#    }
-#  round(U,digits = 3)
-#  }
+f_val <- function(e_w,ew_ng,M,i_v,S){
+  if (round(abs(e_w-ew_ng), digits=2) <= i_v) {
+    U <- 1
+    }else{
+      U <- (M + ((1-(round(abs(e_w-ew_ng), digits=2)))*(1-M))/(1-i_v)) * S
+    }
+  round(U,digits = 2)
+}
 
-#f_val_repr <- function(sim,M,i,S){
-#  if (sim <= i) {
-#    U <- sim/i * S
-#     }else if (sim > i){
-# U <- M + ((1-sim)*(1-M))/(1-i)
-#    }else{
-#         U <- 1}
-#   round(U,digits = 3)
-#   }
+prob <- function(e_w,v_w,d_u_e,d_u_v){1 / (1 + exp(-e_w*(d_u_e)) + exp(-v_w*(d_u_v)))}
 
@@
 
-# library(namelibrary) for the R library
+```
 
-# http://rmarkdown.rstudio.com
-# echo = TRUE <- makes all next cmds appear
+```{r ethnic_utility, moore neighborhood}
 
+# f2 <- function(p,M,x,n,S)
+
+#i_e = 0.5
+M = 0
+S = 1
+n = 8
+
+for (i_e in seq (0.0,1.0, by = 0.1)){
+
+f0m <- f_eth(i_e,M,0,n,S)
+f1m <- f_eth(i_e,M,1,n,S)
+f2m <- f_eth(i_e,M,2,n,S)
+f3m <- f_eth(i_e,M,3,n,S)
+f4m <- f_eth(i_e,M,4,n,S)
+f5m <- f_eth(i_e,M,5,n,S)
+f6m <- f_eth(i_e,M,6,n,S)
+f7m <- f_eth(i_e,M,7,n,S)
+f8m <- f_eth(i_e,M,8,n,S)
+
+num_sim_col <- seq(0, 8, by = 1)
+Utility_E <- c(f0m,f1m,f2m,f3m,f4m,f5m,f6m,f7m,f8m)
+name_E <- paste0("Desired proportion i = ",i_e,"; M = ",M,"; S = ",S)
+
+plot(num_sim_col,Utility_E, xlab = "Similar ethnics neighborhood j", ylab = "Ethnic Utility",  main = "Ethnic Utility for neighborhood j of agent i",  sub = name_E)
+
+report_E <- paste0("M = ",M,"; S = ",S,"; Desired proportion i = ",i_e,"; Similar ethnics neighborhood j = ", seq(0, 8, by = 1), "; Utility ij = ", Utility_E)
+
+print(report_E)
+
+}
 ```
@@
 
-f_val <- function(o,ot,M,i,S){
-  if (round(abs(o-ot), digits=2) <= i) {
-    U <- 1
-    }else{
-      U <- (M + ((1-(round(abs(o-ot), digits=2)))*(1-M))/(1-i)) * S
-    }
-  round(U,digits = 2)
-  }
-
-i <- 0.2
+i_v <- 0
 S  <- 1
@@
 
-for (o in seq (0.0,1.0, by = 0.1)){
+for (e_w in seq (0.0,1.0, by = 0.1)){
 
-fv0d2 <- f_val(o,0,M,i,S)
-fv1d2 <- f_val(o,0.1,M,i,S)
-fv2d2 <- f_val(o,0.2,M,i,S)
-fv3d2 <- f_val(o,0.3,M,i,S)
-fv4d2 <- f_val(o,0.4,M,i,S)
-fv5d2 <- f_val(o,0.5,M,i,S)
-fv6d2 <- f_val(o,0.6,M,i,S)
-fv7d2 <- f_val(o,0.7,M,i,S)
-fv8d2 <- f_val(o,0.8,M,i,S)
-fv9d2 <- f_val(o,0.9,M,i,S)
-fv10d2 <- f_val(o,1.0,M,i,S)
+fv0d2 <- f_val(e_w,0,M,i_v,S)
+fv1d2 <- f_val(e_w,0.1,M,i_v,S)
+fv2d2 <- f_val(e_w,0.2,M,i_v,S)
+fv3d2 <- f_val(e_w,0.3,M,i_v,S)
+fv4d2 <- f_val(e_w,0.4,M,i_v,S)
+fv5d2 <- f_val(e_w,0.5,M,i_v,S)
+fv6d2 <- f_val(e_w,0.6,M,i_v,S)
+fv7d2 <- f_val(e_w,0.7,M,i_v,S)
+fv8d2 <- f_val(e_w,0.8,M,i_v,S)
+fv9d2 <- f_val(e_w,0.9,M,i_v,S)
+fv10d2 <- f_val(e_w,1.0,M,i_v,S)
 
@@
 Utility_V <- c(fv0d2,fv1d2,fv2d2,fv3d2,fv4d2,fv5d2,fv6d2,fv7d2,fv8d2,fv9d2,fv10d2)
-name <- paste0("Ethnic weight i = ", o,";distance desired i = ",i,"; M = ",M,"; S = ",S)
+name <- paste0("Ethnic weight i = ", e_w,"; desired distance i = ",i_v,"; M = ",M,"; S = ",S)
 
@@
 
-report <- paste0("M = ",M," ??? S = ",S," ??? Ethnic weight i = ",o, " ??? desired distance i = ",i," ??? Mean ethnic weight j = ", seq(0.0, 1.0, by = 0.1), " ??? Utility ij = ", Utility_V)
+report_v <- paste0(name,"; Mean ethnic weight j = ", seq(0.0, 1.0, by = 0.1), "; Utility ij = ", Utility_V)
 
-print(report)
+print(report_v)
 
@@
 
-```{ethnic utility, moore neighborhood}
-
-f_eth <- function(p,M,x,n,S){
-  if (x  < (n*p)){
-    U <- (x / (n*p)) * S
-    }else if (x > (n*p)){
-      U <- M + ((1-(x/n))*(1-M))/(1-p)
-    }else{
-        U <- 1}
-  round(U,digits = 2)
-}
-
-# f2 <- function(p,M,x,n,S)
-
-p = 0.5
-M = 1
-S = 1
-
-f0m <- f_eth(p,M,0,8,S)
-f1m <- f_eth(p,M,1,8,S)
-f2m <- f_eth(p,M,2,8,S)
-f3m <- f_eth(p,M,3,8,S)
-f4m <- f_eth(p,M,4,8,S)
-f5m <- f_eth(p,M,5,8,S)
-f6m <- f_eth(p,M,6,8,S)
-f7m <- f_eth(p,M,7,8,S)
-f8m <- f_eth(p,M,8,8,S)
-
-ethnic_concentration_neighborhood <- seq(0.0, 0.8, length.out = 9)
-Utility_E <- c(f0m,f1m,f2m,f3m,f4m,f5m,f6m,f7m,f8m)
-
-# print(utilitym)
-print(c("Ethnic Utility",Utility_E)) 
-plot(ethnic_concentration_neighborhood,Utility_E,title("Ethnic Utility"))
-
-```
-
 ```{r testing logistic}
 
-prob <- function(l,s,t,d,p,q){1 / (1 + exp(-l*(s-t)) + exp(-d*(p-q)))}
+# prob <- function(e_w,s,t,v_w,p,q){1 / (1 + exp(-e_w*(d_u_e)) + exp(-v_w*(d_u_v)))}
+
+# Make: foreach d_u_e [0-1], v_u_e spans within each [0-1]
 
 prob1 <- prob(100,300,100,1,100,100)
+
 plot(prob1)
@@
 
-```{r vn, echo=FALSE, include=FALSE, fig.cap="utility in Von Neumann 4 patches; desired fraction 50%, M=0.6, Z=1"}
-
-f0vn <- f(0.5,0.6,0,4)
-f1vn <- f(0.5,0.6,1,4)
-f2vn <- f(0.5,0.6,2,4)
-f3vn <- f(0.5,0.6,3,4)
-f4vn <- f(0.5,0.6,4,4)
-
-utilityvn <- c(f0vn,f1vn,f2vn,f3vn,f4vn)
-concentrationvn <- c(0:4)
-
-#print(utilityvn)
-plot(concentrationvn,utilityvn)
-
-```
-
-```{r R2,include=FALSE, echo=FALSE, fig.cap="utility in R2 12 patches; desired fraction 50%, M=0.6, Z=1"}
-
-f0r2 <- f(0.5,0.6,0,12)
-f1r2 <- f(0.5,0.6,1,12)
-f2r2 <- f(0.5,0.6,2,12)
-f3r2 <- f(0.5,0.6,3,12)
-f4r2 <- f(0.5,0.6,4,12)
-f5r2 <- f(0.5,0.6,5,12)
-f6r2 <- f(0.5,0.6,6,12)
-f7r2 <- f(0.5,0.6,7,12)
-f8r2 <- f(0.5,0.6,8,12)
-f9r2 <- f(0.5,0.6,9,12)
-f10r2 <- f(0.5,0.6,10,12)
-f11r2 <- f(0.5,0.6,11,12)
-f12r2 <- f(0.5,0.6,12,12)
-
-utilityr2 <- c(f0r2,f1r2,f2r2,f3r2,f4r2,f5r2,f6r2,f7r2,f8r2,f9r2,f10r2,f11r2,f12r2)
-concentrationr2 <- c(0:12)
-
-#print(utilityr2)
-plot(concentrationr2,utilityr2)
-
-```
-
-```{r utzero, echo=FALSE, fig.cap="Results with desired fraction p = 0 in Moore neighborhood 8 patches, M=0.6 and Z=1"}
-
-f0t8 <- f(0,0.6,0,8)
-f1t8 <- f(0,0.6,1,8)
-f2t8 <- f(0,0.6,2,8)
-f3t8 <- f(0,0.6,3,8)
-f4t8 <- f(0,0.6,4,8)
-f5t8 <- f(0,0.6,5,8)
-f6t8 <- f(0,0.6,6,8)
-f7t8 <- f(0,0.6,7,8)
-f8t8 <- f(0,0.6,8,8)
-
-utilityt8 <- c(f0t8,f1t8,f2t8,f3t8,f4t8,f5t8,f6t8,f7t8,f8t8)
-concentrationt8 <- c(0:8)
-
-# print(utilityt8)
-plot(concentrationt8,utilityt8)
-
-```
-
 # Doubts

### 2019-08-05 paper_notes.Rmd
OK logistic regression

@@
 }
-
-prob <- function(e_w,v_w,d_u_e,d_u_v){1 / (1 + exp(-e_w*(d_u_e)) + exp(-v_w*(d_u_v)))}
 
@@
 Utility_V <- c(fv0d2,fv1d2,fv2d2,fv3d2,fv4d2,fv5d2,fv6d2,fv7d2,fv8d2,fv9d2,fv10d2)
-name <- paste0("Ethnic weight i = ", e_w,"; desired distance i = ",i_v,"; M = ",M,"; S = ",S)
+name_V <- paste0("Ethnic weight i = ", e_w,"; desired distance i = ",i_v,"; M = ",M,"; S = ",S)
 
-plot(value_mean_neighborhood,Utility_V, xlab = "Mean ethnic weight neighborhood j", ylab = "Value Utility",  main = "Value Utility for neighborhood j of agent i",  sub = name)
+plot(value_mean_neighborhood,Utility_V, xlab = "Mean ethnic weight neighborhood j", ylab = "Value Utility",  main = "Value Utility for neighborhood j of agent i",  sub = name_V)
 
-report_v <- paste0(name,"; Mean ethnic weight j = ", seq(0.0, 1.0, by = 0.1), "; Utility ij = ", Utility_V)
+report_v <- paste0(name_V,"; Mean ethnic weight j = ", seq(0.0, 1.0, by = 0.1), "; Utility ij = ", Utility_V)
 
@@
 
-# prob <- function(e_w,s,t,v_w,p,q){1 / (1 + exp(-e_w*(d_u_e)) + exp(-v_w*(d_u_v)))}
+# prob <- function(e_w,v_w,d_u_e,d_u_v){1 / (1 + exp(-e_w*(d_u_e)) + exp(-v_w*(d_u_v)))}
 
@@
 
-prob1 <- prob(100,300,100,1,100,100)
+prob <- function(d_u_e,d_u_v,par_e,par_v){round(1 / (1 + exp(-par_e*(d_u_e) + (-par_v*(d_u_v)))),digits= 2)}
 
-plot(prob1)
+e_w <- 0.2
+v_w <- (1 - e_w)
+
+par_e <- 0
+par_v <- 10-par_e
+
+d_u_e <- -1
+
+  dis_0   <- prob(d_u_e,0.0,par_e,par_v)
+  dis_0.1 <- prob(d_u_e,0.1,par_e,par_v)
+  dis_0.2 <- prob(d_u_e,0.2,par_e,par_v)
+  dis_0.3 <- prob(d_u_e,0.3,par_e,par_v)
+  dis_0.4 <- prob(d_u_e,0.4,par_e,par_v)
+  dis_0.5 <- prob(d_u_e,0.5,par_e,par_v)
+  dis_0.6 <- prob(d_u_e,0.6,par_e,par_v)
+  dis_0.7 <- prob(d_u_e,0.7,par_e,par_v)
+  dis_0.8 <- prob(d_u_e,0.8,par_e,par_v)
+  dis_0.9 <- prob(d_u_e,0.9,par_e,par_v)
+  dis_1   <- prob(d_u_e,1.0,par_e,par_v)
+  dis_0.1neg <- prob(d_u_e,-0.1,par_e,par_v)
+  dis_0.2neg <- prob(d_u_e,-0.2,par_e,par_v)
+  dis_0.3neg <- prob(d_u_e,-0.3,par_e,par_v)
+  dis_0.4neg <- prob(d_u_e,-0.4,par_e,par_v)
+  dis_0.5neg <- prob(d_u_e,-0.5,par_e,par_v)
+  dis_0.6neg <- prob(d_u_e,-0.6,par_e,par_v)
+  dis_0.7neg <- prob(d_u_e,-0.7,par_e,par_v)
+  dis_0.8neg <- prob(d_u_e,-0.8,par_e,par_v)
+  dis_0.9neg <- prob(d_u_e,-0.9,par_e,par_v)
+  dis_1neg   <- prob(d_u_e,-1.0,par_e,par_v)
+
+  value_difference <- seq(-1.0,1.0, by = 0.1)
+  prob_choice <- c(dis_1neg,dis_0.9neg,dis_0.8neg,dis_0.7neg,dis_0.6neg,dis_0.5neg,dis_0.4neg,dis_0.3neg,dis_0.2neg,dis_0.1neg,dis_0,dis_0.1,dis_0.2,dis_0.3,dis_0.4,dis_0.5,dis_0.6,dis_0.7,dis_0.8,dis_0.9,dis_1)
+
+  name_diff <- paste0("Ethnic Difference New - Old = ",d_u_e,"Ethnic parameter = ", par_e, "Value parameter = ", par_v, 
+                      "\r\n Utility Difference -1 = MIN Utility Alternative, 1 = MAX Utility Alternative")
+
+plot(value_difference,prob_choice,xlab = "Value Difference Alternative - Current \r\n",ylab = "probability to choose alternative", main = "Probability to choose alternative", sub = name_diff)
+
 ```

### 2019-08-06 paper_notes.Rmd
updated 05_08
ok parameter for abm

--- 2019-08-05 paper_notes.Rmd
@@
 
-```{r testing logistic}
+```{r logistic putting as in abm ethnic_weight, value_weight}
 
-# prob <- function(e_w,s,t,v_w,p,q){1 / (1 + exp(-e_w*(d_u_e)) + exp(-v_w*(d_u_v)))}
+prob <- function(d_u_e,d_u_v,e_w,par_v){round(1 / (1 + exp(-(e_w*10)*(d_u_e) + (-(v_w*10)*(d_u_v)))),digits= 2)}
 
-# Make: foreach d_u_e [0-1], v_u_e spans within each [0-1]
+for (d_u_e in seq (-1.0,1.0, by = 0.1)){
 
-prob1 <- prob(100,300,100,1,100,100)
+e_w <- 0
+v_w <- 0
 
-plot(prob1)
+# d_u_e <- -1
+
+  dis_0   <- prob(d_u_e,0.0,e_w,v_w)
+dis_0.1 <- prob(d_u_e,0.1,e_w,v_w)
+dis_0.2 <- prob(d_u_e,0.2,e_w,v_w)
+dis_0.3 <- prob(d_u_e,0.3,e_w,v_w)
+dis_0.4 <- prob(d_u_e,0.4,e_w,v_w)
+dis_0.5 <- prob(d_u_e,0.5,e_w,v_w)
+dis_0.6 <- prob(d_u_e,0.6,e_w,v_w)
+dis_0.7 <- prob(d_u_e,0.7,e_w,v_w)
+dis_0.8 <- prob(d_u_e,0.8,e_w,v_w)
+dis_0.9 <- prob(d_u_e,0.9,e_w,v_w)
+dis_1   <- prob(d_u_e,1.0,e_w,v_w)
+dis_0.1neg <- prob(d_u_e,-0.1,e_w,v_w)
+dis_0.2neg <- prob(d_u_e,-0.2,e_w,v_w)
+dis_0.3neg <- prob(d_u_e,-0.3,e_w,v_w)
+dis_0.4neg <- prob(d_u_e,-0.4,e_w,v_w)
+dis_0.5neg <- prob(d_u_e,-0.5,e_w,v_w)
+dis_0.6neg <- prob(d_u_e,-0.6,e_w,v_w)
+dis_0.7neg <- prob(d_u_e,-0.7,e_w,v_w)
+dis_0.8neg <- prob(d_u_e,-0.8,e_w,v_w)
+dis_0.9neg <- prob(d_u_e,-0.9,e_w,v_w)
+dis_1neg   <- prob(d_u_e,-1.0,e_w,v_w)
+
+  value_difference <- seq(-1.0,1.0, by = 0.1)
+  prob_relocation <- seq(0.0, 1.0,  by = 0.1)
+
+  prob_choice <- c(dis_1neg,dis_0.9neg,dis_0.8neg,dis_0.7neg,dis_0.6neg,dis_0.5neg,dis_0.4neg,dis_0.3neg,dis_0.2neg,dis_0.1neg,dis_0,dis_0.1,dis_0.2,dis_0.3,dis_0.4,dis_0.5,dis_0.6,dis_0.7,dis_0.8,dis_0.9,dis_1)
+
+  name_diff <- paste0("Note: "," Ethnic parameter = ", e_w*10," ;"," Value parameter = ", v_w*10, 
+                      "\r\n Utility Difference -1 = MIN Utility Alternative, 1 = MAX Utility Alternative")
+
+  name_diff_title <-paste0("Probability to move to alternative","\r\n Difference Ethnic Utility (Alternative - Current) = ", d_u_e)
+
+plot(value_difference,prob_choice, xlab = "x-axis: Difference Value Utility (Alternative - Current) \r\n",ylab = "probability", main = name_diff_title, sub = name_diff,ylim = c(0,1), yaxt = 'n')
+axis(2,at=seq(0.0, 1.0, by = 0.25))
+
+}
+
+```
+
+```{r logistic in sequence, to test with parameters, to be deleted}
+
+prob <- function(d_u_e,d_u_v,par_e,par_v){round(1 / (1 + exp(-par_e*(d_u_e) + (-par_v*(d_u_v)))),digits= 2)}
+
+for (d_u_e in seq (-1.0,1.0, by = 0.1)){
+
+par_e <- 10
+par_v <- 10 - par_e
+
+# d_u_e <- -1
+
+  dis_0p   <- prob(d_u_e,0.0,par_e,par_v)
+dis_0.1p <- prob(d_u_e,0.1,par_e,par_v)
+dis_0.2p <- prob(d_u_e,0.2,par_e,par_v)
+dis_0.3p <- prob(d_u_e,0.3,par_e,par_v)
+dis_0.4p <- prob(d_u_e,0.4,par_e,par_v)
+dis_0.5p <- prob(d_u_e,0.5,par_e,par_v)
+dis_0.6p <- prob(d_u_e,0.6,par_e,par_v)
+dis_0.7p <- prob(d_u_e,0.7,par_e,par_v)
+dis_0.8p <- prob(d_u_e,0.8,par_e,par_v)
+dis_0.9p <- prob(d_u_e,0.9,par_e,par_v)
+dis_1p  <- prob(d_u_e,1.0,par_e,par_v)
+dis_0.1negp <- prob(d_u_e,-0.1,par_e,par_v)
+dis_0.2negp <- prob(d_u_e,-0.2,par_e,par_v)
+dis_0.3negp <- prob(d_u_e,-0.3,par_e,par_v)
+dis_0.4negp <- prob(d_u_e,-0.4,par_e,par_v)
+dis_0.5negp <- prob(d_u_e,-0.5,par_e,par_v)
+dis_0.6negp <- prob(d_u_e,-0.6,par_e,par_v)
+dis_0.7negp <- prob(d_u_e,-0.7,par_e,par_v)
+dis_0.8negp <- prob(d_u_e,-0.8,par_e,par_v)
+dis_0.9negp <- prob(d_u_e,-0.9,par_e,par_v)
+dis_1negp   <- prob(d_u_e,-1.0,par_e,par_v)
+
+  value_difference <- seq(-1.0,1.0, by = 0.1)
+  prob_relocation <- seq(0.0, 1.0,  by = 0.1)
+
+  prob_choicep <- c(dis_1negp,dis_0.9negp,dis_0.8negp,dis_0.7negp,dis_0.6negp,dis_0.5negp,dis_0.4negp,dis_0.3negp,dis_0.2negp,dis_0.1negp,dis_0p,dis_0.1p,dis_0.2p,dis_0.3p,dis_0.4p,dis_0.5p,dis_0.6p,dis_0.7p,dis_0.8p,dis_0.9p,dis_1p)
+
+  name_diff <- paste0("Note: "," Ethnic parameter = ", par_e," ;"," Value parameter = ", par_v, 
+                      "\r\n Utility Difference -1 = MIN Utility Alternative, 1 = MAX Utility Alternative")
+
+  name_diff_title <-paste0("Probability to move to alternative","\r\n Difference Ethnic Utility (Alternative - Current) = ", d_u_e)
+
+plot(value_difference,prob_choicep, xlab = "x-axis: Difference Value Utility (Alternative - Current) \r\n",ylab = "probability", main = name_diff_title, sub = name_diff,ylim = c(0,1), yaxt = 'n')
+axis(2,at=seq(0.0, 1.0, by = 0.25))
+
+}
+
 ```

### 2019-08-06 paper_notes.Rmd
implement in the abm

@@
 
+\newcommand{\rocco}[1]{\textcolor{red}{{Rocco:}#1}} <!-- <- this is a command to appear in pdf -->
+<!-- command not to appear in pdf -->
 ```{r setup, include=FALSE}
@@
 
-# v_w <- 1 - e_w
+# Here functions that are used.
+
+# Calculation ethnic utility (for each option)
 
@@
 
+# Calculation value utility (for each option)
+
 f_val <- function(e_w,ew_ng,M,i_v,S){
@@
 
+# Probability (random utility with logistic regression) to relocate
+
+prob <- function(d_u_e,d_u_v,e_w,par_v){round(1 / (1 + exp(-(e_w*10)*(d_u_e) + (-(v_w*10)*(d_u_v)))),digits= 2)}
+
 # install.packages("tinytex", repos = "https://cloud.r-project.org" ) if debug needed?
@@
 
-```{r ethnic_utility, moore neighborhood}
+Write down how the three types of functions (Zhang, Schelling, new -> symmetric, threshold, costant) can be built out of the parameters M and S. Make a graph
+
+Ethnic utility, separating ethnic_weight and ideal payoff for ethnicity (i_e) -> based on ethnicity of agents (color)
+The ethnic weight follows the beta distribution, *maybe* report Blitzstein 4 beta cases, and anyway considering ethnic_weight and value_weight are complementary
+
+```{r ethnic_utility, moore neighborhood, include=TRUE, echo=FALSE}
 
@@
 
+Value utility, based on agents' desired distance (i_v) between the agent's ethnic_weight (e_w) and neighborhood's average ethnic_weight (calculated out of agents residing there)
+Calculate ethnic weight average of neighborhoods with n agents > 0.
+
+ **check:** Explain how S and M vary for the constant function, the comment seems lost
+
 ```{r value_similarity, echo=FALSE, }
@@
 M <- 0
-
-#  f_dist <- (o,ot,M,i,S)
 
@@
 
-plot(value_mean_neighborhood,Utility_V, xlab = "Mean ethnic weight neighborhood j", ylab = "Value Utility",  main = "Value Utility for neighborhood j of agent i",  sub = name_V)
+plot(value_mean_neighborhood,Utility_V, xlab = "Mean ethnic weight neighborhood j", ylab = "Value Utility neighborhood j",  main = "Value Utility for neighborhood j of agent i",  sub = name_V)
 
@@
 
-\newcommand{\rocco}[1]{\textcolor{red}{{Rocco:}#1}} <!-- <- this is a command to appear in pdf -->
-<!-- command not to appear in pdf -->
+Once calculated the ethnic utility and value utility, apply prob above (logistic function) in the decision rule of the agent, with prob(to_new) >= random-float 0-1
 
@@
 
-prob <- function(d_u_e,d_u_v,e_w,par_v){round(1 / (1 + exp(-(e_w*10)*(d_u_e) + (-(v_w*10)*(d_u_v)))),digits= 2)}
-
 for (d_u_e in seq (-1.0,1.0, by = 0.1)){
 
-e_w <- 0
-v_w <- 0
+e_w <- 0.8
+v_w <- 1 - e_w
 

### 2019-08-07 paper_notes.Rmd
single run function

@@
 # Calculation ethnic utility (for each option)
+# i_e: ethnic threshold (ideal point)
+# M: right-side slope
+# x: number agents in neighborhood with same color
+# n: total number agents in neighborhood
+# S: left-side slope
+# Note: if (x > n){U <- NA} to show the case number of agents in neighborhood different from 8, so that utility is calculated based on this, although x-axis in graph has 8 points  (excluded from calculation)
 
@@
 The ethnic weight follows the beta distribution, *maybe* report Blitzstein 4 beta cases, and anyway considering ethnic_weight and value_weight are complementary
+
+Specify n > x <- U:NA in formula
+
+```{r ethnic utility individual-run include=TRUE, echo=FALSE}
+
+# f2 <- function(p,M,x,n,S)
+
+i_e = 0.5
+M = 0
+S = 1
+n = 8
+
+f0m <- f_eth(i_e,M,0,n,S)
+f1m <- f_eth(i_e,M,1,n,S)
+f2m <- f_eth(i_e,M,2,n,S)
+f3m <- f_eth(i_e,M,3,n,S)
+f4m <- f_eth(i_e,M,4,n,S)
+f5m <- f_eth(i_e,M,5,n,S)
+f6m <- f_eth(i_e,M,6,n,S)
+f7m <- f_eth(i_e,M,7,n,S)
+f8m <- f_eth(i_e,M,8,n,S)
+
+num_sim_col <- seq(0, 8, by = 1)
+Utility_E <- c(f0m,f1m,f2m,f3m,f4m,f5m,f6m,f7m,f8m)
+name_E <- paste0("Desired proportion i = ",i_e,"; M = ",M,"; S = ",S)
+
+plot(num_sim_col,Utility_E, xlab = "Similar ethnics neighborhood j", ylab = "Ethnic Utility",  main = "Ethnic Utility for neighborhood j of agent i",  sub = name_E)
+
+report_E <- paste0("M = ",M,"; S = ",S,"; Desired proportion i = ",i_e,"; Similar ethnics neighborhood j = ", seq(0, 8, by = 1), "; Utility ij = ", Utility_E)
+
+print(report_E)
+
+```
 

### 2019-08-08 paper_notes.Rmd
test utility added
added functions overlapping

@@
 library(Hmisc)
+library(ggplot2)
 
@@
 
+```{r graph function include=TRUE, echo=FALSE}
+
+# f2 <- function(p,M,x,n,S)
+
+i_e = 0.5
+M = 0
+S = 1
+n = 8
+
+f0s <- f_eth(i_e,M,0,n,S)
+f1s <- f_eth(i_e,M,1,n,S)
+f2s <- f_eth(i_e,M,2,n,S)
+f3s <- f_eth(i_e,M,3,n,S)
+f4s <- f_eth(i_e,M,4,n,S)
+f5s <- f_eth(i_e,M,5,n,S)
+f6s <- f_eth(i_e,M,6,n,S)
+f7s <- f_eth(i_e,M,7,n,S)
+f8s <- f_eth(i_e,M,8,n,S)
+
+i_e = 0.5
+M = 1
+S = 1
+n = 8
+
+f0c <- f_eth(i_e,M,0,n,S)
+f1c <- f_eth(i_e,M,1,n,S)
+f2c <- f_eth(i_e,M,2,n,S)
+f3c <- f_eth(i_e,M,3,n,S)
+f4c <- f_eth(i_e,M,4,n,S)
+f5c <- f_eth(i_e,M,5,n,S)
+f6c <- f_eth(i_e,M,6,n,S)
+f7c <- f_eth(i_e,M,7,n,S)
+f8c <- f_eth(i_e,M,8,n,S)
+
+i_e = 0.5
+M = 1
+S = 0
+n = 8
+
+f0t <- f_eth(i_e,M,0,n,S)
+f1t <- f_eth(i_e,M,1,n,S)
+f2t <- f_eth(i_e,M,2,n,S)
+f3t <- f_eth(i_e,M,3,n,S)
+f4t <- f_eth(i_e,M,4,n,S)
+f5t <- f_eth(i_e,M,5,n,S)
+f6t <- f_eth(i_e,M,6,n,S)
+f7t <- f_eth(i_e,M,7,n,S)
+f8t <- f_eth(i_e,M,8,n,S)
+
+Utility_S <- c(f0s,f1s,f2s,f3s,f4s,f5s,f6s,f7s,f8s)
+Utility_C <- c(f0c,f1c,f2c,f3c,f4c,f5c,f6c,f7c,f8c)
+Utility_T <- c(f0t,f1t,f2t,f3t,f4t,f5t,f6t,f7t,f8t)
+
+# name_E <- paste0("Desired proportion i = ",i_e,"; M = ",M,"; S = ",S)
+# plot(num_sim_col,Utility_T, xlab = "Similar ethnics neighborhood j", ylab = "Ethnic Utility",  main = "Ethnic Utility for neighborhood j of agent i",  sub = name_E)
+# report_E <- paste0("M = ",M,"; S = ",S,"; Desired proportion i = ",i_e,"; Similar ethnics neighborhood j = ", seq(0, 8, by = 1), "; Utility ij = ", Utility_T)
+# print(report_E)
+
+# func_type <- c(rep("symmetric",9),rep("constant",9),rep("threshold",9))
+
+x_graph <- rep(seq(0, 8, by = 1),3)
+funct_symm <- c(rep("symmetric",9),rep("constant",9),rep("threshold",9))
+utility_location <- c(Utility_S,Utility_C,Utility_T)
+
+A <- data.frame(x_graph,utility_location,funct_symm)
+
+A
+
+write.csv2(A,file="C:/Users/rocpa/OneDrive/Desktop/08_08_2019/ethnic-value_multinomial/data_utility")
+
+A_graph <- ggplot(A,aes(x_graph,utility_location))
+
+A_graph + geom_point(aes(colour = funct_symm, shape= funct_symm, size = funct_symm)) + scale_size_manual(values = c(4,5,3)) + scale_shape_manual(values = c(19,19,19)) + scale_color_manual(values = c("darkorchid","forestgreen","black"))
+
+```
+
+```{r overlap_function include=TRUE, echo=FALSE}
+
+x_graph_overlap <- rep(seq(0, 100, by = 12.5),4)
+
+S_0 <- c(0,0,0,0,0,NA,NA,NA,NA)
+M_1 <- c(NA,NA,NA,NA,1,1,1,1,1)
+S_1 <- c(0,0.25,0.5,0.75,1,NA,NA,NA,NA)
+M_0 <- c(NA,NA,NA,NA,1,0.76,0.5,0.24,0)  # should be 0.75 and 0.24, I think due to round(U)2 in the function
+
+funct_overlap <- c(rep("S = 0",9),rep("M = 1",9),rep("S = 1",9),rep("M = 0",9))
+utility_overlap <- c(S_0,M_1,S_1,M_0)
+
+overlap <- data.frame(x_graph_overlap,utility_overlap,funct_overlap)
+
+# overlap
+
+graph_overlap <- ggplot(overlap,aes(x_graph_overlap,utility_overlap))
+
+suppressWarnings(print(
+graph_overlap + geom_line(aes(colour = funct_overlap)) + scale_color_manual(values = c("red","forestgreen","black","purple"),name = "Parameters Setting") + theme_bw() + labs(x = "percentage similars",y = "utility for location")
+))
+
+```
+
 Ethnic utility, separating ethnic_weight and ideal payoff for ethnicity (i_e) -> based on ethnicity of agents (color)
@@
 S = 1
-n = 8
+n = 7
 

### 2019-08-09 paper_notes.Rmd
ok symmetric decreasing slope

@@
     }else if (x > round((n*i_e),digits = 2)){
-      U <- M + ((1- round((x/n),digits = 2))*(1-M))/(1-i_e)
+      U <- M + ((1- (x/n))*(1-M))/(1-i_e)   
     }else{
@@
 
-A <- data.frame(x_graph,utility_location,funct_symm)
+A <- data.frame(x_graph[c(0:9)],utility_location[c(0:9)],funct_symm[c(0:9)])
 
@@
 
-write.csv2(A,file="C:/Users/rocpa/OneDrive/Desktop/08_08_2019/ethnic-value_multinomial/data_utility")
+# write.csv2(A,file="C:/Users/rocpa/OneDrive/Desktop/08_08_2019/ethnic-value_multinomial/data_utility")
 
-A_graph <- ggplot(A,aes(x_graph,utility_location))
+A_graph <- ggplot(A,aes(x_graph[c(0:9)],utility_location[c(0:9)]))
+
+A_graph + geom_point()
 
@@
 S_1 <- c(0,0.25,0.5,0.75,1,NA,NA,NA,NA)
-M_0 <- c(NA,NA,NA,NA,1,0.76,0.5,0.24,0)  # should be 0.75 and 0.24, I think due to round(U)2 in the function
+M_0 <- c(NA,NA,NA,NA,1,0.75,0.5,0.25,0)  # should be 0.75 and 0.24, I think due to round(U)2 in the function
 
@@
 S = 1
-n = 7
+n = 8
 

### 2019-08-09 paper_notes.Rmd
test, ignore
3 functions plot in 1 page

@@
 library(ggplot2)
-
+library(gridExtra)
+library(ggpubr)
 # Here functions that are used.
@@
 
-```{r graph function include=TRUE, echo=FALSE}
+```{r graph function, include=TRUE, echo=FALSE}
 
@@
 
-x_graph <- rep(seq(0, 8, by = 1),3)
+x_graph <- rep(seq(0, 100, by = 12.5),3)
 funct_symm <- c(rep("symmetric",9),rep("constant",9),rep("threshold",9))
@@
 
-A <- data.frame(x_graph[c(0:9)],utility_location[c(0:9)],funct_symm[c(0:9)])
+symmetric <- data.frame(x_graph[c(0:9)],utility_location[c(0:9)],funct_symm[c(0:9)])
+constant <- data.frame(x_graph[c(10:18)],utility_location[c(10:18)],funct_symm[c(10:18)])
+threshold <- data.frame(x_graph[c(19:27)],utility_location[c(19:27)],funct_symm[c(19:27)])
 
-A
+# symmetric
+# constant
+# threshold
 
@@
 
-A_graph <- ggplot(A,aes(x_graph[c(0:9)],utility_location[c(0:9)]))
+symmetric_graph <- ggplot(symmetric,aes(x_graph[c(0:9)],utility_location[c(0:9)])) 
+constant_graph <- ggplot(constant,aes(x_graph[c(10:18)],utility_location[c(10:18)])) 
+threshold_graph <- ggplot(threshold,aes(x_graph[c(19:27)],utility_location[c(19:27)]))
 
-A_graph + geom_point()
+symmetric_plot <- symmetric_graph + geom_point() + theme_bw() + labs(x = "percentage similars",y = "utility for location") + ggtitle("Symmetric Single Peaked \n\r (S=1,M=0) ") + theme(plot.title = element_text(hjust = 0.5))
+constant_plot <- constant_graph + geom_point() + theme_bw() + labs(x = "percentage similars",y = "utility for location") + ggtitle("Linear + Constant \n\r (S=1,M=1)") + theme(plot.title = element_text(hjust = 0.5))
+threshold_plot <- threshold_graph + geom_point() + theme_bw() + labs(x = "percentage similars",y = "utility for location") + ggtitle("Schelling Threshold \n\r (S=0,M=1) ") + theme(plot.title = element_text(hjust = 0.5))
 
-A_graph + geom_point(aes(colour = funct_symm, shape= funct_symm, size = funct_symm)) + scale_size_manual(values = c(4,5,3)) + scale_shape_manual(values = c(19,19,19)) + scale_color_manual(values = c("darkorchid","forestgreen","black"))
+suppressWarnings(
+grid.arrange(symmetric_plot, constant_plot,threshold_plot, ncol= 2,nrow = 2)
+)
 
@@
 
-```{r overlap_function include=TRUE, echo=FALSE}
+```{r overlap_function, include=TRUE, echo=FALSE}
 
@@
 S_1 <- c(0,0.25,0.5,0.75,1,NA,NA,NA,NA)
-M_0 <- c(NA,NA,NA,NA,1,0.75,0.5,0.25,0)  # should be 0.75 and 0.24, I think due to round(U)2 in the function
+M_0 <- c(NA,NA,NA,NA,1,0.75,0.5,0.25,0)
 
@@
 
-```{r ethnic utility individual-run include=TRUE, echo=FALSE}
+```{r ethnic utility individual-run, include=TRUE, echo=FALSE}
 
@@
 
-```{r value_similarity, echo=FALSE, }
+```{r value_similarity, echo=FALSE }
 

### 2019-08-12 paper_notes.Rmd
Add files via upload

@@
 
-\newcommand{\rocco}[1]{\textcolor{red}{{Rocco:}#1}} <!-- <- this is a command to appear in pdf -->
-<!-- command not to appear in pdf -->
 ```{r setup, include=FALSE}
@@
 library(ggpubr)
+
 # Here functions that are used.
@@
 # i_e: ethnic threshold (ideal point)
-# M: right-side slope
+# M: right-side decreasing slope
 # x: number agents in neighborhood with same color
 # n: total number agents in neighborhood
-# S: left-side slope
+# S: left-side increasing slope
 # Note: if (x > n){U <- NA} to show the case number of agents in neighborhood different from 8, so that utility is calculated based on this, although x-axis in graph has 8 points  (excluded from calculation)
@@
 ```
+
+The basic idea is to introduce a beta distribution for $\beta$ in the utility definition of neighborhood $j$ for agent $i$ :
+
+$$
+U_{(xj,yj)}   = \beta_xx_j + \beta_yy_j + \epsilon_j
+$$
+
+With $\beta_x$ the importance of ethnic composition $x_j$ of neighborhood $j$ and $\beta_y$ its value composition $y_i$.
+
+To avoid confusion between parameter beta and beta distribution used in the simulation, $\beta_x$ is called ethnic weight (ew in R code), $\beta_y$ is called value weight (v_w in R code).
+
+We want to compare different type of functions, in particular to compare the single-peaked function as modeled by [@zhang2011, graphic p.
+174] with the Schelling's original threshold we also  used in the ACS paper, and a mixed one where utility increases until the ideal point as in Zhang, and remains constant at max.
+1 when the ethnic composition exceeds the ideal point.
+The last function comes from the idea that it can be a realistic scenario in people's relocation choice.
+
+To have all of the functions coming from the same computation and reduce as much, I modified @zhang2011's formula, assuming max Utility = 1 and introducing 2 parameters to the formula, as in the simulation:\par
+* $S[0,1]$, regulating the increasing left slope
+* $M[0,1]$, regulating the decreasing right slope (as in Zhang)
+
+$$
+U=
+\begin{cases}
+1, & \text{if} \ \frac{x}{n} = np, \\
+\frac{x}{np}\times S, & \text{if} \ x < np, \\
+M + ((1 - \frac{x}{n}) \times (1 - M)) / (1 - p), & \text{if} \ x > np
+\end{cases}
+$$
 
@@
 
-# symmetric
-# constant
-# threshold
+symmetric
+ constant
+ threshold
 
@@
 
-e_w <- 0.8
-v_w <- 1 - e_w
+e_w <- 1
+v_w <- 1-e_w
 

### 2019-08-12 paper_notes.Rmd
math notation Uet, add value

@@
 To have all of the functions coming from the same computation and reduce as much, I modified @zhang2011's formula, assuming max Utility = 1 and introducing 2 parameters to the formula, as in the simulation:\par
-* $S[0,1]$, regulating the increasing left slope
-* $M[0,1]$, regulating the decreasing right slope (as in Zhang)
+- $S[0,1]$, regulating the increasing left slope
+- $M[0,1]$, regulating the decreasing right slope (as in Zhang)
 
 $$
-U=
+U_e=
 \begin{cases}
-1, & \text{if} \ \frac{x}{n} = np, \\
-\frac{x}{np}\times S, & \text{if} \ x < np, \\
-M + ((1 - \frac{x}{n}) \times (1 - M)) / (1 - p), & \text{if} \ x > np
+1, & \text{if} \ x = n\times i_e, \\
+(\frac{x}{n \times i_e})\times S, & \text{if} \ x < n\times i_e, \\
+M + ((1 - \frac{x}{n}) \times (1 - M)) / (1 - i_e), & \text{if} \ x > n\times i_e 
 \end{cases}
@@
 
-Write down how the three types of functions (Zhang, Schelling, new -> symmetric, threshold, costant) can be built out of the parameters M and S. Make a graph
+Where: \par
+- $U_e$: Ethnic utility
+- $x$: number of similar agents in the neighborhood
+- $n$: total number of agents in the neighborhood
+- $i_e$: desired ethnic composition
 
-```{r graph function, include=TRUE, echo=FALSE}
+Below example of the three functions, reporting how $S$ and $M$ are set to calculate them.
+The example refer to desired compostion $50\%$ ($i_e = 0.5$).
+It was calculated out of a 8 agents neighborhood (with 4 agents of same ethnicity representing the $50 \%$)
+
+```{r ethnic graph function, include=TRUE, echo=FALSE}
 
@@
 
-symmetric
- constant
- threshold
-
-# write.csv2(A,file="C:/Users/rocpa/OneDrive/Desktop/08_08_2019/ethnic-value_multinomial/data_utility")
+# symmetric
+# constant
+# threshold
 
@@
 
-```{r overlap_function, include=TRUE, echo=FALSE}
+*DOUBT*: for the value composition, have a distribution of opinions/beliefs for agents within ethnic groups, the value weight would be still  1 - e_w, and a parameter of how similar others are considered based on how they distantiate from the own opinion.
+This would be a comparison to Schelling's definition of similarity based on twofold, exhaustive and exclusive category (i.e.
+ethnicity), but rather on an cross-categorical, individual and constructed definition of similarity/desirability, and how important it is.
 
-x_graph_overlap <- rep(seq(0, 100, by = 12.5),4)
+```{r value graph function, include=TRUE, echo=FALSE}
 
-S_0 <- c(0,0,0,0,0,NA,NA,NA,NA)
-M_1 <- c(NA,NA,NA,NA,1,1,1,1,1)
-S_1 <- c(0,0.25,0.5,0.75,1,NA,NA,NA,NA)
-M_0 <- c(NA,NA,NA,NA,1,0.75,0.5,0.25,0)
+# f_val <- function(e_w,ew_ng,M,i_v,S)
 
-funct_overlap <- c(rep("S = 0",9),rep("M = 1",9),rep("S = 1",9),rep("M = 0",9))
-utility_overlap <- c(S_0,M_1,S_1,M_0)
-
-overlap <- data.frame(x_graph_overlap,utility_overlap,funct_overlap)
-
-# overlap
-
-graph_overlap <- ggplot(overlap,aes(x_graph_overlap,utility_overlap))
-
-suppressWarnings(print(
-graph_overlap + geom_line(aes(colour = funct_overlap)) + scale_color_manual(values = c("red","forestgreen","black","purple"),name = "Parameters Setting") + theme_bw() + labs(x = "percentage similars",y = "utility for location")
-))
+e_w <-
+e_w_ng <- 
+i_v <- 
+M <- 
+S <-
 
@@
 
-i_v <- 0
-S  <- 1
-M <- 0
+i_v <- 0.2
+S  <- 0
+M <- 1
 
@@
 
-# Doubts
+I think for a paper would be worth it to show how the three functions can overlap due to setting, something like this
+```{r overlap_function, include=TRUE, echo=FALSE}
 
-* It is still not very clear to me what you can get out of a regression model for what concerns utility.
-Some material I am reading describes dependent variable y as the probability to choose option x, and assumes this to be expression of the term utility quantified in beta coefficient times variable(characteristic) for each characteristic.
-But following @zhang2004, utility of the option made per se would be already the product of $\beta$ probability of choice * $u$ ideal payoff.
-I do not understand if it is possible to disentangle the two components from a regression, although intuitive cases come to mind (e.g.
-finding negative correlation between costs in @esser2010 and probability of choice).
-@borghans2015 use the deviance of betas related to difference within groups, which I understand how to connect to multinomial choice as differences in choice due to characteristics of people, but it is not to my doubt.
-It is how to disentangle utility in empirical terms which is not very clear to me, and how the modeling choice can be related to empirical data, or if I am overthinking on it.
-In  any case I would need to study more.
+x_graph_overlap <- rep(seq(0, 100, by = 12.5),4)
 
-* Some models as @zhang2004 and @bruch2006 put random utility models within Schelling's framework.
-As I understand so far there  are different components that collapse as multinomial choice, single-peaked function etc.
-In general they seems to me to fit within utility perspective, but it is not clear to me how much these utility models conceptually fit in @schelling1969 threshold model they cite or are innerly different.
-In my understanding a threshold model would not care about the left-slope of a single-peaked function, and utility would be constant as @bruch2006 also describes.
-There would be not consideration of (random) probabilities but prob = 1 once threshold is guaranteed, despite adding randomness, and not assessment of different options, as in the white flight.
-I think there is a difference conceptually and it should be marked.
-I also wonder how much a threshold model and utility models would differ when compared with empirical data and how they could be compared, which many abm paper do not focus on.
-I would like to study this as well, would make sense considering the ACS paper is a threshold model and now shifting to utility, but I think it would be beyond this paper.
-In general for my PhD I have to wite a paper of my onw.
+S_0 <- c(0,0,0,0,0,NA,NA,NA,NA)
+M_1 <- c(NA,NA,NA,NA,1,1,1,1,1)
+S_1 <- c(0,0.25,0.5,0.75,1,NA,NA,NA,NA)
+M_0 <- c(NA,NA,NA,NA,1,0.75,0.5,0.25,0)
+
+funct_overlap <- c(rep("S = 0",9),rep("M = 1",9),rep("S = 1",9),rep("M = 0",9))
+utility_overlap <- c(S_0,M_1,S_1,M_0)
+
+overlap <- data.frame(x_graph_overlap,utility_overlap,funct_overlap)
+
+# overlap
+
+graph_overlap <- ggplot(overlap,aes(x_graph_overlap,utility_overlap))
+
+suppressWarnings(print(
+graph_overlap + geom_line(aes(colour = funct_overlap)) + scale_color_manual(values = c("red","forestgreen","black","purple"),name = "Parameters Setting") + theme_bw() + labs(x = "percentage similars",y = "utility for location")
+))
+
+```
 

### 2019-08-15 paper_notes.Rmd
Add files via upload

@@
 
-e_w <-
-e_w_ng <- 
-i_v <- 
-M <- 
-S <-
+e_w <- 0.2
+e_w_ng <- seq(0.0,1.0, by = 0.1)
+i_v <- 0.1
+S <- 1
+M <- 0
+
+fvf0p  <- f_val(e_w,0,M,i_v,S)
+fvf1p  <- f_val(e_w,0.1,M,i_v,S)
+fvf2p   <- f_val(e_w,0.2,M,i_v,S)
+fvf3p   <- f_val(e_w,0.3,M,i_v,S)
+fvf4p   <- f_val(e_w,0.4,M,i_v,S)
+fvf5p   <- f_val(e_w,0.5,M,i_v,S)
+fvf6p   <- f_val(e_w,0.6,M,i_v,S)
+fvf7p   <- f_val(e_w,0.7,M,i_v,S)
+fvf8p   <- f_val(e_w,0.8,M,i_v,S)
+fvf9p  <- f_val(e_w,0.9,M,i_v,S)
+fvf10p  <- f_val(e_w,1.0,M,i_v,S)
+
+e_w <- 0.2
+e_w_ng <- seq(0.0,1.0, by = 0.1)
+i_v <- 0.1
+S <- 0
+M <- 1
+
+fvf0t <- f_val(e_w,0,M,i_v,S)
+fvf1t  <- f_val(e_w,0.1,M,i_v,S)
+fvf2t   <- f_val(e_w,0.2,M,i_v,S)
+fvf3t   <- f_val(e_w,0.3,M,i_v,S)
+fvf4t   <- f_val(e_w,0.4,M,i_v,S)
+fvf5t   <- f_val(e_w,0.5,M,i_v,S)
+fvf6t  <- f_val(e_w,0.6,M,i_v,S)
+fvf7t   <- f_val(e_w,0.7,M,i_v,S)
+fvf8t   <- f_val(e_w,0.8,M,i_v,S)
+fvf9t  <- f_val(e_w,0.9,M,i_v,S)
+fvf10t  <- f_val(e_w,1.0,M,i_v,S)
+
+x_graph_val <- seq(0.0,1.0, by = 0.1) #rep(seq(0.0,1.0, by = 0.1),2)
+uti_val_pf <- c(fvf0p,fvf1p,fvf2p,fvf3p,fvf4p,fvf5p,fvf6p,fvf7p,fvf8p,fvf9p,fvf10p)
+uti_val_th <- c(fvf0t,fvf1t,fvf2t,fvf3t,fvf4t,fvf5t,fvf6t,fvf7t,fvf8t,fvf9t,fvf10t)
+
+symm_val <- data.frame(x_graph_val,uti_val_pf)
+threshold_val <- data.frame(x_graph_val,uti_val_th)
+
+# funct_symm_v <- c(rep("symmetric",9),rep("threshold",9))
+
+symm_val_graph <- ggplot(symm_val,aes(x_graph_val,uti_val_pf))
+thres_val_graph <- ggplot(threshold_val,aes(x_graph_val,uti_val_th))
+
+symm_val_plot <- symm_val_graph + geom_point() + theme_bw() + labs(x = "Mean ethnic weight neighborhood j",y = "utility for location") + ggtitle(label = "Symmetric Single Peaked \n\r (S=1,M=0) ",subtitle = "desired distance = 0.2") + theme(plot.title = element_text(hjust = 0.5), plot.subtitle = element_text(hjust = 0.5))  + scale_x_continuous(breaks = seq(0.0,1.0,by = 0.1))
+
+thres_val_plot <- thres_val_graph + geom_point() + theme_bw() + labs(x = "Mean ethnic weight neighborhood j",y = "utility for location") + ggtitle(label = "Threshold Schelling \n\r (S=0,M=1) ",subtitle = "desired distance = 0.2") + theme(plot.title = element_text(hjust = 0.5), plot.subtitle = element_text(hjust = 0.5))  + scale_x_continuous(breaks = seq(0.0,1.0,by = 0.1))
+
+# symm_val_plot
+# thres_val_plot
+
+suppressWarnings(
+grid.arrange(symm_val_plot, thres_val_plot, ncol= 2,nrow = 2)
+)
 

### 2019-08-15 paper_notes.Rmd
OK formula

@@
     U <- (x / round((n*i_e),digits = 2)) * S
-    }else if (x > round((n*i_e),digits = 2)){
+     }else {
        U <- M + ((1- (x/n))*(1-M))/(1-i_e)   
-    }else{
-        U <- 1}
+     }
    round(U,digits = 2)
@@
  }
+
+# f_val <- function(e_w,ew_ng,M,i_v,S){
+#   if (round(abs(e_w-ew_ng), digits=2) < i_v) {
+#     U <- 1
+#     }else{
+#       U <- (M + ((1-(round(abs(e_w-ew_ng), digits=2)))*(1-M))/(1-i_v)) * S
+#     }
+#   round(U,digits = 2)
+# }
 
@@
 \begin{cases}
-1, & \text{if} \ x = n\times i_e, \\
 (\frac{x}{n \times i_e})\times S, & \text{if} \ x < n\times i_e, \\
-M + ((1 - \frac{x}{n}) \times (1 - M)) / (1 - i_e), & \text{if} \ x > n\times i_e 
+M + \frac{(1 - \frac{x}{n}) \times (1 - M)}{1 - i_e}, & \text{if} \ x \geq n\times i_e 
 \end{cases}
@@
 
+$$
+U_v=
+\begin{cases}
+1, & \text{if} \ e_w \leq i_v, \\
+\left(M + \frac{(1 - \mid{\overline{ew}_j - ew_i}\mid) \times (1 - M)}{1 - i_v}\right) \times S, & otherwise
+\end{cases}
+$$
+
 *DOUBT*: for the value composition, have a distribution of opinions/beliefs for agents within ethnic groups, the value weight would be still  1 - e_w, and a parameter of how similar others are considered based on how they distantiate from the own opinion.
@@
 S <- 0
-M <- 1
+M <- 0 #M can be either 0 or 1, M = 0 is for declining slope, M = 1 keeps utility = 1 for values out of range, so S = 0 keeps  the threshold  with values out of the distance equal 0
 
@@
 
-symm_val_plot <- symm_val_graph + geom_point() + theme_bw() + labs(x = "Mean ethnic weight neighborhood j",y = "utility for location") + ggtitle(label = "Symmetric Single Peaked \n\r (S=1,M=0) ",subtitle = "desired distance = 0.2") + theme(plot.title = element_text(hjust = 0.5), plot.subtitle = element_text(hjust = 0.5))  + scale_x_continuous(breaks = seq(0.0,1.0,by = 0.1))
+subt_cont <- paste0("desired distance = ",i_v)
 
-thres_val_plot <- thres_val_graph + geom_point() + theme_bw() + labs(x = "Mean ethnic weight neighborhood j",y = "utility for location") + ggtitle(label = "Threshold Schelling \n\r (S=0,M=1) ",subtitle = "desired distance = 0.2") + theme(plot.title = element_text(hjust = 0.5), plot.subtitle = element_text(hjust = 0.5))  + scale_x_continuous(breaks = seq(0.0,1.0,by = 0.1))
+symm_val_plot <- symm_val_graph + geom_point() + theme_bw() + labs(x = "Mean ethnic weight neighborhood j",y = "utility for location") + ggtitle(label = "Symmetric Single Peaked \n\r (S=1,M=0) ",subtitle = subt_cont) + theme(plot.title = element_text(hjust = 0.5), plot.subtitle = element_text(hjust = 0.5))  + scale_x_continuous(breaks = seq(0.0,1.0,by = 0.1))
+
+thres_val_plot <- thres_val_graph + geom_point() + theme_bw() + labs(x = "Mean ethnic weight neighborhood j",y = "utility for location") + ggtitle(label = "Threshold Schelling \n\r (S=0,M=1) ",subtitle = subt_cont) + theme(plot.title = element_text(hjust = 0.5), plot.subtitle = element_text(hjust = 0.5))  + scale_x_continuous(breaks = seq(0.0,1.0,by = 0.1))
 
@@
 
-i_e = 0.5
-M = 0
-S = 1
-n = 7
+i_e = 0.7
+M = 1
+S = 0
+n = 8
 
@@
 
-i_v <- 0.2
-S  <- 0
-M <- 1
+i_v <- 0.1
+S  <- 1
+M <- 0 #different values  of M do change results, even for M < 1
 

### 2019-08-15 paper_notes.Rmd
Update paper_notes.Rmd

@@
 bibliography: "references.bib"
+# target: BIGSSS Research Day by September 15th, presented  on October 25th. 6000 words: around 12 pages.
 # csl: apa.csl # by default: Chicago style

### 2019-08-15 paper_notes.Rmd
OK editable

@@
 
+install.packages("tinytex", repos = "https://cloud.r-project.org" )
+
+library(knitr)
 library(Hmisc)
@@
 library(ggpubr)
-
+# library(kableExtra)
+library(dplyr)
+library(grid)
 # Here functions that are used.
@@
 
-# f_val <- function(e_w,ew_ng,M,i_v,S){
-#   if (round(abs(e_w-ew_ng), digits=2) < i_v) {
-#     U <- 1
-#     }else{
-#       U <- (M + ((1-(round(abs(e_w-ew_ng), digits=2)))*(1-M))/(1-i_v)) * S
-#     }
-#   round(U,digits = 2)
-# }
-
 # Probability (random utility with logistic regression) to relocate
@@
 $$
-U_{(xj,yj)}   = \beta_xx_j + \beta_yy_j + \epsilon_j
+U^i_{(ej,yj)}   = \beta_xe_j + \beta_yv_j + \epsilon_j
 $$
@@
 
+# Ethnic Utility {-}
+
 $$
-U_e=
+U^i_e=
 \begin{cases}
 (\frac{x}{n \times i_e})\times S, & \text{if} \ x < n\times i_e, \\
+\\
 M + \frac{(1 - \frac{x}{n}) \times (1 - M)}{1 - i_e}, & \text{if} \ x \geq n\times i_e 
@@
 Where: \par
-- $U_e$: Ethnic utility
+- $U^i_e$: Ethnic utility of agent i
 - $x$: number of similar agents in the neighborhood
@@
 
-```{r ethnic graph function, include=TRUE, echo=FALSE}
+```{r ethnic graph function, fig.width=6,fig.height= 8, fig.align="center",  include=TRUE, echo=FALSE}
 
@@
 
-symmetric_plot <- symmetric_graph + geom_point() + theme_bw() + labs(x = "percentage similars",y = "utility for location") + ggtitle("Symmetric Single Peaked \n\r (S=1,M=0) ") + theme(plot.title = element_text(hjust = 0.5))
-constant_plot <- constant_graph + geom_point() + theme_bw() + labs(x = "percentage similars",y = "utility for location") + ggtitle("Linear + Constant \n\r (S=1,M=1)") + theme(plot.title = element_text(hjust = 0.5))
-threshold_plot <- threshold_graph + geom_point() + theme_bw() + labs(x = "percentage similars",y = "utility for location") + ggtitle("Schelling Threshold \n\r (S=0,M=1) ") + theme(plot.title = element_text(hjust = 0.5))
+subt_cont_e <- paste0("Desired proportion i = ",i_e)
+
+symmetric_plot <- symmetric_graph + geom_point() + theme_bw() + labs(x = "percentage similars",y = "Ethnic Utility j") + ggtitle("Symmetric Single Peaked (S=1,M=0) ",subtitle = subt_cont_e) + theme(plot.title = element_text(hjust = 0.5), plot.subtitle = element_text(hjust = 0.5)) + scale_y_continuous(limits =  c(0.0,1.0), breaks = seq(0.0,1.0,by = 0.25))
+constant_plot <- constant_graph + geom_point() + theme_bw() + labs(x = "percentage similars",y = "Ethnic Utility j") + ggtitle("Linear + Constant (S=1,M=1)",subtitle = subt_cont_e) + theme(plot.title = element_text(hjust = 0.5), plot.subtitle = element_text(hjust = 0.5)) + scale_y_continuous(limits =  c(0.0,1.0), breaks = seq(0.0,1.0,by = 0.25))
+threshold_plot <- threshold_graph + geom_point() + theme_bw() + labs(x = "percentage similars",y = "Ethnic Utility j") + ggtitle("Schelling Threshold (S=0,M=1)",subtitle = subt_cont_e) + theme(plot.title = element_text(hjust = 0.5), plot.subtitle = element_text(hjust = 0.5)) + scale_y_continuous(limits =  c(0.0,1.0), breaks = seq(0.0,1.0,by = 0.25))
 
 suppressWarnings(
-grid.arrange(symmetric_plot, constant_plot,threshold_plot, ncol= 2,nrow = 2)
+grid.arrange(symmetric_plot, constant_plot,threshold_plot, bottom = "Comparison of the three functions for ethnic utility of a neighborhood j")
 )
@@
 
+# Value Utility {-}
+
 $$
-U_v=
+U^i_v=
 \begin{cases}
 1, & \text{if} \ e_w \leq i_v, \\
+\\
 \left(M + \frac{(1 - \mid{\overline{ew}_j - ew_i}\mid) \times (1 - M)}{1 - i_v}\right) \times S, & otherwise
@@
 $$
+
+Where: \par
+- $U^i_v$: Ethnic utility of agent i
+- $\overline{ew}_j$: average ethnic weight in neighborhood \textit{j}
+- $ew_i$: ethnic weight of agent \textit{i}
+- $i_e$: desired ethnic composition
 
@@
 
-```{r value graph function, include=TRUE, echo=FALSE}
+```{r value graph function, fig.width=5,fig.height= 6, fig.align="center", include=TRUE, echo=FALSE}
 
@@
 M <- 0 #M can be either 0 or 1, M = 0 is for declining slope, M = 1 keeps utility = 1 for values out of range, so S = 0 keeps  the threshold  with values out of the distance equal 0
+# M regulates the right side of the slope, S the left side of the slope
 
@@
 
-subt_cont <- paste0("desired distance = ",i_v)
+subt_cont_v <- paste0("Ethnic weight i = ",e_w,"; ","Desired distance = ",i_v)
 
-symm_val_plot <- symm_val_graph + geom_point() + theme_bw() + labs(x = "Mean ethnic weight neighborhood j",y = "utility for location") + ggtitle(label = "Symmetric Single Peaked \n\r (S=1,M=0) ",subtitle = subt_cont) + theme(plot.title = element_text(hjust = 0.5), plot.subtitle = element_text(hjust = 0.5))  + scale_x_continuous(breaks = seq(0.0,1.0,by = 0.1))
+symm_val_plot <- symm_val_graph + geom_point() + theme_bw() + labs(x = "Mean ethnic weight neighborhood j",y = "Value utility j") + ggtitle(label = "Symmetric Single Peaked (S=1,M=0) ",subtitle = subt_cont_v) + theme(plot.title = element_text(hjust = 0.5), plot.subtitle = element_text(hjust = 0.5))  + scale_x_continuous(breaks = seq(0.0,1.0,by = 0.1)) + scale_y_continuous(limits =  c(0.0,1.0), breaks = seq(0.0,1.0,by = 0.25))
 
-thres_val_plot <- thres_val_graph + geom_point() + theme_bw() + labs(x = "Mean ethnic weight neighborhood j",y = "utility for location") + ggtitle(label = "Threshold Schelling \n\r (S=0,M=1) ",subtitle = subt_cont) + theme(plot.title = element_text(hjust = 0.5), plot.subtitle = element_text(hjust = 0.5))  + scale_x_continuous(breaks = seq(0.0,1.0,by = 0.1))
+thres_val_plot <- thres_val_graph + geom_point() + theme_bw() + labs(x = "Mean ethnic weight neighborhood j",y = "Value utility j") + ggtitle(label = "Threshold Schelling (S=0) ",subtitle = subt_cont_v) + theme(plot.title = element_text(hjust = 0.5), plot.subtitle = element_text(hjust = 0.5))  + scale_x_continuous(breaks = seq(0.0,1.0,by = 0.1)) + scale_y_continuous(limits =  c(0.0,1.0), breaks = seq(0.0,1.0,by = 0.25))
 
@@
 suppressWarnings(
-grid.arrange(symm_val_plot, thres_val_plot, ncol= 2,nrow = 2)
+grid.arrange(symm_val_plot, thres_val_plot, bottom = "Comparison of the two functions for value utility of a neighborhood j.")
 )
@@
 
-```{r ethnic utility individual-run, include=TRUE, echo=FALSE}
+```{r ethnic utility individual-run,fig.align="center", fig.pos="H", include=TRUE, echo=FALSE}
 
@@
 
-i_e = 0.7
+i_e = 0.3
 M = 1
 S = 0
-n = 8
+n = 7
 
@@
 
-report_E <- paste0("M = ",M,"; S = ",S,"; Desired proportion i = ",i_e,"; Similar ethnics neighborhood j = ", seq(0, 8, by = 1), "; Utility ij = ", Utility_E)
+#report_E <- paste0("M = ",M,"; S = ",S,"; Desired proportion i = ",i_e,"; Similar ethnics neighborhood j = ", seq(0, 8, by = 1), "; Utility ij = ", Utility_E)
 
-print(report_E)
+M. <- rep(M,9)
+S. <- rep(S,9)
+prop_des <- rep(i_e,9)
+num_tot <- rep(n,9)
+num_sim <- seq(0, 8, by = 1)
+
+report_E <- data.frame(M.,S.,prop_des,num_tot,num_sim,Utility_E)
+
+knitr::kable(report_E,align="c") # much better printed visualization
 

### 2019-08-16 paper_notes.Rmd
improved graphs

@@
 library(grid)
+library(ggrepel)
 # Here functions that are used.
@@
 
+ #  f_eth <- function(i_e,M,x,n,S){
+  #   if (x > n){
+  #     U <- NA}else{
+ #   if (x < round(n*i_e,digits = 2)){
+  #    U <- (x / round((n*i_e),digits = 2)) * S
+ #      }else {
+ #      U <- M + ((1- (x/n))*(1-M))/(1-i_e)   
+  #    }
+#     round(U,digits = 2)
+ #      }
+#   }
+
   f_eth <- function(i_e,M,x,n,S){
@@
    U <- (x / round((n*i_e),digits = 2)) * S
-     }else {
+      }else if (x > round((n*i_e),digits = 2)){
          U <- M + ((1- (x/n))*(1-M))/(1-i_e) 
-     }
-   round(U,digits = 2)
+        }else{
+     U <- 1}
+        round(U,digits = 3)
       }
@@
       }
-  round(U,digits = 2)
+  round(U,digits = 3)
   }
@@
 \begin{cases}
+1, & \text{if} x =  n\times i_e, \\
+\\
 (\frac{x}{n \times i_e})\times S, & \text{if} \ x < n\times i_e, \\
 \\
-M + \frac{(1 - \frac{x}{n}) \times (1 - M)}{1 - i_e}, & \text{if} \ x \geq n\times i_e 
+M + \frac{(1 - \frac{x}{n}) \times (1 - M)}{1 - i_e}, & \text{if} \ x > n\times i_e 
 \end{cases}
@@
 
-```{r value graph function, fig.width=5,fig.height= 6, fig.align="center", include=TRUE, echo=FALSE}
+```{r value graph function, fig.width=6,fig.height=5, fig.align="center", include=TRUE, echo=FALSE}
 
@@
 
-```{r ethnic utility individual-run,fig.align="center", fig.pos="H", include=TRUE, echo=FALSE}
+```{r logistic,  fig.width=4,fig.height=3, fig.align="center", include=TRUE, echo=FALSE}
 
-# f2 <- function(p,M,x,n,S)
-
-i_e = 0.3
-M = 1
-S = 0
-n = 7
-
-f0m <- f_eth(i_e,M,0,n,S)
-f1m <- f_eth(i_e,M,1,n,S)
-f2m <- f_eth(i_e,M,2,n,S)
-f3m <- f_eth(i_e,M,3,n,S)
-f4m <- f_eth(i_e,M,4,n,S)
-f5m <- f_eth(i_e,M,5,n,S)
-f6m <- f_eth(i_e,M,6,n,S)
-f7m <- f_eth(i_e,M,7,n,S)
-f8m <- f_eth(i_e,M,8,n,S)
-
-num_sim_col <- seq(0, 8, by = 1)
-Utility_E <- c(f0m,f1m,f2m,f3m,f4m,f5m,f6m,f7m,f8m)
-name_E <- paste0("Desired proportion i = ",i_e,"; M = ",M,"; S = ",S)
-
-plot(num_sim_col,Utility_E, xlab = "Similar ethnics neighborhood j", ylab = "Ethnic Utility",  main = "Ethnic Utility for neighborhood j of agent i",  sub = name_E)
-
-#report_E <- paste0("M = ",M,"; S = ",S,"; Desired proportion i = ",i_e,"; Similar ethnics neighborhood j = ", seq(0, 8, by = 1), "; Utility ij = ", Utility_E)
-
-M. <- rep(M,9)
-S. <- rep(S,9)
-prop_des <- rep(i_e,9)
-num_tot <- rep(n,9)
-num_sim <- seq(0, 8, by = 1)
-
-report_E <- data.frame(M.,S.,prop_des,num_tot,num_sim,Utility_E)
-
-knitr::kable(report_E,align="c") # much better printed visualization
-
-```
-
-```{r ethnic_utility, moore neighborhood, include=TRUE, echo=FALSE}
-
-# f2 <- function(p,M,x,n,S)
-
-#i_e = 0.5
-M = 0
-S = 1
-n = 8
-
-for (i_e in seq (0.0,1.0, by = 0.1)){
-
-f0m <- f_eth(i_e,M,0,n,S)
-f1m <- f_eth(i_e,M,1,n,S)
-f2m <- f_eth(i_e,M,2,n,S)
-f3m <- f_eth(i_e,M,3,n,S)
-f4m <- f_eth(i_e,M,4,n,S)
-f5m <- f_eth(i_e,M,5,n,S)
-f6m <- f_eth(i_e,M,6,n,S)
-f7m <- f_eth(i_e,M,7,n,S)
-f8m <- f_eth(i_e,M,8,n,S)
-
-num_sim_col <- seq(0, 8, by = 1)
-Utility_E <- c(f0m,f1m,f2m,f3m,f4m,f5m,f6m,f7m,f8m)
-name_E <- paste0("Desired proportion i = ",i_e,"; M = ",M,"; S = ",S)
-
-plot(num_sim_col,Utility_E, xlab = "Similar ethnics neighborhood j", ylab = "Ethnic Utility",  main = "Ethnic Utility for neighborhood j of agent i",  sub = name_E)
-
-report_E <- paste0("M = ",M,"; S = ",S,"; Desired proportion i = ",i_e,"; Similar ethnics neighborhood j = ", seq(0, 8, by = 1), "; Utility ij = ", Utility_E)
-
-print(report_E)
-
-}
-```
-
-Value utility, based on agents' desired distance (i_v) between the agent's ethnic_weight (e_w) and neighborhood's average ethnic_weight (calculated out of agents residing there)
-Calculate ethnic weight average of neighborhoods with n agents > 0.
-
- **check:** Explain how S and M vary for the constant function, the comment seems lost
-
-```{r value_similarity, echo=FALSE }
-
-i_v <- 0.1
-S  <- 1
-M <- 0 #different values  of M do change results, even for M < 1
-
-for (e_w in seq (0.0,1.0, by = 0.1)){
-
-fv0d2 <- f_val(e_w,0,M,i_v,S)
-fv1d2 <- f_val(e_w,0.1,M,i_v,S)
-fv2d2 <- f_val(e_w,0.2,M,i_v,S)
-fv3d2 <- f_val(e_w,0.3,M,i_v,S)
-fv4d2 <- f_val(e_w,0.4,M,i_v,S)
-fv5d2 <- f_val(e_w,0.5,M,i_v,S)
-fv6d2 <- f_val(e_w,0.6,M,i_v,S)
-fv7d2 <- f_val(e_w,0.7,M,i_v,S)
-fv8d2 <- f_val(e_w,0.8,M,i_v,S)
-fv9d2 <- f_val(e_w,0.9,M,i_v,S)
-fv10d2 <- f_val(e_w,1.0,M,i_v,S)
-
-value_mean_neighborhood <- seq(0.0, 1.0, by = 0.1)
-Utility_V <- c(fv0d2,fv1d2,fv2d2,fv3d2,fv4d2,fv5d2,fv6d2,fv7d2,fv8d2,fv9d2,fv10d2)
-name_V <- paste0("Ethnic weight i = ", e_w,"; desired distance i = ",i_v,"; M = ",M,"; S = ",S)
-
-plot(value_mean_neighborhood,Utility_V, xlab = "Mean ethnic weight neighborhood j", ylab = "Value Utility neighborhood j",  main = "Value Utility for neighborhood j of agent i",  sub = name_V)
-
-report_v <- paste0(name_V,"; Mean ethnic weight j = ", seq(0.0, 1.0, by = 0.1), "; Utility ij = ", Utility_V)
-
-print(report_v)
-
-}
-
-```
-
-Once calculated the ethnic utility and value utility, apply prob above (logistic function) in the decision rule of the agent, with prob(to_new) >= random-float 0-1
-
-```{r logistic putting as in abm ethnic_weight, value_weight}
+# to add: -1 for MIN. Utility Alternative, +1 for MAX Alternative Utility
 
@@
 
-e_w <- 1
+e_w <- 0.4
 v_w <- 1-e_w
@@
   value_difference <- seq(-1.0,1.0, by = 0.1)
-  prob_relocation <- seq(0.0, 1.0,  by = 0.1)
+#  prob_relocation <- seq(0.0, 1.0,  by = 0.1)
 
@@
 
-  name_diff <- paste0("Note: "," Ethnic parameter = ", e_w*10," ;"," Value parameter = ", v_w*10, 
-                      "\r\n Utility Difference -1 = MIN Utility Alternative, 1 = MAX Utility Alternative")
+  title_cond_prob <- paste0("PROB ALT","Diff eth = ",d_u_e,"Ew = ",e_w*10,"Vw = ",v_w*10)
 
-  name_diff_title <-paste0("Probability to move to alternative","\r\n Difference Ethnic Utility (Alternative - Current) = ", d_u_e)
+  report_prob <- na.omit(data.frame(value_difference,prob_choice))
 
-plot(value_difference,prob_choice, xlab = "x-axis: Difference Value Utility (Alternative - Current) \r\n",ylab = "probability", main = name_diff_title, sub = name_diff,ylim = c(0,1), yaxt = 'n')
-axis(2,at=seq(0.0, 1.0, by = 0.25))
+  plot_report_prob <- ggplot(report_prob,aes(value_difference,prob_choice))
+
+ final_prob <-  suppressWarnings(suppressMessages(
+    plot_report_prob + geom_point() + theme_bw() + labs(x = "DIFF VAL",y = "Probability") + ggtitle(label = title_cond_prob) + theme(plot.title = element_text(hjust = 0.5)) + scale_y_continuous(limits =  c(0.0,1.0), breaks = seq(0.0,1.0,by = 0.25)) + scale_x_continuous(limits =  c(-1,1), breaks = seq(-1,1,by = 0.2)) + geom_vline(xintercept = 0, colour = "red", linetype = "dotted") + geom_hline(yintercept = 0.5, colour = "red", linetype = "dotted")
+  ))
+
+  print(final_prob)
 
@@
 
-```{r logistic in sequence, to test with parameters, to be deleted}
+```{r ethnic utility individual-run,fig.width=4,fig.height= 3, fig.align="center", fig.pos="H", include=TRUE, echo=FALSE}
 
-prob <- function(d_u_e,d_u_v,par_e,par_v){round(1 / (1 + exp(-par_e*(d_u_e) + (-par_v*(d_u_v)))),digits= 2)}
+# f2 <- function(p,M,x,n,S)
 
-for (d_u_e in seq (-1.0,1.0, by = 0.1)){
+i_e = 0.2
+S = 0
+M = 1
+n = 6
 
-par_e <- 10
-par_v <- 10 - par_e
+f0m <- f_eth(i_e,M,0,n,S)
+f1m <- f_eth(i_e,M,1,n,S)
+f2m <- f_eth(i_e,M,2,n,S)
+f3m <- f_eth(i_e,M,3,n,S)
+f4m <- f_eth(i_e,M,4,n,S)
+f5m <- f_eth(i_e,M,5,n,S)
+f6m <- f_eth(i_e,M,6,n,S)
+f7m <- f_eth(i_e,M,7,n,S)
+f8m <- f_eth(i_e,M,8,n,S)
 
-# d_u_e <- -1
+# num_sim_col <- seq(0, 8, by = 1)
+Utility_E <- c(f0m,f1m,f2m,f3m,f4m,f5m,f6m,f7m,f8m)
+# name_E <- paste0("Desired proportion i = ",i_e,"; M = ",M,"; S = ",S)
 
-  dis_0p   <- prob(d_u_e,0.0,par_e,par_v)
-dis_0.1p <- prob(d_u_e,0.1,par_e,par_v)
-dis_0.2p <- prob(d_u_e,0.2,par_e,par_v)
-dis_0.3p <- prob(d_u_e,0.3,par_e,par_v)
-dis_0.4p <- prob(d_u_e,0.4,par_e,par_v)
-dis_0.5p <- prob(d_u_e,0.5,par_e,par_v)
-dis_0.6p <- prob(d_u_e,0.6,par_e,par_v)
-dis_0.7p <- prob(d_u_e,0.7,par_e,par_v)
-dis_0.8p <- prob(d_u_e,0.8,par_e,par_v)
-dis_0.9p <- prob(d_u_e,0.9,par_e,par_v)
-dis_1p  <- prob(d_u_e,1.0,par_e,par_v)
-dis_0.1negp <- prob(d_u_e,-0.1,par_e,par_v)
-dis_0.2negp <- prob(d_u_e,-0.2,par_e,par_v)
-dis_0.3negp <- prob(d_u_e,-0.3,par_e,par_v)
-dis_0.4negp <- prob(d_u_e,-0.4,par_e,par_v)
-dis_0.5negp <- prob(d_u_e,-0.5,par_e,par_v)
-dis_0.6negp <- prob(d_u_e,-0.6,par_e,par_v)
-dis_0.7negp <- prob(d_u_e,-0.7,par_e,par_v)
-dis_0.8negp <- prob(d_u_e,-0.8,par_e,par_v)
-dis_0.9negp <- prob(d_u_e,-0.9,par_e,par_v)
-dis_1negp   <- prob(d_u_e,-1.0,par_e,par_v)
+# plot(num_sim_col,Utility_E, xlab = "Similar ethnics neighborhood j", ylab = "Ethnic Utility",  main = "Ethnic Utility for neighborhood j of agent i",  sub = name_E)
 
-  value_difference <- seq(-1.0,1.0, by = 0.1)
-  prob_relocation <- seq(0.0, 1.0,  by = 0.1)
+#report_E <- paste0("M = ",M,"; S = ",S,"; Desired proportion i = ",i_e,"; Similar ethnics neighborhood j = ", seq(0, 8, by = 1), "; Utility ij = ", Utility_E)
 
-  prob_choicep <- c(dis_1negp,dis_0.9negp,dis_0.8negp,dis_0.7negp,dis_0.6negp,dis_0.5negp,dis_0.4negp,dis_0.3negp,dis_0.2negp,dis_0.1negp,dis_0p,dis_0.1p,dis_0.2p,dis_0.3p,dis_0.4p,dis_0.5p,dis_0.6p,dis_0.7p,dis_0.8p,dis_0.9p,dis_1p)
+M. <- rep(M,9)
+S. <- rep(S,9)
+prop_des <- rep(i_e,9)
+num_tot <- rep(n,9)
+num_sim <- seq(0, 8, by = 1)
 
-  name_diff <- paste0("Note: "," Ethnic parameter = ", par_e," ;"," Value parameter = ", par_v, 
-                      "\r\n Utility Difference -1 = MIN Utility Alternative, 1 = MAX Utility Alternative")
+report_E <- na.omit(data.frame(M.,S.,prop_des,num_tot,num_sim,Utility_E))
 
-  name_diff_title <-paste0("Probability to move to alternative","\r\n Difference Ethnic Utility (Alternative - Current) = ", d_u_e)
+title_cond <- paste0("Desired proportion = ", i_e,"; ", "S = ", S,"; " ,"M = ", M)
 
-plot(value_difference,prob_choicep, xlab = "x-axis: Difference Value Utility (Alternative - Current) \r\n",ylab = "probability", main = name_diff_title, sub = name_diff,ylim = c(0,1), yaxt = 'n')
-axis(2,at=seq(0.0, 1.0, by = 0.25))
+plot_report_E <- ggplot(report_E,aes(num_sim,Utility_E))
+
+suppressWarnings(suppressMessages(
+plot_report_E + geom_point() + theme_bw() + labs(x = "Number similar agents in j",y = "Ethnic Utility j") + ggtitle(label = title_cond) + theme(plot.title = element_text(hjust = 0.5)) + scale_y_continuous(limits =  c(0.0,1.0), breaks = seq(0.0,1.0,by = 0.25)) + scale_x_continuous(limits =  c(0,n), breaks = seq(0,n,by = 1))
+))
+
+knitr::kable(report_E,align="c") # much better printed visualization
+
+```
+
+```{r value individual run,fig.width=5,fig.height= 3, fig.align="center", fig.pos="H", include=TRUE, echo=FALSE }
+
+e_w <- 0.4
+i_v <- 0.2
+S  <- 1
+M <- 0 #S regulates the left side of the slope, M the right side
+
+fv0d2 <- f_val(e_w,0,M,i_v,S)
+fv1d2 <- f_val(e_w,0.1,M,i_v,S)
+fv2d2 <- f_val(e_w,0.2,M,i_v,S)
+fv3d2 <- f_val(e_w,0.3,M,i_v,S)
+fv4d2 <- f_val(e_w,0.4,M,i_v,S)
+fv5d2 <- f_val(e_w,0.5,M,i_v,S)
+fv6d2 <- f_val(e_w,0.6,M,i_v,S)
+fv7d2 <- f_val(e_w,0.7,M,i_v,S)
+fv8d2 <- f_val(e_w,0.8,M,i_v,S)
+fv9d2 <- f_val(e_w,0.9,M,i_v,S)
+fv10d2 <- f_val(e_w,1.0,M,i_v,S)
+
+# name_V <- paste0("Ethnic weight i = ", e_w,"; desired distance i = ",i_v,"; M = ",M,"; S = ",S)
+
+mean_ew_ng <- seq(0.0, 1.0, by = 0.1)
+ew_agent <- rep(e_w,11)
+Utility_V <- c(fv0d2,fv1d2,fv2d2,fv3d2,fv4d2,fv5d2,fv6d2,fv7d2,fv8d2,fv9d2,fv10d2)
+Mv <- rep(M,11)
+Sv <- rep(S,11)
+des_dist <- rep(i_v,11)
+
+report_V <- na.omit(data.frame(Mv,Sv,des_dist,ew_agent,mean_ew_ng,Utility_V))
+
+title_cond_V <- paste0("Ethnic weight i = ", e_w,"; desired distance i = ",i_v,"\n\r","M = ",M,"S = ",S)
+
+plot_report_V <- ggplot(report_V,aes(mean_ew_ng,Utility_V))
+
+suppressWarnings(suppressMessages(
+plot_report_V + geom_point() + theme_bw() + labs(x = "Mean ethnic weight j",y = "Value Utility j") + ggtitle(label = title_cond_V) + theme(plot.title = element_text(hjust = 0.5)) + scale_y_continuous(limits =  c(0.0,1.0), breaks = seq(0.0,1.0,by = 0.25)) + scale_x_continuous(limits =  c(0,1), breaks = seq(0,1,by = 0.1))
+))
+
+# plot(value_mean_neighborhood,Utility_V, xlab = "Mean ethnic weight neighborhood j", ylab = "Value Utility neighborhood j",  main = "Value Utility for neighborhood j of agent i",  sub = name_V)
+
+# report_v <- paste0(name_V,"; Mean ethnic weight j = ", seq(0.0, 1.0, by = 0.1), "; Utility ij = ", Utility_V)
+
+knitr::kable(report_V,align="c") # much better printed visualization
+
+# print(final_v)
+# print(final_repV)
+
+```
+
+```{r ANNEX - ethnic_multiple_run, moore neighborhood, include=TRUE, echo=FALSE}
+
+# f2 <- function(p,M,x,n,S)
+
+#i_e = 0.5
+M = 0
+S = 1
+n = 8
+
+for (i_e in seq (0.0,1.0, by = 0.1)){
+
+f0m <- f_eth(i_e,M,0,n,S)
+f1m <- f_eth(i_e,M,1,n,S)
+f2m <- f_eth(i_e,M,2,n,S)
+f3m <- f_eth(i_e,M,3,n,S)
+f4m <- f_eth(i_e,M,4,n,S)
+f5m <- f_eth(i_e,M,5,n,S)
+f6m <- f_eth(i_e,M,6,n,S)
+f7m <- f_eth(i_e,M,7,n,S)
+f8m <- f_eth(i_e,M,8,n,S)
+
+#num_sim_col <- seq(0, n, by = 1)
+Utility_E <- c(f0m,f1m,f2m,f3m,f4m,f5m,f6m,f7m,f8m)
+#name_E <- paste0("Desired proportion i = ",i_e,"; M = ",M,"; S = ",S)
+
+#plot(num_sim_col,Utility_Es, xlab = "Similar ethnics neighborhood j", ylab = "Ethnic Utility", ylim = c(0,1),xlim = c(0,n),  main = "Ethnic Utility for neighborhood j of agent i",  sub = name_E)
+
+#report_Es <- paste0("M = ",M,"; S = ",S,"; Desired proportion i = ",i_e,"; Similars in j= ", seq(0, n, by = 1), "; Utility ij = ", Utility_Es)
+
+#print(report_Es)
+
+M. <- rep(M,9)
+S. <- rep(S,9)
+prop_des <- rep(i_e,9)
+num_tot <- rep(n,9)
+num_sim <- seq(0, 8, by = 1)
+
+report_E <- na.omit(data.frame(M.,S.,prop_des,num_tot,num_sim,Utility_E))
+
+title_cond <- paste0("Desired proportion = ", i_e,"; ", "S = ", S,"; " ,"M = ", M)
+
+plot_report_E <- ggplot(report_E,aes(num_sim,Utility_E))
+
+final_E <- suppressWarnings(suppressMessages(
+plot_report_E + geom_point() + theme_bw() + labs(x = "Number similar agents in j",y = "Ethnic Utility j") + ggtitle(label = title_cond) + theme(plot.title = element_text(hjust = 0.5)) + scale_y_continuous(limits =  c(0.0,1.0), breaks = seq(0.0,1.0,by = 0.25)) + scale_x_continuous(limits =  c(0,n), breaks = seq(0,n,by = 1))
+))
+
+final_repE <- knitr::kable(report_E,align="c") # much better printed visualization
+
+print(final_E)
+print(final_repE)
 
 }
+```
+
+Value utility, based on agents' desired distance (i_v) between the agent's ethnic_weight (e_w) and neighborhood's average ethnic_weight (calculated out of agents residing there)
+Calculate ethnic weight average of neighborhoods with n agents > 0.
+
+ **check:** Explain how S and M vary for the constant function, the comment seems lost
+
+```{r ANNEX- value_similarity, echo=FALSE }
+
+i_v <- 0.1
+S  <- 1
+M <- 0 #different values  of M do change results, even for M < 1
+
+for (e_w in seq (0.0,1.0, by = 0.1)){
+
+fv0d2 <- f_val(e_w,0,M,i_v,S)
+fv1d2 <- f_val(e_w,0.1,M,i_v,S)
+fv2d2 <- f_val(e_w,0.2,M,i_v,S)
+fv3d2 <- f_val(e_w,0.3,M,i_v,S)
+fv4d2 <- f_val(e_w,0.4,M,i_v,S)
+fv5d2 <- f_val(e_w,0.5,M,i_v,S)
+fv6d2 <- f_val(e_w,0.6,M,i_v,S)
+fv7d2 <- f_val(e_w,0.7,M,i_v,S)
+fv8d2 <- f_val(e_w,0.8,M,i_v,S)
+fv9d2 <- f_val(e_w,0.9,M,i_v,S)
+fv10d2 <- f_val(e_w,1.0,M,i_v,S)
+
+# name_V <- paste0("Ethnic weight i = ", e_w,"; desired distance i = ",i_v,"; M = ",M,"; S = ",S)
+
+mean_ew_ng <- seq(0.0, 1.0, by = 0.1)
+ew_agent <- rep(e_w,11)
+Utility_V <- c(fv0d2,fv1d2,fv2d2,fv3d2,fv4d2,fv5d2,fv6d2,fv7d2,fv8d2,fv9d2,fv10d2)
+Mv <- rep(M,11)
+Sv <- rep(S,11)
+des_dist <- rep(i_v,11)
+
+report_V <- na.omit(data.frame(Mv,Sv,des_dist,ew_agent,mean_ew_ng,Utility_V))
+
+title_cond_V <- paste0("Ethnic weight i = ", e_w,"; desired distance i = ",i_v,"; M = ",M,"; S = ",S)
+
+plot_report_V <- ggplot(report_V,aes(mean_ew_ng,Utility_V))
+
+final_v <- suppressWarnings(suppressMessages(
+plot_report_V + geom_point() + theme_bw() + labs(x = "Mean ethnic weight j",y = "Value Utility j") + ggtitle(label = title_cond_V) + theme(plot.title = element_text(hjust = 0.5)) + scale_y_continuous(limits =  c(0.0,1.0), breaks = seq(0.0,1.0,by = 0.25)) + scale_x_continuous(limits =  c(0,1), breaks = seq(0,1,by = 0.1))
+))
+
+# plot(value_mean_neighborhood,Utility_V, xlab = "Mean ethnic weight neighborhood j", ylab = "Value Utility neighborhood j",  main = "Value Utility for neighborhood j of agent i",  sub = name_V)
+
+# report_v <- paste0(name_V,"; Mean ethnic weight j = ", seq(0.0, 1.0, by = 0.1), "; Utility ij = ", Utility_V)
+
+final_repV <- knitr::kable(report_V,align="c") # much better printed visualization
+
+print(final_v)
+print(final_repV)
+
+}
+
+```
+
+Once calculated the ethnic utility and value utility, apply prob above (logistic function) in the decision rule of the agent, with prob(to_new) >= random-float 0-1
+
+```{r logistic in sequence, to test with parameters, to be deleted}
+# 
+# prob <- function(d_u_e,d_u_v,par_e,par_v){round(1 / (1 + exp(-par_e*(d_u_e) + (-par_v*(d_u_v)))),digits= 2)}
+# 
+# for (d_u_e in seq (-1.0,1.0, by = 0.1)){
+#   
+# par_e <- 10
+# par_v <- 10 - par_e
+# 
+# # d_u_e <- -1
+# 
+#   dis_0p   <- prob(d_u_e,0.0,par_e,par_v)
+# dis_0.1p <- prob(d_u_e,0.1,par_e,par_v)
+# dis_0.2p <- prob(d_u_e,0.2,par_e,par_v)
+# dis_0.3p <- prob(d_u_e,0.3,par_e,par_v)
+# dis_0.4p <- prob(d_u_e,0.4,par_e,par_v)
+# dis_0.5p <- prob(d_u_e,0.5,par_e,par_v)
+# dis_0.6p <- prob(d_u_e,0.6,par_e,par_v)
+# dis_0.7p <- prob(d_u_e,0.7,par_e,par_v)
+# dis_0.8p <- prob(d_u_e,0.8,par_e,par_v)
+# dis_0.9p <- prob(d_u_e,0.9,par_e,par_v)
+# dis_1p  <- prob(d_u_e,1.0,par_e,par_v)
+# dis_0.1negp <- prob(d_u_e,-0.1,par_e,par_v)
+# dis_0.2negp <- prob(d_u_e,-0.2,par_e,par_v)
+# dis_0.3negp <- prob(d_u_e,-0.3,par_e,par_v)
+# dis_0.4negp <- prob(d_u_e,-0.4,par_e,par_v)
+# dis_0.5negp <- prob(d_u_e,-0.5,par_e,par_v)
+# dis_0.6negp <- prob(d_u_e,-0.6,par_e,par_v)
+# dis_0.7negp <- prob(d_u_e,-0.7,par_e,par_v)
+# dis_0.8negp <- prob(d_u_e,-0.8,par_e,par_v)
+# dis_0.9negp <- prob(d_u_e,-0.9,par_e,par_v)
+# dis_1negp   <- prob(d_u_e,-1.0,par_e,par_v)
+#   
+#   value_difference <- seq(-1.0,1.0, by = 0.1)
+#   prob_relocation <- seq(0.0, 1.0,  by = 0.1)
+#   
+#   prob_choicep <- c(dis_1negp,dis_0.9negp,dis_0.8negp,dis_0.7negp,dis_0.6negp,dis_0.5negp,dis_0.4negp,dis_0.3negp,dis_0.2negp,dis_0.1negp,dis_0p,dis_0.1p,dis_0.2p,dis_0.3p,dis_0.4p,dis_0.5p,dis_0.6p,dis_0.7p,dis_0.8p,dis_0.9p,dis_1p)
+#   
+#   name_diff <- paste0("Note: "," Ethnic parameter = ", par_e," ;"," Value parameter = ", par_v, 
+#                       "\r\n Utility Difference -1 = MIN Utility Alternative, 1 = MAX Utility Alternative")
+#   
+#   name_diff_title <-paste0("Probability to move to alternative","\r\n Difference Ethnic Utility (Alternative - Current) = ", d_u_e)
+#   
+# plot(value_difference,prob_choicep, xlab = "x-axis: Difference Value Utility (Alternative - Current) \r\n",ylab = "probability", main = name_diff_title, sub = name_diff,ylim = c(0,1), yaxt = 'n')
+# axis(2,at=seq(0.0, 1.0, by = 0.25))
+
+#}
 

### 2019-08-19 paper_notes.Rmd
ok 3d

@@
 library(ggrepel)
+library(magicfor)
+library(dplyr)
+library(plot3D)
+library(rgl)
+library(plotly)
+
 # Here functions that are used.
@@
 
-prob <- function(d_u_e,d_u_v,e_w,par_v){round(1 / (1 + exp(-(e_w*10)*(d_u_e) + (-(v_w*10)*(d_u_v)))),digits= 2)}
+prob <- function(d_u_e,d_u_v,e_w,v_w){round(1 / (1 + exp(-(e_w*k)*(d_u_e) + (-(v_w*k)*(d_u_v)))),digits= 2)}
 
@@
 
+```{r heatmap-log,  fig.width=5,fig.height=4,fig.cap="Probability to choose alternative location",fig.align="center", include=TRUE, echo=FALSE}
+
+# to add: -1 for MIN. Utility Alternative, +1 for MAX Alternative Utility
+
+magic_for(print,silent = TRUE)
+
+for (i in seq (-1.0,1.0, by = 0.1)){
+  eth_diff <- rep(i,21)
+  print(eth_diff)
+}
+
+d_u_e <-  magic_result_as_vector()
+d_u_v <- rep(seq(-1,1,by = 0.1),21) 
+e_w <- 0
+v_w <- 1-e_w
+k <- 10
+
+df <- data.frame(d_u_e,d_u_v,e_w,v_w)
+
+title_cond_fin <- paste0("Ethnic weight = ",e_w*k,"; ","Value weight = ",v_w*k)
+ass <- mutate(df, prap = prob(d_u_e, d_u_v,e_w,v_w))
+fina_rast <- ggplot(ass,aes(d_u_e,d_u_v))
+
+ plot_fina_rast <-  suppressWarnings(suppressMessages(
+    fina_rast + geom_raster(aes(fill = prap)) + theme_bw() + labs(x = "Diff.
+ethnic (alternative - current)",y = "Diff.
+value (alternative - current)") + labs(title = title_cond_fin, caption = "-1: Min Utility Alternative; 1: Max Utility Alternative") + theme(plot.title = element_text(hjust = 0.5), plot.subtitle = element_text(hjust=0.5),plot.caption = element_text(hjust=0.5))
+    + geom_vline(xintercept = 0, colour = "red", linetype = "dotted") + geom_hline(yintercept = 0, colour = "red", linetype = "dotted") + scale_fill_continuous(name = "Probability")
+  ))
+
+ fx <- d_u_e
+ fy <- d_u_v
+ fz <- ass$prap
+
+ # persp(x = seq(-1, 1, by = 0.1),
+   #   y = seq(-1, 1, by = 0.1),
+   #   fz)
+
+  d <- plot3d(fx,fy,fz,col="blue")
+  rgl.postscript("d.eps",fmt="eps")
+
+ test_trida <- plot_ly(x=fx,y=fy,z=fz, type="scatter3d", mode="markers", color=fz) %>% layout(legend = list(x = 0.1, y = 0.9))
+ #p <- export(p = last_plot(),file = "plotly.png", selenium = NULL)
+ #fx
+
+# test_trid <- plot3d(df_3$a,df_3$b,df_3$C)
+
+# plotly_IMAGE(test_trida, width = 500, height = 500, format = "png", scale = 2, out_file = "test.png")
+
+#is.data.frame(ass)
+#  print(plot_fina_rast)
+
+print(plot_fina_rast)
+
+# knitr::include_graphics("gg.png" )
+
+# plot3d(fx,fy,fz, col = "blue",xlab = "eth",ylab="val",zlab="prob", type = "s",size = 2)
+
+```
+
+```{r heat2,  fig.width=5,fig.height=4,fig.cap="Probability to choose alternative location",fig.align="center", include=TRUE, echo=FALSE}
+
+# to add: -1 for MIN. Utility Alternative, +1 for MAX Alternative Utility
+
+magic_for(print,silent = TRUE)
+
+for (i in seq (-1.0,1.0, by = 0.1)){
+  eth_diff <- rep(i,21)
+  print(eth_diff)
+}
+
+d_u_e <-  magic_result_as_vector()
+d_u_v <- rep(seq(-1,1,by = 0.1),21) 
+e_w <- 0
+v_w <- 1-e_w
+k <- 10
+
+df <- data.frame(d_u_e,d_u_v,e_w,v_w)
+
+title_cond_fin <- paste0("Ethnic weight = ",e_w*k,"; ","Value weight = ",v_w*k)
+ass <- mutate(df, prap = prob(d_u_e, d_u_v,e_w,v_w))
+fina_rast <- ggplot(ass,aes(d_u_e,d_u_v))
+
+ plot_fina_rast <-  suppressWarnings(suppressMessages(
+    fina_rast + geom_raster(aes(fill = prap)) + theme_bw() + labs(x = "Diff.
+ethnic (alternative - current)",y = "Diff.
+value (alternative - current)") + labs(title = title_cond_fin, caption = "-1: Min Utility Alternative; 1: Max Utility Alternative") + theme(plot.title = element_text(hjust = 0.5), plot.subtitle = element_text(hjust=0.5),plot.caption = element_text(hjust=0.5))
+    + geom_vline(xintercept = 0, colour = "red", linetype = "dotted") + geom_hline(yintercept = 0, colour = "red", linetype = "dotted") + scale_fill_continuous(name = "Probability")
+  ))
+
+ fx <- d_u_e
+ fy <- d_u_v
+ fz <- ass$prap
+
+ # persp(x = seq(-1, 1, by = 0.1),
+   #   y = seq(-1, 1, by = 0.1),
+   #   fz)
+
+#  d <- plot3d(fx,fy,fz,col="blue")
+#  rgl.postscript("d.eps",fmt="eps")
+
+ test_trida <- plot_ly(x=fx,y=fy,z=fz, type="scatter3d", mode="markers", color=fz) 
+ #p <- export(p = last_plot(),file = "plotly.png", selenium = NULL)
+ #fx
+
+# test_trid <- plot3d(df_3$a,df_3$b,df_3$C)
+
+# plotly_IMAGE(test_trida, width = 500, height = 500, format = "png", scale = 2, out_file = "test.png")
+
+#is.data.frame(ass)
+#  print(plot_fina_rast)
+
+print(test_trida)
+print(plot_fina_rast)
+
+# knitr::include_graphics("gg.png" )
+
+# plot3d(fx,fy,fz, col = "blue",xlab = "eth",ylab="val",zlab="prob", type = "s",size = 2)
+
+```
+
 ```{r logistic,  fig.width=4,fig.height=3, fig.align="center", include=TRUE, echo=FALSE}
@@
 
-e_w <- 0.4
-v_w <- 1-e_w
+e_w <- 0.6
+v_w <- 1 - e_w
+k <- 10
 
@@
 
+dis_1neg   <- prob(d_u_e,-1.0,e_w,v_w)
+dis_0.9neg <- prob(d_u_e,-0.9,e_w,v_w)
+dis_0.8neg <- prob(d_u_e,-0.8,e_w,v_w)
+dis_0.7neg <- prob(d_u_e,-0.7,e_w,v_w)
+dis_0.6neg <- prob(d_u_e,-0.6,e_w,v_w)
+dis_0.5neg <- prob(d_u_e,-0.5,e_w,v_w)
+dis_0.4neg <- prob(d_u_e,-0.4,e_w,v_w)
+dis_0.3neg <- prob(d_u_e,-0.3,e_w,v_w)
+dis_0.2neg <- prob(d_u_e,-0.2,e_w,v_w)
+dis_0.1neg <- prob(d_u_e,-0.1,e_w,v_w)
 dis_0   <- prob(d_u_e,0.0,e_w,v_w)
@@
 dis_1   <- prob(d_u_e,1.0,e_w,v_w)
-dis_0.1neg <- prob(d_u_e,-0.1,e_w,v_w)
-dis_0.2neg <- prob(d_u_e,-0.2,e_w,v_w)
-dis_0.3neg <- prob(d_u_e,-0.3,e_w,v_w)
-dis_0.4neg <- prob(d_u_e,-0.4,e_w,v_w)
-dis_0.5neg <- prob(d_u_e,-0.5,e_w,v_w)
-dis_0.6neg <- prob(d_u_e,-0.6,e_w,v_w)
-dis_0.7neg <- prob(d_u_e,-0.7,e_w,v_w)
-dis_0.8neg <- prob(d_u_e,-0.8,e_w,v_w)
-dis_0.9neg <- prob(d_u_e,-0.9,e_w,v_w)
-dis_1neg   <- prob(d_u_e,-1.0,e_w,v_w)
 

### 2019-08-20 paper_notes.Rmd
OK, to finish and delete chunks

@@
 bibliography: "references.bib"
+always_allow_html: yes
 # target: BIGSSS Research Day by September 15th, presented  on October 25th. 6000 words: around 12 pages.
@@
 library(magicfor)
-library(dplyr)
+# library(dplyr)
 library(plot3D)
@@
 library(plotly)
+library(tidyr)
+library(plyr)
+library(rgl)
+library(graphics)
+library(cowplot)
+library(magick)
 
@@
 
-```{r heatmap-log,  fig.width=5,fig.height=4,fig.cap="Probability to choose alternative location",fig.align="center", include=TRUE, echo=FALSE}
+```{r heatmap-log,  fig.width=5,fig.height=4,fig.cap="Probability to choose alternative location",fig.align="center", include=FALSE, echo=FALSE}
+
+# # to add: -1 for MIN. Utility Alternative, +1 for MAX Alternative Utility
+# 
+# magic_for(print,silent = TRUE)
+# 
+# for (i in seq (-1.0,1.0, by = 0.1)){
+#   eth_diff <- rep(i,21)
+#   print(eth_diff)
+# }
+# 
+# d_u_e <-  magic_result_as_vector()
+# d_u_v <- rep(seq(-1,1,by = 0.1),21) 
+# e_w <- 0
+# v_w <- 1-e_w
+# k <- 10
+# 
+# df <- data.frame(d_u_e,d_u_v,e_w,v_w)
+# 
+# title_cond_fin <- paste0("Ethnic weight = ",e_w*k,"; ","Value weight = ",v_w*k)
+# ass <- mutate(df, prap = prob(d_u_e, d_u_v,e_w,v_w))
+# fina_rast <- ggplot(ass,aes(d_u_e,d_u_v))
+# 
+#  plot_fina_rast <-  suppressWarnings(suppressMessages(
+#     fina_rast + geom_raster(aes(fill = prap)) + theme_bw() + labs(x = "Diff.
+ethnic (alternative - current)",y = "Diff.
+value (alternative - current)") + labs(title = title_cond_fin, caption = "-1: Min Utility Alternative; 1: Max Utility Alternative") + theme(plot.title = element_text(hjust = 0.5), plot.subtitle = element_text(hjust=0.5),plot.caption = element_text(hjust=0.5))
+#     + geom_vline(xintercept = 0, colour = "red", linetype = "dotted") + geom_hline(yintercept = 0, colour = "red", linetype = "dotted") + scale_fill_continuous(name = "Probability")
+#   ))
+#   
+# 
+#  fx <- d_u_e
+#  fy <- d_u_v
+#  fz <- ass$prap
+#  
+#  # persp(x = seq(-1, 1, by = 0.1),
+#    #   y = seq(-1, 1, by = 0.1),
+#    #   fz)
+#  
+#   d <- plot3d(fx,fy,fz,col="blue")
+#   rgl.postscript("d.eps",fmt="eps")
+#  
+#  
+#  test_trida <- plot_ly(x=fx,y=fy,z=fz, type="scatter3d", mode="markers", color=fz) %>% layout(legend = list(x = 0.1, y = 0.9))
+#  #p <- export(p = last_plot(),file = "plotly.png", selenium = NULL)
+#  #fx
+#  
+# # test_trid <- plot3d(df_3$a,df_3$b,df_3$C)
+#  
+# # plotly_IMAGE(test_trida, width = 500, height = 500, format = "png", scale = 2, out_file = "test.png")
+#  
+# #is.data.frame(ass)
+# #  print(plot_fina_rast)
+#  
+# print(plot_fina_rast)
+# 
+# # knitr::include_graphics("gg.png" )
+
+# plot3d(fx,fy,fz, col = "blue",xlab = "eth",ylab="val",zlab="prob", type = "s",size = 2)
+
+```
+
+```{r heat2,  fig.width=5,fig.height=4,fig.cap="Probability to choose alternative location",fig.align="center", include=FALSE, echo=FALSE}
+
+# # to add: -1 for MIN. Utility Alternative, +1 for MAX Alternative Utility
+# 
+# magic_for(print,silent = TRUE)
+# 
+# for (i in seq (-1.0,1.0, by = 0.1)){
+#   eth_diff <- rep(i,21)
+#   print(eth_diff)
+# }
+# 
+# 
+# d_u_e <-  magic_result_as_vector()
+# d_u_v <- rep(seq(-1,1,by = 0.1),21)
+# 
+# k <- 10
+# 
+# e_w <- 0
+# v_w <- 1-e_w
+# df <- data.frame(d_u_e,d_u_v,e_w,v_w)
+# 
+# title_cond_fin <- paste0("Ethnic weight = ",e_w*k,"; ","Value weight = ",v_w*k)
+# fin_prob <- mutate(df, proba = prob(d_u_e, d_u_v,e_w,v_w))
+# fina_rast <- ggplot(fin_prob,aes(d_u_e,d_u_v))
+# 
+#  plot_fina_rast <-  suppressWarnings(suppressMessages(
+#     fina_rast + geom_raster(aes(fill = proba)) + theme_bw() + labs(x = "Diff.
+ethnic (alternative - current)",y = "Diff.
+value (alternative - current)") + labs(title = title_cond_fin, caption = "-1: Min Utility Alternative; 1: Max Utility Alternative") + theme(plot.title = element_text(hjust = 0.5), plot.subtitle = element_text(hjust=0.5),plot.caption = element_text(hjust=0.5))
+#     + geom_vline(xintercept = 0, colour = "red", linetype = "dotted") + geom_hline(yintercept = 0, colour = "red", linetype = "dotted") + scale_fill_continuous(name = "Probability")
+#   ))
+#   
+# 
+#  fx <- d_u_e
+#  fy <- d_u_v
+#  fz <- ass$prap
+#  
+#  # persp(x = seq(-1, 1, by = 0.1),
+#    #   y = seq(-1, 1, by = 0.1),
+#    #   fz)
+#  
+# #  d <- plot3d(fx,fy,fz,col="blue")
+# #  rgl.postscript("d.eps",fmt="eps")
+#  
+#  
+#  test_trida <- plot_ly(x=fx,y=fy,z=fz, type="scatter3d", mode="markers", color=fz) 
+#  #p <- export(p = last_plot(),file = "plotly.png", selenium = NULL)
+#  #fx
+#  
+# # test_trid <- plot3d(df_3$a,df_3$b,df_3$C)
+#  
+# # plotly_IMAGE(test_trida, width = 500, height = 500, format = "png", scale = 2, out_file = "test.png")
+#  
+# #is.data.frame(ass)
+# #  print(plot_fina_rast)
+# 
+# print(test_trida)
+# print(plot_fina_rast)
+# 
+# df
+
+# knitr::include_graphics("gg.png" )
+
+# plot3d(fx,fy,fz, col = "blue",xlab = "eth",ylab="val",zlab="prob", type = "s",size = 2)
+
+```
+
+```{r testaa,  fig.width=12,fig.height=12,fig.cap="Probability to choose alternative location",fig.align="center", include=TRUE, echo=FALSE}
 
@@
 d_u_v <- rep(seq(-1,1,by = 0.1),21)
-e_w <- 0
-v_w <- 1-e_w
+
 k <- 10
 
-df <- data.frame(d_u_e,d_u_v,e_w,v_w)
-
-title_cond_fin <- paste0("Ethnic weight = ",e_w*k,"; ","Value weight = ",v_w*k)
-ass <- mutate(df, prap = prob(d_u_e, d_u_v,e_w,v_w))
-fina_rast <- ggplot(ass,aes(d_u_e,d_u_v))
+#e_w <- 0
+#v_w <- 1-e_w
+
+prob_comb <- function(a){
+title_cond_fin <- paste0("Ethnic weight = ",a$e_w*k,"; ","Value weight = ",a$v_w*k)
+# fin_prob <- mutate(a, proba = prob(d_u_e, d_u_v,e_w,v_w))
+fina_rast <- ggplot(a,aes(d_u_e,d_u_v))
 
  plot_fina_rast <-  suppressWarnings(suppressMessages(
-    fina_rast + geom_raster(aes(fill = prap)) + theme_bw() + labs(x = "Diff.
+    fina_rast + geom_raster(aes(fill = proba)) + theme_bw() + labs(x = "Diff.
 ethnic (alternative - current)",y = "Diff.
 value (alternative - current)") + labs(title = title_cond_fin, caption = "-1: Min Utility Alternative; 1: Max Utility Alternative") + theme(plot.title = element_text(hjust = 0.5), plot.subtitle = element_text(hjust=0.5),plot.caption = element_text(hjust=0.5))
-    + geom_vline(xintercept = 0, colour = "red", linetype = "dotted") + geom_hline(yintercept = 0, colour = "red", linetype = "dotted") + scale_fill_continuous(name = "Probability")
+    + geom_vline(xintercept = 0, colour = "red", linetype = "dotted") + geom_hline(yintercept = 0, colour = "red", linetype = "dotted") + scale_fill_continuous(name = "Probability",limits=c(0,1), breaks=seq(0,1,0.25))
   ))
-
+ # print(plot_fina_rast)
+
+ # fx <- d_u_e
+# fy <- d_u_v
+#  fz <- df_0$prob
+
+# test_trida <- plot_ly(x=fx,y=fy,z=fz, type="scatter3d", mode="markers", color=fz) 
+}
+
+df_0 <- mutate(data.frame(d_u_e,d_u_v,e_w=0,v_w=0), proba = prob(d_u_e, d_u_v,e_w,v_w))
+df_05 <- mutate(data.frame(d_u_e,d_u_v,e_w=0.5,v_w=0.5),proba = prob(d_u_e, d_u_v,e_w,v_w))
+df_maxe <- mutate(data.frame(d_u_e,d_u_v,e_w=1,v_w=0),proba = prob(d_u_e, d_u_v,e_w,v_w))
+df_maxv <- mutate(data.frame(d_u_e,d_u_v,e_w=0,v_w=1),proba = prob(d_u_e, d_u_v,e_w,v_w))
+df_r <- mutate(data.frame(d_u_e,d_u_v,e_w=0.1,v_w=0.1),proba = prob(d_u_e, d_u_v,e_w,v_w))
+df_1 <- mutate(data.frame(d_u_e,d_u_v,e_w=10,v_w=10),proba = prob(d_u_e, d_u_v,e_w,v_w))
+
+# df_05
+
+plot_0 <- prob_comb(df_0)
+plot_05 <- prob_comb(df_05)
+plot_maxe <- prob_comb(df_maxe)
+plot_maxv <- prob_comb(df_maxv)
+plot_r <- prob_comb(df_r)
+plot_1 <- prob_comb(df_1)
+
+grid.arrange( plot_0,plot_05,plot_maxe,plot_maxv,plot_r,  plot_1,nrow=3,ncol=2)
+
+```
+
+```{r test3D,  fig.width=18,fig.height=18,fig.cap="Probability to choose alternative location 3D",fig.align="center", include=TRUE, echo=FALSE}
+
+ prob_3d <- function(b){
  fx <- d_u_e
   fy <- d_u_v
- fz <- ass$prap
-
- # persp(x = seq(-1, 1, by = 0.1),
-   #   y = seq(-1, 1, by = 0.1),
-   #   fz)
-
-  d <- plot3d(fx,fy,fz,col="blue")
-  rgl.postscript("d.eps",fmt="eps")
-
- test_trida <- plot_ly(x=fx,y=fy,z=fz, type="scatter3d", mode="markers", color=fz) %>% layout(legend = list(x = 0.1, y = 0.9))
- #p <- export(p = last_plot(),file = "plotly.png", selenium = NULL)
- #fx
-
-# test_trid <- plot3d(df_3$a,df_3$b,df_3$C)
-
-# plotly_IMAGE(test_trida, width = 500, height = 500, format = "png", scale = 2, out_file = "test.png")
-
-#is.data.frame(ass)
-#  print(plot_fina_rast)
-
-print(plot_fina_rast)
-
-# knitr::include_graphics("gg.png" )
-
-# plot3d(fx,fy,fz, col = "blue",xlab = "eth",ylab="val",zlab="prob", type = "s",size = 2)
-
-```
-
-```{r heat2,  fig.width=5,fig.height=4,fig.cap="Probability to choose alternative location",fig.align="center", include=TRUE, echo=FALSE}
+  fz <- b$prob
+
+  tit <- paste0("Ethnic weight = ",b$e_w*k,"; ","Value weight = ",b$v_w*k, "\n\r -1:MIN Alternative, 1:MAX Alternative")
+
+   test_trida <- plot_ly(x=fx,y=fy,z=fz, type="scatter3d", color=fz, mode="markers")  %>% 
+    layout(
+         #  title =  "Prob. relocate to alternative", font=list(size = 10),
+     scene = list(
+       xaxis = list(title = "x = Diff. Ethnic Ut."),
+       yaxis = list(title = "y = Diff. Value Ut."),
+       zaxis = list(title = "z = Probability")
+     ), annotations = (list(x = 0.5, y = 0.8, text = tit ,
+                           showarrow = F, font=list(size=18) #,
+     #  xref='paper', yref='paper',
+      # xanchor='right', yanchor='auto', xshift=0, yshift=0,
+   #  font=list(size=15, color="red")
+     ))
+  # , legend = list(color = fz)
+   ) %>% hide_colorbar()
+
+ test_trida
+
+ }
+
+# 
+# 
+#  plot3d_0 <- prob_3d(df_0)
+#  plot3d_5 <- prob_3d(df_05)
+#  plot3d_maxe <- prob_3d(df_maxe)
+#  plot3d_maxv <- prob_3d(df_maxv)
+#  plot3d_1 <- prob_3d(df_1)
+#  plot3d_r <- prob_3d(df_r)
+
+                  # prob_3d(df_0)
+                  # prob_3d(df_05)
+                  # prob_3d(df_maxe)
+                  # prob_3d(df_maxv)
+                  # prob_3d(df_1)
+                  # prob_3d(df_r)
+  # 
+  # plot3d_0
+  # plot3d_5
+  # plot3d_maxe
+  # plot3d_maxv
+  # plot3d_1
+  # plot3d_r
+
+p_0 <- image_read("3d_0_0.png") %>% image_trim()
+p_5 <- image_read("3d_5_5.png") %>% image_trim()
+p_10_0 <- image_read("3d_10_0.png") %>% image_trim()
+p_0_10 <- image_read("3d_0_10.png") %>% image_trim()
+p_100 <- image_read("3d_100_100.png") %>% image_trim()
+p_1 <- image_read("3d_1_1.png") %>% image_trim()
+
+de <- ggdraw() + draw_image("3d_0_0.png")
+fe <- ggdraw() + draw_image("3d_5_5.png")
+te <- ggdraw() + draw_image("3d_10_0.png")
+ne <- ggdraw() + draw_image("3d_0_10.png")
+se <- ggdraw() + draw_image("3d_100_100.png")
+ze <- ggdraw() + draw_image("3d_1_1.png")
+# 
+grid.arrange(de,fe,te,ne,se,ze,ncol=2,nrow=3)
+
+# knitr::include_graphics("3d_0_0.png")
+# knitr::include_graphics("3d_5_5.png")
+# knitr::include_graphics("3d_10_0.png")
+# knitr::include_graphics("3d_0_10.png")
+# knitr::include_graphics("3d_100_100.png")
+# knitr::include_graphics("3d_1_1.png")
+
+```
+
+```{r logistic,  fig.width=4,fig.height=3, fig.align="center", include=TRUE, echo=FALSE}
 
@@
 
-magic_for(print,silent = TRUE)
-
-for (i in seq (-1.0,1.0, by = 0.1)){
-  eth_diff <- rep(i,21)
-  print(eth_diff)
-}
-
-d_u_e <-  magic_result_as_vector()
-d_u_v <- rep(seq(-1,1,by = 0.1),21) 
-e_w <- 0
-v_w <- 1-e_w
-k <- 10
-
-df <- data.frame(d_u_e,d_u_v,e_w,v_w)
-
-title_cond_fin <- paste0("Ethnic weight = ",e_w*k,"; ","Value weight = ",v_w*k)
-ass <- mutate(df, prap = prob(d_u_e, d_u_v,e_w,v_w))
-fina_rast <- ggplot(ass,aes(d_u_e,d_u_v))
-
- plot_fina_rast <-  suppressWarnings(suppressMessages(
-    fina_rast + geom_raster(aes(fill = prap)) + theme_bw() + labs(x = "Diff.
-ethnic (alternative - current)",y = "Diff.
-value (alternative - current)") + labs(title = title_cond_fin, caption = "-1: Min Utility Alternative; 1: Max Utility Alternative") + theme(plot.title = element_text(hjust = 0.5), plot.subtitle = element_text(hjust=0.5),plot.caption = element_text(hjust=0.5))
-    + geom_vline(xintercept = 0, colour = "red", linetype = "dotted") + geom_hline(yintercept = 0, colour = "red", linetype = "dotted") + scale_fill_continuous(name = "Probability")
-  ))
-
- fx <- d_u_e
- fy <- d_u_v
- fz <- ass$prap
-
- # persp(x = seq(-1, 1, by = 0.1),
-   #   y = seq(-1, 1, by = 0.1),
-   #   fz)
-
-#  d <- plot3d(fx,fy,fz,col="blue")
-#  rgl.postscript("d.eps",fmt="eps")
-
- test_trida <- plot_ly(x=fx,y=fy,z=fz, type="scatter3d", mode="markers", color=fz) 
- #p <- export(p = last_plot(),file = "plotly.png", selenium = NULL)
- #fx
-
-# test_trid <- plot3d(df_3$a,df_3$b,df_3$C)
-
-# plotly_IMAGE(test_trida, width = 500, height = 500, format = "png", scale = 2, out_file = "test.png")
-
-#is.data.frame(ass)
-#  print(plot_fina_rast)
-
-print(test_trida)
-print(plot_fina_rast)
-
-# knitr::include_graphics("gg.png" )
-
-# plot3d(fx,fy,fz, col = "blue",xlab = "eth",ylab="val",zlab="prob", type = "s",size = 2)
-
-```
-
-```{r logistic,  fig.width=4,fig.height=3, fig.align="center", include=TRUE, echo=FALSE}
-
-# to add: -1 for MIN. Utility Alternative, +1 for MAX Alternative Utility
-
 for (d_u_e in seq (-1.0,1.0, by = 0.1)){
 
-e_w <- 0.6
-v_w <- 1 - e_w
+e_w <- 100
+v_w <- 100
 k <- 10
@@
 
-  print(final_prob)
+  plot(final_prob)
 

### 2019-08-21 paper_notes.Rmd
OK, to simplify

@@
 
-install.packages("tinytex", repos = "https://cloud.r-project.org" )
+# install.packages("tinytex", repos = "https://cloud.r-project.org" )
 
@@
 
-prob <- function(d_u_e,d_u_v,e_w,v_w){round(1 / (1 + exp(-(e_w*k)*(d_u_e) + (-(v_w*k)*(d_u_v)))),digits= 2)}
+prob <- function(d_u_e,d_u_v,e_w,v_w){round(1 / (1 + exp((-(e_w*k)*(d_u_e)) + (-(v_w*k)*(d_u_v)))),digits= 2)}
 
@@
 
-```{r testaa,  fig.width=12,fig.height=12,fig.cap="Probability to choose alternative location",fig.align="center", include=TRUE, echo=FALSE}
+$$
+P_j=\frac{1}{1 + \exp((-ew\cdot k\times \Delta_{U_e})+(-vw\cdot k \times \Delta_{U_v}))}
+% P_{xj}=\frac{1}{1 + \exp((-ew\cdot k\times \Delta(U_e^x,U_e^j))+(-vw\cdot k \times \Delta(U_v^x,U_v^j))}
+$$
+
+Where:\par
+- $P_j$: Probability to relocate to alternative neighborhood \textit{j} leaving the current neighborhood
+- $ew$:  Ethnic weight of agent \textit{i}
+- $\Delta_{U_e}$: Ethnic Utility Difference (alternative - current)
+- $vw$: Value weight \textit{i}
+- $\Delta_{U_e}$: Value Utility Difference (alternative - current)
+- $k$: constant
+
+The idea of $k$ constant is to include the parameter of determinism in the random utility formula, i.e.
+from 0: the probabiity to choose the alternative is totally random due to random term $\epsilon$, to infinity, the best option is taken with probability equal to 1.
+To reduce the number of parameters, and being constitent with the conceptual model, I derive the parameter for ethnic utility from the ethnic weight $ew$ and the parameter for value utility from the value weight $vw$ in the agent-based  model.
+Remember that $ew$ ranges $[0,1]$ according to beta distribution, and $vw$ is calculated as $1-ew$.
+The parameter is calculated as $k\cdot ew$ and $k \cdot vw$, meaning that with $k=10$, the parameter for ethnic utility will range from 0 to 10, $k=100$, range from 0 to 100, $k = 0$: all agents will have parameter equal 0.
+It will be one slider in the agent-based model.\par
+The aim of the logistic function above is to implement the random  utility for a binary choice for the agent between the current location $x$ and alternative location $j$, with $P_{xj}=0$ meaning the agent stays on the current location, $P_{xj}=1$ the agent moves to the alternative location $j$.\par
+Below I report some graphs on $P_{xj}$ where the logistic funtion above is implemented for each combination of ethnic utility difference $\Delta_{U_e}$ and value utility difference $\Delta_{U_v}$.
+These are the possible values expected from the agent-based model: assuming that both the ethnic and value utility for each location ranges from 0 to 1, the difference (alternative - current) ranges from -1 (alternative = 0, current = 1), to 1 (alternative =1, current = 0), with 0 meaning equal utility sizes.
+This creates 11 levels  for each utility, $\times$ 2 number of utility = 441 conditions.
+The aim of the graphs was to relate the probability as function of 2 dimensions, so I use the heatmaps in fig.\ref{fig:heatmaps}.
+They have the same content of the 3D plots in fig.\ref{fig:prob3D} which I think serve better the scope: in the R code you can interact with the graph and see actual probability for each point, but need to do it from the RStudio interface.\par
+Each graph reports the parameter ethnic weight $ew \cdot k$ and parameter value weight $vw \cdot k$.
+In all conditions $k = 10$, which I saw shows most realistic scenarios, i.e.
+lower probability for lower ethnic/utility difference.
+To check if the random utility for binary choice is correctly implemented, $P_{xj}=0.50$ with $ew \cdot k = 0$ and $vw \cdot k = 0$, meaning the choice between current and alternative location is totally random.
+In the last condition $ew \cdot k = 100$ and $vw \cdot k = 100$, $P_{xj}=0$ for all conditions where current location is higher in both types of utility (below the diagonal), shifts to $P_{xj}=1$ for all conditions with both utilities higher in the alternative location (above the diagonal), and $P_{xj}=0.5$ on the diagonal where the alternatives have same utility with difference equal 0.
+So the choice is totally dependent on the characteristic of the neighborhood, with the best option being taken.
+I think it can confirm the random utility framework for two options.
+
+```{r heatmaps,  fig.width=12,fig.height=12,fig.cap="Probability to choose alternative location",fig.align="center", include=TRUE, echo=FALSE}
 
@@
 
-```{r test3D,  fig.width=18,fig.height=18,fig.cap="Probability to choose alternative location 3D",fig.align="center", include=TRUE, echo=FALSE}
+```{r prob3D,  fig.width=18,fig.height=18,fig.cap="Probability to choose alternative location 3D",fig.align="center", include=TRUE, echo=FALSE}
 
@@
        zaxis = list(title = "z = Probability")
-     ), annotations = (list(x = 0.5, y = 0.8, text = tit ,
+     ), annotations = (list(x = 0.5, y = 1, text = tit ,
                            showarrow = F, font=list(size=18) #,
@@
   #
-  # plot3d_0
-  # plot3d_5
-  # plot3d_maxe
-  # plot3d_maxv
-  # plot3d_1
-  # plot3d_r
-
-p_0 <- image_read("3d_0_0.png") %>% image_trim()
-p_5 <- image_read("3d_5_5.png") %>% image_trim()
-p_10_0 <- image_read("3d_10_0.png") %>% image_trim()
-p_0_10 <- image_read("3d_0_10.png") %>% image_trim()
-p_100 <- image_read("3d_100_100.png") %>% image_trim()
-p_1 <- image_read("3d_1_1.png") %>% image_trim()
+
+# p_0 <- image_read("3d_0_0.png") %>% image_trim()
+# p_5 <- image_read("3d_5_5.png") %>% image_trim()
+# p_10_0 <- image_read("3d_10_0.png") %>% image_trim()
+# p_0_10 <- image_read("3d_0_10.png") %>% image_trim()
+# p_100 <- image_read("3d_100_100.png") %>% image_trim()
+# p_1 <- image_read("3d_1_1.png") %>% image_trim()
 
@@
 # 
-grid.arrange(de,fe,te,ne,se,ze,ncol=2,nrow=3)
+grid.arrange(de,fe,te,ne,ze,se,ncol=2,nrow=3)
 

### 2019-08-22 paper_notes.Rmd
Add files via upload

--- 2019-08-19 paper_notes.Rmd
@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE, fig.lp="fig:")
+knitr::opts_chunk$set(echo = TRUE, fig.lp="fig:",warning = FALSE)
 
-install.packages("tinytex", repos = "https://cloud.r-project.org" )
+# install.packages("tinytex", repos = "https://cloud.r-project.org" )
 
@@
 library(ggpubr)
-# library(kableExtra)
 library(dplyr)
@@
 library(plotly)
+library(tidyr)
+library(plyr)
+library(rgl)
+library(graphics)
+library(cowplot)
+library(magick) 
+library(xtable)
 
-# Here functions that are used.
-
-# Calculation ethnic utility (for each option)
-# i_e: ethnic threshold (ideal point)
-# M: right-side decreasing slope
-# x: number agents in neighborhood with same color
-# n: total number agents in neighborhood
-# S: left-side increasing slope
-# Note: if (x > n){U <- NA} to show the case number of agents in neighborhood different from 8, so that utility is calculated based on this, although x-axis in graph has 8 points  (excluded from calculation)
-
- #  f_eth <- function(i_e,M,x,n,S){
-  #   if (x > n){
-  #     U <- NA}else{
- #   if (x < round(n*i_e,digits = 2)){
-  #    U <- (x / round((n*i_e),digits = 2)) * S
- #      }else {
- #      U <- M + ((1- (x/n))*(1-M))/(1-i_e)   
-  #    }
-#     round(U,digits = 2)
- #      }
-#   }
+# Calculation ethnic utility
 
@@
 
-# Calculation value utility (for each option)
+# Calculation value utility
 
@@
 
-# Probability (random utility with logistic regression) to relocate
+# ethnic utility difference and value utility difference
 
-prob <- function(d_u_e,d_u_v,e_w,v_w){round(1 / (1 + exp(-(e_w*k)*(d_u_e) + (-(v_w*k)*(d_u_v)))),digits= 2)}
+magic_for(print,silent = TRUE)
 
-# install.packages("tinytex", repos = "https://cloud.r-project.org" ) if debug needed?
+for (i in seq (-1.0,1.0, by = 0.1)){
+  eth_diff <- rep(i,21)
+  print(eth_diff)
+}
+
+d_u_e <-  magic_result_as_vector()
+d_u_v <- rep(seq(-1,1,by = 0.1),21)
+
+dfprob <- data.frame(d_u_e,d_u_v,e_w=0,v_w=0,k=0)
+
+dfprob
+# Probability to move to alternative (random utility with logistic regression)
+
+prob <- function(d_u_e,d_u_v,e_w,v_w,k){round(1 / (1 + exp((-(e_w*k)*(d_u_e)) + (-(v_w*k)*(d_u_v)))),digits= 2)}
+
+prob_3d <- function(b){
+  fx <- d_u_e
+  fy <- d_u_v
+  fz <- b$prob
+
+  tit <- paste0("Ethnic weight = ",b$e_w*b$k,"; ","Value weight = ",b$v_w*b$k, "\n\r -1:MIN Alternative, 1:MAX Alternative")
+
+   tridi_prob <- plot_ly(x=fx,y=fy,z=fz, type="scatter3d", color=fz, mode="markers")  %>% 
+    layout(scene = list(
+       xaxis = list(title = "x = Diff. Ethnic Ut."),
+       yaxis = list(title = "y = Diff. Value Ut."),
+       zaxis = list(title = "z = Probability")
+     ), 
+     annotations = (list(x = 0.5, y = 1, text = tit, showarrow = F, font=list(size=18)
+     ))
+   ) %>% hide_colorbar()
+
+ tridi_prob
+
+ }
+
+# install.packages("tinytex", repos = "https://cloud.r-project.org" ), try if debug needed
 
@@
 ```{r ethnic graph function, fig.width=6,fig.height= 8, fig.align="center",  include=TRUE, echo=FALSE}
-
-# f2 <- function(p,M,x,n,S)
 
@@
 
-# name_E <- paste0("Desired proportion i = ",i_e,"; M = ",M,"; S = ",S)
-# plot(num_sim_col,Utility_T, xlab = "Similar ethnics neighborhood j", ylab = "Ethnic Utility",  main = "Ethnic Utility for neighborhood j of agent i",  sub = name_E)
-# report_E <- paste0("M = ",M,"; S = ",S,"; Desired proportion i = ",i_e,"; Similar ethnics neighborhood j = ", seq(0, 8, by = 1), "; Utility ij = ", Utility_T)
-# print(report_E)
-
-# func_type <- c(rep("symmetric",9),rep("constant",9),rep("threshold",9))
-
 x_graph <- rep(seq(0, 100, by = 12.5),3)
@@
 threshold <- data.frame(x_graph[c(19:27)],utility_location[c(19:27)],funct_symm[c(19:27)])
-
-# symmetric
-# constant
-# threshold
 
@@
 
-# f_val <- function(e_w,ew_ng,M,i_v,S)
-
 e_w <- 0.2
@@
 S <- 0
-M <- 0 #M can be either 0 or 1, M = 0 is for declining slope, M = 1 keeps utility = 1 for values out of range, so S = 0 keeps  the threshold  with values out of the distance equal 0
-# M regulates the right side of the slope, S the left side of the slope
+M <- 0
 
@@
 
-# funct_symm_v <- c(rep("symmetric",9),rep("threshold",9))
-
 symm_val_graph <- ggplot(symm_val,aes(x_graph_val,uti_val_pf))
@@
 
-thres_val_plot <- thres_val_graph + geom_point() + theme_bw() + labs(x = "Mean ethnic weight neighborhood j",y = "Value utility j") + ggtitle(label = "Threshold Schelling (S=0) ",subtitle = subt_cont_v) + theme(plot.title = element_text(hjust = 0.5), plot.subtitle = element_text(hjust = 0.5))  + scale_x_continuous(breaks = seq(0.0,1.0,by = 0.1)) + scale_y_continuous(limits =  c(0.0,1.0), breaks = seq(0.0,1.0,by = 0.25))
-
-# symm_val_plot
-# thres_val_plot
+thres_val_plot <- thres_val_graph + geom_point() + theme_bw() + labs(x = "Mean ethnic weight neighborhood j",y = "Value utility j") + ggtitle(label = "Threshold Schelling (S=0,M=0) ",subtitle = subt_cont_v) + theme(plot.title = element_text(hjust = 0.5), plot.subtitle = element_text(hjust = 0.5))  + scale_x_continuous(breaks = seq(0.0,1.0,by = 0.1)) + scale_y_continuous(limits =  c(0.0,1.0), breaks = seq(0.0,1.0,by = 0.25))
 
@@
 
-Ethnic utility, separating ethnic_weight and ideal payoff for ethnicity (i_e) -> based on ethnicity of agents (color)
-The ethnic weight follows the beta distribution, *maybe* report Blitzstein 4 beta cases, and anyway considering ethnic_weight and value_weight are complementary
+$$
+P_j=\frac{1}{1 + \exp((-ew\cdot k\times \Delta_{U_e})+(-vw\cdot k \times \Delta_{U_v}))}
+$$
 
-Specify n > x <- U:NA in formula
+Where:\par
+- $P_j$: Probability to relocate to alternative neighborhood \textit{j} leaving the current neighborhood
+- $ew$:  Ethnic weight of agent \textit{i}
+- $\Delta_{U_e}$: Ethnic Utility Difference (alternative - current)
+- $vw$: Value weight \textit{i}
+- $\Delta_{U_e}$: Value Utility Difference (alternative - current)
+- $k$: constant
 
-```{r heatmap-log,  fig.width=5,fig.height=4,fig.cap="Probability to choose alternative location",fig.align="center", include=TRUE, echo=FALSE}
+The idea of $k$ constant is to include the parameter of determinism in the random utility formula, i.e.
+from 0: the probabiity to choose the alternative is totally random due to random term $\epsilon$, to infinity, the best option is taken with probability equal to 1.
+To reduce the number of parameters, and being constitent with the conceptual model, I derive the parameter for ethnic utility from the ethnic weight $ew$ and the parameter for value utility from the value weight $vw$ in the agent-based  model.
+Remember that $ew$ ranges $[0,1]$ according to beta distribution, and $vw$ is calculated as $1-ew$.
+The parameter is calculated as $k\cdot ew$ and $k \cdot vw$, meaning that with $k=10$, the parameter for ethnic utility will range from 0 to 10, $k=100$, range from 0 to 100, $k = 0$: all agents will have parameter equal 0.
+It will be one slider in the agent-based model.\par
+The aim of the logistic function above is to implement the random  utility for a binary choice for the agent between the current location $x$ and alternative location $j$, with $P_{xj}=0$ meaning the agent stays on the current location, $P_{xj}=1$ the agent moves to the alternative location $j$.\par
+Below I report some graphs on $P_{xj}$ where the logistic funtion above is implemented for each combination of ethnic utility difference $\Delta_{U_e}$ and value utility difference $\Delta_{U_v}$.
+These are the possible values expected from the agent-based model: assuming that both the ethnic and value utility for each location ranges from 0 to 1, the difference (alternative - current) ranges from -1 (alternative = 0, current = 1), to 1 (alternative =1, current = 0), with 0 meaning equal utility sizes.
+This creates 11 levels  for each utility, $\times$ 2 number of utility = 441 conditions.
+The aim of the graphs was to relate the probability as function of 2 dimensions, so I use the heatmaps in fig.\ref{fig:heatmaps}.
+They have the same content of the 3D plots in fig.\ref{fig:prob3D} which I think serve better the scope: in the R code you can interact with the graph and see actual probability for each point, but need to do it from the RStudio interface (chunk "interact3d").\par
+Each graph reports the parameter ethnic weight $ew \cdot k$ and parameter value weight $vw \cdot k$.
+In all conditions $k = 10$, which I saw shows most realistic scenarios, i.e.
+lower probability for lower ethnic/utility difference.
+To check if the random utility for binary choice is correctly implemented, $P_{xj}=0.50$ with $ew \cdot k = 0$ and $vw \cdot k = 0$, meaning the choice between current and alternative location is totally random.
+In the last condition $ew \cdot k = 100$ and $vw \cdot k = 100$, $P_{xj}=0$ for all conditions where current location is higher in both types of utility (below the diagonal), shifts to $P_{xj}=1$ for all conditions with both utilities higher in the alternative location (above the diagonal), and $P_{xj}=0.5$ on the diagonal where the alternatives have same utility with difference equal 0.
+So the choice is totally dependent on the characteristic of the neighborhood, with the best option being taken.
+I think it can confirm the random utility framework for two options.
 
-# to add: -1 for MIN. Utility Alternative, +1 for MAX Alternative Utility
+```{r heatmaps,  fig.width=12,fig.height=12,fig.cap="Probability to choose alternative location",fig.align="center", include=TRUE, echo=FALSE}
 
-magic_for(print,silent = TRUE)
+k_v <- 10
 
-for (i in seq (-1.0,1.0, by = 0.1)){
-  eth_diff <- rep(i,21)
-  print(eth_diff)
+df_0 <- mutate(dfprob,e_w=0,v_w=0,k=k_v, proba = prob(d_u_e, d_u_v,e_w,v_w,k))
+df_05 <- mutate(dfprob,e_w=0.5,v_w=0.5,k=k_v, proba = prob(d_u_e, d_u_v,e_w,v_w,k))
+df_maxe <- mutate(dfprob,e_w=1,v_w=0,k=k_v, proba = prob(d_u_e, d_u_v,e_w,v_w,k))
+df_maxv <- mutate(dfprob,e_w=0,v_w=1,k=k_v, proba = prob(d_u_e, d_u_v,e_w,v_w,k))
+df_r <- mutate(dfprob,e_w=0.1,v_w=0.1,k=k_v, proba = prob(d_u_e, d_u_v,e_w,v_w,k))
+df_1 <- mutate(dfprob,e_w=10,v_w=10,k=k_v, proba = prob(d_u_e, d_u_v,e_w,v_w,k))
+
+prob_comb <- function(a){
+title_cond_fin <- paste0("Ethnic weight = ",a$e_w*a$k,"; ","Value weight = ",a$v_w*a$k)
+fina_rast <- ggplot(a,aes(d_u_e,d_u_v))
+
+ plot_fina_rast <-  suppressWarnings(suppressMessages(
+    fina_rast + geom_raster(aes(fill = proba)) + theme_bw() + labs(x = "Diff.
+ethnic (alternative - current)",y = "Diff.
+value (alternative - current)") + labs(title = title_cond_fin, caption = "-1: Min Utility Alternative; 1: Max Utility Alternative") + theme(plot.title = element_text(hjust = 0.5), plot.subtitle = element_text(hjust=0.5),plot.caption = element_text(hjust=0.5))
+    + geom_vline(xintercept = 0, colour = "red", linetype = "dotted") + geom_hline(yintercept = 0, colour = "red", linetype = "dotted") + scale_fill_continuous(name = "Probability",limits=c(0,1), breaks=seq(0,1,0.25))
+  ))
 }
 
-d_u_e <-  magic_result_as_vector()
-d_u_v <- rep(seq(-1,1,by = 0.1),21) 
-e_w <- 0
-v_w <- 1-e_w
-k <- 10
+plot_0 <- prob_comb(df_0)
+plot_05 <- prob_comb(df_05)
+plot_maxe <- prob_comb(df_maxe)
+plot_maxv <- prob_comb(df_maxv)
+plot_r <- prob_comb(df_r)
+plot_1 <- prob_comb(df_1)
 
-df <- data.frame(d_u_e,d_u_v,e_w,v_w)
-
-title_cond_fin <- paste0("Ethnic weight = ",e_w*k,"; ","Value weight = ",v_w*k)
-ass <- mutate(df, prap = prob(d_u_e, d_u_v,e_w,v_w))
-fina_rast <- ggplot(ass,aes(d_u_e,d_u_v))
-
- plot_fina_rast <-  suppressWarnings(suppressMessages(
-    fina_rast + geom_raster(aes(fill = prap)) + theme_bw() + labs(x = "Diff.
-ethnic (alternative - current)",y = "Diff.
-value (alternative - current)") + labs(title = title_cond_fin, caption = "-1: Min Utility Alternative; 1: Max Utility Alternative") + theme(plot.title = element_text(hjust = 0.5), plot.subtitle = element_text(hjust=0.5),plot.caption = element_text(hjust=0.5))
-    + geom_vline(xintercept = 0, colour = "red", linetype = "dotted") + geom_hline(yintercept = 0, colour = "red", linetype = "dotted") + scale_fill_continuous(name = "Probability")
-  ))
-
- fx <- d_u_e
- fy <- d_u_v
- fz <- ass$prap
-
- # persp(x = seq(-1, 1, by = 0.1),
-   #   y = seq(-1, 1, by = 0.1),
-   #   fz)
-
-  d <- plot3d(fx,fy,fz,col="blue")
-  rgl.postscript("d.eps",fmt="eps")
-
- test_trida <- plot_ly(x=fx,y=fy,z=fz, type="scatter3d", mode="markers", color=fz) %>% layout(legend = list(x = 0.1, y = 0.9))
- #p <- export(p = last_plot(),file = "plotly.png", selenium = NULL)
- #fx
-
-# test_trid <- plot3d(df_3$a,df_3$b,df_3$C)
-
-# plotly_IMAGE(test_trida, width = 500, height = 500, format = "png", scale = 2, out_file = "test.png")
-
-#is.data.frame(ass)
-#  print(plot_fina_rast)
-
-print(plot_fina_rast)
-
-# knitr::include_graphics("gg.png" )
-
-# plot3d(fx,fy,fz, col = "blue",xlab = "eth",ylab="val",zlab="prob", type = "s",size = 2)
+grid.arrange( plot_0,plot_05,plot_maxe,plot_maxv,plot_r,  plot_1,nrow=3,ncol=2)
 
@@
 
-```{r heat2,  fig.width=5,fig.height=4,fig.cap="Probability to choose alternative location",fig.align="center", include=TRUE, echo=FALSE}
+```{r prob3D,  fig.width=18,fig.height=18,fig.cap="Probability to choose alternative location 3D",fig.align="center", include=TRUE, echo=FALSE}
 
-# to add: -1 for MIN. Utility Alternative, +1 for MAX Alternative Utility
+tridi_0_0 <- ggdraw() + draw_image("3d_0_0.png")
+tridi_5_5 <- ggdraw() + draw_image("3d_5_5.png")
+tridi_10_0 <- ggdraw() + draw_image("3d_10_0.png")
+tridi_0_10 <- ggdraw() + draw_image("3d_0_10.png")
+tridi_100_100 <- ggdraw() + draw_image("3d_100_100.png")
+tridi_1_1 <- ggdraw() + draw_image("3d_1_1.png")
 
-magic_for(print,silent = TRUE)
-
-for (i in seq (-1.0,1.0, by = 0.1)){
-  eth_diff <- rep(i,21)
-  print(eth_diff)
-}
-
-d_u_e <-  magic_result_as_vector()
-d_u_v <- rep(seq(-1,1,by = 0.1),21) 
-e_w <- 0
-v_w <- 1-e_w
-k <- 10
-
-df <- data.frame(d_u_e,d_u_v,e_w,v_w)
-
-title_cond_fin <- paste0("Ethnic weight = ",e_w*k,"; ","Value weight = ",v_w*k)
-ass <- mutate(df, prap = prob(d_u_e, d_u_v,e_w,v_w))
-fina_rast <- ggplot(ass,aes(d_u_e,d_u_v))
-
- plot_fina_rast <-  suppressWarnings(suppressMessages(
-    fina_rast + geom_raster(aes(fill = prap)) + theme_bw() + labs(x = "Diff.
-ethnic (alternative - current)",y = "Diff.
-value (alternative - current)") + labs(title = title_cond_fin, caption = "-1: Min Utility Alternative; 1: Max Utility Alternative") + theme(plot.title = element_text(hjust = 0.5), plot.subtitle = element_text(hjust=0.5),plot.caption = element_text(hjust=0.5))
-    + geom_vline(xintercept = 0, colour = "red", linetype = "dotted") + geom_hline(yintercept = 0, colour = "red", linetype = "dotted") + scale_fill_continuous(name = "Probability")
-  ))
-
- fx <- d_u_e
- fy <- d_u_v
- fz <- ass$prap
-
- # persp(x = seq(-1, 1, by = 0.1),
-   #   y = seq(-1, 1, by = 0.1),
-   #   fz)
-
-#  d <- plot3d(fx,fy,fz,col="blue")
-#  rgl.postscript("d.eps",fmt="eps")
-
- test_trida <- plot_ly(x=fx,y=fy,z=fz, type="scatter3d", mode="markers", color=fz) 
- #p <- export(p = last_plot(),file = "plotly.png", selenium = NULL)
- #fx
-
-# test_trid <- plot3d(df_3$a,df_3$b,df_3$C)
-
-# plotly_IMAGE(test_trida, width = 500, height = 500, format = "png", scale = 2, out_file = "test.png")
-
-#is.data.frame(ass)
-#  print(plot_fina_rast)
-
-print(test_trida)
-print(plot_fina_rast)
-
-# knitr::include_graphics("gg.png" )
-
-# plot3d(fx,fy,fz, col = "blue",xlab = "eth",ylab="val",zlab="prob", type = "s",size = 2)
+grid.arrange(tridi_0_0,tridi_5_5,tridi_10_0,tridi_0_10,tridi_1_1,tridi_100_100,ncol=2,nrow=3)
 
@@
 
-```{r logistic,  fig.width=4,fig.height=3, fig.align="center", include=TRUE, echo=FALSE}
+```{r interact3D, include=TRUE,echo= FALSE}
 
-# to add: -1 for MIN. Utility Alternative, +1 for MAX Alternative Utility
+# To explore the 3D graph, select all lines and run (alt + Enter), or change in line above r interact3D, include = TRUE
 
-for (d_u_e in seq (-1.0,1.0, by = 0.1)){
+prob_3d(df_0)
+prob_3d(df_05)
+prob_3d(df_maxe)
+prob_3d(df_maxv)
+prob_3d(df_1)
+prob_3d(df_r)
 
-e_w <- 0.6
-v_w <- 1 - e_w
-k <- 10
-
-# d_u_e <- -1
-
-dis_1neg   <- prob(d_u_e,-1.0,e_w,v_w)
-dis_0.9neg <- prob(d_u_e,-0.9,e_w,v_w)
-dis_0.8neg <- prob(d_u_e,-0.8,e_w,v_w)
-dis_0.7neg <- prob(d_u_e,-0.7,e_w,v_w)
-dis_0.6neg <- prob(d_u_e,-0.6,e_w,v_w)
-dis_0.5neg <- prob(d_u_e,-0.5,e_w,v_w)
-dis_0.4neg <- prob(d_u_e,-0.4,e_w,v_w)
-dis_0.3neg <- prob(d_u_e,-0.3,e_w,v_w)
-dis_0.2neg <- prob(d_u_e,-0.2,e_w,v_w)
-dis_0.1neg <- prob(d_u_e,-0.1,e_w,v_w)
-dis_0   <- prob(d_u_e,0.0,e_w,v_w)
-dis_0.1 <- prob(d_u_e,0.1,e_w,v_w)
-dis_0.2 <- prob(d_u_e,0.2,e_w,v_w)
-dis_0.3 <- prob(d_u_e,0.3,e_w,v_w)
-dis_0.4 <- prob(d_u_e,0.4,e_w,v_w)
-dis_0.5 <- prob(d_u_e,0.5,e_w,v_w)
-dis_0.6 <- prob(d_u_e,0.6,e_w,v_w)
-dis_0.7 <- prob(d_u_e,0.7,e_w,v_w)
-dis_0.8 <- prob(d_u_e,0.8,e_w,v_w)
-dis_0.9 <- prob(d_u_e,0.9,e_w,v_w)
-dis_1   <- prob(d_u_e,1.0,e_w,v_w)
-
-  value_difference <- seq(-1.0,1.0, by = 0.1)
-#  prob_relocation <- seq(0.0, 1.0,  by = 0.1)
-
-  prob_choice <- c(dis_1neg,dis_0.9neg,dis_0.8neg,dis_0.7neg,dis_0.6neg,dis_0.5neg,dis_0.4neg,dis_0.3neg,dis_0.2neg,dis_0.1neg,dis_0,dis_0.1,dis_0.2,dis_0.3,dis_0.4,dis_0.5,dis_0.6,dis_0.7,dis_0.8,dis_0.9,dis_1)
-
-  title_cond_prob <- paste0("PROB ALT","Diff eth = ",d_u_e,"Ew = ",e_w*10,"Vw = ",v_w*10)
-
-  report_prob <- na.omit(data.frame(value_difference,prob_choice))
-
-  plot_report_prob <- ggplot(report_prob,aes(value_difference,prob_choice))
-
- final_prob <-  suppressWarnings(suppressMessages(
-    plot_report_prob + geom_point() + theme_bw() + labs(x = "DIFF VAL",y = "Probability") + ggtitle(label = title_cond_prob) + theme(plot.title = element_text(hjust = 0.5)) + scale_y_continuous(limits =  c(0.0,1.0), breaks = seq(0.0,1.0,by = 0.25)) + scale_x_continuous(limits =  c(-1,1), breaks = seq(-1,1,by = 0.2)) + geom_vline(xintercept = 0, colour = "red", linetype = "dotted") + geom_hline(yintercept = 0.5, colour = "red", linetype = "dotted")
-  ))
-
-  print(final_prob)
-
-}
-
+#Plotly seems more adapted for html, but works here
 ```
@@
 ```{r ethnic utility individual-run,fig.width=4,fig.height= 3, fig.align="center", fig.pos="H", include=TRUE, echo=FALSE}
+# ETHNIC UTILITY:
+# Choose parameters for desired ethnic similar proportion (i_e, float number), left-slope utility curve (S),right-slope utility curve (M),total number of agents in the neighborhood (n), then run (green arrow top-right).
+# The calculations are done for a max=8 neighbors (assuming we keep 8-patches Moore neighbor in NetLogo). Utility can be calculated with n > 8, but table row and x-axis graph will stop at 8.
 
-# f2 <- function(p,M,x,n,S)
+i_e = 0.5   # parameters to manipulate
+S = 0     # Symmetric single-peaked function: S=1,M=0
+M = 0     # Linear + Constant function = S=1,M=1
+n = 8     # Schelling Threshold function = S=0,M=1
 
-i_e = 0.2
-S = 0
-M = 1
-n = 6
-
-f0m <- f_eth(i_e,M,0,n,S)
+f0m <- f_eth(i_e,M,0,n,S) # ethnic utility for each option, the increasing number is the number of agents of same ethnicity
 f1m <- f_eth(i_e,M,1,n,S)
@@
 
-# num_sim_col <- seq(0, 8, by = 1)
-Utility_E <- c(f0m,f1m,f2m,f3m,f4m,f5m,f6m,f7m,f8m)
-# name_E <- paste0("Desired proportion i = ",i_e,"; M = ",M,"; S = ",S)
-
-# plot(num_sim_col,Utility_E, xlab = "Similar ethnics neighborhood j", ylab = "Ethnic Utility",  main = "Ethnic Utility for neighborhood j of agent i",  sub = name_E)
-
-#report_E <- paste0("M = ",M,"; S = ",S,"; Desired proportion i = ",i_e,"; Similar ethnics neighborhood j = ", seq(0, 8, by = 1), "; Utility ij = ", Utility_E)
+Utility_E <- c(f0m,f1m,f2m,f3m,f4m,f5m,f6m,f7m,f8m)    # used to make up table and graph
 
@@
 
-knitr::kable(report_E,align="c") # much better printed visualization
+suppressWarnings(suppressMessages(
+knitr::kable(report_E,align="c")
+))
 
@@
 
-```{r value individual run,fig.width=5,fig.height= 3, fig.align="center", fig.pos="H", include=TRUE, echo=FALSE }
+```{r value individual run,fig.width=5, fig.height= 3, fig.align="center", fig.pos="H", include=TRUE, echo=FALSE }
+# VALUE UTILITY:
+# Choose parameters for ethnic weight of agent i (e_w), desired value distance (i_v), left-slope utility curve (S),right-slope utility curve (M).
+# The calculations are done for each ethnic weight mean of the neighborhood, from 0 to 1.
+The extreme case is desired value distance 1, meaning all mean ethnic weight of the neighborhood are included.
+Values of i_v > 1 would not affect results, but nonsense
 
-e_w <- 0.4
-i_v <- 0.2
-S  <- 1
-M <- 0 #S regulates the left side of the slope, M the right side
+e_w <- 0.4    # parameters to manipulate
+i_v <- 0
+S  <- 0
+M <- 0
 
-fv0d2 <- f_val(e_w,0,M,i_v,S)
+fv0d2 <- f_val(e_w,0,M,i_v,S)      # value utility for each option, the increasing number is the ethnic weight of neighborhood j
 fv1d2 <- f_val(e_w,0.1,M,i_v,S)
@@
 
-# name_V <- paste0("Ethnic weight i = ", e_w,"; desired distance i = ",i_v,"; M = ",M,"; S = ",S)
+Utility_V <- c(fv0d2,fv1d2,fv2d2,fv3d2,fv4d2,fv5d2,fv6d2,fv7d2,fv8d2,fv9d2,fv10d2)  # used to make up table and graph
 
@@
 ew_agent <- rep(e_w,11)
-Utility_V <- c(fv0d2,fv1d2,fv2d2,fv3d2,fv4d2,fv5d2,fv6d2,fv7d2,fv8d2,fv9d2,fv10d2)
 Mv <- rep(M,11)
@@
 
-title_cond_V <- paste0("Ethnic weight i = ", e_w,"; desired distance i = ",i_v,"\n\r","M = ",M,"S = ",S)
+title_cond_V <- paste0("Ethnic weight i = ", e_w,"; desired distance i = ",i_v,"\n\r","M =", M,"; ", "S = ",S)
 
@@
 
-# plot(value_mean_neighborhood,Utility_V, xlab = "Mean ethnic weight neighborhood j", ylab = "Value Utility neighborhood j",  main = "Value Utility for neighborhood j of agent i",  sub = name_V)
-
-# report_v <- paste0(name_V,"; Mean ethnic weight j = ", seq(0.0, 1.0, by = 0.1), "; Utility ij = ", Utility_V)
-
-knitr::kable(report_V,align="c") # much better printed visualization
-
-# print(final_v)
-# print(final_repV)
+suppressWarnings(suppressMessages(
+knitr::kable(report_V,align = "c")
+))
 
@@
 
-```{r ANNEX - ethnic_multiple_run, moore neighborhood, include=TRUE, echo=FALSE}
+```{r logistic, fig.width=5,fig.height=4,fig.align='left',include=TRUE, echo=FALSE}
 
-# f2 <- function(p,M,x,n,S)
+magic_for()
 
-#i_e = 0.5
-M = 0
-S = 1
-n = 8
+e_w <- 0.5
+v_w <- 0.5
+k <- 10
 
-for (i_e in seq (0.0,1.0, by = 0.1)){
+for (d_u_e in seq (-1.0,1.0, by = 0.1)){
 
-f0m <- f_eth(i_e,M,0,n,S)
-f1m <- f_eth(i_e,M,1,n,S)
-f2m <- f_eth(i_e,M,2,n,S)
-f3m <- f_eth(i_e,M,3,n,S)
-f4m <- f_eth(i_e,M,4,n,S)
-f5m <- f_eth(i_e,M,5,n,S)
-f6m <- f_eth(i_e,M,6,n,S)
-f7m <- f_eth(i_e,M,7,n,S)
-f8m <- f_eth(i_e,M,8,n,S)
+dis_1neg   <- prob(d_u_e,-1.0,e_w,v_w,k)
+dis_0.9neg <- prob(d_u_e,-0.9,e_w,v_w,k)
+dis_0.8neg <- prob(d_u_e,-0.8,e_w,v_w,k)
+dis_0.7neg <- prob(d_u_e,-0.7,e_w,v_w,k)
+dis_0.6neg <- prob(d_u_e,-0.6,e_w,v_w,k)
+dis_0.5neg <- prob(d_u_e,-0.5,e_w,v_w,k)
+dis_0.4neg <- prob(d_u_e,-0.4,e_w,v_w,k)
+dis_0.3neg <- prob(d_u_e,-0.3,e_w,v_w,k)
+dis_0.2neg <- prob(d_u_e,-0.2,e_w,v_w,k)
+dis_0.1neg <- prob(d_u_e,-0.1,e_w,v_w,k)
+dis_0   <- prob(d_u_e,0.0,e_w,v_w,k)
+dis_0.1 <- prob(d_u_e,0.1,e_w,v_w,k)
+dis_0.2 <- prob(d_u_e,0.2,e_w,v_w,k)
+dis_0.3 <- prob(d_u_e,0.3,e_w,v_w,k)
+dis_0.4 <- prob(d_u_e,0.4,e_w,v_w,k)
+dis_0.5 <- prob(d_u_e,0.5,e_w,v_w,k)
+dis_0.6 <- prob(d_u_e,0.6,e_w,v_w,k)
+dis_0.7 <- prob(d_u_e,0.7,e_w,v_w,k)
+dis_0.8 <- prob(d_u_e,0.8,e_w,v_w,k)
+dis_0.9 <- prob(d_u_e,0.9,e_w,v_w,k)
+dis_1   <- prob(d_u_e,1.0,e_w,v_w,k)
 
-#num_sim_col <- seq(0, n, by = 1)
-Utility_E <- c(f0m,f1m,f2m,f3m,f4m,f5m,f6m,f7m,f8m)
-#name_E <- paste0("Desired proportion i = ",i_e,"; M = ",M,"; S = ",S)
+  value_difference <- seq(-1.0,1.0, by = 0.1)
 
-#plot(num_sim_col,Utility_Es, xlab = "Similar ethnics neighborhood j", ylab = "Ethnic Utility", ylim = c(0,1),xlim = c(0,n),  main = "Ethnic Utility for neighborhood j of agent i",  sub = name_E)
+  prob_choice <- c(dis_1neg,dis_0.9neg,dis_0.8neg,dis_0.7neg,dis_0.6neg,dis_0.5neg,dis_0.4neg,dis_0.3neg,dis_0.2neg,dis_0.1neg,dis_0,dis_0.1,dis_0.2,dis_0.3,dis_0.4,dis_0.5,dis_0.6,dis_0.7,dis_0.8,dis_0.9,dis_1)
 
-#report_Es <- paste0("M = ",M,"; S = ",S,"; Desired proportion i = ",i_e,"; Similars in j= ", seq(0, n, by = 1), "; Utility ij = ", Utility_Es)
+  title_cond_prob <- paste0("Diff. Ethnic Utility (alternative - current): ",d_u_e)
+  title_caption <-  paste0("Ethnic weight = ",e_w*10," ; ","Value weight = ",v_w*10
+                           ,"\n\r","-1: Min Utility Alternative; 1: Max Utility Alternative"
+                           )
 
-#print(report_Es)
+  report_prob <- na.omit(data.frame(value_difference,prob_choice))
 
-M. <- rep(M,9)
-S. <- rep(S,9)
-prop_des <- rep(i_e,9)
-num_tot <- rep(n,9)
-num_sim <- seq(0, 8, by = 1)
+  plot_report_prob <- ggplot(report_prob,aes(value_difference,prob_choice))
 
-report_E <- na.omit(data.frame(M.,S.,prop_des,num_tot,num_sim,Utility_E))
+ final_prob <-  suppressWarnings(suppressMessages(
+    plot_report_prob + geom_point() + theme_bw() + labs(x = "Diff. Value Utility (alternative - current)",y = "Probability") +
+      labs(title=title_cond_prob, caption = title_caption)
 
-title_cond <- paste0("Desired proportion = ", i_e,"; ", "S = ", S,"; " ,"M = ", M)
-
-plot_report_E <- ggplot(report_E,aes(num_sim,Utility_E))
-
-final_E <- suppressWarnings(suppressMessages(
-plot_report_E + geom_point() + theme_bw() + labs(x = "Number similar agents in j",y = "Ethnic Utility j") + ggtitle(label = title_cond) + theme(plot.title = element_text(hjust = 0.5)) + scale_y_continuous(limits =  c(0.0,1.0), breaks = seq(0.0,1.0,by = 0.25)) + scale_x_continuous(limits =  c(0,n), breaks = seq(0,n,by = 1))
+      + theme(plot.title = element_text(hjust = 0.5),plot.caption = element_text(hjust=0.5)) + scale_y_continuous(limits =  c(0.0,1.0), breaks = seq(0.0,1.0,by = 0.25)) + scale_x_continuous(limits =  c(-1,1), breaks = seq(-1,1,by = 0.2)) + geom_vline(xintercept = 0, colour = "red", linetype = "dotted") + geom_hline(yintercept = 0.5, colour = "red", linetype = "dotted")
   ))
 
-final_repE <- knitr::kable(report_E,align="c") # much better printed visualization
-
-print(final_E)
-print(final_repE)
-
-}
-```
-
-Value utility, based on agents' desired distance (i_v) between the agent's ethnic_weight (e_w) and neighborhood's average ethnic_weight (calculated out of agents residing there)
-Calculate ethnic weight average of neighborhoods with n agents > 0.
-
- **check:** Explain how S and M vary for the constant function, the comment seems lost
-
-```{r ANNEX- value_similarity, echo=FALSE }
-
-i_v <- 0.1
-S  <- 1
-M <- 0 #different values  of M do change results, even for M < 1
-
-for (e_w in seq (0.0,1.0, by = 0.1)){
-
-fv0d2 <- f_val(e_w,0,M,i_v,S)
-fv1d2 <- f_val(e_w,0.1,M,i_v,S)
-fv2d2 <- f_val(e_w,0.2,M,i_v,S)
-fv3d2 <- f_val(e_w,0.3,M,i_v,S)
-fv4d2 <- f_val(e_w,0.4,M,i_v,S)
-fv5d2 <- f_val(e_w,0.5,M,i_v,S)
-fv6d2 <- f_val(e_w,0.6,M,i_v,S)
-fv7d2 <- f_val(e_w,0.7,M,i_v,S)
-fv8d2 <- f_val(e_w,0.8,M,i_v,S)
-fv9d2 <- f_val(e_w,0.9,M,i_v,S)
-fv10d2 <- f_val(e_w,1.0,M,i_v,S)
-
-# name_V <- paste0("Ethnic weight i = ", e_w,"; desired distance i = ",i_v,"; M = ",M,"; S = ",S)
-
-mean_ew_ng <- seq(0.0, 1.0, by = 0.1)
-ew_agent <- rep(e_w,11)
-Utility_V <- c(fv0d2,fv1d2,fv2d2,fv3d2,fv4d2,fv5d2,fv6d2,fv7d2,fv8d2,fv9d2,fv10d2)
-Mv <- rep(M,11)
-Sv <- rep(S,11)
-des_dist <- rep(i_v,11)
-
-report_V <- na.omit(data.frame(Mv,Sv,des_dist,ew_agent,mean_ew_ng,Utility_V))
-
-title_cond_V <- paste0("Ethnic weight i = ", e_w,"; desired distance i = ",i_v,"; M = ",M,"; S = ",S)
-
-plot_report_V <- ggplot(report_V,aes(mean_ew_ng,Utility_V))
-
-final_v <- suppressWarnings(suppressMessages(
-plot_report_V + geom_point() + theme_bw() + labs(x = "Mean ethnic weight j",y = "Value Utility j") + ggtitle(label = title_cond_V) + theme(plot.title = element_text(hjust = 0.5)) + scale_y_continuous(limits =  c(0.0,1.0), breaks = seq(0.0,1.0,by = 0.25)) + scale_x_continuous(limits =  c(0,1), breaks = seq(0,1,by = 0.1))
-))
-
-# plot(value_mean_neighborhood,Utility_V, xlab = "Mean ethnic weight neighborhood j", ylab = "Value Utility neighborhood j",  main = "Value Utility for neighborhood j of agent i",  sub = name_V)
-
-# report_v <- paste0(name_V,"; Mean ethnic weight j = ", seq(0.0, 1.0, by = 0.1), "; Utility ij = ", Utility_V)
-
-final_repV <- knitr::kable(report_V,align="c") # much better printed visualization
-
-print(final_v)
-print(final_repV)
+  plot(final_prob)
 
@@
 
-Once calculated the ethnic utility and value utility, apply prob above (logistic function) in the decision rule of the agent, with prob(to_new) >= random-float 0-1
+```{r test, fig.width=5,fig.height=4,fig.align='left',include=TRUE, echo=FALSE}
 
-```{r logistic in sequence, to test with parameters, to be deleted}
-# 
-# prob <- function(d_u_e,d_u_v,par_e,par_v){round(1 / (1 + exp(-par_e*(d_u_e) + (-par_v*(d_u_v)))),digits= 2)}
-# 
-# for (d_u_e in seq (-1.0,1.0, by = 0.1)){
-#   
-# par_e <- 10
-# par_v <- 10 - par_e
-# 
-# # d_u_e <- -1
-# 
-#   dis_0p   <- prob(d_u_e,0.0,par_e,par_v)
-# dis_0.1p <- prob(d_u_e,0.1,par_e,par_v)
-# dis_0.2p <- prob(d_u_e,0.2,par_e,par_v)
-# dis_0.3p <- prob(d_u_e,0.3,par_e,par_v)
-# dis_0.4p <- prob(d_u_e,0.4,par_e,par_v)
-# dis_0.5p <- prob(d_u_e,0.5,par_e,par_v)
-# dis_0.6p <- prob(d_u_e,0.6,par_e,par_v)
-# dis_0.7p <- prob(d_u_e,0.7,par_e,par_v)
-# dis_0.8p <- prob(d_u_e,0.8,par_e,par_v)
-# dis_0.9p <- prob(d_u_e,0.9,par_e,par_v)
-# dis_1p  <- prob(d_u_e,1.0,par_e,par_v)
-# dis_0.1negp <- prob(d_u_e,-0.1,par_e,par_v)
-# dis_0.2negp <- prob(d_u_e,-0.2,par_e,par_v)
-# dis_0.3negp <- prob(d_u_e,-0.3,par_e,par_v)
-# dis_0.4negp <- prob(d_u_e,-0.4,par_e,par_v)
-# dis_0.5negp <- prob(d_u_e,-0.5,par_e,par_v)
-# dis_0.6negp <- prob(d_u_e,-0.6,par_e,par_v)
-# dis_0.7negp <- prob(d_u_e,-0.7,par_e,par_v)
-# dis_0.8negp <- prob(d_u_e,-0.8,par_e,par_v)
-# dis_0.9negp <- prob(d_u_e,-0.9,par_e,par_v)
-# dis_1negp   <- prob(d_u_e,-1.0,par_e,par_v)
-#   
-#   value_difference <- seq(-1.0,1.0, by = 0.1)
-#   prob_relocation <- seq(0.0, 1.0,  by = 0.1)
-#   
-#   prob_choicep <- c(dis_1negp,dis_0.9negp,dis_0.8negp,dis_0.7negp,dis_0.6negp,dis_0.5negp,dis_0.4negp,dis_0.3negp,dis_0.2negp,dis_0.1negp,dis_0p,dis_0.1p,dis_0.2p,dis_0.3p,dis_0.4p,dis_0.5p,dis_0.6p,dis_0.7p,dis_0.8p,dis_0.9p,dis_1p)
-#   
-#   name_diff <- paste0("Note: "," Ethnic parameter = ", par_e," ;"," Value parameter = ", par_v, 
-#                       "\r\n Utility Difference -1 = MIN Utility Alternative, 1 = MAX Utility Alternative")
-#   
-#   name_diff_title <-paste0("Probability to move to alternative","\r\n Difference Ethnic Utility (Alternative - Current) = ", d_u_e)
-#   
-# plot(value_difference,prob_choicep, xlab = "x-axis: Difference Value Utility (Alternative - Current) \r\n",ylab = "probability", main = name_diff_title, sub = name_diff,ylim = c(0,1), yaxt = 'n')
-# axis(2,at=seq(0.0, 1.0, by = 0.25))
+e_w_v <- 0.5
+v_w_v <- 1-e_w_v
+k_v <- 10
 
-#}
+dfprob_log <- mutate(dfprob,e_w=e_w_v,v_w=v_w_v,k=k_v, probalog = prob(d_u_e, d_u_v,e_w,v_w,k))
+
+#  report_prob <- na.omit(dfprob_log(d_u_v,probalog))
+
+logi <- function(lo){
+plot_report_prob <- ggplot(dfprob_log[which(d_u_e == lo),],aes(d_u_v,probalog))
+
+  title_cond_prob <- paste0("Diff. Ethnic Utility (alternative - current): ",lo)
+  title_caption <-  paste0("Ethnic weight = ",e_w_v*k_v," ; ","Value weight = ",v_w_v*k_v
+                           ,"\n\r","-1: Min Utility Alternative; 1: Max Utility Alternative"
+                           )
+
+ final_prob <-  suppressWarnings(suppressMessages(
+    plot_report_prob + geom_point() + theme_bw() + labs(x = "Diff. Value Utility (alternative - current)",y = "Probability") +
+      labs(title=title_cond_prob, caption = title_caption)
+
+      + theme(plot.title = element_text(hjust = 0.5),plot.caption = element_text(hjust=0.5)) + scale_y_continuous(limits =  c(0.0,1.0), breaks = seq(0.0,1.0,by = 0.25)) + scale_x_continuous(limits =  c(-1,1), breaks = seq(-1,1,by = 0.2)) + geom_vline(xintercept = 0, colour = "red", linetype = "dotted") + geom_hline(yintercept = 0.5, colour = "red", linetype = "dotted")
+  ))
+
+ final_prob
+
+}
+
+logi(-1)
+logi(-0.9)
+
+}
 
@@
 
-# Component of probability of the choice
-
-- Object of choice: neighborhood
-- Choice: relocate to a neighborhood
-- Utility: payoff one is likely to accept to make the choice, i.e. to relocate to one neighborhood (or stay on current one). In @zhang2004 it is made up of:
-  - deterministic component $U$: how much people desire/value one preference  in order to make the choice as ideal payoff, e.g.
-degree of ethnic concentration (e.g.
-max utility = 1 at 100% similars).
-@zhang2004 uses a single-peaked function (vs maximization).
-  - random term $\epsilon$ that refers to other characteristics of the option, i.e.
-the neighborhood, that influence the choice but independent of utility payoff.
-In regression models  this is the random  error terms.
-Random utility models in abm recreate with the exponential function, so that not always the best option according to the deterministic component $U$ is chosen.
-- Probability of the choice: $\beta u (.) + \epsilon$\, which is conceptually different but related to payoff $u$
-  - $\beta$ is a parameter indicating how much the characteristic of the option is important in the probability to make a choice, or the random term $\epsilon$.
-It is modeled as a positive constant: the lower is $\beta$, the higher is random term $\epsilon$, i.e.
-other random characteristics, are relevant to choose one neighborhood.
-The higher is $\beta$, the lower will be the importance of random term $\epsilon$ and higher the importance of deterministic utility component to make a choice, i.e.
-moving to the neighborhood.
-\
-
-# Aim of the paper
-
-- Independent of the ideal payoff $u$ people have for one characteristic of the neighborhood, my question is why someone should give more importance to that characteristic over the others, that is:
-\par
-why should $\beta$ vary among individuals?
-\par
-An answer in @esser2010 is social, educational, economic capital and how it translates into the investment of people into receiving context/ethnic context and his general suggestion. For instance:
-  - The lower an agent speaks a language, the higher the need for aggregating with co-ethnics would be, so to increase $\beta_{ethnic}$ independently of what is the ideal payoff for ethnic composition of the neighborhood;
-  - the higher is social mobility intention either as investment or value in the own community, the higher the wealth (socio-economic status) of the neighborhood would be $\beta_{status}$
-  - the higher the need to associate with people sharing the same values of local community (receiving context in Esser [@esser2010] (e.g.
-political orientations, norm beliefs...) even as strategy for crossing ethnic boundaries [@wimmer2013], the higher the composition of value-orientation would become with increase of $\beta_{value}$
-- Costs of relocation can be included as costs that hinder relocation despite the choice.
-This can be one application of  @esser2010's definition of costs as limit to the investment on the receving context option.
-In @esser2010 costs is loosely derived from social, economic and cultural capital milieu and are basically conceptualized upon the concrete choice actors (i.e.
-migrants) want to engage in, costs of relocation can be one of many.
-
-- In the ACS paper [@paolillo2018] we focused on the interplay of different homophily preferences in Schelling's threshold model and diffent type of segregation that emerge.
-With this direction the next paper could link to the ACS paper [@paolillo2018] by:
-  * addressing the reason why people would have preference for one characteristic over the other
-  * what's the effect of people holding different preferences at same grades, while in the ACS they were exclusive tolerant: value, intolerant: ethnicity
-  * extension to the random utility model as in @zhang2004 would distinguish between the ideal payoff $u$ for a characteristic and how important is that characteristic to people $\beta$
-  * an additional point to random utility models would be to link $\beta$ to needs and resources of people as in @esser2010. This has some advantages to me:
-    - relative group size and ethnic boundary making in @esser2010 are supposed to influence probability to make a choice.In the ACS paper we included symbolic boundaries through the definition of similarity and relative group size, now we would include the overall frame of the model with need $\rightarrow$ change in $\beta$) and costs of relocation
-    - as in the original Schelling [@schelling1969;@schelling1971] and other literature, homophily *per se* is a mechanism which describes the aggregation dynamics, but it does not provide causal mechanism on why people should aggregate based on one dimension over the others.
-This frame of the paper could fill this point
-    - foster the linkage between @esser2010's speculation and Schelling's model, so to benefit the long term agenda of the project
-    - deeper definition of utility frame and rational choice, linking to the literature in abm and concretisize @esser2010's model itself, which was elaborated as a summa of general and abstract rational choice
-
-- Linking $\beta$ to needs and including costs, $\beta u (.) + \epsilon$ should become something like $$N_{e} U_{e} + N_{v} U_{v} + N_{s} U_{s} - C$$ where $N$ =  needs, $C$ = costs and $e,v,s$ the ethnic, value and socio-economic status dimension.
-The random term $\epsilon$ is implemented through the exponential function.
-
-# Notes on the model
-
-- Now agents' characteristics of ethnicity, value and ses are nested.
-I think it would be worth to have a change in $u$ and $\beta$ for any intersection, but with risk to increase the number of parameters.
-The simplest solution I found so far was to link it to the value-orientation of agents as in the ACS paper [@paolillo2018].
-
-- A way to reduce the number of parameters and make the model more realistic might be to have $u$ changing as function of the identification agents hold for the three categories (value, ethnicity and ses), changing the categories to a gradient $-1 ...+1$, e.g.:
-  - value: extreme right-wing $\longleftrightarrow$ extreme leftwing, or pro local norms $\longleftrightarrow$ vs local norms.
-  - ses: extrem low $\longleftrightarrow$ extreme high
-  - ethnicity: dychotomous group 1 vs group 2
-This way would maybe allow to explore more with fewer parameters: 
-  - ideal payoff function $u$ as in the single-peaked function could derive from how people positionate along the continuum, as well combination of different homophily preferences.
-Assuming value as tolerance towards diversity, people extremely conservative would likely want in their neighborhood people both of the same ethnic group, but also of the same value orientation.
-People in the middler positions would care less about the value-orientation of others (as in the current ACS paper)
-  - the model would be relaxated which would justify the single-peaked function, linking $u$ to  shift in $M$ and affect the right slope: people who aim at 100% similar neighborhood would be more likely to choose a 90% similar neighborhood than 30%, as well as people aiming at a mixed 50% neighborhood would be more likely to choose a 60% of similar, as in Zhang [@zhang2004]
-  - different and more realistic scenarios, and examples in literature could be compared [@van2012] or what data show.
-This supports  the aim of the abm/project to clarify how different scenarios of integration/segregation are possible in an unified model and theory building
-
-I implemented in the model the single-peaked funcition as in @zhang2004 since I think it allows to explore more articulated scenarios. I think it would be worth to question about as above.
-
-$$
-U=
-\begin{cases}
-\frac{x}{np}, & \text{if} \ x \leq np, \\
-(2Z-M)+\frac{(M-Z)x}{np}, & otherwise
-\end{cases}
-$$
-
-Assuming $Z=1$ as peak of utility at desired fraction $P$, then the equation becomes as follow.
-This is how I implemented  for the three utilities (ethnicity, value, ses).
-Did not understand to be honest how the second equation @zhang2004 (otherwise) is reduced to the one used  in Andreas Flache's slides and Sage's model (how 2Z-M disappears).
-I adapted their equation, but I  understand it and it works as I tested.
-
-$$
-U=
-\begin{cases}
-\frac{x}{np}, & \text{if} \ x \leq np, \\
-M+\frac{(1-(x/n))*(1-M)}{(1-p)}, & otherwise
-\end{cases}
-$$
-\
-
-where
-M = constant for the right slope \
-x = number of similar ones in Moore neighborhood \
-n = number of agents in the Moore neighborhod $\rightarrow$ x/n: fraction similars \
-p = desired concentration \
-
-Fig. \ref{fig:moore} replicates @zhang2004 for desired fraction $p=0.5$ in an 8 patches Moore neighborhood, $Z=1$ and $M=0.6$.\
-Fig  \ref{fig:sechneg} shows how the function will not change for the same proportion within a different number of patches occupied in the neighborhood, here with occupied patches equal to 6.\
-Fig. \ref{fig:emmeone} shows how for M=1 utility becomes constant once the ideal payoff is reached, kind similar to threshold models\
-Fig. \ref{fig:emmezero} shows how for M=0 the right slope is symmetrical with left one.
-
-Fig.
-\ref{fig:utzero} shows the condition where desired concentration $p=0$ in a 8 patches neighborhoood, with $M=0.6$, which means agents actively do not want any similar in the neighborhood.
-This means that although utility = 1 at 0 is not possible, the function becomes linear decreasing.\
-Fig.
-\ref{fig:integr} shows how this translates in the  model with $\beta=100$.
-Seems to me it increases stable integration, and it is not an error: as @zhang2004 describes, with $\beta=0$ agents just move randomly, with equal chance to move to alternative patch or stay in neighborhood.
-Here with $\beta=100$ the characteristic of the neighborhood is relevant to them, although the payoff is 0 and $\beta * u=0$, correct I think conceptually and as the stable patterns of emerged segregations and average utility show.
-To check if this can be related to @bruch2006's error cited by @van2009
-
-```{r sechneg, echo=FALSE, fig.cap="utility in Moore 6 patches; desired fraction 50%, M=0.6, Z=1"}
-
-# f0t6 <- f(0.5,0.6,0,6)
-# f1t6 <- f(0.5,0.6,1,6)
-# f2t6<- f(0.5,0.6,2,6)
-# f3t6 <- f(0.5,0.6,3,6)
-# f4t6 <- f(0.5,0.6,4,6)
-# f5t6 <- f(0.5,0.6,5,6)
-# f6t6 <- f(0.5,0.6,6,6)
-
-# utilityt6 <- c(f0t6,f1t6,f2t6,f3t6,f4t6,f5t6,f6t6)
-# concentrationt6 <- c(0:6)
-
-# print(utilityt8)
-# plot(concentrationt6,utilityt6)
-
-```
-
-```{r emmeone, echo=FALSE, fig.cap="utility in Moore 8 patches; desired fraction 50%, M=1, Z=1"}
-
-# f0m <- f(0.5,1,0,8)
-# f1m <- f(0.5,1,1,8)
-# f2m <- f(0.5,1,2,8)
-# f3m <- f(0.5,1,3,8)
-# f4m <- f(0.5,1,4,8)
-# f5m <- f(0.5,1,5,8)
-# f6m <- f(0.5,1,6,8)
-# f7m <- f(0.5,1,7,8)
-# f8m <- f(0.5,1,8,8)
-
-# utility_Moore <- c(f0m,f1m,f2m,f3m,f4m,f5m,f6m,f7m,f8m)
-# concentrationm <- c(0:8)
-
-# print(utilitym)
-# plot(concentrationm,utility_Moore)
-```
-
-```{r emmezero, echo=FALSE, fig.cap="utility in Moore 8 patches; desired fraction 50%, M=0, Z=1"}
-
-# f0m <- f(0.5,0,0,8)
-# f1m <- f(0.5,0,1,8)
-# f2m <- f(0.5,0,2,8)
-# f3m <- f(0.5,0,3,8)
-# f4m <- f(0.5,0,4,8)
-# f5m <- f(0.5,0,5,8)
-# f6m <- f(0.5,0,6,8)
-# f7m <- f(0.5,0,7,8)
-# f8m <- f(0.5,0,8,8)
-
-# utility_Moore <- c(f0m,f1m,f2m,f3m,f4m,f5m,f6m,f7m,f8m)
-# concentrationm <- c(0:8)
-
-# print(utilitym)
-# plot(concentrationm,utility_Moore)
-```
-
-I think for a paper would be worth it to show how the three functions can overlap due to setting, something like this
-```{r overlap_function, include=TRUE, echo=FALSE}
-
-x_graph_overlap <- rep(seq(0, 100, by = 12.5),4)
-
-S_0 <- c(0,0,0,0,0,NA,NA,NA,NA)
-M_1 <- c(NA,NA,NA,NA,1,1,1,1,1)
-S_1 <- c(0,0.25,0.5,0.75,1,NA,NA,NA,NA)
-M_0 <- c(NA,NA,NA,NA,1,0.75,0.5,0.25,0)
-
-funct_overlap <- c(rep("S = 0",9),rep("M = 1",9),rep("S = 1",9),rep("M = 0",9))
-utility_overlap <- c(S_0,M_1,S_1,M_0)
-
-overlap <- data.frame(x_graph_overlap,utility_overlap,funct_overlap)
-
-# overlap
-
-graph_overlap <- ggplot(overlap,aes(x_graph_overlap,utility_overlap))
-
-suppressWarnings(print(
-graph_overlap + geom_line(aes(colour = funct_overlap)) + scale_color_manual(values = c("red","forestgreen","black","purple"),name = "Parameters Setting") + theme_bw() + labs(x = "percentage similars",y = "utility for location")
-))
-
-```
-
-<!-- read @Brock2001, @Brock1997 -->
-
 # References

### 2019-08-22 paper_notes.Rmd
Add files via upload

@@
 
-# ethnic utility difference and value utility difference
+# Ethnic utility difference and value utility difference
 
@@
 
-dfprob
 # Probability to move to alternative (random utility with logistic regression)
@@
 prob <- function(d_u_e,d_u_v,e_w,v_w,k){round(1 / (1 + exp((-(e_w*k)*(d_u_e)) + (-(v_w*k)*(d_u_v)))),digits= 2)}
+
+# For the 3D plots
 
@@
 
+# ANNEX {-}
+
+## Ethnic Utility Calculation
+
 ```{r ethnic utility individual-run,fig.width=4,fig.height= 3, fig.align="center", fig.pos="H", include=TRUE, echo=FALSE}
@@
 ```
+
+## Value Utility Calculation {-}
 
@@
 
-```{r logistic, fig.width=5,fig.height=4,fig.align='left',include=TRUE, echo=FALSE}
+## Logistic Function calculation {-}
 
-magic_for()
+```{r logistic, fig.width=5,fig.height=3,fig.align='left',include=TRUE, echo=FALSE}
+
+# PROBABILITY to relocate to alternative
+# Choose the parameters for ethnic weight (e_w), value weight (v_w) and the cstant k. As default v_w is complementar to e_w (1-e_w, as will be in the abm), you can change this.
+# The parameter for importance of relative utility is equal to e_w*k for ethnic utility and v_w*k for value utility.
+The highest the parameter for that dimension, the less random is the choice and the more depending on the option with highest relative utility
+# Each vignette is one level of ethnic utility difference (-1 to 1), the x-axis the value-difference (-1 to 1), on y-axis the probability to relocate.
 
 e_w <- 0.5              
-v_w <- 0.5
+v_w <- 1-e_w
 k <- 10
 
-for (d_u_e in seq (-1.0,1.0, by = 0.1)){
-
+for (d_u_e in seq (-1.0,1.0, by = 0.1)){    # Runs the same function for each level of ethnic utility difference
+                                            # d_u_e, the increasing number is the value utility difference
 dis_1neg   <- prob(d_u_e,-1.0,e_w,v_w,k)
@@
 
-  value_difference <- seq(-1.0,1.0, by = 0.1)
+value_difference <- seq(-1.0,1.0, by = 0.1)       # here to setup the plot and change info for each vignette
 
@@
 title_cond_prob <- paste0("Diff. Ethnic Utility (alternative - current): ",d_u_e)
-  title_caption <-  paste0("Ethnic weight = ",e_w*10," ; ","Value weight = ",v_w*10
-                           ,"\n\r","-1: Min Utility Alternative; 1: Max Utility Alternative"
-                           )
+title_caption <-  paste0("Ethnic weight = ",e_w*10," ; ","Value weight = ",v_w*10,"\n\r","-1: Min Utility Alternative; 1: Max Utility Alternative")
 
@@
 
- final_prob <-  suppressWarnings(suppressMessages(
-    plot_report_prob + geom_point() + theme_bw() + labs(x = "Diff. Value Utility (alternative - current)",y = "Probability") +
-      labs(title=title_cond_prob, caption = title_caption)
-
-      + theme(plot.title = element_text(hjust = 0.5),plot.caption = element_text(hjust=0.5)) + scale_y_continuous(limits =  c(0.0,1.0), breaks = seq(0.0,1.0,by = 0.25)) + scale_x_continuous(limits =  c(-1,1), breaks = seq(-1,1,by = 0.2)) + geom_vline(xintercept = 0, colour = "red", linetype = "dotted") + geom_hline(yintercept = 0.5, colour = "red", linetype = "dotted")
-  ))
+final_prob <-  suppressWarnings(suppressMessages(plot_report_prob + geom_point() + theme_bw() + labs(x = "Diff.
+Value Utility (alternative - current)",y = "Probability") + labs(title=title_cond_prob, caption = title_caption) + theme(plot.title = element_text(hjust = 0.5),plot.caption = element_text(hjust=0.5)) + scale_y_continuous(limits =  c(0.0,1.0), breaks = seq(0.0,1.0,by = 0.25)) + scale_x_continuous(limits =  c(-1,1), breaks = seq(-1,1,by = 0.2)) + geom_vline(xintercept = 0, colour = "red", linetype = "dotted") + geom_hline(yintercept = 0.5, colour = "red", linetype = "dotted")))
 
@@
 
-```{r test, fig.width=5,fig.height=4,fig.align='left',include=TRUE, echo=FALSE}
-
-e_w_v <- 0.5
-v_w_v <- 1-e_w_v
-k_v <- 10
-
-dfprob_log <- mutate(dfprob,e_w=e_w_v,v_w=v_w_v,k=k_v, probalog = prob(d_u_e, d_u_v,e_w,v_w,k))
-
-#  report_prob <- na.omit(dfprob_log(d_u_v,probalog))
-
-logi <- function(lo){
-plot_report_prob <- ggplot(dfprob_log[which(d_u_e == lo),],aes(d_u_v,probalog))
-
-  title_cond_prob <- paste0("Diff. Ethnic Utility (alternative - current): ",lo)
-  title_caption <-  paste0("Ethnic weight = ",e_w_v*k_v," ; ","Value weight = ",v_w_v*k_v
-                           ,"\n\r","-1: Min Utility Alternative; 1: Max Utility Alternative"
-                           )
-
- final_prob <-  suppressWarnings(suppressMessages(
-    plot_report_prob + geom_point() + theme_bw() + labs(x = "Diff. Value Utility (alternative - current)",y = "Probability") +
-      labs(title=title_cond_prob, caption = title_caption)
-
-      + theme(plot.title = element_text(hjust = 0.5),plot.caption = element_text(hjust=0.5)) + scale_y_continuous(limits =  c(0.0,1.0), breaks = seq(0.0,1.0,by = 0.25)) + scale_x_continuous(limits =  c(-1,1), breaks = seq(-1,1,by = 0.2)) + geom_vline(xintercept = 0, colour = "red", linetype = "dotted") + geom_hline(yintercept = 0.5, colour = "red", linetype = "dotted")
-  ))
-
- final_prob
-
-}
-
-logi(-1)
-logi(-0.9)
-
-}
-
-```
-
 # References

### 2019-08-27 paper_notes.Rmd
Add files via upload

@@
 title: "Paper notes"
+subtitle: "Target: BIGSSS Research Day"
 author: Rocco Paolillo
+date: "`r  as.Date(Sys.time(), '%d %m %Y')`" 
+language: en-GB
 bibliography: "references.bib"
 always_allow_html: yes
+
 # target: BIGSSS Research Day by September 15th, presented  on October 25th. 6000 words: around 12 pages.
@@
 
-The basic idea is to introduce a beta distribution for $\beta$ in the utility definition of neighborhood $j$ for agent $i$ :
+In the agent-based model, an agent chooses between current location and one alternative location according to the ethnic utility and value utility attributed to neighborhoods.
+The aim is to fit the random utility framework for a discrete choice model and advance on the ACS paper [@paolillo2018].
+I liked  @bruch2009preferences's description disentangling between utility, probability and how they relate in the empirical data / agent-based models relation.
+
+Probability that an agent will choose the alternative relies on the difference between the utility of the two neighborhood options:
+
+$$
+P_{alterntive}=U_{alternative} -  U_{current}
+$$
+Where: \par
+- $P_{alternative}=1$ means moving to alternative, implying its utility is higher than the current one
+- $P_{alternative}=0$ means staying on the current location, implying its utility is higher than alternative
+
+Definition of utility for a neighborhood, and its implication for the probability to relocate, fits the random utility framework:
 
@@
 
-With $\beta_x$ the importance of ethnic composition $x_j$ of neighborhood $j$ and $\beta_y$ its value composition $y_i$.
+With $\beta_x$ being the importance of ethnic composition $e_j$ of neighborhood $j$, $\beta_y$ the importance of its value composition $v_j$, and $\epsilon_j$ the random term.
+The random term refers to other characteristics of neighborhoods or of decision makers that can influence the utility and probability of choice, but that are totally unknown.
+$\beta$ regulates the systematic component of utility, and $\epsilon$ the random component of utility [@bruch2009preferences].
+Random component is assumed to be independent and identically distributed (i.i.d.) among options, while the systematic component of utility depends on the formalized functional form and how it interacts with $\beta$ values.
+The higher is the parameter $\beta \in[0,\infty)$, the lower is the effect of random term and the more utility and probability of choice is based on the observed characteristics of interest of the option (here ethnic and value composition) and how they relate to the functional form implemented.
 
-To avoid confusion between parameter beta and beta distribution used in the simulation, $\beta_x$ is called ethnic weight (ew in R code), $\beta_y$ is called value weight (v_w in R code).
+In this implementation of the model, $beta_x$ follows a beta distribution.
+To avoid confusion between terms of parameter beta and beta distribution used in the simulation, $\beta_x$ is called ethnic weight $ew$ (e_w in R code), $\beta_y$ is called value weight $vw$ (v_w in R code), with $v_w = 1-e_w$.
 
-We want to compare different type of functions, in particular to compare the single-peaked function as modeled by [@zhang2011, graphic p.
-174] with the Schelling's original threshold we also  used in the ACS paper, and a mixed one where utility increases until the ideal point as in Zhang, and remains constant at max.
-1 when the ethnic composition exceeds the ideal point.
-The last function comes from the idea that it can be a realistic scenario in people's relocation choice.
+Following @zhang2011, and also @bruch2006, we want to implement and compare the consequences of adopting different functional forms in the definition of utility as individual behavior of agents.
+In particular, we want to compare a range of functional forms of individual behavior spanning from the single-peaked function as in @zhang2011[ graphic p.
+174] to the threshold function as in the original Schelling's model and that we used in the ACS paper [@paolillo2018].
+The idea was a third function as a combination between linear growing as in @zhang2011 until the ideal point (proportion of similars) is reached, and then constant for higher proportions that include the ideal point as it would be in Schelling.
 
-To have all of the functions coming from the same computation and reduce as much, I modified @zhang2011's formula, assuming max Utility = 1 and introducing 2 parameters to the formula, as in the simulation:\par
-- $S[0,1]$, regulating the increasing left slope
-- $M[0,1]$, regulating the decreasing right slope (as in Zhang)
+Since the task was to reduce number of parameters as much and reproduce the functions we need, I modified @zhang2011's formula, assuming max Utility = 1 and introducing S parameter that combined with M generates the functions we need:\par
+- $S[0,1]$, regulates the increasing left slope 
+- $M[0,1]$, regulates the decreasing right slope (same in Zhang)
 
@@
 
-Below example of the three functions, reporting how $S$ and $M$ are set to calculate them.
-The example refer to desired compostion $50\%$ ($i_e = 0.5$).
-It was calculated out of a 8 agents neighborhood (with 4 agents of same ethnicity representing the $50 \%$)
+Fig.\ref{fig:ethnicf} reports the example of the three functions, and how $S$ and $M$ are set to calculate them.
+The example refers to desired compostion $50\%$ ($i_e = 0.5$).
+It was calculated out of a 8 agents neighborhood (with 4 agents of same ethnicity representing the $50 \%$), I changed the units on x-axis to percentage.
 
-```{r ethnic graph function, fig.width=6,fig.height= 8, fig.align="center",  include=TRUE, echo=FALSE}
+*IDEA/DOUBT*: A fourth function we could include is for S=0 and M=0.
+In a computational framework,the aim of the paper is to explore and formalize the consequences of different functional forms, which represent different behaviors of how people attribute utility to a neighborhood, whatever might be the reason for this.
+Following this I think there would be no need to exclude one scenario out of the set and would be more sound to compare the four exteme cases.
+As in fig.
+\ref{fig:ethnicf}:\par
+- S=1,M=0, the symmetric single-peaked function with ideal point: people have a preference they value maximally, and devalue equally options that are below or above such preference
+- S=1,M=1, people increasingly value options below their ideal point as long as they get closer to it, and are equally happy for those  options that include and guarantee the ideal point
+- S=0,M=1, the original threshold Schelling: people have a threshold preference, devalue and refuse (Utility = 0) options below it and are equally happy for those above it
+- S=0,M=0 (to add): people devalue and refuse any option below their ideal point (Utility = 0), and decreasingly devalue those options that exceed their ideal point
 
-i_e = 0.5
-M = 0
+```{r ethnicf, fig.width=6,fig.height= 8, fig.align="center", fig.pos="H",include=TRUE, echo=FALSE, fig.cap = "Ethnic Utility Function"}
+
+i_e = 0.5                   # definition of parameters for each function: i_e desired ethnic concentration
+M = 0                       # M: right-side slope, S: left-side slope, n = total number of agents in neighborhood
 S = 1
@@
 
-f0s <- f_eth(i_e,M,0,n,S)
+f0s <- f_eth(i_e,M,0,n,S)     # computation for each neighborhood, the increasing number is number of  similars
 f1s <- f_eth(i_e,M,1,n,S)
@@
 
+# here below to make up for dataframe and plots
+
 Utility_S <- c(f0s,f1s,f2s,f3s,f4s,f5s,f6s,f7s,f8s)                     
@@
 suppressWarnings(
-grid.arrange(symmetric_plot, constant_plot,threshold_plot, bottom = "Comparison of the three functions for ethnic utility of a neighborhood j")
+grid.arrange(symmetric_plot, constant_plot,threshold_plot)
 )
@@
 
+In the ANNEX here you can see the function slope and values of ethnic utility given some parameteres. In the R-code you can set the parameters and test, e.g. comparing with NetLogo
+
 # Value Utility {-}
+
+The idea we discussed with Jan about value utility was to use the ethnic weight $ew$ of each agent and how distant it is from the average of ethnic weights of other agents in the potential neighborhood.
+To do so, I include the parameter $i_v \in [0,1]$, meaning the absolute desired distance between the agent's ethnic weight and the average of ethnic weights in its neighborhood.
+Values range from 0: only similars in the neighborhood are desired, to 1: any possible extrem distance is accepted.
+Here the ideal point becomes an interval, with average points outside of the ideal interval being equally distant.
+The function for ethnic utility as above with left increasing slope and right decreasing slope would not work.
+I elaborated another function using the same parameters S and M:\par
+- $S[0,1]$, regulates the extreme of the slope closer to the ideal point 
+- $M[0,1]$, regulates the extreme of the slope further the ideal point
+
+Fig.\ref{fig:valuef} reports the 2 possible functions:\par
+- S=1,M=0. Symmetric single peaked. Has a similar shape as ethnic utility, but due to different computation
+- S=0, independent from the value of M: Schelling's Threshold function
 
@@
 \begin{cases}
-1, & \text{if} \ e_w \leq i_v, \\
+1, & \text{if} \ \mid{\overline{ew}_j - ew_i}\mid \leq i_v, \\
 \\
@@
 Where: \par
-- $U^i_v$: Ethnic utility of agent i
+- $U^i_v$: Value utility of agent i
 - $\overline{ew}_j$: average ethnic weight in neighborhood \textit{j}
 - $ew_i$: ethnic weight of agent \textit{i}
-- $i_e$: desired ethnic composition
+- $i_v$: desired value distance of agent \textit{i}
 
-*DOUBT*: for the value composition, have a distribution of opinions/beliefs for agents within ethnic groups, the value weight would be still  1 - e_w, and a parameter of how similar others are considered based on how they distantiate from the own opinion.
-This would be a comparison to Schelling's definition of similarity based on twofold, exhaustive and exclusive category (i.e.
-ethnicity), but rather on an cross-categorical, individual and constructed definition of similarity/desirability, and how important it is.
-
-```{r value graph function, fig.width=6,fig.height=5, fig.align="center", include=TRUE, echo=FALSE}
+```{r valuef, fig.width=6,fig.height=5, fig.align="center",fig.pos="H", include=TRUE, echo=FALSE, fig.cap="Comparison of the two function for the value utility of a neighborhood j"}
 
@@
 
-thres_val_plot <- thres_val_graph + geom_point() + theme_bw() + labs(x = "Mean ethnic weight neighborhood j",y = "Value utility j") + ggtitle(label = "Threshold Schelling (S=0,M=0) ",subtitle = subt_cont_v) + theme(plot.title = element_text(hjust = 0.5), plot.subtitle = element_text(hjust = 0.5))  + scale_x_continuous(breaks = seq(0.0,1.0,by = 0.1)) + scale_y_continuous(limits =  c(0.0,1.0), breaks = seq(0.0,1.0,by = 0.25))
+thres_val_plot <- thres_val_graph + geom_point() + theme_bw() + labs(x = "Mean ethnic weight neighborhood j",y = "Value utility j") + ggtitle(label = "Threshold Schelling (S=0) ",subtitle = subt_cont_v) + theme(plot.title = element_text(hjust = 0.5), plot.subtitle = element_text(hjust = 0.5))  + scale_x_continuous(breaks = seq(0.0,1.0,by = 0.1)) + scale_y_continuous(limits =  c(0.0,1.0), breaks = seq(0.0,1.0,by = 0.25))
 
 suppressWarnings(
-grid.arrange(symm_val_plot, thres_val_plot, bottom = "Comparison of the two functions for value utility of a neighborhood j.")
+grid.arrange(symm_val_plot, thres_val_plot)
 )
@@
 ```
+
+In the ANNEX here you can see the function slope and computation of value utility given some parameteres. In the R-code you can set the parameters and test.
+
+*DOUBT/IDEA*: I have doubts with this definition of value utility (distance between agent and average ethnic weights of neighborhood), conceptually and for the computation.
+I will come back after implementing as above.
+As an extension of Schelling's model, I would focus on how similarity can be defined at the individual level between people as the distance between values/opinions, opposite to Schelling's condition of a "twofold, exhaustive and recognizable distinction" [@schelling1969, p.
+488].
+Defined the different types of similarity, the mechanism of threshold preferences and cascades would be the same, exploring how the value segregation and ethnic segregation interplay.
+This was the point of the ACS paper, I think it would better fit the ethnic boundary making's framework [@wimmer2013] and @esser2010's point along with the value homophily we mentioned in the ACS [@mcpherson2001], and my dissertation project.
+In this terms, in the ACS there were 2 levels of values (tolerants vs intolerants) and related preferences (value-oriented vs ethnicity-oriented), with the ideal distance of value-oriented tolerants equal to 0 (similars are only other tolerants).
+Here we expand this and extend the residential preferences.
+For the number of parameters and simplicity, the desired distance $i_v$ already must be included (it would only shift to distance between individual agents); to add there would be one continuous distribution of the values across the population (stylized parameter for norms, political orientations etc.
+in a population across the ethnic groups).
+The same functional form as for ethnic utility would then be used, making it more simple and any effect related to average computation/functional form avoided, focusing on the proportion as in Schelling.
+A simplest way is to use the distance between ethnic weights of agents as "values".
+I also have some doubts here both because they should be parameters of the choice and not definition of a person [@manski1977structure], plus literature and choices of the model.
+To not overwhelm and create confusion now I will come to it later when more clear.
+
+# Probability to relocate to alternative {-}
+
+Calculated the value utility and ethnic utility, the agent chooses between current location and the alternative location.
+The probability is calcualted using the logistic function.
+We decided to limit the number of options to 2, both for computational reasons and because there is not need to do otherwise.
+This is the condition for the logit model of discrete choice with two conditions [@liao1994interpreting], which calculates the probability to select an option with the logistic function $P_j=\frac{1}{1 + \exp(-\lambda\times \Delta_{(U_j,U_l)})}$
+
+Using the logistic function applies the discrete choice for a logit model [@liao1994interpreting], where the probability is calculated for the event to select a probability or not.
+In terms of residential move as in the model, $P=1$ means to select the choice, $P=0$ means to not select, and consequently to stay with the current option.
+
+event to calculate the
+
+This fits the discete choice model for logit model [@liao1994interpreting], which calculates the probability of an event to occur or not.
+
+take on to happen outcome of a probability to occur or not. Given two options, P=1 means choosing the option, P=0 necessary to choose the other alternative.
+
+under the this justifies using the
+one differentiation between discrete choice models is:\par
+- Logit model: used for 2 options using the logitisc function. Since the probability calculated estimates the chance to choose one option with $P=1$, it can be used for 2 options where $P=0$ means
+
+used for two options, the probability calculated with logistic function $P_j=\frac{1}{1 + \exp(-\lambda\times \Delta_{(U_j,U_l)})}$ refers to the event that one option is chosen choose one option with $P_j=1$
+
+- Conditional logit model for multinomial distribution: used for more than two options.
+The probability $P_j=\frac{\exp(U_{(xjyj)})}{\sum_{l}exp((U_{xl,yl}))}$ from @mcfadden1973conditional calculates how one option will be selected out of the set of discrete choices
+
+As I summarized via e.mail, for two options a multinomial choice model can be considered substantially a binary logit model, in our case since the.
+The two computations of probability above both assume that the random term $\epsilon$ is idependently and identically distributed among options, and the systematic difference
+
+the assumptions of random utility model on systematic variation in utility and independent and identical distribution of the random term
+
+. This link synthetizes: [logit_binary_choice, point C](https://en.wikipedia.org/wiki/Discrete_choice#A._Logit_with_attributes_of_the_person_but_no_attributes_of_the_alternatives)
+
+Here is the logistic function implemented in the model for the choice between current location and alternative location:
 
@@
 
-The idea of $k$ constant is to include the parameter of determinism in the random utility formula, i.e.
-from 0: the probabiity to choose the alternative is totally random due to random term $\epsilon$, to infinity, the best option is taken with probability equal to 1.
-To reduce the number of parameters, and being constitent with the conceptual model, I derive the parameter for ethnic utility from the ethnic weight $ew$ and the parameter for value utility from the value weight $vw$ in the agent-based  model.
-Remember that $ew$ ranges $[0,1]$ according to beta distribution, and $vw$ is calculated as $1-ew$.
-The parameter is calculated as $k\cdot ew$ and $k \cdot vw$, meaning that with $k=10$, the parameter for ethnic utility will range from 0 to 10, $k=100$, range from 0 to 100, $k = 0$: all agents will have parameter equal 0.
-It will be one slider in the agent-based model.\par
-The aim of the logistic function above is to implement the random  utility for a binary choice for the agent between the current location $x$ and alternative location $j$, with $P_{xj}=0$ meaning the agent stays on the current location, $P_{xj}=1$ the agent moves to the alternative location $j$.\par
-Below I report some graphs on $P_{xj}$ where the logistic funtion above is implemented for each combination of ethnic utility difference $\Delta_{U_e}$ and value utility difference $\Delta_{U_v}$.
-These are the possible values expected from the agent-based model: assuming that both the ethnic and value utility for each location ranges from 0 to 1, the difference (alternative - current) ranges from -1 (alternative = 0, current = 1), to 1 (alternative =1, current = 0), with 0 meaning equal utility sizes.
-This creates 11 levels  for each utility, $\times$ 2 number of utility = 441 conditions.
-The aim of the graphs was to relate the probability as function of 2 dimensions, so I use the heatmaps in fig.\ref{fig:heatmaps}.
-They have the same content of the 3D plots in fig.\ref{fig:prob3D} which I think serve better the scope: in the R code you can interact with the graph and see actual probability for each point, but need to do it from the RStudio interface (chunk "interact3d").\par
-Each graph reports the parameter ethnic weight $ew \cdot k$ and parameter value weight $vw \cdot k$.
-In all conditions $k = 10$, which I saw shows most realistic scenarios, i.e.
-lower probability for lower ethnic/utility difference.
-To check if the random utility for binary choice is correctly implemented, $P_{xj}=0.50$ with $ew \cdot k = 0$ and $vw \cdot k = 0$, meaning the choice between current and alternative location is totally random.
-In the last condition $ew \cdot k = 100$ and $vw \cdot k = 100$, $P_{xj}=0$ for all conditions where current location is higher in both types of utility (below the diagonal), shifts to $P_{xj}=1$ for all conditions with both utilities higher in the alternative location (above the diagonal), and $P_{xj}=0.5$ on the diagonal where the alternatives have same utility with difference equal 0.
-So the choice is totally dependent on the characteristic of the neighborhood, with the best option being taken.
-I think it can confirm the random utility framework for two options.
+$P_j$ thus ranges from 0 = the agent remains in its current location, to 1 = the agent moves to the alternative location.
+
+which uses the conditioanl logit to calculate the probability to choose $\textit{j}$ ($P_j=\frac{\exp(U_{(xjyj)})}{\sum_{l}exp((U_{xl,yl}))}$).
+As I wrote and as I understand so far, for two options the calculation of probability according to the multinomial choice formulation and the logistic function for binary choice can be considered equivalent as they both will assure the $i.i.d$ distribution of the random term, which is the priority of random utility models.\\
+
+$k$ times ethnic weight $ew$ and $k$ times $vw$ substitute the parameters in random  utility for how important the ethnic composition and value composition are in the logistic function ($\lambda$ in $P_j=\frac{1}{1 + \exp(-\lambda\times \Delta_{U_e})+(-\lambda \times \Delta_{U_v}))}$ and $\beta_xe_j$ $\beta_yv_j$ in  $\textit{j}$ ($P_j=\frac{\exp(U_{(xjyj)})}{\sum_{l}exp((U_{xl,yl}))}$.
+My idea is that ethnic weight and value weight range from 0 to 1, whose value is too low causing random choices, by multiplying by a constant the ratio in the distribution point stay the same.\par
+Below I report some graphs where I implement the logistic function as above tuning $k \cdot ew$ and $k \cdot vw$, checking if it would reproduce what expected from random utility models, I think it does.
+For parameters equal to 0, the probability to choose the alternative is $50%$ in all conditions.
+The best option is taken when parameters are increased, always $50%$ when the actual difference is 0.
+I tested some conditions considering the 2 types of utility (some would be not possible in the simulation if we keep $vw=1-ew$, but here was to see how it worked).\par
+On the x-axis is ethnic utility difference, on the y-axis the value utility difference.
+Each ranges from -1 (alternative = 0, current = 1), to 1 (alternative = 1, current = 0), with 0 = no difference between the options.
+I made up them out of possible conditions.
+For each condition (21x21= 441), the probability function is calculated using the logisticdunction above.
+Heatmaps in fig.
+\ref{fig:heatmaps}
+
+In the ANNEX of pdf is the sigmoid function for the logistic function, too long.
+Each vignette is one level of ethnic utility difference, the x-axis is the whole value utility difference range.
+You can manipulate $ew$, $vw$ and $k$ in the R code.
 
@@
 
-```{r ethnic utility individual-run,fig.width=4,fig.height= 3, fig.align="center", fig.pos="H", include=TRUE, echo=FALSE}
+```{r ethnic utility individual-run,fig.width=4,fig.height= 3, fig.align="center", include=TRUE, echo=FALSE}
 # ETHNIC UTILITY:
@@
 i_e = 0.5   # parameters to manipulate
-S = 0     # Symmetric single-peaked function: S=1,M=0
+S = 1     # Symmetric single-peaked function: S=1,M=0
 M = 0     # Linear + Constant function = S=1,M=1
@@
 
-```{r value individual run,fig.width=5, fig.height= 3, fig.align="center", fig.pos="H", include=TRUE, echo=FALSE }
+```{r value individual run,fig.width=5, fig.height= 3, fig.align="center", include=TRUE, echo=FALSE }
 # VALUE UTILITY:
 # Choose parameters for ethnic weight of agent i (e_w), desired value distance (i_v), left-slope utility curve (S),right-slope utility curve (M).
-# The calculations are done for each ethnic weight mean of the neighborhood, from 0 to 1.
+# Calculations are done for each ethnic weight mean of the neighborhood, from 0 to 1.
 The extreme case is desired value distance 1, meaning all mean ethnic weight of the neighborhood are included.
@@
 e_w <- 0.4    # parameters to manipulate
-i_v <- 0
-S  <- 0
+i_v <- 0.2    # Symmetric = S:1,M:0/Threshold = S:0
+S  <- 1
 M <-  0
 
-fv0d2 <- f_val(e_w,0,M,i_v,S)      # value utility for each option, the increasing number is the ethnic weight of neighborhood j
-fv1d2 <- f_val(e_w,0.1,M,i_v,S)
+fv0d2 <- f_val(e_w,0,M,i_v,S)             # value utility for each option, 
+fv1d2 <- f_val(e_w,0.1,M,i_v,S)           # increasing number is average ethnic weight of neighborhood j
 fv2d2 <- f_val(e_w,0.2,M,i_v,S)
@@
 ew_agent <- rep(e_w,11)
-Mv <- rep(M,11)
-Sv <- rep(S,11)
+# Mv <- rep(M,11)
+# Sv <- rep(S,11)
 des_dist <- rep(i_v,11)
 
-report_V <- na.omit(data.frame(Mv,Sv,des_dist,ew_agent,mean_ew_ng,Utility_V))
+report_V <- na.omit(data.frame(M,S,des_dist,ew_agent,mean_ew_ng,Utility_V))
 
@@
 ```
+<!-- 
+Notes on the value utility
+While in Schelling the integration/segregation continuum is on the twofold dimension of ethnicity, here would be on the likelihood to have someone with opinions too far from the own in the neighborhood or not, as in the geographical polarization literature.
+If I am not wrong, I also think that if the average of neighorhood is used, then one agent highly distant would influence the choice, which I think might be not realistic.
+Even though there might be solutions for this, my doubt is on the corresponding assumption and theory behind.
+Connecting to the ACS paper, in the ACS paper there would be 2 levels of values (intolerant vs tolerant) with different homophily behavior (ethnicity-oriented vs value-oriented), and for the value homophily the ideal distance 0 (tolerant only accepts other tolerant).
+As for parameters to include, the ideal distance is as already envisaged here (it will be between agents and not agent-average of neighborhood).
+Additionally, a distribution of values among agents [0,1] shoud be included, or the same ethnic weights as first try to keep simple.
+-->
 

### 2019-08-27 paper_notes.Rmd
Add files via upload

@@
 
-prob <- function(d_u_e,d_u_v,e_w,v_w,k){round(1 / (1 + exp((-(e_w*k)*(d_u_e)) + (-(v_w*k)*(d_u_v)))),digits= 2)}
+#prob <- function(d_u_e,d_u_v,e_w,v_w,k){round(1 / (1 + exp((-(e_w*k)*(d_u_e)) + (-(v_w*k)*(d_u_v)))),digits= 2)}
+prob <- function(d_u_e,d_u_v,e_w,v_w,k){1 / (1 + exp((-(e_w*k)*(d_u_e)) + (-(v_w*k)*(d_u_v))))}
+
+# prob <- function(d_u_e,d_u_v,e_w,v_w,k){round(1 / (1 + exp(-(e_w*k)*(d_u_e)) + -(v_w*k)*(d_u_v)),digits= 2)}
 
@@
 $$
-U^i_{(ej,yj)}   = \beta_xe_j + \beta_yv_j + \epsilon_j
+U^i_{(ej,yj)}   = \beta_ee_j + \beta_vv_j + \epsilon_j
 $$
 
-With $\beta_x$ being the importance of ethnic composition $e_j$ of neighborhood $j$, $\beta_y$ the importance of its value composition $v_j$, and $\epsilon_j$ the random term.
+With $\beta_e$ being the importance of ethnic composition $e_j$ of neighborhood $j$, $\beta_v$ the importance of its value composition $v_j$, and $\epsilon_j$ the random term.
 The random term refers to other characteristics of neighborhoods or of decision makers that can influence the utility and probability of choice, but that are totally unknown.
@@
 Random component is assumed to be independent and identically distributed (i.i.d.) among options, while the systematic component of utility depends on the formalized functional form and how it interacts with $\beta$ values.
-The higher is the parameter $\beta \in[0,\infty)$, the lower is the effect of random term and the more utility and probability of choice is based on the observed characteristics of interest of the option (here ethnic and value composition) and how they relate to the functional form implemented.
+This condition allows that the higher is the parameter $\beta \in[0,\infty)$, the lower is the effect of random term and the more the utility derived from one option depends on their characteristics (here ethnic and value composition) and how they interact with the functional forms of utility implemented.
+The probability to choose one option over the others relies on the difference of utility so computed, with the option with the highest utility being selected.
+As a consequence, for high $\beta \in[0,\infty)$, the probability will depend on the systematic component of utility, selecting the best option.
+For low levels of $\beta$, the probability will be random due to the higher component of the random term.
 
@@
 We decided to limit the number of options to 2, both for computational reasons and because there is not need to do otherwise.
-This is the condition for the logit model of discrete choice with two conditions [@liao1994interpreting], which calculates the probability to select an option with the logistic function $P_j=\frac{1}{1 + \exp(-\lambda\times \Delta_{(U_j,U_l)})}$
+This is the condition for the logit model for binary discrete choice model with two options [@liao1994interpreting].
+The dependent variable in such a model is the probability that an event will occur ($P=1$), or not ($P=0$).
+In a residential choice model and for two options as the agent-based model here, the agent must make a choice between moving to alternative location ($P=1$) or not ($P=0$), where the latter outcome implies to stay on the current location.
+Fitting the paradigm of maximization of utility, the probability to relocate to alternative increases if the utility derived from the alternative location is higher than the current one, as described above from @bruch2009preferences.
+Translated in the logistic function:
 
-Using the logistic function applies the discrete choice for a logit model [@liao1994interpreting], where the probability is calculated for the event to select a probability or not.
-In terms of residential move as in the model, $P=1$ means to select the choice, $P=0$ means to not select, and consequently to stay with the current option.
+$P_j=\frac{1}{1 + \exp(-\lambda\times \Delta_{(U_j,U_i)})}$
 
-event to calculate the
+An alternative to the logit model is the multinomial choice model, which is a generalization of the binary model where the choice is between more than two options [@train2009discrete].
+The probability to choose one option over the others is calculated according to the conditional logit model [@mcfadden1973conditional], depending on the characteristics of the options.
+Applied to utility maximization and random utility models [@mcfadden1973conditional;@van2009]:
 
-This fits the discete choice model for logit model [@liao1994interpreting], which calculates the probability of an event to occur or not.
+$P_j=\frac{\exp(U_j)}{\sum_{}exp((U_k))}$
 
-take on to happen outcome of a probability to occur or not. Given two options, P=1 means choosing the option, P=0 necessary to choose the other alternative.
+$P_j=\frac{1}{1 + \exp((-\beta_e{(e_j-e_i)}) + (-\beta_v{(v_j-v_i)}) }$
 
-under the this justifies using the
-one differentiation between discrete choice models is:\par
-- Logit model: used for 2 options using the logitisc function. Since the probability calculated estimates the chance to choose one option with $P=1$, it can be used for 2 options where $P=0$ means
+$P_j=\frac{\exp(U_{(xj,yj)})}{\sum_{l}exp((U_{xl,yl}))}$
 
-used for two options, the probability calculated with logistic function $P_j=\frac{1}{1 + \exp(-\lambda\times \Delta_{(U_j,U_l)})}$ refers to the event that one option is chosen choose one option with $P_j=1$
+$P_j=\frac{1}{1 + \exp((-\beta_xe_j - \beta_xe_i)}$
 
-- Conditional logit model for multinomial distribution: used for more than two options.
-The probability $P_j=\frac{\exp(U_{(xjyj)})}{\sum_{l}exp((U_{xl,yl}))}$ from @mcfadden1973conditional calculates how one option will be selected out of the set of discrete choices
+In Manski for probability to stay on current cell i$P_i=\frac{\exp(\beta_ee_j + \beta_vv_j)}{\exp(\beta_ee_j + \beta_vv_j) + \exp(\beta_ee_i + \beta_vv_i)}$
 
-As I summarized via e.mail, for two options a multinomial choice model can be considered substantially a binary logit model, in our case since the.
-The two computations of probability above both assume that the random term $\epsilon$ is idependently and identically distributed among options, and the systematic difference
+$P_i=\frac{1}{1 + \exp((\beta_ee_j + \beta_vv_j) - (\beta_ee_i + \beta_vv_i))}$
 
-the assumptions of random utility model on systematic variation in utility and independent and identical distribution of the random term
+$P_j=\frac{1}{1 + \exp((-\beta_e(ej-ei)) + (-\beta_v(vj-vi)))$
 
-. This link synthetizes: [logit_binary_choice, point C](https://en.wikipedia.org/wiki/Discrete_choice#A._Logit_with_attributes_of_the_person_but_no_attributes_of_the_alternatives)
+To my understanding, the two forms to calculate probability with logit model (logistic function) or multinomial choice (conditional logit), would be equivalent in representing a random utility model, as long as the number of options is limited to 2.
+This is the case of our model where the choice of the agent is between the current location and an alternative location.
+Both guarantee that the probability computed is between 0 and 1, that the maximization of utility drives the  agent to choose one option over the other.
+Both model a systematic component of utility and a  random component.
+Both assume that the random term $\epsilon$ is independent and equally distributed among options (i.i.d.).
+This link synthetizes: [logit_binary_choice, point C](https://en.wikipedia.org/wiki/Discrete_choice#A._Logit_with_attributes_of_the_person_but_no_attributes_of_the_alternatives)
+
+The condition of random terms as independent and identically distributed
+
+The random utility frame assumes an extreme-value distribution (Gumbel distribution) of the unknown random terms to fit this assumption.
+The difference of two Gumbel-distributed random variables has a logistic distribution, whose probability density function is the logistic function.
+The logistic function in the logit model implemented in this agent-based model calculates probability based on the difference of the two random utility
+
+The implementation of the logit model here in the agent-based model fits this condition, since the probability to
+
+Since the logit model as formulated in the agent-based model uses the difference in the utility between the two options,
+
+(need of the exponential function), in the conditional logit through the Gumbel distribution,  in the
+
+have in our model where th
+
+should be equivalent in representing a random utility model and what we need.
+They both are probabilities ranging from 0 to 1, the characteristic of the option regulates the probability to be selected, i.e.
+the utility derived from the alternative neighborhood.
+
+This link synthetizes: [logit_binary_choice, point C](https://en.wikipedia.org/wiki/Discrete_choice#A._Logit_with_attributes_of_the_person_but_no_attributes_of_the_alternatives)
 
@@
 e_w <- 0.5              
-v_w <- 1-e_w
+v_w <- 1 - e_w
 k <- 10

### 2019-08-28 paper_notes.Rmd
Add files via upload

@@
      U <- NA}else{
-     if (x < round(n*i_e,digits = 2)){
-   U <- (x / round((n*i_e),digits = 2)) * S
-      }else if (x > round((n*i_e),digits = 2)){
+     if (x < (n*i_e)){
+   U <- (x / (n*i_e)) * S
+      }else if (x > (n*i_e)){
          U <- M + ((1- (x/n))*(1-M))/(1-i_e) 
@@
 
-f_val <- function(e_w,ew_ng,M,i_v,S){
+f_val <- function(e_w,ew_ng,M,i_v,S_v){
   if (round(abs(e_w-ew_ng), digits=2) <= i_v) {
@@
     }else{
-      U <- (M + ((1-(round(abs(e_w-ew_ng), digits=2)))*(1-M))/(1-i_v)) * S
+      U <- (M + ((1-(round(abs(e_w-ew_ng), digits=2)))*(1-M))/(1-i_v)) * S_v
       }
@@
 
-#prob <- function(d_u_e,d_u_v,e_w,v_w,k){round(1 / (1 + exp((-(e_w*k)*(d_u_e)) + (-(v_w*k)*(d_u_v)))),digits= 2)}
-prob <- function(d_u_e,d_u_v,e_w,v_w,k){1 / (1 + exp((-(e_w*k)*(d_u_e)) + (-(v_w*k)*(d_u_v))))}
+prob <- function(d_u_e,d_u_v,e_w,v_w,k){round(1 / (1 + exp((-(e_w*k)*(d_u_e)) + (-(v_w*k)*(d_u_v)))),digits= 2)}
+# prob <- function(d_u_e,d_u_v,e_w,v_w,k){1 / (1 + exp((-(e_w*k)*(d_u_e)) + (-(v_w*k)*(d_u_v))))}
 
@@
 \\
-\left(M + \frac{(1 - \mid{\overline{ew}_j - ew_i}\mid) \times (1 - M)}{1 - i_v}\right) \times S, & otherwise
+\left(M + \frac{(1 - \mid{\overline{ew}_j - ew_i}\mid) \times (1 - M)}{1 - i_v}\right) \times S_v, & otherwise
 \end{cases}
@@
 i_v <- 0.1
-S <- 1
-M <- 0
+S_v <- 1
+M <- 1
 
-fvf0p  <- f_val(e_w,0,M,i_v,S)
-fvf1p  <- f_val(e_w,0.1,M,i_v,S)
-fvf2p   <- f_val(e_w,0.2,M,i_v,S)
-fvf3p   <- f_val(e_w,0.3,M,i_v,S)
-fvf4p   <- f_val(e_w,0.4,M,i_v,S)
-fvf5p   <- f_val(e_w,0.5,M,i_v,S)
-fvf6p   <- f_val(e_w,0.6,M,i_v,S)
-fvf7p   <- f_val(e_w,0.7,M,i_v,S)
-fvf8p   <- f_val(e_w,0.8,M,i_v,S)
-fvf9p  <- f_val(e_w,0.9,M,i_v,S)
-fvf10p  <- f_val(e_w,1.0,M,i_v,S)
+fvf0p  <- f_val(e_w,0,M,i_v,S_v)
+fvf1p  <- f_val(e_w,0.1,M,i_v,S_v)
+fvf2p   <- f_val(e_w,0.2,M,i_v,S_v)
+fvf3p   <- f_val(e_w,0.3,M,i_v,S_v)
+fvf4p   <- f_val(e_w,0.4,M,i_v,S_v)
+fvf5p   <- f_val(e_w,0.5,M,i_v,S_v)
+fvf6p   <- f_val(e_w,0.6,M,i_v,S_v)
+fvf7p   <- f_val(e_w,0.7,M,i_v,S_v)
+fvf8p   <- f_val(e_w,0.8,M,i_v,S_v)
+fvf9p  <- f_val(e_w,0.9,M,i_v,S_v)
+fvf10p  <- f_val(e_w,1.0,M,i_v,S_v)
 
@@
 i_v <- 0.1
-S <- 0
+S_v <- 0
 M <- 0
 
-fvf0t <- f_val(e_w,0,M,i_v,S)
-fvf1t  <- f_val(e_w,0.1,M,i_v,S)
-fvf2t   <- f_val(e_w,0.2,M,i_v,S)
-fvf3t   <- f_val(e_w,0.3,M,i_v,S)
-fvf4t   <- f_val(e_w,0.4,M,i_v,S)
-fvf5t   <- f_val(e_w,0.5,M,i_v,S)
-fvf6t  <- f_val(e_w,0.6,M,i_v,S)
-fvf7t   <- f_val(e_w,0.7,M,i_v,S)
-fvf8t   <- f_val(e_w,0.8,M,i_v,S)
-fvf9t  <- f_val(e_w,0.9,M,i_v,S)
-fvf10t  <- f_val(e_w,1.0,M,i_v,S)
+fvf0t <- f_val(e_w,0,M,i_v,S_v)
+fvf1t  <- f_val(e_w,0.1,M,i_v,S_v)
+fvf2t   <- f_val(e_w,0.2,M,i_v,S_v)
+fvf3t   <- f_val(e_w,0.3,M,i_v,S_v)
+fvf4t   <- f_val(e_w,0.4,M,i_v,S_v)
+fvf5t   <- f_val(e_w,0.5,M,i_v,S_v)
+fvf6t  <- f_val(e_w,0.6,M,i_v,S_v)
+fvf7t   <- f_val(e_w,0.7,M,i_v,S_v)
+fvf8t   <- f_val(e_w,0.8,M,i_v,S_v)
+fvf9t  <- f_val(e_w,0.9,M,i_v,S_v)
+fvf10t  <- f_val(e_w,1.0,M,i_v,S_v)
 
@@
 
-$P_j=\frac{1}{1 + \exp((-\beta_e{(e_j-e_i)}) + (-\beta_v{(v_j-v_i)}) }$
+$P_j=\frac{1}{1 + \exp((-\beta_e{(e_j-e_i)}) + (-\beta_v{(v_j-v_i)})}$
 
@@
 
-$P_j=\frac{1}{1 + \exp((-\beta_e(ej-ei)) + (-\beta_v(vj-vi)))$
+$P_j=\frac{1}{1 + \exp((-\beta_e(ej-ei)) + (-\beta_v(vj-vi)))}$
 
@@
 
-i_e = 0.5   # parameters to manipulate
+i_e = 0.6   # parameters to manipulate
 S = 1     # Symmetric single-peaked function: S=1,M=0
@@
 
-e_w <- 0.4    # parameters to manipulate
+e_w <- 0.5    # parameters to manipulate
 i_v <- 0.2    # Symmetric = S:1,M:0/Threshold = S:0
-S  <- 1
+S_v  <- 0
 M <-  0
 
-fv0d2 <- f_val(e_w,0,M,i_v,S)             # value utility for each option, 
-fv1d2 <- f_val(e_w,0.1,M,i_v,S)           # increasing number is average ethnic weight of neighborhood j
-fv2d2 <- f_val(e_w,0.2,M,i_v,S)
-fv3d2 <- f_val(e_w,0.3,M,i_v,S)
-fv4d2 <- f_val(e_w,0.4,M,i_v,S)
-fv5d2 <- f_val(e_w,0.5,M,i_v,S)
-fv6d2 <- f_val(e_w,0.6,M,i_v,S)
-fv7d2 <- f_val(e_w,0.7,M,i_v,S)
-fv8d2 <- f_val(e_w,0.8,M,i_v,S)
-fv9d2 <- f_val(e_w,0.9,M,i_v,S)
-fv10d2 <- f_val(e_w,1.0,M,i_v,S)
+fv0d2 <- f_val(e_w,0,M,i_v,S_v)             # value utility for each option, 
+fv1d2 <- f_val(e_w,0.1,M,i_v,S_v)           # increasing nuMber is average ethnic weight of neighborhood j
+fv2d2 <- f_val(e_w,0.2,M,i_v,S_v)
+fv3d2 <- f_val(e_w,0.3,M,i_v,S_v)
+fv4d2 <- f_val(e_w,0.4,M,i_v,S_v)
+fv5d2 <- f_val(e_w,0.5,M,i_v,S_v)
+fv6d2 <- f_val(e_w,0.6,M,i_v,S_v)
+fv7d2 <- f_val(e_w,0.7,M,i_v,S_v)
+fv8d2 <- f_val(e_w,0.8,M,i_v,S_v)
+fv9d2 <- f_val(e_w,0.9,M,i_v,S_v)
+fv10d2 <- f_val(e_w,1.0,M,i_v,S_v)
 
@@
 
-report_V <- na.omit(data.frame(M,S,des_dist,ew_agent,mean_ew_ng,Utility_V))
+report_V <- na.omit(data.frame(M,S_v,des_dist,ew_agent,mean_ew_ng,Utility_V))
 
-title_cond_V <- paste0("Ethnic weight i = ", e_w,"; desired distance i = ",i_v,"\n\r","M =", M,"; ", "S = ",S)
+title_cond_V <- paste0("Ethnic weight i = ", e_w,"; desired distance i = ",i_v,"\n\r","M =", M,"; ", "S = ",S_v)
 

### 2019-08-28 paper_notes.Rmd
ok_values

@@
 
-f_val <- function(e_w,ew_ng,M,i_v,S_v){
+f_val <- function(e_w,ew_ng,i_v,S_v){
   if (round(abs(e_w-ew_ng), digits=2) <= i_v) {
@@
     }else{
-      U <- (M + ((1-(round(abs(e_w-ew_ng), digits=2)))*(1-M))/(1-i_v)) * S_v
+      U <- ((1-(round(abs(e_w-ew_ng), digits=2)))/(1-i_v)) * S_v
       }
@@
 \\
-\left(M + \frac{(1 - \mid{\overline{ew}_j - ew_i}\mid) \times (1 - M)}{1 - i_v}\right) \times S_v, & otherwise
+\left(\frac{(1 - \mid{\overline{ew}_j - ew_i}\mid) }{1 - i_v}\right) \times S_v, & otherwise
 \end{cases}
@@
 S_v <- 1
-M <- 1
 
-fvf0p  <- f_val(e_w,0,M,i_v,S_v)
-fvf1p  <- f_val(e_w,0.1,M,i_v,S_v)
-fvf2p   <- f_val(e_w,0.2,M,i_v,S_v)
-fvf3p   <- f_val(e_w,0.3,M,i_v,S_v)
-fvf4p   <- f_val(e_w,0.4,M,i_v,S_v)
-fvf5p   <- f_val(e_w,0.5,M,i_v,S_v)
-fvf6p   <- f_val(e_w,0.6,M,i_v,S_v)
-fvf7p   <- f_val(e_w,0.7,M,i_v,S_v)
-fvf8p   <- f_val(e_w,0.8,M,i_v,S_v)
-fvf9p  <- f_val(e_w,0.9,M,i_v,S_v)
-fvf10p  <- f_val(e_w,1.0,M,i_v,S_v)
+fvf0p  <- f_val(e_w,0,i_v,S_v)
+fvf1p  <- f_val(e_w,0.1,i_v,S_v)
+fvf2p   <- f_val(e_w,0.2,i_v,S_v)
+fvf3p   <- f_val(e_w,0.3,i_v,S_v)
+fvf4p   <- f_val(e_w,0.4,i_v,S_v)
+fvf5p   <- f_val(e_w,0.5,i_v,S_v)
+fvf6p   <- f_val(e_w,0.6,i_v,S_v)
+fvf7p   <- f_val(e_w,0.7,i_v,S_v)
+fvf8p   <- f_val(e_w,0.8,i_v,S_v)
+fvf9p  <- f_val(e_w,0.9,i_v,S_v)
+fvf10p  <- f_val(e_w,1.0,i_v,S_v)
 
@@
 S_v <- 0
-M <- 0
 
-fvf0t <- f_val(e_w,0,M,i_v,S_v)
-fvf1t  <- f_val(e_w,0.1,M,i_v,S_v)
-fvf2t   <- f_val(e_w,0.2,M,i_v,S_v)
-fvf3t   <- f_val(e_w,0.3,M,i_v,S_v)
-fvf4t   <- f_val(e_w,0.4,M,i_v,S_v)
-fvf5t   <- f_val(e_w,0.5,M,i_v,S_v)
-fvf6t  <- f_val(e_w,0.6,M,i_v,S_v)
-fvf7t   <- f_val(e_w,0.7,M,i_v,S_v)
-fvf8t   <- f_val(e_w,0.8,M,i_v,S_v)
-fvf9t  <- f_val(e_w,0.9,M,i_v,S_v)
-fvf10t  <- f_val(e_w,1.0,M,i_v,S_v)
+fvf0t <- f_val(e_w,0,i_v,S_v)
+fvf1t  <- f_val(e_w,0.1,i_v,S_v)
+fvf2t   <- f_val(e_w,0.2,i_v,S_v)
+fvf3t   <- f_val(e_w,0.3,i_v,S_v)
+fvf4t   <- f_val(e_w,0.4,i_v,S_v)
+fvf5t   <- f_val(e_w,0.5,i_v,S_v)
+fvf6t  <- f_val(e_w,0.6,i_v,S_v)
+fvf7t   <- f_val(e_w,0.7,i_v,S_v)
+fvf8t   <- f_val(e_w,0.8,i_v,S_v)
+fvf9t  <- f_val(e_w,0.9,i_v,S_v)
+fvf10t  <- f_val(e_w,1.0,i_v,S_v)
 
@@
 
-symm_val_plot <- symm_val_graph + geom_point() + theme_bw() + labs(x = "Mean ethnic weight neighborhood j",y = "Value utility j") + ggtitle(label = "Symmetric Single Peaked (S=1,M=0) ",subtitle = subt_cont_v) + theme(plot.title = element_text(hjust = 0.5), plot.subtitle = element_text(hjust = 0.5))  + scale_x_continuous(breaks = seq(0.0,1.0,by = 0.1)) + scale_y_continuous(limits =  c(0.0,1.0), breaks = seq(0.0,1.0,by = 0.25))
+symm_val_plot <- symm_val_graph + geom_point() + theme_bw() + labs(x = "Mean ethnic weight neighborhood j",y = "Value utility j") + ggtitle(label = "Symmetric Single Peaked (S=1) ",subtitle = subt_cont_v) + theme(plot.title = element_text(hjust = 0.5), plot.subtitle = element_text(hjust = 0.5))  + scale_x_continuous(breaks = seq(0.0,1.0,by = 0.1)) + scale_y_continuous(limits =  c(0.0,1.0), breaks = seq(0.0,1.0,by = 0.25))
 

### 2019-08-28 paper_notes.Rmd
check formula, no M value, simplify ethnic

@@
      U <- NA}else{
-     if (x < (n*i_e)){
+     if (x <= (n*i_e)){
    U <- (x / (n*i_e)) * S
-      }else if (x > (n*i_e)){
+      }else {
          U <- M + ((1- (x/n))*(1-M))/(1-i_e) 
-        }else{
-     U <- 1}
+        }
         round(U,digits = 3)
@@
 
-f_val <- function(e_w,ew_ng,i_v,S_v){
+f_val <- function(e_w,ew_ng,i_v,S_v,Mv){
   if (round(abs(e_w-ew_ng), digits=2) <= i_v) {
@@
     }else{
-      U <- ((1-(round(abs(e_w-ew_ng), digits=2)))/(1-i_v)) * S_v
+      U <- (Mv + ((1-(round(abs(e_w-ew_ng), digits=2)))*(1-Mv))/(1-i_v)) * S_v
+        # (M + ((1-(round(abs(e_w-ew_ng), digits=2)))*(1-M))/(1-i_v)) * S
       }
@@
 S_v <- 1
+Mv <- 0
 
-fvf0p  <- f_val(e_w,0,i_v,S_v)
-fvf1p  <- f_val(e_w,0.1,i_v,S_v)
-fvf2p   <- f_val(e_w,0.2,i_v,S_v)
-fvf3p   <- f_val(e_w,0.3,i_v,S_v)
-fvf4p   <- f_val(e_w,0.4,i_v,S_v)
-fvf5p   <- f_val(e_w,0.5,i_v,S_v)
-fvf6p   <- f_val(e_w,0.6,i_v,S_v)
-fvf7p   <- f_val(e_w,0.7,i_v,S_v)
-fvf8p   <- f_val(e_w,0.8,i_v,S_v)
-fvf9p  <- f_val(e_w,0.9,i_v,S_v)
-fvf10p  <- f_val(e_w,1.0,i_v,S_v)
+fvf0p  <- f_val(e_w,0,i_v,S_v,Mv)
+fvf1p  <- f_val(e_w,0.1,i_v,S_v,Mv)
+fvf2p   <- f_val(e_w,0.2,i_v,S_v,Mv)
+fvf3p   <- f_val(e_w,0.3,i_v,S_v,Mv)
+fvf4p   <- f_val(e_w,0.4,i_v,S_v,Mv)
+fvf5p   <- f_val(e_w,0.5,i_v,S_v,Mv)
+fvf6p   <- f_val(e_w,0.6,i_v,S_v,Mv)
+fvf7p   <- f_val(e_w,0.7,i_v,S_v,Mv)
+fvf8p   <- f_val(e_w,0.8,i_v,S_v,Mv)
+fvf9p  <- f_val(e_w,0.9,i_v,S_v,Mv)
+fvf10p  <- f_val(e_w,1.0,i_v,S_v,Mv)
 
@@
 
-fvf0t <- f_val(e_w,0,i_v,S_v)
-fvf1t  <- f_val(e_w,0.1,i_v,S_v)
-fvf2t   <- f_val(e_w,0.2,i_v,S_v)
-fvf3t   <- f_val(e_w,0.3,i_v,S_v)
-fvf4t   <- f_val(e_w,0.4,i_v,S_v)
-fvf5t   <- f_val(e_w,0.5,i_v,S_v)
-fvf6t  <- f_val(e_w,0.6,i_v,S_v)
-fvf7t   <- f_val(e_w,0.7,i_v,S_v)
-fvf8t   <- f_val(e_w,0.8,i_v,S_v)
-fvf9t  <- f_val(e_w,0.9,i_v,S_v)
-fvf10t  <- f_val(e_w,1.0,i_v,S_v)
+fvf0t <- f_val(e_w,0,i_v,S_v,Mv)
+fvf1t  <- f_val(e_w,0.1,i_v,S_v,Mv)
+fvf2t   <- f_val(e_w,0.2,i_v,S_v,Mv)
+fvf3t   <- f_val(e_w,0.3,i_v,S_v,Mv)
+fvf4t   <- f_val(e_w,0.4,i_v,S_v,Mv)
+fvf5t   <- f_val(e_w,0.5,i_v,S_v,Mv)
+fvf6t  <- f_val(e_w,0.6,i_v,S_v,Mv)
+fvf7t   <- f_val(e_w,0.7,i_v,S_v,Mv)
+fvf8t   <- f_val(e_w,0.8,i_v,S_v,Mv)
+fvf9t  <- f_val(e_w,0.9,i_v,S_v,Mv)
+fvf10t  <- f_val(e_w,1.0,i_v,S_v,Mv)
 
@@
 
+## Single Run
+```{r single-run,fig.width=4,fig.height= 3, fig.align="center", include=TRUE, echo=FALSE}
+
+e_w = 0.875
+  v_w = 1-e_w
+ew_ng_curr = 0.933
+ew_ng_alt = 0.906
+i_e = 0.5
+S = 1
+M = 0
+i_v = 0.1
+S_v = 0
+k = 2
+n_curr = 8
+  eth_curr = 5
+n_alt = 7
+  eth_alt = 4
+
+param_eth <- k * e_w
+param_val <- k * v_w
+
+dist_curr <- abs(ew_ng_curr - e_w)
+  dist_alt <- abs(ew_ng_alt - e_w)
+
+conc_curr <- (eth_curr / n_curr)
+conc_alt <- (eth_alt / n_alt)
+
+uti_eth_curr <- f_eth(i_e,M,eth_curr,n_curr,S)
+uti_eth_alt <- f_eth(i_e,M,eth_alt,n_alt,S)
+
+uti_val_curr <- f_val(e_w,ew_ng_curr,i_v,S_v)
+uti_val_alt <- f_val(e_w,ew_ng_alt,i_v,S_v)
+
+diff_eth <- (uti_eth_alt - uti_eth_curr)
+  diff_val <- (uti_val_alt - uti_val_curr )
+
+prob_one_run <- prob(diff_eth,diff_val,e_w,v_w,k)
+
+report_one_run <- na.omit(data.frame(param_eth,param_val,i_e,i_v,S,M,dist_curr,dist_alt,conc_curr,conc_alt,uti_eth_curr,uti_eth_alt,uti_val_curr,uti_val_alt,prob_one_run))
+
+suppressWarnings(suppressMessages(
+knitr::kable(report_one_run,align="c")
+))
+
+```
+
 ## Ethnic Utility Calculation
@@
 
-i_e = 0.6   # parameters to manipulate
+i_e = 0.3   # parameters to manipulate
 S = 1     # Symmetric single-peaked function: S=1,M=0
@@
 e_w <- 0.5    # parameters to manipulate
-i_v <- 0.2    # Symmetric = S:1,M:0/Threshold = S:0
-S_v  <- 0
-M <-  0
+i_v <- 0.0    # Symmetric = S:1,M:0/Threshold = S:0
+S_v  <- 1
+Mv <- 0
 
-fv0d2 <- f_val(e_w,0,M,i_v,S_v)             # value utility for each option, 
-fv1d2 <- f_val(e_w,0.1,M,i_v,S_v)           # increasing nuMber is average ethnic weight of neighborhood j
-fv2d2 <- f_val(e_w,0.2,M,i_v,S_v)
-fv3d2 <- f_val(e_w,0.3,M,i_v,S_v)
-fv4d2 <- f_val(e_w,0.4,M,i_v,S_v)
-fv5d2 <- f_val(e_w,0.5,M,i_v,S_v)
-fv6d2 <- f_val(e_w,0.6,M,i_v,S_v)
-fv7d2 <- f_val(e_w,0.7,M,i_v,S_v)
-fv8d2 <- f_val(e_w,0.8,M,i_v,S_v)
-fv9d2 <- f_val(e_w,0.9,M,i_v,S_v)
-fv10d2 <- f_val(e_w,1.0,M,i_v,S_v)
+fv0d2 <- f_val(e_w,0,i_v,S_v,Mv)             # value utility for each option, 
+fv1d2 <- f_val(e_w,0.1,i_v,S_v,Mv)           # increasing nuMber is average ethnic weight of neighborhood j
+fv2d2 <- f_val(e_w,0.2,i_v,S_v,Mv)
+fv3d2 <- f_val(e_w,0.3,i_v,S_v,Mv)
+fv4d2 <- f_val(e_w,0.4,i_v,S_v,Mv)
+fv5d2 <- f_val(e_w,0.5,i_v,S_v,Mv)
+fv6d2 <- f_val(e_w,0.6,i_v,S_v,Mv)
+fv7d2 <- f_val(e_w,0.7,i_v,S_v,Mv)
+fv8d2 <- f_val(e_w,0.8,i_v,S_v,Mv)
+fv9d2 <- f_val(e_w,0.9,i_v,S_v,Mv)
+fv10d2 <- f_val(e_w,1.0,i_v,S_v,Mv)
 
@@
 
-report_V <- na.omit(data.frame(M,S_v,des_dist,ew_agent,mean_ew_ng,Utility_V))
+report_V <- na.omit(data.frame(Mv,S_v,des_dist,ew_agent,mean_ew_ng,Utility_V))
 
-title_cond_V <- paste0("Ethnic weight i = ", e_w,"; desired distance i = ",i_v,"\n\r","M =", M,"; ", "S = ",S_v)
+title_cond_V <- paste0("Ethnic weight i = ", e_w,"; desired distance i = ",i_v,"\n\r", "S = ",S_v)
 

### 2019-09-03 paper_notes.Rmd
updates 03_09_2019

--- 2019-08-28 paper_notes.Rmd
@@
 \begin{cases}
-1, & \text{if} x =  n\times i_e, \\
+1, & \text{if} \ x =  n\times i_e, \\
 \\
@@
 M = 0                       # M: right-side slope, S: left-side slope, n = total number of agents in neighborhood
-S = 1
+S = 0
 n = 8
@@
 
-e_w <- 0.2
+e_w <- 0.9
 e_w_ng <- seq(0.0,1.0, by = 0.1)
-i_v <- 0.1
+i_v <- 0.0
 S_v <- 1
@@
 
-i_e = 0.6   # parameters to manipulate
+i_e = 0.8  # parameters to manipulate
 S = 1     # Symmetric single-peaked function: S=1,M=0
 M = 0    # Linear + Constant function = S=1,M=1
-n = 8     # Schelling Threshold function = S=0,M=1
+n = 4     # Schelling Threshold function = S=0,M=1
 
@@
 
-e_w <- 0.5    # parameters to manipulate
+e_w <- 0.2    # parameters to manipulate
 i_v <- 0.2   # Symmetric = S:1,M:0/Threshold = S:0
 S_v  <- 0
-M <-  0
 
-fv0d2 <- f_val(e_w,0,M,i_v,S_v)             # value utility for each option, 
-fv1d2 <- f_val(e_w,0.1,M,i_v,S_v)           # increasing nuMber is average ethnic weight of neighborhood j
-fv2d2 <- f_val(e_w,0.2,M,i_v,S_v)
-fv3d2 <- f_val(e_w,0.3,M,i_v,S_v)
-fv4d2 <- f_val(e_w,0.4,M,i_v,S_v)
-fv5d2 <- f_val(e_w,0.5,M,i_v,S_v)
-fv6d2 <- f_val(e_w,0.6,M,i_v,S_v)
-fv7d2 <- f_val(e_w,0.7,M,i_v,S_v)
-fv8d2 <- f_val(e_w,0.8,M,i_v,S_v)
-fv9d2 <- f_val(e_w,0.9,M,i_v,S_v)
-fv10d2 <- f_val(e_w,1.0,M,i_v,S_v)
+fv0d2 <- f_val(e_w,0,i_v,S_v)             # value utility for each option, 
+fv1d2 <- f_val(e_w,0.1,i_v,S_v)           # increasing nuMber is average ethnic weight of neighborhood j
+fv2d2 <- f_val(e_w,0.2,i_v,S_v)
+fv3d2 <- f_val(e_w,0.3,i_v,S_v)
+fv4d2 <- f_val(e_w,0.4,i_v,S_v)
+fv5d2 <- f_val(e_w,0.5,i_v,S_v)
+fv6d2 <- f_val(e_w,0.6,i_v,S_v)
+fv7d2 <- f_val(e_w,0.7,i_v,S_v)
+fv8d2 <- f_val(e_w,0.8,i_v,S_v)
+fv9d2 <- f_val(e_w,0.9,i_v,S_v)
+fv10d2 <- f_val(e_w,1.0,i_v,S_v)
 
@@
 
-report_V <- na.omit(data.frame(M,S_v,des_dist,ew_agent,mean_ew_ng,Utility_V))
+report_V <- na.omit(data.frame(S_v,des_dist,ew_agent,mean_ew_ng,Utility_V))
 
-title_cond_V <- paste0("Ethnic weight i = ", e_w,"; desired distance i = ",i_v,"\n\r","M =", M,"; ", "S = ",S_v)
+title_cond_V <- paste0("Ethnic weight i = ", e_w,"; desired distance i = ",i_v,"\n\r", "S = ",S_v)
 

### 2019-09-08 paper_notes.Rmd
update 03_09_2019
ok 08_09

@@
 
-$P_j=\frac{1}{1 + \exp(-\lambda\times \Delta_{(U_j,U_i)})}$
+$P_j=\frac{1}{1 + \exp(-\beta\times \Delta_{(U_j,U_i)})}$
 
-An alternative to the logit model is the multinomial choice model, which is a generalization of the binary model where the choice is between more than two options [@train2009discrete].
-The probability to choose one option over the others is calculated according to the conditional logit model [@mcfadden1973conditional], depending on the characteristics of the options.
-Applied to utility maximization and random utility models [@mcfadden1973conditional;@van2009]:
-
-$P_j=\frac{\exp(U_j)}{\sum_{}exp((U_k))}$
-
-$P_j=\frac{1}{1 + \exp((-\beta_e{(e_j-e_i)}) + (-\beta_v{(v_j-v_i)})}$
-
-$P_j=\frac{\exp(U_{(xj,yj)})}{\sum_{l}exp((U_{xl,yl}))}$
-
-$P_j=\frac{1}{1 + \exp((-\beta_xe_j - \beta_xe_i)}$
-
-In Manski for probability to stay on current cell i$P_i=\frac{\exp(\beta_ee_j + \beta_vv_j)}{\exp(\beta_ee_j + \beta_vv_j) + \exp(\beta_ee_i + \beta_vv_i)}$
-
-$P_i=\frac{1}{1 + \exp((\beta_ee_j + \beta_vv_j) - (\beta_ee_i + \beta_vv_i))}$
-
-$P_j=\frac{1}{1 + \exp((-\beta_e(ej-ei)) + (-\beta_v(vj-vi)))}$
-
-To my understanding, the two forms to calculate probability with logit model (logistic function) or multinomial choice (conditional logit), would be equivalent in representing a random utility model, as long as the number of options is limited to 2.
-This is the case of our model where the choice of the agent is between the current location and an alternative location.
-Both guarantee that the probability computed is between 0 and 1, that the maximization of utility drives the  agent to choose one option over the other.
-Both model a systematic component of utility and a  random component.
-Both assume that the random term $\epsilon$ is independent and equally distributed among options (i.i.d.).
-This link synthetizes: [logit_binary_choice, point C](https://en.wikipedia.org/wiki/Discrete_choice#A._Logit_with_attributes_of_the_person_but_no_attributes_of_the_alternatives)
-
-The condition of random terms as independent and identically distributed
-
-The random utility frame assumes an extreme-value distribution (Gumbel distribution) of the unknown random terms to fit this assumption.
-The difference of two Gumbel-distributed random variables has a logistic distribution, whose probability density function is the logistic function.
-The logistic function in the logit model implemented in this agent-based model calculates probability based on the difference of the two random utility
-
-The implementation of the logit model here in the agent-based model fits this condition, since the probability to
-
-Since the logit model as formulated in the agent-based model uses the difference in the utility between the two options,
-
-(need of the exponential function), in the conditional logit through the Gumbel distribution,  in the
-
-have in our model where th
-
-should be equivalent in representing a random utility model and what we need.
-They both are probabilities ranging from 0 to 1, the characteristic of the option regulates the probability to be selected, i.e.
-the utility derived from the alternative neighborhood.
-
-This link synthetizes: [logit_binary_choice, point C](https://en.wikipedia.org/wiki/Discrete_choice#A._Logit_with_attributes_of_the_person_but_no_attributes_of_the_alternatives)
-
-Here is the logistic function implemented in the model for the choice between current location and alternative location:
+Here is the logistic function implemented in the model for the choice between current location and alternative location and the two dimensions ethnic and value utility used:
 
@@
 
-which uses the conditioanl logit to calculate the probability to choose $\textit{j}$ ($P_j=\frac{\exp(U_{(xjyj)})}{\sum_{l}exp((U_{xl,yl}))}$).
-As I wrote and as I understand so far, for two options the calculation of probability according to the multinomial choice formulation and the logistic function for binary choice can be considered equivalent as they both will assure the $i.i.d$ distribution of the random term, which is the priority of random utility models.\\
-
-$k$ times ethnic weight $ew$ and $k$ times $vw$ substitute the parameters in random  utility for how important the ethnic composition and value composition are in the logistic function ($\lambda$ in $P_j=\frac{1}{1 + \exp(-\lambda\times \Delta_{U_e})+(-\lambda \times \Delta_{U_v}))}$ and $\beta_xe_j$ $\beta_yv_j$ in  $\textit{j}$ ($P_j=\frac{\exp(U_{(xjyj)})}{\sum_{l}exp((U_{xl,yl}))}$.
+$k$ times ethnic weight $ew$ and $k$ times $vw$ substitute the parameters in random  utility for how important the ethnic composition and value composition are in the logistic function.
 My idea is that ethnic weight and value weight range from 0 to 1, whose value is too low causing random choices, by multiplying by a constant the ratio in the distribution point stay the same.\par
@@
 \ref{fig:heatmaps}
+
+An alternative to the logit model is the multinomial choice model, which is a generalization of the binary model where the choice is between more than two options [@train2009discrete].
+The probability to choose one option over the others is calculated according to the conditional logit model [@mcfadden1973conditional], depending on the characteristics of the options.
+Applied to utility maximization and random utility models [@mcfadden1973conditional;@van2009]:
+
+$P_j=\frac{\exp(U_j)}{\sum_{}exp((U_k))}$
+
+With utility calculated as above $\beta_ee_j + \beta_vv_j$ and $exp((U_k))$ the exponential function of the sum of all set of options
+
+$P_j=\frac{1}{1 + \exp((-\beta_e{(e_j-e_i)}) + (-\beta_v{(v_j-v_i)})}$
+
+$P_j=\frac{\exp(U_{(xj,yj)})}{\sum_{l}exp((U_{xl,yl}))}$
+
+$P_j=\frac{1}{1 + \exp((-\beta_xe_j - \beta_xe_i)}$
+
+In Manski for probability to stay on current cell i$P_i=\frac{\exp(\beta_ee_j + \beta_vv_j)}{\exp(\beta_ee_j + \beta_vv_j) + \exp(\beta_ee_i + \beta_vv_i)}$
+
+$P_i=\frac{1}{1 + \exp((\beta_eUe_j + \beta_vUv_j) - (\beta_eUe_i + \beta_vUv_i))}$
+
+From here, in terms of two options, the probability of an agent to relocate from current node \textit{i} to alternative \textit{j}  becomes:
+
+$P_j=\frac{1}{1 + \exp((-\beta_e{(Ue_j-Ue_i)}) + (-\beta_v{(Uv_j-Uv_i)})}$
+
+I applied it to the beta distribution of ethnic weights and value weights
+
+To my understanding, the two forms to calculate probability with logit model (logistic function) or multinomial choice (conditional logit), would be equivalent in representing a random utility model, as long as the number of options is limited to 2.
+This is the case of our model where the choice of the agent is between the current location and an alternative location.
+Both guarantee that the probability computed is between 0 and 1, that the maximization of utility drives the  agent to choose one option over the other.
+Both model a systematic component of utility and a  random component.
+Both assume that the random term $\epsilon$ is independent and equally distributed among options (i.i.d.).
+This link synthetizes: [logit_binary_choice, point C](https://en.wikipedia.org/wiki/Discrete_choice#A._Logit_with_attributes_of_the_person_but_no_attributes_of_the_alternatives)
+
+The random utility frame assumes an extreme-value distribution (Gumbel distribution) of the unknown random terms to fit this assumption.
+The difference of two Gumbel-distributed random variables has a logistic distribution, whose probability density function is the logistic function.
+The logistic function in the logit model implemented in this agent-based model calculates probability based on the difference of the two random utility
 
@@
 i_v <- 0.2   # Symmetric = S:1,M:0/Threshold = S:0
-S_v  <- 0
+S_v  <- 1
 

### 2019-09-16 paper_notes.Rmd
Add files via upload

@@
 
-i_e = 0.8  # parameters to manipulate
+i_e = 0.5  # parameters to manipulate
 S = 1     # Symmetric single-peaked function: S=1,M=0
-M = 0    # Linear + Constant function = S=1,M=1
-n = 4     # Schelling Threshold function = S=0,M=1
+M = 0.5    # Linear + Constant function = S=1,M=1
+n = 8     # Schelling Threshold function = S=0,M=1
 

### 2019-11-04 ethnic_value_rum.Rmd
to add eq 30 hg beta

---
output:
  bookdown::pdf_document2:
    toc: false
 #   keep_tex: false
    fig_caption: yes
title: "Preferences interact: what consequences for a Schelling scenario?"
# subtitle: "Target: BIGSSS Research Day"
author:  Rocco Paolillo, Andreas Flache, Jan Lorenz
date:  "`r  as.Date(Sys.time(), '%d %B %Y')`"
# "`r  as.Date(Sys.time(), '%d %B %Y')`"
language: en-GB
bibliography: "references.bib"
always_allow_html: yes
header-includes:
- \usepackage{float}
- \usepackage{multirow}
- \usepackage{xcolor} 
- \usepackage{amsmath}
- \usepackage{graphicx}

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.lp="fig:",warning = FALSE)

# install.packages("tinytex", repos = "https://cloud.r-project.org" )

library(tidyverse)
library(ggplot2)
library(gridExtra)
library(tidyr)
library(plyr)
library(foreach)

# data_eq_30_10 <- read.csv("50_g_30_bh_10bl.csv",sep = ",",skip = 6)      # eq_30 equal conditionn for high beta 30 beig recollected
#  names(data_eq_30_10) <- pull(read_csv("code_names.csv"))
#  data_eq_30_20 <- read.csv("50_g_30_bh_20bl.csv",sep = ",",skip = 6)
#   names(data_eq_30_20) <- pull(read_csv("code_names.csv"))
#  data_eq_30_30 <- read.csv("50_g_30_bh_30bl.csv",sep = ",",skip = 6)
#   names(data_eq_30_30) <- pull(read_csv("code_names.csv"))
#  raw_eq_30 <- rbind(data_eq_30_10,data_eq_30_20,data_eq_30_30)
#  write.csv(raw_eq_30, file = "eq_30.csv",row.names=FALSE)
# 
# 
# 
# eq_30 <- read.csv("eq_30.csv",sep = ",",skip = 6)
# names(eq_30) <- pull(read_csv("code_names.csv"))

eq_10 <- read.csv("50g_10_bh_10_bl.csv",sep = ",",skip = 6)
names(eq_10) <- pull(read_csv("code_names.csv"))

mj_30 <- read.csv("80_g_30_bh.csv",sep = ",",skip = 6)
names(mj_30) <- pull(read_csv("code_names.csv"))

mj_10 <- read.csv("80_g_10_bh.csv",sep = ",",skip = 6)
names(mj_10) <- pull(read_csv("code_names.csv"))

 f_spk <- function(i_e,x,n){      # utility function as single-peaked
  if (x > n){
    U <- NA}else{
    if (x < (n*i_e)){
  U <- (x / (n*i_e))
     }else if (x > (n*i_e)){
        U <- i_e + (((1- (x/n))*(1-i_e))/(1-i_e))
       }else{
    U <- 1}
       round(U,digits = 3)
     }
}

 f_thr <- function(i_e,x,n){  # to plot threshold function
  if (x >= (n*i_e)){
    U <- 1}else{
   U <- 0 }
}

 # install.packages("tinytex", repos = "https://cloud.r-project.org" ) #, try if debug needed

```

\abstract{}

# Introduction {-}

# Model and Experiments

# Results

# References

### 2019-11-05 ethnic_value_rum.Rmd
add data

@@
 library(foreach)
+library(dplyr)
 
-# data_eq_30_10 <- read.csv("50_g_30_bh_10bl.csv",sep = ",",skip = 6)      # eq_30 equal conditionn for high beta 30 beig recollected
-#  names(data_eq_30_10) <- pull(read_csv("code_names.csv"))
-#  data_eq_30_20 <- read.csv("50_g_30_bh_20bl.csv",sep = ",",skip = 6)
-#   names(data_eq_30_20) <- pull(read_csv("code_names.csv"))
-#  data_eq_30_30 <- read.csv("50_g_30_bh_30bl.csv",sep = ",",skip = 6)
-#   names(data_eq_30_30) <- pull(read_csv("code_names.csv"))
-#  raw_eq_30 <- rbind(data_eq_30_10,data_eq_30_20,data_eq_30_30)
-#  write.csv(raw_eq_30, file = "eq_30.csv",row.names=FALSE)
-# 
-# 
-# 
-# eq_30 <- read.csv("eq_30.csv",sep = ",",skip = 6)
-# names(eq_30) <- pull(read_csv("code_names.csv"))
+eq_10 <- read.csv("50_g_10_bh.csv",sep = ",",skip = 6)
+names(eq_10) <- pull(read_csv("code_names.csv"))
 
-eq_10 <- read.csv("50g_10_bh_10_bl.csv",sep = ",",skip = 6)
-names(eq_10) <- pull(read_csv("code_names.csv"))
+mj_10 <- read.csv("80_g_10_bh.csv",sep = ",",skip = 6)
+names(mj_10) <- pull(read_csv("code_names.csv"))
+
+eq_30 <- read.csv("50_g_30_hb.csv", sep = ",", skip = 6)
+names(eq_30) <- pull(read_csv("code_names.csv"))
 
@@
 
-mj_10 <- read.csv("80_g_10_bh.csv",sep = ",",skip = 6)
-names(mj_10) <- pull(read_csv("code_names.csv"))
+raw_f <- rbind(eq_30,eq_10,mj_30,mj_10)
+
+df_e_sqr <- raw_f$e_sqr - raw_f$v_sqr
+df_v_crl <-  raw_f$v_crl - raw_f$e_crl
+
+dataset <- cbind(raw_f,df_e_sqr,df_v_crl)
+
+# check <- final[,c(9,10,27,11,12,28)]
+
+write.csv(dataset, file = "dataset.csv",row.names=FALSE) # later for reproduction
 
@@
 
+```{r  heatmap, echo = FALSE}
+
+dataset %>% filter(e_sqr == 30, v_crl == 30)
+
+```
+
 # References

### 2019-11-06 ethnic_value_rum.Rmd
writing up

@@
 
+test <- read.csv("cond1.csv",sep = ",", skip = 6)
+names(test) <- pull(read_csv("code_names.csv"))
+
 raw_f <- rbind(eq_30,eq_10,mj_30,mj_10)
@@
 
+* Schelling's model and previous work. Interaction of preferences.
+Schelling's model
+Literature update
+@paolillo2018 Diverse dimensions can define individuals and their similarity. Results from @paolillo2018
+
+* Update: justification for random utility models
+Better define the individual  decision process
+Link with empirical data
+
+* Research question
+How would the interaction between $\beta$ for different dimensions affect Schelling's scenarios
+
 # Model and Experiments
+
+The model^[The model can be found here:https://github.com/RoccoPaolillo/BIGSSS_ResearchDay.git] was built in NetLogo 6.1.0 and extends work by @paolillo2018.
+Agents interact on a regular grid 51 times 51 with periodic boundary conditions (torus world).
+Each node of the grid can host 1 agent or being empty.
+Agents represents individuals who relocate and are  defined by two static and overlapping variables: ethnicity and value orientation.
+Ethnicity is modeled through color tag.
+Agents with blue color represent the local population, agents with orange color represent the minority group.
+Value orientation through shape tag.
+
+We define value orientation as the common membership of agents sharing same beliefs, preferences etc.
+potentially subject to change and independent of their attributed ethnicity.
+As such value orientation relates to value homophily compared to ethncity related to ascribed status homophily.
+Each agent hold a preference for the ethnic composition and the value composition of each neighborhood.
+Neighborhoods are defined as a Moore distance.
+At each step, an agent randomly selected compares its current location to a number of alternative ones, calculates utility for each and decides which location they prefer.
+
+* Calculation utility and probability function
 
@@
 
-```{r  heatmap, echo = FALSE}
+```{r  heatmap, include = FALSE, echo = FALSE}
 

### 2019-11-07 ethnic_value_rum.Rmd
Add files via upload
added data, simplified check

@@
 library(plyr)
-library(foreach)
 library(dplyr)
@@
 
-test <- read.csv("cond1.csv",sep = ",", skip = 6)
-names(test) <- pull(read_csv("code_names.csv"))
+mj_30_10 <- read.csv("80_g_30_10.csv",sep = ",", skip = 6)
+names(mj_30_10) <- pull(read_csv("code_names.csv"))
+
+eq_30_10 <- read.csv("50_g_30_10.csv",sep = ",", skip = 6)
+names(eq_30_10) <- pull(read_csv("code_names.csv"))
 
@@
 
-```{r  heatmap, include = FALSE, echo = FALSE}
+```{r gg }
 
-dataset %>% filter(e_sqr == 30, v_crl == 30)
+eq_30_10 %>% filter(e_sqr == 30, v_crl == 10)
+mj_30_10 %>% filter(e_sqr == 30, v_crl == 10)
 

### 2019-11-07 ethnic_value_rum.Rmd
Add files via upload

@@
 
-raw_f <- rbind(eq_30,eq_10,mj_30,mj_10)
+test <- read.csv("test-beta-eth.csv",sep = ",",skip = 6)
+names(test)[names(test) == "X.step."] <- "step"
+names(test)[names(test) == "X.run.number."] <- "run"
+names(test)[names(test) == "beta.ie"] <- "beta_ie"
+names(test)[names(test) == "mean..count..turtles.on.neighbors..with..ethnicity....ethnicity..of.myself...of.turtles.with..count..turtles.on.neighbors.....1."] <- "eth_seg"
+
+raw_f <- rbind(eq_30,eq_10,mj_30,mj_10,eq_30_10,mj_30_10)
 
@@
 
-eq_30_10 %>% filter(e_sqr == 30, v_crl == 10)
-mj_30_10 %>% filter(e_sqr == 30, v_crl == 10)
+raw_f %>% filter(e_sqr == 30, v_crl == 10)
 

### 2019-11-08 ethnic_value_rum.Rmd
setup and ref

@@
 @paolillo2018 Diverse dimensions can define individuals and their similarity. Results from @paolillo2018
+@hedstrom2009oxford, chapter 11, 12
 
-* Update: justification for random utility models
+* Why an additional characteristic than ethnicity, literature in residential studies
+
+* Update: justification for random utility models, literature in ABM
 Better define the individual  decision process
 Link with empirical data
+@huang2014review
+@klabunde2016decision
+@bruch2019choice
 

### 2019-11-11 ethnic_value_rum.Rmd
updates check

@@
 author:  Rocco Paolillo, Andreas Flache, Jan Lorenz
-date:  "`r  as.Date(Sys.time(), '%d %B %Y')`"
+# date:  "`r  as.Date(Sys.time(), '%d %B %Y')`"
 # "`r  as.Date(Sys.time(), '%d %B %Y')`"
@@
 - \usepackage{graphicx}
-
 ---
@@
 # install.packages("tinytex", repos = "https://cloud.r-project.org" )
-
 library(tidyverse)
@@
 library(dplyr)
-
-eq_10 <- read.csv("50_g_10_bh.csv",sep = ",",skip = 6)
-names(eq_10) <- pull(read_csv("code_names.csv"))
-
-mj_10 <- read.csv("80_g_10_bh.csv",sep = ",",skip = 6)
-names(mj_10) <- pull(read_csv("code_names.csv"))
-
-eq_30 <- read.csv("50_g_30_hb.csv", sep = ",", skip = 6)
-names(eq_30) <- pull(read_csv("code_names.csv"))
-
-mj_30 <- read.csv("80_g_30_bh.csv",sep = ",",skip = 6)
-names(mj_30) <- pull(read_csv("code_names.csv"))
-
-mj_30_10 <- read.csv("80_g_30_10.csv",sep = ",", skip = 6)
-names(mj_30_10) <- pull(read_csv("code_names.csv"))
-
-eq_30_10 <- read.csv("50_g_30_10.csv",sep = ",", skip = 6)
-names(eq_30_10) <- pull(read_csv("code_names.csv"))
-
-test <- read.csv("test-beta-eth.csv",sep = ",",skip = 6)
-names(test)[names(test) == "X.step."] <- "step"
-names(test)[names(test) == "X.run.number."] <- "run"
-names(test)[names(test) == "beta.ie"] <- "beta_ie"
-names(test)[names(test) == "mean..count..turtles.on.neighbors..with..ethnicity....ethnicity..of.myself...of.turtles.with..count..turtles.on.neighbors.....1."] <- "eth_seg"
-
-raw_f <- rbind(eq_30,eq_10,mj_30,mj_10,eq_30_10,mj_30_10)
-
-df_e_sqr <- raw_f$e_sqr - raw_f$v_sqr
-df_v_crl <-  raw_f$v_crl - raw_f$e_crl
-
-dataset <- cbind(raw_f,df_e_sqr,df_v_crl)
-
-# check <- final[,c(9,10,27,11,12,28)]
-
-write.csv(dataset, file = "dataset.csv",row.names=FALSE) # later for reproduction
 
@@
 
-# Results
+To explore what levels of $\beta$ should not be excluded from the manipulations, I built a specific model with a unique beta for ethnic composition ($\beta_{ie}$ ) that does not change among agents.
+At each run I incremented degree of $\beta_{ie} \in[0,100]$ and let run for 1000 ticks with agents asynchronously relocating (not 1 agent for 1 tick, all to complete the procedure to restart).
+In each condition linear function was used: the preference peak of agents was $100\%$ for ethnically similar
 
-```{r gg }
+To explore what levels of $\beta$ should not be excluded from the manipulations, I made a specific model "rum_eth.nlogo" (in material), with a unique $\beta$ for all agents.
+I run the simulation for 1000 ticks (not 1 agent 1 tick):
+* linear function: peak preference for all agents at $100 \%$
+* density == $70 \%$
+* equal distribution of value orientation in each ethnic group
+* changing $beta_ie$ at each run $beta_ie \in[0,100]$
 
-raw_f %>% filter(e_sqr == 30, v_crl == 10)
+```{r one-beta, fig.cap="Comparison of ethnic segregation for one beta-ethnic, not interaction. Used one-beta.csv from simulation rum-eth.nlogo" , include=TRUE}
+
+a <- read.csv("one-beta.csv",sep = ",",skip = 6)
+names(a)[names(a) == "mean..count..turtles.on.neighbors..with..ethnicity....ethnicity..of.myself....count..turtles.on.neighbors....of.turtles.with..count..turtles.on.neighbors.....1." ] <- "eth_seg"
+
+a %>% filter(ticks == 0  | ticks == 500  | ticks == 100 | ticks == 1000)  %>%  filter(beta.ie >= 0 & beta.ie <= 15) %>% ggplot(aes(x = beta.ie, y = eth_seg)) + geom_bar(stat="identity") + facet_wrap(~ ticks, labeller = label_both)
 
@@
 
+# Results
+
 # References

### 2019-11-11 ethnic_value_rum.tex
updates check

\documentclass[]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={Preferences interact: what consequences for a Schelling scenario?},
            pdfauthor={Rocco Paolillo, Andreas Flache, Jan Lorenz},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{color}
\usepackage{fancyvrb}
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\usepackage{framed}
\definecolor{shadecolor}{RGB}{248,248,248}
\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{#1}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\BuiltInTok}[1]{#1}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{#1}}}
\newcommand{\ExtensionTok}[1]{#1}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\ImportTok}[1]{#1}
\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\NormalTok}[1]{#1}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\RegionMarkerTok}[1]{#1}
\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\usepackage{longtable,booktabs}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

%%% Use protect on footnotes to avoid problems with footnotes in titles
\let\rmarkdownfootnote\footnote%
\def\footnote{\protect\rmarkdownfootnote}

%%% Change title format to be more compact
\usepackage{titling}

% Create subtitle command for use in maketitle
\providecommand{\subtitle}[1]{
  \posttitle{
    \begin{center}\large#1\end{center}
    }
}

\setlength{\droptitle}{-2em}

  \title{Preferences interact: what consequences for a Schelling scenario?}
    \pretitle{\vspace{\droptitle}\centering\huge}
  \posttitle{\par}
    \author{Rocco Paolillo, Andreas Flache, Jan Lorenz}
    \preauthor{\centering\large\emph}
  \postauthor{\par}
    \date{}
    \predate{}\postdate{}

\usepackage{float}
\usepackage{multirow}
\usepackage{xcolor}
\usepackage{amsmath}
\usepackage{graphicx}

\begin{document}
\maketitle

\abstract{}

\hypertarget{introduction}{%
\section*{Introduction}\label{introduction}}
\addcontentsline{toc}{section}{Introduction}

\begin{itemize}
\item
  Schelling's model and previous work. Interaction of preferences.
  Schelling's model
  Literature update
  Paolillo and Lorenz (2018) Diverse dimensions can define individuals and their similarity. Results from Paolillo and Lorenz (2018)
  ({\textbf{???}}), chapter 11, 12
\item
  Why an additional characteristic than ethnicity, literature in residential studies
\item
  Update: justification for random utility models, literature in ABM
  Better define the individual decision process
  Link with empirical data
  ({\textbf{???}})
  Klabunde and Willekens (2016)
  Bruch and Swait (2019)
\item
  Research question
  How would the interaction between \(\beta\) for different dimensions affect Schelling's scenarios
\end{itemize}

\hypertarget{model-and-experiments}{%
\section{Model and Experiments}\label{model-and-experiments}}

The model\footnote{The model can be found here:\url{https://github.com/RoccoPaolillo/BIGSSS_ResearchDay.git}} was built in NetLogo 6.1.0 and extends work by Paolillo and Lorenz (2018).
Agents interact on a regular grid 51 times 51 with periodic boundary conditions (torus world). Each node of the grid can host 1 agent or being empty. Agents represents individuals who relocate and are defined by two static and overlapping variables: ethnicity and value orientation. Ethnicity is modeled through color tag. Agents with blue color represent the local population, agents with orange color represent the minority group. Value orientation through shape tag.

We define value orientation as the common membership of agents sharing same beliefs, preferences etc. potentially subject to change and independent of their attributed ethnicity. As such value orientation relates to value homophily compared to ethncity related to ascribed status homophily.
Each agent hold a preference for the ethnic composition and the value composition of each neighborhood.
Neighborhoods are defined as a Moore distance.
At each step, an agent randomly selected compares its current location to a number of alternative ones, calculates utility for each and decides which location they prefer.

\begin{itemize}
\tightlist
\item
  Calculation utility and probability function
\end{itemize}

To explore what levels of \(\beta\) should not be excluded from the manipulations, I built a specific model with a unique beta for ethnic composition (\(\beta_{ie}\) ) that does not change among agents. At each run I incremented degree of \(\beta_{ie} \in[0,100]\) and let run for 1000 ticks with agents asynchronously relocating (not 1 agent for 1 tick, all to complete the procedure to restart). In each condition linear function was used: the preference peak of agents was \(100\%\) for ethnically similar

To explore what levels of \(\beta\) should not be excluded from the manipulations, I made a specific model ``rum\_eth.nlogo'' (in material), with a unique \(\beta\) for all agents. I run the simulation for 1000 ticks (not 1 agent 1 tick):
* linear function: peak preference for all agents at \(100 \%\)
* density == \(70 \%\)
* equal distribution of value orientation in each ethnic group
* changing \(beta_ie\) at each run \(beta_ie \in[0,100]\)

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{a <-}\StringTok{ }\KeywordTok{read.csv}\NormalTok{(}\StringTok{"one-beta.csv"}\NormalTok{,}\DataTypeTok{sep =} \StringTok{","}\NormalTok{,}\DataTypeTok{skip =} \DecValTok{6}\NormalTok{)}
\KeywordTok{names}\NormalTok{(a)[}\KeywordTok{names}\NormalTok{(a) }\OperatorTok{==}\StringTok{ "mean..count..turtles.on.neighbors..with..ethnicity....ethnicity..of.myself....count..turtles.on.neighbors....of.turtles.with..count..turtles.on.neighbors.....1."}\NormalTok{ ] <-}\StringTok{ "eth_seg"}

\NormalTok{a }\OperatorTok{%>%}\StringTok{ }\KeywordTok{filter}\NormalTok{(ticks }\OperatorTok{==}\StringTok{ }\DecValTok{0}  \OperatorTok{|}\StringTok{ }\NormalTok{ticks }\OperatorTok{==}\StringTok{ }\DecValTok{500}  \OperatorTok{|}\StringTok{ }\NormalTok{ticks }\OperatorTok{==}\StringTok{ }\DecValTok{100} \OperatorTok{|}\StringTok{ }\NormalTok{ticks }\OperatorTok{==}\StringTok{ }\DecValTok{1000}\NormalTok{)  }\OperatorTok{%>%}\StringTok{  }\KeywordTok{filter}\NormalTok{(beta.ie }\OperatorTok{>=}\StringTok{ }\DecValTok{0} \OperatorTok{&}\StringTok{ }\NormalTok{beta.ie }\OperatorTok{<=}\StringTok{ }\DecValTok{15}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }\KeywordTok{ggplot}\NormalTok{(}\KeywordTok{aes}\NormalTok{(}\DataTypeTok{x =}\NormalTok{ beta.ie, }\DataTypeTok{y =}\NormalTok{ eth_seg)) }\OperatorTok{+}\StringTok{ }\KeywordTok{geom_bar}\NormalTok{(}\DataTypeTok{stat=}\StringTok{"identity"}\NormalTok{) }\OperatorTok{+}\StringTok{ }\KeywordTok{facet_wrap}\NormalTok{(}\OperatorTok{~}\StringTok{ }\NormalTok{ticks, }\DataTypeTok{labeller =}\NormalTok{ label_both)}
\end{Highlighting}
\end{Shaded}

\begin{figure}
\centering
\includegraphics{ethnic_value_rum_files/figure-latex/one-beta-1.pdf}
\caption{\label{fig:one-beta}Comparison of ethnic segregation for one beta-ethnic, not interaction. Used one-beta.csv from simulation rum-eth.nlogo}
\end{figure}

\hypertarget{results}{%
\section{Results}\label{results}}

\hypertarget{references}{%
\section*{References}\label{references}}
\addcontentsline{toc}{section}{References}

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-bruch2019choice}{}%
Bruch, Elizabeth, and Joffre Swait. 2019. ``Choice Set Formation in Residential Mobility and Its Implications for Segregation Dynamics.'' \emph{Demography}, 1--28.

\leavevmode\hypertarget{ref-klabunde2016decision}{}%
Klabunde, Anna, and Frans Willekens. 2016. ``Decision-Making in Agent-Based Models of Migration: State of the Art and Challenges.'' \emph{European Journal of Population} 32 (1): 73--97.

\leavevmode\hypertarget{ref-paolillo2018}{}%
Paolillo, Rocco, and Jan Lorenz. 2018. ``How Different Homophily Preferences Mitigate and Spur Ethnic and Value Segregation: Schelling's Model Extended.'' \emph{Advances in Complex Systems} 21 (06n07): 1850026.

\end{document}

### 2019-11-12 test.Rmd
Add files via upload

---
title: "Untitled"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(tidyverse)

a <- read.csv("one-beta.csv",sep = ",",skip = 6)
names(a)[names(a) == "mean..count..turtles.on.neighbors..with..ethnicity....ethnicity..of.myself....count..turtles.on.neighbors....of.turtles.with..count..turtles.on.neighbors.....1." ] <- "eth_seg"

a %>% filter(ticks == 0  | ticks == 500  | ticks == 100 | ticks == 1000)  %>%  filter(beta.ie >= 0 & beta.ie <= 15) %>% ggplot(aes(x = beta.ie, y = eth_seg)) + geom_bar(stat="identity") + facet_wrap(~ ticks, labeller = label_both)

b  <-  read.csv("diff_10.csv",sep = ",",skip = 6)
names(b)[names(b) == "mean..count..turtles.on.neighbors..with..ethnicity....ethnicity..of.myself....count..turtles.on.neighbors...of.turtles.with..count..turtles.on.neighbors.....1." ] <- "eth_seg"
names(b)[names(b) == "mean..count..turtles.on.neighbors..with..shape....shape..of.myself....count..turtles.on.neighbors...of.turtles.with..count..turtles.on.neighbors.....1."] <- "val_seg"

c  <- b %>% filter(beta.ie >= beta.iv )

diff_ev <- c$beta.ie - c$beta.iv
c  <- cbind(c,diff_ev)

c %>%  filter(ticks == 1000)  %>% ggplot(aes(x = beta.ie, y = eth_seg)) + geom_bar(stat = "identity") + facet_wrap(~  beta.iv, labeller = label_both)

```

## R Markdown

This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

### 2019-12-02 ethnic_value_rum.Rmd
Add files via upload

@@
 
+```{r att_income , include=TRUE}
+
+f_att <- function(i,b){   # utility function as single-peaked
+ A <- 1 / (1 + exp(-b(i)))
+}
+
+  b <- 0.5
+
+a_0 <- f_cst(a,0)
+a_1 <- f_cst(a,0.1)
+a_2 <- f_cst(a,0.2)
+a_3 <- f_cst(a,0.3)
+a_4 <- f_cst(a,0.4)
+a_5 <- f_cst(a,0.5)
+a_6 <- f_cst(a,0.6)
+a_7 <- f_cst(a,0.7)
+a_8 <- f_cst(a,0.8)
+a_9 <- f_cst(a,0.9)
+a_10 <- f_cst(a,1)
+
+Prob_A <- c(a_0,a_1,a_2,a_3,a_4,a_5,a_6,a_7,a_8,a_9,a_10)
+income <- seq(0,i, by = 0.1)
+
+plot(price,na.omit(utility),ylab = "utility_ec",xlab="price", main = paste0("income =",i))
+
+```
+
+```{r income_price , include=TRUE}
+
+# tentative of utility economic, given by the difference (income - price), so to represent how convenient a location is. 
+# ideally identity equation: if income < price, probability would be 0. If beta is negative, the probability could still be computed, which is nonsense
+
+f_cst <- function(i,p){   # utility function as single-peaked
+ if (i < p){
+    U <- NA}else{
+  U <- ((i - p) / i)}
+}
+
+  i <- 0.5
+
+i_0 <- f_cst(i,0)
+i_1 <- f_cst(i,0.1)
+i_2 <- f_cst(i,0.2)
+i_3 <- f_cst(i,0.3)
+i_4 <- f_cst(i,0.4)
+i_5 <- f_cst(i,0.5)
+i_6 <- f_cst(i,0.6)
+i_7 <- f_cst(i,0.7)
+i_8 <- f_cst(i,0.8)
+i_9 <- f_cst(i,0.9)
+i_10 <- f_cst(i,1)
+
+utility <- c(i_0,i_1,i_2,i_3,i_4,i_5,i_6,i_7,i_8,i_9,i_10)
+price <- seq(0,i, by = 0.1)
+
+plot(price,na.omit(utility),ylab = "utility_ec",xlab="price", main = paste0("income =",i))
+
+```
+
 # Results

### 2020-01-10 ethnic_value_rum.Rmd
update GR stay

--- 2019-11-11 ethnic_value_rum.Rmd
@@
 title: "Preferences interact: what consequences for a Schelling scenario?"
-# subtitle: "Target: BIGSSS Research Day"
-author:  Rocco Paolillo, Andreas Flache, Jan Lorenz
+subtitle: "Title to define"
+author:  Rocco Paolillo, Andreas Flache
 # date:  "`r  as.Date(Sys.time(), '%d %B %Y')`"
@@
 library(dplyr)
+
+# Beta distribution parameters mean and standard deviation
+# https://stats.stackexchange.com/questions/12232/calculating-the-parameters-of-a-beta-distribution-using-the-mean-and-variance
 
@@
 Schelling's model
-Literature update
+Literature update @verweij2006clumsy
 @paolillo2018 Diverse dimensions can define individuals and their similarity. Results from @paolillo2018
@@
 
-* Why an additional characteristic than ethnicity, literature in residential studies
+* Why an additional characteristic than ethnicity, literature in residential studies. How it correlates with income/social mobility
+@esser2010, transmission of capital
+south2016neighborhood on life course economic capital transmission
 
@@
 Link with empirical data
-@huang2014review
 @klabunde2016decision
@@
 
+* Costs
+
 * Research question
-How would the interaction between $\beta$ for different dimensions affect Schelling's scenarios
+How would the interaction between $\beta$ for different dimensions affect Schelling's scenarios?
+How the effect would change when income is included? And correlation between income and socio-demographic characteristics (value) included?
 
@@
 
-To explore what levels of $\beta$ should not be excluded from the manipulations, I built a specific model with a unique beta for ethnic composition ($\beta_{ie}$ ) that does not change among agents.
-At each run I incremented degree of $\beta_{ie} \in[0,100]$ and let run for 1000 ticks with agents asynchronously relocating (not 1 agent for 1 tick, all to complete the procedure to restart).
-In each condition linear function was used: the preference peak of agents was $100\%$ for ethnically similar
-
-To explore what levels of $\beta$ should not be excluded from the manipulations, I made a specific model "rum_eth.nlogo" (in material), with a unique $\beta$ for all agents.
-I run the simulation for 1000 ticks (not 1 agent 1 tick):
-* linear function: peak preference for all agents at $100 \%$
-* density == $70 \%$
-* equal distribution of value orientation in each ethnic group
+To explore what levels of $\beta$ should not be excluded, I made a specific model "beta-et.nlogo" (in "material/beta-diff"), with an uniform $\beta_{ie}$ for ethnic composition.
+The simulation was simplified with one slider $\beta_{ie}$ for all agents  (same as 4 subgroup with equal $\beta$), to simplify code and lift computational power.
+I run the simulation for 1000 ticks (not 1 tick 1 agent, as in NetLogo asynchronous behavior: all agents run the procedure and then repeat):
+* monotonic linear function: desired concentration ethnically similar $100 \%$ \par
+* density == $70 \%$ \par
+* $50 \%$ distribution of value orientation in each ethnic group \par
 * changing $beta_ie$ at each run $beta_ie \in[0,100]$
 
-```{r one-beta, fig.cap="Comparison of ethnic segregation for one beta-ethnic, not interaction. Used one-beta.csv from simulation rum-eth.nlogo" , include=TRUE}
+Collected ethnic segregation, here reported for different ticks (Fig: \ref{fig:onebeta}) \par
 
-a <- read.csv("one-beta.csv",sep = ",",skip = 6)
+```{r onebeta, fig.cap="Comparison of ethnic segregation for one beta-ethnic, not interaction. Used one-beta.csv from simulation rum-eth.nlogo" , include=TRUE, echo=FALSE}
+
+# setwd("C:/Users/rocpa/OneDrive/Desktop/AF-02-12/ethnic-value_multinomial/material/beta-diff")
+
+a <- read.csv("beta-et.csv",sep = ",",skip = 6)
 names(a)[names(a) == "mean..count..turtles.on.neighbors..with..ethnicity....ethnicity..of.myself....count..turtles.on.neighbors....of.turtles.with..count..turtles.on.neighbors.....1." ] <- "eth_seg"
 
-a %>% filter(ticks == 0  | ticks == 500  | ticks == 100 | ticks == 1000)  %>%  filter(beta.ie >= 0 & beta.ie <= 15) %>% ggplot(aes(x = beta.ie, y = eth_seg)) + geom_bar(stat="identity") + facet_wrap(~ ticks, labeller = label_both)
+a %>% filter(ticks == 0  | ticks == 500  | ticks == 100 | ticks == 1000)  %>%  filter(beta.ie >= 0 & beta.ie <= 30) %>% ggplot(aes(x = beta.ie, y = eth_seg)) + geom_bar(stat="identity") + facet_wrap(~ ticks, labeller = label_both)
+
+```
+
+To test if the effect of  $\beta_{ie}$ for ethnic composition would be different if interacting with $\beta_{iv}$, I run another
+
+what levels of $\beta$ should not be excluded, I made a specific model "beta-et-vl.nlogo" (in "material/beta-diff"), with uniform $\beta_{ie}$ for ethnic composition and $\beta_{iv}$ for value composition.
+The simulation was simplified with a slider $\beta_{ie}$ and a slider $\beta_{iv}$ for all agents (same as 4 subgroup with equal $\beta$), to simplify code and lift computational power.
+I run the simulation for 1000 ticks (not 1 agent 1 tick):
+* monotonic linear function: desired concentration ethnically similar $100 \%$, desired concentration value simular $100 \%$ \par
+* density == $70 \%$ \par
+* $50 \%$ distribution of value orientation in each ethnic group \par
+* changing $beta_ie$ at each run $\beta_{ie} \in[0,20]$ and $\beta_{iv} \in[0,20]$, with condition of $\beta_{ie} \geq \beta_{iv}$
+
+Collected ethnic segregation, here reported at ticks = 1000, and faceted $\beta_{ie}$ x $\beta_{iv}$ (Fig: \ref{fig:twobeta}).
+
+```{r twobeta, fig.cap="Comparison of ethnic segregation for interaction beta-ethnic and beta-value.
+Used diff_10.csv from simulation rum_eth-val.nlogo.
+Histogram don't appear for conditions of b_iv > b_ie, which are excluded from BehaviorSpace.", include=TRUE, echo=FALSE}
+
+# setwd("C:/Users/rocpa/OneDrive/Desktop/AF-02-12/ethnic-value_multinomial/material/beta-diff")
+
+b  <-  read.csv("beta-et-vl.csv",sep = ",",skip = 6)
+names(b)[names(b) == "mean..count..turtles.on.neighbors..with..ethnicity....ethnicity..of.myself....count..turtles.on.neighbors...of.turtles.with..count..turtles.on.neighbors.....1." ] <- "eth_seg"
+names(b)[names(b) == "mean..count..turtles.on.neighbors..with..shape....shape..of.myself....count..turtles.on.neighbors...of.turtles.with..count..turtles.on.neighbors.....1."] <- "val_seg"
+
+c  <- b %>% filter(beta.ie >= beta.iv )
+
+diff_ev <- c$beta.ie - c$beta.iv
+c  <- cbind(c,diff_ev)
+
+c %>%  filter(ticks == 1000)  %>% ggplot(aes(x = beta.ie, y = eth_seg)) + geom_bar(stat = "identity") + facet_wrap(~  beta.iv, labeller = label_both)
+
+```
+
+# APPENDIX, Functions used in the simulations
+
+##  Derivate probability being tolerant/not tolerant from income
+
+Already in the model, income follows beta distribution.
+Tolerance is one possible implementation, the main point is a cross-ethnic category that might depend on the income distribution (Fig: \ref{fig:attincome})
+
+$$P = \frac{1}{(1 + \exp(-\lambda\times(i - 0.5)))}$$
+
+where: \par
+$\textit{i}$: income \par
+$i - 0.5$: considering income follows beta distribution $i\in{[0,1]}$. The higher income is than 0.5, the higher the probability the agent is tolerant \par
+$\lambda$: parameter of randomness on the derivation tolerance from income \par
+
+```{r attincome,fig.pos='H',out.width="80%",fig.align='center',fig.cap="Probability of binary cross-category (tolerant/not tolerant) from the distribution of income",include=TRUE, echo=FALSE}
+
+# How the cross-category, e.g. tolerance can depend on wealth/income distribution, which can be used also for housing purchasing
+# Seems feasible to me to use beta distribution for wealth at this point. To be used: logistic function, which
+
+f_att <- function(i,l){   # utility function as single-peaked
+ A <- 1 / (1 + exp((-l)*(i - 0.5)))
+}
+
+  l <- 6
+
+# a_1n <- f_att(-1,l)
+# a_2n <- f_att(-0.9,l)
+# a_3n <- f_att(-0.8,l)
+# a_4n <- f_att(-0.7,l)
+# a_5n <- f_att(-0.6,l)
+# a_6n <- f_att(-0.5,l)
+# a_7n <- f_att(-0.4,l)
+# a_8n <- f_att(-0.3,l)
+# a_9n <- f_att(-0.2,l)
+# a_10n <- f_att(-0.1,l)
+
+a_0 <- f_att(0,l)
+a_1 <- f_att(0.1,l)
+a_2 <- f_att(0.2,l)
+a_3 <- f_att(0.3,l)
+a_4 <- f_att(0.4,l)
+a_5 <- f_att(0.5,l)
+a_6 <- f_att(0.6,l)
+a_7 <- f_att(0.7,l)
+a_8 <- f_att(0.8,l)
+a_9 <- f_att(0.9,l)
+a_10 <- f_att(1,l)
+
+Prob_A <- c(a_0,a_1,a_2,a_3,a_4,a_5,a_6,a_7,a_8,a_9,a_10)
+income <- seq(0,1, by = 0.1)
+
+plot(income,Prob_A,ylab = "P_attA",xlab="income")
+
+```
+
+##  Economic Utility related to price
+
+Utility for the agent to select the most advantageous option  (Fig: \ref{fig:economic}).
+I figured it out so that income will have an indirect effect on costs of relocation.
+Role within the agent to rank the options (preferring the cheapest one), but also between agents: given the same price for a location, utility will be higher for agents who have higher income, since they can afford higher costs.
+
+$$U_{ec} = \frac{i - p}{i}$$
+
+where: \par
+$\textit{i}$: income \par
+$p$: price of potential relocation \par
+
+```{r economic,fig.pos='H',out.width="80%",fig.align='center',fig.cap="Cost formation",include=TRUE, echo=FALSE}
+
+# tentative of utility economic, given by the difference (income - price), so to represent how convenient a location is. 
+# ideally identity equation: if income < price, probability would be 0. If beta is negative, the probability could still be computed, which is nonsense
+
+f_cst <- function(i,p){   # utility function as single-peaked
+ if (i < p){
+    U <- NA}else{
+  U <- ((i - p) / i)}
+}
+
+  i <- 0.7
+
+i_0 <- f_cst(i,0)
+i_1 <- f_cst(i,0.1)
+i_2 <- f_cst(i,0.2)
+i_3 <- f_cst(i,0.3)
+i_4 <- f_cst(i,0.4)
+i_5 <- f_cst(i,0.5)
+i_6 <- f_cst(i,0.6)
+i_7 <- f_cst(i,0.7)
+i_8 <- f_cst(i,0.8)
+i_9 <- f_cst(i,0.9)
+i_10 <- f_cst(i,1)
+
+utility <- c(i_0,i_1,i_2,i_3,i_4,i_5,i_6,i_7,i_8,i_9,i_10)
+price <- seq(0,1, by = 0.1)
+
+plot(price,utility,ylab = "Economic Utility",xlab="price", main = paste0("income =",i))
+
+```
+
+```{r economic0,fig.pos='H',out.width="80%",fig.align='center',fig.cap="Cost formation",include=TRUE, echo=FALSE}
+
+# tentative of utility economic, given by the difference (income - price), so to represent how convenient a location is. 
+# ideally identity equation: if income < price, probability would be 0. If beta is negative, the probability could still be computed, which is nonsense
+
+f_cst <- function(i,p){   # utility function as single-peaked
+ if (i < p){
+    U <- NA}else{
+  U <- ((i - p) / i)}
+}
+
+inc <- c(rep(0.80,11), rep(0.50,11))
+price <- rep(seq(0,1, by = 0.1),2)
+
+df <- cbind(inc,price)
+
+df_fin <- data.frame(cbind(df,ut_ec = mapply(function(x,y)  if (x < y){NA}else{round(((x - y) / x),2)}, inc, price) ))
+
+ggplot(df_fin,aes(x = price, y = ut_ec, color = as.factor(inc))) + geom_point() + scale_color_manual(values=c("red", "blue"), guide = guide_legend(title="Income")) + theme_bw() +  labs(y = "Economic Utility")# + scale_color_manual(values=c("red", "blue"))
+
+# i_07 <- f_cst(i,0)
+# i_17 <- f_cst(i,0.1)
+# i_27 <- f_cst(i,0.2)
+# i_37 <- f_cst(i,0.3)
+# i_47 <- f_cst(i,0.4)
+# i_57 <- f_cst(i,0.5)
+# i_67 <- f_cst(i,0.6)
+# i_77 <- f_cst(i,0.7)
+# i_87 <- f_cst(i,0.8)
+# i_97 <- f_cst(i,0.9)
+# i_107 <- f_cst(i,1)
+# 
+# i_05 <- f_cst(i,0)
+# i_15 <- f_cst(i,0.1)
+# i_25 <- f_cst(i,0.2)
+# i_35 <- f_cst(i,0.3)
+# i_45 <- f_cst(i,0.4)
+# i_55 <- f_cst(i,0.5)
+# i_65 <- f_cst(i,0.6)
+# i_75 <- f_cst(i,0.7)
+# i_85 <- f_cst(i,0.8)
+# i_95 <- f_cst(i,0.9)
+# i_105 <- f_cst(i,1)
+# 
+# utility <- c(i_0,i_1,i_2,i_3,i_4,i_5,i_6,i_7,i_8,i_9,i_10)
+# 
+# plot(price,utility,ylab = "Economic Utility",xlab="price", main = paste0("income =",i))
+
+```
+
+PRICE: num. neighbors/8 * mean(income) of neighbors
+
+```{r att_income-linear , include=FALSE, echo=FALSE}
+
+# How the cross-category, e.g. tolerance can depend on wealth/income distribution, which can be used also for housing purchasing
+# Seems feasible to me to use beta distribution for wealth at this point. To be used: logistic function, which
+
+f_att <- function(i){   # utility function as single-peaked
+A <- (((i*10)^i) / 10)
+}
+
+# a_1n <- f_att(-1,l)
+# a_2n <- f_att(-0.9,l)
+# a_3n <- f_att(-0.8,l)
+# a_4n <- f_att(-0.7,l)
+# a_5n <- f_att(-0.6,l)
+# a_6n <- f_att(-0.5,l)
+# a_7n <- f_att(-0.4,l)
+# a_8n <- f_att(-0.3,l)
+# a_9n <- f_att(-0.2,l)
+# a_10n <- f_att(-0.1,l)
+
+a_0 <- f_att(0)
+a_05 <- f_att(0.05)
+a_1 <- f_att(0.1)
+a_15<- f_att(0.15)
+a_2 <- f_att(0.2)
+a_25<- f_att(0.25)
+a_3 <- f_att(0.3)
+a_35<- f_att(0.35)
+a_4 <- f_att(0.4)
+a_45<- f_att(0.45)
+a_5 <- f_att(0.5)
+a_55<- f_att(0.55)
+a_6 <- f_att(0.6)
+a_65<- f_att(0.65)
+a_7 <- f_att(0.7)
+a_75<- f_att(0.75)
+a_8 <- f_att(0.8)
+a_85<- f_att(0.85)
+a_9 <- f_att(0.9)
+a_95<- f_att(0.95)
+a_10 <- f_att(1)
+
+Prob_A <- c(a_0,a_05,a_1,a_15,a_2,a_25,a_3,a_35,a_4,a_45,a_5,a_55,a_6,a_65,a_7,a_75,a_8,a_85,a_9,a_95,a_10)
+income <- seq(0,1, by = 0.05)
+
+plot(income,Prob_A,ylab = "P_attA",xlab="income")
 

### 2020-01-14 ethnic_value_rum.Rmd
literature Schelling-focus

--- 2019-11-11 ethnic_value_rum.Rmd
@@
 language: en-GB
-bibliography: "references.bib"
+bibliography: "material/references.bib"
 always_allow_html: yes
@@
 
-* Schelling's model and previous work. Interaction of preferences.
-Schelling's model
-Literature update
-@paolillo2018 Diverse dimensions can define individuals and their similarity. Results from @paolillo2018
-@hedstrom2009oxford, chapter 11, 12
+Residential segregation can be defined as the unequal and non random distribution of people  belonging to different groups within the spatial units of a city [@bruch2009segregation;@clark2008understanding].
+The interest of the social sciences on the topic is due the consequences it can have on the chance of interaction and integration between groups [@bolt2010linking], with exclusion of minorities in deprived neighborhoods and perpetuation of inequalities through generations [@van2012understanding].
+A key research question in literature is on the dynamics of emergence of residential segregation.
+Two hystorical hypothesis are the spatial assimilation theory and the place stratification theory.
+According to the former, spatial distance reflects the social distance between groups, and can change as effect of social moblity (@coulter2019ethnic), while the latter focuses on the strategies of gatekeepers, e.g.
+sellers, to prevent undesired newcomers to neighborhood (@horr2018ethnic).
+Both have in common the assumption that residential  segregation is the intended result of individual behavior.
+A third perspective can be that of social complexity and Schelling's agent-based model of residential segregation, which addresses residential segregation as a stable property of the aggregated behavior of people who seek to satisfy even mild homophily preferences within spatial constraints [@schelling1969;@schelling1971;@schelling1978].
+The paper here presented follows this stream of literature and aims at contributing to Schelling's type dynamics.
+\par
 
-* Why an additional characteristic than ethnicity, literature in residential studies
+Schelling focused on the black and white population in the U.S.
+cities in the '60s and proposed an alternative to segregation as due to overt discrimination.
+His model is built on homophily preferences of movers and threshold function of their relocation choice [@schelling1969;@schelling1971;@schelling1978].
+Homophily preferences refer to the tendency of people to aggregate with similar ones, with not derogation of the outgroup, while threshold function means that people will move out of a neighborhood to a random relocation only under the condition that the concentration of similar ones falls below a desired percentage.
+Residential segregation emerges from the interaction of people following such behavior within spatial constraints due first to density of population, even in case of mild preferences.
+Within the literature stemming from Schelling, @paolillo2018 focused on his concept of similarity as based on a "twofold, exhaustive and recognizable distinction" [@schelling1969, p.488].
+Although not in the intention of Schelling, literature has most interpreted this as a binary definition of ethnicity as fundamental to group membership and segregation.
+As basic consideration, @paolillo2018 argued that in modern and diverse societies ethnicity might not be the unique driver to membership and exclusion [@alba2014twilight;@crul2016super] and that the way people navigate diversity in society might be more important than ethnicity per se.
+The authors introduced an additional definition of similarity as value-orientation independent of ethnic membership, and focused on the value of tolerance towards diversity [@dragolov2016social].
+Theoretically, they backed this idea with the ethnic boundary making perspective, which focuses on the mechanisms that generate and consolidate boundaries of in-group/out-group definition over the given ethnic membership [@wimmer2013;@wimmer09;@esser2010].
+They divided the population of agents between intolerant ethnicity-oriented, which considered as similar those agents of the same ethnicity regardless of their value orientation, and tolerant value-oriented, which considered as similar those agents of the same value orientation despite their ethnicity.
+They kept the original threshold behavior for both types of agents.
+Additionally, they investigated the consequences of relative group sizes, as critical in the social sciences [@esser2010; @blau1977macrosociological] and less studied in Schelling's literature [@schelling1971;@troitzsch2017axiomatic].
+As overall results, the emergence of value segregation by tolerant agents reduced ethhnic segregation compared to the original Schelling's model.
+Yet, the key result was the spillover effect between the two types of segregation: ethnically mixed neighborhoods formed by tolerant agents became eventually attractive to intolerant agents, due to higher chance to find members of their ethnic group.
+The tendency was higher for intolerants in the minority condition.
+The author investigated under what rate of desired concentration for the two groups all agents were happy with their relocation, in particular until when value-oriented agents would have accepted intolerant agents before leaving, so that originally ethnically mixed neighborhoods turned ethnically homogeneous.
+In this paper, we want to extend the modifications made by @paolillo2018 with introduction of value oriented agents to the recent progress in Schelling's literature for what concerns the relocation choice of agents, in particular adopting a different function than threshold and the framework of random utility models.\par
+Random utility models are not new in empirical studies of residential segregation [@frankhauser2016deciding].
+Stemming from utility maximization paradigm, this class of models assumes that people aim at taking the option that best satisfies their needs, summarized within an utility function, but still, they incorporate randomness as a component of the choice, meaning not always the maximization of utility is granted [@hess2018revisiting].
+Assumption of these models is that utility is defined by diverse dimensions and each is quantified by a parameter $\beta$ unknown in principle, and that can be only estimated by empirical observation of the options people selected from [@manski1977structure].
+Randomness in utility has several reasons, e.g.
+people don't know all available options, utility might differ among people in a population, and people can fail in picking up the desired option [@hess2018revisiting].
+Within these models, the conditional logit model by @mcfadden1973conditional ($P_{i \in k} = \frac{expU{i}}{\sum U^{k}}$) had particular success into residential studies, since it allows to combine socio-demographic characteristics of the selector with the characteristics of the options to select from.
+In recent years, the paradigm of random utility model and McFadden's conditional logit have been implemented into Schelling's  type dynamics [@zhang2004;@xie2012modeling;@bruch2014population].
+The interest of agent-based modelers was to model a more appropriate decision rule under relocation choice, linking with literature in empirical studies and comparison with empirical data through calibration of $\beta$ and utility function [@bruch2012methodological].
+In particular @bruch2006 paper implemented alternative to the Schelling's threshold function, and focused on the linear continuuous function, which means agents have the maximum of utility at $100 \%$ similars' concentration (monotonic linearity).
+Revising results after detenction of a coding error by @van2009, @bruch2009preferences show how the linear function compared to the threshold function slows down the convergence towards segregation of the Schelling's model that remains a constant outcome, and that agents become more sensitive to change in the neighborhood composition with more fined scenarios that a threshold model would show.
+Both for the insights into segregation dynamics and for the threoretical fit of linear function to utility paradigm, this approach appears noteworthy.
+Despite the inclusion of contingencies to relocation choice as price formation, most of these studies remains on the original Schelling's dimension of ethnic homophily as definition of individual preferences.
+We want to extend this aspect and implement the linear function used by @bruch2009preferences and random utility model within the extension of both ethnic and value preferences of agents [@paolillo2018].\par
+In sum, the aim of this paper is to contribute to the literature on Schelling's dynamics by including both ethnic and value preferences underlying relocation choice of agents and emerging segregation, investigating their mutual interdependence.
+To this goal, we extend the work by @paolillo2018 by aligning it to recent trends in Schelling's implementation within random utility models and substituting the original threshold function with linear utility function.
+We include a different parameter $\beta$ for ethnic homophily and value homophily for each type of agent (\ref{fig:model}), which is a more realistic assumption.
+Following the conditional logit model, such implementation can disentangle the case of people's preferences varying across ethnic groups as well as within ethnic groups due to the value orientation of agents.
+Similarly, the difference in degree of value homophily (or ethnic homophily) can vary for agents identified as tolerant but belonging to different ethnic groups.
+Additionally, we will explore these sets within the condition of relative group size for ethnicity and value orientation.
+The main contribution of the paper is to link such parameter for subgroups of population  and distribution of different types of agents to both ethnic and value segregation compared to previous studies.
+Furthermore, the paper aims at disentangle the conditions under which value segregation might mitigate, or spur ethnic segregation, and vice versa for the interdependence of ethnic segregation over value segregation.
 
-* Update: justification for random utility models, literature in ABM
-Better define the individual  decision process
-Link with empirical data
-@huang2014review
-@klabunde2016decision
-@bruch2019choice
-
-* Research question
-How would the interaction between $\beta$ for different dimensions affect Schelling's scenarios
+```{r model, fig.pos ='h!',out.width='50%',out.height='90%',fig.show='hold',fig.align='center', fig.cap= "Draft of agents attribution and emerging segregations, to revise.",  echo = FALSE, include=TRUE}
+knitr::include_graphics("C:/Users/rocpa/OneDrive/Desktop/AF/ethnic-value_multinomial/material/model_pr.jpg")
+```
 
@@
 
-To explore what levels of $\beta$ should not be excluded from the manipulations, I built a specific model with a unique beta for ethnic composition ($\beta_{ie}$ ) that does not change among agents.
-At each run I incremented degree of $\beta_{ie} \in[0,100]$ and let run for 1000 ticks with agents asynchronously relocating (not 1 agent for 1 tick, all to complete the procedure to restart).
-In each condition linear function was used: the preference peak of agents was $100\%$ for ethnically similar
-
-To explore what levels of $\beta$ should not be excluded from the manipulations, I made a specific model "rum_eth.nlogo" (in material), with a unique $\beta$ for all agents.
-I run the simulation for 1000 ticks (not 1 agent 1 tick):
-* linear function: peak preference for all agents at $100 \%$
-* density == $70 \%$
-* equal distribution of value orientation in each ethnic group
+To explore what levels of $\beta$ should not be excluded, I made a specific model "beta-et.nlogo" (in "material/beta-diff"), with an uniform $\beta_{ie}$ for ethnic composition.
+The simulation was simplified with one slider $\beta_{ie}$ for all agents  (same as 4 subgroup with equal $\beta$), to simplify code and lift computational power.
+I run the simulation for 1000 ticks (not 1 tick 1 agent, as in NetLogo asynchronous behavior: all agents run the procedure and then repeat):
+* monotonic linear function: desired concentration ethnically similar $100 \%$ \par
+* density == $70 \%$ \par
+* $50 \%$ distribution of value orientation in each ethnic group \par
 * changing $beta_ie$ at each run $beta_ie \in[0,100]$
 
-```{r one-beta, fig.cap="Comparison of ethnic segregation for one beta-ethnic, not interaction. Used one-beta.csv from simulation rum-eth.nlogo" , include=TRUE}
+Collected ethnic segregation, here reported for different ticks (Fig: \ref{fig:onebeta}) \par
 
-a <- read.csv("one-beta.csv",sep = ",",skip = 6)
+```{r onebeta, fig.cap="Comparison of ethnic segregation for one beta-ethnic, not interaction. Used one-beta.csv from simulation rum-eth.nlogo" , include=TRUE, echo=FALSE}
+
+setwd("C:/Users/rocpa/OneDrive/Desktop/AF/ethnic-value_multinomial/material/beta-diff/")
+
+a <- read.csv("beta-et.csv",sep = ",",skip = 6)
 names(a)[names(a) == "mean..count..turtles.on.neighbors..with..ethnicity....ethnicity..of.myself....count..turtles.on.neighbors....of.turtles.with..count..turtles.on.neighbors.....1." ] <- "eth_seg"
 
-a %>% filter(ticks == 0  | ticks == 500  | ticks == 100 | ticks == 1000)  %>%  filter(beta.ie >= 0 & beta.ie <= 15) %>% ggplot(aes(x = beta.ie, y = eth_seg)) + geom_bar(stat="identity") + facet_wrap(~ ticks, labeller = label_both)
+a %>% filter(ticks == 0  | ticks == 500  | ticks == 100 | ticks == 1000)  %>%  filter(beta.ie >= 0 & beta.ie <= 30) %>% ggplot(aes(x = beta.ie, y = eth_seg)) + geom_bar(stat="identity") + facet_wrap(~ ticks, labeller = label_both)
+
+```
+
+To test if the effect of  $\beta_{ie}$ for ethnic composition would be different if interacting with $\beta_{iv}$, I run another
+
+what levels of $\beta$ should not be excluded, I made a specific model "beta-et-vl.nlogo" (in "material/beta-diff"), with uniform $\beta_{ie}$ for ethnic composition and $\beta_{iv}$ for value composition.
+The simulation was simplified with a slider $\beta_{ie}$ and a slider $\beta_{iv}$ for all agents (same as 4 subgroup with equal $\beta$), to simplify code and lift computational power.
+I run the simulation for 1000 ticks (not 1 agent 1 tick):
+* monotonic linear function: desired concentration ethnically similar $100 \%$, desired concentration value simular $100 \%$ \par
+* density == $70 \%$ \par
+* $50 \%$ distribution of value orientation in each ethnic group \par
+* changing $beta_ie$ at each run $\beta_{ie} \in[0,20]$ and $\beta_{iv} \in[0,20]$, with condition of $\beta_{ie} \geq \beta_{iv}$
+
+Collected ethnic segregation, here reported at ticks = 1000, and faceted $\beta_{ie}$ x $\beta_{iv}$ (Fig: \ref{fig:twobeta}).
+
+```{r twobeta, fig.cap="Comparison of ethnic segregation for interaction beta-ethnic and beta-value.
+Used diff_10.csv from simulation rum_eth-val.nlogo.
+Histogram don't appear for conditions of b_iv > b_ie, which are excluded from BehaviorSpace.", include=TRUE, echo=FALSE}
+
+setwd("C:/Users/rocpa/OneDrive/Desktop/AF/ethnic-value_multinomial/material/beta-diff/")
+
+b  <-  read.csv("beta-et-vl.csv",sep = ",",skip = 6)
+names(b)[names(b) == "mean..count..turtles.on.neighbors..with..ethnicity....ethnicity..of.myself....count..turtles.on.neighbors...of.turtles.with..count..turtles.on.neighbors.....1." ] <- "eth_seg"
+names(b)[names(b) == "mean..count..turtles.on.neighbors..with..shape....shape..of.myself....count..turtles.on.neighbors...of.turtles.with..count..turtles.on.neighbors.....1."] <- "val_seg"
+
+c  <- b %>% filter(beta.ie >= beta.iv )
+
+diff_ev <- c$beta.ie - c$beta.iv
+c  <- cbind(c,diff_ev)
+
+c %>%  filter(ticks == 1000)  %>% ggplot(aes(x = beta.ie, y = eth_seg)) + geom_bar(stat = "identity") + facet_wrap(~  beta.iv, labeller = label_both)
 

### 2020-01-23 ethnic_value_rum.Rmd
Update ethnic_value_rum.Rmd
After meeting AF Groningen 13

--- 2019-12-02 ethnic_value_rum.Rmd
@@
     fig_caption: yes
-title: "Preferences interact: what consequences for a Schelling scenario?"
-# subtitle: "Target: BIGSSS Research Day"
-author:  Rocco Paolillo, Andreas Flache, Jan Lorenz
+title: "Tolerant  to ethnic diversity, intolerant to intolerance"
+subtitle: "Title to define"
+author:  Rocco Paolillo, Andreas Flache
 # date:  "`r  as.Date(Sys.time(), '%d %B %Y')`"
@@
 
+# INTRO FOCUSED ON SCHELLING, MUST BE ON HYBRID SEGREGATION
+
 # Introduction {-}
 
-* Schelling's model and previous work. Interaction of preferences.
-Schelling's model
-Literature update
-@paolillo2018 Diverse dimensions can define individuals and their similarity. Results from @paolillo2018
-@hedstrom2009oxford, chapter 11, 12
+STRESS A LINEARITY APPROACH vs SYSTEMIC APPROACH.
+Residential segregation can be defined as the unequal and non random distribution of people  belonging to different groups within the spatial units of a city [@bruch2009segregation;@clark2008understanding].
+The interest of the social sciences on the topic is due the consequences it can have on the chance of interaction and integration between groups [@bolt2010linking], with exclusion of minorities in deprived neighborhoods and perpetuation of inequalities through generations [@van2012understanding].
+A key research question in literature is on the dynamics of emergence of residential segregation.
+Two hystorical hypothesis are the spatial assimilation theory and the place stratification theory.
+According to the former, spatial distance reflects the social distance between groups, and can change as effect of social moblity (@coulter2019ethnic), while the latter focuses on the strategies of gatekeepers, e.g.
+sellers, to prevent undesired newcomers to neighborhood (@horr2018ethnic).
+Both have in common the assumption that residential  segregation is the intended result of individual behavior.
+A third perspective can be that of social complexity and Schelling's agent-based model of residential segregation, which addresses residential segregation as a stable property of the aggregated behavior of people who seek to satisfy even mild homophily preferences within spatial constraints [@schelling1969;@schelling1971;@schelling1978].
+The paper here presented follows this stream of literature and aims at contributing to Schelling's type dynamics.
+\par
 
-* Why an additional characteristic than ethnicity, literature in residential studies
+Diversity in cities: how to navigate the difference: Heterogeneity in ethnic preferences and competing preferences
 
-* Update: justification for random utility models, literature in ABM
-Better define the individual  decision process
-Link with empirical data
-@huang2014review
-@klabunde2016decision
-@bruch2019choice
+Lead Question (ex):
+* how can we explain hybrid ethnic segregation patterns? (The Economist)
+* hybrid segregation on value and ethnic for different types of people
 
-* Research question
-How would the interaction between $\beta$ for different dimensions affect Schelling's scenarios
+Assumption: 
+* people differ in their degree of ethnic preferences (lit. @xie2012modeling, @hatna2015combining)
+* peole have different preferences and sort out of different factors [@bruch2009segregation]
 
-# Model and Experiments
+@xie2012modeling: use different threshold size according to class from Guttman, the 6th class not conforming to Guttman linear function and rum.
+Their concept of heterogeneity is on the different threshold levels (within 5 classes, with the 5th being tolerant to $57 \%$ to $100 \%$) black, so indifferent), with the consequence to decrease segregation.
+This trend holds also when continuous preferences are included, meaning cumulative threshold between agents.
+We would modify $\beta$, decomposing a random utility model, assuming the desired concentration peak 1 and varying $\beta$ \par
+
+In  the definition of competing preferences, stress that the value-orientation across ethnicity is defiant to Schelling's dichotomous definition of similarity (see @clark1991residential for a critical view)
+
+@clark1991residential old: for historical excursus
+@chen2005emergence: good perspective to position with value similarity (not in their paper). Update literature, consider heterogeneity within the same race
+
+Define need of value similarity
+
+Role of relative group size for both the ethnic and the value dimension
+
+```{r model, fig.pos ='h!',out.width='50%',out.height='90%',fig.show='hold',fig.align='center', fig.cap= "Draft of agents attribution and emerging segregations, to revise.",  echo = FALSE, include=TRUE}
+knitr::include_graphics("C:/Users/rocpa/OneDrive/Desktop/AF/ethnic-value_multinomial/material/model_pr.jpg")
+```
+
+# Model
 
@@
 
-* Calculation utility and probability function
+$\beta^\Box_e \geq \beta^\circ_e$
 
-To explore what levels of $\beta$ should not be excluded from the manipulations, I built a specific model with a unique beta for ethnic composition ($\beta_{ie}$ ) that does not change among agents.
-At each run I incremented degree of $\beta_{ie} \in[0,100]$ and let run for 1000 ticks with agents asynchronously relocating (not 1 agent for 1 tick, all to complete the procedure to restart).
-In each condition linear function was used: the preference peak of agents was $100\%$ for ethnically similar
+# Experiments
 
-To explore what levels of $\beta$ should not be excluded from the manipulations, I made a specific model "rum_eth.nlogo" (in material), with a unique $\beta$ for all agents.
-I run the simulation for 1000 ticks (not 1 agent 1 tick):
-* linear function: peak preference for all agents at $100 \%$
-* density == $70 \%$
-* equal distribution of value orientation in each ethnic group
-* changing $beta_ie$ at each run $beta_ie \in[0,100]$
+Study 1: heterogeneity of ethnic preferences in agents \par
+* Tune $\beta_e$ for all agents, with condition $\beta^\Box_e \geq \beta^\circ_e$
+* Same conditions, increase $\beta_v$
 
-```{r one-beta, fig.cap="Comparison of ethnic segregation for one beta-ethnic, not interaction. Used one-beta.csv from simulation rum-eth.nlogo" , include=TRUE}
+The concept of heterogeneity is reflected into the experiments: \par
+* individual: $\beta^\Box_e \geq \beta^\Box_v$, $\beta^\circ_v \geq \beta^\circ_e$  \par
+* within ethnic group:  $\beta^\Box_e \geq \beta^\circ_e$, $\beta^\circ_v \geq \beta^\Box_v$, should specify the ethnic group  \par
+NO * between ethnic group: $\beta^{\Box B}_e \geq \beta^{\Box R}_e$ (and implying $\beta^{\Box B}_e \geq \beta^{\circ R}_e$  ) NO \par
 
-a <- read.csv("one-beta.csv",sep = ",",skip = 6)
-names(a)[names(a) == "mean..count..turtles.on.neighbors..with..ethnicity....ethnicity..of.myself....count..turtles.on.neighbors....of.turtles.with..count..turtles.on.neighbors.....1." ] <- "eth_seg"
+These are the conditions kept in the experiments, ranging $\beta \in{0,10}$  \par
 
-a %>% filter(ticks == 0  | ticks == 500  | ticks == 100 | ticks == 1000)  %>%  filter(beta.ie >= 0 & beta.ie <= 15) %>% ggplot(aes(x = beta.ie, y = eth_seg)) + geom_bar(stat="identity") + facet_wrap(~ ticks, labeller = label_both)
-
-```
-
-```{r att_income , include=TRUE}
-
-f_att <- function(i,b){   # utility function as single-peaked
- A <- 1 / (1 + exp(-b(i)))
-}
-
-  b <- 0.5
-
-a_0 <- f_cst(a,0)
-a_1 <- f_cst(a,0.1)
-a_2 <- f_cst(a,0.2)
-a_3 <- f_cst(a,0.3)
-a_4 <- f_cst(a,0.4)
-a_5 <- f_cst(a,0.5)
-a_6 <- f_cst(a,0.6)
-a_7 <- f_cst(a,0.7)
-a_8 <- f_cst(a,0.8)
-a_9 <- f_cst(a,0.9)
-a_10 <- f_cst(a,1)
-
-Prob_A <- c(a_0,a_1,a_2,a_3,a_4,a_5,a_6,a_7,a_8,a_9,a_10)
-income <- seq(0,i, by = 0.1)
-
-plot(price,na.omit(utility),ylab = "utility_ec",xlab="price", main = paste0("income =",i))
-
-```
-
-```{r income_price , include=TRUE}
-
-# tentative of utility economic, given by the difference (income - price), so to represent how convenient a location is. 
-# ideally identity equation: if income < price, probability would be 0. If beta is negative, the probability could still be computed, which is nonsense
-
-f_cst <- function(i,p){   # utility function as single-peaked
- if (i < p){
-    U <- NA}else{
-  U <- ((i - p) / i)}
-}
-
-  i <- 0.5
-
-i_0 <- f_cst(i,0)
-i_1 <- f_cst(i,0.1)
-i_2 <- f_cst(i,0.2)
-i_3 <- f_cst(i,0.3)
-i_4 <- f_cst(i,0.4)
-i_5 <- f_cst(i,0.5)
-i_6 <- f_cst(i,0.6)
-i_7 <- f_cst(i,0.7)
-i_8 <- f_cst(i,0.8)
-i_9 <- f_cst(i,0.9)
-i_10 <- f_cst(i,1)
-
-utility <- c(i_0,i_1,i_2,i_3,i_4,i_5,i_6,i_7,i_8,i_9,i_10)
-price <- seq(0,i, by = 0.1)
-
-plot(price,na.omit(utility),ylab = "utility_ec",xlab="price", main = paste0("income =",i))
-
-```
+Think about it.
 

### 2020-01-26 ethnic_value_rum.Rmd
Broad lead research question

@@
 Diversity in cities: how to navigate the difference: Heterogeneity in ethnic preferences and competing preferences
+People can rank their preferences differently based on their value-orientation
+Still, ethnic groups can differ on their degree of ethnic, either value preferences
 
-Lead Question (ex):
-* how can we explain hybrid ethnic segregation patterns? (The Economist)
-* hybrid segregation on value and ethnic for different types of people
+Literature on Schelling's model on heterogeneity within group (between agents) [@xie2012modeling]. Check for heterogeneity between groups
+
+NEW: the competing homophily preference based on the value-orientation
+
+Lead Question (ex): \par
+* how can we explain hybrid ethnic segregation patterns (some members of the same ethnic group are ethnically integrated, others are ethnically segregated)? (The Economist) \par
+* how can we explain hybrid value segregation patterns (some members of the same ethnic group are ethnically integrated, others are ethnically segregated)? \par
+* what is the effect of value segregation on  ethnic segregation and vice versa? \par
+* Factors underlying the mechanism of interest:  \par
+- degree of parameter beta: how one dimension is important over the other in the relocation choice  \par
+- relative group size for both the ethnic and the value dimension, since they would have a direct effect on the utility of a location
+and on the number of agents defined as ethnicity-oriented and value-oriented
+- heterogeneity within same ethnic group and between ethnic groups
+* what is the role of heterogeneity in preferences within a group, and between groups? \par
+* hybrid segregation on value and ethnic for different types of people \par
+* What is the effect on such dynamics of relative group size \par
 
@@
 
+We define the condition where people hold different ethnic and value preferences.
+We can impose at the individual level due by value-orientation that one group holds one preference higher than the other and that the degree of one preference is higher than the other one
+
+DOUBT: if an agent likes "diversity", then I would expect the peak to change, and it being at $50 \%$ for the ethnic dimension, so integrationist attitudes, and the peak of value concentration of these agents to change according  to the $100 \%$ similar others integrationists, but you are making a different reasoning, that people aim at ethnic diversity, and the dimension of ethnicity would be less/more important in the relocation choice
+
+The concept of heterogeneity is reflected into the experiments: \par
+* individual: $\beta^\Box_e \geq \beta^\Box_v$, $\beta^\circ_v \geq \beta^\circ_e$  \par
+* within ethnic group:  $\beta^\Box_e \geq \beta^\circ_e$, $\beta^\circ_v \geq \beta^\Box_v$, should specify the ethnic group  \par
+
+This does not prevent than between groups there might be difference in terms of ethnic preferences, and similarly on value preferences
+
 Define need of value similarity 
-
 Role of relative group size for both the ethnic and the value dimension
@@
 Study 1: heterogeneity of ethnic preferences in agents \par
-* Tune $\beta_e$ for all agents, with condition $\beta^\Box_e \geq \beta^\circ_e$
-* Same conditions, increase $\beta_v$
+* 1.1 Tune $\beta_e$ for all agents, with condition $\beta^\Box_e \geq \beta^\circ_e$, no difference between agents
+* 1.2 Change  $\beta_e$ between groups (supported by literature on which group is going to be more conservative, or anyway argumented).
+Observe the emergence of ethnic segregation first
+* Same conditions, increase $\beta_v$ Either with first 1.1 and then compar, either compare first the effect of ethnic preference heterogeneity between groups over within group
+In both cases, the effect of relative group sizes
 
@@
 
+If a society is "conservative", the less ethnic-oriented of that society/scenario would have high level as well.
+In the end, you could narrow down so to have 3 conditions for each low, medium, high beta (e.g.
+1, 5, 10), and calculate the $\beta_e$ of less ethnicity-oriented agents out of a ratio, e.g.
+min $n/n$,  $n/(n:2)$ (check), max $n/1$ \par
+* 1 = 1,0.5,1 (check)
+* 5 = 1,2.5,5
+* 10 = 1,5,10
+
 # Results

### 2020-02-03 ethnic_value_rum.Rmd
Add files via upload

@@
 
+\newcommand{\rocco}[1]{\textcolor{red}{{Rocco:}#1}}
+
 \abstract{}
@@
 
-STRESS A LINEARITY APPROACH vs SYSTEMIC APPROACH.
+<!-- STRESS A LINEARITY APPROACH vs SYSTEMIC APPROACH.
 Residential segregation can be defined as the unequal and non random distribution of people  belonging to different groups within the spatial units of a city [@bruch2009segregation;@clark2008understanding].
@@
 The paper here presented follows this stream of literature and aims at contributing to Schelling's type dynamics.
-\par
+\rocco{this paragraph should be more in medias res: explaining the approach of Schelling and random utility models on the question how different degrees of segregation can be reduced out of ethnic diversity}-->
 
-Diversity in cities: how to navigate the difference: Heterogeneity in ethnic preferences and competing preferences
-People can rank their preferences differently based on their value-orientation
-Still, ethnic groups can differ on their degree of ethnic, either value preferences
+* Increasing diversity in city, segregation and integration do not apply equally to stratum and places of society
+    1. diversity and ethnic tolerance in cities
+    2. interplay and potential factors: ses-ethnicity, relative group sizes
+    3. our interest: different taste
+
+Residential segregation can be defined as the unequal and non random distribution of people  belonging to different groups within the spatial units of a city [@bruch2009segregation;@clark2008understanding].
+A main dimension of interest in literature is that of ethnic segregation as a salient dimension of majority/minority condition.
+<!-- Hystorical hypotheses focus on the spatial assimilation focus on how the spatial distance of ethnic minorities reflect the social distance to mainstream society, and how this would shorten as effect of social mobility and cultural assimilation.
+Place  stratification theory highlights the role of stakeholders on limit access to newcomers from other ethnic groups.
+--> .
+An overarching hypothesis for relocation choice is that of homophily preferences, that is people prefer to live close to other similars.
+Although this might correlate with other tools and resources of people, this is a usual paradigm in housing studies to explain the relocation choice of people.
+However, ethnicity per se is losing its explanatory power in recent years [@albaclashofethncity].
+Several reasons might support this.
+First of all, the concept of superdiversity highlights how western cities have already  reached a high level of diversity as effect of increasing migration flows, social mobility and residential mobility.
+Not only numerous ethnic group cohexist in the same city, but also the membership people belong to are different and overlapping.
+One example is socio-economic status, as a dynamic category acquire as effect of social mobility.
+There is growing evidence that in the last decades socio-economic segregation has reached higher levels than ethnic-racial segregation.
+Implicitly, this means that members of the same ethnic group might be differently integrated depending on their degree of social mobility.
+
+In this paper, we focus on two concepts that can be associated with ethncity in diverse societies: tolerance toward ethnic diversity and tastes for dimensions other than ethnicity.
+At the theoretical level, rational models and ethnic boundary making can support the frame of our work.
+
+Generally within random utility models, the place where people live can be considered the result of preferences of people for neighborhood composition, in addition to costs and resources to relocation.
+Given ethnic heterogeneity of a neighborhood, people might simply differ in their degree of preference for ethnically cohesive or ethnically mixed neighborhood.
+Such difference can correlate with other characteristics people belong to.
+Blurring boundaries (@albeda) focuses on the strict or not division between groups.
+@weldon2006institutional countries can vary in their degree of tolerance toward minority, and policy orientation of countries toward assimilation or multiculturalism affect the degree of tolerance of citizens.
+
+Symbolic boundaries (@albeda) in superdiverse neighborhood.
+We can assume that one of this is the same taste people have.
+@diversity show how people who like diversity move to similar neighborhoods for cultural consumption, although their preferences did not transmitt to their network, they showed preferences for having other cultural diversity lovers in their neighborhood.
+@Musterd correlate the tastes  and preferences of people in term of gender balance within the household with social class people belong to.
+Their study confirmed the social homophily preference for cultural consumption (as a proxy of economic activities).
+
+<<!-- . Superdiversity in cities put this to the test.
+1.
+Superdiversity of cities, in terms of many ethnic groups belonging.
+In this paper, we focus on two concepts that can be associated with ethncity in diverse societies: tolerance toward ethnic diversity and tastes for dimensions other than ethnicity.
+In detail, for each of them:
+1.1. how tolerance diversity might differ between individuals of the same group and between groups
+1.2. for different tastes and preferences, how these could trigger or alleviate ethnic segregation.-->
+
+Both for ethnic preferences and non-ethnic preferences, following an homophily preference would imply the role of relative group sizes.
+
+One main point in residential studies is not the lack of empirical data, rather than they rely on observed preferences or stated preferences  through correlation studies.
+What is lack is the understanding of the mechanisms linking the relocation choice preferences and contextual resources, with aggregating patterns.
+Ethnic segregation is an example of emerged phenomena.
+This is the contribution of agent-based modeling and social complexity.
+We use Edmonds as explanation of possible outcomes of residential segregation
+
+When it comes to residential segregation, the implementation of these two mechanisms might be non linear.
+
+People belong to different groups and identify others over many categories, as well, they can segregate along many scales.
+Residential segregation can be defined as the unequal and non random distribution of people  belonging to different groups within the spatial units of a city [@bruch2009segregation;@clark2008understanding].
+The interest of the social sciences on the topic is due the consequences it can have on the chance of interaction and integration between groups [@bolt2010linking], with exclusion of minorities in deprived neighborhoods and perpetuation of inequalities through generations [@van2012understanding].
+A critical  dimension of segregation for long time in housing has been the ethnic segregation, associating the spatial distance between ethnic groups as reflection of their social distance (spatial assimilation), or the intention to distance member of the outgroup (place stratification), as reflected in measures of ethnic concentration.
+Segregation is not experienced equally within groups and it might be due to many causes.
+Multicomplexity implies that societies can be different for many dimensions  and people indeed belong to different categories.
+People can express different tastes,  which can correlate with their characteristics [@van2019sociocultural].
+what dimension matters and how it correlates with characteristics of people [@andersson2007mix]
+Different tastes can link to different classes.
+
+2. Focus on emergence of segregation which demonstrates puzzling effects.
+
+Indeed, it is a known trend in literature that socio-economic segregation is becoming more relevant than ethnic segregation.
+This can be due to social mobility achievement, as well as housing policies.
+This implies that degree of segregation might be different for different strata of societies.
+The difference is not necessarily due to resources, but also to preferences.
+
+* Need to understand the dynamics of relocation choice and relocate to macro outcomes: Schelling and random utility models
+    1. Schelling and agent-based modeling
+    2. random utility: why/how we implement in an  agent-based model (Mare reply)
+
+* Examples on integration issue and advances in Schelling:
+    1. random  utility models  in Schelling: Bruch and Mare linear function
+    2. xie, hatna,  etc. specific studies, what they have in common: heterogeneity of threshold tolerance
+    3. @paolillo2018 focused on threshold model for different tastes
+
+* What is new/peculiar of the paper (what could be possible mechanisms that explain hybrid segregation): 
+    2. heterogeneity within group: specific scenario of tolerant and ethnic and higher preference of them
+    3. heterogeneity between groups: one group is on average more/less tolerant than the other+
+    4. tastes other than ethnicity
+    4. relative group size effect
+
+* Overall, marking the lead research question and contributions of the paper
+
+Lead Question (ex):
+
+* how can we explain hybrid ethnic segregation patterns (some members of the same ethnic group are ethnically integrated, others are ethnically segregated)? (The Economist)
+* how can we explain hybrid value segregation patterns (some members of the same ethnic group are ethnically integrated, others are ethnically segregated)?
+* what is the effect of value segregation on  ethnic segregation and vice versa?
+Using agent-based modeling, we can disentangle and model specific beta distribution
+* Factors underlying the mechanism of interest:  
+   + degree of parameter beta: how one dimension is important over the other in the relocation choice 
+   + relative group size for both the ethnic and the value dimension, since they would have a direct effect on the utility of a location
+and on the number of agents defined as ethnicity-oriented and value-oriented
+   + heterogeneity within same ethnic group and between ethnic groups
+* what is the role of heterogeneity in preferences within a group, and between groups? 
+* hybrid segregation on value and ethnic for different types of people
+* What is the effect on such dynamics of relative group size
+
+<!--
+
+@xie2012modeling and @hatna2015combining on heterogeneity.
+@hatna2015combining: heterogeneous within the group  due to threshold F: blue F1, green F1, blue F2, green F2.
+They had a linear to peak and then constant function of Schelling, not rum, using difference threshold  to explore the cases of integration and segregation and mixed patterns.
+In last experiment with beta-binomial distribution of threshold of agents.
+@xie2012modeling  the heterogeneity between agents.
+
+Here we propose a different approach to how hybrid segregation
 
@@
 
-Lead Question (ex): \par
-* how can we explain hybrid ethnic segregation patterns (some members of the same ethnic group are ethnically integrated, others are ethnically segregated)? (The Economist) \par
-* how can we explain hybrid value segregation patterns (some members of the same ethnic group are ethnically integrated, others are ethnically segregated)? \par
-* what is the effect of value segregation on  ethnic segregation and vice versa? \par
-* Factors underlying the mechanism of interest:  \par
-- degree of parameter beta: how one dimension is important over the other in the relocation choice  \par
-- relative group size for both the ethnic and the value dimension, since they would have a direct effect on the utility of a location
+Lead Question (ex):
+
+* how can we explain hybrid ethnic segregation patterns (some members of the same ethnic group are ethnically integrated, others are ethnically segregated)? (The Economist)
+* how can we explain hybrid value segregation patterns (some members of the same ethnic group are ethnically integrated, others are ethnically segregated)?
+* what is the effect of value segregation on  ethnic segregation and vice versa?
+* Factors underlying the mechanism of interest:  
+   + degree of parameter beta: how one dimension is important over the other in the relocation choice 
+   + relative group size for both the ethnic and the value dimension, since they would have a direct effect on the utility of a location
 and on the number of agents defined as ethnicity-oriented and value-oriented
-- heterogeneity within same ethnic group and between ethnic groups
-* what is the role of heterogeneity in preferences within a group, and between groups? \par
-* hybrid segregation on value and ethnic for different types of people \par
-* What is the effect on such dynamics of relative group size \par
+   + heterogeneity within same ethnic group and between ethnic groups
+* what is the role of heterogeneity in preferences within a group, and between groups? 
+* hybrid segregation on value and ethnic for different types of people
+* What is the effect on such dynamics of relative group size
 
 Assumption:
+
 * people differ in their degree of ethnic preferences (lit. @xie2012modeling, @hatna2015combining)
@@
 This trend holds also when continuous preferences are included, meaning cumulative threshold between agents.
-We would modify $\beta$, decomposing a random utility model, assuming the desired concentration peak 1 and varying $\beta$ \par
+We would modify $\beta$, decomposing a random utility model, assuming the desired concentration peak 1 and varying $\beta$
 
 In  the definition of competing preferences, stress that the value-orientation across ethnicity is defiant to Schelling's dichotomous definition of similarity (see @clark1991residential for a critical view)
+
+\vspace{10pt}
 
@@
 
-The concept of heterogeneity is reflected into the experiments: \par
-* individual: $\beta^\Box_e \geq \beta^\Box_v$, $\beta^\circ_v \geq \beta^\circ_e$  \par
-* within ethnic group:  $\beta^\Box_e \geq \beta^\circ_e$, $\beta^\circ_v \geq \beta^\Box_v$, should specify the ethnic group  \par
+The concept of heterogeneity is reflected into the experiments: 
+* individual: $\beta^\Box_e \geq \beta^\Box_v$, $\beta^\circ_v \geq \beta^\circ_e$  
+* within ethnic group:  $\beta^\Box_e \geq \beta^\circ_e$, $\beta^\circ_v \geq \beta^\Box_v$, should specify the ethnic group
 
@@
 Role of relative group size for both the ethnic and the value dimension
+
+-->
 
@@
 
+\vspace{10pt}
+
+@hatna2015combining: in previous studies, they had a "F critical", maybe we could use on the critical $\beta$?
+
+\vspace{10pt}
+
 The concept of heterogeneity is reflected into the experiments: \par
@@
 
+Dependent measure:
+
+* ethnic segregation exposure as Schelling (color)
+* value segregation exposure as Schelling (shape)
+* C index in @hatna2012schelling, to check
+
+**beta-binomial distribution? Discrete values deriving from beta distribution but not limit [0,1] @hatna2015combining**
+
 # Results
 
+# Conclusions/ further ideas
+
+@van2019sociocultural introduction: social homophily as due to preferences and constraints' approach. They also use social class as proxy for  socio-cultural differentiation
+
 # References

### 2020-02-10 ethnic_value_rum.Rmd
Add files via upload

--- 2020-01-23 ethnic_value_rum.Rmd
@@
 The paper here presented follows this stream of literature and aims at contributing to Schelling's type dynamics.
-\par
+\rocco{this paragraph should be more in medias res: explaining the approach of Schelling and random utility models on the question how different degrees of segregation can be reduced out of ethnic diversity}-->
 
-Diversity in cities: how to navigate the difference: Heterogeneity in ethnic preferences and competing preferences
+* Increasing diversity in city, segregation and integration do not apply equally to stratum and places of society
+    1. diversity and ethnic tolerance in cities
+    2. interplay and potential factors: ses-ethnicity, relative group sizes
+    3. our interest: different taste
 
-Lead Question (ex):
-* how can we explain hybrid ethnic segregation patterns? (The Economist)
-* hybrid segregation on value and ethnic for different types of people
+Societies are increasingly diverse
+people segregate along different dimensions
 
-Assumption: 
-* people differ in their degree of ethnic preferences (lit. @xie2012modeling, @hatna2015combining)
-* peole have different preferences and sort out of different factors [@bruch2009segregation]
+Residential segregation can be defined as the unequal and non random distribution of people  belonging to different groups within the spatial units of a city [@bruch2009segregation;@clark2008understanding].
+A main dimension of interest in the social sciences and housing policies is that of ethnic segregation, considering ethnicity as a salient dimension of in-group/out-group membership and consideration of disadvanted minorities in deprived neighbrohoods.
+In residential move, a simple explanatory variable that is implemented also to explain ethnic concentration is that of spatial sorting or homophily preference, i.e.
+the preference to aggregate with people of the same ethnic group.
+Nevertheless, in modern and diverse societies the effect of ethnicity as the main factor in inter-ethnic relations and social integration could not be taken straightforward [@alba2014twilight] for a number of reasons.
+First of all, the concept of superdiversity highlights how most western cities nowadays have reached tremendous degree of ethnic diversity and the dimensions that define category of people are  numerous and overlapping.
+As a matter of fact, literature is much unanimous that in the last decades socio-economic segregation has increased while racial-ethnic ethnic segregation as decreased.
+Indeed, this would highlight the effect of income inequalities in relocation costs and relate to other mechanisms of relocation choice as neighborhood attainment.
+As a matter of fact, also remaning within the assumption of homophily preferences, these can vary within the same ethnic group due to different economic distribution [@andersson2007mix].
 
-@xie2012modeling: use different threshold size according to class from Guttman, the 6th class not conforming to Guttman linear function and rum.
-Their concept of heterogeneity is on the different threshold levels (within 5 classes, with the 5th being tolerant to $57 \%$ to $100 \%$) black, so indifferent), with the consequence to decrease segregation.
-This trend holds also when continuous preferences are included, meaning cumulative threshold between agents.
-We would modify $\beta$, decomposing a random utility model, assuming the desired concentration peak 1 and varying $\beta$ \par
+In this paper, we focus on two concepts associated with ethnic diversity in modern societies when considering relocation choice, i.e.
+heterogeneity and tolerance in ethnic preferences at individual and groupal level, and preferences for other dimensions that can interact with ethnicity.
+As a rational choice and at individual level, people can differ in their degree of preference for ethnic composition.
+Literature shows how preferences for ethnic composition vary within the same ethnic group according to other characteristics as socio-economic status.
+At a group level, acceptance of diversity is one necessary component to foster social cohesion and can be the result of social policies or embedded in culture.
+@weldon2006institutional countries can vary in their degree of tolerance toward minority, and policy orientation of countries toward assimilation or multiculturalism affect the degree of tolerance of citizens.
+As culture, some groups are more likely to blur the boundaries towards more similar cultures than others (@albeda2018symbolic).
 
-In  the definition of competing preferences, stress that the value-orientation across ethnicity is defiant to Schelling's dichotomous definition of similarity (see @clark1991residential for a critical view)
+Having less preference for ethnic composition, does  not neglect the preference for other dimensions of similarity.
+Here the theoretical framework of ethnic boundary making is relevant.
+The framework is built upon the dynamic and symbolic boundaries that distinguish between "us" and "them" [@bail2008configuration] and that are built by individuals in the interaction between groups [@wimmer2013ethnic].
+The role of ethnic boundaries is therefore to define the belonging of individuals to group and orient both individual attribution of similarity and access to  resources between groups [@esser2010assimilation].
+Out of this, people can define similarity with individuals despite their ethnicity and based on common characteristics mutually recognized.
+Taste for diversity can be an example and it would have a straight consequence on the dimension of ethnic neighborhood concentration.
+@blokland2010people show how people who like diversity prefer to live in neighborhoods with other people who like diversity as well, apart the common interest in utilities for  cultural consumptions (e.g.
+libraries).
+@van2019sociocultural address directly sociocultural dispositions (i.e.
+gender balance in household work) within spatial sorting along income and ethncity and linking different dispositions to social class indepenent of ethnicity.
+Their result show how sociocultural disposition might predict the willingness to live in a neighborhood.
 
-@clark1991residential old: for historical excursus
-@chen2005emergence: good perspective to position with value similarity (not in their paper). Update literature, consider heterogeneity within the same race
+In both cases of ethnic preference or sociocultural dispositions, relative group sizes play a critical role in orienting relocation choice and attractiveness of neighborhoods.
+Within the broad framework of inter-ethnic relations, relative group sizes are critical to inter-ethnic relations and assimilation processes, since the minority group is more likely to be absorbed by majority  not reaching a critical mass [@blau1977macrosociological; @esser2010assimilation].
+As regards spatial sorting, the link is immediate  since the proportion of people considered  as similar will be the direct attractor of relocation preference.
+Considering the overlap of categories people belong to in diverse societies, individuals can belong to both an overrepresented category (e.g.
+cultural disposition or middle-class), and an underrepresented  one (e.g.
+minority ethnic group).
+In both cases the correlation between categories would influence the spatial sorting of people in resulting segregation.
 
-Define need of value similarity
+Assuming the critical factors of heterogeneity towards ethnic preference, interaction with other dimensions than ethnicity and relative group sizes, the questions is opened on how they contribute to explain different degree of ethnic segregation for different members of society as effect of relocation choice.
+The interest of this paper is to formalize such mechanisms, for which agent-based modeling and Schelling's model is justified.
+Differently from theories as spatial assimilation and place stratification that focus on individual strategies of movers and stake holders, the perspective of social complexity focuses on residential segregation as a complex and dynamic phenomenon that emerge from interaction between residential movers and the contextual parameters of their action.
+The study of similar phenomena cannot be reduced to individual preferences but requires agent-based computer simulations where such interactions can be implemented, experimented to the aim of formalizing mechanisms underlying macro phenoomena.
+Schelling's model is an example of this framework and a known agent-based model.
+Fitting the homophily hypothesis, Schelling described a scenario where people stay  in a neighborhood as long as the concentration of similar ones is not less than a desired threshold (e.g.
+$50 \%$), leaving to a random relocation otherwise.
+Given the spatial constraint to relocate, e.g.
+due to density of population, the interplay of people pursuing the same behavior would cause high level of segregation, even if the desired concentration of similar ones is extremely low.
+Schelling's model has been subject to many applications and extensions in literature.
+In recent years, some extensions aim at implementing random utility models of agents' behavior that better simulate the utility functions used in relocation choice.
+Random utility models are not new in relocation choice.
+Stemming from microeconomics, they reflect the utility maximization of consumers who must select between options (i.e.
+neighborhoods where to relocate).
+Being utility a random variable unknown to researchers, this can be derived by the observed characteristics of options people selected from, using these as predictor to the probability to select one neighborhood in addition to randomness in the choice.
+Out of regression models that allow such calculations, @mcfadden1973conditional's conditional logit has received ample attention in residential studies, since it allows to estimate through coefficients of regression (parameter $\beta$) indicating how important one dimension of utility was to relocation choice compared to random term and correlate these to demographic characteristics of the population.
 
-Role of relative group size for both the ethnic and the value dimension
+A critical example is by Elizabeth E.
+Bruch and Robert D.
+Mare @bruch2006neighborhood @bruch2009preferences \rocco{to trace back the paper history} who implemented  @mcfadden1973conditional's conditional logit within Schelling's dynamic and substitute threshold function with utility linear function, meaning agents become sensitive to fine-grained change in neighborhood ethnic composition.
+Following this trend, other studies have extended Schelling to fit ethnically diverse scenarios as stressed above.
+@xie2012modeling uses random utility models and threshold function, but introduce heterogeneity at individual level of agents to reproduce whites heterogeneity for ethnic composition in U.S.
+survey.
+Their result show how increasing heterogeneity can reduce ethnic concentration compared to @bruch2009preferences.
+Although not with random utility models, @hatna2014combining reproduce heterogeneity of thresholds not at individual level, but within groups, presenting more tolerant agents in each ethnic group, with tolerant agents holding the same theshold, so to formalize how this combination can lead to hybrid combination of integration and segregation.
+@paolillo2018 were the first to the best of our knowledge to adapt Schelling's homophily preferences to ethnic composition and value composition.
+In their adaptation, agents of both ethnic groups were divided into ethnicity-oriented agents, who considered as similar agents of their ethnicity, regardless their values, and value-oriented agents who considered similar those agents sharing similar values regardless of their ethncity.
+The authors explored how the inclusion of value-oriented agents reduced ethnic segregation compared to Schelling, and under which threshold both agents would be satisfied with their neighborhoods, including role of relative group sizes.
+The main discover was a spillover effect so that ethnicity-oriented in minority condition would find attractive ethnically mixed neighborhood formed by value-oriented agents, because of availability of ethnically similar ones, until the point their concentration caused value-oriented to leave.
+
+In this paper, we want to extend @paolillo2018 differentiation between value-oriented and ethnically-oriented agents to explain different integration degree for members of the same group, adapting it to random utility models as proposed by @bruch2006neighborhood.
+Following @bruch2009preferences, random utility models in observed preferences and agent-based models have a critical difference.
+While utility functions and parameters beta can be estimated by observed characteristics of the options, they remain ultimately unknown, whereas in the agent-based modeling framework these components are expressly built within the cognitive process of simulated agents.
+We want to take advantage of this for what concerns the role of $\beta$ parameters for value orientation and ethnic membership in agents' relocation, and keeping the linear function for concentration of similar ones.
+We believe this strategy  opens up more distinguished scenarios than in @xie2012modeling and  @hatna2014combining where only the threshold preference changes, but weight in the relocation choice relies only on the ethnic composition.
+By varying $\beta$ indicators of agents for both ethnicity and value dimension, we expect to better observe the interdependence of the two dimensions.
+To this aim, we explore the heterogeneity for ethnic and value preferences at individual level (with agents holding higher beta thant the other) and between groups (with one group showing more ethnic tolerance that the other).
+In addition, the role of relative group sizes for both dimensions.
 
@@
 Study 1: heterogeneity of ethnic preferences in agents \par
-* Tune $\beta_e$ for all agents, with condition $\beta^\Box_e \geq \beta^\circ_e$
-* Same conditions, increase $\beta_v$
+* 1.1 Tune $\beta_e$ for all agents, with condition $\beta^\Box_e \geq \beta^\circ_e$, no difference between agents
+* 1.2 Change  $\beta_e$ between groups (supported by literature on which group is going to be more conservative, or anyway argumented).
+Observe the emergence of ethnic segregation first
+* Same conditions, increase $\beta_v$ Either with first 1.1 and then compar, either compare first the effect of ethnic preference heterogeneity between groups over within group
+In both cases, the effect of relative group sizes
+
+\vspace{10pt}
+
+@hatna2015combining: in previous studies, they had a "F critical", maybe we could use on the critical $\beta$?
+
+\vspace{10pt}
 
@@
 
+If a society is "conservative", the less ethnic-oriented of that society/scenario would have high level as well.
+In the end, you could narrow down so to have 3 conditions for each low, medium, high beta (e.g.
+1, 5, 10), and calculate the $\beta_e$ of less ethnicity-oriented agents out of a ratio, e.g.
+min $n/n$,  $n/(n:2)$ (check), max $n/1$ \par
+* 1 = 1,0.5,1 (check)
+* 5 = 1,2.5,5
+* 10 = 1,5,10
+
+Dependent measure:
+
+* ethnic segregation exposure as Schelling (color)
+* value segregation exposure as Schelling (shape)
+* C index in @hatna2012schelling, to check
+
+**beta-binomial distribution? Discrete values deriving from beta distribution but not limit [0,1] @hatna2015combining**
+
 # Results
 
+# Conclusions/ further ideas
+
+@van2019sociocultural introduction: social homophily as due to preferences and constraints' approach. They also use social class as proxy for  socio-cultural differentiation
+
 # References

### 2020-02-13 ethnic_value_rum.Rmd
after feb 11

--- 2020-01-26 ethnic_value_rum.Rmd
@@
 ---
-output:
-  bookdown::pdf_document2:
-    toc: false
- #   keep_tex: false
-    fig_caption: yes
 title: "Tolerant  to ethnic diversity, intolerant to intolerance"
 subtitle: "Title to define"
-author:  Rocco Paolillo, Andreas Flache
-# date:  "`r  as.Date(Sys.time(), '%d %B %Y')`"
+author:  "Rocco Paolillo, Andreas Flache"
+date:  "`r  as.Date(Sys.time(), '%d %B %Y')`"
 # "`r  as.Date(Sys.time(), '%d %B %Y')`"
@@
 always_allow_html: yes
+output: pdf_document
+    # toc: false
+ #   keep_tex: false
+#fig_caption: yes
 header-includes:
@@
 
-# install.packages("tinytex", repos = "https://cloud.r-project.org" )
+install.packages("tinytex", repos = "https://cloud.r-project.org" )
 library(tidyverse)
@@
 
+\newcommand{\rocco}[1]{\textcolor{red}{{Rocco:}#1}}
+
 \abstract{}
 
-# INTRO FOCUSED ON SCHELLING, MUST BE ON HYBRID SEGREGATION
+# NOTES FOR March 5, to shuffle focusing on Schelling and from ethnicity to value/cosmopolitan
+
+* TO READ: D. J. Haw & S. J. Hogan (2020) A dynamical systems model of unorganized segregation in two neighborhoods, The Journal of Mathematical Sociology, DOI: 10.1080/0022250X.2019.1695608
+
+* We aim at Journal of Mathematical Sociology
 
@@
 
-STRESS A LINEARITY APPROACH vs SYSTEMIC APPROACH.
 Residential segregation can be defined as the unequal and non random distribution of people  belonging to different groups within the spatial units of a city [@bruch2009segregation;@clark2008understanding].
-The interest of the social sciences on the topic is due the consequences it can have on the chance of interaction and integration between groups [@bolt2010linking], with exclusion of minorities in deprived neighborhoods and perpetuation of inequalities through generations [@van2012understanding].
-A key research question in literature is on the dynamics of emergence of residential segregation.
-Two hystorical hypothesis are the spatial assimilation theory and the place stratification theory.
-According to the former, spatial distance reflects the social distance between groups, and can change as effect of social moblity (@coulter2019ethnic), while the latter focuses on the strategies of gatekeepers, e.g.
-sellers, to prevent undesired newcomers to neighborhood (@horr2018ethnic).
-Both have in common the assumption that residential  segregation is the intended result of individual behavior.
-A third perspective can be that of social complexity and Schelling's agent-based model of residential segregation, which addresses residential segregation as a stable property of the aggregated behavior of people who seek to satisfy even mild homophily preferences within spatial constraints [@schelling1969;@schelling1971;@schelling1978].
-The paper here presented follows this stream of literature and aims at contributing to Schelling's type dynamics.
-\par
+Ethnicity has long been a main dimension of segregation, both as indicator of in-group/out-group relations and for its correlation with deprived neighborhoods [@VanHam2012].
+Nevertheless, in modern societies members of the same ethnic group can positionate differently on the continuum between integration and segregation, due to many reasons.
+In this paper we focus  on the possible mechanisms that underlying hybrid scenarios of residential segregation focusing on two factors, i.e.
+heterogeneity for ethnic preferences  within and between groups, and preferences for like-minded people who share the same conservative or integrationist attitudes.
+We advocate for usage of agent-based modeling and proceed by extending previous work on Schelling's model of residential segregation.
 
-Diversity in cities: how to navigate the difference: Heterogeneity in ethnic preferences and competing preferences
-People can rank their preferences differently based on their value-orientation
-Still, ethnic groups can differ on their degree of ethnic, either value preferences
+A simple but long-standing mechanism used in literature to explain ethnic concentration is that of spatial sorting or homophily preferences [@magi2016types;@muller2018residential], i.e.
+the tendency to aggregate with people of the same ethnic group [@mcpherson2001birds] .
+Although ethnic segregation is still considered a relevant issue, especially for modern and diverse societies the simple ethnic homophily assumption might not be that influential, and it should be included within more complex dynamics [@alba2014twilight].
+First of all, a growing concept in literature is that of superdiversity that characterizes western societies [@crul2016super], as effect of social mobility, inner-neighborhoods migration flows and multicultural households [@neal2013multiculture; @albeda2018symbolic].
+Out of many ethnic groups cohabiting in the same city, segregation might imply more than a binary definition between in-group/out-group and tolerance toward diversity become critical to social cohesion [@DragolovIgnaczea2016SocialCohesionin;@clark2018can; @vervoort2011ethnic].
+Furthermore, people belong to many and overlapping categories [@roccas2002social] that can prevail that of ethnicity in defining residential preferences as well as similarity in spatial sorting [@van2019sociocultural].
+Indeed, literature is most unanimous that in the last decades socio-economic segregation has increased at faster rates than racial-ethnic segregation which is generally decreased [@clark2002residential;@clark2015residential].
+Finally, people within the same ethnic group or social class can vary in their preferences, and differences in affordability give rise to more variegated scenarios  [@andersson2007mix].
+In sum, in super-diverse societies ethnic segregation has become a hybrid and complex phenomenon, where ethnicity correlates with other dimensions and people of the same ethnic membership can experience different degree of segregation/integration.
 
-Literature on Schelling's model on heterogeneity within group (between agents) [@xie2012modeling]. Check for heterogeneity between groups
+In this paper, we focus on two concepts associated with ethnic segregation in diverse societies when considering relocation choice, i.e.
+heterogeneity in ethnic preferences, and preferences for other dimensions that can interact with ethnic membership.
+As for heterogeneity in preferences, it is intuitive that people of the same group might differ in their preferences [@hess2018revisiting], this can increase when other subdivisions as socio-economic class are taken into account [@bruch2014population;@friedman2019muslim].
+Considering the context of multi-ethnic societies, difference between social groups are relevant.
+Some groups might be innerly more tolerant towards minorities, with consequences on inter-ethnic contacts [@bourhis1997towards] or they  might be likely to blur the boundaries towards specific groups as effect of their cultural similarities [@albeda2018symbolic].
+On the other side, tolerance towards ehtnic minorities  of citizens can result from the multicultural or assimilationist policies adopted by different governments [@weldon2006institutional].
+As for different preferences that could interact with the dimension of ethnicity, the perspective of ethnic boundary making is relevant.
+This theoretical framework focuses on the dynamic and symbolic boundaries that distinguish between "us" and "them" [@bail2008configuration], built by individuals in the continuous and different forms of interaction between groups [@wimmer2013ethnic].
+The core of ethnic boundary making is to understand how boundaries between in-group and out-group are socially constructed above the categories of ethnic membership, and not as a rigid consequence of them [@esser2010assimilation; @wimmer2013ethnic].
+Following this perspective, a taste for ethnic and cultural diversity can serve both to blur  ethnic boundaries and to define similarity with other people despite their ethnic membership.
+@blokland2010people show how people who like diversity tend to live in ethnically integrated neighborhoods with other people who like diversity as well.
+@van2019sociocultural use similarity for sociocultural dispositions (i.e.
+gender balance in household tenure) as predictor to leave the neighborhood, compared to ethnic membership and income similarity, with socio-cultural dispositions resulting the most influential.
+As people who like diversity can distinguish  ethnic diversity of neighborhood from the concentration of people who share the same tastes and show independent appreciation for both [@blokland2010people;@clark2018can], so people who prefer ethnically concentrated neighborhood can consider an additional value to live close to other ethnically conservative people.
+The overlap of these two preferences can have consequences on the different scenarios of segregation.
+Since we are focusing on a spatial sorting mechanism, relative group sizes remains a critical factor.
+@blau1977macrosociological defines relative group sizes as the structural conditions that can influence inter-ethnic relations, not matter what socio-psychological drivers guide such interactions.
+Minority groups are per definition more at risk of incorporation from the majority [@esser2010assimilation].
+Considering the overlap category between ethnicity and taste for ethnic diversity, the concept of relative group size becomes much complex.
+For instance, a person might belong to the ethnic minority group, but to the majority of tolerant people in the broad society.
+Different distributions of people along the categories of ethnic membership and preferences for diversity/homogeneity is noteworthy.
 
-NEW: the competing homophily preference based on the value-orientation
+Assuming the critical factors of heterogeneity towards ethnic preference, preference for people who share similar values or preferences and relative group sizes, the questions is opened on how they interact to shape hybrid scenarios of segregation for members of society.
+To this aim, we advocate the usage of social complexity and agent-based modelling.
+Differently from theories as spatial assimilation and place stratification centered on individual strategies of movers and stake holders, social complexity would focus on residential segregation as a complex and dynamic phenomenon that emerges from the interaction between residential movers and the constraints to their action [ @huang2014review; @schelling1971;@clark2015residential].
+The study of similar phenomena requires agent-based computer simulations where such interactions can be implemented and experimented on, to the aim of formalizing mechanisms underlying emergence of macro phenomena [@macy2002factors;@gilbert2005simulation].
+In particular, we build our work upon Schelling's model of residential segregation [@schelling1971;@schelling1969].
+Fitting the homophily hypothesis, Schelling described a scenario where people stay  in a neighborhood as long as the proportion between similar ones and others is not less than a desired threshold, leaving to a random relocation otherwise.
+Given the spatial constraints to relocate, e.g.
+unavailability of empty places due to density of population, the interplay of people pursuing the same behavior can cause high level of segregation even for low thresholds.
+The original Schelling's model has received interest from scholars outside of computational methods due to its contribution to understanding segregation dynamics [@clark1991residential;@clark2008understanding], as well as numerous extensions and studies by complexity scholars.
+We want to contribute to those studies focusing on random utility models for discrete choice in Schelling's dynamics and ethnically diverse scenarios.
+Simply stated, discrete choice models allow to deduce prerefernces in utility by observing the difference between neighoborhood chosen and alternative ones  [@train2009discrete;@frankhauser2016deciding].
+Among regression models for the execution of random utility models, @mcfadden1973conditional's conditional logit allow to estimate the parameters of utility for different characteristics of neighborhoods ($\beta$ parameters) and sort them according to socio-demographic characteristics of movers [@boschman2015neighbourhood].
+@zhang2004 was among the first to implement the conditional logit within Schelling's dynamics, although @bruch2006neighborhood moved forward by matching discrete choice of agents with parameters calculated from empirical data, along with a continuous linear function instead of Schelling's threshold.
+Despite pitfalls in the code implementation of their model [@van2009neighborhood] and consequent corrections [@bruch2009preferences], extensions resulted in agents being more sensitive to fine-grained change in neighborhood ethnic composition.
+Adopting a similar discrete choice method would benefit the chance of the model to disentangle the relative effect of different preferences.
+@xie2012modeling extended the model by @bruch2009preferences to reflect the heterogeneity in whites' tolerance towards blacks in US, both as categorical classes with different threshold preferences each, and continuous heterogenous preferences.
+In both cases heterogeneity between agents, and a class of agent indifferent to ethnic composition resulted in less segregated scenarios due to mutual adaptation of agents.
+Though not with discrete choice models,  @hatna2014combining focused on heterogenous preferences between groups, using an increasing linear function until the desired proportion, and dividing each ethnic group in two subgroups of agents more tolerant and less tolerant due to difference in ethnic threshold.
+The combination of a different utility function and heterogeneous preferences between groups for ethnic thresholds generated hybrid scenarios of integration and segregation.
+With a different focus of tolerance towards diversity, @paolillo2018 investigated the interaction of different homophily preferences in Schelling.
+Keeping threshold behavior as in the original model, they split the population into intolerant ethnic-oriented agents, defining similarity based on shared ethnicity, and tolerant value-oriented agents defining similarity on shared values for tolerance, and explored  their adaptation in different conditions of relative group sizes.
+The introduction of value-oriented agents decreased ethnic segregation compared to the original model.
+The main discover was a spillover effect for ethnicity-oriented agents in the minority condition who found attractive ethnically mixed neighborhoods formed by value-oriented agents, because of availability of ethnically similar ones, until the point that their concentration caused value-oriented to leave.
+It can be noteworthy to extend the intuition of @paolillo2018 for different homophily preferences to the scenarios of heterogeneity as presented by @xie2012modeling and  @hatna2014combining and within the framework of discrete choice and linear utility function as in @bruch2009preferences which is consistent with utility maximization.
 
-Lead Question (ex): \par
-* how can we explain hybrid ethnic segregation patterns (some members of the same ethnic group are ethnically integrated, others are ethnically segregated)? (The Economist) \par
-* how can we explain hybrid value segregation patterns (some members of the same ethnic group are ethnically integrated, others are ethnically segregated)? \par
-* what is the effect of value segregation on  ethnic segregation and vice versa? \par
-* Factors underlying the mechanism of interest:  \par
-- degree of parameter beta: how one dimension is important over the other in the relocation choice  \par
-- relative group size for both the ethnic and the value dimension, since they would have a direct effect on the utility of a location
-and on the number of agents defined as ethnicity-oriented and value-oriented
-- heterogeneity within same ethnic group and between ethnic groups
-* what is the role of heterogeneity in preferences within a group, and between groups? \par
-* hybrid segregation on value and ethnic for different types of people \par
-* What is the effect on such dynamics of relative group size \par
-
-Assumption: 
-* people differ in their degree of ethnic preferences (lit. @xie2012modeling, @hatna2015combining)
-* peole have different preferences and sort out of different factors [@bruch2009segregation]
-
-@xie2012modeling: use different threshold size according to class from Guttman, the 6th class not conforming to Guttman linear function and rum.
-Their concept of heterogeneity is on the different threshold levels (within 5 classes, with the 5th being tolerant to $57 \%$ to $100 \%$) black, so indifferent), with the consequence to decrease segregation.
-This trend holds also when continuous preferences are included, meaning cumulative threshold between agents.
-We would modify $\beta$, decomposing a random utility model, assuming the desired concentration peak 1 and varying $\beta$ \par
-
-In  the definition of competing preferences, stress that the value-orientation across ethnicity is defiant to Schelling's dichotomous definition of similarity (see @clark1991residential for a critical view)
-
-@clark1991residential old: for historical excursus
-@chen2005emergence: good perspective to position with value similarity (not in their paper). Update literature, consider heterogeneity within the same race
-
-We define the condition where people hold different ethnic and value preferences.
-We can impose at the individual level due by value-orientation that one group holds one preference higher than the other and that the degree of one preference is higher than the other one
-
-DOUBT: if an agent likes "diversity", then I would expect the peak to change, and it being at $50 \%$ for the ethnic dimension, so integrationist attitudes, and the peak of value concentration of these agents to change according  to the $100 \%$ similar others integrationists, but you are making a different reasoning, that people aim at ethnic diversity, and the dimension of ethnicity would be less/more important in the relocation choice
-
-The concept of heterogeneity is reflected into the experiments: \par
-* individual: $\beta^\Box_e \geq \beta^\Box_v$, $\beta^\circ_v \geq \beta^\circ_e$  \par
-* within ethnic group:  $\beta^\Box_e \geq \beta^\circ_e$, $\beta^\circ_v \geq \beta^\Box_v$, should specify the ethnic group  \par
-
-This does not prevent than between groups there might be difference in terms of ethnic preferences, and similarly on value preferences
-
-Define need of value similarity 
-Role of relative group size for both the ethnic and the value dimension
+In sum, in this paper we propose a Schelling-type agent-based model to identify possible mechanisms that can explain hybrid segregation in modern and diverse societies, i.e.
+the scenario where some members of the same ethnic group are ethnically integrated while others are ethnically segregated.
+We focus on a discrete choice model of homophily preferences for spatial sorting to explain such a scenario.
+We include similarity based on ethnic membership and on shared values towards ethnic diversity or ethnic conservatism.
+The expected advantage of this choice is on the consequences it can have on inner cohesion of groups together with the blurry of boundaries between groups.
+That is, we model scenarios where both intolerant ethnicity-oriented agents and tolerant value-oriented agents share ethnic preferences and value preferences at some degree.
+While ethnic preferences would consider as similar members of the same ethnic group despite their value-orientation, members of the same ethnic group with different values would be excluded from the value spatial sorting of agents, in favor of members of the out-group with similar values.
+We will impose as condition that ethnicity-oriented agents hold higher ethnic preferences than value preferences and vice versa for value-oriented agents.
+We include relative group sizes for both categories of agents as constraints to neighborhood composition and heterogeneity for both preferences within groups and between groups.
+Additionally, the case of a more conservative group over another can be included.
+The contributions of the paper are that, compared to previous studies that focused on heterogeneous preferences for ethnic composition [@xie2012modeling:@hatna2014combining], the interplay of ethnicity and values introduced by @paolillo2018 may shed deeper insights on the continuum between integration and segregation at the spatial scale.
+Moreover, not only hybrid segregation would be explored, but also the new form of value segregation and its relation to ethnic segregation, which might serve to describe the sorting of people in diverse societies.
+The application of random utility models might facilitate the match with quantitative estimate parameters of preferences.
 
@@
 
-The model^[The model can be found here:https://github.com/RoccoPaolillo/BIGSSS_ResearchDay.git] was built in NetLogo 6.1.0 and extends work by @paolillo2018.
+The model^[The model can be found here:https://github.com/RoccoPaolillo/ethnic-value_multinomial.git] was built in NetLogo 6.1.0 and extends work by @paolillo2018.
 Agents interact on a regular grid 51 times 51 with periodic boundary conditions (torus world).
@@
 
+\vspace{10pt}
+
+@hatna2014combining: in previous studies, they had a "F critical", maybe we could use on the critical $\beta$?
+
+\vspace{10pt}
+
 The concept of heterogeneity is reflected into the experiments: \par

### 2020-03-10 ethnic_value_rum.Rmd
update to 10.03.2020

@@
 
-* We aim at Journal of Mathematical Sociology
+* We aim at Journal of Mathematical Sociology:
+- models and mathematical techniques useful to professional sociologist, connection between disciplines
+- emergent complex social structures
+- editor -> single-blind peer reviews
+- 200 words abstract, 3-5 keywords
+- color figures and format OK, fee if color on printed
+- DOI dataset, e.g. Zenodo
+
+Read Laurie & Jaggi, 2003
+
+<!-- instructors: https://authorservices.taylorandfrancis.com/tf_quick_guide/ -->
 
@@
 Residential segregation can be defined as the unequal and non random distribution of people  belonging to different groups within the spatial units of a city [@bruch2009segregation;@clark2008understanding].
-Ethnicity has long been a main dimension of segregation, both as indicator of in-group/out-group relations and for its correlation with deprived neighborhoods [@VanHam2012].
-Nevertheless, in modern societies members of the same ethnic group can positionate differently on the continuum between integration and segregation, due to many reasons.
-In this paper we focus  on the possible mechanisms that underlying hybrid scenarios of residential segregation focusing on two factors, i.e.
-heterogeneity for ethnic preferences  within and between groups, and preferences for like-minded people who share the same conservative or integrationist attitudes.
-We advocate for usage of agent-based modeling and proceed by extending previous work on Schelling's model of residential segregation.
+It is a critical topic due to the consequences on interaction between groups [@bolt2010linking] and perpetuation of inequalities for people living in deprived neighborhoods [@van2012understanding].
+<!-- X segregation is complex process, traditionally Schelling etc has been used to understand the complex micro-macro interaction involved-->
+@haw2018dynamical: difference between organized segregation and self-organized segregation as Schelling.
+@schelling1971dynamic: different threshold level (on x-axys fig.
+8),not together,i.e.
+not heterogeneity, but never a function different than threshold and similarity twofold and binary.
+Many have focused on the different function, using a linear one, other on heterogeneity, we would blend this together.
+On the other side, linear function fully satisfy discrete choic methods that are central in segregation studies.
 
+Segregation is a complex process and researchers have long been interested in understanding the dynamics of segregation patterns.
+Two hystorical hypothesis are the spatial assimilation theory and the place stratification theory.
+According to the former, spatial distance reflects the social distance between groups, and can change as effect of social moblity (@coulter2019ethnic), while the latter focuses on the strategies of gatekeepers, e.g.
+sellers, to prevent undesired newcomers to neighborhood (@horr2018ethnic).
+Both have in common the assumption that residential  segregation is the intended result of individual behavior.
+A third perspective can be that of social complexity and Schelling's agent-based model of residential segregation, which addresses residential segregation as a stable property of the aggregated behavior of people who seek to satisfy even mild homophily preferences within spatial constraints [@schelling1969;@schelling1971;@schelling1978].
+The paper here presented follows this stream of literature and aims at contributing to Schelling's type dynamics.
+Although not in its original intention, ethnic composition has been widely considered as main dimension of segregation, both as indicator of in-group/out-group relations and for its correlation with deprived neighborhoods [@VanHam2012].
 A simple but long-standing mechanism used in literature to explain ethnic concentration is that of spatial sorting or homophily preferences [@magi2016types;@muller2018residential], i.e.
 the tendency to aggregate with people of the same ethnic group [@mcpherson2001birds] .
-Although ethnic segregation is still considered a relevant issue, especially for modern and diverse societies the simple ethnic homophily assumption might not be that influential, and it should be included within more complex dynamics [@alba2014twilight].
+
+<!-- X however, Schelling typically assume that people only care for ethnic composition -->
+
+Nevertheless, in modern societies members of the same ethnic group can positionate differently on the continuum between integration and segregation, due to many reasons, and ethnicity per se can be only one of the many dimensions people segregate along.
+
+<!--  In recent decades western societies have come increasingly ethnically diverse and especially second+ generation migrants have assimilated in some ways but still remain different.-->
+
+[@alba2014twilight].
 First of all, a growing concept in literature is that of superdiversity that characterizes western societies [@crul2016super], as effect of social mobility, inner-neighborhoods migration flows and multicultural households [@neal2013multiculture; @albeda2018symbolic].
-Out of many ethnic groups cohabiting in the same city, segregation might imply more than a binary definition between in-group/out-group and tolerance toward diversity become critical to social cohesion [@DragolovIgnaczea2016SocialCohesionin;@clark2018can; @vervoort2011ethnic].
-Furthermore, people belong to many and overlapping categories [@roccas2002social] that can prevail that of ethnicity in defining residential preferences as well as similarity in spatial sorting [@van2019sociocultural].
+
+Considering the context of multi-ethnic societies, difference between social groups are relevant.
+Some groups might be innerly more tolerant towards minorities, with consequences on inter-ethnic contacts [@bourhis1997towards] or they  might be likely to blur the boundaries towards specific groups as effect of their cultural similarities [@albeda2018symbolic].
+On the other side, tolerance towards ehtnic minorities  of citizens can result from the multicultural or assimilationist policies adopted by different governments [@weldon2006institutional].
+
 Indeed, literature is most unanimous that in the last decades socio-economic segregation has increased at faster rates than racial-ethnic segregation which is generally decreased [@clark2002residential;@clark2015residential].
+
+<!-- X Similarly some parts of the population have become more modern / cosmopolitation. -->
+
 Finally, people within the same ethnic group or social class can vary in their preferences, and differences in affordability give rise to more variegated scenarios  [@andersson2007mix].
@@
 
-In this paper, we focus on two concepts associated with ethnic segregation in diverse societies when considering relocation choice, i.e.
-heterogeneity in ethnic preferences, and preferences for other dimensions that can interact with ethnic membership.
-As for heterogeneity in preferences, it is intuitive that people of the same group might differ in their preferences [@hess2018revisiting], this can increase when other subdivisions as socio-economic class are taken into account [@bruch2014population;@friedman2019muslim].
-Considering the context of multi-ethnic societies, difference between social groups are relevant.
-Some groups might be innerly more tolerant towards minorities, with consequences on inter-ethnic contacts [@bourhis1997towards] or they  might be likely to blur the boundaries towards specific groups as effect of their cultural similarities [@albeda2018symbolic].
-On the other side, tolerance towards ehtnic minorities  of citizens can result from the multicultural or assimilationist policies adopted by different governments [@weldon2006institutional].
-As for different preferences that could interact with the dimension of ethnicity, the perspective of ethnic boundary making is relevant.
-This theoretical framework focuses on the dynamic and symbolic boundaries that distinguish between "us" and "them" [@bail2008configuration], built by individuals in the continuous and different forms of interaction between groups [@wimmer2013ethnic].
-The core of ethnic boundary making is to understand how boundaries between in-group and out-group are socially constructed above the categories of ethnic membership, and not as a rigid consequence of them [@esser2010assimilation; @wimmer2013ethnic].
+<!-- X There is evidence that people consider both types of similarity when assessing composition of prospective neighborhoods they want to live in, but also that people differ in the extent to which ethnic or value similarity matters to them.
+-->
+
+[@van2019sociocultural]
 Following this perspective, a taste for ethnic and cultural diversity can serve both to blur  ethnic boundaries and to define similarity with other people despite their ethnic membership.
@@
 As people who like diversity can distinguish  ethnic diversity of neighborhood from the concentration of people who share the same tastes and show independent appreciation for both [@blokland2010people;@clark2018can], so people who prefer ethnically concentrated neighborhood can consider an additional value to live close to other ethnically conservative people.
-The overlap of these two preferences can have consequences on the different scenarios of segregation.
-Since we are focusing on a spatial sorting mechanism, relative group sizes remains a critical factor.
-@blau1977macrosociological defines relative group sizes as the structural conditions that can influence inter-ethnic relations, not matter what socio-psychological drivers guide such interactions.
-Minority groups are per definition more at risk of incorporation from the majority [@esser2010assimilation].
-Considering the overlap category between ethnicity and taste for ethnic diversity, the concept of relative group size becomes much complex.
-For instance, a person might belong to the ethnic minority group, but to the majority of tolerant people in the broad society.
-Different distributions of people along the categories of ethnic membership and preferences for diversity/homogeneity is noteworthy.
 
-Assuming the critical factors of heterogeneity towards ethnic preference, preference for people who share similar values or preferences and relative group sizes, the questions is opened on how they interact to shape hybrid scenarios of segregation for members of society.
-To this aim, we advocate the usage of social complexity and agent-based modelling.
-Differently from theories as spatial assimilation and place stratification centered on individual strategies of movers and stake holders, social complexity would focus on residential segregation as a complex and dynamic phenomenon that emerges from the interaction between residential movers and the constraints to their action [ @huang2014review; @schelling1971;@clark2015residential].
-The study of similar phenomena requires agent-based computer simulations where such interactions can be implemented and experimented on, to the aim of formalizing mechanisms underlying emergence of macro phenomena [@macy2002factors;@gilbert2005simulation].
-In particular, we build our work upon Schelling's model of residential segregation [@schelling1971;@schelling1969].
-Fitting the homophily hypothesis, Schelling described a scenario where people stay  in a neighborhood as long as the proportion between similar ones and others is not less than a desired threshold, leaving to a random relocation otherwise.
+<!-- X -> this multidimensional homophily (Blok et al) has only rarely been considered in complexity models of segregation dynamics (few exceptions).
+We add to this line of research by proposing a new model that allows to assess how residential segregation patterns depend on the mix of preferences in a heterogeneous population.
+Unlike earlier models, we assume that everyone prefers both ethnic and value similarity, but different social groups in the population put different weight on each of the aspects of similarity.
+(in line with survey evidence?) -->
+
+-> we study in this paper what are the consequences of this new form of preference heterogeneity in abm of residential segregation dynamics 
+-> whether and under which conditions it can explain the empirical pattern of hybrid residential segregation ..
+
+<!-- goog point -->>
+ It can be noteworthy to extend the intuition of @paolillo2018 for different homophily preferences to the scenarios of heterogeneity as presented by @xie2012modeling and  @hatna2014combining and within the framework of discrete choice and linear utility function as in @bruch2009preferences which is consistent with utility maximization.
+
+<!-- goog point, empirical substain (last paragraph) -->>
+In sum, in this paper we propose a Schelling-type agent-based model to identify possible mechanisms that can explain hybrid segregation in modern and diverse societies, i.e.
+the scenario where some members of the same ethnic group are ethnically integrated while others are ethnically segregated.
+We focus on a discrete choice model of homophily preferences for spatial sorting to explain such a scenario.
+We include similarity based on ethnic membership and on shared values towards ethnic diversity or ethnic conservatism.
+
+<!-- In this paper we focus  on the possible mechanisms that underlying hybrid scenarios of residential segregation focusing on two factors, i.e.
+heterogeneity for ethnic preferences  within and between groups, and preferences for like-minded people who share the same conservative or integrationist attitudes.
+We advocate for usage of agent-based modeling and proceed by extending previous work on Schelling's model of residential segregation.-->
+
+<!-- Residential segregation can be defined as the unequal and non random distribution of people  belonging to different groups within the spatial units of a city [@bruch2009segregation;@clark2008understanding].
+The interest of the social sciences on the topic is due the consequences it can have on the chance of interaction and integration between groups [@bolt2010linking], with exclusion of minorities in deprived neighborhoods and perpetuation of inequalities through generations [@van2012understanding].
+A key research question in literature is on the dynamics of emergence of residential segregation.
+-->
+
+With a different focus of tolerance towards diversity, @paolillo2018 investigated the interaction of different homophily preferences in Schelling.
+Keeping threshold behavior as in the original model, they split the population into intolerant ethnic-oriented agents, defining similarity based on shared ethnicity, and tolerant value-oriented agents defining similarity on shared values for tolerance, and explored  their adaptation in different conditions of relative group sizes.
+The introduction of value-oriented agents decreased ethnic segregation compared to the original model.
+The main discover was a spillover effect for ethnicity-oriented agents in the minority condition who found attractive ethnically mixed neighborhoods formed by value-oriented agents, because of availability of ethnically similar ones, until the point that their concentration caused value-oriented to leave.
+
+<!-- The expected advantage of this choice is on the consequences it can have on inner cohesion of groups together with the blurry of boundaries between groups.
+That is, we model scenarios where both intolerant ethnicity-oriented agents and tolerant value-oriented agents share ethnic preferences and value preferences at some degree.
+While ethnic preferences would consider as similar members of the same ethnic group despite their value-orientation, members of the same ethnic group with different values would be excluded from the value spatial sorting of agents, in favor of members of the out-group with similar values.
+We will impose as condition that ethnicity-oriented agents hold higher ethnic preferences than value preferences and vice versa for value-oriented agents.
+We include relative group sizes for both categories of agents as constraints to neighborhood composition and heterogeneity for both preferences within groups and between groups.
+Additionally, the case of a more conservative group over another can be included.
+The contributions of the paper are that, compared to previous studies that focused on heterogeneous preferences for ethnic composition [@xie2012modeling:@hatna2014combining], the interplay of ethnicity and values introduced by @paolillo2018 may shed deeper insights on the continuum between integration and segregation at the spatial scale.
+Moreover, not only hybrid segregation would be explored, but also the new form of value segregation and its relation to ethnic segregation, which might serve to describe the sorting of people in diverse societies.
+The application of random utility models might facilitate the match with quantitative estimate parameters of preferences.-->
+
+<!-- NO Out of many ethnic groups cohabiting in the same city, segregation might imply more than a binary definition between in-group/out-group and tolerance toward diversity become critical to social cohesion [@DragolovIgnaczea2016SocialCohesionin;@clark2018can; @vervoort2011ethnic].
+Furthermore, people belong to many and overlapping categories [@roccas2002social] that can prevail that of ethnicity in defining residential preferences as well as similarity in spatial sorting [@van2019sociocultural].
+-->
+
+<!-- NO In this paper, we focus on two concepts associated with ethnic segregation in diverse societies when considering relocation choice, i.e.
+heterogeneity in ethnic preferences, and preferences for other dimensions that can interact with ethnic membership.
+As for heterogeneity in preferences, it is intuitive that people of the same group might differ in their preferences [@hess2018revisiting], this can increase when other subdivisions as socio-economic class are taken into account [@bruch2014population;@friedman2019muslim].
+As for different preferences that could interact with the dimension of ethnicity, the perspective of ethnic boundary making is relevant.
+This theoretical framework focuses on the dynamic and symbolic boundaries that distinguish between "us" and "them" [@bail2008configuration], built by individuals in the continuous and different forms of interaction between groups [@wimmer2013ethnic].
+The core of ethnic boundary making is to understand how boundaries between in-group and out-group are socially constructed above the categories of ethnic membership, and not as a rigid consequence of them [@esser2010assimilation; @wimmer2013ethnic].
+The overlap of these two preferences can have consequences on the different scenarios of segregation.-->
+
+# Theory: Modeling Discrete Choice in Schelling Framework
+
+Fitting the homophily hypothesis, Schelling described a scenario where people stay  in a neighborhood as long as the proportion between similar ones and others is not less than a desired threshold, leaving to a random relocation otherwise  [@schelling1971;@schelling1969].
 Given the spatial constraints to relocate, e.g.
@@
 The original Schelling's model has received interest from scholars outside of computational methods due to its contribution to understanding segregation dynamics [@clark1991residential;@clark2008understanding], as well as numerous extensions and studies by complexity scholars.
+
+- utility function
+- heterogeneity
+- different preferences
+
 We want to contribute to those studies focusing on random utility models for discrete choice in Schelling's dynamics and ethnically diverse scenarios.
@@
 Though not with discrete choice models,  @hatna2014combining focused on heterogenous preferences between groups, using an increasing linear function until the desired proportion, and dividing each ethnic group in two subgroups of agents more tolerant and less tolerant due to difference in ethnic threshold.
-The combination of a different utility function and heterogeneous preferences between groups for ethnic thresholds generated hybrid scenarios of integration and segregation.
-With a different focus of tolerance towards diversity, @paolillo2018 investigated the interaction of different homophily preferences in Schelling.
-Keeping threshold behavior as in the original model, they split the population into intolerant ethnic-oriented agents, defining similarity based on shared ethnicity, and tolerant value-oriented agents defining similarity on shared values for tolerance, and explored  their adaptation in different conditions of relative group sizes.
-The introduction of value-oriented agents decreased ethnic segregation compared to the original model.
-The main discover was a spillover effect for ethnicity-oriented agents in the minority condition who found attractive ethnically mixed neighborhoods formed by value-oriented agents, because of availability of ethnically similar ones, until the point that their concentration caused value-oriented to leave.
-It can be noteworthy to extend the intuition of @paolillo2018 for different homophily preferences to the scenarios of heterogeneity as presented by @xie2012modeling and  @hatna2014combining and within the framework of discrete choice and linear utility function as in @bruch2009preferences which is consistent with utility maximization.
 
-In sum, in this paper we propose a Schelling-type agent-based model to identify possible mechanisms that can explain hybrid segregation in modern and diverse societies, i.e.
-the scenario where some members of the same ethnic group are ethnically integrated while others are ethnically segregated.
-We focus on a discrete choice model of homophily preferences for spatial sorting to explain such a scenario.
-We include similarity based on ethnic membership and on shared values towards ethnic diversity or ethnic conservatism.
-The expected advantage of this choice is on the consequences it can have on inner cohesion of groups together with the blurry of boundaries between groups.
-That is, we model scenarios where both intolerant ethnicity-oriented agents and tolerant value-oriented agents share ethnic preferences and value preferences at some degree.
-While ethnic preferences would consider as similar members of the same ethnic group despite their value-orientation, members of the same ethnic group with different values would be excluded from the value spatial sorting of agents, in favor of members of the out-group with similar values.
-We will impose as condition that ethnicity-oriented agents hold higher ethnic preferences than value preferences and vice versa for value-oriented agents.
-We include relative group sizes for both categories of agents as constraints to neighborhood composition and heterogeneity for both preferences within groups and between groups.
-Additionally, the case of a more conservative group over another can be included.
-The contributions of the paper are that, compared to previous studies that focused on heterogeneous preferences for ethnic composition [@xie2012modeling:@hatna2014combining], the interplay of ethnicity and values introduced by @paolillo2018 may shed deeper insights on the continuum between integration and segregation at the spatial scale.
-Moreover, not only hybrid segregation would be explored, but also the new form of value segregation and its relation to ethnic segregation, which might serve to describe the sorting of people in diverse societies.
-The application of random utility models might facilitate the match with quantitative estimate parameters of preferences.
+Since we are focusing on a spatial sorting mechanism, relative group sizes remains a critical factor.
+@blau1977macrosociological defines relative group sizes as the structural conditions that can influence inter-ethnic relations, not matter what socio-psychological drivers guide such interactions.
+Minority groups are per definition more at risk of incorporation from the majority [@esser2010assimilation].
+Considering the overlap category between ethnicity and taste for ethnic diversity, the concept of relative group size becomes much complex.
+For instance, a person might belong to the ethnic minority group, but to the majority of tolerant people in the broad society.
+Different distributions of people along the categories of ethnic membership and preferences for diversity/homogeneity is noteworthy.
 
+<!--
 ```{r model, fig.pos ='h!',out.width='50%',out.height='90%',fig.show='hold',fig.align='center', fig.cap= "Draft of agents attribution and emerging segregations, to revise.",  echo = FALSE, include=TRUE}
@@
 ```
+-->
 

### 2020-04-27 ethnic_value_rum.Rmd
old

--- 2020-02-13 ethnic_value_rum.Rmd
@@
 date:  "`r  as.Date(Sys.time(), '%d %B %Y')`"
+output:
+  word_document:
+   # keep_tex: true
+
 # "`r  as.Date(Sys.time(), '%d %B %Y')`"
-language: en-GB
+#language: en-GB
 bibliography: "references.bib"
-always_allow_html: yes
-output: pdf_document
-    # toc: false
- #   keep_tex: false
+# always_allow_html: yes
 #fig_caption: yes
@@
 
+ nrml <- function(mx,mn,x,s){
+
+  s <- ((x - mn) / (mx-mn))
+}
+
+ bt_10 <- for (x in seq(5,10,by=1)) {
+
+  mx <- 10
+  mn <- 5
+
+  s <- nrml(mx,mn,x,s)
+  print(c(x,s))
+
+}
+
+ bt_5 <- for (x in seq(0,5,by=1)) {
+
+  mx <- 5
+  mn <- 0
+
+  s <- nrml(mx,mn,x,s)
+  print(c(x,s))
+
+}
+
  # install.packages("tinytex", repos = "https://cloud.r-project.org" ) #, try if debug needed
@@
 \newcommand{\rocco}[1]{\textcolor{red}{{Rocco:}#1}} 
+<!-- Read Laurie & Jaggi, 2003 -->
 
@@
 
-# NOTES FOR March 5, to shuffle focusing on Schelling and from ethnicity to value/cosmopolitan
-
-* TO READ: D. J. Haw & S. J. Hogan (2020) A dynamical systems model of unorganized segregation in two neighborhoods, The Journal of Mathematical Sociology, DOI: 10.1080/0022250X.2019.1695608
-
-* We aim at Journal of Mathematical Sociology
-
 # Introduction {-}
 
+<!-- X segregation is complex process, traditionally Schelling etc has been used to understand the complex micro-macro interaction involved-->
+<!-- X however, Schelling typically assume that people only care for ethnic composition -->
 Residential segregation can be defined as the unequal and non random distribution of people  belonging to different groups within the spatial units of a city [@bruch2009segregation;@clark2008understanding].
-Ethnicity has long been a main dimension of segregation, both as indicator of in-group/out-group relations and for its correlation with deprived neighborhoods [@VanHam2012].
-Nevertheless, in modern societies members of the same ethnic group can positionate differently on the continuum between integration and segregation, due to many reasons.
-In this paper we focus  on the possible mechanisms that underlying hybrid scenarios of residential segregation focusing on two factors, i.e.
-heterogeneity for ethnic preferences  within and between groups, and preferences for like-minded people who share the same conservative or integrationist attitudes.
-We advocate for usage of agent-based modeling and proceed by extending previous work on Schelling's model of residential segregation.
+Researhers are interested in the dynamics of this complex process and several theories have been elaborated.
+\rocco{maybe here to supersynthetize and explain in detail in theory/modeling section} In a couple of influential papers, @schelling1969models [-@schelling1971dynamic] proposed an alternative explanation to racial discrimination as cause of residential segregation.
+His intention was to demonstrate how segregation can be an emergent property of the "interplay of individual choices" [@schelling1969models, p.
+488] of people within the spatial constraints of a city.
+He proposed a model of individual behavior and preferences for neighborhood composition based on a threshold behavior: people would stay in a neighborhood as long as the ratio of the members of the other group to the members of the own group does not exceed a desired threshold.
+For instance, a threshold $\theta =0.50$ would mean that the in-group should not be in a condition of minority, a threshold of $\theta = 0.40$ would mean people would be happy until the minority does not exceed the $40 \%$ of neighborhood composition.
+Individual relocations of people trying to satisfy such preferences within the spatial constraints of a city would generate stable spatial combination that define residential segregation.
+The complexity of Schelling model is that this simple behavior can generate high level of segregation even for mild preferences for similar ones.
+Schelling so proposed a model of unorganized segregation [@haw2018dynamical], meaning that residential segregation would self-organize from the interplay of individual moves of citizens, and as a matter of fact, one of the first agent-based models [@epstein1996growing].
+One condition that Schelling imposed to his reasoning was that similarity was defined as a "twofold, exhaustive and recognizable distinction" [@schelling1969models, p.
+488].
+Although not in his original intentions, this specification has caused many to interpret only ethnic segregation as dimension relevant to neighborhood preferences and spatial dynamics.
+Nevertheless, the model found wide application in understanding the complexity of residential segregation, not only in the field of complex systems, but also in empirical studies of spatial sorting [@magi2016types;@muller2018residential].
+In detail, the focus on ethnic membership let Schelling model found an easy application to the hypothesis of homophily behavior, i.e.
+the tendency to aggregate and show a preference for those considered as similar, in this case based on the shared ascribed status of ethnic membership [@mcpherson2001birds].
+However, only considering the dimension of ethnic similarity in Schelling dynamics might hinder its application to modern and diverse societies and contribution.
+Current trends in integration literature stress out how ethnicity is experiencing a constant decline [@alba2014twilight] as only dimension able to explain the integration processes and social composition of Western societies.
+As for residential segregation, there is quite unanimous agreement that despite ethnic segregation persists, it is generally decreased compared to levels in the 1970's in Europe and U.S.
+compared to otherd dimensions such as socio-economic segregation [@clark2015residential].
+Members of the same ethnic group differing for other socio-demographic characteristics can experience different degree of segregation not only along ethnicity, and due to increased heteorogeneity of preferences and different access to resources [@clark2002residential].
+In this paper we refer to this as "hybrid segregation" and we want to extend Schelling model to explain such a scenario.
+ \vspace{10pt}
+Literature provides different inputs to the causes of hybrid scenarios of segregation for members of the same ethnic group in modern and diverse societies.
+First of all, a common trait of Western societies is that of super-diversity.
+Originally formulated by @vertovec2007super in the UK context, the term now describes the complexity of most of Western receiving countries as effect of second and further generations of migrants, as well as ease of new migration flows from different parts of the world.
+As a consequence, much more than two ethnic groups will cohabit and influence the chances to segregate, along with change in the population due to new generations.
+A commonn trait of modern societies as  effect of mixed marriage is the rise of mixed households @ellis2012agents, plus the occurrence that the size of migrant population through generations equal the local populatin.
+The result is that the receiving context of new generations of migrants will not be a homogeneous ethnic majority, but an "amalgam" of ehtnic groups, in addition to different cohorts and social classes [@crul2016super, p.57].
+Second, new generations can differ from previous ones in terms of residential preferences and resources to relocate.
+Although inequalities can depend on the degree of integration of parents, e.g.
+neighborhood where children live and capital to their social mobility [@Esser2010assimilation], societies who have long experienced migration became more resilient in adopting strategies to guarantee equal education [@crul2016super].
+The result is that new generations are likely to reach higher level of educational attainment and professional success than their parents [@crul2017upcoming], so to have higher resources to relocate to more affluent neighborhoods and possibly different tastes.
+The consequence is that more evident differences in integration can occurr between cohorts of the same ethnic group rather than between ethnic groups, and in any case related to unequal access to resources to relocate [@crul2016super].
+The differences in income can explain the different degree of integration for members of the same group: while well-off generations move to more affluent and more integrated neighborhoods, low-income members of the same ethnic group experience hyper-segregation in deprived neighborhoods @clark2002residential.
+Finally, the concept of super-diversity stresses out how people in diverse societies can differ and find similarities along many dimensions that add to ethnic membership, such as social class, cultural practices etc.
+In this multitude of definitions of the self and groups, people are more likely to use individual characteristics to navigate diversity and define similarity and inclusion, rather than a rigid division in ethnic categorizations [@crul2016super].
+Ethnic boundaries become fluid and socially constructed, so that other criteria than ethnicity can mark the limit of in-group and out-group inclusion [@albeda2018symbolic].
+Shared values, defined as common beliefs, preferences or expectations on acceptable behavior can become one of this criteria for the definition of acceptance and inclusion across the boundaries of ethnic membership [@wimmer2013ethnic].
+This last point becomes critical to define how spatial sorting based on homophily behavior would work in diverse societies to explain scenarios of hybrid segregation.
+A growing number of studies confirm that people consider different dimensions of neighborhood composition, such as ethnic similarity and shared values, though each dimension can matter differently depending on individual characteristics.
+For instance, @van2019sociocultural use similarity for sociocultural dispositions (i.e.
+gender balance in household tenure) as predictor to leave the neighborhood, compared to ethnic membership and income similarity, with socio-cultural dispositions resulting the most influential.
+@blokland2010people, using survey methodology in The Netherlands, show how people who are attracted  by diversity in neighborhood selection tend to live close to other people who like diversity as well.
+@clark2018can estimate with census-track the preferences of mixed-race young generation in Los Angeles, who prefer ethnically integrated and well-off neighborhood.
 
-A simple but long-standing mechanism used in literature to explain ethnic concentration is that of spatial sorting or homophily preferences [@magi2016types;@muller2018residential], i.e.
-the tendency to aggregate with people of the same ethnic group [@mcpherson2001birds] .
-Although ethnic segregation is still considered a relevant issue, especially for modern and diverse societies the simple ethnic homophily assumption might not be that influential, and it should be included within more complex dynamics [@alba2014twilight].
-First of all, a growing concept in literature is that of superdiversity that characterizes western societies [@crul2016super], as effect of social mobility, inner-neighborhoods migration flows and multicultural households [@neal2013multiculture; @albeda2018symbolic].
-Out of many ethnic groups cohabiting in the same city, segregation might imply more than a binary definition between in-group/out-group and tolerance toward diversity become critical to social cohesion [@DragolovIgnaczea2016SocialCohesionin;@clark2018can; @vervoort2011ethnic].
-Furthermore, people belong to many and overlapping categories [@roccas2002social] that can prevail that of ethnicity in defining residential preferences as well as similarity in spatial sorting [@van2019sociocultural].
-Indeed, literature is most unanimous that in the last decades socio-economic segregation has increased at faster rates than racial-ethnic segregation which is generally decreased [@clark2002residential;@clark2015residential].
-Finally, people within the same ethnic group or social class can vary in their preferences, and differences in affordability give rise to more variegated scenarios  [@andersson2007mix].
-In sum, in super-diverse societies ethnic segregation has become a hybrid and complex phenomenon, where ethnicity correlates with other dimensions and people of the same ethnic membership can experience different degree of segregation/integration.
+ \vspace{10pt}
+In sum, there is evidence that homophily behavior in spatial sorting in modern and diverse societies spans along different dimensions.
+Among these, the interplay of value similarity and ethnic similarity can intuitevely be useful in describing hybrid segregation of members of the same group.
+Although such complexity is addressed in empirical studies of segregation, it has been rarely considered in complexity models of segregation stemming from Schelling.
+We want to add to this line of research by proposing a model where agents assess neighborhood composition both for value and ethnic similarity in their relocation choice, and focusing on heterogeneous preferences for the two dimensions to explain hybrid segregation.
+To this aim, we collect from recent models that have  implemented discrete choice in Schelling dynamics along with heterogeneous preferences.
+\rocco{should the next part going into theory/modeling section?} Studies as  @bruch2009preferences  have tested the consequences of implementing not random relocation, but a discrete choice, implementing a different utility function than threshold.
+@xie2012modeling extended the updated model by @bruch2009preferences for discrete choice to reflect the heterogeneity in whites' tolerance towards blacks in U.S., both as categorical classes with different threshold preferences each, and continuous heterogenous preferences.
+In both cases heterogeneity between agents, and a class of agent indifferent to ethnic composition resulted in less segregated scenarios due to mutual adaptation of agents.
+Similarly, @haw2020dynamical conclude that integration can  be reached by structural conditions of small minority and large tolerant majority, and letting tolerance in each neighborhood increase linearly as function of the proportion of other race under the desired threshold.
+Though not with discrete choice models,  @hatna2014combining focused on heterogenous preferences between groups, using an increasing linear function until the desired proportion, and dividing each ethnic group in two subgroups of agents more tolerant and less tolerant due to difference in ethnic threshold.
+The results showed mixed patterns of integration and segregation rather than a dycothomous scenario.
+@paolillo2018 address specifically the interaction of different homophily preferences in Schelling.
+Keeping threshold behavior as in the original model, they split the population into intolerant ethnic-oriented agents, defining similarity based on shared ethnicity, and tolerant value-oriented agents defining similarity on shared values for tolerance towards diversity, and explored  their adaptation in different conditions of relative group sizes.
+The intention of the authors was to introduce value similarity as a cross-ethnic category, investingating under what conditions this would have fostered or hindered ethnic spatial sorting.
+The introduction of value-oriented agents decreased ethnic segregation compared to the original model.
+The main discover was a spillover effect for ethnicity-oriented agents in the minority condition who found attractive ethnically mixed neighborhoods formed by value-oriented agents, because of availability of ethnically similar ones, until the point that their concentration caused value-oriented to leave.
 
-In this paper, we focus on two concepts associated with ethnic segregation in diverse societies when considering relocation choice, i.e.
-heterogeneity in ethnic preferences, and preferences for other dimensions that can interact with ethnic membership.
-As for heterogeneity in preferences, it is intuitive that people of the same group might differ in their preferences [@hess2018revisiting], this can increase when other subdivisions as socio-economic class are taken into account [@bruch2014population;@friedman2019muslim].
-Considering the context of multi-ethnic societies, difference between social groups are relevant.
-Some groups might be innerly more tolerant towards minorities, with consequences on inter-ethnic contacts [@bourhis1997towards] or they  might be likely to blur the boundaries towards specific groups as effect of their cultural similarities [@albeda2018symbolic].
-On the other side, tolerance towards ehtnic minorities  of citizens can result from the multicultural or assimilationist policies adopted by different governments [@weldon2006institutional].
-As for different preferences that could interact with the dimension of ethnicity, the perspective of ethnic boundary making is relevant.
-This theoretical framework focuses on the dynamic and symbolic boundaries that distinguish between "us" and "them" [@bail2008configuration], built by individuals in the continuous and different forms of interaction between groups [@wimmer2013ethnic].
-The core of ethnic boundary making is to understand how boundaries between in-group and out-group are socially constructed above the categories of ethnic membership, and not as a rigid consequence of them [@esser2010assimilation; @wimmer2013ethnic].
-Following this perspective, a taste for ethnic and cultural diversity can serve both to blur  ethnic boundaries and to define similarity with other people despite their ethnic membership.
-@blokland2010people show how people who like diversity tend to live in ethnically integrated neighborhoods with other people who like diversity as well.
-@van2019sociocultural use similarity for sociocultural dispositions (i.e.
-gender balance in household tenure) as predictor to leave the neighborhood, compared to ethnic membership and income similarity, with socio-cultural dispositions resulting the most influential.
-As people who like diversity can distinguish  ethnic diversity of neighborhood from the concentration of people who share the same tastes and show independent appreciation for both [@blokland2010people;@clark2018can], so people who prefer ethnically concentrated neighborhood can consider an additional value to live close to other ethnically conservative people.
-The overlap of these two preferences can have consequences on the different scenarios of segregation.
-Since we are focusing on a spatial sorting mechanism, relative group sizes remains a critical factor.
-@blau1977macrosociological defines relative group sizes as the structural conditions that can influence inter-ethnic relations, not matter what socio-psychological drivers guide such interactions.
-Minority groups are per definition more at risk of incorporation from the majority [@esser2010assimilation].
-Considering the overlap category between ethnicity and taste for ethnic diversity, the concept of relative group size becomes much complex.
-For instance, a person might belong to the ethnic minority group, but to the majority of tolerant people in the broad society.
-Different distributions of people along the categories of ethnic membership and preferences for diversity/homogeneity is noteworthy.
+In the next section, we extend the intuition of @paolillo2018 for different homophily dimensions to heterogeneous preferences as @xie2012modeling and @hatna2014combining within the framework of discrete choice, which allows us to calibrate the weight of value or ethnic similarity in the relocation choice for different types of agents.
 
-Assuming the critical factors of heterogeneity towards ethnic preference, preference for people who share similar values or preferences and relative group sizes, the questions is opened on how they interact to shape hybrid scenarios of segregation for members of society.
-To this aim, we advocate the usage of social complexity and agent-based modelling.
-Differently from theories as spatial assimilation and place stratification centered on individual strategies of movers and stake holders, social complexity would focus on residential segregation as a complex and dynamic phenomenon that emerges from the interaction between residential movers and the constraints to their action [ @huang2014review; @schelling1971;@clark2015residential].
-The study of similar phenomena requires agent-based computer simulations where such interactions can be implemented and experimented on, to the aim of formalizing mechanisms underlying emergence of macro phenomena [@macy2002factors;@gilbert2005simulation].
-In particular, we build our work upon Schelling's model of residential segregation [@schelling1971;@schelling1969].
-Fitting the homophily hypothesis, Schelling described a scenario where people stay  in a neighborhood as long as the proportion between similar ones and others is not less than a desired threshold, leaving to a random relocation otherwise.
-Given the spatial constraints to relocate, e.g.
-unavailability of empty places due to density of population, the interplay of people pursuing the same behavior can cause high level of segregation even for low thresholds.
-The original Schelling's model has received interest from scholars outside of computational methods due to its contribution to understanding segregation dynamics [@clark1991residential;@clark2008understanding], as well as numerous extensions and studies by complexity scholars.
+# Theory: Modeling Discrete Choice in Schelling Framework
+
+Schelling described preferences for neighborhood composition and tolerance to the presence of outgroups as a threshold behavior representing the desired ratio between similar ones and not.
+For instance, a threshold $\theta =0.50$ would mean that the in-group should not be in a condition of minority, a threshold of $\theta = 0.40$ would mean people would be happy until the minority does not exceed the $40 \%$ of neighborhood composition.
+The space below such threshold $\theta$ constitutes the tolerance schedule of how many members of the other group would be tolerated until a person would randomly relocate to another neighborhood.
+Given the spatial constraints of  a city, only a few conditions might satisfy  most of the population, which become points of convergence [@schelling1971dynamic;@haw2020dynamical] and lead to stable equilibria in residential segregation.
+The key point of Schelling complexity is that even mild preferences expressed by low threshold would bring to high levels of residential segregation.
+Schelling proved his mathematical models through  graphical models of spatial proximity on a one-dimension linear distribution of agents [@schelling1971dynamic, p.
+149], referred to as "dots and stars model" and on a bi-dimensional area distribution  [@schelling1971dynamic, p.
+154] which is commonly know as "bounded neighborhood model" [@hatna2012schelling,@haw2018dynamical], which has become the common and most studied version of Schelling model in lattice models.
+\par
+From here, extensions to discrete choice and random utility models. Describing regression model and mathematical formulations of what we need to model: \par
+\par
+- utility function\par
+- heterogeneity\par
+- different preferences\par
+- relative group size -> probability of interaction\par
+
+A brief description of model to summarize\par
+Selection of cases to show interesting results of mixed segregation
+
+Here discrete choice, to formulate more mathematically and use their explanation to describe the model \par
+
 We want to contribute to those studies focusing on random utility models for discrete choice in Schelling's dynamics and ethnically diverse scenarios.
@@
 Adopting a similar discrete choice method would benefit the chance of the model to disentangle the relative effect of different preferences.
-@xie2012modeling extended the model by @bruch2009preferences to reflect the heterogeneity in whites' tolerance towards blacks in US, both as categorical classes with different threshold preferences each, and continuous heterogenous preferences.
-In both cases heterogeneity between agents, and a class of agent indifferent to ethnic composition resulted in less segregated scenarios due to mutual adaptation of agents.
-Though not with discrete choice models,  @hatna2014combining focused on heterogenous preferences between groups, using an increasing linear function until the desired proportion, and dividing each ethnic group in two subgroups of agents more tolerant and less tolerant due to difference in ethnic threshold.
-The combination of a different utility function and heterogeneous preferences between groups for ethnic thresholds generated hybrid scenarios of integration and segregation.
-With a different focus of tolerance towards diversity, @paolillo2018 investigated the interaction of different homophily preferences in Schelling.
-Keeping threshold behavior as in the original model, they split the population into intolerant ethnic-oriented agents, defining similarity based on shared ethnicity, and tolerant value-oriented agents defining similarity on shared values for tolerance, and explored  their adaptation in different conditions of relative group sizes.
-The introduction of value-oriented agents decreased ethnic segregation compared to the original model.
-The main discover was a spillover effect for ethnicity-oriented agents in the minority condition who found attractive ethnically mixed neighborhoods formed by value-oriented agents, because of availability of ethnically similar ones, until the point that their concentration caused value-oriented to leave.
-It can be noteworthy to extend the intuition of @paolillo2018 for different homophily preferences to the scenarios of heterogeneity as presented by @xie2012modeling and  @hatna2014combining and within the framework of discrete choice and linear utility function as in @bruch2009preferences which is consistent with utility maximization.
 
-In sum, in this paper we propose a Schelling-type agent-based model to identify possible mechanisms that can explain hybrid segregation in modern and diverse societies, i.e.
-the scenario where some members of the same ethnic group are ethnically integrated while others are ethnically segregated.
-We focus on a discrete choice model of homophily preferences for spatial sorting to explain such a scenario.
-We include similarity based on ethnic membership and on shared values towards ethnic diversity or ethnic conservatism.
-The expected advantage of this choice is on the consequences it can have on inner cohesion of groups together with the blurry of boundaries between groups.
-That is, we model scenarios where both intolerant ethnicity-oriented agents and tolerant value-oriented agents share ethnic preferences and value preferences at some degree.
-While ethnic preferences would consider as similar members of the same ethnic group despite their value-orientation, members of the same ethnic group with different values would be excluded from the value spatial sorting of agents, in favor of members of the out-group with similar values.
-We will impose as condition that ethnicity-oriented agents hold higher ethnic preferences than value preferences and vice versa for value-oriented agents.
-We include relative group sizes for both categories of agents as constraints to neighborhood composition and heterogeneity for both preferences within groups and between groups.
-Additionally, the case of a more conservative group over another can be included.
-The contributions of the paper are that, compared to previous studies that focused on heterogeneous preferences for ethnic composition [@xie2012modeling:@hatna2014combining], the interplay of ethnicity and values introduced by @paolillo2018 may shed deeper insights on the continuum between integration and segregation at the spatial scale.
-Moreover, not only hybrid segregation would be explored, but also the new form of value segregation and its relation to ethnic segregation, which might serve to describe the sorting of people in diverse societies.
-The application of random utility models might facilitate the match with quantitative estimate parameters of preferences.
+Since we are focusing on a spatial sorting mechanism, relative group sizes remains a critical factor.
+@blau1977macrosociological defines relative group sizes as the structural conditions that can influence inter-ethnic relations, not matter what socio-psychological drivers guide such interactions.
+Minority groups are per definition more at risk of incorporation from the majority [@Esser2010assimilation].
+Considering the overlap category between ethnicity and taste for ethnic diversity, the concept of relative group size becomes much complex.
+For instance, a person might belong to the ethnic minority group, but to the majority of tolerant people in the broad society.
+Different distributions of people along the categories of ethnic membership and preferences for diversity/homogeneity is noteworthy.
 
-```{r model, fig.pos ='h!',out.width='50%',out.height='90%',fig.show='hold',fig.align='center', fig.cap= "Draft of agents attribution and emerging segregations, to revise.",  echo = FALSE, include=TRUE}
-knitr::include_graphics("C:/Users/rocpa/OneDrive/Desktop/AF/ethnic-value_multinomial/material/model_pr.jpg")
+```{r model, fig.pos ='h!',out.width='50%',out.height='90%',fig.show='hold',fig.align='center', fig.cap= "Prototype of the model",  echo = FALSE, include=TRUE}
+knitr::include_graphics("C:/Users/rocpa/OneDrive/Desktop/AF/ethnic-value_multinomial-master/material/model_pr.jpg")
 ```
@@
 # Model
+\rocco{probably to include into modeling above}
 
@@
 As such value orientation relates to value homophily compared to ethncity related to ascribed status homophily.
-Each agent hold a preference for the ethnic composition and the value composition of each neighborhood.
+Each agent hold a preference for the ethnic similarity and the value similarity of each neighborhood.
 Neighborhoods are defined as a Moore distance.
@@
 
-# Experiments
+# Case studies
 
-Study 1: heterogeneity of ethnic preferences in agents \par
-* 1.1 Tune $\beta_e$ for all agents, with condition $\beta^\Box_e \geq \beta^\circ_e$, no difference between agents
-* 1.2 Change  $\beta_e$ between groups (supported by literature on which group is going to be more conservative, or anyway argumented).
-Observe the emergence of ethnic segregation first
-* Same conditions, increase $\beta_v$ Either with first 1.1 and then compar, either compare first the effect of ethnic preference heterogeneity between groups over within group
-In both cases, the effect of relative group sizes
+```{r test-utility,  echo = FALSE, include=TRUE}
 
-\vspace{10pt}
+ f_spk <- function(i_e,x,n){      # utility function as single-peaked
+  if (x > n){
+    U <- NA}else{
+    if (x < (n*i_e)){
+  U <- (x / (n*i_e))
+     }else if (x > (n*i_e)){
+        U <- i_e + (((1- (x/n))*(1-i_e))/(1-i_e))
+       }else{
+    U <- 1}
+       round(U,digits = 3)
+     }
+}
 
-@hatna2014combining: in previous studies, they had a "F critical", maybe we could use on the critical $\beta$?
+for (y in seq(0,8,by=1)) {
+  i_e = 0.9
+ p <- f_spk(i_e,y,8)
+  print(c(y,p))
+}
 
-\vspace{10pt}
+```
 
-The concept of heterogeneity is reflected into the experiments: \par
-* individual: $\beta^\Box_e \geq \beta^\Box_v$, $\beta^\circ_v \geq \beta^\circ_e$  \par
-* within ethnic group:  $\beta^\Box_e \geq \beta^\circ_e$, $\beta^\circ_v \geq \beta^\Box_v$, should specify the ethnic group  \par
-NO * between ethnic group: $\beta^{\Box B}_e \geq \beta^{\Box R}_e$ (and implying $\beta^{\Box B}_e \geq \beta^{\circ R}_e$  ) NO \par
+- heterogeneous ethnic preferences, value preferences and relative group sizes \par
 
-These are the conditions kept in the experiments, ranging $\beta \in{0,10}$  \par
-
-Think about it.
-
-If a society is "conservative", the less ethnic-oriented of that society/scenario would have high level as well.
-In the end, you could narrow down so to have 3 conditions for each low, medium, high beta (e.g.
-1, 5, 10), and calculate the $\beta_e$ of less ethnicity-oriented agents out of a ratio, e.g.
-min $n/n$,  $n/(n:2)$ (check), max $n/1$ \par
-* 1 = 1,0.5,1 (check)
-* 5 = 1,2.5,5
-* 10 = 1,5,10
-
-Dependent measure:
-
-* ethnic segregation exposure as Schelling (color)
-* value segregation exposure as Schelling (shape)
-* C index in @hatna2012schelling, to check
-
-**beta-binomial distribution? Discrete values deriving from beta distribution but not limit [0,1] @hatna2015combining**
+IDEA: Since generations have been introduced, what about including scenarios for each generations, manipulating relative group sizes and preferences between generations?\par
 
@@
 
-@van2019sociocultural introduction: social homophily as due to preferences and constraints' approach. They also use social class as proxy for  socio-cultural differentiation
-
 # References

### 2020-04-27 exp_eth_val.Rmd
ee

---
output:
  bookdown::pdf_document2:
    toc: false
 #   keep_tex: false
    fig_caption: yes
title: "Observations"
# subtitle: "Target: BIGSSS Research Day"
author: Rocco Paolillo

# date: JU 
#language: en-GB
#bibliography: "references.bib"
# always_allow_html: yes

# target: BIGSSS Research Day by September 15th, presented  on October 25th. 6000 words: around 12 pages.
# csl: apa.csl # by default: Chicago style
header-includes:
- \usepackage{float}
- \usepackage{multirow}
- \usepackage{xcolor} 
- \usepackage{amsmath}
- \usepackage{graphicx}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, fig.lp="fig:",warning = FALSE)

library(knitr)
library(ggplot2)
library(forcats)
library(reshape2)
library(tidyr)
library(dplyr)
library(reshape)
library(ggpubr)
library(magick)

#theme_set(theme_pubr())

wd <- setwd("C:/Users/rocpa/OneDrive/Desktop/AF/")
dataone <- read.csv("experiments/80_50_onebeta.csv",sep = ";",skip = 1)

```

Fig: \ref{fig:squaret} Ethnic global segregation

<!--
```{r prep, fig.pos="h!", out.width="98%",fig.align='center',fig.show="hold", fig.cap="prep fig", echo=FALSE, include=FALSE }

circle_local.labs <- c("20% Local Circle", "50% Local Circle","80% Local Circle")
names(circle_local.labs) <- c("20", "50","80")
 circle_minority.labs <-  c("20% Minority Circle", "50% Minority Circle","80% Minority Circle")
names(circle_minority.labs) <- c("20", "50","80")
circle_minority.labs <-  c("20% \nMinority Circle", "50% \nMinority Circle","80% \nMinority Circle")
names(circle_minority.labs) <- c("20", "50","80")

pl_sq_e20 <- dataone %>% filter(step == 1000 & fraction_blue == 50 & circle_blue == 20) %>%  
  gather(key = square, value = Segra, eth_sq_bl,val_sq_bl,eth_sq_or,val_sq_or) %>% 
  mutate("segregation" = fct_relevel(fct_collapse(square,"ethnic segregation" = c("eth_sq_bl","eth_sq_or"), "value segregation" = c("val_sq_bl","val_sq_or")), "ethnic segregation"), "group" = fct_relevel(fct_collapse(square, "squared majority" = c("eth_sq_bl","val_sq_bl"), "squared minority" = c("eth_sq_or","val_sq_or")),"majority")) %>%  
  ggplot(aes(x = beta_ie,y = beta_iv, fill = Segra)) + geom_tile() + 
  facet_grid(circle_orange ~ group + segregation, labeller = labeller(circle_orange = circle_minority.labs)) +
  scale_fill_distiller(palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) +
  scale_x_discrete( limits=c(0,10, by = 5)) +
  scale_y_discrete( limits=c(0,10, by = 5)) +
  xlab("ß ethnic") + ylab("ß value") + ggtitle("Square population, Majority:Minority = .5:.5, 20% Majority Circle") + 
  theme_bw() +  theme(legend.position = "right", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0))

pl_sq_m20 <- dataone %>% filter(step == 1000 & fraction_blue == 80 & circle_blue == 20) %>%  
  gather(key = square, value = Segra, eth_sq_bl,val_sq_bl,eth_sq_or,val_sq_or) %>% 
  mutate("segregation" = fct_relevel(fct_collapse(square,"ethnic segregation" = c("eth_sq_bl","eth_sq_or"), "value segregation" = c("val_sq_bl","val_sq_or")), "ethnic segregation"), "group" = fct_relevel(fct_collapse(square, "squared majority" = c("eth_sq_bl","val_sq_bl"), "squared minority" = c("eth_sq_or","val_sq_or")),"majority")) %>%  
  ggplot(aes(x = beta_ie,y = beta_iv, fill = Segra)) + geom_tile() + 
  facet_grid(circle_orange ~ group + segregation, labeller = labeller(circle_orange = circle_minority.labs)) +
  scale_fill_distiller(palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) +
  scale_x_discrete( limits=c(0,10, by = 5)) +
  scale_y_discrete( limits=c(0,10, by = 5)) +
  xlab("ß ethnic") + ylab("ß value") + ggtitle("Square population, Majority:Minority = .8:.2, 20% Majority Circle") + 
  theme_bw() +  theme(legend.position = "right", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0))

 ggsave("pl_sq_e20.png",pl_sq_e20)
 ggsave("pl_sq_m20.png",pl_sq_m20)
# a <- image_read("pl_sq_e20.png")
# b <- image_read("pl_sq_m20.png")

#knitr::include_graphics(c("pl_sq_e20.png","pl_sq_m20.png"))

img <-c(image_read("pl_sq_e20.png"),image_read("pl_sq_m20.png"))
c <- image_append(img, stack = TRUE)
image_write(c, path = "square20.png", format = "png")

#

pl_sq_e50 <- dataone %>% filter(step == 1000 & fraction_blue == 50 & circle_blue == 50) %>%  
  gather(key = square, value = Segra, eth_sq_bl,val_sq_bl,eth_sq_or,val_sq_or) %>% 
  mutate("segregation" = fct_relevel(fct_collapse(square,"ethnic segregation" = c("eth_sq_bl","eth_sq_or"), "value segregation" = c("val_sq_bl","val_sq_or")), "ethnic segregation"), "group" = fct_relevel(fct_collapse(square, "squared majority" = c("eth_sq_bl","val_sq_bl"), "squared minority" = c("eth_sq_or","val_sq_or")),"majority")) %>%  
  ggplot(aes(x = beta_ie,y = beta_iv, fill = Segra)) + geom_tile() + 
  facet_grid(circle_orange ~ group + segregation, labeller = labeller(circle_orange = circle_minority.labs)) +
  scale_fill_distiller(palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) +
  scale_x_discrete( limits=c(0,10, by = 5)) +
  scale_y_discrete( limits=c(0,10, by = 5)) +
  xlab("ß ethnic") + ylab("ß value") + ggtitle("Square population, Majority:Minority = .5:.5, 50% Majority Circle") + 
  theme_bw() +  theme(legend.position = "right", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0))

pl_sq_m50 <- dataone %>% filter(step == 1000 & fraction_blue == 80 & circle_blue == 50) %>%  
  gather(key = square, value = Segra, eth_sq_bl,val_sq_bl,eth_sq_or,val_sq_or) %>% 
  mutate("segregation" = fct_relevel(fct_collapse(square,"ethnic segregation" = c("eth_sq_bl","eth_sq_or"), "value segregation" = c("val_sq_bl","val_sq_or")), "ethnic segregation"), "group" = fct_relevel(fct_collapse(square, "squared majority" = c("eth_sq_bl","val_sq_bl"), "squared minority" = c("eth_sq_or","val_sq_or")),"majority")) %>%  
  ggplot(aes(x = beta_ie,y = beta_iv, fill = Segra)) + geom_tile() + 
  facet_grid(circle_orange ~ group + segregation, labeller = labeller(circle_orange = circle_minority.labs)) +
  scale_fill_distiller(palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) +
  scale_x_discrete( limits=c(0,10, by = 5)) +
  scale_y_discrete( limits=c(0,10, by = 5)) +
  xlab("ß ethnic") + ylab("ß value") + ggtitle("Square population, Majority:Minority = .8:.2, 50% Majority Circle") + 
  theme_bw() +  theme(legend.position = "right", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0))

ggsave("pl_sq_e50.png",pl_sq_e50)
ggsave("pl_sq_m50.png",pl_sq_m50)

img <-c(image_read("pl_sq_e50.png"),image_read("pl_sq_m50.png"))
c <- image_append(img, stack = TRUE)
image_write(c, path = "square50.png", format = "png")

#

pl_sq_e80 <- dataone %>% filter(step == 1000 & fraction_blue == 50 & circle_blue == 80) %>%  
  gather(key = square, value = Segra, eth_sq_bl,val_sq_bl,eth_sq_or,val_sq_or) %>% 
  mutate("segregation" = fct_relevel(fct_collapse(square,"ethnic segregation" = c("eth_sq_bl","eth_sq_or"), "value segregation" = c("val_sq_bl","val_sq_or")), "ethnic segregation"), "group" = fct_relevel(fct_collapse(square, "squared majority" = c("eth_sq_bl","val_sq_bl"), "squared minority" = c("eth_sq_or","val_sq_or")),"majority")) %>%  
  ggplot(aes(x = beta_ie,y = beta_iv, fill = Segra)) + geom_tile() + 
  facet_grid(circle_orange ~ group + segregation, labeller = labeller(circle_orange = circle_minority.labs)) +
  scale_fill_distiller(palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) +
  scale_x_discrete( limits=c(0,10, by = 5)) +
  scale_y_discrete( limits=c(0,10, by = 5)) +
  xlab("ß ethnic") + ylab("ß value") + ggtitle("Square population, Majority:Minority = .5:.5, 80% Majority Circle") + 
  theme_bw() +  theme(legend.position = "right", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0))

pl_sq_m80 <- dataone %>% filter(step == 1000 & fraction_blue == 80 & circle_blue == 80) %>%  
  gather(key = square, value = Segra, eth_sq_bl,val_sq_bl,eth_sq_or,val_sq_or) %>% 
  mutate("segregation" = fct_relevel(fct_collapse(square,"ethnic segregation" = c("eth_sq_bl","eth_sq_or"), "value segregation" = c("val_sq_bl","val_sq_or")), "ethnic segregation"), "group" = fct_relevel(fct_collapse(square, "squared majority" = c("eth_sq_bl","val_sq_bl"), "squared minority" = c("eth_sq_or","val_sq_or")),"majority")) %>%  
  ggplot(aes(x = beta_ie,y = beta_iv, fill = Segra)) + geom_tile() + 
  facet_grid(circle_orange ~ group + segregation, labeller = labeller(circle_orange = circle_minority.labs)) +
  scale_fill_distiller(palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) +
  scale_x_discrete( limits=c(0,10, by = 5)) +
  scale_y_discrete( limits=c(0,10, by = 5)) +
  xlab("ß ethnic") + ylab("ß value") + ggtitle("Square population, Majority:Minority = .8:.2, 80% Majority Circle") + 
  theme_bw() +  theme(legend.position = "right", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0))

ggsave("pl_sq_e80.png",pl_sq_e80)
ggsave("pl_sq_m80.png",pl_sq_m80)

img <-c(image_read("pl_sq_e80.png"),image_read("pl_sq_m80.png"))
c <- image_append(img, stack = TRUE)
image_write(c, path = "square80.png", format = "png")

# circle

pl_cl_e20 <- dataone %>% filter(step == 1000 & fraction_blue == 50 & circle_blue == 20) %>%   gather(key = circlec, value = Segrac, eth_cl_bl,val_cl_bl,eth_cl_or,val_cl_or) %>% mutate("segregation" = fct_relevel(fct_collapse(circlec,"ethnic segregation" = c("eth_cl_bl","eth_cl_or"), "value segregation" = c("val_cl_bl","val_cl_or")), "ethnic segregation"), "group" = fct_relevel(fct_collapse(circlec, "cirle majority" = c("eth_cl_bl","val_cl_bl"), "circle minority" = c("eth_cl_or","val_cl_or")),"majority"))%>%  
  ggplot(aes(x = beta_ie,y = beta_iv, fill = Segrac)) + geom_tile() + 
  facet_grid(circle_orange ~ group + segregation, labeller = labeller(circle_orange = circle_minority.labs)) +
  scale_fill_distiller(palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) +
  scale_x_discrete( limits=c(0,10, by = 5)) +
  scale_y_discrete( limits=c(0,10, by = 5)) +
  xlab("ß ethnic") + ylab("ß value") + ggtitle("Circle population, Majority:Minority = .5:.5, 20% Majority Circle") + 
  theme_bw() +  theme(legend.position = "right", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0))

pl_cl_m20 <- dataone %>% filter(step == 1000 & fraction_blue == 80 & circle_blue == 20) %>%   gather(key = circlec, value = Segrac, eth_cl_bl,val_cl_bl,eth_cl_or,val_cl_or) %>% mutate("segregation" = fct_relevel(fct_collapse(circlec,"ethnic segregation" = c("eth_cl_bl","eth_cl_or"), "value segregation" = c("val_cl_bl","val_cl_or")), "ethnic segregation"), "group" = fct_relevel(fct_collapse(circlec, "cirle majority" = c("eth_cl_bl","val_cl_bl"), "circle minority" = c("eth_cl_or","val_cl_or")),"majority"))%>%  
  ggplot(aes(x = beta_ie,y = beta_iv, fill = Segrac)) + geom_tile() + 
  facet_grid(circle_orange ~ group + segregation, labeller = labeller(circle_orange = circle_minority.labs)) +
  scale_fill_distiller(palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) +
  scale_x_discrete( limits=c(0,10, by = 5)) +
  scale_y_discrete( limits=c(0,10, by = 5)) +
  xlab("ß ethnic") + ylab("ß value") + ggtitle("Circle population, Majority:Minority = .8:.2, 20% Majority Circle") + 
  theme_bw() +  theme(legend.position = "right", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0))

ggsave("pl_cl_e20.png",pl_cl_e20)
ggsave("pl_cl_m20.png",pl_cl_m20)

img <-c(image_read("pl_cl_e20.png"),image_read("pl_cl_m20.png"))
c <- image_append(img, stack = TRUE)
image_write(c, path = "circle20.png", format = "png")

#

pl_cl_e50 <- dataone %>% filter(step == 1000 & fraction_blue == 50 & circle_blue == 50) %>%   gather(key = circlec, value = Segrac, eth_cl_bl,val_cl_bl,eth_cl_or,val_cl_or) %>% mutate("segregation" = fct_relevel(fct_collapse(circlec,"ethnic segregation" = c("eth_cl_bl","eth_cl_or"), "value segregation" = c("val_cl_bl","val_cl_or")), "ethnic segregation"), "group" = fct_relevel(fct_collapse(circlec, "cirle majority" = c("eth_cl_bl","val_cl_bl"), "circle minority" = c("eth_cl_or","val_cl_or")),"majority"))%>%  
  ggplot(aes(x = beta_ie,y = beta_iv, fill = Segrac)) + geom_tile() + 
  facet_grid(circle_orange ~ group + segregation, labeller = labeller(circle_orange = circle_minority.labs)) +
  scale_fill_distiller(palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) +
  scale_x_discrete( limits=c(0,10, by = 5)) +
  scale_y_discrete( limits=c(0,10, by = 5)) +
  xlab("ß ethnic") + ylab("ß value") + ggtitle("Circle population, Majority:Minority = .5:.5, 50% Majority Circle") + 
  theme_bw() +  theme(legend.position = "right", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0))

pl_cl_m50 <- dataone %>% filter(step == 1000 & fraction_blue == 80 & circle_blue == 50) %>%   gather(key = circlec, value = Segrac, eth_cl_bl,val_cl_bl,eth_cl_or,val_cl_or) %>% mutate("segregation" = fct_relevel(fct_collapse(circlec,"ethnic segregation" = c("eth_cl_bl","eth_cl_or"), "value segregation" = c("val_cl_bl","val_cl_or")), "ethnic segregation"), "group" = fct_relevel(fct_collapse(circlec, "cirle majority" = c("eth_cl_bl","val_cl_bl"), "circle minority" = c("eth_cl_or","val_cl_or")),"majority"))%>%  
  ggplot(aes(x = beta_ie,y = beta_iv, fill = Segrac)) + geom_tile() + 
  facet_grid(circle_orange ~ group + segregation, labeller = labeller(circle_orange = circle_minority.labs)) +
  scale_fill_distiller(palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) +
  scale_x_discrete( limits=c(0,10, by = 5)) +
  scale_y_discrete( limits=c(0,10, by = 5)) +
  xlab("ß ethnic") + ylab("ß value") + ggtitle("Circle population, Majority:Minority = .8:.2, 50% Majority Circle") + 
  theme_bw() +  theme(legend.position = "right", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0))

ggsave("pl_cl_e50.png",pl_cl_e50)
ggsave("pl_cl_m50.png",pl_cl_m50)

img <-c(image_read("pl_cl_e50.png"),image_read("pl_cl_m50.png"))
c <- image_append(img, stack = TRUE)
image_write(c, path = "circle50.png", format = "png")

#

pl_cl_e80 <- dataone %>% filter(step == 1000 & fraction_blue == 50 & circle_blue == 80) %>%   gather(key = circlec, value = Segrac, eth_cl_bl,val_cl_bl,eth_cl_or,val_cl_or) %>% mutate("segregation" = fct_relevel(fct_collapse(circlec,"ethnic segregation" = c("eth_cl_bl","eth_cl_or"), "value segregation" = c("val_cl_bl","val_cl_or")), "ethnic segregation"), "group" = fct_relevel(fct_collapse(circlec, "cirle majority" = c("eth_cl_bl","val_cl_bl"), "circle minority" = c("eth_cl_or","val_cl_or")),"majority"))%>%  
  ggplot(aes(x = beta_ie,y = beta_iv, fill = Segrac)) + geom_tile() + 
  facet_grid(circle_orange ~ group + segregation, labeller = labeller(circle_orange = circle_minority.labs)) +
  scale_fill_distiller(palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) +
  scale_x_discrete( limits=c(0,10, by = 5)) +
  scale_y_discrete( limits=c(0,10, by = 5)) +
  xlab("ß ethnic") + ylab("ß value") + ggtitle("Circle population, Majority:Minority = .5:.5, 80% Majority Circle") + 
  theme_bw() +  theme(legend.position = "right", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0))

pl_cl_m80 <- dataone %>% filter(step == 1000 & fraction_blue == 80 & circle_blue == 80) %>%   gather(key = circlec, value = Segrac, eth_cl_bl,val_cl_bl,eth_cl_or,val_cl_or) %>% mutate("segregation" = fct_relevel(fct_collapse(circlec,"ethnic segregation" = c("eth_cl_bl","eth_cl_or"), "value segregation" = c("val_cl_bl","val_cl_or")), "ethnic segregation"), "group" = fct_relevel(fct_collapse(circlec, "cirle majority" = c("eth_cl_bl","val_cl_bl"), "circle minority" = c("eth_cl_or","val_cl_or")),"majority"))%>%  
  ggplot(aes(x = beta_ie,y = beta_iv, fill = Segrac)) + geom_tile() + 
  facet_grid(circle_orange ~ group + segregation, labeller = labeller(circle_orange = circle_minority.labs)) +
  scale_fill_distiller(palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) +
  scale_x_discrete( limits=c(0,10, by = 5)) +
  scale_y_discrete( limits=c(0,10, by = 5)) +
  xlab("ß ethnic") + ylab("ß value") + ggtitle("Circle population, Majority:Minority = .8:.2, 80% Majority Circle") + 
  theme_bw() +  theme(legend.position = "right", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0))

ggsave("pl_cl_e80.png",pl_cl_e80)
ggsave("pl_cl_m80.png",pl_cl_m80)

img <-c(image_read("pl_cl_e80.png"),image_read("pl_cl_m80.png"))
c <- image_append(img, stack = TRUE)
image_write(c, path = "circle80.png", format = "png")

```
-->

```{r ethnicp, fig.pos="h!", out.width="98%",fig.align='center',fig.show="hold", fig.cap="prep fig ethnic population", echo=FALSE, include=FALSE}

circle_local.labs <- c("20% Local Circle", "50% Local Circle","80% Local Circle")
names(circle_local.labs) <- c("20", "50","80")
 circle_minority.labs <-  c("20% Minority Circle", "50% Minority Circle","80% Minority Circle")
names(circle_minority.labs) <- c("20", "50","80")
circle_minority.labs <-  c("20% \nMinority Circle", "50% \nMinority Circle","80% \nMinority Circle")
names(circle_minority.labs) <- c("20", "50","80")

mj_e20 <- dataone %>% filter(step == 1000 & fraction_blue == 50 & circle_blue == 20) %>%  
  gather(key = square, value = Segra, eth_sq_bl,val_sq_bl,eth_cl_bl,val_cl_bl) %>% 
  mutate("segregation" = fct_relevel(fct_collapse(square,"ethnic segregation" = c("eth_sq_bl","eth_cl_bl"), "value segregation" = c("val_sq_bl","val_cl_bl")), "ethnic segregation"), "group" = fct_relevel(fct_collapse(square, "majority squared" = c("eth_sq_bl","val_sq_bl"), "majority circle" = c("eth_cl_bl","val_cl_bl")),"majority squared")) %>%  
  ggplot(aes(x = beta_ie,y = beta_iv, fill = Segra)) + geom_tile() + 
  facet_grid(circle_orange ~ group + segregation, labeller = labeller(circle_orange = circle_minority.labs)) +
  scale_fill_distiller(palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) +
  scale_x_discrete( limits=c(0,10, by = 5)) +
  scale_y_discrete( limits=c(0,10, by = 5)) +
  xlab("ß ethnic") + ylab("ß value") + ggtitle("Majority population, Majority:Minority = .5:.5, 20% Majority Circle") + 
  theme_bw() +  theme(legend.position = "right", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0))

mj_m20 <- dataone %>% filter(step == 1000 & fraction_blue == 80 & circle_blue == 20) %>%  
  gather(key = square, value = Segra, eth_sq_bl,val_sq_bl,eth_cl_bl,val_cl_bl) %>% 
  mutate("segregation" = fct_relevel(fct_collapse(square,"ethnic segregation" = c("eth_sq_bl","eth_cl_bl"), "value segregation" = c("val_sq_bl","val_cl_bl")), "ethnic segregation"), "group" = fct_relevel(fct_collapse(square, "majority squared" = c("eth_sq_bl","val_sq_bl"), "majority circle" = c("eth_cl_bl","val_cl_bl")),"majority squared")) %>%  
  ggplot(aes(x = beta_ie,y = beta_iv, fill = Segra)) + geom_tile() + 
  facet_grid(circle_orange ~ group + segregation, labeller = labeller(circle_orange = circle_minority.labs)) +
  scale_fill_distiller(palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) +
  scale_x_discrete( limits=c(0,10, by = 5)) +
  scale_y_discrete( limits=c(0,10, by = 5)) +
  xlab("ß ethnic") + ylab("ß value") + ggtitle("Majority population, Majority:Minority = .8:.2, 20% Majority Circle") + 
  theme_bw() +  theme(legend.position = "right", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0))

 ggsave("mj_e20.png",mj_e20)
 ggsave("mj_m20.png",mj_m20)
# a <- image_read("pl_sq_e20.png")
# b <- image_read("pl_sq_m20.png")

#knitr::include_graphics(c("pl_sq_e20.png","pl_sq_m20.png"))

img <-c(image_read("mj_e20.png"),image_read("mj_m20.png"))
c <- image_append(img, stack = TRUE)
image_write(c, path = "majo20.png", format = "png")

#

mj_e50 <- dataone %>% filter(step == 1000 & fraction_blue == 50 & circle_blue == 50) %>%  
  gather(key = square, value = Segra, eth_sq_bl,val_sq_bl,eth_cl_bl,val_cl_bl) %>% 
  mutate("segregation" = fct_relevel(fct_collapse(square,"ethnic segregation" = c("eth_sq_bl","eth_cl_bl"), "value segregation" = c("val_sq_bl","val_cl_bl")), "ethnic segregation"), "group" = fct_relevel(fct_collapse(square, "majority squared" = c("eth_sq_bl","val_sq_bl"), "majority circle" = c("eth_cl_bl","val_cl_bl")),"majority squared")) %>%  
  ggplot(aes(x = beta_ie,y = beta_iv, fill = Segra)) + geom_tile() + 
  facet_grid(circle_orange ~ group + segregation, labeller = labeller(circle_orange = circle_minority.labs)) +
  scale_fill_distiller(palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) +
  scale_x_discrete( limits=c(0,10, by = 5)) +
  scale_y_discrete( limits=c(0,10, by = 5)) +
  xlab("ß ethnic") + ylab("ß value") + ggtitle("Majority population, Majority:Minority = .5:.5, 50% Majority Circle") + 
  theme_bw() +  theme(legend.position = "right", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0))

mj_m50 <- dataone %>% filter(step == 1000 & fraction_blue == 80 & circle_blue == 50) %>%  
  gather(key = square, value = Segra, eth_sq_bl,val_sq_bl,eth_cl_bl,val_cl_bl) %>% 
  mutate("segregation" = fct_relevel(fct_collapse(square,"ethnic segregation" = c("eth_sq_bl","eth_cl_bl"), "value segregation" = c("val_sq_bl","val_cl_bl")), "ethnic segregation"), "group" = fct_relevel(fct_collapse(square, "majority squared" = c("eth_sq_bl","val_sq_bl"), "majority circle" = c("eth_cl_bl","val_cl_bl")),"majority squared")) %>%  
  ggplot(aes(x = beta_ie,y = beta_iv, fill = Segra)) + geom_tile() + 
  facet_grid(circle_orange ~ group + segregation, labeller = labeller(circle_orange = circle_minority.labs)) +
  scale_fill_distiller(palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) +
  scale_x_discrete( limits=c(0,10, by = 5)) +
  scale_y_discrete( limits=c(0,10, by = 5)) +
  xlab("ß ethnic") + ylab("ß value") + ggtitle("Majority population, Majority:Minority = .8:.2, 50% Majority Circle") + 
  theme_bw() +  theme(legend.position = "right", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0))

 ggsave("mj_e50.png",mj_e50)
 ggsave("mj_m50.png",mj_m50)
# a <- image_read("pl_sq_e20.png")
# b <- image_read("pl_sq_m20.png")

#knitr::include_graphics(c("pl_sq_e20.png","pl_sq_m20.png"))

img <-c(image_read("mj_e50.png"),image_read("mj_m50.png"))
c <- image_append(img, stack = TRUE)
image_write(c, path = "majo50.png", format = "png")

#

mj_e80 <- dataone %>% filter(step == 1000 & fraction_blue == 50 & circle_blue == 80) %>%  
  gather(key = square, value = Segra, eth_sq_bl,val_sq_bl,eth_cl_bl,val_cl_bl) %>% 
  mutate("segregation" = fct_relevel(fct_collapse(square,"ethnic segregation" = c("eth_sq_bl","eth_cl_bl"), "value segregation" = c("val_sq_bl","val_cl_bl")), "ethnic segregation"), "group" = fct_relevel(fct_collapse(square, "majority squared" = c("eth_sq_bl","val_sq_bl"), "majority circle" = c("eth_cl_bl","val_cl_bl")),"majority squared")) %>%  
  ggplot(aes(x = beta_ie,y = beta_iv, fill = Segra)) + geom_tile() + 
  facet_grid(circle_orange ~ group + segregation, labeller = labeller(circle_orange = circle_minority.labs)) +
  scale_fill_distiller(palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) +
  scale_x_discrete( limits=c(0,10, by = 5)) +
  scale_y_discrete( limits=c(0,10, by = 5)) +
  xlab("ß ethnic") + ylab("ß value") + ggtitle("Majority population, Majority:Minority = .5:.5, 80% Majority Circle") + 
  theme_bw() +  theme(legend.position = "right", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0))

mj_m80 <- dataone %>% filter(step == 1000 & fraction_blue == 80 & circle_blue == 80) %>%  
  gather(key = square, value = Segra, eth_sq_bl,val_sq_bl,eth_cl_bl,val_cl_bl) %>% 
  mutate("segregation" = fct_relevel(fct_collapse(square,"ethnic segregation" = c("eth_sq_bl","eth_cl_bl"), "value segregation" = c("val_sq_bl","val_cl_bl")), "ethnic segregation"), "group" = fct_relevel(fct_collapse(square, "majority squared" = c("eth_sq_bl","val_sq_bl"), "majority circle" = c("eth_cl_bl","val_cl_bl")),"majority squared")) %>%  
  ggplot(aes(x = beta_ie,y = beta_iv, fill = Segra)) + geom_tile() + 
  facet_grid(circle_orange ~ group + segregation, labeller = labeller(circle_orange = circle_minority.labs)) +
  scale_fill_distiller(palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) +
  scale_x_discrete( limits=c(0,10, by = 5)) +
  scale_y_discrete( limits=c(0,10, by = 5)) +
  xlab("ß ethnic") + ylab("ß value") + ggtitle("Majority population, Majority:Minority = .8:.2, 80% Majority Circle") + 
  theme_bw() +  theme(legend.position = "right", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0))

 ggsave("mj_e80.png",mj_e80)
 ggsave("mj_m80.png",mj_m80)
# a <- image_read("pl_sq_e20.png")
# b <- image_read("pl_sq_m20.png")

#knitr::include_graphics(c("pl_sq_e20.png","pl_sq_m20.png"))

img <-c(image_read("mj_e80.png"),image_read("mj_m80.png"))
c <- image_append(img, stack = TRUE)
image_write(c, path = "majo80.png", format = "png")

# minority

circle_local.labs <- c("20% Local Circle", "50% Local Circle","80% Local Circle")
names(circle_local.labs) <- c("20", "50","80")
 circle_minority.labs <-  c("20% Minority Circle", "50% Minority Circle","80% Minority Circle")
names(circle_minority.labs) <- c("20", "50","80")
circle_minority.labs <-  c("20% \nMinority Circle", "50% \nMinority Circle","80% \nMinority Circle")
names(circle_minority.labs) <- c("20", "50","80")

mn_e20 <- dataone %>% filter(step == 1000 & fraction_blue == 50 & circle_blue == 20) %>%  
  gather(key = square, value = Segra, eth_sq_or,val_sq_or,eth_cl_or,val_cl_or) %>% 
  mutate("segregation" = fct_relevel(fct_collapse(square,"ethnic segregation" = c("eth_sq_or","eth_cl_or"), "value segregation" = c("val_sq_or","val_cl_or")), "ethnic segregation"), "group" = fct_relevel(fct_collapse(square, "minority squared" = c("eth_sq_or","val_sq_or"), "minority circle" = c("eth_cl_or","val_cl_or")),"minority squared")) %>%  
  ggplot(aes(x = beta_ie,y = beta_iv, fill = Segra)) + geom_tile() + 
  facet_grid(circle_orange ~ group + segregation, labeller = labeller(circle_orange = circle_minority.labs)) +
  scale_fill_distiller(palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) +
  scale_x_discrete( limits=c(0,10, by = 5)) +
  scale_y_discrete( limits=c(0,10, by = 5)) +
  xlab("ß ethnic") + ylab("ß value") + ggtitle("Minority population, Majority:Minority = .5:.5, 20% Majority Circle") + 
  theme_bw() +  theme(legend.position = "right", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0))

mn_m20 <- dataone %>% filter(step == 1000 & fraction_blue == 80 & circle_blue == 20) %>%  
  gather(key = square, value = Segra, eth_sq_or,val_sq_or,eth_cl_or,val_cl_or) %>% 
  mutate("segregation" = fct_relevel(fct_collapse(square,"ethnic segregation" = c("eth_sq_or","eth_cl_or"), "value segregation" = c("val_sq_or","val_cl_or")), "ethnic segregation"), "group" = fct_relevel(fct_collapse(square, "minority squared" = c("eth_sq_or","val_sq_or"), "minority circle" = c("eth_cl_or","val_cl_or")),"minority squared")) %>%  
  ggplot(aes(x = beta_ie,y = beta_iv, fill = Segra)) + geom_tile() + 
  facet_grid(circle_orange ~ group + segregation, labeller = labeller(circle_orange = circle_minority.labs)) +
  scale_fill_distiller(palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) +
  scale_x_discrete( limits=c(0,10, by = 5)) +
  scale_y_discrete( limits=c(0,10, by = 5)) +
  xlab("ß ethnic") + ylab("ß value") + ggtitle("Minority population, Majority:Minority = .8:.2, 20% Majority Circle") + 
  theme_bw() +  theme(legend.position = "right", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0))

 ggsave("mn_e20.png",mn_e20)
 ggsave("mn_m20.png",mn_m20)
# a <- image_read("pl_sq_e20.png")
# b <- image_read("pl_sq_m20.png")

#knitr::include_graphics(c("pl_sq_e20.png","pl_sq_m20.png"))

img <-c(image_read("mn_e20.png"),image_read("mn_m20.png"))
c <- image_append(img, stack = TRUE)
image_write(c, path = "min20.png", format = "png")

#

mn_e50 <- dataone %>% filter(step == 1000 & fraction_blue == 50 & circle_blue == 50) %>%  
  gather(key = square, value = Segra, eth_sq_or,val_sq_or,eth_cl_or,val_cl_or) %>% 
  mutate("segregation" = fct_relevel(fct_collapse(square,"ethnic segregation" = c("eth_sq_or","eth_cl_or"), "value segregation" = c("val_sq_or","val_cl_or")), "ethnic segregation"), "group" = fct_relevel(fct_collapse(square, "minority squared" = c("eth_sq_or","val_sq_or"), "minority circle" = c("eth_cl_or","val_cl_or")),"minority squared")) %>%  
  ggplot(aes(x = beta_ie,y = beta_iv, fill = Segra)) + geom_tile() + 
  facet_grid(circle_orange ~ group + segregation, labeller = labeller(circle_orange = circle_minority.labs)) +
  scale_fill_distiller(palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) +
  scale_x_discrete( limits=c(0,10, by = 5)) +
  scale_y_discrete( limits=c(0,10, by = 5)) +
  xlab("ß ethnic") + ylab("ß value") + ggtitle("Minority population, Majority:Minority = .5:.5, 50% Majority Circle") + 
  theme_bw() +  theme(legend.position = "right", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0))

mn_m50 <- dataone %>% filter(step == 1000 & fraction_blue == 80 & circle_blue == 50) %>%  
  gather(key = square, value = Segra, eth_sq_or,val_sq_or,eth_cl_or,val_cl_or) %>% 
  mutate("segregation" = fct_relevel(fct_collapse(square,"ethnic segregation" = c("eth_sq_or","eth_cl_or"), "value segregation" = c("val_sq_or","val_cl_or")), "ethnic segregation"), "group" = fct_relevel(fct_collapse(square, "minority squared" = c("eth_sq_or","val_sq_or"), "minority circle" = c("eth_cl_or","val_cl_or")),"minority squared")) %>%  
  ggplot(aes(x = beta_ie,y = beta_iv, fill = Segra)) + geom_tile() + 
  facet_grid(circle_orange ~ group + segregation, labeller = labeller(circle_orange = circle_minority.labs)) +
  scale_fill_distiller(palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) +
  scale_x_discrete( limits=c(0,10, by = 5)) +
  scale_y_discrete( limits=c(0,10, by = 5)) +
  xlab("ß ethnic") + ylab("ß value") + ggtitle("Minority population, Majority:Minority = .8:.2, 50% Majority Circle") + 
  theme_bw() +  theme(legend.position = "right", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0))

 ggsave("mn_e50.png",mn_e50)
 ggsave("mn_m50.png",mn_m50)
# a <- image_read("pl_sq_e20.png")
# b <- image_read("pl_sq_m20.png")

#knitr::include_graphics(c("pl_sq_e20.png","pl_sq_m20.png"))

img <-c(image_read("mn_e50.png"),image_read("mn_m50.png"))
c <- image_append(img, stack = TRUE)
image_write(c, path = "min50.png", format = "png")

#

mn_e80 <- dataone %>% filter(step == 1000 & fraction_blue == 50 & circle_blue == 80) %>%  
  gather(key = square, value = Segra, eth_sq_or,val_sq_or,eth_cl_or,val_cl_or) %>% 
  mutate("segregation" = fct_relevel(fct_collapse(square,"ethnic segregation" = c("eth_sq_or","eth_cl_or"), "value segregation" = c("val_sq_or","val_cl_or")), "ethnic segregation"), "group" = fct_relevel(fct_collapse(square, "minority squared" = c("eth_sq_or","val_sq_or"), "minority circle" = c("eth_cl_or","val_cl_or")),"minority squared")) %>%  
  ggplot(aes(x = beta_ie,y = beta_iv, fill = Segra)) + geom_tile() + 
  facet_grid(circle_orange ~ group + segregation, labeller = labeller(circle_orange = circle_minority.labs)) +
  scale_fill_distiller(palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) +
  scale_x_discrete( limits=c(0,10, by = 5)) +
  scale_y_discrete( limits=c(0,10, by = 5)) +
  xlab("ß ethnic") + ylab("ß value") + ggtitle("Minority population, Majority:Minority = .5:.5, 80% Majority Circle") + 
  theme_bw() +  theme(legend.position = "right", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0))

mn_m80 <- dataone %>% filter(step == 1000 & fraction_blue == 80 & circle_blue == 80) %>%  
  gather(key = square, value = Segra, eth_sq_or,val_sq_or,eth_cl_or,val_cl_or) %>% 
  mutate("segregation" = fct_relevel(fct_collapse(square,"ethnic segregation" = c("eth_sq_or","eth_cl_or"), "value segregation" = c("val_sq_or","val_cl_or")), "ethnic segregation"), "group" = fct_relevel(fct_collapse(square, "minority squared" = c("eth_sq_or","val_sq_or"), "minority circle" = c("eth_cl_or","val_cl_or")),"minority squared")) %>%  
  ggplot(aes(x = beta_ie,y = beta_iv, fill = Segra)) + geom_tile() + 
  facet_grid(circle_orange ~ group + segregation, labeller = labeller(circle_orange = circle_minority.labs)) +
  scale_fill_distiller(palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) +
  scale_x_discrete( limits=c(0,10, by = 5)) +
  scale_y_discrete( limits=c(0,10, by = 5)) +
  xlab("ß ethnic") + ylab("ß value") + ggtitle("Minority population, Majority:Minority = .8:.2, 80% Majority Circle") + 
  theme_bw() +  theme(legend.position = "right", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0))

 ggsave("mn_e80.png",mn_e80)
 ggsave("mn_m80.png",mn_m80)
# a <- image_read("pl_sq_e20.png")
# b <- image_read("pl_sq_m20.png")

#knitr::include_graphics(c("pl_sq_e20.png","pl_sq_m20.png"))

img <-c(image_read("mn_e80.png"),image_read("mn_m80.png"))
c <- image_append(img, stack = TRUE)
image_write(c, path = "min80.png", format = "png")

```

# Global Results

Global results with heatmap

```{r global, fig.height=8.8, fig.pos="h", include=TRUE, fig.cap="Global Segregation with ethnic equal group size, baseline in boldline", echo=FALSE}

# gen_eq <- filter(dataone, fraction_blue == 50 & step == 1000)
# gen_mj <- filter(dataone, fraction_blue == 80 & step == 1000)

 circle_local.labs <- c("20% Local Circle", "50% Local Circle","80% Local Circle")
names(circle_local.labs) <- c("20", "50","80")
 circle_minority.labs <-  c("20% Minority Circle", "50% Minority Circle","80% Minority Circle")
names(circle_minority.labs) <- c("20", "50","80")

# eth_mj <- ggplot(gen_mj, aes( beta_iv, beta_ie,fill= eth_seg))
# val_mj <- ggplot(gen_mj, aes( beta_iv, beta_ie,fill= val_seg))
#

eth_eq <- ggplot(data=subset(dataone,fraction_blue == 50 & step == 1000), aes( beta_ie, beta_iv,fill= eth_seg)) + geom_tile() +   facet_grid(circle_orange  ~  circle_blue,  space = "free_x", labeller = labeller(circle_blue = circle_local.labs,  circle_orange = circle_minority.labs ))  +
  scale_fill_distiller(name = "ETHNIC",palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) + 
  scale_x_discrete(name = "ß ethnic", limits=seq(0,10 ,by = 1)) + 
  scale_y_discrete(name = "ß value", limits=c(0,3,5,7,10))   + 
  theme_bw() + theme(strip.text.x = element_text(), legend.position = "right", panel.grid.minor.x = element_blank(), plot.title=element_blank(),  legend.margin=margin(0,0,0,0)) +
   geom_rect(data=subset(dataone,fraction_blue == 50 & step == 1000 & circle_orange == 50 & circle_blue == 50),aes(xmin = -1,xmax = 12, ymin = -1, ymax = 11),colour="black",size =2,alpha = 0)

val_eq <- ggplot(data=subset(dataone,fraction_blue == 50 & step == 1000), aes( beta_ie, beta_iv,fill= val_seg)) + geom_tile() +   facet_grid(circle_orange  ~  circle_blue,  space = "free_x", labeller = labeller(circle_blue = circle_local.labs,  circle_orange = circle_minority.labs )) + 
  scale_fill_distiller(name = "VALUE",palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) + 
  scale_x_discrete(name = "ß ethnic", limits=seq(0,10 ,by = 1)) + 
  scale_y_discrete(name = "ß value", limits=c(0,3,5,7,10))  + 
  theme_bw() + theme(strip.text.x = element_text(), legend.position = "right", panel.grid.minor.x = element_blank(), plot.title=element_blank(),  legend.margin=margin(0,0,0,0)) +
  geom_rect(data=subset(dataone,fraction_blue == 50 & step == 1000 & circle_orange == 50 & circle_blue == 50),aes(xmin = -1,xmax = 12, ymin = -1, ymax = 11),colour="black",size =2,alpha = 0)

glb <- annotate_figure(ggarrange(eth_eq , ggarrange(val_eq), nrow = 2), top = text_grob("Global Segregation, Local:Minority = 0.5:0.5",face = "bold", size = 12))

glb
```

```{r global-maj, fig.height=8.8, fig.pos="h",  include=TRUE, fig.cap="Global Segregation with ethnic equal group size, baseline in boldline", echo=FALSE}

# gen_eq <- filter(dataone, fraction_blue == 50 & step == 1000)
# gen_mj <- filter(dataone, fraction_blue == 80 & step == 1000)

 circle_local.labs <- c("20% Local Circle", "50% Local Circle","80% Local Circle")
names(circle_local.labs) <- c("20", "50","80")
 circle_minority.labs <-  c("20% Minority Circle", "50% Minority Circle","80% Minority Circle")
names(circle_minority.labs) <- c("20", "50","80")

# eth_mj <- ggplot(gen_mj, aes( beta_iv, beta_ie,fill= eth_seg))
# val_mj <- ggplot(gen_mj, aes( beta_iv, beta_ie,fill= val_seg))
#

maj_eth <- ggplot(data=subset(dataone,fraction_blue == 80 & step == 1000), aes( beta_ie, beta_iv,fill= eth_seg)) + geom_tile() +   facet_grid(circle_orange  ~  circle_blue,  space = "free_x", labeller = labeller(circle_blue = circle_local.labs,  circle_orange = circle_minority.labs ))  +
  scale_fill_distiller(name = "ETHNIC",palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) + 
  scale_x_discrete(name = "ß ethnic", limits=seq(0,10 ,by = 1)) + 
  scale_y_discrete(name = "ß value", limits=c(0,3,5,7,10)) + 
  theme_bw() + theme(strip.text.x = element_text(), legend.position = "right", panel.grid.minor.x = element_blank(), plot.title=element_blank(),  legend.margin=margin(0,0,0,0)) +
  geom_rect(data=subset(dataone,fraction_blue == 80 & step == 1000 & circle_orange == 50 & circle_blue == 50),aes(xmin = -1,xmax = 12, ymin = -1, ymax = 11),colour="black",size =2,alpha = 0)

maj_val <- ggplot(data=subset(dataone,fraction_blue == 80 & step == 1000), aes( beta_ie, beta_iv,fill= val_seg)) + geom_tile() +   facet_grid(circle_orange  ~  circle_blue,  space = "free_x", labeller = labeller(circle_blue = circle_local.labs,  circle_orange = circle_minority.labs )) + 
  scale_fill_distiller(name = "VALUE",palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) + 
  scale_x_discrete(name = "ß ethnic", limits=seq(0,10 ,by = 1)) + 
  scale_y_discrete(name = "ß value", limits=c(0,3,5,7,10))  + 
  theme_bw() + theme(strip.text.x = element_text(), legend.position = "right", panel.grid.minor.x = element_blank(), plot.title=element_blank(),  legend.margin=margin(0,0,0,0)) +
  geom_rect(data=subset(dataone,fraction_blue == 80 & step == 1000 & circle_orange == 50 & circle_blue == 50),aes(xmin = -1,xmax = 12, ymin = -1, ymax = 11),colour="black",size =2,alpha = 0)

maj_glb <- annotate_figure(ggarrange(maj_eth , ggarrange(maj_val), nrow = 2), top = text_grob("Global Segregation, Local:Minority = 0.8:0.2",face = "bold", size = 12))
maj_glb
```

# Effect of value distribution in group value differences

Each graph is one level of $\%$ circle (value 1) in the local population (majority = blue agents). Each condition panel refers to distribution of  circle agents in the minority population.

<!--
```{r squaret, fig.pos="h", out.width="98%",fig.align='center',fig.show="hold", fig.cap="Square population, 20\\% Majority Circle, equal ethnic (above), minority-majority (below)", echo=FALSE, include=TRUE }

knitr::include_graphics("square20.png")

```

```{r squaref, fig.pos="h", out.width="98%",fig.align='center',fig.show="hold", fig.cap="Square population, 50\\% Majority Circle, equal ethnic (above), minority-majority (below)", echo=FALSE, include=TRUE }

knitr::include_graphics("square50.png")

```

```{r squareg, fig.pos="h", out.width="98%",fig.align='center',fig.show="hold", fig.cap="Square population, 80\\% Majority Circle, equal ethnic (above), minority-majority (below)", echo=FALSE, include=TRUE }

knitr::include_graphics("square80.png")

```

```{r circlet, fig.pos="h", out.width="98%",fig.align='center',fig.show="hold", fig.cap="Circle population, 20\\% Majority Circle, equal ethnic (above), minority-majority (below)", echo=FALSE, include=TRUE }

knitr::include_graphics("circle20.png")

```

```{r circlef, fig.pos="h", out.width="98%",fig.align='center',fig.show="hold", fig.cap="Circle population, 50\\% Majority Circle, equal ethnic (above), minority-majority (below)", echo=FALSE, include=TRUE }

knitr::include_graphics("circle50.png")

```

```{r circleg, fig.pos="h", out.width="98%",fig.align='center',fig.show="hold", fig.cap="Circle population, 80\\% Majority Circle, equal ethnic (above), minority-majority (below)", echo=FALSE, include=TRUE }

knitr::include_graphics("circle80.png")

```

-->

```{r mint, fig.pos="h", out.width="98%",fig.align='center',fig.show="hold", fig.cap="Minority population, 20\\% Majority Circle, equal ethnic (above), minority-majority (below)", echo=FALSE, include=TRUE }

knitr::include_graphics("min20.png")

```

```{r minf, fig.pos="h", out.width="98%",fig.align='center',fig.show="hold", fig.cap="Minority population, 50\\% Majority Circle, equal ethnic (above), minority-majority (below)", echo=FALSE, include=TRUE }

knitr::include_graphics("min50.png")

```

```{r ming, fig.pos="h", out.width="98%",fig.align='center',fig.show="hold", fig.cap="Minority population, 80\\% Majority Circle, equal ethnic (above), minority-majority (below)", echo=FALSE, include=TRUE }

knitr::include_graphics("min80.png")

```

```{r majot, fig.pos="h", out.width="98%",fig.align='center',fig.show="hold", fig.cap="Majority population, 20\\% Majority Circle, equal ethnic (above), minority-majority (below)", echo=FALSE, include=TRUE }

knitr::include_graphics("majo20.png")

```

```{r majof, fig.pos="h", out.width="98%",fig.align='center',fig.show="hold", fig.cap="Majority population, 50\\% Majority Circle, equal ethnic (above), minority-majority (below)", echo=FALSE, include=TRUE }

knitr::include_graphics("majo50.png")

```

```{r majog, fig.pos="h", out.width="98%",fig.align='center',fig.show="hold", fig.cap="Majority population, 80\\% Majority Circle, equal ethnic (above), minority-majority (below)", echo=FALSE, include=TRUE }

knitr::include_graphics("majo80.png")

```

<!--
```{r local_circle, fig.height=8.8, fig.pos="t", include=TRUE, fig.cap="Segregation of circle local equal ethnic, baseline in boldline", echo=FALSE}

# gen_eq <- filter(dataone, fraction_blue == 50 & step == 1000)
# gen_mj <- filter(dataone, fraction_blue == 80 & step == 1000)

 circle_local.labs <- c("20% Local Circle", "50% Local Circle","80% Local Circle")
names(circle_local.labs) <- c("20", "50","80")
 circle_minority.labs <-  c("20% Minority Circle", "50% Minority Circle","80% Minority Circle")
names(circle_minority.labs) <- c("20", "50","80")

# eth_mj <- ggplot(gen_mj, aes( beta_iv, beta_ie,fill= eth_seg))
# val_mj <- ggplot(gen_mj, aes( beta_iv, beta_ie,fill= val_seg))
#

eth_cl_blue <- ggplot(data=subset(dataone,fraction_blue == 50 & step == 1000), aes( beta_ie, beta_iv,fill= eth_cl_bl)) + geom_tile() +   facet_grid(circle_orange  ~  circle_blue,  space = "free_x", labeller = labeller(circle_blue = circle_local.labs,  circle_orange = circle_minority.labs ))  +
  scale_fill_distiller(name = "ETHNIC",palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) + 
  scale_x_discrete(name = "ß ethnic", limits=seq(0,10 ,by = 1)) + 
  scale_y_discrete(name = "ß value", limits=c(0,3,5,7,10)) + 
  theme_bw() + theme(strip.text.x = element_text(), legend.position = "right", panel.grid.minor.x = element_blank(), plot.title=element_blank(),  legend.margin=margin(0,0,0,0)) +
  geom_rect(data=subset(dataone,fraction_blue == 50 & step == 1000 & circle_orange == 50 & circle_blue == 50),aes(xmin = -1,xmax = 12, ymin = -1, ymax = 11),colour="black",size =2,alpha = 0)

val_cl_blue <- ggplot(data=subset(dataone,fraction_blue == 50 & step == 1000), aes( beta_ie, beta_iv,fill= val_cl_bl)) + geom_tile() +   facet_grid(circle_orange  ~  circle_blue,  space = "free_x", labeller = labeller(circle_blue = circle_local.labs,  circle_orange = circle_minority.labs )) + 
  scale_fill_distiller(name = "VALUE",palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) + 
  scale_x_discrete(name = "ß ethnic", limits=seq(0,10 ,by = 1)) + 
  scale_y_discrete(name = "ß value", limits=c(0,3,5,7,10))  + 
  theme_bw() + theme(strip.text.x = element_text(), legend.position = "right", panel.grid.minor.x = element_blank(), plot.title=element_blank(),  legend.margin=margin(0,0,0,0)) +
  geom_rect(data=subset(dataone,fraction_blue == 50 & step == 1000 & circle_orange == 50 & circle_blue == 50),aes(xmin = -1,xmax = 12, ymin = -1, ymax = 11),colour="black",size =2,alpha = 0)

cl_bl <- annotate_figure(ggarrange(eth_cl_blue , ggarrange(val_cl_blue), nrow = 2), top = text_grob("Segregation circle local, Local:Minority = 0.5:0.5",face = "bold", size = 12))
cl_bl
```

```{r min_square, fig.height=8.8, fig.pos="t", include=TRUE, fig.cap="Segregation of squared minority, baseline in boldline", echo=FALSE}

# gen_eq <- filter(dataone, fraction_blue == 50 & step == 1000)
# gen_mj <- filter(dataone, fraction_blue == 80 & step == 1000)

 circle_local.labs <- c("20% Local Circle", "50% Local Circle","80% Local Circle")
names(circle_local.labs) <- c("20", "50","80")
 circle_minority.labs <-  c("20% Minority Circle", "50% Minority Circle","80% Minority Circle")
names(circle_minority.labs) <- c("20", "50","80")

# eth_mj <- ggplot(gen_mj, aes( beta_iv, beta_ie,fill= eth_seg))
# val_mj <- ggplot(gen_mj, aes( beta_iv, beta_ie,fill= val_seg))
#

eth_sq_org <- ggplot(data=subset(dataone,fraction_blue == 50 & step == 1000), aes( beta_ie, beta_iv,fill= eth_sq_or)) + geom_tile() +   facet_grid(circle_orange  ~  circle_blue,  space = "free_x", labeller = labeller(circle_blue = circle_local.labs,  circle_orange = circle_minority.labs ))  +
  scale_fill_distiller(name = "ETHNIC",palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) + 
  scale_x_discrete(name = "ß ethnic", limits=seq(0,10 ,by = 1)) + 
  scale_y_discrete(name = "ß value", limits=c(0,3,5,7,10)) + 
  theme_bw() + theme(strip.text.x = element_text(), legend.position = "right", panel.grid.minor.x = element_blank(), plot.title=element_blank(),  legend.margin=margin(0,0,0,0)) +
  geom_rect(data=subset(dataone,fraction_blue == 50 & step == 1000 & circle_orange == 50 & circle_blue == 50),aes(xmin = -1,xmax = 12, ymin = -1, ymax = 11),colour="black",size =2,alpha = 0)

val_sq_org <- ggplot(data=subset(dataone,fraction_blue == 50 & step == 1000), aes( beta_ie, beta_iv,fill= val_sq_or)) + geom_tile() +   facet_grid(circle_orange  ~  circle_blue,  space = "free_x", labeller = labeller(circle_blue = circle_local.labs,  circle_orange = circle_minority.labs )) + 
  scale_fill_distiller(name = "VALUE",palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) + 
  scale_x_discrete(name = "ß ethnic", limits=seq(0,10 ,by = 1)) + 
  scale_y_discrete(name = "ß value", limits=c(0,3,5,7,10))  + 
  theme_bw() + theme(strip.text.x = element_text(), legend.position = "right", panel.grid.minor.x = element_blank(), plot.title=element_blank(),  legend.margin=margin(0,0,0,0)) +
  geom_rect(data=subset(dataone,fraction_blue == 50 & step == 1000 & circle_orange == 50 & circle_blue == 50),aes(xmin = -1,xmax = 12, ymin = -1, ymax = 11),colour="black",size =2,alpha = 0)

sq_org <- annotate_figure(ggarrange(eth_sq_org , ggarrange(val_sq_org), nrow = 2), top = text_grob("Segregation squared minority, Local:Minority = 0.5:0.5",face = "bold", size = 12))
sq_org
```

```{r min_circle, fig.height=8.8, fig.pos="t", include=TRUE, fig.cap="Segregation of circle local ethnic equal, baseline in boldline", echo=FALSE}

# gen_eq <- filter(dataone, fraction_blue == 50 & step == 1000)
# gen_mj <- filter(dataone, fraction_blue == 80 & step == 1000)

 circle_local.labs <- c("20% Local Circle", "50% Local Circle","80% Local Circle")
names(circle_local.labs) <- c("20", "50","80")
 circle_minority.labs <-  c("20% Minority Circle", "50% Minority Circle","80% Minority Circle")
names(circle_minority.labs) <- c("20", "50","80")

# eth_mj <- ggplot(gen_mj, aes( beta_iv, beta_ie,fill= eth_seg))
# val_mj <- ggplot(gen_mj, aes( beta_iv, beta_ie,fill= val_seg))
#

eth_cl_org <- ggplot(data=subset(dataone,fraction_blue == 50 & step == 1000), aes( beta_ie, beta_iv,fill= eth_cl_or)) + geom_tile() +   facet_grid(circle_orange  ~  circle_blue,  space = "free_x", labeller = labeller(circle_blue = circle_local.labs,  circle_orange = circle_minority.labs ))  +
  scale_fill_distiller(name = "ETHNIC",palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) + 
  scale_x_discrete(name = "ß ethnic", limits=seq(0,10 ,by = 1)) + 
  scale_y_discrete(name = "ß value", limits=c(0,3,5,7,10)) + 
  theme_bw() + theme(strip.text.x = element_text(), legend.position = "right", panel.grid.minor.x = element_blank(), plot.title=element_blank(),  legend.margin=margin(0,0,0,0)) +
  geom_rect(data=subset(dataone,fraction_blue == 50 & step == 1000 & circle_orange == 50 & circle_blue == 50),aes(xmin = -1,xmax = 12, ymin = -1, ymax = 11),colour="black",size =2,alpha = 0)

val_cl_org <- ggplot(data=subset(dataone,fraction_blue == 50 & step == 1000), aes( beta_ie, beta_iv,fill= val_cl_or)) + geom_tile() +   facet_grid(circle_orange  ~  circle_blue,  space = "free_x", labeller = labeller(circle_blue = circle_local.labs,  circle_orange = circle_minority.labs )) + 
  scale_fill_distiller(name = "VALUE",palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) + 
  scale_x_discrete(name = "ß ethnic", limits=seq(0,10 ,by = 1)) + 
  scale_y_discrete(name = "ß value", limits=c(0,3,5,7,10))  + 
  theme_bw() + theme(strip.text.x = element_text(), legend.position = "right", panel.grid.minor.x = element_blank(), plot.title=element_blank(),  legend.margin=margin(0,0,0,0)) +
  geom_rect(data=subset(dataone,fraction_blue == 50 & step == 1000 & circle_orange == 50 & circle_blue == 50),aes(xmin = -1,xmax = 12, ymin = -1, ymax = 11),colour="black",size =2,alpha = 0)

cl_org <- annotate_figure(ggarrange(eth_cl_org , ggarrange(val_cl_org), nrow = 2), top = text_grob("Segregation circle minority, Local:Minority = 0.5:0.5",face = "bold", size = 12))
cl_org
```

majority

```{r maj_local_square, fig.height=8.8, fig.pos="t", include=TRUE, fig.cap="Segregation of squared local, baseline in boldline", echo=FALSE}

# gen_eq <- filter(dataone, fraction_blue == 50 & step == 1000)
# gen_mj <- filter(dataone, fraction_blue == 80 & step == 1000)

 circle_local.labs <- c("20% Local Circle", "50% Local Circle","80% Local Circle")
names(circle_local.labs) <- c("20", "50","80")
 circle_minority.labs <-  c("20% Minority Circle", "50% Minority Circle","80% Minority Circle")
names(circle_minority.labs) <- c("20", "50","80")

# eth_mj <- ggplot(gen_mj, aes( beta_iv, beta_ie,fill= eth_seg))
# val_mj <- ggplot(gen_mj, aes( beta_iv, beta_ie,fill= val_seg))
#

maj_eth_sq_blue <- ggplot(data=subset(dataone,fraction_blue == 80 & step == 1000), aes( beta_ie, beta_iv,fill= eth_sq_bl)) + geom_tile() +   facet_grid(circle_orange  ~  circle_blue,  space = "free_x", labeller = labeller(circle_blue = circle_local.labs,  circle_orange = circle_minority.labs ))  +
  scale_fill_distiller(name = "ETHNIC",palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) + 
  scale_x_discrete(name = "ß ethnic", limits=seq(0,10 ,by = 1)) + 
  scale_y_discrete(name = "ß value", limits=c(0,3,5,7,10)) + 
  theme_bw() + theme(strip.text.x = element_text(), legend.position = "right", panel.grid.minor.x = element_blank(), plot.title=element_blank(),  legend.margin=margin(0,0,0,0)) +
  geom_rect(data=subset(dataone,fraction_blue == 80 & step == 1000 & circle_orange == 50 & circle_blue == 50),aes(xmin = -1,xmax = 12, ymin = -1, ymax = 11),colour="black",size =2,alpha = 0)

maj_val_sq_blue <- ggplot(data=subset(dataone,fraction_blue == 80 & step == 1000), aes( beta_ie, beta_iv,fill= val_sq_bl)) + geom_tile() +   facet_grid(circle_orange  ~  circle_blue,  space = "free_x", labeller = labeller(circle_blue = circle_local.labs,  circle_orange = circle_minority.labs )) + 
  scale_fill_distiller(name = "VALUE",palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) + 
  scale_x_discrete(name = "ß ethnic", limits=seq(0,10 ,by = 1)) + 
  scale_y_discrete(name = "ß value", limits=c(0,3,5,7,10))  + 
  theme_bw() + theme(strip.text.x = element_text(), legend.position = "right", panel.grid.minor.x = element_blank(), plot.title=element_blank(),  legend.margin=margin(0,0,0,0)) +
  geom_rect(data=subset(dataone,fraction_blue == 80 & step == 1000 & circle_orange == 50 & circle_blue == 50),aes(xmin = -1,xmax = 12, ymin = -1, ymax = 11),colour="black",size =2,alpha = 0)

maj_sq_bl <- annotate_figure(ggarrange(maj_eth_sq_blue , ggarrange(maj_val_sq_blue), nrow = 2), top = text_grob("Segregation squared local, Local:Minority = 0.8:0.2",face = "bold", size = 12))

maj_sq_bl
```

```{r maj_local_circle, fig.height=8.8, fig.pos="t", include=TRUE, fig.cap="Segregation of circle local, baseline in boldline", echo=FALSE}

# gen_eq <- filter(dataone, fraction_blue == 50 & step == 1000)
# gen_mj <- filter(dataone, fraction_blue == 80 & step == 1000)

 circle_local.labs <- c("20% Local Circle", "50% Local Circle","80% Local Circle")
names(circle_local.labs) <- c("20", "50","80")
 circle_minority.labs <-  c("20% Minority Circle", "50% Minority Circle","80% Minority Circle")
names(circle_minority.labs) <- c("20", "50","80")

# eth_mj <- ggplot(gen_mj, aes( beta_iv, beta_ie,fill= eth_seg))
# val_mj <- ggplot(gen_mj, aes( beta_iv, beta_ie,fill= val_seg))
#

maj_eth_cl_blue <- ggplot(data=subset(dataone,fraction_blue == 80 & step == 1000), aes( beta_ie, beta_iv,fill= eth_cl_bl)) + geom_tile() +   facet_grid(circle_orange  ~  circle_blue,  space = "free_x", labeller = labeller(circle_blue = circle_local.labs,  circle_orange = circle_minority.labs ))  +
  scale_fill_distiller(name = "ETHNIC",palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) + 
  scale_x_discrete(name = "ß ethnic", limits=seq(0,10 ,by = 1)) + 
  scale_y_discrete(name = "ß value", limits=c(0,3,5,7,10)) + 
  theme_bw() + theme(strip.text.x = element_text(), legend.position = "right", panel.grid.minor.x = element_blank(), plot.title=element_blank(),  legend.margin=margin(0,0,0,0)) +
  geom_rect(data=subset(dataone,fraction_blue == 80 & step == 1000 & circle_orange == 50 & circle_blue == 50),aes(xmin = -1,xmax = 12, ymin = -1, ymax = 11),colour="black",size =2,alpha = 0)

maj_val_cl_blue <- ggplot(data=subset(dataone,fraction_blue == 80 & step == 1000), aes( beta_ie, beta_iv,fill= val_cl_bl)) + geom_tile() +   facet_grid(circle_orange  ~  circle_blue,  space = "free_x", labeller = labeller(circle_blue = circle_local.labs,  circle_orange = circle_minority.labs )) + 
  scale_fill_distiller(name = "VALUE",palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) + 
  scale_x_discrete(name = "ß ethnic", limits=seq(0,10 ,by = 1)) + 
  scale_y_discrete(name = "ß value", limits=c(0,3,5,7,10))  + 
  theme_bw() + theme(strip.text.x = element_text(), legend.position = "right", panel.grid.minor.x = element_blank(), plot.title=element_blank(),  legend.margin=margin(0,0,0,0)) +
  geom_rect(data=subset(dataone,fraction_blue == 80 & step == 1000 & circle_orange == 50 & circle_blue == 50),aes(xmin = -1,xmax = 12, ymin = -1, ymax = 11),colour="black",size =2,alpha = 0)

maj_cl_bl <- annotate_figure(ggarrange(maj_eth_cl_blue , ggarrange(maj_val_cl_blue), nrow = 2), top = text_grob("Segregation circle local, Local:Minority = 0.8:0.2",face = "bold", size = 12))
maj_cl_bl

```

```{r maj_min_square, fig.height=8.8, fig.pos="t", include=TRUE, fig.cap="Segregation of squared local, baseline in boldline", echo=FALSE}

# gen_eq <- filter(dataone, fraction_blue == 50 & step == 1000)
# gen_mj <- filter(dataone, fraction_blue == 80 & step == 1000)

 circle_local.labs <- c("20% Local Circle", "50% Local Circle","80% Local Circle")
names(circle_local.labs) <- c("20", "50","80")
 circle_minority.labs <-  c("20% Minority Circle", "50% Minority Circle","80% Minority Circle")
names(circle_minority.labs) <- c("20", "50","80")

# eth_mj <- ggplot(gen_mj, aes( beta_iv, beta_ie,fill= eth_seg))
# val_mj <- ggplot(gen_mj, aes( beta_iv, beta_ie,fill= val_seg))
#

maj_eth_sq_org <- ggplot(data=subset(dataone,fraction_blue == 80 & step == 1000), aes( beta_ie, beta_iv,fill= eth_sq_or)) + geom_tile() +   facet_grid(circle_orange  ~  circle_blue,  space = "free_x", labeller = labeller(circle_blue = circle_local.labs,  circle_orange = circle_minority.labs ))  +
  scale_fill_distiller(name = "ETHNIC",palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) + 
  scale_x_discrete(name = "ß ethnic", limits=seq(0,10 ,by = 1)) + 
  scale_y_discrete(name = "ß value", limits=c(0,3,5,7,10)) + 
  theme_bw() + theme(strip.text.x = element_text(), legend.position = "right", panel.grid.minor.x = element_blank(), plot.title=element_blank(),  legend.margin=margin(0,0,0,0)) +
  geom_rect(data=subset(dataone,fraction_blue == 80 & step == 1000 & circle_orange == 50 & circle_blue == 50),aes(xmin = -1,xmax = 12, ymin = -1, ymax = 11),colour="black",size =2,alpha = 0)

maj_val_sq_org <- ggplot(data=subset(dataone,fraction_blue == 80 & step == 1000), aes( beta_ie, beta_iv,fill= val_sq_or)) + geom_tile() +   facet_grid(circle_orange  ~  circle_blue,  space = "free_x", labeller = labeller(circle_blue = circle_local.labs,  circle_orange = circle_minority.labs )) + 
  scale_fill_distiller(name = "VALUE",palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) + 
  scale_x_discrete(name = "ß ethnic", limits=seq(0,10 ,by = 1)) + 
  scale_y_discrete(name = "ß value", limits=c(0,3,5,7,10))  + 
  theme_bw() + theme(strip.text.x = element_text(), legend.position = "right", panel.grid.minor.x = element_blank(), plot.title=element_blank(),  legend.margin=margin(0,0,0,0)) +
  geom_rect(data=subset(dataone,fraction_blue == 80 & step == 1000 & circle_orange == 50 & circle_blue == 50),aes(xmin = -1,xmax = 12, ymin = -1, ymax = 11),colour="black",size =2,alpha = 0)

maj_sq_org <- annotate_figure(ggarrange(maj_eth_sq_org , ggarrange(maj_val_sq_org), nrow = 2), top = text_grob("Segregation squared minority, Local:Minority = 0.8:0.2",face = "bold", size = 12))
maj_sq_org

```

```{r maj_min_circle, fig.height=8.8, fig.pos="t", include=TRUE, fig.cap="Segregation of circle local, baseline in boldline", echo=FALSE}

# gen_eq <- filter(dataone, fraction_blue == 50 & step == 1000)
# gen_mj <- filter(dataone, fraction_blue == 80 & step == 1000)

 circle_local.labs <- c("20% Local Circle", "50% Local Circle","80% Local Circle")
names(circle_local.labs) <- c("20", "50","80")
 circle_minority.labs <-  c("20% Minority Circle", "50% Minority Circle","80% Minority Circle")
names(circle_minority.labs) <- c("20", "50","80")

# eth_mj <- ggplot(gen_mj, aes( beta_iv, beta_ie,fill= eth_seg))
# val_mj <- ggplot(gen_mj, aes( beta_iv, beta_ie,fill= val_seg))
#

maj_eth_cl_org <- ggplot(data=subset(dataone,fraction_blue == 80 & step == 1000), aes( beta_ie, beta_iv,fill= eth_cl_or)) + geom_tile() +   facet_grid(circle_orange  ~  circle_blue,  space = "free_x", labeller = labeller(circle_blue = circle_local.labs,  circle_orange = circle_minority.labs ))  +
  scale_fill_distiller(name = "ETHNIC",palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) + 
  scale_x_discrete(name = "ß ethnic", limits=seq(0,10 ,by = 1)) + 
  scale_y_discrete(name = "ß value", limits=c(0,3,5,7,10)) + 
  theme_bw() + theme(strip.text.x = element_text(), legend.position = "right", panel.grid.minor.x = element_blank(), plot.title=element_blank(),  legend.margin=margin(0,0,0,0)) +
  geom_rect(data=subset(dataone,fraction_blue == 80 & step == 1000 & circle_orange == 50 & circle_blue == 50),aes(xmin = -1,xmax = 12, ymin = -1, ymax = 11),colour="black",size =2,alpha = 0)

maj_val_cl_org <- ggplot(data=subset(dataone,fraction_blue == 80 & step == 1000), aes( beta_ie, beta_iv,fill= val_cl_or)) + geom_tile() +   facet_grid(circle_orange  ~  circle_blue,  space = "free_x", labeller = labeller(circle_blue = circle_local.labs,  circle_orange = circle_minority.labs )) + 
  scale_fill_distiller(name = "VALUE",palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) + 
  scale_x_discrete(name = "ß ethnic", limits=seq(0,10 ,by = 1)) + 
  scale_y_discrete(name = "ß value", limits=c(0,3,5,7,10))  + 
  theme_bw() + theme(strip.text.x = element_text(), legend.position = "right", panel.grid.minor.x = element_blank(), plot.title=element_blank(),  legend.margin=margin(0,0,0,0)) +
  geom_rect(data=subset(dataone,fraction_blue == 80 & step == 1000 & circle_orange == 50 & circle_blue == 50),aes(xmin = -1,xmax = 12, ymin = -1, ymax = 11),colour="black",size =2,alpha = 0)

maj_cl_org <- annotate_figure(ggarrange(maj_eth_cl_org , ggarrange(maj_val_cl_org), nrow = 2), top = text_grob("Segregation circle minority, Local:Minority = 0.8:0.2",face = "bold", size = 12))
maj_cl_org
```
-->

```{r testnorm, echo=FALSE, include= FALSE}

nrml <- function(mx,mn,x,s){

  s <- ((x - mn) / (mx-mn))
}

 bt_10 <- for (x in seq(5,10,by=1)) {

  mx <- 10
  mn <- 5

  s <- nrml(mx,mn,x,s)
  print(c(x,s))

}

 bt_5 <- for (x in seq(0,5,by=1)) {

  mx <- 5
  mn <- 0

  s <- nrml(mx,mn,x,s)
  print(c(x,s))

}

```

### 2020-04-27 exp_eth_val.Rmd
experiment on 270420
all experiments to select

@@
 dataone <- read.csv("experiments/80_50_onebeta.csv",sep = ";",skip = 1)
+datatwo <- read.csv("experiments/two_beta.csv", sep = ";",skip = 1)
 
@@
   geom_rect(data=subset(dataone,fraction_blue == 80 & step == 1000 & circle_orange == 50 & circle_blue == 50),aes(xmin = -1,xmax = 12, ymin = -1, ymax = 11),colour="black",size =2,alpha = 0)
+maj_val
 
@@
 knitr::include_graphics("majo80.png")
+
+```
+
+```{r betatwoethnic,out.width="96%", fig.pos="t",fig.show = "hold",fig.pos='t',fig.align='center',fig.show="hold", fig.cap="Difference segregation between value groups (equal ethnic group).
+X-axis: determinism ethnic utility circle.", echo=FALSE, include=TRUE }
+
+circle_frame <- datatwo %>% filter(step == 1000) %>% filter(beta_iv_circle == 0 |beta_iv_circle == 5 |beta_iv_circle == 10 ) %>% filter(beta_ie_circle == 0 | beta_ie_circle == 5 | beta_ie_circle == 10)
+
+ v_circle.labs <- c("ß value circle 0", "ß value circle 5", "ß value circle 10")
+names(v_circle.labs) <- c("0", "5","10")
+e_circle.labs <- c("ß ethnic circle 0", "ß ethnic circle 5", "ß ethnic circle 10")
+names(e_circle.labs) <- c("0", "5","10")
+
+ie_10 <- circle_frame %>%  filter(beta_ie_square == 10) %>% gather(key = subgroup, value = Segra, eth_sq_or,val_sq_or,eth_cl_or,val_cl_or) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"ethnic segregation" = c("eth_sq_or","eth_cl_or"), "value segregation" = c("val_sq_or","val_cl_or")), "ethnic segregation"), `group` = fct_relevel(fct_collapse(subgroup, "square minority" = c("eth_sq_or","val_sq_or"), "circle minority" = c("eth_cl_or","val_cl_or"), "square minority"))) %>%
+  ggplot(aes(x = (beta_ie_square - beta_iv_square), y = Segra, color = `segregation`, shape = `group`)) + geom_line() + geom_point() + facet_grid(beta_iv_circle ~  beta_ie_circle, labeller = labeller(beta_iv_circle = v_circle.labs,  beta_ie_circle = e_circle.labs )) +
+  geom_vline(xintercept = 5, color = "red") +
+  scale_x_discrete(name = "ß ethnic square 10 - ß value square", limits = seq(0,10, by = 1)) +  ylab("Segregation") +
+  scale_color_manual(values = c("dark violet","dark green"), guide = guide_legend(title="")) +
+  scale_shape_manual(values = c(16,15), guide = guide_legend(title="")) +
+    theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0))
+
+ie_5 <- circle_frame %>%  filter(beta_ie_square == 5) %>% gather(key = subgroup, value = Segra, eth_sq_or,val_sq_or,eth_cl_or,val_cl_or) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"ethnic segregation" = c("eth_sq_or","eth_cl_or"), "value segregation" = c("val_sq_or","val_cl_or")), "ethnic segregation"), `group` = fct_relevel(fct_collapse(subgroup, "square minority" = c("eth_sq_or","val_sq_or"), "circle minority" = c("eth_cl_or","val_cl_or"), "square minority"))) %>%
+  ggplot(aes(x = (beta_ie_square - beta_iv_square), y = Segra, color = `segregation`, shape = `group`)) + geom_line() + geom_point() + facet_grid(beta_iv_circle ~  beta_ie_circle, labeller = labeller(beta_iv_circle = v_circle.labs,  beta_ie_circle = e_circle.labs )) +
+  scale_x_discrete(name = "ß ethnic square 5 - ß value square", limits = seq(0,5, by = 1)) +  ylab("Segregation") +
+  scale_color_manual(values = c("dark violet","dark green"), guide = guide_legend(title="")) +
+  scale_shape_manual(values = c(16,15), guide = guide_legend(title="")) +
+    theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0))
+
+ie_5
+ie_10
+```
+
+```{r betatwovalue, out.width="96%", fig.pos="t",fig.show = "hold",fig.pos='t',fig.align='center',fig.show="hold", fig.cap="Difference segregation between value groups (equal ethnic group).
+X-axis: determinism value utility circle.", echo=FALSE, include=TRUE  }
+
+circle_frame <- datatwo %>% filter(step == 1000) %>% filter(beta_ie_square == 0 |beta_ie_square == 5 |beta_ie_square == 10 ) %>% filter(beta_iv_square == 0 | beta_iv_square == 5 | beta_iv_square == 10)
+
+e_square.labs <- c("ß ethnic \nsquare 0", "ß ethnic \nsquare 5", "ß ethnic \nsquare 10")
+names(e_square.labs) <- c("0", "5","10")
+v_square.labs <- c("ß value square 0", "ß value square 5", "ß value square 10")
+names(v_square.labs) <- c("0", "5","10")
+
+iv_10 <- circle_frame %>%  filter(beta_iv_circle == 10) %>% gather(key = subgroup, value = Segra, eth_sq_or,val_sq_or,eth_cl_or,val_cl_or) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"ethnic segregation" = c("eth_sq_or","eth_cl_or"), "value segregation" = c("val_sq_or","val_cl_or")), "ethnic segregation"), `group` = fct_relevel(fct_collapse(subgroup, "square minority" = c("eth_sq_or","val_sq_or"), "circle minority" = c("eth_cl_or","val_cl_or"), "square minority")))  %>%
+  ggplot(aes(x = (beta_iv_circle - beta_ie_circle), y = Segra, color = `segregation`, shape = `group`)) + geom_line() + geom_point() + facet_grid(beta_ie_square ~  beta_iv_square, labeller = labeller(beta_ie_square = e_square.labs, beta_iv_square = v_square.labs))  +
+  geom_vline(xintercept = 5, color = "red") +
+  scale_x_discrete(name = "ß value circle 10 - ß ethnic circle", limits = seq(0,10, by = 1)) +  ylab("Segregation") +
+  scale_color_manual(values = c("dark violet","dark green"), guide = guide_legend(title="")) +
+  scale_shape_manual(values = c(16,15), guide = guide_legend(title="")) +
+    theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0))
+
+iv_5 <- circle_frame %>%  filter(beta_iv_circle == 5) %>% gather(key = subgroup, value = Segra, eth_sq_or,val_sq_or,eth_cl_or,val_cl_or) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"ethnic segregation" = c("eth_sq_or","eth_cl_or"), "value segregation" = c("val_sq_or","val_cl_or")), "ethnic segregation"), `group` = fct_relevel(fct_collapse(subgroup, "square minority" = c("eth_sq_or","val_sq_or"), "circle minority" = c("eth_cl_or","val_cl_or"), "square minority")))  %>%
+  ggplot(aes(x = (beta_iv_circle - beta_ie_circle), y = Segra, color = `segregation`, shape = `group`)) + geom_line() + geom_point() + facet_grid(beta_ie_square ~  beta_iv_square, labeller = labeller(beta_ie_square = e_square.labs, beta_iv_square = v_square.labs))  +
+  scale_x_discrete(name = "ß value circle 5 - ß ethnic circle", limits = seq(0,5, by = 1)) +  ylab("Segregation") +
+  scale_color_manual(values = c("dark violet","dark green"), guide = guide_legend(title="")) +
+  scale_shape_manual(values = c(16,15), guide = guide_legend(title="")) +
+    theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0))
+
+iv_5
+iv_10
 
@@
 ```
-
-majority
 
@@
 
-```{r testnorm, echo=FALSE, include= FALSE}
+<!--
+```{r testnormdelete, echo=FALSE, include= FALSE}
 
-nrml <- function(mx,mn,x,s){
+nrml <- function(mx,mn,x){
 
@@
 
- bt_10 <- for (x in seq(5,10,by=1)) {
+ bt_10 <- for (x in seq(0,5,by=1)) {
 
-  mx <- 10
-  mn <- 5
+  mx <- 5
+  mn <- 0
 
-  s <- nrml(mx,mn,x,s)
+  s <- nrml(mx,mn,x)
   print(c(x,s))
@@
 
-  s <- nrml(mx,mn,x,s)
+  s <- nrml(mx,mn,x)
   print(c(x,s))
@@
 ```
+
+-->

### 2020-05-01 exp_eth_val.Rmd
resetting maps

@@
 library(magick)
+library(gridExtra)
+library(grid)
 
@@
 ```
-
-Fig: \ref{fig:squaret} Ethnic global segregation
-
-<!--
-```{r prep, fig.pos="h!", out.width="98%",fig.align='center',fig.show="hold", fig.cap="prep fig", echo=FALSE, include=FALSE }
-
-circle_local.labs <- c("20% Local Circle", "50% Local Circle","80% Local Circle")
-names(circle_local.labs) <- c("20", "50","80")
- circle_minority.labs <-  c("20% Minority Circle", "50% Minority Circle","80% Minority Circle")
-names(circle_minority.labs) <- c("20", "50","80")
-circle_minority.labs <-  c("20% \nMinority Circle", "50% \nMinority Circle","80% \nMinority Circle")
-names(circle_minority.labs) <- c("20", "50","80")
-
-pl_sq_e20 <- dataone %>% filter(step == 1000 & fraction_blue == 50 & circle_blue == 20) %>%  
-  gather(key = square, value = Segra, eth_sq_bl,val_sq_bl,eth_sq_or,val_sq_or) %>% 
-  mutate("segregation" = fct_relevel(fct_collapse(square,"ethnic segregation" = c("eth_sq_bl","eth_sq_or"), "value segregation" = c("val_sq_bl","val_sq_or")), "ethnic segregation"), "group" = fct_relevel(fct_collapse(square, "squared majority" = c("eth_sq_bl","val_sq_bl"), "squared minority" = c("eth_sq_or","val_sq_or")),"majority")) %>%
-  ggplot(aes(x = beta_ie,y = beta_iv, fill = Segra)) + geom_tile() + 
-  facet_grid(circle_orange ~ group + segregation, labeller = labeller(circle_orange = circle_minority.labs)) +
-  scale_fill_distiller(palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) +
-  scale_x_discrete( limits=c(0,10, by = 5)) +
-  scale_y_discrete( limits=c(0,10, by = 5)) +
-  xlab("ß ethnic") + ylab("ß value") + ggtitle("Square population, Majority:Minority = .5:.5, 20% Majority Circle") + 
-  theme_bw() +  theme(legend.position = "right", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0))
-
-pl_sq_m20 <- dataone %>% filter(step == 1000 & fraction_blue == 80 & circle_blue == 20) %>%  
-  gather(key = square, value = Segra, eth_sq_bl,val_sq_bl,eth_sq_or,val_sq_or) %>% 
-  mutate("segregation" = fct_relevel(fct_collapse(square,"ethnic segregation" = c("eth_sq_bl","eth_sq_or"), "value segregation" = c("val_sq_bl","val_sq_or")), "ethnic segregation"), "group" = fct_relevel(fct_collapse(square, "squared majority" = c("eth_sq_bl","val_sq_bl"), "squared minority" = c("eth_sq_or","val_sq_or")),"majority")) %>%
-  ggplot(aes(x = beta_ie,y = beta_iv, fill = Segra)) + geom_tile() + 
-  facet_grid(circle_orange ~ group + segregation, labeller = labeller(circle_orange = circle_minority.labs)) +
-  scale_fill_distiller(palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) +
-  scale_x_discrete( limits=c(0,10, by = 5)) +
-  scale_y_discrete( limits=c(0,10, by = 5)) +
-  xlab("ß ethnic") + ylab("ß value") + ggtitle("Square population, Majority:Minority = .8:.2, 20% Majority Circle") + 
-  theme_bw() +  theme(legend.position = "right", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0))
-
- ggsave("pl_sq_e20.png",pl_sq_e20)
- ggsave("pl_sq_m20.png",pl_sq_m20)
-# a <- image_read("pl_sq_e20.png")
-# b <- image_read("pl_sq_m20.png")
-
-#knitr::include_graphics(c("pl_sq_e20.png","pl_sq_m20.png"))
-
-img <-c(image_read("pl_sq_e20.png"),image_read("pl_sq_m20.png"))
-c <- image_append(img, stack = TRUE)
-image_write(c, path = "square20.png", format = "png")
-
-#
-
-pl_sq_e50 <- dataone %>% filter(step == 1000 & fraction_blue == 50 & circle_blue == 50) %>%  
-  gather(key = square, value = Segra, eth_sq_bl,val_sq_bl,eth_sq_or,val_sq_or) %>% 
-  mutate("segregation" = fct_relevel(fct_collapse(square,"ethnic segregation" = c("eth_sq_bl","eth_sq_or"), "value segregation" = c("val_sq_bl","val_sq_or")), "ethnic segregation"), "group" = fct_relevel(fct_collapse(square, "squared majority" = c("eth_sq_bl","val_sq_bl"), "squared minority" = c("eth_sq_or","val_sq_or")),"majority")) %>%
-  ggplot(aes(x = beta_ie,y = beta_iv, fill = Segra)) + geom_tile() + 
-  facet_grid(circle_orange ~ group + segregation, labeller = labeller(circle_orange = circle_minority.labs)) +
-  scale_fill_distiller(palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) +
-  scale_x_discrete( limits=c(0,10, by = 5)) +
-  scale_y_discrete( limits=c(0,10, by = 5)) +
-  xlab("ß ethnic") + ylab("ß value") + ggtitle("Square population, Majority:Minority = .5:.5, 50% Majority Circle") + 
-  theme_bw() +  theme(legend.position = "right", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0))
-
-pl_sq_m50 <- dataone %>% filter(step == 1000 & fraction_blue == 80 & circle_blue == 50) %>%  
-  gather(key = square, value = Segra, eth_sq_bl,val_sq_bl,eth_sq_or,val_sq_or) %>% 
-  mutate("segregation" = fct_relevel(fct_collapse(square,"ethnic segregation" = c("eth_sq_bl","eth_sq_or"), "value segregation" = c("val_sq_bl","val_sq_or")), "ethnic segregation"), "group" = fct_relevel(fct_collapse(square, "squared majority" = c("eth_sq_bl","val_sq_bl"), "squared minority" = c("eth_sq_or","val_sq_or")),"majority")) %>%
-  ggplot(aes(x = beta_ie,y = beta_iv, fill = Segra)) + geom_tile() + 
-  facet_grid(circle_orange ~ group + segregation, labeller = labeller(circle_orange = circle_minority.labs)) +
-  scale_fill_distiller(palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) +
-  scale_x_discrete( limits=c(0,10, by = 5)) +
-  scale_y_discrete( limits=c(0,10, by = 5)) +
-  xlab("ß ethnic") + ylab("ß value") + ggtitle("Square population, Majority:Minority = .8:.2, 50% Majority Circle") + 
-  theme_bw() +  theme(legend.position = "right", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0))
-
-ggsave("pl_sq_e50.png",pl_sq_e50)
-ggsave("pl_sq_m50.png",pl_sq_m50)
-
-img <-c(image_read("pl_sq_e50.png"),image_read("pl_sq_m50.png"))
-c <- image_append(img, stack = TRUE)
-image_write(c, path = "square50.png", format = "png")
-
-#
-
-pl_sq_e80 <- dataone %>% filter(step == 1000 & fraction_blue == 50 & circle_blue == 80) %>%  
-  gather(key = square, value = Segra, eth_sq_bl,val_sq_bl,eth_sq_or,val_sq_or) %>% 
-  mutate("segregation" = fct_relevel(fct_collapse(square,"ethnic segregation" = c("eth_sq_bl","eth_sq_or"), "value segregation" = c("val_sq_bl","val_sq_or")), "ethnic segregation"), "group" = fct_relevel(fct_collapse(square, "squared majority" = c("eth_sq_bl","val_sq_bl"), "squared minority" = c("eth_sq_or","val_sq_or")),"majority")) %>%
-  ggplot(aes(x = beta_ie,y = beta_iv, fill = Segra)) + geom_tile() + 
-  facet_grid(circle_orange ~ group + segregation, labeller = labeller(circle_orange = circle_minority.labs)) +
-  scale_fill_distiller(palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) +
-  scale_x_discrete( limits=c(0,10, by = 5)) +
-  scale_y_discrete( limits=c(0,10, by = 5)) +
-  xlab("ß ethnic") + ylab("ß value") + ggtitle("Square population, Majority:Minority = .5:.5, 80% Majority Circle") + 
-  theme_bw() +  theme(legend.position = "right", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0))
-
-pl_sq_m80 <- dataone %>% filter(step == 1000 & fraction_blue == 80 & circle_blue == 80) %>%  
-  gather(key = square, value = Segra, eth_sq_bl,val_sq_bl,eth_sq_or,val_sq_or) %>% 
-  mutate("segregation" = fct_relevel(fct_collapse(square,"ethnic segregation" = c("eth_sq_bl","eth_sq_or"), "value segregation" = c("val_sq_bl","val_sq_or")), "ethnic segregation"), "group" = fct_relevel(fct_collapse(square, "squared majority" = c("eth_sq_bl","val_sq_bl"), "squared minority" = c("eth_sq_or","val_sq_or")),"majority")) %>%
-  ggplot(aes(x = beta_ie,y = beta_iv, fill = Segra)) + geom_tile() + 
-  facet_grid(circle_orange ~ group + segregation, labeller = labeller(circle_orange = circle_minority.labs)) +
-  scale_fill_distiller(palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) +
-  scale_x_discrete( limits=c(0,10, by = 5)) +
-  scale_y_discrete( limits=c(0,10, by = 5)) +
-  xlab("ß ethnic") + ylab("ß value") + ggtitle("Square population, Majority:Minority = .8:.2, 80% Majority Circle") + 
-  theme_bw() +  theme(legend.position = "right", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0))
-
-ggsave("pl_sq_e80.png",pl_sq_e80)
-ggsave("pl_sq_m80.png",pl_sq_m80)
-
-img <-c(image_read("pl_sq_e80.png"),image_read("pl_sq_m80.png"))
-c <- image_append(img, stack = TRUE)
-image_write(c, path = "square80.png", format = "png")
-
-# circle
-
-pl_cl_e20 <- dataone %>% filter(step == 1000 & fraction_blue == 50 & circle_blue == 20) %>%   gather(key = circlec, value = Segrac, eth_cl_bl,val_cl_bl,eth_cl_or,val_cl_or) %>% mutate("segregation" = fct_relevel(fct_collapse(circlec,"ethnic segregation" = c("eth_cl_bl","eth_cl_or"), "value segregation" = c("val_cl_bl","val_cl_or")), "ethnic segregation"), "group" = fct_relevel(fct_collapse(circlec, "cirle majority" = c("eth_cl_bl","val_cl_bl"), "circle minority" = c("eth_cl_or","val_cl_or")),"majority"))%>%
-  ggplot(aes(x = beta_ie,y = beta_iv, fill = Segrac)) + geom_tile() + 
-  facet_grid(circle_orange ~ group + segregation, labeller = labeller(circle_orange = circle_minority.labs)) +
-  scale_fill_distiller(palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) +
-  scale_x_discrete( limits=c(0,10, by = 5)) +
-  scale_y_discrete( limits=c(0,10, by = 5)) +
-  xlab("ß ethnic") + ylab("ß value") + ggtitle("Circle population, Majority:Minority = .5:.5, 20% Majority Circle") + 
-  theme_bw() +  theme(legend.position = "right", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0))
-
-pl_cl_m20 <- dataone %>% filter(step == 1000 & fraction_blue == 80 & circle_blue == 20) %>%   gather(key = circlec, value = Segrac, eth_cl_bl,val_cl_bl,eth_cl_or,val_cl_or) %>% mutate("segregation" = fct_relevel(fct_collapse(circlec,"ethnic segregation" = c("eth_cl_bl","eth_cl_or"), "value segregation" = c("val_cl_bl","val_cl_or")), "ethnic segregation"), "group" = fct_relevel(fct_collapse(circlec, "cirle majority" = c("eth_cl_bl","val_cl_bl"), "circle minority" = c("eth_cl_or","val_cl_or")),"majority"))%>%
-  ggplot(aes(x = beta_ie,y = beta_iv, fill = Segrac)) + geom_tile() + 
-  facet_grid(circle_orange ~ group + segregation, labeller = labeller(circle_orange = circle_minority.labs)) +
-  scale_fill_distiller(palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) +
-  scale_x_discrete( limits=c(0,10, by = 5)) +
-  scale_y_discrete( limits=c(0,10, by = 5)) +
-  xlab("ß ethnic") + ylab("ß value") + ggtitle("Circle population, Majority:Minority = .8:.2, 20% Majority Circle") + 
-  theme_bw() +  theme(legend.position = "right", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0))
-
-ggsave("pl_cl_e20.png",pl_cl_e20)
-ggsave("pl_cl_m20.png",pl_cl_m20)
-
-img <-c(image_read("pl_cl_e20.png"),image_read("pl_cl_m20.png"))
-c <- image_append(img, stack = TRUE)
-image_write(c, path = "circle20.png", format = "png")
-
-#
-
-pl_cl_e50 <- dataone %>% filter(step == 1000 & fraction_blue == 50 & circle_blue == 50) %>%   gather(key = circlec, value = Segrac, eth_cl_bl,val_cl_bl,eth_cl_or,val_cl_or) %>% mutate("segregation" = fct_relevel(fct_collapse(circlec,"ethnic segregation" = c("eth_cl_bl","eth_cl_or"), "value segregation" = c("val_cl_bl","val_cl_or")), "ethnic segregation"), "group" = fct_relevel(fct_collapse(circlec, "cirle majority" = c("eth_cl_bl","val_cl_bl"), "circle minority" = c("eth_cl_or","val_cl_or")),"majority"))%>%
-  ggplot(aes(x = beta_ie,y = beta_iv, fill = Segrac)) + geom_tile() + 
-  facet_grid(circle_orange ~ group + segregation, labeller = labeller(circle_orange = circle_minority.labs)) +
-  scale_fill_distiller(palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) +
-  scale_x_discrete( limits=c(0,10, by = 5)) +
-  scale_y_discrete( limits=c(0,10, by = 5)) +
-  xlab("ß ethnic") + ylab("ß value") + ggtitle("Circle population, Majority:Minority = .5:.5, 50% Majority Circle") + 
-  theme_bw() +  theme(legend.position = "right", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0))
-
-pl_cl_m50 <- dataone %>% filter(step == 1000 & fraction_blue == 80 & circle_blue == 50) %>%   gather(key = circlec, value = Segrac, eth_cl_bl,val_cl_bl,eth_cl_or,val_cl_or) %>% mutate("segregation" = fct_relevel(fct_collapse(circlec,"ethnic segregation" = c("eth_cl_bl","eth_cl_or"), "value segregation" = c("val_cl_bl","val_cl_or")), "ethnic segregation"), "group" = fct_relevel(fct_collapse(circlec, "cirle majority" = c("eth_cl_bl","val_cl_bl"), "circle minority" = c("eth_cl_or","val_cl_or")),"majority"))%>%
-  ggplot(aes(x = beta_ie,y = beta_iv, fill = Segrac)) + geom_tile() + 
-  facet_grid(circle_orange ~ group + segregation, labeller = labeller(circle_orange = circle_minority.labs)) +
-  scale_fill_distiller(palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) +
-  scale_x_discrete( limits=c(0,10, by = 5)) +
-  scale_y_discrete( limits=c(0,10, by = 5)) +
-  xlab("ß ethnic") + ylab("ß value") + ggtitle("Circle population, Majority:Minority = .8:.2, 50% Majority Circle") + 
-  theme_bw() +  theme(legend.position = "right", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0))
-
-ggsave("pl_cl_e50.png",pl_cl_e50)
-ggsave("pl_cl_m50.png",pl_cl_m50)
-
-img <-c(image_read("pl_cl_e50.png"),image_read("pl_cl_m50.png"))
-c <- image_append(img, stack = TRUE)
-image_write(c, path = "circle50.png", format = "png")
-
-#
-
-pl_cl_e80 <- dataone %>% filter(step == 1000 & fraction_blue == 50 & circle_blue == 80) %>%   gather(key = circlec, value = Segrac, eth_cl_bl,val_cl_bl,eth_cl_or,val_cl_or) %>% mutate("segregation" = fct_relevel(fct_collapse(circlec,"ethnic segregation" = c("eth_cl_bl","eth_cl_or"), "value segregation" = c("val_cl_bl","val_cl_or")), "ethnic segregation"), "group" = fct_relevel(fct_collapse(circlec, "cirle majority" = c("eth_cl_bl","val_cl_bl"), "circle minority" = c("eth_cl_or","val_cl_or")),"majority"))%>%
-  ggplot(aes(x = beta_ie,y = beta_iv, fill = Segrac)) + geom_tile() + 
-  facet_grid(circle_orange ~ group + segregation, labeller = labeller(circle_orange = circle_minority.labs)) +
-  scale_fill_distiller(palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) +
-  scale_x_discrete( limits=c(0,10, by = 5)) +
-  scale_y_discrete( limits=c(0,10, by = 5)) +
-  xlab("ß ethnic") + ylab("ß value") + ggtitle("Circle population, Majority:Minority = .5:.5, 80% Majority Circle") + 
-  theme_bw() +  theme(legend.position = "right", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0))
-
-pl_cl_m80 <- dataone %>% filter(step == 1000 & fraction_blue == 80 & circle_blue == 80) %>%   gather(key = circlec, value = Segrac, eth_cl_bl,val_cl_bl,eth_cl_or,val_cl_or) %>% mutate("segregation" = fct_relevel(fct_collapse(circlec,"ethnic segregation" = c("eth_cl_bl","eth_cl_or"), "value segregation" = c("val_cl_bl","val_cl_or")), "ethnic segregation"), "group" = fct_relevel(fct_collapse(circlec, "cirle majority" = c("eth_cl_bl","val_cl_bl"), "circle minority" = c("eth_cl_or","val_cl_or")),"majority"))%>%
-  ggplot(aes(x = beta_ie,y = beta_iv, fill = Segrac)) + geom_tile() + 
-  facet_grid(circle_orange ~ group + segregation, labeller = labeller(circle_orange = circle_minority.labs)) +
-  scale_fill_distiller(palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) +
-  scale_x_discrete( limits=c(0,10, by = 5)) +
-  scale_y_discrete( limits=c(0,10, by = 5)) +
-  xlab("ß ethnic") + ylab("ß value") + ggtitle("Circle population, Majority:Minority = .8:.2, 80% Majority Circle") + 
-  theme_bw() +  theme(legend.position = "right", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0))
-
-ggsave("pl_cl_e80.png",pl_cl_e80)
-ggsave("pl_cl_m80.png",pl_cl_m80)
-
-img <-c(image_read("pl_cl_e80.png"),image_read("pl_cl_m80.png"))
-c <- image_append(img, stack = TRUE)
-image_write(c, path = "circle80.png", format = "png")
-
-```
--->
 
@@
  ggsave("mn_m80.png",mn_m80)
-# a <- image_read("pl_sq_e20.png")
-# b <- image_read("pl_sq_m20.png")
-
+# a <- image_r
 #knitr::include_graphics(c("pl_sq_e20.png","pl_sq_m20.png"))
@@
 
-# Global Results
+# Recap
 
-Global results with heatmap
+- Research question: How the interplay of ethnic and value homophily preferences can explain difference in the degree of integration for the members of the same ethnic group (hybrid segregation) for both ethnic and value segregation.
+- Focus: different weight on the two dimensions, heterogeneity among agents, relative group size for both dimensions \par
+
+Utility of agents in Schelling relocation
+
+$$
+U= \beta_eX_v + \beta_vX_v + \epsilon
+$$
+
+```{r thheory, fig.pos="h", out.width="50%",out.width='\\textwidth',fig.align='left',fig.show="hold", fig.cap="Agents distinction and utility function", echo=FALSE, include=TRUE }
+
+knitr::include_graphics("recapp.png")
+```
+
+# First Section (effect of relative group size)
+
+* Aim:
+    + Effect of different homophily preferences: independent effect of $\beta_e$ on ethnic segregation, and direct effect of beta value $\beta_v$ on value segregation.
+
+Table \ref{tab:first}
+
+\begin{table}[H]
+\begin{tabular}{llll}
+\midrule
+ Static agent variable                      & Range         &      &                \\ \midrule
+ Ethnicity  (\textit{color})         & Blue, Orange        \\
+ Value orientation (\textit{shape}) & Square, Circle &  &  \\
+ \midrule
+
+ Parameters kept constant    & Slider & Range   & Experiments  \\ 
+ \midrule
+ Population density    & density                 & $[0,0.99]$   & $0.7$          \\
+ Peak ethnic utility & similar\_wanted\_ethnic & $[0,1]$ & $1$ (linear function) \\
+ Peak value utility & similar\_wanted\_value & $[0,1]$ & $1$ (linear function) \\
+ \midrule
+ Parameters modified in experiment & Slider  & Range   & Experiments  \\ 
+ \midrule
+ Ethnic group ratio (local\/minority)  & fraction\_blue &  $[0,1]$      & $0.5,0.8$  \\
+ value ratio  blue population & circle\_blue & $[0,1]$      & $0.20,0.5,0.8$  \\
+ value ratio  orange population & circle\_blue & $[0,1]$      & $0.20,0.5,0.8$  \\
+ Determinism ethnic utility ($\beta_e$) & beta-ie for all agents & $[0,1]$ & $[0,10]$  \\
+ Determinism value utility ($\beta_v$) & beta-iv for all agents & $[0,1]$ & $[0,10]$ \\
+ \midrule
+ Global output measures    & Computation &   Range & \\ 
+ \midrule
+ Ethnic segregation  & same color neighborhood proportion & $0,\stackrel{+0.1}{\dots}, 1$ & global and subgroups\\
+ Value segregation  & same shape neighborhood proportion & $0,\stackrel{+0.1}{\dots}, 1$ & global and subgroups\\
+   \midrule
+\end{tabular}
+\label{tab:first}
+ \caption{Basic Model}
+
+\end{table}
 
@@
 
-glb <- annotate_figure(ggarrange(eth_eq , ggarrange(val_eq), nrow = 2), top = text_grob("Global Segregation, Local:Minority = 0.5:0.5",face = "bold", size = 12))
+glb <- annotate_figure(ggarrange(eth_eq , ggarrange(val_eq), nrow = 2), top = text_grob("Global Segregation, Majority:Minority = 0.5:0.5",face = "bold", size = 12))
 
 glb
+
 ```
@@
   geom_rect(data=subset(dataone,fraction_blue == 80 & step == 1000 & circle_orange == 50 & circle_blue == 50),aes(xmin = -1,xmax = 12, ymin = -1, ymax = 11),colour="black",size =2,alpha = 0)
-maj_val
 
-maj_glb <- annotate_figure(ggarrange(maj_eth , ggarrange(maj_val), nrow = 2), top = text_grob("Global Segregation, Local:Minority = 0.8:0.2",face = "bold", size = 12))
+maj_glb <- annotate_figure(ggarrange(maj_eth , ggarrange(maj_val), nrow = 2), top = text_grob("Global Segregation, Majority:Minority = 0.8:0.2",face = "bold", size = 12))
 maj_glb
+
+```
+
+```{r sqro, fig.pos="t",out.width='\\textwidth',fig.show = "hold",fig.pos='t',fig.align='center',fig.show="hold", fig.cap="", echo=FALSE, include=TRUE  }
+
+ circle_local.labs <- c("20% Circle \nMajority", "50% Circle \nMajority","80% Circle \nMajority")
+names(circle_local.labs) <- c("20", "50","80")
+ circle_minority.labs <-  c("20% Circle \nMinority", "50% Circle \nMinority","80% Circle \nMinority")
+names(circle_minority.labs) <- c("20", "50","80")
+
+sqroeq <- dataone %>%  filter(fraction_blue == 50) %>%  gather(key = subgroup, value = Segra, eth_sq_or,val_sq_or) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"Value" = "val_sq_or","Ethnic" = "eth_sq_or"), "Value"))  %>%
+  ggplot(aes(x = beta_ie,y = beta_iv, fill = Segra)) + geom_tile() + 
+  facet_grid(circle_orange ~ circle_blue + segregation, labeller = labeller(circle_orange = circle_minority.labs, circle_blue = circle_local.labs)) +
+  scale_fill_distiller(palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) +
+  scale_x_discrete( limits=c(0,10, by = 5)) +
+  scale_y_discrete( limits=c(0,10, by = 5)) +
+  xlab("ß ethnic") + ylab("ß value") + ggtitle("Square orange, ethnic minority") + 
+  theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0), 
+                      panel.spacing.x  = unit(0.2, "lines"),panel.spacing.y  = unit(0.1, "lines") )
+
+sqromj<- dataone %>%  filter(fraction_blue == 80) %>%  gather(key = subgroup, value = Segra, eth_sq_or,val_sq_or) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"Value" = "val_sq_or","Ethnic" = "eth_sq_or"), "Value"))  %>%
+  ggplot(aes(x = beta_ie,y = beta_iv, fill = Segra)) + geom_tile() + 
+  facet_grid(circle_orange ~ circle_blue + segregation, labeller = labeller(circle_orange = circle_minority.labs, circle_blue = circle_local.labs)) +
+  scale_fill_distiller(palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) +
+  scale_x_discrete( limits=c(0,10, by = 5)) +
+  scale_y_discrete( limits=c(0,10, by = 5)) +
+  xlab("ß ethnic") + ylab("ß value") + ggtitle("Square orange, ethnic minority") + 
+  theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0), 
+                      panel.spacing.x  = unit(0.2, "lines"),panel.spacing.y  = unit(0.1, "lines") )
+
+#grid.arrange(grob(sqroeq),grob(sqromj), ncol =  1, common.legend = TRUE,legend = "bottom")
+
+ sqroeq
+ sqromj
+```
+
+```{r crloA, fig.pos="t",out.width='\\textwidth',fig.show = "hold",fig.pos='t',fig.align='center',fig.show="hold", fig.cap="", echo=FALSE, include=TRUE  }
+
+dataone$rev_circle_orange <- fct_rev(factor(dataone$circle_orange))
+
+ circle_blue.labs <- c("20% Circle Blue", "50% Circle Blue","80% Circle Blue")
+names(circle_blue.labs) <- c("20", "50","80")
+ rev_circle_orange.labs <-  c("80% Circle \nOrange", "50% Circle \nOrange","20% Circle \nOrange")
+names(rev_circle_orange.labs) <- c("80", "50","20")
+
+crloeq <- dataone %>%  filter(fraction_blue == 50) %>%  gather(key = subgroup, value = Segra, eth_cl_or,val_cl_or) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"Value" = "val_cl_or","Ethnic" = "eth_cl_or"), "Value"))  %>%
+  ggplot(aes(x = beta_ie,y = beta_iv, fill = Segra)) + geom_tile() + 
+  facet_grid(rev_circle_orange ~ circle_blue + segregation, labeller = labeller(rev_circle_orange = rev_circle_orange.labs, circle_blue = circle_blue.labs), switch  = "y") +
+  scale_fill_distiller(palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) +
+  scale_x_discrete( limits=c(0,10, by = 5)) +
+  scale_y_discrete( limits=c(0,10, by = 5), position = "right") +
+  xlab("ß ethnic") + ylab("ß value") + ggtitle("Circle orange, equal ethnic size") + 
+  theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0), 
+                      panel.spacing.x  = unit(0.2, "lines"),panel.spacing.y  = unit(0.1, "lines") )
+ crloeq
+
+crlomj <- dataone %>%  filter(fraction_blue == 80) %>%  gather(key = subgroup, value = Segra, eth_cl_or,val_cl_or) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"Value" = "val_cl_or","Ethnic" = "eth_cl_or"), "Value"))  %>%
+  ggplot(aes(x = beta_ie,y = beta_iv, fill = Segra)) + geom_tile() + 
+  facet_grid(circle_orange ~ circle_blue + segregation, labeller = labeller(circle_orange = circle_minority.labs, circle_blue = circle_local.labs)) +
+  scale_fill_distiller(palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) +
+  scale_x_discrete( limits=c(0,10, by = 5)) +
+  scale_y_discrete( limits=c(0,10, by = 5)) +
+  xlab("ß ethnic") + ylab("ß value") + ggtitle("Circle orange, ethnic minority") + 
+  theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0), 
+                      panel.spacing.x  = unit(0.2, "lines"),panel.spacing.y  = unit(0.1, "lines") )
+
+#grid.arrange(grob(sqroeq),grob(sqromj), ncol =  1, common.legend = TRUE,legend = "bottom")
+
+ crloeq
+ crlomj
+```
+
+```{r sqrb, fig.pos="t",out.width='\\textwidth',fig.show = "hold",fig.pos='t',fig.align='center',fig.show="hold", fig.cap="", echo=FALSE, include=TRUE  }
+
+ circle_local.labs <- c("20% Circle \nMajority", "50% Circle \nMajority","80% Circle \nMajority")
+names(circle_local.labs) <- c("20", "50","80")
+ circle_minority.labs <-  c("20% Circle \nMinority", "50% Circle \nMinority","80% Circle \nMinority")
+names(circle_minority.labs) <- c("20", "50","80")
+
+sqrbeq <- dataone %>%  filter(fraction_blue == 50) %>%  gather(key = subgroup, value = Segra, eth_sq_bl,val_sq_bl) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"Value" = "val_sq_bl","Ethnic" = "eth_sq_bl"), "Value"))  %>%
+  ggplot(aes(x = beta_ie,y = beta_iv, fill = Segra)) + geom_tile() + 
+  facet_grid(circle_orange ~ circle_blue + segregation, labeller = labeller(circle_orange = circle_minority.labs, circle_blue = circle_local.labs)) +
+  scale_fill_distiller(palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) +
+  scale_x_discrete( limits=c(0,10, by = 5)) +
+  scale_y_discrete( limits=c(0,10, by = 5)) +
+  xlab("ß ethnic") + ylab("ß value") + ggtitle("Square blue, equal ethnic size") + 
+  theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0), 
+                      panel.spacing.x  = unit(0.2, "lines"),panel.spacing.y  = unit(0.1, "lines") )
+
+sqrbmj <- dataone %>%  filter(fraction_blue == 80) %>%  gather(key = subgroup, value = Segra, eth_sq_bl,val_sq_bl) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"Value" = "val_sq_bl","Ethnic" = "eth_sq_bl"), "Value"))  %>%
+  ggplot(aes(x = beta_ie,y = beta_iv, fill = Segra)) + geom_tile() + 
+  facet_grid(circle_orange ~ circle_blue + segregation, labeller = labeller(circle_orange = circle_minority.labs, circle_blue = circle_local.labs)) +
+  scale_fill_distiller(palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) +
+  scale_x_discrete( limits=c(0,10, by = 5)) +
+  scale_y_discrete( limits=c(0,10, by = 5)) +
+  xlab("ß ethnic") + ylab("ß value") + ggtitle("Square blue, ethnic majority") + 
+  theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0), 
+                      panel.spacing.x  = unit(0.2, "lines"),panel.spacing.y  = unit(0.1, "lines") )
+
+#grid.arrange(grob(sqroeq),grob(sqromj), ncol =  1, common.legend = TRUE,legend = "bottom")
+
+ sqrbeq
+ sqrbmj
+```
+
+```{r crlb, fig.pos="t",out.width='\\textwidth',fig.show = "hold",fig.pos='t',fig.align='center',fig.show="hold", fig.cap="", echo=FALSE, include=TRUE  }
+
+ circle_local.labs <- c("20% Circle \nMajority", "50% Circle \nMajority","80% Circle \nMajority")
+names(circle_local.labs) <- c("20", "50","80")
+ circle_minority.labs <-  c("20% Circle \nMinority", "50% Circle \nMinority","80% Circle \nMinority")
+names(circle_minority.labs) <- c("20", "50","80")
+
+crlbeq <- dataone %>%  filter(fraction_blue == 50) %>%  gather(key = subgroup, value = Segra, eth_cl_bl,val_cl_bl) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"Value" = "val_cl_bl","Ethnic" = "eth_cl_bl"), "Value"))  %>%
+  ggplot(aes(x = beta_ie,y = beta_iv, fill = Segra)) + geom_tile() + 
+  facet_grid(circle_orange ~ circle_blue + segregation, labeller = labeller(circle_orange = circle_minority.labs, circle_blue = circle_local.labs)) +
+  scale_fill_distiller(palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) +
+  scale_x_discrete( limits=c(0,10, by = 5)) +
+  scale_y_discrete( limits=c(0,10, by = 5)) +
+  xlab("ß ethnic") + ylab("ß value") + ggtitle("Circle blue, equal ethnic size") + 
+  theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0), 
+                      panel.spacing.x  = unit(0.2, "lines"),panel.spacing.y  = unit(0.1, "lines") )
+
+crlbmj <- dataone %>%  filter(fraction_blue == 80) %>%  gather(key = subgroup, value = Segra, eth_cl_bl,val_cl_bl) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"Value" = "val_cl_bl","Ethnic" = "eth_cl_bl"), "Value"))  %>%
+  ggplot(aes(x = beta_ie,y = beta_iv, fill = Segra)) + geom_tile() + 
+  facet_grid(circle_orange ~ circle_blue + segregation, labeller = labeller(circle_orange = circle_minority.labs, circle_blue = circle_local.labs)) +
+  scale_fill_distiller(palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) +
+  scale_x_discrete( limits=c(0,10, by = 5)) +
+  scale_y_discrete( limits=c(0,10, by = 5)) +
+  xlab("ß ethnic") + ylab("ß value") + ggtitle("Cirle blue, ethnic majority") + 
+  theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0), 
+                      panel.spacing.x  = unit(0.2, "lines"),panel.spacing.y  = unit(0.1, "lines") )
+
+#grid.arrange(grob(sqroeq),grob(sqromj), ncol =  1, common.legend = TRUE,legend = "bottom")
+
+ crlbeq
+ crlbmj
 ```
@@
 Each graph is one level of $\%$ circle (value 1) in the local population (majority = blue agents). Each condition panel refers to distribution of  circle agents in the minority population.
-
-<!--
-```{r squaret, fig.pos="h", out.width="98%",fig.align='center',fig.show="hold", fig.cap="Square population, 20\\% Majority Circle, equal ethnic (above), minority-majority (below)", echo=FALSE, include=TRUE }
-
-knitr::include_graphics("square20.png")
-
-```
-
-```{r squaref, fig.pos="h", out.width="98%",fig.align='center',fig.show="hold", fig.cap="Square population, 50\\% Majority Circle, equal ethnic (above), minority-majority (below)", echo=FALSE, include=TRUE }
-
-knitr::include_graphics("square50.png")
-
-```
-
-```{r squareg, fig.pos="h", out.width="98%",fig.align='center',fig.show="hold", fig.cap="Square population, 80\\% Majority Circle, equal ethnic (above), minority-majority (below)", echo=FALSE, include=TRUE }
-
-knitr::include_graphics("square80.png")
-
-```
-
-```{r circlet, fig.pos="h", out.width="98%",fig.align='center',fig.show="hold", fig.cap="Circle population, 20\\% Majority Circle, equal ethnic (above), minority-majority (below)", echo=FALSE, include=TRUE }
-
-knitr::include_graphics("circle20.png")
-
-```
-
-```{r circlef, fig.pos="h", out.width="98%",fig.align='center',fig.show="hold", fig.cap="Circle population, 50\\% Majority Circle, equal ethnic (above), minority-majority (below)", echo=FALSE, include=TRUE }
-
-knitr::include_graphics("circle50.png")
-
-```
-
-```{r circleg, fig.pos="h", out.width="98%",fig.align='center',fig.show="hold", fig.cap="Circle population, 80\\% Majority Circle, equal ethnic (above), minority-majority (below)", echo=FALSE, include=TRUE }
-
-knitr::include_graphics("circle80.png")
-
-```
-
--->
 
@@
 ```
-
-<!--
-```{r local_circle, fig.height=8.8, fig.pos="t", include=TRUE, fig.cap="Segregation of circle local equal ethnic, baseline in boldline", echo=FALSE}
-
-# gen_eq <- filter(dataone, fraction_blue == 50 & step == 1000)
-# gen_mj <- filter(dataone, fraction_blue == 80 & step == 1000)
-
- circle_local.labs <- c("20% Local Circle", "50% Local Circle","80% Local Circle")
-names(circle_local.labs) <- c("20", "50","80")
- circle_minority.labs <-  c("20% Minority Circle", "50% Minority Circle","80% Minority Circle")
-names(circle_minority.labs) <- c("20", "50","80")
-
-# eth_mj <- ggplot(gen_mj, aes( beta_iv, beta_ie,fill= eth_seg))
-# val_mj <- ggplot(gen_mj, aes( beta_iv, beta_ie,fill= val_seg))
-#
-
-eth_cl_blue <- ggplot(data=subset(dataone,fraction_blue == 50 & step == 1000), aes( beta_ie, beta_iv,fill= eth_cl_bl)) + geom_tile() +   facet_grid(circle_orange  ~  circle_blue,  space = "free_x", labeller = labeller(circle_blue = circle_local.labs,  circle_orange = circle_minority.labs ))  +
-  scale_fill_distiller(name = "ETHNIC",palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) + 
-  scale_x_discrete(name = "ß ethnic", limits=seq(0,10 ,by = 1)) + 
-  scale_y_discrete(name = "ß value", limits=c(0,3,5,7,10)) + 
-  theme_bw() + theme(strip.text.x = element_text(), legend.position = "right", panel.grid.minor.x = element_blank(), plot.title=element_blank(),  legend.margin=margin(0,0,0,0)) +
-  geom_rect(data=subset(dataone,fraction_blue == 50 & step == 1000 & circle_orange == 50 & circle_blue == 50),aes(xmin = -1,xmax = 12, ymin = -1, ymax = 11),colour="black",size =2,alpha = 0)
-
-val_cl_blue <- ggplot(data=subset(dataone,fraction_blue == 50 & step == 1000), aes( beta_ie, beta_iv,fill= val_cl_bl)) + geom_tile() +   facet_grid(circle_orange  ~  circle_blue,  space = "free_x", labeller = labeller(circle_blue = circle_local.labs,  circle_orange = circle_minority.labs )) +
-  scale_fill_distiller(name = "VALUE",palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) + 
-  scale_x_discrete(name = "ß ethnic", limits=seq(0,10 ,by = 1)) + 
-  scale_y_discrete(name = "ß value", limits=c(0,3,5,7,10))  + 
-  theme_bw() + theme(strip.text.x = element_text(), legend.position = "right", panel.grid.minor.x = element_blank(), plot.title=element_blank(),  legend.margin=margin(0,0,0,0)) +
-  geom_rect(data=subset(dataone,fraction_blue == 50 & step == 1000 & circle_orange == 50 & circle_blue == 50),aes(xmin = -1,xmax = 12, ymin = -1, ymax = 11),colour="black",size =2,alpha = 0)
-
-cl_bl <- annotate_figure(ggarrange(eth_cl_blue , ggarrange(val_cl_blue), nrow = 2), top = text_grob("Segregation circle local, Local:Minority = 0.5:0.5",face = "bold", size = 12))
-cl_bl
-```
-
-```{r min_square, fig.height=8.8, fig.pos="t", include=TRUE, fig.cap="Segregation of squared minority, baseline in boldline", echo=FALSE}
-
-# gen_eq <- filter(dataone, fraction_blue == 50 & step == 1000)
-# gen_mj <- filter(dataone, fraction_blue == 80 & step == 1000)
-
- circle_local.labs <- c("20% Local Circle", "50% Local Circle","80% Local Circle")
-names(circle_local.labs) <- c("20", "50","80")
- circle_minority.labs <-  c("20% Minority Circle", "50% Minority Circle","80% Minority Circle")
-names(circle_minority.labs) <- c("20", "50","80")
-
-# eth_mj <- ggplot(gen_mj, aes( beta_iv, beta_ie,fill= eth_seg))
-# val_mj <- ggplot(gen_mj, aes( beta_iv, beta_ie,fill= val_seg))
-#
-
-eth_sq_org <- ggplot(data=subset(dataone,fraction_blue == 50 & step == 1000), aes( beta_ie, beta_iv,fill= eth_sq_or)) + geom_tile() +   facet_grid(circle_orange  ~  circle_blue,  space = "free_x", labeller = labeller(circle_blue = circle_local.labs,  circle_orange = circle_minority.labs ))  +
-  scale_fill_distiller(name = "ETHNIC",palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) + 
-  scale_x_discrete(name = "ß ethnic", limits=seq(0,10 ,by = 1)) + 
-  scale_y_discrete(name = "ß value", limits=c(0,3,5,7,10)) + 
-  theme_bw() + theme(strip.text.x = element_text(), legend.position = "right", panel.grid.minor.x = element_blank(), plot.title=element_blank(),  legend.margin=margin(0,0,0,0)) +
-  geom_rect(data=subset(dataone,fraction_blue == 50 & step == 1000 & circle_orange == 50 & circle_blue == 50),aes(xmin = -1,xmax = 12, ymin = -1, ymax = 11),colour="black",size =2,alpha = 0)
-
-val_sq_org <- ggplot(data=subset(dataone,fraction_blue == 50 & step == 1000), aes( beta_ie, beta_iv,fill= val_sq_or)) + geom_tile() +   facet_grid(circle_orange  ~  circle_blue,  space = "free_x", labeller = labeller(circle_blue = circle_local.labs,  circle_orange = circle_minority.labs )) +
-  scale_fill_distiller(name = "VALUE",palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) + 
-  scale_x_discrete(name = "ß ethnic", limits=seq(0,10 ,by = 1)) + 
-  scale_y_discrete(name = "ß value", limits=c(0,3,5,7,10))  + 
-  theme_bw() + theme(strip.text.x = element_text(), legend.position = "right", panel.grid.minor.x = element_blank(), plot.title=element_blank(),  legend.margin=margin(0,0,0,0)) +
-  geom_rect(data=subset(dataone,fraction_blue == 50 & step == 1000 & circle_orange == 50 & circle_blue == 50),aes(xmin = -1,xmax = 12, ymin = -1, ymax = 11),colour="black",size =2,alpha = 0)
-
-sq_org <- annotate_figure(ggarrange(eth_sq_org , ggarrange(val_sq_org), nrow = 2), top = text_grob("Segregation squared minority, Local:Minority = 0.5:0.5",face = "bold", size = 12))
-sq_org
-```
-
-```{r min_circle, fig.height=8.8, fig.pos="t", include=TRUE, fig.cap="Segregation of circle local ethnic equal, baseline in boldline", echo=FALSE}
-
-# gen_eq <- filter(dataone, fraction_blue == 50 & step == 1000)
-# gen_mj <- filter(dataone, fraction_blue == 80 & step == 1000)
-
- circle_local.labs <- c("20% Local Circle", "50% Local Circle","80% Local Circle")
-names(circle_local.labs) <- c("20", "50","80")
- circle_minority.labs <-  c("20% Minority Circle", "50% Minority Circle","80% Minority Circle")
-names(circle_minority.labs) <- c("20", "50","80")
-
-# eth_mj <- ggplot(gen_mj, aes( beta_iv, beta_ie,fill= eth_seg))
-# val_mj <- ggplot(gen_mj, aes( beta_iv, beta_ie,fill= val_seg))
-#
-
-eth_cl_org <- ggplot(data=subset(dataone,fraction_blue == 50 & step == 1000), aes( beta_ie, beta_iv,fill= eth_cl_or)) + geom_tile() +   facet_grid(circle_orange  ~  circle_blue,  space = "free_x", labeller = labeller(circle_blue = circle_local.labs,  circle_orange = circle_minority.labs ))  +
-  scale_fill_distiller(name = "ETHNIC",palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) + 
-  scale_x_discrete(name = "ß ethnic", limits=seq(0,10 ,by = 1)) + 
-  scale_y_discrete(name = "ß value", limits=c(0,3,5,7,10)) + 
-  theme_bw() + theme(strip.text.x = element_text(), legend.position = "right", panel.grid.minor.x = element_blank(), plot.title=element_blank(),  legend.margin=margin(0,0,0,0)) +
-  geom_rect(data=subset(dataone,fraction_blue == 50 & step == 1000 & circle_orange == 50 & circle_blue == 50),aes(xmin = -1,xmax = 12, ymin = -1, ymax = 11),colour="black",size =2,alpha = 0)
-
-val_cl_org <- ggplot(data=subset(dataone,fraction_blue == 50 & step == 1000), aes( beta_ie, beta_iv,fill= val_cl_or)) + geom_tile() +   facet_grid(circle_orange  ~  circle_blue,  space = "free_x", labeller = labeller(circle_blue = circle_local.labs,  circle_orange = circle_minority.labs )) +
-  scale_fill_distiller(name = "VALUE",palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) + 
-  scale_x_discrete(name = "ß ethnic", limits=seq(0,10 ,by = 1)) + 
-  scale_y_discrete(name = "ß value", limits=c(0,3,5,7,10))  + 
-  theme_bw() + theme(strip.text.x = element_text(), legend.position = "right", panel.grid.minor.x = element_blank(), plot.title=element_blank(),  legend.margin=margin(0,0,0,0)) +
-  geom_rect(data=subset(dataone,fraction_blue == 50 & step == 1000 & circle_orange == 50 & circle_blue == 50),aes(xmin = -1,xmax = 12, ymin = -1, ymax = 11),colour="black",size =2,alpha = 0)
-
-cl_org <- annotate_figure(ggarrange(eth_cl_org , ggarrange(val_cl_org), nrow = 2), top = text_grob("Segregation circle minority, Local:Minority = 0.5:0.5",face = "bold", size = 12))
-cl_org
-```
-
-```{r maj_local_square, fig.height=8.8, fig.pos="t", include=TRUE, fig.cap="Segregation of squared local, baseline in boldline", echo=FALSE}
-
-# gen_eq <- filter(dataone, fraction_blue == 50 & step == 1000)
-# gen_mj <- filter(dataone, fraction_blue == 80 & step == 1000)
-
- circle_local.labs <- c("20% Local Circle", "50% Local Circle","80% Local Circle")
-names(circle_local.labs) <- c("20", "50","80")
- circle_minority.labs <-  c("20% Minority Circle", "50% Minority Circle","80% Minority Circle")
-names(circle_minority.labs) <- c("20", "50","80")
-
-# eth_mj <- ggplot(gen_mj, aes( beta_iv, beta_ie,fill= eth_seg))
-# val_mj <- ggplot(gen_mj, aes( beta_iv, beta_ie,fill= val_seg))
-#
-
-maj_eth_sq_blue <- ggplot(data=subset(dataone,fraction_blue == 80 & step == 1000), aes( beta_ie, beta_iv,fill= eth_sq_bl)) + geom_tile() +   facet_grid(circle_orange  ~  circle_blue,  space = "free_x", labeller = labeller(circle_blue = circle_local.labs,  circle_orange = circle_minority.labs ))  +
-  scale_fill_distiller(name = "ETHNIC",palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) + 
-  scale_x_discrete(name = "ß ethnic", limits=seq(0,10 ,by = 1)) + 
-  scale_y_discrete(name = "ß value", limits=c(0,3,5,7,10)) + 
-  theme_bw() + theme(strip.text.x = element_text(), legend.position = "right", panel.grid.minor.x = element_blank(), plot.title=element_blank(),  legend.margin=margin(0,0,0,0)) +
-  geom_rect(data=subset(dataone,fraction_blue == 80 & step == 1000 & circle_orange == 50 & circle_blue == 50),aes(xmin = -1,xmax = 12, ymin = -1, ymax = 11),colour="black",size =2,alpha = 0)
-
-maj_val_sq_blue <- ggplot(data=subset(dataone,fraction_blue == 80 & step == 1000), aes( beta_ie, beta_iv,fill= val_sq_bl)) + geom_tile() +   facet_grid(circle_orange  ~  circle_blue,  space = "free_x", labeller = labeller(circle_blue = circle_local.labs,  circle_orange = circle_minority.labs )) +
-  scale_fill_distiller(name = "VALUE",palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) + 
-  scale_x_discrete(name = "ß ethnic", limits=seq(0,10 ,by = 1)) + 
-  scale_y_discrete(name = "ß value", limits=c(0,3,5,7,10))  + 
-  theme_bw() + theme(strip.text.x = element_text(), legend.position = "right", panel.grid.minor.x = element_blank(), plot.title=element_blank(),  legend.margin=margin(0,0,0,0)) +
-  geom_rect(data=subset(dataone,fraction_blue == 80 & step == 1000 & circle_orange == 50 & circle_blue == 50),aes(xmin = -1,xmax = 12, ymin = -1, ymax = 11),colour="black",size =2,alpha = 0)
-
-maj_sq_bl <- annotate_figure(ggarrange(maj_eth_sq_blue , ggarrange(maj_val_sq_blue), nrow = 2), top = text_grob("Segregation squared local, Local:Minority = 0.8:0.2",face = "bold", size = 12))
-
-maj_sq_bl
-```
-
-```{r maj_local_circle, fig.height=8.8, fig.pos="t", include=TRUE, fig.cap="Segregation of circle local, baseline in boldline", echo=FALSE}
-
-# gen_eq <- filter(dataone, fraction_blue == 50 & step == 1000)
-# gen_mj <- filter(dataone, fraction_blue == 80 & step == 1000)
-
- circle_local.labs <- c("20% Local Circle", "50% Local Circle","80% Local Circle")
-names(circle_local.labs) <- c("20", "50","80")
- circle_minority.labs <-  c("20% Minority Circle", "50% Minority Circle","80% Minority Circle")
-names(circle_minority.labs) <- c("20", "50","80")
-
-# eth_mj <- ggplot(gen_mj, aes( beta_iv, beta_ie,fill= eth_seg))
-# val_mj <- ggplot(gen_mj, aes( beta_iv, beta_ie,fill= val_seg))
-#
-
-maj_eth_cl_blue <- ggplot(data=subset(dataone,fraction_blue == 80 & step == 1000), aes( beta_ie, beta_iv,fill= eth_cl_bl)) + geom_tile() +   facet_grid(circle_orange  ~  circle_blue,  space = "free_x", labeller = labeller(circle_blue = circle_local.labs,  circle_orange = circle_minority.labs ))  +
-  scale_fill_distiller(name = "ETHNIC",palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) + 
-  scale_x_discrete(name = "ß ethnic", limits=seq(0,10 ,by = 1)) + 
-  scale_y_discrete(name = "ß value", limits=c(0,3,5,7,10)) + 
-  theme_bw() + theme(strip.text.x = element_text(), legend.position = "right", panel.grid.minor.x = element_blank(), plot.title=element_blank(),  legend.margin=margin(0,0,0,0)) +
-  geom_rect(data=subset(dataone,fraction_blue == 80 & step == 1000 & circle_orange == 50 & circle_blue == 50),aes(xmin = -1,xmax = 12, ymin = -1, ymax = 11),colour="black",size =2,alpha = 0)
-
-maj_val_cl_blue <- ggplot(data=subset(dataone,fraction_blue == 80 & step == 1000), aes( beta_ie, beta_iv,fill= val_cl_bl)) + geom_tile() +   facet_grid(circle_orange  ~  circle_blue,  space = "free_x", labeller = labeller(circle_blue = circle_local.labs,  circle_orange = circle_minority.labs )) +
-  scale_fill_distiller(name = "VALUE",palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) + 
-  scale_x_discrete(name = "ß ethnic", limits=seq(0,10 ,by = 1)) + 
-  scale_y_discrete(name = "ß value", limits=c(0,3,5,7,10))  + 
-  theme_bw() + theme(strip.text.x = element_text(), legend.position = "right", panel.grid.minor.x = element_blank(), plot.title=element_blank(),  legend.margin=margin(0,0,0,0)) +
-  geom_rect(data=subset(dataone,fraction_blue == 80 & step == 1000 & circle_orange == 50 & circle_blue == 50),aes(xmin = -1,xmax = 12, ymin = -1, ymax = 11),colour="black",size =2,alpha = 0)
-
-maj_cl_bl <- annotate_figure(ggarrange(maj_eth_cl_blue , ggarrange(maj_val_cl_blue), nrow = 2), top = text_grob("Segregation circle local, Local:Minority = 0.8:0.2",face = "bold", size = 12))
-maj_cl_bl
-
-```
-
-```{r maj_min_square, fig.height=8.8, fig.pos="t", include=TRUE, fig.cap="Segregation of squared local, baseline in boldline", echo=FALSE}
-
-# gen_eq <- filter(dataone, fraction_blue == 50 & step == 1000)
-# gen_mj <- filter(dataone, fraction_blue == 80 & step == 1000)
-
- circle_local.labs <- c("20% Local Circle", "50% Local Circle","80% Local Circle")
-names(circle_local.labs) <- c("20", "50","80")
- circle_minority.labs <-  c("20% Minority Circle", "50% Minority Circle","80% Minority Circle")
-names(circle_minority.labs) <- c("20", "50","80")
-
-# eth_mj <- ggplot(gen_mj, aes( beta_iv, beta_ie,fill= eth_seg))
-# val_mj <- ggplot(gen_mj, aes( beta_iv, beta_ie,fill= val_seg))
-#
-
-maj_eth_sq_org <- ggplot(data=subset(dataone,fraction_blue == 80 & step == 1000), aes( beta_ie, beta_iv,fill= eth_sq_or)) + geom_tile() +   facet_grid(circle_orange  ~  circle_blue,  space = "free_x", labeller = labeller(circle_blue = circle_local.labs,  circle_orange = circle_minority.labs ))  +
-  scale_fill_distiller(name = "ETHNIC",palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) + 
-  scale_x_discrete(name = "ß ethnic", limits=seq(0,10 ,by = 1)) + 
-  scale_y_discrete(name = "ß value", limits=c(0,3,5,7,10)) + 
-  theme_bw() + theme(strip.text.x = element_text(), legend.position = "right", panel.grid.minor.x = element_blank(), plot.title=element_blank(),  legend.margin=margin(0,0,0,0)) +
-  geom_rect(data=subset(dataone,fraction_blue == 80 & step == 1000 & circle_orange == 50 & circle_blue == 50),aes(xmin = -1,xmax = 12, ymin = -1, ymax = 11),colour="black",size =2,alpha = 0)
-
-maj_val_sq_org <- ggplot(data=subset(dataone,fraction_blue == 80 & step == 1000), aes( beta_ie, beta_iv,fill= val_sq_or)) + geom_tile() +   facet_grid(circle_orange  ~  circle_blue,  space = "free_x", labeller = labeller(circle_blue = circle_local.labs,  circle_orange = circle_minority.labs )) +
-  scale_fill_distiller(name = "VALUE",palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) + 
-  scale_x_discrete(name = "ß ethnic", limits=seq(0,10 ,by = 1)) + 
-  scale_y_discrete(name = "ß value", limits=c(0,3,5,7,10))  + 
-  theme_bw() + theme(strip.text.x = element_text(), legend.position = "right", panel.grid.minor.x = element_blank(), plot.title=element_blank(),  legend.margin=margin(0,0,0,0)) +
-  geom_rect(data=subset(dataone,fraction_blue == 80 & step == 1000 & circle_orange == 50 & circle_blue == 50),aes(xmin = -1,xmax = 12, ymin = -1, ymax = 11),colour="black",size =2,alpha = 0)
-
-maj_sq_org <- annotate_figure(ggarrange(maj_eth_sq_org , ggarrange(maj_val_sq_org), nrow = 2), top = text_grob("Segregation squared minority, Local:Minority = 0.8:0.2",face = "bold", size = 12))
-maj_sq_org
-
-```
-
-```{r maj_min_circle, fig.height=8.8, fig.pos="t", include=TRUE, fig.cap="Segregation of circle local, baseline in boldline", echo=FALSE}
-
-# gen_eq <- filter(dataone, fraction_blue == 50 & step == 1000)
-# gen_mj <- filter(dataone, fraction_blue == 80 & step == 1000)
-
- circle_local.labs <- c("20% Local Circle", "50% Local Circle","80% Local Circle")
-names(circle_local.labs) <- c("20", "50","80")
- circle_minority.labs <-  c("20% Minority Circle", "50% Minority Circle","80% Minority Circle")
-names(circle_minority.labs) <- c("20", "50","80")
-
-# eth_mj <- ggplot(gen_mj, aes( beta_iv, beta_ie,fill= eth_seg))
-# val_mj <- ggplot(gen_mj, aes( beta_iv, beta_ie,fill= val_seg))
-#
-
-maj_eth_cl_org <- ggplot(data=subset(dataone,fraction_blue == 80 & step == 1000), aes( beta_ie, beta_iv,fill= eth_cl_or)) + geom_tile() +   facet_grid(circle_orange  ~  circle_blue,  space = "free_x", labeller = labeller(circle_blue = circle_local.labs,  circle_orange = circle_minority.labs ))  +
-  scale_fill_distiller(name = "ETHNIC",palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) + 
-  scale_x_discrete(name = "ß ethnic", limits=seq(0,10 ,by = 1)) + 
-  scale_y_discrete(name = "ß value", limits=c(0,3,5,7,10)) + 
-  theme_bw() + theme(strip.text.x = element_text(), legend.position = "right", panel.grid.minor.x = element_blank(), plot.title=element_blank(),  legend.margin=margin(0,0,0,0)) +
-  geom_rect(data=subset(dataone,fraction_blue == 80 & step == 1000 & circle_orange == 50 & circle_blue == 50),aes(xmin = -1,xmax = 12, ymin = -1, ymax = 11),colour="black",size =2,alpha = 0)
-
-maj_val_cl_org <- ggplot(data=subset(dataone,fraction_blue == 80 & step == 1000), aes( beta_ie, beta_iv,fill= val_cl_or)) + geom_tile() +   facet_grid(circle_orange  ~  circle_blue,  space = "free_x", labeller = labeller(circle_blue = circle_local.labs,  circle_orange = circle_minority.labs )) +
-  scale_fill_distiller(name = "VALUE",palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) + 
-  scale_x_discrete(name = "ß ethnic", limits=seq(0,10 ,by = 1)) + 
-  scale_y_discrete(name = "ß value", limits=c(0,3,5,7,10))  + 
-  theme_bw() + theme(strip.text.x = element_text(), legend.position = "right", panel.grid.minor.x = element_blank(), plot.title=element_blank(),  legend.margin=margin(0,0,0,0)) +
-  geom_rect(data=subset(dataone,fraction_blue == 80 & step == 1000 & circle_orange == 50 & circle_blue == 50),aes(xmin = -1,xmax = 12, ymin = -1, ymax = 11),colour="black",size =2,alpha = 0)
-
-maj_cl_org <- annotate_figure(ggarrange(maj_eth_cl_org , ggarrange(maj_val_cl_org), nrow = 2), top = text_grob("Segregation circle minority, Local:Minority = 0.8:0.2",face = "bold", size = 12))
-maj_cl_org
-```
--->
-
-<!--
-```{r testnormdelete, echo=FALSE, include= FALSE}
-
-nrml <- function(mx,mn,x){
-
-  s <-  ((x - mn) / (mx-mn))
-}
-
- bt_10 <- for (x in seq(0,5,by=1)) {
-
-  mx <- 5
-  mn <- 0
-
-  s <- nrml(mx,mn,x)
-  print(c(x,s))
-
-}
-
- bt_5 <- for (x in seq(0,5,by=1)) {
-
-  mx <- 5
-  mn <- 0
-
-  s <- nrml(mx,mn,x)
-  print(c(x,s))
-
-}
-
-```
-
--->

### 2020-05-02 exp_eth_val.Rmd
Add files via upload

@@
 
-```
+dataone$rev_circle_orange <- fct_rev(factor(dataone$circle_orange))
+dataone$rev_circle_blue <- fct_rev(factor(dataone$circle_blue))
 
-```{r ethnicp, fig.pos="h!", out.width="98%",fig.align='center',fig.show="hold", fig.cap="prep fig ethnic population", echo=FALSE, include=FALSE}
+datatwo$rev_beta_iv_circle <- fct_rev(factor(datatwo$beta_iv_circle))
+datatwo$rev_beta_ie_square <- fct_rev(factor(datatwo$beta_ie_square))
 
-circle_local.labs <- c("20% Local Circle", "50% Local Circle","80% Local Circle")
-names(circle_local.labs) <- c("20", "50","80")
- circle_minority.labs <-  c("20% Minority Circle", "50% Minority Circle","80% Minority Circle")
-names(circle_minority.labs) <- c("20", "50","80")
-circle_minority.labs <-  c("20% \nMinority Circle", "50% \nMinority Circle","80% \nMinority Circle")
-names(circle_minority.labs) <- c("20", "50","80")
+  rev_circle_blue.labs <- c("80% Circle \nBlue" ,"50% Circle \nBlue","20% Circle \nBlue")
+names(rev_circle_blue.labs) <- c("80", "50","20")
+ rev_circle_orange.labs <-  c("80% Circle \nOrange", "50% Circle \nOrange","20% Circle \nOrange")
+names(rev_circle_orange.labs) <- c("80", "50","20")
 
-mj_e20 <- dataone %>% filter(step == 1000 & fraction_blue == 50 & circle_blue == 20) %>%  
-  gather(key = square, value = Segra, eth_sq_bl,val_sq_bl,eth_cl_bl,val_cl_bl) %>% 
-  mutate("segregation" = fct_relevel(fct_collapse(square,"ethnic segregation" = c("eth_sq_bl","eth_cl_bl"), "value segregation" = c("val_sq_bl","val_cl_bl")), "ethnic segregation"), "group" = fct_relevel(fct_collapse(square, "majority squared" = c("eth_sq_bl","val_sq_bl"), "majority circle" = c("eth_cl_bl","val_cl_bl")),"majority squared")) %>%
-  ggplot(aes(x = beta_ie,y = beta_iv, fill = Segra)) + geom_tile() + 
-  facet_grid(circle_orange ~ group + segregation, labeller = labeller(circle_orange = circle_minority.labs)) +
-  scale_fill_distiller(palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) +
-  scale_x_discrete( limits=c(0,10, by = 5)) +
-  scale_y_discrete( limits=c(0,10, by = 5)) +
-  xlab("ß ethnic") + ylab("ß value") + ggtitle("Majority population, Majority:Minority = .5:.5, 20% Majority Circle") + 
-  theme_bw() +  theme(legend.position = "right", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0))
-
-mj_m20 <- dataone %>% filter(step == 1000 & fraction_blue == 80 & circle_blue == 20) %>%  
-  gather(key = square, value = Segra, eth_sq_bl,val_sq_bl,eth_cl_bl,val_cl_bl) %>% 
-  mutate("segregation" = fct_relevel(fct_collapse(square,"ethnic segregation" = c("eth_sq_bl","eth_cl_bl"), "value segregation" = c("val_sq_bl","val_cl_bl")), "ethnic segregation"), "group" = fct_relevel(fct_collapse(square, "majority squared" = c("eth_sq_bl","val_sq_bl"), "majority circle" = c("eth_cl_bl","val_cl_bl")),"majority squared")) %>%
-  ggplot(aes(x = beta_ie,y = beta_iv, fill = Segra)) + geom_tile() + 
-  facet_grid(circle_orange ~ group + segregation, labeller = labeller(circle_orange = circle_minority.labs)) +
-  scale_fill_distiller(palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) +
-  scale_x_discrete( limits=c(0,10, by = 5)) +
-  scale_y_discrete( limits=c(0,10, by = 5)) +
-  xlab("ß ethnic") + ylab("ß value") + ggtitle("Majority population, Majority:Minority = .8:.2, 20% Majority Circle") + 
-  theme_bw() +  theme(legend.position = "right", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0))
-
- ggsave("mj_e20.png",mj_e20)
- ggsave("mj_m20.png",mj_m20)
-# a <- image_read("pl_sq_e20.png")
-# b <- image_read("pl_sq_m20.png")
-
-#knitr::include_graphics(c("pl_sq_e20.png","pl_sq_m20.png"))
-
-img <-c(image_read("mj_e20.png"),image_read("mj_m20.png"))
-c <- image_append(img, stack = TRUE)
-image_write(c, path = "majo20.png", format = "png")
-
-#
-
-mj_e50 <- dataone %>% filter(step == 1000 & fraction_blue == 50 & circle_blue == 50) %>%  
-  gather(key = square, value = Segra, eth_sq_bl,val_sq_bl,eth_cl_bl,val_cl_bl) %>% 
-  mutate("segregation" = fct_relevel(fct_collapse(square,"ethnic segregation" = c("eth_sq_bl","eth_cl_bl"), "value segregation" = c("val_sq_bl","val_cl_bl")), "ethnic segregation"), "group" = fct_relevel(fct_collapse(square, "majority squared" = c("eth_sq_bl","val_sq_bl"), "majority circle" = c("eth_cl_bl","val_cl_bl")),"majority squared")) %>%
-  ggplot(aes(x = beta_ie,y = beta_iv, fill = Segra)) + geom_tile() + 
-  facet_grid(circle_orange ~ group + segregation, labeller = labeller(circle_orange = circle_minority.labs)) +
-  scale_fill_distiller(palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) +
-  scale_x_discrete( limits=c(0,10, by = 5)) +
-  scale_y_discrete( limits=c(0,10, by = 5)) +
-  xlab("ß ethnic") + ylab("ß value") + ggtitle("Majority population, Majority:Minority = .5:.5, 50% Majority Circle") + 
-  theme_bw() +  theme(legend.position = "right", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0))
-
-mj_m50 <- dataone %>% filter(step == 1000 & fraction_blue == 80 & circle_blue == 50) %>%  
-  gather(key = square, value = Segra, eth_sq_bl,val_sq_bl,eth_cl_bl,val_cl_bl) %>% 
-  mutate("segregation" = fct_relevel(fct_collapse(square,"ethnic segregation" = c("eth_sq_bl","eth_cl_bl"), "value segregation" = c("val_sq_bl","val_cl_bl")), "ethnic segregation"), "group" = fct_relevel(fct_collapse(square, "majority squared" = c("eth_sq_bl","val_sq_bl"), "majority circle" = c("eth_cl_bl","val_cl_bl")),"majority squared")) %>%
-  ggplot(aes(x = beta_ie,y = beta_iv, fill = Segra)) + geom_tile() + 
-  facet_grid(circle_orange ~ group + segregation, labeller = labeller(circle_orange = circle_minority.labs)) +
-  scale_fill_distiller(palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) +
-  scale_x_discrete( limits=c(0,10, by = 5)) +
-  scale_y_discrete( limits=c(0,10, by = 5)) +
-  xlab("ß ethnic") + ylab("ß value") + ggtitle("Majority population, Majority:Minority = .8:.2, 50% Majority Circle") + 
-  theme_bw() +  theme(legend.position = "right", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0))
-
- ggsave("mj_e50.png",mj_e50)
- ggsave("mj_m50.png",mj_m50)
-# a <- image_read("pl_sq_e20.png")
-# b <- image_read("pl_sq_m20.png")
-
-#knitr::include_graphics(c("pl_sq_e20.png","pl_sq_m20.png"))
-
-img <-c(image_read("mj_e50.png"),image_read("mj_m50.png"))
-c <- image_append(img, stack = TRUE)
-image_write(c, path = "majo50.png", format = "png")
-
-#
-
-mj_e80 <- dataone %>% filter(step == 1000 & fraction_blue == 50 & circle_blue == 80) %>%  
-  gather(key = square, value = Segra, eth_sq_bl,val_sq_bl,eth_cl_bl,val_cl_bl) %>% 
-  mutate("segregation" = fct_relevel(fct_collapse(square,"ethnic segregation" = c("eth_sq_bl","eth_cl_bl"), "value segregation" = c("val_sq_bl","val_cl_bl")), "ethnic segregation"), "group" = fct_relevel(fct_collapse(square, "majority squared" = c("eth_sq_bl","val_sq_bl"), "majority circle" = c("eth_cl_bl","val_cl_bl")),"majority squared")) %>%
-  ggplot(aes(x = beta_ie,y = beta_iv, fill = Segra)) + geom_tile() + 
-  facet_grid(circle_orange ~ group + segregation, labeller = labeller(circle_orange = circle_minority.labs)) +
-  scale_fill_distiller(palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) +
-  scale_x_discrete( limits=c(0,10, by = 5)) +
-  scale_y_discrete( limits=c(0,10, by = 5)) +
-  xlab("ß ethnic") + ylab("ß value") + ggtitle("Majority population, Majority:Minority = .5:.5, 80% Majority Circle") + 
-  theme_bw() +  theme(legend.position = "right", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0))
-
-mj_m80 <- dataone %>% filter(step == 1000 & fraction_blue == 80 & circle_blue == 80) %>%  
-  gather(key = square, value = Segra, eth_sq_bl,val_sq_bl,eth_cl_bl,val_cl_bl) %>% 
-  mutate("segregation" = fct_relevel(fct_collapse(square,"ethnic segregation" = c("eth_sq_bl","eth_cl_bl"), "value segregation" = c("val_sq_bl","val_cl_bl")), "ethnic segregation"), "group" = fct_relevel(fct_collapse(square, "majority squared" = c("eth_sq_bl","val_sq_bl"), "majority circle" = c("eth_cl_bl","val_cl_bl")),"majority squared")) %>%
-  ggplot(aes(x = beta_ie,y = beta_iv, fill = Segra)) + geom_tile() + 
-  facet_grid(circle_orange ~ group + segregation, labeller = labeller(circle_orange = circle_minority.labs)) +
-  scale_fill_distiller(palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) +
-  scale_x_discrete( limits=c(0,10, by = 5)) +
-  scale_y_discrete( limits=c(0,10, by = 5)) +
-  xlab("ß ethnic") + ylab("ß value") + ggtitle("Majority population, Majority:Minority = .8:.2, 80% Majority Circle") + 
-  theme_bw() +  theme(legend.position = "right", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0))
-
- ggsave("mj_e80.png",mj_e80)
- ggsave("mj_m80.png",mj_m80)
-# a <- image_read("pl_sq_e20.png")
-# b <- image_read("pl_sq_m20.png")
-
-#knitr::include_graphics(c("pl_sq_e20.png","pl_sq_m20.png"))
-
-img <-c(image_read("mj_e80.png"),image_read("mj_m80.png"))
-c <- image_append(img, stack = TRUE)
-image_write(c, path = "majo80.png", format = "png")
-
-# minority
-
-circle_local.labs <- c("20% Local Circle", "50% Local Circle","80% Local Circle")
-names(circle_local.labs) <- c("20", "50","80")
- circle_minority.labs <-  c("20% Minority Circle", "50% Minority Circle","80% Minority Circle")
-names(circle_minority.labs) <- c("20", "50","80")
-circle_minority.labs <-  c("20% \nMinority Circle", "50% \nMinority Circle","80% \nMinority Circle")
-names(circle_minority.labs) <- c("20", "50","80")
-
-mn_e20 <- dataone %>% filter(step == 1000 & fraction_blue == 50 & circle_blue == 20) %>%  
-  gather(key = square, value = Segra, eth_sq_or,val_sq_or,eth_cl_or,val_cl_or) %>% 
-  mutate("segregation" = fct_relevel(fct_collapse(square,"ethnic segregation" = c("eth_sq_or","eth_cl_or"), "value segregation" = c("val_sq_or","val_cl_or")), "ethnic segregation"), "group" = fct_relevel(fct_collapse(square, "minority squared" = c("eth_sq_or","val_sq_or"), "minority circle" = c("eth_cl_or","val_cl_or")),"minority squared")) %>%
-  ggplot(aes(x = beta_ie,y = beta_iv, fill = Segra)) + geom_tile() + 
-  facet_grid(circle_orange ~ group + segregation, labeller = labeller(circle_orange = circle_minority.labs)) +
-  scale_fill_distiller(palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) +
-  scale_x_discrete( limits=c(0,10, by = 5)) +
-  scale_y_discrete( limits=c(0,10, by = 5)) +
-  xlab("ß ethnic") + ylab("ß value") + ggtitle("Minority population, Majority:Minority = .5:.5, 20% Majority Circle") + 
-  theme_bw() +  theme(legend.position = "right", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0))
-
-mn_m20 <- dataone %>% filter(step == 1000 & fraction_blue == 80 & circle_blue == 20) %>%  
-  gather(key = square, value = Segra, eth_sq_or,val_sq_or,eth_cl_or,val_cl_or) %>% 
-  mutate("segregation" = fct_relevel(fct_collapse(square,"ethnic segregation" = c("eth_sq_or","eth_cl_or"), "value segregation" = c("val_sq_or","val_cl_or")), "ethnic segregation"), "group" = fct_relevel(fct_collapse(square, "minority squared" = c("eth_sq_or","val_sq_or"), "minority circle" = c("eth_cl_or","val_cl_or")),"minority squared")) %>%
-  ggplot(aes(x = beta_ie,y = beta_iv, fill = Segra)) + geom_tile() + 
-  facet_grid(circle_orange ~ group + segregation, labeller = labeller(circle_orange = circle_minority.labs)) +
-  scale_fill_distiller(palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) +
-  scale_x_discrete( limits=c(0,10, by = 5)) +
-  scale_y_discrete( limits=c(0,10, by = 5)) +
-  xlab("ß ethnic") + ylab("ß value") + ggtitle("Minority population, Majority:Minority = .8:.2, 20% Majority Circle") + 
-  theme_bw() +  theme(legend.position = "right", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0))
-
- ggsave("mn_e20.png",mn_e20)
- ggsave("mn_m20.png",mn_m20)
-# a <- image_read("pl_sq_e20.png")
-# b <- image_read("pl_sq_m20.png")
-
-#knitr::include_graphics(c("pl_sq_e20.png","pl_sq_m20.png"))
-
-img <-c(image_read("mn_e20.png"),image_read("mn_m20.png"))
-c <- image_append(img, stack = TRUE)
-image_write(c, path = "min20.png", format = "png")
-
-#
-
-mn_e50 <- dataone %>% filter(step == 1000 & fraction_blue == 50 & circle_blue == 50) %>%  
-  gather(key = square, value = Segra, eth_sq_or,val_sq_or,eth_cl_or,val_cl_or) %>% 
-  mutate("segregation" = fct_relevel(fct_collapse(square,"ethnic segregation" = c("eth_sq_or","eth_cl_or"), "value segregation" = c("val_sq_or","val_cl_or")), "ethnic segregation"), "group" = fct_relevel(fct_collapse(square, "minority squared" = c("eth_sq_or","val_sq_or"), "minority circle" = c("eth_cl_or","val_cl_or")),"minority squared")) %>%
-  ggplot(aes(x = beta_ie,y = beta_iv, fill = Segra)) + geom_tile() + 
-  facet_grid(circle_orange ~ group + segregation, labeller = labeller(circle_orange = circle_minority.labs)) +
-  scale_fill_distiller(palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) +
-  scale_x_discrete( limits=c(0,10, by = 5)) +
-  scale_y_discrete( limits=c(0,10, by = 5)) +
-  xlab("ß ethnic") + ylab("ß value") + ggtitle("Minority population, Majority:Minority = .5:.5, 50% Majority Circle") + 
-  theme_bw() +  theme(legend.position = "right", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0))
-
-mn_m50 <- dataone %>% filter(step == 1000 & fraction_blue == 80 & circle_blue == 50) %>%  
-  gather(key = square, value = Segra, eth_sq_or,val_sq_or,eth_cl_or,val_cl_or) %>% 
-  mutate("segregation" = fct_relevel(fct_collapse(square,"ethnic segregation" = c("eth_sq_or","eth_cl_or"), "value segregation" = c("val_sq_or","val_cl_or")), "ethnic segregation"), "group" = fct_relevel(fct_collapse(square, "minority squared" = c("eth_sq_or","val_sq_or"), "minority circle" = c("eth_cl_or","val_cl_or")),"minority squared")) %>%
-  ggplot(aes(x = beta_ie,y = beta_iv, fill = Segra)) + geom_tile() + 
-  facet_grid(circle_orange ~ group + segregation, labeller = labeller(circle_orange = circle_minority.labs)) +
-  scale_fill_distiller(palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) +
-  scale_x_discrete( limits=c(0,10, by = 5)) +
-  scale_y_discrete( limits=c(0,10, by = 5)) +
-  xlab("ß ethnic") + ylab("ß value") + ggtitle("Minority population, Majority:Minority = .8:.2, 50% Majority Circle") + 
-  theme_bw() +  theme(legend.position = "right", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0))
-
- ggsave("mn_e50.png",mn_e50)
- ggsave("mn_m50.png",mn_m50)
-# a <- image_read("pl_sq_e20.png")
-# b <- image_read("pl_sq_m20.png")
-
-#knitr::include_graphics(c("pl_sq_e20.png","pl_sq_m20.png"))
-
-img <-c(image_read("mn_e50.png"),image_read("mn_m50.png"))
-c <- image_append(img, stack = TRUE)
-image_write(c, path = "min50.png", format = "png")
-
-#
-
-mn_e80 <- dataone %>% filter(step == 1000 & fraction_blue == 50 & circle_blue == 80) %>%  
-  gather(key = square, value = Segra, eth_sq_or,val_sq_or,eth_cl_or,val_cl_or) %>% 
-  mutate("segregation" = fct_relevel(fct_collapse(square,"ethnic segregation" = c("eth_sq_or","eth_cl_or"), "value segregation" = c("val_sq_or","val_cl_or")), "ethnic segregation"), "group" = fct_relevel(fct_collapse(square, "minority squared" = c("eth_sq_or","val_sq_or"), "minority circle" = c("eth_cl_or","val_cl_or")),"minority squared")) %>%
-  ggplot(aes(x = beta_ie,y = beta_iv, fill = Segra)) + geom_tile() + 
-  facet_grid(circle_orange ~ group + segregation, labeller = labeller(circle_orange = circle_minority.labs)) +
-  scale_fill_distiller(palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) +
-  scale_x_discrete( limits=c(0,10, by = 5)) +
-  scale_y_discrete( limits=c(0,10, by = 5)) +
-  xlab("ß ethnic") + ylab("ß value") + ggtitle("Minority population, Majority:Minority = .5:.5, 80% Majority Circle") + 
-  theme_bw() +  theme(legend.position = "right", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0))
-
-mn_m80 <- dataone %>% filter(step == 1000 & fraction_blue == 80 & circle_blue == 80) %>%  
-  gather(key = square, value = Segra, eth_sq_or,val_sq_or,eth_cl_or,val_cl_or) %>% 
-  mutate("segregation" = fct_relevel(fct_collapse(square,"ethnic segregation" = c("eth_sq_or","eth_cl_or"), "value segregation" = c("val_sq_or","val_cl_or")), "ethnic segregation"), "group" = fct_relevel(fct_collapse(square, "minority squared" = c("eth_sq_or","val_sq_or"), "minority circle" = c("eth_cl_or","val_cl_or")),"minority squared")) %>%
-  ggplot(aes(x = beta_ie,y = beta_iv, fill = Segra)) + geom_tile() + 
-  facet_grid(circle_orange ~ group + segregation, labeller = labeller(circle_orange = circle_minority.labs)) +
-  scale_fill_distiller(palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) +
-  scale_x_discrete( limits=c(0,10, by = 5)) +
-  scale_y_discrete( limits=c(0,10, by = 5)) +
-  xlab("ß ethnic") + ylab("ß value") + ggtitle("Minority population, Majority:Minority = .8:.2, 80% Majority Circle") + 
-  theme_bw() +  theme(legend.position = "right", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0))
-
- ggsave("mn_e80.png",mn_e80)
- ggsave("mn_m80.png",mn_m80)
-# a <- image_r
-#knitr::include_graphics(c("pl_sq_e20.png","pl_sq_m20.png"))
-
-img <-c(image_read("mn_e80.png"),image_read("mn_m80.png"))
-c <- image_append(img, stack = TRUE)
-image_write(c, path = "min80.png", format = "png")
+ circle_blue.labs <- c("20% Circle \nBlue", "50% Circle \nBlue","80% Circle \nBlue")
+names(circle_blue.labs) <- c("20", "50","80")
+ circle_orange.labs <-  c("20% Circle \nOrange", "50% Circle \nOrange","80% Circle \nOrange")
+names(circle_orange.labs) <- c("20", "50","80")
 
@@
 
-```{r sqro, fig.pos="t",out.width='\\textwidth',fig.show = "hold",fig.pos='t',fig.align='center',fig.show="hold", fig.cap="", echo=FALSE, include=TRUE  }
+```{r baselineone,fig.pos='t',out.width='\\textwidth',fig.show = "hold",fig.align='center', fig.cap=" Baseline space", echo=FALSE, include=TRUE  }
 
- circle_local.labs <- c("20% Circle \nMajority", "50% Circle \nMajority","80% Circle \nMajority")
-names(circle_local.labs) <- c("20", "50","80")
- circle_minority.labs <-  c("20% Circle \nMinority", "50% Circle \nMinority","80% Circle \nMinority")
-names(circle_minority.labs) <- c("20", "50","80")
+knitr::include_graphics("baseline_1.png")
 
-sqroeq <- dataone %>%  filter(fraction_blue == 50) %>%  gather(key = subgroup, value = Segra, eth_sq_or,val_sq_or) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"Value" = "val_sq_or","Ethnic" = "eth_sq_or"), "Value"))  %>%
-  ggplot(aes(x = beta_ie,y = beta_iv, fill = Segra)) + geom_tile() + 
-  facet_grid(circle_orange ~ circle_blue + segregation, labeller = labeller(circle_orange = circle_minority.labs, circle_blue = circle_local.labs)) +
-  scale_fill_distiller(palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) +
-  scale_x_discrete( limits=c(0,10, by = 5)) +
-  scale_y_discrete( limits=c(0,10, by = 5)) +
-  xlab("ß ethnic") + ylab("ß value") + ggtitle("Square orange, ethnic minority") + 
-  theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0), 
-                      panel.spacing.x  = unit(0.2, "lines"),panel.spacing.y  = unit(0.1, "lines") )
-
-sqromj<- dataone %>%  filter(fraction_blue == 80) %>%  gather(key = subgroup, value = Segra, eth_sq_or,val_sq_or) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"Value" = "val_sq_or","Ethnic" = "eth_sq_or"), "Value"))  %>%
-  ggplot(aes(x = beta_ie,y = beta_iv, fill = Segra)) + geom_tile() + 
-  facet_grid(circle_orange ~ circle_blue + segregation, labeller = labeller(circle_orange = circle_minority.labs, circle_blue = circle_local.labs)) +
-  scale_fill_distiller(palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) +
-  scale_x_discrete( limits=c(0,10, by = 5)) +
-  scale_y_discrete( limits=c(0,10, by = 5)) +
-  xlab("ß ethnic") + ylab("ß value") + ggtitle("Square orange, ethnic minority") + 
-  theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0), 
-                      panel.spacing.x  = unit(0.2, "lines"),panel.spacing.y  = unit(0.1, "lines") )
-
-#grid.arrange(grob(sqroeq),grob(sqromj), ncol =  1, common.legend = TRUE,legend = "bottom")
-
- sqroeq
- sqromj
 ```
 
-```{r crloA, fig.pos="t",out.width='\\textwidth',fig.show = "hold",fig.pos='t',fig.align='center',fig.show="hold", fig.cap="", echo=FALSE, include=TRUE  }
-
-dataone$rev_circle_orange <- fct_rev(factor(dataone$circle_orange))
-
- circle_blue.labs <- c("20% Circle Blue", "50% Circle Blue","80% Circle Blue")
-names(circle_blue.labs) <- c("20", "50","80")
- rev_circle_orange.labs <-  c("80% Circle \nOrange", "50% Circle \nOrange","20% Circle \nOrange")
-names(rev_circle_orange.labs) <- c("80", "50","20")
+```{r crlo,fig.pos='t',out.width='\\textwidth',fig.show = "hold",fig.align='center', fig.cap="Circle orange, first section", echo=FALSE, include=TRUE  }
 
@@
                       panel.spacing.x  = unit(0.2, "lines"),panel.spacing.y  = unit(0.1, "lines") )
- crloeq
 
@@
   ggplot(aes(x = beta_ie,y = beta_iv, fill = Segra)) + geom_tile() + 
-  facet_grid(circle_orange ~ circle_blue + segregation, labeller = labeller(circle_orange = circle_minority.labs, circle_blue = circle_local.labs)) +
+  facet_grid(rev_circle_orange ~ circle_blue + segregation, labeller = labeller(rev_circle_orange = rev_circle_orange.labs, circle_blue = circle_blue.labs), switch  = "y") +
   scale_fill_distiller(palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) +
   scale_x_discrete( limits=c(0,10, by = 5)) +
-  scale_y_discrete( limits=c(0,10, by = 5)) +
+  scale_y_discrete( limits=c(0,10, by = 5), position = "right") +
   xlab("ß ethnic") + ylab("ß value") + ggtitle("Circle orange, ethnic minority") + 
@@
 
-```{r sqrb, fig.pos="t",out.width='\\textwidth',fig.show = "hold",fig.pos='t',fig.align='center',fig.show="hold", fig.cap="", echo=FALSE, include=TRUE  }
+```{r crlblmajority, fig.pos='t',out.width='\\textwidth',fig.show = "hold",fig.align='center',fig.show="hold", fig.cap="Circle in majority condition.", echo=FALSE, include=TRUE}
 
- circle_local.labs <- c("20% Circle \nMajority", "50% Circle \nMajority","80% Circle \nMajority")
-names(circle_local.labs) <- c("20", "50","80")
- circle_minority.labs <-  c("20% Circle \nMinority", "50% Circle \nMinority","80% Circle \nMinority")
-names(circle_minority.labs) <- c("20", "50","80")
+  rev_circle_blue.labs <- c("80% Circle \nBlue" ,"50% Circle \nBlue","20% Circle \nBlue")
+names(rev_circle_blue.labs) <- c("80", "50","20")
 
-sqrbeq <- dataone %>%  filter(fraction_blue == 50) %>%  gather(key = subgroup, value = Segra, eth_sq_bl,val_sq_bl) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"Value" = "val_sq_bl","Ethnic" = "eth_sq_bl"), "Value"))  %>%
+ rev_circle_orange.labs <-  c("80% Circle \nOrange", "50% Circle \nOrange","20% Circle \nOrange")
+names(rev_circle_orange.labs) <- c("80", "50","20")
+
+dataone %>%  filter(fraction_blue == 80) %>%  gather(key = subgroup, value = Segra, eth_cl_bl,val_cl_bl) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"Value" = "val_cl_bl","Ethnic" = "eth_cl_bl"), "Value"))  %>%
   ggplot(aes(x = beta_ie,y = beta_iv, fill = Segra)) + geom_tile() + 
-  facet_grid(circle_orange ~ circle_blue + segregation, labeller = labeller(circle_orange = circle_minority.labs, circle_blue = circle_local.labs)) +
+  facet_grid( rev_circle_blue  ~ circle_orange  + segregation, labeller = labeller(circle_orange =circle_orange.labs, rev_circle_blue = rev_circle_blue.labs), switch  = "y") +
+  scale_fill_distiller(palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) +
+  scale_x_discrete( limits=c(0,10, by = 5)) +
+  scale_y_discrete( limits=c(0,10, by = 5), position = "right") +
+  xlab("ß ethnic") + ylab("ß value") + ggtitle("Circle blue, ethnic majority") + 
+  theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0), 
+                      panel.spacing.x  = unit(0.2, "lines"),panel.spacing.y  = unit(0.1, "lines") )
+
+```
+
+# Effect of value distribution in group value differences
+
+Each graph is one level of $\%$ circle (value 1) in the local population (majority = blue agents). Each condition panel refers to distribution of  circle agents in the minority population.
+
+```{r heatmapdsquare,fig.pos='t',out.width='\\textwidth',fig.show = "hold",fig.align='center', fig.cap="Square orange, heterogenous preferences", echo=FALSE, include=TRUE }
+
+circle_frame <- datatwo %>% filter(step == 1000) %>% filter(beta_iv_circle == 0 |beta_iv_circle == 5 |beta_iv_circle == 10 ) %>% filter(beta_ie_circle == 0 | beta_ie_circle == 5 | beta_ie_circle == 10)
+
+rev_beta_iv_circle.labs <- c("Circle \nß value 10" ,"Circle \nß value 5", "Circle \nß value 0")
+names(rev_beta_iv_circle.labs) <- c("10", "5","0")
+beta_ie_circle.labs <- c("Circle \nß ethnic 0", "Circle \nß ethnic 5","Circle \nß ethnic 10")
+names(beta_ie_circle.labs) <- c("0", "5","10")
+
+circle_frame %>%   gather(key = subgroup, value = Segra, eth_sq_or,val_sq_or) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"ETHNIC" = "eth_sq_or", "VALUE" = "val_sq_or"), "ethnic segregation")) %>%
+  ggplot(aes(x = beta_iv_square, y = beta_ie_square, fill = Segra)) + geom_tile() + facet_grid(rev_beta_iv_circle ~  beta_ie_circle + segregation, labeller = labeller(rev_beta_iv_circle = rev_beta_iv_circle.labs, beta_ie_circle = beta_ie_circle.labs)) +
    scale_fill_distiller(palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) +
@@
   scale_y_discrete( limits=c(0,10, by = 5)) +
-  xlab("ß ethnic") + ylab("ß value") + ggtitle("Square blue, equal ethnic size") + 
+ xlab("ß value square") + ylab("ß ethnic square") + ggtitle("Square orange, baseline") + 
+    theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0))
+
+```
+
+```{r heatmapdcircle, fig.pos='t',out.width='\\textwidth',fig.show = "hold",fig.align='center', fig.cap="Circle orange, heterogeneous preferences", echo=FALSE, include=TRUE }
+
+circle_frame <- datatwo %>% filter(step == 1000) %>% filter(beta_ie_square == 0 |beta_ie_square == 5 |beta_ie_square == 10 ) %>% filter(beta_iv_square == 0 | beta_iv_square == 5 | beta_iv_square == 10)
+
+rev_beta_ie_square.labs <- c("Square \nß ethnic 10" ,"Square \nß ethnic 5","Square \nß ethnic 0")
+names(rev_beta_ie_square.labs) <- c("10", "5","0")
+beta_iv_square.labs <- c("Square \nß value 0", "Square \nß value 5","Square \nß value 10")
+names(beta_iv_square.labs) <- c("0", "5","10")
+
+circle_frame %>%   gather(key = subgroup, value = Segra, eth_cl_or,val_cl_or) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"ETHNIC" = "eth_cl_or", "VALUE" = "val_cl_or"), "ethnic segregation")) %>%
+  ggplot(aes(x = beta_ie_circle, y = beta_iv_circle, fill = Segra)) + geom_tile() + facet_grid(rev_beta_ie_square ~  beta_iv_square + segregation, labeller = labeller(rev_beta_ie_square = rev_beta_ie_square.labs, beta_iv_square = beta_iv_square.labs)) +
+   scale_fill_distiller(palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) +
+  scale_x_discrete( limits=c(0,10, by = 5)) +
+  scale_y_discrete( limits=c(0,10, by = 5)) +
+ xlab("ß ethnic circle") + ylab("ß value circle") + ggtitle("Circle orange, baseline") + 
+    theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0))
+
+```
+
+```{r betatwoethnic,fig.pos='t',out.width="96%",fig.show = "hold",fig.align='center',fig.cap="Difference segregation", echo=FALSE, include=TRUE }
+
+circle_frame <- datatwo %>% filter(step == 1000) %>% filter(beta_iv_circle == 0 |beta_iv_circle == 5 |beta_iv_circle == 10 ) %>% filter(beta_ie_circle == 0 | beta_ie_circle == 5 | beta_ie_circle == 10)
+
+rev_beta_iv_circle.labs <- c("Circle ß value 10" ,"Circle ß value 5", "Circle ß value 0")
+names(rev_beta_iv_circle.labs) <- c("10", "5","0")
+beta_ie_circle.labs <- c("Circle \nß ethnic 0", "Circle \nß ethnic 5","Circle \nß ethnic 10")
+names(beta_ie_circle.labs) <- c("0", "5","10")
+
+#  v_circle.labs <- c("ß value circle 0", "ß value circle 5", "ß value circle 10")
+# names(v_circle.labs) <- c("0", "5","10")
+e_circle.labs <- c("Circle ß ethnic 0", "Circle ß ethnic 5", "Circle ß ethnic 10")
+names(e_circle.labs) <- c("0", "5","10")
+
+ie_10 <- circle_frame %>%  filter(beta_ie_square == 10) %>% gather(key = subgroup, value = Segra, eth_sq_or,val_sq_or,eth_cl_or,val_cl_or) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"ethnic segregation" = c("eth_sq_or","eth_cl_or"), "value segregation" = c("val_sq_or","val_cl_or")), "ethnic segregation"), `group` = fct_relevel(fct_collapse(subgroup, "square minority" = c("eth_sq_or","val_sq_or"), "circle minority" = c("eth_cl_or","val_cl_or"), "square minority"))) %>%
+  ggplot(aes(x = (beta_ie_square - beta_iv_square), y = Segra, color = `segregation`, shape = `group`)) + geom_line() + geom_point() + facet_grid(rev_beta_iv_circle ~  beta_ie_circle, labeller = labeller(rev_beta_iv_circle = rev_beta_iv_circle.labs,  beta_ie_circle = e_circle.labs )) +
+  geom_vline(xintercept = 5, color = "red") +
+  scale_x_discrete(name = "ß ethnic square 10 - ß value square", limits = seq(0,10, by = 1)) +  ylab("Segregation") +
+  scale_color_manual(values = c("dark violet","dark green"), guide = guide_legend(title="")) +
+  scale_shape_manual(values = c(16,15), guide = guide_legend(title="")) +
+    theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0))
+
+ie_5 <- circle_frame %>%  filter(beta_ie_square == 5) %>% gather(key = subgroup, value = Segra, eth_sq_or,val_sq_or,eth_cl_or,val_cl_or) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"ethnic segregation" = c("eth_sq_or","eth_cl_or"), "value segregation" = c("val_sq_or","val_cl_or")), "ethnic segregation"), `group` = fct_relevel(fct_collapse(subgroup, "square minority" = c("eth_sq_or","val_sq_or"), "circle minority" = c("eth_cl_or","val_cl_or"), "square minority"))) %>%
+  ggplot(aes(x = (beta_ie_square - beta_iv_square), y = Segra, color = `segregation`, shape = `group`)) + geom_line() + geom_point() + facet_grid(rev_beta_iv_circle ~  beta_ie_circle, labeller = labeller(rev_beta_iv_circle = rev_beta_iv_circle.labs,  beta_ie_circle = e_circle.labs )) +
+  scale_x_discrete(name = "ß ethnic square 5 - ß value square", limits = seq(0,5, by = 1)) +  ylab("Segregation") +
+  scale_color_manual(values = c("dark violet","dark green"), guide = guide_legend(title="")) +
+  scale_shape_manual(values = c(16,15), guide = guide_legend(title="")) +
+    theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0))
+
+ie_5
+ie_10
+```
+
+```{r betatwovalue,  fig.pos="t",fig.show = "hold", fig.align='center',fig.show="hold", fig.cap="Difference segregation between", echo=FALSE, include=TRUE  }
+
+circle_frame <- datatwo %>% filter(step == 1000) %>% filter(beta_ie_square == 0 |beta_ie_square == 5 |beta_ie_square == 10 ) %>% filter(beta_iv_square == 0 | beta_iv_square == 5 | beta_iv_square == 10)
+
+rev_beta_ie_square.labs <- c("Square \nß ethnic 10" ,"Square \nß ethnic 5", "Square \nß ethnic 0")
+names(rev_beta_ie_square.labs) <- c("10", "5","0")
+
+e_square.labs <- c("ß ethnic \nsquare 0", "ß ethnic \nsquare 5", "ß ethnic \nsquare 10")
+names(e_square.labs) <- c("0", "5","10")
+v_square.labs <- c("ß value square 0", "ß value square 5", "ß value square 10")
+names(v_square.labs) <- c("0", "5","10")
+
+iv_10 <- circle_frame %>%  filter(beta_iv_circle == 10) %>% gather(key = subgroup, value = Segra, eth_sq_or,val_sq_or,eth_cl_or,val_cl_or) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"ethnic segregation" = c("eth_sq_or","eth_cl_or"), "value segregation" = c("val_sq_or","val_cl_or")), "ethnic segregation"), `group` = fct_relevel(fct_collapse(subgroup, "square minority" = c("eth_sq_or","val_sq_or"), "circle minority" = c("eth_cl_or","val_cl_or"), "square minority")))  %>%
+  ggplot(aes(x = (beta_iv_circle - beta_ie_circle), y = Segra, color = `segregation`, shape = `group`)) + geom_line() + geom_point() + facet_grid(rev_beta_ie_square ~  beta_iv_square, labeller = labeller(rev_beta_ie_square = rev_beta_ie_square.labs, beta_iv_square = v_square.labs))  +
+  geom_vline(xintercept = 5, color = "red") +
+  scale_x_discrete(name = "ß value circle 10 - ß ethnic circle", limits = seq(0,10, by = 1)) +  ylab("Segregation") +
+  scale_color_manual(values = c("dark violet","dark green"), guide = guide_legend(title="")) +
+  scale_shape_manual(values = c(16,15), guide = guide_legend(title="")) +
+    theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0))
+
+iv_5 <- circle_frame %>%  filter(beta_iv_circle == 5) %>% gather(key = subgroup, value = Segra, eth_sq_or,val_sq_or,eth_cl_or,val_cl_or) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"ethnic segregation" = c("eth_sq_or","eth_cl_or"), "value segregation" = c("val_sq_or","val_cl_or")), "ethnic segregation"), `group` = fct_relevel(fct_collapse(subgroup, "square minority" = c("eth_sq_or","val_sq_or"), "circle minority" = c("eth_cl_or","val_cl_or"), "square minority")))  %>%
+  ggplot(aes(x = (beta_iv_circle - beta_ie_circle), y = Segra, color = `segregation`, shape = `group`)) + geom_line() + geom_point() + facet_grid(rev_beta_ie_square ~  beta_iv_square, labeller = labeller(rev_beta_ie_square = rev_beta_ie_square.labs, beta_iv_square = v_square.labs))  +
+  scale_x_discrete(name = "ß value circle 10 - ß ethnic circle", limits = seq(0,5, by = 1)) +  ylab("Segregation") +
+  scale_color_manual(values = c("dark violet","dark green"), guide = guide_legend(title="")) +
+  scale_shape_manual(values = c(16,15), guide = guide_legend(title="")) +
+    theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0))
+
+iv_5
+iv_10
+
+```
+
+# ANNEX
+
+```{r sqro, fig.pos='t',out.width='\\textwidth',fig.show = "hold",fig.align='center',fig.show="hold", fig.cap="First Section, Square Orange", echo=FALSE, include=TRUE  }
+
+sqroeq <- dataone %>%  filter(fraction_blue == 50) %>%  gather(key = subgroup, value = Segra, eth_sq_or,val_sq_or) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"Value" = "val_sq_or","Ethnic" = "eth_sq_or"), "Value"))  %>%
+  ggplot(aes(x = beta_ie,y = beta_iv, fill = Segra)) + geom_tile() + 
+  facet_grid(circle_orange ~ rev_circle_blue + segregation, labeller = labeller(circle_orange = circle_orange.labs, rev_circle_blue = rev_circle_blue.labs), switch  = "y") +
+  scale_fill_distiller(palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) +
+  scale_x_discrete( limits=c(0,10, by = 5)) +
+  scale_y_discrete( limits=c(0,10, by = 5), position = "right") +
+  xlab("ß ethnic") + ylab("ß value") + ggtitle("Square orange, equal ethnic size") + 
   theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0), 
@@
 
-sqrbmj <- dataone %>%  filter(fraction_blue == 80) %>%  gather(key = subgroup, value = Segra, eth_sq_bl,val_sq_bl) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"Value" = "val_sq_bl","Ethnic" = "eth_sq_bl"), "Value"))  %>%
+sqroqmj <- dataone %>%  filter(fraction_blue == 80) %>%  gather(key = subgroup, value = Segra, eth_sq_or,val_sq_or) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"Value" = "val_sq_or","Ethnic" = "eth_sq_or"), "Value"))  %>%
   ggplot(aes(x = beta_ie,y = beta_iv, fill = Segra)) + geom_tile() + 
-  facet_grid(circle_orange ~ circle_blue + segregation, labeller = labeller(circle_orange = circle_minority.labs, circle_blue = circle_local.labs)) +
+  facet_grid(circle_orange ~ rev_circle_blue + segregation, labeller = labeller(circle_orange = circle_orange.labs, rev_circle_blue = rev_circle_blue.labs), switch  = "y") +
   scale_fill_distiller(palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) +
   scale_x_discrete( limits=c(0,10, by = 5)) +
-  scale_y_discrete( limits=c(0,10, by = 5)) +
-  xlab("ß ethnic") + ylab("ß value") + ggtitle("Square blue, ethnic majority") + 
+  scale_y_discrete( limits=c(0,10, by = 5), position = "right") +
+  xlab("ß ethnic") + ylab("ß value") + ggtitle("Square orange, ethnic minority") + 
   theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0), 
@@
 
-#grid.arrange(grob(sqroeq),grob(sqromj), ncol =  1, common.legend = TRUE,legend = "bottom")
-
- sqrbeq
- sqrbmj
+sqroeq
+sqroqmj
 ```
 
-```{r crlb, fig.pos="t",out.width='\\textwidth',fig.show = "hold",fig.pos='t',fig.align='center',fig.show="hold", fig.cap="", echo=FALSE, include=TRUE  }
+```{r crlbl,fig.pos='t' ,out.width='\\textwidth',fig.show = "hold",fig.align='center',fig.show="hold", fig.cap="First Section, Circle Blue", echo=FALSE, include=TRUE}
 
- circle_local.labs <- c("20% Circle \nMajority", "50% Circle \nMajority","80% Circle \nMajority")
-names(circle_local.labs) <- c("20", "50","80")
- circle_minority.labs <-  c("20% Circle \nMinority", "50% Circle \nMinority","80% Circle \nMinority")
-names(circle_minority.labs) <- c("20", "50","80")
+ rev_circle_orange.labs <-  c("80% Circle \nOrange", "50% Circle \nOrange","20% Circle \nOrange")
+names(rev_circle_orange.labs) <- c("80", "50","20")
+
+ circle_blue.labs <- c("20% Circle \nBlue", "50% Circle \nBlue","80% Circle \nBlue")
+names(circle_blue.labs) <- c("20", "50","80")
 
@@
   ggplot(aes(x = beta_ie,y = beta_iv, fill = Segra)) + geom_tile() + 
-  facet_grid(circle_orange ~ circle_blue + segregation, labeller = labeller(circle_orange = circle_minority.labs, circle_blue = circle_local.labs)) +
+  facet_grid( rev_circle_blue  ~ circle_orange  + segregation, labeller = labeller(circle_orange =circle_orange.labs, rev_circle_blue = rev_circle_blue.labs), switch  = "y") +
   scale_fill_distiller(palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) +
   scale_x_discrete( limits=c(0,10, by = 5)) +
-  scale_y_discrete( limits=c(0,10, by = 5)) +
+  scale_y_discrete( limits=c(0,10, by = 5), position = "right") +
   xlab("ß ethnic") + ylab("ß value") + ggtitle("Circle blue, equal ethnic size") + 
@@
   ggplot(aes(x = beta_ie,y = beta_iv, fill = Segra)) + geom_tile() + 
-  facet_grid(circle_orange ~ circle_blue + segregation, labeller = labeller(circle_orange = circle_minority.labs, circle_blue = circle_local.labs)) +
+  facet_grid( rev_circle_blue  ~ circle_orange  + segregation, labeller = labeller(circle_orange =circle_orange.labs, rev_circle_blue = rev_circle_blue.labs), switch  = "y") +
   scale_fill_distiller(palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) +
   scale_x_discrete( limits=c(0,10, by = 5)) +
-  scale_y_discrete( limits=c(0,10, by = 5)) +
-  xlab("ß ethnic") + ylab("ß value") + ggtitle("Cirle blue, ethnic majority") + 
+  scale_y_discrete( limits=c(0,10, by = 5), position = "right") +
+  xlab("ß ethnic") + ylab("ß value") + ggtitle("Circle blue, ethnic majority") + 
   theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0), 
@@
 
-# Effect of value distribution in group value differences
+```{r sqrbl, fig.pos='t' ,out.width='\\textwidth',fig.show = "hold",fig.align='center',fig.show="hold", fig.cap="First Section, Square Blue", echo=FALSE, include=TRUE}
 
-Each graph is one level of $\%$ circle (value 1) in the local population (majority = blue agents). Each condition panel refers to distribution of  circle agents in the minority population.
+sqrbeq <- dataone %>%  filter(fraction_blue == 50) %>%  gather(key = subgroup, value = Segra, eth_sq_bl,val_sq_bl) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"Value" = "val_sq_bl","Ethnic" = "eth_sq_bl"), "Value"))  %>%
+  ggplot(aes(x = beta_ie,y = beta_iv, fill = Segra)) + geom_tile() + 
+  facet_grid(circle_blue ~  rev_circle_orange  + segregation, labeller = labeller(rev_circle_orange = rev_circle_orange.labs, circle_blue = circle_blue.labs), switch  = "y") +
+  scale_fill_distiller(palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) +
+  scale_x_discrete( limits=c(0,10, by = 5)) +
+  scale_y_discrete( limits=c(0,10, by = 5), position = "right") +
+  xlab("ß ethnic") + ylab("ß value") + ggtitle("Square blue, equal ethnic size") + 
+  theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0), 
+                      panel.spacing.x  = unit(0.2, "lines"),panel.spacing.y  = unit(0.1, "lines") )
 
-```{r mint, fig.pos="h", out.width="98%",fig.align='center',fig.show="hold", fig.cap="Minority population, 20\\% Majority Circle, equal ethnic (above), minority-majority (below)", echo=FALSE, include=TRUE }
+sqrbomj <- dataone %>%  filter(fraction_blue == 80) %>%  gather(key = subgroup, value = Segra, eth_sq_bl,val_sq_bl) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"Value" = "val_sq_bl","Ethnic" = "eth_sq_bl"), "Value"))  %>%
+  ggplot(aes(x = beta_ie,y = beta_iv, fill = Segra)) + geom_tile() + 
+  facet_grid(circle_blue ~  rev_circle_orange  + segregation, labeller = labeller(rev_circle_orange = rev_circle_orange.labs, circle_blue = circle_blue.labs), switch  = "y") +
+  scale_fill_distiller(palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) +
+  scale_x_discrete( limits=c(0,10, by = 5)) +
+  scale_y_discrete( limits=c(0,10, by = 5), position = "right") +
+  xlab("ß ethnic") + ylab("ß value") + ggtitle("Square blue, ethnic majority") + 
+  theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0), 
+                      panel.spacing.x  = unit(0.2, "lines"),panel.spacing.y  = unit(0.1, "lines") )
 
-knitr::include_graphics("min20.png")
-
+sqrbeq
+sqrbomj
 ```
-
-```{r minf, fig.pos="h", out.width="98%",fig.align='center',fig.show="hold", fig.cap="Minority population, 50\\% Majority Circle, equal ethnic (above), minority-majority (below)", echo=FALSE, include=TRUE }
-
-knitr::include_graphics("min50.png")
-
-```
-
-```{r ming, fig.pos="h", out.width="98%",fig.align='center',fig.show="hold", fig.cap="Minority population, 80\\% Majority Circle, equal ethnic (above), minority-majority (below)", echo=FALSE, include=TRUE }
-
-knitr::include_graphics("min80.png")
-
-```
-
-```{r majot, fig.pos="h", out.width="98%",fig.align='center',fig.show="hold", fig.cap="Majority population, 20\\% Majority Circle, equal ethnic (above), minority-majority (below)", echo=FALSE, include=TRUE }
-
-knitr::include_graphics("majo20.png")
-
-```
-
-```{r majof, fig.pos="h", out.width="98%",fig.align='center',fig.show="hold", fig.cap="Majority population, 50\\% Majority Circle, equal ethnic (above), minority-majority (below)", echo=FALSE, include=TRUE }
-
-knitr::include_graphics("majo50.png")
-
-```
-
-```{r majog, fig.pos="h", out.width="98%",fig.align='center',fig.show="hold", fig.cap="Majority population, 80\\% Majority Circle, equal ethnic (above), minority-majority (below)", echo=FALSE, include=TRUE }
-
-knitr::include_graphics("majo80.png")
-
-```
-
-```{r betatwoethnic,out.width="96%", fig.pos="t",fig.show = "hold",fig.pos='t',fig.align='center',fig.show="hold", fig.cap="Difference segregation between value groups (equal ethnic group).
-X-axis: determinism ethnic utility circle.", echo=FALSE, include=TRUE }
-
-circle_frame <- datatwo %>% filter(step == 1000) %>% filter(beta_iv_circle == 0 |beta_iv_circle == 5 |beta_iv_circle == 10 ) %>% filter(beta_ie_circle == 0 | beta_ie_circle == 5 | beta_ie_circle == 10)
-
- v_circle.labs <- c("ß value circle 0", "ß value circle 5", "ß value circle 10")
-names(v_circle.labs) <- c("0", "5","10")
-e_circle.labs <- c("ß ethnic circle 0", "ß ethnic circle 5", "ß ethnic circle 10")
-names(e_circle.labs) <- c("0", "5","10")
-
-ie_10 <- circle_frame %>%  filter(beta_ie_square == 10) %>% gather(key = subgroup, value = Segra, eth_sq_or,val_sq_or,eth_cl_or,val_cl_or) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"ethnic segregation" = c("eth_sq_or","eth_cl_or"), "value segregation" = c("val_sq_or","val_cl_or")), "ethnic segregation"), `group` = fct_relevel(fct_collapse(subgroup, "square minority" = c("eth_sq_or","val_sq_or"), "circle minority" = c("eth_cl_or","val_cl_or"), "square minority"))) %>%
-  ggplot(aes(x = (beta_ie_square - beta_iv_square), y = Segra, color = `segregation`, shape = `group`)) + geom_line() + geom_point() + facet_grid(beta_iv_circle ~  beta_ie_circle, labeller = labeller(beta_iv_circle = v_circle.labs,  beta_ie_circle = e_circle.labs )) +
-  geom_vline(xintercept = 5, color = "red") +
-  scale_x_discrete(name = "ß ethnic square 10 - ß value square", limits = seq(0,10, by = 1)) +  ylab("Segregation") +
-  scale_color_manual(values = c("dark violet","dark green"), guide = guide_legend(title="")) +
-  scale_shape_manual(values = c(16,15), guide = guide_legend(title="")) +
-    theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0))
-
-ie_5 <- circle_frame %>%  filter(beta_ie_square == 5) %>% gather(key = subgroup, value = Segra, eth_sq_or,val_sq_or,eth_cl_or,val_cl_or) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"ethnic segregation" = c("eth_sq_or","eth_cl_or"), "value segregation" = c("val_sq_or","val_cl_or")), "ethnic segregation"), `group` = fct_relevel(fct_collapse(subgroup, "square minority" = c("eth_sq_or","val_sq_or"), "circle minority" = c("eth_cl_or","val_cl_or"), "square minority"))) %>%
-  ggplot(aes(x = (beta_ie_square - beta_iv_square), y = Segra, color = `segregation`, shape = `group`)) + geom_line() + geom_point() + facet_grid(beta_iv_circle ~  beta_ie_circle, labeller = labeller(beta_iv_circle = v_circle.labs,  beta_ie_circle = e_circle.labs )) +
-  scale_x_discrete(name = "ß ethnic square 5 - ß value square", limits = seq(0,5, by = 1)) +  ylab("Segregation") +
-  scale_color_manual(values = c("dark violet","dark green"), guide = guide_legend(title="")) +
-  scale_shape_manual(values = c(16,15), guide = guide_legend(title="")) +
-    theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0))
-
-ie_5
-ie_10
-```
-
-```{r betatwovalue, out.width="96%", fig.pos="t",fig.show = "hold",fig.pos='t',fig.align='center',fig.show="hold", fig.cap="Difference segregation between value groups (equal ethnic group).
-X-axis: determinism value utility circle.", echo=FALSE, include=TRUE  }
-
-circle_frame <- datatwo %>% filter(step == 1000) %>% filter(beta_ie_square == 0 |beta_ie_square == 5 |beta_ie_square == 10 ) %>% filter(beta_iv_square == 0 | beta_iv_square == 5 | beta_iv_square == 10)
-
-e_square.labs <- c("ß ethnic \nsquare 0", "ß ethnic \nsquare 5", "ß ethnic \nsquare 10")
-names(e_square.labs) <- c("0", "5","10")
-v_square.labs <- c("ß value square 0", "ß value square 5", "ß value square 10")
-names(v_square.labs) <- c("0", "5","10")
-
-iv_10 <- circle_frame %>%  filter(beta_iv_circle == 10) %>% gather(key = subgroup, value = Segra, eth_sq_or,val_sq_or,eth_cl_or,val_cl_or) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"ethnic segregation" = c("eth_sq_or","eth_cl_or"), "value segregation" = c("val_sq_or","val_cl_or")), "ethnic segregation"), `group` = fct_relevel(fct_collapse(subgroup, "square minority" = c("eth_sq_or","val_sq_or"), "circle minority" = c("eth_cl_or","val_cl_or"), "square minority")))  %>%
-  ggplot(aes(x = (beta_iv_circle - beta_ie_circle), y = Segra, color = `segregation`, shape = `group`)) + geom_line() + geom_point() + facet_grid(beta_ie_square ~  beta_iv_square, labeller = labeller(beta_ie_square = e_square.labs, beta_iv_square = v_square.labs))  +
-  geom_vline(xintercept = 5, color = "red") +
-  scale_x_discrete(name = "ß value circle 10 - ß ethnic circle", limits = seq(0,10, by = 1)) +  ylab("Segregation") +
-  scale_color_manual(values = c("dark violet","dark green"), guide = guide_legend(title="")) +
-  scale_shape_manual(values = c(16,15), guide = guide_legend(title="")) +
-    theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0))
-
-iv_5 <- circle_frame %>%  filter(beta_iv_circle == 5) %>% gather(key = subgroup, value = Segra, eth_sq_or,val_sq_or,eth_cl_or,val_cl_or) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"ethnic segregation" = c("eth_sq_or","eth_cl_or"), "value segregation" = c("val_sq_or","val_cl_or")), "ethnic segregation"), `group` = fct_relevel(fct_collapse(subgroup, "square minority" = c("eth_sq_or","val_sq_or"), "circle minority" = c("eth_cl_or","val_cl_or"), "square minority")))  %>%
-  ggplot(aes(x = (beta_iv_circle - beta_ie_circle), y = Segra, color = `segregation`, shape = `group`)) + geom_line() + geom_point() + facet_grid(beta_ie_square ~  beta_iv_square, labeller = labeller(beta_ie_square = e_square.labs, beta_iv_square = v_square.labs))  +
-  scale_x_discrete(name = "ß value circle 5 - ß ethnic circle", limits = seq(0,5, by = 1)) +  ylab("Segregation") +
-  scale_color_manual(values = c("dark violet","dark green"), guide = guide_legend(title="")) +
-  scale_shape_manual(values = c(16,15), guide = guide_legend(title="")) +
-    theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0))
-
-iv_5
-iv_10
-
-```

### 2020-05-04 exp_eth_val.Rmd
Add files via upload

@@
 ```
+\newcommand*{\thead}[1]{\multicolumn{1}{c}{\bfseries #1}}
 
@@
 * Aim:
-    + Effect of different homophily preferences: independent effect of $\beta_e$ on ethnic segregation, and direct effect of beta value $\beta_v$ on value segregation.
+    + Effect of different homophily preferences: direct effect of $\beta_e$ on ethnic segregation, and direct effect of beta value $\beta_v$ on value segregation, and reciprocal influences, i.e.
+how of $\beta_v$ influences effect of  $\beta_e$ on ethnic segregation and how $\beta_e$ influences effect of $\beta_v$ on value segregation
+* Focus: interaction between relative group size for each dimension with degree of $\beta$, since group size directly influence the probability to find similar ones and the systematic utility computed for each neighborhood
+* Assumption: 
+    + not heterogeneity: all agents hold both ethnic preference (same color) and value preference (same shape)
+    + ethnic size at global level: equal size (blue/orange: $0.50$), majority/minority (blue/orange: $0.80$)
+    + value size within each ethnic group: minority circle circle/square $0.20$, equal size circle/square $0.50$, majority circle circle/square $0.80$, imagining tolerant (circle) and intolerant (square),this means to move from more tolerant to less tolerant groups, both majority and minority.
+In this section there is not difference in preferences implied.
+* Figures:
+    + Fig: \ref{fig:baselineone} represents how results are presented through the space of the model.
+Axis represent the ratio of $circle/square$ in each ethnic group, expressed as percentage: on y-axis the percentage of circle value in the orange ethnic group, on the x-axis the percentage of circle value in the blue ethnic group.
+The percentage of square agents can be calculated from it.
+The \textbf{baseline} condition is represented by the black dot, where each ethnicity is split equally into the two value groups ($0.50$ circle, $0.50$ square); following the diagonal, each ethnic group moves from minority circle to majority circle.
+Each obervation is repeated  for ethnic equal group sizes (blue/orange = $0.50$) and ethnic majority/minority condition (blue/orange = $0.80$).
+In the baseline condition for equal ethnic size, each group $valueXethnicity$ represents the $25 \%$ of the overall population.
+This means each agent in Fig: \ref{fig:thheory} has potentially probability $0.25$ to relocate close to someone who shares both ethnicity and value orientation.
+    + In all results $\beta = 5$ seems a threshold between area of high randomness and low randomness. I would use this as reference point in describing figures and change in conditions
 
@@
  \midrule
- Parameters modified in experiment & Slider  & Range   & Experiments  \\ 
+ \textbf{Parameters modified in experiment} & \textbf{Slider} & \textbf{Range}   & \textbf{Experiments}  \\ 
  \midrule
@@
 
-```{r global, fig.height=8.8, fig.pos="h", include=TRUE, fig.cap="Global Segregation with ethnic equal group size, baseline in boldline", echo=FALSE}
+* Global Observations:
+    + Fig: \ref{fig:global} and  Fig: \ref{fig:global-maj} shows the global ethnic and value segregation, for equal ethnic group sizes in Fig: \ref{fig:global}  and majority/minority ethnic condition in Fig: \ref{fig:global-maj}  .
+The heatmaps report in each condition  $\beta_e$ on x-axis, and  $\beta_v$ on y-axis.
+    + Ethnic segregation increases along the axis of $\beta_e$, while value segregation symmetrically along the axis of $\beta_v$.
+In both cases $\beta = 5$ shows a threshold between areas of integration and area of segregation.
+    + While area below $\beta = 5$ is linearly increasing, areas above $\beta = 5$ seem to show same degree of high segregation.
+Attributing this to randomness component, I would identify area $\beta < 5$ as low randomness, area  $\beta \geq 5$ high randomness, and focus on threshold of $\beta = 5$, this helps presenting figures later
+    + The direct effect of $\beta_e$ on ethnic segregation and  $\beta_v$ on value segregation seems unaffected by the other systemic component, both when  $\beta = 0$, so that agents relocate randomly for value or ethnic homophily, and when they increase the systemic utility for either ethnic (increase in  $\beta_e$) or value homophily (increase in $\beta_v$)
+    + Condition of ethnic majority/minority shows basically the same patterns, slighter high ethnic segregation for the area of high randomness, which is direct effect of unequal group sizes.
+    + Change in ethnic segregation compared to the baseline seem to occur only along the diagonal, where circle orientation represents the minority in one group and majority in the other, or vice versa.
+Similar slightly changes occur in the area of high randomness $\beta_e < 5$ with increase of $\beta_v$, which is counterintuitive.
+Circle of both ethnic group not care about ethnic composition of the neighborhood, but they care about the value composition.
+Since in one ethnic group circle represent the value majority, and in the other the circle minority, circle in the minority condition will result in ethnically mixed or majority out-group neighborhoods, circle in the majority in ethnically homogeneous neighborhoods, since they have more probability to find someone circle of the own ethnic group than the other.
+So, for these agents ethnic segregation is the more likely outcome, also if the systematic component of utility is for value segregation and ethnic utility random.
+The global results are influenced by the numeric superiority of these  agents.
+    + Next figures look at the behavior of specific subgroup in Fig. \ref{fig:thheory}
+
+```{r baselineone,fig.pos='H',out.width='\\textwidth',fig.show = "hold",fig.align='center', fig.cap=" Baseline space", echo=FALSE, include=TRUE  }
+
+knitr::include_graphics("baseline_1.png")
+
+```
+
+```{r global, fig.height=8.8, fig.pos="H", include=TRUE, fig.cap="Global Segregation with ethnic equal group size, baseline in boldline", echo=FALSE}
 
@@
 
-circle_local.labs <- c("20% Local Circle", "50% Local Circle","80% Local Circle")
+ circle_local.labs <- c("20% Circle \nBlue", "50% Circle \nBlue","80% Circle \nBlue")
 names(circle_local.labs) <- c("20", "50","80")
-circle_minority.labs <-  c("20% Minority Circle", "50% Minority Circle","80% Minority Circle")
+ circle_minority.labs <-  c("20% Circle \nOrange","50% Circle \nOrange","80% Circle \nOrange")
 names(circle_minority.labs) <- c("20", "50","80")
@@
 
-glb <- annotate_figure(ggarrange(eth_eq , ggarrange(val_eq), nrow = 2), top = text_grob("Global Segregation, Majority:Minority = 0.5:0.5",face = "bold", size = 12))
+glb <- annotate_figure(ggarrange(eth_eq , ggarrange(val_eq), nrow = 2), top = text_grob("Global Segregation, Blue:Orange = 0.5:0.5",face = "bold", size = 12))
 
@@
 
-```{r global-maj, fig.height=8.8, fig.pos="h",  include=TRUE, fig.cap="Global Segregation with ethnic equal group size, baseline in boldline", echo=FALSE}
+```{r global-maj, fig.height=8.8, fig.pos="H",  include=TRUE, fig.cap="Global Segregation with majority/minority ethnicity, baseline in boldline", echo=FALSE}
 
@@
 
- circle_local.labs <- c("20% Local Circle", "50% Local Circle","80% Local Circle")
+ circle_local.labs <- c("20% Circle \nBlue", "50% Circle \nBlue","80% Circle \nBlue")
 names(circle_local.labs) <- c("20", "50","80")
- circle_minority.labs <-  c("20% Minority Circle", "50% Minority Circle","80% Minority Circle")
+ circle_minority.labs <-  c("20% Circle \nOrange","50% Circle \nOrange","80% Circle \nOrange")
 names(circle_minority.labs) <- c("20", "50","80")
@@
 
-maj_glb <- annotate_figure(ggarrange(maj_eth , ggarrange(maj_val), nrow = 2), top = text_grob("Global Segregation, Majority:Minority = 0.8:0.2",face = "bold", size = 12))
+maj_glb <- annotate_figure(ggarrange(maj_eth , ggarrange(maj_val), nrow = 2), top = text_grob("Global Segregation, Blue:Orange = 0.8:0.2",face = "bold", size = 12))
 maj_glb
@@
 
-```{r baselineone,fig.pos='t',out.width='\\textwidth',fig.show = "hold",fig.align='center', fig.cap=" Baseline space", echo=FALSE, include=TRUE  }
+* Observations for group $ethnicityXvalue$:
+    + I report the results of circle orange in the condition of ethnic equal size, ethnic minority and ethnic majority.
+Since agents  follow the same homophily preferences, the only difference is due to the manipulation of relative group sizes for ethnicity and value orientation, so that the results here presented can be applied to all other group by rotating the axis on Fig: \ref{fig:baselineone} or results along the diagonal.
+I do this in the ANNEX as demonstration
 
-knitr::include_graphics("baseline_1.png")
-
-```
-
-```{r crlo,fig.pos='t',out.width='\\textwidth',fig.show = "hold",fig.align='center', fig.cap="Circle orange, first section", echo=FALSE, include=TRUE  }
+```{r crlo,fig.pos='H',out.width='\\textwidth',fig.show = "hold",fig.align='center', fig.cap="Circle orange, first section", echo=FALSE, include=TRUE  }
 
@@
 
-```{r sqro, fig.pos='t',out.width='\\textwidth',fig.show = "hold",fig.align='center',fig.show="hold", fig.cap="First Section, Square Orange", echo=FALSE, include=TRUE  }
+```{r sqro, fig.pos='H',out.width='\\textwidth',fig.show = "hold",fig.align='center',fig.show="hold", fig.cap="First Section, Square Orange", echo=FALSE, include=TRUE  }
 
@@
 
-```{r crlbl,fig.pos='t' ,out.width='\\textwidth',fig.show = "hold",fig.align='center',fig.show="hold", fig.cap="First Section, Circle Blue", echo=FALSE, include=TRUE}
+```{r crlbl,fig.pos='H' ,out.width='\\textwidth',fig.show = "hold",fig.align='center',fig.show="hold", fig.cap="First Section, Circle Blue", echo=FALSE, include=TRUE}
 
@@
 
-```{r sqrbl, fig.pos='t' ,out.width='\\textwidth',fig.show = "hold",fig.align='center',fig.show="hold", fig.cap="First Section, Square Blue", echo=FALSE, include=TRUE}
+```{r sqrbl, fig.pos='H' ,out.width='\\textwidth',fig.show = "hold",fig.align='center',fig.show="hold", fig.cap="First Section, Square Blue", echo=FALSE, include=TRUE}
 

### 2020-05-05 exp_eth_val.Rmd
updating second part

@@
 #language: en-GB
-#bibliography: "references.bib"
+bibliography: "references.bib"
 # always_allow_html: yes
@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = FALSE, fig.lp="fig:",warning = FALSE)
+knitr::opts_chunk$set(echo = FALSE, fig.lp="fig:"  ,warning = FALSE)
 
@@
     + value size within each ethnic group: minority circle circle/square $0.20$, equal size circle/square $0.50$, majority circle circle/square $0.80$, imagining tolerant (circle) and intolerant (square),this means to move from more tolerant to less tolerant groups, both majority and minority.
-In this section there is not difference in preferences implied.
+In this section there is not difference in preferences implied Tab \ref{tab:a}
 * Figures:
@@
     + In all results $\beta = 5$ seems a threshold between area of high randomness and low randomness. I would use this as reference point in describing figures and change in conditions
-
-Table \ref{tab:first}
 
@@
    \midrule
+Number of Runs   & 1 &  & \\ 
+ \midrule
 \end{tabular}
-\label{tab:first}
  \caption{Basic Model} 
-
+ \label{tab:a}
 \end{table}
 
-* Global Observations:
-    + Fig: \ref{fig:global} and  Fig: \ref{fig:global-maj} shows the global ethnic and value segregation, for equal ethnic group sizes in Fig: \ref{fig:global}  and majority/minority ethnic condition in Fig: \ref{fig:global-maj}  .
+## Global Observations
+* Fig: \ref{fig:global} and  Fig: \ref{fig:global-maj} shows the global ethnic and value segregation, for equal ethnic group sizes in Fig: \ref{fig:global}  and majority/minority ethnic condition in Fig: \ref{fig:global-maj}  .
 The heatmaps report in each condition  $\beta_e$ on x-axis, and  $\beta_v$ on y-axis.
-    + Ethnic segregation increases along the axis of $\beta_e$, while value segregation symmetrically along the axis of $\beta_v$.
+* Ethnic segregation increases along the axis of $\beta_e$, while value segregation symmetrically along the axis of $\beta_v$.
 In both cases $\beta = 5$ shows a threshold between areas of integration and area of segregation.
-    + While area below $\beta = 5$ is linearly increasing, areas above $\beta = 5$ seem to show same degree of high segregation.
+* While area below $\beta = 5$ is linearly increasing, areas above $\beta = 5$ seem to show same degree of high segregation.
 Attributing this to randomness component, I would identify area $\beta < 5$ as low randomness, area  $\beta \geq 5$ high randomness, and focus on threshold of $\beta = 5$, this helps presenting figures later
-    + The direct effect of $\beta_e$ on ethnic segregation and  $\beta_v$ on value segregation seems unaffected by the other systemic component, both when  $\beta = 0$, so that agents relocate randomly for value or ethnic homophily, and when they increase the systemic utility for either ethnic (increase in  $\beta_e$) or value homophily (increase in $\beta_v$)
-    + Condition of ethnic majority/minority shows basically the same patterns, slighter high ethnic segregation for the area of high randomness, which is direct effect of unequal group sizes.
-    + Change in ethnic segregation compared to the baseline seem to occur only along the diagonal, where circle orientation represents the minority in one group and majority in the other, or vice versa.
+* The threshold of $\beta = 5$ to me can relate to "sensitivity to change" in @van2009neighborhood: since the shape of utility is linearly increasing, each change in the composition of neighborhood will increase the difference between options.
+Once the difference is multiplied times $\beta$, the effect of utility difference is too high and soon the best option is taken.
+This means that only for very low levels of $\beta$ it is possible to see a linear increasing in the systematic utility.
+At $\beta = 5$ the systematic utility becomes too strong and agents highly sensitive to the change in neighborhood composition, moving to the best solution, increasing segregation of neighborhoods.
+This soon attires other agents and equilibria towards segregation are easily reached.
+* The direct effect of $\beta_e$ on ethnic segregation and  $\beta_v$ on value segregation seems unaffected by the other systemic component, both when  $\beta = 0$, so that agents relocate randomly for value or ethnic homophily, and when they increase the systemic utility for either ethnic (increase in  $\beta_e$) or value homophily (increase in $\beta_v$)
+* Condition of ethnic majority/minority shows basically the same patterns, slighter high ethnic segregation for the area of high randomness, which is direct effect of unequal group sizes.
+* Change in ethnic segregation compared to the baseline seem to occur only along the diagonal, where circle orientation represents the minority in one group and majority in the other, or vice versa.
 Similar slightly changes occur in the area of high randomness $\beta_e < 5$ with increase of $\beta_v$, which is counterintuitive.
@@
 The global results are influenced by the numeric superiority of these  agents.
-    + Next figures look at the behavior of specific subgroup in Fig. \ref{fig:thheory}
+    * Next figures look at the behavior of specific subgroup in Fig. \ref{fig:thheory}
 
@@
 
-* Observations for group $ethnicityXvalue$:
-    + I report the results of circle orange in the condition of ethnic equal size, ethnic minority and ethnic majority.
+## Observations for group $ethnicityXvalue$:
+
+* Figures \ref{fig:crlo}, \ref{fig:crlominority} and \ref{fig:crlblmajority} replicate the behavior space in Fig: \ref{fig:baselineone} used in the previous section.
+For each condition the ethnic and value segregation are reported.
+* I report the results of circle orange in the condition of ethnic equal size, ethnic minority and ethnic majority.
 Since agents  follow the same homophily preferences, the only difference is due to the manipulation of relative group sizes for ethnicity and value orientation, so that the results here presented can be applied to all other group by rotating the axis on Fig: \ref{fig:baselineone} or results along the diagonal.
 I do this in the ANNEX as demonstration
+* 3 outcomes are evident, rather than 2 as in traditional assessment of Schelling: integration (filler white  0.5), segregation (filler red above 0.5), and assimilation (filler blue close to 0, only members outgroup).
+This can relate as measure of *hybrid segregation*
 
-```{r crlo,fig.pos='H',out.width='\\textwidth',fig.show = "hold",fig.align='center', fig.cap="Circle orange, first section", echo=FALSE, include=TRUE  }
+### Equal ethnic group size (Fig: \ref{fig:crlo})
 
-crloeq <- dataone %>%  filter(fraction_blue == 50) %>%  gather(key = subgroup, value = Segra, eth_cl_or,val_cl_or) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"Value" = "val_cl_or","Ethnic" = "eth_cl_or"), "Value"))  %>%
+* Given ethnic equal group size, at the baseline condition ($50 \%$ circle orange, $50 \%$ circle blue), each group replicates what observed for global segregation: high randomness close to integration for $\beta < 5$, low randomness high segregation for $\beta \geq 5$.
+For ethnic segregation this is the same along the diagonal, given equal ethnic sizes
+* On the top left corner,  where the value group represents majority in the own ethnic group, but minority in the other, integration is the most likely outcome  only for low levels of both $\beta_e$ and  $\beta_v$ (low left corner), with middle segregation in the rest of high randomness area.
+While the value becomes more represented in the other ethnic group, ethnic integration increases  with increase of  $\beta_v$ in the area of high randomness ($\beta_e < 5$), untouched in the area of low  randomess ($\beta_e \geq 5$).
+In the same conditions, high value segregation appears as direct effect of increase in the proportion of same value oriented circle in the other group
+* Low row, where the value group represents minority in the own group: value assimilation to square is the case when circle is the minority in both etnic groups.
+Still, comparing to ethnic segregation, area of high randomenss appears ethnically integrated, area of low randomness ethnically segregated.
+This implies that for  low $\beta_e$ and low $\beta_v$ value minority relocate in ethnically mixed neighborhoods, but where square is the majority.
+For high  $\beta_e$, circle live  in ethnically segregated neighborhoods, where still value represent the majority of the own ethnic group.
+Though low $\beta_e$ reproduces the  initial random ethnic distribution, this doesn't happen for value distribution due to effect of majority size of square in both groups.
+* Proceeding with increase of same  value in the other ethnic group (x-axis), value assimilation increases for high levels of $\beta_e$ and low levels of $\beta_v$, in the same conditions ethnic segregation.
+As before circle agents increase  ethnic utility, but still have more chance to relocate close to square co-ethnics.
+Along $\beta_v$, increase implies value segregation as expected,  but ethnic assimilation when $\beta_e$ is low: circle agents not care about ethnic utility, but maxize value orientation, so that most appealing neighborhoods are those inhabited by circle of the other group.
+* The last observation is noteworthy to me, though predictable: as alternative to assimilation due to being in the ethnic minority size, people can fall into ethnic (spatial) assimilation because of an other characteristic (value) which is unequally represented in two ethnic group numerically equal
+
+```{r crlo,fig.pos='H',out.width='\\textwidth',fig.show = "hold",fig.align='center', fig.cap="Circle orange, equal ethnic size", echo=FALSE, include=TRUE  }
+
+dataone %>%  filter(fraction_blue == 50) %>%  gather(key = subgroup, value = Segra, eth_cl_or,val_cl_or) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"Value" = "val_cl_or","Ethnic" = "eth_cl_or"), "Value"))  %>%
   ggplot(aes(x = beta_ie,y = beta_iv, fill = Segra)) + geom_tile() + 
@@
 
-crlomj <- dataone %>%  filter(fraction_blue == 80) %>%  gather(key = subgroup, value = Segra, eth_cl_or,val_cl_or) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"Value" = "val_cl_or","Ethnic" = "eth_cl_or"), "Value"))  %>%
+```
+
+### Ethnic minority (Fig: \ref{fig:crlominority})
+
+* Trends are generally similar to Fig: \ref{fig:crlo}
+* In the baseline, ethnic assimilation emerges instead of ethnic integration, becuase of the ethnic minority of the group.
+* Up left corner, where circle represent the majority value of ethnic  minority and the minority value of ethnic majority, compared to Fig: \ref{fig:crlo} ethnic assimilation rather than integration emerges for the area of high randomness for both dimensions, and ethnic integration rather than segregation for the increase of $\beta_v$ and low values of $\beta_e$.
+While for areas of high randomness agents fall into assimilation because of numeric inferiority, when they increase value utility $\beta_v$ they want to relocate close to other circle agents, regardless of their ethnicity.
+Since in this condition circle represent the minority value of the majority ethnic population (the opposite of circle orange in ethnic minority), the combination allows for the increase in value preference to make up for the ethnic numeric inferiority, so that both circle minority and circle majority end up in neighborhoods ethnically integrated and value circle homogeneous (cfr Fig: \ref{fig:crlbl}, right down corner).
+* Low row: the effect of increase in $\beta_e$ on value assimilation is similar as Fig: \ref{fig:crlo}, since circle here represents the minority in the own group.
+Increase of $\beta_v$ shows instead higher assimilation, because circle minority has more chance to relocate close to similar circle value of the other ethnic group, proportionally to value circle being the majority value in the majority ethnic group.
+Interestingly, given the area of high ethnic utility for $\beta_e \geq 5$, at the increase of $\beta_v$ less homogenous ethnic segregation emerges compared to the equal ethnic size.
+* The last two  points are noteworthy to me: the assumption that similar values can foster ethnic integration over ethnic segregation can work provided that an adjustement between distribution of values in both ethnic group and preferences for ethnic or value utility are  taken into account.
+
+```{r crlominority,fig.pos='H',out.width='\\textwidth',fig.show = "hold",fig.align='center', fig.cap="Circle orange, ethnic minority", echo=FALSE, include=TRUE  }
+
+dataone %>%  filter(fraction_blue == 80) %>%  gather(key = subgroup, value = Segra, eth_cl_or,val_cl_or) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"Value" = "val_cl_or","Ethnic" = "eth_cl_or"), "Value"))  %>%
   ggplot(aes(x = beta_ie,y = beta_iv, fill = Segra)) + geom_tile() + 
@@
 
- crloeq
- crlomj
 ```
 
-```{r crlblmajority, fig.pos='t',out.width='\\textwidth',fig.show = "hold",fig.align='center',fig.show="hold", fig.cap="Circle in majority condition.", echo=FALSE, include=TRUE}
+### Ethnic majority (Fig: \ref{fig:crlblmajority})
+* Low row where circle are the minority in the ethnic majority blue, show the same pattern for the circle in minority and equal ethnic size: increasing in ethnic utility implies value assimilation to square  members of the same ethnic group, because of value numeric minority
+* Value integration occurs in the upper row ($50 \% $ circle in blue majority ethnic) for random area of low $\beta_v$, because eqaul chance to relocate close to either circle or square, but in both cases of same ethnic group
+* Compared to the baseline in Fig: \ref{fig:crlo}, ethnic segregation emerges also in area of high randomness ($\beta_e < 5$), because of numeric superiority, also for the upper side of the diagonal
+* Low right corner, where circle are the minority in the blue ethnicity, but majority in the ethnic minority, ethnic integration emerges for high values of $\beta_v$, despite ethnic minority of orange.
+Same as in Fig: \ref{fig:crlominority}
+
+```{r crlblmajority, fig.pos='t',out.width='\\textwidth',fig.show = "hold",fig.align='center',fig.show="hold", fig.cap="Circle blue, ethnic majority", echo=FALSE, include=TRUE}
 
@@
 
-# Effect of value distribution in group value differences
+# Second Section (heterogeneous preferences)
 
-Each graph is one level of $\%$ circle (value 1) in the local population (majority = blue agents). Each condition panel refers to distribution of  circle agents in the minority population.
+* Aim:
+    + Effect of different homophily preferences: direct effect of $\beta_e$ on ethnic segregation, and direct effect of beta value $\beta_v$ on value segregation, and reciprocal influences, i.e.
+how of $\beta_v$ influences effect of  $\beta_e$ on ethnic segregation and how $\beta_e$ influences effect of $\beta_v$ on value segregation
+* Focus: interaction between relative group size for each dimension with degree of $\beta$, since group size directly influence the probability to find similar ones and the systematic utility computed for each neighborhood
+* Assumption: 
+    + not heterogeneity: all agents hold both ethnic preference (same color) and value preference (same shape)
+    + ethnic size at global level: equal size (blue/orange: $0.50$), majority/minority (blue/orange: $0.80$)
+    + value size within each ethnic group: minority circle circle/square $0.20$, equal size circle/square $0.50$, majority circle circle/square $0.80$, imagining tolerant (circle) and intolerant (square),this means to move from more tolerant to less tolerant groups, both majority and minority.
+In this section there is not difference in preferences implied Tab \ref{tab:a}
+* Figures:
+    + Fig: \ref{fig:baselineone} represents how results are presented through the space of the model.
+Axis represent the ratio of $circle/square$ in each ethnic group, expressed as percentage: on y-axis the percentage of circle value in the orange ethnic group, on the x-axis the percentage of circle value in the blue ethnic group.
+The percentage of square agents can be calculated from it.
+The \textbf{baseline} condition is represented by the black dot, where each ethnicity is split equally into the two value groups ($0.50$ circle, $0.50$ square); following the diagonal, each ethnic group moves from minority circle to majority circle.
+Each obervation is repeated  for ethnic equal group sizes (blue/orange = $0.50$) and ethnic majority/minority condition (blue/orange = $0.80$).
+In the baseline condition for equal ethnic size, each group $valueXethnicity$ represents the $25 \%$ of the overall population.
+This means each agent in Fig: \ref{fig:thheory} has potentially probability $0.25$ to relocate close to someone who shares both ethnicity and value orientation.
+    + In all results $\beta = 5$ seems a threshold between area of high randomness and low randomness. I would use this as reference point in describing figures and change in conditions
 
-```{r heatmapdsquare,fig.pos='t',out.width='\\textwidth',fig.show = "hold",fig.align='center', fig.cap="Square orange, heterogenous preferences", echo=FALSE, include=TRUE }
+\begin{table}[H]
+\begin{tabular}{llll}
+\midrule
+ Static agent variable                      & Range         &      &                \\ \midrule
+ Ethnicity  (\textit{color})         & Blue, Orange        \\
+ Value orientation (\textit{shape}) & Square, Circle &  &  \\
+ \midrule
+
+ Parameters kept constant    & Slider & Range   & Experiments  \\ 
+ \midrule
+ Population density    & density                 & $[0,0.99]$   & $0.7$          \\
+ Peak ethnic utility & similar\_wanted\_ethnic & $[0,1]$ & $1$ (linear function) \\
+ Peak value utility & similar\_wanted\_value & $[0,1]$ & $1$ (linear function) \\
+ \midrule
+ \textbf{Parameters modified in experiment} & \textbf{Slider} & \textbf{Range}   & \textbf{Experiments}  \\ 
+ \midrule
+ Ethnic group ratio (local\/minority)  & fraction\_blue &  $[0,1]$      & $0.5,0.8$  \\
+ value ratio  blue population & circle\_blue & $[0,1]$      & $0.20,0.5,0.8$  \\
+ value ratio  orange population & circle\_blue & $[0,1]$      & $0.20,0.5,0.8$  \\
+ Determinism ethnic utility ($\beta_e$) & beta-ie for all agents & $[0,1]$ & $[0,10]$  \\
+ Determinism value utility ($\beta_v$) & beta-iv for all agents & $[0,1]$ & $[0,10]$ \\
+ \midrule
+ Global output measures    & Computation &   Range & \\ 
+ \midrule
+ Ethnic segregation  & same color neighborhood proportion & $0,\stackrel{+0.1}{\dots}, 1$ & global and subgroups\\
+ Value segregation  & same shape neighborhood proportion & $0,\stackrel{+0.1}{\dots}, 1$ & global and subgroups\\
+   \midrule
+Number of Runs   & 1 &  & \\ 
+ \midrule
+\end{tabular}
+ \caption{Basic Model} 
+ \label{tab:a}
+\end{table}
+
+```{r heatmapdsquare,fig.pos='H',out.width='\\textwidth',fig.show = "hold",fig.align='center', fig.cap="Square orange, heterogenous preferences", echo=FALSE, include=TRUE }
 
@@
 
-```{r heatmapdcircle, fig.pos='t',out.width='\\textwidth',fig.show = "hold",fig.align='center', fig.cap="Circle orange, heterogeneous preferences", echo=FALSE, include=TRUE }
+```{r heatmapdcircle, fig.pos='H',out.width='\\textwidth',fig.show = "hold",fig.align='center', fig.cap="Circle orange, heterogeneous preferences", echo=FALSE, include=TRUE }
 
@@
 
-```{r betatwoethnic,fig.pos='t',out.width="96%",fig.show = "hold",fig.align='center',fig.cap="Difference segregation", echo=FALSE, include=TRUE }
+```{r betatwoethnic,fig.pos='H',out.width="96%",fig.show = "hold",fig.align='center',fig.cap="Difference segregation", echo=FALSE, include=TRUE }
 
@@
 
-```{r betatwovalue,  fig.pos="t",fig.show = "hold", fig.align='center',fig.show="hold", fig.cap="Difference segregation between", echo=FALSE, include=TRUE  }
+```{r betatwovalue,  fig.pos="H",fig.show = "hold", fig.align='center',fig.show="hold", fig.cap="Difference segregation between", echo=FALSE, include=TRUE  }
 

### 2020-05-06 exp_eth_val.Rmd
Add files via upload

@@
  value ratio  orange population & circle\_blue & $[0,1]$      & $0.20,0.5,0.8$  \\
- Determinism ethnic utility ($\beta_e$) & beta-ie for all agents & $[0,1]$ & $[0,10]$  \\
- Determinism value utility ($\beta_v$) & beta-iv for all agents & $[0,1]$ & $[0,10]$ \\
+ Determinism ethnic utility ($\beta_e$) & beta-ie for all agents & $[0,10]$ & $[0,10]$  \\
+ Determinism value utility ($\beta_v$) & beta-iv for all agents & $[0,10]$ & $[0,10]$ \\
  \midrule
@@
  \midrule
- Ethnic segregation  & same color neighborhood proportion & $0,\stackrel{+0.1}{\dots}, 1$ & global and subgroups\\
- Value segregation  & same shape neighborhood proportion & $0,\stackrel{+0.1}{\dots}, 1$ & global and subgroups\\
+ Ethnic segregation  & same color neighborhood $\%$ & $0,\stackrel{+0.1}{\dots}, 1$ & global and subgroups\\
+ Value segregation  & same shape neighborhood $\%$  & $0,\stackrel{+0.1}{\dots}, 1$ & global and subgroups\\
    \midrule
-Number of Runs   & 1 &  & \\ 
+Number of Runs   & 1 & Numer of steps & 1000 \\ 
  \midrule
 \end{tabular}
- \caption{Basic Model} 
- \label{tab:a}
+ \caption{First Section} 
+ \label{tab:First}
 \end{table}
@@
 
-```{r crlblmajority, fig.pos='t',out.width='\\textwidth',fig.show = "hold",fig.align='center',fig.show="hold", fig.cap="Circle blue, ethnic majority", echo=FALSE, include=TRUE}
+```{r crlblmajority, fig.pos='H',out.width='\\textwidth',fig.show = "hold",fig.align='center',fig.show="hold", fig.cap="Circle blue, ethnic majority", echo=FALSE, include=TRUE}
 
@@
 
-# Second Section (heterogeneous preferences)
+# Second Section (heterogeneous preferences for tolerant and intolerants)
 
 * Aim:
-    + Effect of different homophily preferences: direct effect of $\beta_e$ on ethnic segregation, and direct effect of beta value $\beta_v$ on value segregation, and reciprocal influences, i.e.
-how of $\beta_v$ influences effect of  $\beta_e$ on ethnic segregation and how $\beta_e$ influences effect of $\beta_v$ on value segregation
-* Focus: interaction between relative group size for each dimension with degree of $\beta$, since group size directly influence the probability to find similar ones and the systematic utility computed for each neighborhood
+    + Test the effect of heterogeneous preferences for two value groups, i.e.
+circle value-oriented care more about value than ethnic neighborhood composition, square ethnicity-oriented care more about ethnic than value composition
+    + This would relate to the difference between tolerant (circle) and intolerant (square) as in the ACS paper and that we discussed
+    + Observe how heterogeneity in agents' preferences along two value oriented groups will affect results in the previous section, through their mutual adaptation
+    + Interaction between heterogeneous preferences and relative group sizes for both dimensions (here only equal ethnic and value group)
 * Assumption: 
-    + not heterogeneity: all agents hold both ethnic preference (same color) and value preference (same shape)
-    + ethnic size at global level: equal size (blue/orange: $0.50$), majority/minority (blue/orange: $0.80$)
-    + value size within each ethnic group: minority circle circle/square $0.20$, equal size circle/square $0.50$, majority circle circle/square $0.80$, imagining tolerant (circle) and intolerant (square),this means to move from more tolerant to less tolerant groups, both majority and minority.
-In this section there is not difference in preferences implied Tab \ref{tab:a}
+    + Agents hold both ethnic and value preferences, but $\beta$ for each dimension depends on their value orientation, either circle or square.
+Not difference due to ethnic membership are taken into consideration
+    + Given the linear function, utility increases with value or ethnic homogeneity of neighborhood, but determinism component $\beta_e$ and $\beta_v$ are differently distributed to value groups: ethnic preferences of circle cannot be higher than value preferences ($\beta^{\circ}_e \leq \beta^{\circ}_v$) and value preferences of square cannot be higher than thier value preferences ($\beta^{\square}_v \leq \beta^{\square}_e$)
+    + Ideally also condition of ethnic majority/minority and circle majority/minority should be included.
+Here for matter of time it is reduced to equal ethnic group size (blue/orange $0.50$) and for each ethnic group equal value group (circle/square $0.50$).
+So, each of the four subgroup in Fig: \ref{fig:thheory} represents the $25 \%$ of the global agents' population
 * Figures:
-    + Fig: \ref{fig:baselineone} represents how results are presented through the space of the model.
-Axis represent the ratio of $circle/square$ in each ethnic group, expressed as percentage: on y-axis the percentage of circle value in the orange ethnic group, on the x-axis the percentage of circle value in the blue ethnic group.
-The percentage of square agents can be calculated from it.
-The \textbf{baseline} condition is represented by the black dot, where each ethnicity is split equally into the two value groups ($0.50$ circle, $0.50$ square); following the diagonal, each ethnic group moves from minority circle to majority circle.
-Each obervation is repeated  for ethnic equal group sizes (blue/orange = $0.50$) and ethnic majority/minority condition (blue/orange = $0.80$).
-In the baseline condition for equal ethnic size, each group $valueXethnicity$ represents the $25 \%$ of the overall population.
-This means each agent in Fig: \ref{fig:thheory} has potentially probability $0.25$ to relocate close to someone who shares both ethnicity and value orientation.
-    + In all results $\beta = 5$ seems a threshold between area of high randomness and low randomness. I would use this as reference point in describing figures and change in conditions
+    + I compare the ethnic and value segregation of both circle and square agents
+    + Focus on the difference between ethnic and value segregation (being close to agents sharing both ethnicity and value)
+    + To reduce observations given the numbers of parameters, I jump on 3 critical points individualized in the previous section: $\beta = 0$: total randomness, $\beta = 5$: min.
+determinism, $\beta = 10$: max determinism
+    + For each value group, in the baseline I put on x-axis the difference between the highest reference $\beta$ of that group and the other one, i.e.
+$\beta_e - \beta_v$ for square, $\beta_v - \beta_e$ for circle.
+Considering the critical point, I repeat observation for reference $\beta = 5$: min.
+determinism, and $\beta = 10$: max determinism, $\beta = 0$ is included in bot.
+Thus, along the x-axis the group becomes more sensitive to the reference dimension, ethnicity for square group, value for circle group.
+I compare how the baseline condition changes for interaction of value and ethnic preferences of the other group faceting the 3 critical points $\beta = 0; \beta = 5;\beta = 10$
 
@@
  \midrule
- Ethnic group ratio (local\/minority)  & fraction\_blue &  $[0,1]$      & $0.5,0.8$  \\
- value ratio  blue population & circle\_blue & $[0,1]$      & $0.20,0.5,0.8$  \\
- value ratio  orange population & circle\_blue & $[0,1]$      & $0.20,0.5,0.8$  \\
- Determinism ethnic utility ($\beta_e$) & beta-ie for all agents & $[0,1]$ & $[0,10]$  \\
- Determinism value utility ($\beta_v$) & beta-iv for all agents & $[0,1]$ & $[0,10]$ \\
+ Ethnic group ratio (local\/minority)  & fraction\_blue &  $[0,1]$      & $0.5$  \\
+ value ratio  blue population & circle\_blue & $[0,1]$      & $0.5$  \\
+ value ratio  orange population & circle\_blue & $[0,1]$      & $0.5$  \\
+ Determinism ethnic utility square ($\beta^{\square}_e$) & beta-ie-sqr & $[0,10]$ & $[0,10]$  \\
+ Determinism value utility square ($\beta^{\square}_v$) & beta-iv-sqr  & $[0,10]$ & $[0,10], if \beta^{\square}_v \leq \beta^{\square}_e$ \\
+ Determinism value utility circle ($\beta^{\circ}_v$) & beta-iv-crl  & $[0,10]$ & $[0,10]$  \\
+ Determinism ethnic utility circle ($\beta^{\circ}_e$) & beta-ie-crl & $[0,10]$ & $[0,10], if \beta^{\circ}_e \leq \beta^{\circ}_v$  \\
  \midrule
@@
  \midrule
- Ethnic segregation  & same color neighborhood proportion & $0,\stackrel{+0.1}{\dots}, 1$ & global and subgroups\\
- Value segregation  & same shape neighborhood proportion & $0,\stackrel{+0.1}{\dots}, 1$ & global and subgroups\\
+ Ethnic segregation  & same color neighborhood $\%$ & $0,\stackrel{+0.1}{\dots}, 1$ & global and subgroups\\
+ Value segregation  & same shape neighborhood $\%$ & $0,\stackrel{+0.1}{\dots}, 1$ & global and subgroups\\
    \midrule
-Number of Runs   & 1 &  & \\ 
+Number of Runs   & 1 & Number of steps & 1000 \\ 
  \midrule
 \end{tabular}
- \caption{Basic Model} 
- \label{tab:a}
+ \caption{Second section: heterogeneous preferences} 
+ \label{tab:Second}
 \end{table}
 
-```{r heatmapdsquare,fig.pos='H',out.width='\\textwidth',fig.show = "hold",fig.align='center', fig.cap="Square orange, heterogenous preferences", echo=FALSE, include=TRUE }
+## Comparison different value orientation
+* Fig: \ref{fig:betatwoethnic}: x-axis $\beta^{\square}_e - \beta^{\square}_v$, on the top panel with $\beta^{\square}_e = 5$ (area of high randomness), on bottom panel  $\beta^{\square}_e = 10$ (area of low randomness).
+X-axis = 0,  ethnic and value utility have equal weight, along the x-axis ethnic weight prevails over value weight.
+the lower the distance between ethnic and value segregation, the more agents live close to others similar for both ethnicity and value.
+* Viewing at lower left panel, where behavior of circle is totally random, not only the distance between ethnic and value segregation of square is lower when $\beta^{\square}_e = \beta^{\square}_v$ (x-axis 0), but also higher for both dimensions, progressing towards x-axis (ethnic becomes higher than 10), value segregation decreases, with more linear slope for high determinism area (bottom panel).
+* It persists that each $\beta$ rules the reference dimension, but the random behavior of the other group decreases the segregation expected for that level of $\beta$, higher determinism of the other group increases  the level of segregation for that dimension.
+Demonstration, moving from $\beta^{\circ}_v = 5$ to  $\beta^{\circ}_v = 10$
+* As $\beta^{\square}_e$ becomes higher than  $\beta^{\square}_v$, moving on the x-axis, ethnic segregation persists constantly, while value segregation diminishes.
+* The threshold of $\beta = 5$ seen in the previous section is somehow replicated: in the top panel, max value and ethnic segregation are equal 1 when both  $\beta^{\square}_e = \beta^{\square}_v = 0$, on the x-axis 0, and value segregation declines once $\beta^{\square}_v$ comes close to 0.
+Looking at panel below (high determinism), the decline of value segregation occurs equally when $\beta^{\square}_v$ declines from 5 to 0 (on the right of red line 10-5:5 and so on)
+* Even though the direct effect of $\beta_v$ is assumed and same patterns are observed from low determinism (top panel) and high determinism (bottom panel), the high determinism of  $\beta^{\square}_e$ is associated with very slight increase in the value segregation of square, also for same level of $\beta^{\square}_v = 0$, though negligeable
+* The distance between ethnic and value segregation is higher in the middle panel, where circle hold same min utility preferences $\beta^{\circ}_e = \beta^{\circ}_v = 5$, and also square increase in ethnic over value preference (x-axis = 5).
+Basically the only random component is the value orientation of square agents, which has the same effect on both circle and square population patterns
+* Moving on the diagonal, where $\beta^{\circ}_e = \beta^{\circ}_v = 10$, the distance between ethnic and value decreases, meaning agents are more likely to live close to agents of both same ethnicity and value: the increase in utility at max level of circle ($\beta^{\circ}_e = \beta^{\circ}_v = 10$) compensates for random value behavior of square, since circle will avoid neighborhoods with square
+* Fig: \ref{fig:betatwovalue} shows the similar trends, focusing on value segregation over ethnic segregation for the circle population.
+Nevertheless, in the middle panel ($\beta^{\square}_e = \beta^{\square}_v = 5$), I would expect symmetric scenario than in Fig: \ref{fig:betatwoethnic}, with ethnic segregation of circle being same as value segregatiion than square.
+Why here circle are completed ethnically integrared?
+There is a difference between the two dimensions?
+Think about.
 
-circle_frame <- datatwo %>% filter(step == 1000) %>% filter(beta_iv_circle == 0 |beta_iv_circle == 5 |beta_iv_circle == 10 ) %>% filter(beta_ie_circle == 0 | beta_ie_circle == 5 | beta_ie_circle == 10)
-
-rev_beta_iv_circle.labs <- c("Circle \nß value 10" ,"Circle \nß value 5", "Circle \nß value 0")
-names(rev_beta_iv_circle.labs) <- c("10", "5","0")
-beta_ie_circle.labs <- c("Circle \nß ethnic 0", "Circle \nß ethnic 5","Circle \nß ethnic 10")
-names(beta_ie_circle.labs) <- c("0", "5","10")
-
-circle_frame %>%   gather(key = subgroup, value = Segra, eth_sq_or,val_sq_or) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"ETHNIC" = "eth_sq_or", "VALUE" = "val_sq_or"), "ethnic segregation")) %>%
-  ggplot(aes(x = beta_iv_square, y = beta_ie_square, fill = Segra)) + geom_tile() + facet_grid(rev_beta_iv_circle ~  beta_ie_circle + segregation, labeller = labeller(rev_beta_iv_circle = rev_beta_iv_circle.labs, beta_ie_circle = beta_ie_circle.labs)) +
-   scale_fill_distiller(palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) +
-  scale_x_discrete( limits=c(0,10, by = 5)) +
-  scale_y_discrete( limits=c(0,10, by = 5)) +
- xlab("ß value square") + ylab("ß ethnic square") + ggtitle("Square orange, baseline") + 
-    theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0))
-
-```
-
-```{r heatmapdcircle, fig.pos='H',out.width='\\textwidth',fig.show = "hold",fig.align='center', fig.cap="Circle orange, heterogeneous preferences", echo=FALSE, include=TRUE }
-
-circle_frame <- datatwo %>% filter(step == 1000) %>% filter(beta_ie_square == 0 |beta_ie_square == 5 |beta_ie_square == 10 ) %>% filter(beta_iv_square == 0 | beta_iv_square == 5 | beta_iv_square == 10)
-
-rev_beta_ie_square.labs <- c("Square \nß ethnic 10" ,"Square \nß ethnic 5","Square \nß ethnic 0")
-names(rev_beta_ie_square.labs) <- c("10", "5","0")
-beta_iv_square.labs <- c("Square \nß value 0", "Square \nß value 5","Square \nß value 10")
-names(beta_iv_square.labs) <- c("0", "5","10")
-
-circle_frame %>%   gather(key = subgroup, value = Segra, eth_cl_or,val_cl_or) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"ETHNIC" = "eth_cl_or", "VALUE" = "val_cl_or"), "ethnic segregation")) %>%
-  ggplot(aes(x = beta_ie_circle, y = beta_iv_circle, fill = Segra)) + geom_tile() + facet_grid(rev_beta_ie_square ~  beta_iv_square + segregation, labeller = labeller(rev_beta_ie_square = rev_beta_ie_square.labs, beta_iv_square = beta_iv_square.labs)) +
-   scale_fill_distiller(palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) +
-  scale_x_discrete( limits=c(0,10, by = 5)) +
-  scale_y_discrete( limits=c(0,10, by = 5)) +
- xlab("ß ethnic circle") + ylab("ß value circle") + ggtitle("Circle orange, baseline") + 
-    theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0))
-
-```
-
-```{r betatwoethnic,fig.pos='H',out.width="96%",fig.show = "hold",fig.align='center',fig.cap="Difference segregation", echo=FALSE, include=TRUE }
+```{r betatwoethnic,fig.pos='H',fig.show = "hold",fig.align='center',fig.cap="Difference segregation, x-axis: difference ethnic and value preference square, faceting conditions: preferences of circle", echo=FALSE, include=TRUE }
 
@@
 ie_10 <- circle_frame %>%  filter(beta_ie_square == 10) %>% gather(key = subgroup, value = Segra, eth_sq_or,val_sq_or,eth_cl_or,val_cl_or) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"ethnic segregation" = c("eth_sq_or","eth_cl_or"), "value segregation" = c("val_sq_or","val_cl_or")), "ethnic segregation"), `group` = fct_relevel(fct_collapse(subgroup, "square minority" = c("eth_sq_or","val_sq_or"), "circle minority" = c("eth_cl_or","val_cl_or"), "square minority"))) %>%
-  ggplot(aes(x = (beta_ie_square - beta_iv_square), y = Segra, color = `segregation`, shape = `group`)) + geom_line() + geom_point() + facet_grid(rev_beta_iv_circle ~  beta_ie_circle, labeller = labeller(rev_beta_iv_circle = rev_beta_iv_circle.labs,  beta_ie_circle = e_circle.labs )) +
+  ggplot(aes(x = (beta_ie_square - beta_iv_square), y = Segra, color = `segregation`, shape = `group`)) + geom_line() + geom_point( size = 2) + facet_grid(rev_beta_iv_circle ~  beta_ie_circle, labeller = labeller(rev_beta_iv_circle = rev_beta_iv_circle.labs,  beta_ie_circle = e_circle.labs )) +
   geom_vline(xintercept = 5, color = "red") +
@@
 ie_5 <- circle_frame %>%  filter(beta_ie_square == 5) %>% gather(key = subgroup, value = Segra, eth_sq_or,val_sq_or,eth_cl_or,val_cl_or) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"ethnic segregation" = c("eth_sq_or","eth_cl_or"), "value segregation" = c("val_sq_or","val_cl_or")), "ethnic segregation"), `group` = fct_relevel(fct_collapse(subgroup, "square minority" = c("eth_sq_or","val_sq_or"), "circle minority" = c("eth_cl_or","val_cl_or"), "square minority"))) %>%
-  ggplot(aes(x = (beta_ie_square - beta_iv_square), y = Segra, color = `segregation`, shape = `group`)) + geom_line() + geom_point() + facet_grid(rev_beta_iv_circle ~  beta_ie_circle, labeller = labeller(rev_beta_iv_circle = rev_beta_iv_circle.labs,  beta_ie_circle = e_circle.labs )) +
+  ggplot(aes(x = (beta_ie_square - beta_iv_square), y = Segra, color = `segregation`, shape = `group`)) + geom_line() + geom_point( size = 2) + facet_grid(rev_beta_iv_circle ~  beta_ie_circle, labeller = labeller(rev_beta_iv_circle = rev_beta_iv_circle.labs,  beta_ie_circle = e_circle.labs )) +
   scale_x_discrete(name = "ß ethnic square 5 - ß value square", limits = seq(0,5, by = 1)) +  ylab("Segregation") +
@@
 iv_10 <- circle_frame %>%  filter(beta_iv_circle == 10) %>% gather(key = subgroup, value = Segra, eth_sq_or,val_sq_or,eth_cl_or,val_cl_or) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"ethnic segregation" = c("eth_sq_or","eth_cl_or"), "value segregation" = c("val_sq_or","val_cl_or")), "ethnic segregation"), `group` = fct_relevel(fct_collapse(subgroup, "square minority" = c("eth_sq_or","val_sq_or"), "circle minority" = c("eth_cl_or","val_cl_or"), "square minority")))  %>%
-  ggplot(aes(x = (beta_iv_circle - beta_ie_circle), y = Segra, color = `segregation`, shape = `group`)) + geom_line() + geom_point() + facet_grid(rev_beta_ie_square ~  beta_iv_square, labeller = labeller(rev_beta_ie_square = rev_beta_ie_square.labs, beta_iv_square = v_square.labs))  +
+  ggplot(aes(x = (beta_iv_circle - beta_ie_circle), y = Segra, color = `segregation`, shape = `group`)) + geom_line() + geom_point( size = 2) + facet_grid(rev_beta_ie_square ~  beta_iv_square, labeller = labeller(rev_beta_ie_square = rev_beta_ie_square.labs, beta_iv_square = v_square.labs))  +
   geom_vline(xintercept = 5, color = "red") +
@@
 iv_5 <- circle_frame %>%  filter(beta_iv_circle == 5) %>% gather(key = subgroup, value = Segra, eth_sq_or,val_sq_or,eth_cl_or,val_cl_or) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"ethnic segregation" = c("eth_sq_or","eth_cl_or"), "value segregation" = c("val_sq_or","val_cl_or")), "ethnic segregation"), `group` = fct_relevel(fct_collapse(subgroup, "square minority" = c("eth_sq_or","val_sq_or"), "circle minority" = c("eth_cl_or","val_cl_or"), "square minority")))  %>%
-  ggplot(aes(x = (beta_iv_circle - beta_ie_circle), y = Segra, color = `segregation`, shape = `group`)) + geom_line() + geom_point() + facet_grid(rev_beta_ie_square ~  beta_iv_square, labeller = labeller(rev_beta_ie_square = rev_beta_ie_square.labs, beta_iv_square = v_square.labs))  +
+  ggplot(aes(x = (beta_iv_circle - beta_ie_circle), y = Segra, color = `segregation`, shape = `group`)) + geom_line() + geom_point( size = 2) + facet_grid(rev_beta_ie_square ~  beta_iv_square, labeller = labeller(rev_beta_ie_square = rev_beta_ie_square.labs, beta_iv_square = v_square.labs))  +
   scale_x_discrete(name = "ß value circle 10 - ß ethnic circle", limits = seq(0,5, by = 1)) +  ylab("Segregation") +
@@
 
-# ANNEX
+# ANNEX A {-}
 
@@
 ```
+
+# ANNEX B  {-}
+
+```{r heatmapdsquare,fig.pos='H',out.width='\\textwidth',fig.show = "hold",fig.align='center', fig.cap="Square orange, heterogenous preferences", echo=FALSE, include=TRUE }
+
+circle_frame <- datatwo %>% filter(step == 1000) %>% filter(beta_iv_circle == 0 |beta_iv_circle == 5 |beta_iv_circle == 10 ) %>% filter(beta_ie_circle == 0 | beta_ie_circle == 5 | beta_ie_circle == 10)
+
+rev_beta_iv_circle.labs <- c("Circle \nß value 10" ,"Circle \nß value 5", "Circle \nß value 0")
+names(rev_beta_iv_circle.labs) <- c("10", "5","0")
+beta_ie_circle.labs <- c("Circle \nß ethnic 0", "Circle \nß ethnic 5","Circle \nß ethnic 10")
+names(beta_ie_circle.labs) <- c("0", "5","10")
+
+circle_frame %>%   gather(key = subgroup, value = Segra, eth_sq_or,val_sq_or) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"ETHNIC" = "eth_sq_or", "VALUE" = "val_sq_or"), "ethnic segregation")) %>%
+  ggplot(aes(x = beta_iv_square, y = beta_ie_square, fill = Segra)) + geom_tile() + facet_grid(rev_beta_iv_circle ~  beta_ie_circle + segregation, labeller = labeller(rev_beta_iv_circle = rev_beta_iv_circle.labs, beta_ie_circle = beta_ie_circle.labs)) +
+   scale_fill_distiller(palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) +
+  scale_x_discrete( limits=c(0,10, by = 5)) +
+  scale_y_discrete( limits=c(0,10, by = 5)) +
+ xlab("ß value square") + ylab("ß ethnic square") + ggtitle("Square orange, baseline") + 
+    theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0))
+
+```
+
+```{r heatmapdcircle, fig.pos='H',out.width='\\textwidth',fig.show = "hold",fig.align='center', fig.cap="Circle orange, heterogeneous preferences", echo=FALSE, include=TRUE }
+
+circle_frame <- datatwo %>% filter(step == 1000) %>% filter(beta_ie_square == 0 |beta_ie_square == 5 |beta_ie_square == 10 ) %>% filter(beta_iv_square == 0 | beta_iv_square == 5 | beta_iv_square == 10)
+
+rev_beta_ie_square.labs <- c("Square \nß ethnic 10" ,"Square \nß ethnic 5","Square \nß ethnic 0")
+names(rev_beta_ie_square.labs) <- c("10", "5","0")
+beta_iv_square.labs <- c("Square \nß value 0", "Square \nß value 5","Square \nß value 10")
+names(beta_iv_square.labs) <- c("0", "5","10")
+
+circle_frame %>%   gather(key = subgroup, value = Segra, eth_cl_or,val_cl_or) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"ETHNIC" = "eth_cl_or", "VALUE" = "val_cl_or"), "ethnic segregation")) %>%
+  ggplot(aes(x = beta_ie_circle, y = beta_iv_circle, fill = Segra)) + geom_tile() + facet_grid(rev_beta_ie_square ~  beta_iv_square + segregation, labeller = labeller(rev_beta_ie_square = rev_beta_ie_square.labs, beta_iv_square = beta_iv_square.labs)) +
+   scale_fill_distiller(palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) +
+  scale_x_discrete( limits=c(0,10, by = 5)) +
+  scale_y_discrete( limits=c(0,10, by = 5)) +
+ xlab("ß ethnic circle") + ylab("ß value circle") + ggtitle("Circle orange, baseline") + 
+    theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0))
+
+```
+
+## Fig: \ref{fig:heatmapdsquare}
+*  Fig: \ref{fig:heatmapdsquare} reports in heatmaps $\beta^{\square}_e$ on y-axis $\beta^{\square}_v$ on x-axis for square agents, as such on y-axis is the most important preference for the value group square, the triangle shape is due to the condition $\beta^{\square}_v \leq \beta^{\square}_e$.
+* Faceted for the condition of the other group, focusin on 3 degree: total randomness $\beta^{\circ} = 0$, threshold between area of high and low randomness $\beta^{\circ} = 5$ and highest systematic component $\beta^{\circ} = 10$.
+For each condition ethnic and value segregation of squared population is calculated
+* Lower area, where the other group shows total random behavior ($\beta^{\circ} = 0$) for both ethnic and value utility, value integration emerges with low $\beta^{\square}_v$ regardless the increase in $\beta^{\square}_e$.
+Higher value segregation occurs only for the highest levels of $\beta^{\square}_v$ and $\beta^{\square}_e$.
+Ethnic segregation increases along the diagonal where $\beta^{\square}_v = \beta^{\square}_e$.
+Lower ethnic segregation compared to the other conditions in the area of high ethnic utility $\beta^{\square}_e$
+* Second row, first panel: for total random value behavior of square $\beta^{\square}_v = 0$, the ethnic segregation is linear to the increase of  $\beta^{\square}_e$, not showing the threshold difference as in Fig: \ref{fig:crlo}, this only with ethnic randomness of circle agents $\beta^{\circ}_e = 0$, but reach the critical point of $\beta^{\circ}_v = 5$ for value preferences.
+The sensitivity to change persists, but the sensitivity to chance decreases, because agents are split into two groups, for the same dimension that both share (ethnicity), one maximizes, the other not, and viceversa one doesn't care about value, while the other group maximizes value.
+* My guess: circle agents would gather together in ethnically mixed neighborhoods (cfr Fig: \ref{fig:heatmapdcircle}, ethnic integration along $\beta^{\circ}_v$), which attract square ethnicity-oriented at increase of  $\beta^{\square}_e$, they not care about the value orientation of the neighborhood.
+Compared to the previous section, $\beta^{\square}_e$ applies to $50\%$ of the population, so that the reduced amount of square agents entering the neighborhood would be tolerated by circle, but not when the $\beta^{\square}_e$ increases and too square agents enter the neighborhood, which would explain why value segregation persists rather than value integration as would be expected.
+* In the next panel where circle hold minimum threshold for both ethnic and value preferences $\beta^{\circ}_v = \beta^{\circ}_e = 5$, the demark between high randomness for $\beta^{\square}_e < 5$ and high utility $\beta^{\square}_e \geq 5$ returns and corresponds to value integration.
+* value segregation increases homogeneously when circle population maximizes  $\beta^{\circ}_v = 10$
+
+## Fig: \ref{fig:heatmapdsquare}
+* Fig: \ref{fig:heatmapdsquare}, for cirlce agents with higher value preferences than ethnic preferences, ethnic integration emerges for area of ethnic randomness with $\beta^{\circ}_e < 5$
+* Value segregation on the top right, where square agents show maximal ethnic and value utility  $\beta^{\square}_e = \beta^{\square}_v = 10$, full value segregation emerges for all conditions of $\beta$ levels, while in high ethnic utility area $\beta^{\square}_e \geq 5$ circle live in neighborhoods both value and ethnic homogeneous, for $\beta^{\square}_e <  5$ they live in ethnically mixed neighborhoods with circle of other ethnicity

### 2020-05-07 exp_eth_val.Rmd
presentation

@@
     toc: false
- #   keep_tex: false
+    keep_tex: true
     fig_caption: yes
@@
 - Research question: How the interplay of ethnic and value homophily preferences can explain difference in the degree of integration for the members of the same ethnic group (hybrid segregation) for both ethnic and value segregation.
-- Focus: different weight on the two dimensions, heterogeneity among agents, relative group size for both dimensions \par
+- Focus: different weight on ethnic homogeneity ($\beta_e$) and value homogeneity ($\beta_v$), heterogeneity among agents, relative group size for both dimensions \par
 
@@
 
-```{r thheory, fig.pos="h", out.width="50%",out.width='\\textwidth',fig.align='left',fig.show="hold", fig.cap="Agents distinction and utility function", echo=FALSE, include=TRUE }
+```{r thheory, fig.pos="h", out.width="50%",out.width='\\textwidth',fig.align='left',fig.show="hold", fig.cap="Agents distinction (subgroups) and utility function", echo=FALSE, include=TRUE }
 
@@
 
-# First Section (effect of relative group size)
+# First Section (Tab: \ref{tab:First})
 
 * Aim:
-    + Effect of different homophily preferences: direct effect of $\beta_e$ on ethnic segregation, and direct effect of beta value $\beta_v$ on value segregation, and reciprocal influences, i.e.
-how of $\beta_v$ influences effect of  $\beta_e$ on ethnic segregation and how $\beta_e$ influences effect of $\beta_v$ on value segregation
-* Focus: interaction between relative group size for each dimension with degree of $\beta$, since group size directly influence the probability to find similar ones and the systematic utility computed for each neighborhood
+    + Effect of different homophily preferences: direct effect of $\beta_e$ on ethnic segregation, and direct effect of beta value $\beta_v$ on value segregation; how $\beta_v$ influences effect of  $\beta_e$ on ethnic segregation and how $\beta_e$ influences effect of $\beta_v$ on value segregation
+* Focus: relative group size for ethnicity and value distribution within each ethnic group, considering how they directly influence probability to sort with similars; interaction with levels of $\beta_e$,$\beta_v$
 * Assumption: 
-    + not heterogeneity: all agents hold both ethnic preference (same color) and value preference (same shape)
-    + ethnic size at global level: equal size (blue/orange: $0.50$), majority/minority (blue/orange: $0.80$)
-    + value size within each ethnic group: minority circle circle/square $0.20$, equal size circle/square $0.50$, majority circle circle/square $0.80$, imagining tolerant (circle) and intolerant (square),this means to move from more tolerant to less tolerant groups, both majority and minority.
-In this section there is not difference in preferences implied Tab \ref{tab:a}
+    + not heterogeneity: all agents hold both ethnic preference (same color) and value preference (same shape) depending on level of global $\beta_e$ and $\beta_v$
+    + equal ethnic size (blue/orange: $0.50$) vs majority/minority (blue/orange: $0.80$)
+    + value distribution within each ethnic group: proportion circle/square, moving from minority circle to majority cirlce:  $0.20$,$0.50$,$0.80$.
+It can be seen as moving from more intolerant to  more intolerant society when value-dependent heterogeneous preferences are included.
+In this section, there is not heterogeneous preferences
 * Figures:
     + Fig: \ref{fig:baselineone} represents how results are presented through the space of the model.
-Axis represent the ratio of $circle/square$ in each ethnic group, expressed as percentage: on y-axis the percentage of circle value in the orange ethnic group, on the x-axis the percentage of circle value in the blue ethnic group.
-The percentage of square agents can be calculated from it.
-The \textbf{baseline} condition is represented by the black dot, where each ethnicity is split equally into the two value groups ($0.50$ circle, $0.50$ square); following the diagonal, each ethnic group moves from minority circle to majority circle.
-Each obervation is repeated  for ethnic equal group sizes (blue/orange = $0.50$) and ethnic majority/minority condition (blue/orange = $0.80$).
-In the baseline condition for equal ethnic size, each group $valueXethnicity$ represents the $25 \%$ of the overall population.
-This means each agent in Fig: \ref{fig:thheory} has potentially probability $0.25$ to relocate close to someone who shares both ethnicity and value orientation.
-    + In all results $\beta = 5$ seems a threshold between area of high randomness and low randomness. I would use this as reference point in describing figures and change in conditions
+I identified $\beta =5$ for both ethnic and value preferences as threshold between area of high randomness and low randomness.
+Results can be explained as within the space resulting from area of high randomness and low randomness (i.e.
+high systematic component) for ethnic and value utility.
+    + Relative group sizes: the bold frame in Fig: \ref{fig:global} would represent the baseline, where each subgroup in Fig: \ref{fig:thheory} represents the $25 \%$ of the population and has probability $0.25$ to meet an agent of same ethnicity and same value (baseline: blue/orange = $0.5$ and within each ethnic group cirlce/square = $0.5$)
+    + Relative group sizes (value orientation): in each figure from Fig: \ref{fig:global} to Fig: \ref{fig:crlblmajority} along the diagonal, moves from minority circle (low corner) in the population to majority circle (upper corner)
+    + x-axis = ethnic weight $\beta_e$, y-axis = value weight $\beta_v$
 
@@
 
-## Global Observations
-* Fig: \ref{fig:global} and  Fig: \ref{fig:global-maj} shows the global ethnic and value segregation, for equal ethnic group sizes in Fig: \ref{fig:global}  and majority/minority ethnic condition in Fig: \ref{fig:global-maj}  .
-The heatmaps report in each condition  $\beta_e$ on x-axis, and  $\beta_v$ on y-axis.
-* Ethnic segregation increases along the axis of $\beta_e$, while value segregation symmetrically along the axis of $\beta_v$.
-In both cases $\beta = 5$ shows a threshold between areas of integration and area of segregation.
-* While area below $\beta = 5$ is linearly increasing, areas above $\beta = 5$ seem to show same degree of high segregation.
-Attributing this to randomness component, I would identify area $\beta < 5$ as low randomness, area  $\beta \geq 5$ high randomness, and focus on threshold of $\beta = 5$, this helps presenting figures later
-* The threshold of $\beta = 5$ to me can relate to "sensitivity to change" in @van2009neighborhood: since the shape of utility is linearly increasing, each change in the composition of neighborhood will increase the difference between options.
-Once the difference is multiplied times $\beta$, the effect of utility difference is too high and soon the best option is taken.
-This means that only for very low levels of $\beta$ it is possible to see a linear increasing in the systematic utility.
-At $\beta = 5$ the systematic utility becomes too strong and agents highly sensitive to the change in neighborhood composition, moving to the best solution, increasing segregation of neighborhoods.
-This soon attires other agents and equilibria towards segregation are easily reached.
-* The direct effect of $\beta_e$ on ethnic segregation and  $\beta_v$ on value segregation seems unaffected by the other systemic component, both when  $\beta = 0$, so that agents relocate randomly for value or ethnic homophily, and when they increase the systemic utility for either ethnic (increase in  $\beta_e$) or value homophily (increase in $\beta_v$)
-* Condition of ethnic majority/minority shows basically the same patterns, slighter high ethnic segregation for the area of high randomness, which is direct effect of unequal group sizes.
-* Change in ethnic segregation compared to the baseline seem to occur only along the diagonal, where circle orientation represents the minority in one group and majority in the other, or vice versa.
-Similar slightly changes occur in the area of high randomness $\beta_e < 5$ with increase of $\beta_v$, which is counterintuitive.
-Circle of both ethnic group not care about ethnic composition of the neighborhood, but they care about the value composition.
-Since in one ethnic group circle represent the value majority, and in the other the circle minority, circle in the minority condition will result in ethnically mixed or majority out-group neighborhoods, circle in the majority in ethnically homogeneous neighborhoods, since they have more probability to find someone circle of the own ethnic group than the other.
-So, for these agents ethnic segregation is the more likely outcome, also if the systematic component of utility is for value segregation and ethnic utility random.
-The global results are influenced by the numeric superiority of these  agents.
-    * Next figures look at the behavior of specific subgroup in Fig. \ref{fig:thheory}
-
-```{r baselineone,fig.pos='H',out.width='\\textwidth',fig.show = "hold",fig.align='center', fig.cap=" Baseline space", echo=FALSE, include=TRUE  }
+```{r baselineone,fig.pos='H',out.width="96%",fig.show = "hold",fig.align='center', fig.cap="Space of model", echo=FALSE, include=TRUE  }
 
@@
 ```
+
+## Global value and  ethnic segregation (Fig: \ref{fig:global}, Fig: \ref{fig:global-maj})
+
+* Fig: \ref{fig:global}: equal ethnic size, Fig: \ref{fig:global-maj}: majority/minority condition
+* Ethnic segregation increases along the axis of $\beta_e$, while value segregation symmetrically along the axis of $\beta_v$.
+In both cases $\beta = 5$ seems a critical limit between high randomness and low randomness (high systematic utility).
+Consequently, area in the space $\beta < 5$ is closer  to ethnic and value integration, due to random relocation, area $\beta >= 5$ shows complete segregation because of the systematic component
+* While ethnic and value segregation linearly increase for the high randomness area below  $\beta = 5$, segregation for both dimensions for $\beta > 5$ seems homogeneous at high level
+* The limit of $\beta = 5$ to me can relate to "sensitivity to change" in @van2009neighborhood: since the shape of utility is linearly increasing, each difference in neighborhood composition corresponds to a change in utility.
+The product $\beta * \Delta Utility$ is affected by randomness only for very low levels of $\beta$, with $\beta =5$ it becomes too strong: agents are too sensitive to the systematic utility, moving to the neighborhood with the higher utility, affecting its composition, which will increase the utility difference and attractiveness of the neighborhood to agents in next step, falling shortly into complete segregation.
+Difference for higher levels of $\beta = 5$ is negligible.
+* At $\beta = 0$ for each dimnension, increase in the other $\beta$ ($\beta_v$ on $\beta_e$ and $\beta_e$ on $\beta_v$) does not produce effects, apart in the area of high randomness when one value group represents the minority in one ethnicity and the majority on the other (upper left and lower right panel).
+Affected  by relocation of majority value.
+* Condition of ethnic majority/minority shows basically the same patterns, slightly higher ethnic segregation for the area of high randomness, which is direct effect of unequal group sizes.
 
@@
 
+  rev_circle_blue.labs <- c("80% Circle \nBlue" ,"50% Circle \nBlue","20% Circle \nBlue")
+names(rev_circle_blue.labs) <- c("80", "50","20")
+ rev_circle_orange.labs <-  c("80% Circle \nOrange", "50% Circle \nOrange","20% Circle \nOrange")
+names(rev_circle_orange.labs) <- c("80", "50","20")
+
 # eth_mj <- ggplot(gen_mj, aes( beta_iv, beta_ie,fill= eth_seg))
@@
 
-eth_eq <- ggplot(data=subset(dataone,fraction_blue == 50 & step == 1000), aes( beta_ie, beta_iv,fill= eth_seg)) + geom_tile() +   facet_grid(circle_orange  ~  circle_blue,  space = "free_x", labeller = labeller(circle_blue = circle_local.labs,  circle_orange = circle_minority.labs ))  +
+eth_eq <- ggplot(data=subset(dataone,fraction_blue == 50 & step == 1000), aes( beta_ie, beta_iv,fill= eth_seg)) + geom_tile() +   facet_grid(rev_circle_orange  ~  circle_blue,  space = "free_x", labeller = labeller(circle_blue = circle_local.labs,  rev_circle_orange = rev_circle_orange.labs ), switch  = "y")  +
   scale_fill_distiller(name = "ETHNIC",palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) + 
   scale_x_discrete(name = "ß ethnic", limits=seq(0,10 ,by = 1)) + 
-  scale_y_discrete(name = "ß value", limits=c(0,3,5,7,10))   + 
+  scale_y_discrete(name = "ß value", limits=c(0,3,5,7,10), position = "right")   + 
   theme_bw() + theme(strip.text.x = element_text(), legend.position = "right", panel.grid.minor.x = element_blank(), plot.title=element_blank(),  legend.margin=margin(0,0,0,0)) +
@@
 
-val_eq <- ggplot(data=subset(dataone,fraction_blue == 50 & step == 1000), aes( beta_ie, beta_iv,fill= val_seg)) + geom_tile() +   facet_grid(circle_orange  ~  circle_blue,  space = "free_x", labeller = labeller(circle_blue = circle_local.labs,  circle_orange = circle_minority.labs )) +
+val_eq <- ggplot(data=subset(dataone,fraction_blue == 50 & step == 1000), aes( beta_ie, beta_iv,fill= val_seg)) + geom_tile() +   facet_grid(rev_circle_orange  ~  circle_blue,  space = "free_x", labeller = labeller(circle_blue = circle_local.labs,  rev_circle_orange = rev_circle_orange.labs ), switch  = "y")  +
   scale_fill_distiller(name = "VALUE",palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) + 
   scale_x_discrete(name = "ß ethnic", limits=seq(0,10 ,by = 1)) + 
-  scale_y_discrete(name = "ß value", limits=c(0,3,5,7,10))  + 
+  scale_y_discrete(name = "ß value", limits=c(0,3,5,7,10), position = "right")  + 
   theme_bw() + theme(strip.text.x = element_text(), legend.position = "right", panel.grid.minor.x = element_blank(), plot.title=element_blank(),  legend.margin=margin(0,0,0,0)) +
@@
 
-maj_eth <- ggplot(data=subset(dataone,fraction_blue == 80 & step == 1000), aes( beta_ie, beta_iv,fill= eth_seg)) + geom_tile() +   facet_grid(circle_orange  ~  circle_blue,  space = "free_x", labeller = labeller(circle_blue = circle_local.labs,  circle_orange = circle_minority.labs ))  +
+maj_eth <- ggplot(data=subset(dataone,fraction_blue == 80 & step == 1000), aes( beta_ie, beta_iv,fill= eth_seg)) + geom_tile() +   facet_grid(rev_circle_orange  ~  circle_blue,  space = "free_x", labeller = labeller(circle_blue = circle_local.labs,  rev_circle_orange = rev_circle_orange.labs ), switch  = "y")  +
   scale_fill_distiller(name = "ETHNIC",palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) + 
   scale_x_discrete(name = "ß ethnic", limits=seq(0,10 ,by = 1)) + 
-  scale_y_discrete(name = "ß value", limits=c(0,3,5,7,10)) + 
+  scale_y_discrete(name = "ß value", limits=c(0,3,5,7,10), position = "right") + 
   theme_bw() + theme(strip.text.x = element_text(), legend.position = "right", panel.grid.minor.x = element_blank(), plot.title=element_blank(),  legend.margin=margin(0,0,0,0)) +
@@
 
-maj_val <- ggplot(data=subset(dataone,fraction_blue == 80 & step == 1000), aes( beta_ie, beta_iv,fill= val_seg)) + geom_tile() +   facet_grid(circle_orange  ~  circle_blue,  space = "free_x", labeller = labeller(circle_blue = circle_local.labs,  circle_orange = circle_minority.labs )) +
+maj_val <- ggplot(data=subset(dataone,fraction_blue == 80 & step == 1000), aes( beta_ie, beta_iv,fill= val_seg)) + geom_tile() +   facet_grid(rev_circle_orange  ~  circle_blue,  space = "free_x", labeller = labeller(circle_blue = circle_local.labs,  rev_circle_orange = rev_circle_orange.labs ), switch  = "y")  +
   scale_fill_distiller(name = "VALUE",palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) + 
  scale_x_discrete(name = "ß ethnic", limits=seq(0,10 ,by = 1)) + 
-  scale_y_discrete(name = "ß value", limits=c(0,3,5,7,10))  + 
+  scale_y_discrete(name = "ß value", limits=c(0,3,5,7,10), position = "right")  + 
   theme_bw() + theme(strip.text.x = element_text(), legend.position = "right", panel.grid.minor.x = element_blank(), plot.title=element_blank(),  legend.margin=margin(0,0,0,0)) +
@@
 
-## Observations for group $ethnicityXvalue$:
+## Subgroup behavior (Fig: \ref{fig:crlo} to Fig: \ref{fig:crlblmajority})
 
-* Figures \ref{fig:crlo}, \ref{fig:crlominority} and \ref{fig:crlblmajority} replicate the behavior space in Fig: \ref{fig:baselineone} used in the previous section.
-For each condition the ethnic and value segregation are reported.
-* I report the results of circle orange in the condition of ethnic equal size, ethnic minority and ethnic majority.
-Since agents  follow the same homophily preferences, the only difference is due to the manipulation of relative group sizes for ethnicity and value orientation, so that the results here presented can be applied to all other group by rotating the axis on Fig: \ref{fig:baselineone} or results along the diagonal.
-I do this in the ANNEX as demonstration
+* Circle orange is used as model for equal ethnic size and ethnic group in the minority condition.
+Circle  blue as model for ethnic group in majority condition.
+The observed behavior can be applied symmetrically to the other subgroups imposing same conditions, I do this in ANNEX A rotating the axes.
 * 3 outcomes are evident, rather than 2 as in traditional assessment of Schelling: integration (filler white  0.5), segregation (filler red above 0.5), and assimilation (filler blue close to 0, only members outgroup).
@@
 
-* Given ethnic equal group size, at the baseline condition ($50 \%$ circle orange, $50 \%$ circle blue), each group replicates what observed for global segregation: high randomness close to integration for $\beta < 5$, low randomness high segregation for $\beta \geq 5$.
-For ethnic segregation this is the same along the diagonal, given equal ethnic sizes
-* On the top left corner,  where the value group represents majority in the own ethnic group, but minority in the other, integration is the most likely outcome  only for low levels of both $\beta_e$ and  $\beta_v$ (low left corner), with middle segregation in the rest of high randomness area.
-While the value becomes more represented in the other ethnic group, ethnic integration increases  with increase of  $\beta_v$ in the area of high randomness ($\beta_e < 5$), untouched in the area of low  randomess ($\beta_e \geq 5$).
-In the same conditions, high value segregation appears as direct effect of increase in the proportion of same value oriented circle in the other group
-* Low row, where the value group represents minority in the own group: value assimilation to square is the case when circle is the minority in both etnic groups.
-Still, comparing to ethnic segregation, area of high randomenss appears ethnically integrated, area of low randomness ethnically segregated.
-This implies that for  low $\beta_e$ and low $\beta_v$ value minority relocate in ethnically mixed neighborhoods, but where square is the majority.
-For high  $\beta_e$, circle live  in ethnically segregated neighborhoods, where still value represent the majority of the own ethnic group.
-Though low $\beta_e$ reproduces the  initial random ethnic distribution, this doesn't happen for value distribution due to effect of majority size of square in both groups.
-* Proceeding with increase of same  value in the other ethnic group (x-axis), value assimilation increases for high levels of $\beta_e$ and low levels of $\beta_v$, in the same conditions ethnic segregation.
-As before circle agents increase  ethnic utility, but still have more chance to relocate close to square co-ethnics.
-Along $\beta_v$, increase implies value segregation as expected,  but ethnic assimilation when $\beta_e$ is low: circle agents not care about ethnic utility, but maxize value orientation, so that most appealing neighborhoods are those inhabited by circle of the other group.
-* The last observation is noteworthy to me, though predictable: as alternative to assimilation due to being in the ethnic minority size, people can fall into ethnic (spatial) assimilation because of an other characteristic (value) which is unequally represented in two ethnic group numerically equal
+* Baseline reproduces the same as global observations.
+Ethnic segregation doesn't change along the diagonal; value segregation does, as effect of different value distribution (minority circle in the low left; majority circle in the upper right)
+* Top left corner, circle is majority value in the own ethnic group (orange), minority in the other group (blue): integration occurs in the high randomnessfor both preferences (low left corner); ethnic segregation in high random ethnic area increases with increase of $\beta_v$; increase also of value segregation for increase in $\beta_e$: Both results  are due to the majority value circle increasing both value and  ethnic preferences, in condition of equal ethnic size.
+* Top row: proceding on x-axis with increase in percentage similar value in the other ethnic group: for area of ethnic randomness, ethnic integration more evident over ethnic segregation at increase of $\beta_v$, because more equal chance to satisfy value preferences with agents of both ethnic groups
+* Bottom left corner, circle value is minority value in both groups: value assimilation to square happens for all levels of $\beta_e$, as direct consequence of minority position.
+Ethnic integration emerges for high ethnic randomness ($\beta_e=5$)  also for increase in $\beta_v$, because agents need to cluster with value similars of the other ethnic group, which still are a minority.
+Value segregation results constantly high for all area  $\beta_v \geq 5$.
+Still, looking at overlap of ethnic and value space, moving from high ethnic randomness to low ethnic randomness area, ethnic integration shifts to ethnic segregation.
+This means that agents still manage to live in neighborhoods value homogeneous, but only with members of the own ethnic group.
+Maybe good to include density observation here, and compare with ACS.
+* Bottom row: proceding on x-axis with increase of circle in the other ethnic group: value assimilation for $\beta_v < 5$ narrows down to high $\beta_e$, since for random ethnic behavior there is more chance to find value similar in the other group being equally represented.
+When value preference increases, ethnic assimilation becomes more evident since circle have more chance to find similar value, though of the other ethnic group, which they don't care about.
+* Middle row (circle are 50% value in ethnic group): transition in between observations above, not  different patters
 
@@
 * Value segregation on the top right, where square agents show maximal ethnic and value utility  $\beta^{\square}_e = \beta^{\square}_v = 10$, full value segregation emerges for all conditions of $\beta$ levels, while in high ethnic utility area $\beta^{\square}_e \geq 5$ circle live in neighborhoods both value and ethnic homogeneous, for $\beta^{\square}_e <  5$ they live in ethnically mixed neighborhoods with circle of other ethnicity
+
+# References {-}

### 2020-05-08 exp_eth_val.Rmd
Add files via upload

@@
 Ethnic segregation doesn't change along the diagonal; value segregation does, as effect of different value distribution (minority circle in the low left; majority circle in the upper right)
-* Top left corner, circle is majority value in the own ethnic group (orange), minority in the other group (blue): integration occurs in the high randomnessfor both preferences (low left corner); ethnic segregation in high random ethnic area increases with increase of $\beta_v$; increase also of value segregation for increase in $\beta_e$: Both results  are due to the majority value circle increasing both value and  ethnic preferences, in condition of equal ethnic size.
+* Top left corner, circle is majority value in the own ethnic group (orange), minority value in the other ethnicity (blue): integration occurs in the high randomnessfor both preferences (low left corner); ethnic segregation in high random ethnic area increases with increase of $\beta_v$; increase also of value segregation for increase in $\beta_e$: Both results  are due to the majority value circle increasing both value and  ethnic preferences, in condition of equal ethnic size.
 * Top row: proceding on x-axis with increase in percentage similar value in the other ethnic group: for area of ethnic randomness, ethnic integration more evident over ethnic segregation at increase of $\beta_v$, because more equal chance to satisfy value preferences with agents of both ethnic groups
@@
 Maybe good to include density observation here, and compare with ACS.
-* Bottom row: proceding on x-axis with increase of circle in the other ethnic group: value assimilation for $\beta_v < 5$ narrows down to high $\beta_e$, since for random ethnic behavior there is more chance to find value similar in the other group being equally represented.
-When value preference increases, ethnic assimilation becomes more evident since circle have more chance to find similar value, though of the other ethnic group, which they don't care about.
+* Bottom row: proceding on x-axis with increase of circle in the other ethnic group: value assimilation for $\beta_v < 5$ narrows down to high $\beta_e$, since for random ethnic behavior there is more chance to find value similar circle in the other group.
+When value preference increases along $\beta_v$, ethnic assimilation becomes more evident since circle have more chance to find similar value, though of the other ethnic group, which they don't care about.
 * Middle row (circle are 50% value in ethnic group): transition in between observations above, not  different patters
@@
 
-* Trends are generally similar to Fig: \ref{fig:crlo}
-* In the baseline, ethnic assimilation emerges instead of ethnic integration, becuase of the ethnic minority of the group.
-* Up left corner, where circle represent the majority value of ethnic  minority and the minority value of ethnic majority, compared to Fig: \ref{fig:crlo} ethnic assimilation rather than integration emerges for the area of high randomness for both dimensions, and ethnic integration rather than segregation for the increase of $\beta_v$ and low values of $\beta_e$.
-While for areas of high randomness agents fall into assimilation because of numeric inferiority, when they increase value utility $\beta_v$ they want to relocate close to other circle agents, regardless of their ethnicity.
-Since in this condition circle represent the minority value of the majority ethnic population (the opposite of circle orange in ethnic minority), the combination allows for the increase in value preference to make up for the ethnic numeric inferiority, so that both circle minority and circle majority end up in neighborhoods ethnically integrated and value circle homogeneous (cfr Fig: \ref{fig:crlbl}, right down corner).
-* Low row: the effect of increase in $\beta_e$ on value assimilation is similar as Fig: \ref{fig:crlo}, since circle here represents the minority in the own group.
-Increase of $\beta_v$ shows instead higher assimilation, because circle minority has more chance to relocate close to similar circle value of the other ethnic group, proportionally to value circle being the majority value in the majority ethnic group.
-Interestingly, given the area of high ethnic utility for $\beta_e \geq 5$, at the increase of $\beta_v$ less homogenous ethnic segregation emerges compared to the equal ethnic size.
-* The last two  points are noteworthy to me: the assumption that similar values can foster ethnic integration over ethnic segregation can work provided that an adjustement between distribution of values in both ethnic group and preferences for ethnic or value utility are  taken into account.
+* Baseline shows ethnic assimilation for the area of high ethnic randomness $\beta_e < 5$, direct effect of numeric minority
+* Top left corner, circle is majority value in the own ethnic minority (orange), minority value in the ethnic majority (blue): in both areas of high randomness (bottom left corner), strong ethnic assimilation and mild value assimilation emerge.
+Due to unbalance of circle in ethnic minority and ethnic majority, for random moves  circle orange have more chance to relocate close to an agent of ethnic majority, but the probability of this agent being value circle or square becomes slightly  similar.
+Increasing value preference for $\beta_v \geq 5$, tendence towards ethnic integration occurs rather than assimilation or segregation, still value segregation is almost complete.
+This because due to value and ethnic distribution, the probability of an agent being circle blue or circle orange is equally $\approx 0.15$, thus, increasing value preference and not caring for ethnicity, circle minority form neighborhoods value homogeneous but ethnically mixed
+* Top row: increasing circle value in the ethnic majority (along x-axis), at circle ethnic majority = $50 \%$, value integration occurs for high ethnic randomness.Increasing $\beta_v$, ethnic assimilation emerges along value segregation more evidently, since now circle is majority value in the ethnic minority, but equally represented at $0.50$ in the ethnic blue majority, thus the probability to find a circle blue is higher than finding a circle orange.
+* Bottom left corner, circle value is minority value in both groups: compared to Fig: \ref{fig:crlo}, ethnic and value assimilation for respective $\beta < 5$ and ethnic and value segregation for $\beta \geq 5$ remains, though less evident in particular for low randomness area $\beta \geq 5$, due to numeric minority.
+* Bottom row: increasing circle value in the ethnic majority (along x-axis), increase in $\beta_v$ for the area of ethnic randomness favors ethnic assimilation, which expands also to the area of high ehtnic utility ($\beta_e \geq 5$) as circle value are most represented in the ethnic majority.
+Here, to satisfy highest levels of value homophily, minority circle must reduce on ethnic homophily, which for the borderline area $\beta = 5$ allows for spillover of value preference on ethnic segregation.
+Increase in $\beta_e$ shows value assimilation narrowly for highest ethnic preferences $\beta \geq 5$ rather than uniformly as in Fig: \ref{fig:crlo}, because to maximize ethnic preference circle orange need to cluster to square who represent the majority value in their ethnic minority.
+The shift from value assimilation towards segregation for random ethnic moves $\beta_e < 5$ is because there is more probability now of a circle being from ethnic blue majority.
 
@@
 ### Ethnic majority (Fig: \ref{fig:crlblmajority})
-* Low row where circle are the minority in the ethnic majority blue, show the same pattern for the circle in minority and equal ethnic size: increasing in ethnic utility implies value assimilation to square  members of the same ethnic group, because of value numeric minority
-* Value integration occurs in the upper row ($50 \% $ circle in blue majority ethnic) for random area of low $\beta_v$, because eqaul chance to relocate close to either circle or square, but in both cases of same ethnic group
-* Compared to the baseline in Fig: \ref{fig:crlo}, ethnic segregation emerges also in area of high randomness ($\beta_e < 5$), because of numeric superiority, also for the upper side of the diagonal
-* Low right corner, where circle are the minority in the blue ethnicity, but majority in the ethnic minority, ethnic integration emerges for high values of $\beta_v$, despite ethnic minority of orange.
-Same as in Fig: \ref{fig:crlominority}
+
+* First column, where circle represent the value minority in the ethnic blue majority: value assimilation is homogeneous for $\beta_e$, due to value minority.
+Ethnic segregation for high ethnic randomness $\beta_e < 5$ moves from integration to segregation as the number of circle in the ethnic orange minority decreases: to maximize value preference, circle blue will form value homogeneous neighborhoods, and the higher percentage of value circle in ethnic minority allows to increase the random probability of circle value being blue either orange, causing ethnic integration.
+As the concentration of value orange decreases, the random probability of circle being co-ethnic blue increases, favoring ethnic segregation.
 
 ```{r crlblmajority, fig.pos='H',out.width='\\textwidth',fig.show = "hold",fig.align='center',fig.show="hold", fig.cap="Circle blue, ethnic majority", echo=FALSE, include=TRUE}
+
+ circle_blue.labs <- c("20% Circle \nBlue", "50% Circle \nBlue","80% Circle \nBlue")
+names(circle_blue.labs) <- c("20", "50","80")
+ circle_orange.labs <-  c("20% Circle \nOrange", "50% Circle \nOrange","80% Circle \nOrange")
+names(circle_orange.labs) <- c("20", "50","80")
 
@@
   ggplot(aes(x = beta_ie,y = beta_iv, fill = Segra)) + geom_tile() + 
-  facet_grid( rev_circle_blue  ~ circle_orange  + segregation, labeller = labeller(circle_orange =circle_orange.labs, rev_circle_blue = rev_circle_blue.labs), switch  = "y") +
+  facet_grid( rev_circle_orange   ~  circle_blue + segregation, labeller = labeller(rev_circle_orange =rev_circle_orange.labs, circle_blue = circle_blue.labs), switch  = "y") +
   scale_fill_distiller(palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) +

### 2020-05-08 exp_eth_val.Rmd
Add files via upload

@@
 
-# First Section (Tab: \ref{tab:First})
+# First Section, relative group size & homogeneous preferences (Tab: \ref{tab:First})
 
@@
 * Focus: relative group size for ethnicity and value distribution within each ethnic group, considering how they directly influence probability to sort with similars; interaction with levels of $\beta_e$,$\beta_v$
-* Assumption: 
+* Assumptions: 
     + not heterogeneity: all agents hold both ethnic preference (same color) and value preference (same shape) depending on level of global $\beta_e$ and $\beta_v$
@@
 
-# Second Section (heterogeneous preferences for tolerant and intolerants)
+# Second Section, heterogeneous (hierarchical?) preferences value vs ethnicity (Tab: \ref{tab:Second})
 
 * Aim:
-    + Test the effect of heterogeneous preferences for two value groups, i.e.
-circle value-oriented care more about value than ethnic neighborhood composition, square ethnicity-oriented care more about ethnic than value composition
-    + This would relate to the difference between tolerant (circle) and intolerant (square) as in the ACS paper and that we discussed
-    + Observe how heterogeneity in agents' preferences along two value oriented groups will affect results in the previous section, through their mutual adaptation
-    + Interaction between heterogeneous preferences and relative group sizes for both dimensions (here only equal ethnic and value group)
-* Assumption: 
-    + Agents hold both ethnic and value preferences, but $\beta$ for each dimension depends on their value orientation, either circle or square.
-Not difference due to ethnic membership are taken into consideration
-    + Given the linear function, utility increases with value or ethnic homogeneity of neighborhood, but determinism component $\beta_e$ and $\beta_v$ are differently distributed to value groups: ethnic preferences of circle cannot be higher than value preferences ($\beta^{\circ}_e \leq \beta^{\circ}_v$) and value preferences of square cannot be higher than thier value preferences ($\beta^{\square}_v \leq \beta^{\square}_e$)
-    + Ideally also condition of ethnic majority/minority and circle majority/minority should be included.
-Here for matter of time it is reduced to equal ethnic group size (blue/orange $0.50$) and for each ethnic group equal value group (circle/square $0.50$).
-So, each of the four subgroup in Fig: \ref{fig:thheory} represents the $25 \%$ of the global agents' population
-* Figures:
-    + I compare the ethnic and value segregation of both circle and square agents
-    + Focus on the difference between ethnic and value segregation (being close to agents sharing both ethnicity and value)
-    + To reduce observations given the numbers of parameters, I jump on 3 critical points individualized in the previous section: $\beta = 0$: total randomness, $\beta = 5$: min.
-determinism, $\beta = 10$: max determinism
-    + For each value group, in the baseline I put on x-axis the difference between the highest reference $\beta$ of that group and the other one, i.e.
-$\beta_e - \beta_v$ for square, $\beta_v - \beta_e$ for circle.
-Considering the critical point, I repeat observation for reference $\beta = 5$: min.
-determinism, and $\beta = 10$: max determinism, $\beta = 0$ is included in bot.
-Thus, along the x-axis the group becomes more sensitive to the reference dimension, ethnicity for square group, value for circle group.
-I compare how the baseline condition changes for interaction of value and ethnic preferences of the other group faceting the 3 critical points $\beta = 0; \beta = 5;\beta = 10$
+    + Test the effect of heterogeneous preferences depending on value attribution: circle care more about value neighborhood composition, square care more about ethnic neighborhood composition.
+    + This is the case  we discussed, adapting to circle tolerant, square intolerant
+    + How preference heterogeneity affects results in  the previous section, where agents hold  same preference
+    + How mutual adaptation of circle and square driven by different hierarchy of preference affect each other segregation patterns
+    + Interaction of heterogeneous preferences with relative group size for ethnic and value membership
+* Assumptions: 
+    + square hold higher ethnic than value preferences: $\beta^{\square}_e \geq \beta^{\square}_v$; circle hold higher value than ethnic preferences: $\beta^{\circ}_v \geq \beta^{\circ}_e$.
+    + No difference due to ethnic membership
+    + \textbf{NOTE: Here only baseline} for question of time/computation server (Tab: \ref{tab:Second}).
+I'd collect conditions of majority and minority circle or square in ethnic different group sizes.
+* Figures
+    + Need to find trade off between 4 parameters (see Tab: \ref{tab:Second}) and behavior of 2 type of agents (circle and blue) in conditions of relative group size
+    + Considering the critical levels of $\beta = 5$ between high randomness and low randomness (space model Fig: \ref{fig:baselineone}), I jump here directly to critical points $\beta = 0$: total ranomness,  $\beta = 5$: min determinism, $\beta = 10$: max determinism, this for each dimensions and faceting for circle and value group.
+    + ANNEX B heatmaps: ethnic and value segregation for all preferences of square faceted for the 3 critical points of circle (Fig: \ref{fig:heatmapdsquare}); ethinic and value segregation for all preferences of circle faceted for the 3 critical points of square (Fig: \ref{fig:heatmapdcircle})
+    + Fig: \ref{fig:betatwoethnic} and Fig: \ref{fig:betatwovalue} compares in the same graph ethnic and value segregation for circle and square agents, narrowing down compared to ANNEX B.
+Focus: the lower the distance between ethnic and value segregation, the more the agent relocates close to a members of the own ethnic and value subgroup (Fig: \ref{fig:thheory})
 
@@
 
-## Comparison different value orientation
-* Fig: \ref{fig:betatwoethnic}: x-axis $\beta^{\square}_e - \beta^{\square}_v$, on the top panel with $\beta^{\square}_e = 5$ (area of high randomness), on bottom panel  $\beta^{\square}_e = 10$ (area of low randomness).
-X-axis = 0,  ethnic and value utility have equal weight, along the x-axis ethnic weight prevails over value weight.
-the lower the distance between ethnic and value segregation, the more agents live close to others similar for both ethnicity and value.
-* Viewing at lower left panel, where behavior of circle is totally random, not only the distance between ethnic and value segregation of square is lower when $\beta^{\square}_e = \beta^{\square}_v$ (x-axis 0), but also higher for both dimensions, progressing towards x-axis (ethnic becomes higher than 10), value segregation decreases, with more linear slope for high determinism area (bottom panel).
-* It persists that each $\beta$ rules the reference dimension, but the random behavior of the other group decreases the segregation expected for that level of $\beta$, higher determinism of the other group increases  the level of segregation for that dimension.
-Demonstration, moving from $\beta^{\circ}_v = 5$ to  $\beta^{\circ}_v = 10$
-* As $\beta^{\square}_e$ becomes higher than  $\beta^{\square}_v$, moving on the x-axis, ethnic segregation persists constantly, while value segregation diminishes.
-* The threshold of $\beta = 5$ seen in the previous section is somehow replicated: in the top panel, max value and ethnic segregation are equal 1 when both  $\beta^{\square}_e = \beta^{\square}_v = 0$, on the x-axis 0, and value segregation declines once $\beta^{\square}_v$ comes close to 0.
-Looking at panel below (high determinism), the decline of value segregation occurs equally when $\beta^{\square}_v$ declines from 5 to 0 (on the right of red line 10-5:5 and so on)
-* Even though the direct effect of $\beta_v$ is assumed and same patterns are observed from low determinism (top panel) and high determinism (bottom panel), the high determinism of  $\beta^{\square}_e$ is associated with very slight increase in the value segregation of square, also for same level of $\beta^{\square}_v = 0$, though negligeable
-* The distance between ethnic and value segregation is higher in the middle panel, where circle hold same min utility preferences $\beta^{\circ}_e = \beta^{\circ}_v = 5$, and also square increase in ethnic over value preference (x-axis = 5).
-Basically the only random component is the value orientation of square agents, which has the same effect on both circle and square population patterns
-* Moving on the diagonal, where $\beta^{\circ}_e = \beta^{\circ}_v = 10$, the distance between ethnic and value decreases, meaning agents are more likely to live close to agents of both same ethnicity and value: the increase in utility at max level of circle ($\beta^{\circ}_e = \beta^{\circ}_v = 10$) compensates for random value behavior of square, since circle will avoid neighborhoods with square
-* Fig: \ref{fig:betatwovalue} shows the similar trends, focusing on value segregation over ethnic segregation for the circle population.
-Nevertheless, in the middle panel ($\beta^{\square}_e = \beta^{\square}_v = 5$), I would expect symmetric scenario than in Fig: \ref{fig:betatwoethnic}, with ethnic segregation of circle being same as value segregatiion than square.
-Why here circle are completed ethnically integrared?
-There is a difference between the two dimensions?
-Think about.
+## Focus on square preferences (Fig: \ref{fig:betatwoethnic})
+* x-axis: difference preferences for square $\beta^{\square}_e - \beta^{\square}_e$.
+x-axis: 0: ethnic and value matter equally with same high $\beta$ to square ($\beta^{\square}_e = \beta^{\square}_v = 5$ top panel, $\beta^{\square}_e = \beta^{\square}_v = 10$ lower panel); proceding on x-axis, ethnic matters more to square than value ($\beta^{\square}_e$ is constant, while $\beta^{\square}_v$ decreases to 0)
+* y-axis: ethnic and value segregation for circle and square
+* bottom left box, where all circle relocate randomly ($\beta$ circle = 0):
+   + bottom panel (high determinism): decline of value segregation for both groups occurs mostly linear monotonic for all values of $\beta^{\square}_v$
+   + ethnic segregation of square population is lower than in other conditions, due to random relocation of circle, both for high ethnic and lower ethnic determinism (top and bottom figure)
+* along the diagonal, as circle population increases equally ethnic and value determinism: 
+   + value segregation for both groups decreases along x-axis, where value matters progressively less for square, given the constant level of square ethnic preference
+   + decline of value segregation above happens in high value randomness when $\beta^{\square}_v \leq 5$: top panel: all conditions; bottom panel: right side of red line (10-5 = 5)
+   + curve of value segregation decline is steeper in all conditions of the bottom panel (higher determinism $\beta^{\square}_e = 10$)
+* above diagonal, ethnic and value segregation of square population decline the most for high values of $\beta^{\square}_e$ when circle relocate randomly for ethnicity.
+I relate this to high randomness of $\beta^{\square}_v < 5$: all conditions top panel, but only right side of red line, where $\beta^{\square}_v < 5$.
+The trend is higher in the top panel of high randomness.
+Basically seems high value and ethnic determinism of square support each other on relative segregation when the other circle group  relocates randomly.
 
-```{r betatwoethnic,fig.pos='H',fig.show = "hold",fig.align='center',fig.cap="Difference segregation, x-axis: difference ethnic and value preference square, faceting conditions: preferences of circle", echo=FALSE, include=TRUE }
+```{r betatwoethnic,fig.pos='H',fig.out="96%",fig.show = "hold",fig.align='center',fig.cap="Difference segregation, x-axis: difference ethnic and value preference square, faceting conditions: preferences of circle", echo=FALSE, include=TRUE }
 
@@
 
-ie_10 <- circle_frame %>%  filter(beta_ie_square == 10) %>% gather(key = subgroup, value = Segra, eth_sq_or,val_sq_or,eth_cl_or,val_cl_or) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"ethnic segregation" = c("eth_sq_or","eth_cl_or"), "value segregation" = c("val_sq_or","val_cl_or")), "ethnic segregation"), `group` = fct_relevel(fct_collapse(subgroup, "square minority" = c("eth_sq_or","val_sq_or"), "circle minority" = c("eth_cl_or","val_cl_or"), "square minority"))) %>%
+ie_10 <- circle_frame %>%  filter(beta_ie_square == 10) %>% gather(key = subgroup, value = Segra, eth_sq_or,val_sq_or,eth_cl_or,val_cl_or) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"ethnic segregation" = c("eth_sq_or","eth_cl_or"), "value segregation" = c("val_sq_or","val_cl_or")), "ethnic segregation"), `group` = fct_relevel(fct_collapse(subgroup, "square" = c("eth_sq_or","val_sq_or"), "circle" = c("eth_cl_or","val_cl_or"), "square"))) %>%
   ggplot(aes(x = (beta_ie_square - beta_iv_square), y = Segra, color = `segregation`, shape = `group`)) + geom_line() + geom_point( size = 2) + facet_grid(rev_beta_iv_circle ~  beta_ie_circle, labeller = labeller(rev_beta_iv_circle = rev_beta_iv_circle.labs,  beta_ie_circle = e_circle.labs )) +
@@
 
-ie_5 <- circle_frame %>%  filter(beta_ie_square == 5) %>% gather(key = subgroup, value = Segra, eth_sq_or,val_sq_or,eth_cl_or,val_cl_or) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"ethnic segregation" = c("eth_sq_or","eth_cl_or"), "value segregation" = c("val_sq_or","val_cl_or")), "ethnic segregation"), `group` = fct_relevel(fct_collapse(subgroup, "square minority" = c("eth_sq_or","val_sq_or"), "circle minority" = c("eth_cl_or","val_cl_or"), "square minority"))) %>%
+ie_5 <- circle_frame %>%  filter(beta_ie_square == 5) %>% gather(key = subgroup, value = Segra, eth_sq_or,val_sq_or,eth_cl_or,val_cl_or) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"ethnic segregation" = c("eth_sq_or","eth_cl_or"), "value segregation" = c("val_sq_or","val_cl_or")), "ethnic segregation"), `group` = fct_relevel(fct_collapse(subgroup, "square" = c("eth_sq_or","val_sq_or"), "circle" = c("eth_cl_or","val_cl_or"), "square"))) %>%
   ggplot(aes(x = (beta_ie_square - beta_iv_square), y = Segra, color = `segregation`, shape = `group`)) + geom_line() + geom_point( size = 2) + facet_grid(rev_beta_iv_circle ~  beta_ie_circle, labeller = labeller(rev_beta_iv_circle = rev_beta_iv_circle.labs,  beta_ie_circle = e_circle.labs )) +
@@
 
-```{r betatwovalue,  fig.pos="H",fig.show = "hold", fig.align='center',fig.show="hold", fig.cap="Difference segregation between", echo=FALSE, include=TRUE  }
+## Focus on circle preferences (Fig: \ref{fig:betatwovalue})
+* x-axis: difference preferences for circle $\beta^{\circ}_v - \beta^{\circ}_e$.
+x-axis: 0: ethnic and value matter equally with same high $\beta$ to square ($\beta^{\circ}_v - \beta^{\circ}_e = 5$ top panel, $\beta^{\circ}_v - \beta^{\circ}_e = 510$ lower panel); proceding on x-axis, value matters more to circle than value ($\beta^{\circ}_v$ is constant, while $\beta^{\circ}_e$ decreases to 0)
+* y-axis: ethnic and value segregation for circle and square
+* bottom left box, where all square relocate randomly ($\beta$ circle = 0):
+
+```{r betatwovalue,  fig.pos="H",fig.out="96%",fig.show = "hold", fig.align='center',fig.show="hold", fig.cap="Difference segregation between", echo=FALSE, include=TRUE  }
 
@@
 
-iv_10 <- circle_frame %>%  filter(beta_iv_circle == 10) %>% gather(key = subgroup, value = Segra, eth_sq_or,val_sq_or,eth_cl_or,val_cl_or) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"ethnic segregation" = c("eth_sq_or","eth_cl_or"), "value segregation" = c("val_sq_or","val_cl_or")), "ethnic segregation"), `group` = fct_relevel(fct_collapse(subgroup, "square minority" = c("eth_sq_or","val_sq_or"), "circle minority" = c("eth_cl_or","val_cl_or"), "square minority")))  %>%
+iv_10 <- circle_frame %>%  filter(beta_iv_circle == 10) %>% gather(key = subgroup, value = Segra, eth_sq_or,val_sq_or,eth_cl_or,val_cl_or) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"ethnic segregation" = c("eth_sq_or","eth_cl_or"), "value segregation" = c("val_sq_or","val_cl_or")), "ethnic segregation"), `group` = fct_relevel(fct_collapse(subgroup, "square" = c("eth_sq_or","val_sq_or"), "circle" = c("eth_cl_or","val_cl_or"), "square")))  %>%
   ggplot(aes(x = (beta_iv_circle - beta_ie_circle), y = Segra, color = `segregation`, shape = `group`)) + geom_line() + geom_point( size = 2) + facet_grid(rev_beta_ie_square ~  beta_iv_square, labeller = labeller(rev_beta_ie_square = rev_beta_ie_square.labs, beta_iv_square = v_square.labs))  +
@@
 
-iv_5 <- circle_frame %>%  filter(beta_iv_circle == 5) %>% gather(key = subgroup, value = Segra, eth_sq_or,val_sq_or,eth_cl_or,val_cl_or) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"ethnic segregation" = c("eth_sq_or","eth_cl_or"), "value segregation" = c("val_sq_or","val_cl_or")), "ethnic segregation"), `group` = fct_relevel(fct_collapse(subgroup, "square minority" = c("eth_sq_or","val_sq_or"), "circle minority" = c("eth_cl_or","val_cl_or"), "square minority")))  %>%
+iv_5 <- circle_frame %>%  filter(beta_iv_circle == 5) %>% gather(key = subgroup, value = Segra, eth_sq_or,val_sq_or,eth_cl_or,val_cl_or) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"ethnic segregation" = c("eth_sq_or","eth_cl_or"), "value segregation" = c("val_sq_or","val_cl_or")), "ethnic segregation"), `group` = fct_relevel(fct_collapse(subgroup, "square" = c("eth_sq_or","val_sq_or"), "circle" = c("eth_cl_or","val_cl_or"), "square")))  %>%
   ggplot(aes(x = (beta_iv_circle - beta_ie_circle), y = Segra, color = `segregation`, shape = `group`)) + geom_line() + geom_point( size = 2) + facet_grid(rev_beta_ie_square ~  beta_iv_square, labeller = labeller(rev_beta_ie_square = rev_beta_ie_square.labs, beta_iv_square = v_square.labs))  +

### 2020-05-09 exp_eth_val.Rmd
Add files via upload

@@
 * Figures
+    + Circle orange and square orange is taken as prototype (in the legend circle, square), since any subgroup in Fig: \ref{fig:thheory} has same probability $0.25$ to relocate close similar one and behavior would be symmetrical \textbf{-> agree?
+I would test otherwise}
     + Need to find trade off between 4 parameters (see Tab: \ref{tab:Second}) and behavior of 2 type of agents (circle and blue) in conditions of relative group size
@@
 
+## Focus on circle preferences (Fig: \ref{fig:betatwovalue})
+* x-axis: difference preferences for circle $\beta^{\circ}_v - \beta^{\circ}_e$.
+x-axis: 0: ethnic and value matter equally with same high $\beta$ to square ($\beta^{\circ}_v - \beta^{\circ}_e = 5$ top panel, $\beta^{\circ}_v - \beta^{\circ}_e = 510$ lower panel); proceding on x-axis, value matters more to circle than value ($\beta^{\circ}_v$ is constant, while $\beta^{\circ}_e$ decreases to 0)
+* y-axis: ethnic and value segregation for circle and square
+* bottom left box, where all square relocate randomly ($\beta$ circle = 0):
+* Basically the extreme of the pictures can be deduced from Fig: \ref{fig:betatwovalue}, inverting circle and value positions
+* along the x-axis, as $\beta^{\circ}_e$ decreases, ethnic segregation decreases linearly, though it reaches always complete ethnic integration compared to Fig: \ref{fig:betatwoethnic}.
+This happens for $\beta^{\circ}_e < 5$ (all conditions top panel and right side of bottom panel), and for all levels  of $\beta^{\circ}_e$ when square moves randomly for value homophily (first column in bottom panel).
+This last note is the same as bottom left box in bottom panel in Fig: \ref{fig:betatwoethnic}.
+The random relocation of square favors  the complete ethnic integration
+* first column, along the x-axis, where value homophily becomes more important to circle and ethnicity moves  to 0, and square don't care about value, but more on ethnicity (from  $\beta^{\square}_e = 5$ to $\beta^{\square}_e = 10$ ).
+Distance between value and ethnic segregation shows that circle live in value homogeneous but ethnically mixed neighborhoods, square in both ethnically and value homogeneous neighborhoods (i.e.
+with square of same ethncity).
+My guess: square would be attracted by neighborhoods of circle, because there is more chance to find a co-ethnic, though they would be refused because of their value by circle who maximize value homophily.
+In the condition of lower determinism $\beta^{\square}_e = 5$, square would still relocate randomly in the world, not threating the value composition of circle neighborhoods.
+When ethnic square determinism increases to $\beta^{\square}_e = 10$, then ethnically mixed neighborhoods of circle become highly appealing and try to move there.
+At next step, circle would refuse square because of  value homophily and would move to value homogeneous neighborhoods (playing with simulations, seems to less dense neighborhoods, might be included).
+As for square of different ethncity, clearly they would not live close to each other for direct effect of increase in ethnic determinism.
+Due to reinforce in value homophily for circle and ethnic homophily for square, equilibria emerge with 3 clusters: circle live in complete ethnically mixed, but complete value segregated neighborhoods, square in both ethnically and value segregated neighborhoods (i.e.
+square with the same ethncity).
+The value segregation of square is  basically emerging un-intended consequence of adaptation between ethnic homophily of square  and value homophily of circle.
+
 ```{r betatwoethnic,fig.pos='H',fig.out="96%",fig.show = "hold",fig.align='center',fig.cap="Difference segregation, x-axis: difference ethnic and value preference square, faceting conditions: preferences of circle", echo=FALSE, include=TRUE }
@@
 
-## Focus on circle preferences (Fig: \ref{fig:betatwovalue})
-* x-axis: difference preferences for circle $\beta^{\circ}_v - \beta^{\circ}_e$.
-x-axis: 0: ethnic and value matter equally with same high $\beta$ to square ($\beta^{\circ}_v - \beta^{\circ}_e = 5$ top panel, $\beta^{\circ}_v - \beta^{\circ}_e = 510$ lower panel); proceding on x-axis, value matters more to circle than value ($\beta^{\circ}_v$ is constant, while $\beta^{\circ}_e$ decreases to 0)
-* y-axis: ethnic and value segregation for circle and square
-* bottom left box, where all square relocate randomly ($\beta$ circle = 0):
-
 ```{r betatwovalue,  fig.pos="H",fig.out="96%",fig.show = "hold", fig.align='center',fig.show="hold", fig.cap="Difference segregation between", echo=FALSE, include=TRUE  }
@@
   ggplot(aes(x = (beta_iv_circle - beta_ie_circle), y = Segra, color = `segregation`, shape = `group`)) + geom_line() + geom_point( size = 2) + facet_grid(rev_beta_ie_square ~  beta_iv_square, labeller = labeller(rev_beta_ie_square = rev_beta_ie_square.labs, beta_iv_square = v_square.labs))  +
-  scale_x_discrete(name = "ß value circle 10 - ß ethnic circle", limits = seq(0,5, by = 1)) +  ylab("Segregation") +
+  scale_x_discrete(name = "ß value circle 5 - ß ethnic circle", limits = seq(0,5, by = 1)) +  ylab("Segregation") +
   scale_color_manual(values = c("dark violet","dark green"), guide = guide_legend(title="")) +
@@
 
-## Fig: \ref{fig:heatmapdsquare}
-*  Fig: \ref{fig:heatmapdsquare} reports in heatmaps $\beta^{\square}_e$ on y-axis $\beta^{\square}_v$ on x-axis for square agents, as such on y-axis is the most important preference for the value group square, the triangle shape is due to the condition $\beta^{\square}_v \leq \beta^{\square}_e$.
-* Faceted for the condition of the other group, focusin on 3 degree: total randomness $\beta^{\circ} = 0$, threshold between area of high and low randomness $\beta^{\circ} = 5$ and highest systematic component $\beta^{\circ} = 10$.
-For each condition ethnic and value segregation of squared population is calculated
-* Lower area, where the other group shows total random behavior ($\beta^{\circ} = 0$) for both ethnic and value utility, value integration emerges with low $\beta^{\square}_v$ regardless the increase in $\beta^{\square}_e$.
-Higher value segregation occurs only for the highest levels of $\beta^{\square}_v$ and $\beta^{\square}_e$.
-Ethnic segregation increases along the diagonal where $\beta^{\square}_v = \beta^{\square}_e$.
-Lower ethnic segregation compared to the other conditions in the area of high ethnic utility $\beta^{\square}_e$
-* Second row, first panel: for total random value behavior of square $\beta^{\square}_v = 0$, the ethnic segregation is linear to the increase of  $\beta^{\square}_e$, not showing the threshold difference as in Fig: \ref{fig:crlo}, this only with ethnic randomness of circle agents $\beta^{\circ}_e = 0$, but reach the critical point of $\beta^{\circ}_v = 5$ for value preferences.
-The sensitivity to change persists, but the sensitivity to chance decreases, because agents are split into two groups, for the same dimension that both share (ethnicity), one maximizes, the other not, and viceversa one doesn't care about value, while the other group maximizes value.
-* My guess: circle agents would gather together in ethnically mixed neighborhoods (cfr Fig: \ref{fig:heatmapdcircle}, ethnic integration along $\beta^{\circ}_v$), which attract square ethnicity-oriented at increase of  $\beta^{\square}_e$, they not care about the value orientation of the neighborhood.
-Compared to the previous section, $\beta^{\square}_e$ applies to $50\%$ of the population, so that the reduced amount of square agents entering the neighborhood would be tolerated by circle, but not when the $\beta^{\square}_e$ increases and too square agents enter the neighborhood, which would explain why value segregation persists rather than value integration as would be expected.
-* In the next panel where circle hold minimum threshold for both ethnic and value preferences $\beta^{\circ}_v = \beta^{\circ}_e = 5$, the demark between high randomness for $\beta^{\square}_e < 5$ and high utility $\beta^{\square}_e \geq 5$ returns and corresponds to value integration.
-* value segregation increases homogeneously when circle population maximizes  $\beta^{\circ}_v = 10$
-
-## Fig: \ref{fig:heatmapdsquare}
-* Fig: \ref{fig:heatmapdsquare}, for cirlce agents with higher value preferences than ethnic preferences, ethnic integration emerges for area of ethnic randomness with $\beta^{\circ}_e < 5$
-* Value segregation on the top right, where square agents show maximal ethnic and value utility  $\beta^{\square}_e = \beta^{\square}_v = 10$, full value segregation emerges for all conditions of $\beta$ levels, while in high ethnic utility area $\beta^{\square}_e \geq 5$ circle live in neighborhoods both value and ethnic homogeneous, for $\beta^{\square}_e <  5$ they live in ethnically mixed neighborhoods with circle of other ethnicity
-
 # References {-}

### 2020-05-09 exp_eth_val.Rmd
Add files via upload

@@
 * Figures
-    + Circle orange and square orange is taken as prototype (in the legend circle, square), since any subgroup in Fig: \ref{fig:thheory} has same probability $0.25$ to relocate close similar one and behavior would be symmetrical \textbf{-> agree?
-I would test otherwise}
+    + Circle orange and square orange is taken as prototype (in the legend circle, square), since any subgroup in Fig: \ref{fig:thheory} has same probability $0.25$ to relocate close to agents of same ethnicity and same value.
+Proof in ANNEX B, reporting behavior of circle blue and square blue
     + Need to find trade off between 4 parameters (see Tab: \ref{tab:Second}) and behavior of 2 type of agents (circle and blue) in conditions of relative group size
@@
 
-```{r betatwoethnic,fig.pos='H',fig.out="96%",fig.show = "hold",fig.align='center',fig.cap="Difference segregation, x-axis: difference ethnic and value preference square, faceting conditions: preferences of circle", echo=FALSE, include=TRUE }
+```{r betatwoethnic,fig.pos='H',fig.out="94%",fig.show = "hold",fig.align='center',fig.cap="Difference segregation, x-axis: difference ethnic and value square preference, faceting: circle preference", echo=FALSE, include=TRUE }
 
@@
 
-```{r betatwovalue,  fig.pos="H",fig.out="96%",fig.show = "hold", fig.align='center',fig.show="hold", fig.cap="Difference segregation between", echo=FALSE, include=TRUE  }
+```{r betatwovalue,  fig.pos="H",fig.out="94%",fig.show = "hold", fig.align='center',fig.show="hold", fig.cap="Difference segregation, x-axis: difference ethnic and value circle preference, faceting: square preference", echo=FALSE, include=TRUE  }
 
@@
 names(e_square.labs) <- c("0", "5","10")
-v_square.labs <- c("ß value square 0", "ß value square 5", "ß value square 10")
+v_square.labs <- c("Square ß value 0", "Square ß value 5", "Square ß value 10")
 names(v_square.labs) <- c("0", "5","10")
@@
 
+```{r betatwoethnicblue,fig.pos='H',fig.out="94%",fig.show = "hold",fig.align='center',fig.cap="Testing blue: Difference segregation, x-axis: difference ethnic and value square preference, faceting: circle preference", echo=FALSE, include=TRUE }
+
+circle_frame <- datatwo %>% filter(step == 1000) %>% filter(beta_iv_circle == 0 |beta_iv_circle == 5 |beta_iv_circle == 10 ) %>% filter(beta_ie_circle == 0 | beta_ie_circle == 5 | beta_ie_circle == 10)
+
+rev_beta_iv_circle.labs <- c("Circle ß value 10" ,"Circle ß value 5", "Circle ß value 0")
+names(rev_beta_iv_circle.labs) <- c("10", "5","0")
+beta_ie_circle.labs <- c("Circle \nß ethnic 0", "Circle \nß ethnic 5","Circle \nß ethnic 10")
+names(beta_ie_circle.labs) <- c("0", "5","10")
+
+#  v_circle.labs <- c("ß value circle 0", "ß value circle 5", "ß value circle 10")
+# names(v_circle.labs) <- c("0", "5","10")
+e_circle.labs <- c("Circle ß ethnic 0", "Circle ß ethnic 5", "Circle ß ethnic 10")
+names(e_circle.labs) <- c("0", "5","10")
+
+ibe_10 <- circle_frame %>%  filter(beta_ie_square == 10) %>% gather(key = subgroup, value = Segra, eth_sq_bl,val_sq_bl,eth_cl_bl,val_cl_bl) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"ethnic segregation" = c("eth_sq_bl","eth_cl_bl"), "value segregation" = c("val_sq_bl","val_cl_bl")), "ethnic segregation"), `group` = fct_relevel(fct_collapse(subgroup, "square" = c("eth_sq_bl","val_sq_bl"), "circle" = c("eth_cl_bl","val_cl_bl"), "square"))) %>%
+  ggplot(aes(x = (beta_ie_square - beta_iv_square), y = Segra, color = `segregation`, shape = `group`)) + geom_line() + geom_point( size = 2) + facet_grid(rev_beta_iv_circle ~  beta_ie_circle, labeller = labeller(rev_beta_iv_circle = rev_beta_iv_circle.labs,  beta_ie_circle = e_circle.labs )) +
+  geom_vline(xintercept = 5, color = "red") +
+  scale_x_discrete(name = "ß ethnic square 10 - ß value square", limits = seq(0,10, by = 1)) +  ylab("Segregation") +
+  scale_color_manual(values = c("dark violet","dark green"), guide = guide_legend(title="")) +
+  scale_shape_manual(values = c(16,15), guide = guide_legend(title="")) +
+    theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0))
+
+ibe_5 <- circle_frame %>%  filter(beta_ie_square == 5) %>% gather(key = subgroup, value = Segra, eth_sq_bl,val_sq_bl,eth_cl_bl,val_cl_bl) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"ethnic segregation" = c("eth_sq_bl","eth_cl_bl"), "value segregation" = c("val_sq_bl","val_cl_bl")), "ethnic segregation"), `group` = fct_relevel(fct_collapse(subgroup, "square" = c("eth_sq_bl","val_sq_bl"), "circle" = c("eth_cl_bl","val_cl_bl"), "square"))) %>%
+  ggplot(aes(x = (beta_ie_square - beta_iv_square), y = Segra, color = `segregation`, shape = `group`)) + geom_line() + geom_point( size = 2) + facet_grid(rev_beta_iv_circle ~  beta_ie_circle, labeller = labeller(rev_beta_iv_circle = rev_beta_iv_circle.labs,  beta_ie_circle = e_circle.labs )) +
+  scale_x_discrete(name = "ß ethnic square 10 - ß value square", limits = seq(0,5, by = 1)) +  ylab("Segregation") +
+  scale_color_manual(values = c("dark violet","dark green"), guide = guide_legend(title="")) +
+  scale_shape_manual(values = c(16,15), guide = guide_legend(title="")) +
+    theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0))
+
+ibe_5
+ibe_10
+```
+
+```{r betatwovalueblue,  fig.pos="H",fig.out="94%",fig.show = "hold", fig.align='center',fig.show="hold", fig.cap="Testing blue: Difference segregation, x-axis: difference ethnic and value circle preference, faceting: square preference", echo=FALSE, include=TRUE  }
+
+circle_frame <- datatwo %>% filter(step == 1000) %>% filter(beta_ie_square == 0 |beta_ie_square == 5 |beta_ie_square == 10 ) %>% filter(beta_iv_square == 0 | beta_iv_square == 5 | beta_iv_square == 10)
+
+rev_beta_ie_square.labs <- c("Square \nß ethnic 10" ,"Square \nß ethnic 5", "Square \nß ethnic 0")
+names(rev_beta_ie_square.labs) <- c("10", "5","0")
+
+e_square.labs <- c("ß ethnic \nsquare 0", "ß ethnic \nsquare 5", "ß ethnic \nsquare 10")
+names(e_square.labs) <- c("0", "5","10")
+v_square.labs <- c("ß value square 0", "ß value square 5", "ß value square 10")
+names(v_square.labs) <- c("0", "5","10")
+
+ibv_10 <- circle_frame %>%  filter(beta_iv_circle == 10) %>% gather(key = subgroup, value = Segra, eth_sq_bl,val_sq_bl,eth_cl_bl,val_cl_bl) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"ethnic segregation" = c("eth_sq_bl","eth_cl_bl"), "value segregation" = c("val_sq_bl","val_cl_bl")), "ethnic segregation"), `group` = fct_relevel(fct_collapse(subgroup, "square" = c("eth_sq_bl","val_sq_bl"), "circle" = c("eth_cl_bl","val_cl_bl"), "square")))  %>%
+  ggplot(aes(x = (beta_iv_circle - beta_ie_circle), y = Segra, color = `segregation`, shape = `group`)) + geom_line() + geom_point( size = 2) + facet_grid(rev_beta_ie_square ~  beta_iv_square, labeller = labeller(rev_beta_ie_square = rev_beta_ie_square.labs, beta_iv_square = v_square.labs))  +
+  geom_vline(xintercept = 5, color = "red") +
+  scale_x_discrete(name = "ß value circle 10 - ß ethnic circle", limits = seq(0,10, by = 1)) +  ylab("Segregation") +
+  scale_color_manual(values = c("dark violet","dark green"), guide = guide_legend(title="")) +
+  scale_shape_manual(values = c(16,15), guide = guide_legend(title="")) +
+    theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0))
+
+ibv_5 <- circle_frame %>%  filter(beta_iv_circle == 5) %>% gather(key = subgroup, value = Segra, eth_sq_bl,val_sq_bl,eth_cl_bl,val_cl_bl) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"ethnic segregation" = c("eth_sq_bl","eth_cl_bl"), "value segregation" = c("val_sq_bl","val_cl_bl")), "ethnic segregation"), `group` = fct_relevel(fct_collapse(subgroup, "square" = c("eth_sq_bl","val_sq_bl"), "circle" = c("eth_cl_bl","val_cl_bl"), "square")))  %>%
+  ggplot(aes(x = (beta_iv_circle - beta_ie_circle), y = Segra, color = `segregation`, shape = `group`)) + geom_line() + geom_point( size = 2) + facet_grid(rev_beta_ie_square ~  beta_iv_square, labeller = labeller(rev_beta_ie_square = rev_beta_ie_square.labs, beta_iv_square = v_square.labs))  +
+  scale_x_discrete(name = "ß value circle 5 - ß ethnic circle", limits = seq(0,5, by = 1)) +  ylab("Segregation") +
+  scale_color_manual(values = c("dark violet","dark green"), guide = guide_legend(title="")) +
+  scale_shape_manual(values = c(16,15), guide = guide_legend(title="")) +
+    theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0))
+
+ibv_5
+ibv_10
+
+```
+
 # References {-}

### 2020-11-23 JMS.Rmd
store of analyses and tests

---
title: "JMS"
output: pdf_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, fig.lp="fig:"  ,warning = FALSE)

# install.packages("tinytex", repos = "https://cloud.r-project.org" )

library(knitr)
library(ggplot2)
library(forcats)
library(reshape2)
library(tidyr)
library(dplyr)
library(reshape)
library(gtable)
library(explore)
library(gridExtra)
library(xtable)
library(ggpubr)

#  This was to simplify dataset of basic conditions
# a <- read.csv("basic_equal.csv", sep = ",", skip = 6)
# names(a) <- pull(read.csv("legend.csv"))
# B <- a %>% filter(dominant >= 0, secondary_circle  <= dominant, secondary_square <= dominant) %>% filter(ticks == 1000)
# write.csv(B, file = "basic_exp.csv", row.names = FALSE)

setwd("C:/Users/rocpa/OneDrive/Desktop/AF/experiments/JMS/")

hc_hc_dis <- read.csv("hc_hc_dis.csv")
# names(test_mj80) <- pull(read.csv("legend_test.csv"))

base_eq <-  read.csv("basic/basic_exp.csv", sep = ",")

majority_bs <- read.csv("maj/majority_bs.csv", sep = ",", skip = 6)
names(majority_bs) <- pull(read.csv("basic/legend_bas.csv"))

majority_bsa <- read.csv("maj/majority_bsa.csv", sep = ",", skip = 6)
names(majority_bsa) <- pull(read.csv("basic/legend_bas.csv"))
names(majority_bsa)[names(majority_bsa) == "circle_orange"] <- "dmnt"
names(majority_bsa)[names(majority_bsa) == "dominant"] <- "circle_orange"
names(majority_bsa)[names(majority_bsa) == "dmnt"] <- "dominant"

majority_bs <- majority_bs %>% filter(ticks == 1000)

# majlib <- read.csv("maj/maj_lib.csv", sep = ",", skip = 6)
# names(majlib) <- pull(read.csv("maj/legend_maj.csv"))

test_5_20 <- read.csv("result5_20.csv", sep = ",", skip = 6)
names(test_5_20) <- pull(read.csv("legend_test.csv"))
test_5_20 <- test_5_20[,-(35:42)]

test_20_5 <- read.csv("result20_5.csv", sep = ",", skip = 6)
names(test_20_5) <- pull(read.csv("legend_test.csv"))

b <- test_20_5 %>% filter(fraction_blue == 60)

a <- test_5_20 %>% filter(fraction_blue == 80)
ftable(xtabs(~ a$circle_orange + a$eth_loc_lib + a$eth_min_lib, data = a))

levels(as.factor(a$eth_loc_con))
levels(as.factor(b$eth_loc_con))

```

```{r onebeta, fig.pos="H",  fig.width=10, fig.cap="Same parameter for ethnic and value homophily for all agents", echo=FALSE}

base_eq %>% filter(dominant == secondary_square & dominant == secondary_circle & secondary_circle == secondary_square)  %>%  gather(key = subgroup, value = Segra, eth_sqr_loc, eth_sqr_min, eth_crl_loc, eth_crl_min, val_sqr_loc,val_sqr_min,val_crl_loc, val_crl_min) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"ethnic\nsegregation" = c("eth_sqr_loc","eth_sqr_min","eth_crl_loc","eth_crl_min"), "value\nsegregation" = c("val_sqr_loc","val_sqr_min","val_crl_loc", "val_crl_min")), "ethnic segregation"), `group` = fct_relevel(fct_collapse(subgroup, "conservative" = c("eth_sqr_loc","eth_sqr_min","val_sqr_loc","val_sqr_min"), "liberal" = c("eth_crl_loc","eth_crl_min","val_crl_loc", "val_crl_min"), "conservative")), 
  `ethnia` = fct_relevel(fct_collapse(subgroup, "local" = c("eth_sqr_loc","eth_crl_loc","val_sqr_loc","val_crl_loc"), "minority" = c("eth_sqr_min","eth_crl_min","val_sqr_min","val_crl_min")),"local" )) %>%

  ggplot( aes(x = dominant, y = Segra, color = `ethnia`, shape = `group`, linetype = `segregation`  )) + geom_line() + geom_point() +     
  scale_x_discrete(limits=c(seq(0,20 ,by = 1))) +
scale_y_continuous(limits=c(0,1), breaks=seq(0,1,by=0.25)) +
  geom_vline(xintercept = c(1,5,10,20), color = "red") +
  geom_hline(yintercept = 0.5, color = "red", linetype = 2) +
  scale_color_manual(values = c("blue","orange"), guide = guide_legend(title="",override.aes = list(size = 2))) +
  scale_linetype_manual(values = c("solid","dashed"), guide = guide_legend(title="",override.aes = list(size = 1))) +
  scale_shape_manual(values = c("circle","square"), guide = guide_legend(title="",override.aes = list(size = 3))) + xlab("ß dominant = ß secondary") + ylab("Segregation") +   
  theme_bw() +  theme( legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(),legend.text = element_text(size = 19),axis.title.x = (element_text(size = 20)), axis.title.y = (element_text(size = 20)), axis.text.x =  (element_text(size = 18)),axis.text.y =  (element_text(size = 18)),
                      plot.title=element_text(hjust = 0.5),  legend.margin=margin(2,2,2,2)) +
  theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))

ggsave("one_beta.jpg",plot = last_plot(),
  device = NULL,
  path = NULL,
  scale = 1,
  width = 11,
  height = 5,
  units = c("in", "cm", "mm"),
  dpi = 300,
  limitsize = FALSE)

```

```{r heatmap,fig.pos="H",  include=TRUE,fig.height=11, fig.width=11, fig.cap="Comparison dominant vs secondary", echo=FALSE}

base_eq  %>% filter(secondary_circle == secondary_square) %>% gather(key = subgroup, value = Segra, eth_sqr,val_sqr,eth_crl,val_crl) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"ethnic segregation" = c("eth_sqr","eth_crl"),"value segregation" = c("val_sqr","val_crl")), "ethnic segregation"),  `group` = fct_relevel(fct_collapse(subgroup,"liberal" = c("eth_crl","val_crl"), "conservative" = c("eth_sqr","val_sqr")),"liberal")) %>%

  ggplot( aes(x = secondary_circle , y = dominant , fill = Segra)) + geom_tile() + 
 facet_grid( group ~  segregation) +
  xlab("Secondary Beta") + ylab("Dominant Beta") +
scale_x_discrete(limits=seq(0, 20 ,by = 1)) +
  scale_y_discrete(limits=seq(0,20 ,by = 1)) + 
  geom_text(aes(label=round(Segra,2)), size=3) +
   scale_fill_distiller(palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1), name = "Segregation") + 
    theme_bw() +  
  theme(legend.position = "bottom", legend.title = element_text(size = 12,vjust = 0.8), legend.text = element_text(size = 15),  legend.key.width  = unit(1, "inch"), 
                        legend.key.height  = unit(0.3, "inch"), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0),
                        axis.title.x = (element_text(size = 18)), axis.title.y = (element_text(size = 18)), axis.text.x =  (element_text(size = 13)),axis.text.y =  (element_text(size = 13)),strip.text.x = element_text(size = 15),
                        strip.text.y = element_text(size = 15))

ggsave("heatmapbase.jpg",plot = last_plot(),
  device = NULL,
  path = NULL,
  scale = 1,
  width = NA,
  height = NA,
  units = c("in", "cm", "mm"),
  dpi = 300,
  limitsize = TRUE)

```

```{r secondary_zero,fig.pos="H",  include=TRUE, fig.width=11,  fig.cap="Secondary preference set to 0. Here only circle minority, patterns are the same", echo=FALSE}

  base_eq  %>% filter(secondary_circle == 0 & secondary_square == 0) %>% gather(key = subgroup, value = Segra, eth_sqr,val_sqr,eth_crl,val_crl) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"ethnic segregation" = c("eth_sqr","eth_crl"),"value segregation" = c("val_sqr","val_crl")), "ethnic segregation"),  `group` = fct_relevel(fct_collapse(subgroup,"liberal" = c("eth_crl","val_crl"), "conservative" = c("eth_sqr","val_sqr")),"liberal")) %>%

  ggplot( aes(x = dominant, y = Segra, color = `segregation`, shape = `group` )) + geom_line() + geom_point(size=3) + scale_x_discrete(limits=seq(0,20 ,by = 1)) +
 scale_y_continuous(breaks=seq(0,1,by = 0.1)) +
  scale_y_continuous(limits=c(0,1), breaks=seq(0,1,by=0.25)) +
        geom_vline(xintercept = c(1,5,10,20), color = "red") +
  geom_hline(yintercept = 0.5, color = "red", linetype = 2) +
    scale_color_manual(values = c("purple","dark green"), guide = guide_legend(title="")) +
  scale_linetype_manual(values = c("solid","dashed"), guide = guide_legend(title="")) +
  scale_shape_manual(values = c("circle","square"), guide = guide_legend(title="")) + xlab("ß dominant") + ylab("Segregation") +   
 theme_bw() +  theme(
   legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(),legend.text = element_text(size = 18), axis.title.x = (element_text(size = 20)), axis.title.y = (element_text(size = 20)), axis.text.x =  (element_text(size = 18)),axis.text.y =  (element_text(size = 18)),
                      plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0),
                     plot.caption = element_text(hjust= 0.5, size = 12)) +
  labs( caption = "Secondary ß for all agents = 0") +
  theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))

ggsave("secondary_zero.jpg",plot = last_plot(),
  device = NULL,
  path = NULL,
  scale = 1,
  width = 11,
  height = 5,
  units = c("in", "cm", "mm"),
  dpi = 300,
  limitsize = FALSE)

```

```{r bas_dom_crl, pos="H",  include=TRUE, fig.width=10,  fig.cap="Sensitivity dominant liberal",    echo=FALSE}

basic_dom <- read.csv("basic/equal_dom_sens.csv", sep = ",", skip = 6)
names(basic_dom) <- pull(read.csv("basic/legend_bas_sens.csv"))

  basic_dom  %>% filter(secondary_circle == 0, secondary_square == 0, dominant_square == 0) %>% gather(key = subgroup, value = Segra, eth_sqr,val_sqr,eth_crl,val_crl) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"ethnic segregation" = c("eth_sqr","eth_crl"),"value segregation" = c("val_sqr","val_crl")), "ethnic segregation"),  `group` = fct_relevel(fct_collapse(subgroup,"liberal" = c("eth_crl","val_crl"), "conservative" = c("eth_sqr","val_sqr")),"liberal")) %>%

  ggplot( aes(x = dominant_circle, y = Segra, color = `segregation`, shape = `group` )) + geom_line() + geom_point(size=3) + scale_x_discrete(limits=seq(0,20 ,by = 1)) +
scale_y_continuous(limits=c(0,1), breaks=seq(0,1,by=0.25)) +
      geom_hline(yintercept = 0.5, color = "red", linetype = 2) +

  scale_color_manual(values = c("purple","dark green"), guide = guide_legend(title="")) +
  scale_linetype_manual(values = c("solid","dashed"), guide = guide_legend(title="")) +
  scale_shape_manual(values = c("circle","square"), guide = guide_legend(title=""))   +
    xlab("ß value liberal") + ylab("Segregation") +   
      geom_vline(xintercept = c(1,5,10,20), color = "red") +
 theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(),legend.text = element_text(size = 18), axis.title.x = (element_text(size = 20)), axis.title.y = (element_text(size = 20)), axis.text.x =  (element_text(size = 18)),axis.text.y =  (element_text(size = 18)),
                      plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0),
                     plot.caption = element_text(hjust= 0.5, size = 12)) +
labs( caption = "ß ethnic liberal = 0\n ß value and ethnic conservative = 0") +
  theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))

ggsave("bas_dom_crl.jpg",plot = last_plot(),
  device = NULL,
  path = NULL,
  scale = 1,
  width = 11,
  height = 7,
  units = c("in", "cm", "mm"),
  dpi = 300,
  limitsize = FALSE)

```

```{r bas_dom_sqr, pos="H",  include=TRUE, fig.width=10,  fig.cap="Sensitivity dominant conservative", echo=FALSE}

basic_dom <- read.csv("basic/equal_dom_sens.csv", sep = ",", skip = 6)
names(basic_dom) <- pull(read.csv("basic/legend_bas_sens.csv"))

  basic_dom  %>% filter(secondary_circle == 0, secondary_square == 0, dominant_circle == 0) %>% gather(key = subgroup, value = Segra, eth_sqr,val_sqr,eth_crl,val_crl) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"ethnic segregation" = c("eth_sqr","eth_crl"),"value segregation" = c("val_sqr","val_crl")), "ethnic segregation"),  `group` = fct_relevel(fct_collapse(subgroup,"liberal" = c("eth_crl","val_crl"), "conservative" = c("eth_sqr","val_sqr")),"liberal")) %>%

  ggplot( aes(x = dominant_square, y = Segra, color = `segregation`, shape = `group` )) + geom_line() + geom_point(size=3) + scale_x_discrete(limits=seq(0,20 ,by = 1)) +
scale_y_continuous(limits=c(0,1), breaks=seq(0,1,by=0.25)) +
  scale_color_manual(values = c("purple","dark green"), guide = guide_legend(title="")) +
  scale_linetype_manual(values = c("solid","dashed"), guide = guide_legend(title="")) +
  scale_shape_manual(values = c("circle","square"), guide = guide_legend(title="")) +
      geom_vline(xintercept = c(1,5,10,20), color = "red") +
      geom_hline(yintercept = 0.5, color = "red", linetype = 2) +
    xlab("ß ethnic conservative") + ylab("Segregation") +

 theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(),legend.text = element_text(size = 18), axis.title.x = (element_text(size = 20)), axis.title.y = (element_text(size = 20)), axis.text.x =  (element_text(size = 18)),axis.text.y =  (element_text(size = 18)),
                      plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0),
                     plot.caption = element_text(hjust= 0.5, size = 12)) +
  labs( caption = "ß value conservative = 0\n ß value and ethnic liberal = 0") +
  theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))

ggsave("bas_dom_sqr.jpg",plot = last_plot(),
  device = NULL,
  path = NULL,
  scale = 1,
  width = 11,
  height = 7,
  units = c("in", "cm", "mm"),
  dpi = 300,
  limitsize = TRUE)

```

```{r random_circle, pos="H",  include=TRUE, fig.width=10,  fig.cap="Sensitivity secondary circle", echo=FALSE}

basic_rand <- read.csv("basic/equal_rand_sens.csv", sep = ",", skip = 6)
names(basic_rand) <- pull(read.csv("basic/legend_bas_sens.csv"))

  basic_rand  %>% filter(secondary_square == 0) %>% gather(key = subgroup, value = Segra, eth_sqr,val_sqr,eth_crl,val_crl) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"ethnic segregation" = c("eth_sqr","eth_crl"),"value segregation" = c("val_sqr","val_crl")), "ethnic segregation"),  `group` = fct_relevel(fct_collapse(subgroup,"liberal" = c("eth_crl","val_crl"), "conservative" = c("eth_sqr","val_sqr")),"liberal")) %>%

  ggplot( aes(x = secondary_circle, y = Segra, color = `segregation`, shape = `group` )) + geom_line() + geom_point(size=3) + scale_x_discrete(limits=seq(0,20 ,by = 1)) +
scale_y_continuous(limits=c(0,1), breaks=seq(0,1,by=0.25)) +
  scale_color_manual(values = c("purple","dark green"), guide = guide_legend(title="")) +
  scale_linetype_manual(values = c("solid","dashed"), guide = guide_legend(title="")) +
  scale_shape_manual(values = c("circle","square"), guide = guide_legend(title="")) + 
      geom_vline(xintercept = c(1,5,10,20), color = "red") +
      geom_hline(yintercept = 0.5, color = "red", linetype = 2) +
    xlab("ß ethnic liberal") + ylab("Segregation") +   
 theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(),legend.text = element_text(size = 18), axis.title.x = (element_text(size = 20)), axis.title.y = (element_text(size = 20)), axis.text.x =  (element_text(size = 18)),axis.text.y =  (element_text(size = 18)),
                      plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0),
                     plot.caption = element_text(hjust= 0.5, size = 12)) +
  labs( caption = "ß value liberal = 20; ß ethnic conservative = 20\n ß value conservative = 0") +
  theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))

ggsave("bas_sec_crl.jpg",plot = last_plot(),
  device = NULL,
  path = NULL,
  scale = 1,
  width = 11,
  height = 6,
  units = c("in", "cm", "mm"),
  dpi = 300,
  limitsize = TRUE)

```

```{r random_square, pos="H",  include=TRUE, fig.width=10,  fig.cap="Sensitivity secondary circle", echo=FALSE}

basic_rand <- read.csv("basic/equal_rand_sens.csv", sep = ",", skip = 6)
names(basic_rand) <- pull(read.csv("basic/legend_bas_sens.csv"))

  basic_rand  %>% filter(secondary_circle == 0) %>% gather(key = subgroup, value = Segra, eth_sqr,val_sqr,eth_crl,val_crl) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"ethnic segregation" = c("eth_sqr","eth_crl"),"value segregation" = c("val_sqr","val_crl")), "ethnic segregation"),  `group` = fct_relevel(fct_collapse(subgroup,"liberal" = c("eth_crl","val_crl"), "conservative" = c("eth_sqr","val_sqr")),"liberal")) %>%

  ggplot( aes(x = secondary_square, y = Segra, color = `segregation`, shape = `group` )) + geom_line() + geom_point(size=3) + scale_x_discrete(limits=seq(0,20 ,by = 1)) +
scale_y_continuous(limits=c(0,1), breaks=seq(0,1,by=0.25)) +
  scale_color_manual(values = c("purple","dark green"), guide = guide_legend(title="")) +
  scale_linetype_manual(values = c("solid","dashed"), guide = guide_legend(title="")) +
  scale_shape_manual(values = c("circle","square"), guide = guide_legend(title="")) + xlab("ß value conservative") + ylab("Segregation") +   
      geom_vline(xintercept = c(1,5,10,20), color = "red") +
       geom_hline(yintercept = 0.5, color = "red", linetype = 2) +
 theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(),legend.text = element_text(size = 18), axis.title.x = (element_text(size = 20)), axis.title.y = (element_text(size = 20)), axis.text.x =  (element_text(size = 18)),axis.text.y =  (element_text(size = 18)),
                      plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0),
                     plot.caption = element_text(hjust= 0.5, size = 12)) +
  labs( caption = "ß value liberal = 20, ß ethnic conservative = 20\n ß ethnic liberal = 0") +
  theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))

ggsave("bas_sec_sqr.jpg",plot = last_plot(),
  device = NULL,
  path = NULL,
  scale = 1,
  width = 11,
  height = 6,
  units = c("in", "cm", "mm"),
  dpi = 300,
  limitsize = TRUE)

```

# Asymmetric CONDITIONS

```{r asymmetricmech5050, fig.pos="H", include=TRUE,fig.cap="Ethnic asymmetric condition. 80% local, 20% minority. Both 50% liberal", echo=FALSE}
# 
# ethnia.labs <- c("Local: 80% population", "Minority: 20% population")
# names(ethnia.labs) <- c("aaaaa", "minority")

majority_bsa %>%   filter(circle_orange == 50, secondary_circle == 0, secondary_square == 0)  %>%  gather(key = subgroup, value = Segra, eth_sqr_loc, eth_sqr_min, eth_crl_loc, eth_crl_min, val_sqr_loc,val_sqr_min,val_crl_loc, val_crl_min) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"ethnic seg." = c("eth_sqr_loc","eth_sqr_min","eth_crl_loc","eth_crl_min"), "value seg." = c("val_sqr_loc","val_sqr_min","val_crl_loc", "val_crl_min")), "ethnic seg."), `group` = fct_relevel(fct_collapse(subgroup, "conservative" = c("eth_sqr_loc","eth_sqr_min","val_sqr_loc","val_sqr_min"), "liberal" = c("eth_crl_loc","eth_crl_min","val_crl_loc", "val_crl_min"), "conservative")), 
    `ethnia` = fct_relevel(fct_collapse(subgroup, "Locals: 80% population | 50% liberals" = c("eth_sqr_loc","eth_crl_loc","val_sqr_loc","val_crl_loc"), "Migrants: 20% population | 50% liberals" = c("eth_sqr_min","eth_crl_min","val_sqr_min","val_crl_min")),"Locals: 80% population | 50% liberals" )) %>%

  ggplot( aes(x = dominant, y = Segra, color = `segregation`, shape = `group`)) + 
  geom_line() + geom_point(size = 3) +           scale_x_discrete(limits= seq(0,20 ,by = 1)) +
  scale_y_continuous(limits=c(0,1), breaks = c(0,0.2,0.5,0.8,1)) +
 #  scale_y_continuous(limits=c(0,1), breaks = c(0.2,0.5,0.8),position = "right") +
  geom_vline(xintercept = c(1,5,10,20), color = "red") +
    geom_hline(yintercept = c(0.5), color = "red", linetype = 2) +
      geom_hline(yintercept = c(0.8), color = "purple", linetype = 5) +
      geom_hline(yintercept = c(0.2), color = "purple", linetype = 2) +
# sec.axis = sec_axis( trans=~.*10, name="Second Axis")

  facet_wrap(~ `ethnia`,nrow =2 , dir = "v") +
 scale_color_manual(values = c("purple","dark green"), guide = guide_legend(title= "")) + # ,nrow=2, byrow = TRUE)) +
 scale_shape_manual(values = c("circle","square"), guide = guide_legend(title= "")) + #,nrow=2, byrow = TRUE)) + 
   xlab("ß Dominant all agents\n ß Secondary all agents = 0") + 
  ylab("Segregation") +   
   theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(),legend.text = element_text(size = 12),
                      axis.title.y = (element_text(size = 12)), # element_blank(),  # 
                      axis.title.x = (element_text(size = 12)), #   element_blank(), # 
                      axis.text.x = (element_text(size = 11)),
                      axis.text.y =  (element_text(size = 11)),
                      plot.title=element_text(hjust = 0.5),  
                      legend.margin=margin(0,2,0,0), panel.spacing = unit(0.8, "lines"), 
                      strip.text.x = element_text(size = 15),  strip.text.y = element_text(size = 15),
                      plot.caption = element_text(hjust= 0.5, size = 12)) +
theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))

ggsave("diffsize.jpg",plot = last_plot(),
  device = NULL,
  path = NULL,
  scale = 1,
  width = 5.5,
  height = 5,
 # units = c("in", "cm", "mm"),
  dpi = 300,
  limitsize = TRUE)

```

```{r asymmetricmech5020, fig.pos="H", include=TRUE,fig.cap="Ethnic asymmetric condition. 80% local, 20% minority. Both 80% liberal", echo=FALSE}
# 
# ethnia.labs <- c("Local: 80% population", "Minority: 20% population")
# names(ethnia.labs) <- c("aaaaa", "minority")

majority_bsa %>%   filter(circle_orange == 20, secondary_circle == 0, secondary_square == 0)  %>% gather(key = subgroup, value = Segra, eth_sqr_loc, eth_sqr_min, eth_crl_loc, eth_crl_min, val_sqr_loc,val_sqr_min,val_crl_loc, val_crl_min) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"ethnic seg." = c("eth_sqr_loc","eth_sqr_min","eth_crl_loc","eth_crl_min"), "value seg." = c("val_sqr_loc","val_sqr_min","val_crl_loc", "val_crl_min")), "ethnic seg."), `group` = fct_relevel(fct_collapse(subgroup, "conservative" = c("eth_sqr_loc","eth_sqr_min","val_sqr_loc","val_sqr_min"), "liberal" = c("eth_crl_loc","eth_crl_min","val_crl_loc", "val_crl_min"), "conservative")), 
    `ethnia` = fct_relevel(fct_collapse(subgroup, "Locals: 80% population | 50% liberals" = c("eth_sqr_loc","eth_crl_loc","val_sqr_loc","val_crl_loc"), "Migrants: 20% population | 20% liberals" = c("eth_sqr_min","eth_crl_min","val_sqr_min","val_crl_min")),"Locals: 80% population | 50% liberals" )) %>%

  ggplot( aes(x = dominant, y = Segra, color = `segregation`, shape = `group`)) + 
  geom_line() + geom_point(size = 3) +           scale_x_discrete(limits= seq(0,20 ,by = 1)) +
  scale_y_continuous(limits=c(0,1), breaks = c(0,0.2,0.5,0.8,1)) +
 #  scale_y_continuous(limits=c(0,1), breaks = c(0.2,0.5,0.8),position = "right") +
  geom_vline(xintercept = c(1,5,10,20), color = "red") +
    geom_hline(yintercept = c(0.5), color = "red", linetype = 2) +
      geom_hline(yintercept = c(0.8), color = "purple", linetype = 5) +
      geom_hline(yintercept = c(0.2), color = "purple", linetype = 2) +
# sec.axis = sec_axis( trans=~.*10, name="Second Axis")

  facet_wrap(~ `ethnia`,nrow =2 , dir = "v") +
 scale_color_manual(values = c("purple","dark green"), guide = guide_legend(title= "")) + # ,nrow=2, byrow = TRUE)) +
 scale_shape_manual(values = c("circle","square"), guide = guide_legend(title= "")) + #,nrow=2, byrow = TRUE)) + 
   xlab("ß Dominant all agents\n ß Secondary all agents = 0") + 
  ylab("Segregation") +   
   theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(),legend.text = element_text(size = 12),
                      axis.title.y = (element_text(size = 12)), # element_blank(),  # 
                      axis.title.x = (element_text(size = 12)), #   element_blank(), # 
                      axis.text.x = (element_text(size = 11)),
                      axis.text.y =  (element_text(size = 11)),
                      plot.title=element_text(hjust = 0.5),  
                      legend.margin=margin(0,2,0,0), panel.spacing = unit(0.8, "lines"), 
                      strip.text.x = element_text(size = 15),  strip.text.y = element_text(size = 15),
                      plot.caption = element_text(hjust= 0.5, size = 12)) +
theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))

ggsave("diffsize20.jpg",plot = last_plot(),
  device = NULL,
  path = NULL,
  scale = 1,
  width = 5.5,
  height = 5,
 # units = c("in", "cm", "mm"),
  dpi = 300,
  limitsize = TRUE)

# +
#  scale_shape_manual(values = c(16,15), guide = guide_legend(title="")) +

```

```{r asymmetricmech5080, fig.pos="H", include=TRUE,fig.cap="Ethnic asymmetric condition. 80% local, 20% minority. Both 50% liberal", echo=FALSE}
# 
# ethnia.labs <- c("Local: 80% population", "Minority: 20% population")
# names(ethnia.labs) <- c("aaaaa", "minority")

majority_bsa %>%   filter(circle_orange == 80, secondary_circle == 0, secondary_square == 0)  %>% gather(key = subgroup, value = Segra, eth_sqr_loc, eth_sqr_min, eth_crl_loc, eth_crl_min, val_sqr_loc,val_sqr_min,val_crl_loc, val_crl_min) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"ethnic seg." = c("eth_sqr_loc","eth_sqr_min","eth_crl_loc","eth_crl_min"), "value seg." = c("val_sqr_loc","val_sqr_min","val_crl_loc", "val_crl_min")), "ethnic seg."), `group` = fct_relevel(fct_collapse(subgroup, "conservative" = c("eth_sqr_loc","eth_sqr_min","val_sqr_loc","val_sqr_min"), "liberal" = c("eth_crl_loc","eth_crl_min","val_crl_loc", "val_crl_min"), "conservative")), 
    `ethnia` = fct_relevel(fct_collapse(subgroup, "Locals: 80% population | 50% liberals" = c("eth_sqr_loc","eth_crl_loc","val_sqr_loc","val_crl_loc"), "Migrants: 20% population | 80% liberals" = c("eth_sqr_min","eth_crl_min","val_sqr_min","val_crl_min")),"Locals: 80% population | 50% liberals" )) %>%

  ggplot( aes(x = dominant, y = Segra, color = `segregation`, shape = `group`)) + 
  geom_line() + geom_point(size = 3) +           scale_x_discrete(limits= seq(0,20 ,by = 1)) +
  scale_y_continuous(limits=c(0,1), breaks = c(0,0.2,0.5,0.8,1)) +
  geom_vline(xintercept = c(1,5,10,20), color = "red") +
    geom_hline(yintercept = c(0.5), color = "red", linetype = 2) +
      geom_hline(yintercept = c(0.8), color = "purple", linetype = 5) +
      geom_hline(yintercept = c(0.2), color = "purple", linetype = 2) +
# sec.axis = sec_axis( trans=~.*10, name="Second Axis")

  facet_wrap(~ `ethnia`,nrow =2 , dir = "v") +
 scale_color_manual(values = c("purple","dark green"), guide = guide_legend(title= "")) + # ,nrow=2, byrow = TRUE)) +
 scale_shape_manual(values = c("circle","square"), guide = guide_legend(title= "")) + #,nrow=2, byrow = TRUE)) + 
    xlab("ß Dominant all agents\n ß Secondary all agents = 0") + 
  ylab("Segregation") +   
   theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(),legend.text = element_text(size = 12),
                      axis.title.y = (element_text(size = 12)), # element_blank(),  # 
                      axis.title.x = (element_text(size = 12)), #   element_blank(), # 
                      axis.text.x = (element_text(size = 11)),
                      axis.text.y =  (element_text(size = 11)),
                      plot.title=element_text(hjust = 0.5),  
                      legend.margin=margin(0,2,0,0), panel.spacing = unit(0.8, "lines"), 
                      strip.text.x = element_text(size = 15),  strip.text.y = element_text(size = 15),
                      plot.caption = element_text(hjust= 0.5, size = 12)) +
theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))

ggsave("diffsize80.jpg",plot = last_plot(),
  device = NULL,
  path = NULL,
  scale = 1,
  width = 5.5,
  height = 5,
 # units = c("in", "cm", "mm"),
  dpi = 300,
  limitsize = TRUE)

# +
#  scale_shape_manual(values = c(16,15), guide = guide_legend(title="")) +

```

## Asymmetric dominant = secondary

```{r asym_sens database, fig.pos="H",include=TRUE,fig.cap="Dominant = Secondary; Migrants change", echo=FALSE}

# Change only in Migrants

domsec_min <- read.csv("maj/sens_asym_min.csv")
ID <- rep("min", length(domsec_min$run))
domsec_min <- cbind(ID,domsec_min)

domsec_maj <- read.csv("maj/sens_asym_maj.csv")
ID <- rep("maj", length(domsec_min$run))
domsec_maj <- cbind(ID,domsec_maj)

dataset_maj <- rbind(domsec_min,domsec_maj)

dominant_locals.labs <- c("ß Dominant Locals: 0", "ß Dominant Locals: 5","ß Dominant Locals: 10")
names(dominant_locals.labs) <- c("0", "5", "10")
circle_orange_labs <- c("20% Liberal Migrants", "50% Liberal Migrants","80% Liberal Migrants")
names(circle_orange_labs) <- c("20", "50", "80")
dominant_migrants.labs <- c("ß Dominant Migrants: 0", "ß Dominant Migrants: 5","ß Dominant Migrants: 10")
names(dominant_migrants.labs) <- c("0", "5", "10")
dominant_locals.labs <- c("ß Dominant Locals: 0", "ß Dominant Locals: 5","ß Dominant Locals: 10")
names(dominant_locals.labs) <- c("0", "5", "10")

```

```{r asym_dom_min, fig.pos="H",include=TRUE,fig.cap="Sensitivity assymetry", echo=FALSE}

## Comparison

loc_0 <- dataset_maj  %>% filter(ID == "min") %>% filter(circle_orange == 50) %>% filter(dominant_locals == 0) 
loc_5 <- dataset_maj  %>% filter(ID == "min") %>% filter(circle_orange == 50) %>% filter(dominant_locals == 5) 
loc_10 <- dataset_maj  %>% filter(ID == "min") %>% filter(circle_orange == 50) %>% filter(dominant_locals == 10)

df <- loc_10
name_min <- paste0("loc_10",".jpg")

df %>% gather(key = subgroup, value = Segra, eth_sqr_loc, eth_sqr_min, eth_crl_loc, eth_crl_min, val_sqr_loc,val_sqr_min,val_crl_loc, val_crl_min) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"ethnic seg." = c("eth_sqr_loc","eth_sqr_min","eth_crl_loc","eth_crl_min"), "value seg." = c("val_sqr_loc","val_sqr_min","val_crl_loc", "val_crl_min")), "ethnic seg."),`group` = fct_relevel(fct_collapse(subgroup, "liberal" = c("eth_crl_loc","eth_crl_min","val_crl_loc", "val_crl_min"), "conservative" = c("eth_sqr_loc","eth_sqr_min","val_sqr_loc","val_sqr_min")), "liberal"), `ethnia` = fct_relevel(fct_collapse(subgroup, "Locals:80% ethnic population | 50% liberal" = c("eth_sqr_loc","eth_crl_loc","val_sqr_loc","val_crl_loc"), "Migrants: 20% ethnic population | 50% liberal" = c("eth_sqr_min","eth_crl_min","val_sqr_min","val_crl_min")),"Locals:80% ethnic population | 50% liberal" ))  %>%

  ggplot( aes(x = dominant_migrants, y = Segra, color = `segregation`, shape = `group`)) + geom_line() + geom_point(size = 3) +

  scale_x_discrete(limits= seq(0,20 ,by = 1)) +

  scale_y_continuous(limits=c(0,1), breaks = c(0,0.2,0.5,0.8,1)) +
  geom_vline(xintercept = c(1,5,10,20), color = "red") +
    geom_hline(yintercept = c(0.5), color = "red", linetype = 2) +
      geom_hline(yintercept = c(0.8), color = "purple", linetype = 5) +
      geom_hline(yintercept = c(0.2), color = "purple", linetype = 2) +
  facet_wrap( ~ `ethnia`,
             nrow =2 , dir = "v")  +

 scale_color_manual(values = c("purple","dark green"), guide = guide_legend(title= "")) + # ,nrow=2, byrow = TRUE)) +
 scale_shape_manual(values = c("circle","square"), guide = guide_legend(title= "")) + #,nrow=2, byrow = TRUE)) + 
   ylab("Segregation") +   
  xlab("ß Dominat Migrants\n ß secondary all agents:0") + 
#  guides(color = FALSE, shape = FALSE) +
  ggtitle(paste0("ß dominant locals: ", df$dominant_locals)) +
  theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(),legend.text = element_text(size = 12),
                      axis.title.y = (element_text(size = 12)), #     
                      axis.title.x = (element_text(size = 12)), #   element_blank(),

                     #  axis.title.y = element_blank(),
                     #  axis.title.x = element_blank(),

                      axis.text.x = (element_text(size = 11)),
                      axis.text.y =  (element_text(size = 11)),
                      plot.title=element_text(hjust = 0.5),  
                      legend.margin=margin(0,2,0,0), panel.spacing = unit(0.8, "lines"), 
                      strip.text.x = element_text(size = 15),  strip.text.y = element_text(size = 15),
                      plot.caption = element_text(hjust= 0.5, size = 12)) +
theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))

ggsave(name_min,plot = last_plot(),
  device = NULL,
  path = NULL,
  scale = 1,
  width = 5.5,
  height = 5,
 # units = c("in", "cm", "mm"),
  dpi = 300,
  limitsize = TRUE)

```

```{r asym_dom_min_dislib, fig.pos="H",include=TRUE,fig.cap="Sensitivity assymetry minority, effect distribution liberal minority", echo=FALSE}

loc_0 <- dataset_maj  %>% filter(ID == "min") %>% filter(circle_orange == 50) %>% filter(dominant_locals == 0) 
loc_5 <- dataset_maj  %>% filter(ID == "min") %>% filter(circle_orange == 20|circle_orange == 50 | circle_orange == 80) %>% filter(dominant_locals == 5)
loc_10 <- dataset_maj  %>% filter(ID == "min") %>% filter(circle_orange == 20|circle_orange == 50 | circle_orange == 80) %>% filter(dominant_locals == 10)

df <- loc_10
name_min <- paste0("loc_10","_dislib.jpg")

df %>% gather(key = subgroup, value = Segra, eth_sqr_loc, eth_sqr_min, eth_crl_loc, eth_crl_min, val_sqr_loc,val_sqr_min,val_crl_loc, val_crl_min) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"ethnic seg." = c("eth_sqr_loc","eth_sqr_min","eth_crl_loc","eth_crl_min"), "value seg." = c("val_sqr_loc","val_sqr_min","val_crl_loc", "val_crl_min")), "ethnic seg."),`group` = fct_relevel(fct_collapse(subgroup, "liberal" = c("eth_crl_loc","eth_crl_min","val_crl_loc", "val_crl_min"), "conservative" = c("eth_sqr_loc","eth_sqr_min","val_sqr_loc","val_sqr_min")), "liberal"), `ethnia` = fct_relevel(fct_collapse(subgroup, "Locals:80% ethnic\n 50% liberal" = c("eth_sqr_loc","eth_crl_loc","val_sqr_loc","val_crl_loc"), "Migrants: 20% ethnic" = c("eth_sqr_min","eth_crl_min","val_sqr_min","val_crl_min")),"Locals:80% ethnic\n 50% liberal" ))  %>%

  ggplot( aes(x = dominant_migrants, y = Segra, color = `segregation`, shape = `group`)) + geom_line() + geom_point(size = 3) +

  scale_x_discrete(limits= seq(0,20 ,by = 1)) +

  scale_y_continuous(limits=c(0,1), breaks = c(0,0.2,0.5,0.8,1)) +
  geom_vline(xintercept = c(1,5,10,20), color = "red") +
    geom_hline(yintercept = c(0.5), color = "red", linetype = 2) +
      geom_hline(yintercept = c(0.8), color = "purple", linetype = 5) +
      geom_hline(yintercept = c(0.2), color = "purple", linetype = 2) +
  facet_grid( `ethnia` ~ circle_orange, labeller = labeller(circle_orange = circle_orange_labs)) +

 scale_color_manual(values = c("purple","dark green"), guide = guide_legend(title= "")) + # ,nrow=2, byrow = TRUE)) +
 scale_shape_manual(values = c("circle","square"), guide = guide_legend(title= "")) + #,nrow=2, byrow = TRUE)) + 
   ylab("Segregation") +   
  xlab("ß Dominat Migrants\n ß secondary all agents:0") + 
# guides(color = FALSE, shape = FALSE) +
 ggtitle(paste0("ß dominant locals: ", df$dominant_locals)) +
  theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(),legend.text = element_text(size = 12),
                     axis.title.y = (element_text(size = 12)), #     
                     axis.title.x = (element_text(size = 12)), #   element_blank(),

                      #  axis.title.y = element_blank(),
                      #  axis.title.x = element_blank(),

                      axis.text.x = (element_text(size = 9)),
                      axis.text.y =  (element_text(size = 9)),
                      plot.title=element_text(hjust = 0.5),  
                      legend.margin=margin(0,2,0,0), panel.spacing = unit(0.8, "lines"), 
                      strip.text.x = element_text(size = 15),  strip.text.y = element_text(size = 15),
                      plot.caption = element_text(hjust= 0.5, size = 12)) +
theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))

ggsave(name_min,plot = last_plot(),
  device = NULL,
  path = NULL,
  scale = 1.5,
  width = 8, #7.3,
  height = 4, #3.8,
 # units = c("in", "cm", "mm"),
  dpi = 300,
  limitsize = TRUE)

```

```{r asym_dom_maj, fig.pos="H",include=TRUE,fig.cap="Sensitivity assymetry majority locals", echo=FALSE}

mig_0 <- dataset_maj  %>% filter(ID == "maj") %>% filter(circle_orange == 50) %>% filter(dominant_migrants == 0) 
mig_5 <- dataset_maj  %>% filter(ID == "maj") %>% filter(circle_orange == 50) %>% filter(dominant_migrants == 5) 
mig_10 <- dataset_maj  %>% filter(ID == "maj") %>% filter(circle_orange == 50) %>% filter(dominant_migrants == 10)

dfm <- mig_5
name_maj <- paste0("mig_5",".jpg")

dfm %>% gather(key = subgroup, value = Segra, eth_sqr_loc, eth_sqr_min, eth_crl_loc, eth_crl_min, val_sqr_loc,val_sqr_min,val_crl_loc, val_crl_min) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"ethnic seg." = c("eth_sqr_loc","eth_sqr_min","eth_crl_loc","eth_crl_min"), "value seg." = c("val_sqr_loc","val_sqr_min","val_crl_loc", "val_crl_min")), "ethnic seg."), `group` = fct_relevel(fct_collapse(subgroup, "liberal" = c("eth_crl_loc","eth_crl_min","val_crl_loc", "val_crl_min"), "conservative" = c("eth_sqr_loc","eth_sqr_min","val_sqr_loc","val_sqr_min")), "liberal"), 
  `ethnia` = fct_relevel(fct_collapse(subgroup, "Locals:80% ethnic population | 50% liberal" = c("eth_sqr_loc","eth_crl_loc","val_sqr_loc","val_crl_loc"), "Migrants: 20% ethnic population | 50% liberal" = c("eth_sqr_min","eth_crl_min","val_sqr_min","val_crl_min")),"Locals:80% ethnic population | 50% liberal" ))  %>%

  ggplot( aes(x = dominant_locals, y = Segra, color = `segregation`, shape = `group`)) + geom_line() + geom_point(size = 3) +

  scale_x_discrete(limits= seq(0,20 ,by = 1)) +

scale_y_continuous(limits=c(0,1), breaks = c(0,0.2,0.5,0.8,1)) +
  geom_vline(xintercept = c(1,5,10,20), color = "red") +
    geom_hline(yintercept = c(0.5), color = "red", linetype = 2) +
      geom_hline(yintercept = c(0.8), color = "purple", linetype = 5) +
      geom_hline(yintercept = c(0.2), color = "purple", linetype = 2) +
  facet_wrap( ~ `ethnia`,
             nrow =2 , dir = "v")  +

 scale_color_manual(values = c("purple","dark green"), guide = guide_legend(title= "")) + # ,nrow=2, byrow = TRUE)) +
 scale_shape_manual(values = c("circle","square"), guide = guide_legend(title= "")) + #,nrow=2, byrow = TRUE)) + 
   ylab("Segregation") +   
  xlab("ß Dominat Locals\n ß secondary all agents:0") + 
# guides(color = FALSE, shape = FALSE) +
  ggtitle(paste0("ß dominant migrants: ", dfm$dominant_migrants)) +
  theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(),legend.text = element_text(size = 12),
                     # axis.title.y = (element_text(size = 12)), #     
                     #  axis.title.x = (element_text(size = 12)), #   element_blank(),

                     axis.title.y = element_blank(),
                      axis.title.x = element_blank(),
                      axis.text.x = (element_text(size = 11)),
                      axis.text.y =  (element_text(size = 11)),
                      plot.title=element_text(hjust = 0.5),  
                      legend.margin=margin(0,2,0,0), panel.spacing = unit(0.8, "lines"), 
                      strip.text.x = element_text(size = 15),  strip.text.y = element_text(size = 15),
                      plot.caption = element_text(hjust= 0.5, size = 12)) +
theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))

ggsave(name_maj,plot = last_plot(),
  device = NULL,
  path = NULL,
  scale = 1,
  width = 5.5,
  height = 5,
 # units = c("in", "cm", "mm"),
  dpi = 300,
  limitsize = TRUE)

```

```{r asym_dom_maj_dislib, fig.pos="H",include=TRUE,fig.cap="Sensitivity assymetry majority locals, effect liberal migrants distribution", echo=FALSE}

# mig_0 <- dataset_maj  %>% filter(ID == "maj") %>% filter(circle_orange == 50) %>% filter(dominant_migrants == 0) 
mig_5 <- dataset_maj  %>% filter(ID == "maj") %>% filter(circle_orange == 20 | circle_orange == 50 |circle_orange == 80) %>% filter(dominant_migrants == 5) 
mig_10 <- dataset_maj  %>% filter(ID == "maj") %>% filter(circle_orange == 20 | circle_orange == 50 |circle_orange == 80) %>% filter(dominant_migrants == 10)

dfm <- mig_5
name_maj <- paste0("mig_5","_dislib.jpg")

dfm %>% gather(key = subgroup, value = Segra, eth_sqr_loc, eth_sqr_min, eth_crl_loc, eth_crl_min, val_sqr_loc,val_sqr_min,val_crl_loc, val_crl_min) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"ethnic seg." = c("eth_sqr_loc","eth_sqr_min","eth_crl_loc","eth_crl_min"), "value seg." = c("val_sqr_loc","val_sqr_min","val_crl_loc", "val_crl_min")), "ethnic seg."),`group` = fct_relevel(fct_collapse(subgroup, "liberal" = c("eth_crl_loc","eth_crl_min","val_crl_loc", "val_crl_min"), "conservative" = c("eth_sqr_loc","eth_sqr_min","val_sqr_loc","val_sqr_min")), "liberal"), `ethnia` = fct_relevel(fct_collapse(subgroup, "Locals:80% ethnic\n 50% liberal" = c("eth_sqr_loc","eth_crl_loc","val_sqr_loc","val_crl_loc"), "Migrants: 20% ethnic" = c("eth_sqr_min","eth_crl_min","val_sqr_min","val_crl_min")),"Locals:80% ethnic\n 50% liberal" ))  %>%

  ggplot( aes(x = dominant_locals, y = Segra, color = `segregation`, shape = `group`)) + geom_line() + geom_point(size = 3) +

  scale_x_discrete(limits= seq(0,20 ,by = 1)) +

scale_y_continuous(limits=c(0,1), breaks = c(0,0.2,0.5,0.8,1)) +
  geom_vline(xintercept = c(1,5,10,20), color = "red") +
    geom_hline(yintercept = c(0.5), color = "red", linetype = 2) +
      geom_hline(yintercept = c(0.8), color = "purple", linetype = 5) +
      geom_hline(yintercept = c(0.2), color = "purple", linetype = 2) +
  facet_grid( `ethnia` ~ circle_orange, labeller = labeller(circle_orange = circle_orange_labs)) + 
 scale_color_manual(values = c("purple","dark green"), guide = guide_legend(title= "")) + # ,nrow=2, byrow = TRUE)) +
 scale_shape_manual(values = c("circle","square"), guide = guide_legend(title= "")) + #,nrow=2, byrow = TRUE)) + 
   ylab("Segregation") +   
  xlab("ß Dominat Locals\n ß secondary all agents:0") + 
# guides(color = FALSE, shape = FALSE) +
  ggtitle(paste0("ß dominant migrants: ", dfm$dominant_migrants)) +
  theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(),legend.text = element_text(size = 12),
                      axis.title.y = (element_text(size = 12)), #     
                      axis.title.x = (element_text(size = 12)), #   element_blank(),

                    # axis.title.y = element_blank(),
                    #   axis.title.x = element_blank(),
                      axis.text.x = (element_text(size = 11)),
                      axis.text.y =  (element_text(size = 11)),
                      plot.title=element_text(hjust = 0.5),  
                      legend.margin=margin(0,2,0,0), panel.spacing = unit(0.8, "lines"), 
                      strip.text.x = element_text(size = 15),  strip.text.y = element_text(size = 15),
                      plot.caption = element_text(hjust= 0.5, size = 12)) +
theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))

ggsave(name_maj, plot = last_plot(),
  device = NULL,
  path = NULL,
  scale = 1.5,
  width = 8,
  height = 4,
 # units = c("in", "cm", "mm"),
  dpi = 300,
  limitsize = TRUE)

```

# Increase in ethnnic liberal

```{r libethn database, fig.width= 7,fig.height= 6, fig.pos="H",include=TRUE,fig.cap="Increase in  ethnic liberal", echo=FALSE}

hc_hc <- read.csv("maj/maj_min_20-20-table.csv", sep = ",", skip = 6)
names(hc_hc) <- pull(read.csv("maj/leg_maj_sens.csv"))
ID <- rep("hc_hc", length(hc_hc$run))
hc_hc <- cbind(ID,hc_hc)

hc_lc <- read.csv("maj/maj_min_20-5-table.csv", sep = ",", skip = 6)
names(hc_lc) <- pull(read.csv("maj/leg_maj_sens.csv"))
ID <- rep("hc_lc", length(hc_lc$run))
hc_lc <- cbind(ID,hc_lc)

lc_hc <- read.csv("maj/maj_min_5-20-table.csv", sep = ",", skip = 6)
names(lc_hc) <- pull(read.csv("maj/leg_maj_sens.csv"))
ID <- rep("lc_hc",length(lc_hc$run))
lc_hc <- cbind(ID,lc_hc)

lc_lc <- read.csv("maj/maj_min_5-5-table.csv", sep = ",", skip = 6)
names(lc_lc) <- pull(read.csv("maj/leg_maj_sens.csv"))
ID <- rep("lc_lc",length(lc_lc$run))
lc_lc <- cbind(ID,lc_lc)

df_eth_loc <- rbind(hc_hc,hc_lc,lc_hc,lc_lc)
#rm(hc_hc,hc_lc,lc_hc,lc_lc)

```

# Final

```{r rand50, fig.width= 8,fig.height= 7, fig.pos="H",include=TRUE,fig.cap="Individual comparison rand 50", echo=FALSE}

eth_min_lib.labs <- c("ß Ethnic liberal migrants: 0", "ß Ethnic liberal migrants: 1", "ß Ethnic liberal migrants: 2","ß Ethnic liberal migrants: 3","ß Ethnic liberal migrants: 4","ß Ethnic liberal migrants: 5","ß Ethnic liberal migrants: 10","ß Ethnic liberal migrants: 15","ß Ethnic liberal migrants: 20")
names(eth_min_lib.labs) <- c("0","1","2","3","4", "5","10","15","20")
eth_loc_lib.labs <- c("ß Ethnic liberal locals: 0", "ß Ethnic liberal locals: 1", "ß Ethnic liberal locals: 2","ß Ethnic liberal locals: 3","ß Ethnic liberal locals: 4","ß Ethnic liberal locals: 5","ß Ethnic liberal locals: 10","ß Ethnic liberal locals: 15","ß Ethnic liberal locals: 20")
names(eth_loc_lib.labs) <-  c("0","1","2","3","4", "5","10","15","20")

# Intermediate randomness Migrants x-axys

 df_eth_loc  %>% filter(ID == "lc_hc") %>% filter(circle_orange == 50)  %>% filter(eth_loc_lib == 0 | eth_loc_lib == 1 | eth_loc_lib == 3 | eth_loc_lib == 5) %>% gather(key = subgroup, value = Segra, eth_sqr_loc, eth_sqr_min, eth_crl_loc, eth_crl_min, val_sqr_loc,val_sqr_min,val_crl_loc, val_crl_min) %>%mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"ethnic seg." = c("eth_sqr_loc","eth_sqr_min","eth_crl_loc","eth_crl_min"), "value seg." = c("val_sqr_loc","val_sqr_min","val_crl_loc", "val_crl_min")), "ethnic seg."), `group` = fct_relevel(fct_collapse(subgroup, "liberal" = c("eth_crl_loc","eth_crl_min","val_crl_loc", "val_crl_min"), "conservative" = c("eth_sqr_loc","eth_sqr_min","val_sqr_loc","val_sqr_min")), "liberal"), 
  `ethnia` = fct_relevel(fct_collapse(subgroup, "Locals:80% ethnic\n 50% liberal" = c("eth_sqr_loc","eth_crl_loc","val_sqr_loc","val_crl_loc"), "Migrants: 20% ethnic\n 50% liberal" = c("eth_sqr_min","eth_crl_min","val_sqr_min","val_crl_min")),"Locals:80% ethnic\n 50% liberal" ))  %>%

  ggplot( aes(x = eth_min_lib, y = Segra, color = `segregation`, shape = `group` )) + geom_line() + geom_point(size = 3) +

  scale_x_discrete(limits= c(0,1,2,3,4,5,10,15,20)) +

  scale_y_continuous(limits=c(0,1), breaks = c(0,0.2,0.5,0.8,1)) +
  geom_vline(xintercept = c(1,5,10,20), color = "red") +
    geom_hline(yintercept = c(0.5), color = "red", linetype = 2) +
      geom_hline(yintercept = c(0.8), color = "purple", linetype = 5) +
      geom_hline(yintercept = c(0.2), color = "purple", linetype = 2) +
  facet_grid(`ethnia` ~ eth_loc_lib, labeller = labeller(eth_loc_lib = eth_loc_lib.labs, circle_orange = circle_orange_labs)) +
               #nrow =2 , dir = "v")  +

 scale_color_manual(values = c("purple","dark green"), guide = guide_legend(title= "")) + # ,nrow=2, byrow = TRUE)) +
 scale_shape_manual(values = c("circle","square"), guide = guide_legend(title= "")) + #,nrow=2, byrow = TRUE)) + 
   ylab("Segregation") +   
  xlab("Ethnic liberal migrants") + 
#  guides(color = FALSE, shape = FALSE) +
ggtitle("ß dominant migrants: 20\nß dominant locals: 5") +
  theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(),legend.text = element_text(size = 12),
                      axis.title.y =   (element_text(size = 12)), # element_blank(),  # 
                      axis.title.x =  (element_text(size = 14)), #   element_blank(),  # 
                      axis.text.x = (element_text(size = 10)),
                      axis.text.y =  (element_text(size = 10)),
                      plot.title=element_text(face="bold", size = 14),   
                      legend.margin=margin(0,0,0,0), panel.spacing = unit(0.8, "lines"), 
                      strip.text.x = element_text(size = 15),  strip.text.y = element_text(size = 15),
                      plot.caption = element_text(hjust= 0.5, size = 12)) +
theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))

ggsave("lc_hc5_min.jpg",last_plot(),
  device = NULL,
  path = NULL,
  scale = 2,
  width = 6,
  height = 3,
 # units = ("in", "cm", "mm"),
  dpi = 300,
  limitsize = TRUE)

# Intermediate randomness Locals x-axys

df_eth_loc  %>% filter(ID == "hc_lc") %>% filter(circle_orange == 50)  %>% filter(eth_min_lib == 0 | eth_min_lib == 1 | eth_min_lib == 3 |   eth_min_lib == 5) %>% gather(key = subgroup, value = Segra, eth_sqr_loc, eth_sqr_min, eth_crl_loc, eth_crl_min, val_sqr_loc,val_sqr_min,val_crl_loc, val_crl_min) %>%mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"ethnic seg." = c("eth_sqr_loc","eth_sqr_min","eth_crl_loc","eth_crl_min"), "value seg." = c("val_sqr_loc","val_sqr_min","val_crl_loc", "val_crl_min")), "ethnic seg."), `group` = fct_relevel(fct_collapse(subgroup, "liberal" = c("eth_crl_loc","eth_crl_min","val_crl_loc", "val_crl_min"), "conservative" = c("eth_sqr_loc","eth_sqr_min","val_sqr_loc","val_sqr_min")), "liberal"), 
  `ethnia` = fct_relevel(fct_collapse(subgroup, "Locals:80% ethnic\n 50% liberal" = c("eth_sqr_loc","eth_crl_loc","val_sqr_loc","val_crl_loc"), "Migrants: 20% ethnic\n 50% liberal" = c("eth_sqr_min","eth_crl_min","val_sqr_min","val_crl_min")),"Locals:80% ethnic\n 50% liberal" ))  %>%

  ggplot( aes(x = eth_loc_lib, y = Segra, color = `segregation`, shape = `group` )) + geom_line() + geom_point(size = 3) +

  scale_x_discrete(limits= c(0,1,2,3,4,5,10,15,20)) +

  scale_y_continuous(limits=c(0,1), breaks = c(0,0.2,0.5,0.8,1)) +
  geom_vline(xintercept = c(1,5,10,20), color = "red") +
    geom_hline(yintercept = c(0.5), color = "red", linetype = 2) +
      geom_hline(yintercept = c(0.8), color = "purple", linetype = 5) +
      geom_hline(yintercept = c(0.2), color = "purple", linetype = 2) +
  facet_grid(`ethnia` ~ eth_min_lib, labeller = labeller(eth_min_lib = eth_min_lib.labs, circle_orange = circle_orange_labs)) +
               #nrow =2 , dir = "v")  +

 scale_color_manual(values = c("purple","dark green"), guide = guide_legend(title= "")) + # ,nrow=2, byrow = TRUE)) +
 scale_shape_manual(values = c("circle","square"), guide = guide_legend(title= "")) + #,nrow=2, byrow = TRUE)) + 
   ylab("Segregation") +   
  xlab("ethnic liberal locals") + 
# guides(color = FALSE, shape = FALSE) +
xlab("Ethnic liberal locals") + 
# guides(color = FALSE, shape = FALSE) +
ggtitle("ß dominant locals: 20\nß dominant migrants: 5") +
  theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(),legend.text = element_text(size = 12),
                      axis.title.y =   (element_text(size = 12)), # element_blank(),  # 
                      axis.title.x =  (element_text(size = 14)), #   element_blank(),  # 
                      axis.text.x = (element_text(size = 10)),
                      axis.text.y =  (element_text(size = 10)),
                      plot.title=element_text(face="bold", size = 14),   
                      legend.margin=margin(0,0,0,0), panel.spacing = unit(0.8, "lines"), 
                      strip.text.x = element_text(size = 15),  strip.text.y = element_text(size = 15),
                      plot.caption = element_text(hjust= 0.5, size = 12)) +
theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))

# 
# comb <- ggarrange(mig,loc, nrow =  2, common.legend = TRUE, legend = "bottom")
# annotate_figure(comb, 
#                # top = text_grob("Dominant ß: 5",  face = "bold", size = 12),
#                left = text_grob("Segregation", rot = 90, size = 12),
#                 bottom = text_grob("ß value conservative both group: 0", hjust = 1, x = 1, size = 12),
#                 )

ggsave("lc_hc5_maj.jpg",last_plot(),
  device = NULL,
  path = NULL,
   scale = 2,
  width = 6,
  height = 3,
 # units = c("in", "cm", "mm"),
  dpi = 300,
  limitsize = TRUE)

```

```{r det50, fig.width= 8,fig.height= 7, fig.pos="H",include=TRUE,fig.cap="Individual comparison determinism beta 20", echo=FALSE}

eth_min_lib.labs <- c("ß Ethnic liberal migrants: 0", "ß Ethnic liberal migrants: 1", "ß Ethnic liberal migrants: 2","ß Ethnic liberal migrants: 3","ß Ethnic liberal migrants: 4","ß Ethnic liberal migrants: 5","ß Ethnic liberal migrants: 10","ß Ethnic liberal migrants: 15","ß Ethnic liberal migrants: 20")
names(eth_min_lib.labs) <- c("0","1","2","3","4", "5","10","15","20")
eth_loc_lib.labs <- c("ß Ethnic liberal locals: 0", "ß Ethnic liberal locals: 1", "ß Ethnic liberal locals: 2","ß Ethnic liberal locals: 3","ß Ethnic liberal locals: 4","ß Ethnic liberal locals: 5","ß Ethnic liberal locals: 10","ß Ethnic liberal locals: 15","ß Ethnic liberal locals: 20")
names(eth_loc_lib.labs) <-  c("0","1","2","3","4", "5","10","15","20")

# Intermediate randomness Migrants x-axys

 df_eth_loc  %>% filter(ID == "hc_hc") %>% filter(circle_orange == 50)  %>% filter(eth_loc_lib == 0 | eth_loc_lib == 5 | eth_loc_lib == 10 | eth_loc_lib == 20) %>% gather(key = subgroup, value = Segra, eth_sqr_loc, eth_sqr_min, eth_crl_loc, eth_crl_min, val_sqr_loc,val_sqr_min,val_crl_loc, val_crl_min) %>%mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"ethnic seg." = c("eth_sqr_loc","eth_sqr_min","eth_crl_loc","eth_crl_min"), "value seg." = c("val_sqr_loc","val_sqr_min","val_crl_loc", "val_crl_min")), "ethnic seg."), `group` = fct_relevel(fct_collapse(subgroup, "liberal" = c("eth_crl_loc","eth_crl_min","val_crl_loc", "val_crl_min"), "conservative" = c("eth_sqr_loc","eth_sqr_min","val_sqr_loc","val_sqr_min")), "liberal"), 
  `ethnia` = fct_relevel(fct_collapse(subgroup, "Locals:80% ethnic\n 50% liberal" = c("eth_sqr_loc","eth_crl_loc","val_sqr_loc","val_crl_loc"), "Migrants: 20% ethnic\n 50% liberal" = c("eth_sqr_min","eth_crl_min","val_sqr_min","val_crl_min")),"Locals:80% ethnic\n 50% liberal" ))  %>%

  ggplot( aes(x = eth_min_lib, y = Segra, color = `segregation`, shape = `group` )) + geom_line() + geom_point(size = 3) +

  scale_x_discrete(limits= c(0,1,2,3,4,5,10,15,20)) +

  scale_y_continuous(limits=c(0,1), breaks = c(0,0.2,0.5,0.8,1)) +
  geom_vline(xintercept = c(1,5,10,20), color = "red") +
    geom_hline(yintercept = c(0.5), color = "red", linetype = 2) +
      geom_hline(yintercept = c(0.8), color = "purple", linetype = 5) +
      geom_hline(yintercept = c(0.2), color = "purple", linetype = 2) +
  facet_grid(`ethnia` ~ eth_loc_lib, labeller = labeller(eth_loc_lib = eth_loc_lib.labs, circle_orange = circle_orange_labs)) +
               #nrow =2 , dir = "v")  +

 scale_color_manual(values = c("purple","dark green"), guide = guide_legend(title= "")) + # ,nrow=2, byrow = TRUE)) +
 scale_shape_manual(values = c("circle","square"), guide = guide_legend(title= "")) + #,nrow=2, byrow = TRUE)) + 
   ylab("Segregation") +   
  xlab("Ethnic liberal migrants") + 
# guides(color = FALSE, shape = FALSE) +
ggtitle("ß dominant migrants: 20\nß dominant locals: 20") +
  theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(),legend.text = element_text(size = 12),
                      axis.title.y =   (element_text(size = 12)), # element_blank(),  # 
                      axis.title.x =  (element_text(size = 14)), #   element_blank(),  # 
                      axis.text.x = (element_text(size = 10)),
                      axis.text.y =  (element_text(size = 10)),
                      plot.title=element_text(face="bold", size = 14),   
                      legend.margin=margin(0,0,0,0), panel.spacing = unit(0.8, "lines"), 
                      strip.text.x = element_text(size = 15),  strip.text.y = element_text(size = 15),
                      plot.caption = element_text(hjust= 0.5, size = 12)) +
theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))

ggsave("hc_hc5_min.jpg",last_plot(),
  device = NULL,
  path = NULL,
  scale = 2,
  width = 6,
  height = 3,
 # units = ("in", "cm", "mm"),
  dpi = 300,
  limitsize = TRUE)

# Intermediate randomness Locals x-axys

df_eth_loc  %>% filter(ID == "hc_hc") %>% filter(circle_orange == 50)  %>%  filter(eth_min_lib == 0 | eth_min_lib == 5 | eth_min_lib == 10 | eth_min_lib == 20)  %>% gather(key = subgroup, value = Segra, eth_sqr_loc, eth_sqr_min, eth_crl_loc, eth_crl_min, val_sqr_loc,val_sqr_min,val_crl_loc, val_crl_min) %>%mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"ethnic seg." = c("eth_sqr_loc","eth_sqr_min","eth_crl_loc","eth_crl_min"), "value seg." = c("val_sqr_loc","val_sqr_min","val_crl_loc", "val_crl_min")), "ethnic seg."), `group` = fct_relevel(fct_collapse(subgroup, "liberal" = c("eth_crl_loc","eth_crl_min","val_crl_loc", "val_crl_min"), "conservative" = c("eth_sqr_loc","eth_sqr_min","val_sqr_loc","val_sqr_min")), "liberal"), 
  `ethnia` = fct_relevel(fct_collapse(subgroup, "Locals:80% ethnic\n 50% liberal" = c("eth_sqr_loc","eth_crl_loc","val_sqr_loc","val_crl_loc"), "Migrants: 20% ethnic\n 50% liberal" = c("eth_sqr_min","eth_crl_min","val_sqr_min","val_crl_min")),"Locals:80% ethnic\n 50% liberal" ))  %>%

  ggplot( aes(x = eth_loc_lib, y = Segra, color = `segregation`, shape = `group` )) + geom_line() + geom_point(size = 3) +

  scale_x_discrete(limits= c(0,1,2,3,4,5,10,15,20)) +

  scale_y_continuous(limits=c(0,1), breaks = c(0,0.2,0.5,0.8,1)) +
  geom_vline(xintercept = c(1,5,10,20), color = "red") +
    geom_hline(yintercept = c(0.5), color = "red", linetype = 2) +
      geom_hline(yintercept = c(0.8), color = "purple", linetype = 5) +
      geom_hline(yintercept = c(0.2), color = "purple", linetype = 2) +
  facet_grid(`ethnia` ~ eth_min_lib, labeller = labeller(eth_min_lib = eth_min_lib.labs, circle_orange = circle_orange_labs)) +
               #nrow =2 , dir = "v")  +

 scale_color_manual(values = c("purple","dark green"), guide = guide_legend(title= "")) + # ,nrow=2, byrow = TRUE)) +
 scale_shape_manual(values = c("circle","square"), guide = guide_legend(title= "")) + #,nrow=2, byrow = TRUE)) + 
   ylab("Segregation") +   
  xlab("ethnic liberal locals") + 
# guides(color = FALSE, shape = FALSE) +
xlab("Ethnic liberal locals") + 
 guides(color = FALSE, shape = FALSE) +
ggtitle("ß dominant locals: 20\nß dominant migrants: 20") +
  theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(),legend.text = element_text(size = 12),
                      axis.title.y =   (element_text(size = 12)), # element_blank(),  # 
                      axis.title.x =  (element_text(size = 14)), #   element_blank(),  # 
                      axis.text.x = (element_text(size = 10)),
                      axis.text.y =  (element_text(size = 10)),
                      plot.title=element_text(face="bold", size = 14),   
                      legend.margin=margin(0,0,0,0), panel.spacing = unit(0.8, "lines"), 
                      strip.text.x = element_text(size = 15),  strip.text.y = element_text(size = 15),
                      plot.caption = element_text(hjust= 0.5, size = 12)) +
theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))

ggsave("hc_hc5_maj.jpg",last_plot(),
  device = NULL,
  path = NULL,
   scale = 2,
  width = 6,
  height = 3,
 # units = c("in", "cm", "mm"),
  dpi = 300,
  limitsize = TRUE)

#######
#######

# Intermediate randomness Migrants x-axys

 df_eth_loc  %>% filter(ID == "lc_lc") %>% filter(circle_orange == 50)  %>% filter(eth_loc_lib == 0 | eth_loc_lib == 1 | eth_loc_lib == 3 | eth_loc_lib == 5) %>% gather(key = subgroup, value = Segra, eth_sqr_loc, eth_sqr_min, eth_crl_loc, eth_crl_min, val_sqr_loc,val_sqr_min,val_crl_loc, val_crl_min) %>%mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"ethnic seg." = c("eth_sqr_loc","eth_sqr_min","eth_crl_loc","eth_crl_min"), "value seg." = c("val_sqr_loc","val_sqr_min","val_crl_loc", "val_crl_min")), "ethnic seg."), `group` = fct_relevel(fct_collapse(subgroup, "liberal" = c("eth_crl_loc","eth_crl_min","val_crl_loc", "val_crl_min"), "conservative" = c("eth_sqr_loc","eth_sqr_min","val_sqr_loc","val_sqr_min")), "liberal"), 
  `ethnia` = fct_relevel(fct_collapse(subgroup, "Locals:80% ethnic\n 50% liberal" = c("eth_sqr_loc","eth_crl_loc","val_sqr_loc","val_crl_loc"), "Migrants: 20% ethnic\n 50% liberal" = c("eth_sqr_min","eth_crl_min","val_sqr_min","val_crl_min")),"Locals:80% ethnic\n 50% liberal" ))  %>%

  ggplot( aes(x = eth_min_lib, y = Segra, color = `segregation`, shape = `group` )) + geom_line() + geom_point(size = 3) +

  scale_x_discrete(limits= c(0,1,2,3,4,5)) +

  scale_y_continuous(limits=c(0,1), breaks = c(0,0.2,0.5,0.8,1)) +
  geom_vline(xintercept = c(1,5), color = "red") +
    geom_hline(yintercept = c(0.5), color = "red", linetype = 2) +
      geom_hline(yintercept = c(0.8), color = "purple", linetype = 5) +
      geom_hline(yintercept = c(0.2), color = "purple", linetype = 2) +
  facet_grid(`ethnia` ~ eth_loc_lib, labeller = labeller(eth_loc_lib = eth_loc_lib.labs, circle_orange = circle_orange_labs)) +
               #nrow =2 , dir = "v")  +

 scale_color_manual(values = c("purple","dark green"), guide = guide_legend(title= "")) + # ,nrow=2, byrow = TRUE)) +
 scale_shape_manual(values = c("circle","square"), guide = guide_legend(title= "")) + #,nrow=2, byrow = TRUE)) + 
   ylab("Segregation") +   
  xlab("Ethnic liberal migrants") + 
# guides(color = FALSE, shape = FALSE) +
ggtitle("ß dominant migrants: 5\nß dominant locals: 5") +
  theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(),legend.text = element_text(size = 12),
                      axis.title.y =   (element_text(size = 12)), # element_blank(),  # 
                      axis.title.x =  (element_text(size = 14)), #   element_blank(),  # 
                      axis.text.x = (element_text(size = 10)),
                      axis.text.y =  (element_text(size = 10)),
                      plot.title=element_text(face="bold", size = 14),   
                      legend.margin=margin(0,0,0,0), panel.spacing = unit(0.8, "lines"), 
                      strip.text.x = element_text(size = 15),  strip.text.y = element_text(size = 15),
                      plot.caption = element_text(hjust= 0.5, size = 12)) +
theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))

ggsave("lc_lc5_min.jpg",last_plot(),
  device = NULL,
  path = NULL,
  scale = 2,
  width = 6,
  height = 3,
 # units = ("in", "cm", "mm"),
  dpi = 300,
  limitsize = TRUE)

# Intermediate randomness Locals x-axys

df_eth_loc  %>% filter(ID == "lc_lc") %>% filter(circle_orange == 50)  %>%  filter(eth_min_lib == 0 | eth_min_lib == 1 | eth_min_lib == 3 | eth_min_lib == 5)  %>% gather(key = subgroup, value = Segra, eth_sqr_loc, eth_sqr_min, eth_crl_loc, eth_crl_min, val_sqr_loc,val_sqr_min,val_crl_loc, val_crl_min) %>%mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"ethnic seg." = c("eth_sqr_loc","eth_sqr_min","eth_crl_loc","eth_crl_min"), "value seg." = c("val_sqr_loc","val_sqr_min","val_crl_loc", "val_crl_min")), "ethnic seg."), `group` = fct_relevel(fct_collapse(subgroup, "liberal" = c("eth_crl_loc","eth_crl_min","val_crl_loc", "val_crl_min"), "conservative" = c("eth_sqr_loc","eth_sqr_min","val_sqr_loc","val_sqr_min")), "liberal"), 
  `ethnia` = fct_relevel(fct_collapse(subgroup, "Locals:80% ethnic\n 50% liberal" = c("eth_sqr_loc","eth_crl_loc","val_sqr_loc","val_crl_loc"), "Migrants: 20% ethnic\n 50% liberal" = c("eth_sqr_min","eth_crl_min","val_sqr_min","val_crl_min")),"Locals:80% ethnic\n 50% liberal" ))  %>%

  ggplot( aes(x = eth_loc_lib, y = Segra, color = `segregation`, shape = `group` )) + geom_line() + geom_point(size = 3) +

  scale_x_discrete(limits= c(0,1,2,3,4,5)) +

  scale_y_continuous(limits=c(0,1), breaks = c(0,0.2,0.5,0.8,1)) +
  geom_vline(xintercept = c(1,5), color = "red") +
    geom_hline(yintercept = c(0.5), color = "red", linetype = 2) +
      geom_hline(yintercept = c(0.8), color = "purple", linetype = 5) +
      geom_hline(yintercept = c(0.2), color = "purple", linetype = 2) +
  facet_grid(`ethnia` ~ eth_min_lib, labeller = labeller(eth_min_lib = eth_min_lib.labs, circle_orange = circle_orange_labs)) +
               #nrow =2 , dir = "v")  +

 scale_color_manual(values = c("purple","dark green"), guide = guide_legend(title= "")) + # ,nrow=2, byrow = TRUE)) +
 scale_shape_manual(values = c("circle","square"), guide = guide_legend(title= "")) + #,nrow=2, byrow = TRUE)) + 
   ylab("Segregation") +   
  xlab("ethnic liberal locals") + 
# guides(color = FALSE, shape = FALSE) +
xlab("Ethnic liberal locals") + 
# guides(color = FALSE, shape = FALSE) +
ggtitle("ß dominant migrants: 5\nß dominant locals: 5") +
  theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(),legend.text = element_text(size = 12),
                      axis.title.y =   (element_text(size = 12)), # element_blank(),  # 
                      axis.title.x =  (element_text(size = 14)), #   element_blank(),  # 
                      axis.text.x = (element_text(size = 10)),
                      axis.text.y =  (element_text(size = 10)),
                      plot.title=element_text(face="bold", size = 14),   
                      legend.margin=margin(0,0,0,0), panel.spacing = unit(0.8, "lines"), 
                      strip.text.x = element_text(size = 15),  strip.text.y = element_text(size = 15),
                      plot.caption = element_text(hjust= 0.5, size = 12)) +
theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))

ggsave("lc_lc5_maj.jpg",last_plot(),
  device = NULL,
  path = NULL,
   scale = 2,
  width = 6,
  height = 3,
 # units = c("in", "cm", "mm"),
  dpi = 300,
  limitsize = TRUE)

##### RANDOM dislib

 df_eth_loc  %>% filter(ID == "lc_lc")   %>% filter(eth_loc_lib == 5) %>% gather(key = subgroup, value = Segra, eth_sqr_loc, eth_sqr_min, eth_crl_loc, eth_crl_min, val_sqr_loc,val_sqr_min,val_crl_loc, val_crl_min) %>%mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"ethnic seg." = c("eth_sqr_loc","eth_sqr_min","eth_crl_loc","eth_crl_min"), "value seg." = c("val_sqr_loc","val_sqr_min","val_crl_loc", "val_crl_min")), "ethnic seg."), `group` = fct_relevel(fct_collapse(subgroup, "liberal" = c("eth_crl_loc","eth_crl_min","val_crl_loc", "val_crl_min"), "conservative" = c("eth_sqr_loc","eth_sqr_min","val_sqr_loc","val_sqr_min")), "liberal"), 
  `ethnia` = fct_relevel(fct_collapse(subgroup, "Locals:80% ethnic\n 50% liberal" = c("eth_sqr_loc","eth_crl_loc","val_sqr_loc","val_crl_loc"), "Migrants: 20% ethnic" = c("eth_sqr_min","eth_crl_min","val_sqr_min","val_crl_min")),"Locals:80% ethnic\n 50% liberal" ))  %>%

  ggplot( aes(x = eth_min_lib, y = Segra, color = `segregation`, shape = `group` )) + geom_line() + geom_point(size = 3) +

  scale_x_discrete(limits= c(0,1,2,3,4,5)) +

  scale_y_continuous(limits=c(0,1), breaks = c(0,0.2,0.5,0.8,1)) +
  geom_vline(xintercept = c(1,5), color = "red") +
    geom_hline(yintercept = c(0.5), color = "red", linetype = 2) +
      geom_hline(yintercept = c(0.8), color = "purple", linetype = 5) +
      geom_hline(yintercept = c(0.2), color = "purple", linetype = 2) +
  facet_grid(`ethnia` ~ circle_orange, labeller = labeller(eth_loc_lib = eth_loc_lib.labs, circle_orange = circle_orange_labs)) +
               #nrow =2 , dir = "v")  +

 scale_color_manual(values = c("purple","dark green"), guide = guide_legend(title= "")) + # ,nrow=2, byrow = TRUE)) +
 scale_shape_manual(values = c("circle","square"), guide = guide_legend(title= "")) + #,nrow=2, byrow = TRUE)) + 
 ylab("Segregation") +   
 xlab("ß ethnic liberal migrants") + 
# guides(color = FALSE, shape = FALSE) +
ggtitle("ß dominant migrants: 5; ß dominant locals: 5\nß ethnic liberal locals: 5") +
  theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(),legend.text = element_text(size = 12),
                      axis.title.y =   (element_text(size = 12)), # element_blank(),  # 
                      axis.title.x =  (element_text(size = 14)), #   element_blank(),  # 
                      axis.text.x = (element_text(size = 10)),
                      axis.text.y =  (element_text(size = 10)),
                      plot.title=element_text(face="bold", size = 14),   
                      legend.margin=margin(0,0,0,0), panel.spacing = unit(0.8, "lines"), 
                      strip.text.x = element_text(size = 15),  strip.text.y = element_text(size = 15),
                      plot.caption = element_text(hjust= 0.5, size = 12)) +
theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))

ggsave("lc_lc_dis_min.jpg",last_plot(),
  device = NULL,
  path = NULL,
   scale = 2,
  width = 5,
  height = 3,
 # units = c("in", "cm", "mm"),
  dpi = 300,
  limitsize = TRUE)

# maj

df_eth_loc  %>% filter(ID == "lc_lc")   %>% filter(eth_min_lib == 5) %>% gather(key = subgroup, value = Segra, eth_sqr_loc, eth_sqr_min, eth_crl_loc, eth_crl_min, val_sqr_loc,val_sqr_min,val_crl_loc, val_crl_min) %>%mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"ethnic seg." = c("eth_sqr_loc","eth_sqr_min","eth_crl_loc","eth_crl_min"), "value seg." = c("val_sqr_loc","val_sqr_min","val_crl_loc", "val_crl_min")), "ethnic seg."), `group` = fct_relevel(fct_collapse(subgroup, "liberal" = c("eth_crl_loc","eth_crl_min","val_crl_loc", "val_crl_min"), "conservative" = c("eth_sqr_loc","eth_sqr_min","val_sqr_loc","val_sqr_min")), "liberal"), 
  `ethnia` = fct_relevel(fct_collapse(subgroup, "Locals:80% ethnic\n 50% liberal" = c("eth_sqr_loc","eth_crl_loc","val_sqr_loc","val_crl_loc"), "Migrants: 20% ethnic" = c("eth_sqr_min","eth_crl_min","val_sqr_min","val_crl_min")),"Locals:80% ethnic\n 50% liberal" ))  %>%

  ggplot( aes(x = eth_loc_lib, y = Segra, color = `segregation`, shape = `group` )) + geom_line() + geom_point(size = 3) +

  scale_x_discrete(limits= c(0,1,2,3,4,5,10,15,20)) +

  scale_y_continuous(limits=c(0,1), breaks = c(0,0.2,0.5,0.8,1)) +
  geom_vline(xintercept = c(1,5,10,20), color = "red") +
    geom_hline(yintercept = c(0.5), color = "red", linetype = 2) +
      geom_hline(yintercept = c(0.8), color = "purple", linetype = 5) +
      geom_hline(yintercept = c(0.2), color = "purple", linetype = 2) +
  facet_grid(`ethnia` ~ circle_orange, labeller = labeller(eth_loc_lib = eth_loc_lib.labs, circle_orange = circle_orange_labs)) +
               #nrow =2 , dir = "v")  +

 scale_color_manual(values = c("purple","dark green"), guide = guide_legend(title= "")) + # ,nrow=2, byrow = TRUE)) +
 scale_shape_manual(values = c("circle","square"), guide = guide_legend(title= "")) + #,nrow=2, byrow = TRUE)) + 
 ylab("Segregation") +   
 xlab("ß ethnic liberal locals") + 
# guides(color = FALSE, shape = FALSE) +
ggtitle("ß dominant locals: 5; ß dominant migrants: 5\nß ethnic liberal migrants: 5") +
  theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(),legend.text = element_text(size = 12),
                      axis.title.y =   (element_text(size = 12)), # element_blank(),  # 
                      axis.title.x =  (element_text(size = 14)), #   element_blank(),  # 
                      axis.text.x = (element_text(size = 10)),
                      axis.text.y =  (element_text(size = 10)),
                      plot.title=element_text(face="bold", size = 14),   
                      legend.margin=margin(0,0,0,0), panel.spacing = unit(0.8, "lines"), 
                      strip.text.x = element_text(size = 15),  strip.text.y = element_text(size = 15),
                      plot.caption = element_text(hjust= 0.5, size = 12)) +
theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))

ggsave("lc_lc_dis_maj.jpg",last_plot(),
  device = NULL,
  path = NULL,
   scale = 2,
  width = 5,
  height = 3,
 # units = c("in", "cm", "mm"),
  dpi = 300,
  limitsize = TRUE)

```

```{r comparison baseline asym, fig.width= 8,fig.height= 7, fig.pos="H",include=TRUE,fig.cap="50% lib migrant", echo=FALSE}

eth_min_lib.labs <- c("ß Ethnic liberal migrants: 0", "ß Ethnic liberal migrants: 1", "ß Ethnic liberal migrants: 2","ß Ethnic liberal migrants: 3","ß Ethnic liberal migrants: 4","ß Ethnic liberal migrants: 5","ß Ethnic liberal migrants: 10","ß Ethnic liberal migrants: 15","ß Ethnic liberal migrants: 20")
names(eth_min_lib.labs) <- c("0","1","2","3","4", "5","10","15","20")
eth_loc_lib.labs <- c("ß Ethnic liberal locals: 0", "ß Ethnic liberal locals: 1", "ß Ethnic liberal locals: 2","ß Ethnic liberal locals: 3","ß Ethnic liberal locals: 4","ß Ethnic liberal locals: 5","ß Ethnic liberal locals: 10","ß Ethnic liberal locals: 15","ß Ethnic liberal locals: 20")
names(eth_loc_lib.labs) <-  c("0","1","2","3","4", "5","10","15","20")

lc_hc_dis_min <-  df_eth_loc  %>% filter(ID == "hc_lc")   %>% filter(eth_loc_lib == 20) %>% gather(key = subgroup, value = Segra, eth_sqr_loc, eth_sqr_min, eth_crl_loc, eth_crl_min, val_sqr_loc,val_sqr_min,val_crl_loc, val_crl_min) %>%mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"ethnic seg." = c("eth_sqr_loc","eth_sqr_min","eth_crl_loc","eth_crl_min"), "value seg." = c("val_sqr_loc","val_sqr_min","val_crl_loc", "val_crl_min")), "ethnic seg."), `group` = fct_relevel(fct_collapse(subgroup, "liberal" = c("eth_crl_loc","eth_crl_min","val_crl_loc", "val_crl_min"), "conservative" = c("eth_sqr_loc","eth_sqr_min","val_sqr_loc","val_sqr_min")), "liberal"), 
  `ethnia` = fct_relevel(fct_collapse(subgroup, "Locals:80% ethnic\n 50% liberal" = c("eth_sqr_loc","eth_crl_loc","val_sqr_loc","val_crl_loc"), "Migrants: 20% ethnic" = c("eth_sqr_min","eth_crl_min","val_sqr_min","val_crl_min")),"Locals:80% ethnic\n 50% liberal" ))  %>%

  ggplot( aes(x = eth_min_lib, y = Segra, color = `segregation`, shape = `group` )) + geom_line() + geom_point(size = 3) +

  scale_x_discrete(limits= c(0,1,2,3,4,5,10,15,20)) +

  scale_y_continuous(limits=c(0,1), breaks = c(0,0.2,0.5,0.8,1)) +
  geom_vline(xintercept = c(1,5,10,20), color = "red") +
    geom_hline(yintercept = c(0.5), color = "red", linetype = 2) +
      geom_hline(yintercept = c(0.8), color = "purple", linetype = 5) +
      geom_hline(yintercept = c(0.2), color = "purple", linetype = 2) +
  facet_grid(`ethnia` ~ circle_orange, labeller = labeller(eth_loc_lib = eth_loc_lib.labs, circle_orange = circle_orange_labs)) +
               #nrow =2 , dir = "v")  +

 scale_color_manual(values = c("purple","dark green"), guide = guide_legend(title= "")) + # ,nrow=2, byrow = TRUE)) +
 scale_shape_manual(values = c("circle","square"), guide = guide_legend(title= "")) + #,nrow=2, byrow = TRUE)) + 
 ylab("Segregation") +   
 xlab("ß ethnic liberal migrants") + 
# guides(color = FALSE, shape = FALSE) +
ggtitle("ß dominant migrants: 20; ß dominant locals: 5\nß ethnic liberal locals: 5") +
  theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(),legend.text = element_text(size = 12),
                      axis.title.y =   (element_text(size = 12)), # element_blank(),  # 
                      axis.title.x =  (element_text(size = 14)), #   element_blank(),  # 
                      axis.text.x = (element_text(size = 10)),
                      axis.text.y =  (element_text(size = 10)),
                      plot.title=element_text(face="bold", size = 14),   
                      legend.margin=margin(0,0,0,0), panel.spacing = unit(0.8, "lines"), 
                      strip.text.x = element_text(size = 15),  strip.text.y = element_text(size = 15),
                      plot.caption = element_text(hjust= 0.5, size = 12)) +
theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))

ggsave("lc_hc_dis_min.jpg",lc_hc_dis_min,
  device = NULL,
  path = NULL,
   scale = 2,
  width = 5,
  height = 3,
 # units = c("in", "cm", "mm"),
  dpi = 300,
  limitsize = TRUE)

hc_lc_dis_maj <-  df_eth_loc  %>% filter(ID == "hc_lc")   %>% filter(eth_min_lib == 5) %>% gather(key = subgroup, value = Segra, eth_sqr_loc, eth_sqr_min, eth_crl_loc, eth_crl_min, val_sqr_loc,val_sqr_min,val_crl_loc, val_crl_min) %>%mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"ethnic seg." = c("eth_sqr_loc","eth_sqr_min","eth_crl_loc","eth_crl_min"), "value seg." = c("val_sqr_loc","val_sqr_min","val_crl_loc", "val_crl_min")), "ethnic seg."), `group` = fct_relevel(fct_collapse(subgroup, "liberal" = c("eth_crl_loc","eth_crl_min","val_crl_loc", "val_crl_min"), "conservative" = c("eth_sqr_loc","eth_sqr_min","val_sqr_loc","val_sqr_min")), "liberal"), 
  `ethnia` = fct_relevel(fct_collapse(subgroup, "Locals:80% ethnic\n 50% liberal" = c("eth_sqr_loc","eth_crl_loc","val_sqr_loc","val_crl_loc"), "Migrants: 20% ethnic" = c("eth_sqr_min","eth_crl_min","val_sqr_min","val_crl_min")),"Locals:80% ethnic\n 50% liberal" ))  %>%

  ggplot( aes(x = eth_loc_lib, y = Segra, color = `segregation`, shape = `group` )) + geom_line() + geom_point(size = 3) +

  scale_x_discrete(limits= c(0,1,2,3,4,5,10,15,20)) +

  scale_y_continuous(limits=c(0,1), breaks = c(0,0.2,0.5,0.8,1)) +
  geom_vline(xintercept = c(1,5,10,20), color = "red") +
    geom_hline(yintercept = c(0.5), color = "red", linetype = 2) +
      geom_hline(yintercept = c(0.8), color = "purple", linetype = 5) +
      geom_hline(yintercept = c(0.2), color = "purple", linetype = 2) +
  facet_grid(`ethnia` ~ circle_orange, labeller = labeller(eth_loc_lib = eth_loc_lib.labs, circle_orange = circle_orange_labs)) +
               #nrow =2 , dir = "v")  +

 scale_color_manual(values = c("purple","dark green"), guide = guide_legend(title= "")) + # ,nrow=2, byrow = TRUE)) +
 scale_shape_manual(values = c("circle","square"), guide = guide_legend(title= "")) + #,nrow=2, byrow = TRUE)) + 
 ylab("Segregation") +   
 xlab("ß ethnic liberal locals") + 
# guides(color = FALSE, shape = FALSE) +
ggtitle("ß dominant locals: 20; ß dominant migrants: 5\nß ethnic liberal migrants: 5") +
  theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(),legend.text = element_text(size = 12),
                      axis.title.y =   (element_text(size = 12)), # element_blank(),  # 
                      axis.title.x =  (element_text(size = 14)), #   element_blank(),  # 
                      axis.text.x = (element_text(size = 10)),
                      axis.text.y =  (element_text(size = 10)),
                      plot.title=element_text(face="bold", size = 14),   
                      legend.margin=margin(0,0,0,0), panel.spacing = unit(0.8, "lines"), 
                      strip.text.x = element_text(size = 15),  strip.text.y = element_text(size = 15),
                      plot.caption = element_text(hjust= 0.5, size = 12)) +
theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))

ggsave("hc_lc_dis_maj.jpg",hc_lc_dis_maj,
  device = NULL,
  path = NULL,
   scale = 2,
  width = 5,
  height = 3,
 # units = c("in", "cm", "mm"),
  dpi = 300,
  limitsize = TRUE)

# Determinism

hc_hc_dis_min <-  df_eth_loc  %>% filter(ID == "hc_hc")   %>% filter(eth_loc_lib == 20) %>% gather(key = subgroup, value = Segra, eth_sqr_loc, eth_sqr_min, eth_crl_loc, eth_crl_min, val_sqr_loc,val_sqr_min,val_crl_loc, val_crl_min) %>%mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"ethnic seg." = c("eth_sqr_loc","eth_sqr_min","eth_crl_loc","eth_crl_min"), "value seg." = c("val_sqr_loc","val_sqr_min","val_crl_loc", "val_crl_min")), "ethnic seg."), `group` = fct_relevel(fct_collapse(subgroup, "liberal" = c("eth_crl_loc","eth_crl_min","val_crl_loc", "val_crl_min"), "conservative" = c("eth_sqr_loc","eth_sqr_min","val_sqr_loc","val_sqr_min")), "liberal"), 
  `ethnia` = fct_relevel(fct_collapse(subgroup, "Locals:80% ethnic\n 50% liberal" = c("eth_sqr_loc","eth_crl_loc","val_sqr_loc","val_crl_loc"), "Migrants: 20% ethnic" = c("eth_sqr_min","eth_crl_min","val_sqr_min","val_crl_min")),"Locals:80% ethnic\n 50% liberal" ))  %>%

  ggplot( aes(x = eth_min_lib, y = Segra, color = `segregation`, shape = `group` )) + geom_line() + geom_point(size = 3) +

  scale_x_discrete(limits= c(0,1,2,3,4,5,10,15,20)) +

  scale_y_continuous(limits=c(0,1), breaks = c(0,0.2,0.5,0.8,1)) +
  geom_vline(xintercept = c(1,5,10,20), color = "red") +
    geom_hline(yintercept = c(0.5), color = "red", linetype = 2) +
      geom_hline(yintercept = c(0.8), color = "purple", linetype = 5) +
      geom_hline(yintercept = c(0.2), color = "purple", linetype = 2) +
  facet_grid(`ethnia` ~ circle_orange, labeller = labeller(eth_loc_lib = eth_loc_lib.labs, circle_orange = circle_orange_labs)) +
               #nrow =2 , dir = "v")  +

 scale_color_manual(values = c("purple","dark green"), guide = guide_legend(title= "")) + # ,nrow=2, byrow = TRUE)) +
 scale_shape_manual(values = c("circle","square"), guide = guide_legend(title= "")) + #,nrow=2, byrow = TRUE)) + 
 ylab("Segregation") +   
 xlab("ß ethnic liberal migrants") + 
guides(color = FALSE, shape = FALSE) +
ggtitle("ß dominant migrants: 20; ß dominant locals: 20\nß ethnic liberal locals: 20") +
  theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(),legend.text = element_text(size = 12),
                      axis.title.y =   (element_text(size = 12)), # element_blank(),  # 
                      axis.title.x =  (element_text(size = 14)), #   element_blank(),  # 
                      axis.text.x = (element_text(size = 10)),
                      axis.text.y =  (element_text(size = 10)),
                      plot.title=element_text(face="bold", size = 14),   
                      legend.margin=margin(0,0,0,0), panel.spacing = unit(0.8, "lines"), 
                      strip.text.x = element_text(size = 15),  strip.text.y = element_text(size = 15),
                      plot.caption = element_text(hjust= 0.5, size = 12)) +
theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))

ggsave("hc_hc_dis_min.jpg",hc_hc_dis_min,
  device = NULL,
  path = NULL,
   scale = 2,
  width = 5,
  height = 3,
 # units = c("in", "cm", "mm"),
  dpi = 300,
  limitsize = TRUE)

hc_hc_dis_maj <-  df_eth_loc  %>% filter(ID == "hc_hc")   %>% filter(eth_min_lib == 20) %>% gather(key = subgroup, value = Segra, eth_sqr_loc, eth_sqr_min, eth_crl_loc, eth_crl_min, val_sqr_loc,val_sqr_min,val_crl_loc, val_crl_min) %>%mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"ethnic seg." = c("eth_sqr_loc","eth_sqr_min","eth_crl_loc","eth_crl_min"), "value seg." = c("val_sqr_loc","val_sqr_min","val_crl_loc", "val_crl_min")), "ethnic seg."), `group` = fct_relevel(fct_collapse(subgroup, "liberal" = c("eth_crl_loc","eth_crl_min","val_crl_loc", "val_crl_min"), "conservative" = c("eth_sqr_loc","eth_sqr_min","val_sqr_loc","val_sqr_min")), "liberal"), 
  `ethnia` = fct_relevel(fct_collapse(subgroup, "Locals:80% ethnic\n 50% liberal" = c("eth_sqr_loc","eth_crl_loc","val_sqr_loc","val_crl_loc"), "Migrants: 20% ethnic" = c("eth_sqr_min","eth_crl_min","val_sqr_min","val_crl_min")),"Locals:80% ethnic\n 50% liberal" ))  %>%

  ggplot( aes(x = eth_loc_lib, y = Segra, color = `segregation`, shape = `group` )) + geom_line() + geom_point(size = 3) +

  scale_x_discrete(limits= c(0,1,2,3,4,5,10,15,20)) +

  scale_y_continuous(limits=c(0,1), breaks = c(0,0.2,0.5,0.8,1)) +
  geom_vline(xintercept = c(1,5,10,20), color = "red") +
    geom_hline(yintercept = c(0.5), color = "red", linetype = 2) +
      geom_hline(yintercept = c(0.8), color = "purple", linetype = 5) +
      geom_hline(yintercept = c(0.2), color = "purple", linetype = 2) +
  facet_grid(`ethnia` ~ circle_orange, labeller = labeller(eth_loc_lib = eth_loc_lib.labs, circle_orange = circle_orange_labs)) +
               #nrow =2 , dir = "v")  +

 scale_color_manual(values = c("purple","dark green"), guide = guide_legend(title= "")) + # ,nrow=2, byrow = TRUE)) +
 scale_shape_manual(values = c("circle","square"), guide = guide_legend(title= "")) + #,nrow=2, byrow = TRUE)) + 
 ylab("Segregation") +   
 xlab("ß ethnic liberal locals") + 
# guides(color = FALSE, shape = FALSE) +
ggtitle("ß dominant locals: 20; ß dominant migrants: 20\nß ethnic liberal migrants: 20") +
  theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(),legend.text = element_text(size = 12),
                      axis.title.y =   (element_text(size = 12)), # element_blank(),  # 
                      axis.title.x =  (element_text(size = 14)), #   element_blank(),  # 
                      axis.text.x = (element_text(size = 10)),
                      axis.text.y =  (element_text(size = 10)),
                      plot.title=element_text(face="bold", size = 14),   
                      legend.margin=margin(0,0,0,0), panel.spacing = unit(0.8, "lines"), 
                      strip.text.x = element_text(size = 15),  strip.text.y = element_text(size = 15),
                      plot.caption = element_text(hjust= 0.5, size = 12)) +
theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))

ggsave("hc_hc_dis_maj.jpg",hc_hc_dis_maj,
  device = NULL,
  path = NULL,
   scale = 2,
  width = 5,
  height = 3,
 # units = c("in", "cm", "mm"),
  dpi = 300,
  limitsize = TRUE)
```

```{r rand20, fig.width= 8,fig.height= 7, fig.pos="H",include=TRUE,fig.cap="Individual comparison rand 20", echo=FALSE}

eth_min_lib.labs <- c("ß Ethnic liberal migrants: 0", "ß Ethnic liberal migrants: 1", "ß Ethnic liberal migrants: 2","ß Ethnic liberal migrants: 3","ß Ethnic liberal migrants: 4","ß Ethnic liberal migrants: 5","ß Ethnic liberal migrants: 10","ß Ethnic liberal migrants: 15","ß Ethnic liberal migrants: 20")
names(eth_min_lib.labs) <- c("0","1","2","3","4", "5","10","15","20")
eth_loc_lib.labs <- c("ß Ethnic liberal locals: 0", "ß Ethnic liberal locals: 1", "ß Ethnic liberal locals: 2","ß Ethnic liberal locals: 3","ß Ethnic liberal locals: 4","ß Ethnic liberal locals: 5","ß Ethnic liberal locals: 10","ß Ethnic liberal locals: 15","ß Ethnic liberal locals: 20")
names(eth_loc_lib.labs) <-  c("0","1","2","3","4", "5","10","15","20")

# Intermediate randomness Migrants x-axys

 df_eth_loc  %>% filter(ID == "lc_hc") %>% filter(circle_orange == 20)  %>% filter(eth_loc_lib == 0 | eth_loc_lib == 1 | eth_loc_lib == 3 | eth_loc_lib == 5) %>% gather(key = subgroup, value = Segra, eth_sqr_loc, eth_sqr_min, eth_crl_loc, eth_crl_min, val_sqr_loc,val_sqr_min,val_crl_loc, val_crl_min) %>%mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"ethnic seg." = c("eth_sqr_loc","eth_sqr_min","eth_crl_loc","eth_crl_min"), "value seg." = c("val_sqr_loc","val_sqr_min","val_crl_loc", "val_crl_min")), "ethnic seg."), `group` = fct_relevel(fct_collapse(subgroup, "liberal" = c("eth_crl_loc","eth_crl_min","val_crl_loc", "val_crl_min"), "conservative" = c("eth_sqr_loc","eth_sqr_min","val_sqr_loc","val_sqr_min")), "liberal"), 
  `ethnia` = fct_relevel(fct_collapse(subgroup, "Locals:80% ethnic\n 50% liberal" = c("eth_sqr_loc","eth_crl_loc","val_sqr_loc","val_crl_loc"), "Migrants: 20% ethnic\n 20% liberal" = c("eth_sqr_min","eth_crl_min","val_sqr_min","val_crl_min")),"Locals:80% ethnic\n 50% liberal" ))  %>%

  ggplot( aes(x = eth_min_lib, y = Segra, color = `segregation`, shape = `group` )) + geom_line() + geom_point(size = 3) +

  scale_x_discrete(limits= c(0,1,2,3,4,5,10,15,20)) +

  scale_y_continuous(limits=c(0,1), breaks = c(0,0.2,0.5,0.8,1)) +
  geom_vline(xintercept = c(1,5,10,20), color = "red") +
    geom_hline(yintercept = c(0.5), color = "red", linetype = 2) +
      geom_hline(yintercept = c(0.8), color = "purple", linetype = 5) +
      geom_hline(yintercept = c(0.2), color = "purple", linetype = 2) +
  facet_grid(`ethnia` ~ eth_loc_lib, labeller = labeller(eth_loc_lib = eth_loc_lib.labs, circle_orange = circle_orange_labs)) +
               #nrow =2 , dir = "v")  +

 scale_color_manual(values = c("purple","dark green"), guide = guide_legend(title= "")) + # ,nrow=2, byrow = TRUE)) +
 scale_shape_manual(values = c("circle","square"), guide = guide_legend(title= "")) + #,nrow=2, byrow = TRUE)) + 
   ylab("Segregation") +   
  xlab("Ethnic liberal migrants") + 
 guides(color = FALSE, shape = FALSE) +
ggtitle("ß dominant migrants: 20\nß dominant locals: 5") +
  theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(),legend.text = element_text(size = 12),
                      axis.title.y =   (element_text(size = 12)), # element_blank(),  # 
                      axis.title.x =  (element_text(size = 14)), #   element_blank(),  # 
                      axis.text.x = (element_text(size = 10)),
                      axis.text.y =  (element_text(size = 10)),
                      plot.title=element_text(face="bold", size = 14),   
                      legend.margin=margin(0,0,0,0), panel.spacing = unit(0.8, "lines"), 
                      strip.text.x = element_text(size = 15),  strip.text.y = element_text(size = 15),
                      plot.caption = element_text(hjust= 0.5, size = 12)) +
theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))

ggsave("lc_hc2_min.jpg",last_plot(),
  device = NULL,
  path = NULL,
  scale = 2,
  width = 6,
  height = 3,
 # units = ("in", "cm", "mm"),
  dpi = 300,
  limitsize = TRUE)

# Intermediate randomness Locals x-axys

df_eth_loc  %>% filter(ID == "hc_lc") %>% filter(circle_orange == 20)  %>% filter(eth_min_lib == 0 | eth_min_lib == 1 | eth_min_lib == 3 |   eth_min_lib == 5) %>% gather(key = subgroup, value = Segra, eth_sqr_loc, eth_sqr_min, eth_crl_loc, eth_crl_min, val_sqr_loc,val_sqr_min,val_crl_loc, val_crl_min) %>%mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"ethnic seg." = c("eth_sqr_loc","eth_sqr_min","eth_crl_loc","eth_crl_min"), "value seg." = c("val_sqr_loc","val_sqr_min","val_crl_loc", "val_crl_min")), "ethnic seg."), `group` = fct_relevel(fct_collapse(subgroup, "liberal" = c("eth_crl_loc","eth_crl_min","val_crl_loc", "val_crl_min"), "conservative" = c("eth_sqr_loc","eth_sqr_min","val_sqr_loc","val_sqr_min")), "liberal"), 
  `ethnia` = fct_relevel(fct_collapse(subgroup, "Locals:80% ethnic\n 50% liberal" = c("eth_sqr_loc","eth_crl_loc","val_sqr_loc","val_crl_loc"), "Migrants: 20% ethnic\n 20% liberal" = c("eth_sqr_min","eth_crl_min","val_sqr_min","val_crl_min")),"Locals:80% ethnic\n 50% liberal" ))  %>%

  ggplot( aes(x = eth_loc_lib, y = Segra, color = `segregation`, shape = `group` )) + geom_line() + geom_point(size = 3) +

  scale_x_discrete(limits= c(0,1,2,3,4,5,10,15,20)) +

  scale_y_continuous(limits=c(0,1), breaks = c(0,0.2,0.5,0.8,1)) +
  geom_vline(xintercept = c(1,5,10,20), color = "red") +
    geom_hline(yintercept = c(0.5), color = "red", linetype = 2) +
      geom_hline(yintercept = c(0.8), color = "purple", linetype = 5) +
      geom_hline(yintercept = c(0.2), color = "purple", linetype = 2) +
  facet_grid(`ethnia` ~ eth_min_lib, labeller = labeller(eth_min_lib = eth_min_lib.labs, circle_orange = circle_orange_labs)) +
               #nrow =2 , dir = "v")  +

 scale_color_manual(values = c("purple","dark green"), guide = guide_legend(title= "")) + # ,nrow=2, byrow = TRUE)) +
 scale_shape_manual(values = c("circle","square"), guide = guide_legend(title= "")) + #,nrow=2, byrow = TRUE)) + 
   ylab("Segregation") +   
  xlab("ethnic liberal locals") + 
# guides(color = FALSE, shape = FALSE) +
xlab("Ethnic liberal locals") + 
# guides(color = FALSE, shape = FALSE) +
ggtitle("ß dominant locals: 20\nß dominant migrants: 5") +
  theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(),legend.text = element_text(size = 12),
                      axis.title.y =   (element_text(size = 12)), # element_blank(),  # 
                      axis.title.x =  (element_text(size = 14)), #   element_blank(),  # 
                      axis.text.x = (element_text(size = 10)),
                      axis.text.y =  (element_text(size = 10)),
                      plot.title=element_text(face="bold", size = 14),   
                      legend.margin=margin(0,0,0,0), panel.spacing = unit(0.8, "lines"), 
                      strip.text.x = element_text(size = 15),  strip.text.y = element_text(size = 15),
                      plot.caption = element_text(hjust= 0.5, size = 12)) +
theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))

# 
# comb <- ggarrange(mig,loc, nrow =  2, common.legend = TRUE, legend = "bottom")
# annotate_figure(comb, 
#                # top = text_grob("Dominant ß: 5",  face = "bold", size = 12),
#                left = text_grob("Segregation", rot = 90, size = 12),
#                 bottom = text_grob("ß value conservative both group: 0", hjust = 1, x = 1, size = 12),
#                 )

ggsave("lc_hc2_maj.jpg",last_plot(),
  device = NULL,
  path = NULL,
   scale = 2,
  width = 6,
  height = 3,
 # units = c("in", "cm", "mm"),
  dpi = 300,
  limitsize = TRUE)

```

```{r rand80, fig.width= 8,fig.height= 7, fig.pos="H",include=TRUE,fig.cap="Individual comparison rand 80", echo=FALSE}

eth_min_lib.labs <- c("ß Ethnic liberal migrants: 0", "ß Ethnic liberal migrants: 1", "ß Ethnic liberal migrants: 2","ß Ethnic liberal migrants: 3","ß Ethnic liberal migrants: 4","ß Ethnic liberal migrants: 5","ß Ethnic liberal migrants: 10","ß Ethnic liberal migrants: 15","ß Ethnic liberal migrants: 20")
names(eth_min_lib.labs) <- c("0","1","2","3","4", "5","10","15","20")
eth_loc_lib.labs <- c("ß Ethnic liberal locals: 0", "ß Ethnic liberal locals: 1", "ß Ethnic liberal locals: 2","ß Ethnic liberal locals: 3","ß Ethnic liberal locals: 4","ß Ethnic liberal locals: 5","ß Ethnic liberal locals: 10","ß Ethnic liberal locals: 15","ß Ethnic liberal locals: 20")
names(eth_loc_lib.labs) <-  c("0","1","2","3","4", "5","10","15","20")

# Intermediate randomness Migrants x-axys

 df_eth_loc  %>% filter(ID == "lc_hc") %>% filter(circle_orange == 80)  %>% filter(eth_loc_lib == 0 | eth_loc_lib == 1 | eth_loc_lib == 3 | eth_loc_lib == 5) %>% gather(key = subgroup, value = Segra, eth_sqr_loc, eth_sqr_min, eth_crl_loc, eth_crl_min, val_sqr_loc,val_sqr_min,val_crl_loc, val_crl_min) %>%mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"ethnic seg." = c("eth_sqr_loc","eth_sqr_min","eth_crl_loc","eth_crl_min"), "value seg." = c("val_sqr_loc","val_sqr_min","val_crl_loc", "val_crl_min")), "ethnic seg."), `group` = fct_relevel(fct_collapse(subgroup, "liberal" = c("eth_crl_loc","eth_crl_min","val_crl_loc", "val_crl_min"), "conservative" = c("eth_sqr_loc","eth_sqr_min","val_sqr_loc","val_sqr_min")), "liberal"), 
  `ethnia` = fct_relevel(fct_collapse(subgroup, "Locals:80% ethnic\n 50% liberal" = c("eth_sqr_loc","eth_crl_loc","val_sqr_loc","val_crl_loc"), "Migrants: 20% ethnic\n 80% liberal" = c("eth_sqr_min","eth_crl_min","val_sqr_min","val_crl_min")),"Locals:80% ethnic\n 50% liberal" ))  %>%

  ggplot( aes(x = eth_min_lib, y = Segra, color = `segregation`, shape = `group` )) + geom_line() + geom_point(size = 3) +

  scale_x_discrete(limits= c(0,1,2,3,4,5,10,15,20)) +

  scale_y_continuous(limits=c(0,1), breaks = c(0,0.2,0.5,0.8,1)) +
  geom_vline(xintercept = c(1,5,10,20), color = "red") +
    geom_hline(yintercept = c(0.5), color = "red", linetype = 2) +
      geom_hline(yintercept = c(0.8), color = "purple", linetype = 5) +
      geom_hline(yintercept = c(0.2), color = "purple", linetype = 2) +
  facet_grid(`ethnia` ~ eth_loc_lib, labeller = labeller(eth_loc_lib = eth_loc_lib.labs, circle_orange = circle_orange_labs)) +
               #nrow =2 , dir = "v")  +

 scale_color_manual(values = c("purple","dark green"), guide = guide_legend(title= "")) + # ,nrow=2, byrow = TRUE)) +
 scale_shape_manual(values = c("circle","square"), guide = guide_legend(title= "")) + #,nrow=2, byrow = TRUE)) + 
   ylab("Segregation") +   
  xlab("Ethnic liberal migrants") + 
 guides(color = FALSE, shape = FALSE) +
ggtitle("ß dominant migrants: 20\nß dominant locals: 5") +
  theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(),legend.text = element_text(size = 12),
                      axis.title.y =   (element_text(size = 12)), # element_blank(),  # 
                      axis.title.x =  (element_text(size = 14)), #   element_blank(),  # 
                      axis.text.x = (element_text(size = 10)),
                      axis.text.y =  (element_text(size = 10)),
                      plot.title=element_text(face="bold", size = 14),   
                      legend.margin=margin(0,0,0,0), panel.spacing = unit(0.8, "lines"), 
                      strip.text.x = element_text(size = 15),  strip.text.y = element_text(size = 15),
                      plot.caption = element_text(hjust= 0.5, size = 12)) +
theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))

ggsave("lc_hc8_min.jpg",last_plot(),
  device = NULL,
  path = NULL,
  scale = 2,
  width = 6,
  height = 3,
 # units = ("in", "cm", "mm"),
  dpi = 300,
  limitsize = TRUE)

# Intermediate randomness Locals x-axys

df_eth_loc  %>% filter(ID == "hc_lc") %>% filter(circle_orange == 80)  %>% filter(eth_min_lib == 0 | eth_min_lib == 1 | eth_min_lib == 3 |   eth_min_lib == 5) %>% gather(key = subgroup, value = Segra, eth_sqr_loc, eth_sqr_min, eth_crl_loc, eth_crl_min, val_sqr_loc,val_sqr_min,val_crl_loc, val_crl_min) %>%mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"ethnic seg." = c("eth_sqr_loc","eth_sqr_min","eth_crl_loc","eth_crl_min"), "value seg." = c("val_sqr_loc","val_sqr_min","val_crl_loc", "val_crl_min")), "ethnic seg."), `group` = fct_relevel(fct_collapse(subgroup, "liberal" = c("eth_crl_loc","eth_crl_min","val_crl_loc", "val_crl_min"), "conservative" = c("eth_sqr_loc","eth_sqr_min","val_sqr_loc","val_sqr_min")), "liberal"), 
  `ethnia` = fct_relevel(fct_collapse(subgroup, "Locals:80% ethnic\n 50% liberal" = c("eth_sqr_loc","eth_crl_loc","val_sqr_loc","val_crl_loc"), "Migrants: 20% ethnic\n 80% liberal" = c("eth_sqr_min","eth_crl_min","val_sqr_min","val_crl_min")),"Locals:80% ethnic\n 50% liberal" ))  %>%

  ggplot( aes(x = eth_loc_lib, y = Segra, color = `segregation`, shape = `group` )) + geom_line() + geom_point(size = 3) +

  scale_x_discrete(limits= c(0,1,2,3,4,5,10,15,20)) +

  scale_y_continuous(limits=c(0,1), breaks = c(0,0.2,0.5,0.8,1)) +
  geom_vline(xintercept = c(1,5,10,20), color = "red") +
    geom_hline(yintercept = c(0.5), color = "red", linetype = 2) +
      geom_hline(yintercept = c(0.8), color = "purple", linetype = 5) +
      geom_hline(yintercept = c(0.2), color = "purple", linetype = 2) +
  facet_grid(`ethnia` ~ eth_min_lib, labeller = labeller(eth_min_lib = eth_min_lib.labs, circle_orange = circle_orange_labs)) +
               #nrow =2 , dir = "v")  +

 scale_color_manual(values = c("purple","dark green"), guide = guide_legend(title= "")) + # ,nrow=2, byrow = TRUE)) +
 scale_shape_manual(values = c("circle","square"), guide = guide_legend(title= "")) + #,nrow=2, byrow = TRUE)) + 
   ylab("Segregation") +   
  xlab("ethnic liberal locals") + 
# guides(color = FALSE, shape = FALSE) +
xlab("Ethnic liberal locals") + 
# guides(color = FALSE, shape = FALSE) +
ggtitle("ß dominant locals: 20\nß dominant migrants: 5") +
  theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(),legend.text = element_text(size = 12),
                      axis.title.y =   (element_text(size = 12)), # element_blank(),  # 
                      axis.title.x =  (element_text(size = 14)), #   element_blank(),  # 
                      axis.text.x = (element_text(size = 10)),
                      axis.text.y =  (element_text(size = 10)),
                      plot.title=element_text(face="bold", size = 14),   
                      legend.margin=margin(0,0,0,0), panel.spacing = unit(0.8, "lines"), 
                      strip.text.x = element_text(size = 15),  strip.text.y = element_text(size = 15),
                      plot.caption = element_text(hjust= 0.5, size = 12)) +
theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))

# 
# comb <- ggarrange(mig,loc, nrow =  2, common.legend = TRUE, legend = "bottom")
# annotate_figure(comb, 
#                # top = text_grob("Dominant ß: 5",  face = "bold", size = 12),
#                left = text_grob("Segregation", rot = 90, size = 12),
#                 bottom = text_grob("ß value conservative both group: 0", hjust = 1, x = 1, size = 12),
#                 )

ggsave("lc_hc8_maj.jpg",last_plot(),
  device = NULL,
  path = NULL,
   scale = 2,
  width = 6,
  height = 3,
 # units = c("in", "cm", "mm"),
  dpi = 300,
  limitsize = TRUE)

```

```{r det20, fig.width= 8,fig.height= 7, fig.pos="H",include=TRUE,fig.cap="Individual comparison determinism beta 20", echo=FALSE}

eth_min_lib.labs <- c("ß Ethnic liberal migrants: 0", "ß Ethnic liberal migrants: 1", "ß Ethnic liberal migrants: 2","ß Ethnic liberal migrants: 3","ß Ethnic liberal migrants: 4","ß Ethnic liberal migrants: 5","ß Ethnic liberal migrants: 10","ß Ethnic liberal migrants: 15","ß Ethnic liberal migrants: 20")
names(eth_min_lib.labs) <- c("0","1","2","3","4", "5","10","15","20")
eth_loc_lib.labs <- c("ß Ethnic liberal locals: 0", "ß Ethnic liberal locals: 1", "ß Ethnic liberal locals: 2","ß Ethnic liberal locals: 3","ß Ethnic liberal locals: 4","ß Ethnic liberal locals: 5","ß Ethnic liberal locals: 10","ß Ethnic liberal locals: 15","ß Ethnic liberal locals: 20")
names(eth_loc_lib.labs) <-  c("0","1","2","3","4", "5","10","15","20")

# Intermediate randomness Migrants x-axys

 df_eth_loc  %>% filter(ID == "hc_hc") %>% filter(circle_orange == 20)  %>% filter(eth_loc_lib == 0 | eth_loc_lib == 5 | eth_loc_lib == 10 | eth_loc_lib == 20) %>% gather(key = subgroup, value = Segra, eth_sqr_loc, eth_sqr_min, eth_crl_loc, eth_crl_min, val_sqr_loc,val_sqr_min,val_crl_loc, val_crl_min) %>%mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"ethnic seg." = c("eth_sqr_loc","eth_sqr_min","eth_crl_loc","eth_crl_min"), "value seg." = c("val_sqr_loc","val_sqr_min","val_crl_loc", "val_crl_min")), "ethnic seg."), `group` = fct_relevel(fct_collapse(subgroup, "liberal" = c("eth_crl_loc","eth_crl_min","val_crl_loc", "val_crl_min"), "conservative" = c("eth_sqr_loc","eth_sqr_min","val_sqr_loc","val_sqr_min")), "liberal"), 
  `ethnia` = fct_relevel(fct_collapse(subgroup, "Locals:80% ethnic\n 50% liberal" = c("eth_sqr_loc","eth_crl_loc","val_sqr_loc","val_crl_loc"), "Migrants: 20% ethnic\n 20% liberal" = c("eth_sqr_min","eth_crl_min","val_sqr_min","val_crl_min")),"Locals:80% ethnic\n 50% liberal" ))  %>%

  ggplot( aes(x = eth_min_lib, y = Segra, color = `segregation`, shape = `group` )) + geom_line() + geom_point(size = 3) +

  scale_x_discrete(limits= c(0,1,2,3,4,5,10,15,20)) +

  scale_y_continuous(limits=c(0,1), breaks = c(0,0.2,0.5,0.8,1)) +
  geom_vline(xintercept = c(1,5,10,20), color = "red") +
    geom_hline(yintercept = c(0.5), color = "red", linetype = 2) +
      geom_hline(yintercept = c(0.8), color = "purple", linetype = 5) +
      geom_hline(yintercept = c(0.2), color = "purple", linetype = 2) +
  facet_grid(`ethnia` ~ eth_loc_lib, labeller = labeller(eth_loc_lib = eth_loc_lib.labs, circle_orange = circle_orange_labs)) +
               #nrow =2 , dir = "v")  +

 scale_color_manual(values = c("purple","dark green"), guide = guide_legend(title= "")) + # ,nrow=2, byrow = TRUE)) +
 scale_shape_manual(values = c("circle","square"), guide = guide_legend(title= "")) + #,nrow=2, byrow = TRUE)) + 
   ylab("Segregation") +   
  xlab("Ethnic liberal migrants") + 
 guides(color = FALSE, shape = FALSE) +
ggtitle("ß dominant migrants: 20\nß dominant locals: 20") +
  theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(),legend.text = element_text(size = 12),
                      axis.title.y =   (element_text(size = 12)), # element_blank(),  # 
                      axis.title.x =  (element_text(size = 14)), #   element_blank(),  # 
                      axis.text.x = (element_text(size = 10)),
                      axis.text.y =  (element_text(size = 10)),
                      plot.title=element_text(face="bold", size = 14),   
                      legend.margin=margin(0,0,0,0), panel.spacing = unit(0.8, "lines"), 
                      strip.text.x = element_text(size = 15),  strip.text.y = element_text(size = 15),
                      plot.caption = element_text(hjust= 0.5, size = 12)) +
theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))

ggsave("hc_hc2_min.jpg",last_plot(),
  device = NULL,
  path = NULL,
  scale = 2,
  width = 6,
  height = 3,
 # units = ("in", "cm", "mm"),
  dpi = 300,
  limitsize = TRUE)

# Intermediate randomness Locals x-axys

df_eth_loc  %>% filter(ID == "hc_hc") %>% filter(circle_orange == 20)  %>% filter(eth_min_lib == 0 | eth_min_lib == 5 | eth_min_lib == 10 | eth_min_lib == 20) %>% gather(key = subgroup, value = Segra, eth_sqr_loc, eth_sqr_min, eth_crl_loc, eth_crl_min, val_sqr_loc,val_sqr_min,val_crl_loc, val_crl_min) %>%mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"ethnic seg." = c("eth_sqr_loc","eth_sqr_min","eth_crl_loc","eth_crl_min"), "value seg." = c("val_sqr_loc","val_sqr_min","val_crl_loc", "val_crl_min")), "ethnic seg."), `group` = fct_relevel(fct_collapse(subgroup, "liberal" = c("eth_crl_loc","eth_crl_min","val_crl_loc", "val_crl_min"), "conservative" = c("eth_sqr_loc","eth_sqr_min","val_sqr_loc","val_sqr_min")), "liberal"), 
  `ethnia` = fct_relevel(fct_collapse(subgroup, "Locals:80% ethnic\n 50% liberal" = c("eth_sqr_loc","eth_crl_loc","val_sqr_loc","val_crl_loc"), "Migrants: 20% ethnic\n 20% liberal" = c("eth_sqr_min","eth_crl_min","val_sqr_min","val_crl_min")),"Locals:80% ethnic\n 50% liberal" ))  %>%

  ggplot( aes(x = eth_loc_lib, y = Segra, color = `segregation`, shape = `group` )) + geom_line() + geom_point(size = 3) +

  scale_x_discrete(limits= c(0,1,2,3,4,5,10,15,20)) +

  scale_y_continuous(limits=c(0,1), breaks = c(0,0.2,0.5,0.8,1)) +
  geom_vline(xintercept = c(1,5,10,20), color = "red") +
    geom_hline(yintercept = c(0.5), color = "red", linetype = 2) +
      geom_hline(yintercept = c(0.8), color = "purple", linetype = 5) +
      geom_hline(yintercept = c(0.2), color = "purple", linetype = 2) +
  facet_grid(`ethnia` ~ eth_min_lib, labeller = labeller(eth_min_lib = eth_min_lib.labs, circle_orange = circle_orange_labs)) +
               #nrow =2 , dir = "v")  +

 scale_color_manual(values = c("purple","dark green"), guide = guide_legend(title= "")) + # ,nrow=2, byrow = TRUE)) +
 scale_shape_manual(values = c("circle","square"), guide = guide_legend(title= "")) + #,nrow=2, byrow = TRUE)) + 
   ylab("Segregation") +   
  xlab("ethnic liberal locals") + 
# guides(color = FALSE, shape = FALSE) +
xlab("Ethnic liberal locals") + 
# guides(color = FALSE, shape = FALSE) +
ggtitle("ß dominant locals: 20\nß dominant migrants: 20") +
  theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(),legend.text = element_text(size = 12),
                      axis.title.y =   (element_text(size = 12)), # element_blank(),  # 
                      axis.title.x =  (element_text(size = 14)), #   element_blank(),  # 
                      axis.text.x = (element_text(size = 10)),
                      axis.text.y =  (element_text(size = 10)),
                      plot.title=element_text(face="bold", size = 14),   
                      legend.margin=margin(0,0,0,0), panel.spacing = unit(0.8, "lines"), 
                      strip.text.x = element_text(size = 15),  strip.text.y = element_text(size = 15),
                      plot.caption = element_text(hjust= 0.5, size = 12)) +
theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))

# 
# comb <- ggarrange(mig,loc, nrow =  2, common.legend = TRUE, legend = "bottom")
# annotate_figure(comb, 
#                # top = text_grob("Dominant ß: 5",  face = "bold", size = 12),
#                left = text_grob("Segregation", rot = 90, size = 12),
#                 bottom = text_grob("ß value conservative both group: 0", hjust = 1, x = 1, size = 12),
#                 )

ggsave("hc_hc2_maj.jpg",last_plot(),
  device = NULL,
  path = NULL,
   scale = 2,
  width = 6,
  height = 3,
 # units = c("in", "cm", "mm"),
  dpi = 300,
  limitsize = TRUE)

```

```{r det80, fig.width= 8,fig.height= 7, fig.pos="H",include=TRUE,fig.cap="Individual comparison determinism beta 20", echo=FALSE}

eth_min_lib.labs <- c("ß Ethnic liberal migrants: 0", "ß Ethnic liberal migrants: 1", "ß Ethnic liberal migrants: 2","ß Ethnic liberal migrants: 3","ß Ethnic liberal migrants: 4","ß Ethnic liberal migrants: 5","ß Ethnic liberal migrants: 10","ß Ethnic liberal migrants: 15","ß Ethnic liberal migrants: 20")
names(eth_min_lib.labs) <- c("0","1","2","3","4", "5","10","15","20")
eth_loc_lib.labs <- c("ß Ethnic liberal locals: 0", "ß Ethnic liberal locals: 1", "ß Ethnic liberal locals: 2","ß Ethnic liberal locals: 3","ß Ethnic liberal locals: 4","ß Ethnic liberal locals: 5","ß Ethnic liberal locals: 10","ß Ethnic liberal locals: 15","ß Ethnic liberal locals: 20")
names(eth_loc_lib.labs) <-  c("0","1","2","3","4", "5","10","15","20")

# Intermediate randomness Migrants x-axys

 df_eth_loc  %>% filter(ID == "hc_hc") %>% filter(circle_orange == 80)  %>% filter(eth_loc_lib == 0 | eth_loc_lib == 5 | eth_loc_lib == 10 | eth_loc_lib == 20) %>% gather(key = subgroup, value = Segra, eth_sqr_loc, eth_sqr_min, eth_crl_loc, eth_crl_min, val_sqr_loc,val_sqr_min,val_crl_loc, val_crl_min) %>%mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"ethnic seg." = c("eth_sqr_loc","eth_sqr_min","eth_crl_loc","eth_crl_min"), "value seg." = c("val_sqr_loc","val_sqr_min","val_crl_loc", "val_crl_min")), "ethnic seg."), `group` = fct_relevel(fct_collapse(subgroup, "liberal" = c("eth_crl_loc","eth_crl_min","val_crl_loc", "val_crl_min"), "conservative" = c("eth_sqr_loc","eth_sqr_min","val_sqr_loc","val_sqr_min")), "liberal"), 
  `ethnia` = fct_relevel(fct_collapse(subgroup, "Locals:80% ethnic\n 50% liberal" = c("eth_sqr_loc","eth_crl_loc","val_sqr_loc","val_crl_loc"), "Migrants: 20% ethnic\n 80% liberal" = c("eth_sqr_min","eth_crl_min","val_sqr_min","val_crl_min")),"Locals:80% ethnic\n 50% liberal" ))  %>%

  ggplot( aes(x = eth_min_lib, y = Segra, color = `segregation`, shape = `group` )) + geom_line() + geom_point(size = 3) +

  scale_x_discrete(limits= c(0,1,2,3,4,5,10,15,20)) +

  scale_y_continuous(limits=c(0,1), breaks = c(0,0.2,0.5,0.8,1)) +
  geom_vline(xintercept = c(1,5,10,20), color = "red") +
    geom_hline(yintercept = c(0.5), color = "red", linetype = 2) +
      geom_hline(yintercept = c(0.8), color = "purple", linetype = 5) +
      geom_hline(yintercept = c(0.2), color = "purple", linetype = 2) +
  facet_grid(`ethnia` ~ eth_loc_lib, labeller = labeller(eth_loc_lib = eth_loc_lib.labs, circle_orange = circle_orange_labs)) +
               #nrow =2 , dir = "v")  +

 scale_color_manual(values = c("purple","dark green"), guide = guide_legend(title= "")) + # ,nrow=2, byrow = TRUE)) +
 scale_shape_manual(values = c("circle","square"), guide = guide_legend(title= "")) + #,nrow=2, byrow = TRUE)) + 
   ylab("Segregation") +   
  xlab("Ethnic liberal migrants") + 
 guides(color = FALSE, shape = FALSE) +
ggtitle("ß dominant migrants: 20\nß dominant locals: 20") +
  theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(),legend.text = element_text(size = 12),
                      axis.title.y =   (element_text(size = 12)), # element_blank(),  # 
                      axis.title.x =  (element_text(size = 14)), #   element_blank(),  # 
                      axis.text.x = (element_text(size = 10)),
                      axis.text.y =  (element_text(size = 10)),
                      plot.title=element_text(face="bold", size = 14),   
                      legend.margin=margin(0,0,0,0), panel.spacing = unit(0.8, "lines"), 
                      strip.text.x = element_text(size = 15),  strip.text.y = element_text(size = 15),
                      plot.caption = element_text(hjust= 0.5, size = 12)) +
theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))

ggsave("hc_hc8_min.jpg",last_plot(),
  device = NULL,
  path = NULL,
  scale = 2,
  width = 6,
  height = 3,
 # units = ("in", "cm", "mm"),
  dpi = 300,
  limitsize = TRUE)

# Intermediate randomness Locals x-axys

hc_hc8_maj <- df_eth_loc  %>% filter(ID == "hc_hc") %>% filter(circle_orange == 80)  %>% filter(eth_min_lib == 0 | eth_min_lib == 5 | eth_min_lib == 10 | eth_min_lib == 20) %>% gather(key = subgroup, value = Segra, eth_sqr_loc, eth_sqr_min, eth_crl_loc, eth_crl_min, val_sqr_loc,val_sqr_min,val_crl_loc, val_crl_min) %>%mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"ethnic seg." = c("eth_sqr_loc","eth_sqr_min","eth_crl_loc","eth_crl_min"), "value seg." = c("val_sqr_loc","val_sqr_min","val_crl_loc", "val_crl_min")), "ethnic seg."), `group` = fct_relevel(fct_collapse(subgroup, "liberal" = c("eth_crl_loc","eth_crl_min","val_crl_loc", "val_crl_min"), "conservative" = c("eth_sqr_loc","eth_sqr_min","val_sqr_loc","val_sqr_min")), "liberal"), 
  `ethnia` = fct_relevel(fct_collapse(subgroup, "Locals:80% ethnic\n 50% liberal" = c("eth_sqr_loc","eth_crl_loc","val_sqr_loc","val_crl_loc"), "Migrants: 20% ethnic\n 80% liberal" = c("eth_sqr_min","eth_crl_min","val_sqr_min","val_crl_min")),"Locals:80% ethnic\n 50% liberal" ))  %>%

  ggplot( aes(x = eth_loc_lib, y = Segra, color = `segregation`, shape = `group` )) + geom_line() + geom_point(size = 3) +

  scale_x_discrete(limits= c(0,1,2,3,4,5,10,15,20)) +

  scale_y_continuous(limits=c(0,1), breaks = c(0,0.2,0.5,0.8,1)) +
  geom_vline(xintercept = c(1,5,10,20), color = "red") +
    geom_hline(yintercept = c(0.5), color = "red", linetype = 2) +
      geom_hline(yintercept = c(0.8), color = "purple", linetype = 5) +
      geom_hline(yintercept = c(0.2), color = "purple", linetype = 2) +
  facet_grid(`ethnia` ~ eth_min_lib, labeller = labeller(eth_min_lib = eth_min_lib.labs, circle_orange = circle_orange_labs)) +
               #nrow =2 , dir = "v")  +

 scale_color_manual(values = c("purple","dark green"), guide = guide_legend(title= "")) + # ,nrow=2, byrow = TRUE)) +
 scale_shape_manual(values = c("circle","square"), guide = guide_legend(title= "")) + #,nrow=2, byrow = TRUE)) + 
   ylab("Segregation") +   
  xlab("ethnic liberal locals") + 
# guides(color = FALSE, shape = FALSE) +
xlab("Ethnic liberal locals") + 
# guides(color = FALSE, shape = FALSE) +
ggtitle("ß dominant locals: 20\nß dominant migrants: 20") +
  theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(),legend.text = element_text(size = 12),
                      axis.title.y =   (element_text(size = 12)), # element_blank(),  # 
                      axis.title.x =  (element_text(size = 14)), #   element_blank(),  # 
                      axis.text.x = (element_text(size = 10)),
                      axis.text.y =  (element_text(size = 10)),
                      plot.title=element_text(face="bold", size = 14),   
                      legend.margin=margin(0,0,0,0), panel.spacing = unit(0.8, "lines"), 
                      strip.text.x = element_text(size = 15),  strip.text.y = element_text(size = 15),
                      plot.caption = element_text(hjust= 0.5, size = 12)) +
theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm")) 
# 
# comb <- ggarrange(mig,loc, nrow =  2, common.legend = TRUE, legend = "bottom")
# annotate_figure(comb, 
#                # top = text_grob("Dominant ß: 5",  face = "bold", size = 12),
#                left = text_grob("Segregation", rot = 90, size = 12),
#                 bottom = text_grob("ß value conservative both group: 0", hjust = 1, x = 1, size = 12),
#                 )

ggsave("hc_hc8_maj.jpg",hc_hc8_maj,
  device = NULL,
  path = NULL,
   scale = 2,
  width = 6,
  height = 3,
 # units = c("in", "cm", "mm"),
  dpi = 300,
  limitsize = TRUE)

```

# TRASH

```{r rand50locals, fig.width= 8,fig.height= 7, fig.pos="H",include=TRUE,fig.cap="Individual comparison rand 50", echo=FALSE}

eth_min_lib.labs <- c("ß Ethnic liberal migrants: 0", "ß Ethnic liberal migrants: 1", "ß Ethnic liberal migrants: 2","ß Ethnic liberal migrants: 3","ß Ethnic liberal migrants: 4","ß Ethnic liberal migrants: 5","ß Ethnic liberal migrants: 10","ß Ethnic liberal migrants: 15","ß Ethnic liberal migrants: 20")
names(eth_min_lib.labs) <- c("0","1","2","3","4", "5","10","15","20")
eth_loc_lib.labs <- c("ß Ethnic liberal locals: 0", "ß Ethnic liberal locals: 1", "ß Ethnic liberal locals: 2","ß Ethnic liberal locals: 3","ß Ethnic liberal locals: 4","ß Ethnic liberal locals: 5","ß Ethnic liberal locals: 10","ß Ethnic liberal locals: 15","ß Ethnic liberal locals: 20")
names(eth_loc_lib.labs) <-  c("0","1","2","3","4", "5","10","15","20")

# Intermediate randomness Migrants x-axys

 df_eth_loc  %>% filter(ID == "lc_hc") %>% filter(circle_orange == 50)  %>% filter(eth_min_lib == 0 | eth_min_lib == 5 | eth_min_lib == 10 | eth_min_lib == 20) %>% gather(key = subgroup, value = Segra, eth_sqr_loc, eth_sqr_min, eth_crl_loc, eth_crl_min, val_sqr_loc,val_sqr_min,val_crl_loc, val_crl_min) %>%mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"ethnic seg." = c("eth_sqr_loc","eth_sqr_min","eth_crl_loc","eth_crl_min"), "value seg." = c("val_sqr_loc","val_sqr_min","val_crl_loc", "val_crl_min")), "ethnic seg."), `group` = fct_relevel(fct_collapse(subgroup, "liberal" = c("eth_crl_loc","eth_crl_min","val_crl_loc", "val_crl_min"), "conservative" = c("eth_sqr_loc","eth_sqr_min","val_sqr_loc","val_sqr_min")), "liberal"), 
  `ethnia` = fct_relevel(fct_collapse(subgroup, "Locals:80% ethnic\n 50% liberal" = c("eth_sqr_loc","eth_crl_loc","val_sqr_loc","val_crl_loc"), "Migrants: 20% ethnic\n 50% liberal" = c("eth_sqr_min","eth_crl_min","val_sqr_min","val_crl_min")),"Locals:80% ethnic\n 50% liberal" ))  %>%

  ggplot( aes(x = eth_loc_lib, y = Segra, color = `segregation`, shape = `group` )) + geom_line() + geom_point(size = 3) +

  scale_x_discrete(limits= c(0,1,2,3,4,5,10,15,20)) +

  scale_y_continuous(limits=c(0,1), breaks = c(0,0.2,0.5,0.8,1)) +
  geom_vline(xintercept = c(1,5,10,20), color = "red") +
    geom_hline(yintercept = c(0.5), color = "red", linetype = 2) +
      geom_hline(yintercept = c(0.8), color = "purple", linetype = 5) +
      geom_hline(yintercept = c(0.2), color = "purple", linetype = 2) +
  facet_grid(`ethnia` ~ eth_min_lib, labeller = labeller(eth_min_lib = eth_min_lib.labs, circle_orange = circle_orange_labs)) +
               #nrow =2 , dir = "v")  +

 scale_color_manual(values = c("purple","dark green"), guide = guide_legend(title= "")) + # ,nrow=2, byrow = TRUE)) +
 scale_shape_manual(values = c("circle","square"), guide = guide_legend(title= "")) + #,nrow=2, byrow = TRUE)) + 
   ylab("Segregation") +   
  xlab("Ethnic liberal locals") + 
#  guides(color = FALSE, shape = FALSE) +
ggtitle("ß dominant migrants: 20\nß dominant locals: 5") +
  theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(),legend.text = element_text(size = 12),
                      axis.title.y =   (element_text(size = 12)), # element_blank(),  # 
                      axis.title.x =  (element_text(size = 14)), #   element_blank(),  # 
                      axis.text.x = (element_text(size = 10)),
                      axis.text.y =  (element_text(size = 10)),
                      plot.title=element_text(face="bold", size = 14),   
                      legend.margin=margin(0,0,0,0), panel.spacing = unit(0.8, "lines"), 
                      strip.text.x = element_text(size = 15),  strip.text.y = element_text(size = 15),
                      plot.caption = element_text(hjust= 0.5, size = 12)) +
theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))

ggsave("lc_hc5_min.jpg",last_plot(),
  device = NULL,
  path = NULL,
  scale = 2,
  width = 6,
  height = 3,
 # units = ("in", "cm", "mm"),
  dpi = 300,
  limitsize = TRUE)

# Intermediate randomness Locals x-axys

df_eth_loc  %>% filter(ID == "hc_lc") %>% filter(circle_orange == 50)  %>% filter(eth_min_lib == 0 | eth_min_lib == 1 | eth_min_lib == 3 |   eth_min_lib == 5) %>% gather(key = subgroup, value = Segra, eth_sqr_loc, eth_sqr_min, eth_crl_loc, eth_crl_min, val_sqr_loc,val_sqr_min,val_crl_loc, val_crl_min) %>%mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"ethnic seg." = c("eth_sqr_loc","eth_sqr_min","eth_crl_loc","eth_crl_min"), "value seg." = c("val_sqr_loc","val_sqr_min","val_crl_loc", "val_crl_min")), "ethnic seg."), `group` = fct_relevel(fct_collapse(subgroup, "liberal" = c("eth_crl_loc","eth_crl_min","val_crl_loc", "val_crl_min"), "conservative" = c("eth_sqr_loc","eth_sqr_min","val_sqr_loc","val_sqr_min")), "liberal"), 
  `ethnia` = fct_relevel(fct_collapse(subgroup, "Locals:80% ethnic\n 50% liberal" = c("eth_sqr_loc","eth_crl_loc","val_sqr_loc","val_crl_loc"), "Migrants: 20% ethnic\n 50% liberal" = c("eth_sqr_min","eth_crl_min","val_sqr_min","val_crl_min")),"Locals:80% ethnic\n 50% liberal" ))  %>%

  ggplot( aes(x = eth_loc_lib, y = Segra, color = `segregation`, shape = `group` )) + geom_line() + geom_point(size = 3) +

  scale_x_discrete(limits= c(0,1,2,3,4,5,10,15,20)) +

  scale_y_continuous(limits=c(0,1), breaks = c(0,0.2,0.5,0.8,1)) +
  geom_vline(xintercept = c(1,5,10,20), color = "red") +
    geom_hline(yintercept = c(0.5), color = "red", linetype = 2) +
      geom_hline(yintercept = c(0.8), color = "purple", linetype = 5) +
      geom_hline(yintercept = c(0.2), color = "purple", linetype = 2) +
  facet_grid(`ethnia` ~ eth_min_lib, labeller = labeller(eth_min_lib = eth_min_lib.labs, circle_orange = circle_orange_labs)) +
               #nrow =2 , dir = "v")  +

 scale_color_manual(values = c("purple","dark green"), guide = guide_legend(title= "")) + # ,nrow=2, byrow = TRUE)) +
 scale_shape_manual(values = c("circle","square"), guide = guide_legend(title= "")) + #,nrow=2, byrow = TRUE)) + 
   ylab("Segregation") +   
  xlab("ethnic liberal locals") + 
# guides(color = FALSE, shape = FALSE) +
xlab("Ethnic liberal locals") + 
# guides(color = FALSE, shape = FALSE) +
ggtitle("ß dominant locals: 20\nß dominant migrants: 5") +
  theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(),legend.text = element_text(size = 12),
                      axis.title.y =   (element_text(size = 12)), # element_blank(),  # 
                      axis.title.x =  (element_text(size = 14)), #   element_blank(),  # 
                      axis.text.x = (element_text(size = 10)),
                      axis.text.y =  (element_text(size = 10)),
                      plot.title=element_text(face="bold", size = 14),   
                      legend.margin=margin(0,0,0,0), panel.spacing = unit(0.8, "lines"), 
                      strip.text.x = element_text(size = 15),  strip.text.y = element_text(size = 15),
                      plot.caption = element_text(hjust= 0.5, size = 12)) +
theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))

# 
# comb <- ggarrange(mig,loc, nrow =  2, common.legend = TRUE, legend = "bottom")
# annotate_figure(comb, 
#                # top = text_grob("Dominant ß: 5",  face = "bold", size = 12),
#                left = text_grob("Segregation", rot = 90, size = 12),
#                 bottom = text_grob("ß value conservative both group: 0", hjust = 1, x = 1, size = 12),
#                 )

ggsave("lc_hc5_maj.jpg",last_plot(),
  device = NULL,
  path = NULL,
   scale = 2,
  width = 6,
  height = 3,
 # units = c("in", "cm", "mm"),
  dpi = 300,
  limitsize = TRUE)

```

### 2021-01-23 analysis.Rmd
remove JMS

--- 2020-11-23 JMS.Rmd
@@
 library(ggplot2)
+library(reshape)
+library(reshape2)
 library(forcats)
-library(reshape2)
 library(tidyr)
 library(dplyr)
-library(reshape)
 library(gtable)
-library(explore)
+library(kableExtra)
+library(magick)
+library(webshot)
+library(xtable)
 library(gridExtra)
-library(xtable)
-library(ggpubr)
-
-#  This was to simplify dataset of basic conditions
-# a <- read.csv("basic_equal.csv", sep = ",", skip = 6)
-# names(a) <- pull(read.csv("legend.csv"))
-# B <- a %>% filter(dominant >= 0, secondary_circle  <= dominant, secondary_square <= dominant) %>% filter(ticks == 1000)
-# write.csv(B, file = "basic_exp.csv", row.names = FALSE)
-
-setwd("C:/Users/rocpa/OneDrive/Desktop/AF/experiments/JMS/")
-
-hc_hc_dis <- read.csv("hc_hc_dis.csv")
-# names(test_mj80) <- pull(read.csv("legend_test.csv"))
-
-base_eq <-  read.csv("basic/basic_exp.csv", sep = ",")
-
-majority_bs <- read.csv("maj/majority_bs.csv", sep = ",", skip = 6)
-names(majority_bs) <- pull(read.csv("basic/legend_bas.csv"))
-
-majority_bsa <- read.csv("maj/majority_bsa.csv", sep = ",", skip = 6)
-names(majority_bsa) <- pull(read.csv("basic/legend_bas.csv"))
-names(majority_bsa)[names(majority_bsa) == "circle_orange"] <- "dmnt"
-names(majority_bsa)[names(majority_bsa) == "dominant"] <- "circle_orange"
-names(majority_bsa)[names(majority_bsa) == "dmnt"] <- "dominant"
-
-majority_bs <- majority_bs %>% filter(ticks == 1000)
-
-# majlib <- read.csv("maj/maj_lib.csv", sep = ",", skip = 6)
-# names(majlib) <- pull(read.csv("maj/legend_maj.csv"))
-
-test_5_20 <- read.csv("result5_20.csv", sep = ",", skip = 6)
-names(test_5_20) <- pull(read.csv("legend_test.csv"))
-test_5_20 <- test_5_20[,-(35:42)]
-
-test_20_5 <- read.csv("result20_5.csv", sep = ",", skip = 6)
-names(test_20_5) <- pull(read.csv("legend_test.csv"))
-
-b <- test_20_5 %>% filter(fraction_blue == 60)
-
-a <- test_5_20 %>% filter(fraction_blue == 80)
-ftable(xtabs(~ a$circle_orange + a$eth_loc_lib + a$eth_min_lib, data = a))
-
-levels(as.factor(a$eth_loc_con))
-levels(as.factor(b$eth_loc_con))
+library(ggrepel)
+options(xtable.floating = FALSE)
+options(xtable.timestamp = "")
+webshot::install_phantomjs()
+
+setwd("C:/Users/rocpa/OneDrive/Desktop/AF2/exp12_2020/")
+
+# Back work, used to combine datasets from diffent runs. To IGNORE OR DELETE
+
+# etlib_min1 <- read.csv("mj_etlib_min.csv",skip = 6)
+# etlib_min2 <- read.csv("mj_etlib_min2.csv",skip = 6)
+# etlib_min <- rbind(etlib_min1,etlib_min2)
+# names(etlib_min) <- pull(read.csv("legend_sec_etlib.csv"))
+# etlib_min <- cbind(ID = "etlib_min",etlib_min)
+
+basic <- read.csv("df_basic.csv",sep =",")
+value_basic <- read.csv("df_valuebasic.csv",sep = ",")
+asym_dom <- read.csv("df_asym_dom.csv",sep = ",")
+dislib <- read.csv("df_dislib.csv", sep = ",")
+sa_asym <- read.csv("df_sa_asym.csv",sep =",")
+etlib <- read.csv("df_etlib.csv",sep =",")
+
+circle_orange.labs <- c("20% liberal minority", "50% liberal minority", "80% liberal minority")
+names(circle_orange.labs) <- c("20","50","80")
+```
+
+```{r basefigure, fig.width=30, fig.cap="Same parameter for ethnic and value homophily for all agents", echo=FALSE}
+
+# database filter
+excl <- names(basic) %in% c("run", "ID","density","step")
+basic_sa <- basic[!excl] %>% filter(dominant == secondary) %>% group_by(dominant,secondary,circle_orange,circle_blue,fraction_blue) %>% summarise_all(c("mean"= mean,"sd"= sd))
+
+# graph
+
+data_f <- basic_sa %>% gather(key= subgroup, value = Segra, et_sq_bl_mean, vl_sq_bl_mean, et_cl_bl_mean, vl_cl_bl_mean, et_sq_or_mean, vl_sq_or_mean, et_cl_or_mean, vl_cl_or_mean) %>% mutate(
+  `segregation` = fct_relevel(fct_collapse(subgroup,"ethnics" = c("et_sq_bl_mean","et_cl_bl_mean","et_sq_or_mean","et_cl_or_mean"), "values" = c("vl_sq_bl_mean","vl_cl_bl_mean","vl_sq_or_mean","vl_cl_or_mean")),"ethnics"),
+ `orientation` = fct_relevel(fct_collapse(subgroup, "conservative" = c("et_sq_bl_mean","vl_sq_bl_mean","et_sq_or_mean","vl_sq_or_mean"), "liberal" = c("et_cl_bl_mean","vl_cl_bl_mean","et_cl_or_mean","vl_cl_or_mean")),"conservative" ),
+ `ethnia` = fct_relevel(fct_collapse(subgroup, "local" = c("et_sq_bl_mean","vl_sq_bl_mean","et_cl_bl_mean","vl_cl_bl_mean"),"minority" = c("et_sq_or_mean","vl_sq_or_mean","et_cl_or_mean","vl_cl_or_mean")), "local"))
+
+ggplot(data = data_f, aes(x = dominant, y = Segra, linetype = `segregation` , color = `ethnia`, shape = `orientation`)) + geom_line()  +  geom_point(size = 3) +
+ scale_x_discrete(limits=c(seq(0,20 ,by = 1))) + scale_y_continuous(limits=c(0,1), breaks=seq(0,1,by=0.10)) +
+  scale_linetype_manual(values=c("solid","dotted"), labels = c("ethnic","value"), guide = guide_legend(title = "Dimension", order = 1)) +
+  scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
+  scale_shape_manual(values = c("square","circle"), guide = guide_legend(title="Orientation" ,override.aes = list(size = 3), order = 3)) +
+  xlab("ß dominant = ß secondary") + ylab("Exposure") + 
+  theme_bw() +  theme( axis.title.x = (element_text(size = 15)), axis.title.y = (element_text(size = 15)), axis.text.x =  (element_text(size = 15)),axis.text.y =  (element_text(size = 15)), legend.title = element_text(size = 13) ,legend.text = element_text(size = 13), plot.title=element_text(hjust = 0.5)) + theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
+
+ggsave("images/one_beta.jpg",plot = last_plot(),
+  device = NULL,path = NULL, 
+  scale = 1,
+  width = 10,
+  height = 4,
+  units = c("in", "cm", "mm"),
+  dpi = 300,
+  limitsize = FALSE)
+
+# robustness table
+
+table_rb <- xtable(basic_sa[,c("dominant","et_sq_bl_mean","et_sq_bl_sd","et_cl_bl_mean","et_cl_bl_sd","et_sq_or_mean","et_sq_or_sd","et_cl_or_mean","et_cl_or_sd","vl_sq_bl_mean","vl_sq_bl_sd","vl_cl_bl_mean","vl_cl_bl_sd","vl_sq_or_mean","vl_sq_or_sd","vl_cl_or_mean","vl_cl_or_sd")], digits = 3)
+align(table_rb) <- "c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|"
+
+addtorow <- list()
+addtorow$pos <- list(0, 0,0,0,0)
+addtorow$command <-  c("\\multicolumn{17}{|c|}{Baseline condition}  \\\\\\hline\n",
+   "Preference &  \\multicolumn{8}{|c|}{Ethnic Exposure} & \\multicolumn{8}{|c|}{Value Exposure}   \\\\\\hline\n",
+  "& \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  & \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  \\\\\n",
+"$\\beta$ dom = $\\beta$ sec & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
+& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
+& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal}\\\\\n",
+" & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD\\\\\n")
+
+print(table_rb,type = "latex", file = "basic_rb.tex", include.rownames=FALSE, add.to.row = addtorow, include.colnames = FALSE, latex.environments = "center")
+
+```
+
+```{r secondary_0, fig.width=30, fig.cap="secondary preference set to 0", echo=FALSE}
+
+# database filter
+excl <- names(basic) %in% c("run", "ID","density","step")
+basic_sa_sec0 <- basic[!excl] %>% filter(secondary == 0) %>% group_by(dominant,circle_orange,circle_blue,fraction_blue,secondary) %>% summarise_all(c("mean"= mean,"sd"= sd))
+
+# graph
+
+data_f <- basic_sa_sec0 %>% gather(key= subgroup, value = Segra, et_sq_bl_mean, vl_sq_bl_mean, et_cl_bl_mean, vl_cl_bl_mean, et_sq_or_mean, vl_sq_or_mean, et_cl_or_mean, vl_cl_or_mean) %>% mutate(
+  `segregation` = fct_relevel(fct_collapse(subgroup,"ethnics" = c("et_sq_bl_mean","et_cl_bl_mean","et_sq_or_mean","et_cl_or_mean"), "values" = c("vl_sq_bl_mean","vl_cl_bl_mean","vl_sq_or_mean","vl_cl_or_mean")),"ethnics"),
+ `orientation` = fct_relevel(fct_collapse(subgroup, "conservative" = c("et_sq_bl_mean","vl_sq_bl_mean","et_sq_or_mean","vl_sq_or_mean"), "liberal" = c("et_cl_bl_mean","vl_cl_bl_mean","et_cl_or_mean","vl_cl_or_mean")),"conservative" ),
+ `ethnia` = fct_relevel(fct_collapse(subgroup, "local" = c("et_sq_bl_mean","vl_sq_bl_mean","et_cl_bl_mean","vl_cl_bl_mean"),"minority" = c("et_sq_or_mean","vl_sq_or_mean","et_cl_or_mean","vl_cl_or_mean")), "local"))
+
+ggplot(data = data_f, aes(x = dominant, y = Segra, linetype = `segregation` , color = `ethnia`, shape = `orientation`)) + geom_line()  +  geom_point(size = 3) +
+ scale_x_discrete(limits=c(seq(0,20 ,by = 1))) + scale_y_continuous(limits=c(0,1), breaks=seq(0,1,by=0.10)) +
+  scale_linetype_manual(values=c("solid","dotted"), labels = c("ethnic","value"), guide = guide_legend(title = "Dimension", order = 1)) +
+  scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
+  scale_shape_manual(values = c("square","circle"), guide = guide_legend(title="Orientation" ,override.aes = list(size = 3), order = 3)) +
+  xlab("ß dominant") + ylab("Exposure") + 
+  theme_bw() +  theme( axis.title.x = (element_text(size = 15)), axis.title.y = (element_text(size = 15)), axis.text.x =  (element_text(size = 15)),axis.text.y =  (element_text(size = 15)), legend.title = element_text(size = 13) ,legend.text = element_text(size = 13), plot.title=element_text(hjust = 0.5)) + theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
+
+ggsave("images/sec_0.jpg",plot = last_plot(),
+  device = NULL,path = NULL, 
+  scale = 1,
+  width = 10,
+  height = 4,
+  units = c("in", "cm", "mm"),
+  dpi = 300,
+  limitsize = FALSE)
+
+# robustness table
+
+table_rb <- xtable(basic_sa_sec0[,c("dominant","et_sq_bl_mean","et_sq_bl_sd","et_cl_bl_mean","et_cl_bl_sd","et_sq_or_mean","et_sq_or_sd","et_cl_or_mean","et_cl_or_sd","vl_sq_bl_mean","vl_sq_bl_sd","vl_cl_bl_mean","vl_cl_bl_sd","vl_sq_or_mean","vl_sq_or_sd","vl_cl_or_mean","vl_cl_or_sd")], digits = 3)
+align(table_rb) <- "c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|"
+
+addtorow <- list()
+addtorow$pos <- list(0, 0,0,0,0)
+addtorow$command <-  c("\\multicolumn{17}{|c|}{Secondary preference = 0}  \\\\\\hline\n",
+   "Preference &  \\multicolumn{8}{|c|}{Ethnic Exposure} & \\multicolumn{8}{|c|}{Value Exposure}   \\\\\\hline\n",
+  "& \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  & \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  \\\\\n",
+"$\\beta$ sec = 0 & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
+& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
+& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal}\\\\\n",
+" & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD\\\\\n")
+
+print(table_rb,type = "latex", file = "basic_rb_sec0.tex", include.rownames=FALSE, add.to.row = addtorow, include.colnames = FALSE, latex.environments = "center")
+
+```
+
+```{r base_lib, fig.width=30, fig.cap="Test mechanism: increase value liberal, all other 0", echo=FALSE}
+
+# database filter
+excl <- names(value_basic) %in% c("run","density","step")
+dom_lib <- value_basic[!excl] %>% filter(ID == "dom_crl") %>%   #,  secondary_circle == 0 & dominant_square == 0 & secondary_square == 0) %>% 
+  group_by(ID, dominant_circle,secondary_circle,dominant_square,secondary_square,fraction_blue,circle_blue,circle_orange) %>% summarise_all(c("mean"= mean,"sd"= sd))
+
+# graph
+
+data_f <- dom_lib %>% gather(key= subgroup, value = Segra, et_sq_bl_mean, vl_sq_bl_mean, et_cl_bl_mean, vl_cl_bl_mean, et_sq_or_mean, vl_sq_or_mean, et_cl_or_mean, vl_cl_or_mean) %>% mutate(
+  `segregation` = fct_relevel(fct_collapse(subgroup,"ethnics" = c("et_sq_bl_mean","et_cl_bl_mean","et_sq_or_mean","et_cl_or_mean"), "values" = c("vl_sq_bl_mean","vl_cl_bl_mean","vl_sq_or_mean","vl_cl_or_mean")),"ethnics"),
+ `orientation` = fct_relevel(fct_collapse(subgroup, "conservative" = c("et_sq_bl_mean","vl_sq_bl_mean","et_sq_or_mean","vl_sq_or_mean"), "liberal" = c("et_cl_bl_mean","vl_cl_bl_mean","et_cl_or_mean","vl_cl_or_mean")),"conservative" ),
+ `ethnia` = fct_relevel(fct_collapse(subgroup, "local" = c("et_sq_bl_mean","vl_sq_bl_mean","et_cl_bl_mean","vl_cl_bl_mean"),"minority" = c("et_sq_or_mean","vl_sq_or_mean","et_cl_or_mean","vl_cl_or_mean")), "local"))
+
+ dom_libpic <- ggplot(data = data_f, aes(x = dominant_circle, y = Segra, linetype = `segregation` , color = `ethnia`, shape = `orientation`)) + geom_line()  +  geom_point(size = 3) +
+ scale_x_discrete(limits=c(seq(0,20 ,by = 1))) + scale_y_continuous(limits=c(0,1), breaks=seq(0,1,by=0.10)) +
+  scale_linetype_manual(values=c("solid","dotted"), labels = c("ethnic","value"), guide = guide_legend(title = "Dimension", order = 1)) +
+  scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
+  scale_shape_manual(values = c("square","circle"), guide = guide_legend(title="Orientation" ,override.aes = list(size = 3), order = 3)) +
+  xlab("ß value liberal") + ylab("Exposure") + 
+  theme_bw() +  theme( axis.title.x = (element_text(size = 15)), axis.title.y = (element_text(size = 15)), axis.text.x =  (element_text(size = 15)),axis.text.y =  (element_text(size = 15)), legend.title = element_text(size = 13) ,legend.text = element_text(size = 13), plot.title=element_text(hjust = 0.5)) + theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
+
+ggsave("images/dom_lib.jpg",plot = last_plot(),
+  device = NULL,path = NULL, 
+  scale = 1,
+  width = 10,
+  height = 4,
+  units = c("in", "cm", "mm"),
+  dpi = 300,
+  limitsize = FALSE)
+
+# robustness table
+
+table_rb <- xtable(dom_lib[,c("dominant_circle","et_sq_bl_mean","et_sq_bl_sd","et_cl_bl_mean","et_cl_bl_sd","et_sq_or_mean","et_sq_or_sd","et_cl_or_mean","et_cl_or_sd","vl_sq_bl_mean","vl_sq_bl_sd","vl_cl_bl_mean","vl_cl_bl_sd","vl_sq_or_mean","vl_sq_or_sd","vl_cl_or_mean","vl_cl_or_sd")], digits = 3)
+align(table_rb) <- "c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|"
+
+addtorow <- list()
+addtorow$pos <- list(0, 0,0,0,0)
+addtorow$command <-  c("\\multicolumn{17}{|c|}{Baseline: sensitivity to value liberal}  \\\\\\hline\n",
+   "Preference &  \\multicolumn{8}{|c|}{Ethnic Exposure} & \\multicolumn{8}{|c|}{Value Exposure}   \\\\\\hline\n",
+  "& \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  & \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  \\\\\n",
+# note
+"$\\beta$ dom liberal & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
+& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
+& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal}\\\\\n",
+" & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD\\\\\n")
+
+print(table_rb,type = "latex", file = "dom_lib_rb.tex", include.rownames=FALSE, add.to.row = addtorow, include.colnames = FALSE, latex.environments = "center")
+
+```
+
+```{r base_con, fig.width=30, fig.cap="Test mechanism: increase ethnic conservative, all other 0", echo=FALSE}
+
+# database filter
+excl <- names(value_basic) %in% c("run","density","step")
+dom_con <- value_basic[!excl] %>% filter(ID == "dom_sqr") %>%
+   group_by(ID,dominant_square, secondary_square,dominant_circle,secondary_circle,fraction_blue,circle_blue,circle_orange) %>%
+  #secondary_square == 0 & dominant_circle == 0 & secondary_circle == 0) %>% group_by(dominant_square) 
+summarise_all(c("mean"= mean,"sd"= sd))
+
+# graph
+
+data_f <- dom_con %>% gather(key= subgroup, value = Segra, et_sq_bl_mean, vl_sq_bl_mean, et_cl_bl_mean, vl_cl_bl_mean, et_sq_or_mean, vl_sq_or_mean, et_cl_or_mean, vl_cl_or_mean) %>% mutate(
+  `segregation` = fct_relevel(fct_collapse(subgroup,"ethnics" = c("et_sq_bl_mean","et_cl_bl_mean","et_sq_or_mean","et_cl_or_mean"), "values" = c("vl_sq_bl_mean","vl_cl_bl_mean","vl_sq_or_mean","vl_cl_or_mean")),"ethnics"),
+ `orientation` = fct_relevel(fct_collapse(subgroup, "conservative" = c("et_sq_bl_mean","vl_sq_bl_mean","et_sq_or_mean","vl_sq_or_mean"), "liberal" = c("et_cl_bl_mean","vl_cl_bl_mean","et_cl_or_mean","vl_cl_or_mean")),"conservative" ),
+ `ethnia` = fct_relevel(fct_collapse(subgroup, "local" = c("et_sq_bl_mean","vl_sq_bl_mean","et_cl_bl_mean","vl_cl_bl_mean"),"minority" = c("et_sq_or_mean","vl_sq_or_mean","et_cl_or_mean","vl_cl_or_mean")), "local"))
+
+dom_conpic <- ggplot(data = data_f, aes(x = dominant_square, y = Segra, linetype = `segregation` , color = `ethnia`, shape = `orientation`)) + geom_line()  +  geom_point(size = 3) +
+ scale_x_discrete(limits=c(seq(0,20 ,by = 1))) + scale_y_continuous(limits=c(0,1), breaks=seq(0,1,by=0.10)) +
+  scale_linetype_manual(values=c("solid","dotted"), labels = c("ethnic","value"), guide = guide_legend(title = "Dimension", order = 1)) +
+  scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
+  scale_shape_manual(values = c("square","circle"), guide = guide_legend(title="Orientation" ,override.aes = list(size = 3), order = 3)) +
+  xlab("ß ethnic conservative") + ylab("Exposure") + 
+  theme_bw() +  theme( axis.title.x = (element_text(size = 15)), axis.title.y = (element_text(size = 15)), axis.text.x =  (element_text(size = 15)),axis.text.y =  (element_text(size = 15)), legend.title = element_text(size = 13) ,legend.text = element_text(size = 13), plot.title=element_text(hjust = 0.5)) + theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
+
+ggsave("images/dom_con.jpg",plot = last_plot(),
+  device = NULL,path = NULL, 
+  scale = 1,
+  width = 10,
+  height = 4,
+  units = c("in", "cm", "mm"),
+  dpi = 300,
+  limitsize = FALSE)
+
+# robustness table
+
+table_rb <- xtable(dom_con[,c("dominant_square","et_sq_bl_mean","et_sq_bl_sd","et_cl_bl_mean","et_cl_bl_sd","et_sq_or_mean","et_sq_or_sd","et_cl_or_mean","et_cl_or_sd","vl_sq_bl_mean","vl_sq_bl_sd","vl_cl_bl_mean","vl_cl_bl_sd","vl_sq_or_mean","vl_sq_or_sd","vl_cl_or_mean","vl_cl_or_sd")], digits = 3)
+align(table_rb) <- "c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|"
+
+addtorow <- list()
+addtorow$pos <- list(0, 0,0,0,0)
+addtorow$command <-  c("\\multicolumn{17}{|c|}{Baseline: sensitivity to ethnic conservative}  \\\\\\hline\n",
+   "Preference &  \\multicolumn{8}{|c|}{Ethnic Exposure} & \\multicolumn{8}{|c|}{Value Exposure}   \\\\\\hline\n",
+  "& \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  & \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  \\\\\n",
+# note
+"$\\beta$ dom & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
+ & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
+& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal}\\\\\n",
+" conservative & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD\\\\\n")
+
+print(table_rb,type = "latex", file = "dom_con_rb.tex", include.rownames=FALSE, add.to.row = addtorow, include.colnames = FALSE, latex.environments = "center")
+
+```
+
+```{r comb_value, fig.cap="Combined picture, value sensitivity", echo=FALSE}
+
+ggpubr::ggarrange(dom_libpic,dom_conpic, nrow = 2, ncol = 1, common.legend = TRUE, legend = "right")
+
+ggsave("images/comb_val.jpg",plot = last_plot(),
+  device = NULL,path = NULL, 
+  scale = 1,
+  width = 8,
+  height = 6,
+  units = c("in", "cm", "mm"),
+  dpi = 300,
+  limitsize = FALSE)
+```
+
+```{r asym, fig.width=30, fig.cap="Baseline asymmetric conditions", echo=FALSE}
+
+# database filter
+excl <- names(asym_dom) %in% c("run", "ID","density","step")
+dataset_sa <- asym_dom[!excl] %>% group_by(dominant,circle_orange,circle_blue,fraction_blue,secondary) %>% summarise_all(c("mean"= mean,"sd"= sd))
+
+xlab_t <- "ß dominant"
+
+row_exp <- c("\\multicolumn{17}{|c|}{Ethnic asymmetric condition: Exposure}  \\\\\\hline\n",
+   "Preference &  \\multicolumn{8}{|c|}{Ethnic Exposure} & \\multicolumn{8}{|c|}{Value Exposure}   \\\\\\hline\n",
+  "& \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  & \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  \\\\\n",
+"$\\beta$ sec = 0 & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
+& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
+& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal}\\\\\n",
+" & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD\\\\\n")
+
+row_prox <- c("\\multicolumn{17}{|c|}{Ethnic Asymmetric condition: Spatial Proximity}  \\\\\\hline\n",
+   "Preference &  \\multicolumn{8}{|c|}{Ethnic Proximity} & \\multicolumn{8}{|c|}{Value Proximity}   \\\\\\hline\n",
+  "& \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  & \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  \\\\\n",
+"$\\beta$ sec = 0 & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
+& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
+& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal}\\\\\n",
+" & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD\\\\\n")
+
+tablerb_expname <- "latex/asym_rb_exp.tex"
+tablerb_proxname <- "latex/asym_rb_prox.tex"
+
+plotname <- "images/comb_index.jpg"
+
+# graph
+
+data_exp <- dataset_sa %>% gather(key= subgroup, value = Expo, et_sq_bl_mean, vl_sq_bl_mean, et_cl_bl_mean, vl_cl_bl_mean, et_sq_or_mean, vl_sq_or_mean, et_cl_or_mean, vl_cl_or_mean) %>% mutate(
+  `segregation` = fct_relevel(fct_collapse(subgroup,"ethnics" = c("et_sq_bl_mean","et_cl_bl_mean","et_sq_or_mean","et_cl_or_mean"), "values" = c("vl_sq_bl_mean","vl_cl_bl_mean","vl_sq_or_mean","vl_cl_or_mean")),"ethnics"),
+ `orientation` = fct_relevel(fct_collapse(subgroup, "conservative" = c("et_sq_bl_mean","vl_sq_bl_mean","et_sq_or_mean","vl_sq_or_mean"), "liberal" = c("et_cl_bl_mean","vl_cl_bl_mean","et_cl_or_mean","vl_cl_or_mean")),"conservative" ),
+ `ethnia` = fct_relevel(fct_collapse(subgroup, "local" = c("et_sq_bl_mean","vl_sq_bl_mean","et_cl_bl_mean","vl_cl_bl_mean"),"minority" = c("et_sq_or_mean","vl_sq_or_mean","et_cl_or_mean","vl_cl_or_mean")), "local"))
+
+fig_exp <- ggplot(data = data_exp, aes(x = dominant, y = Expo, linetype = `segregation` , color = `ethnia`, shape = `orientation`)) + geom_line()  +  geom_point(size = 3) +
+ scale_x_discrete(limits=c(seq(0,20 ,by = 1))) + scale_y_continuous(limits=c(0,1), breaks=seq(0,1,by=0.10)) +
+  scale_linetype_manual(values=c("solid","dotted"), labels = c("ethnic","value"), guide = guide_legend(title = "Segregation", order = 1)) +
+  scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
+  scale_shape_manual(values = c("square","circle"), guide = guide_legend(title="Value" ,override.aes = list(size = 3), order = 3)) +
+  xlab("") + ylab("Exposure") + 
+  theme_bw() +  theme( axis.title.x  = element_blank(), axis.title.y = (element_text(size = 15)), axis.text.x  = (element_text(size = 10)) ,axis.text.y =  (element_text(size = 15)), legend.title = element_text(size = 13) ,legend.text = element_text(size = 13), plot.title=element_text(hjust = 0.5)) + theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
+
+tablerb_exp <- xtable(dataset_sa[,c("dominant","et_sq_bl_mean","et_sq_bl_sd","et_cl_bl_mean","et_cl_bl_sd","et_sq_or_mean","et_sq_or_sd","et_cl_or_mean","et_cl_or_sd","vl_sq_bl_mean","vl_sq_bl_sd","vl_cl_bl_mean","vl_cl_bl_sd","vl_sq_or_mean","vl_sq_or_sd","vl_cl_or_mean","vl_cl_or_sd")], digits = 3)
+align(tablerb_exp) <- "c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|"
+
+addtorow <- list()
+addtorow$pos <- list(0, 0,0,0,0)
+addtorow$command <-  row_exp
+
+print(tablerb_exp,type = "latex", file = tablerb_expname, include.rownames=FALSE, add.to.row = addtorow, include.colnames = FALSE, latex.environments = "center")
+
+## Spatial proximity baseline asymmetric
+
+# graph
+
+data_prox <- dataset_sa %>% gather(key= subgroup, value = Prox, de_sq_bl_mean, dv_sq_bl_mean, de_cl_bl_mean, dv_cl_bl_mean, de_sq_or_mean, dv_sq_or_mean, de_cl_or_mean, dv_cl_or_mean) %>% mutate(
+  `segregation` = fct_relevel(fct_collapse(subgroup,"ethnics" = c("de_sq_bl_mean","de_cl_bl_mean","de_sq_or_mean","de_cl_or_mean"), "values" = c("dv_sq_bl_mean","dv_cl_bl_mean","dv_sq_or_mean","dv_cl_or_mean")),"ethnics"),
+ `orientation` = fct_relevel(fct_collapse(subgroup, "conservative" = c("de_sq_bl_mean","dv_sq_bl_mean","de_sq_or_mean","dv_sq_or_mean"), "liberal" = c("de_cl_bl_mean","dv_cl_bl_mean","de_cl_or_mean","dv_cl_or_mean")),"conservative" ),
+ `ethnia` = fct_relevel(fct_collapse(subgroup, "local" = c("de_sq_bl_mean","dv_sq_bl_mean","de_cl_bl_mean","dv_cl_bl_mean"),"minority" = c("de_sq_or_mean","dv_sq_or_mean","de_cl_or_mean","dv_cl_or_mean")), "local"))
+
+fig_prox <- ggplot(data = data_prox, aes(x = dominant, y = Prox, linetype = `segregation` , color = `ethnia`, shape = `orientation`)) + geom_line()  +  geom_point(size = 3) +
+ scale_x_discrete(limits=c(seq(0,20 ,by = 1))) + scale_y_continuous(limits=c(min(data_prox$Prox),max(data_prox$Prox)), breaks=seq(0,max(data_prox$Prox),by=0.50)) +
+  scale_linetype_manual(values=c("solid","dotted"), labels = c("ethnic","value"), guide = guide_legend(title = "Segregation", order = 1)) +
+  scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
+  scale_shape_manual(values = c("square","circle"), guide = guide_legend(title="Value" ,override.aes = list(size = 3), order = 3)) +
+  xlab(xlab_t) + ylab("Spatial Proximity") + 
+  theme_bw() +  theme( axis.title.x = (element_text(size = 15)), axis.title.y = (element_text(size = 15)), axis.text.x =  (element_text(size = 15)),axis.text.y =  (element_text(size = 15)), legend.title = element_text(size = 13) ,legend.text = element_text(size = 13), plot.title=element_text(hjust = 0.5)) + theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
+
+# robustness table
+
+tablerb_prox <- xtable(dataset_sa[,c("dominant","de_sq_bl_mean","de_sq_bl_sd","de_cl_bl_mean","de_cl_bl_sd","de_sq_or_mean","de_sq_or_sd","de_cl_or_mean","de_cl_or_sd","dv_sq_bl_mean","dv_sq_bl_sd","dv_cl_bl_mean","dv_cl_bl_sd","dv_sq_or_mean","dv_sq_or_sd","dv_cl_or_mean","dv_cl_or_sd")], digits = 3)
+align(tablerb_prox) <- "c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|"
+
+addtorow <- list()
+addtorow$pos <- list(0, 0,0,0,0)
+addtorow$command <-  row_prox
+print(tablerb_prox,type = "latex", file = tablerb_proxname , include.rownames=FALSE, add.to.row = addtorow, include.colnames = FALSE, latex.environments = "center")
+
+# combined image
+
+ggpubr::ggarrange(fig_exp,fig_prox, nrow = 2, ncol = 1, common.legend = TRUE, legend = "right")
+
+ggsave(plotname,plot = last_plot(),
+  device = NULL,path = NULL, 
+  scale = 1,
+  width = 8,
+  height = 6,
+  units = c("in", "cm", "mm"),
+  dpi = 300,
+  limitsize = FALSE)
+
+```
+
+```{r dislib, fig.width=30, fig.cap="Effect distribution liberal minority, asymmetric based condition", echo=FALSE}
+
+# database filter
+excl <- names(dislib) %in% c("run", "ID","density","step","eth_lib_loc","eth_lib_min","val_con_loc","val_con_min")
+dataset_sa <- dislib[!excl] %>% group_by(fraction_blue,circle_blue,eth_con_loc,eth_con_min,val_lib_loc,val_lib_min,circle_orange) %>% summarise_all(c("mean"= mean,"sd"= sd))
+
+xlab_t <- "% liberal minority"
+
+row_exp <- c("\\multicolumn{17}{|c|}{Ethnic asymmetric condition: Exposure}  \\\\\\hline\n",
+   "Preference &  \\multicolumn{8}{|c|}{Ethnic Exposure} & \\multicolumn{8}{|c|}{Value Exposure}   \\\\\\hline\n",
+  "& \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  & \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  \\\\\n",
+"$\\beta$ dom = 20 & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
+& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
+& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal}\\\\\n",
+"$\\beta$ sec = 0  & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD\\\\\n")
+
+row_prox <- c("\\multicolumn{17}{|c|}{Ethnic Asymmetric condition: Spatial Proximity}  \\\\\\hline\n",
+   "Preference &  \\multicolumn{8}{|c|}{Ethnic Proximity} & \\multicolumn{8}{|c|}{Value Proximity}   \\\\\\hline\n",
+  "& \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  & \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  \\\\\n",
+"$\\beta$ dom = 20 & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
+& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
+& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal}\\\\\n",
+"$\\beta$ sec = 0 & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD\\\\\n")
+
+tablerb_expname <- "latex/dislib_rb_exp.tex"
+tablerb_proxname <- "latex/dislib_rb_prox.tex"
+
+plotname <- "images/comb_dislib.jpg"
+
+# graph
+
+dataset_sa <- subset(dataset_sa, circle_orange >= 10 & circle_orange <= 90)
+data_exp <- dataset_sa %>% gather(key= subgroup, value = Expo, et_sq_bl_mean, vl_sq_bl_mean, et_cl_bl_mean, vl_cl_bl_mean, et_sq_or_mean, vl_sq_or_mean, et_cl_or_mean, vl_cl_or_mean) %>% mutate(
+  `segregation` = fct_relevel(fct_collapse(subgroup,"ethnics" = c("et_sq_bl_mean","et_cl_bl_mean","et_sq_or_mean","et_cl_or_mean"), "values" = c("vl_sq_bl_mean","vl_cl_bl_mean","vl_sq_or_mean","vl_cl_or_mean")),"ethnics"),
+ `orientation` = fct_relevel(fct_collapse(subgroup, "conservative" = c("et_sq_bl_mean","vl_sq_bl_mean","et_sq_or_mean","vl_sq_or_mean"), "liberal" = c("et_cl_bl_mean","vl_cl_bl_mean","et_cl_or_mean","vl_cl_or_mean")),"conservative" ),
+ `ethnia` = fct_relevel(fct_collapse(subgroup, "local" = c("et_sq_bl_mean","vl_sq_bl_mean","et_cl_bl_mean","vl_cl_bl_mean"),"minority" = c("et_sq_or_mean","vl_sq_or_mean","et_cl_or_mean","vl_cl_or_mean")), "local"))
+
+fig_exp <- ggplot(data = data_exp, aes(x = circle_orange, y = Expo, linetype = `segregation` , color = `ethnia`, shape = `orientation`)) + geom_line()  +  geom_point(size = 3) +
+ scale_x_discrete(limits=c(seq(10,90 ,by = 10))) + scale_y_continuous(limits=c(0,1), breaks=seq(0,1,by=0.10)) +
+   geom_vline(xintercept = 50, color = "red") +
+  scale_linetype_manual(values=c("solid","dotted"), labels = c("ethnic","value"), guide = guide_legend(title = "Segregation", order = 1)) +
+  scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
+  scale_shape_manual(values = c("square","circle"), guide = guide_legend(title="Value" ,override.aes = list(size = 3), order = 3)) +
+  xlab("") + ylab("Exposure") + 
+  theme_bw() +  theme( axis.title.x  = element_blank(), axis.title.y = (element_text(size = 15)), axis.text.x  = (element_text(size = 10)) ,axis.text.y =  (element_text(size = 15)), legend.title = element_text(size = 13) ,legend.text = element_text(size = 13), plot.title=element_text(hjust = 0.5)) + theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
+
+tablerb_exp <- xtable(dataset_sa[,c("circle_orange","et_sq_bl_mean","et_sq_bl_sd","et_cl_bl_mean","et_cl_bl_sd","et_sq_or_mean","et_sq_or_sd","et_cl_or_mean","et_cl_or_sd","vl_sq_bl_mean","vl_sq_bl_sd","vl_cl_bl_mean","vl_cl_bl_sd","vl_sq_or_mean","vl_sq_or_sd","vl_cl_or_mean","vl_cl_or_sd")], digits = 3)
+align(tablerb_exp) <- "c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|"
+
+addtorow <- list()
+addtorow$pos <- list(0, 0,0,0,0)
+addtorow$command <-  row_exp
+
+print(tablerb_exp,type = "latex", file = tablerb_expname, include.rownames=FALSE, add.to.row = addtorow, include.colnames = FALSE, latex.environments = "center")
+
+## Spatial proximity baseline asymmetric
+
+# graph
+
+data_prox <- dataset_sa %>% gather(key= subgroup, value = Prox, de_sq_bl_mean, dv_sq_bl_mean, de_cl_bl_mean, dv_cl_bl_mean, de_sq_or_mean, dv_sq_or_mean, de_cl_or_mean, dv_cl_or_mean) %>% mutate(
+  `segregation` = fct_relevel(fct_collapse(subgroup,"ethnics" = c("de_sq_bl_mean","de_cl_bl_mean","de_sq_or_mean","de_cl_or_mean"), "values" = c("dv_sq_bl_mean","dv_cl_bl_mean","dv_sq_or_mean","dv_cl_or_mean")),"ethnics"),
+ `orientation` = fct_relevel(fct_collapse(subgroup, "conservative" = c("de_sq_bl_mean","dv_sq_bl_mean","de_sq_or_mean","dv_sq_or_mean"), "liberal" = c("de_cl_bl_mean","dv_cl_bl_mean","de_cl_or_mean","dv_cl_or_mean")),"conservative" ),
+ `ethnia` = fct_relevel(fct_collapse(subgroup, "local" = c("de_sq_bl_mean","dv_sq_bl_mean","de_cl_bl_mean","dv_cl_bl_mean"),"minority" = c("de_sq_or_mean","dv_sq_or_mean","de_cl_or_mean","dv_cl_or_mean")), "local"))
+
+fig_prox <- ggplot(data = data_prox, aes(x = circle_orange, y = Prox, linetype = `segregation` , color = `ethnia`, shape = `orientation`)) + geom_line()  +  geom_point(size = 3) +
+ scale_x_discrete(limits=c(seq(10,90 ,by = 10))) + scale_y_continuous(limits=c(min(data_prox$Prox),max(data_prox$Prox)), breaks=seq(0,max(data_prox$Prox),by=0.50)) +
+    geom_vline(xintercept = 50, color = "red") +
+  scale_linetype_manual(values=c("solid","dotted"), labels = c("ethnic","value"), guide = guide_legend(title = "Segregation", order = 1)) +
+  scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
+  scale_shape_manual(values = c("square","circle"), guide = guide_legend(title="Value" ,override.aes = list(size = 3), order = 3)) +
+  xlab(xlab_t) + ylab("Spatial Proximity") + 
+  theme_bw() +  theme( axis.title.x = (element_text(size = 15)), axis.title.y = (element_text(size = 15)), axis.text.x =  (element_text(size = 15)),axis.text.y =  (element_text(size = 15)), legend.title = element_text(size = 13) ,legend.text = element_text(size = 13), plot.title=element_text(hjust = 0.5)) + theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
+
+# robustness table
+
+tablerb_prox <- xtable(dataset_sa[,c("circle_orange","de_sq_bl_mean","de_sq_bl_sd","de_cl_bl_mean","de_cl_bl_sd","de_sq_or_mean","de_sq_or_sd","de_cl_or_mean","de_cl_or_sd","dv_sq_bl_mean","dv_sq_bl_sd","dv_cl_bl_mean","dv_cl_bl_sd","dv_sq_or_mean","dv_sq_or_sd","dv_cl_or_mean","dv_cl_or_sd")], digits = 3)
+align(tablerb_prox) <- "c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|"
+
+addtorow <- list()
+addtorow$pos <- list(0, 0,0,0,0)
+addtorow$command <-  row_prox
+print(tablerb_prox,type = "latex", file = tablerb_proxname , include.rownames=FALSE, add.to.row = addtorow, include.colnames = FALSE, latex.environments = "center")
+
+# combined image
+
+ggpubr::ggarrange(fig_exp,fig_prox, nrow = 2, ncol = 1, common.legend = TRUE, legend = "right")
+
+ggsave(plotname,plot = last_plot(),
+  device = NULL,path = NULL, 
+  scale = 1,
+  width = 8,
+  height = 6,
+  units = c("in", "cm", "mm"),
+  dpi = 300,
+  limitsize = FALSE)
+
+```
+
+```{r sa_dom_50prox, fig.width=30, fig.cap="Sensitivity proximity ethnic conservative local, baseline asymmetric conditions", echo=FALSE}
+
+# database filter
+excl <- names(sa_asym) %in% c("run", "ID","density","step","eth_lib_loc","val_con_loc","eth_lib_min","val_con_min")
+dataset_sa <- sa_asym[!excl] %>% filter(val_lib_loc  == 20,eth_con_min == 20, val_lib_min == 20)  %>% 
+ filter(circle_orange == 50) %>%
+  group_by(eth_con_loc,fraction_blue,circle_blue, circle_orange) %>% summarise_all(c("mean"= mean,"sd"= sd))
+
+xlab_t <- "ß ethnic conservative local"
+
+# graph
+
+data_prox <- dataset_sa %>% gather(key= subgroup, value = Prox, de_sq_bl_mean, dv_sq_bl_mean, de_cl_bl_mean, dv_cl_bl_mean, de_sq_or_mean, dv_sq_or_mean, de_cl_or_mean, dv_cl_or_mean) %>% mutate(
+  `segregation` = fct_relevel(fct_collapse(subgroup,"ethnics" = c("de_sq_bl_mean","de_cl_bl_mean","de_sq_or_mean","de_cl_or_mean"), "values" = c("dv_sq_bl_mean","dv_cl_bl_mean","dv_sq_or_mean","dv_cl_or_mean")),"ethnics"),
+ `orientation` = fct_relevel(fct_collapse(subgroup, "conservative" = c("de_sq_bl_mean","dv_sq_bl_mean","de_sq_or_mean","dv_sq_or_mean"), "liberal" = c("de_cl_bl_mean","dv_cl_bl_mean","de_cl_or_mean","dv_cl_or_mean")),"conservative" ),
+ `ethnia` = fct_relevel(fct_collapse(subgroup, "local" = c("de_sq_bl_mean","dv_sq_bl_mean","de_cl_bl_mean","dv_cl_bl_mean"),"minority" = c("de_sq_or_mean","dv_sq_or_mean","de_cl_or_mean","dv_cl_or_mean")), "local"))
+
+prox_eth_con_loc <- ggplot(data = data_prox, aes(x = eth_con_loc, y = Prox, linetype = `segregation` , color = `ethnia`, shape = `orientation`)) + geom_line()  +  geom_point(size = 3) + 
+ scale_x_discrete(limits=c(seq(0,20 ,by = 1))) + scale_y_continuous(limits=c(min(data_prox$Prox),max(data_prox$Prox)), breaks=seq(0,max(data_prox$Prox),by=0.50)) +
+#    facet_wrap(~ circle_orange, labeller = labeller(circle_orange = circle_orange.labs)) +
+    geom_vline(xintercept = 20, color = "red") +
+  scale_linetype_manual(values=c("solid","dotted"), labels = c("ethnic","value"), guide = guide_legend(title = "Segregation", order = 1)) +
+  scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
+  scale_shape_manual(values = c("square","circle"), guide = guide_legend(title="Value" ,override.aes = list(size = 3), order = 3)) +
+  xlab(xlab_t) + ylab("Spatial Proximity") + 
+  theme_bw() +  theme( axis.title.x = (element_text(size = 15)), axis.title.y = (element_text(size = 15)), axis.text.x =  (element_text(size = 12)),axis.text.y =  (element_text(size = 15)), legend.title = element_text(size = 13) ,legend.text = element_text(size = 13),plot.title=element_text(hjust = 0.5)) + theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
+
+# ggsave("images/eth_con_loc50.jpg",plot = fig_prox,
+#   device = NULL,path = NULL, 
+#   scale = 1,
+#   width = 8,
+#   height = 6,
+#   units = c("in", "cm", "mm"),
+#   dpi = 300,
+#   limitsize = FALSE)
+
+# database filter
+excl <- names(sa_asym) %in% c("run", "ID","density","step","eth_lib_loc","val_con_loc","eth_lib_min","val_con_min")
+dataset_sa <- sa_asym[!excl] %>% filter(eth_con_loc   == 20,eth_con_min == 20, val_lib_min == 20)  %>% 
+ filter(circle_orange == 50) %>%
+  group_by(val_lib_loc,fraction_blue,circle_blue, circle_orange) %>% summarise_all(c("mean"= mean,"sd"= sd))
+
+xlab_t <- "ß value liberal local"
+
+# graph
+
+data_prox <- dataset_sa %>% gather(key= subgroup, value = Prox, de_sq_bl_mean, dv_sq_bl_mean, de_cl_bl_mean, dv_cl_bl_mean, de_sq_or_mean, dv_sq_or_mean, de_cl_or_mean, dv_cl_or_mean) %>% mutate(
+  `segregation` = fct_relevel(fct_collapse(subgroup,"ethnics" = c("de_sq_bl_mean","de_cl_bl_mean","de_sq_or_mean","de_cl_or_mean"), "values" = c("dv_sq_bl_mean","dv_cl_bl_mean","dv_sq_or_mean","dv_cl_or_mean")),"ethnics"),
+ `orientation` = fct_relevel(fct_collapse(subgroup, "conservative" = c("de_sq_bl_mean","dv_sq_bl_mean","de_sq_or_mean","dv_sq_or_mean"), "liberal" = c("de_cl_bl_mean","dv_cl_bl_mean","de_cl_or_mean","dv_cl_or_mean")),"conservative" ),
+ `ethnia` = fct_relevel(fct_collapse(subgroup, "local" = c("de_sq_bl_mean","dv_sq_bl_mean","de_cl_bl_mean","dv_cl_bl_mean"),"minority" = c("de_sq_or_mean","dv_sq_or_mean","de_cl_or_mean","dv_cl_or_mean")), "local"))
+
+prox_val_lib_loc <- ggplot(data = data_prox, aes(x = val_lib_loc, y = Prox, linetype = `segregation` , color = `ethnia`, shape = `orientation`)) + geom_line()  +  geom_point(size = 3) +
+ scale_x_discrete(limits=c(seq(0,20 ,by = 1))) + scale_y_continuous(limits=c(min(data_prox$Prox),max(data_prox$Prox)), breaks=seq(0,max(data_prox$Prox),by=0.50)) +
+#☻    facet_wrap(~ circle_orange, labeller = labeller(circle_orange = circle_orange.labs)) +
+      geom_vline(xintercept = 20, color = "red") +
+  scale_linetype_manual(values=c("solid","dotted"), labels = c("ethnic","value"), guide = guide_legend(title = "Segregation", order = 1)) +
+  scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
+  scale_shape_manual(values = c("square","circle"), guide = guide_legend(title="Value" ,override.aes = list(size = 3), order = 3)) +
+  xlab(xlab_t) + ylab("Spatial Proximity") + 
+  theme_bw() +  theme( axis.title.x = (element_text(size = 15)), axis.title.y = (element_text(size = 15)), axis.text.x =  (element_text(size = 12)),axis.text.y =  (element_text(size = 15)), legend.title = element_text(size = 13) ,legend.text = element_text(size = 13),plot.title=element_text(hjust = 0.5)) + theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
+
+# ggsave("images/val_lib_loc50.jpg",plot = fig_prox,
+#   device = NULL,path = NULL, 
+#   scale = 1,
+#   width = 8,
+#   height = 6,
+#   units = c("in", "cm", "mm"),
+#   dpi = 300,
+#   limitsize = FALSE)
+
+# database filter
+excl <- names(sa_asym) %in% c("run", "ID","density","step","eth_lib_loc","val_con_loc","eth_lib_min","val_con_min")
+dataset_sa <- sa_asym[!excl] %>% filter(eth_con_loc   == 20, val_lib_loc  == 20, val_lib_min == 20)  %>% 
+ filter(circle_orange == 50) %>%
+  group_by(eth_con_min,fraction_blue,circle_blue, circle_orange) %>% summarise_all(c("mean"= mean,"sd"= sd))
+
+xlab_t <- "ß ethnic conservative minority"
+
+# graph
+
+data_prox <- dataset_sa %>% gather(key= subgroup, value = Prox, de_sq_bl_mean, dv_sq_bl_mean, de_cl_bl_mean, dv_cl_bl_mean, de_sq_or_mean, dv_sq_or_mean, de_cl_or_mean, dv_cl_or_mean) %>% mutate(
+  `segregation` = fct_relevel(fct_collapse(subgroup,"ethnics" = c("de_sq_bl_mean","de_cl_bl_mean","de_sq_or_mean","de_cl_or_mean"), "values" = c("dv_sq_bl_mean","dv_cl_bl_mean","dv_sq_or_mean","dv_cl_or_mean")),"ethnics"),
+ `orientation` = fct_relevel(fct_collapse(subgroup, "conservative" = c("de_sq_bl_mean","dv_sq_bl_mean","de_sq_or_mean","dv_sq_or_mean"), "liberal" = c("de_cl_bl_mean","dv_cl_bl_mean","de_cl_or_mean","dv_cl_or_mean")),"conservative" ),
+ `ethnia` = fct_relevel(fct_collapse(subgroup, "local" = c("de_sq_bl_mean","dv_sq_bl_mean","de_cl_bl_mean","dv_cl_bl_mean"),"minority" = c("de_sq_or_mean","dv_sq_or_mean","de_cl_or_mean","dv_cl_or_mean")), "local"))
+
+prox_eth_con_min <- ggplot(data = data_prox, aes(x = eth_con_min, y = Prox, linetype = `segregation` , color = `ethnia`, shape = `orientation`)) + geom_line()  +  geom_point(size = 3) +
+ scale_x_discrete(limits=c(seq(0,20 ,by = 1))) + scale_y_continuous(limits=c(min(data_prox$Prox),max(data_prox$Prox)), breaks=seq(0,max(data_prox$Prox),by=0.50)) +
+#☻    facet_wrap(~ circle_orange, labeller = labeller(circle_orange = circle_orange.labs)) +
+      geom_vline(xintercept = 20, color = "red") +
+  scale_linetype_manual(values=c("solid","dotted"), labels = c("ethnic","value"), guide = guide_legend(title = "Segregation", order = 1)) +
+  scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
+  scale_shape_manual(values = c("square","circle"), guide = guide_legend(title="Value" ,override.aes = list(size = 3), order = 3)) +
+  xlab(xlab_t) + ylab("Spatial Proximity") + 
+  theme_bw() +  theme( axis.title.x = (element_text(size = 15)), axis.title.y = (element_text(size = 15)), axis.text.x =  (element_text(size = 12)),axis.text.y =  (element_text(size = 15)), legend.title = element_text(size = 13) ,legend.text = element_text(size = 13),plot.title=element_text(hjust = 0.5)) + theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
+
+# ggsave("images/eth_con_min50.jpg",plot = fig_prox,
+#   device = NULL,path = NULL, 
+#   scale = 1,
+#   width = 8,
+#   height = 6,
+#   units = c("in", "cm", "mm"),
+#   dpi = 300,
+#   limitsize = FALSE)
+
+# database filter
+excl <- names(sa_asym) %in% c("run", "ID","density","step","eth_lib_loc","val_con_loc","eth_lib_min","val_con_min")
+dataset_sa <- sa_asym[!excl] %>% filter(eth_con_loc   == 20, val_lib_loc  == 20, eth_con_min  == 20)  %>% 
+ filter(circle_orange == 50) %>%
+  group_by(val_lib_min,fraction_blue,circle_blue, circle_orange) %>% summarise_all(c("mean"= mean,"sd"= sd))
+
+xlab_t <- "ß value liberal minority"
+
+# graph
+
+data_prox <- dataset_sa %>% gather(key= subgroup, value = Prox, de_sq_bl_mean, dv_sq_bl_mean, de_cl_bl_mean, dv_cl_bl_mean, de_sq_or_mean, dv_sq_or_mean, de_cl_or_mean, dv_cl_or_mean) %>% mutate(
+  `segregation` = fct_relevel(fct_collapse(subgroup,"ethnics" = c("de_sq_bl_mean","de_cl_bl_mean","de_sq_or_mean","de_cl_or_mean"), "values" = c("dv_sq_bl_mean","dv_cl_bl_mean","dv_sq_or_mean","dv_cl_or_mean")),"ethnics"),
+ `orientation` = fct_relevel(fct_collapse(subgroup, "conservative" = c("de_sq_bl_mean","dv_sq_bl_mean","de_sq_or_mean","dv_sq_or_mean"), "liberal" = c("de_cl_bl_mean","dv_cl_bl_mean","de_cl_or_mean","dv_cl_or_mean")),"conservative" ),
+ `ethnia` = fct_relevel(fct_collapse(subgroup, "local" = c("de_sq_bl_mean","dv_sq_bl_mean","de_cl_bl_mean","dv_cl_bl_mean"),"minority" = c("de_sq_or_mean","dv_sq_or_mean","de_cl_or_mean","dv_cl_or_mean")), "local"))
+
+prox_val_lib_min <- ggplot(data = data_prox, aes(x = val_lib_min, y = Prox, linetype = `segregation` , color = `ethnia`, shape = `orientation`)) + geom_line()  +  geom_point(size = 3) +
+ scale_x_discrete(limits=c(seq(0,20 ,by = 1))) + scale_y_continuous(limits=c(min(data_prox$Prox),max(data_prox$Prox)), breaks=seq(0,max(data_prox$Prox),by=0.50)) +
+#☻    facet_wrap(~ circle_orange, labeller = labeller(circle_orange = circle_orange.labs)) +
+      geom_vline(xintercept = 20, color = "red") +
+
+  scale_linetype_manual(values=c("solid","dotted"), labels = c("ethnic","value"), guide = guide_legend(title = "Segregation", order = 1)) +
+  scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
+  scale_shape_manual(values = c("square","circle"), guide = guide_legend(title="Value" ,override.aes = list(size = 3), order = 3)) +
+  xlab(xlab_t) + ylab("Spatial Proximity") + 
+  theme_bw() +  theme( axis.title.x = (element_text(size = 15)), axis.title.y = (element_text(size = 15)), axis.text.x =  (element_text(size = 12)),axis.text.y =  (element_text(size = 15)), legend.title = element_text(size = 13) ,legend.text = element_text(size = 13),plot.title=element_text(hjust = 0.5)) + theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
+
+ggpubr::ggarrange(prox_eth_con_loc,prox_val_lib_loc,prox_eth_con_min,prox_val_lib_min, nrow = 2, ncol = 2, common.legend = TRUE, legend = "bottom")
+
+ggsave("images/sa_asym_bt.jpg",plot = last_plot(),
+  device = NULL,path = NULL,
+  scale = 1,
+  width = 11,
+  height = 8,
+  units = c("in", "cm", "mm"),
+  dpi = 300,
+  limitsize = FALSE)
+
+```
+
+```{r sa_dom_50exp, fig.width=30, fig.cap="exposure Sensitivity ethnic conservative local, baseline asymmetric conditions", echo=FALSE}
+
+# database filter
+excl <- names(sa_asym) %in% c("run", "ID","density","step","eth_lib_loc","val_con_loc","eth_lib_min","val_con_min")
+dataset_sa <- sa_asym[!excl] %>% filter(val_lib_loc  == 20,eth_con_min == 20, val_lib_min == 20)  %>% 
+ filter(circle_orange == 50) %>%
+  group_by(eth_con_loc,fraction_blue,circle_blue, circle_orange) %>% summarise_all(c("mean"= mean,"sd"= sd))
+
+xlab_t <- "ß ethnic conservative local"
+
+# graph
+
+data_exp <- dataset_sa %>% gather(key= subgroup, value = Expo, et_sq_bl_mean, vl_sq_bl_mean, et_cl_bl_mean, vl_cl_bl_mean, et_sq_or_mean, vl_sq_or_mean, et_cl_or_mean, vl_cl_or_mean) %>% mutate(
+  `segregation` = fct_relevel(fct_collapse(subgroup,"ethnics" = c("et_sq_bl_mean","et_cl_bl_mean","et_sq_or_mean","et_cl_or_mean"), "values" = c("vl_sq_bl_mean","vl_cl_bl_mean","vl_sq_or_mean","vl_cl_or_mean")),"ethnics"),
+ `orientation` = fct_relevel(fct_collapse(subgroup, "conservative" = c("et_sq_bl_mean","vl_sq_bl_mean","et_sq_or_mean","vl_sq_or_mean"), "liberal" = c("et_cl_bl_mean","vl_cl_bl_mean","et_cl_or_mean","vl_cl_or_mean")),"conservative" ),
+ `ethnia` = fct_relevel(fct_collapse(subgroup, "local" = c("et_sq_bl_mean","vl_sq_bl_mean","et_cl_bl_mean","vl_cl_bl_mean"),"minority" = c("et_sq_or_mean","vl_sq_or_mean","et_cl_or_mean","vl_cl_or_mean")), "local"))
+
+exp_eth_con_loc <- ggplot(data = data_exp, aes(x = eth_con_loc, y = Expo, linetype = `segregation` , color = `ethnia`, shape = `orientation`)) + geom_line()  +  geom_point(size = 3) +
+ scale_x_discrete(limits=c(seq(0,20 ,by = 1))) + scale_y_continuous(limits=c(0,1), breaks=seq(0,1,by=0.10)) +
+ #    facet_wrap(~ circle_orange, labeller = labeller(circle_orange = circle_orange.labs)) +
+    geom_vline(xintercept = 20, color = "red") +
+  scale_linetype_manual(values=c("solid","dotted"), labels = c("ethnic","value"), guide = guide_legend(title = "Segregation", order = 1)) +
+  scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
+  scale_shape_manual(values = c("square","circle"), guide = guide_legend(title="Value" ,override.aes = list(size = 3), order = 3)) +
+  xlab(xlab_t) + ylab("Exposure") + 
+  theme_bw() +  theme( axis.title.x = (element_text(size = 15)), axis.title.y = (element_text(size = 15)), axis.text.x =  (element_text(size = 12)),axis.text.y =  (element_text(size = 15)), legend.title = element_text(size = 13) ,legend.text = element_text(size = 13),plot.title=element_text(hjust = 0.5)) + theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
+# ggsave("images/eth_con_loc50.jpg",plot = fig_expo,
+#   device = NULL,path = NULL, 
+#   scale = 1,
+#   width = 8,
+#   height = 6,
+#   units = c("in", "cm", "mm"),
+#   dpi = 300,
+#   limitsize = FALSE)
+
+# database filter
+excl <- names(sa_asym) %in% c("run", "ID","density","step","eth_lib_loc","val_con_loc","eth_lib_min","val_con_min")
+dataset_sa <- sa_asym[!excl] %>% filter(eth_con_loc   == 20,eth_con_min == 20, val_lib_min == 20)  %>% 
+ filter(circle_orange == 50) %>%
+  group_by(val_lib_loc,fraction_blue,circle_blue, circle_orange) %>% summarise_all(c("mean"= mean,"sd"= sd))
+
+xlab_t <- "ß value liberal local"
+
+# graph
+
+data_exp <- dataset_sa %>% gather(key= subgroup, value = Expo, et_sq_bl_mean, vl_sq_bl_mean, et_cl_bl_mean, vl_cl_bl_mean, et_sq_or_mean, vl_sq_or_mean, et_cl_or_mean, vl_cl_or_mean) %>% mutate(
+  `segregation` = fct_relevel(fct_collapse(subgroup,"ethnics" = c("et_sq_bl_mean","et_cl_bl_mean","et_sq_or_mean","et_cl_or_mean"), "values" = c("vl_sq_bl_mean","vl_cl_bl_mean","vl_sq_or_mean","vl_cl_or_mean")),"ethnics"),
+ `orientation` = fct_relevel(fct_collapse(subgroup, "conservative" = c("et_sq_bl_mean","vl_sq_bl_mean","et_sq_or_mean","vl_sq_or_mean"), "liberal" = c("et_cl_bl_mean","vl_cl_bl_mean","et_cl_or_mean","vl_cl_or_mean")),"conservative" ),
+ `ethnia` = fct_relevel(fct_collapse(subgroup, "local" = c("et_sq_bl_mean","vl_sq_bl_mean","et_cl_bl_mean","vl_cl_bl_mean"),"minority" = c("et_sq_or_mean","vl_sq_or_mean","et_cl_or_mean","vl_cl_or_mean")), "local"))
+
+exp_val_lib_loc <- ggplot(data = data_exp, aes(x = val_lib_loc, y = Expo, linetype = `segregation` , color = `ethnia`, shape = `orientation`)) + geom_line()  +  geom_point(size = 3) +
+ scale_x_discrete(limits=c(seq(0,20 ,by = 1)))  + scale_y_continuous(limits=c(0,1), breaks=seq(0,1,by=0.10)) +
+ #    facet_wrap(~ circle_orange, labeller = labeller(circle_orange = circle_orange.labs)) +
+    geom_vline(xintercept = 20, color = "red") +
+  scale_linetype_manual(values=c("solid","dotted"), labels = c("ethnic","value"), guide = guide_legend(title = "Segregation", order = 1)) +
+  scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
+  scale_shape_manual(values = c("square","circle"), guide = guide_legend(title="Value" ,override.aes = list(size = 3), order = 3)) +
+  xlab(xlab_t) + ylab("Exposure") + 
+  theme_bw() +  theme( axis.title.x = (element_text(size = 15)), axis.title.y = (element_text(size = 15)), axis.text.x =  (element_text(size = 12)),axis.text.y =  (element_text(size = 15)), legend.title = element_text(size = 13) ,legend.text = element_text(size = 13),plot.title=element_text(hjust = 0.5)) + theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
+
+# ggsave("images/val_lib_loc50.jpg",plot = fig_expo,
+#   device = NULL,path = NULL, 
+#   scale = 1,
+#   width = 8,
+#   height = 6,
+#   units = c("in", "cm", "mm"),
+#   dpi = 300,
+#   limitsize = FALSE)
+
+# database filter
+excl <- names(sa_asym) %in% c("run", "ID","density","step","eth_lib_loc","val_con_loc","eth_lib_min","val_con_min")
+dataset_sa <- sa_asym[!excl] %>% filter(eth_con_loc   == 20, val_lib_loc  == 20, val_lib_min == 20)  %>% 
+ filter(circle_orange == 50) %>%
+  group_by(eth_con_min,fraction_blue,circle_blue, circle_orange) %>% summarise_all(c("mean"= mean,"sd"= sd))
+
+xlab_t <- "ß ethnic conservative minority"
+
+# graph
+
+data_exp <- dataset_sa %>% gather(key= subgroup, value = Expo, et_sq_bl_mean, vl_sq_bl_mean, et_cl_bl_mean, vl_cl_bl_mean, et_sq_or_mean, vl_sq_or_mean, et_cl_or_mean, vl_cl_or_mean) %>% mutate(
+  `segregation` = fct_relevel(fct_collapse(subgroup,"ethnics" = c("et_sq_bl_mean","et_cl_bl_mean","et_sq_or_mean","et_cl_or_mean"), "values" = c("vl_sq_bl_mean","vl_cl_bl_mean","vl_sq_or_mean","vl_cl_or_mean")),"ethnics"),
+ `orientation` = fct_relevel(fct_collapse(subgroup, "conservative" = c("et_sq_bl_mean","vl_sq_bl_mean","et_sq_or_mean","vl_sq_or_mean"), "liberal" = c("et_cl_bl_mean","vl_cl_bl_mean","et_cl_or_mean","vl_cl_or_mean")),"conservative" ),
+ `ethnia` = fct_relevel(fct_collapse(subgroup, "local" = c("et_sq_bl_mean","vl_sq_bl_mean","et_cl_bl_mean","vl_cl_bl_mean"),"minority" = c("et_sq_or_mean","vl_sq_or_mean","et_cl_or_mean","vl_cl_or_mean")), "local"))
+
+exp_eth_con_min <-  ggplot(data = data_exp, aes(x = eth_con_min, y = Expo, linetype = `segregation` , color = `ethnia`, shape = `orientation`)) + geom_line()  +  geom_point(size = 3) +
+ scale_x_discrete(limits=c(seq(0,20 ,by = 1)))  + scale_y_continuous(limits=c(0,1), breaks=seq(0,1,by=0.10)) +
+ #    facet_wrap(~ circle_orange, labeller = labeller(circle_orange = circle_orange.labs)) +
+    geom_vline(xintercept = 20, color = "red") +
+  scale_linetype_manual(values=c("solid","dotted"), labels = c("ethnic","value"), guide = guide_legend(title = "Segregation", order = 1)) +
+  scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
+  scale_shape_manual(values = c("square","circle"), guide = guide_legend(title="Value" ,override.aes = list(size = 3), order = 3)) +
+  xlab(xlab_t) + ylab("Exposure") + 
+  theme_bw() +  theme( axis.title.x = (element_text(size = 15)), axis.title.y = (element_text(size = 15)), axis.text.x =  (element_text(size = 12)),axis.text.y =  (element_text(size = 15)), legend.title = element_text(size = 13) ,legend.text = element_text(size = 13),plot.title=element_text(hjust = 0.5)) + theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
+
+# ggsave("images/eth_con_min50.jpg",plot = fig_expo,
+#   device = NULL,path = NULL, 
+#   scale = 1,
+#   width = 8,
+#   height = 6,
+#   units = c("in", "cm", "mm"),
+#   dpi = 300,
+#   limitsize = FALSE)
+
+# database filter
+excl <- names(sa_asym) %in% c("run", "ID","density","step","eth_lib_loc","val_con_loc","eth_lib_min","val_con_min")
+dataset_sa <- sa_asym[!excl] %>% filter(eth_con_loc   == 20, val_lib_loc  == 20, eth_con_min  == 20)  %>% 
+ filter(circle_orange == 50) %>%
+  group_by(val_lib_min,fraction_blue,circle_blue, circle_orange) %>% summarise_all(c("mean"= mean,"sd"= sd))
+
+xlab_t <- "ß value liberal minority"
+
+# graph
+
+data_exp <- dataset_sa %>% gather(key= subgroup, value = Expo, et_sq_bl_mean, vl_sq_bl_mean, et_cl_bl_mean, vl_cl_bl_mean, et_sq_or_mean, vl_sq_or_mean, et_cl_or_mean, vl_cl_or_mean) %>% mutate(
+  `segregation` = fct_relevel(fct_collapse(subgroup,"ethnics" = c("et_sq_bl_mean","et_cl_bl_mean","et_sq_or_mean","et_cl_or_mean"), "values" = c("vl_sq_bl_mean","vl_cl_bl_mean","vl_sq_or_mean","vl_cl_or_mean")),"ethnics"),
+ `orientation` = fct_relevel(fct_collapse(subgroup, "conservative" = c("et_sq_bl_mean","vl_sq_bl_mean","et_sq_or_mean","vl_sq_or_mean"), "liberal" = c("et_cl_bl_mean","vl_cl_bl_mean","et_cl_or_mean","vl_cl_or_mean")),"conservative" ),
+ `ethnia` = fct_relevel(fct_collapse(subgroup, "local" = c("et_sq_bl_mean","vl_sq_bl_mean","et_cl_bl_mean","vl_cl_bl_mean"),"minority" = c("et_sq_or_mean","vl_sq_or_mean","et_cl_or_mean","vl_cl_or_mean")), "local"))
+
+exp_val_lib_min <- ggplot(data = data_exp, aes(x = val_lib_min, y = Expo, linetype = `segregation` , color = `ethnia`, shape = `orientation`)) + geom_line()  +  geom_point(size = 3) +
+ scale_x_discrete(limits=c(seq(0,20 ,by = 1)))  + scale_y_continuous(limits=c(0,1), breaks=seq(0,1,by=0.10)) +
+  #    facet_wrap(~ circle_orange, labeller = labeller(circle_orange = circle_orange.labs)) +
+    geom_vline(xintercept = 20, color = "red") +
+  scale_linetype_manual(values=c("solid","dotted"), labels = c("ethnic","value"), guide = guide_legend(title = "Segregation", order = 1)) +
+  scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
+  scale_shape_manual(values = c("square","circle"), guide = guide_legend(title="Value" ,override.aes = list(size = 3), order = 3)) +
+  xlab(xlab_t) + ylab("Exposure") + 
+  theme_bw() +  theme( axis.title.x = (element_text(size = 15)), axis.title.y = (element_text(size = 15)), axis.text.x =  (element_text(size = 12)),axis.text.y =  (element_text(size = 15)), legend.title = element_text(size = 13) ,legend.text = element_text(size = 13),plot.title=element_text(hjust = 0.5)) + theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
+
+ggpubr::ggarrange(exp_eth_con_loc,exp_val_lib_loc,exp_eth_con_min,exp_val_lib_min, nrow = 2, ncol = 2, common.legend = TRUE, legend = "right")
+
+ggsave("images/exp_sa_asym_bt.jpg",plot = last_plot(),
+  device = NULL,path = NULL,
+  scale = 1,
+  width = 11,
+  height = 8,
+  units = c("in", "cm", "mm"),
+  dpi = 300,
+  limitsize = FALSE)
+
+```
+
+```{r sa_etcnlc,  fig.cap="Sensitivity proximity ethnic conservative local, distribution liberals", echo=FALSE}
+
+# database filter
+excl <- names(sa_asym) %in% c("run", "ID","density","step","eth_lib_loc","val_con_loc","eth_lib_min","val_con_min")
+dataset_sa <- sa_asym[!excl] %>% filter(val_lib_loc  == 20,eth_con_min == 20, val_lib_min == 20)  %>% 
+group_by(eth_con_loc,fraction_blue,circle_blue, circle_orange) %>% summarise_all(c("mean"= mean,"sd"= sd))
+
+plotname <- "images/etcnlc.jpg"
+xlab_t <- "ß ethnic conservative local"
+
+xvalues <- c(dataset_sa$de_sq_bl_mean,dataset_sa$de_cl_bl_mean,dataset_sa$de_sq_or_mean,dataset_sa$de_cl_or_mean,
+       dataset_sa$dv_sq_bl_mean,dataset_sa$dv_cl_bl_mean,dataset_sa$dv_sq_or_mean,dataset_sa$dv_cl_or_mean)
+
+ expo_pic <-   ggplot(data = dataset_sa) + 
+  geom_point(aes(x = dataset_sa$de_sq_bl_mean, y = dataset_sa$et_sq_bl_mean),color = "black", fill = "blue", shape = 22, size = 5) +
+  geom_point(aes(x = dataset_sa$de_cl_bl_mean, y = dataset_sa$et_cl_bl_mean),color = "black",fill = "blue", shape = 21, size = 5) +
+  geom_point(aes(x = dataset_sa$de_sq_or_mean, y = dataset_sa$et_sq_or_mean),color = "black", fill = "orange", shape = 22, size = 5) +
+  geom_point(aes(x = dataset_sa$de_cl_or_mean, y = dataset_sa$et_cl_or_mean),color = "black", fill = "orange", shape = 21, size = 5) +
+
+  geom_point(aes(x = dataset_sa$dv_sq_bl_mean, y = dataset_sa$vl_sq_bl_mean),color = "black", fill = "blue", shape = 8, size = 5.1) + 
+   geom_point(aes(x = dataset_sa$dv_sq_bl_mean, y = dataset_sa$vl_sq_bl_mean),color = "black", fill = "blue", shape = 22, size = 5) +
+
+   geom_point(aes(x = dataset_sa$dv_cl_bl_mean, y = dataset_sa$vl_cl_bl_mean),color = "black",fill = "blue", shape = 8, size = 5.1) + 
+  geom_point(aes(x = dataset_sa$dv_cl_bl_mean, y = dataset_sa$vl_cl_bl_mean),color = "black",fill = "blue", shape = 21, size = 5) +
+
+    geom_point(aes(x = dataset_sa$dv_sq_or_mean, y = dataset_sa$vl_sq_or_mean),color = "black", fill = "orange", shape = 8, size = 5.1) +
+  geom_point(aes(x = dataset_sa$dv_sq_or_mean, y = dataset_sa$vl_sq_or_mean),color = "black", fill = "orange", shape = 22, size = 5) +
+
+  geom_point(aes(x = dataset_sa$dv_cl_or_mean, y = dataset_sa$vl_cl_or_mean),color = "black", fill = "orange", shape = 8, size = 5.1) +
+geom_point(aes(x = dataset_sa$dv_cl_or_mean, y = dataset_sa$vl_cl_or_mean),color = "black", fill = "orange", shape = 21, size = 5) +
+
+ scale_x_continuous(limits = c(min(xvalues),max(xvalues)), breaks = seq(0,max(xvalues), by = 0.5)) + 
+  scale_y_continuous(breaks= seq(0,1,by=0.1)) + 
+  geom_vline(xintercept = 1, color = "red") +
+  xlab("Spatial proximity") + ylab("Exposure") +
+  theme_bw()
+
+data_prox <- dataset_sa  %>% gather(key= subgroup, value = Prox, de_sq_bl_mean, dv_sq_bl_mean, de_cl_bl_mean, dv_cl_bl_mean, de_sq_or_mean, dv_sq_or_mean, de_cl_or_mean, dv_cl_or_mean) %>% mutate(
+  `segregation` = fct_relevel(fct_collapse(subgroup,"ethnics" = c("de_sq_bl_mean","de_cl_bl_mean","de_sq_or_mean","de_cl_or_mean"), "values" = c("dv_sq_bl_mean","dv_cl_bl_mean","dv_sq_or_mean","dv_cl_or_mean")),"ethnics"),
+ `orientation` = fct_relevel(fct_collapse(subgroup, "conservative" = c("de_sq_bl_mean","dv_sq_bl_mean","de_sq_or_mean","dv_sq_or_mean"), "liberal" = c("de_cl_bl_mean","dv_cl_bl_mean","de_cl_or_mean","dv_cl_or_mean")),"conservative" ),
+ `ethnia` = fct_relevel(fct_collapse(subgroup, "local" = c("de_sq_bl_mean","dv_sq_bl_mean","de_cl_bl_mean","dv_cl_bl_mean"),"minority" = c("de_sq_or_mean","dv_sq_or_mean","de_cl_or_mean","dv_cl_or_mean")), "local"))
+
+plot_50 <- ggplot(data = subset(data_prox, circle_orange == 50), aes(x = eth_con_loc, y = Prox, linetype = `segregation` , color = `ethnia`, shape = `orientation`)) + geom_line()  +  geom_point(size = 3) +
+ scale_x_discrete(limits=c(seq(0,20 ,by = 1))) + scale_y_continuous(limits=c(min(data_prox$Prox),max(data_prox$Prox)), breaks=seq(0,max(data_prox$Prox),by=0.50)) +
+# facet_wrap(~ circle_orange, ncol = 2, nrow = 2, labeller = labeller(circle_orange = circle_orange.labs)) +
+    geom_vline(xintercept = 20, color = "red") +
+  geom_hline(yintercept = 1, color = "red") +
+  scale_linetype_manual(values=c("solid","dashed"), labels = c("ethnic","value"), guide = guide_legend(title = "Segregation", order = 1)) +
+  scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
+  scale_shape_manual(values = c("square","circle"), guide = guide_legend(title="Value" ,override.aes = list(size = 3), order = 3)) +
+  xlab(xlab_t) + ylab("Spatial Proximity") + 
+  theme_bw() +  theme( axis.title.x = (element_text(size = 13)), axis.title.y = (element_text(size = 15)), axis.text.x =  (element_text(size = 12)),axis.text.y =  (element_text(size = 15)), legend.title = element_text(size = 13),legend.position = "bottom", legend.text = element_text(size = 13),plot.title=element_text(hjust = 0.5), plot.caption = element_text(hjust= 0.5, size = 11)) + theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm")) +
+ labs( caption = paste0(subset(data_prox, circle_orange == 50)$circle_orange,"% liberal migrants"))
+
+plot_20 <- ggplot(data = subset(data_prox, circle_orange == 20), aes(x = eth_con_loc, y = Prox, linetype = `segregation` , color = `ethnia`, shape = `orientation`)) + geom_line()  +  geom_point(size = 3) +
+ scale_x_discrete(limits=c(seq(0,20 ,by = 1))) + scale_y_continuous(limits=c(min(data_prox$Prox),max(data_prox$Prox)), breaks=seq(0,max(data_prox$Prox),by=0.50)) +
+# facet_wrap(~ circle_orange, ncol = 2, nrow = 2, labeller = labeller(circle_orange = circle_orange.labs)) +
+    geom_vline(xintercept = 20, color = "red") +
+    geom_hline(yintercept = 1, color = "red") +
+  scale_linetype_manual(values=c("solid","dashed"), labels = c("ethnic","value"), guide = guide_legend(title = "Segregation", order = 1)) +
+  scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
+  scale_shape_manual(values = c("square","circle"), guide = guide_legend(title="Value" ,override.aes = list(size = 3), order = 3)) +
+  xlab(xlab_t) + ylab("Spatial Proximity") + 
+  theme_bw() +  theme( axis.title.x = (element_text(size = 13)), axis.title.y = (element_text(size = 15)), axis.text.x =  (element_text(size = 12)),axis.text.y =  (element_text(size = 15)), legend.title = element_text(size = 13),legend.position = "bottom", legend.text = element_text(size = 13),plot.title=element_text(hjust = 0.5), plot.caption = element_text(hjust= 0.5, size = 11)) + theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm")) +
+ labs( caption = paste0(subset(data_prox, circle_orange == 20)$circle_orange,"% liberal migrants"))
+
+plot_80 <- ggplot(data = subset(data_prox, circle_orange == 80), aes(x = eth_con_loc, y = Prox, linetype = `segregation` , color = `ethnia`, shape = `orientation`)) + geom_line()  +  geom_point(size = 3) +
+ scale_x_discrete(limits=c(seq(0,20 ,by = 1))) + scale_y_continuous(limits=c(min(data_prox$Prox),max(data_prox$Prox)), breaks=seq(0,max(data_prox$Prox),by=0.50)) +
+# facet_wrap(~ circle_orange, ncol = 2, nrow = 2, labeller = labeller(circle_orange = circle_orange.labs)) +
+    geom_vline(xintercept = 20, color = "red") +
+    geom_hline(yintercept = 1, color = "red") +
+  scale_linetype_manual(values=c("solid","dashed"), labels = c("ethnic","value"), guide = guide_legend(title = "Segregation", order = 1)) +
+  scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
+  scale_shape_manual(values = c("square","circle"), guide = guide_legend(title="Value" ,override.aes = list(size = 3), order = 3)) +
+  xlab(xlab_t) + ylab("Spatial Proximity") + 
+  theme_bw() +  theme( axis.title.x = (element_text(size = 13)), axis.title.y = (element_text(size = 15)), axis.text.x =  (element_text(size = 12)),axis.text.y =  (element_text(size = 15)), legend.title = element_text(size = 13),legend.position = "bottom", legend.text = element_text(size = 13),plot.title=element_text(hjust = 0.5), plot.caption = element_text(hjust= 0.5, size = 11)) + theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm")) +
+ labs( caption = paste0(subset(data_prox, circle_orange == 80)$circle_orange,"% liberal migrants"))
+
+ggpubr::ggarrange(plot_50,plot_80,plot_20,expo_pic, nrow = 2, ncol = 2, common.legend = TRUE, legend = "bottom")
+
+ggsave(plotname,plot = last_plot(),
+  device = NULL,path = NULL,
+  scale = 1,
+  width = 11,
+  height = 8,
+  units = c("in", "cm", "mm"),
+  dpi = 300,
+  limitsize = FALSE)
+
+```
+
+```{r sa_vllblc,  fig.cap="Sensitivity proximity value liberal locals, distribution liberals", echo=FALSE}
+
+# database filter
+excl <- names(sa_asym) %in% c("run", "ID","density","step","eth_lib_loc","val_con_loc","eth_lib_min","val_con_min")
+dataset_sa <- sa_asym[!excl] %>% filter(eth_con_loc  == 20,eth_con_min == 20, val_lib_min == 20)  %>% 
+group_by(val_lib_loc,fraction_blue,circle_blue, circle_orange) %>% summarise_all(c("mean"= mean,"sd"= sd))
+
+plotname <- "images/vllblc.jpg"
+xlab_t <- "ß value liberal local"
+
+xvalues <- c(dataset_sa$de_sq_bl_mean,dataset_sa$de_cl_bl_mean,dataset_sa$de_sq_or_mean,dataset_sa$de_cl_or_mean,
+       dataset_sa$dv_sq_bl_mean,dataset_sa$dv_cl_bl_mean,dataset_sa$dv_sq_or_mean,dataset_sa$dv_cl_or_mean)
+
+ expo_pic <-   ggplot(data = dataset_sa) + 
+  geom_point(aes(x = dataset_sa$de_sq_bl_mean, y = dataset_sa$et_sq_bl_mean),color = "black", fill = "blue", shape = 22, size = 5) +
+  geom_point(aes(x = dataset_sa$de_cl_bl_mean, y = dataset_sa$et_cl_bl_mean),color = "black",fill = "blue", shape = 21, size = 5) +
+  geom_point(aes(x = dataset_sa$de_sq_or_mean, y = dataset_sa$et_sq_or_mean),color = "black", fill = "orange", shape = 22, size = 5) +
+  geom_point(aes(x = dataset_sa$de_cl_or_mean, y = dataset_sa$et_cl_or_mean),color = "black", fill = "orange", shape = 21, size = 5) +
+
+  geom_point(aes(x = dataset_sa$dv_sq_bl_mean, y = dataset_sa$vl_sq_bl_mean),color = "black", fill = "blue", shape = 8, size = 5.1) + 
+   geom_point(aes(x = dataset_sa$dv_sq_bl_mean, y = dataset_sa$vl_sq_bl_mean),color = "black", fill = "blue", shape = 22, size = 5) +
+
+   geom_point(aes(x = dataset_sa$dv_cl_bl_mean, y = dataset_sa$vl_cl_bl_mean),color = "black",fill = "blue", shape = 8, size = 5.1) + 
+  geom_point(aes(x = dataset_sa$dv_cl_bl_mean, y = dataset_sa$vl_cl_bl_mean),color = "black",fill = "blue", shape = 21, size = 5) +
+
+    geom_point(aes(x = dataset_sa$dv_sq_or_mean, y = dataset_sa$vl_sq_or_mean),color = "black", fill = "orange", shape = 8, size = 5.1) +
+  geom_point(aes(x = dataset_sa$dv_sq_or_mean, y = dataset_sa$vl_sq_or_mean),color = "black", fill = "orange", shape = 22, size = 5) +
+
+  geom_point(aes(x = dataset_sa$dv_cl_or_mean, y = dataset_sa$vl_cl_or_mean),color = "black", fill = "orange", shape = 8, size = 5.1) +
+geom_point(aes(x = dataset_sa$dv_cl_or_mean, y = dataset_sa$vl_cl_or_mean),color = "black", fill = "orange", shape = 21, size = 5) +
+
+ scale_x_continuous(limits = c(min(xvalues),max(xvalues)), breaks = seq(0,max(xvalues), by = 0.5)) + 
+  scale_y_continuous(breaks= seq(0,1,by=0.1)) + 
+  geom_vline(xintercept = 1, color = "red") +
+  xlab("Spatial proximity") + ylab("Exposure") +
+  theme_bw()
+
+data_prox <- dataset_sa  %>% gather(key= subgroup, value = Prox, de_sq_bl_mean, dv_sq_bl_mean, de_cl_bl_mean, dv_cl_bl_mean, de_sq_or_mean, dv_sq_or_mean, de_cl_or_mean, dv_cl_or_mean) %>% mutate(
+  `segregation` = fct_relevel(fct_collapse(subgroup,"ethnics" = c("de_sq_bl_mean","de_cl_bl_mean","de_sq_or_mean","de_cl_or_mean"), "values" = c("dv_sq_bl_mean","dv_cl_bl_mean","dv_sq_or_mean","dv_cl_or_mean")),"ethnics"),
+ `orientation` = fct_relevel(fct_collapse(subgroup, "conservative" = c("de_sq_bl_mean","dv_sq_bl_mean","de_sq_or_mean","dv_sq_or_mean"), "liberal" = c("de_cl_bl_mean","dv_cl_bl_mean","de_cl_or_mean","dv_cl_or_mean")),"conservative" ),
+ `ethnia` = fct_relevel(fct_collapse(subgroup, "local" = c("de_sq_bl_mean","dv_sq_bl_mean","de_cl_bl_mean","dv_cl_bl_mean"),"minority" = c("de_sq_or_mean","dv_sq_or_mean","de_cl_or_mean","dv_cl_or_mean")), "local"))
+
+plot_50 <- ggplot(data = subset(data_prox, circle_orange == 50), aes(x = val_lib_loc, y = Prox, linetype = `segregation` , color = `ethnia`, shape = `orientation`)) + geom_line()  +  geom_point(size = 3) +
+ scale_x_discrete(limits=c(seq(0,20 ,by = 1))) + scale_y_continuous(limits=c(min(data_prox$Prox),max(data_prox$Prox)), breaks=seq(0,max(data_prox$Prox),by=0.50)) +
+# facet_wrap(~ circle_orange, ncol = 2, nrow = 2, labeller = labeller(circle_orange = circle_orange.labs)) +
+    geom_vline(xintercept = 20, color = "red") +  geom_hline(yintercept = 1, color = "red") +
+  scale_linetype_manual(values=c("solid","dashed"), labels = c("ethnic","value"), guide = guide_legend(title = "Segregation", order = 1)) +
+  scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
+  scale_shape_manual(values = c("square","circle"), guide = guide_legend(title="Value" ,override.aes = list(size = 3), order = 3)) +
+  xlab(xlab_t) + ylab("Spatial Proximity") + 
+  theme_bw() +  theme( axis.title.x = (element_text(size = 13)), axis.title.y = (element_text(size = 15)), axis.text.x =  (element_text(size = 12)),axis.text.y =  (element_text(size = 15)), legend.title = element_text(size = 13),legend.position = "bottom", legend.text = element_text(size = 13),plot.title=element_text(hjust = 0.5), plot.caption = element_text(hjust= 0.5, size = 11)) + theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm")) +
+ labs( caption = paste0(subset(data_prox, circle_orange == 50)$circle_orange,"% liberal migrants"))
+
+plot_20 <- ggplot(data = subset(data_prox, circle_orange == 20), aes(x = val_lib_loc, y = Prox, linetype = `segregation` , color = `ethnia`, shape = `orientation`)) + geom_line()  +  geom_point(size = 3) +
+ scale_x_discrete(limits=c(seq(0,20 ,by = 1))) + scale_y_continuous(limits=c(min(data_prox$Prox),max(data_prox$Prox)), breaks=seq(0,max(data_prox$Prox),by=0.50)) +
+# facet_wrap(~ circle_orange, ncol = 2, nrow = 2, labeller = labeller(circle_orange = circle_orange.labs)) +
+    geom_vline(xintercept = 20, color = "red") +  geom_hline(yintercept = 1, color = "red") +
+  scale_linetype_manual(values=c("solid","dashed"), labels = c("ethnic","value"), guide = guide_legend(title = "Segregation", order = 1)) +
+  scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
+  scale_shape_manual(values = c("square","circle"), guide = guide_legend(title="Value" ,override.aes = list(size = 3), order = 3)) +
+  xlab(xlab_t) + ylab("Spatial Proximity") + 
+  theme_bw() +  theme( axis.title.x = (element_text(size = 13)), axis.title.y = (element_text(size = 15)), axis.text.x =  (element_text(size = 12)),axis.text.y =  (element_text(size = 15)), legend.title = element_text(size = 13),legend.position = "bottom", legend.text = element_text(size = 13),plot.title=element_text(hjust = 0.5), plot.caption = element_text(hjust= 0.5, size = 11)) + theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm")) +
+ labs( caption = paste0(subset(data_prox, circle_orange == 20)$circle_orange,"% liberal migrants"))
+
+plot_80 <- ggplot(data = subset(data_prox, circle_orange == 80), aes(x = val_lib_loc, y = Prox, linetype = `segregation` , color = `ethnia`, shape = `orientation`)) + geom_line()  +  geom_point(size = 3) +
+ scale_x_discrete(limits=c(seq(0,20 ,by = 1))) + scale_y_continuous(limits=c(min(data_prox$Prox),max(data_prox$Prox)), breaks=seq(0,max(data_prox$Prox),by=0.50)) +
+# facet_wrap(~ circle_orange, ncol = 2, nrow = 2, labeller = labeller(circle_orange = circle_orange.labs)) +
+    geom_vline(xintercept = 20, color = "red") +  geom_hline(yintercept = 1, color = "red") +
+  scale_linetype_manual(values=c("solid","dashed"), labels = c("ethnic","value"), guide = guide_legend(title = "Segregation", order = 1)) +
+  scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
+  scale_shape_manual(values = c("square","circle"), guide = guide_legend(title="Value" ,override.aes = list(size = 3), order = 3)) +
+  xlab(xlab_t) + ylab("Spatial Proximity") + 
+  theme_bw() +  theme( axis.title.x = (element_text(size = 13)), axis.title.y = (element_text(size = 15)), axis.text.x =  (element_text(size = 12)),axis.text.y =  (element_text(size = 15)), legend.title = element_text(size = 13),legend.position = "bottom", legend.text = element_text(size = 13),plot.title=element_text(hjust = 0.5), plot.caption = element_text(hjust= 0.5, size = 11)) + theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm")) +
+ labs( caption = paste0(subset(data_prox, circle_orange == 80)$circle_orange,"% liberal migrants"))
+
+ggpubr::ggarrange(plot_50,plot_80,plot_20,expo_pic, nrow = 2, ncol = 2, common.legend = TRUE, legend = "bottom")
+
+ggsave(plotname,plot = last_plot(),
+  device = NULL,path = NULL,
+  scale = 1,
+  width = 11,
+  height = 8,
+  units = c("in", "cm", "mm"),
+  dpi = 300,
+  limitsize = FALSE)
+
+```
+
+```{r sa_etcnmn,  fig.cap="Sensitivity proximity ethnic conservative minority, distribution liberals", echo=FALSE}
+
+# database filter
+excl <- names(sa_asym) %in% c("run", "ID","density","step","eth_lib_loc","val_con_loc","eth_lib_min","val_con_min")
+dataset_sa <- sa_asym[!excl] %>% filter(eth_con_loc  == 20,val_lib_loc == 20, val_lib_min == 20)  %>% 
+group_by(eth_con_min ,fraction_blue,circle_blue, circle_orange) %>% summarise_all(c("mean"= mean,"sd"= sd))
+
+plotname <- "images/etcnmn.jpg"
+xlab_t <- "ß ethnic conservative minority"
+
+xvalues <- c(dataset_sa$de_sq_bl_mean,dataset_sa$de_cl_bl_mean,dataset_sa$de_sq_or_mean,dataset_sa$de_cl_or_mean,
+       dataset_sa$dv_sq_bl_mean,dataset_sa$dv_cl_bl_mean,dataset_sa$dv_sq_or_mean,dataset_sa$dv_cl_or_mean)
+
+ expo_pic <-   ggplot(data = dataset_sa) + 
+  geom_point(aes(x = dataset_sa$de_sq_bl_mean, y = dataset_sa$et_sq_bl_mean),color = "black", fill = "blue", shape = 22, size = 5) +
+  geom_point(aes(x = dataset_sa$de_cl_bl_mean, y = dataset_sa$et_cl_bl_mean),color = "black",fill = "blue", shape = 21, size = 5) +
+  geom_point(aes(x = dataset_sa$de_sq_or_mean, y = dataset_sa$et_sq_or_mean),color = "black", fill = "orange", shape = 22, size = 5) +
+  geom_point(aes(x = dataset_sa$de_cl_or_mean, y = dataset_sa$et_cl_or_mean),color = "black", fill = "orange", shape = 21, size = 5) +
+
+  geom_point(aes(x = dataset_sa$dv_sq_bl_mean, y = dataset_sa$vl_sq_bl_mean),color = "black", fill = "blue", shape = 8, size = 5.1) + 
+   geom_point(aes(x = dataset_sa$dv_sq_bl_mean, y = dataset_sa$vl_sq_bl_mean),color = "black", fill = "blue", shape = 22, size = 5) +
+
+   geom_point(aes(x = dataset_sa$dv_cl_bl_mean, y = dataset_sa$vl_cl_bl_mean),color = "black",fill = "blue", shape = 8, size = 5.1) + 
+  geom_point(aes(x = dataset_sa$dv_cl_bl_mean, y = dataset_sa$vl_cl_bl_mean),color = "black",fill = "blue", shape = 21, size = 5) +
+
+    geom_point(aes(x = dataset_sa$dv_sq_or_mean, y = dataset_sa$vl_sq_or_mean),color = "black", fill = "orange", shape = 8, size = 5.1) +
+  geom_point(aes(x = dataset_sa$dv_sq_or_mean, y = dataset_sa$vl_sq_or_mean),color = "black", fill = "orange", shape = 22, size = 5) +
+
+  geom_point(aes(x = dataset_sa$dv_cl_or_mean, y = dataset_sa$vl_cl_or_mean),color = "black", fill = "orange", shape = 8, size = 5.1) +
+geom_point(aes(x = dataset_sa$dv_cl_or_mean, y = dataset_sa$vl_cl_or_mean),color = "black", fill = "orange", shape = 21, size = 5) +
+
+ scale_x_continuous(limits = c(min(xvalues),max(xvalues)), breaks = seq(0,max(xvalues), by = 0.5)) + 
+  scale_y_continuous(breaks= seq(0,1,by=0.1)) + 
+  geom_vline(xintercept = 1, color = "red") +
+  xlab("Spatial proximity") + ylab("Exposure") +
+  theme_bw()
+
+data_prox <- dataset_sa  %>% gather(key= subgroup, value = Prox, de_sq_bl_mean, dv_sq_bl_mean, de_cl_bl_mean, dv_cl_bl_mean, de_sq_or_mean, dv_sq_or_mean, de_cl_or_mean, dv_cl_or_mean) %>% mutate(
+  `segregation` = fct_relevel(fct_collapse(subgroup,"ethnics" = c("de_sq_bl_mean","de_cl_bl_mean","de_sq_or_mean","de_cl_or_mean"), "values" = c("dv_sq_bl_mean","dv_cl_bl_mean","dv_sq_or_mean","dv_cl_or_mean")),"ethnics"),
+ `orientation` = fct_relevel(fct_collapse(subgroup, "conservative" = c("de_sq_bl_mean","dv_sq_bl_mean","de_sq_or_mean","dv_sq_or_mean"), "liberal" = c("de_cl_bl_mean","dv_cl_bl_mean","de_cl_or_mean","dv_cl_or_mean")),"conservative" ),
+ `ethnia` = fct_relevel(fct_collapse(subgroup, "local" = c("de_sq_bl_mean","dv_sq_bl_mean","de_cl_bl_mean","dv_cl_bl_mean"),"minority" = c("de_sq_or_mean","dv_sq_or_mean","de_cl_or_mean","dv_cl_or_mean")), "local"))
+
+plot_50 <- ggplot(data = subset(data_prox, circle_orange == 50), aes(x = eth_con_min, y = Prox, linetype = `segregation` , color = `ethnia`, shape = `orientation`)) + geom_line()  +  geom_point(size = 3) +
+ scale_x_discrete(limits=c(seq(0,20 ,by = 1))) + scale_y_continuous(limits=c(min(data_prox$Prox),max(data_prox$Prox)), breaks=seq(0,max(data_prox$Prox),by=0.50)) +
+# facet_wrap(~ circle_orange, ncol = 2, nrow = 2, labeller = labeller(circle_orange = circle_orange.labs)) +
+    geom_vline(xintercept = 20, color = "red") +  geom_hline(yintercept = 1, color = "red") +
+  scale_linetype_manual(values=c("solid","dashed"), labels = c("ethnic","value"), guide = guide_legend(title = "Segregation", order = 1)) +
+  scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
+  scale_shape_manual(values = c("square","circle"), guide = guide_legend(title="Value" ,override.aes = list(size = 3), order = 3)) +
+  xlab(xlab_t) + ylab("Spatial Proximity") + 
+  theme_bw() +  theme( axis.title.x = (element_text(size = 13)), axis.title.y = (element_text(size = 15)), axis.text.x =  (element_text(size = 12)),axis.text.y =  (element_text(size = 15)), legend.title = element_text(size = 13),legend.position = "bottom", legend.text = element_text(size = 13),plot.title=element_text(hjust = 0.5), plot.caption = element_text(hjust= 0.5, size = 11)) + theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm")) +
+ labs( caption = paste0(subset(data_prox, circle_orange == 50)$circle_orange,"% liberal migrants"))
+
+plot_20 <- ggplot(data = subset(data_prox, circle_orange == 20), aes(x = eth_con_min, y = Prox, linetype = `segregation` , color = `ethnia`, shape = `orientation`)) + geom_line()  +  geom_point(size = 3) +
+ scale_x_discrete(limits=c(seq(0,20 ,by = 1))) + scale_y_continuous(limits=c(min(data_prox$Prox),max(data_prox$Prox)), breaks=seq(0,max(data_prox$Prox),by=0.50)) +
+# facet_wrap(~ circle_orange, ncol = 2, nrow = 2, labeller = labeller(circle_orange = circle_orange.labs)) +
+    geom_vline(xintercept = 20, color = "red") +  geom_hline(yintercept = 1, color = "red") +
+  scale_linetype_manual(values=c("solid","dashed"), labels = c("ethnic","value"), guide = guide_legend(title = "Segregation", order = 1)) +
+  scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
+  scale_shape_manual(values = c("square","circle"), guide = guide_legend(title="Value" ,override.aes = list(size = 3), order = 3)) +
+  xlab(xlab_t) + ylab("Spatial Proximity") + 
+  theme_bw() +  theme( axis.title.x = (element_text(size = 13)), axis.title.y = (element_text(size = 15)), axis.text.x =  (element_text(size = 12)),axis.text.y =  (element_text(size = 15)), legend.title = element_text(size = 13),legend.position = "bottom", legend.text = element_text(size = 13),plot.title=element_text(hjust = 0.5), plot.caption = element_text(hjust= 0.5, size = 11)) + theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm")) +
+ labs( caption = paste0(subset(data_prox, circle_orange == 20)$circle_orange,"% liberal migrants"))
+
+plot_80 <- ggplot(data = subset(data_prox, circle_orange == 80), aes(x = eth_con_min, y = Prox, linetype = `segregation` , color = `ethnia`, shape = `orientation`)) + geom_line()  +  geom_point(size = 3) +
+ scale_x_discrete(limits=c(seq(0,20 ,by = 1))) + scale_y_continuous(limits=c(min(data_prox$Prox),max(data_prox$Prox)), breaks=seq(0,max(data_prox$Prox),by=0.50)) +
+# facet_wrap(~ circle_orange, ncol = 2, nrow = 2, labeller = labeller(circle_orange = circle_orange.labs)) +
+    geom_vline(xintercept = 20, color = "red") +  geom_hline(yintercept = 1, color = "red") +
+  scale_linetype_manual(values=c("solid","dashed"), labels = c("ethnic","value"), guide = guide_legend(title = "Segregation", order = 1)) +
+  scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
+  scale_shape_manual(values = c("square","circle"), guide = guide_legend(title="Value" ,override.aes = list(size = 3), order = 3)) +
+  xlab(xlab_t) + ylab("Spatial Proximity") + 
+  theme_bw() +  theme( axis.title.x = (element_text(size = 13)), axis.title.y = (element_text(size = 15)), axis.text.x =  (element_text(size = 12)),axis.text.y =  (element_text(size = 15)), legend.title = element_text(size = 13),legend.position = "bottom", legend.text = element_text(size = 13),plot.title=element_text(hjust = 0.5), plot.caption = element_text(hjust= 0.5, size = 11)) + theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm")) +
+ labs( caption = paste0(subset(data_prox, circle_orange == 80)$circle_orange,"% liberal migrants"))
+
+ggpubr::ggarrange(plot_50,plot_80,plot_20,expo_pic, nrow = 2, ncol = 2, common.legend = TRUE, legend = "bottom")
+
+ggsave(plotname,plot = last_plot(),
+  device = NULL,path = NULL,
+  scale = 1,
+  width = 11,
+  height = 8,
+  units = c("in", "cm", "mm"),
+  dpi = 300,
+  limitsize = FALSE)
+
+```
+
+```{r sa_vllbmn,  fig.cap="Sensitivity proximity value liberal minority, distribution liberals", echo=FALSE}
+
+# database filter
+excl <- names(sa_asym) %in% c("run", "ID","density","step","eth_lib_loc","val_con_loc","eth_lib_min","val_con_min")
+dataset_sa <- sa_asym[!excl] %>% filter(eth_con_loc  == 20,val_lib_loc == 20,eth_con_min  == 20)  %>% 
+group_by(val_lib_min ,fraction_blue,circle_blue, circle_orange) %>% summarise_all(c("mean"= mean,"sd"= sd))
+
+plotname <- "images/vllbmn.jpg"
+xlab_t <- "ß value liberal minority"
+
+xvalues <- c(dataset_sa$de_sq_bl_mean,dataset_sa$de_cl_bl_mean,dataset_sa$de_sq_or_mean,dataset_sa$de_cl_or_mean,
+       dataset_sa$dv_sq_bl_mean,dataset_sa$dv_cl_bl_mean,dataset_sa$dv_sq_or_mean,dataset_sa$dv_cl_or_mean)
+
+ expo_pic <-   ggplot(data = dataset_sa) + 
+  geom_point(aes(x = dataset_sa$de_sq_bl_mean, y = dataset_sa$et_sq_bl_mean),color = "black", fill = "blue", shape = 22, size = 5) +
+  geom_point(aes(x = dataset_sa$de_cl_bl_mean, y = dataset_sa$et_cl_bl_mean),color = "black",fill = "blue", shape = 21, size = 5) +
+  geom_point(aes(x = dataset_sa$de_sq_or_mean, y = dataset_sa$et_sq_or_mean),color = "black", fill = "orange", shape = 22, size = 5) +
+  geom_point(aes(x = dataset_sa$de_cl_or_mean, y = dataset_sa$et_cl_or_mean),color = "black", fill = "orange", shape = 21, size = 5) +
+
+  geom_point(aes(x = dataset_sa$dv_sq_bl_mean, y = dataset_sa$vl_sq_bl_mean),color = "black", fill = "blue", shape = 8, size = 5.1) + 
+   geom_point(aes(x = dataset_sa$dv_sq_bl_mean, y = dataset_sa$vl_sq_bl_mean),color = "black", fill = "blue", shape = 22, size = 5) +
+
+   geom_point(aes(x = dataset_sa$dv_cl_bl_mean, y = dataset_sa$vl_cl_bl_mean),color = "black",fill = "blue", shape = 8, size = 5.1) + 
+  geom_point(aes(x = dataset_sa$dv_cl_bl_mean, y = dataset_sa$vl_cl_bl_mean),color = "black",fill = "blue", shape = 21, size = 5) +
+
+    geom_point(aes(x = dataset_sa$dv_sq_or_mean, y = dataset_sa$vl_sq_or_mean),color = "black", fill = "orange", shape = 8, size = 5.1) +
+  geom_point(aes(x = dataset_sa$dv_sq_or_mean, y = dataset_sa$vl_sq_or_mean),color = "black", fill = "orange", shape = 22, size = 5) +
+
+  geom_point(aes(x = dataset_sa$dv_cl_or_mean, y = dataset_sa$vl_cl_or_mean),color = "black", fill = "orange", shape = 8, size = 5.1) +
+geom_point(aes(x = dataset_sa$dv_cl_or_mean, y = dataset_sa$vl_cl_or_mean),color = "black", fill = "orange", shape = 21, size = 5) +
+
+ scale_x_continuous(limits = c(min(xvalues),max(xvalues)), breaks = seq(0,max(xvalues), by = 0.5)) + 
+  scale_y_continuous(breaks= seq(0,1,by=0.1)) + 
+  geom_vline(xintercept = 1, color = "red") +
+  xlab("Spatial proximity") + ylab("Exposure") +
+  theme_bw()
+
+data_prox <- dataset_sa  %>% gather(key= subgroup, value = Prox, de_sq_bl_mean, dv_sq_bl_mean, de_cl_bl_mean, dv_cl_bl_mean, de_sq_or_mean, dv_sq_or_mean, de_cl_or_mean, dv_cl_or_mean) %>% mutate(
+  `segregation` = fct_relevel(fct_collapse(subgroup,"ethnics" = c("de_sq_bl_mean","de_cl_bl_mean","de_sq_or_mean","de_cl_or_mean"), "values" = c("dv_sq_bl_mean","dv_cl_bl_mean","dv_sq_or_mean","dv_cl_or_mean")),"ethnics"),
+ `orientation` = fct_relevel(fct_collapse(subgroup, "conservative" = c("de_sq_bl_mean","dv_sq_bl_mean","de_sq_or_mean","dv_sq_or_mean"), "liberal" = c("de_cl_bl_mean","dv_cl_bl_mean","de_cl_or_mean","dv_cl_or_mean")),"conservative" ),
+ `ethnia` = fct_relevel(fct_collapse(subgroup, "local" = c("de_sq_bl_mean","dv_sq_bl_mean","de_cl_bl_mean","dv_cl_bl_mean"),"minority" = c("de_sq_or_mean","dv_sq_or_mean","de_cl_or_mean","dv_cl_or_mean")), "local"))
+
+plot_50 <- ggplot(data = subset(data_prox, circle_orange == 50), aes(x = val_lib_min, y = Prox, linetype = `segregation` , color = `ethnia`, shape = `orientation`)) + geom_line()  +  geom_point(size = 3) +
+ scale_x_discrete(limits=c(seq(0,20 ,by = 1))) + scale_y_continuous(limits=c(min(data_prox$Prox),max(data_prox$Prox)), breaks=seq(0,max(data_prox$Prox),by=0.50)) +
+# facet_wrap(~ circle_orange, ncol = 2, nrow = 2, labeller = labeller(circle_orange = circle_orange.labs)) +
+    geom_vline(xintercept = 20, color = "red") +  geom_hline(yintercept = 1, color = "red") +
+  scale_linetype_manual(values=c("solid","dashed"), labels = c("ethnic","value"), guide = guide_legend(title = "Segregation", order = 1)) +
+  scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
+  scale_shape_manual(values = c("square","circle"), guide = guide_legend(title="Value" ,override.aes = list(size = 3), order = 3)) +
+  xlab(xlab_t) + ylab("Spatial Proximity") + 
+  theme_bw() +  theme( axis.title.x = (element_text(size = 13)), axis.title.y = (element_text(size = 15)), axis.text.x =  (element_text(size = 12)),axis.text.y =  (element_text(size = 15)), legend.title = element_text(size = 13),legend.position = "bottom", legend.text = element_text(size = 13),plot.title=element_text(hjust = 0.5), plot.caption = element_text(hjust= 0.5, size = 11)) + theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm")) +
+ labs( caption = paste0(subset(data_prox, circle_orange == 50)$circle_orange,"% liberal migrants"))
+
+plot_20 <- ggplot(data = subset(data_prox, circle_orange == 20), aes(x = val_lib_min, y = Prox, linetype = `segregation` , color = `ethnia`, shape = `orientation`)) + geom_line()  +  geom_point(size = 3) +
+ scale_x_discrete(limits=c(seq(0,20 ,by = 1))) + scale_y_continuous(limits=c(min(data_prox$Prox),max(data_prox$Prox)), breaks=seq(0,max(data_prox$Prox),by=0.50)) +
+# facet_wrap(~ circle_orange, ncol = 2, nrow = 2, labeller = labeller(circle_orange = circle_orange.labs)) +
+    geom_vline(xintercept = 20, color = "red") +  geom_hline(yintercept = 1, color = "red") +
+  scale_linetype_manual(values=c("solid","dashed"), labels = c("ethnic","value"), guide = guide_legend(title = "Segregation", order = 1)) +
+  scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
+  scale_shape_manual(values = c("square","circle"), guide = guide_legend(title="Value" ,override.aes = list(size = 3), order = 3)) +
+  xlab(xlab_t) + ylab("Spatial Proximity") + 
+  theme_bw() +  theme( axis.title.x = (element_text(size = 13)), axis.title.y = (element_text(size = 15)), axis.text.x =  (element_text(size = 12)),axis.text.y =  (element_text(size = 15)), legend.title = element_text(size = 13),legend.position = "bottom", legend.text = element_text(size = 13),plot.title=element_text(hjust = 0.5), plot.caption = element_text(hjust= 0.5, size = 11)) + theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm")) +
+ labs( caption = paste0(subset(data_prox, circle_orange == 20)$circle_orange,"% liberal migrants"))
+
+plot_80 <- ggplot(data = subset(data_prox, circle_orange == 80), aes(x = val_lib_min, y = Prox, linetype = `segregation` , color = `ethnia`, shape = `orientation`)) + geom_line()  +  geom_point(size = 3) +
+ scale_x_discrete(limits=c(seq(0,20 ,by = 1))) + scale_y_continuous(limits=c(min(data_prox$Prox),max(data_prox$Prox)), breaks=seq(0,max(data_prox$Prox),by=0.50)) +
+# facet_wrap(~ circle_orange, ncol = 2, nrow = 2, labeller = labeller(circle_orange = circle_orange.labs)) +
+    geom_vline(xintercept = 20, color = "red") +  geom_hline(yintercept = 1, color = "red") +
+  scale_linetype_manual(values=c("solid","dashed"), labels = c("ethnic","value"), guide = guide_legend(title = "Segregation", order = 1)) +
+  scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
+  scale_shape_manual(values = c("square","circle"), guide = guide_legend(title="Value" ,override.aes = list(size = 3), order = 3)) +
+  xlab(xlab_t) + ylab("Spatial Proximity") + 
+  theme_bw() +  theme( axis.title.x = (element_text(size = 13)), axis.title.y = (element_text(size = 15)), axis.text.x =  (element_text(size = 12)),axis.text.y =  (element_text(size = 15)), legend.title = element_text(size = 13),legend.position = "bottom", legend.text = element_text(size = 13),plot.title=element_text(hjust = 0.5), plot.caption = element_text(hjust= 0.5, size = 11)) + theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm")) +
+ labs( caption = paste0(subset(data_prox, circle_orange == 80)$circle_orange,"% liberal migrants"))
+
+ggpubr::ggarrange(plot_50,plot_80,plot_20,expo_pic, nrow = 2, ncol = 2, common.legend = TRUE, legend = "bottom")
+
+ggsave(plotname,plot = last_plot(),
+  device = NULL,path = NULL,
+  scale = 1,
+  width = 11,
+  height = 8,
+  units = c("in", "cm", "mm"),
+  dpi = 300,
+  limitsize = FALSE)
+
+```
+
+```{r sa_vllbmnTEST,  fig.cap="Sensitivity proximity value liberal minority, distribution liberals", echo=FALSE}
+
+# database filter
+excl <- names(sa_asym) %in% c("run", "ID","density","step","eth_lib_loc","val_con_loc","eth_lib_min","val_con_min")
+dataset_sa <- sa_asym[!excl] %>% filter(eth_con_loc  == 20,val_lib_loc == 20,eth_con_min  == 20)  %>% 
+group_by(val_lib_min ,fraction_blue,circle_blue, circle_orange) %>% summarise_all(c("mean"= mean,"sd"= sd))
+
+plotname <- "images/vllbmn.jpg"
+xlab_t <- "ß value liberal minority"
+
+xvalues <- c(dataset_sa$de_sq_bl_mean,dataset_sa$de_cl_bl_mean,dataset_sa$de_sq_or_mean,dataset_sa$de_cl_or_mean,
+       dataset_sa$dv_sq_bl_mean,dataset_sa$dv_cl_bl_mean,dataset_sa$dv_sq_or_mean,dataset_sa$dv_cl_or_mean)
+
+ expo_pic <-   ggplot(data = dataset_sa) + 
+  geom_point(aes(x = dataset_sa$de_sq_bl_mean, y = dataset_sa$et_sq_bl_mean),color = "black", fill = "blue", shape = 22, size = 5) +
+  geom_point(aes(x = dataset_sa$de_cl_bl_mean, y = dataset_sa$et_cl_bl_mean),color = "black",fill = "blue", shape = 21, size = 5) +
+  geom_point(aes(x = dataset_sa$de_sq_or_mean, y = dataset_sa$et_sq_or_mean),color = "black", fill = "orange", shape = 22, size = 5) +
+  geom_point(aes(x = dataset_sa$de_cl_or_mean, y = dataset_sa$et_cl_or_mean),color = "black", fill = "orange", shape = 21, size = 5) +
+
+  geom_point(aes(x = dataset_sa$dv_sq_bl_mean, y = dataset_sa$vl_sq_bl_mean),color = "black", fill = "blue", shape = 8, size = 5.1) + 
+   geom_point(aes(x = dataset_sa$dv_sq_bl_mean, y = dataset_sa$vl_sq_bl_mean),color = "black", fill = "blue", shape = 22, size = 5) +
+
+   geom_point(aes(x = dataset_sa$dv_cl_bl_mean, y = dataset_sa$vl_cl_bl_mean),color = "black",fill = "blue", shape = 8, size = 5.1) + 
+  geom_point(aes(x = dataset_sa$dv_cl_bl_mean, y = dataset_sa$vl_cl_bl_mean),color = "black",fill = "blue", shape = 21, size = 5) +
+
+    geom_point(aes(x = dataset_sa$dv_sq_or_mean, y = dataset_sa$vl_sq_or_mean),color = "black", fill = "orange", shape = 8, size = 5.1) +
+  geom_point(aes(x = dataset_sa$dv_sq_or_mean, y = dataset_sa$vl_sq_or_mean),color = "black", fill = "orange", shape = 22, size = 5) +
+
+  geom_point(aes(x = dataset_sa$dv_cl_or_mean, y = dataset_sa$vl_cl_or_mean),color = "black", fill = "orange", shape = 8, size = 5.1) +
+geom_point(aes(x = dataset_sa$dv_cl_or_mean, y = dataset_sa$vl_cl_or_mean),color = "black", fill = "orange", shape = 21, size = 5) +
+
+ scale_x_continuous(limits = c(min(xvalues),max(xvalues)), breaks = seq(0,max(xvalues), by = 0.5)) + 
+  scale_y_continuous(breaks= seq(0,1,by=0.1)) + 
+  geom_vline(xintercept = 1, color = "red") +
+  xlab("Spatial proximity") + ylab("Exposure") +
+  theme_bw()
+
+data_prox <- dataset_sa  %>% gather(key= subgroup, value = Prox, de_sq_bl_mean, dv_sq_bl_mean, de_cl_bl_mean, dv_cl_bl_mean, de_sq_or_mean, dv_sq_or_mean, de_cl_or_mean, dv_cl_or_mean) %>% mutate(
+  `segregation` = fct_relevel(fct_collapse(subgroup,"ethnics" = c("de_sq_bl_mean","de_cl_bl_mean","de_sq_or_mean","de_cl_or_mean"), "values" = c("dv_sq_bl_mean","dv_cl_bl_mean","dv_sq_or_mean","dv_cl_or_mean")),"ethnics"),
+ `orientation` = fct_relevel(fct_collapse(subgroup, "conservative" = c("de_sq_bl_mean","dv_sq_bl_mean","de_sq_or_mean","dv_sq_or_mean"), "liberal" = c("de_cl_bl_mean","dv_cl_bl_mean","de_cl_or_mean","dv_cl_or_mean")),"conservative" ),
+ `ethnia` = fct_relevel(fct_collapse(subgroup, "local" = c("de_sq_bl_mean","dv_sq_bl_mean","de_cl_bl_mean","dv_cl_bl_mean"),"minority" = c("de_sq_or_mean","dv_sq_or_mean","de_cl_or_mean","dv_cl_or_mean")), "local"))
+
+plot_50 <- ggplot(data = data_prox, aes(x = val_lib_min, y = Prox, linetype = `segregation` , fill = `ethnia`,  shape = `orientation`)) + geom_line(aes(color = `ethnia`))  +  geom_point(color = "black", size = 4) +
+ scale_x_discrete(limits=c(seq(0,20 ,by = 1))) + scale_y_continuous(limits=c(min(data_prox$Prox),max(data_prox$Prox)), breaks=seq(0,max(data_prox$Prox),by=0.50)) +
+ facet_wrap(~ circle_orange, dir = "v", labeller = labeller(circle_orange = circle_orange.labs)) +
+    geom_vline(xintercept = 20, color = "red") +  geom_hline(yintercept = 1, color = "red") +
+  scale_linetype_manual(values=c("solid","dotted"), labels = c("ethnic","value"), guide = guide_legend(title = "Segregation", order = 1)) +
+  scale_fill_manual(values = c("blue","darkorange")) + 
+   scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
+  scale_shape_manual(values = c(22,21), guide = guide_legend(title="Value" ,override.aes = list(size = 3), order = 3)) +
+  guides(fill = FALSE) +
+  xlab(xlab_t) + ylab("Spatial Proximity") + 
+  theme_bw() +  theme( 
+    axis.title.x = (element_text(size = 13)), axis.title.y = (element_text(size = 15)),
+    axis.text.x =  (element_text(size = 12)), axis.text.y =  (element_text(size = 15)), 
+    legend.title = element_text(size = 13),legend.position = "bottom", legend.text = element_text(size = 13),
+    plot.title=element_text(hjust = 0.5), plot.caption = element_text(hjust= 0.5, size = 11), plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
+
+ggpubr::ggarrange(plot_50, expo_pic, common.legend = TRUE, legend = "bottom")
+
+ggsave(plotname,plot = last_plot(),
+  device = NULL,path = NULL,
+  scale = 1,
+  width = 12,
+  height = 9,
+  units = c("in", "cm", "mm"),
+  dpi = 300,
+  limitsize = FALSE)
+
+plot_50
+```
+
+<!--
+
+```{r sa_etcnlc50, fig.width=30, fig.cap="Sensitivity ethnic conservative local, baseline asymmetric conditions", echo=FALSE}
+
+# database filter
+excl <- names(sa_asym) %in% c("run", "ID","density","step","eth_lib_loc","val_con_loc","eth_lib_min","val_con_min")
+dataset_sa <- sa_asym[!excl] %>% filter(val_lib_loc  == 20,eth_con_min == 20, val_lib_min == 20)  %>% 
+ filter(circle_orange == 50) %>%
+  group_by(eth_con_loc,fraction_blue,circle_blue, circle_orange) %>% summarise_all(c("mean"= mean,"sd"= sd))
+
+xlab_t <- "ß ethnic conservative local"
+
+ circle_orange.labs <- c("20% liberal minority", "50% liberal minority", "80% liberal minority")
+names(circle_orange.labs) <- c("20","50","80")
+
+plotname <- "images/etcnlc50.jpg"
+
+# row_exp <- c("\\multicolumn{17}{|c|}{Ethnic asymmetric condition: Exposure, 50% liberal minority}  \\\\\\hline\n",
+#    "Preference &  \\multicolumn{8}{|c|}{Ethnic Exposure} & \\multicolumn{8}{|c|}{Value Exposure}   \\\\\\hline\n",
+#   "& \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  & \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  \\\\\n",
+# "$\\beta$ dom = 20 & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
+# & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
+# & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal}\\\\\n",
+# " & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD\\\\\n")
+# 
+# row_prox <- c("\\multicolumn{17}{|c|}{Ethnic Asymmetric condition: Spatial Proximity, 50% liberal minority}  \\\\\\hline\n",
+#    "Preference &  \\multicolumn{8}{|c|}{Ethnic Proximity} & \\multicolumn{8}{|c|}{Value Proximity}   \\\\\\hline\n",
+#   "& \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  & \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  \\\\\n",
+# "$\\beta$ dom = 20 & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
+# & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
+# & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal}\\\\\n",
+# " & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD\\\\\n")
+#
+
+# tablerb_expname <- "latex/etcnlc50_rb_exp.tex"
+# tablerb_proxname <- "latex/etcnlc50_prox.tex"
+
+# graph
+
+data_exp <- dataset_sa %>% gather(key= subgroup, value = Expo, et_sq_bl_mean, vl_sq_bl_mean, et_cl_bl_mean, vl_cl_bl_mean, et_sq_or_mean, vl_sq_or_mean, et_cl_or_mean, vl_cl_or_mean) %>% mutate(
+  `segregation` = fct_relevel(fct_collapse(subgroup,"ethnics" = c("et_sq_bl_mean","et_cl_bl_mean","et_sq_or_mean","et_cl_or_mean"), "values" = c("vl_sq_bl_mean","vl_cl_bl_mean","vl_sq_or_mean","vl_cl_or_mean")),"ethnics"),
+ `orientation` = fct_relevel(fct_collapse(subgroup, "conservative" = c("et_sq_bl_mean","vl_sq_bl_mean","et_sq_or_mean","vl_sq_or_mean"), "liberal" = c("et_cl_bl_mean","vl_cl_bl_mean","et_cl_or_mean","vl_cl_or_mean")),"conservative" ),
+ `ethnia` = fct_relevel(fct_collapse(subgroup, "local" = c("et_sq_bl_mean","vl_sq_bl_mean","et_cl_bl_mean","vl_cl_bl_mean"),"minority" = c("et_sq_or_mean","vl_sq_or_mean","et_cl_or_mean","vl_cl_or_mean")), "local"))
+
+fig_exp <- ggplot(data = data_exp, aes(x = eth_con_loc, y = Expo, linetype = `segregation` , color = `ethnia`, shape = `orientation`)) + geom_line()  +  geom_point(size = 3) +
+ scale_x_discrete(limits=c(seq(0,20 ,by = 1))) + scale_y_continuous(limits=c(0,1), breaks=seq(0,1,by=0.10)) +
+#  facet_wrap(~ circle_orange, labeller = labeller(circle_orange = circle_orange.labs)) +
+  scale_linetype_manual(values=c("solid","dotted"), labels = c("ethnic","value"), guide = guide_legend(title = "Segregation", order = 1)) +
+  scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
+  scale_shape_manual(values = c("square","circle"), guide = guide_legend(title="Value" ,override.aes = list(size = 3), order = 3)) +
+  xlab("") + ylab("Exposure") + 
+  theme_bw() +  theme( axis.title.x  = element_blank(), axis.title.y = (element_text(size = 15)), axis.text.x  = (element_text(size = 10)) ,axis.text.y =  (element_text(size = 15)), legend.title = element_text(size = 13) ,legend.text = element_text(size = 13), plot.title=element_text(hjust = 0.5)) + theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
+
+# tablerb_exp <- xtable(dataset_sa[,c("dominant","et_sq_bl_mean","et_sq_bl_sd","et_cl_bl_mean","et_cl_bl_sd","et_sq_or_mean","et_sq_or_sd","et_cl_or_mean","et_cl_or_sd","vl_sq_bl_mean","vl_sq_bl_sd","vl_cl_bl_mean","vl_cl_bl_sd","vl_sq_or_mean","vl_sq_or_sd","vl_cl_or_mean","vl_cl_or_sd")], digits = 3)
+# align(tablerb_exp) <- "c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|"
+# 
+# addtorow <- list()
+# addtorow$pos <- list(0, 0,0,0,0)
+# addtorow$command <-  row_exp
+# 
+# print(tablerb_exp,type = "latex", file = tablerb_expname, include.rownames=FALSE, add.to.row = addtorow, include.colnames = FALSE, latex.environments = "center")
+
+## Spatial proximity baseline asymmetric
+
+# graph
+
+data_prox <- dataset_sa %>% gather(key= subgroup, value = Prox, de_sq_bl_mean, dv_sq_bl_mean, de_cl_bl_mean, dv_cl_bl_mean, de_sq_or_mean, dv_sq_or_mean, de_cl_or_mean, dv_cl_or_mean) %>% mutate(
+  `segregation` = fct_relevel(fct_collapse(subgroup,"ethnics" = c("de_sq_bl_mean","de_cl_bl_mean","de_sq_or_mean","de_cl_or_mean"), "values" = c("dv_sq_bl_mean","dv_cl_bl_mean","dv_sq_or_mean","dv_cl_or_mean")),"ethnics"),
+ `orientation` = fct_relevel(fct_collapse(subgroup, "conservative" = c("de_sq_bl_mean","dv_sq_bl_mean","de_sq_or_mean","dv_sq_or_mean"), "liberal" = c("de_cl_bl_mean","dv_cl_bl_mean","de_cl_or_mean","dv_cl_or_mean")),"conservative" ),
+ `ethnia` = fct_relevel(fct_collapse(subgroup, "local" = c("de_sq_bl_mean","dv_sq_bl_mean","de_cl_bl_mean","dv_cl_bl_mean"),"minority" = c("de_sq_or_mean","dv_sq_or_mean","de_cl_or_mean","dv_cl_or_mean")), "local"))
+
+fig_prox <- ggplot(data = data_prox, aes(x = eth_con_loc, y = Prox, linetype = `segregation` , color = `ethnia`, shape = `orientation`)) + geom_line()  +  geom_point(size = 3) +
+ scale_x_discrete(limits=c(seq(0,20 ,by = 1))) + scale_y_continuous(limits=c(min(data_prox$Prox),max(data_prox$Prox)), breaks=seq(0,max(data_prox$Prox),by=0.50)) +
+#☻    facet_wrap(~ circle_orange, labeller = labeller(circle_orange = circle_orange.labs)) +
+  scale_linetype_manual(values=c("solid","dotted"), labels = c("ethnic","value"), guide = guide_legend(title = "Segregation", order = 1)) +
+  scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
+  scale_shape_manual(values = c("square","circle"), guide = guide_legend(title="Value" ,override.aes = list(size = 3), order = 3)) +
+  xlab(xlab_t) + ylab("Spatial Proximity") + 
+  theme_bw() +  theme( axis.title.x = (element_text(size = 15)), axis.title.y = (element_text(size = 15)), axis.text.x =  (element_text(size = 15)),axis.text.y =  (element_text(size = 15)), legend.title = element_text(size = 13) ,legend.text = element_text(size = 13),plot.title=element_text(hjust = 0.5)) + theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
+
+# robustness table
+
+# tablerb_prox <- xtable(dataset_sa[,c("dominant","de_sq_bl_mean","de_sq_bl_sd","de_cl_bl_mean","de_cl_bl_sd","de_sq_or_mean","de_sq_or_sd","de_cl_or_mean","de_cl_or_sd","dv_sq_bl_mean","dv_sq_bl_sd","dv_cl_bl_mean","dv_cl_bl_sd","dv_sq_or_mean","dv_sq_or_sd","dv_cl_or_mean","dv_cl_or_sd")], digits = 3)
+# align(tablerb_prox) <- "c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|"
+# 
+# addtorow <- list()
+# addtorow$pos <- list(0, 0,0,0,0)
+# addtorow$command <-  row_prox
+# print(tablerb_prox,type = "latex", file = tablerb_proxname , include.rownames=FALSE, add.to.row = addtorow, include.colnames = FALSE, latex.environments = "center")
+
+# combined image
+
+ggpubr::ggarrange(fig_exp,fig_prox, nrow = 2, ncol = 1, common.legend = TRUE, legend = "right")
+
+ggsave(plotname,plot = fig_prox,
+  device = NULL,path = NULL, 
+  scale = 1,
+  width = 8,
+  height = 6,
+  units = c("in", "cm", "mm"),
+  dpi = 300,
+  limitsize = FALSE)
+
+```
+
+```{r CODE INDEX FACET  WRAP, fig.width=30, fig.cap="Baseline asymmetric conditions", echo=FALSE}
+
+# database filter
+excl <- names(asym_dom) %in% c("run", "ID","density","step")
+asym_dom_sa <- asym_dom[!excl] %>% group_by(dominant,circle_orange,circle_blue,fraction_blue,secondary) %>% summarise_all(c("mean"= mean,"sd"= sd))
+
+# graph
+# LEAVE! Combined indexes
+data_s <- asym_dom_sa  %>% gather(key= subgroup, value = Segra, de_sq_bl_mean, dv_sq_bl_mean, de_cl_bl_mean, dv_cl_bl_mean, de_sq_or_mean, dv_sq_or_mean, de_cl_or_mean, dv_cl_or_mean,
+       et_sq_bl_mean, vl_sq_bl_mean, et_cl_bl_mean, vl_cl_bl_mean, et_sq_or_mean, vl_sq_or_mean, et_cl_or_mean, vl_cl_or_mean) %>% mutate(
+  `dimensions` = fct_relevel(fct_collapse(subgroup,"ethnic" = c("de_sq_bl_mean","de_cl_bl_mean","de_sq_or_mean","de_cl_or_mean", "et_sq_bl_mean","et_cl_bl_mean","et_sq_or_mean","et_cl_or_mean"), "values" = c("dv_sq_bl_mean","dv_cl_bl_mean","dv_sq_or_mean","dv_cl_or_mean",
+   "vl_sq_bl_mean","vl_cl_bl_mean","vl_sq_or_mean","vl_cl_or_mean")),"ethnic"),
+ `orientation` = fct_relevel(fct_collapse(subgroup, "conservative" = c("de_sq_bl_mean","dv_sq_bl_mean","de_sq_or_mean","dv_sq_or_mean",  "et_sq_bl_mean","vl_sq_bl_mean","et_sq_or_mean","vl_sq_or_mean" ), "liberal" = c("de_cl_bl_mean","dv_cl_bl_mean","de_cl_or_mean","dv_cl_or_mean",
+                         "et_cl_bl_mean", "vl_cl_bl_mean", "et_cl_or_mean","vl_cl_or_mean")),"conservative" ),
+ `ethnia` = fct_relevel(fct_collapse(subgroup, "local" = c("de_sq_bl_mean","dv_sq_bl_mean","de_cl_bl_mean","dv_cl_bl_mean",
+                                    "et_sq_bl_mean","vl_sq_bl_mean","et_cl_bl_mean", "vl_cl_bl_mean" ),"minority" = c("de_sq_or_mean","dv_sq_or_mean","de_cl_or_mean","dv_cl_or_mean","et_sq_or_mean", "vl_sq_or_mean", "et_cl_or_mean", "vl_cl_or_mean")), "local"),
+  `index` = fct_relevel(fct_collapse(subgroup,  "exposure" = c("et_sq_bl_mean","vl_sq_bl_mean","et_cl_bl_mean", "vl_cl_bl_mean","et_sq_or_mean", "vl_sq_or_mean", "et_cl_or_mean", "vl_cl_or_mean" ), "proximity" = c("de_sq_bl_mean","dv_sq_bl_mean","de_cl_bl_mean","dv_cl_bl_mean","de_sq_or_mean","dv_sq_or_mean","de_cl_or_mean","dv_cl_or_mean")),"exposure"))
+
+data_f <- asym_dom_sa %>% gather(key= subgroup, value = Segra, de_sq_bl_mean, dv_sq_bl_mean, de_cl_bl_mean, dv_cl_bl_mean, de_sq_or_mean, dv_sq_or_mean, de_cl_or_mean, dv_cl_or_mean) %>% mutate(
+  `segregation` = fct_relevel(fct_collapse(subgroup,"ethnics" = c("de_sq_bl_mean","de_cl_bl_mean","de_sq_or_mean","de_cl_or_mean"), "values" = c("dv_sq_bl_mean","dv_cl_bl_mean","dv_sq_or_mean","dv_cl_or_mean")),"ethnics"),
+ `orientation` = fct_relevel(fct_collapse(subgroup, "conservative" = c("de_sq_bl_mean","dv_sq_bl_mean","de_sq_or_mean","dv_sq_or_mean"), "liberal" = c("de_cl_bl_mean","dv_cl_bl_mean","de_cl_or_mean","dv_cl_or_mean")),"conservative" ),
+ `ethnia` = fct_relevel(fct_collapse(subgroup, "local" = c("de_sq_bl_mean","dv_sq_bl_mean","de_cl_bl_mean","dv_cl_bl_mean"),"minority" = c("de_sq_or_mean","dv_sq_or_mean","de_cl_or_mean","dv_cl_or_mean")), "local"))
+
+data_e <- asym_dom_sa %>% gather(key= subgroup, value = Segra, et_sq_bl_mean, vl_sq_bl_mean, et_cl_bl_mean, vl_cl_bl_mean, et_sq_or_mean, vl_sq_or_mean, et_cl_or_mean, vl_cl_or_mean) %>% mutate(
+  `segregation` = fct_relevel(fct_collapse(subgroup,"ethnics" = c("et_sq_bl_mean","et_cl_bl_mean","et_sq_or_mean","et_cl_or_mean"), "values" = c("vl_sq_bl_mean","vl_cl_bl_mean","vl_sq_or_mean","vl_cl_or_mean")),"ethnics"),
+ `orientation` = fct_relevel(fct_collapse(subgroup, "conservative" = c("et_sq_bl_mean","vl_sq_bl_mean","et_sq_or_mean","vl_sq_or_mean"), "liberal" = c("et_cl_bl_mean","vl_cl_bl_mean","et_cl_or_mean","vl_cl_or_mean")),"conservative" ),
+ `ethnia` = fct_relevel(fct_collapse(subgroup, "local" = c("et_sq_bl_mean","vl_sq_bl_mean","et_cl_bl_mean","vl_cl_bl_mean"),"minority" = c("et_sq_or_mean","vl_sq_or_mean","et_cl_or_mean","vl_cl_or_mean")), "local"))
+
+ggplot(data = data_f, aes(x = dominant, y = Segra, color = `ethnia` , linetype = `segregation`, shape = `orientation`)) +   geom_point(size = 3) + geom_line() + 
+# scale_color_gradient(low="green", high="red")
+ scale_x_discrete(limits=c(seq(0,20 ,by = 1))) + 
+ scale_y_continuous(breaks=seq(0,max(data_f$Segra),by=0.25)) +
+  scale_linetype_manual(values=c("solid","dashed"), labels = c("ethnic","value"), guide = guide_legend(title = "Dimension", order = 1)) +
+scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
+ scale_shape_manual(values = c("square","circle"), guide = guide_legend(title="Orientation" ,override.aes = list(size = 3), order = 3)) +
+  xlab("ß dominant") + ylab("Index") + 
+# facet_wrap(~ `index`, dir = "v", scales = "free_y") + 
+  geom_blank() +
+  theme_bw() +  theme( axis.title.x = (element_text(size = 15)), axis.title.y = (element_text(size = 15)), axis.text.x =  (element_text(size = 15)),axis.text.y =  (element_text(size = 15)), legend.title = element_text(size = 13) ,legend.text = element_text(size = 13), plot.title=element_text(hjust = 0.5)) + theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
+
+ggsave("images/prox_asym_dom.jpg",plot = last_plot(),
+  device = NULL,path = NULL, 
+  scale = 1,
+  width = 10,
+  height = 4,
+  units = c("in", "cm", "mm"),
+  dpi = 300,
+  limitsize = FALSE)
+
+# robustness table
+
+table_rb <- xtable(asym_dom_sa[,c("dominant","de_sq_bl_mean","de_sq_bl_sd","de_cl_bl_mean","de_cl_bl_sd","de_sq_or_mean","de_sq_or_sd","de_cl_or_mean","de_cl_or_sd","dv_sq_bl_mean","dv_sq_bl_sd","dv_cl_bl_mean","dv_cl_bl_sd","dv_sq_or_mean","dv_sq_or_sd","dv_cl_or_mean","dv_cl_or_sd")], digits = 3)
+align(table_rb) <- "c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|"
+
+addtorow <- list()
+addtorow$pos <- list(0, 0,0,0,0)
+addtorow$command <-  c("\\multicolumn{17}{|c|}{Ethnic Asymmetric condition: Spatial Proximity}  \\\\\\hline\n",
+   "Preference &  \\multicolumn{8}{|c|}{Ethnic Exposure} & \\multicolumn{8}{|c|}{Value Exposure}   \\\\\\hline\n",
+  "& \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  & \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  \\\\\n",
+"$\\beta$ sec = 0 & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
+& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
+& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal}\\\\\n",
+" & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD\\\\\n")
+
+print(table_rb,type = "latex", file = "prox_asym_rb.tex", include.rownames=FALSE, add.to.row = addtorow, include.colnames = FALSE, latex.environments = "center")
+
+A = data.frame(x = rnorm(10),y=rnorm(10))
+B = data.frame(x = rnorm(10),y=rnorm(10))
+ggplot(A,aes(x,y)) +geom_point() +geom_point(data=B,colour='red') + xlim(0, 10)
 
@@
 ```
+-->

### 2021-02-28 analysis.Rmd
28/02/21: exp & prox graph

--- 2020-11-23 JMS.Rmd
@@
 library(ggplot2)
+library(reshape)
+library(reshape2)
 library(forcats)
-library(reshape2)
 library(tidyr)
 library(dplyr)
-library(reshape)
 library(gtable)
-library(explore)
+library(kableExtra)
+library(magick)
+library(webshot)
+library(xtable)
 library(gridExtra)
-library(xtable)
-library(ggpubr)
-
-#  This was to simplify dataset of basic conditions
-# a <- read.csv("basic_equal.csv", sep = ",", skip = 6)
-# names(a) <- pull(read.csv("legend.csv"))
-# B <- a %>% filter(dominant >= 0, secondary_circle  <= dominant, secondary_square <= dominant) %>% filter(ticks == 1000)
-# write.csv(B, file = "basic_exp.csv", row.names = FALSE)
-
-setwd("C:/Users/rocpa/OneDrive/Desktop/AF/experiments/JMS/")
-
-hc_hc_dis <- read.csv("hc_hc_dis.csv")
-# names(test_mj80) <- pull(read.csv("legend_test.csv"))
-
-base_eq <-  read.csv("basic/basic_exp.csv", sep = ",")
-
-majority_bs <- read.csv("maj/majority_bs.csv", sep = ",", skip = 6)
-names(majority_bs) <- pull(read.csv("basic/legend_bas.csv"))
-
-majority_bsa <- read.csv("maj/majority_bsa.csv", sep = ",", skip = 6)
-names(majority_bsa) <- pull(read.csv("basic/legend_bas.csv"))
-names(majority_bsa)[names(majority_bsa) == "circle_orange"] <- "dmnt"
-names(majority_bsa)[names(majority_bsa) == "dominant"] <- "circle_orange"
-names(majority_bsa)[names(majority_bsa) == "dmnt"] <- "dominant"
-
-majority_bs <- majority_bs %>% filter(ticks == 1000)
-
-# majlib <- read.csv("maj/maj_lib.csv", sep = ",", skip = 6)
-# names(majlib) <- pull(read.csv("maj/legend_maj.csv"))
-
-test_5_20 <- read.csv("result5_20.csv", sep = ",", skip = 6)
-names(test_5_20) <- pull(read.csv("legend_test.csv"))
-test_5_20 <- test_5_20[,-(35:42)]
-
-test_20_5 <- read.csv("result20_5.csv", sep = ",", skip = 6)
-names(test_20_5) <- pull(read.csv("legend_test.csv"))
-
-b <- test_20_5 %>% filter(fraction_blue == 60)
-
-a <- test_5_20 %>% filter(fraction_blue == 80)
-ftable(xtabs(~ a$circle_orange + a$eth_loc_lib + a$eth_min_lib, data = a))
-
-levels(as.factor(a$eth_loc_con))
-levels(as.factor(b$eth_loc_con))
+library(ggrepel)
+library(viridis)
+options(xtable.floating = FALSE)
+options(xtable.timestamp = "")
+webshot::install_phantomjs()
+
+setwd("C:/Users/rocpa/OneDrive/Desktop/AF2/exp12_2020/")
+
+# Back work, used to combine datasets from diffent runs. To IGNORE OR DELETE
+
+# etlib_min1 <- read.csv("mj_etlib_min.csv",skip = 6)
+# etlib_min2 <- read.csv("mj_etlib_min2.csv",skip = 6)
+# etlib_min <- rbind(etlib_min1,etlib_min2)
+# names(etlib_min) <- pull(read.csv("legend_sec_etlib.csv"))
+# etlib_min <- cbind(ID = "etlib_min",etlib_min)
+
+basic <- read.csv("df_basic.csv",sep =",")
+value_basic <- read.csv("df_valuebasic.csv",sep = ",")
+asym_dom <- read.csv("df_asym_dom.csv",sep = ",")
+dislib <- read.csv("df_dislib.csv", sep = ",")
+sa_asym <- read.csv("df_sa_asym.csv",sep =",")
+etlib <- read.csv("df_etlib.csv",sep =",")
+
+circle_orange.labs <- c("20% liberal minority", "50% liberal minority", "80% liberal minority")
+names(circle_orange.labs) <- c("20","50","80")
+
+segregation.labs  <- c("ethnic segregation","value segregation")
+names(segregation.labs) <- c("ethnics","values")
+
+```
+
+```{r heatmap, include=TRUE, fig.cap="Comparison dominant vs secondary", echo=FALSE}
+
+excl <- names(basic) %in% c("run", "ID","density","step")
+basic_sa <- basic[!excl]  %>% group_by(dominant,secondary,circle_orange,circle_blue,fraction_blue) %>% summarise_all(c("mean"= mean,"sd"= sd))
+
+data_f <- basic_sa %>% filter(dominant >= secondary)   %>% gather(key= subgroup, value = Segra, et_sq_bl_mean, vl_sq_bl_mean, et_cl_bl_mean, vl_cl_bl_mean, et_sq_or_mean, vl_sq_or_mean, et_cl_or_mean, vl_cl_or_mean) %>% mutate(
+  `segregation` = fct_relevel(fct_collapse(subgroup,"ethnics" = c("et_sq_bl_mean","et_cl_bl_mean","et_sq_or_mean","et_cl_or_mean"), "values" = c("vl_sq_bl_mean","vl_cl_bl_mean","vl_sq_or_mean","vl_cl_or_mean")),"ethnics"),
+ `orientation` = fct_relevel(fct_collapse(subgroup, "conservative" = c("et_sq_bl_mean","vl_sq_bl_mean","et_sq_or_mean","vl_sq_or_mean"), "liberal" = c("et_cl_bl_mean","vl_cl_bl_mean","et_cl_or_mean","vl_cl_or_mean")),"conservative" ),
+ `ethnia` = fct_relevel(fct_collapse(subgroup, "local" = c("et_sq_bl_mean","vl_sq_bl_mean","et_cl_bl_mean","vl_cl_bl_mean"),"minority" = c("et_sq_or_mean","vl_sq_or_mean","et_cl_or_mean","vl_cl_or_mean")), "local"))
+
+  ggplot(data = data_f, aes(x = secondary , y = dominant , fill = Segra)) + geom_tile() + 
+ facet_grid( `orientation` ~  `segregation`, labeller = labeller(`segregation` = segregation.labs)) +
+  xlab("ß secondary") + ylab("ß dominant") +
+scale_x_discrete(limits=seq(0, 20 ,by = 1)) +
+  scale_y_discrete(limits=seq(0,20 ,by = 1)) + 
+ # geom_text(aes(label=round(Segra,2)), size=3) +
+    scale_fill_gradient(low = "grey", high = "brown", limits=c(min(data_f$Segra),1), breaks=round(seq(min(data_f$Segra),1,by=0.1),2),  name = "Segregation") +
+    # scale_fill_distiller(palette = "BlRd", limits=c(min(data_f$Segra),1), breaks=round(seq(min(data_f$Segra),1,by=0.05),2),  name = "Segregation") +
+    theme_bw()  +   theme(legend.position = "bottom", legend.title = element_text(size = 15,vjust = 0.8), legend.text = element_text(size = 15),  legend.key.width  = unit(1, "inch"), legend.key.height  = unit(0.3, "inch"), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0), axis.title.x = (element_text(size = 18)), axis.title.y = (element_text(size = 18)), axis.text.x =  (element_text(size = 13)),axis.text.y =  (element_text(size = 13)),strip.text.x = element_text(size = 15), strip.text.y = element_text(size = 15))
+
+ggsave("images/heatmapbase.jpg",plot = last_plot(),
+  device = NULL,
+  path = NULL,
+  scale = 1,
+  width = 11,
+  height = 11,
+  units = c("in", "cm", "mm"),
+  dpi = 300,
+  limitsize = TRUE)
+
+```
+
+```{r basefigure, fig.width=30, fig.cap="Same parameter for ethnic and value homophily for all agents", echo=FALSE}
+
+# database filter
+excl <- names(basic) %in% c("run", "ID","density","step")
+basic_sa <- basic[!excl] %>% filter(dominant == secondary) %>% group_by(dominant,secondary,circle_orange,circle_blue,fraction_blue) %>% summarise_all(c("mean"= mean,"sd"= sd))
+
+# graph
+
+data_f <- basic_sa %>% gather(key= subgroup, value = Segra, et_sq_bl_mean, vl_sq_bl_mean, et_cl_bl_mean, vl_cl_bl_mean, et_sq_or_mean, vl_sq_or_mean, et_cl_or_mean, vl_cl_or_mean) %>% mutate(
+  `segregation` = fct_relevel(fct_collapse(subgroup,"ethnics" = c("et_sq_bl_mean","et_cl_bl_mean","et_sq_or_mean","et_cl_or_mean"), "values" = c("vl_sq_bl_mean","vl_cl_bl_mean","vl_sq_or_mean","vl_cl_or_mean")),"ethnics"),
+ `orientation` = fct_relevel(fct_collapse(subgroup, "conservative" = c("et_sq_bl_mean","vl_sq_bl_mean","et_sq_or_mean","vl_sq_or_mean"), "liberal" = c("et_cl_bl_mean","vl_cl_bl_mean","et_cl_or_mean","vl_cl_or_mean")),"conservative" ),
+ `ethnia` = fct_relevel(fct_collapse(subgroup, "local" = c("et_sq_bl_mean","vl_sq_bl_mean","et_cl_bl_mean","vl_cl_bl_mean"),"minority" = c("et_sq_or_mean","vl_sq_or_mean","et_cl_or_mean","vl_cl_or_mean")), "local"))
+
+ggplot(data = data_f, aes(x = dominant, y = Segra,  linetype = `segregation` , fill = `ethnia`,  shape = `orientation`)) + geom_line(aes(color = `ethnia`))  +  geom_point(color = "black", size = 4) + 
+ scale_x_discrete(limits=c(seq(0,20 ,by = 1))) + scale_y_continuous(limits=c(0,1), breaks=seq(0,1,by=0.10)) +
+  scale_linetype_manual(values=c("solid","dashed"), labels = c("ethnic","value"), guide = guide_legend(title = "Segregation", order = 1)) +
+  scale_fill_manual(values = c("blue","darkorange")) + 
+  scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
+  scale_shape_manual(values = c(22,21), guide = guide_legend(title="Value" ,override.aes = list(size = 3), order = 3)) +
+  guides(fill = FALSE) +
+  xlab("ß dominant = ß secondary") + ylab("Exposure") + 
+  theme_bw() +  theme( axis.title.x = (element_text(size = 15)), axis.title.y = (element_text(size = 15)), axis.text.x =  (element_text(size = 15)),axis.text.y =  (element_text(size = 15)), legend.title = element_text(size = 13) ,legend.text = element_text(size = 13), plot.title=element_text(hjust = 0.5)) + theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
+
+ggsave("images/one_beta.jpg",plot = last_plot(),
+  device = NULL,path = NULL, 
+  scale = 1,
+  width = 10,
+  height = 4,
+  units = c("in", "cm", "mm"),
+  dpi = 300,
+  limitsize = FALSE)
+
+# robustness table
+
+table_rb <- xtable(basic_sa[,c("dominant","et_sq_bl_mean","et_sq_bl_sd","et_cl_bl_mean","et_cl_bl_sd","et_sq_or_mean","et_sq_or_sd","et_cl_or_mean","et_cl_or_sd","vl_sq_bl_mean","vl_sq_bl_sd","vl_cl_bl_mean","vl_cl_bl_sd","vl_sq_or_mean","vl_sq_or_sd","vl_cl_or_mean","vl_cl_or_sd")], digits = 3)
+align(table_rb) <- "c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|"
+
+addtorow <- list()
+addtorow$pos <- list(0, 0,0,0,0)
+addtorow$command <-  c("\\multicolumn{17}{|c|}{Baseline condition}  \\\\\\hline\n",
+   "Preference &  \\multicolumn{8}{|c|}{Ethnic Exposure} & \\multicolumn{8}{|c|}{Value Exposure}   \\\\\\hline\n",
+  "& \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  & \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  \\\\\n",
+"$\\beta$ dom = $\\beta$ sec & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
+& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
+& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal}\\\\\n",
+" & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD\\\\\n")
+
+print(table_rb,type = "latex", file = "latex/basic_rb.tex", include.rownames=FALSE, add.to.row = addtorow, include.colnames = FALSE, latex.environments = "center")
+
+```
+
+```{r secondary_0, fig.width=30, fig.cap="secondary preference set to 0", echo=FALSE}
+
+# database filter
+excl <- names(basic) %in% c("run", "ID","density","step")
+basic_sa_sec0 <- basic[!excl] %>% filter(secondary == 0) %>% group_by(dominant,circle_orange,circle_blue,fraction_blue,secondary) %>% summarise_all(c("mean"= mean,"sd"= sd))
+
+# graph
+
+data_f <- basic_sa_sec0 %>% gather(key= subgroup, value = Segra, et_sq_bl_mean, vl_sq_bl_mean, et_cl_bl_mean, vl_cl_bl_mean, et_sq_or_mean, vl_sq_or_mean, et_cl_or_mean, vl_cl_or_mean) %>% mutate(
+  `segregation` = fct_relevel(fct_collapse(subgroup,"ethnics" = c("et_sq_bl_mean","et_cl_bl_mean","et_sq_or_mean","et_cl_or_mean"), "values" = c("vl_sq_bl_mean","vl_cl_bl_mean","vl_sq_or_mean","vl_cl_or_mean")),"ethnics"),
+ `orientation` = fct_relevel(fct_collapse(subgroup, "conservative" = c("et_sq_bl_mean","vl_sq_bl_mean","et_sq_or_mean","vl_sq_or_mean"), "liberal" = c("et_cl_bl_mean","vl_cl_bl_mean","et_cl_or_mean","vl_cl_or_mean")),"conservative" ),
+ `ethnia` = fct_relevel(fct_collapse(subgroup, "local" = c("et_sq_bl_mean","vl_sq_bl_mean","et_cl_bl_mean","vl_cl_bl_mean"),"minority" = c("et_sq_or_mean","vl_sq_or_mean","et_cl_or_mean","vl_cl_or_mean")), "local"))
+
+ggplot(data = data_f, aes(x = dominant, y = Segra, linetype = `segregation` , fill = `ethnia`,  shape = `orientation`)) + geom_line(aes(color = `ethnia`))  +  geom_point(color = "black", size = 4) + 
+ scale_x_discrete(limits=c(seq(0,20 ,by = 1))) + scale_y_continuous(limits=c(0,1), breaks=seq(0,1,by=0.10)) +
+   scale_linetype_manual(values=c("solid","dashed"), labels = c("ethnic","value"), guide = guide_legend(title = "Segregation", order = 1)) +
+  scale_fill_manual(values = c("blue","darkorange")) + 
+  scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
+  scale_shape_manual(values = c(22,21), guide = guide_legend(title="Value" ,override.aes = list(size = 3), order = 3)) +
+  guides(fill = FALSE) +
+  xlab("ß dominant") + ylab("Exposure") + 
+  theme_bw() +  theme( axis.title.x = (element_text(size = 15)), axis.title.y = (element_text(size = 15)), axis.text.x =  (element_text(size = 15)),axis.text.y =  (element_text(size = 15)), legend.title = element_text(size = 13) ,legend.text = element_text(size = 13), plot.title=element_text(hjust = 0.5)) + theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
+
+ggsave("images/sec_0.jpg",plot = last_plot(),
+  device = NULL,path = NULL, 
+  scale = 1,
+  width = 10,
+  height = 4,
+  units = c("in", "cm", "mm"),
+  dpi = 300,
+  limitsize = FALSE)
+
+# robustness table
+
+table_rb <- xtable(basic_sa_sec0[,c("dominant","et_sq_bl_mean","et_sq_bl_sd","et_cl_bl_mean","et_cl_bl_sd","et_sq_or_mean","et_sq_or_sd","et_cl_or_mean","et_cl_or_sd","vl_sq_bl_mean","vl_sq_bl_sd","vl_cl_bl_mean","vl_cl_bl_sd","vl_sq_or_mean","vl_sq_or_sd","vl_cl_or_mean","vl_cl_or_sd")], digits = 3)
+align(table_rb) <- "c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|"
+
+addtorow <- list()
+addtorow$pos <- list(0, 0,0,0,0)
+addtorow$command <-  c("\\multicolumn{17}{|c|}{Secondary preference = 0}  \\\\\\hline\n",
+   "Preference &  \\multicolumn{8}{|c|}{Ethnic Exposure} & \\multicolumn{8}{|c|}{Value Exposure}   \\\\\\hline\n",
+  "& \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  & \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  \\\\\n",
+"$\\beta$ sec = 0 & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
+& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
+& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal}\\\\\n",
+" & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD\\\\\n")
+
+print(table_rb,type = "latex", file = "latex/basic_rb_sec0.tex", include.rownames=FALSE, add.to.row = addtorow, include.colnames = FALSE, latex.environments = "center")
+
+```
+
+```{r sensval, fig.width=30, fig.cap="Test mechanism: increase liberal and conservative, all other 0", echo=FALSE}
+
+# database filter
+excl <- names(value_basic) %in% c("run","density","step")
+dom_lib <- value_basic[!excl] %>% filter(ID == "dom_crl") %>%   #,  secondary_circle == 0 & dominant_square == 0 & secondary_square == 0) %>% 
+  group_by(ID, dominant_circle,secondary_circle,dominant_square,secondary_square,fraction_blue,circle_blue,circle_orange) %>% summarise_all(c("mean"= mean,"sd"= sd))
+
+# graph
+
+data_f <- dom_lib %>% gather(key= subgroup, value = Segra, et_sq_bl_mean, vl_sq_bl_mean, et_cl_bl_mean, vl_cl_bl_mean, et_sq_or_mean, vl_sq_or_mean, et_cl_or_mean, vl_cl_or_mean) %>% mutate(
+  `segregation` = fct_relevel(fct_collapse(subgroup,"ethnics" = c("et_sq_bl_mean","et_cl_bl_mean","et_sq_or_mean","et_cl_or_mean"), "values" = c("vl_sq_bl_mean","vl_cl_bl_mean","vl_sq_or_mean","vl_cl_or_mean")),"ethnics"),
+ `orientation` = fct_relevel(fct_collapse(subgroup, "conservative" = c("et_sq_bl_mean","vl_sq_bl_mean","et_sq_or_mean","vl_sq_or_mean"), "liberal" = c("et_cl_bl_mean","vl_cl_bl_mean","et_cl_or_mean","vl_cl_or_mean")),"conservative" ),
+ `ethnia` = fct_relevel(fct_collapse(subgroup, "local" = c("et_sq_bl_mean","vl_sq_bl_mean","et_cl_bl_mean","vl_cl_bl_mean"),"minority" = c("et_sq_or_mean","vl_sq_or_mean","et_cl_or_mean","vl_cl_or_mean")), "local"))
+
+ dom_libpic <- ggplot(data = data_f, aes(x = dominant_circle, y = Segra, linetype = `segregation` , fill = `ethnia`,  shape = `orientation`)) + geom_line(aes(color = `ethnia`))  +  geom_point(color = "black", size = 4) +
+ scale_x_discrete(limits=c(seq(0,20 ,by = 1))) + scale_y_continuous(limits=c(0,1), breaks=seq(0,1,by=0.10)) +
+#geom_hline(yintercept = 0.50, color = "red") +
+ scale_linetype_manual(values=c("solid","dashed"), labels = c("ethnic","value"), guide = guide_legend(title = "Segregation", order = 1)) +
+  scale_fill_manual(values = c("blue","darkorange")) + 
+  scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
+  scale_shape_manual(values = c(22,21), guide = guide_legend(title="Value" ,override.aes = list(size = 3), order = 3)) +
+  guides(fill = FALSE) +
+  xlab("ß value liberal") + ylab("Exposure") + 
+  theme_bw() +  theme( axis.title.x = (element_text(size = 15)), axis.title.y = (element_text(size = 15)), axis.text.x =  (element_text(size = 13)),axis.text.y =  (element_text(size = 15)), legend.title = element_text(size = 13) ,legend.text = element_text(size = 13), plot.title=element_text(hjust = 0.5)) + theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
+
+# ggsave("images/dom_lib.jpg",plot = last_plot(),
+#   device = NULL,path = NULL, 
+#   scale = 1,
+#   width = 10,
+#   height = 4,
+#   units = c("in", "cm", "mm"),
+#   dpi = 300,
+#   limitsize = FALSE)
+
+# sensitivity to conservative
+
+excl <- names(value_basic) %in% c("run","density","step")
+dom_con <- value_basic[!excl] %>% filter(ID == "dom_sqr") %>%
+   group_by(ID,dominant_square, secondary_square,dominant_circle,secondary_circle,fraction_blue,circle_blue,circle_orange) %>% summarise_all(c("mean"= mean,"sd"= sd))
+
+# graph
+
+data_f <- dom_con %>% gather(key= subgroup, value = Segra, et_sq_bl_mean, vl_sq_bl_mean, et_cl_bl_mean, vl_cl_bl_mean, et_sq_or_mean, vl_sq_or_mean, et_cl_or_mean, vl_cl_or_mean) %>% mutate(
+  `segregation` = fct_relevel(fct_collapse(subgroup,"ethnics" = c("et_sq_bl_mean","et_cl_bl_mean","et_sq_or_mean","et_cl_or_mean"), "values" = c("vl_sq_bl_mean","vl_cl_bl_mean","vl_sq_or_mean","vl_cl_or_mean")),"ethnics"),
+ `orientation` = fct_relevel(fct_collapse(subgroup, "conservative" = c("et_sq_bl_mean","vl_sq_bl_mean","et_sq_or_mean","vl_sq_or_mean"), "liberal" = c("et_cl_bl_mean","vl_cl_bl_mean","et_cl_or_mean","vl_cl_or_mean")),"conservative" ),
+ `ethnia` = fct_relevel(fct_collapse(subgroup, "local" = c("et_sq_bl_mean","vl_sq_bl_mean","et_cl_bl_mean","vl_cl_bl_mean"),"minority" = c("et_sq_or_mean","vl_sq_or_mean","et_cl_or_mean","vl_cl_or_mean")), "local"))
+
+dom_conpic <- ggplot(data = data_f, aes(x = dominant_square, y = Segra, linetype = `segregation` , fill = `ethnia`,  shape = `orientation`)) + geom_line(aes(color = `ethnia`))  +  geom_point(color = "black", size = 4) +
+ scale_x_discrete(limits=c(seq(0,20 ,by = 1))) + scale_y_continuous(limits=c(0,1), breaks=seq(0,1,by=0.10)) +
+  scale_linetype_manual(values=c("solid","dashed"), labels = c("ethnic","value"), guide = guide_legend(title = "Segregation", order = 1)) +
+  scale_fill_manual(values = c("blue","darkorange")) + 
+  scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
+  scale_shape_manual(values = c(22,21), guide = guide_legend(title="Value" ,override.aes = list(size = 3), order = 3)) +
+  guides(fill = FALSE) +
+  xlab("ß ethnic conservative") + ylab("Exposure") + 
+  theme_bw() +  theme( axis.title.x = (element_text(size = 15)), axis.title.y = (element_text(size = 15)), axis.text.x =  (element_text(size = 13)),axis.text.y =  (element_text(size = 15)), legend.title = element_text(size = 13) ,legend.text = element_text(size = 13), plot.title=element_text(hjust = 0.5)) + theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
+
+# ggsave("images/dom_con.jpg",plot = last_plot(),
+#   device = NULL,path = NULL, 
+#   scale = 1,
+#   width = 10,
+#   height = 4,
+#   units = c("in", "cm", "mm"),
+#   dpi = 300,
+#   limitsize = FALSE)
+#
+
+ggpubr::ggarrange(dom_libpic,dom_conpic, nrow = 2, ncol = 1, common.legend = TRUE, legend = "right")
+
+ggsave("images/comb_val.jpg",plot = last_plot(),
+  device = NULL,path = NULL, 
+  scale = 1,
+ width = 8,
+  height = 6,
+  units = c("in", "cm", "mm"),
+  dpi = 300,
+  limitsize = FALSE)
+
+# robustness table
+
+row_lib <-  c("\\multicolumn{17}{|c|}{Baseline: sensitivity to value liberal}  \\\\\\hline\n",
+   "Preference &  \\multicolumn{8}{|c|}{Ethnic Exposure} & \\multicolumn{8}{|c|}{Value Exposure}   \\\\\\hline\n",
+  "& \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  & \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  \\\\\n",
+# note
+"$\\beta$ dom & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
+& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
+& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal}\\\\\n",
+"liberal & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD\\\\\n")
+
+row_con <- c("\\multicolumn{17}{|c|}{Baseline: sensitivity to ethnic conservative}  \\\\\\hline\n",
+   "Preference &  \\multicolumn{8}{|c|}{Ethnic Exposure} & \\multicolumn{8}{|c|}{Value Exposure}   \\\\\\hline\n",
+  "& \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  & \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  \\\\\n",
+# note
+"$\\beta$ dom & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
+ & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
+& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal}\\\\\n",
+" conservative & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD\\\\\n")
+
+table_lib <- xtable(dom_lib[,c("dominant_circle","et_sq_bl_mean","et_sq_bl_sd","et_cl_bl_mean","et_cl_bl_sd","et_sq_or_mean","et_sq_or_sd","et_cl_or_mean","et_cl_or_sd","vl_sq_bl_mean","vl_sq_bl_sd","vl_cl_bl_mean","vl_cl_bl_sd","vl_sq_or_mean","vl_sq_or_sd","vl_cl_or_mean","vl_cl_or_sd")], digits = 3)
+align(table_lib) <- "c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|"
+
+addtorow <- list()
+addtorow$pos <- list(0, 0,0,0,0)
+addtorow$command <- row_lib
+
+print(table_lib,type = "latex", file = "latex/dom_lib_rb.tex", include.rownames=FALSE, add.to.row = addtorow, include.colnames = FALSE, latex.environments = "center")
+
+table_con <- xtable(dom_con[,c("dominant_square","et_sq_bl_mean","et_sq_bl_sd","et_cl_bl_mean","et_cl_bl_sd","et_sq_or_mean","et_sq_or_sd","et_cl_or_mean","et_cl_or_sd","vl_sq_bl_mean","vl_sq_bl_sd","vl_cl_bl_mean","vl_cl_bl_sd","vl_sq_or_mean","vl_sq_or_sd","vl_cl_or_mean","vl_cl_or_sd")], digits = 3)
+align(table_con) <- "c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|"
+
+addtorow <- list()
+addtorow$pos <- list(0, 0,0,0,0)
+addtorow$command <-  row_con
+
+print(table_con,type = "latex", file = "latex/dom_con_rb.tex", include.rownames=FALSE, add.to.row = addtorow, include.colnames = FALSE, latex.environments = "center")
+
+```
+
+```{r sens_secondary, fig.width=30, fig.cap="Test mechanism: increase secondary preference, all determinism high", echo=FALSE}
+
+# database filter
+excl <- names(value_basic) %in% c("run","density","step")
+sec_crl <- value_basic[!excl] %>% filter(ID == "sec_crl") %>%   #,  secondary_circle == 0 & dominant_square == 0 & secondary_square == 0)
+  group_by(ID,secondary_circle, dominant_circle,dominant_square,secondary_square,fraction_blue,circle_blue,circle_orange) %>% summarise_all(c("mean"= mean,"sd"= sd))
+
+# graph
+
+data_f <- sec_crl %>% gather(key= subgroup, value = Segra, et_sq_bl_mean, vl_sq_bl_mean, et_cl_bl_mean, vl_cl_bl_mean, et_sq_or_mean, vl_sq_or_mean, et_cl_or_mean, vl_cl_or_mean) %>% mutate(
+  `segregation` = fct_relevel(fct_collapse(subgroup,"ethnics" = c("et_sq_bl_mean","et_cl_bl_mean","et_sq_or_mean","et_cl_or_mean"), "values" = c("vl_sq_bl_mean","vl_cl_bl_mean","vl_sq_or_mean","vl_cl_or_mean")),"ethnics"),
+ `orientation` = fct_relevel(fct_collapse(subgroup, "conservative" = c("et_sq_bl_mean","vl_sq_bl_mean","et_sq_or_mean","vl_sq_or_mean"), "liberal" = c("et_cl_bl_mean","vl_cl_bl_mean","et_cl_or_mean","vl_cl_or_mean")),"conservative" ),
+ `ethnia` = fct_relevel(fct_collapse(subgroup, "local" = c("et_sq_bl_mean","vl_sq_bl_mean","et_cl_bl_mean","vl_cl_bl_mean"),"minority" = c("et_sq_or_mean","vl_sq_or_mean","et_cl_or_mean","vl_cl_or_mean")), "local"))
+
+sec_crl_pic <- ggplot(data = data_f, aes(x = secondary_circle, y = Segra, linetype = `segregation` , fill = `ethnia`,  shape = `orientation`)) + geom_line(aes(color = `ethnia`))  +  geom_point(color = "black", size = 4) +
+ scale_x_discrete(limits=c(seq(0,20 ,by = 1))) + scale_y_continuous(limits=c(0,1), breaks=seq(0,1,by=0.10)) +
+#geom_hline(yintercept = 0.50, color = "red") +
+ scale_linetype_manual(values=c("solid","dashed"), labels = c("ethnic","value"), guide = guide_legend(title = "Segregation", order = 1)) +
+  scale_fill_manual(values = c("blue","darkorange")) + 
+  scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
+  scale_shape_manual(values = c(22,21), guide = guide_legend(title="Value" ,override.aes = list(size = 3), order = 3)) +
+  guides(fill = FALSE) +
+  xlab("ß ethnic liberal") + ylab("Exposure") + 
+  theme_bw() +  theme( axis.title.x = (element_text(size = 15)), axis.title.y = (element_text(size = 15)), axis.text.x =  (element_text(size = 13)),axis.text.y =  (element_text(size = 15)), legend.title = element_text(size = 13) ,legend.text = element_text(size = 13), plot.title=element_text(hjust = 0.5)) + theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
+
+# ggsave("images/dom_lib.jpg",plot = last_plot(),
+#   device = NULL,path = NULL, 
+#   scale = 1,
+#   width = 10,
+#   height = 4,
+#   units = c("in", "cm", "mm"),
+#   dpi = 300,
+#   limitsize = FALSE)
+
+# sensitivity to conservative
+
+excl <- names(value_basic) %in% c("run","density","step")
+sec_sqr <- value_basic[!excl] %>% filter(ID == "sec_sqr") %>%
+   group_by(ID,secondary_square, dominant_square,dominant_circle,secondary_circle,fraction_blue,circle_blue,circle_orange) %>% summarise_all(c("mean"= mean,"sd"= sd))
+
+# graph
+
+data_f <- sec_sqr %>% gather(key= subgroup, value = Segra, et_sq_bl_mean, vl_sq_bl_mean, et_cl_bl_mean, vl_cl_bl_mean, et_sq_or_mean, vl_sq_or_mean, et_cl_or_mean, vl_cl_or_mean) %>% mutate(
+  `segregation` = fct_relevel(fct_collapse(subgroup,"ethnics" = c("et_sq_bl_mean","et_cl_bl_mean","et_sq_or_mean","et_cl_or_mean"), "values" = c("vl_sq_bl_mean","vl_cl_bl_mean","vl_sq_or_mean","vl_cl_or_mean")),"ethnics"),
+ `orientation` = fct_relevel(fct_collapse(subgroup, "conservative" = c("et_sq_bl_mean","vl_sq_bl_mean","et_sq_or_mean","vl_sq_or_mean"), "liberal" = c("et_cl_bl_mean","vl_cl_bl_mean","et_cl_or_mean","vl_cl_or_mean")),"conservative" ),
+ `ethnia` = fct_relevel(fct_collapse(subgroup, "local" = c("et_sq_bl_mean","vl_sq_bl_mean","et_cl_bl_mean","vl_cl_bl_mean"),"minority" = c("et_sq_or_mean","vl_sq_or_mean","et_cl_or_mean","vl_cl_or_mean")), "local"))
+
+sec_sqr_pic <- ggplot(data = data_f, aes(x = secondary_square, y = Segra, linetype = `segregation` , fill = `ethnia`,  shape = `orientation`)) + geom_line(aes(color = `ethnia`))  +  geom_point(color = "black", size = 4) +
+ scale_x_discrete(limits=c(seq(0,20 ,by = 1))) + scale_y_continuous(limits=c(0,1), breaks=seq(0,1,by=0.10)) +
+  scale_linetype_manual(values=c("solid","dashed"), labels = c("ethnic","value"), guide = guide_legend(title = "Segregation", order = 1)) +
+  scale_fill_manual(values = c("blue","darkorange")) + 
+  scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
+  scale_shape_manual(values = c(22,21), guide = guide_legend(title="Value" ,override.aes = list(size = 3), order = 3)) +
+  guides(fill = FALSE) +
+  xlab("ß value conservative") + ylab("Exposure") + 
+  theme_bw() +  theme( axis.title.x = (element_text(size = 15)), axis.title.y = (element_text(size = 15)), axis.text.x =  (element_text(size = 13)),axis.text.y =  (element_text(size = 15)), legend.title = element_text(size = 13) ,legend.text = element_text(size = 13), plot.title=element_text(hjust = 0.5)) + theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
+
+# ggsave("images/dom_con.jpg",plot = last_plot(),
+#   device = NULL,path = NULL, 
+#   scale = 1,
+#   width = 10,
+#   height = 4,
+#   units = c("in", "cm", "mm"),
+#   dpi = 300,
+#   limitsize = FALSE)
+#
+
+ggpubr::ggarrange(sec_crl_pic,sec_sqr_pic, nrow = 2, ncol = 1, common.legend = TRUE, legend = "right")
+
+ggsave("images/comb_sec_bln.jpg",plot = last_plot(),
+  device = NULL,path = NULL, 
+  scale = 1,
+ width = 8,
+  height = 6,
+  units = c("in", "cm", "mm"),
+  dpi = 300,
+  limitsize = FALSE)
+
+# robustness table
+
+row_lib <-  c("\\multicolumn{17}{|c|}{Baseline: increase ethnic liberal}  \\\\\\hline\n",
+   "Preference &  \\multicolumn{8}{|c|}{Ethnic Exposure} & \\multicolumn{8}{|c|}{Value Exposure}   \\\\\\hline\n",
+  "& \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  & \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  \\\\\n",
+# note
+"$\\beta$ ethnic & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
+& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
+& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal}\\\\\n",
+"liberal & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD\\\\\n")
+
+row_con <- c("\\multicolumn{17}{|c|}{Baseline: increase value conservative}  \\\\\\hline\n",
+   "Preference &  \\multicolumn{8}{|c|}{Ethnic Exposure} & \\multicolumn{8}{|c|}{Value Exposure}   \\\\\\hline\n",
+  "& \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  & \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  \\\\\n",
+# note
+"$\\beta$ value & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
+ & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
+& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal}\\\\\n",
+" conservative & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD\\\\\n")
+
+table_lib <- xtable(sec_crl[,c("secondary_circle","et_sq_bl_mean","et_sq_bl_sd","et_cl_bl_mean","et_cl_bl_sd","et_sq_or_mean","et_sq_or_sd","et_cl_or_mean","et_cl_or_sd","vl_sq_bl_mean","vl_sq_bl_sd","vl_cl_bl_mean","vl_cl_bl_sd","vl_sq_or_mean","vl_sq_or_sd","vl_cl_or_mean","vl_cl_or_sd")], digits = 3)
+align(table_lib) <- "c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|"
+
+addtorow <- list()
+addtorow$pos <- list(0, 0,0,0,0)
+addtorow$command <- row_lib
+
+print(table_lib,type = "latex", file = "latex/sec_crl_rb.tex", include.rownames=FALSE, add.to.row = addtorow, include.colnames = FALSE, latex.environments = "center")
+
+table_con <- xtable(sec_sqr[,c("secondary_square","et_sq_bl_mean","et_sq_bl_sd","et_cl_bl_mean","et_cl_bl_sd","et_sq_or_mean","et_sq_or_sd","et_cl_or_mean","et_cl_or_sd","vl_sq_bl_mean","vl_sq_bl_sd","vl_cl_bl_mean","vl_cl_bl_sd","vl_sq_or_mean","vl_sq_or_sd","vl_cl_or_mean","vl_cl_or_sd")], digits = 3)
+align(table_con) <- "c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|"
+
+addtorow <- list()
+addtorow$pos <- list(0, 0,0,0,0)
+addtorow$command <-  row_con
+
+print(table_con,type = "latex", file = "latex/sec_sqr_rb.tex", include.rownames=FALSE, add.to.row = addtorow, include.colnames = FALSE, latex.environments = "center")
+
+```
+
+```{r asym, fig.width=30, fig.cap="Baseline asymmetric conditions", echo=FALSE}
+
+# database filter
+excl <- names(asym_dom) %in% c("run", "ID","density","step")
+dataset_sa <- asym_dom[!excl] %>% group_by(dominant,circle_orange,circle_blue,fraction_blue,secondary) %>% summarise_all(c("mean"= mean,"sd"= sd))
+
+xlab_t <- "ß dominant"
+
+row_exp <- c("\\multicolumn{17}{|c|}{Ethnic asymmetric condition: Exposure}  \\\\\\hline\n",
+   "Preference &  \\multicolumn{8}{|c|}{Ethnic Exposure} & \\multicolumn{8}{|c|}{Value Exposure}   \\\\\\hline\n",
+  "& \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  & \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  \\\\\n",
+"$\\beta$ sec = 0 & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
+& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
+& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal}\\\\\n",
+" & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD\\\\\n")
+
+row_prox <- c("\\multicolumn{17}{|c|}{Ethnic Asymmetric condition: Spatial Proximity}  \\\\\\hline\n",
+   "Preference &  \\multicolumn{8}{|c|}{Ethnic Proximity} & \\multicolumn{8}{|c|}{Value Proximity}   \\\\\\hline\n",
+  "& \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  & \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  \\\\\n",
+"$\\beta$ sec = 0 & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
+& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
+& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal}\\\\\n",
+" & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD\\\\\n")
+
+tablerb_expname <- "latex/asym_rb_exp.tex"
+tablerb_proxname <- "latex/asym_rb_prox.tex"
+
+plotname <- "images/asym_dom.jpg"
+
+# graph
+
+data_exp <- dataset_sa %>% gather(key= subgroup, value = Expo, et_sq_bl_mean, vl_sq_bl_mean, et_cl_bl_mean, vl_cl_bl_mean, et_sq_or_mean, vl_sq_or_mean, et_cl_or_mean, vl_cl_or_mean) %>% mutate(
+  `segregation` = fct_relevel(fct_collapse(subgroup,"ethnics" = c("et_sq_bl_mean","et_cl_bl_mean","et_sq_or_mean","et_cl_or_mean"), "values" = c("vl_sq_bl_mean","vl_cl_bl_mean","vl_sq_or_mean","vl_cl_or_mean")),"ethnics"),
+ `orientation` = fct_relevel(fct_collapse(subgroup, "conservative" = c("et_sq_bl_mean","vl_sq_bl_mean","et_sq_or_mean","vl_sq_or_mean"), "liberal" = c("et_cl_bl_mean","vl_cl_bl_mean","et_cl_or_mean","vl_cl_or_mean")),"conservative" ),
+ `ethnia` = fct_relevel(fct_collapse(subgroup, "local" = c("et_sq_bl_mean","vl_sq_bl_mean","et_cl_bl_mean","vl_cl_bl_mean"),"minority" = c("et_sq_or_mean","vl_sq_or_mean","et_cl_or_mean","vl_cl_or_mean")), "local"))
+
+fig_exp <- ggplot(data = data_exp, aes(x = dominant, y = Expo, linetype = `segregation` , fill = `ethnia`,  shape = `orientation`)) + geom_line(aes(color = `ethnia`))  +  geom_point(color = "black", size = 4) +
+ scale_x_discrete(limits=c(seq(0,20 ,by = 1))) + scale_y_continuous(limits=c(0,1), breaks=seq(0,1,by=0.10)) +
+  geom_vline(xintercept = 20, color = "red") +
+  scale_linetype_manual(values=c("solid","dashed"), labels = c("ethnic","value"), guide = guide_legend(title = "Segregation", order = 1)) +
+  scale_fill_manual(values = c("blue","darkorange")) + 
+  scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
+  scale_shape_manual(values = c(22,21), guide = guide_legend(title="Value" ,override.aes = list(size = 3), order = 3)) +
+  guides(fill = FALSE) +
+  xlab("") + ylab("Exposure") + 
+  theme_bw() +  theme( axis.title.x  = element_blank(), axis.title.y = (element_text(size = 15)), axis.text.x  = (element_text(size = 10)) ,axis.text.y =  (element_text(size = 15)), legend.title = element_text(size = 13) ,legend.text = element_text(size = 13), plot.title=element_text(hjust = 0.5)) + theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
+
+tablerb_exp <- xtable(dataset_sa[,c("dominant","et_sq_bl_mean","et_sq_bl_sd","et_cl_bl_mean","et_cl_bl_sd","et_sq_or_mean","et_sq_or_sd","et_cl_or_mean","et_cl_or_sd","vl_sq_bl_mean","vl_sq_bl_sd","vl_cl_bl_mean","vl_cl_bl_sd","vl_sq_or_mean","vl_sq_or_sd","vl_cl_or_mean","vl_cl_or_sd")], digits = 3)
+align(tablerb_exp) <- "c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|"
+
+addtorow <- list()
+addtorow$pos <- list(0, 0,0,0,0)
+addtorow$command <-  row_exp
+
+print(tablerb_exp,type = "latex", file = tablerb_expname, include.rownames=FALSE, add.to.row = addtorow, include.colnames = FALSE, latex.environments = "center")
+
+## Spatial proximity baseline asymmetric
+
+# graph
+
+data_prox <- dataset_sa %>% gather(key= subgroup, value = Prox, de_sq_bl_mean, dv_sq_bl_mean, de_cl_bl_mean, dv_cl_bl_mean, de_sq_or_mean, dv_sq_or_mean, de_cl_or_mean, dv_cl_or_mean) %>% mutate(
+  `segregation` = fct_relevel(fct_collapse(subgroup,"ethnics" = c("de_sq_bl_mean","de_cl_bl_mean","de_sq_or_mean","de_cl_or_mean"), "values" = c("dv_sq_bl_mean","dv_cl_bl_mean","dv_sq_or_mean","dv_cl_or_mean")),"ethnics"),
+ `orientation` = fct_relevel(fct_collapse(subgroup, "conservative" = c("de_sq_bl_mean","dv_sq_bl_mean","de_sq_or_mean","dv_sq_or_mean"), "liberal" = c("de_cl_bl_mean","dv_cl_bl_mean","de_cl_or_mean","dv_cl_or_mean")),"conservative" ),
+ `ethnia` = fct_relevel(fct_collapse(subgroup, "local" = c("de_sq_bl_mean","dv_sq_bl_mean","de_cl_bl_mean","dv_cl_bl_mean"),"minority" = c("de_sq_or_mean","dv_sq_or_mean","de_cl_or_mean","dv_cl_or_mean")), "local"))
+
+fig_prox <- ggplot(data = data_prox, aes(x = dominant, y = Prox, linetype = `segregation` , fill = `ethnia`,  shape = `orientation`)) + geom_line(aes(color = `ethnia`))  +  geom_point(color = "black", size = 4) +
+ scale_x_discrete(limits=c(seq(0,20 ,by = 1))) + scale_y_continuous(limits=c(min(data_prox$Prox),max(data_prox$Prox)), breaks=seq(0,max(data_prox$Prox),by=0.50)) +
+  geom_vline(xintercept = 20, color = "red") +
+  scale_linetype_manual(values=c("solid","dashed"), labels = c("ethnic","value"), guide = guide_legend(title = "Segregation", order = 1)) +
+  scale_fill_manual(values = c("blue","darkorange")) + 
+  scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
+  scale_shape_manual(values = c(22,21), guide = guide_legend(title="Value" ,override.aes = list(size = 3), order = 3)) +
+  guides(fill = FALSE) +
+  xlab(xlab_t) + ylab("Spatial Proximity") + 
+  theme_bw() +  theme( axis.title.x = (element_text(size = 15)), axis.title.y = (element_text(size = 15)), axis.text.x =  (element_text(size = 15)),axis.text.y =  (element_text(size = 15)), legend.title = element_text(size = 13) ,legend.text = element_text(size = 13), plot.title=element_text(hjust = 0.5)) + theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
+
+# robustness table
+
+tablerb_prox <- xtable(dataset_sa[,c("dominant","de_sq_bl_mean","de_sq_bl_sd","de_cl_bl_mean","de_cl_bl_sd","de_sq_or_mean","de_sq_or_sd","de_cl_or_mean","de_cl_or_sd","dv_sq_bl_mean","dv_sq_bl_sd","dv_cl_bl_mean","dv_cl_bl_sd","dv_sq_or_mean","dv_sq_or_sd","dv_cl_or_mean","dv_cl_or_sd")], digits = 3)
+align(tablerb_prox) <- "c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|"
+
+addtorow <- list()
+addtorow$pos <- list(0, 0,0,0,0)
+addtorow$command <-  row_prox
+print(tablerb_prox,type = "latex", file = tablerb_proxname , include.rownames=FALSE, add.to.row = addtorow, include.colnames = FALSE, latex.environments = "center")
+
+# combined image
+
+ggpubr::ggarrange(fig_exp,fig_prox, nrow = 2, ncol = 1, common.legend = TRUE, legend = "right")
+
+ggsave(plotname,plot = last_plot(),
+  device = NULL,path = NULL, 
+  scale = 1,
+  width = 8,
+  height = 6,
+  units = c("in", "cm", "mm"),
+  dpi = 300,
+  limitsize = FALSE)
+
+```
+
+```{r dislib, fig.width=30, fig.cap="Effect distribution liberal minority, asymmetric based condition", echo=FALSE}
+
+# CHECK LATEX! Re-edited
+
+# database filter
+excl <- names(dislib) %in% c("run", "ID","density","step","eth_lib_loc","eth_lib_min","val_con_loc","val_con_min")
+dataset_sa <- dislib[!excl] %>% group_by(fraction_blue,circle_blue,eth_con_loc,eth_con_min,val_lib_loc,val_lib_min,circle_orange) %>% summarise_all(c("mean"= mean,"sd"= sd))
+
+xlab_t <- "% liberal minority"
+
+row_exp <- c("\\multicolumn{17}{|c|}{Ethnic asymmetric condition: Exposure}  \\\\\\hline\n",
+   "$\\beta$ dom = 20 &  \\multicolumn{8}{|c|}{Ethnic Exposure} & \\multicolumn{8}{|c|}{Value Exposure}   \\\\\\n",
+     "$\\beta$ sec = 0 &  \\multicolumn{8}{|c|}{} & \\multicolumn{8}{|c|}{}   \\\\\\hline\n",
+  "& \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  & \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  \\\\\n",
+"$\\%$ liberal & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
+& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
+& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal}\\\\\n",
+"minority  & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD\\\\\n")
+
+row_prox <-  c("\\multicolumn{17}{|c|}{Ethnic asymmetric condition: Spatial Proximity}  \\\\\\hline\n",
+   "$\\beta$ dom = 20 &  \\multicolumn{8}{|c|}{Ethnic Exposure} & \\multicolumn{8}{|c|}{Value Exposure}   \\\\\\n",
+     "$\\beta$ sec = 0 &  \\multicolumn{8}{|c|}{} & \\multicolumn{8}{|c|}{}   \\\\\\hline\n",
+  "& \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  & \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  \\\\\n",
+"$\\%$ liberal & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
+& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
+& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal}\\\\\n",
+"minority  & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD\\\\\n")
+
+tablerb_expname <- "latex/dislib_rb_exp.tex"
+tablerb_proxname <- "latex/dislib_rb_prox.tex"
+
+plotname <- "images/comb_dislib.jpg"
+
+# graph
+
+dataset_sa <- subset(dataset_sa, circle_orange >= 10 & circle_orange <= 90)
+data_exp <- dataset_sa %>% gather(key= subgroup, value = Expo, et_sq_bl_mean, vl_sq_bl_mean, et_cl_bl_mean, vl_cl_bl_mean, et_sq_or_mean, vl_sq_or_mean, et_cl_or_mean, vl_cl_or_mean) %>% mutate(
+  `segregation` = fct_relevel(fct_collapse(subgroup,"ethnics" = c("et_sq_bl_mean","et_cl_bl_mean","et_sq_or_mean","et_cl_or_mean"), "values" = c("vl_sq_bl_mean","vl_cl_bl_mean","vl_sq_or_mean","vl_cl_or_mean")),"ethnics"),
+ `orientation` = fct_relevel(fct_collapse(subgroup, "conservative" = c("et_sq_bl_mean","vl_sq_bl_mean","et_sq_or_mean","vl_sq_or_mean"), "liberal" = c("et_cl_bl_mean","vl_cl_bl_mean","et_cl_or_mean","vl_cl_or_mean")),"conservative" ),
+ `ethnia` = fct_relevel(fct_collapse(subgroup, "local" = c("et_sq_bl_mean","vl_sq_bl_mean","et_cl_bl_mean","vl_cl_bl_mean"),"minority" = c("et_sq_or_mean","vl_sq_or_mean","et_cl_or_mean","vl_cl_or_mean")), "local"))
+
+fig_exp <- ggplot(data = data_exp, aes(x = circle_orange, y = Expo, linetype = `segregation` , fill = `ethnia`,  shape = `orientation`)) + geom_line(aes(color = `ethnia`))  +  geom_point(color = "black", size = 4) +
+ scale_x_discrete(limits=c(seq(10,90 ,by = 10))) + scale_y_continuous(limits=c(0,1), breaks=seq(0,1,by=0.10)) +
+   geom_vline(xintercept = 50, color = "red") +
+ scale_linetype_manual(values=c("solid","dashed"), labels = c("ethnic","value"), guide = guide_legend(title = "Segregation", order = 1)) +
+  scale_fill_manual(values = c("blue","darkorange")) + 
+  scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
+  scale_shape_manual(values = c(22,21), guide = guide_legend(title="Value" ,override.aes = list(size = 3), order = 3)) +
+  guides(fill = FALSE) +
+  xlab("") + ylab("Exposure") + 
+  theme_bw() +  theme( axis.title.x  = element_blank(), axis.title.y = (element_text(size = 15)), axis.text.x  = (element_text(size = 10)) ,axis.text.y =  (element_text(size = 15)), legend.title = element_text(size = 13) ,legend.text = element_text(size = 13), plot.title=element_text(hjust = 0.5)) + theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
+
+tablerb_exp <- xtable(dataset_sa[,c("circle_orange","et_sq_bl_mean","et_sq_bl_sd","et_cl_bl_mean","et_cl_bl_sd","et_sq_or_mean","et_sq_or_sd","et_cl_or_mean","et_cl_or_sd","vl_sq_bl_mean","vl_sq_bl_sd","vl_cl_bl_mean","vl_cl_bl_sd","vl_sq_or_mean","vl_sq_or_sd","vl_cl_or_mean","vl_cl_or_sd")], digits = 3)
+align(tablerb_exp) <- "c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|"
+
+addtorow <- list()
+addtorow$pos <- list(0, 0,0,0,0)
+addtorow$command <-  row_exp
+
+print(tablerb_exp,type = "latex", file = tablerb_expname, include.rownames=FALSE, add.to.row = addtorow, include.colnames = FALSE, latex.environments = "center")
+
+## Spatial proximity baseline asymmetric
+
+# graph
+
+data_prox <- dataset_sa %>% gather(key= subgroup, value = Prox, de_sq_bl_mean, dv_sq_bl_mean, de_cl_bl_mean, dv_cl_bl_mean, de_sq_or_mean, dv_sq_or_mean, de_cl_or_mean, dv_cl_or_mean) %>% mutate(
+  `segregation` = fct_relevel(fct_collapse(subgroup,"ethnics" = c("de_sq_bl_mean","de_cl_bl_mean","de_sq_or_mean","de_cl_or_mean"), "values" = c("dv_sq_bl_mean","dv_cl_bl_mean","dv_sq_or_mean","dv_cl_or_mean")),"ethnics"),
+ `orientation` = fct_relevel(fct_collapse(subgroup, "conservative" = c("de_sq_bl_mean","dv_sq_bl_mean","de_sq_or_mean","dv_sq_or_mean"), "liberal" = c("de_cl_bl_mean","dv_cl_bl_mean","de_cl_or_mean","dv_cl_or_mean")),"conservative" ),
+ `ethnia` = fct_relevel(fct_collapse(subgroup, "local" = c("de_sq_bl_mean","dv_sq_bl_mean","de_cl_bl_mean","dv_cl_bl_mean"),"minority" = c("de_sq_or_mean","dv_sq_or_mean","de_cl_or_mean","dv_cl_or_mean")), "local"))
+
+fig_prox <- ggplot(data = data_prox, aes(x = circle_orange, y = Prox, linetype = `segregation` , fill = `ethnia`,  shape = `orientation`)) + geom_line(aes(color = `ethnia`))  +  geom_point(color = "black", size = 4) +
+ scale_x_discrete(limits=c(seq(10,90 ,by = 10))) + scale_y_continuous(limits=c(min(data_prox$Prox),max(data_prox$Prox)), breaks = seq(0,max(data_prox$Prox), by = 0.5)) +
+   geom_vline(xintercept = 50, color = "red") +
+ scale_linetype_manual(values=c("solid","dashed"), labels = c("ethnic","value"), guide = guide_legend(title = "Segregation", order = 1)) +
+  scale_fill_manual(values = c("blue","darkorange")) + 
+  scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
+  scale_shape_manual(values = c(22,21), guide = guide_legend(title="Value" ,override.aes = list(size = 3), order = 3)) +
+  guides(fill = FALSE) +
+  xlab(xlab_t) + ylab("Spatial Proximity") + 
+theme_bw() +  theme( axis.title.x = (element_text(size = 15)), axis.title.y = (element_text(size = 15)), axis.text.x =  (element_text(size = 15)),axis.text.y =  (element_text(size = 15)), legend.title = element_text(size = 13) ,legend.text = element_text(size = 13), plot.title=element_text(hjust = 0.5)) + theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
+
+# robustness table
+
+tablerb_prox <- xtable(dataset_sa[,c("circle_orange","de_sq_bl_mean","de_sq_bl_sd","de_cl_bl_mean","de_cl_bl_sd","de_sq_or_mean","de_sq_or_sd","de_cl_or_mean","de_cl_or_sd","dv_sq_bl_mean","dv_sq_bl_sd","dv_cl_bl_mean","dv_cl_bl_sd","dv_sq_or_mean","dv_sq_or_sd","dv_cl_or_mean","dv_cl_or_sd")], digits = 3)
+align(tablerb_prox) <- "c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|"
+
+addtorow <- list()
+addtorow$pos <- list(0, 0,0,0,0)
+addtorow$command <-  row_prox
+print(tablerb_prox,type = "latex", file = tablerb_proxname , include.rownames=FALSE, add.to.row = addtorow, include.colnames = FALSE, latex.environments = "center")
+
+# combined image
+
+ggpubr::ggarrange(fig_exp,fig_prox, nrow = 2, ncol = 1, common.legend = TRUE, legend = "right")
+
+ggsave(plotname,plot = last_plot(),
+  device = NULL,path = NULL, 
+  scale = 1,
+  width = 8,
+  height = 6,
+  units = c("in", "cm", "mm"),
+  dpi = 300,
+  limitsize = FALSE)
+
+```
+
+```{r sa_dom_50prox, fig.width=30, fig.cap="Sensitivity proximity ethnic conservative local, baseline asymmetric conditions", echo=FALSE}
+
+# database filter
+excl <- names(sa_asym) %in% c("run", "ID","density","step","eth_lib_loc","val_con_loc","eth_lib_min","val_con_min")
+dataset_sa <- sa_asym[!excl] %>% filter(val_lib_loc  == 20,eth_con_min == 20, val_lib_min == 20)  %>% 
+ filter(circle_orange == 50) %>%
+  group_by(eth_con_loc,fraction_blue,circle_blue, circle_orange) %>% summarise_all(c("mean"= mean,"sd"= sd))
+
+xlab_t <- "ß ethnic conservative local"
+
+# graph
+
+data_prox <- dataset_sa %>% gather(key= subgroup, value = Prox, de_sq_bl_mean, dv_sq_bl_mean, de_cl_bl_mean, dv_cl_bl_mean, de_sq_or_mean, dv_sq_or_mean, de_cl_or_mean, dv_cl_or_mean) %>% mutate(
+  `segregation` = fct_relevel(fct_collapse(subgroup,"ethnics" = c("de_sq_bl_mean","de_cl_bl_mean","de_sq_or_mean","de_cl_or_mean"), "values" = c("dv_sq_bl_mean","dv_cl_bl_mean","dv_sq_or_mean","dv_cl_or_mean")),"ethnics"),
+ `orientation` = fct_relevel(fct_collapse(subgroup, "conservative" = c("de_sq_bl_mean","dv_sq_bl_mean","de_sq_or_mean","dv_sq_or_mean"), "liberal" = c("de_cl_bl_mean","dv_cl_bl_mean","de_cl_or_mean","dv_cl_or_mean")),"conservative" ),
+ `ethnia` = fct_relevel(fct_collapse(subgroup, "local" = c("de_sq_bl_mean","dv_sq_bl_mean","de_cl_bl_mean","dv_cl_bl_mean"),"minority" = c("de_sq_or_mean","dv_sq_or_mean","de_cl_or_mean","dv_cl_or_mean")), "local"))
+
+prox_eth_con_loc <- ggplot(data = data_prox, aes(x = eth_con_loc, y = Prox, linetype = `segregation` , fill = `ethnia`,  shape = `orientation`)) + geom_line(aes(color = `ethnia`))  +  geom_point(color = "black", size = 4) +
+ scale_x_discrete(limits=c(seq(0,20 ,by = 1)))  + scale_y_continuous(limits=c(min(data_prox$Prox),5), breaks=seq(0,5,by=0.50)) +
+  #    facet_wrap(~ circle_orange, labeller = labeller(circle_orange = circle_orange.labs)) +
+    geom_vline(xintercept = 20, color = "red") +
+
+  scale_linetype_manual(values=c("solid","dashed"), labels = c("ethnic","value"), guide = guide_legend(title = "Segregation", order = 1)) +
+  scale_fill_manual(values = c("blue","darkorange")) + 
+  scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
+  scale_shape_manual(values = c(22,21), guide = guide_legend(title="Value" ,override.aes = list(size = 3), order = 3)) +
+  guides(fill = FALSE) +
+  xlab(xlab_t) + ylab("Spatial Proximity") + 
+  theme_bw() +  theme( axis.title.x = (element_text(size = 15)), axis.title.y = (element_text(size = 15)), axis.text.x =  (element_text(size = 12)),axis.text.y =  (element_text(size = 15)), legend.title = element_text(size = 13) ,legend.text = element_text(size = 13),plot.title=element_text(hjust = 0.5)) + theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
+
+# database filter
+excl <- names(sa_asym) %in% c("run", "ID","density","step","eth_lib_loc","val_con_loc","eth_lib_min","val_con_min")
+dataset_sa <- sa_asym[!excl] %>% filter(eth_con_loc   == 20,eth_con_min == 20, val_lib_min == 20)  %>% 
+ filter(circle_orange == 50) %>%
+  group_by(val_lib_loc,fraction_blue,circle_blue, circle_orange) %>% summarise_all(c("mean"= mean,"sd"= sd))
+
+xlab_t <- "ß value liberal local"
+
+# graph
+
+data_prox <- dataset_sa %>% gather(key= subgroup, value = Prox, de_sq_bl_mean, dv_sq_bl_mean, de_cl_bl_mean, dv_cl_bl_mean, de_sq_or_mean, dv_sq_or_mean, de_cl_or_mean, dv_cl_or_mean) %>% mutate(
+  `segregation` = fct_relevel(fct_collapse(subgroup,"ethnics" = c("de_sq_bl_mean","de_cl_bl_mean","de_sq_or_mean","de_cl_or_mean"), "values" = c("dv_sq_bl_mean","dv_cl_bl_mean","dv_sq_or_mean","dv_cl_or_mean")),"ethnics"),
+ `orientation` = fct_relevel(fct_collapse(subgroup, "conservative" = c("de_sq_bl_mean","dv_sq_bl_mean","de_sq_or_mean","dv_sq_or_mean"), "liberal" = c("de_cl_bl_mean","dv_cl_bl_mean","de_cl_or_mean","dv_cl_or_mean")),"conservative" ),
+ `ethnia` = fct_relevel(fct_collapse(subgroup, "local" = c("de_sq_bl_mean","dv_sq_bl_mean","de_cl_bl_mean","dv_cl_bl_mean"),"minority" = c("de_sq_or_mean","dv_sq_or_mean","de_cl_or_mean","dv_cl_or_mean")), "local"))
+
+prox_val_lib_loc <-  ggplot(data = data_prox, aes(x = val_lib_loc, y = Prox, linetype = `segregation` , fill = `ethnia`,  shape = `orientation`)) + geom_line(aes(color = `ethnia`))  +  geom_point(color = "black", size = 4) +
+ scale_x_discrete(limits=c(seq(0,20 ,by = 1)))  + scale_y_continuous(limits=c(min(data_prox$Prox),5), breaks=seq(0,5,by=0.50)) +
+  #    facet_wrap(~ circle_orange, labeller = labeller(circle_orange = circle_orange.labs)) +
+    geom_vline(xintercept = 20, color = "red") +
+
+  scale_linetype_manual(values=c("solid","dashed"), labels = c("ethnic","value"), guide = guide_legend(title = "Segregation", order = 1)) +
+  scale_fill_manual(values = c("blue","darkorange")) + 
+  scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
+  scale_shape_manual(values = c(22,21), guide = guide_legend(title="Value" ,override.aes = list(size = 3), order = 3)) +
+  guides(fill = FALSE) +
+  xlab(xlab_t) + ylab("Spatial Proximity") + 
+  theme_bw() +  theme( axis.title.x = (element_text(size = 15)), axis.title.y = (element_text(size = 15)), axis.text.x =  (element_text(size = 12)),axis.text.y =  (element_text(size = 15)), legend.title = element_text(size = 13) ,legend.text = element_text(size = 13),plot.title=element_text(hjust = 0.5)) + theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
+
+# ggsave("images/val_lib_loc50.jpg",plot = fig_prox,
+#   device = NULL,path = NULL, 
+#   scale = 1,
+#   width = 8,
+#   height = 6,
+#   units = c("in", "cm", "mm"),
+#   dpi = 300,
+#   limitsize = FALSE)
+
+# database filter
+excl <- names(sa_asym) %in% c("run", "ID","density","step","eth_lib_loc","val_con_loc","eth_lib_min","val_con_min")
+dataset_sa <- sa_asym[!excl] %>% filter(eth_con_loc   == 20, val_lib_loc  == 20, val_lib_min == 20)  %>% 
+ filter(circle_orange == 50) %>%
+  group_by(eth_con_min,fraction_blue,circle_blue, circle_orange) %>% summarise_all(c("mean"= mean,"sd"= sd))
+
+xlab_t <- "ß ethnic conservative minority"
+
+# graph
+
+data_prox <- dataset_sa %>% gather(key= subgroup, value = Prox, de_sq_bl_mean, dv_sq_bl_mean, de_cl_bl_mean, dv_cl_bl_mean, de_sq_or_mean, dv_sq_or_mean, de_cl_or_mean, dv_cl_or_mean) %>% mutate(
+  `segregation` = fct_relevel(fct_collapse(subgroup,"ethnics" = c("de_sq_bl_mean","de_cl_bl_mean","de_sq_or_mean","de_cl_or_mean"), "values" = c("dv_sq_bl_mean","dv_cl_bl_mean","dv_sq_or_mean","dv_cl_or_mean")),"ethnics"),
+ `orientation` = fct_relevel(fct_collapse(subgroup, "conservative" = c("de_sq_bl_mean","dv_sq_bl_mean","de_sq_or_mean","dv_sq_or_mean"), "liberal" = c("de_cl_bl_mean","dv_cl_bl_mean","de_cl_or_mean","dv_cl_or_mean")),"conservative" ),
+ `ethnia` = fct_relevel(fct_collapse(subgroup, "local" = c("de_sq_bl_mean","dv_sq_bl_mean","de_cl_bl_mean","dv_cl_bl_mean"),"minority" = c("de_sq_or_mean","dv_sq_or_mean","de_cl_or_mean","dv_cl_or_mean")), "local"))
+
+prox_eth_con_min <- ggplot(data = data_prox, aes(x = eth_con_min, y = Prox, linetype = `segregation` , fill = `ethnia`,  shape = `orientation`)) + geom_line(aes(color = `ethnia`))  +  geom_point(color = "black", size = 4) +
+ scale_x_discrete(limits=c(seq(0,20 ,by = 1)))  + scale_y_continuous(limits=c(min(data_prox$Prox),5), breaks=seq(0,5,by=0.50)) +
+  #    facet_wrap(~ circle_orange, labeller = labeller(circle_orange = circle_orange.labs)) +
+    geom_vline(xintercept = 20, color = "red") +
+
+  scale_linetype_manual(values=c("solid","dashed"), labels = c("ethnic","value"), guide = guide_legend(title = "Segregation", order = 1)) +
+  scale_fill_manual(values = c("blue","darkorange")) + 
+  scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
+  scale_shape_manual(values = c(22,21), guide = guide_legend(title="Value" ,override.aes = list(size = 3), order = 3)) +
+  guides(fill = FALSE) +
+  xlab(xlab_t) + ylab("Spatial Proximity") + 
+  theme_bw() +  theme( axis.title.x = (element_text(size = 15)), axis.title.y = (element_text(size = 15)), axis.text.x =  (element_text(size = 12)),axis.text.y =  (element_text(size = 15)), legend.title = element_text(size = 13) ,legend.text = element_text(size = 13),plot.title=element_text(hjust = 0.5)) + theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
+
+# ggsave("images/eth_con_min50.jpg",plot = fig_prox,
+#   device = NULL,path = NULL, 
+#   scale = 1,
+#   width = 8,
+#   height = 6,
+#   units = c("in", "cm", "mm"),
+#   dpi = 300,
+#   limitsize = FALSE)
+
+# database filter
+excl <- names(sa_asym) %in% c("run", "ID","density","step","eth_lib_loc","val_con_loc","eth_lib_min","val_con_min")
+dataset_sa <- sa_asym[!excl] %>% filter(eth_con_loc   == 20, val_lib_loc  == 20, eth_con_min  == 20)  %>% 
+ filter(circle_orange == 50) %>%
+  group_by(val_lib_min,fraction_blue,circle_blue, circle_orange) %>% summarise_all(c("mean"= mean,"sd"= sd))
+
+xlab_t <- "ß value liberal minority"
+
+# graph
+
+data_prox <- dataset_sa %>% gather(key= subgroup, value = Prox, de_sq_bl_mean, dv_sq_bl_mean, de_cl_bl_mean, dv_cl_bl_mean, de_sq_or_mean, dv_sq_or_mean, de_cl_or_mean, dv_cl_or_mean) %>% mutate(
+  `segregation` = fct_relevel(fct_collapse(subgroup,"ethnics" = c("de_sq_bl_mean","de_cl_bl_mean","de_sq_or_mean","de_cl_or_mean"), "values" = c("dv_sq_bl_mean","dv_cl_bl_mean","dv_sq_or_mean","dv_cl_or_mean")),"ethnics"),
+ `orientation` = fct_relevel(fct_collapse(subgroup, "conservative" = c("de_sq_bl_mean","dv_sq_bl_mean","de_sq_or_mean","dv_sq_or_mean"), "liberal" = c("de_cl_bl_mean","dv_cl_bl_mean","de_cl_or_mean","dv_cl_or_mean")),"conservative" ),
+ `ethnia` = fct_relevel(fct_collapse(subgroup, "local" = c("de_sq_bl_mean","dv_sq_bl_mean","de_cl_bl_mean","dv_cl_bl_mean"),"minority" = c("de_sq_or_mean","dv_sq_or_mean","de_cl_or_mean","dv_cl_or_mean")), "local"))
+
+prox_val_lib_min <-  ggplot(data = data_prox, aes(x = val_lib_min, y = Prox, linetype = `segregation` , fill = `ethnia`,  shape = `orientation`)) + geom_line(aes(color = `ethnia`))  +  geom_point(color = "black", size = 4) +
+ scale_x_discrete(limits=c(seq(0,20 ,by = 1)))  + scale_y_continuous(limits=c(min(data_prox$Prox),5), breaks=seq(0,5,by=0.50)) +
+  #    facet_wrap(~ circle_orange, labeller = labeller(circle_orange = circle_orange.labs)) +
+    geom_vline(xintercept = 20, color = "red") +
+
+  scale_linetype_manual(values=c("solid","dashed"), labels = c("ethnic","value"), guide = guide_legend(title = "Segregation", order = 1)) +
+  scale_fill_manual(values = c("blue","darkorange")) + 
+  scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
+  scale_shape_manual(values = c(22,21), guide = guide_legend(title="Value" ,override.aes = list(size = 3), order = 3)) +
+  guides(fill = FALSE) +
+  xlab(xlab_t) + ylab("Spatial Proximity") + 
+  theme_bw() +  theme( axis.title.x = (element_text(size = 15)), axis.title.y = (element_text(size = 15)), axis.text.x =  (element_text(size = 12)),axis.text.y =  (element_text(size = 15)), legend.title = element_text(size = 13) ,legend.text = element_text(size = 13),plot.title=element_text(hjust = 0.5)) + theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
+
+ggpubr::ggarrange(prox_eth_con_loc,prox_val_lib_loc,prox_eth_con_min,prox_val_lib_min, nrow = 2, ncol = 2, common.legend = TRUE, legend = "bottom")
+
+ggsave("images/sa_asym_bt.jpg",plot = last_plot(),
+  device = NULL,path = NULL,
+  scale = 1,
+  width = 11,
+  height = 8,
+  units = c("in", "cm", "mm"),
+  dpi = 300,
+  limitsize = FALSE)
+
+```
+
+```{r sa_dom_50exp, fig.width=30, fig.cap="exposure Sensitivity ethnic conservative local, baseline asymmetric conditions", echo=FALSE}
+## NOT INCLUDED IN THE PAPER
+# database filter
+excl <- names(sa_asym) %in% c("run", "ID","density","step","eth_lib_loc","val_con_loc","eth_lib_min","val_con_min")
+dataset_sa <- sa_asym[!excl] %>% filter(val_lib_loc  == 20,eth_con_min == 20, val_lib_min == 20)  %>% 
+ filter(circle_orange == 50) %>%
+  group_by(eth_con_loc,fraction_blue,circle_blue, circle_orange) %>% summarise_all(c("mean"= mean,"sd"= sd))
+
+xlab_t <- "ß ethnic conservative local"
+
+# graph
+
+data_exp <- dataset_sa %>% gather(key= subgroup, value = Expo, et_sq_bl_mean, vl_sq_bl_mean, et_cl_bl_mean, vl_cl_bl_mean, et_sq_or_mean, vl_sq_or_mean, et_cl_or_mean, vl_cl_or_mean) %>% mutate(
+  `segregation` = fct_relevel(fct_collapse(subgroup,"ethnics" = c("et_sq_bl_mean","et_cl_bl_mean","et_sq_or_mean","et_cl_or_mean"), "values" = c("vl_sq_bl_mean","vl_cl_bl_mean","vl_sq_or_mean","vl_cl_or_mean")),"ethnics"),
+ `orientation` = fct_relevel(fct_collapse(subgroup, "conservative" = c("et_sq_bl_mean","vl_sq_bl_mean","et_sq_or_mean","vl_sq_or_mean"), "liberal" = c("et_cl_bl_mean","vl_cl_bl_mean","et_cl_or_mean","vl_cl_or_mean")),"conservative" ),
+ `ethnia` = fct_relevel(fct_collapse(subgroup, "local" = c("et_sq_bl_mean","vl_sq_bl_mean","et_cl_bl_mean","vl_cl_bl_mean"),"minority" = c("et_sq_or_mean","vl_sq_or_mean","et_cl_or_mean","vl_cl_or_mean")), "local"))
+
+exp_eth_con_loc <- ggplot(data = data_exp, aes(x = eth_con_loc, y = Expo, linetype = `segregation` , fill = `ethnia`,  shape = `orientation`)) + geom_line(aes(color = `ethnia`))  +  geom_point(color = "black", size = 4) +
+ scale_x_discrete(limits=c(seq(0,20 ,by = 1)))  + scale_y_continuous(limits=c(0,1), breaks=seq(0,1,by=0.10)) +
+  #    facet_wrap(~ circle_orange, labeller = labeller(circle_orange = circle_orange.labs)) +
+    geom_vline(xintercept = 20, color = "red") +
+
+  scale_linetype_manual(values=c("solid","dashed"), labels = c("ethnic","value"), guide = guide_legend(title = "Segregation", order = 1)) +
+  scale_fill_manual(values = c("blue","darkorange")) + 
+  scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
+  scale_shape_manual(values = c(22,21), guide = guide_legend(title="Value" ,override.aes = list(size = 3), order = 3)) +
+  guides(fill = FALSE) +
+  xlab(xlab_t) + ylab("Exposure") + 
+  theme_bw() +  theme( axis.title.x = (element_text(size = 15)), axis.title.y = (element_text(size = 15)), axis.text.x =  (element_text(size = 12)),axis.text.y =  (element_text(size = 15)), legend.title = element_text(size = 13) ,legend.text = element_text(size = 13),plot.title=element_text(hjust = 0.5)) + theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
+# ggsave("images/eth_con_loc50.jpg",plot = fig_expo,
+#   device = NULL,path = NULL, 
+#   scale = 1,
+#   width = 8,
+#   height = 6,
+#   units = c("in", "cm", "mm"),
+#   dpi = 300,
+#   limitsize = FALSE)
+
+# database filter
+excl <- names(sa_asym) %in% c("run", "ID","density","step","eth_lib_loc","val_con_loc","eth_lib_min","val_con_min")
+dataset_sa <- sa_asym[!excl] %>% filter(eth_con_loc   == 20,eth_con_min == 20, val_lib_min == 20)  %>% 
+ filter(circle_orange == 50) %>%
+  group_by(val_lib_loc,fraction_blue,circle_blue, circle_orange) %>% summarise_all(c("mean"= mean,"sd"= sd))
+
+xlab_t <- "ß value liberal local"
+
+# graph
+
+data_exp <- dataset_sa %>% gather(key= subgroup, value = Expo, et_sq_bl_mean, vl_sq_bl_mean, et_cl_bl_mean, vl_cl_bl_mean, et_sq_or_mean, vl_sq_or_mean, et_cl_or_mean, vl_cl_or_mean) %>% mutate(
+  `segregation` = fct_relevel(fct_collapse(subgroup,"ethnics" = c("et_sq_bl_mean","et_cl_bl_mean","et_sq_or_mean","et_cl_or_mean"), "values" = c("vl_sq_bl_mean","vl_cl_bl_mean","vl_sq_or_mean","vl_cl_or_mean")),"ethnics"),
+ `orientation` = fct_relevel(fct_collapse(subgroup, "conservative" = c("et_sq_bl_mean","vl_sq_bl_mean","et_sq_or_mean","vl_sq_or_mean"), "liberal" = c("et_cl_bl_mean","vl_cl_bl_mean","et_cl_or_mean","vl_cl_or_mean")),"conservative" ),
+ `ethnia` = fct_relevel(fct_collapse(subgroup, "local" = c("et_sq_bl_mean","vl_sq_bl_mean","et_cl_bl_mean","vl_cl_bl_mean"),"minority" = c("et_sq_or_mean","vl_sq_or_mean","et_cl_or_mean","vl_cl_or_mean")), "local"))
+
+exp_val_lib_loc <- ggplot(data = data_exp, aes(x = val_lib_loc, y = Expo, linetype = `segregation` , fill = `ethnia`,  shape = `orientation`)) + geom_line(aes(color = `ethnia`))  +  geom_point(color = "black", size = 4) +
+ scale_x_discrete(limits=c(seq(0,20 ,by = 1)))  + scale_y_continuous(limits=c(0,1), breaks=seq(0,1,by=0.10)) +
+  #    facet_wrap(~ circle_orange, labeller = labeller(circle_orange = circle_orange.labs)) +
+    geom_vline(xintercept = 20, color = "red") +
+
+  scale_linetype_manual(values=c("solid","dashed"), labels = c("ethnic","value"), guide = guide_legend(title = "Segregation", order = 1)) +
+  scale_fill_manual(values = c("blue","darkorange")) + 
+  scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
+  scale_shape_manual(values = c(22,21), guide = guide_legend(title="Value" ,override.aes = list(size = 3), order = 3)) +
+  guides(fill = FALSE) +
+  xlab(xlab_t) + ylab("Exposure") + 
+  theme_bw() +  theme( axis.title.x = (element_text(size = 15)), axis.title.y = (element_text(size = 15)), axis.text.x =  (element_text(size = 12)),axis.text.y =  (element_text(size = 15)), legend.title = element_text(size = 13) ,legend.text = element_text(size = 13),plot.title=element_text(hjust = 0.5)) + theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
+
+# ggsave("images/val_lib_loc50.jpg",plot = fig_expo,
+#   device = NULL,path = NULL, 
+#   scale = 1,
+#   width = 8,
+#   height = 6,
+#   units = c("in", "cm", "mm"),
+#   dpi = 300,
+#   limitsize = FALSE)
+
+# database filter
+excl <- names(sa_asym) %in% c("run", "ID","density","step","eth_lib_loc","val_con_loc","eth_lib_min","val_con_min")
+dataset_sa <- sa_asym[!excl] %>% filter(eth_con_loc   == 20, val_lib_loc  == 20, val_lib_min == 20)  %>% 
+ filter(circle_orange == 50) %>%
+  group_by(eth_con_min,fraction_blue,circle_blue, circle_orange) %>% summarise_all(c("mean"= mean,"sd"= sd))
+
+###
+
+xlab_t <- "ß ethnic conservative minority"
+
+# graph
+
+data_exp <- dataset_sa %>% gather(key= subgroup, value = Expo, et_sq_bl_mean, vl_sq_bl_mean, et_cl_bl_mean, vl_cl_bl_mean, et_sq_or_mean, vl_sq_or_mean, et_cl_or_mean, vl_cl_or_mean) %>% mutate(
+  `segregation` = fct_relevel(fct_collapse(subgroup,"ethnics" = c("et_sq_bl_mean","et_cl_bl_mean","et_sq_or_mean","et_cl_or_mean"), "values" = c("vl_sq_bl_mean","vl_cl_bl_mean","vl_sq_or_mean","vl_cl_or_mean")),"ethnics"),
+ `orientation` = fct_relevel(fct_collapse(subgroup, "conservative" = c("et_sq_bl_mean","vl_sq_bl_mean","et_sq_or_mean","vl_sq_or_mean"), "liberal" = c("et_cl_bl_mean","vl_cl_bl_mean","et_cl_or_mean","vl_cl_or_mean")),"conservative" ),
+ `ethnia` = fct_relevel(fct_collapse(subgroup, "local" = c("et_sq_bl_mean","vl_sq_bl_mean","et_cl_bl_mean","vl_cl_bl_mean"),"minority" = c("et_sq_or_mean","vl_sq_or_mean","et_cl_or_mean","vl_cl_or_mean")), "local"))
+
+exp_eth_con_min <-  ggplot(data = data_exp, aes(x = eth_con_min, y = Expo, linetype = `segregation` , fill = `ethnia`,  shape = `orientation`)) + geom_line(aes(color = `ethnia`))  +  geom_point(color = "black", size = 4) +
+ scale_x_discrete(limits=c(seq(0,20 ,by = 1)))  + scale_y_continuous(limits=c(0,1), breaks=seq(0,1,by=0.10)) +
+  #    facet_wrap(~ circle_orange, labeller = labeller(circle_orange = circle_orange.labs)) +
+    geom_vline(xintercept = 20, color = "red") +
+
+  scale_linetype_manual(values=c("solid","dashed"), labels = c("ethnic","value"), guide = guide_legend(title = "Segregation", order = 1)) +
+  scale_fill_manual(values = c("blue","darkorange")) + 
+  scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
+  scale_shape_manual(values = c(22,21), guide = guide_legend(title="Value" ,override.aes = list(size = 3), order = 3)) +
+  guides(fill = FALSE) +
+  xlab(xlab_t) + ylab("Exposure") + 
+  theme_bw() +  theme( axis.title.x = (element_text(size = 15)), axis.title.y = (element_text(size = 15)), axis.text.x =  (element_text(size = 12)),axis.text.y =  (element_text(size = 15)), legend.title = element_text(size = 13) ,legend.text = element_text(size = 13),plot.title=element_text(hjust = 0.5)) + theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
+
+# database filter
+excl <- names(sa_asym) %in% c("run", "ID","density","step","eth_lib_loc","val_con_loc","eth_lib_min","val_con_min")
+dataset_sa <- sa_asym[!excl] %>% filter(eth_con_loc   == 20, val_lib_loc  == 20, eth_con_min  == 20)  %>% 
+ filter(circle_orange == 50) %>%
+  group_by(val_lib_min,fraction_blue,circle_blue, circle_orange) %>% summarise_all(c("mean"= mean,"sd"= sd))
+
+###
+xlab_t <- "ß value liberal minority"
+
+# graph
+
+data_exp <- dataset_sa %>% gather(key= subgroup, value = Expo, et_sq_bl_mean, vl_sq_bl_mean, et_cl_bl_mean, vl_cl_bl_mean, et_sq_or_mean, vl_sq_or_mean, et_cl_or_mean, vl_cl_or_mean) %>% mutate(
+  `segregation` = fct_relevel(fct_collapse(subgroup,"ethnics" = c("et_sq_bl_mean","et_cl_bl_mean","et_sq_or_mean","et_cl_or_mean"), "values" = c("vl_sq_bl_mean","vl_cl_bl_mean","vl_sq_or_mean","vl_cl_or_mean")),"ethnics"),
+ `orientation` = fct_relevel(fct_collapse(subgroup, "conservative" = c("et_sq_bl_mean","vl_sq_bl_mean","et_sq_or_mean","vl_sq_or_mean"), "liberal" = c("et_cl_bl_mean","vl_cl_bl_mean","et_cl_or_mean","vl_cl_or_mean")),"conservative" ),
+ `ethnia` = fct_relevel(fct_collapse(subgroup, "local" = c("et_sq_bl_mean","vl_sq_bl_mean","et_cl_bl_mean","vl_cl_bl_mean"),"minority" = c("et_sq_or_mean","vl_sq_or_mean","et_cl_or_mean","vl_cl_or_mean")), "local"))
+
+exp_val_lib_min <- ggplot(data = data_exp, aes(x = val_lib_min, y = Expo, linetype = `segregation` , fill = `ethnia`,  shape = `orientation`)) + geom_line(aes(color = `ethnia`))  +  geom_point(color = "black", size = 4) +
+ scale_x_discrete(limits=c(seq(0,20 ,by = 1)))  + scale_y_continuous(limits=c(0,1), breaks=seq(0,1,by=0.10)) +
+  #    facet_wrap(~ circle_orange, labeller = labeller(circle_orange = circle_orange.labs)) +
+    geom_vline(xintercept = 20, color = "red") +
+
+  scale_linetype_manual(values=c("solid","dashed"), labels = c("ethnic","value"), guide = guide_legend(title = "Segregation", order = 1)) +
+  scale_fill_manual(values = c("blue","darkorange")) + 
+  scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
+  scale_shape_manual(values = c(22,21), guide = guide_legend(title="Value" ,override.aes = list(size = 3), order = 3)) +
+  guides(fill = FALSE) +
+  xlab(xlab_t) + ylab("Exposure") + 
+  theme_bw() +  theme( axis.title.x = (element_text(size = 15)), axis.title.y = (element_text(size = 15)), axis.text.x =  (element_text(size = 12)),axis.text.y =  (element_text(size = 15)), legend.title = element_text(size = 13) ,legend.text = element_text(size = 13),plot.title=element_text(hjust = 0.5)) + theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
+
+ggpubr::ggarrange(exp_eth_con_loc,exp_val_lib_loc,exp_eth_con_min,exp_val_lib_min, nrow = 2, ncol = 2, common.legend = TRUE, legend = "right")
+
+ggsave("images/exp_sa_asym_bt.jpg",plot = last_plot(),
+  device = NULL,path = NULL,
+  scale = 1,
+  width = 11,
+  height = 8,
+  units = c("in", "cm", "mm"),
+  dpi = 300,
+  limitsize = FALSE)
+
+```
+
+```{r sa_vllblc,  fig.cap="Sensitivity proximity value liberal locals, distribution liberals", echo=FALSE}
+
+# database filter
+excl <- names(sa_asym) %in% c("run", "ID","density","step","eth_lib_loc","val_con_loc","eth_lib_min","val_con_min")
+dataset_sa <- sa_asym[!excl] %>% filter(eth_con_loc  == 20,eth_con_min   == 20,val_lib_min == 20)  %>% 
+group_by(val_lib_loc ,fraction_blue,circle_blue, circle_orange) %>% summarise_all(c("mean"= mean,"sd"= sd))
+
+plotname <- "images/vllblc.jpg"
+xlab_t <- "ß value liberal local"
+
+xvalues <- c(dataset_sa$de_sq_bl_mean,dataset_sa$de_cl_bl_mean,dataset_sa$de_sq_or_mean,dataset_sa$de_cl_or_mean,
+       dataset_sa$dv_sq_bl_mean,dataset_sa$dv_cl_bl_mean,dataset_sa$dv_sq_or_mean,dataset_sa$dv_cl_or_mean)
+
+ expo_pic <-   ggplot(data = dataset_sa) + 
+  geom_point(aes(x = dataset_sa$de_sq_bl_mean, y = dataset_sa$et_sq_bl_mean),color = "black", fill = "blue", shape = 22, size = 5) +
+  geom_point(aes(x = dataset_sa$de_cl_bl_mean, y = dataset_sa$et_cl_bl_mean),color = "black",fill = "blue", shape = 21, size = 5) +
+  geom_point(aes(x = dataset_sa$de_sq_or_mean, y = dataset_sa$et_sq_or_mean),color = "black", fill = "orange", shape = 22, size = 5) +
+  geom_point(aes(x = dataset_sa$de_cl_or_mean, y = dataset_sa$et_cl_or_mean),color = "black", fill = "orange", shape = 21, size = 5) +
+
+  geom_point(aes(x = dataset_sa$dv_sq_bl_mean, y = dataset_sa$vl_sq_bl_mean),color = "black", fill = "blue", shape = 8, size = 5.1) + 
+   geom_point(aes(x = dataset_sa$dv_sq_bl_mean, y = dataset_sa$vl_sq_bl_mean),color = "black", fill = "blue", shape = 22, size = 5) +
+
+   geom_point(aes(x = dataset_sa$dv_cl_bl_mean, y = dataset_sa$vl_cl_bl_mean),color = "black",fill = "blue", shape = 8, size = 5.1) + 
+  geom_point(aes(x = dataset_sa$dv_cl_bl_mean, y = dataset_sa$vl_cl_bl_mean),color = "black",fill = "blue", shape = 21, size = 5) +
+
+    geom_point(aes(x = dataset_sa$dv_sq_or_mean, y = dataset_sa$vl_sq_or_mean),color = "black", fill = "orange", shape = 8, size = 5.1) +
+  geom_point(aes(x = dataset_sa$dv_sq_or_mean, y = dataset_sa$vl_sq_or_mean),color = "black", fill = "orange", shape = 22, size = 5) +
+
+  geom_point(aes(x = dataset_sa$dv_cl_or_mean, y = dataset_sa$vl_cl_or_mean),color = "black", fill = "orange", shape = 8, size = 5.1) +
+geom_point(aes(x = dataset_sa$dv_cl_or_mean, y = dataset_sa$vl_cl_or_mean),color = "black", fill = "orange", shape = 21, size = 5) +
+
+ scale_x_continuous(limits = c(min(xvalues),max(xvalues)), breaks = seq(0,max(xvalues), by = 0.5)) + 
+  scale_y_continuous(breaks= seq(0,1,by=0.1)) + 
+  geom_vline(xintercept = 1, color = "red") +
+  xlab("Spatial proximity") + ylab("Exposure") +
+  theme_bw() + theme( 
+    axis.title.x = (element_text(size = 13)), axis.title.y = (element_text(size = 15)),
+    axis.text.x =  (element_text(size = 12)), axis.text.y =  (element_text(size = 15)), 
+    legend.title = element_text(size = 13),legend.position = "bottom", legend.text = element_text(size = 13),
+    plot.title=element_text(hjust = 0.5), plot.caption = element_text(hjust= 0.5, size = 11), plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
+
+data_prox <- dataset_sa  %>% gather(key= subgroup, value = Prox, de_sq_bl_mean, dv_sq_bl_mean, de_cl_bl_mean, dv_cl_bl_mean, de_sq_or_mean, dv_sq_or_mean, de_cl_or_mean, dv_cl_or_mean) %>% mutate(
+  `segregation` = fct_relevel(fct_collapse(subgroup,"ethnics" = c("de_sq_bl_mean","de_cl_bl_mean","de_sq_or_mean","de_cl_or_mean"), "values" = c("dv_sq_bl_mean","dv_cl_bl_mean","dv_sq_or_mean","dv_cl_or_mean")),"ethnics"),
+ `orientation` = fct_relevel(fct_collapse(subgroup, "conservative" = c("de_sq_bl_mean","dv_sq_bl_mean","de_sq_or_mean","dv_sq_or_mean"), "liberal" = c("de_cl_bl_mean","dv_cl_bl_mean","de_cl_or_mean","dv_cl_or_mean")),"conservative" ),
+ `ethnia` = fct_relevel(fct_collapse(subgroup, "local" = c("de_sq_bl_mean","dv_sq_bl_mean","de_cl_bl_mean","dv_cl_bl_mean"),"minority" = c("de_sq_or_mean","dv_sq_or_mean","de_cl_or_mean","dv_cl_or_mean")), "local"))
+
+prox_pic <- ggplot(data = data_prox, aes(x = val_lib_loc, y = Prox, linetype = `segregation` , fill = `ethnia`,  shape = `orientation`)) + geom_line(aes(color = `ethnia`))  +  geom_point(color = "black", size = 4) +
+ scale_x_discrete(limits=c(seq(0,20 ,by = 1))) + scale_y_continuous(limits=c(min(data_prox$Prox),max(data_prox$Prox)), breaks=seq(0,max(data_prox$Prox),by=0.50)) +
+ facet_wrap(~ circle_orange, dir = "v", labeller = labeller(circle_orange = circle_orange.labs)) +
+    geom_vline(xintercept = 20, color = "red") +  geom_hline(yintercept = 1, color = "red") +
+  scale_linetype_manual(values=c("solid","dashed"), labels = c("ethnic","value"), guide = guide_legend(title = "Segregation", order = 1)) +
+  scale_fill_manual(values = c("blue","darkorange")) + 
+   scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
+  scale_shape_manual(values = c(22,21), guide = guide_legend(title="Value" ,override.aes = list(size = 3), order = 3)) +
+  guides(fill = FALSE) +
+  xlab(xlab_t) + ylab("Spatial Proximity") + 
+  theme_bw() +  theme( 
+    axis.title.x = (element_text(size = 13)), axis.title.y = (element_text(size = 15)),
+    axis.text.x =  (element_text(size = 12)), axis.text.y =  (element_text(size = 15)), 
+    strip.text = element_text(size=13),
+    legend.title = element_text(size = 13),legend.position = "bottom", legend.text = element_text(size = 14),
+    plot.title=element_text(hjust = 0.5), plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
+
+#, plot.caption = element_text(hjust= 0.5, size = 11)
+ggpubr::ggarrange(prox_pic, expo_pic, common.legend = TRUE, legend = "bottom", widths = c(1.3,1))
+
+ggsave(plotname,plot = last_plot(),
+  device = NULL,path = NULL,
+  scale = 1,
+  width = 12,
+  height = 9,
+  units = c("in", "cm", "mm"),
+  dpi = 300,
+  limitsize = FALSE)
+
+```
+
+```{r sa_vllblc_table,  fig.cap="TABLE Sensitivity proximity value liberal locals, distribution liberals", echo=FALSE}
+
+# database filter
+
+excl <- names(sa_asym) %in% c("run", "ID","density","step","eth_lib_loc","val_con_loc","eth_lib_min","val_con_min")
+dataset_sa <- sa_asym[!excl] %>% filter(eth_con_loc  == 20,eth_con_min   == 20,val_lib_min == 20)  %>% 
+group_by(val_lib_loc ,fraction_blue,circle_blue, circle_orange) %>% summarise_all(c("mean"= mean,"sd"= sd))
+
+df_vllblc50 <- dataset_sa %>%  filter(circle_orange == 50)
+tablerb_prox50 <- xtable(df_vllblc50[,c("val_lib_loc","de_sq_bl_mean","de_sq_bl_sd","de_cl_bl_mean","de_cl_bl_sd","de_sq_or_mean","de_sq_or_sd","de_cl_or_mean","de_cl_or_sd","dv_sq_bl_mean","dv_sq_bl_sd","dv_cl_bl_mean","dv_cl_bl_sd","dv_sq_or_mean","dv_sq_or_sd","dv_cl_or_mean","dv_cl_or_sd")], digits = 3)
+align(tablerb_prox50) <- "c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|"
+addtorow <- list()
+addtorow$pos <- list(0, 0,0,0,0)
+addtorow$command <-  c("\\multicolumn{17}{|c|}{Ethnic Asymmetry, $50 \\%$ Liberal Migrants: Spatial Proximity}  \\\\\\hline\n",
+   "Preference &  \\multicolumn{8}{|c|}{Ethnic Proximity} & \\multicolumn{8}{|c|}{Value Proximity}   \\\\\\hline\n",
+  "& \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  & \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  \\\\\n",
+"$\\beta$ value & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
+& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
+& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal}\\\\\n",
+"liberal local & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD\\\\\n")
+print(tablerb_prox50,type = "latex", file = "latex/vllblc50.tex"  , include.rownames=FALSE, add.to.row = addtorow, include.colnames = FALSE, latex.environments = "center")
+
+df_vllblc20 <- dataset_sa %>%  filter(circle_orange == 20)
+tablerb_prox20 <- xtable(df_vllblc20[,c("val_lib_loc","de_sq_bl_mean","de_sq_bl_sd","de_cl_bl_mean","de_cl_bl_sd","de_sq_or_mean","de_sq_or_sd","de_cl_or_mean","de_cl_or_sd","dv_sq_bl_mean","dv_sq_bl_sd","dv_cl_bl_mean","dv_cl_bl_sd","dv_sq_or_mean","dv_sq_or_sd","dv_cl_or_mean","dv_cl_or_sd")], digits = 3)
+align(tablerb_prox20) <- "c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|"
+addtorow <- list()
+addtorow$pos <- list(0, 0,0,0,0)
+addtorow$command <- c("\\multicolumn{17}{|c|}{Ethnic Asymmetry, $20 \\%$ Liberal Migrants: Spatial Proximity}  \\\\\\hline\n",
+   "Preference &  \\multicolumn{8}{|c|}{Ethnic Proximity} & \\multicolumn{8}{|c|}{Value Proximity}   \\\\\\hline\n",
+  "& \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  & \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  \\\\\n",
+"$\\beta$ value & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
+& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
+& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal}\\\\\n",
+"liberal local & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD\\\\\n")
+print(tablerb_prox20,type = "latex", file = "latex/vllblc20.tex" , include.rownames=FALSE, add.to.row = addtorow, include.colnames = FALSE, latex.environments = "center")
+
+df_vllblc80 <- dataset_sa %>%  filter(circle_orange == 80)
+tablerb_prox80 <- xtable(df_vllblc80[,c("val_lib_loc","de_sq_bl_mean","de_sq_bl_sd","de_cl_bl_mean","de_cl_bl_sd","de_sq_or_mean","de_sq_or_sd","de_cl_or_mean","de_cl_or_sd","dv_sq_bl_mean","dv_sq_bl_sd","dv_cl_bl_mean","dv_cl_bl_sd","dv_sq_or_mean","dv_sq_or_sd","dv_cl_or_mean","dv_cl_or_sd")], digits = 3)
+align(tablerb_prox80) <- "c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|"
+addtorow <- list()
+addtorow$pos <- list(0, 0,0,0,0)
+addtorow$command <- c("\\multicolumn{17}{|c|}{Ethnic Asymmetry, $80 \\%$ Liberal Migrants: Spatial Proximity}  \\\\\\hline\n",
+   "Preference &  \\multicolumn{8}{|c|}{Ethnic Proximity} & \\multicolumn{8}{|c|}{Value Proximity}   \\\\\\hline\n",
+  "& \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  & \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  \\\\\n",
+"$\\beta$ value & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
+& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
+& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal}\\\\\n",
+"liberal local & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD\\\\\n")
+print(tablerb_prox80,type = "latex", file = "latex/vllblc80.tex" , include.rownames=FALSE, add.to.row = addtorow, include.colnames = FALSE, latex.environments = "center")
+
+```
+
+```{r sa_vllbmn,  fig.cap="Sensitivity proximity value liberal minority, distribution liberals", echo=FALSE}
+
+# database filter
+excl <- names(sa_asym) %in% c("run", "ID","density","step","eth_lib_loc","val_con_loc","eth_lib_min","val_con_min")
+dataset_sa <- sa_asym[!excl] %>% filter(eth_con_loc  == 20,val_lib_loc == 20,eth_con_min  == 20)  %>% 
+group_by(val_lib_min ,fraction_blue,circle_blue, circle_orange) %>% summarise_all(c("mean"= mean,"sd"= sd))
+
+plotname <- "images/vllbmn.jpg"
+xlab_t <- "ß value liberal minority"
+
+xvalues <- c(dataset_sa$de_sq_bl_mean,dataset_sa$de_cl_bl_mean,dataset_sa$de_sq_or_mean,dataset_sa$de_cl_or_mean,
+       dataset_sa$dv_sq_bl_mean,dataset_sa$dv_cl_bl_mean,dataset_sa$dv_sq_or_mean,dataset_sa$dv_cl_or_mean)
+
+ expo_pic <-   ggplot(data = dataset_sa) + 
+  geom_point(aes(x = dataset_sa$de_sq_bl_mean, y = dataset_sa$et_sq_bl_mean),color = "black", fill = "blue", shape = 22, size = 5) +
+  geom_point(aes(x = dataset_sa$de_cl_bl_mean, y = dataset_sa$et_cl_bl_mean),color = "black",fill = "blue", shape = 21, size = 5) +
+  geom_point(aes(x = dataset_sa$de_sq_or_mean, y = dataset_sa$et_sq_or_mean),color = "black", fill = "orange", shape = 22, size = 5) +
+  geom_point(aes(x = dataset_sa$de_cl_or_mean, y = dataset_sa$et_cl_or_mean),color = "black", fill = "orange", shape = 21, size = 5) +
+
+  geom_point(aes(x = dataset_sa$dv_sq_bl_mean, y = dataset_sa$vl_sq_bl_mean),color = "black", fill = "blue", shape = 8, size = 5.1) + 
+   geom_point(aes(x = dataset_sa$dv_sq_bl_mean, y = dataset_sa$vl_sq_bl_mean),color = "black", fill = "blue", shape = 22, size = 5) +
+
+   geom_point(aes(x = dataset_sa$dv_cl_bl_mean, y = dataset_sa$vl_cl_bl_mean),color = "black",fill = "blue", shape = 8, size = 5.1) + 
+  geom_point(aes(x = dataset_sa$dv_cl_bl_mean, y = dataset_sa$vl_cl_bl_mean),color = "black",fill = "blue", shape = 21, size = 5) +
+
+    geom_point(aes(x = dataset_sa$dv_sq_or_mean, y = dataset_sa$vl_sq_or_mean),color = "black", fill = "orange", shape = 8, size = 5.1) +
+  geom_point(aes(x = dataset_sa$dv_sq_or_mean, y = dataset_sa$vl_sq_or_mean),color = "black", fill = "orange", shape = 22, size = 5) +
+
+  geom_point(aes(x = dataset_sa$dv_cl_or_mean, y = dataset_sa$vl_cl_or_mean),color = "black", fill = "orange", shape = 8, size = 5.1) +
+geom_point(aes(x = dataset_sa$dv_cl_or_mean, y = dataset_sa$vl_cl_or_mean),color = "black", fill = "orange", shape = 21, size = 5) +
+
+ scale_x_continuous(limits = c(min(xvalues),max(xvalues)), breaks = seq(0,max(xvalues), by = 0.5)) + 
+  scale_y_continuous(breaks= seq(0,1,by=0.1)) + 
+  geom_vline(xintercept = 1, color = "red") +
+  xlab("Spatial proximity") + ylab("Exposure") +
+  theme_bw() + theme( 
+    axis.title.x = (element_text(size = 13)), axis.title.y = (element_text(size = 15)),
+    axis.text.x =  (element_text(size = 12)), axis.text.y =  (element_text(size = 15)), 
+    legend.title = element_text(size = 13),legend.position = "bottom", legend.text = element_text(size = 13),
+    plot.title=element_text(hjust = 0.5), plot.caption = element_text(hjust= 0.5, size = 11), plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
+
+data_prox <- dataset_sa  %>% gather(key= subgroup, value = Prox, de_sq_bl_mean, dv_sq_bl_mean, de_cl_bl_mean, dv_cl_bl_mean, de_sq_or_mean, dv_sq_or_mean, de_cl_or_mean, dv_cl_or_mean) %>% mutate(
+  `segregation` = fct_relevel(fct_collapse(subgroup,"ethnics" = c("de_sq_bl_mean","de_cl_bl_mean","de_sq_or_mean","de_cl_or_mean"), "values" = c("dv_sq_bl_mean","dv_cl_bl_mean","dv_sq_or_mean","dv_cl_or_mean")),"ethnics"),
+ `orientation` = fct_relevel(fct_collapse(subgroup, "conservative" = c("de_sq_bl_mean","dv_sq_bl_mean","de_sq_or_mean","dv_sq_or_mean"), "liberal" = c("de_cl_bl_mean","dv_cl_bl_mean","de_cl_or_mean","dv_cl_or_mean")),"conservative" ),
+ `ethnia` = fct_relevel(fct_collapse(subgroup, "local" = c("de_sq_bl_mean","dv_sq_bl_mean","de_cl_bl_mean","dv_cl_bl_mean"),"minority" = c("de_sq_or_mean","dv_sq_or_mean","de_cl_or_mean","dv_cl_or_mean")), "local"))
+
+prox_pic <- ggplot(data = data_prox, aes(x = val_lib_min, y = Prox, linetype = `segregation` , fill = `ethnia`,  shape = `orientation`)) + geom_line(aes(color = `ethnia`))  +  geom_point(color = "black", size = 4) +
+ scale_x_discrete(limits=c(seq(0,20 ,by = 1))) + scale_y_continuous(limits=c(min(data_prox$Prox),max(data_prox$Prox)), breaks=seq(0,max(data_prox$Prox),by=0.50)) +
+ facet_wrap(~ circle_orange, dir = "v", labeller = labeller(circle_orange = circle_orange.labs)) +
+    geom_vline(xintercept = 20, color = "red") +  geom_hline(yintercept = 1, color = "red") +
+  scale_linetype_manual(values=c("solid","dashed"), labels = c("ethnic","value"), guide = guide_legend(title = "Segregation", order = 1)) +
+  scale_fill_manual(values = c("blue","darkorange")) + 
+   scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
+  scale_shape_manual(values = c(22,21), guide = guide_legend(title="Value" ,override.aes = list(size = 3), order = 3)) +
+  guides(fill = FALSE) +
+  xlab(xlab_t) + ylab("Spatial Proximity") + 
+  theme_bw() +  theme( 
+    axis.title.x = (element_text(size = 13)), axis.title.y = (element_text(size = 15)),
+    axis.text.x =  (element_text(size = 12)), axis.text.y =  (element_text(size = 15)), 
+    strip.text = element_text(size=13),
+    legend.title = element_text(size = 13),legend.position = "bottom", legend.text = element_text(size = 14),
+    plot.title=element_text(hjust = 0.5), plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
+
+#, plot.caption = element_text(hjust= 0.5, size = 11)
+ggpubr::ggarrange(prox_pic, expo_pic, common.legend = TRUE, legend = "bottom", widths = c(1.3,1))
+
+ggsave(plotname,plot = last_plot(),
+  device = NULL,path = NULL,
+  scale = 1,
+  width = 12,
+  height = 9,
+  units = c("in", "cm", "mm"),
+  dpi = 300,
+  limitsize = FALSE)
+
+```
+
+```{r sa_vllbmn_table,  fig.cap="TABLE Sensitivity proximity value liberal minority, distribution liberals", echo=FALSE}
+
+# database filter
+
+excl <- names(sa_asym) %in% c("run", "ID","density","step","eth_lib_loc","val_con_loc","eth_lib_min","val_con_min")
+dataset_sa <- sa_asym[!excl] %>% filter(eth_con_loc  == 20,eth_con_min   == 20,val_lib_loc == 20)  %>% 
+group_by(val_lib_min ,fraction_blue,circle_blue, circle_orange) %>% summarise_all(c("mean"= mean,"sd"= sd))
+
+df_vllbmn50 <- dataset_sa %>%  filter(circle_orange == 50)
+tablerb_mn50 <- xtable(df_vllbmn50[,c("val_lib_min","de_sq_bl_mean","de_sq_bl_sd","de_cl_bl_mean","de_cl_bl_sd","de_sq_or_mean","de_sq_or_sd","de_cl_or_mean","de_cl_or_sd","dv_sq_bl_mean","dv_sq_bl_sd","dv_cl_bl_mean","dv_cl_bl_sd","dv_sq_or_mean","dv_sq_or_sd","dv_cl_or_mean","dv_cl_or_sd")], digits = 3)
+align(tablerb_mn50) <- "c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|"
+addtorow <- list()
+addtorow$pos <- list(0, 0,0,0,0)
+addtorow$command <-  c("\\multicolumn{17}{|c|}{Ethnic Asymmetry, $50 \\%$ Liberal Migrants: Spatial Proximity}  \\\\\\hline\n",
+   "Preference &  \\multicolumn{8}{|c|}{Ethnic Proximity} & \\multicolumn{8}{|c|}{Value Proximity}   \\\\\\hline\n",
+  "& \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  & \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  \\\\\n",
+"$\\beta$ value & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
+& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
+& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal}\\\\\n",
+"liberal minority & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD\\\\\n")
+print(tablerb_mn50,type = "latex", file = "latex/vllbmn50.tex"  , include.rownames=FALSE, add.to.row = addtorow, include.colnames = FALSE, latex.environments = "center")
+
+df_vllbmn20 <- dataset_sa %>%  filter(circle_orange == 20)
+tablerb_mn20 <- xtable(df_vllbmn20[,c("val_lib_min","de_sq_bl_mean","de_sq_bl_sd","de_cl_bl_mean","de_cl_bl_sd","de_sq_or_mean","de_sq_or_sd","de_cl_or_mean","de_cl_or_sd","dv_sq_bl_mean","dv_sq_bl_sd","dv_cl_bl_mean","dv_cl_bl_sd","dv_sq_or_mean","dv_sq_or_sd","dv_cl_or_mean","dv_cl_or_sd")], digits = 3)
+align(tablerb_mn20) <- "c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|"
+addtorow <- list()
+addtorow$pos <- list(0, 0,0,0,0)
+addtorow$command <- c("\\multicolumn{17}{|c|}{Ethnic Asymmetry, $20 \\%$ Liberal Migrants: Spatial Proximity}  \\\\\\hline\n",
+   "Preference &  \\multicolumn{8}{|c|}{Ethnic Proximity} & \\multicolumn{8}{|c|}{Value Proximity}   \\\\\\hline\n",
+  "& \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  & \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  \\\\\n",
+"$\\beta$ value & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
+& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
+& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal}\\\\\n",
+"liberal minority & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD\\\\\n")
+print(tablerb_mn20,type = "latex", file = "latex/vllbmn20.tex" , include.rownames=FALSE, add.to.row = addtorow, include.colnames = FALSE, latex.environments = "center")
+
+df_vllbmn80 <- dataset_sa %>%  filter(circle_orange == 80)
+tablerb_mn80 <- xtable(df_vllbmn80[,c("val_lib_min","de_sq_bl_mean","de_sq_bl_sd","de_cl_bl_mean","de_cl_bl_sd","de_sq_or_mean","de_sq_or_sd","de_cl_or_mean","de_cl_or_sd","dv_sq_bl_mean","dv_sq_bl_sd","dv_cl_bl_mean","dv_cl_bl_sd","dv_sq_or_mean","dv_sq_or_sd","dv_cl_or_mean","dv_cl_or_sd")], digits = 3)
+align(tablerb_mn80) <- "c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|"
+addtorow <- list()
+addtorow$pos <- list(0, 0,0,0,0)
+addtorow$command <- c("\\multicolumn{17}{|c|}{Ethnic Asymmetry, $80 \\%$ Liberal Migrants: Spatial Proximity}  \\\\\\hline\n",
+   "Preference &  \\multicolumn{8}{|c|}{Ethnic Proximity} & \\multicolumn{8}{|c|}{Value Proximity}   \\\\\\hline\n",
+  "& \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  & \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  \\\\\n",
+"$\\beta$ value & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
+& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
+& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal}\\\\\n",
+"liberal minority & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD\\\\\n")
+print(tablerb_mn80,type = "latex", file = "latex/vllbmn80.tex" , include.rownames=FALSE, add.to.row = addtorow, include.colnames = FALSE, latex.environments = "center")
+
+```
+
+```{r sa_etcnlc,  fig.cap="Sensitivity proximity ethnic conservative local, distribution liberals", echo=FALSE}
+
+# database filter
+excl <- names(sa_asym) %in% c("run", "ID","density","step","eth_lib_loc","val_con_loc","eth_lib_min","val_con_min")
+dataset_sa <- sa_asym[!excl] %>% filter(val_lib_loc   == 20,eth_con_min   == 20, val_lib_min == 20)  %>% 
+group_by(eth_con_loc ,fraction_blue,circle_blue, circle_orange) %>% summarise_all(c("mean"= mean,"sd"= sd))
+
+plotname <- "images/etcnlc.jpg"
+xlab_t <- "ß ethnic conservative local"
+
+xvalues <- c(dataset_sa$de_sq_bl_mean,dataset_sa$de_cl_bl_mean,dataset_sa$de_sq_or_mean,dataset_sa$de_cl_or_mean,
+       dataset_sa$dv_sq_bl_mean,dataset_sa$dv_cl_bl_mean,dataset_sa$dv_sq_or_mean,dataset_sa$dv_cl_or_mean)
+
+ expo_pic <-   ggplot(data = dataset_sa) + 
+  geom_point(aes(x = dataset_sa$de_sq_bl_mean, y = dataset_sa$et_sq_bl_mean),color = "black", fill = "blue", shape = 22, size = 5) +
+  geom_point(aes(x = dataset_sa$de_cl_bl_mean, y = dataset_sa$et_cl_bl_mean),color = "black",fill = "blue", shape = 21, size = 5) +
+  geom_point(aes(x = dataset_sa$de_sq_or_mean, y = dataset_sa$et_sq_or_mean),color = "black", fill = "orange", shape = 22, size = 5) +
+  geom_point(aes(x = dataset_sa$de_cl_or_mean, y = dataset_sa$et_cl_or_mean),color = "black", fill = "orange", shape = 21, size = 5) +
+
+  geom_point(aes(x = dataset_sa$dv_sq_bl_mean, y = dataset_sa$vl_sq_bl_mean),color = "black", fill = "blue", shape = 8, size = 5.1) + 
+   geom_point(aes(x = dataset_sa$dv_sq_bl_mean, y = dataset_sa$vl_sq_bl_mean),color = "black", fill = "blue", shape = 22, size = 5) +
+
+   geom_point(aes(x = dataset_sa$dv_cl_bl_mean, y = dataset_sa$vl_cl_bl_mean),color = "black",fill = "blue", shape = 8, size = 5.1) + 
+  geom_point(aes(x = dataset_sa$dv_cl_bl_mean, y = dataset_sa$vl_cl_bl_mean),color = "black",fill = "blue", shape = 21, size = 5) +
+
+    geom_point(aes(x = dataset_sa$dv_sq_or_mean, y = dataset_sa$vl_sq_or_mean),color = "black", fill = "orange", shape = 8, size = 5.1) +
+  geom_point(aes(x = dataset_sa$dv_sq_or_mean, y = dataset_sa$vl_sq_or_mean),color = "black", fill = "orange", shape = 22, size = 5) +
+
+  geom_point(aes(x = dataset_sa$dv_cl_or_mean, y = dataset_sa$vl_cl_or_mean),color = "black", fill = "orange", shape = 8, size = 5.1) +
+geom_point(aes(x = dataset_sa$dv_cl_or_mean, y = dataset_sa$vl_cl_or_mean),color = "black", fill = "orange", shape = 21, size = 5) +
+
+ scale_x_continuous(limits = c(min(xvalues),max(xvalues)), breaks = seq(0,max(xvalues), by = 0.5)) + 
+  scale_y_continuous(breaks= seq(0,1,by=0.1)) + 
+  geom_vline(xintercept = 1, color = "red") +
+  xlab("Spatial proximity") + ylab("Exposure") +
+  theme_bw() + theme( 
+    axis.title.x = (element_text(size = 13)), axis.title.y = (element_text(size = 15)),
+    axis.text.x =  (element_text(size = 12)), axis.text.y =  (element_text(size = 15)), 
+    legend.title = element_text(size = 13),legend.position = "bottom", legend.text = element_text(size = 13),
+    plot.title=element_text(hjust = 0.5), plot.caption = element_text(hjust= 0.5, size = 11), plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
+
+data_prox <- dataset_sa  %>% gather(key= subgroup, value = Prox, de_sq_bl_mean, dv_sq_bl_mean, de_cl_bl_mean, dv_cl_bl_mean, de_sq_or_mean, dv_sq_or_mean, de_cl_or_mean, dv_cl_or_mean) %>% mutate(
+  `segregation` = fct_relevel(fct_collapse(subgroup,"ethnics" = c("de_sq_bl_mean","de_cl_bl_mean","de_sq_or_mean","de_cl_or_mean"), "values" = c("dv_sq_bl_mean","dv_cl_bl_mean","dv_sq_or_mean","dv_cl_or_mean")),"ethnics"),
+ `orientation` = fct_relevel(fct_collapse(subgroup, "conservative" = c("de_sq_bl_mean","dv_sq_bl_mean","de_sq_or_mean","dv_sq_or_mean"), "liberal" = c("de_cl_bl_mean","dv_cl_bl_mean","de_cl_or_mean","dv_cl_or_mean")),"conservative" ),
+ `ethnia` = fct_relevel(fct_collapse(subgroup, "local" = c("de_sq_bl_mean","dv_sq_bl_mean","de_cl_bl_mean","dv_cl_bl_mean"),"minority" = c("de_sq_or_mean","dv_sq_or_mean","de_cl_or_mean","dv_cl_or_mean")), "local"))
+
+prox_pic <- ggplot(data = data_prox, aes(x = eth_con_loc, y = Prox, linetype = `segregation` , fill = `ethnia`,  shape = `orientation`)) + geom_line(aes(color = `ethnia`))  +  geom_point(color = "black", size = 4) +
+ scale_x_discrete(limits=c(seq(0,20 ,by = 1))) + scale_y_continuous(limits=c(min(data_prox$Prox),max(data_prox$Prox)), breaks=seq(0,max(data_prox$Prox),by=0.50)) +
+ facet_wrap(~ circle_orange, dir = "v", labeller = labeller(circle_orange = circle_orange.labs)) +
+    geom_vline(xintercept = 20, color = "red") +  geom_hline(yintercept = 1, color = "red") +
+  scale_linetype_manual(values=c("solid","dashed"), labels = c("ethnic","value"), guide = guide_legend(title = "Segregation", order = 1)) +
+  scale_fill_manual(values = c("blue","darkorange")) + 
+   scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
+  scale_shape_manual(values = c(22,21), guide = guide_legend(title="Value" ,override.aes = list(size = 3), order = 3)) +
+  guides(fill = FALSE) +
+  xlab(xlab_t) + ylab("Spatial Proximity") + 
+  theme_bw() +  theme( 
+    axis.title.x = (element_text(size = 13)), axis.title.y = (element_text(size = 15)),
+    axis.text.x =  (element_text(size = 12)), axis.text.y =  (element_text(size = 15)), 
+    strip.text = element_text(size=13),
+    legend.title = element_text(size = 13),legend.position = "bottom", legend.text = element_text(size = 14),
+    plot.title=element_text(hjust = 0.5), plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
+
+#, plot.caption = element_text(hjust= 0.5, size = 11)
+ggpubr::ggarrange(prox_pic, expo_pic, common.legend = TRUE, legend = "bottom", widths = c(1.3,1))
+
+ggsave(plotname,plot = last_plot(),
+  device = NULL,path = NULL,
+  scale = 1,
+  width = 12,
+  height = 9,
+  units = c("in", "cm", "mm"),
+  dpi = 300,
+  limitsize = FALSE)
+```
+
+```{r sa_etcnlc_table,  fig.cap="TABLE Sensitivity proximity ethnic conservative local, distribution liberals", echo=FALSE}
+
+# database filter
+
+excl <- names(sa_asym) %in% c("run", "ID","density","step","eth_lib_loc","val_con_loc","eth_lib_min","val_con_min")
+dataset_sa <- sa_asym[!excl] %>% filter(val_lib_min == 20,  val_lib_loc == 20, eth_con_min == 20)  %>% 
+group_by(eth_con_loc ,fraction_blue,circle_blue, circle_orange) %>% summarise_all(c("mean"= mean,"sd"= sd))
+
+df_etcnlc50 <- dataset_sa %>%  filter(circle_orange == 50)
+etcnlc50 <- xtable(df_etcnlc50[,c("eth_con_loc","de_sq_bl_mean","de_sq_bl_sd","de_cl_bl_mean","de_cl_bl_sd","de_sq_or_mean","de_sq_or_sd","de_cl_or_mean","de_cl_or_sd","dv_sq_bl_mean","dv_sq_bl_sd","dv_cl_bl_mean","dv_cl_bl_sd","dv_sq_or_mean","dv_sq_or_sd","dv_cl_or_mean","dv_cl_or_sd")], digits = 3)
+align(etcnlc50) <- "c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|"
+addtorow <- list()
+addtorow$pos <- list(0, 0,0,0,0)
+addtorow$command <-  c("\\multicolumn{17}{|c|}{Ethnic Asymmetry, $50 \\%$ Liberal Migrants: Spatial Proximity}  \\\\\\hline\n",
+   "Preference &  \\multicolumn{8}{|c|}{Ethnic Proximity} & \\multicolumn{8}{|c|}{Value Proximity}   \\\\\\hline\n",
+  "& \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  & \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  \\\\\n",
+"$\\beta$ ethnic & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
+& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
+& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal}\\\\\n",
+"conservative local & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD\\\\\n")
+print(etcnlc50,type = "latex", file = "latex/etcnlc50.tex"  , include.rownames=FALSE, add.to.row = addtorow, include.colnames = FALSE, latex.environments = "center")
+
+df_etcnlc20 <- dataset_sa %>%  filter(circle_orange == 20)
+etcnlc20 <- xtable(df_etcnlc20[,c("eth_con_loc","de_sq_bl_mean","de_sq_bl_sd","de_cl_bl_mean","de_cl_bl_sd","de_sq_or_mean","de_sq_or_sd","de_cl_or_mean","de_cl_or_sd","dv_sq_bl_mean","dv_sq_bl_sd","dv_cl_bl_mean","dv_cl_bl_sd","dv_sq_or_mean","dv_sq_or_sd","dv_cl_or_mean","dv_cl_or_sd")], digits = 3)
+align(etcnlc20) <- "c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|"
+addtorow <- list()
+addtorow$pos <- list(0, 0,0,0,0)
+addtorow$command <- c("\\multicolumn{17}{|c|}{Ethnic Asymmetry, $20 \\%$ Liberal Migrants: Spatial Proximity}  \\\\\\hline\n",
+   "Preference &  \\multicolumn{8}{|c|}{Ethnic Proximity} & \\multicolumn{8}{|c|}{Value Proximity}   \\\\\\hline\n",
+  "& \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  & \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  \\\\\n",
+"$\\beta$ ethnic & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
+& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
+& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal}\\\\\n",
+"conservative local & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD\\\\\n")
+print(etcnlc20,type = "latex", file = "latex/etcnlc20.tex" , include.rownames=FALSE, add.to.row = addtorow, include.colnames = FALSE, latex.environments = "center")
+
+df_etcnlc80 <- dataset_sa %>%  filter(circle_orange == 80)
+etcnlc80 <- xtable(df_etcnlc80[,c("eth_con_loc","de_sq_bl_mean","de_sq_bl_sd","de_cl_bl_mean","de_cl_bl_sd","de_sq_or_mean","de_sq_or_sd","de_cl_or_mean","de_cl_or_sd","dv_sq_bl_mean","dv_sq_bl_sd","dv_cl_bl_mean","dv_cl_bl_sd","dv_sq_or_mean","dv_sq_or_sd","dv_cl_or_mean","dv_cl_or_sd")], digits = 3)
+align(etcnlc80) <- "c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|"
+addtorow <- list()
+addtorow$pos <- list(0, 0,0,0,0)
+addtorow$command <- c("\\multicolumn{17}{|c|}{Ethnic Asymmetry, $80 \\%$ Liberal Migrants: Spatial Proximity}  \\\\\\hline\n",
+   "Preference &  \\multicolumn{8}{|c|}{Ethnic Proximity} & \\multicolumn{8}{|c|}{Value Proximity}   \\\\\\hline\n",
+  "& \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  & \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  \\\\\n",
+"$\\beta$ ethnic & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
+& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
+& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal}\\\\\n",
+"conservative local & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD\\\\\n")
+print(etcnlc80,type = "latex", file = "latex/etcnlc80.tex" , include.rownames=FALSE, add.to.row = addtorow, include.colnames = FALSE, latex.environments = "center")
+
+```
+
+```{r sa_etcnmn,  fig.cap="Sensitivity proximity ethnic conservative minority, distribution liberals", echo=FALSE}
+
+# database filter
+excl <- names(sa_asym) %in% c("run", "ID","density","step","eth_lib_loc","val_con_loc","eth_lib_min","val_con_min")
+dataset_sa <- sa_asym[!excl] %>% filter(eth_con_loc  == 20,val_lib_loc == 20,val_lib_min == 20)  %>% 
+group_by(eth_con_min ,fraction_blue,circle_blue, circle_orange) %>% summarise_all(c("mean"= mean,"sd"= sd))
+
+plotname <- "images/etcnmn.jpg"
+xlab_t <- "ß ethnic conservative minority"
+
+xvalues <- c(dataset_sa$de_sq_bl_mean,dataset_sa$de_cl_bl_mean,dataset_sa$de_sq_or_mean,dataset_sa$de_cl_or_mean,
+       dataset_sa$dv_sq_bl_mean,dataset_sa$dv_cl_bl_mean,dataset_sa$dv_sq_or_mean,dataset_sa$dv_cl_or_mean)
+
+ expo_pic <-   ggplot(data = dataset_sa) + 
+  geom_point(aes(x = dataset_sa$de_sq_bl_mean, y = dataset_sa$et_sq_bl_mean),color = "black", fill = "blue", shape = 22, size = 5) +
+  geom_point(aes(x = dataset_sa$de_cl_bl_mean, y = dataset_sa$et_cl_bl_mean),color = "black",fill = "blue", shape = 21, size = 5) +
+  geom_point(aes(x = dataset_sa$de_sq_or_mean, y = dataset_sa$et_sq_or_mean),color = "black", fill = "orange", shape = 22, size = 5) +
+  geom_point(aes(x = dataset_sa$de_cl_or_mean, y = dataset_sa$et_cl_or_mean),color = "black", fill = "orange", shape = 21, size = 5) +
+
+  geom_point(aes(x = dataset_sa$dv_sq_bl_mean, y = dataset_sa$vl_sq_bl_mean),color = "black", fill = "blue", shape = 8, size = 5.1) + 
+   geom_point(aes(x = dataset_sa$dv_sq_bl_mean, y = dataset_sa$vl_sq_bl_mean),color = "black", fill = "blue", shape = 22, size = 5) +
+
+   geom_point(aes(x = dataset_sa$dv_cl_bl_mean, y = dataset_sa$vl_cl_bl_mean),color = "black",fill = "blue", shape = 8, size = 5.1) + 
+  geom_point(aes(x = dataset_sa$dv_cl_bl_mean, y = dataset_sa$vl_cl_bl_mean),color = "black",fill = "blue", shape = 21, size = 5) +
+
+    geom_point(aes(x = dataset_sa$dv_sq_or_mean, y = dataset_sa$vl_sq_or_mean),color = "black", fill = "orange", shape = 8, size = 5.1) +
+  geom_point(aes(x = dataset_sa$dv_sq_or_mean, y = dataset_sa$vl_sq_or_mean),color = "black", fill = "orange", shape = 22, size = 5) +
+
+  geom_point(aes(x = dataset_sa$dv_cl_or_mean, y = dataset_sa$vl_cl_or_mean),color = "black", fill = "orange", shape = 8, size = 5.1) +
+geom_point(aes(x = dataset_sa$dv_cl_or_mean, y = dataset_sa$vl_cl_or_mean),color = "black", fill = "orange", shape = 21, size = 5) +
+
+ scale_x_continuous(limits = c(min(xvalues),max(xvalues)), breaks = seq(0,max(xvalues), by = 0.5)) + 
+  scale_y_continuous(breaks= seq(0,1,by=0.1)) + 
+  geom_vline(xintercept = 1, color = "red") +
+  xlab("Spatial proximity") + ylab("Exposure") +
+  theme_bw() + theme( 
+    axis.title.x = (element_text(size = 13)), axis.title.y = (element_text(size = 15)),
+    axis.text.x =  (element_text(size = 12)), axis.text.y =  (element_text(size = 15)), 
+    legend.title = element_text(size = 13),legend.position = "bottom", legend.text = element_text(size = 13),
+    plot.title=element_text(hjust = 0.5), plot.caption = element_text(hjust= 0.5, size = 11), plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
+
+data_prox <- dataset_sa  %>% gather(key= subgroup, value = Prox, de_sq_bl_mean, dv_sq_bl_mean, de_cl_bl_mean, dv_cl_bl_mean, de_sq_or_mean, dv_sq_or_mean, de_cl_or_mean, dv_cl_or_mean) %>% mutate(
+  `segregation` = fct_relevel(fct_collapse(subgroup,"ethnics" = c("de_sq_bl_mean","de_cl_bl_mean","de_sq_or_mean","de_cl_or_mean"), "values" = c("dv_sq_bl_mean","dv_cl_bl_mean","dv_sq_or_mean","dv_cl_or_mean")),"ethnics"),
+ `orientation` = fct_relevel(fct_collapse(subgroup, "conservative" = c("de_sq_bl_mean","dv_sq_bl_mean","de_sq_or_mean","dv_sq_or_mean"), "liberal" = c("de_cl_bl_mean","dv_cl_bl_mean","de_cl_or_mean","dv_cl_or_mean")),"conservative" ),
+ `ethnia` = fct_relevel(fct_collapse(subgroup, "local" = c("de_sq_bl_mean","dv_sq_bl_mean","de_cl_bl_mean","dv_cl_bl_mean"),"minority" = c("de_sq_or_mean","dv_sq_or_mean","de_cl_or_mean","dv_cl_or_mean")), "local"))
+
+prox_pic <- ggplot(data = data_prox, aes(x = eth_con_min, y = Prox, linetype = `segregation` , fill = `ethnia`,  shape = `orientation`)) + geom_line(aes(color = `ethnia`))  +  geom_point(color = "black", size = 4) +
+ scale_x_discrete(limits=c(seq(0,20 ,by = 1))) + scale_y_continuous(limits=c(min(data_prox$Prox),max(data_prox$Prox)), breaks=seq(0,max(data_prox$Prox),by=0.50)) +
+ facet_wrap(~ circle_orange, dir = "v", labeller = labeller(circle_orange = circle_orange.labs)) +
+    geom_vline(xintercept = 20, color = "red") +  geom_hline(yintercept = 1, color = "red") +
+  scale_linetype_manual(values=c("solid","dashed"), labels = c("ethnic","value"), guide = guide_legend(title = "Segregation", order = 1)) +
+  scale_fill_manual(values = c("blue","darkorange")) + 
+   scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
+  scale_shape_manual(values = c(22,21), guide = guide_legend(title="Value" ,override.aes = list(size = 3), order = 3)) +
+  guides(fill = FALSE) +
+  xlab(xlab_t) + ylab("Spatial Proximity") + 
+  theme_bw() +  theme( 
+    axis.title.x = (element_text(size = 13)), axis.title.y = (element_text(size = 15)),
+    axis.text.x =  (element_text(size = 12)), axis.text.y =  (element_text(size = 15)), 
+    strip.text = element_text(size=13),
+    legend.title = element_text(size = 13),legend.position = "bottom", legend.text = element_text(size = 14),
+    plot.title=element_text(hjust = 0.5), plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
+
+#, plot.caption = element_text(hjust= 0.5, size = 11)
+ggpubr::ggarrange(prox_pic, expo_pic, common.legend = TRUE, legend = "bottom", widths = c(1.3,1))
+
+ggsave(plotname,plot = last_plot(),
+  device = NULL,path = NULL,
+  scale = 1,
+  width = 12,
+  height = 9,
+  units = c("in", "cm", "mm"),
+  dpi = 300,
+  limitsize = FALSE)
+```
+
+```{r sa_etcnmn_table,  fig.cap="TABLE Sensitivity proximity ethnic conservative minority, distribution liberals", echo=FALSE}
+
+# database filter
+
+excl <- names(sa_asym) %in% c("run", "ID","density","step","eth_lib_loc","val_con_loc","eth_lib_min","val_con_min")
+dataset_sa <- sa_asym[!excl] %>% filter(val_lib_min == 20,  val_lib_loc == 20, eth_con_loc == 20)  %>% 
+group_by(eth_con_min ,fraction_blue,circle_blue, circle_orange) %>% summarise_all(c("mean"= mean,"sd"= sd))
+
+df_etcnmn50 <- dataset_sa %>%  filter(circle_orange == 50)
+etcnmn50 <- xtable(df_etcnmn50[,c("eth_con_min","de_sq_bl_mean","de_sq_bl_sd","de_cl_bl_mean","de_cl_bl_sd","de_sq_or_mean","de_sq_or_sd","de_cl_or_mean","de_cl_or_sd","dv_sq_bl_mean","dv_sq_bl_sd","dv_cl_bl_mean","dv_cl_bl_sd","dv_sq_or_mean","dv_sq_or_sd","dv_cl_or_mean","dv_cl_or_sd")], digits = 3)
+align(etcnmn50) <- "c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|"
+addtorow <- list()
+addtorow$pos <- list(0, 0,0,0,0)
+addtorow$command <-  c("\\multicolumn{17}{|c|}{Ethnic Asymmetry, $50 \\%$ Liberal Migrants: Spatial Proximity}  \\\\\\hline\n",
+   "Preference &  \\multicolumn{8}{|c|}{Ethnic Proximity} & \\multicolumn{8}{|c|}{Value Proximity}   \\\\\\hline\n",
+  "& \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  & \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  \\\\\n",
+"$\\beta$ ethnic & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
+& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
+& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal}\\\\\n",
+"conservative minority & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD\\\\\n")
+print(etcnmn50,type = "latex", file = "latex/etcnmn50.tex"  , include.rownames=FALSE, add.to.row = addtorow, include.colnames = FALSE, latex.environments = "center")
+
+df_etcnmn20 <- dataset_sa %>%  filter(circle_orange == 20)
+etcnmn20 <- xtable(df_etcnmn20[,c("eth_con_min","de_sq_bl_mean","de_sq_bl_sd","de_cl_bl_mean","de_cl_bl_sd","de_sq_or_mean","de_sq_or_sd","de_cl_or_mean","de_cl_or_sd","dv_sq_bl_mean","dv_sq_bl_sd","dv_cl_bl_mean","dv_cl_bl_sd","dv_sq_or_mean","dv_sq_or_sd","dv_cl_or_mean","dv_cl_or_sd")], digits = 3)
+align(etcnmn20) <- "c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|"
+addtorow <- list()
+addtorow$pos <- list(0, 0,0,0,0)
+addtorow$command <- c("\\multicolumn{17}{|c|}{Ethnic Asymmetry, $20 \\%$ Liberal Migrants: Spatial Proximity}  \\\\\\hline\n",
+   "Preference &  \\multicolumn{8}{|c|}{Ethnic Proximity} & \\multicolumn{8}{|c|}{Value Proximity}   \\\\\\hline\n",
+  "& \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  & \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  \\\\\n",
+"$\\beta$ ethnic & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
+& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
+& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal}\\\\\n",
+"conservative minority & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD\\\\\n")
+print(etcnmn20,type = "latex", file = "latex/etcnmn20.tex" , include.rownames=FALSE, add.to.row = addtorow, include.colnames = FALSE, latex.environments = "center")
+
+df_etcnmn80 <- dataset_sa %>%  filter(circle_orange == 80)
+etcnmn80 <- xtable(df_etcnmn80[,c("eth_con_min","de_sq_bl_mean","de_sq_bl_sd","de_cl_bl_mean","de_cl_bl_sd","de_sq_or_mean","de_sq_or_sd","de_cl_or_mean","de_cl_or_sd","dv_sq_bl_mean","dv_sq_bl_sd","dv_cl_bl_mean","dv_cl_bl_sd","dv_sq_or_mean","dv_sq_or_sd","dv_cl_or_mean","dv_cl_or_sd")], digits = 3)
+align(etcnmn80) <- "c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|"
+addtorow <- list()
+addtorow$pos <- list(0, 0,0,0,0)
+addtorow$command <- c("\\multicolumn{17}{|c|}{Ethnic Asymmetry, $80 \\%$ Liberal Migrants: Spatial Proximity}  \\\\\\hline\n",
+   "Preference &  \\multicolumn{8}{|c|}{Ethnic Proximity} & \\multicolumn{8}{|c|}{Value Proximity}   \\\\\\hline\n",
+  "& \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  & \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  \\\\\n",
+"$\\beta$ ethnic & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
+& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
+& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal}\\\\\n",
+"conservative minority & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD\\\\\n")
+print(etcnmn80,type = "latex", file = "latex/etcnmn80.tex" , include.rownames=FALSE, add.to.row = addtorow, include.colnames = FALSE, latex.environments = "center")
+
+# test_all <- rbind(etcnmn20,etcnmn50,etcnmn80)
+# print(test_all, type = "latex", file = "latex/test_all.tex",include.rownames=FALSE, add.to.row = addtorow, include.colnames = FALSE, latex.environments = "center")
+
+```
+
+```{r et_lib_loc,  fig.cap="Sensitivity proximity ETHNIC liberal majority", echo=FALSE}
+
+# database filter
+excl <- names(etlib) %in% c("run", "ID","density","step","eth_con_loc","eth_con_min","val_lib_loc","val_lib_min","val_con_loc","val_con_min")
+etlib_df <- etlib[!excl] %>% filter(eth_lib_min  == 0)  %>% 
+group_by(eth_lib_loc,fraction_blue,circle_blue, circle_orange,eth_lib_min) %>% summarise_all(c("mean"= mean,"sd"= sd))
+
+plotname <- "images/et_libloc.jpg"
+xlab_t <- "ß ethnic liberal local"
+
+xvalues <- c(etlib_df$de_sq_bl_mean,etlib_df$de_cl_bl_mean,etlib_df$de_sq_or_mean,etlib_df$de_cl_or_mean,
+       etlib_df$dv_sq_bl_mean,etlib_df$dv_cl_bl_mean,etlib_df$dv_sq_or_mean,etlib_df$dv_cl_or_mean)
+
+ expo_pic <-   ggplot(data = etlib_df) + 
+  geom_point(aes(x = etlib_df$de_sq_bl_mean, y = etlib_df$et_sq_bl_mean),color = "black", fill = "blue", shape = 22, size = 5) +
+  geom_point(aes(x = etlib_df$de_cl_bl_mean, y = etlib_df$et_cl_bl_mean),color = "black",fill = "blue", shape = 21, size = 5) +
+  geom_point(aes(x = etlib_df$de_sq_or_mean, y = etlib_df$et_sq_or_mean),color = "black", fill = "orange", shape = 22, size = 5) +
+  geom_point(aes(x = etlib_df$de_cl_or_mean, y = etlib_df$et_cl_or_mean),color = "black", fill = "orange", shape = 21, size = 5) +
+
+  geom_point(aes(x = etlib_df$dv_sq_bl_mean, y = etlib_df$vl_sq_bl_mean),color = "black", fill = "blue", shape = 8, size = 5.1) + 
+   geom_point(aes(x = etlib_df$dv_sq_bl_mean, y = etlib_df$vl_sq_bl_mean),color = "black", fill = "blue", shape = 22, size = 5) +
+
+   geom_point(aes(x = etlib_df$dv_cl_bl_mean, y = etlib_df$vl_cl_bl_mean),color = "black",fill = "blue", shape = 8, size = 5.1) + 
+  geom_point(aes(x = etlib_df$dv_cl_bl_mean, y = etlib_df$vl_cl_bl_mean),color = "black",fill = "blue", shape = 21, size = 5) +
+
+    geom_point(aes(x = etlib_df$dv_sq_or_mean, y = etlib_df$vl_sq_or_mean),color = "black", fill = "orange", shape = 8, size = 5.1) +
+  geom_point(aes(x = etlib_df$dv_sq_or_mean, y = etlib_df$vl_sq_or_mean),color = "black", fill = "orange", shape = 22, size = 5) +
+
+  geom_point(aes(x = etlib_df$dv_cl_or_mean, y = etlib_df$vl_cl_or_mean),color = "black", fill = "orange", shape = 8, size = 5.1) +
+geom_point(aes(x = etlib_df$dv_cl_or_mean, y = etlib_df$vl_cl_or_mean),color = "black", fill = "orange", shape = 21, size = 5) +
+
+ scale_x_continuous(limits = c(min(xvalues),max(xvalues)), breaks = seq(0,max(xvalues), by = 0.5)) + 
+  scale_y_continuous(breaks= seq(0,1,by=0.1)) + 
+  geom_vline(xintercept = 1, color = "red") +
+  xlab("Spatial proximity") + ylab("Exposure") +
+  theme_bw() + theme( 
+    axis.title.x = (element_text(size = 13)), axis.title.y = (element_text(size = 15)),
+    axis.text.x =  (element_text(size = 12)), axis.text.y =  (element_text(size = 15)), 
+    legend.title = element_text(size = 13),legend.position = "bottom", legend.text = element_text(size = 13),
+    plot.title=element_text(hjust = 0.5), plot.caption = element_text(hjust= 0.5, size = 11), plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
+
+data_prox <- etlib_df  %>% gather(key= subgroup, value = Prox, de_sq_bl_mean, dv_sq_bl_mean, de_cl_bl_mean, dv_cl_bl_mean, de_sq_or_mean, dv_sq_or_mean, de_cl_or_mean, dv_cl_or_mean) %>% mutate(
+  `segregation` = fct_relevel(fct_collapse(subgroup,"ethnics" = c("de_sq_bl_mean","de_cl_bl_mean","de_sq_or_mean","de_cl_or_mean"), "values" = c("dv_sq_bl_mean","dv_cl_bl_mean","dv_sq_or_mean","dv_cl_or_mean")),"ethnics"),
+ `orientation` = fct_relevel(fct_collapse(subgroup, "conservative" = c("de_sq_bl_mean","dv_sq_bl_mean","de_sq_or_mean","dv_sq_or_mean"), "liberal" = c("de_cl_bl_mean","dv_cl_bl_mean","de_cl_or_mean","dv_cl_or_mean")),"conservative" ),
+ `ethnia` = fct_relevel(fct_collapse(subgroup, "local" = c("de_sq_bl_mean","dv_sq_bl_mean","de_cl_bl_mean","dv_cl_bl_mean"),"minority" = c("de_sq_or_mean","dv_sq_or_mean","de_cl_or_mean","dv_cl_or_mean")), "local"))
+
+prox_pic <- ggplot(data = data_prox, aes(x = eth_lib_loc, y = Prox, linetype = `segregation` , fill = `ethnia`,  shape = `orientation`)) + geom_line(aes(color = `ethnia`))  +  geom_point(color = "black", size = 4) +
+ scale_x_discrete(limits=c(seq(0,20 ,by = 1))) + scale_y_continuous(limits=c(min(data_prox$Prox),max(data_prox$Prox)), breaks=seq(0,max(data_prox$Prox),by=0.50)) +
+ facet_wrap(~ circle_orange, dir = "v", labeller = labeller(circle_orange = circle_orange.labs)) +
+    geom_vline(xintercept = 20, color = "red") +  geom_hline(yintercept = 1, color = "red") +
+  scale_linetype_manual(values=c("solid","dashed"), labels = c("ethnic","value"), guide = guide_legend(title = "Segregation", order = 1)) +
+  scale_fill_manual(values = c("blue","darkorange")) + 
+   scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
+  scale_shape_manual(values = c(22,21), guide = guide_legend(title="Value" ,override.aes = list(size = 3), order = 3)) +
+  guides(fill = FALSE) +
+  xlab(xlab_t) + ylab("Spatial Proximity") + 
+  theme_bw() +  theme( 
+    axis.title.x = (element_text(size = 13)), axis.title.y = (element_text(size = 15)),
+    axis.text.x =  (element_text(size = 12)), axis.text.y =  (element_text(size = 15)), 
+    strip.text = element_text(size=13),
+    legend.title = element_text(size = 13),legend.position = "bottom", legend.text = element_text(size = 14),
+    plot.title=element_text(hjust = 0.5), plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
+
+#, plot.caption = element_text(hjust= 0.5, size = 11)
+ggpubr::ggarrange(prox_pic, expo_pic, common.legend = TRUE, legend = "bottom", widths = c(1.3,1))
+
+ggsave(plotname,plot = last_plot(),
+  device = NULL,path = NULL,
+  scale = 1,
+  width = 12,
+  height = 9,
+  units = c("in", "cm", "mm"),
+  dpi = 300,
+  limitsize = FALSE)
+
+```
+
+```{r et_lib_loc_table,  fig.cap="TABLE Sensitivity proximity ETHNIC liberal majority", echo=FALSE}
+
+# database filter
+
+excl <- names(etlib) %in% c("run", "ID","density","step","eth_con_loc","eth_con_min","val_lib_loc","val_lib_min","val_con_loc","val_con_min")
+etlib_df <- etlib[!excl] %>% filter(eth_lib_min  == 0)  %>% 
+group_by(eth_lib_loc,fraction_blue,circle_blue, circle_orange,eth_lib_min) %>% summarise_all(c("mean"= mean,"sd"= sd))
+
+df_etlib_loc50 <- etlib_df %>%  filter(circle_orange == 50)
+etlib_loc50 <- xtable(df_etlib_loc50[,c("eth_lib_loc","de_sq_bl_mean","de_sq_bl_sd","de_cl_bl_mean","de_cl_bl_sd","de_sq_or_mean","de_sq_or_sd","de_cl_or_mean","de_cl_or_sd","dv_sq_bl_mean","dv_sq_bl_sd","dv_cl_bl_mean","dv_cl_bl_sd","dv_sq_or_mean","dv_sq_or_sd","dv_cl_or_mean","dv_cl_or_sd")], digits = 3)
+align(etlib_loc50) <- "c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|"
+addtorow <- list()
+addtorow$pos <- list(0, 0,0,0,0)
+addtorow$command <-  c("\\multicolumn{17}{|c|}{Ethnic Asymmetry, $50 \\%$ Liberal Migrants: Spatial Proximity}  \\\\\\hline\n",
+   "Preference &  \\multicolumn{8}{|c|}{Ethnic Proximity} & \\multicolumn{8}{|c|}{Value Proximity}   \\\\\\hline\n",
+  "& \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  & \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  \\\\\n",
+"$\\beta$ ethnic & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
+& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
+& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal}\\\\\n",
+"liberal local & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD\\\\\n")
+print(etlib_loc50,type = "latex", file = "latex/etlib_loc50.tex"  , include.rownames=FALSE, add.to.row = addtorow, include.colnames = FALSE, latex.environments = "center")
+
+df_etlib_loc20 <- etlib_df %>%  filter(circle_orange == 20)
+etlib_loc20 <- xtable(df_etlib_loc20[,c("eth_lib_loc","de_sq_bl_mean","de_sq_bl_sd","de_cl_bl_mean","de_cl_bl_sd","de_sq_or_mean","de_sq_or_sd","de_cl_or_mean","de_cl_or_sd","dv_sq_bl_mean","dv_sq_bl_sd","dv_cl_bl_mean","dv_cl_bl_sd","dv_sq_or_mean","dv_sq_or_sd","dv_cl_or_mean","dv_cl_or_sd")], digits = 3)
+align(etlib_loc20) <- "c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|"
+addtorow <- list()
+addtorow$pos <- list(0, 0,0,0,0)
+addtorow$command <- c("\\multicolumn{17}{|c|}{Ethnic Asymmetry, $20 \\%$ Liberal Migrants: Spatial Proximity}  \\\\\\hline\n",
+   "Preference &  \\multicolumn{8}{|c|}{Ethnic Proximity} & \\multicolumn{8}{|c|}{Value Proximity}   \\\\\\hline\n",
+  "& \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  & \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  \\\\\n",
+"$\\beta$ ethnic & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
+& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
+& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal}\\\\\n",
+"liberal local & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD\\\\\n")
+print(etlib_loc20,type = "latex", file = "latex/etlib_loc20.tex" , include.rownames=FALSE, add.to.row = addtorow, include.colnames = FALSE, latex.environments = "center")
+
+df_etlib_loc80 <- etlib_df %>%  filter(circle_orange == 80)
+etlib_loc80 <- xtable(df_etlib_loc80[,c("eth_lib_loc","de_sq_bl_mean","de_sq_bl_sd","de_cl_bl_mean","de_cl_bl_sd","de_sq_or_mean","de_sq_or_sd","de_cl_or_mean","de_cl_or_sd","dv_sq_bl_mean","dv_sq_bl_sd","dv_cl_bl_mean","dv_cl_bl_sd","dv_sq_or_mean","dv_sq_or_sd","dv_cl_or_mean","dv_cl_or_sd")], digits = 3)
+align(etlib_loc80) <- "c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|"
+addtorow <- list()
+addtorow$pos <- list(0, 0,0,0,0)
+addtorow$command <- c("\\multicolumn{17}{|c|}{Ethnic Asymmetry, $80 \\%$ Liberal Migrants: Spatial Proximity}  \\\\\\hline\n",
+   "Preference &  \\multicolumn{8}{|c|}{Ethnic Proximity} & \\multicolumn{8}{|c|}{Value Proximity}   \\\\\\hline\n",
+  "& \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  & \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  \\\\\n",
+"$\\beta$ ethnic & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
+& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
+& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal}\\\\\n",
+"liberal local & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD\\\\\n")
+print(etcnmn80,type = "latex", file = "latex/etlib_loc80.tex" , include.rownames=FALSE, add.to.row = addtorow, include.colnames = FALSE, latex.environments = "center")
+
+```
+
+```{r et_lib_min,  fig.cap="Sensitivity proximity ETHNIC liberal minority", echo=FALSE}
+
+# database filter
+excl <- names(etlib) %in% c("run", "ID","density","step","eth_con_loc","eth_con_min","val_lib_loc","val_lib_min","val_con_loc","val_con_min")
+etlib_df <- etlib[!excl] %>% filter(eth_lib_loc  == 0)  %>% 
+group_by(eth_lib_min,fraction_blue,circle_blue, circle_orange,eth_lib_loc) %>% summarise_all(c("mean"= mean,"sd"= sd))
+
+plotname <- "images/et_libmin.jpg"
+xlab_t <- "ß ethnic liberal minority"
+
+xvalues <- c(etlib_df$de_sq_bl_mean,etlib_df$de_cl_bl_mean,etlib_df$de_sq_or_mean,etlib_df$de_cl_or_mean,
+       etlib_df$dv_sq_bl_mean,etlib_df$dv_cl_bl_mean,etlib_df$dv_sq_or_mean,etlib_df$dv_cl_or_mean)
+
+ expo_pic <-   ggplot(data = etlib_df) + 
+  geom_point(aes(x = etlib_df$de_sq_bl_mean, y = etlib_df$et_sq_bl_mean),color = "black", fill = "blue", shape = 22, size = 5) +
+  geom_point(aes(x = etlib_df$de_cl_bl_mean, y = etlib_df$et_cl_bl_mean),color = "black",fill = "blue", shape = 21, size = 5) +
+  geom_point(aes(x = etlib_df$de_sq_or_mean, y = etlib_df$et_sq_or_mean),color = "black", fill = "orange", shape = 22, size = 5) +
+  geom_point(aes(x = etlib_df$de_cl_or_mean, y = etlib_df$et_cl_or_mean),color = "black", fill = "orange", shape = 21, size = 5) +
+
+  geom_point(aes(x = etlib_df$dv_sq_bl_mean, y = etlib_df$vl_sq_bl_mean),color = "black", fill = "blue", shape = 8, size = 5.1) + 
+   geom_point(aes(x = etlib_df$dv_sq_bl_mean, y = etlib_df$vl_sq_bl_mean),color = "black", fill = "blue", shape = 22, size = 5) +
+
+   geom_point(aes(x = etlib_df$dv_cl_bl_mean, y = etlib_df$vl_cl_bl_mean),color = "black",fill = "blue", shape = 8, size = 5.1) + 
+  geom_point(aes(x = etlib_df$dv_cl_bl_mean, y = etlib_df$vl_cl_bl_mean),color = "black",fill = "blue", shape = 21, size = 5) +
+
+    geom_point(aes(x = etlib_df$dv_sq_or_mean, y = etlib_df$vl_sq_or_mean),color = "black", fill = "orange", shape = 8, size = 5.1) +
+  geom_point(aes(x = etlib_df$dv_sq_or_mean, y = etlib_df$vl_sq_or_mean),color = "black", fill = "orange", shape = 22, size = 5) +
+
+  geom_point(aes(x = etlib_df$dv_cl_or_mean, y = etlib_df$vl_cl_or_mean),color = "black", fill = "orange", shape = 8, size = 5.1) +
+geom_point(aes(x = etlib_df$dv_cl_or_mean, y = etlib_df$vl_cl_or_mean),color = "black", fill = "orange", shape = 21, size = 5) +
+
+ scale_x_continuous(limits = c(min(xvalues),max(xvalues)), breaks = seq(0,max(xvalues), by = 0.5)) + 
+  scale_y_continuous(breaks= seq(0,1,by=0.1)) + 
+  geom_vline(xintercept = 1, color = "red") +
+  xlab("Spatial proximity") + ylab("Exposure") +
+  theme_bw() + theme( 
+    axis.title.x = (element_text(size = 13)), axis.title.y = (element_text(size = 15)),
+    axis.text.x =  (element_text(size = 12)), axis.text.y =  (element_text(size = 15)), 
+    legend.title = element_text(size = 13),legend.position = "bottom", legend.text = element_text(size = 13),
+    plot.title=element_text(hjust = 0.5), plot.caption = element_text(hjust= 0.5, size = 11), plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
+
+data_prox <- etlib_df  %>% gather(key= subgroup, value = Prox, de_sq_bl_mean, dv_sq_bl_mean, de_cl_bl_mean, dv_cl_bl_mean, de_sq_or_mean, dv_sq_or_mean, de_cl_or_mean, dv_cl_or_mean) %>% mutate(
+  `segregation` = fct_relevel(fct_collapse(subgroup,"ethnics" = c("de_sq_bl_mean","de_cl_bl_mean","de_sq_or_mean","de_cl_or_mean"), "values" = c("dv_sq_bl_mean","dv_cl_bl_mean","dv_sq_or_mean","dv_cl_or_mean")),"ethnics"),
+ `orientation` = fct_relevel(fct_collapse(subgroup, "conservative" = c("de_sq_bl_mean","dv_sq_bl_mean","de_sq_or_mean","dv_sq_or_mean"), "liberal" = c("de_cl_bl_mean","dv_cl_bl_mean","de_cl_or_mean","dv_cl_or_mean")),"conservative" ),
+ `ethnia` = fct_relevel(fct_collapse(subgroup, "local" = c("de_sq_bl_mean","dv_sq_bl_mean","de_cl_bl_mean","dv_cl_bl_mean"),"minority" = c("de_sq_or_mean","dv_sq_or_mean","de_cl_or_mean","dv_cl_or_mean")), "local"))
+
+prox_pic <- ggplot(data = data_prox, aes(x = eth_lib_min, y = Prox, linetype = `segregation` , fill = `ethnia`,  shape = `orientation`)) + geom_line(aes(color = `ethnia`))  +  geom_point(color = "black", size = 4) +
+ scale_x_discrete(limits=c(seq(0,20 ,by = 1))) + scale_y_continuous(limits=c(min(data_prox$Prox),max(data_prox$Prox)), breaks=seq(0,max(data_prox$Prox),by=0.50)) +
+ facet_wrap(~ circle_orange, dir = "v", labeller = labeller(circle_orange = circle_orange.labs)) +
+    geom_vline(xintercept = 20, color = "red") +  geom_hline(yintercept = 1, color = "red") +
+  scale_linetype_manual(values=c("solid","dashed"), labels = c("ethnic","value"), guide = guide_legend(title = "Segregation", order = 1)) +
+  scale_fill_manual(values = c("blue","darkorange")) + 
+   scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
+  scale_shape_manual(values = c(22,21), guide = guide_legend(title="Value" ,override.aes = list(size = 3), order = 3)) +
+  guides(fill = FALSE) +
+  xlab(xlab_t) + ylab("Spatial Proximity") + 
+  theme_bw() +  theme( 
+    axis.title.x = (element_text(size = 13)), axis.title.y = (element_text(size = 15)),
+    axis.text.x =  (element_text(size = 12)), axis.text.y =  (element_text(size = 15)), 
+    strip.text = element_text(size=13),
+    legend.title = element_text(size = 13),legend.position = "bottom", legend.text = element_text(size = 14),
+    plot.title=element_text(hjust = 0.5), plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
+
+#, plot.caption = element_text(hjust= 0.5, size = 11)
+ggpubr::ggarrange(prox_pic, expo_pic, common.legend = TRUE, legend = "bottom", widths = c(1.3,1))
+
+ggsave(plotname,plot = last_plot(),
+  device = NULL,path = NULL,
+  scale = 1,
+  width = 12,
+  height = 9,
+  units = c("in", "cm", "mm"),
+  dpi = 300,
+  limitsize = FALSE)
+
+```
+
+```{r et_lib_min_table,  fig.cap="TABLE Sensitivity proximity ETHNIC liberal minority", echo=FALSE}
+
+# database filter
+
+excl <- names(etlib) %in% c("run", "ID","density","step","eth_con_loc","eth_con_min","val_lib_loc","val_lib_min","val_con_loc","val_con_min")
+etlib_df <- etlib[!excl] %>% filter(eth_lib_loc  == 0)  %>% 
+group_by(eth_lib_min,fraction_blue,circle_blue, circle_orange,eth_lib_min) %>% summarise_all(c("mean"= mean,"sd"= sd))
+
+df_etlib_min50 <- etlib_df %>%  filter(circle_orange == 50)
+etlib_min50 <- xtable(df_etlib_min50[,c("eth_lib_min","de_sq_bl_mean","de_sq_bl_sd","de_cl_bl_mean","de_cl_bl_sd","de_sq_or_mean","de_sq_or_sd","de_cl_or_mean","de_cl_or_sd","dv_sq_bl_mean","dv_sq_bl_sd","dv_cl_bl_mean","dv_cl_bl_sd","dv_sq_or_mean","dv_sq_or_sd","dv_cl_or_mean","dv_cl_or_sd")], digits = 3)
+align(etlib_min50) <- "c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|"
+addtorow <- list()
+addtorow$pos <- list(0, 0,0,0,0)
+addtorow$command <-  c("\\multicolumn{17}{|c|}{Ethnic Asymmetry, $50 \\%$ Liberal Migrants: Spatial Proximity}  \\\\\\hline\n",
+   "Preference &  \\multicolumn{8}{|c|}{Ethnic Proximity} & \\multicolumn{8}{|c|}{Value Proximity}   \\\\\\hline\n",
+  "& \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  & \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  \\\\\n",
+"$\\beta$ ethnic & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
+& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
+& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal}\\\\\n",
+"liberal minority & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD\\\\\n")
+print(etlib_loc50,type = "latex", file = "latex/etlib_min50.tex"  , include.rownames=FALSE, add.to.row = addtorow, include.colnames = FALSE, latex.environments = "center")
+
+df_etlib_min20 <- etlib_df %>%  filter(circle_orange == 20)
+etlib_min20 <- xtable(df_etlib_min20[,c("eth_lib_min","de_sq_bl_mean","de_sq_bl_sd","de_cl_bl_mean","de_cl_bl_sd","de_sq_or_mean","de_sq_or_sd","de_cl_or_mean","de_cl_or_sd","dv_sq_bl_mean","dv_sq_bl_sd","dv_cl_bl_mean","dv_cl_bl_sd","dv_sq_or_mean","dv_sq_or_sd","dv_cl_or_mean","dv_cl_or_sd")], digits = 3)
+align(etlib_min20) <- "c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|"
+addtorow <- list()
+addtorow$pos <- list(0, 0,0,0,0)
+addtorow$command <- c("\\multicolumn{17}{|c|}{Ethnic Asymmetry, $20 \\%$ Liberal Migrants: Spatial Proximity}  \\\\\\hline\n",
+   "Preference &  \\multicolumn{8}{|c|}{Ethnic Proximity} & \\multicolumn{8}{|c|}{Value Proximity}   \\\\\\hline\n",
+  "& \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  & \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  \\\\\n",
+"$\\beta$ ethnic & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
+& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
+& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal}\\\\\n",
+"liberal minority & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD\\\\\n")
+print(etlib_loc20,type = "latex", file = "latex/etlib_min20.tex" , include.rownames=FALSE, add.to.row = addtorow, include.colnames = FALSE, latex.environments = "center")
+
+df_etlib_min80 <- etlib_df %>%  filter(circle_orange == 80)
+etlib_min80 <- xtable(df_etlib_min80[,c("eth_lib_min","de_sq_bl_mean","de_sq_bl_sd","de_cl_bl_mean","de_cl_bl_sd","de_sq_or_mean","de_sq_or_sd","de_cl_or_mean","de_cl_or_sd","dv_sq_bl_mean","dv_sq_bl_sd","dv_cl_bl_mean","dv_cl_bl_sd","dv_sq_or_mean","dv_sq_or_sd","dv_cl_or_mean","dv_cl_or_sd")], digits = 3)
+align(etlib_min80) <- "c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|"
+addtorow <- list()
+addtorow$pos <- list(0, 0,0,0,0)
+addtorow$command <- c("\\multicolumn{17}{|c|}{Ethnic Asymmetry, $80 \\%$ Liberal Migrants: Spatial Proximity}  \\\\\\hline\n",
+   "Preference &  \\multicolumn{8}{|c|}{Ethnic Proximity} & \\multicolumn{8}{|c|}{Value Proximity}   \\\\\\hline\n",
+  "& \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  & \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  \\\\\n",
+"$\\beta$ ethnic & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
+& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
+& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal}\\\\\n",
+"liberal minority & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD\\\\\n")
+print(etcnmn80,type = "latex", file = "latex/etlib_min80.tex" , include.rownames=FALSE, add.to.row = addtorow, include.colnames = FALSE, latex.environments = "center")
+
+```
+
+<!--
+
+```{r sa_etcnlc50, fig.width=30, fig.cap="Sensitivity ethnic conservative local, baseline asymmetric conditions", echo=FALSE}
+
+# database filter
+excl <- names(sa_asym) %in% c("run", "ID","density","step","eth_lib_loc","val_con_loc","eth_lib_min","val_con_min")
+dataset_sa <- sa_asym[!excl] %>% filter(val_lib_loc  == 20,eth_con_min == 20, val_lib_min == 20)  %>% 
+ filter(circle_orange == 50) %>%
+  group_by(eth_con_loc,fraction_blue,circle_blue, circle_orange) %>% summarise_all(c("mean"= mean,"sd"= sd))
+
+xlab_t <- "ß ethnic conservative local"
+
+ circle_orange.labs <- c("20% liberal minority", "50% liberal minority", "80% liberal minority")
+names(circle_orange.labs) <- c("20","50","80")
+
+plotname <- "images/etcnlc50.jpg"
+
+# row_exp <- c("\\multicolumn{17}{|c|}{Ethnic asymmetric condition: Exposure, 50% liberal minority}  \\\\\\hline\n",
+#    "Preference &  \\multicolumn{8}{|c|}{Ethnic Exposure} & \\multicolumn{8}{|c|}{Value Exposure}   \\\\\\hline\n",
+#   "& \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  & \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  \\\\\n",
+# "$\\beta$ dom = 20 & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
+# & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
+# & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal}\\\\\n",
+# " & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD\\\\\n")
+# 
+# row_prox <- c("\\multicolumn{17}{|c|}{Ethnic Asymmetric condition: Spatial Proximity, 50% liberal minority}  \\\\\\hline\n",
+#    "Preference &  \\multicolumn{8}{|c|}{Ethnic Proximity} & \\multicolumn{8}{|c|}{Value Proximity}   \\\\\\hline\n",
+#   "& \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  & \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  \\\\\n",
+# "$\\beta$ dom = 20 & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
+# & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
+# & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal}\\\\\n",
+# " & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD\\\\\n")
+#
+
+# tablerb_expname <- "latex/etcnlc50_rb_exp.tex"
+# tablerb_proxname <- "latex/etcnlc50_prox.tex"
+
+# graph
+
+data_exp <- dataset_sa %>% gather(key= subgroup, value = Expo, et_sq_bl_mean, vl_sq_bl_mean, et_cl_bl_mean, vl_cl_bl_mean, et_sq_or_mean, vl_sq_or_mean, et_cl_or_mean, vl_cl_or_mean) %>% mutate(
+  `segregation` = fct_relevel(fct_collapse(subgroup,"ethnics" = c("et_sq_bl_mean","et_cl_bl_mean","et_sq_or_mean","et_cl_or_mean"), "values" = c("vl_sq_bl_mean","vl_cl_bl_mean","vl_sq_or_mean","vl_cl_or_mean")),"ethnics"),
+ `orientation` = fct_relevel(fct_collapse(subgroup, "conservative" = c("et_sq_bl_mean","vl_sq_bl_mean","et_sq_or_mean","vl_sq_or_mean"), "liberal" = c("et_cl_bl_mean","vl_cl_bl_mean","et_cl_or_mean","vl_cl_or_mean")),"conservative" ),
+ `ethnia` = fct_relevel(fct_collapse(subgroup, "local" = c("et_sq_bl_mean","vl_sq_bl_mean","et_cl_bl_mean","vl_cl_bl_mean"),"minority" = c("et_sq_or_mean","vl_sq_or_mean","et_cl_or_mean","vl_cl_or_mean")), "local"))
+
+fig_exp <- ggplot(data = data_exp, aes(x = eth_con_loc, y = Expo, linetype = `segregation` , color = `ethnia`, shape = `orientation`)) + geom_line()  +  geom_point(size = 3) +
+ scale_x_discrete(limits=c(seq(0,20 ,by = 1))) + scale_y_continuous(limits=c(0,1), breaks=seq(0,1,by=0.10)) +
+#  facet_wrap(~ circle_orange, labeller = labeller(circle_orange = circle_orange.labs)) +
+  scale_linetype_manual(values=c("solid","dotted"), labels = c("ethnic","value"), guide = guide_legend(title = "Segregation", order = 1)) +
+  scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
+  scale_shape_manual(values = c("square","circle"), guide = guide_legend(title="Value" ,override.aes = list(size = 3), order = 3)) +
+  xlab("") + ylab("Exposure") + 
+  theme_bw() +  theme( axis.title.x  = element_blank(), axis.title.y = (element_text(size = 15)), axis.text.x  = (element_text(size = 10)) ,axis.text.y =  (element_text(size = 15)), legend.title = element_text(size = 13) ,legend.text = element_text(size = 13), plot.title=element_text(hjust = 0.5)) + theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
+
+# tablerb_exp <- xtable(dataset_sa[,c("dominant","et_sq_bl_mean","et_sq_bl_sd","et_cl_bl_mean","et_cl_bl_sd","et_sq_or_mean","et_sq_or_sd","et_cl_or_mean","et_cl_or_sd","vl_sq_bl_mean","vl_sq_bl_sd","vl_cl_bl_mean","vl_cl_bl_sd","vl_sq_or_mean","vl_sq_or_sd","vl_cl_or_mean","vl_cl_or_sd")], digits = 3)
+# align(tablerb_exp) <- "c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|"
+# 
+# addtorow <- list()
+# addtorow$pos <- list(0, 0,0,0,0)
+# addtorow$command <-  row_exp
+# 
+# print(tablerb_exp,type = "latex", file = tablerb_expname, include.rownames=FALSE, add.to.row = addtorow, include.colnames = FALSE, latex.environments = "center")
+
+## Spatial proximity baseline asymmetric
+
+# graph
+
+data_prox <- dataset_sa %>% gather(key= subgroup, value = Prox, de_sq_bl_mean, dv_sq_bl_mean, de_cl_bl_mean, dv_cl_bl_mean, de_sq_or_mean, dv_sq_or_mean, de_cl_or_mean, dv_cl_or_mean) %>% mutate(
+  `segregation` = fct_relevel(fct_collapse(subgroup,"ethnics" = c("de_sq_bl_mean","de_cl_bl_mean","de_sq_or_mean","de_cl_or_mean"), "values" = c("dv_sq_bl_mean","dv_cl_bl_mean","dv_sq_or_mean","dv_cl_or_mean")),"ethnics"),
+ `orientation` = fct_relevel(fct_collapse(subgroup, "conservative" = c("de_sq_bl_mean","dv_sq_bl_mean","de_sq_or_mean","dv_sq_or_mean"), "liberal" = c("de_cl_bl_mean","dv_cl_bl_mean","de_cl_or_mean","dv_cl_or_mean")),"conservative" ),
+ `ethnia` = fct_relevel(fct_collapse(subgroup, "local" = c("de_sq_bl_mean","dv_sq_bl_mean","de_cl_bl_mean","dv_cl_bl_mean"),"minority" = c("de_sq_or_mean","dv_sq_or_mean","de_cl_or_mean","dv_cl_or_mean")), "local"))
+
+fig_prox <- ggplot(data = data_prox, aes(x = eth_con_loc, y = Prox, linetype = `segregation` , color = `ethnia`, shape = `orientation`)) + geom_line()  +  geom_point(size = 3) +
+ scale_x_discrete(limits=c(seq(0,20 ,by = 1))) + scale_y_continuous(limits=c(min(data_prox$Prox),max(data_prox$Prox)), breaks=seq(0,max(data_prox$Prox),by=0.50)) +
+#☻    facet_wrap(~ circle_orange, labeller = labeller(circle_orange = circle_orange.labs)) +
+  scale_linetype_manual(values=c("solid","dotted"), labels = c("ethnic","value"), guide = guide_legend(title = "Segregation", order = 1)) +
+  scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
+  scale_shape_manual(values = c("square","circle"), guide = guide_legend(title="Value" ,override.aes = list(size = 3), order = 3)) +
+  xlab(xlab_t) + ylab("Spatial Proximity") + 
+  theme_bw() +  theme( axis.title.x = (element_text(size = 15)), axis.title.y = (element_text(size = 15)), axis.text.x =  (element_text(size = 15)),axis.text.y =  (element_text(size = 15)), legend.title = element_text(size = 13) ,legend.text = element_text(size = 13),plot.title=element_text(hjust = 0.5)) + theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
+
+# robustness table
+
+# tablerb_prox <- xtable(dataset_sa[,c("dominant","de_sq_bl_mean","de_sq_bl_sd","de_cl_bl_mean","de_cl_bl_sd","de_sq_or_mean","de_sq_or_sd","de_cl_or_mean","de_cl_or_sd","dv_sq_bl_mean","dv_sq_bl_sd","dv_cl_bl_mean","dv_cl_bl_sd","dv_sq_or_mean","dv_sq_or_sd","dv_cl_or_mean","dv_cl_or_sd")], digits = 3)
+# align(tablerb_prox) <- "c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|"
+# 
+# addtorow <- list()
+# addtorow$pos <- list(0, 0,0,0,0)
+# addtorow$command <-  row_prox
+# print(tablerb_prox,type = "latex", file = tablerb_proxname , include.rownames=FALSE, add.to.row = addtorow, include.colnames = FALSE, latex.environments = "center")
+
+# combined image
+
+ggpubr::ggarrange(fig_exp,fig_prox, nrow = 2, ncol = 1, common.legend = TRUE, legend = "right")
+
+ggsave(plotname,plot = fig_prox,
+  device = NULL,path = NULL, 
+  scale = 1,
+  width = 8,
+  height = 6,
+  units = c("in", "cm", "mm"),
+  dpi = 300,
+  limitsize = FALSE)
+
+```
+
+```{r CODE INDEX FACET  WRAP, fig.width=30, fig.cap="Baseline asymmetric conditions", echo=FALSE}
+
+# database filter
+excl <- names(asym_dom) %in% c("run", "ID","density","step")
+asym_dom_sa <- asym_dom[!excl] %>% group_by(dominant,circle_orange,circle_blue,fraction_blue,secondary) %>% summarise_all(c("mean"= mean,"sd"= sd))
+
+# graph
+# LEAVE! Combined indexes
+data_s <- asym_dom_sa  %>% gather(key= subgroup, value = Segra, de_sq_bl_mean, dv_sq_bl_mean, de_cl_bl_mean, dv_cl_bl_mean, de_sq_or_mean, dv_sq_or_mean, de_cl_or_mean, dv_cl_or_mean,
+       et_sq_bl_mean, vl_sq_bl_mean, et_cl_bl_mean, vl_cl_bl_mean, et_sq_or_mean, vl_sq_or_mean, et_cl_or_mean, vl_cl_or_mean) %>% mutate(
+  `dimensions` = fct_relevel(fct_collapse(subgroup,"ethnic" = c("de_sq_bl_mean","de_cl_bl_mean","de_sq_or_mean","de_cl_or_mean", "et_sq_bl_mean","et_cl_bl_mean","et_sq_or_mean","et_cl_or_mean"), "values" = c("dv_sq_bl_mean","dv_cl_bl_mean","dv_sq_or_mean","dv_cl_or_mean",
+   "vl_sq_bl_mean","vl_cl_bl_mean","vl_sq_or_mean","vl_cl_or_mean")),"ethnic"),
+ `orientation` = fct_relevel(fct_collapse(subgroup, "conservative" = c("de_sq_bl_mean","dv_sq_bl_mean","de_sq_or_mean","dv_sq_or_mean",  "et_sq_bl_mean","vl_sq_bl_mean","et_sq_or_mean","vl_sq_or_mean" ), "liberal" = c("de_cl_bl_mean","dv_cl_bl_mean","de_cl_or_mean","dv_cl_or_mean",
+                         "et_cl_bl_mean", "vl_cl_bl_mean", "et_cl_or_mean","vl_cl_or_mean")),"conservative" ),
+ `ethnia` = fct_relevel(fct_collapse(subgroup, "local" = c("de_sq_bl_mean","dv_sq_bl_mean","de_cl_bl_mean","dv_cl_bl_mean",
+                                    "et_sq_bl_mean","vl_sq_bl_mean","et_cl_bl_mean", "vl_cl_bl_mean" ),"minority" = c("de_sq_or_mean","dv_sq_or_mean","de_cl_or_mean","dv_cl_or_mean","et_sq_or_mean", "vl_sq_or_mean", "et_cl_or_mean", "vl_cl_or_mean")), "local"),
+  `index` = fct_relevel(fct_collapse(subgroup,  "exposure" = c("et_sq_bl_mean","vl_sq_bl_mean","et_cl_bl_mean", "vl_cl_bl_mean","et_sq_or_mean", "vl_sq_or_mean", "et_cl_or_mean", "vl_cl_or_mean" ), "proximity" = c("de_sq_bl_mean","dv_sq_bl_mean","de_cl_bl_mean","dv_cl_bl_mean","de_sq_or_mean","dv_sq_or_mean","de_cl_or_mean","dv_cl_or_mean")),"exposure"))
+
+data_f <- asym_dom_sa %>% gather(key= subgroup, value = Segra, de_sq_bl_mean, dv_sq_bl_mean, de_cl_bl_mean, dv_cl_bl_mean, de_sq_or_mean, dv_sq_or_mean, de_cl_or_mean, dv_cl_or_mean) %>% mutate(
+  `segregation` = fct_relevel(fct_collapse(subgroup,"ethnics" = c("de_sq_bl_mean","de_cl_bl_mean","de_sq_or_mean","de_cl_or_mean"), "values" = c("dv_sq_bl_mean","dv_cl_bl_mean","dv_sq_or_mean","dv_cl_or_mean")),"ethnics"),
+ `orientation` = fct_relevel(fct_collapse(subgroup, "conservative" = c("de_sq_bl_mean","dv_sq_bl_mean","de_sq_or_mean","dv_sq_or_mean"), "liberal" = c("de_cl_bl_mean","dv_cl_bl_mean","de_cl_or_mean","dv_cl_or_mean")),"conservative" ),
+ `ethnia` = fct_relevel(fct_collapse(subgroup, "local" = c("de_sq_bl_mean","dv_sq_bl_mean","de_cl_bl_mean","dv_cl_bl_mean"),"minority" = c("de_sq_or_mean","dv_sq_or_mean","de_cl_or_mean","dv_cl_or_mean")), "local"))
+
+data_e <- asym_dom_sa %>% gather(key= subgroup, value = Segra, et_sq_bl_mean, vl_sq_bl_mean, et_cl_bl_mean, vl_cl_bl_mean, et_sq_or_mean, vl_sq_or_mean, et_cl_or_mean, vl_cl_or_mean) %>% mutate(
+  `segregation` = fct_relevel(fct_collapse(subgroup,"ethnics" = c("et_sq_bl_mean","et_cl_bl_mean","et_sq_or_mean","et_cl_or_mean"), "values" = c("vl_sq_bl_mean","vl_cl_bl_mean","vl_sq_or_mean","vl_cl_or_mean")),"ethnics"),
+ `orientation` = fct_relevel(fct_collapse(subgroup, "conservative" = c("et_sq_bl_mean","vl_sq_bl_mean","et_sq_or_mean","vl_sq_or_mean"), "liberal" = c("et_cl_bl_mean","vl_cl_bl_mean","et_cl_or_mean","vl_cl_or_mean")),"conservative" ),
+ `ethnia` = fct_relevel(fct_collapse(subgroup, "local" = c("et_sq_bl_mean","vl_sq_bl_mean","et_cl_bl_mean","vl_cl_bl_mean"),"minority" = c("et_sq_or_mean","vl_sq_or_mean","et_cl_or_mean","vl_cl_or_mean")), "local"))
+
+ggplot(data = data_f, aes(x = dominant, y = Segra, color = `ethnia` , linetype = `segregation`, shape = `orientation`)) +   geom_point(size = 3) + geom_line() + 
+# scale_color_gradient(low="green", high="red")
+ scale_x_discrete(limits=c(seq(0,20 ,by = 1))) + 
+ scale_y_continuous(breaks=seq(0,max(data_f$Segra),by=0.25)) +
+  scale_linetype_manual(values=c("solid","dashed"), labels = c("ethnic","value"), guide = guide_legend(title = "Dimension", order = 1)) +
+scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
+ scale_shape_manual(values = c("square","circle"), guide = guide_legend(title="Orientation" ,override.aes = list(size = 3), order = 3)) +
+  xlab("ß dominant") + ylab("Index") + 
+# facet_wrap(~ `index`, dir = "v", scales = "free_y") + 
+  geom_blank() +
+  theme_bw() +  theme( axis.title.x = (element_text(size = 15)), axis.title.y = (element_text(size = 15)), axis.text.x =  (element_text(size = 15)),axis.text.y =  (element_text(size = 15)), legend.title = element_text(size = 13) ,legend.text = element_text(size = 13), plot.title=element_text(hjust = 0.5)) + theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
+
+ggsave("images/prox_asym_dom.jpg",plot = last_plot(),
+  device = NULL,path = NULL, 
+  scale = 1,
+  width = 10,
+  height = 4,
+  units = c("in", "cm", "mm"),
+  dpi = 300,
+  limitsize = FALSE)
+
+# robustness table
+
+table_rb <- xtable(asym_dom_sa[,c("dominant","de_sq_bl_mean","de_sq_bl_sd","de_cl_bl_mean","de_cl_bl_sd","de_sq_or_mean","de_sq_or_sd","de_cl_or_mean","de_cl_or_sd","dv_sq_bl_mean","dv_sq_bl_sd","dv_cl_bl_mean","dv_cl_bl_sd","dv_sq_or_mean","dv_sq_or_sd","dv_cl_or_mean","dv_cl_or_sd")], digits = 3)
+align(table_rb) <- "c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|"
+
+addtorow <- list()
+addtorow$pos <- list(0, 0,0,0,0)
+addtorow$command <-  c("\\multicolumn{17}{|c|}{Ethnic Asymmetric condition: Spatial Proximity}  \\\\\\hline\n",
+   "Preference &  \\multicolumn{8}{|c|}{Ethnic Exposure} & \\multicolumn{8}{|c|}{Value Exposure}   \\\\\\hline\n",
+  "& \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  & \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  \\\\\n",
+"$\\beta$ sec = 0 & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
+& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
+& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal}\\\\\n",
+" & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD\\\\\n")
+
+print(table_rb,type = "latex", file = "prox_asym_rb.tex", include.rownames=FALSE, add.to.row = addtorow, include.colnames = FALSE, latex.environments = "center")
+
+A = data.frame(x = rnorm(10),y=rnorm(10))
+B = data.frame(x = rnorm(10),y=rnorm(10))
+ggplot(A,aes(x,y)) +geom_point() +geom_point(data=B,colour='red') + xlim(0, 10)
 

### 2021-03-30 analysis.Rmd
analysis simulation data

@@
 
+# fig.cap in the titles of chunk reports figure number in the text
+# Each chunk reports code for dataset filter, summary: mean and standard deviation, plotting graph, raw material latex, output details. They can vary if image was combined or other tweaks needed
+# Fig. 9 (sensitivity to group-type preference) selects distribution liberals 50% and combines for 4 group-type
+# Outputs create folder "image" for images and "latex" for latex raw tables
+# Name of index (often used in y-lab and in table): exposure for ethnic symmetric, spatial proximity or exposure correct for ethnic asymmetric
+
+# Change work directory in quotes
 setwd("C:/Users/rocpa/OneDrive/Desktop/AF2/exp12_2020/")
 
-# Back work, used to combine datasets from diffent runs. To IGNORE OR DELETE
-
-# etlib_min1 <- read.csv("mj_etlib_min.csv",skip = 6)
-# etlib_min2 <- read.csv("mj_etlib_min2.csv",skip = 6)
-# etlib_min <- rbind(etlib_min1,etlib_min2)
-# names(etlib_min) <- pull(read.csv("legend_sec_etlib.csv"))
-# etlib_min <- cbind(ID = "etlib_min",etlib_min)
-
-basic <- read.csv("df_basic.csv",sep =",")
-value_basic <- read.csv("df_valuebasic.csv",sep = ",")
-asym_dom <- read.csv("df_asym_dom.csv",sep = ",")
-dislib <- read.csv("df_dislib.csv", sep = ",")
-sa_asym <- read.csv("df_sa_asym.csv",sep =",")
-etlib <- read.csv("df_etlib.csv",sep =",")
+# Datasets
+
+basic <- read.csv("df_basic.csv",sep =",")                 # basic condition
+value_basic <- read.csv("df_valuebasic.csv",sep = ",")     # value basic
+asym_dom <- read.csv("df_asym_dom.csv",sep = ",")          # asymmetric conditions, baseline figure dominant preference
+dislib <- read.csv("df_dislib.csv", sep = ",")             # sensitivity to distribution of liberals
+sa_asym <- read.csv("df_sa_asym.csv",sep =",")             # sensitivity analysis, ethnic asymmetry
+etlib <- read.csv("df_etlib.csv",sep =",")                 # ethnic preference liberals, ethnic asymmetry
+asym_all <- read.csv("df_asym_all.csv",sep =",")           # baseline ethnic  asymmetry
+
+# for labels
 
@@
 
-```{r heatmap, include=TRUE, fig.cap="Comparison dominant vs secondary", echo=FALSE}
-
+# Symmetric Conditions
+
+```{r basefigure, fig.width=30, fig.cap="Fig. 3 Baseline symmetric. Same parameter for ethnic and value homophily for all agents", echo=FALSE}
+
+# database filter AND summary mean and standard deviation
+excl <- names(basic) %in% c("run", "ID","density","step")
+basic_sa <- basic[!excl] %>% filter(dominant == secondary) %>% group_by(dominant,secondary,circle_orange,circle_blue,fraction_blue) %>% summarise_all(c("mean"= mean,"sd"= sd))
+
+# graph
+
+data_f <- basic_sa %>% gather(key= subgroup, value = Segra, et_sq_bl_mean, vl_sq_bl_mean, et_cl_bl_mean, vl_cl_bl_mean, et_sq_or_mean, vl_sq_or_mean, et_cl_or_mean, vl_cl_or_mean) %>% mutate(
+  `segregation` = fct_relevel(fct_collapse(subgroup,"ethnics" = c("et_sq_bl_mean","et_cl_bl_mean","et_sq_or_mean","et_cl_or_mean"), "values" = c("vl_sq_bl_mean","vl_cl_bl_mean","vl_sq_or_mean","vl_cl_or_mean")),"ethnics"),
+ `orientation` = fct_relevel(fct_collapse(subgroup, "conservative" = c("et_sq_bl_mean","vl_sq_bl_mean","et_sq_or_mean","vl_sq_or_mean"), "liberal" = c("et_cl_bl_mean","vl_cl_bl_mean","et_cl_or_mean","vl_cl_or_mean")),"conservative" ),
+ `ethnia` = fct_relevel(fct_collapse(subgroup, "local" = c("et_sq_bl_mean","vl_sq_bl_mean","et_cl_bl_mean","vl_cl_bl_mean"),"minority" = c("et_sq_or_mean","vl_sq_or_mean","et_cl_or_mean","vl_cl_or_mean")), "local"))
+
+ggplot(data = data_f, aes(x = dominant, y = Segra,  linetype = `segregation` , fill = `ethnia`,  shape = `orientation`)) + geom_line(aes(color = `ethnia`))  +  geom_point(color = "black", size = 4) + 
+ scale_x_discrete(limits=c(seq(0,20 ,by = 1))) + scale_y_continuous(limits=c(0,1), breaks=seq(0,1,by=0.10)) +
+  scale_linetype_manual(values=c("solid","dashed"), labels = c("ethnic","value"), guide = guide_legend(title = "Segregation", order = 1)) +
+  scale_fill_manual(values = c("blue","darkorange")) + 
+  scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
+  scale_shape_manual(values = c(22,21), guide = guide_legend(title="Value" ,override.aes = list(size = 3), order = 3)) +
+  guides(fill = FALSE) +
+  xlab("ß dominant = ß secondary") + ylab("Exposure") + 
+  theme_bw() +  theme( axis.title.x = (element_text(size = 15)), axis.title.y = (element_text(size = 15)), axis.text.x =  (element_text(size = 15)),axis.text.y =  (element_text(size = 15)), legend.title = element_text(size = 13) ,legend.text = element_text(size = 13), plot.title=element_text(hjust = 0.5)) + theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
+
+ggsave("images/one_beta.jpg",plot = last_plot(),
+  device = NULL,path = NULL, 
+  scale = 1,
+  width = 10,
+  height = 4,
+  units = c("in", "cm", "mm"),
+  dpi = 300,
+  limitsize = FALSE)
+
+# robustness table
+
+table_rb <- xtable(basic_sa[,c("dominant","et_sq_bl_mean","et_sq_bl_sd","et_cl_bl_mean","et_cl_bl_sd","et_sq_or_mean","et_sq_or_sd","et_cl_or_mean","et_cl_or_sd","vl_sq_bl_mean","vl_sq_bl_sd","vl_cl_bl_mean","vl_cl_bl_sd","vl_sq_or_mean","vl_sq_or_sd","vl_cl_or_mean","vl_cl_or_sd")], digits = 3)
+align(table_rb) <- "c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|"
+
+addtorow <- list()
+addtorow$pos <- list(0, 0,0,0,0)
+addtorow$command <-  c("\\multicolumn{17}{|c|}{Baseline condition}  \\\\\\hline\n",
+   "Preference &  \\multicolumn{8}{|c|}{Ethnic Exposure} & \\multicolumn{8}{|c|}{Value Exposure}   \\\\\\hline\n",
+  "& \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  & \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  \\\\\n",
+"$\\beta$ dom = $\\beta$ sec & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
+& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
+& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal}\\\\\n",
+" & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD\\\\\n")
+
+print(table_rb,type = "latex", file = "latex/basic_rb.tex", include.rownames=FALSE, add.to.row = addtorow, include.colnames = FALSE, latex.environments = "center")
+
+```
+
+```{r secondary_0, fig.width=30, fig.cap="Fig. 4 Secondary preference set to 0. Baseline symmetric", echo=FALSE}
+
+# database filter
+excl <- names(basic) %in% c("run", "ID","density","step")
+basic_sa_sec0 <- basic[!excl] %>% filter(secondary == 0) %>% group_by(dominant,circle_orange,circle_blue,fraction_blue,secondary) %>% summarise_all(c("mean"= mean,"sd"= sd))
+
+# graph
+
+data_f <- basic_sa_sec0 %>% gather(key= subgroup, value = Segra, et_sq_bl_mean, vl_sq_bl_mean, et_cl_bl_mean, vl_cl_bl_mean, et_sq_or_mean, vl_sq_or_mean, et_cl_or_mean, vl_cl_or_mean) %>% mutate(
+  `segregation` = fct_relevel(fct_collapse(subgroup,"ethnics" = c("et_sq_bl_mean","et_cl_bl_mean","et_sq_or_mean","et_cl_or_mean"), "values" = c("vl_sq_bl_mean","vl_cl_bl_mean","vl_sq_or_mean","vl_cl_or_mean")),"ethnics"),
+ `orientation` = fct_relevel(fct_collapse(subgroup, "conservative" = c("et_sq_bl_mean","vl_sq_bl_mean","et_sq_or_mean","vl_sq_or_mean"), "liberal" = c("et_cl_bl_mean","vl_cl_bl_mean","et_cl_or_mean","vl_cl_or_mean")),"conservative" ),
+ `ethnia` = fct_relevel(fct_collapse(subgroup, "local" = c("et_sq_bl_mean","vl_sq_bl_mean","et_cl_bl_mean","vl_cl_bl_mean"),"minority" = c("et_sq_or_mean","vl_sq_or_mean","et_cl_or_mean","vl_cl_or_mean")), "local"))
+
+ggplot(data = data_f, aes(x = dominant, y = Segra, linetype = `segregation` , fill = `ethnia`,  shape = `orientation`)) + geom_line(aes(color = `ethnia`))  +  geom_point(color = "black", size = 4) + 
+ scale_x_discrete(limits=c(seq(0,20 ,by = 1))) + scale_y_continuous(limits=c(0,1), breaks=seq(0,1,by=0.10)) +
+   scale_linetype_manual(values=c("solid","dashed"), labels = c("ethnic","value"), guide = guide_legend(title = "Segregation", order = 1)) +
+  scale_fill_manual(values = c("blue","darkorange")) + 
+  scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
+  scale_shape_manual(values = c(22,21), guide = guide_legend(title="Value" ,override.aes = list(size = 3), order = 3)) +
+  guides(fill = FALSE) +
+  xlab("ß dominant") + ylab("Exposure") + 
+  theme_bw() +  theme( axis.title.x = (element_text(size = 15)), axis.title.y = (element_text(size = 15)), axis.text.x =  (element_text(size = 15)),axis.text.y =  (element_text(size = 15)), legend.title = element_text(size = 13) ,legend.text = element_text(size = 13), plot.title=element_text(hjust = 0.5)) + theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
+
+ggsave("images/sec_0.jpg",plot = last_plot(),
+  device = NULL,path = NULL, 
+  scale = 1,
+  width = 10,
+  height = 4,
+  units = c("in", "cm", "mm"),
+  dpi = 300,
+  limitsize = FALSE)
+
+# robustness table
+
+table_rb <- xtable(basic_sa_sec0[,c("dominant","et_sq_bl_mean","et_sq_bl_sd","et_cl_bl_mean","et_cl_bl_sd","et_sq_or_mean","et_sq_or_sd","et_cl_or_mean","et_cl_or_sd","vl_sq_bl_mean","vl_sq_bl_sd","vl_cl_bl_mean","vl_cl_bl_sd","vl_sq_or_mean","vl_sq_or_sd","vl_cl_or_mean","vl_cl_or_sd")], digits = 3)
+align(table_rb) <- "c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|"
+
+addtorow <- list()
+addtorow$pos <- list(0, 0,0,0,0)
+addtorow$command <-  c("\\multicolumn{17}{|c|}{Secondary preference = 0}  \\\\\\hline\n",
+   "Preference &  \\multicolumn{8}{|c|}{Ethnic Exposure} & \\multicolumn{8}{|c|}{Value Exposure}   \\\\\\hline\n",
+  "& \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  & \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  \\\\\n",
+"$\\beta$ sec = 0 & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
+& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
+& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal}\\\\\n",
+" & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD\\\\\n")
+
+print(table_rb,type = "latex", file = "latex/basic_rb_sec0.tex", include.rownames=FALSE, add.to.row = addtorow, include.colnames = FALSE, latex.environments = "center")
+
+```
+
+```{r sensval, fig.width=30, fig.cap="Fig. 5 Test mechanism: increase liberal and conservative, all other 0. Baselie  symmetric", echo=FALSE}
+
+# database filter
+excl <- names(value_basic) %in% c("run","density","step")
+dom_lib <- value_basic[!excl] %>% filter(ID == "dom_crl") %>%   #,  secondary_circle == 0 & dominant_square == 0 & secondary_square == 0) %>% 
+  group_by(ID, dominant_circle,secondary_circle,dominant_square,secondary_square,fraction_blue,circle_blue,circle_orange) %>% summarise_all(c("mean"= mean,"sd"= sd))
+
+# graph
+
+data_f <- dom_lib %>% gather(key= subgroup, value = Segra, et_sq_bl_mean, vl_sq_bl_mean, et_cl_bl_mean, vl_cl_bl_mean, et_sq_or_mean, vl_sq_or_mean, et_cl_or_mean, vl_cl_or_mean) %>% mutate(
+  `segregation` = fct_relevel(fct_collapse(subgroup,"ethnics" = c("et_sq_bl_mean","et_cl_bl_mean","et_sq_or_mean","et_cl_or_mean"), "values" = c("vl_sq_bl_mean","vl_cl_bl_mean","vl_sq_or_mean","vl_cl_or_mean")),"ethnics"),
+ `orientation` = fct_relevel(fct_collapse(subgroup, "conservative" = c("et_sq_bl_mean","vl_sq_bl_mean","et_sq_or_mean","vl_sq_or_mean"), "liberal" = c("et_cl_bl_mean","vl_cl_bl_mean","et_cl_or_mean","vl_cl_or_mean")),"conservative" ),
+ `ethnia` = fct_relevel(fct_collapse(subgroup, "local" = c("et_sq_bl_mean","vl_sq_bl_mean","et_cl_bl_mean","vl_cl_bl_mean"),"minority" = c("et_sq_or_mean","vl_sq_or_mean","et_cl_or_mean","vl_cl_or_mean")), "local"))
+
+ dom_libpic <- ggplot(data = data_f, aes(x = dominant_circle, y = Segra, linetype = `segregation` , fill = `ethnia`,  shape = `orientation`)) + geom_line(aes(color = `ethnia`))  +  geom_point(color = "black", size = 4) +
+ scale_x_discrete(limits=c(seq(0,20 ,by = 1))) + scale_y_continuous(limits=c(0,1), breaks=seq(0,1,by=0.10)) +
+#geom_hline(yintercept = 0.50, color = "red") +
+ scale_linetype_manual(values=c("solid","dashed"), labels = c("ethnic","value"), guide = guide_legend(title = "Segregation", order = 1)) +
+  scale_fill_manual(values = c("blue","darkorange")) + 
+  scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
+  scale_shape_manual(values = c(22,21), guide = guide_legend(title="Value" ,override.aes = list(size = 3), order = 3)) +
+  guides(fill = FALSE) +
+  xlab("ß value liberal") + ylab("Exposure") + 
+  theme_bw() +  theme( axis.title.x = (element_text(size = 15)), axis.title.y = (element_text(size = 15)), axis.text.x =  (element_text(size = 13)),axis.text.y =  (element_text(size = 15)), legend.title = element_text(size = 13) ,legend.text = element_text(size = 13), plot.title=element_text(hjust = 0.5)) + theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
+
+# ggsave("images/dom_lib.jpg",plot = last_plot(),
+#   device = NULL,path = NULL, 
+#   scale = 1,
+#   width = 10,
+#   height = 4,
+#   units = c("in", "cm", "mm"),
+#   dpi = 300,
+#   limitsize = FALSE)
+
+# sensitivity to conservative
+
+excl <- names(value_basic) %in% c("run","density","step")
+dom_con <- value_basic[!excl] %>% filter(ID == "dom_sqr") %>%
+   group_by(ID,dominant_square, secondary_square,dominant_circle,secondary_circle,fraction_blue,circle_blue,circle_orange) %>% summarise_all(c("mean"= mean,"sd"= sd))
+
+# graph
+
+data_f <- dom_con %>% gather(key= subgroup, value = Segra, et_sq_bl_mean, vl_sq_bl_mean, et_cl_bl_mean, vl_cl_bl_mean, et_sq_or_mean, vl_sq_or_mean, et_cl_or_mean, vl_cl_or_mean) %>% mutate(
+  `segregation` = fct_relevel(fct_collapse(subgroup,"ethnics" = c("et_sq_bl_mean","et_cl_bl_mean","et_sq_or_mean","et_cl_or_mean"), "values" = c("vl_sq_bl_mean","vl_cl_bl_mean","vl_sq_or_mean","vl_cl_or_mean")),"ethnics"),
+ `orientation` = fct_relevel(fct_collapse(subgroup, "conservative" = c("et_sq_bl_mean","vl_sq_bl_mean","et_sq_or_mean","vl_sq_or_mean"), "liberal" = c("et_cl_bl_mean","vl_cl_bl_mean","et_cl_or_mean","vl_cl_or_mean")),"conservative" ),
+ `ethnia` = fct_relevel(fct_collapse(subgroup, "local" = c("et_sq_bl_mean","vl_sq_bl_mean","et_cl_bl_mean","vl_cl_bl_mean"),"minority" = c("et_sq_or_mean","vl_sq_or_mean","et_cl_or_mean","vl_cl_or_mean")), "local"))
+
+dom_conpic <- ggplot(data = data_f, aes(x = dominant_square, y = Segra, linetype = `segregation` , fill = `ethnia`,  shape = `orientation`)) + geom_line(aes(color = `ethnia`))  +  geom_point(color = "black", size = 4) +
+ scale_x_discrete(limits=c(seq(0,20 ,by = 1))) + scale_y_continuous(limits=c(0,1), breaks=seq(0,1,by=0.10)) +
+  scale_linetype_manual(values=c("solid","dashed"), labels = c("ethnic","value"), guide = guide_legend(title = "Segregation", order = 1)) +
+  scale_fill_manual(values = c("blue","darkorange")) + 
+  scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
+  scale_shape_manual(values = c(22,21), guide = guide_legend(title="Value" ,override.aes = list(size = 3), order = 3)) +
+  guides(fill = FALSE) +
+  xlab("ß ethnic conservative") + ylab("Exposure") + 
+  theme_bw() +  theme( axis.title.x = (element_text(size = 15)), axis.title.y = (element_text(size = 15)), axis.text.x =  (element_text(size = 13)),axis.text.y =  (element_text(size = 15)), legend.title = element_text(size = 13) ,legend.text = element_text(size = 13), plot.title=element_text(hjust = 0.5)) + theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
+
+# ggsave("images/dom_con.jpg",plot = last_plot(),
+#   device = NULL,path = NULL, 
+#   scale = 1,
+#   width = 10,
+#   height = 4,
+#   units = c("in", "cm", "mm"),
+#   dpi = 300,
+#   limitsize = FALSE)
+#
+
+ggpubr::ggarrange(dom_libpic,dom_conpic, nrow = 2, ncol = 1, common.legend = TRUE, legend = "right")
+
+ggsave("images/comb_val.jpg",plot = last_plot(),
+  device = NULL,path = NULL, 
+  scale = 1,
+ width = 8,
+  height = 6,
+  units = c("in", "cm", "mm"),
+  dpi = 300,
+  limitsize = FALSE)
+
+# robustness table
+
+row_lib <-  c("\\multicolumn{17}{|c|}{Baseline: sensitivity to value liberal}  \\\\\\hline\n",
+   "Preference &  \\multicolumn{8}{|c|}{Ethnic Exposure} & \\multicolumn{8}{|c|}{Value Exposure}   \\\\\\hline\n",
+  "& \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  & \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  \\\\\n",
+# note
+"$\\beta$ dom & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
+& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
+& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal}\\\\\n",
+"liberal & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD\\\\\n")
+
+row_con <- c("\\multicolumn{17}{|c|}{Baseline: sensitivity to ethnic conservative}  \\\\\\hline\n",
+   "Preference &  \\multicolumn{8}{|c|}{Ethnic Exposure} & \\multicolumn{8}{|c|}{Value Exposure}   \\\\\\hline\n",
+  "& \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  & \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  \\\\\n",
+# note
+"$\\beta$ dom & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
+ & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
+& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal}\\\\\n",
+" conservative & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD\\\\\n")
+
+table_lib <- xtable(dom_lib[,c("dominant_circle","et_sq_bl_mean","et_sq_bl_sd","et_cl_bl_mean","et_cl_bl_sd","et_sq_or_mean","et_sq_or_sd","et_cl_or_mean","et_cl_or_sd","vl_sq_bl_mean","vl_sq_bl_sd","vl_cl_bl_mean","vl_cl_bl_sd","vl_sq_or_mean","vl_sq_or_sd","vl_cl_or_mean","vl_cl_or_sd")], digits = 3)
+align(table_lib) <- "c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|"
+
+addtorow <- list()
+addtorow$pos <- list(0, 0,0,0,0)
+addtorow$command <- row_lib
+
+print(table_lib,type = "latex", file = "latex/dom_lib_rb.tex", include.rownames=FALSE, add.to.row = addtorow, include.colnames = FALSE, latex.environments = "center")
+
+table_con <- xtable(dom_con[,c("dominant_square","et_sq_bl_mean","et_sq_bl_sd","et_cl_bl_mean","et_cl_bl_sd","et_sq_or_mean","et_sq_or_sd","et_cl_or_mean","et_cl_or_sd","vl_sq_bl_mean","vl_sq_bl_sd","vl_cl_bl_mean","vl_cl_bl_sd","vl_sq_or_mean","vl_sq_or_sd","vl_cl_or_mean","vl_cl_or_sd")], digits = 3)
+align(table_con) <- "c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|"
+
+addtorow <- list()
+addtorow$pos <- list(0, 0,0,0,0)
+addtorow$command <-  row_con
+
+print(table_con,type = "latex", file = "latex/dom_con_rb.tex", include.rownames=FALSE, add.to.row = addtorow, include.colnames = FALSE, latex.environments = "center")
+
+```
+
+```{r sens_secondary, fig.width=30, fig.cap="Fig. 6 Test mechanism: increase secondary preference, all determinism high. Baseline symmetric", echo=FALSE}
+
+# database filter
+excl <- names(value_basic) %in% c("run","density","step")
+sec_crl <- value_basic[!excl] %>% filter(ID == "sec_crl") %>%   #,  secondary_circle == 0 & dominant_square == 0 & secondary_square == 0)
+  group_by(ID,secondary_circle, dominant_circle,dominant_square,secondary_square,fraction_blue,circle_blue,circle_orange) %>% summarise_all(c("mean"= mean,"sd"= sd))
+
+# graph
+
+data_f <- sec_crl %>% gather(key= subgroup, value = Segra, et_sq_bl_mean, vl_sq_bl_mean, et_cl_bl_mean, vl_cl_bl_mean, et_sq_or_mean, vl_sq_or_mean, et_cl_or_mean, vl_cl_or_mean) %>% mutate(
+  `segregation` = fct_relevel(fct_collapse(subgroup,"ethnics" = c("et_sq_bl_mean","et_cl_bl_mean","et_sq_or_mean","et_cl_or_mean"), "values" = c("vl_sq_bl_mean","vl_cl_bl_mean","vl_sq_or_mean","vl_cl_or_mean")),"ethnics"),
+ `orientation` = fct_relevel(fct_collapse(subgroup, "conservative" = c("et_sq_bl_mean","vl_sq_bl_mean","et_sq_or_mean","vl_sq_or_mean"), "liberal" = c("et_cl_bl_mean","vl_cl_bl_mean","et_cl_or_mean","vl_cl_or_mean")),"conservative" ),
+ `ethnia` = fct_relevel(fct_collapse(subgroup, "local" = c("et_sq_bl_mean","vl_sq_bl_mean","et_cl_bl_mean","vl_cl_bl_mean"),"minority" = c("et_sq_or_mean","vl_sq_or_mean","et_cl_or_mean","vl_cl_or_mean")), "local"))
+
+sec_crl_pic <- ggplot(data = data_f, aes(x = secondary_circle, y = Segra, linetype = `segregation` , fill = `ethnia`,  shape = `orientation`)) + geom_line(aes(color = `ethnia`))  +  geom_point(color = "black", size = 4) +
+ scale_x_discrete(limits=c(seq(0,20 ,by = 1))) + scale_y_continuous(limits=c(0,1), breaks=seq(0,1,by=0.10)) +
+#geom_hline(yintercept = 0.50, color = "red") +
+ scale_linetype_manual(values=c("solid","dashed"), labels = c("ethnic","value"), guide = guide_legend(title = "Segregation", order = 1)) +
+  scale_fill_manual(values = c("blue","darkorange")) + 
+  scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
+  scale_shape_manual(values = c(22,21), guide = guide_legend(title="Value" ,override.aes = list(size = 3), order = 3)) +
+  guides(fill = FALSE) +
+  xlab("ß ethnic liberal") + ylab("Exposure") + 
+  theme_bw() +  theme( axis.title.x = (element_text(size = 15)), axis.title.y = (element_text(size = 15)), axis.text.x =  (element_text(size = 13)),axis.text.y =  (element_text(size = 15)), legend.title = element_text(size = 13) ,legend.text = element_text(size = 13), plot.title=element_text(hjust = 0.5)) + theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
+
+# ggsave("images/dom_lib.jpg",plot = last_plot(),
+#   device = NULL,path = NULL, 
+#   scale = 1,
+#   width = 10,
+#   height = 4,
+#   units = c("in", "cm", "mm"),
+#   dpi = 300,
+#   limitsize = FALSE)
+
+# sensitivity to conservative
+
+excl <- names(value_basic) %in% c("run","density","step")
+sec_sqr <- value_basic[!excl] %>% filter(ID == "sec_sqr") %>%
+   group_by(ID,secondary_square, dominant_square,dominant_circle,secondary_circle,fraction_blue,circle_blue,circle_orange) %>% summarise_all(c("mean"= mean,"sd"= sd))
+
+# graph
+
+data_f <- sec_sqr %>% gather(key= subgroup, value = Segra, et_sq_bl_mean, vl_sq_bl_mean, et_cl_bl_mean, vl_cl_bl_mean, et_sq_or_mean, vl_sq_or_mean, et_cl_or_mean, vl_cl_or_mean) %>% mutate(
+  `segregation` = fct_relevel(fct_collapse(subgroup,"ethnics" = c("et_sq_bl_mean","et_cl_bl_mean","et_sq_or_mean","et_cl_or_mean"), "values" = c("vl_sq_bl_mean","vl_cl_bl_mean","vl_sq_or_mean","vl_cl_or_mean")),"ethnics"),
+ `orientation` = fct_relevel(fct_collapse(subgroup, "conservative" = c("et_sq_bl_mean","vl_sq_bl_mean","et_sq_or_mean","vl_sq_or_mean"), "liberal" = c("et_cl_bl_mean","vl_cl_bl_mean","et_cl_or_mean","vl_cl_or_mean")),"conservative" ),
+ `ethnia` = fct_relevel(fct_collapse(subgroup, "local" = c("et_sq_bl_mean","vl_sq_bl_mean","et_cl_bl_mean","vl_cl_bl_mean"),"minority" = c("et_sq_or_mean","vl_sq_or_mean","et_cl_or_mean","vl_cl_or_mean")), "local"))
+
+sec_sqr_pic <- ggplot(data = data_f, aes(x = secondary_square, y = Segra, linetype = `segregation` , fill = `ethnia`,  shape = `orientation`)) + geom_line(aes(color = `ethnia`))  +  geom_point(color = "black", size = 4) +
+ scale_x_discrete(limits=c(seq(0,20 ,by = 1))) + scale_y_continuous(limits=c(0,1), breaks=seq(0,1,by=0.10)) +
+  scale_linetype_manual(values=c("solid","dashed"), labels = c("ethnic","value"), guide = guide_legend(title = "Segregation", order = 1)) +
+  scale_fill_manual(values = c("blue","darkorange")) + 
+  scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
+  scale_shape_manual(values = c(22,21), guide = guide_legend(title="Value" ,override.aes = list(size = 3), order = 3)) +
+  guides(fill = FALSE) +
+  xlab("ß value conservative") + ylab("Exposure") + 
+  theme_bw() +  theme( axis.title.x = (element_text(size = 15)), axis.title.y = (element_text(size = 15)), axis.text.x =  (element_text(size = 13)),axis.text.y =  (element_text(size = 15)), legend.title = element_text(size = 13) ,legend.text = element_text(size = 13), plot.title=element_text(hjust = 0.5)) + theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
+
+# ggsave("images/dom_con.jpg",plot = last_plot(),
+#   device = NULL,path = NULL, 
+#   scale = 1,
+#   width = 10,
+#   height = 4,
+#   units = c("in", "cm", "mm"),
+#   dpi = 300,
+#   limitsize = FALSE)
+#
+
+ggpubr::ggarrange(sec_crl_pic,sec_sqr_pic, nrow = 2, ncol = 1, common.legend = TRUE, legend = "right")
+
+ggsave("images/comb_sec_bln.jpg",plot = last_plot(),
+  device = NULL,path = NULL, 
+  scale = 1,
+ width = 8,
+  height = 6,
+  units = c("in", "cm", "mm"),
+  dpi = 300,
+  limitsize = FALSE)
+
+# robustness table
+
+row_lib <-  c("\\multicolumn{17}{|c|}{Baseline: increase ethnic liberal}  \\\\\\hline\n",
+   "Preference &  \\multicolumn{8}{|c|}{Ethnic Exposure} & \\multicolumn{8}{|c|}{Value Exposure}   \\\\\\hline\n",
+  "& \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  & \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  \\\\\n",
+# note
+"$\\beta$ ethnic & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
+& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
+& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal}\\\\\n",
+"liberal & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD\\\\\n")
+
+row_con <- c("\\multicolumn{17}{|c|}{Baseline: increase value conservative}  \\\\\\hline\n",
+   "Preference &  \\multicolumn{8}{|c|}{Ethnic Exposure} & \\multicolumn{8}{|c|}{Value Exposure}   \\\\\\hline\n",
+  "& \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  & \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  \\\\\n",
+# note
+"$\\beta$ value & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
+ & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
+& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal}\\\\\n",
+" conservative & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD\\\\\n")
+
+table_lib <- xtable(sec_crl[,c("secondary_circle","et_sq_bl_mean","et_sq_bl_sd","et_cl_bl_mean","et_cl_bl_sd","et_sq_or_mean","et_sq_or_sd","et_cl_or_mean","et_cl_or_sd","vl_sq_bl_mean","vl_sq_bl_sd","vl_cl_bl_mean","vl_cl_bl_sd","vl_sq_or_mean","vl_sq_or_sd","vl_cl_or_mean","vl_cl_or_sd")], digits = 3)
+align(table_lib) <- "c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|"
+
+addtorow <- list()
+addtorow$pos <- list(0, 0,0,0,0)
+addtorow$command <- row_lib
+
+print(table_lib,type = "latex", file = "latex/sec_crl_rb.tex", include.rownames=FALSE, add.to.row = addtorow, include.colnames = FALSE, latex.environments = "center")
+
+table_con <- xtable(sec_sqr[,c("secondary_square","et_sq_bl_mean","et_sq_bl_sd","et_cl_bl_mean","et_cl_bl_sd","et_sq_or_mean","et_sq_or_sd","et_cl_or_mean","et_cl_or_sd","vl_sq_bl_mean","vl_sq_bl_sd","vl_cl_bl_mean","vl_cl_bl_sd","vl_sq_or_mean","vl_sq_or_sd","vl_cl_or_mean","vl_cl_or_sd")], digits = 3)
+align(table_con) <- "c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|"
+
+addtorow <- list()
+addtorow$pos <- list(0, 0,0,0,0)
+addtorow$command <-  row_con
+
+print(table_con,type = "latex", file = "latex/sec_sqr_rb.tex", include.rownames=FALSE, add.to.row = addtorow, include.colnames = FALSE, latex.environments = "center")
+
+```
+
+```{r heatmap, include=TRUE, fig.cap="Fig. 7 Heatmap dominant vs secondary. Baseline symmetric", echo=FALSE}
+
+# database filter
 excl <- names(basic) %in% c("run", "ID","density","step")
@@
 
+# data preparation: long format
 data_f <- basic_sa %>% filter(dominant >= secondary)   %>% gather(key= subgroup, value = Segra, et_sq_bl_mean, vl_sq_bl_mean, et_cl_bl_mean, vl_cl_bl_mean, et_sq_or_mean, vl_sq_or_mean, et_cl_or_mean, vl_cl_or_mean) %>% mutate(
@@
 
-```{r basefigure, fig.width=30, fig.cap="Same parameter for ethnic and value homophily for all agents", echo=FALSE}
-
-# database filter
-excl <- names(basic) %in% c("run", "ID","density","step")
-basic_sa <- basic[!excl] %>% filter(dominant == secondary) %>% group_by(dominant,secondary,circle_orange,circle_blue,fraction_blue) %>% summarise_all(c("mean"= mean,"sd"= sd))
-
-# graph
-
-data_f <- basic_sa %>% gather(key= subgroup, value = Segra, et_sq_bl_mean, vl_sq_bl_mean, et_cl_bl_mean, vl_cl_bl_mean, et_sq_or_mean, vl_sq_or_mean, et_cl_or_mean, vl_cl_or_mean) %>% mutate(
-  `segregation` = fct_relevel(fct_collapse(subgroup,"ethnics" = c("et_sq_bl_mean","et_cl_bl_mean","et_sq_or_mean","et_cl_or_mean"), "values" = c("vl_sq_bl_mean","vl_cl_bl_mean","vl_sq_or_mean","vl_cl_or_mean")),"ethnics"),
- `orientation` = fct_relevel(fct_collapse(subgroup, "conservative" = c("et_sq_bl_mean","vl_sq_bl_mean","et_sq_or_mean","vl_sq_or_mean"), "liberal" = c("et_cl_bl_mean","vl_cl_bl_mean","et_cl_or_mean","vl_cl_or_mean")),"conservative" ),
- `ethnia` = fct_relevel(fct_collapse(subgroup, "local" = c("et_sq_bl_mean","vl_sq_bl_mean","et_cl_bl_mean","vl_cl_bl_mean"),"minority" = c("et_sq_or_mean","vl_sq_or_mean","et_cl_or_mean","vl_cl_or_mean")), "local"))
-
-ggplot(data = data_f, aes(x = dominant, y = Segra,  linetype = `segregation` , fill = `ethnia`,  shape = `orientation`)) + geom_line(aes(color = `ethnia`))  +  geom_point(color = "black", size = 4) + 
- scale_x_discrete(limits=c(seq(0,20 ,by = 1))) + scale_y_continuous(limits=c(0,1), breaks=seq(0,1,by=0.10)) +
-  scale_linetype_manual(values=c("solid","dashed"), labels = c("ethnic","value"), guide = guide_legend(title = "Segregation", order = 1)) +
-  scale_fill_manual(values = c("blue","darkorange")) + 
-  scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
-  scale_shape_manual(values = c(22,21), guide = guide_legend(title="Value" ,override.aes = list(size = 3), order = 3)) +
-  guides(fill = FALSE) +
-  xlab("ß dominant = ß secondary") + ylab("Exposure") + 
-  theme_bw() +  theme( axis.title.x = (element_text(size = 15)), axis.title.y = (element_text(size = 15)), axis.text.x =  (element_text(size = 15)),axis.text.y =  (element_text(size = 15)), legend.title = element_text(size = 13) ,legend.text = element_text(size = 13), plot.title=element_text(hjust = 0.5)) + theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
-
-ggsave("images/one_beta.jpg",plot = last_plot(),
-  device = NULL,path = NULL, 
-  scale = 1,
-  width = 10,
-  height = 4,
-  units = c("in", "cm", "mm"),
-  dpi = 300,
-  limitsize = FALSE)
-
-# robustness table
-
-table_rb <- xtable(basic_sa[,c("dominant","et_sq_bl_mean","et_sq_bl_sd","et_cl_bl_mean","et_cl_bl_sd","et_sq_or_mean","et_sq_or_sd","et_cl_or_mean","et_cl_or_sd","vl_sq_bl_mean","vl_sq_bl_sd","vl_cl_bl_mean","vl_cl_bl_sd","vl_sq_or_mean","vl_sq_or_sd","vl_cl_or_mean","vl_cl_or_sd")], digits = 3)
-align(table_rb) <- "c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|"
-
-addtorow <- list()
-addtorow$pos <- list(0, 0,0,0,0)
-addtorow$command <-  c("\\multicolumn{17}{|c|}{Baseline condition}  \\\\\\hline\n",
-   "Preference &  \\multicolumn{8}{|c|}{Ethnic Exposure} & \\multicolumn{8}{|c|}{Value Exposure}   \\\\\\hline\n",
-  "& \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  & \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  \\\\\n",
-"$\\beta$ dom = $\\beta$ sec & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
-& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
-& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal}\\\\\n",
-" & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD\\\\\n")
-
-print(table_rb,type = "latex", file = "latex/basic_rb.tex", include.rownames=FALSE, add.to.row = addtorow, include.colnames = FALSE, latex.environments = "center")
-
-```
-
-```{r secondary_0, fig.width=30, fig.cap="secondary preference set to 0", echo=FALSE}
-
-# database filter
-excl <- names(basic) %in% c("run", "ID","density","step")
-basic_sa_sec0 <- basic[!excl] %>% filter(secondary == 0) %>% group_by(dominant,circle_orange,circle_blue,fraction_blue,secondary) %>% summarise_all(c("mean"= mean,"sd"= sd))
-
-# graph
-
-data_f <- basic_sa_sec0 %>% gather(key= subgroup, value = Segra, et_sq_bl_mean, vl_sq_bl_mean, et_cl_bl_mean, vl_cl_bl_mean, et_sq_or_mean, vl_sq_or_mean, et_cl_or_mean, vl_cl_or_mean) %>% mutate(
-  `segregation` = fct_relevel(fct_collapse(subgroup,"ethnics" = c("et_sq_bl_mean","et_cl_bl_mean","et_sq_or_mean","et_cl_or_mean"), "values" = c("vl_sq_bl_mean","vl_cl_bl_mean","vl_sq_or_mean","vl_cl_or_mean")),"ethnics"),
- `orientation` = fct_relevel(fct_collapse(subgroup, "conservative" = c("et_sq_bl_mean","vl_sq_bl_mean","et_sq_or_mean","vl_sq_or_mean"), "liberal" = c("et_cl_bl_mean","vl_cl_bl_mean","et_cl_or_mean","vl_cl_or_mean")),"conservative" ),
- `ethnia` = fct_relevel(fct_collapse(subgroup, "local" = c("et_sq_bl_mean","vl_sq_bl_mean","et_cl_bl_mean","vl_cl_bl_mean"),"minority" = c("et_sq_or_mean","vl_sq_or_mean","et_cl_or_mean","vl_cl_or_mean")), "local"))
-
-ggplot(data = data_f, aes(x = dominant, y = Segra, linetype = `segregation` , fill = `ethnia`,  shape = `orientation`)) + geom_line(aes(color = `ethnia`))  +  geom_point(color = "black", size = 4) + 
- scale_x_discrete(limits=c(seq(0,20 ,by = 1))) + scale_y_continuous(limits=c(0,1), breaks=seq(0,1,by=0.10)) +
-   scale_linetype_manual(values=c("solid","dashed"), labels = c("ethnic","value"), guide = guide_legend(title = "Segregation", order = 1)) +
-  scale_fill_manual(values = c("blue","darkorange")) + 
-  scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
-  scale_shape_manual(values = c(22,21), guide = guide_legend(title="Value" ,override.aes = list(size = 3), order = 3)) +
-  guides(fill = FALSE) +
-  xlab("ß dominant") + ylab("Exposure") + 
-  theme_bw() +  theme( axis.title.x = (element_text(size = 15)), axis.title.y = (element_text(size = 15)), axis.text.x =  (element_text(size = 15)),axis.text.y =  (element_text(size = 15)), legend.title = element_text(size = 13) ,legend.text = element_text(size = 13), plot.title=element_text(hjust = 0.5)) + theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
-
-ggsave("images/sec_0.jpg",plot = last_plot(),
-  device = NULL,path = NULL, 
-  scale = 1,
-  width = 10,
-  height = 4,
-  units = c("in", "cm", "mm"),
-  dpi = 300,
-  limitsize = FALSE)
-
-# robustness table
-
-table_rb <- xtable(basic_sa_sec0[,c("dominant","et_sq_bl_mean","et_sq_bl_sd","et_cl_bl_mean","et_cl_bl_sd","et_sq_or_mean","et_sq_or_sd","et_cl_or_mean","et_cl_or_sd","vl_sq_bl_mean","vl_sq_bl_sd","vl_cl_bl_mean","vl_cl_bl_sd","vl_sq_or_mean","vl_sq_or_sd","vl_cl_or_mean","vl_cl_or_sd")], digits = 3)
-align(table_rb) <- "c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|"
-
-addtorow <- list()
-addtorow$pos <- list(0, 0,0,0,0)
-addtorow$command <-  c("\\multicolumn{17}{|c|}{Secondary preference = 0}  \\\\\\hline\n",
-   "Preference &  \\multicolumn{8}{|c|}{Ethnic Exposure} & \\multicolumn{8}{|c|}{Value Exposure}   \\\\\\hline\n",
-  "& \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  & \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  \\\\\n",
-"$\\beta$ sec = 0 & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
-& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
-& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal}\\\\\n",
-" & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD\\\\\n")
-
-print(table_rb,type = "latex", file = "latex/basic_rb_sec0.tex", include.rownames=FALSE, add.to.row = addtorow, include.colnames = FALSE, latex.environments = "center")
-
-```
-
-```{r sensval, fig.width=30, fig.cap="Test mechanism: increase liberal and conservative, all other 0", echo=FALSE}
-
-# database filter
-excl <- names(value_basic) %in% c("run","density","step")
-dom_lib <- value_basic[!excl] %>% filter(ID == "dom_crl") %>%   #,  secondary_circle == 0 & dominant_square == 0 & secondary_square == 0) %>% 
-  group_by(ID, dominant_circle,secondary_circle,dominant_square,secondary_square,fraction_blue,circle_blue,circle_orange) %>% summarise_all(c("mean"= mean,"sd"= sd))
-
-# graph
-
-data_f <- dom_lib %>% gather(key= subgroup, value = Segra, et_sq_bl_mean, vl_sq_bl_mean, et_cl_bl_mean, vl_cl_bl_mean, et_sq_or_mean, vl_sq_or_mean, et_cl_or_mean, vl_cl_or_mean) %>% mutate(
-  `segregation` = fct_relevel(fct_collapse(subgroup,"ethnics" = c("et_sq_bl_mean","et_cl_bl_mean","et_sq_or_mean","et_cl_or_mean"), "values" = c("vl_sq_bl_mean","vl_cl_bl_mean","vl_sq_or_mean","vl_cl_or_mean")),"ethnics"),
- `orientation` = fct_relevel(fct_collapse(subgroup, "conservative" = c("et_sq_bl_mean","vl_sq_bl_mean","et_sq_or_mean","vl_sq_or_mean"), "liberal" = c("et_cl_bl_mean","vl_cl_bl_mean","et_cl_or_mean","vl_cl_or_mean")),"conservative" ),
- `ethnia` = fct_relevel(fct_collapse(subgroup, "local" = c("et_sq_bl_mean","vl_sq_bl_mean","et_cl_bl_mean","vl_cl_bl_mean"),"minority" = c("et_sq_or_mean","vl_sq_or_mean","et_cl_or_mean","vl_cl_or_mean")), "local"))
-
- dom_libpic <- ggplot(data = data_f, aes(x = dominant_circle, y = Segra, linetype = `segregation` , fill = `ethnia`,  shape = `orientation`)) + geom_line(aes(color = `ethnia`))  +  geom_point(color = "black", size = 4) +
- scale_x_discrete(limits=c(seq(0,20 ,by = 1))) + scale_y_continuous(limits=c(0,1), breaks=seq(0,1,by=0.10)) +
-#geom_hline(yintercept = 0.50, color = "red") +
- scale_linetype_manual(values=c("solid","dashed"), labels = c("ethnic","value"), guide = guide_legend(title = "Segregation", order = 1)) +
-  scale_fill_manual(values = c("blue","darkorange")) + 
-  scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
-  scale_shape_manual(values = c(22,21), guide = guide_legend(title="Value" ,override.aes = list(size = 3), order = 3)) +
-  guides(fill = FALSE) +
-  xlab("ß value liberal") + ylab("Exposure") + 
-  theme_bw() +  theme( axis.title.x = (element_text(size = 15)), axis.title.y = (element_text(size = 15)), axis.text.x =  (element_text(size = 13)),axis.text.y =  (element_text(size = 15)), legend.title = element_text(size = 13) ,legend.text = element_text(size = 13), plot.title=element_text(hjust = 0.5)) + theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
-
-# ggsave("images/dom_lib.jpg",plot = last_plot(),
-#   device = NULL,path = NULL, 
-#   scale = 1,
-#   width = 10,
-#   height = 4,
-#   units = c("in", "cm", "mm"),
-#   dpi = 300,
-#   limitsize = FALSE)
-
-# sensitivity to conservative
-
-excl <- names(value_basic) %in% c("run","density","step")
-dom_con <- value_basic[!excl] %>% filter(ID == "dom_sqr") %>%
-   group_by(ID,dominant_square, secondary_square,dominant_circle,secondary_circle,fraction_blue,circle_blue,circle_orange) %>% summarise_all(c("mean"= mean,"sd"= sd))
-
-# graph
-
-data_f <- dom_con %>% gather(key= subgroup, value = Segra, et_sq_bl_mean, vl_sq_bl_mean, et_cl_bl_mean, vl_cl_bl_mean, et_sq_or_mean, vl_sq_or_mean, et_cl_or_mean, vl_cl_or_mean) %>% mutate(
-  `segregation` = fct_relevel(fct_collapse(subgroup,"ethnics" = c("et_sq_bl_mean","et_cl_bl_mean","et_sq_or_mean","et_cl_or_mean"), "values" = c("vl_sq_bl_mean","vl_cl_bl_mean","vl_sq_or_mean","vl_cl_or_mean")),"ethnics"),
- `orientation` = fct_relevel(fct_collapse(subgroup, "conservative" = c("et_sq_bl_mean","vl_sq_bl_mean","et_sq_or_mean","vl_sq_or_mean"), "liberal" = c("et_cl_bl_mean","vl_cl_bl_mean","et_cl_or_mean","vl_cl_or_mean")),"conservative" ),
- `ethnia` = fct_relevel(fct_collapse(subgroup, "local" = c("et_sq_bl_mean","vl_sq_bl_mean","et_cl_bl_mean","vl_cl_bl_mean"),"minority" = c("et_sq_or_mean","vl_sq_or_mean","et_cl_or_mean","vl_cl_or_mean")), "local"))
-
-dom_conpic <- ggplot(data = data_f, aes(x = dominant_square, y = Segra, linetype = `segregation` , fill = `ethnia`,  shape = `orientation`)) + geom_line(aes(color = `ethnia`))  +  geom_point(color = "black", size = 4) +
- scale_x_discrete(limits=c(seq(0,20 ,by = 1))) + scale_y_continuous(limits=c(0,1), breaks=seq(0,1,by=0.10)) +
-  scale_linetype_manual(values=c("solid","dashed"), labels = c("ethnic","value"), guide = guide_legend(title = "Segregation", order = 1)) +
-  scale_fill_manual(values = c("blue","darkorange")) + 
-  scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
-  scale_shape_manual(values = c(22,21), guide = guide_legend(title="Value" ,override.aes = list(size = 3), order = 3)) +
-  guides(fill = FALSE) +
-  xlab("ß ethnic conservative") + ylab("Exposure") + 
-  theme_bw() +  theme( axis.title.x = (element_text(size = 15)), axis.title.y = (element_text(size = 15)), axis.text.x =  (element_text(size = 13)),axis.text.y =  (element_text(size = 15)), legend.title = element_text(size = 13) ,legend.text = element_text(size = 13), plot.title=element_text(hjust = 0.5)) + theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
-
-# ggsave("images/dom_con.jpg",plot = last_plot(),
-#   device = NULL,path = NULL, 
-#   scale = 1,
-#   width = 10,
-#   height = 4,
-#   units = c("in", "cm", "mm"),
-#   dpi = 300,
-#   limitsize = FALSE)
-#
-
-ggpubr::ggarrange(dom_libpic,dom_conpic, nrow = 2, ncol = 1, common.legend = TRUE, legend = "right")
-
-ggsave("images/comb_val.jpg",plot = last_plot(),
-  device = NULL,path = NULL, 
-  scale = 1,
- width = 8,
-  height = 6,
-  units = c("in", "cm", "mm"),
-  dpi = 300,
-  limitsize = FALSE)
-
-# robustness table
-
-row_lib <-  c("\\multicolumn{17}{|c|}{Baseline: sensitivity to value liberal}  \\\\\\hline\n",
-   "Preference &  \\multicolumn{8}{|c|}{Ethnic Exposure} & \\multicolumn{8}{|c|}{Value Exposure}   \\\\\\hline\n",
-  "& \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  & \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  \\\\\n",
-# note
-"$\\beta$ dom & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
-& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
-& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal}\\\\\n",
-"liberal & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD\\\\\n")
-
-row_con <- c("\\multicolumn{17}{|c|}{Baseline: sensitivity to ethnic conservative}  \\\\\\hline\n",
-   "Preference &  \\multicolumn{8}{|c|}{Ethnic Exposure} & \\multicolumn{8}{|c|}{Value Exposure}   \\\\\\hline\n",
-  "& \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  & \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  \\\\\n",
-# note
-"$\\beta$ dom & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
- & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
-& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal}\\\\\n",
-" conservative & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD\\\\\n")
-
-table_lib <- xtable(dom_lib[,c("dominant_circle","et_sq_bl_mean","et_sq_bl_sd","et_cl_bl_mean","et_cl_bl_sd","et_sq_or_mean","et_sq_or_sd","et_cl_or_mean","et_cl_or_sd","vl_sq_bl_mean","vl_sq_bl_sd","vl_cl_bl_mean","vl_cl_bl_sd","vl_sq_or_mean","vl_sq_or_sd","vl_cl_or_mean","vl_cl_or_sd")], digits = 3)
-align(table_lib) <- "c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|"
-
-addtorow <- list()
-addtorow$pos <- list(0, 0,0,0,0)
-addtorow$command <- row_lib
-
-print(table_lib,type = "latex", file = "latex/dom_lib_rb.tex", include.rownames=FALSE, add.to.row = addtorow, include.colnames = FALSE, latex.environments = "center")
-
-table_con <- xtable(dom_con[,c("dominant_square","et_sq_bl_mean","et_sq_bl_sd","et_cl_bl_mean","et_cl_bl_sd","et_sq_or_mean","et_sq_or_sd","et_cl_or_mean","et_cl_or_sd","vl_sq_bl_mean","vl_sq_bl_sd","vl_cl_bl_mean","vl_cl_bl_sd","vl_sq_or_mean","vl_sq_or_sd","vl_cl_or_mean","vl_cl_or_sd")], digits = 3)
-align(table_con) <- "c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|"
-
-addtorow <- list()
-addtorow$pos <- list(0, 0,0,0,0)
-addtorow$command <-  row_con
-
-print(table_con,type = "latex", file = "latex/dom_con_rb.tex", include.rownames=FALSE, add.to.row = addtorow, include.colnames = FALSE, latex.environments = "center")
-
-```
-
-```{r sens_secondary, fig.width=30, fig.cap="Test mechanism: increase secondary preference, all determinism high", echo=FALSE}
-
-# database filter
-excl <- names(value_basic) %in% c("run","density","step")
-sec_crl <- value_basic[!excl] %>% filter(ID == "sec_crl") %>%   #,  secondary_circle == 0 & dominant_square == 0 & secondary_square == 0)
-  group_by(ID,secondary_circle, dominant_circle,dominant_square,secondary_square,fraction_blue,circle_blue,circle_orange) %>% summarise_all(c("mean"= mean,"sd"= sd))
-
-# graph
-
-data_f <- sec_crl %>% gather(key= subgroup, value = Segra, et_sq_bl_mean, vl_sq_bl_mean, et_cl_bl_mean, vl_cl_bl_mean, et_sq_or_mean, vl_sq_or_mean, et_cl_or_mean, vl_cl_or_mean) %>% mutate(
-  `segregation` = fct_relevel(fct_collapse(subgroup,"ethnics" = c("et_sq_bl_mean","et_cl_bl_mean","et_sq_or_mean","et_cl_or_mean"), "values" = c("vl_sq_bl_mean","vl_cl_bl_mean","vl_sq_or_mean","vl_cl_or_mean")),"ethnics"),
- `orientation` = fct_relevel(fct_collapse(subgroup, "conservative" = c("et_sq_bl_mean","vl_sq_bl_mean","et_sq_or_mean","vl_sq_or_mean"), "liberal" = c("et_cl_bl_mean","vl_cl_bl_mean","et_cl_or_mean","vl_cl_or_mean")),"conservative" ),
- `ethnia` = fct_relevel(fct_collapse(subgroup, "local" = c("et_sq_bl_mean","vl_sq_bl_mean","et_cl_bl_mean","vl_cl_bl_mean"),"minority" = c("et_sq_or_mean","vl_sq_or_mean","et_cl_or_mean","vl_cl_or_mean")), "local"))
-
-sec_crl_pic <- ggplot(data = data_f, aes(x = secondary_circle, y = Segra, linetype = `segregation` , fill = `ethnia`,  shape = `orientation`)) + geom_line(aes(color = `ethnia`))  +  geom_point(color = "black", size = 4) +
- scale_x_discrete(limits=c(seq(0,20 ,by = 1))) + scale_y_continuous(limits=c(0,1), breaks=seq(0,1,by=0.10)) +
-#geom_hline(yintercept = 0.50, color = "red") +
- scale_linetype_manual(values=c("solid","dashed"), labels = c("ethnic","value"), guide = guide_legend(title = "Segregation", order = 1)) +
-  scale_fill_manual(values = c("blue","darkorange")) + 
-  scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
-  scale_shape_manual(values = c(22,21), guide = guide_legend(title="Value" ,override.aes = list(size = 3), order = 3)) +
-  guides(fill = FALSE) +
-  xlab("ß ethnic liberal") + ylab("Exposure") + 
-  theme_bw() +  theme( axis.title.x = (element_text(size = 15)), axis.title.y = (element_text(size = 15)), axis.text.x =  (element_text(size = 13)),axis.text.y =  (element_text(size = 15)), legend.title = element_text(size = 13) ,legend.text = element_text(size = 13), plot.title=element_text(hjust = 0.5)) + theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
-
-# ggsave("images/dom_lib.jpg",plot = last_plot(),
-#   device = NULL,path = NULL, 
-#   scale = 1,
-#   width = 10,
-#   height = 4,
-#   units = c("in", "cm", "mm"),
-#   dpi = 300,
-#   limitsize = FALSE)
-
-# sensitivity to conservative
-
-excl <- names(value_basic) %in% c("run","density","step")
-sec_sqr <- value_basic[!excl] %>% filter(ID == "sec_sqr") %>%
-   group_by(ID,secondary_square, dominant_square,dominant_circle,secondary_circle,fraction_blue,circle_blue,circle_orange) %>% summarise_all(c("mean"= mean,"sd"= sd))
-
-# graph
-
-data_f <- sec_sqr %>% gather(key= subgroup, value = Segra, et_sq_bl_mean, vl_sq_bl_mean, et_cl_bl_mean, vl_cl_bl_mean, et_sq_or_mean, vl_sq_or_mean, et_cl_or_mean, vl_cl_or_mean) %>% mutate(
-  `segregation` = fct_relevel(fct_collapse(subgroup,"ethnics" = c("et_sq_bl_mean","et_cl_bl_mean","et_sq_or_mean","et_cl_or_mean"), "values" = c("vl_sq_bl_mean","vl_cl_bl_mean","vl_sq_or_mean","vl_cl_or_mean")),"ethnics"),
- `orientation` = fct_relevel(fct_collapse(subgroup, "conservative" = c("et_sq_bl_mean","vl_sq_bl_mean","et_sq_or_mean","vl_sq_or_mean"), "liberal" = c("et_cl_bl_mean","vl_cl_bl_mean","et_cl_or_mean","vl_cl_or_mean")),"conservative" ),
- `ethnia` = fct_relevel(fct_collapse(subgroup, "local" = c("et_sq_bl_mean","vl_sq_bl_mean","et_cl_bl_mean","vl_cl_bl_mean"),"minority" = c("et_sq_or_mean","vl_sq_or_mean","et_cl_or_mean","vl_cl_or_mean")), "local"))
-
-sec_sqr_pic <- ggplot(data = data_f, aes(x = secondary_square, y = Segra, linetype = `segregation` , fill = `ethnia`,  shape = `orientation`)) + geom_line(aes(color = `ethnia`))  +  geom_point(color = "black", size = 4) +
- scale_x_discrete(limits=c(seq(0,20 ,by = 1))) + scale_y_continuous(limits=c(0,1), breaks=seq(0,1,by=0.10)) +
-  scale_linetype_manual(values=c("solid","dashed"), labels = c("ethnic","value"), guide = guide_legend(title = "Segregation", order = 1)) +
-  scale_fill_manual(values = c("blue","darkorange")) + 
-  scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
-  scale_shape_manual(values = c(22,21), guide = guide_legend(title="Value" ,override.aes = list(size = 3), order = 3)) +
-  guides(fill = FALSE) +
-  xlab("ß value conservative") + ylab("Exposure") + 
-  theme_bw() +  theme( axis.title.x = (element_text(size = 15)), axis.title.y = (element_text(size = 15)), axis.text.x =  (element_text(size = 13)),axis.text.y =  (element_text(size = 15)), legend.title = element_text(size = 13) ,legend.text = element_text(size = 13), plot.title=element_text(hjust = 0.5)) + theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
-
-# ggsave("images/dom_con.jpg",plot = last_plot(),
-#   device = NULL,path = NULL, 
-#   scale = 1,
-#   width = 10,
-#   height = 4,
-#   units = c("in", "cm", "mm"),
-#   dpi = 300,
-#   limitsize = FALSE)
-#
-
-ggpubr::ggarrange(sec_crl_pic,sec_sqr_pic, nrow = 2, ncol = 1, common.legend = TRUE, legend = "right")
-
-ggsave("images/comb_sec_bln.jpg",plot = last_plot(),
-  device = NULL,path = NULL, 
-  scale = 1,
- width = 8,
-  height = 6,
-  units = c("in", "cm", "mm"),
-  dpi = 300,
-  limitsize = FALSE)
-
-# robustness table
-
-row_lib <-  c("\\multicolumn{17}{|c|}{Baseline: increase ethnic liberal}  \\\\\\hline\n",
-   "Preference &  \\multicolumn{8}{|c|}{Ethnic Exposure} & \\multicolumn{8}{|c|}{Value Exposure}   \\\\\\hline\n",
-  "& \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  & \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  \\\\\n",
-# note
-"$\\beta$ ethnic & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
-& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
-& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal}\\\\\n",
-"liberal & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD\\\\\n")
-
-row_con <- c("\\multicolumn{17}{|c|}{Baseline: increase value conservative}  \\\\\\hline\n",
-   "Preference &  \\multicolumn{8}{|c|}{Ethnic Exposure} & \\multicolumn{8}{|c|}{Value Exposure}   \\\\\\hline\n",
-  "& \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  & \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  \\\\\n",
-# note
-"$\\beta$ value & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
- & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
-& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal}\\\\\n",
-" conservative & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD\\\\\n")
-
-table_lib <- xtable(sec_crl[,c("secondary_circle","et_sq_bl_mean","et_sq_bl_sd","et_cl_bl_mean","et_cl_bl_sd","et_sq_or_mean","et_sq_or_sd","et_cl_or_mean","et_cl_or_sd","vl_sq_bl_mean","vl_sq_bl_sd","vl_cl_bl_mean","vl_cl_bl_sd","vl_sq_or_mean","vl_sq_or_sd","vl_cl_or_mean","vl_cl_or_sd")], digits = 3)
-align(table_lib) <- "c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|"
-
-addtorow <- list()
-addtorow$pos <- list(0, 0,0,0,0)
-addtorow$command <- row_lib
-
-print(table_lib,type = "latex", file = "latex/sec_crl_rb.tex", include.rownames=FALSE, add.to.row = addtorow, include.colnames = FALSE, latex.environments = "center")
-
-table_con <- xtable(sec_sqr[,c("secondary_square","et_sq_bl_mean","et_sq_bl_sd","et_cl_bl_mean","et_cl_bl_sd","et_sq_or_mean","et_sq_or_sd","et_cl_or_mean","et_cl_or_sd","vl_sq_bl_mean","vl_sq_bl_sd","vl_cl_bl_mean","vl_cl_bl_sd","vl_sq_or_mean","vl_sq_or_sd","vl_cl_or_mean","vl_cl_or_sd")], digits = 3)
-align(table_con) <- "c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|"
-
-addtorow <- list()
-addtorow$pos <- list(0, 0,0,0,0)
-addtorow$command <-  row_con
-
-print(table_con,type = "latex", file = "latex/sec_sqr_rb.tex", include.rownames=FALSE, add.to.row = addtorow, include.colnames = FALSE, latex.environments = "center")
-
-```
-
-```{r asym, fig.width=30, fig.cap="Baseline asymmetric conditions", echo=FALSE}
+# Asymmetric Conditions
+
+```{r asym, fig.width=30, fig.cap="Fig. 8 Baseline asymmetric conditions, secondary = 0", echo=FALSE}
 
@@
   guides(fill = FALSE) +
-  xlab(xlab_t) + ylab("Spatial Proximity") + 
+  xlab(xlab_t) + ylab(expression(Exposure[correct])) + 
   theme_bw() +  theme( axis.title.x = (element_text(size = 15)), axis.title.y = (element_text(size = 15)), axis.text.x =  (element_text(size = 15)),axis.text.y =  (element_text(size = 15)), legend.title = element_text(size = 13) ,legend.text = element_text(size = 13), plot.title=element_text(hjust = 0.5)) + theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
@@
 
-```{r dislib, fig.width=30, fig.cap="Effect distribution liberal minority, asymmetric based condition", echo=FALSE}
+```{r sa_dom_50prox, fig.width=30, fig.cap="Fig. 9, Sensitivity analysis group-type. Each panel reports 50 % then combined", echo=FALSE}
+
+# database filter
+excl <- names(sa_asym) %in% c("run", "ID","density","step","eth_lib_loc","val_con_loc","eth_lib_min","val_con_min")
+dataset_sa <- sa_asym[!excl] %>% filter(val_lib_loc  == 20,eth_con_min == 20, val_lib_min == 20)  %>% 
+ filter(circle_orange == 50) %>%
+  group_by(eth_con_loc,fraction_blue,circle_blue, circle_orange) %>% summarise_all(c("mean"= mean,"sd"= sd))
+
+xlab_t <- "ß ethnic conservative local"
+
+# graph
+
+data_prox <- dataset_sa %>% gather(key= subgroup, value = Prox, de_sq_bl_mean, dv_sq_bl_mean, de_cl_bl_mean, dv_cl_bl_mean, de_sq_or_mean, dv_sq_or_mean, de_cl_or_mean, dv_cl_or_mean) %>% mutate(
+  `segregation` = fct_relevel(fct_collapse(subgroup,"ethnics" = c("de_sq_bl_mean","de_cl_bl_mean","de_sq_or_mean","de_cl_or_mean"), "values" = c("dv_sq_bl_mean","dv_cl_bl_mean","dv_sq_or_mean","dv_cl_or_mean")),"ethnics"),
+ `orientation` = fct_relevel(fct_collapse(subgroup, "conservative" = c("de_sq_bl_mean","dv_sq_bl_mean","de_sq_or_mean","dv_sq_or_mean"), "liberal" = c("de_cl_bl_mean","dv_cl_bl_mean","de_cl_or_mean","dv_cl_or_mean")),"conservative" ),
+ `ethnia` = fct_relevel(fct_collapse(subgroup, "local" = c("de_sq_bl_mean","dv_sq_bl_mean","de_cl_bl_mean","dv_cl_bl_mean"),"minority" = c("de_sq_or_mean","dv_sq_or_mean","de_cl_or_mean","dv_cl_or_mean")), "local"))
+
+prox_eth_con_loc <- ggplot(data = data_prox, aes(x = eth_con_loc, y = Prox, linetype = `segregation` , fill = `ethnia`,  shape = `orientation`)) + geom_line(aes(color = `ethnia`))  +  geom_point(color = "black", size = 4) +
+ scale_x_discrete(limits=c(seq(0,20 ,by = 1)))  + scale_y_continuous(limits=c(min(data_prox$Prox),5), breaks=seq(0,5,by=0.50)) +
+  #    facet_wrap(~ circle_orange, labeller = labeller(circle_orange = circle_orange.labs)) +
+    geom_vline(xintercept = 20, color = "red") +
+
+  scale_linetype_manual(values=c("solid","dashed"), labels = c("ethnic","value"), guide = guide_legend(title = "Segregation", order = 1)) +
+  scale_fill_manual(values = c("blue","darkorange")) + 
+  scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
+  scale_shape_manual(values = c(22,21), guide = guide_legend(title="Value" ,override.aes = list(size = 3), order = 3)) +
+  guides(fill = FALSE) +
+  xlab(xlab_t) + ylab(expression(Exposure[correct])) + 
+  theme_bw() +  theme( axis.title.x = (element_text(size = 15)), axis.title.y = (element_text(size = 15)), axis.text.x =  (element_text(size = 12)),axis.text.y =  (element_text(size = 15)), legend.title = element_text(size = 13) ,legend.text = element_text(size = 13),plot.title=element_text(hjust = 0.5)) + theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
+
+# database filter
+excl <- names(sa_asym) %in% c("run", "ID","density","step","eth_lib_loc","val_con_loc","eth_lib_min","val_con_min")
+dataset_sa <- sa_asym[!excl] %>% filter(eth_con_loc   == 20,eth_con_min == 20, val_lib_min == 20)  %>% 
+ filter(circle_orange == 50) %>%
+  group_by(val_lib_loc,fraction_blue,circle_blue, circle_orange) %>% summarise_all(c("mean"= mean,"sd"= sd))
+
+xlab_t <- "ß value liberal local"
+
+# graph
+
+data_prox <- dataset_sa %>% gather(key= subgroup, value = Prox, de_sq_bl_mean, dv_sq_bl_mean, de_cl_bl_mean, dv_cl_bl_mean, de_sq_or_mean, dv_sq_or_mean, de_cl_or_mean, dv_cl_or_mean) %>% mutate(
+  `segregation` = fct_relevel(fct_collapse(subgroup,"ethnics" = c("de_sq_bl_mean","de_cl_bl_mean","de_sq_or_mean","de_cl_or_mean"), "values" = c("dv_sq_bl_mean","dv_cl_bl_mean","dv_sq_or_mean","dv_cl_or_mean")),"ethnics"),
+ `orientation` = fct_relevel(fct_collapse(subgroup, "conservative" = c("de_sq_bl_mean","dv_sq_bl_mean","de_sq_or_mean","dv_sq_or_mean"), "liberal" = c("de_cl_bl_mean","dv_cl_bl_mean","de_cl_or_mean","dv_cl_or_mean")),"conservative" ),
+ `ethnia` = fct_relevel(fct_collapse(subgroup, "local" = c("de_sq_bl_mean","dv_sq_bl_mean","de_cl_bl_mean","dv_cl_bl_mean"),"minority" = c("de_sq_or_mean","dv_sq_or_mean","de_cl_or_mean","dv_cl_or_mean")), "local"))
+
+prox_val_lib_loc <-  ggplot(data = data_prox, aes(x = val_lib_loc, y = Prox, linetype = `segregation` , fill = `ethnia`,  shape = `orientation`)) + geom_line(aes(color = `ethnia`))  +  geom_point(color = "black", size = 4) +
+ scale_x_discrete(limits=c(seq(0,20 ,by = 1)))  + scale_y_continuous(limits=c(min(data_prox$Prox),5), breaks=seq(0,5,by=0.50)) +
+  #    facet_wrap(~ circle_orange, labeller = labeller(circle_orange = circle_orange.labs)) +
+    geom_vline(xintercept = 20, color = "red") +
+
+  scale_linetype_manual(values=c("solid","dashed"), labels = c("ethnic","value"), guide = guide_legend(title = "Segregation", order = 1)) +
+  scale_fill_manual(values = c("blue","darkorange")) + 
+  scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
+  scale_shape_manual(values = c(22,21), guide = guide_legend(title="Value" ,override.aes = list(size = 3), order = 3)) +
+  guides(fill = FALSE) +
+  xlab(xlab_t) + ylab(expression(Exposure[correct])) + 
+  theme_bw() +  theme( axis.title.x = (element_text(size = 15)), axis.title.y = (element_text(size = 15)), axis.text.x =  (element_text(size = 12)),axis.text.y =  (element_text(size = 15)), legend.title = element_text(size = 13) ,legend.text = element_text(size = 13),plot.title=element_text(hjust = 0.5)) + theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
+
+# ggsave("images/val_lib_loc50.jpg",plot = fig_prox,
+#   device = NULL,path = NULL, 
+#   scale = 1,
+#   width = 8,
+#   height = 6,
+#   units = c("in", "cm", "mm"),
+#   dpi = 300,
+#   limitsize = FALSE)
+
+# database filter
+excl <- names(sa_asym) %in% c("run", "ID","density","step","eth_lib_loc","val_con_loc","eth_lib_min","val_con_min")
+dataset_sa <- sa_asym[!excl] %>% filter(eth_con_loc   == 20, val_lib_loc  == 20, val_lib_min == 20)  %>% 
+ filter(circle_orange == 50) %>%
+  group_by(eth_con_min,fraction_blue,circle_blue, circle_orange) %>% summarise_all(c("mean"= mean,"sd"= sd))
+
+xlab_t <- "ß ethnic conservative minority"
+
+# graph
+
+data_prox <- dataset_sa %>% gather(key= subgroup, value = Prox, de_sq_bl_mean, dv_sq_bl_mean, de_cl_bl_mean, dv_cl_bl_mean, de_sq_or_mean, dv_sq_or_mean, de_cl_or_mean, dv_cl_or_mean) %>% mutate(
+  `segregation` = fct_relevel(fct_collapse(subgroup,"ethnics" = c("de_sq_bl_mean","de_cl_bl_mean","de_sq_or_mean","de_cl_or_mean"), "values" = c("dv_sq_bl_mean","dv_cl_bl_mean","dv_sq_or_mean","dv_cl_or_mean")),"ethnics"),
+ `orientation` = fct_relevel(fct_collapse(subgroup, "conservative" = c("de_sq_bl_mean","dv_sq_bl_mean","de_sq_or_mean","dv_sq_or_mean"), "liberal" = c("de_cl_bl_mean","dv_cl_bl_mean","de_cl_or_mean","dv_cl_or_mean")),"conservative" ),
+ `ethnia` = fct_relevel(fct_collapse(subgroup, "local" = c("de_sq_bl_mean","dv_sq_bl_mean","de_cl_bl_mean","dv_cl_bl_mean"),"minority" = c("de_sq_or_mean","dv_sq_or_mean","de_cl_or_mean","dv_cl_or_mean")), "local"))
+
+prox_eth_con_min <- ggplot(data = data_prox, aes(x = eth_con_min, y = Prox, linetype = `segregation` , fill = `ethnia`,  shape = `orientation`)) + geom_line(aes(color = `ethnia`))  +  geom_point(color = "black", size = 4) +
+ scale_x_discrete(limits=c(seq(0,20 ,by = 1)))  + scale_y_continuous(limits=c(min(data_prox$Prox),5), breaks=seq(0,5,by=0.50)) +
+  #    facet_wrap(~ circle_orange, labeller = labeller(circle_orange = circle_orange.labs)) +
+    geom_vline(xintercept = 20, color = "red") +
+
+  scale_linetype_manual(values=c("solid","dashed"), labels = c("ethnic","value"), guide = guide_legend(title = "Segregation", order = 1)) +
+  scale_fill_manual(values = c("blue","darkorange")) + 
+  scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
+  scale_shape_manual(values = c(22,21), guide = guide_legend(title="Value" ,override.aes = list(size = 3), order = 3)) +
+  guides(fill = FALSE) +
+  xlab(xlab_t) + ylab(expression(Exposure[correct])) + 
+  theme_bw() +  theme( axis.title.x = (element_text(size = 15)), axis.title.y = (element_text(size = 15)), axis.text.x =  (element_text(size = 12)),axis.text.y =  (element_text(size = 15)), legend.title = element_text(size = 13) ,legend.text = element_text(size = 13),plot.title=element_text(hjust = 0.5)) + theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
+
+# ggsave("images/eth_con_min50.jpg",plot = fig_prox,
+#   device = NULL,path = NULL, 
+#   scale = 1,
+#   width = 8,
+#   height = 6,
+#   units = c("in", "cm", "mm"),
+#   dpi = 300,
+#   limitsize = FALSE)
+
+# database filter
+excl <- names(sa_asym) %in% c("run", "ID","density","step","eth_lib_loc","val_con_loc","eth_lib_min","val_con_min")
+dataset_sa <- sa_asym[!excl] %>% filter(eth_con_loc   == 20, val_lib_loc  == 20, eth_con_min  == 20)  %>% 
+ filter(circle_orange == 50) %>%
+  group_by(val_lib_min,fraction_blue,circle_blue, circle_orange) %>% summarise_all(c("mean"= mean,"sd"= sd))
+
+xlab_t <- "ß value liberal minority"
+
+# graph
+
+data_prox <- dataset_sa %>% gather(key= subgroup, value = Prox, de_sq_bl_mean, dv_sq_bl_mean, de_cl_bl_mean, dv_cl_bl_mean, de_sq_or_mean, dv_sq_or_mean, de_cl_or_mean, dv_cl_or_mean) %>% mutate(
+  `segregation` = fct_relevel(fct_collapse(subgroup,"ethnics" = c("de_sq_bl_mean","de_cl_bl_mean","de_sq_or_mean","de_cl_or_mean"), "values" = c("dv_sq_bl_mean","dv_cl_bl_mean","dv_sq_or_mean","dv_cl_or_mean")),"ethnics"),
+ `orientation` = fct_relevel(fct_collapse(subgroup, "conservative" = c("de_sq_bl_mean","dv_sq_bl_mean","de_sq_or_mean","dv_sq_or_mean"), "liberal" = c("de_cl_bl_mean","dv_cl_bl_mean","de_cl_or_mean","dv_cl_or_mean")),"conservative" ),
+ `ethnia` = fct_relevel(fct_collapse(subgroup, "local" = c("de_sq_bl_mean","dv_sq_bl_mean","de_cl_bl_mean","dv_cl_bl_mean"),"minority" = c("de_sq_or_mean","dv_sq_or_mean","de_cl_or_mean","dv_cl_or_mean")), "local"))
+
+prox_val_lib_min <-  ggplot(data = data_prox, aes(x = val_lib_min, y = Prox, linetype = `segregation` , fill = `ethnia`,  shape = `orientation`)) + geom_line(aes(color = `ethnia`))  +  geom_point(color = "black", size = 4) +
+ scale_x_discrete(limits=c(seq(0,20 ,by = 1)))  + scale_y_continuous(limits=c(min(data_prox$Prox),5), breaks=seq(0,5,by=0.50)) +
+  #    facet_wrap(~ circle_orange, labeller = labeller(circle_orange = circle_orange.labs)) +
+    geom_vline(xintercept = 20, color = "red") +
+
+  scale_linetype_manual(values=c("solid","dashed"), labels = c("ethnic","value"), guide = guide_legend(title = "Segregation", order = 1)) +
+  scale_fill_manual(values = c("blue","darkorange")) + 
+  scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
+  scale_shape_manual(values = c(22,21), guide = guide_legend(title="Value" ,override.aes = list(size = 3), order = 3)) +
+  guides(fill = FALSE) +
+  xlab(xlab_t) + ylab(expression(Exposure[correct])) + 
+  theme_bw() +  theme( axis.title.x = (element_text(size = 15)), axis.title.y = (element_text(size = 15)), axis.text.x =  (element_text(size = 12)),axis.text.y =  (element_text(size = 15)), legend.title = element_text(size = 13) ,legend.text = element_text(size = 13),plot.title=element_text(hjust = 0.5)) + theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
+
+ggpubr::ggarrange(prox_eth_con_loc,prox_val_lib_loc,prox_eth_con_min,prox_val_lib_min, nrow = 2, ncol = 2, common.legend = TRUE, legend = "bottom")
+
+ggsave("images/sa_asym_bt.jpg",plot = last_plot(),
+  device = NULL,path = NULL,
+  scale = 1,
+  width = 11,
+  height = 8,
+  units = c("in", "cm", "mm"),
+  dpi = 300,
+  limitsize = FALSE)
+
+```
+
+```{r dislib, fig.width=30, fig.cap="Fig. 10, Effect distribution liberals minority, asymmetric condition", echo=FALSE}
 
@@
   guides(fill = FALSE) +
-  xlab(xlab_t) + ylab("Spatial Proximity") + 
+  xlab(xlab_t) + ylab(expression(Exposure[correct])) + 
 theme_bw() +  theme( axis.title.x = (element_text(size = 15)), axis.title.y = (element_text(size = 15)), axis.text.x =  (element_text(size = 15)),axis.text.y =  (element_text(size = 15)), legend.title = element_text(size = 13) ,legend.text = element_text(size = 13), plot.title=element_text(hjust = 0.5)) + theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
@@
 
-```{r sa_dom_50prox, fig.width=30, fig.cap="Sensitivity proximity ethnic conservative local, baseline asymmetric conditions", echo=FALSE}
+```{r sa_vllblc,  fig.cap="Fig 11, Sensitivity value liberals majority - exposure correct, asymmetric conditions", echo=FALSE}
 
@@
 excl <- names(sa_asym) %in% c("run", "ID","density","step","eth_lib_loc","val_con_loc","eth_lib_min","val_con_min")
-dataset_sa <- sa_asym[!excl] %>% filter(val_lib_loc  == 20,eth_con_min == 20, val_lib_min == 20)  %>% 
- filter(circle_orange == 50) %>%
-  group_by(eth_con_loc,fraction_blue,circle_blue, circle_orange) %>% summarise_all(c("mean"= mean,"sd"= sd))
-
-xlab_t <- "ß ethnic conservative local"
-
-# graph
+dataset_sa <- sa_asym[!excl] %>% filter(eth_con_loc  == 20,eth_con_min   == 20,val_lib_min == 20)  %>% 
+group_by(val_lib_loc ,fraction_blue,circle_blue, circle_orange) %>% summarise_all(c("mean"= mean,"sd"= sd))
+
+plotname <- "images/vllblc.jpg"
+xlab_t <- "ß value liberal local"
+
+xvalues <- c(dataset_sa$de_sq_bl_mean,dataset_sa$de_cl_bl_mean,dataset_sa$de_sq_or_mean,dataset_sa$de_cl_or_mean,
+       dataset_sa$dv_sq_bl_mean,dataset_sa$dv_cl_bl_mean,dataset_sa$dv_sq_or_mean,dataset_sa$dv_cl_or_mean)
+
+ expo_pic <-   ggplot(data = dataset_sa) + 
+  geom_point(aes(x = dataset_sa$de_sq_bl_mean, y = dataset_sa$et_sq_bl_mean),color = "black", fill = "blue", shape = 22, size = 5) +
+  geom_point(aes(x = dataset_sa$de_cl_bl_mean, y = dataset_sa$et_cl_bl_mean),color = "black",fill = "blue", shape = 21, size = 5) +
+  geom_point(aes(x = dataset_sa$de_sq_or_mean, y = dataset_sa$et_sq_or_mean),color = "black", fill = "orange", shape = 22, size = 5) +
+  geom_point(aes(x = dataset_sa$de_cl_or_mean, y = dataset_sa$et_cl_or_mean),color = "black", fill = "orange", shape = 21, size = 5) +
+
+  geom_point(aes(x = dataset_sa$dv_sq_bl_mean, y = dataset_sa$vl_sq_bl_mean),color = "black", fill = "blue", shape = 8, size = 5.1) + 
+   geom_point(aes(x = dataset_sa$dv_sq_bl_mean, y = dataset_sa$vl_sq_bl_mean),color = "black", fill = "blue", shape = 22, size = 5) +
+
+   geom_point(aes(x = dataset_sa$dv_cl_bl_mean, y = dataset_sa$vl_cl_bl_mean),color = "black",fill = "blue", shape = 8, size = 5.1) + 
+  geom_point(aes(x = dataset_sa$dv_cl_bl_mean, y = dataset_sa$vl_cl_bl_mean),color = "black",fill = "blue", shape = 21, size = 5) +
+
+    geom_point(aes(x = dataset_sa$dv_sq_or_mean, y = dataset_sa$vl_sq_or_mean),color = "black", fill = "orange", shape = 8, size = 5.1) +
+  geom_point(aes(x = dataset_sa$dv_sq_or_mean, y = dataset_sa$vl_sq_or_mean),color = "black", fill = "orange", shape = 22, size = 5) +
+
+  geom_point(aes(x = dataset_sa$dv_cl_or_mean, y = dataset_sa$vl_cl_or_mean),color = "black", fill = "orange", shape = 8, size = 5.1) +
+geom_point(aes(x = dataset_sa$dv_cl_or_mean, y = dataset_sa$vl_cl_or_mean),color = "black", fill = "orange", shape = 21, size = 5) +
+
+ scale_x_continuous(limits = c(min(xvalues),max(xvalues)), breaks = seq(0,max(xvalues), by = 0.5)) + 
+  scale_y_continuous(breaks= seq(0,1,by=0.1)) + 
+  geom_vline(xintercept = 1, color = "red") +
+   xlab(expression(Exposure[correct])) + ylab("Exposure") +
+  theme_bw() + theme( 
+    axis.title.x = (element_text(size = 13)), axis.title.y = (element_text(size = 15)),
+    axis.text.x =  (element_text(size = 12)), axis.text.y =  (element_text(size = 15)), 
+    legend.title = element_text(size = 13),legend.position = "bottom", legend.text = element_text(size = 13),
+    plot.title=element_text(hjust = 0.5), plot.caption = element_text(hjust= 0.5, size = 11), plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
 
@@
 
-prox_eth_con_loc <- ggplot(data = data_prox, aes(x = eth_con_loc, y = Prox, linetype = `segregation` , fill = `ethnia`,  shape = `orientation`)) + geom_line(aes(color = `ethnia`))  +  geom_point(color = "black", size = 4) +
- scale_x_discrete(limits=c(seq(0,20 ,by = 1)))  + scale_y_continuous(limits=c(min(data_prox$Prox),5), breaks=seq(0,5,by=0.50)) +
-  #    facet_wrap(~ circle_orange, labeller = labeller(circle_orange = circle_orange.labs)) +
-    geom_vline(xintercept = 20, color = "red") +
-
-  scale_linetype_manual(values=c("solid","dashed"), labels = c("ethnic","value"), guide = guide_legend(title = "Segregation", order = 1)) +
-  scale_fill_manual(values = c("blue","darkorange")) + 
-  scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
-  scale_shape_manual(values = c(22,21), guide = guide_legend(title="Value" ,override.aes = list(size = 3), order = 3)) +
-  guides(fill = FALSE) +
-  xlab(xlab_t) + ylab("Spatial Proximity") + 
-  theme_bw() +  theme( axis.title.x = (element_text(size = 15)), axis.title.y = (element_text(size = 15)), axis.text.x =  (element_text(size = 12)),axis.text.y =  (element_text(size = 15)), legend.title = element_text(size = 13) ,legend.text = element_text(size = 13),plot.title=element_text(hjust = 0.5)) + theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
+prox_pic <- ggplot(data = data_prox, aes(x = val_lib_loc, y = Prox, linetype = `segregation` , fill = `ethnia`,  shape = `orientation`)) + geom_line(aes(color = `ethnia`))  +  geom_point(color = "black", size = 4) +
+ scale_x_discrete(limits=c(seq(0,20 ,by = 1))) + scale_y_continuous(limits=c(min(data_prox$Prox),max(data_prox$Prox)), breaks=seq(0,max(data_prox$Prox),by=0.50)) +
+ facet_wrap(~ circle_orange, dir = "v", labeller = labeller(circle_orange = circle_orange.labs)) +
+    geom_vline(xintercept = 20, color = "red") +  geom_hline(yintercept = 1, color = "red") +
+  scale_linetype_manual(values=c("solid","dashed"), labels = c("ethnic","value"), guide = guide_legend(title = "Segregation", order = 1)) +
+  scale_fill_manual(values = c("blue","darkorange")) + 
+   scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
+  scale_shape_manual(values = c(22,21), guide = guide_legend(title="Value" ,override.aes = list(size = 3), order = 3)) +
+  guides(fill = FALSE) +
+  xlab(xlab_t) + ylab(expression(Exposure[correct])) + 
+  theme_bw() +  theme( 
+    axis.title.x = (element_text(size = 13)), axis.title.y = (element_text(size = 15)),
+    axis.text.x =  (element_text(size = 12)), axis.text.y =  (element_text(size = 15)), 
+    strip.text = element_text(size=13),
+    legend.title = element_text(size = 13),legend.position = "bottom", legend.text = element_text(size = 14),
+    plot.title=element_text(hjust = 0.5), plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
+
+#, plot.caption = element_text(hjust= 0.5, size = 11)
+ggpubr::ggarrange(prox_pic, expo_pic, common.legend = TRUE, legend = "bottom", widths = c(1.3,1))
+
+ggsave(plotname,plot = last_plot(),
+  device = NULL,path = NULL,
+  scale = 1,
+  width = 12,
+  height = 9,
+  units = c("in", "cm", "mm"),
+  dpi = 300,
+  limitsize = FALSE)
+
+```
+
+```{r sa_vllbmn,  fig.cap="Fig. 12: Sensitivity value liberals minority - exposure correct, asymmetric conditions", echo=FALSE}
 
@@
 excl <- names(sa_asym) %in% c("run", "ID","density","step","eth_lib_loc","val_con_loc","eth_lib_min","val_con_min")
-dataset_sa <- sa_asym[!excl] %>% filter(eth_con_loc   == 20,eth_con_min == 20, val_lib_min == 20)  %>% 
- filter(circle_orange == 50) %>%
-  group_by(val_lib_loc,fraction_blue,circle_blue, circle_orange) %>% summarise_all(c("mean"= mean,"sd"= sd))
-
-xlab_t <- "ß value liberal local"
-
-# graph
+dataset_sa <- sa_asym[!excl] %>% filter(eth_con_loc  == 20,val_lib_loc == 20,eth_con_min  == 20)  %>% 
+group_by(val_lib_min ,fraction_blue,circle_blue, circle_orange) %>% summarise_all(c("mean"= mean,"sd"= sd))
+
+# for image output
+
+plotname <- "images/vllbmn.jpg"
+xlab_t <- "ß value liberal minority"
+
+xvalues <- c(dataset_sa$de_sq_bl_mean,dataset_sa$de_cl_bl_mean,dataset_sa$de_sq_or_mean,dataset_sa$de_cl_or_mean,
+       dataset_sa$dv_sq_bl_mean,dataset_sa$dv_cl_bl_mean,dataset_sa$dv_sq_or_mean,dataset_sa$dv_cl_or_mean)
+
+# ethnic exposure plot
+
+ expo_pic <-   ggplot(data = dataset_sa) + 
+  geom_point(aes(x = dataset_sa$de_sq_bl_mean, y = dataset_sa$et_sq_bl_mean),color = "black", fill = "blue", shape = 22, size = 5) +
+  geom_point(aes(x = dataset_sa$de_cl_bl_mean, y = dataset_sa$et_cl_bl_mean),color = "black",fill = "blue", shape = 21, size = 5) +
+  geom_point(aes(x = dataset_sa$de_sq_or_mean, y = dataset_sa$et_sq_or_mean),color = "black", fill = "orange", shape = 22, size = 5) +
+  geom_point(aes(x = dataset_sa$de_cl_or_mean, y = dataset_sa$et_cl_or_mean),color = "black", fill = "orange", shape = 21, size = 5) +
+
+  geom_point(aes(x = dataset_sa$dv_sq_bl_mean, y = dataset_sa$vl_sq_bl_mean),color = "black", fill = "blue", shape = 8, size = 5.1) + 
+   geom_point(aes(x = dataset_sa$dv_sq_bl_mean, y = dataset_sa$vl_sq_bl_mean),color = "black", fill = "blue", shape = 22, size = 5) +
+
+   geom_point(aes(x = dataset_sa$dv_cl_bl_mean, y = dataset_sa$vl_cl_bl_mean),color = "black",fill = "blue", shape = 8, size = 5.1) + 
+  geom_point(aes(x = dataset_sa$dv_cl_bl_mean, y = dataset_sa$vl_cl_bl_mean),color = "black",fill = "blue", shape = 21, size = 5) +
+
+    geom_point(aes(x = dataset_sa$dv_sq_or_mean, y = dataset_sa$vl_sq_or_mean),color = "black", fill = "orange", shape = 8, size = 5.1) +
+  geom_point(aes(x = dataset_sa$dv_sq_or_mean, y = dataset_sa$vl_sq_or_mean),color = "black", fill = "orange", shape = 22, size = 5) +
+
+  geom_point(aes(x = dataset_sa$dv_cl_or_mean, y = dataset_sa$vl_cl_or_mean),color = "black", fill = "orange", shape = 8, size = 5.1) +
+geom_point(aes(x = dataset_sa$dv_cl_or_mean, y = dataset_sa$vl_cl_or_mean),color = "black", fill = "orange", shape = 21, size = 5) +
+
+ scale_x_continuous(limits = c(min(xvalues),max(xvalues)), breaks = seq(0,max(xvalues), by = 0.5)) + 
+  scale_y_continuous(breaks= seq(0,1,by=0.1)) + 
+  geom_vline(xintercept = 1, color = "red") +
+   xlab(expression(Exposure[correct])) + ylab("Exposure") +
+  theme_bw() + theme( 
+    axis.title.x = (element_text(size = 13)), axis.title.y = (element_text(size = 15)),
+    axis.text.x =  (element_text(size = 12)), axis.text.y =  (element_text(size = 15)), 
+    legend.title = element_text(size = 13),legend.position = "bottom", legend.text = element_text(size = 13),
+    plot.title=element_text(hjust = 0.5), plot.caption = element_text(hjust= 0.5, size = 11), plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
+
+# exposure corrected plot
 
@@
 
-prox_val_lib_loc <-  ggplot(data = data_prox, aes(x = val_lib_loc, y = Prox, linetype = `segregation` , fill = `ethnia`,  shape = `orientation`)) + geom_line(aes(color = `ethnia`))  +  geom_point(color = "black", size = 4) +
- scale_x_discrete(limits=c(seq(0,20 ,by = 1)))  + scale_y_continuous(limits=c(min(data_prox$Prox),5), breaks=seq(0,5,by=0.50)) +
-  #    facet_wrap(~ circle_orange, labeller = labeller(circle_orange = circle_orange.labs)) +
+prox_pic <- ggplot(data = data_prox, aes(x = val_lib_min, y = Prox, linetype = `segregation` , fill = `ethnia`,  shape = `orientation`)) + geom_line(aes(color = `ethnia`))  +  geom_point(color = "black", size = 4) +
+ scale_x_discrete(limits=c(seq(0,20 ,by = 1))) + scale_y_continuous(limits=c(min(data_prox$Prox),max(data_prox$Prox)), breaks=seq(0,max(data_prox$Prox),by=0.50)) +
+ facet_wrap(~ circle_orange, dir = "v", labeller = labeller(circle_orange = circle_orange.labs)) +
+    geom_vline(xintercept = 20, color = "red") +  geom_hline(yintercept = 1, color = "red") +
+  scale_linetype_manual(values=c("solid","dashed"), labels = c("ethnic","value"), guide = guide_legend(title = "Segregation", order = 1)) +
+  scale_fill_manual(values = c("blue","darkorange")) + 
+   scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
+  scale_shape_manual(values = c(22,21), guide = guide_legend(title="Value" ,override.aes = list(size = 3), order = 3)) +
+  guides(fill = FALSE) +
+  xlab(xlab_t) + ylab(expression(Exposure[correct])) + 
+  theme_bw() +  theme( 
+    axis.title.x = (element_text(size = 13)), axis.title.y = (element_text(size = 15)),
+    axis.text.x =  (element_text(size = 12)), axis.text.y =  (element_text(size = 15)), 
+    strip.text = element_text(size=13),
+    legend.title = element_text(size = 13),legend.position = "bottom", legend.text = element_text(size = 14),
+    plot.title=element_text(hjust = 0.5), plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
+
+#, plot.caption = element_text(hjust= 0.5, size = 11)
+ggpubr::ggarrange(prox_pic, expo_pic, common.legend = TRUE, legend = "bottom", widths = c(1.3,1))
+
+ggsave(plotname,plot = last_plot(),
+  device = NULL,path = NULL,
+  scale = 1,
+  width = 12,
+  height = 9,
+  units = c("in", "cm", "mm"),
+  dpi = 300,
+  limitsize = FALSE)
+
+```
+
+```{r et_lib_loc,  fig.cap="Fig. 13: Ethnic liberals majority, asymmetric conditions", echo=FALSE}
+
+# database filter
+excl <- names(etlib) %in% c("run", "ID","density","step","eth_con_loc","eth_con_min","val_lib_loc","val_lib_min","val_con_loc","val_con_min")
+etlib_df <- etlib[!excl] %>% filter(eth_lib_min  == 0)  %>% 
+group_by(eth_lib_loc,fraction_blue,circle_blue, circle_orange,eth_lib_min) %>% summarise_all(c("mean"= mean,"sd"= sd))
+
+plotname <- "images/et_libloc.jpg"
+xlab_t <- "ß ethnic liberal local"
+
+xvalues <- c(etlib_df$de_sq_bl_mean,etlib_df$de_cl_bl_mean,etlib_df$de_sq_or_mean,etlib_df$de_cl_or_mean,
+       etlib_df$dv_sq_bl_mean,etlib_df$dv_cl_bl_mean,etlib_df$dv_sq_or_mean,etlib_df$dv_cl_or_mean)
+
+ expo_pic <-   ggplot(data = etlib_df) + 
+  geom_point(aes(x = etlib_df$de_sq_bl_mean, y = etlib_df$et_sq_bl_mean),color = "black", fill = "blue", shape = 22, size = 5) +
+  geom_point(aes(x = etlib_df$de_cl_bl_mean, y = etlib_df$et_cl_bl_mean),color = "black",fill = "blue", shape = 21, size = 5) +
+  geom_point(aes(x = etlib_df$de_sq_or_mean, y = etlib_df$et_sq_or_mean),color = "black", fill = "orange", shape = 22, size = 5) +
+  geom_point(aes(x = etlib_df$de_cl_or_mean, y = etlib_df$et_cl_or_mean),color = "black", fill = "orange", shape = 21, size = 5) +
+
+  geom_point(aes(x = etlib_df$dv_sq_bl_mean, y = etlib_df$vl_sq_bl_mean),color = "black", fill = "blue", shape = 8, size = 5.1) + 
+   geom_point(aes(x = etlib_df$dv_sq_bl_mean, y = etlib_df$vl_sq_bl_mean),color = "black", fill = "blue", shape = 22, size = 5) +
+
+   geom_point(aes(x = etlib_df$dv_cl_bl_mean, y = etlib_df$vl_cl_bl_mean),color = "black",fill = "blue", shape = 8, size = 5.1) + 
+  geom_point(aes(x = etlib_df$dv_cl_bl_mean, y = etlib_df$vl_cl_bl_mean),color = "black",fill = "blue", shape = 21, size = 5) +
+
+    geom_point(aes(x = etlib_df$dv_sq_or_mean, y = etlib_df$vl_sq_or_mean),color = "black", fill = "orange", shape = 8, size = 5.1) +
+  geom_point(aes(x = etlib_df$dv_sq_or_mean, y = etlib_df$vl_sq_or_mean),color = "black", fill = "orange", shape = 22, size = 5) +
+
+  geom_point(aes(x = etlib_df$dv_cl_or_mean, y = etlib_df$vl_cl_or_mean),color = "black", fill = "orange", shape = 8, size = 5.1) +
+geom_point(aes(x = etlib_df$dv_cl_or_mean, y = etlib_df$vl_cl_or_mean),color = "black", fill = "orange", shape = 21, size = 5) +
+
+ scale_x_continuous(limits = c(min(xvalues),max(xvalues)), breaks = seq(0,max(xvalues), by = 0.5)) + 
+  scale_y_continuous(breaks= seq(0,1,by=0.1)) + 
+  geom_vline(xintercept = 1, color = "red") +
+  xlab(expression(Exposure[correct])) +  + ylab("Exposure") +
+  theme_bw() + theme( 
+    axis.title.x = (element_text(size = 13)), axis.title.y = (element_text(size = 15)),
+    axis.text.x =  (element_text(size = 12)), axis.text.y =  (element_text(size = 15)), 
+    legend.title = element_text(size = 13),legend.position = "bottom", legend.text = element_text(size = 13),
+    plot.title=element_text(hjust = 0.5), plot.caption = element_text(hjust= 0.5, size = 11), plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
+
+data_prox <- etlib_df  %>% gather(key= subgroup, value = Prox, de_sq_bl_mean, dv_sq_bl_mean, de_cl_bl_mean, dv_cl_bl_mean, de_sq_or_mean, dv_sq_or_mean, de_cl_or_mean, dv_cl_or_mean) %>% mutate(
+  `segregation` = fct_relevel(fct_collapse(subgroup,"ethnics" = c("de_sq_bl_mean","de_cl_bl_mean","de_sq_or_mean","de_cl_or_mean"), "values" = c("dv_sq_bl_mean","dv_cl_bl_mean","dv_sq_or_mean","dv_cl_or_mean")),"ethnics"),
+ `orientation` = fct_relevel(fct_collapse(subgroup, "conservative" = c("de_sq_bl_mean","dv_sq_bl_mean","de_sq_or_mean","dv_sq_or_mean"), "liberal" = c("de_cl_bl_mean","dv_cl_bl_mean","de_cl_or_mean","dv_cl_or_mean")),"conservative" ),
+ `ethnia` = fct_relevel(fct_collapse(subgroup, "local" = c("de_sq_bl_mean","dv_sq_bl_mean","de_cl_bl_mean","dv_cl_bl_mean"),"minority" = c("de_sq_or_mean","dv_sq_or_mean","de_cl_or_mean","dv_cl_or_mean")), "local"))
+
+prox_pic <- ggplot(data = data_prox, aes(x = eth_lib_loc, y = Prox, linetype = `segregation` , fill = `ethnia`,  shape = `orientation`)) + geom_line(aes(color = `ethnia`))  +  geom_point(color = "black", size = 4) +
+ scale_x_discrete(limits=c(seq(0,20 ,by = 1))) + scale_y_continuous(limits=c(min(data_prox$Prox),max(data_prox$Prox)), breaks=seq(0,max(data_prox$Prox),by=0.50)) +
+ facet_wrap(~ circle_orange, dir = "v", labeller = labeller(circle_orange = circle_orange.labs)) +
+    geom_vline(xintercept = 0, color = "red") +  geom_hline(yintercept = 1, color = "red") +
+  scale_linetype_manual(values=c("solid","dashed"), labels = c("ethnic","value"), guide = guide_legend(title = "Segregation", order = 1)) +
+  scale_fill_manual(values = c("blue","darkorange")) + 
+   scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
+  scale_shape_manual(values = c(22,21), guide = guide_legend(title="Value" ,override.aes = list(size = 3), order = 3)) +
+  guides(fill = FALSE) +
+  xlab(xlab_t) + ylab(expression(Exposure[correct])) + 
+  theme_bw() +  theme( 
+    axis.title.x = (element_text(size = 13)), axis.title.y = (element_text(size = 15)),
+    axis.text.x =  (element_text(size = 12)), axis.text.y =  (element_text(size = 15)), 
+    strip.text = element_text(size=13),
+    legend.title = element_text(size = 13),legend.position = "bottom", legend.text = element_text(size = 14),
+    plot.title=element_text(hjust = 0.5), plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
+
+#, plot.caption = element_text(hjust= 0.5, size = 11)
+ggpubr::ggarrange(prox_pic, expo_pic, common.legend = TRUE, legend = "bottom", widths = c(1.3,1))
+
+ggsave(plotname,plot = last_plot(),
+  device = NULL,path = NULL,
+  scale = 1,
+  width = 12,
+  height = 9,
+  units = c("in", "cm", "mm"),
+  dpi = 300,
+  limitsize = FALSE)
+
+```
+
+```{r et_lib_min,  fig.cap="Fig. 14: Ethnic liberals minority, asymmetric conditions", echo=FALSE}
+
+# database filter
+excl <- names(etlib) %in% c("run", "ID","density","step","eth_con_loc","eth_con_min","val_lib_loc","val_lib_min","val_con_loc","val_con_min")
+etlib_df <- etlib[!excl] %>% filter(eth_lib_loc  == 0)  %>% 
+group_by(eth_lib_min,fraction_blue,circle_blue, circle_orange,eth_lib_loc) %>% summarise_all(c("mean"= mean,"sd"= sd))
+
+plotname <- "images/et_libmin.jpg"
+xlab_t <- "ß ethnic liberal minority"
+
+xvalues <- c(etlib_df$de_sq_bl_mean,etlib_df$de_cl_bl_mean,etlib_df$de_sq_or_mean,etlib_df$de_cl_or_mean,
+       etlib_df$dv_sq_bl_mean,etlib_df$dv_cl_bl_mean,etlib_df$dv_sq_or_mean,etlib_df$dv_cl_or_mean)
+
+ expo_pic <-   ggplot(data = etlib_df) + 
+  geom_point(aes(x = etlib_df$de_sq_bl_mean, y = etlib_df$et_sq_bl_mean),color = "black", fill = "blue", shape = 22, size = 5) +
+  geom_point(aes(x = etlib_df$de_cl_bl_mean, y = etlib_df$et_cl_bl_mean),color = "black",fill = "blue", shape = 21, size = 5) +
+  geom_point(aes(x = etlib_df$de_sq_or_mean, y = etlib_df$et_sq_or_mean),color = "black", fill = "orange", shape = 22, size = 5) +
+  geom_point(aes(x = etlib_df$de_cl_or_mean, y = etlib_df$et_cl_or_mean),color = "black", fill = "orange", shape = 21, size = 5) +
+
+  geom_point(aes(x = etlib_df$dv_sq_bl_mean, y = etlib_df$vl_sq_bl_mean),color = "black", fill = "blue", shape = 8, size = 5.1) + 
+   geom_point(aes(x = etlib_df$dv_sq_bl_mean, y = etlib_df$vl_sq_bl_mean),color = "black", fill = "blue", shape = 22, size = 5) +
+
+   geom_point(aes(x = etlib_df$dv_cl_bl_mean, y = etlib_df$vl_cl_bl_mean),color = "black",fill = "blue", shape = 8, size = 5.1) + 
+  geom_point(aes(x = etlib_df$dv_cl_bl_mean, y = etlib_df$vl_cl_bl_mean),color = "black",fill = "blue", shape = 21, size = 5) +
+
+    geom_point(aes(x = etlib_df$dv_sq_or_mean, y = etlib_df$vl_sq_or_mean),color = "black", fill = "orange", shape = 8, size = 5.1) +
+  geom_point(aes(x = etlib_df$dv_sq_or_mean, y = etlib_df$vl_sq_or_mean),color = "black", fill = "orange", shape = 22, size = 5) +
+
+  geom_point(aes(x = etlib_df$dv_cl_or_mean, y = etlib_df$vl_cl_or_mean),color = "black", fill = "orange", shape = 8, size = 5.1) +
+geom_point(aes(x = etlib_df$dv_cl_or_mean, y = etlib_df$vl_cl_or_mean),color = "black", fill = "orange", shape = 21, size = 5) +
+
+ scale_x_continuous(limits = c(min(xvalues),max(xvalues)), breaks = seq(0,max(xvalues), by = 0.5)) + 
+  scale_y_continuous(breaks= seq(0,1,by=0.1)) + 
+  geom_vline(xintercept = 1, color = "red") +
+  xlab(expression(Exposure[correct])) + ylab("Exposure") +
+  theme_bw() + theme( 
+    axis.title.x = (element_text(size = 13)), axis.title.y = (element_text(size = 15)),
+    axis.text.x =  (element_text(size = 12)), axis.text.y =  (element_text(size = 15)), 
+    legend.title = element_text(size = 13),legend.position = "bottom", legend.text = element_text(size = 13),
+    plot.title=element_text(hjust = 0.5), plot.caption = element_text(hjust= 0.5, size = 11), plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
+
+data_prox <- etlib_df  %>% gather(key= subgroup, value = Prox, de_sq_bl_mean, dv_sq_bl_mean, de_cl_bl_mean, dv_cl_bl_mean, de_sq_or_mean, dv_sq_or_mean, de_cl_or_mean, dv_cl_or_mean) %>% mutate(
+  `segregation` = fct_relevel(fct_collapse(subgroup,"ethnics" = c("de_sq_bl_mean","de_cl_bl_mean","de_sq_or_mean","de_cl_or_mean"), "values" = c("dv_sq_bl_mean","dv_cl_bl_mean","dv_sq_or_mean","dv_cl_or_mean")),"ethnics"),
+ `orientation` = fct_relevel(fct_collapse(subgroup, "conservative" = c("de_sq_bl_mean","dv_sq_bl_mean","de_sq_or_mean","dv_sq_or_mean"), "liberal" = c("de_cl_bl_mean","dv_cl_bl_mean","de_cl_or_mean","dv_cl_or_mean")),"conservative" ),
+ `ethnia` = fct_relevel(fct_collapse(subgroup, "local" = c("de_sq_bl_mean","dv_sq_bl_mean","de_cl_bl_mean","dv_cl_bl_mean"),"minority" = c("de_sq_or_mean","dv_sq_or_mean","de_cl_or_mean","dv_cl_or_mean")), "local"))
+
+prox_pic <- ggplot(data = data_prox, aes(x = eth_lib_min, y = Prox, linetype = `segregation` , fill = `ethnia`,  shape = `orientation`)) + geom_line(aes(color = `ethnia`))  +  geom_point(color = "black", size = 4) +
+ scale_x_discrete(limits=c(seq(0,20 ,by = 1))) + scale_y_continuous(limits=c(min(data_prox$Prox),max(data_prox$Prox)), breaks=seq(0,max(data_prox$Prox),by=0.50)) +
+ facet_wrap(~ circle_orange, dir = "v", labeller = labeller(circle_orange = circle_orange.labs)) +
+    geom_vline(xintercept = 0, color = "red") +  geom_hline(yintercept = 1, color = "red") +
+  scale_linetype_manual(values=c("solid","dashed"), labels = c("ethnic","value"), guide = guide_legend(title = "Segregation", order = 1)) +
+  scale_fill_manual(values = c("blue","darkorange")) + 
+   scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
+  scale_shape_manual(values = c(22,21), guide = guide_legend(title="Value" ,override.aes = list(size = 3), order = 3)) +
+  guides(fill = FALSE) +
+  xlab(xlab_t) + ylab(expression(Exposure[correct])) + 
+  theme_bw() +  theme( 
+    axis.title.x = (element_text(size = 13)), axis.title.y = (element_text(size = 15)),
+    axis.text.x =  (element_text(size = 12)), axis.text.y =  (element_text(size = 15)), 
+    strip.text = element_text(size=13),
+    legend.title = element_text(size = 13),legend.position = "bottom", legend.text = element_text(size = 14),
+    plot.title=element_text(hjust = 0.5), plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
+
+#, plot.caption = element_text(hjust= 0.5, size = 11)
+ggpubr::ggarrange(prox_pic, expo_pic, common.legend = TRUE, legend = "bottom", widths = c(1.3,1))
+
+ggsave(plotname,plot = last_plot(),
+  device = NULL,path = NULL,
+  scale = 1,
+  width = 12,
+  height = 9,
+  units = c("in", "cm", "mm"),
+  dpi = 300,
+  limitsize = FALSE)
+
+```
+
+```{r asym_ALL, fig.width=30, fig.cap="Fig. 16 Baseline asymmetric conditions, dominant preferene ==  secondary preference", echo=FALSE}
+
+# database filter
+excl <- names(asym_all) %in% c("run", "density","step")
+dataset_sa <- asym_all[!excl] %>% group_by(dominant,circle_orange,circle_blue,fraction_blue) %>% summarise_all(c("mean"= mean,"sd"= sd))
+
+xlab_t <- "ß dominant = ß secondary"
+
+row_exp <- c("\\multicolumn{17}{|c|}{Ethnic asymmetric condition: Exposure}  \\\\\\hline\n",
+   "Preference &  \\multicolumn{8}{|c|}{Ethnic Exposure} & \\multicolumn{8}{|c|}{Value Exposure}   \\\\\\hline\n",
+  "& \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  & \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  \\\\\n",
+"$\\beta$ sec = $\\beta$ doom  & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
+& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
+& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal}\\\\\n",
+" & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD\\\\\n")
+
+row_prox <- c("\\multicolumn{17}{|c|}{Ethnic Asymmetric condition: Spatial Proximity}  \\\\\\hline\n",
+   "Preference &  \\multicolumn{8}{|c|}{Ethnic Proximity} & \\multicolumn{8}{|c|}{Value Proximity}   \\\\\\hline\n",
+  "& \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  & \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  \\\\\n",
+"$\\beta$ sec = $\\beta$ doom   & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
+& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
+& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal}\\\\\n",
+" & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD\\\\\n")
+
+tablerb_expname <- "latex/asym_all_rb_exp.tex"
+tablerb_proxname <- "latex/asym_all_rb_prox.tex"
+
+plotname <- "images/asym_all.jpg"
+
+# graph
+
+data_exp <- dataset_sa %>% gather(key= subgroup, value = Expo, et_sq_bl_mean, vl_sq_bl_mean, et_cl_bl_mean, vl_cl_bl_mean, et_sq_or_mean, vl_sq_or_mean, et_cl_or_mean, vl_cl_or_mean) %>% mutate(
+  `segregation` = fct_relevel(fct_collapse(subgroup,"ethnics" = c("et_sq_bl_mean","et_cl_bl_mean","et_sq_or_mean","et_cl_or_mean"), "values" = c("vl_sq_bl_mean","vl_cl_bl_mean","vl_sq_or_mean","vl_cl_or_mean")),"ethnics"),
+ `orientation` = fct_relevel(fct_collapse(subgroup, "conservative" = c("et_sq_bl_mean","vl_sq_bl_mean","et_sq_or_mean","vl_sq_or_mean"), "liberal" = c("et_cl_bl_mean","vl_cl_bl_mean","et_cl_or_mean","vl_cl_or_mean")),"conservative" ),
+ `ethnia` = fct_relevel(fct_collapse(subgroup, "local" = c("et_sq_bl_mean","vl_sq_bl_mean","et_cl_bl_mean","vl_cl_bl_mean"),"minority" = c("et_sq_or_mean","vl_sq_or_mean","et_cl_or_mean","vl_cl_or_mean")), "local"))
+
+fig_exp <- ggplot(data = data_exp, aes(x = dominant, y = Expo, linetype = `segregation` , fill = `ethnia`,  shape = `orientation`)) + geom_line(aes(color = `ethnia`))  +  geom_point(color = "black", size = 4) +
+ scale_x_discrete(limits=c(seq(0,20 ,by = 1))) + scale_y_continuous(limits=c(0,1), breaks=seq(0,1,by=0.10)) +
   geom_vline(xintercept = 20, color = "red") +
-
-  scale_linetype_manual(values=c("solid","dashed"), labels = c("ethnic","value"), guide = guide_legend(title = "Segregation", order = 1)) +
-  scale_fill_manual(values = c("blue","darkorange")) + 
-  scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
-  scale_shape_manual(values = c(22,21), guide = guide_legend(title="Value" ,override.aes = list(size = 3), order = 3)) +
-  guides(fill = FALSE) +
-  xlab(xlab_t) + ylab("Spatial Proximity") + 
-  theme_bw() +  theme( axis.title.x = (element_text(size = 15)), axis.title.y = (element_text(size = 15)), axis.text.x =  (element_text(size = 12)),axis.text.y =  (element_text(size = 15)), legend.title = element_text(size = 13) ,legend.text = element_text(size = 13),plot.title=element_text(hjust = 0.5)) + theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
-
-# ggsave("images/val_lib_loc50.jpg",plot = fig_prox,
-#   device = NULL,path = NULL, 
-#   scale = 1,
-#   width = 8,
-#   height = 6,
-#   units = c("in", "cm", "mm"),
-#   dpi = 300,
-#   limitsize = FALSE)
-
-# database filter
-excl <- names(sa_asym) %in% c("run", "ID","density","step","eth_lib_loc","val_con_loc","eth_lib_min","val_con_min")
-dataset_sa <- sa_asym[!excl] %>% filter(eth_con_loc   == 20, val_lib_loc  == 20, val_lib_min == 20)  %>% 
- filter(circle_orange == 50) %>%
-  group_by(eth_con_min,fraction_blue,circle_blue, circle_orange) %>% summarise_all(c("mean"= mean,"sd"= sd))
-
-xlab_t <- "ß ethnic conservative minority"
+  scale_linetype_manual(values=c("solid","dashed"), labels = c("ethnic","value"), guide = guide_legend(title = "Segregation", order = 1)) +
+  scale_fill_manual(values = c("blue","darkorange")) + 
+  scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
+  scale_shape_manual(values = c(22,21), guide = guide_legend(title="Value" ,override.aes = list(size = 3), order = 3)) +
+  guides(fill = FALSE) +
+  xlab("") + ylab("Exposure") + 
+  theme_bw() +  theme( axis.title.x  = element_blank(), axis.title.y = (element_text(size = 15)), axis.text.x  = (element_text(size = 10)) ,axis.text.y =  (element_text(size = 15)), legend.title = element_text(size = 13) ,legend.text = element_text(size = 13), plot.title=element_text(hjust = 0.5)) + theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
+
+tablerb_exp <- xtable(dataset_sa[,c("dominant","et_sq_bl_mean","et_sq_bl_sd","et_cl_bl_mean","et_cl_bl_sd","et_sq_or_mean","et_sq_or_sd","et_cl_or_mean","et_cl_or_sd","vl_sq_bl_mean","vl_sq_bl_sd","vl_cl_bl_mean","vl_cl_bl_sd","vl_sq_or_mean","vl_sq_or_sd","vl_cl_or_mean","vl_cl_or_sd")], digits = 3)
+align(tablerb_exp) <- "c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|"
+
+addtorow <- list()
+addtorow$pos <- list(0, 0,0,0,0)
+addtorow$command <-  row_exp
+
+print(tablerb_exp,type = "latex", file = tablerb_expname, include.rownames=FALSE, add.to.row = addtorow, include.colnames = FALSE, latex.environments = "center")
+
+## Spatial proximity baseline asymmetric
 
@@
 
-prox_eth_con_min <- ggplot(data = data_prox, aes(x = eth_con_min, y = Prox, linetype = `segregation` , fill = `ethnia`,  shape = `orientation`)) + geom_line(aes(color = `ethnia`))  +  geom_point(color = "black", size = 4) +
- scale_x_discrete(limits=c(seq(0,20 ,by = 1)))  + scale_y_continuous(limits=c(min(data_prox$Prox),5), breaks=seq(0,5,by=0.50)) +
-  #    facet_wrap(~ circle_orange, labeller = labeller(circle_orange = circle_orange.labs)) +
+fig_prox <- ggplot(data = data_prox, aes(x = dominant, y = Prox, linetype = `segregation` , fill = `ethnia`,  shape = `orientation`)) + geom_line(aes(color = `ethnia`))  +  geom_point(color = "black", size = 4) +
+ scale_x_discrete(limits=c(seq(0,20 ,by = 1))) + scale_y_continuous(limits=c(min(data_prox$Prox),max(data_prox$Prox)), breaks=seq(0,max(data_prox$Prox),by=0.50)) +
   geom_vline(xintercept = 20, color = "red") +
-
-  scale_linetype_manual(values=c("solid","dashed"), labels = c("ethnic","value"), guide = guide_legend(title = "Segregation", order = 1)) +
-  scale_fill_manual(values = c("blue","darkorange")) + 
-  scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
-  scale_shape_manual(values = c(22,21), guide = guide_legend(title="Value" ,override.aes = list(size = 3), order = 3)) +
-  guides(fill = FALSE) +
-  xlab(xlab_t) + ylab("Spatial Proximity") + 
-  theme_bw() +  theme( axis.title.x = (element_text(size = 15)), axis.title.y = (element_text(size = 15)), axis.text.x =  (element_text(size = 12)),axis.text.y =  (element_text(size = 15)), legend.title = element_text(size = 13) ,legend.text = element_text(size = 13),plot.title=element_text(hjust = 0.5)) + theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
-
-# ggsave("images/eth_con_min50.jpg",plot = fig_prox,
-#   device = NULL,path = NULL, 
-#   scale = 1,
-#   width = 8,
-#   height = 6,
-#   units = c("in", "cm", "mm"),
-#   dpi = 300,
-#   limitsize = FALSE)
+  scale_linetype_manual(values=c("solid","dashed"), labels = c("ethnic","value"), guide = guide_legend(title = "Segregation", order = 1)) +
+  scale_fill_manual(values = c("blue","darkorange")) + 
+  scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
+  scale_shape_manual(values = c(22,21), guide = guide_legend(title="Value" ,override.aes = list(size = 3), order = 3)) +
+  guides(fill = FALSE) +
+  xlab(xlab_t) + ylab(expression(Exposure[correct])) + 
+  theme_bw() +  theme( axis.title.x = (element_text(size = 15)), axis.title.y = (element_text(size = 15)), axis.text.x =  (element_text(size = 15)),axis.text.y =  (element_text(size = 15)), legend.title = element_text(size = 13) ,legend.text = element_text(size = 13), plot.title=element_text(hjust = 0.5)) + theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
+
+# robustness table
+
+tablerb_prox <- xtable(dataset_sa[,c("dominant","de_sq_bl_mean","de_sq_bl_sd","de_cl_bl_mean","de_cl_bl_sd","de_sq_or_mean","de_sq_or_sd","de_cl_or_mean","de_cl_or_sd","dv_sq_bl_mean","dv_sq_bl_sd","dv_cl_bl_mean","dv_cl_bl_sd","dv_sq_or_mean","dv_sq_or_sd","dv_cl_or_mean","dv_cl_or_sd")], digits = 3)
+align(tablerb_prox) <- "c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|"
+
+addtorow <- list()
+addtorow$pos <- list(0, 0,0,0,0)
+addtorow$command <-  row_prox
+print(tablerb_prox,type = "latex", file = tablerb_proxname , include.rownames=FALSE, add.to.row = addtorow, include.colnames = FALSE, latex.environments = "center")
+
+# combined image
+
+ggpubr::ggarrange(fig_exp,fig_prox, nrow = 2, ncol = 1, common.legend = TRUE, legend = "right")
+
+ggsave(plotname,plot = last_plot(),
+  device = NULL,path = NULL, 
+  scale = 1,
+  width = 8,
+  height = 6,
+  units = c("in", "cm", "mm"),
+  dpi = 300,
+  limitsize = FALSE)
+
+```
+
+```{r sa_etcnlc,  fig.cap="Fig. 17. Sensitivity ethnic conservative majority, asymmetric conditions", echo=FALSE}
 
@@
 excl <- names(sa_asym) %in% c("run", "ID","density","step","eth_lib_loc","val_con_loc","eth_lib_min","val_con_min")
-dataset_sa <- sa_asym[!excl] %>% filter(eth_con_loc   == 20, val_lib_loc  == 20, eth_con_min  == 20)  %>% 
- filter(circle_orange == 50) %>%
-  group_by(val_lib_min,fraction_blue,circle_blue, circle_orange) %>% summarise_all(c("mean"= mean,"sd"= sd))
-
-xlab_t <- "ß value liberal minority"
-
-# graph
+dataset_sa <- sa_asym[!excl] %>% filter(val_lib_loc   == 20,eth_con_min   == 20, val_lib_min == 20)  %>% 
+group_by(eth_con_loc ,fraction_blue,circle_blue, circle_orange) %>% summarise_all(c("mean"= mean,"sd"= sd))
+
+# image output location
+
+plotname <- "images/etcnlc.jpg"
+xlab_t <- "ß ethnic conservative local"
+
+xvalues <- c(dataset_sa$de_sq_bl_mean,dataset_sa$de_cl_bl_mean,dataset_sa$de_sq_or_mean,dataset_sa$de_cl_or_mean,
+       dataset_sa$dv_sq_bl_mean,dataset_sa$dv_cl_bl_mean,dataset_sa$dv_sq_or_mean,dataset_sa$dv_cl_or_mean)
+
+ expo_pic <-   ggplot(data = dataset_sa) + 
+  geom_point(aes(x = dataset_sa$de_sq_bl_mean, y = dataset_sa$et_sq_bl_mean),color = "black", fill = "blue", shape = 22, size = 5) +
+  geom_point(aes(x = dataset_sa$de_cl_bl_mean, y = dataset_sa$et_cl_bl_mean),color = "black",fill = "blue", shape = 21, size = 5) +
+  geom_point(aes(x = dataset_sa$de_sq_or_mean, y = dataset_sa$et_sq_or_mean),color = "black", fill = "orange", shape = 22, size = 5) +
+  geom_point(aes(x = dataset_sa$de_cl_or_mean, y = dataset_sa$et_cl_or_mean),color = "black", fill = "orange", shape = 21, size = 5) +
+
+  geom_point(aes(x = dataset_sa$dv_sq_bl_mean, y = dataset_sa$vl_sq_bl_mean),color = "black", fill = "blue", shape = 8, size = 5.1) + 
+   geom_point(aes(x = dataset_sa$dv_sq_bl_mean, y = dataset_sa$vl_sq_bl_mean),color = "black", fill = "blue", shape = 22, size = 5) +
+
+   geom_point(aes(x = dataset_sa$dv_cl_bl_mean, y = dataset_sa$vl_cl_bl_mean),color = "black",fill = "blue", shape = 8, size = 5.1) + 
+  geom_point(aes(x = dataset_sa$dv_cl_bl_mean, y = dataset_sa$vl_cl_bl_mean),color = "black",fill = "blue", shape = 21, size = 5) +
+
+    geom_point(aes(x = dataset_sa$dv_sq_or_mean, y = dataset_sa$vl_sq_or_mean),color = "black", fill = "orange", shape = 8, size = 5.1) +
+  geom_point(aes(x = dataset_sa$dv_sq_or_mean, y = dataset_sa$vl_sq_or_mean),color = "black", fill = "orange", shape = 22, size = 5) +
+
+  geom_point(aes(x = dataset_sa$dv_cl_or_mean, y = dataset_sa$vl_cl_or_mean),color = "black", fill = "orange", shape = 8, size = 5.1) +
+geom_point(aes(x = dataset_sa$dv_cl_or_mean, y = dataset_sa$vl_cl_or_mean),color = "black", fill = "orange", shape = 21, size = 5) +
+
+ scale_x_continuous(limits = c(min(xvalues),max(xvalues)), breaks = seq(0,max(xvalues), by = 0.5)) + 
+  scale_y_continuous(breaks= seq(0,1,by=0.1)) + 
+  geom_vline(xintercept = 1, color = "red") +
+   xlab(expression(Exposure[correct])) + ylab("Exposure") +
+  theme_bw() + theme( 
+    axis.title.x = (element_text(size = 13)), axis.title.y = (element_text(size = 15)),
+    axis.text.x =  (element_text(size = 12)), axis.text.y =  (element_text(size = 15)), 
+    legend.title = element_text(size = 13),legend.position = "bottom", legend.text = element_text(size = 13),
+    plot.title=element_text(hjust = 0.5), plot.caption = element_text(hjust= 0.5, size = 11), plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
 
@@
 
-prox_val_lib_min <-  ggplot(data = data_prox, aes(x = val_lib_min, y = Prox, linetype = `segregation` , fill = `ethnia`,  shape = `orientation`)) + geom_line(aes(color = `ethnia`))  +  geom_point(color = "black", size = 4) +
- scale_x_discrete(limits=c(seq(0,20 ,by = 1)))  + scale_y_continuous(limits=c(min(data_prox$Prox),5), breaks=seq(0,5,by=0.50)) +
-  #    facet_wrap(~ circle_orange, labeller = labeller(circle_orange = circle_orange.labs)) +
-    geom_vline(xintercept = 20, color = "red") +
-
-  scale_linetype_manual(values=c("solid","dashed"), labels = c("ethnic","value"), guide = guide_legend(title = "Segregation", order = 1)) +
-  scale_fill_manual(values = c("blue","darkorange")) + 
-  scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
-  scale_shape_manual(values = c(22,21), guide = guide_legend(title="Value" ,override.aes = list(size = 3), order = 3)) +
-  guides(fill = FALSE) +
-  xlab(xlab_t) + ylab("Spatial Proximity") + 
-  theme_bw() +  theme( axis.title.x = (element_text(size = 15)), axis.title.y = (element_text(size = 15)), axis.text.x =  (element_text(size = 12)),axis.text.y =  (element_text(size = 15)), legend.title = element_text(size = 13) ,legend.text = element_text(size = 13),plot.title=element_text(hjust = 0.5)) + theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
-
-ggpubr::ggarrange(prox_eth_con_loc,prox_val_lib_loc,prox_eth_con_min,prox_val_lib_min, nrow = 2, ncol = 2, common.legend = TRUE, legend = "bottom")
-
-ggsave("images/sa_asym_bt.jpg",plot = last_plot(),
+# plot ethnic exposure corrected
+
+prox_pic <- ggplot(data = data_prox, aes(x = eth_con_loc, y = Prox, linetype = `segregation` , fill = `ethnia`,  shape = `orientation`)) + geom_line(aes(color = `ethnia`))  +  geom_point(color = "black", size = 4) +
+ scale_x_discrete(limits=c(seq(0,20 ,by = 1))) + scale_y_continuous(limits=c(min(data_prox$Prox),max(data_prox$Prox)), breaks=seq(0,max(data_prox$Prox),by=0.50)) +
+ facet_wrap(~ circle_orange, dir = "v", labeller = labeller(circle_orange = circle_orange.labs)) +
+    geom_vline(xintercept = 20, color = "red") +  geom_hline(yintercept = 1, color = "red") +
+  scale_linetype_manual(values=c("solid","dashed"), labels = c("ethnic","value"), guide = guide_legend(title = "Segregation", order = 1)) +
+  scale_fill_manual(values = c("blue","darkorange")) + 
+   scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
+  scale_shape_manual(values = c(22,21), guide = guide_legend(title="Value" ,override.aes = list(size = 3), order = 3)) +
+  guides(fill = FALSE) +
+  xlab(xlab_t) + ylab(expression(Exposure[correct])) + 
+  theme_bw() +  theme( 
+    axis.title.x = (element_text(size = 13)), axis.title.y = (element_text(size = 15)),
+    axis.text.x =  (element_text(size = 12)), axis.text.y =  (element_text(size = 15)), 
+    strip.text = element_text(size=13),
+    legend.title = element_text(size = 13),legend.position = "bottom", legend.text = element_text(size = 14),
+    plot.title=element_text(hjust = 0.5), plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
+
+#, plot.caption = element_text(hjust= 0.5, size = 11)
+ggpubr::ggarrange(prox_pic, expo_pic, common.legend = TRUE, legend = "bottom", widths = c(1.3,1))
+
+ggsave(plotname,plot = last_plot(),
   device = NULL,path = NULL,
   scale = 1,
-  width = 11,
-  height = 8,
+  width = 12,
+  height = 9,
   units = c("in", "cm", "mm"),
@@
   limitsize = FALSE)
-
-```
-
-```{r sa_dom_50exp, fig.width=30, fig.cap="exposure Sensitivity ethnic conservative local, baseline asymmetric conditions", echo=FALSE}
+```
+
+```{r sa_etcnmn,  fig.cap="Fig. 18: Sensitivity ethnic conservative minority, asymmetric conditions", echo=FALSE}
+
+# database filter
+excl <- names(sa_asym) %in% c("run", "ID","density","step","eth_lib_loc","val_con_loc","eth_lib_min","val_con_min")
+dataset_sa <- sa_asym[!excl] %>% filter(eth_con_loc  == 20,val_lib_loc == 20,val_lib_min == 20)  %>% 
+group_by(eth_con_min ,fraction_blue,circle_blue, circle_orange) %>% summarise_all(c("mean"= mean,"sd"= sd))
+
+# image folder output
+
+plotname <- "images/etcnmn.jpg"
+xlab_t <- "ß ethnic conservative minority"
+
+xvalues <- c(dataset_sa$de_sq_bl_mean,dataset_sa$de_cl_bl_mean,dataset_sa$de_sq_or_mean,dataset_sa$de_cl_or_mean,
+       dataset_sa$dv_sq_bl_mean,dataset_sa$dv_cl_bl_mean,dataset_sa$dv_sq_or_mean,dataset_sa$dv_cl_or_mean)
+
+ expo_pic <-   ggplot(data = dataset_sa) + 
+  geom_point(aes(x = dataset_sa$de_sq_bl_mean, y = dataset_sa$et_sq_bl_mean),color = "black", fill = "blue", shape = 22, size = 5) +
+  geom_point(aes(x = dataset_sa$de_cl_bl_mean, y = dataset_sa$et_cl_bl_mean),color = "black",fill = "blue", shape = 21, size = 5) +
+  geom_point(aes(x = dataset_sa$de_sq_or_mean, y = dataset_sa$et_sq_or_mean),color = "black", fill = "orange", shape = 22, size = 5) +
+  geom_point(aes(x = dataset_sa$de_cl_or_mean, y = dataset_sa$et_cl_or_mean),color = "black", fill = "orange", shape = 21, size = 5) +
+
+  geom_point(aes(x = dataset_sa$dv_sq_bl_mean, y = dataset_sa$vl_sq_bl_mean),color = "black", fill = "blue", shape = 8, size = 5.1) + 
+   geom_point(aes(x = dataset_sa$dv_sq_bl_mean, y = dataset_sa$vl_sq_bl_mean),color = "black", fill = "blue", shape = 22, size = 5) +
+
+   geom_point(aes(x = dataset_sa$dv_cl_bl_mean, y = dataset_sa$vl_cl_bl_mean),color = "black",fill = "blue", shape = 8, size = 5.1) + 
+  geom_point(aes(x = dataset_sa$dv_cl_bl_mean, y = dataset_sa$vl_cl_bl_mean),color = "black",fill = "blue", shape = 21, size = 5) +
+
+    geom_point(aes(x = dataset_sa$dv_sq_or_mean, y = dataset_sa$vl_sq_or_mean),color = "black", fill = "orange", shape = 8, size = 5.1) +
+  geom_point(aes(x = dataset_sa$dv_sq_or_mean, y = dataset_sa$vl_sq_or_mean),color = "black", fill = "orange", shape = 22, size = 5) +
+
+  geom_point(aes(x = dataset_sa$dv_cl_or_mean, y = dataset_sa$vl_cl_or_mean),color = "black", fill = "orange", shape = 8, size = 5.1) +
+geom_point(aes(x = dataset_sa$dv_cl_or_mean, y = dataset_sa$vl_cl_or_mean),color = "black", fill = "orange", shape = 21, size = 5) +
+
+ scale_x_continuous(limits = c(min(xvalues),max(xvalues)), breaks = seq(0,max(xvalues), by = 0.5)) + 
+  scale_y_continuous(breaks= seq(0,1,by=0.1)) + 
+  geom_vline(xintercept = 1, color = "red") +
+   xlab(expression(Exposure[correct])) + ylab("Exposure") +
+  theme_bw() + theme( 
+    axis.title.x = (element_text(size = 13)), axis.title.y = (element_text(size = 15)),
+    axis.text.x =  (element_text(size = 12)), axis.text.y =  (element_text(size = 15)), 
+    legend.title = element_text(size = 13),legend.position = "bottom", legend.text = element_text(size = 13),
+    plot.title=element_text(hjust = 0.5), plot.caption = element_text(hjust= 0.5, size = 11), plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
+
+data_prox <- dataset_sa  %>% gather(key= subgroup, value = Prox, de_sq_bl_mean, dv_sq_bl_mean, de_cl_bl_mean, dv_cl_bl_mean, de_sq_or_mean, dv_sq_or_mean, de_cl_or_mean, dv_cl_or_mean) %>% mutate(
+  `segregation` = fct_relevel(fct_collapse(subgroup,"ethnics" = c("de_sq_bl_mean","de_cl_bl_mean","de_sq_or_mean","de_cl_or_mean"), "values" = c("dv_sq_bl_mean","dv_cl_bl_mean","dv_sq_or_mean","dv_cl_or_mean")),"ethnics"),
+ `orientation` = fct_relevel(fct_collapse(subgroup, "conservative" = c("de_sq_bl_mean","dv_sq_bl_mean","de_sq_or_mean","dv_sq_or_mean"), "liberal" = c("de_cl_bl_mean","dv_cl_bl_mean","de_cl_or_mean","dv_cl_or_mean")),"conservative" ),
+ `ethnia` = fct_relevel(fct_collapse(subgroup, "local" = c("de_sq_bl_mean","dv_sq_bl_mean","de_cl_bl_mean","dv_cl_bl_mean"),"minority" = c("de_sq_or_mean","dv_sq_or_mean","de_cl_or_mean","dv_cl_or_mean")), "local"))
+
+prox_pic <- ggplot(data = data_prox, aes(x = eth_con_min, y = Prox, linetype = `segregation` , fill = `ethnia`,  shape = `orientation`)) + geom_line(aes(color = `ethnia`))  +  geom_point(color = "black", size = 4) +
+ scale_x_discrete(limits=c(seq(0,20 ,by = 1))) + scale_y_continuous(limits=c(min(data_prox$Prox),max(data_prox$Prox)), breaks=seq(0,max(data_prox$Prox),by=0.50)) +
+ facet_wrap(~ circle_orange, dir = "v", labeller = labeller(circle_orange = circle_orange.labs)) +
+    geom_vline(xintercept = 20, color = "red") +  geom_hline(yintercept = 1, color = "red") +
+  scale_linetype_manual(values=c("solid","dashed"), labels = c("ethnic","value"), guide = guide_legend(title = "Segregation", order = 1)) +
+  scale_fill_manual(values = c("blue","darkorange")) + 
+   scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
+  scale_shape_manual(values = c(22,21), guide = guide_legend(title="Value" ,override.aes = list(size = 3), order = 3)) +
+  guides(fill = FALSE) +
+  xlab(xlab_t) + ylab(expression(Exposure[correct])) + 
+  theme_bw() +  theme( 
+    axis.title.x = (element_text(size = 13)), axis.title.y = (element_text(size = 15)),
+    axis.text.x =  (element_text(size = 12)), axis.text.y =  (element_text(size = 15)), 
+    strip.text = element_text(size=13),
+    legend.title = element_text(size = 13),legend.position = "bottom", legend.text = element_text(size = 14),
+    plot.title=element_text(hjust = 0.5), plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
+
+#, plot.caption = element_text(hjust= 0.5, size = 11)
+ggpubr::ggarrange(prox_pic, expo_pic, common.legend = TRUE, legend = "bottom", widths = c(1.3,1))
+
+ggsave(plotname,plot = last_plot(),
+  device = NULL,path = NULL,
+  scale = 1,
+  width = 12,
+  height = 9,
+  units = c("in", "cm", "mm"),
+  dpi = 300,
+  limitsize = FALSE)
+```
+
+```{r sa_dom_50exp, fig.width=30, fig.cap="NO in text: sensitivity each group-type, exposure index", echo=FALSE}
 ## NOT INCLUDED IN THE PAPER
@@
   guides(fill = FALSE) +
-  xlab(xlab_t) + ylab("Exposure") + 
+  xlab(xlab_t) + ylab(expression(Exposure[correct])) + 
   theme_bw() +  theme( axis.title.x = (element_text(size = 15)), axis.title.y = (element_text(size = 15)), axis.text.x =  (element_text(size = 12)),axis.text.y =  (element_text(size = 15)), legend.title = element_text(size = 13) ,legend.text = element_text(size = 13),plot.title=element_text(hjust = 0.5)) + theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
@@
 
-```{r sa_vllblc,  fig.cap="Sensitivity proximity value liberal locals, distribution liberals", echo=FALSE}
-
-# database filter
+# Table Robustness Analysis
+
+```{r sa_etcnlc_table,  fig.cap="Tab. 11: Sensitivity ethnic conservative majority, asymmetric conditions", echo=FALSE}
+
+# database filter
+
+excl <- names(sa_asym) %in% c("run", "ID","density","step","eth_lib_loc","val_con_loc","eth_lib_min","val_con_min")
+dataset_sa <- sa_asym[!excl] %>% filter(val_lib_min == 20,  val_lib_loc == 20, eth_con_min == 20)  %>% 
+group_by(eth_con_loc ,fraction_blue,circle_blue, circle_orange) %>% summarise_all(c("mean"= mean,"sd"= sd))
+
+# latex different distributions of liberals minority
+
+df_etcnlc50 <- dataset_sa %>%  filter(circle_orange == 50)
+etcnlc50 <- xtable(df_etcnlc50[,c("eth_con_loc","de_sq_bl_mean","de_sq_bl_sd","de_cl_bl_mean","de_cl_bl_sd","de_sq_or_mean","de_sq_or_sd","de_cl_or_mean","de_cl_or_sd","dv_sq_bl_mean","dv_sq_bl_sd","dv_cl_bl_mean","dv_cl_bl_sd","dv_sq_or_mean","dv_sq_or_sd","dv_cl_or_mean","dv_cl_or_sd")], digits = 3)
+align(etcnlc50) <- "c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|"
+addtorow <- list()
+addtorow$pos <- list(0, 0,0,0,0)
+addtorow$command <-  c("\\multicolumn{17}{|c|}{Ethnic Asymmetry, $50 \\%$ Liberal Migrants: Spatial Proximity}  \\\\\\hline\n",
+   "Preference &  \\multicolumn{8}{|c|}{Ethnic Proximity} & \\multicolumn{8}{|c|}{Value Proximity}   \\\\\\hline\n",
+  "& \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  & \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  \\\\\n",
+"$\\beta$ ethnic & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
+& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
+& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal}\\\\\n",
+"conservative local & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD\\\\\n")
+print(etcnlc50,type = "latex", file = "latex/etcnlc50.tex"  , include.rownames=FALSE, add.to.row = addtorow, include.colnames = FALSE, latex.environments = "center")
+
+df_etcnlc20 <- dataset_sa %>%  filter(circle_orange == 20)
+etcnlc20 <- xtable(df_etcnlc20[,c("eth_con_loc","de_sq_bl_mean","de_sq_bl_sd","de_cl_bl_mean","de_cl_bl_sd","de_sq_or_mean","de_sq_or_sd","de_cl_or_mean","de_cl_or_sd","dv_sq_bl_mean","dv_sq_bl_sd","dv_cl_bl_mean","dv_cl_bl_sd","dv_sq_or_mean","dv_sq_or_sd","dv_cl_or_mean","dv_cl_or_sd")], digits = 3)
+align(etcnlc20) <- "c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|"
+addtorow <- list()
+addtorow$pos <- list(0, 0,0,0,0)
+addtorow$command <- c("\\multicolumn{17}{|c|}{Ethnic Asymmetry, $20 \\%$ Liberal Migrants: Spatial Proximity}  \\\\\\hline\n",
+   "Preference &  \\multicolumn{8}{|c|}{Ethnic Proximity} & \\multicolumn{8}{|c|}{Value Proximity}   \\\\\\hline\n",
+  "& \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  & \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  \\\\\n",
+"$\\beta$ ethnic & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
+& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
+& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal}\\\\\n",
+"conservative local & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD\\\\\n")
+print(etcnlc20,type = "latex", file = "latex/etcnlc20.tex" , include.rownames=FALSE, add.to.row = addtorow, include.colnames = FALSE, latex.environments = "center")
+
+df_etcnlc80 <- dataset_sa %>%  filter(circle_orange == 80)
+etcnlc80 <- xtable(df_etcnlc80[,c("eth_con_loc","de_sq_bl_mean","de_sq_bl_sd","de_cl_bl_mean","de_cl_bl_sd","de_sq_or_mean","de_sq_or_sd","de_cl_or_mean","de_cl_or_sd","dv_sq_bl_mean","dv_sq_bl_sd","dv_cl_bl_mean","dv_cl_bl_sd","dv_sq_or_mean","dv_sq_or_sd","dv_cl_or_mean","dv_cl_or_sd")], digits = 3)
+align(etcnlc80) <- "c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|"
+addtorow <- list()
+addtorow$pos <- list(0, 0,0,0,0)
+addtorow$command <- c("\\multicolumn{17}{|c|}{Ethnic Asymmetry, $80 \\%$ Liberal Migrants: Spatial Proximity}  \\\\\\hline\n",
+   "Preference &  \\multicolumn{8}{|c|}{Ethnic Proximity} & \\multicolumn{8}{|c|}{Value Proximity}   \\\\\\hline\n",
+  "& \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  & \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  \\\\\n",
+"$\\beta$ ethnic & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
+& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
+& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal}\\\\\n",
+"conservative local & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD\\\\\n")
+print(etcnlc80,type = "latex", file = "latex/etcnlc80.tex" , include.rownames=FALSE, add.to.row = addtorow, include.colnames = FALSE, latex.environments = "center")
+
+```
+
+```{r sa_etcnmn_table,  fig.cap="Tab. 12: Ethnic conservative minority, asymmetric conditions", echo=FALSE}
+
+# database filter
+
+excl <- names(sa_asym) %in% c("run", "ID","density","step","eth_lib_loc","val_con_loc","eth_lib_min","val_con_min")
+dataset_sa <- sa_asym[!excl] %>% filter(val_lib_min == 20,  val_lib_loc == 20, eth_con_loc == 20)  %>% 
+group_by(eth_con_min ,fraction_blue,circle_blue, circle_orange) %>% summarise_all(c("mean"= mean,"sd"= sd))
+
+df_etcnmn50 <- dataset_sa %>%  filter(circle_orange == 50)
+etcnmn50 <- xtable(df_etcnmn50[,c("eth_con_min","de_sq_bl_mean","de_sq_bl_sd","de_cl_bl_mean","de_cl_bl_sd","de_sq_or_mean","de_sq_or_sd","de_cl_or_mean","de_cl_or_sd","dv_sq_bl_mean","dv_sq_bl_sd","dv_cl_bl_mean","dv_cl_bl_sd","dv_sq_or_mean","dv_sq_or_sd","dv_cl_or_mean","dv_cl_or_sd")], digits = 3)
+align(etcnmn50) <- "c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|"
+addtorow <- list()
+addtorow$pos <- list(0, 0,0,0,0)
+addtorow$command <-  c("\\multicolumn{17}{|c|}{Ethnic Asymmetry, $50 \\%$ Liberal Migrants: Spatial Proximity}  \\\\\\hline\n",
+   "Preference &  \\multicolumn{8}{|c|}{Ethnic Proximity} & \\multicolumn{8}{|c|}{Value Proximity}   \\\\\\hline\n",
+  "& \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  & \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  \\\\\n",
+"$\\beta$ ethnic & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
+& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
+& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal}\\\\\n",
+"conservative minority & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD\\\\\n")
+print(etcnmn50,type = "latex", file = "latex/etcnmn50.tex"  , include.rownames=FALSE, add.to.row = addtorow, include.colnames = FALSE, latex.environments = "center")
+
+df_etcnmn20 <- dataset_sa %>%  filter(circle_orange == 20)
+etcnmn20 <- xtable(df_etcnmn20[,c("eth_con_min","de_sq_bl_mean","de_sq_bl_sd","de_cl_bl_mean","de_cl_bl_sd","de_sq_or_mean","de_sq_or_sd","de_cl_or_mean","de_cl_or_sd","dv_sq_bl_mean","dv_sq_bl_sd","dv_cl_bl_mean","dv_cl_bl_sd","dv_sq_or_mean","dv_sq_or_sd","dv_cl_or_mean","dv_cl_or_sd")], digits = 3)
+align(etcnmn20) <- "c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|"
+addtorow <- list()
+addtorow$pos <- list(0, 0,0,0,0)
+addtorow$command <- c("\\multicolumn{17}{|c|}{Ethnic Asymmetry, $20 \\%$ Liberal Migrants: Spatial Proximity}  \\\\\\hline\n",
+   "Preference &  \\multicolumn{8}{|c|}{Ethnic Proximity} & \\multicolumn{8}{|c|}{Value Proximity}   \\\\\\hline\n",
+  "& \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  & \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  \\\\\n",
+"$\\beta$ ethnic & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
+& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
+& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal}\\\\\n",
+"conservative minority & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD\\\\\n")
+print(etcnmn20,type = "latex", file = "latex/etcnmn20.tex" , include.rownames=FALSE, add.to.row = addtorow, include.colnames = FALSE, latex.environments = "center")
+
+df_etcnmn80 <- dataset_sa %>%  filter(circle_orange == 80)
+etcnmn80 <- xtable(df_etcnmn80[,c("eth_con_min","de_sq_bl_mean","de_sq_bl_sd","de_cl_bl_mean","de_cl_bl_sd","de_sq_or_mean","de_sq_or_sd","de_cl_or_mean","de_cl_or_sd","dv_sq_bl_mean","dv_sq_bl_sd","dv_cl_bl_mean","dv_cl_bl_sd","dv_sq_or_mean","dv_sq_or_sd","dv_cl_or_mean","dv_cl_or_sd")], digits = 3)
+align(etcnmn80) <- "c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|"
+addtorow <- list()
+addtorow$pos <- list(0, 0,0,0,0)
+addtorow$command <- c("\\multicolumn{17}{|c|}{Ethnic Asymmetry, $80 \\%$ Liberal Migrants: Spatial Proximity}  \\\\\\hline\n",
+   "Preference &  \\multicolumn{8}{|c|}{Ethnic Proximity} & \\multicolumn{8}{|c|}{Value Proximity}   \\\\\\hline\n",
+  "& \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  & \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  \\\\\n",
+"$\\beta$ ethnic & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
+& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
+& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal}\\\\\n",
+"conservative minority & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD\\\\\n")
+print(etcnmn80,type = "latex", file = "latex/etcnmn80.tex" , include.rownames=FALSE, add.to.row = addtorow, include.colnames = FALSE, latex.environments = "center")
+
+# test_all <- rbind(etcnmn20,etcnmn50,etcnmn80)
+# print(test_all, type = "latex", file = "latex/test_all.tex",include.rownames=FALSE, add.to.row = addtorow, include.colnames = FALSE, latex.environments = "center")
+
+```
+
+```{r sa_vllblc_table,  fig.cap="Tab. 13: Sensitivity value liberals majority - exposure correct, asymmetric conditions", echo=FALSE}
+
+# database filter
+
 excl <- names(sa_asym) %in% c("run", "ID","density","step","eth_lib_loc","val_con_loc","eth_lib_min","val_con_min")
@@
 
-plotname <- "images/vllblc.jpg"
-xlab_t <- "ß value liberal local"
-
-xvalues <- c(dataset_sa$de_sq_bl_mean,dataset_sa$de_cl_bl_mean,dataset_sa$de_sq_or_mean,dataset_sa$de_cl_or_mean,
-       dataset_sa$dv_sq_bl_mean,dataset_sa$dv_cl_bl_mean,dataset_sa$dv_sq_or_mean,dataset_sa$dv_cl_or_mean)
-
- expo_pic <-   ggplot(data = dataset_sa) + 
-  geom_point(aes(x = dataset_sa$de_sq_bl_mean, y = dataset_sa$et_sq_bl_mean),color = "black", fill = "blue", shape = 22, size = 5) +
-  geom_point(aes(x = dataset_sa$de_cl_bl_mean, y = dataset_sa$et_cl_bl_mean),color = "black",fill = "blue", shape = 21, size = 5) +
-  geom_point(aes(x = dataset_sa$de_sq_or_mean, y = dataset_sa$et_sq_or_mean),color = "black", fill = "orange", shape = 22, size = 5) +
-  geom_point(aes(x = dataset_sa$de_cl_or_mean, y = dataset_sa$et_cl_or_mean),color = "black", fill = "orange", shape = 21, size = 5) +
-
-  geom_point(aes(x = dataset_sa$dv_sq_bl_mean, y = dataset_sa$vl_sq_bl_mean),color = "black", fill = "blue", shape = 8, size = 5.1) + 
-   geom_point(aes(x = dataset_sa$dv_sq_bl_mean, y = dataset_sa$vl_sq_bl_mean),color = "black", fill = "blue", shape = 22, size = 5) +
-
-   geom_point(aes(x = dataset_sa$dv_cl_bl_mean, y = dataset_sa$vl_cl_bl_mean),color = "black",fill = "blue", shape = 8, size = 5.1) + 
-  geom_point(aes(x = dataset_sa$dv_cl_bl_mean, y = dataset_sa$vl_cl_bl_mean),color = "black",fill = "blue", shape = 21, size = 5) +
-
-    geom_point(aes(x = dataset_sa$dv_sq_or_mean, y = dataset_sa$vl_sq_or_mean),color = "black", fill = "orange", shape = 8, size = 5.1) +
-  geom_point(aes(x = dataset_sa$dv_sq_or_mean, y = dataset_sa$vl_sq_or_mean),color = "black", fill = "orange", shape = 22, size = 5) +
-
-  geom_point(aes(x = dataset_sa$dv_cl_or_mean, y = dataset_sa$vl_cl_or_mean),color = "black", fill = "orange", shape = 8, size = 5.1) +
-geom_point(aes(x = dataset_sa$dv_cl_or_mean, y = dataset_sa$vl_cl_or_mean),color = "black", fill = "orange", shape = 21, size = 5) +
-
- scale_x_continuous(limits = c(min(xvalues),max(xvalues)), breaks = seq(0,max(xvalues), by = 0.5)) + 
-  scale_y_continuous(breaks= seq(0,1,by=0.1)) + 
-  geom_vline(xintercept = 1, color = "red") +
-  xlab("Spatial proximity") + ylab("Exposure") +
-  theme_bw() + theme( 
-    axis.title.x = (element_text(size = 13)), axis.title.y = (element_text(size = 15)),
-    axis.text.x =  (element_text(size = 12)), axis.text.y =  (element_text(size = 15)), 
-    legend.title = element_text(size = 13),legend.position = "bottom", legend.text = element_text(size = 13),
-    plot.title=element_text(hjust = 0.5), plot.caption = element_text(hjust= 0.5, size = 11), plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
-
-data_prox <- dataset_sa  %>% gather(key= subgroup, value = Prox, de_sq_bl_mean, dv_sq_bl_mean, de_cl_bl_mean, dv_cl_bl_mean, de_sq_or_mean, dv_sq_or_mean, de_cl_or_mean, dv_cl_or_mean) %>% mutate(
-  `segregation` = fct_relevel(fct_collapse(subgroup,"ethnics" = c("de_sq_bl_mean","de_cl_bl_mean","de_sq_or_mean","de_cl_or_mean"), "values" = c("dv_sq_bl_mean","dv_cl_bl_mean","dv_sq_or_mean","dv_cl_or_mean")),"ethnics"),
- `orientation` = fct_relevel(fct_collapse(subgroup, "conservative" = c("de_sq_bl_mean","dv_sq_bl_mean","de_sq_or_mean","dv_sq_or_mean"), "liberal" = c("de_cl_bl_mean","dv_cl_bl_mean","de_cl_or_mean","dv_cl_or_mean")),"conservative" ),
- `ethnia` = fct_relevel(fct_collapse(subgroup, "local" = c("de_sq_bl_mean","dv_sq_bl_mean","de_cl_bl_mean","dv_cl_bl_mean"),"minority" = c("de_sq_or_mean","dv_sq_or_mean","de_cl_or_mean","dv_cl_or_mean")), "local"))
-
-prox_pic <- ggplot(data = data_prox, aes(x = val_lib_loc, y = Prox, linetype = `segregation` , fill = `ethnia`,  shape = `orientation`)) + geom_line(aes(color = `ethnia`))  +  geom_point(color = "black", size = 4) +
- scale_x_discrete(limits=c(seq(0,20 ,by = 1))) + scale_y_continuous(limits=c(min(data_prox$Prox),max(data_prox$Prox)), breaks=seq(0,max(data_prox$Prox),by=0.50)) +
- facet_wrap(~ circle_orange, dir = "v", labeller = labeller(circle_orange = circle_orange.labs)) +
-    geom_vline(xintercept = 20, color = "red") +  geom_hline(yintercept = 1, color = "red") +
-  scale_linetype_manual(values=c("solid","dashed"), labels = c("ethnic","value"), guide = guide_legend(title = "Segregation", order = 1)) +
-  scale_fill_manual(values = c("blue","darkorange")) + 
-   scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
-  scale_shape_manual(values = c(22,21), guide = guide_legend(title="Value" ,override.aes = list(size = 3), order = 3)) +
-  guides(fill = FALSE) +
-  xlab(xlab_t) + ylab("Spatial Proximity") + 
-  theme_bw() +  theme( 
-    axis.title.x = (element_text(size = 13)), axis.title.y = (element_text(size = 15)),
-    axis.text.x =  (element_text(size = 12)), axis.text.y =  (element_text(size = 15)), 
-    strip.text = element_text(size=13),
-    legend.title = element_text(size = 13),legend.position = "bottom", legend.text = element_text(size = 14),
-    plot.title=element_text(hjust = 0.5), plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
-
-#, plot.caption = element_text(hjust= 0.5, size = 11)
-ggpubr::ggarrange(prox_pic, expo_pic, common.legend = TRUE, legend = "bottom", widths = c(1.3,1))
-
-ggsave(plotname,plot = last_plot(),
-  device = NULL,path = NULL,
-  scale = 1,
-  width = 12,
-  height = 9,
-  units = c("in", "cm", "mm"),
-  dpi = 300,
-  limitsize = FALSE)
-
-```
-
-```{r sa_vllblc_table,  fig.cap="TABLE Sensitivity proximity value liberal locals, distribution liberals", echo=FALSE}
-
-# database filter
-
-excl <- names(sa_asym) %in% c("run", "ID","density","step","eth_lib_loc","val_con_loc","eth_lib_min","val_con_min")
-dataset_sa <- sa_asym[!excl] %>% filter(eth_con_loc  == 20,eth_con_min   == 20,val_lib_min == 20)  %>% 
-group_by(val_lib_loc ,fraction_blue,circle_blue, circle_orange) %>% summarise_all(c("mean"= mean,"sd"= sd))
+# for latex output
 
@@
 
-```{r sa_vllbmn,  fig.cap="Sensitivity proximity value liberal minority, distribution liberals", echo=FALSE}
-
-# database filter
-excl <- names(sa_asym) %in% c("run", "ID","density","step","eth_lib_loc","val_con_loc","eth_lib_min","val_con_min")
-dataset_sa <- sa_asym[!excl] %>% filter(eth_con_loc  == 20,val_lib_loc == 20,eth_con_min  == 20)  %>% 
-group_by(val_lib_min ,fraction_blue,circle_blue, circle_orange) %>% summarise_all(c("mean"= mean,"sd"= sd))
-
-plotname <- "images/vllbmn.jpg"
-xlab_t <- "ß value liberal minority"
-
-xvalues <- c(dataset_sa$de_sq_bl_mean,dataset_sa$de_cl_bl_mean,dataset_sa$de_sq_or_mean,dataset_sa$de_cl_or_mean,
-       dataset_sa$dv_sq_bl_mean,dataset_sa$dv_cl_bl_mean,dataset_sa$dv_sq_or_mean,dataset_sa$dv_cl_or_mean)
-
- expo_pic <-   ggplot(data = dataset_sa) + 
-  geom_point(aes(x = dataset_sa$de_sq_bl_mean, y = dataset_sa$et_sq_bl_mean),color = "black", fill = "blue", shape = 22, size = 5) +
-  geom_point(aes(x = dataset_sa$de_cl_bl_mean, y = dataset_sa$et_cl_bl_mean),color = "black",fill = "blue", shape = 21, size = 5) +
-  geom_point(aes(x = dataset_sa$de_sq_or_mean, y = dataset_sa$et_sq_or_mean),color = "black", fill = "orange", shape = 22, size = 5) +
-  geom_point(aes(x = dataset_sa$de_cl_or_mean, y = dataset_sa$et_cl_or_mean),color = "black", fill = "orange", shape = 21, size = 5) +
-
-  geom_point(aes(x = dataset_sa$dv_sq_bl_mean, y = dataset_sa$vl_sq_bl_mean),color = "black", fill = "blue", shape = 8, size = 5.1) + 
-   geom_point(aes(x = dataset_sa$dv_sq_bl_mean, y = dataset_sa$vl_sq_bl_mean),color = "black", fill = "blue", shape = 22, size = 5) +
-
-   geom_point(aes(x = dataset_sa$dv_cl_bl_mean, y = dataset_sa$vl_cl_bl_mean),color = "black",fill = "blue", shape = 8, size = 5.1) + 
-  geom_point(aes(x = dataset_sa$dv_cl_bl_mean, y = dataset_sa$vl_cl_bl_mean),color = "black",fill = "blue", shape = 21, size = 5) +
-
-    geom_point(aes(x = dataset_sa$dv_sq_or_mean, y = dataset_sa$vl_sq_or_mean),color = "black", fill = "orange", shape = 8, size = 5.1) +
-  geom_point(aes(x = dataset_sa$dv_sq_or_mean, y = dataset_sa$vl_sq_or_mean),color = "black", fill = "orange", shape = 22, size = 5) +
-
-  geom_point(aes(x = dataset_sa$dv_cl_or_mean, y = dataset_sa$vl_cl_or_mean),color = "black", fill = "orange", shape = 8, size = 5.1) +
-geom_point(aes(x = dataset_sa$dv_cl_or_mean, y = dataset_sa$vl_cl_or_mean),color = "black", fill = "orange", shape = 21, size = 5) +
-
- scale_x_continuous(limits = c(min(xvalues),max(xvalues)), breaks = seq(0,max(xvalues), by = 0.5)) + 
-  scale_y_continuous(breaks= seq(0,1,by=0.1)) + 
-  geom_vline(xintercept = 1, color = "red") +
-  xlab("Spatial proximity") + ylab("Exposure") +
-  theme_bw() + theme( 
-    axis.title.x = (element_text(size = 13)), axis.title.y = (element_text(size = 15)),
-    axis.text.x =  (element_text(size = 12)), axis.text.y =  (element_text(size = 15)), 
-    legend.title = element_text(size = 13),legend.position = "bottom", legend.text = element_text(size = 13),
-    plot.title=element_text(hjust = 0.5), plot.caption = element_text(hjust= 0.5, size = 11), plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
-
-data_prox <- dataset_sa  %>% gather(key= subgroup, value = Prox, de_sq_bl_mean, dv_sq_bl_mean, de_cl_bl_mean, dv_cl_bl_mean, de_sq_or_mean, dv_sq_or_mean, de_cl_or_mean, dv_cl_or_mean) %>% mutate(
-  `segregation` = fct_relevel(fct_collapse(subgroup,"ethnics" = c("de_sq_bl_mean","de_cl_bl_mean","de_sq_or_mean","de_cl_or_mean"), "values" = c("dv_sq_bl_mean","dv_cl_bl_mean","dv_sq_or_mean","dv_cl_or_mean")),"ethnics"),
- `orientation` = fct_relevel(fct_collapse(subgroup, "conservative" = c("de_sq_bl_mean","dv_sq_bl_mean","de_sq_or_mean","dv_sq_or_mean"), "liberal" = c("de_cl_bl_mean","dv_cl_bl_mean","de_cl_or_mean","dv_cl_or_mean")),"conservative" ),
- `ethnia` = fct_relevel(fct_collapse(subgroup, "local" = c("de_sq_bl_mean","dv_sq_bl_mean","de_cl_bl_mean","dv_cl_bl_mean"),"minority" = c("de_sq_or_mean","dv_sq_or_mean","de_cl_or_mean","dv_cl_or_mean")), "local"))
-
-prox_pic <- ggplot(data = data_prox, aes(x = val_lib_min, y = Prox, linetype = `segregation` , fill = `ethnia`,  shape = `orientation`)) + geom_line(aes(color = `ethnia`))  +  geom_point(color = "black", size = 4) +
- scale_x_discrete(limits=c(seq(0,20 ,by = 1))) + scale_y_continuous(limits=c(min(data_prox$Prox),max(data_prox$Prox)), breaks=seq(0,max(data_prox$Prox),by=0.50)) +
- facet_wrap(~ circle_orange, dir = "v", labeller = labeller(circle_orange = circle_orange.labs)) +
-    geom_vline(xintercept = 20, color = "red") +  geom_hline(yintercept = 1, color = "red") +
-  scale_linetype_manual(values=c("solid","dashed"), labels = c("ethnic","value"), guide = guide_legend(title = "Segregation", order = 1)) +
-  scale_fill_manual(values = c("blue","darkorange")) + 
-   scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
-  scale_shape_manual(values = c(22,21), guide = guide_legend(title="Value" ,override.aes = list(size = 3), order = 3)) +
-  guides(fill = FALSE) +
-  xlab(xlab_t) + ylab("Spatial Proximity") + 
-  theme_bw() +  theme( 
-    axis.title.x = (element_text(size = 13)), axis.title.y = (element_text(size = 15)),
-    axis.text.x =  (element_text(size = 12)), axis.text.y =  (element_text(size = 15)), 
-    strip.text = element_text(size=13),
-    legend.title = element_text(size = 13),legend.position = "bottom", legend.text = element_text(size = 14),
-    plot.title=element_text(hjust = 0.5), plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
-
-#, plot.caption = element_text(hjust= 0.5, size = 11)
-ggpubr::ggarrange(prox_pic, expo_pic, common.legend = TRUE, legend = "bottom", widths = c(1.3,1))
-
-ggsave(plotname,plot = last_plot(),
-  device = NULL,path = NULL,
-  scale = 1,
-  width = 12,
-  height = 9,
-  units = c("in", "cm", "mm"),
-  dpi = 300,
-  limitsize = FALSE)
-
-```
-
-```{r sa_vllbmn_table,  fig.cap="TABLE Sensitivity proximity value liberal minority, distribution liberals", echo=FALSE}
+```{r sa_vllbmn_table,  fig.cap="Tab. 14: Sensitivity value liberals minority - exposure correct, asymmetric conditions", echo=FALSE}
 
@@
 
+# latex  for different distribution liberals minority
+
 df_vllbmn50 <- dataset_sa %>%  filter(circle_orange == 50)
@@
 
-```{r sa_etcnlc,  fig.cap="Sensitivity proximity ethnic conservative local, distribution liberals", echo=FALSE}
-
-# database filter
-excl <- names(sa_asym) %in% c("run", "ID","density","step","eth_lib_loc","val_con_loc","eth_lib_min","val_con_min")
-dataset_sa <- sa_asym[!excl] %>% filter(val_lib_loc   == 20,eth_con_min   == 20, val_lib_min == 20)  %>% 
-group_by(eth_con_loc ,fraction_blue,circle_blue, circle_orange) %>% summarise_all(c("mean"= mean,"sd"= sd))
-
-plotname <- "images/etcnlc.jpg"
-xlab_t <- "ß ethnic conservative local"
-
-xvalues <- c(dataset_sa$de_sq_bl_mean,dataset_sa$de_cl_bl_mean,dataset_sa$de_sq_or_mean,dataset_sa$de_cl_or_mean,
-       dataset_sa$dv_sq_bl_mean,dataset_sa$dv_cl_bl_mean,dataset_sa$dv_sq_or_mean,dataset_sa$dv_cl_or_mean)
-
- expo_pic <-   ggplot(data = dataset_sa) + 
-  geom_point(aes(x = dataset_sa$de_sq_bl_mean, y = dataset_sa$et_sq_bl_mean),color = "black", fill = "blue", shape = 22, size = 5) +
-  geom_point(aes(x = dataset_sa$de_cl_bl_mean, y = dataset_sa$et_cl_bl_mean),color = "black",fill = "blue", shape = 21, size = 5) +
-  geom_point(aes(x = dataset_sa$de_sq_or_mean, y = dataset_sa$et_sq_or_mean),color = "black", fill = "orange", shape = 22, size = 5) +
-  geom_point(aes(x = dataset_sa$de_cl_or_mean, y = dataset_sa$et_cl_or_mean),color = "black", fill = "orange", shape = 21, size = 5) +
-
-  geom_point(aes(x = dataset_sa$dv_sq_bl_mean, y = dataset_sa$vl_sq_bl_mean),color = "black", fill = "blue", shape = 8, size = 5.1) + 
-   geom_point(aes(x = dataset_sa$dv_sq_bl_mean, y = dataset_sa$vl_sq_bl_mean),color = "black", fill = "blue", shape = 22, size = 5) +
-
-   geom_point(aes(x = dataset_sa$dv_cl_bl_mean, y = dataset_sa$vl_cl_bl_mean),color = "black",fill = "blue", shape = 8, size = 5.1) + 
-  geom_point(aes(x = dataset_sa$dv_cl_bl_mean, y = dataset_sa$vl_cl_bl_mean),color = "black",fill = "blue", shape = 21, size = 5) +
-
-    geom_point(aes(x = dataset_sa$dv_sq_or_mean, y = dataset_sa$vl_sq_or_mean),color = "black", fill = "orange", shape = 8, size = 5.1) +
-  geom_point(aes(x = dataset_sa$dv_sq_or_mean, y = dataset_sa$vl_sq_or_mean),color = "black", fill = "orange", shape = 22, size = 5) +
-
-  geom_point(aes(x = dataset_sa$dv_cl_or_mean, y = dataset_sa$vl_cl_or_mean),color = "black", fill = "orange", shape = 8, size = 5.1) +
-geom_point(aes(x = dataset_sa$dv_cl_or_mean, y = dataset_sa$vl_cl_or_mean),color = "black", fill = "orange", shape = 21, size = 5) +
-
- scale_x_continuous(limits = c(min(xvalues),max(xvalues)), breaks = seq(0,max(xvalues), by = 0.5)) + 
-  scale_y_continuous(breaks= seq(0,1,by=0.1)) + 
-  geom_vline(xintercept = 1, color = "red") +
-  xlab("Spatial proximity") + ylab("Exposure") +
-  theme_bw() + theme( 
-    axis.title.x = (element_text(size = 13)), axis.title.y = (element_text(size = 15)),
-    axis.text.x =  (element_text(size = 12)), axis.text.y =  (element_text(size = 15)), 
-    legend.title = element_text(size = 13),legend.position = "bottom", legend.text = element_text(size = 13),
-    plot.title=element_text(hjust = 0.5), plot.caption = element_text(hjust= 0.5, size = 11), plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
-
-data_prox <- dataset_sa  %>% gather(key= subgroup, value = Prox, de_sq_bl_mean, dv_sq_bl_mean, de_cl_bl_mean, dv_cl_bl_mean, de_sq_or_mean, dv_sq_or_mean, de_cl_or_mean, dv_cl_or_mean) %>% mutate(
-  `segregation` = fct_relevel(fct_collapse(subgroup,"ethnics" = c("de_sq_bl_mean","de_cl_bl_mean","de_sq_or_mean","de_cl_or_mean"), "values" = c("dv_sq_bl_mean","dv_cl_bl_mean","dv_sq_or_mean","dv_cl_or_mean")),"ethnics"),
- `orientation` = fct_relevel(fct_collapse(subgroup, "conservative" = c("de_sq_bl_mean","dv_sq_bl_mean","de_sq_or_mean","dv_sq_or_mean"), "liberal" = c("de_cl_bl_mean","dv_cl_bl_mean","de_cl_or_mean","dv_cl_or_mean")),"conservative" ),
- `ethnia` = fct_relevel(fct_collapse(subgroup, "local" = c("de_sq_bl_mean","dv_sq_bl_mean","de_cl_bl_mean","dv_cl_bl_mean"),"minority" = c("de_sq_or_mean","dv_sq_or_mean","de_cl_or_mean","dv_cl_or_mean")), "local"))
-
-prox_pic <- ggplot(data = data_prox, aes(x = eth_con_loc, y = Prox, linetype = `segregation` , fill = `ethnia`,  shape = `orientation`)) + geom_line(aes(color = `ethnia`))  +  geom_point(color = "black", size = 4) +
- scale_x_discrete(limits=c(seq(0,20 ,by = 1))) + scale_y_continuous(limits=c(min(data_prox$Prox),max(data_prox$Prox)), breaks=seq(0,max(data_prox$Prox),by=0.50)) +
- facet_wrap(~ circle_orange, dir = "v", labeller = labeller(circle_orange = circle_orange.labs)) +
-    geom_vline(xintercept = 20, color = "red") +  geom_hline(yintercept = 1, color = "red") +
-  scale_linetype_manual(values=c("solid","dashed"), labels = c("ethnic","value"), guide = guide_legend(title = "Segregation", order = 1)) +
-  scale_fill_manual(values = c("blue","darkorange")) + 
-   scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
-  scale_shape_manual(values = c(22,21), guide = guide_legend(title="Value" ,override.aes = list(size = 3), order = 3)) +
-  guides(fill = FALSE) +
-  xlab(xlab_t) + ylab("Spatial Proximity") + 
-  theme_bw() +  theme( 
-    axis.title.x = (element_text(size = 13)), axis.title.y = (element_text(size = 15)),
-    axis.text.x =  (element_text(size = 12)), axis.text.y =  (element_text(size = 15)), 
-    strip.text = element_text(size=13),
-    legend.title = element_text(size = 13),legend.position = "bottom", legend.text = element_text(size = 14),
-    plot.title=element_text(hjust = 0.5), plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
-
-#, plot.caption = element_text(hjust= 0.5, size = 11)
-ggpubr::ggarrange(prox_pic, expo_pic, common.legend = TRUE, legend = "bottom", widths = c(1.3,1))
-
-ggsave(plotname,plot = last_plot(),
-  device = NULL,path = NULL,
-  scale = 1,
-  width = 12,
-  height = 9,
-  units = c("in", "cm", "mm"),
-  dpi = 300,
-  limitsize = FALSE)
-```
-
-```{r sa_etcnlc_table,  fig.cap="TABLE Sensitivity proximity ethnic conservative local, distribution liberals", echo=FALSE}
-
-# database filter
-
-excl <- names(sa_asym) %in% c("run", "ID","density","step","eth_lib_loc","val_con_loc","eth_lib_min","val_con_min")
-dataset_sa <- sa_asym[!excl] %>% filter(val_lib_min == 20,  val_lib_loc == 20, eth_con_min == 20)  %>% 
-group_by(eth_con_loc ,fraction_blue,circle_blue, circle_orange) %>% summarise_all(c("mean"= mean,"sd"= sd))
-
-df_etcnlc50 <- dataset_sa %>%  filter(circle_orange == 50)
-etcnlc50 <- xtable(df_etcnlc50[,c("eth_con_loc","de_sq_bl_mean","de_sq_bl_sd","de_cl_bl_mean","de_cl_bl_sd","de_sq_or_mean","de_sq_or_sd","de_cl_or_mean","de_cl_or_sd","dv_sq_bl_mean","dv_sq_bl_sd","dv_cl_bl_mean","dv_cl_bl_sd","dv_sq_or_mean","dv_sq_or_sd","dv_cl_or_mean","dv_cl_or_sd")], digits = 3)
-align(etcnlc50) <- "c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|"
-addtorow <- list()
-addtorow$pos <- list(0, 0,0,0,0)
-addtorow$command <-  c("\\multicolumn{17}{|c|}{Ethnic Asymmetry, $50 \\%$ Liberal Migrants: Spatial Proximity}  \\\\\\hline\n",
-   "Preference &  \\multicolumn{8}{|c|}{Ethnic Proximity} & \\multicolumn{8}{|c|}{Value Proximity}   \\\\\\hline\n",
-  "& \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  & \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  \\\\\n",
-"$\\beta$ ethnic & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
-& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
-& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal}\\\\\n",
-"conservative local & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD\\\\\n")
-print(etcnlc50,type = "latex", file = "latex/etcnlc50.tex"  , include.rownames=FALSE, add.to.row = addtorow, include.colnames = FALSE, latex.environments = "center")
-
-df_etcnlc20 <- dataset_sa %>%  filter(circle_orange == 20)
-etcnlc20 <- xtable(df_etcnlc20[,c("eth_con_loc","de_sq_bl_mean","de_sq_bl_sd","de_cl_bl_mean","de_cl_bl_sd","de_sq_or_mean","de_sq_or_sd","de_cl_or_mean","de_cl_or_sd","dv_sq_bl_mean","dv_sq_bl_sd","dv_cl_bl_mean","dv_cl_bl_sd","dv_sq_or_mean","dv_sq_or_sd","dv_cl_or_mean","dv_cl_or_sd")], digits = 3)
-align(etcnlc20) <- "c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|"
-addtorow <- list()
-addtorow$pos <- list(0, 0,0,0,0)
-addtorow$command <- c("\\multicolumn{17}{|c|}{Ethnic Asymmetry, $20 \\%$ Liberal Migrants: Spatial Proximity}  \\\\\\hline\n",
-   "Preference &  \\multicolumn{8}{|c|}{Ethnic Proximity} & \\multicolumn{8}{|c|}{Value Proximity}   \\\\\\hline\n",
-  "& \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  & \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  \\\\\n",
-"$\\beta$ ethnic & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
-& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
-& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal}\\\\\n",
-"conservative local & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD\\\\\n")
-print(etcnlc20,type = "latex", file = "latex/etcnlc20.tex" , include.rownames=FALSE, add.to.row = addtorow, include.colnames = FALSE, latex.environments = "center")
-
-df_etcnlc80 <- dataset_sa %>%  filter(circle_orange == 80)
-etcnlc80 <- xtable(df_etcnlc80[,c("eth_con_loc","de_sq_bl_mean","de_sq_bl_sd","de_cl_bl_mean","de_cl_bl_sd","de_sq_or_mean","de_sq_or_sd","de_cl_or_mean","de_cl_or_sd","dv_sq_bl_mean","dv_sq_bl_sd","dv_cl_bl_mean","dv_cl_bl_sd","dv_sq_or_mean","dv_sq_or_sd","dv_cl_or_mean","dv_cl_or_sd")], digits = 3)
-align(etcnlc80) <- "c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|"
-addtorow <- list()
-addtorow$pos <- list(0, 0,0,0,0)
-addtorow$command <- c("\\multicolumn{17}{|c|}{Ethnic Asymmetry, $80 \\%$ Liberal Migrants: Spatial Proximity}  \\\\\\hline\n",
-   "Preference &  \\multicolumn{8}{|c|}{Ethnic Proximity} & \\multicolumn{8}{|c|}{Value Proximity}   \\\\\\hline\n",
-  "& \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  & \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  \\\\\n",
-"$\\beta$ ethnic & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
-& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
-& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal}\\\\\n",
-"conservative local & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD\\\\\n")
-print(etcnlc80,type = "latex", file = "latex/etcnlc80.tex" , include.rownames=FALSE, add.to.row = addtorow, include.colnames = FALSE, latex.environments = "center")
-
-```
-
-```{r sa_etcnmn,  fig.cap="Sensitivity proximity ethnic conservative minority, distribution liberals", echo=FALSE}
-
-# database filter
-excl <- names(sa_asym) %in% c("run", "ID","density","step","eth_lib_loc","val_con_loc","eth_lib_min","val_con_min")
-dataset_sa <- sa_asym[!excl] %>% filter(eth_con_loc  == 20,val_lib_loc == 20,val_lib_min == 20)  %>% 
-group_by(eth_con_min ,fraction_blue,circle_blue, circle_orange) %>% summarise_all(c("mean"= mean,"sd"= sd))
-
-plotname <- "images/etcnmn.jpg"
-xlab_t <- "ß ethnic conservative minority"
-
-xvalues <- c(dataset_sa$de_sq_bl_mean,dataset_sa$de_cl_bl_mean,dataset_sa$de_sq_or_mean,dataset_sa$de_cl_or_mean,
-       dataset_sa$dv_sq_bl_mean,dataset_sa$dv_cl_bl_mean,dataset_sa$dv_sq_or_mean,dataset_sa$dv_cl_or_mean)
-
- expo_pic <-   ggplot(data = dataset_sa) + 
-  geom_point(aes(x = dataset_sa$de_sq_bl_mean, y = dataset_sa$et_sq_bl_mean),color = "black", fill = "blue", shape = 22, size = 5) +
-  geom_point(aes(x = dataset_sa$de_cl_bl_mean, y = dataset_sa$et_cl_bl_mean),color = "black",fill = "blue", shape = 21, size = 5) +
-  geom_point(aes(x = dataset_sa$de_sq_or_mean, y = dataset_sa$et_sq_or_mean),color = "black", fill = "orange", shape = 22, size = 5) +
-  geom_point(aes(x = dataset_sa$de_cl_or_mean, y = dataset_sa$et_cl_or_mean),color = "black", fill = "orange", shape = 21, size = 5) +
-
-  geom_point(aes(x = dataset_sa$dv_sq_bl_mean, y = dataset_sa$vl_sq_bl_mean),color = "black", fill = "blue", shape = 8, size = 5.1) + 
-   geom_point(aes(x = dataset_sa$dv_sq_bl_mean, y = dataset_sa$vl_sq_bl_mean),color = "black", fill = "blue", shape = 22, size = 5) +
-
-   geom_point(aes(x = dataset_sa$dv_cl_bl_mean, y = dataset_sa$vl_cl_bl_mean),color = "black",fill = "blue", shape = 8, size = 5.1) + 
-  geom_point(aes(x = dataset_sa$dv_cl_bl_mean, y = dataset_sa$vl_cl_bl_mean),color = "black",fill = "blue", shape = 21, size = 5) +
-
-    geom_point(aes(x = dataset_sa$dv_sq_or_mean, y = dataset_sa$vl_sq_or_mean),color = "black", fill = "orange", shape = 8, size = 5.1) +
-  geom_point(aes(x = dataset_sa$dv_sq_or_mean, y = dataset_sa$vl_sq_or_mean),color = "black", fill = "orange", shape = 22, size = 5) +
-
-  geom_point(aes(x = dataset_sa$dv_cl_or_mean, y = dataset_sa$vl_cl_or_mean),color = "black", fill = "orange", shape = 8, size = 5.1) +
-geom_point(aes(x = dataset_sa$dv_cl_or_mean, y = dataset_sa$vl_cl_or_mean),color = "black", fill = "orange", shape = 21, size = 5) +
-
- scale_x_continuous(limits = c(min(xvalues),max(xvalues)), breaks = seq(0,max(xvalues), by = 0.5)) + 
-  scale_y_continuous(breaks= seq(0,1,by=0.1)) + 
-  geom_vline(xintercept = 1, color = "red") +
-  xlab("Spatial proximity") + ylab("Exposure") +
-  theme_bw() + theme( 
-    axis.title.x = (element_text(size = 13)), axis.title.y = (element_text(size = 15)),
-    axis.text.x =  (element_text(size = 12)), axis.text.y =  (element_text(size = 15)), 
-    legend.title = element_text(size = 13),legend.position = "bottom", legend.text = element_text(size = 13),
-    plot.title=element_text(hjust = 0.5), plot.caption = element_text(hjust= 0.5, size = 11), plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
-
-data_prox <- dataset_sa  %>% gather(key= subgroup, value = Prox, de_sq_bl_mean, dv_sq_bl_mean, de_cl_bl_mean, dv_cl_bl_mean, de_sq_or_mean, dv_sq_or_mean, de_cl_or_mean, dv_cl_or_mean) %>% mutate(
-  `segregation` = fct_relevel(fct_collapse(subgroup,"ethnics" = c("de_sq_bl_mean","de_cl_bl_mean","de_sq_or_mean","de_cl_or_mean"), "values" = c("dv_sq_bl_mean","dv_cl_bl_mean","dv_sq_or_mean","dv_cl_or_mean")),"ethnics"),
- `orientation` = fct_relevel(fct_collapse(subgroup, "conservative" = c("de_sq_bl_mean","dv_sq_bl_mean","de_sq_or_mean","dv_sq_or_mean"), "liberal" = c("de_cl_bl_mean","dv_cl_bl_mean","de_cl_or_mean","dv_cl_or_mean")),"conservative" ),
- `ethnia` = fct_relevel(fct_collapse(subgroup, "local" = c("de_sq_bl_mean","dv_sq_bl_mean","de_cl_bl_mean","dv_cl_bl_mean"),"minority" = c("de_sq_or_mean","dv_sq_or_mean","de_cl_or_mean","dv_cl_or_mean")), "local"))
-
-prox_pic <- ggplot(data = data_prox, aes(x = eth_con_min, y = Prox, linetype = `segregation` , fill = `ethnia`,  shape = `orientation`)) + geom_line(aes(color = `ethnia`))  +  geom_point(color = "black", size = 4) +
- scale_x_discrete(limits=c(seq(0,20 ,by = 1))) + scale_y_continuous(limits=c(min(data_prox$Prox),max(data_prox$Prox)), breaks=seq(0,max(data_prox$Prox),by=0.50)) +
- facet_wrap(~ circle_orange, dir = "v", labeller = labeller(circle_orange = circle_orange.labs)) +
-    geom_vline(xintercept = 20, color = "red") +  geom_hline(yintercept = 1, color = "red") +
-  scale_linetype_manual(values=c("solid","dashed"), labels = c("ethnic","value"), guide = guide_legend(title = "Segregation", order = 1)) +
-  scale_fill_manual(values = c("blue","darkorange")) + 
-   scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
-  scale_shape_manual(values = c(22,21), guide = guide_legend(title="Value" ,override.aes = list(size = 3), order = 3)) +
-  guides(fill = FALSE) +
-  xlab(xlab_t) + ylab("Spatial Proximity") + 
-  theme_bw() +  theme( 
-    axis.title.x = (element_text(size = 13)), axis.title.y = (element_text(size = 15)),
-    axis.text.x =  (element_text(size = 12)), axis.text.y =  (element_text(size = 15)), 
-    strip.text = element_text(size=13),
-    legend.title = element_text(size = 13),legend.position = "bottom", legend.text = element_text(size = 14),
-    plot.title=element_text(hjust = 0.5), plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
-
-#, plot.caption = element_text(hjust= 0.5, size = 11)
-ggpubr::ggarrange(prox_pic, expo_pic, common.legend = TRUE, legend = "bottom", widths = c(1.3,1))
-
-ggsave(plotname,plot = last_plot(),
-  device = NULL,path = NULL,
-  scale = 1,
-  width = 12,
-  height = 9,
-  units = c("in", "cm", "mm"),
-  dpi = 300,
-  limitsize = FALSE)
-```
-
-```{r sa_etcnmn_table,  fig.cap="TABLE Sensitivity proximity ethnic conservative minority, distribution liberals", echo=FALSE}
-
-# database filter
-
-excl <- names(sa_asym) %in% c("run", "ID","density","step","eth_lib_loc","val_con_loc","eth_lib_min","val_con_min")
-dataset_sa <- sa_asym[!excl] %>% filter(val_lib_min == 20,  val_lib_loc == 20, eth_con_loc == 20)  %>% 
-group_by(eth_con_min ,fraction_blue,circle_blue, circle_orange) %>% summarise_all(c("mean"= mean,"sd"= sd))
-
-df_etcnmn50 <- dataset_sa %>%  filter(circle_orange == 50)
-etcnmn50 <- xtable(df_etcnmn50[,c("eth_con_min","de_sq_bl_mean","de_sq_bl_sd","de_cl_bl_mean","de_cl_bl_sd","de_sq_or_mean","de_sq_or_sd","de_cl_or_mean","de_cl_or_sd","dv_sq_bl_mean","dv_sq_bl_sd","dv_cl_bl_mean","dv_cl_bl_sd","dv_sq_or_mean","dv_sq_or_sd","dv_cl_or_mean","dv_cl_or_sd")], digits = 3)
-align(etcnmn50) <- "c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|"
-addtorow <- list()
-addtorow$pos <- list(0, 0,0,0,0)
-addtorow$command <-  c("\\multicolumn{17}{|c|}{Ethnic Asymmetry, $50 \\%$ Liberal Migrants: Spatial Proximity}  \\\\\\hline\n",
-   "Preference &  \\multicolumn{8}{|c|}{Ethnic Proximity} & \\multicolumn{8}{|c|}{Value Proximity}   \\\\\\hline\n",
-  "& \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  & \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  \\\\\n",
-"$\\beta$ ethnic & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
-& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
-& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal}\\\\\n",
-"conservative minority & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD\\\\\n")
-print(etcnmn50,type = "latex", file = "latex/etcnmn50.tex"  , include.rownames=FALSE, add.to.row = addtorow, include.colnames = FALSE, latex.environments = "center")
-
-df_etcnmn20 <- dataset_sa %>%  filter(circle_orange == 20)
-etcnmn20 <- xtable(df_etcnmn20[,c("eth_con_min","de_sq_bl_mean","de_sq_bl_sd","de_cl_bl_mean","de_cl_bl_sd","de_sq_or_mean","de_sq_or_sd","de_cl_or_mean","de_cl_or_sd","dv_sq_bl_mean","dv_sq_bl_sd","dv_cl_bl_mean","dv_cl_bl_sd","dv_sq_or_mean","dv_sq_or_sd","dv_cl_or_mean","dv_cl_or_sd")], digits = 3)
-align(etcnmn20) <- "c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|"
-addtorow <- list()
-addtorow$pos <- list(0, 0,0,0,0)
-addtorow$command <- c("\\multicolumn{17}{|c|}{Ethnic Asymmetry, $20 \\%$ Liberal Migrants: Spatial Proximity}  \\\\\\hline\n",
-   "Preference &  \\multicolumn{8}{|c|}{Ethnic Proximity} & \\multicolumn{8}{|c|}{Value Proximity}   \\\\\\hline\n",
-  "& \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  & \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  \\\\\n",
-"$\\beta$ ethnic & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
-& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
-& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal}\\\\\n",
-"conservative minority & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD\\\\\n")
-print(etcnmn20,type = "latex", file = "latex/etcnmn20.tex" , include.rownames=FALSE, add.to.row = addtorow, include.colnames = FALSE, latex.environments = "center")
-
-df_etcnmn80 <- dataset_sa %>%  filter(circle_orange == 80)
-etcnmn80 <- xtable(df_etcnmn80[,c("eth_con_min","de_sq_bl_mean","de_sq_bl_sd","de_cl_bl_mean","de_cl_bl_sd","de_sq_or_mean","de_sq_or_sd","de_cl_or_mean","de_cl_or_sd","dv_sq_bl_mean","dv_sq_bl_sd","dv_cl_bl_mean","dv_cl_bl_sd","dv_sq_or_mean","dv_sq_or_sd","dv_cl_or_mean","dv_cl_or_sd")], digits = 3)
-align(etcnmn80) <- "c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|"
-addtorow <- list()
-addtorow$pos <- list(0, 0,0,0,0)
-addtorow$command <- c("\\multicolumn{17}{|c|}{Ethnic Asymmetry, $80 \\%$ Liberal Migrants: Spatial Proximity}  \\\\\\hline\n",
-   "Preference &  \\multicolumn{8}{|c|}{Ethnic Proximity} & \\multicolumn{8}{|c|}{Value Proximity}   \\\\\\hline\n",
-  "& \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  & \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  \\\\\n",
-"$\\beta$ ethnic & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
-& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
-& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal}\\\\\n",
-"conservative minority & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD\\\\\n")
-print(etcnmn80,type = "latex", file = "latex/etcnmn80.tex" , include.rownames=FALSE, add.to.row = addtorow, include.colnames = FALSE, latex.environments = "center")
-
-# test_all <- rbind(etcnmn20,etcnmn50,etcnmn80)
-# print(test_all, type = "latex", file = "latex/test_all.tex",include.rownames=FALSE, add.to.row = addtorow, include.colnames = FALSE, latex.environments = "center")
-
-```
-
-```{r et_lib_loc,  fig.cap="Sensitivity proximity ETHNIC liberal majority", echo=FALSE}
-
-# database filter
+```{r et_lib_loc_table,  fig.cap="Tab. 15: Ethnic liberals majority, asymmetric conditions", echo=FALSE}
+
+# database filter
+
 excl <- names(etlib) %in% c("run", "ID","density","step","eth_con_loc","eth_con_min","val_lib_loc","val_lib_min","val_con_loc","val_con_min")
@@
 
-plotname <- "images/et_libloc.jpg"
-xlab_t <- "ß ethnic liberal local"
-
-xvalues <- c(etlib_df$de_sq_bl_mean,etlib_df$de_cl_bl_mean,etlib_df$de_sq_or_mean,etlib_df$de_cl_or_mean,
-       etlib_df$dv_sq_bl_mean,etlib_df$dv_cl_bl_mean,etlib_df$dv_sq_or_mean,etlib_df$dv_cl_or_mean)
-
- expo_pic <-   ggplot(data = etlib_df) + 
-  geom_point(aes(x = etlib_df$de_sq_bl_mean, y = etlib_df$et_sq_bl_mean),color = "black", fill = "blue", shape = 22, size = 5) +
-  geom_point(aes(x = etlib_df$de_cl_bl_mean, y = etlib_df$et_cl_bl_mean),color = "black",fill = "blue", shape = 21, size = 5) +
-  geom_point(aes(x = etlib_df$de_sq_or_mean, y = etlib_df$et_sq_or_mean),color = "black", fill = "orange", shape = 22, size = 5) +
-  geom_point(aes(x = etlib_df$de_cl_or_mean, y = etlib_df$et_cl_or_mean),color = "black", fill = "orange", shape = 21, size = 5) +
-
-  geom_point(aes(x = etlib_df$dv_sq_bl_mean, y = etlib_df$vl_sq_bl_mean),color = "black", fill = "blue", shape = 8, size = 5.1) + 
-   geom_point(aes(x = etlib_df$dv_sq_bl_mean, y = etlib_df$vl_sq_bl_mean),color = "black", fill = "blue", shape = 22, size = 5) +
-
-   geom_point(aes(x = etlib_df$dv_cl_bl_mean, y = etlib_df$vl_cl_bl_mean),color = "black",fill = "blue", shape = 8, size = 5.1) + 
-  geom_point(aes(x = etlib_df$dv_cl_bl_mean, y = etlib_df$vl_cl_bl_mean),color = "black",fill = "blue", shape = 21, size = 5) +
-
-    geom_point(aes(x = etlib_df$dv_sq_or_mean, y = etlib_df$vl_sq_or_mean),color = "black", fill = "orange", shape = 8, size = 5.1) +
-  geom_point(aes(x = etlib_df$dv_sq_or_mean, y = etlib_df$vl_sq_or_mean),color = "black", fill = "orange", shape = 22, size = 5) +
-
-  geom_point(aes(x = etlib_df$dv_cl_or_mean, y = etlib_df$vl_cl_or_mean),color = "black", fill = "orange", shape = 8, size = 5.1) +
-geom_point(aes(x = etlib_df$dv_cl_or_mean, y = etlib_df$vl_cl_or_mean),color = "black", fill = "orange", shape = 21, size = 5) +
-
- scale_x_continuous(limits = c(min(xvalues),max(xvalues)), breaks = seq(0,max(xvalues), by = 0.5)) + 
-  scale_y_continuous(breaks= seq(0,1,by=0.1)) + 
-  geom_vline(xintercept = 1, color = "red") +
-  xlab("Spatial proximity") + ylab("Exposure") +
-  theme_bw() + theme( 
-    axis.title.x = (element_text(size = 13)), axis.title.y = (element_text(size = 15)),
-    axis.text.x =  (element_text(size = 12)), axis.text.y =  (element_text(size = 15)), 
-    legend.title = element_text(size = 13),legend.position = "bottom", legend.text = element_text(size = 13),
-    plot.title=element_text(hjust = 0.5), plot.caption = element_text(hjust= 0.5, size = 11), plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
-
-data_prox <- etlib_df  %>% gather(key= subgroup, value = Prox, de_sq_bl_mean, dv_sq_bl_mean, de_cl_bl_mean, dv_cl_bl_mean, de_sq_or_mean, dv_sq_or_mean, de_cl_or_mean, dv_cl_or_mean) %>% mutate(
-  `segregation` = fct_relevel(fct_collapse(subgroup,"ethnics" = c("de_sq_bl_mean","de_cl_bl_mean","de_sq_or_mean","de_cl_or_mean"), "values" = c("dv_sq_bl_mean","dv_cl_bl_mean","dv_sq_or_mean","dv_cl_or_mean")),"ethnics"),
- `orientation` = fct_relevel(fct_collapse(subgroup, "conservative" = c("de_sq_bl_mean","dv_sq_bl_mean","de_sq_or_mean","dv_sq_or_mean"), "liberal" = c("de_cl_bl_mean","dv_cl_bl_mean","de_cl_or_mean","dv_cl_or_mean")),"conservative" ),
- `ethnia` = fct_relevel(fct_collapse(subgroup, "local" = c("de_sq_bl_mean","dv_sq_bl_mean","de_cl_bl_mean","dv_cl_bl_mean"),"minority" = c("de_sq_or_mean","dv_sq_or_mean","de_cl_or_mean","dv_cl_or_mean")), "local"))
-
-prox_pic <- ggplot(data = data_prox, aes(x = eth_lib_loc, y = Prox, linetype = `segregation` , fill = `ethnia`,  shape = `orientation`)) + geom_line(aes(color = `ethnia`))  +  geom_point(color = "black", size = 4) +
- scale_x_discrete(limits=c(seq(0,20 ,by = 1))) + scale_y_continuous(limits=c(min(data_prox$Prox),max(data_prox$Prox)), breaks=seq(0,max(data_prox$Prox),by=0.50)) +
- facet_wrap(~ circle_orange, dir = "v", labeller = labeller(circle_orange = circle_orange.labs)) +
-    geom_vline(xintercept = 20, color = "red") +  geom_hline(yintercept = 1, color = "red") +
-  scale_linetype_manual(values=c("solid","dashed"), labels = c("ethnic","value"), guide = guide_legend(title = "Segregation", order = 1)) +
-  scale_fill_manual(values = c("blue","darkorange")) + 
-   scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
-  scale_shape_manual(values = c(22,21), guide = guide_legend(title="Value" ,override.aes = list(size = 3), order = 3)) +
-  guides(fill = FALSE) +
-  xlab(xlab_t) + ylab("Spatial Proximity") + 
-  theme_bw() +  theme( 
-    axis.title.x = (element_text(size = 13)), axis.title.y = (element_text(size = 15)),
-    axis.text.x =  (element_text(size = 12)), axis.text.y =  (element_text(size = 15)), 
-    strip.text = element_text(size=13),
-    legend.title = element_text(size = 13),legend.position = "bottom", legend.text = element_text(size = 14),
-    plot.title=element_text(hjust = 0.5), plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
-
-#, plot.caption = element_text(hjust= 0.5, size = 11)
-ggpubr::ggarrange(prox_pic, expo_pic, common.legend = TRUE, legend = "bottom", widths = c(1.3,1))
-
-ggsave(plotname,plot = last_plot(),
-  device = NULL,path = NULL,
-  scale = 1,
-  width = 12,
-  height = 9,
-  units = c("in", "cm", "mm"),
-  dpi = 300,
-  limitsize = FALSE)
-
-```
-
-```{r et_lib_loc_table,  fig.cap="TABLE Sensitivity proximity ETHNIC liberal majority", echo=FALSE}
-
-# database filter
-
-excl <- names(etlib) %in% c("run", "ID","density","step","eth_con_loc","eth_con_min","val_lib_loc","val_lib_min","val_con_loc","val_con_min")
-etlib_df <- etlib[!excl] %>% filter(eth_lib_min  == 0)  %>% 
-group_by(eth_lib_loc,fraction_blue,circle_blue, circle_orange,eth_lib_min) %>% summarise_all(c("mean"= mean,"sd"= sd))
-
 df_etlib_loc50 <- etlib_df %>%  filter(circle_orange == 50)
@@
 "liberal local & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD\\\\\n")
-print(etcnmn80,type = "latex", file = "latex/etlib_loc80.tex" , include.rownames=FALSE, add.to.row = addtorow, include.colnames = FALSE, latex.environments = "center")
-
-```
-
-```{r et_lib_min,  fig.cap="Sensitivity proximity ETHNIC liberal minority", echo=FALSE}
-
-# database filter
+print(etlib_loc80,type = "latex", file = "latex/etlib_loc80.tex" , include.rownames=FALSE, add.to.row = addtorow, include.colnames = FALSE, latex.environments = "center")
+
+```
+
+```{r et_lib_min_table,  fig.cap="Tab. 16: Ethnic liberals minority, asymmetric conditions", echo=FALSE}
+
+# database filter
+
 excl <- names(etlib) %in% c("run", "ID","density","step","eth_con_loc","eth_con_min","val_lib_loc","val_lib_min","val_con_loc","val_con_min")
 etlib_df <- etlib[!excl] %>% filter(eth_lib_loc  == 0)  %>% 
-group_by(eth_lib_min,fraction_blue,circle_blue, circle_orange,eth_lib_loc) %>% summarise_all(c("mean"= mean,"sd"= sd))
-
-plotname <- "images/et_libmin.jpg"
-xlab_t <- "ß ethnic liberal minority"
-
-xvalues <- c(etlib_df$de_sq_bl_mean,etlib_df$de_cl_bl_mean,etlib_df$de_sq_or_mean,etlib_df$de_cl_or_mean,
-       etlib_df$dv_sq_bl_mean,etlib_df$dv_cl_bl_mean,etlib_df$dv_sq_or_mean,etlib_df$dv_cl_or_mean)
-
- expo_pic <-   ggplot(data = etlib_df) + 
-  geom_point(aes(x = etlib_df$de_sq_bl_mean, y = etlib_df$et_sq_bl_mean),color = "black", fill = "blue", shape = 22, size = 5) +
-  geom_point(aes(x = etlib_df$de_cl_bl_mean, y = etlib_df$et_cl_bl_mean),color = "black",fill = "blue", shape = 21, size = 5) +
-  geom_point(aes(x = etlib_df$de_sq_or_mean, y = etlib_df$et_sq_or_mean),color = "black", fill = "orange", shape = 22, size = 5) +
-  geom_point(aes(x = etlib_df$de_cl_or_mean, y = etlib_df$et_cl_or_mean),color = "black", fill = "orange", shape = 21, size = 5) +
-
-  geom_point(aes(x = etlib_df$dv_sq_bl_mean, y = etlib_df$vl_sq_bl_mean),color = "black", fill = "blue", shape = 8, size = 5.1) + 
-   geom_point(aes(x = etlib_df$dv_sq_bl_mean, y = etlib_df$vl_sq_bl_mean),color = "black", fill = "blue", shape = 22, size = 5) +
-
-   geom_point(aes(x = etlib_df$dv_cl_bl_mean, y = etlib_df$vl_cl_bl_mean),color = "black",fill = "blue", shape = 8, size = 5.1) + 
-  geom_point(aes(x = etlib_df$dv_cl_bl_mean, y = etlib_df$vl_cl_bl_mean),color = "black",fill = "blue", shape = 21, size = 5) +
-
-    geom_point(aes(x = etlib_df$dv_sq_or_mean, y = etlib_df$vl_sq_or_mean),color = "black", fill = "orange", shape = 8, size = 5.1) +
-  geom_point(aes(x = etlib_df$dv_sq_or_mean, y = etlib_df$vl_sq_or_mean),color = "black", fill = "orange", shape = 22, size = 5) +
-
-  geom_point(aes(x = etlib_df$dv_cl_or_mean, y = etlib_df$vl_cl_or_mean),color = "black", fill = "orange", shape = 8, size = 5.1) +
-geom_point(aes(x = etlib_df$dv_cl_or_mean, y = etlib_df$vl_cl_or_mean),color = "black", fill = "orange", shape = 21, size = 5) +
-
- scale_x_continuous(limits = c(min(xvalues),max(xvalues)), breaks = seq(0,max(xvalues), by = 0.5)) + 
-  scale_y_continuous(breaks= seq(0,1,by=0.1)) + 
-  geom_vline(xintercept = 1, color = "red") +
-  xlab("Spatial proximity") + ylab("Exposure") +
-  theme_bw() + theme( 
-    axis.title.x = (element_text(size = 13)), axis.title.y = (element_text(size = 15)),
-    axis.text.x =  (element_text(size = 12)), axis.text.y =  (element_text(size = 15)), 
-    legend.title = element_text(size = 13),legend.position = "bottom", legend.text = element_text(size = 13),
-    plot.title=element_text(hjust = 0.5), plot.caption = element_text(hjust= 0.5, size = 11), plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
-
-data_prox <- etlib_df  %>% gather(key= subgroup, value = Prox, de_sq_bl_mean, dv_sq_bl_mean, de_cl_bl_mean, dv_cl_bl_mean, de_sq_or_mean, dv_sq_or_mean, de_cl_or_mean, dv_cl_or_mean) %>% mutate(
-  `segregation` = fct_relevel(fct_collapse(subgroup,"ethnics" = c("de_sq_bl_mean","de_cl_bl_mean","de_sq_or_mean","de_cl_or_mean"), "values" = c("dv_sq_bl_mean","dv_cl_bl_mean","dv_sq_or_mean","dv_cl_or_mean")),"ethnics"),
- `orientation` = fct_relevel(fct_collapse(subgroup, "conservative" = c("de_sq_bl_mean","dv_sq_bl_mean","de_sq_or_mean","dv_sq_or_mean"), "liberal" = c("de_cl_bl_mean","dv_cl_bl_mean","de_cl_or_mean","dv_cl_or_mean")),"conservative" ),
- `ethnia` = fct_relevel(fct_collapse(subgroup, "local" = c("de_sq_bl_mean","dv_sq_bl_mean","de_cl_bl_mean","dv_cl_bl_mean"),"minority" = c("de_sq_or_mean","dv_sq_or_mean","de_cl_or_mean","dv_cl_or_mean")), "local"))
-
-prox_pic <- ggplot(data = data_prox, aes(x = eth_lib_min, y = Prox, linetype = `segregation` , fill = `ethnia`,  shape = `orientation`)) + geom_line(aes(color = `ethnia`))  +  geom_point(color = "black", size = 4) +
- scale_x_discrete(limits=c(seq(0,20 ,by = 1))) + scale_y_continuous(limits=c(min(data_prox$Prox),max(data_prox$Prox)), breaks=seq(0,max(data_prox$Prox),by=0.50)) +
- facet_wrap(~ circle_orange, dir = "v", labeller = labeller(circle_orange = circle_orange.labs)) +
-    geom_vline(xintercept = 20, color = "red") +  geom_hline(yintercept = 1, color = "red") +
-  scale_linetype_manual(values=c("solid","dashed"), labels = c("ethnic","value"), guide = guide_legend(title = "Segregation", order = 1)) +
-  scale_fill_manual(values = c("blue","darkorange")) + 
-   scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
-  scale_shape_manual(values = c(22,21), guide = guide_legend(title="Value" ,override.aes = list(size = 3), order = 3)) +
-  guides(fill = FALSE) +
-  xlab(xlab_t) + ylab("Spatial Proximity") + 
-  theme_bw() +  theme( 
-    axis.title.x = (element_text(size = 13)), axis.title.y = (element_text(size = 15)),
-    axis.text.x =  (element_text(size = 12)), axis.text.y =  (element_text(size = 15)), 
-    strip.text = element_text(size=13),
-    legend.title = element_text(size = 13),legend.position = "bottom", legend.text = element_text(size = 14),
-    plot.title=element_text(hjust = 0.5), plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
-
-#, plot.caption = element_text(hjust= 0.5, size = 11)
-ggpubr::ggarrange(prox_pic, expo_pic, common.legend = TRUE, legend = "bottom", widths = c(1.3,1))
-
-ggsave(plotname,plot = last_plot(),
-  device = NULL,path = NULL,
-  scale = 1,
-  width = 12,
-  height = 9,
-  units = c("in", "cm", "mm"),
-  dpi = 300,
-  limitsize = FALSE)
-
-```
-
-```{r et_lib_min_table,  fig.cap="TABLE Sensitivity proximity ETHNIC liberal minority", echo=FALSE}
-
-# database filter
-
-excl <- names(etlib) %in% c("run", "ID","density","step","eth_con_loc","eth_con_min","val_lib_loc","val_lib_min","val_con_loc","val_con_min")
-etlib_df <- etlib[!excl] %>% filter(eth_lib_loc  == 0)  %>% 
-group_by(eth_lib_min,fraction_blue,circle_blue, circle_orange,eth_lib_min) %>% summarise_all(c("mean"= mean,"sd"= sd))
+group_by(eth_lib_min,fraction_blue,circle_blue, circle_orange) %>% summarise_all(c("mean"= mean,"sd"= sd))
 
@@
 "liberal minority & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD\\\\\n")
-print(etlib_loc50,type = "latex", file = "latex/etlib_min50.tex"  , include.rownames=FALSE, add.to.row = addtorow, include.colnames = FALSE, latex.environments = "center")
+print(etlib_min50,type = "latex", file = "latex/etlib_min50.tex"  , include.rownames=FALSE, add.to.row = addtorow, include.colnames = FALSE, latex.environments = "center")
 
@@
 "liberal minority & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD\\\\\n")
-print(etlib_loc20,type = "latex", file = "latex/etlib_min20.tex" , include.rownames=FALSE, add.to.row = addtorow, include.colnames = FALSE, latex.environments = "center")
+print(etlib_min20,type = "latex", file = "latex/etlib_min20.tex" , include.rownames=FALSE, add.to.row = addtorow, include.colnames = FALSE, latex.environments = "center")
 
@@
 "liberal minority & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD\\\\\n")
-print(etcnmn80,type = "latex", file = "latex/etlib_min80.tex" , include.rownames=FALSE, add.to.row = addtorow, include.colnames = FALSE, latex.environments = "center")
-
-```
-
-<!--
-
-```{r sa_etcnlc50, fig.width=30, fig.cap="Sensitivity ethnic conservative local, baseline asymmetric conditions", echo=FALSE}
-
-# database filter
-excl <- names(sa_asym) %in% c("run", "ID","density","step","eth_lib_loc","val_con_loc","eth_lib_min","val_con_min")
-dataset_sa <- sa_asym[!excl] %>% filter(val_lib_loc  == 20,eth_con_min == 20, val_lib_min == 20)  %>% 
- filter(circle_orange == 50) %>%
-  group_by(eth_con_loc,fraction_blue,circle_blue, circle_orange) %>% summarise_all(c("mean"= mean,"sd"= sd))
-
-xlab_t <- "ß ethnic conservative local"
-
- circle_orange.labs <- c("20% liberal minority", "50% liberal minority", "80% liberal minority")
-names(circle_orange.labs) <- c("20","50","80")
-
-plotname <- "images/etcnlc50.jpg"
-
-# row_exp <- c("\\multicolumn{17}{|c|}{Ethnic asymmetric condition: Exposure, 50% liberal minority}  \\\\\\hline\n",
-#    "Preference &  \\multicolumn{8}{|c|}{Ethnic Exposure} & \\multicolumn{8}{|c|}{Value Exposure}   \\\\\\hline\n",
-#   "& \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  & \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  \\\\\n",
-# "$\\beta$ dom = 20 & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
-# & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
-# & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal}\\\\\n",
-# " & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD\\\\\n")
-# 
-# row_prox <- c("\\multicolumn{17}{|c|}{Ethnic Asymmetric condition: Spatial Proximity, 50% liberal minority}  \\\\\\hline\n",
-#    "Preference &  \\multicolumn{8}{|c|}{Ethnic Proximity} & \\multicolumn{8}{|c|}{Value Proximity}   \\\\\\hline\n",
-#   "& \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  & \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  \\\\\n",
-# "$\\beta$ dom = 20 & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
-# & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
-# & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal}\\\\\n",
-# " & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD\\\\\n")
-#
-
-# tablerb_expname <- "latex/etcnlc50_rb_exp.tex"
-# tablerb_proxname <- "latex/etcnlc50_prox.tex"
-
-# graph
-
-data_exp <- dataset_sa %>% gather(key= subgroup, value = Expo, et_sq_bl_mean, vl_sq_bl_mean, et_cl_bl_mean, vl_cl_bl_mean, et_sq_or_mean, vl_sq_or_mean, et_cl_or_mean, vl_cl_or_mean) %>% mutate(
-  `segregation` = fct_relevel(fct_collapse(subgroup,"ethnics" = c("et_sq_bl_mean","et_cl_bl_mean","et_sq_or_mean","et_cl_or_mean"), "values" = c("vl_sq_bl_mean","vl_cl_bl_mean","vl_sq_or_mean","vl_cl_or_mean")),"ethnics"),
- `orientation` = fct_relevel(fct_collapse(subgroup, "conservative" = c("et_sq_bl_mean","vl_sq_bl_mean","et_sq_or_mean","vl_sq_or_mean"), "liberal" = c("et_cl_bl_mean","vl_cl_bl_mean","et_cl_or_mean","vl_cl_or_mean")),"conservative" ),
- `ethnia` = fct_relevel(fct_collapse(subgroup, "local" = c("et_sq_bl_mean","vl_sq_bl_mean","et_cl_bl_mean","vl_cl_bl_mean"),"minority" = c("et_sq_or_mean","vl_sq_or_mean","et_cl_or_mean","vl_cl_or_mean")), "local"))
-
-fig_exp <- ggplot(data = data_exp, aes(x = eth_con_loc, y = Expo, linetype = `segregation` , color = `ethnia`, shape = `orientation`)) + geom_line()  +  geom_point(size = 3) +
- scale_x_discrete(limits=c(seq(0,20 ,by = 1))) + scale_y_continuous(limits=c(0,1), breaks=seq(0,1,by=0.10)) +
-#  facet_wrap(~ circle_orange, labeller = labeller(circle_orange = circle_orange.labs)) +
-  scale_linetype_manual(values=c("solid","dotted"), labels = c("ethnic","value"), guide = guide_legend(title = "Segregation", order = 1)) +
-  scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
-  scale_shape_manual(values = c("square","circle"), guide = guide_legend(title="Value" ,override.aes = list(size = 3), order = 3)) +
-  xlab("") + ylab("Exposure") + 
-  theme_bw() +  theme( axis.title.x  = element_blank(), axis.title.y = (element_text(size = 15)), axis.text.x  = (element_text(size = 10)) ,axis.text.y =  (element_text(size = 15)), legend.title = element_text(size = 13) ,legend.text = element_text(size = 13), plot.title=element_text(hjust = 0.5)) + theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
-
-# tablerb_exp <- xtable(dataset_sa[,c("dominant","et_sq_bl_mean","et_sq_bl_sd","et_cl_bl_mean","et_cl_bl_sd","et_sq_or_mean","et_sq_or_sd","et_cl_or_mean","et_cl_or_sd","vl_sq_bl_mean","vl_sq_bl_sd","vl_cl_bl_mean","vl_cl_bl_sd","vl_sq_or_mean","vl_sq_or_sd","vl_cl_or_mean","vl_cl_or_sd")], digits = 3)
-# align(tablerb_exp) <- "c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|"
-# 
-# addtorow <- list()
-# addtorow$pos <- list(0, 0,0,0,0)
-# addtorow$command <-  row_exp
-# 
-# print(tablerb_exp,type = "latex", file = tablerb_expname, include.rownames=FALSE, add.to.row = addtorow, include.colnames = FALSE, latex.environments = "center")
-
-## Spatial proximity baseline asymmetric
-
-# graph
-
-data_prox <- dataset_sa %>% gather(key= subgroup, value = Prox, de_sq_bl_mean, dv_sq_bl_mean, de_cl_bl_mean, dv_cl_bl_mean, de_sq_or_mean, dv_sq_or_mean, de_cl_or_mean, dv_cl_or_mean) %>% mutate(
-  `segregation` = fct_relevel(fct_collapse(subgroup,"ethnics" = c("de_sq_bl_mean","de_cl_bl_mean","de_sq_or_mean","de_cl_or_mean"), "values" = c("dv_sq_bl_mean","dv_cl_bl_mean","dv_sq_or_mean","dv_cl_or_mean")),"ethnics"),
- `orientation` = fct_relevel(fct_collapse(subgroup, "conservative" = c("de_sq_bl_mean","dv_sq_bl_mean","de_sq_or_mean","dv_sq_or_mean"), "liberal" = c("de_cl_bl_mean","dv_cl_bl_mean","de_cl_or_mean","dv_cl_or_mean")),"conservative" ),
- `ethnia` = fct_relevel(fct_collapse(subgroup, "local" = c("de_sq_bl_mean","dv_sq_bl_mean","de_cl_bl_mean","dv_cl_bl_mean"),"minority" = c("de_sq_or_mean","dv_sq_or_mean","de_cl_or_mean","dv_cl_or_mean")), "local"))
-
-fig_prox <- ggplot(data = data_prox, aes(x = eth_con_loc, y = Prox, linetype = `segregation` , color = `ethnia`, shape = `orientation`)) + geom_line()  +  geom_point(size = 3) +
- scale_x_discrete(limits=c(seq(0,20 ,by = 1))) + scale_y_continuous(limits=c(min(data_prox$Prox),max(data_prox$Prox)), breaks=seq(0,max(data_prox$Prox),by=0.50)) +
-#☻    facet_wrap(~ circle_orange, labeller = labeller(circle_orange = circle_orange.labs)) +
-  scale_linetype_manual(values=c("solid","dotted"), labels = c("ethnic","value"), guide = guide_legend(title = "Segregation", order = 1)) +
-  scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
-  scale_shape_manual(values = c("square","circle"), guide = guide_legend(title="Value" ,override.aes = list(size = 3), order = 3)) +
-  xlab(xlab_t) + ylab("Spatial Proximity") + 
-  theme_bw() +  theme( axis.title.x = (element_text(size = 15)), axis.title.y = (element_text(size = 15)), axis.text.x =  (element_text(size = 15)),axis.text.y =  (element_text(size = 15)), legend.title = element_text(size = 13) ,legend.text = element_text(size = 13),plot.title=element_text(hjust = 0.5)) + theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
-
-# robustness table
-
-# tablerb_prox <- xtable(dataset_sa[,c("dominant","de_sq_bl_mean","de_sq_bl_sd","de_cl_bl_mean","de_cl_bl_sd","de_sq_or_mean","de_sq_or_sd","de_cl_or_mean","de_cl_or_sd","dv_sq_bl_mean","dv_sq_bl_sd","dv_cl_bl_mean","dv_cl_bl_sd","dv_sq_or_mean","dv_sq_or_sd","dv_cl_or_mean","dv_cl_or_sd")], digits = 3)
-# align(tablerb_prox) <- "c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|"
-# 
-# addtorow <- list()
-# addtorow$pos <- list(0, 0,0,0,0)
-# addtorow$command <-  row_prox
-# print(tablerb_prox,type = "latex", file = tablerb_proxname , include.rownames=FALSE, add.to.row = addtorow, include.colnames = FALSE, latex.environments = "center")
-
-# combined image
-
-ggpubr::ggarrange(fig_exp,fig_prox, nrow = 2, ncol = 1, common.legend = TRUE, legend = "right")
-
-ggsave(plotname,plot = fig_prox,
-  device = NULL,path = NULL, 
-  scale = 1,
-  width = 8,
-  height = 6,
-  units = c("in", "cm", "mm"),
-  dpi = 300,
-  limitsize = FALSE)
-
-```
-
-```{r CODE INDEX FACET  WRAP, fig.width=30, fig.cap="Baseline asymmetric conditions", echo=FALSE}
-
-# database filter
-excl <- names(asym_dom) %in% c("run", "ID","density","step")
-asym_dom_sa <- asym_dom[!excl] %>% group_by(dominant,circle_orange,circle_blue,fraction_blue,secondary) %>% summarise_all(c("mean"= mean,"sd"= sd))
-
-# graph
-# LEAVE! Combined indexes
-data_s <- asym_dom_sa  %>% gather(key= subgroup, value = Segra, de_sq_bl_mean, dv_sq_bl_mean, de_cl_bl_mean, dv_cl_bl_mean, de_sq_or_mean, dv_sq_or_mean, de_cl_or_mean, dv_cl_or_mean,
-       et_sq_bl_mean, vl_sq_bl_mean, et_cl_bl_mean, vl_cl_bl_mean, et_sq_or_mean, vl_sq_or_mean, et_cl_or_mean, vl_cl_or_mean) %>% mutate(
-  `dimensions` = fct_relevel(fct_collapse(subgroup,"ethnic" = c("de_sq_bl_mean","de_cl_bl_mean","de_sq_or_mean","de_cl_or_mean", "et_sq_bl_mean","et_cl_bl_mean","et_sq_or_mean","et_cl_or_mean"), "values" = c("dv_sq_bl_mean","dv_cl_bl_mean","dv_sq_or_mean","dv_cl_or_mean",
-   "vl_sq_bl_mean","vl_cl_bl_mean","vl_sq_or_mean","vl_cl_or_mean")),"ethnic"),
- `orientation` = fct_relevel(fct_collapse(subgroup, "conservative" = c("de_sq_bl_mean","dv_sq_bl_mean","de_sq_or_mean","dv_sq_or_mean",  "et_sq_bl_mean","vl_sq_bl_mean","et_sq_or_mean","vl_sq_or_mean" ), "liberal" = c("de_cl_bl_mean","dv_cl_bl_mean","de_cl_or_mean","dv_cl_or_mean",
-                         "et_cl_bl_mean", "vl_cl_bl_mean", "et_cl_or_mean","vl_cl_or_mean")),"conservative" ),
- `ethnia` = fct_relevel(fct_collapse(subgroup, "local" = c("de_sq_bl_mean","dv_sq_bl_mean","de_cl_bl_mean","dv_cl_bl_mean",
-                                    "et_sq_bl_mean","vl_sq_bl_mean","et_cl_bl_mean", "vl_cl_bl_mean" ),"minority" = c("de_sq_or_mean","dv_sq_or_mean","de_cl_or_mean","dv_cl_or_mean","et_sq_or_mean", "vl_sq_or_mean", "et_cl_or_mean", "vl_cl_or_mean")), "local"),
-  `index` = fct_relevel(fct_collapse(subgroup,  "exposure" = c("et_sq_bl_mean","vl_sq_bl_mean","et_cl_bl_mean", "vl_cl_bl_mean","et_sq_or_mean", "vl_sq_or_mean", "et_cl_or_mean", "vl_cl_or_mean" ), "proximity" = c("de_sq_bl_mean","dv_sq_bl_mean","de_cl_bl_mean","dv_cl_bl_mean","de_sq_or_mean","dv_sq_or_mean","de_cl_or_mean","dv_cl_or_mean")),"exposure"))
-
-data_f <- asym_dom_sa %>% gather(key= subgroup, value = Segra, de_sq_bl_mean, dv_sq_bl_mean, de_cl_bl_mean, dv_cl_bl_mean, de_sq_or_mean, dv_sq_or_mean, de_cl_or_mean, dv_cl_or_mean) %>% mutate(
-  `segregation` = fct_relevel(fct_collapse(subgroup,"ethnics" = c("de_sq_bl_mean","de_cl_bl_mean","de_sq_or_mean","de_cl_or_mean"), "values" = c("dv_sq_bl_mean","dv_cl_bl_mean","dv_sq_or_mean","dv_cl_or_mean")),"ethnics"),
- `orientation` = fct_relevel(fct_collapse(subgroup, "conservative" = c("de_sq_bl_mean","dv_sq_bl_mean","de_sq_or_mean","dv_sq_or_mean"), "liberal" = c("de_cl_bl_mean","dv_cl_bl_mean","de_cl_or_mean","dv_cl_or_mean")),"conservative" ),
- `ethnia` = fct_relevel(fct_collapse(subgroup, "local" = c("de_sq_bl_mean","dv_sq_bl_mean","de_cl_bl_mean","dv_cl_bl_mean"),"minority" = c("de_sq_or_mean","dv_sq_or_mean","de_cl_or_mean","dv_cl_or_mean")), "local"))
-
-data_e <- asym_dom_sa %>% gather(key= subgroup, value = Segra, et_sq_bl_mean, vl_sq_bl_mean, et_cl_bl_mean, vl_cl_bl_mean, et_sq_or_mean, vl_sq_or_mean, et_cl_or_mean, vl_cl_or_mean) %>% mutate(
-  `segregation` = fct_relevel(fct_collapse(subgroup,"ethnics" = c("et_sq_bl_mean","et_cl_bl_mean","et_sq_or_mean","et_cl_or_mean"), "values" = c("vl_sq_bl_mean","vl_cl_bl_mean","vl_sq_or_mean","vl_cl_or_mean")),"ethnics"),
- `orientation` = fct_relevel(fct_collapse(subgroup, "conservative" = c("et_sq_bl_mean","vl_sq_bl_mean","et_sq_or_mean","vl_sq_or_mean"), "liberal" = c("et_cl_bl_mean","vl_cl_bl_mean","et_cl_or_mean","vl_cl_or_mean")),"conservative" ),
- `ethnia` = fct_relevel(fct_collapse(subgroup, "local" = c("et_sq_bl_mean","vl_sq_bl_mean","et_cl_bl_mean","vl_cl_bl_mean"),"minority" = c("et_sq_or_mean","vl_sq_or_mean","et_cl_or_mean","vl_cl_or_mean")), "local"))
-
-ggplot(data = data_f, aes(x = dominant, y = Segra, color = `ethnia` , linetype = `segregation`, shape = `orientation`)) +   geom_point(size = 3) + geom_line() + 
-# scale_color_gradient(low="green", high="red")
- scale_x_discrete(limits=c(seq(0,20 ,by = 1))) + 
- scale_y_continuous(breaks=seq(0,max(data_f$Segra),by=0.25)) +
-  scale_linetype_manual(values=c("solid","dashed"), labels = c("ethnic","value"), guide = guide_legend(title = "Dimension", order = 1)) +
-scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
- scale_shape_manual(values = c("square","circle"), guide = guide_legend(title="Orientation" ,override.aes = list(size = 3), order = 3)) +
-  xlab("ß dominant") + ylab("Index") + 
-# facet_wrap(~ `index`, dir = "v", scales = "free_y") + 
-  geom_blank() +
-  theme_bw() +  theme( axis.title.x = (element_text(size = 15)), axis.title.y = (element_text(size = 15)), axis.text.x =  (element_text(size = 15)),axis.text.y =  (element_text(size = 15)), legend.title = element_text(size = 13) ,legend.text = element_text(size = 13), plot.title=element_text(hjust = 0.5)) + theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
-
-ggsave("images/prox_asym_dom.jpg",plot = last_plot(),
-  device = NULL,path = NULL, 
-  scale = 1,
-  width = 10,
-  height = 4,
-  units = c("in", "cm", "mm"),
-  dpi = 300,
-  limitsize = FALSE)
-
-# robustness table
-
-table_rb <- xtable(asym_dom_sa[,c("dominant","de_sq_bl_mean","de_sq_bl_sd","de_cl_bl_mean","de_cl_bl_sd","de_sq_or_mean","de_sq_or_sd","de_cl_or_mean","de_cl_or_sd","dv_sq_bl_mean","dv_sq_bl_sd","dv_cl_bl_mean","dv_cl_bl_sd","dv_sq_or_mean","dv_sq_or_sd","dv_cl_or_mean","dv_cl_or_sd")], digits = 3)
-align(table_rb) <- "c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|"
-
-addtorow <- list()
-addtorow$pos <- list(0, 0,0,0,0)
-addtorow$command <-  c("\\multicolumn{17}{|c|}{Ethnic Asymmetric condition: Spatial Proximity}  \\\\\\hline\n",
-   "Preference &  \\multicolumn{8}{|c|}{Ethnic Exposure} & \\multicolumn{8}{|c|}{Value Exposure}   \\\\\\hline\n",
-  "& \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  & \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  \\\\\n",
-"$\\beta$ sec = 0 & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
-& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
-& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal}\\\\\n",
-" & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD\\\\\n")
-
-print(table_rb,type = "latex", file = "prox_asym_rb.tex", include.rownames=FALSE, add.to.row = addtorow, include.colnames = FALSE, latex.environments = "center")
-
-A = data.frame(x = rnorm(10),y=rnorm(10))
-B = data.frame(x = rnorm(10),y=rnorm(10))
-ggplot(A,aes(x,y)) +geom_point() +geom_point(data=B,colour='red') + xlim(0, 10)
-
-```
-
-```{r onebeta, fig.pos="H",  fig.width=10, fig.cap="Same parameter for ethnic and value homophily for all agents", echo=FALSE}
-
-base_eq %>% filter(dominant == secondary_square & dominant == secondary_circle & secondary_circle == secondary_square)  %>%  gather(key = subgroup, value = Segra, eth_sqr_loc, eth_sqr_min, eth_crl_loc, eth_crl_min, val_sqr_loc,val_sqr_min,val_crl_loc, val_crl_min) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"ethnic\nsegregation" = c("eth_sqr_loc","eth_sqr_min","eth_crl_loc","eth_crl_min"), "value\nsegregation" = c("val_sqr_loc","val_sqr_min","val_crl_loc", "val_crl_min")), "ethnic segregation"), `group` = fct_relevel(fct_collapse(subgroup, "conservative" = c("eth_sqr_loc","eth_sqr_min","val_sqr_loc","val_sqr_min"), "liberal" = c("eth_crl_loc","eth_crl_min","val_crl_loc", "val_crl_min"), "conservative")),
-  `ethnia` = fct_relevel(fct_collapse(subgroup, "local" = c("eth_sqr_loc","eth_crl_loc","val_sqr_loc","val_crl_loc"), "minority" = c("eth_sqr_min","eth_crl_min","val_sqr_min","val_crl_min")),"local" )) %>%
-
-  ggplot( aes(x = dominant, y = Segra, color = `ethnia`, shape = `group`, linetype = `segregation`  )) + geom_line() + geom_point() +     
-  scale_x_discrete(limits=c(seq(0,20 ,by = 1))) +
-scale_y_continuous(limits=c(0,1), breaks=seq(0,1,by=0.25)) +
-  geom_vline(xintercept = c(1,5,10,20), color = "red") +
-  geom_hline(yintercept = 0.5, color = "red", linetype = 2) +
-  scale_color_manual(values = c("blue","orange"), guide = guide_legend(title="",override.aes = list(size = 2))) +
-  scale_linetype_manual(values = c("solid","dashed"), guide = guide_legend(title="",override.aes = list(size = 1))) +
-  scale_shape_manual(values = c("circle","square"), guide = guide_legend(title="",override.aes = list(size = 3))) + xlab("ß dominant = ß secondary") + ylab("Segregation") +   
-  theme_bw() +  theme( legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(),legend.text = element_text(size = 19),axis.title.x = (element_text(size = 20)), axis.title.y = (element_text(size = 20)), axis.text.x =  (element_text(size = 18)),axis.text.y =  (element_text(size = 18)),
-                      plot.title=element_text(hjust = 0.5),  legend.margin=margin(2,2,2,2)) +
-  theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
-
-ggsave("one_beta.jpg",plot = last_plot(),
-  device = NULL,
-  path = NULL,
-  scale = 1,
-  width = 11,
-  height = 5,
-  units = c("in", "cm", "mm"),
-  dpi = 300,
-  limitsize = FALSE)
-
-```
-
-```{r heatmap,fig.pos="H",  include=TRUE,fig.height=11, fig.width=11, fig.cap="Comparison dominant vs secondary", echo=FALSE}
-
-base_eq  %>% filter(secondary_circle == secondary_square) %>% gather(key = subgroup, value = Segra, eth_sqr,val_sqr,eth_crl,val_crl) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"ethnic segregation" = c("eth_sqr","eth_crl"),"value segregation" = c("val_sqr","val_crl")), "ethnic segregation"),  `group` = fct_relevel(fct_collapse(subgroup,"liberal" = c("eth_crl","val_crl"), "conservative" = c("eth_sqr","val_sqr")),"liberal")) %>%
-
-  ggplot( aes(x = secondary_circle , y = dominant , fill = Segra)) + geom_tile() + 
- facet_grid( group ~  segregation) +
-  xlab("Secondary Beta") + ylab("Dominant Beta") +
-scale_x_discrete(limits=seq(0, 20 ,by = 1)) +
-  scale_y_discrete(limits=seq(0,20 ,by = 1)) + 
-  geom_text(aes(label=round(Segra,2)), size=3) +
-   scale_fill_distiller(palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1), name = "Segregation") + 
-    theme_bw() +  
-  theme(legend.position = "bottom", legend.title = element_text(size = 12,vjust = 0.8), legend.text = element_text(size = 15),  legend.key.width  = unit(1, "inch"), 
-                        legend.key.height  = unit(0.3, "inch"), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0),
-                        axis.title.x = (element_text(size = 18)), axis.title.y = (element_text(size = 18)), axis.text.x =  (element_text(size = 13)),axis.text.y =  (element_text(size = 13)),strip.text.x = element_text(size = 15),
-                        strip.text.y = element_text(size = 15))
-
-ggsave("heatmapbase.jpg",plot = last_plot(),
-  device = NULL,
-  path = NULL,
-  scale = 1,
-  width = NA,
-  height = NA,
-  units = c("in", "cm", "mm"),
-  dpi = 300,
-  limitsize = TRUE)
-
-```
-
-```{r secondary_zero,fig.pos="H",  include=TRUE, fig.width=11,  fig.cap="Secondary preference set to 0. Here only circle minority, patterns are the same", echo=FALSE}
-
-  base_eq  %>% filter(secondary_circle == 0 & secondary_square == 0) %>% gather(key = subgroup, value = Segra, eth_sqr,val_sqr,eth_crl,val_crl) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"ethnic segregation" = c("eth_sqr","eth_crl"),"value segregation" = c("val_sqr","val_crl")), "ethnic segregation"),  `group` = fct_relevel(fct_collapse(subgroup,"liberal" = c("eth_crl","val_crl"), "conservative" = c("eth_sqr","val_sqr")),"liberal")) %>%
-
-  ggplot( aes(x = dominant, y = Segra, color = `segregation`, shape = `group` )) + geom_line() + geom_point(size=3) + scale_x_discrete(limits=seq(0,20 ,by = 1)) +
- scale_y_continuous(breaks=seq(0,1,by = 0.1)) +
-  scale_y_continuous(limits=c(0,1), breaks=seq(0,1,by=0.25)) +
-        geom_vline(xintercept = c(1,5,10,20), color = "red") +
-  geom_hline(yintercept = 0.5, color = "red", linetype = 2) +
-    scale_color_manual(values = c("purple","dark green"), guide = guide_legend(title="")) +
-  scale_linetype_manual(values = c("solid","dashed"), guide = guide_legend(title="")) +
-  scale_shape_manual(values = c("circle","square"), guide = guide_legend(title="")) + xlab("ß dominant") + ylab("Segregation") +   
- theme_bw() +  theme(
-   legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(),legend.text = element_text(size = 18), axis.title.x = (element_text(size = 20)), axis.title.y = (element_text(size = 20)), axis.text.x =  (element_text(size = 18)),axis.text.y =  (element_text(size = 18)),
-                      plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0),
-                     plot.caption = element_text(hjust= 0.5, size = 12)) +
-  labs( caption = "Secondary ß for all agents = 0") +
-  theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
-
-ggsave("secondary_zero.jpg",plot = last_plot(),
-  device = NULL,
-  path = NULL,
-  scale = 1,
-  width = 11,
-  height = 5,
-  units = c("in", "cm", "mm"),
-  dpi = 300,
-  limitsize = FALSE)
-
-```
-
-```{r bas_dom_crl, pos="H",  include=TRUE, fig.width=10,  fig.cap="Sensitivity dominant liberal",    echo=FALSE}
-
-basic_dom <- read.csv("basic/equal_dom_sens.csv", sep = ",", skip = 6)
-names(basic_dom) <- pull(read.csv("basic/legend_bas_sens.csv"))
-
-  basic_dom  %>% filter(secondary_circle == 0, secondary_square == 0, dominant_square == 0) %>% gather(key = subgroup, value = Segra, eth_sqr,val_sqr,eth_crl,val_crl) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"ethnic segregation" = c("eth_sqr","eth_crl"),"value segregation" = c("val_sqr","val_crl")), "ethnic segregation"),  `group` = fct_relevel(fct_collapse(subgroup,"liberal" = c("eth_crl","val_crl"), "conservative" = c("eth_sqr","val_sqr")),"liberal")) %>%
-
-  ggplot( aes(x = dominant_circle, y = Segra, color = `segregation`, shape = `group` )) + geom_line() + geom_point(size=3) + scale_x_discrete(limits=seq(0,20 ,by = 1)) +
-scale_y_continuous(limits=c(0,1), breaks=seq(0,1,by=0.25)) +
-      geom_hline(yintercept = 0.5, color = "red", linetype = 2) +
-
-  scale_color_manual(values = c("purple","dark green"), guide = guide_legend(title="")) +
-  scale_linetype_manual(values = c("solid","dashed"), guide = guide_legend(title="")) +
-  scale_shape_manual(values = c("circle","square"), guide = guide_legend(title=""))   +
-    xlab("ß value liberal") + ylab("Segregation") +   
-      geom_vline(xintercept = c(1,5,10,20), color = "red") +
- theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(),legend.text = element_text(size = 18), axis.title.x = (element_text(size = 20)), axis.title.y = (element_text(size = 20)), axis.text.x =  (element_text(size = 18)),axis.text.y =  (element_text(size = 18)),
-                      plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0),
-                     plot.caption = element_text(hjust= 0.5, size = 12)) +
-labs( caption = "ß ethnic liberal = 0\n ß value and ethnic conservative = 0") +
-  theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
-
-ggsave("bas_dom_crl.jpg",plot = last_plot(),
-  device = NULL,
-  path = NULL,
-  scale = 1,
-  width = 11,
-  height = 7,
-  units = c("in", "cm", "mm"),
-  dpi = 300,
-  limitsize = FALSE)
-
-```
-
-```{r bas_dom_sqr, pos="H",  include=TRUE, fig.width=10,  fig.cap="Sensitivity dominant conservative", echo=FALSE}
-
-basic_dom <- read.csv("basic/equal_dom_sens.csv", sep = ",", skip = 6)
-names(basic_dom) <- pull(read.csv("basic/legend_bas_sens.csv"))
-
-  basic_dom  %>% filter(secondary_circle == 0, secondary_square == 0, dominant_circle == 0) %>% gather(key = subgroup, value = Segra, eth_sqr,val_sqr,eth_crl,val_crl) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"ethnic segregation" = c("eth_sqr","eth_crl"),"value segregation" = c("val_sqr","val_crl")), "ethnic segregation"),  `group` = fct_relevel(fct_collapse(subgroup,"liberal" = c("eth_crl","val_crl"), "conservative" = c("eth_sqr","val_sqr")),"liberal")) %>%
-
-  ggplot( aes(x = dominant_square, y = Segra, color = `segregation`, shape = `group` )) + geom_line() + geom_point(size=3) + scale_x_discrete(limits=seq(0,20 ,by = 1)) +
-scale_y_continuous(limits=c(0,1), breaks=seq(0,1,by=0.25)) +
-  scale_color_manual(values = c("purple","dark green"), guide = guide_legend(title="")) +
-  scale_linetype_manual(values = c("solid","dashed"), guide = guide_legend(title="")) +
-  scale_shape_manual(values = c("circle","square"), guide = guide_legend(title="")) +
-      geom_vline(xintercept = c(1,5,10,20), color = "red") +
-      geom_hline(yintercept = 0.5, color = "red", linetype = 2) +
-    xlab("ß ethnic conservative") + ylab("Segregation") +
-
- theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(),legend.text = element_text(size = 18), axis.title.x = (element_text(size = 20)), axis.title.y = (element_text(size = 20)), axis.text.x =  (element_text(size = 18)),axis.text.y =  (element_text(size = 18)),
-                      plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0),
-                     plot.caption = element_text(hjust= 0.5, size = 12)) +
-  labs( caption = "ß value conservative = 0\n ß value and ethnic liberal = 0") +
-  theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
-
-ggsave("bas_dom_sqr.jpg",plot = last_plot(),
-  device = NULL,
-  path = NULL,
-  scale = 1,
-  width = 11,
-  height = 7,
-  units = c("in", "cm", "mm"),
-  dpi = 300,
-  limitsize = TRUE)
-
-```
-
-```{r random_circle, pos="H",  include=TRUE, fig.width=10,  fig.cap="Sensitivity secondary circle", echo=FALSE}
-
-basic_rand <- read.csv("basic/equal_rand_sens.csv", sep = ",", skip = 6)
-names(basic_rand) <- pull(read.csv("basic/legend_bas_sens.csv"))
-
-  basic_rand  %>% filter(secondary_square == 0) %>% gather(key = subgroup, value = Segra, eth_sqr,val_sqr,eth_crl,val_crl) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"ethnic segregation" = c("eth_sqr","eth_crl"),"value segregation" = c("val_sqr","val_crl")), "ethnic segregation"),  `group` = fct_relevel(fct_collapse(subgroup,"liberal" = c("eth_crl","val_crl"), "conservative" = c("eth_sqr","val_sqr")),"liberal")) %>%
-
-  ggplot( aes(x = secondary_circle, y = Segra, color = `segregation`, shape = `group` )) + geom_line() + geom_point(size=3) + scale_x_discrete(limits=seq(0,20 ,by = 1)) +
-scale_y_continuous(limits=c(0,1), breaks=seq(0,1,by=0.25)) +
-  scale_color_manual(values = c("purple","dark green"), guide = guide_legend(title="")) +
-  scale_linetype_manual(values = c("solid","dashed"), guide = guide_legend(title="")) +
-  scale_shape_manual(values = c("circle","square"), guide = guide_legend(title="")) + 
-      geom_vline(xintercept = c(1,5,10,20), color = "red") +
-      geom_hline(yintercept = 0.5, color = "red", linetype = 2) +
-    xlab("ß ethnic liberal") + ylab("Segregation") +   
- theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(),legend.text = element_text(size = 18), axis.title.x = (element_text(size = 20)), axis.title.y = (element_text(size = 20)), axis.text.x =  (element_text(size = 18)),axis.text.y =  (element_text(size = 18)),
-                      plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0),
-                     plot.caption = element_text(hjust= 0.5, size = 12)) +
-  labs( caption = "ß value liberal = 20; ß ethnic conservative = 20\n ß value conservative = 0") +
-  theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
-
-ggsave("bas_sec_crl.jpg",plot = last_plot(),
-  device = NULL,
-  path = NULL,
-  scale = 1,
-  width = 11,
-  height = 6,
-  units = c("in", "cm", "mm"),
-  dpi = 300,
-  limitsize = TRUE)
-
-```
-
-```{r random_square, pos="H",  include=TRUE, fig.width=10,  fig.cap="Sensitivity secondary circle", echo=FALSE}
-
-basic_rand <- read.csv("basic/equal_rand_sens.csv", sep = ",", skip = 6)
-names(basic_rand) <- pull(read.csv("basic/legend_bas_sens.csv"))
-
-  basic_rand  %>% filter(secondary_circle == 0) %>% gather(key = subgroup, value = Segra, eth_sqr,val_sqr,eth_crl,val_crl) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"ethnic segregation" = c("eth_sqr","eth_crl"),"value segregation" = c("val_sqr","val_crl")), "ethnic segregation"),  `group` = fct_relevel(fct_collapse(subgroup,"liberal" = c("eth_crl","val_crl"), "conservative" = c("eth_sqr","val_sqr")),"liberal")) %>%
-
-  ggplot( aes(x = secondary_square, y = Segra, color = `segregation`, shape = `group` )) + geom_line() + geom_point(size=3) + scale_x_discrete(limits=seq(0,20 ,by = 1)) +
-scale_y_continuous(limits=c(0,1), breaks=seq(0,1,by=0.25)) +
-  scale_color_manual(values = c("purple","dark green"), guide = guide_legend(title="")) +
-  scale_linetype_manual(values = c("solid","dashed"), guide = guide_legend(title="")) +
-  scale_shape_manual(values = c("circle","square"), guide = guide_legend(title="")) + xlab("ß value conservative") + ylab("Segregation") +   
-      geom_vline(xintercept = c(1,5,10,20), color = "red") +
-       geom_hline(yintercept = 0.5, color = "red", linetype = 2) +
- theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(),legend.text = element_text(size = 18), axis.title.x = (element_text(size = 20)), axis.title.y = (element_text(size = 20)), axis.text.x =  (element_text(size = 18)),axis.text.y =  (element_text(size = 18)),
-                      plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0),
-                     plot.caption = element_text(hjust= 0.5, size = 12)) +
-  labs( caption = "ß value liberal = 20, ß ethnic conservative = 20\n ß ethnic liberal = 0") +
-  theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
-
-ggsave("bas_sec_sqr.jpg",plot = last_plot(),
-  device = NULL,
-  path = NULL,
-  scale = 1,
-  width = 11,
-  height = 6,
-  units = c("in", "cm", "mm"),
-  dpi = 300,
-  limitsize = TRUE)
-
-```
-
-# Asymmetric CONDITIONS
-
-```{r asymmetricmech5050, fig.pos="H", include=TRUE,fig.cap="Ethnic asymmetric condition. 80% local, 20% minority. Both 50% liberal", echo=FALSE}
-# 
-# ethnia.labs <- c("Local: 80% population", "Minority: 20% population")
-# names(ethnia.labs) <- c("aaaaa", "minority")
-
-majority_bsa %>%   filter(circle_orange == 50, secondary_circle == 0, secondary_square == 0)  %>%  gather(key = subgroup, value = Segra, eth_sqr_loc, eth_sqr_min, eth_crl_loc, eth_crl_min, val_sqr_loc,val_sqr_min,val_crl_loc, val_crl_min) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"ethnic seg." = c("eth_sqr_loc","eth_sqr_min","eth_crl_loc","eth_crl_min"), "value seg." = c("val_sqr_loc","val_sqr_min","val_crl_loc", "val_crl_min")), "ethnic seg."), `group` = fct_relevel(fct_collapse(subgroup, "conservative" = c("eth_sqr_loc","eth_sqr_min","val_sqr_loc","val_sqr_min"), "liberal" = c("eth_crl_loc","eth_crl_min","val_crl_loc", "val_crl_min"), "conservative")),
-    `ethnia` = fct_relevel(fct_collapse(subgroup, "Locals: 80% population | 50% liberals" = c("eth_sqr_loc","eth_crl_loc","val_sqr_loc","val_crl_loc"), "Migrants: 20% population | 50% liberals" = c("eth_sqr_min","eth_crl_min","val_sqr_min","val_crl_min")),"Locals: 80% population | 50% liberals" )) %>%
-
-  ggplot( aes(x = dominant, y = Segra, color = `segregation`, shape = `group`)) + 
-  geom_line() + geom_point(size = 3) +           scale_x_discrete(limits= seq(0,20 ,by = 1)) +
-  scale_y_continuous(limits=c(0,1), breaks = c(0,0.2,0.5,0.8,1)) +
- #  scale_y_continuous(limits=c(0,1), breaks = c(0.2,0.5,0.8),position = "right") +
-  geom_vline(xintercept = c(1,5,10,20), color = "red") +
-    geom_hline(yintercept = c(0.5), color = "red", linetype = 2) +
-      geom_hline(yintercept = c(0.8), color = "purple", linetype = 5) +
-      geom_hline(yintercept = c(0.2), color = "purple", linetype = 2) +
-# sec.axis = sec_axis( trans=~.*10, name="Second Axis")
-
-  facet_wrap(~ `ethnia`,nrow =2 , dir = "v") +
- scale_color_manual(values = c("purple","dark green"), guide = guide_legend(title= "")) + # ,nrow=2, byrow = TRUE)) +
- scale_shape_manual(values = c("circle","square"), guide = guide_legend(title= "")) + #,nrow=2, byrow = TRUE)) + 
-   xlab("ß Dominant all agents\n ß Secondary all agents = 0") + 
-  ylab("Segregation") +   
-   theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(),legend.text = element_text(size = 12),
-                      axis.title.y = (element_text(size = 12)), # element_blank(),  # 
-                      axis.title.x = (element_text(size = 12)), #   element_blank(), # 
-                      axis.text.x = (element_text(size = 11)),
-                      axis.text.y =  (element_text(size = 11)),
-                      plot.title=element_text(hjust = 0.5),  
-                      legend.margin=margin(0,2,0,0), panel.spacing = unit(0.8, "lines"), 
-                      strip.text.x = element_text(size = 15),  strip.text.y = element_text(size = 15),
-                      plot.caption = element_text(hjust= 0.5, size = 12)) +
-theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
-
-ggsave("diffsize.jpg",plot = last_plot(),
-  device = NULL,
-  path = NULL,
-  scale = 1,
-  width = 5.5,
-  height = 5,
- # units = c("in", "cm", "mm"),
-  dpi = 300,
-  limitsize = TRUE)
-
-```
-
-```{r asymmetricmech5020, fig.pos="H", include=TRUE,fig.cap="Ethnic asymmetric condition. 80% local, 20% minority. Both 80% liberal", echo=FALSE}
-# 
-# ethnia.labs <- c("Local: 80% population", "Minority: 20% population")
-# names(ethnia.labs) <- c("aaaaa", "minority")
-
-majority_bsa %>%   filter(circle_orange == 20, secondary_circle == 0, secondary_square == 0)  %>% gather(key = subgroup, value = Segra, eth_sqr_loc, eth_sqr_min, eth_crl_loc, eth_crl_min, val_sqr_loc,val_sqr_min,val_crl_loc, val_crl_min) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"ethnic seg." = c("eth_sqr_loc","eth_sqr_min","eth_crl_loc","eth_crl_min"), "value seg." = c("val_sqr_loc","val_sqr_min","val_crl_loc", "val_crl_min")), "ethnic seg."), `group` = fct_relevel(fct_collapse(subgroup, "conservative" = c("eth_sqr_loc","eth_sqr_min","val_sqr_loc","val_sqr_min"), "liberal" = c("eth_crl_loc","eth_crl_min","val_crl_loc", "val_crl_min"), "conservative")),
-    `ethnia` = fct_relevel(fct_collapse(subgroup, "Locals: 80% population | 50% liberals" = c("eth_sqr_loc","eth_crl_loc","val_sqr_loc","val_crl_loc"), "Migrants: 20% population | 20% liberals" = c("eth_sqr_min","eth_crl_min","val_sqr_min","val_crl_min")),"Locals: 80% population | 50% liberals" )) %>%
-
-  ggplot( aes(x = dominant, y = Segra, color = `segregation`, shape = `group`)) + 
-  geom_line() + geom_point(size = 3) +           scale_x_discrete(limits= seq(0,20 ,by = 1)) +
-  scale_y_continuous(limits=c(0,1), breaks = c(0,0.2,0.5,0.8,1)) +
- #  scale_y_continuous(limits=c(0,1), breaks = c(0.2,0.5,0.8),position = "right") +
-  geom_vline(xintercept = c(1,5,10,20), color = "red") +
-    geom_hline(yintercept = c(0.5), color = "red", linetype = 2) +
-      geom_hline(yintercept = c(0.8), color = "purple", linetype = 5) +
-      geom_hline(yintercept = c(0.2), color = "purple", linetype = 2) +
-# sec.axis = sec_axis( trans=~.*10, name="Second Axis")
-
-  facet_wrap(~ `ethnia`,nrow =2 , dir = "v") +
- scale_color_manual(values = c("purple","dark green"), guide = guide_legend(title= "")) + # ,nrow=2, byrow = TRUE)) +
- scale_shape_manual(values = c("circle","square"), guide = guide_legend(title= "")) + #,nrow=2, byrow = TRUE)) + 
-   xlab("ß Dominant all agents\n ß Secondary all agents = 0") + 
-  ylab("Segregation") +   
-   theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(),legend.text = element_text(size = 12),
-                      axis.title.y = (element_text(size = 12)), # element_blank(),  # 
-                      axis.title.x = (element_text(size = 12)), #   element_blank(), # 
-                      axis.text.x = (element_text(size = 11)),
-                      axis.text.y =  (element_text(size = 11)),
-                      plot.title=element_text(hjust = 0.5),  
-                      legend.margin=margin(0,2,0,0), panel.spacing = unit(0.8, "lines"), 
-                      strip.text.x = element_text(size = 15),  strip.text.y = element_text(size = 15),
-                      plot.caption = element_text(hjust= 0.5, size = 12)) +
-theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
-
-ggsave("diffsize20.jpg",plot = last_plot(),
-  device = NULL,
-  path = NULL,
-  scale = 1,
-  width = 5.5,
-  height = 5,
- # units = c("in", "cm", "mm"),
-  dpi = 300,
-  limitsize = TRUE)
-
-# +
-#  scale_shape_manual(values = c(16,15), guide = guide_legend(title="")) +
-
-```
-
-```{r asymmetricmech5080, fig.pos="H", include=TRUE,fig.cap="Ethnic asymmetric condition. 80% local, 20% minority. Both 50% liberal", echo=FALSE}
-# 
-# ethnia.labs <- c("Local: 80% population", "Minority: 20% population")
-# names(ethnia.labs) <- c("aaaaa", "minority")
-
-majority_bsa %>%   filter(circle_orange == 80, secondary_circle == 0, secondary_square == 0)  %>% gather(key = subgroup, value = Segra, eth_sqr_loc, eth_sqr_min, eth_crl_loc, eth_crl_min, val_sqr_loc,val_sqr_min,val_crl_loc, val_crl_min) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"ethnic seg." = c("eth_sqr_loc","eth_sqr_min","eth_crl_loc","eth_crl_min"), "value seg." = c("val_sqr_loc","val_sqr_min","val_crl_loc", "val_crl_min")), "ethnic seg."), `group` = fct_relevel(fct_collapse(subgroup, "conservative" = c("eth_sqr_loc","eth_sqr_min","val_sqr_loc","val_sqr_min"), "liberal" = c("eth_crl_loc","eth_crl_min","val_crl_loc", "val_crl_min"), "conservative")),
-    `ethnia` = fct_relevel(fct_collapse(subgroup, "Locals: 80% population | 50% liberals" = c("eth_sqr_loc","eth_crl_loc","val_sqr_loc","val_crl_loc"), "Migrants: 20% population | 80% liberals" = c("eth_sqr_min","eth_crl_min","val_sqr_min","val_crl_min")),"Locals: 80% population | 50% liberals" )) %>%
-
-  ggplot( aes(x = dominant, y = Segra, color = `segregation`, shape = `group`)) + 
-  geom_line() + geom_point(size = 3) +           scale_x_discrete(limits= seq(0,20 ,by = 1)) +
-  scale_y_continuous(limits=c(0,1), breaks = c(0,0.2,0.5,0.8,1)) +
-  geom_vline(xintercept = c(1,5,10,20), color = "red") +
-    geom_hline(yintercept = c(0.5), color = "red", linetype = 2) +
-      geom_hline(yintercept = c(0.8), color = "purple", linetype = 5) +
-      geom_hline(yintercept = c(0.2), color = "purple", linetype = 2) +
-# sec.axis = sec_axis( trans=~.*10, name="Second Axis")
-
-  facet_wrap(~ `ethnia`,nrow =2 , dir = "v") +
- scale_color_manual(values = c("purple","dark green"), guide = guide_legend(title= "")) + # ,nrow=2, byrow = TRUE)) +
- scale_shape_manual(values = c("circle","square"), guide = guide_legend(title= "")) + #,nrow=2, byrow = TRUE)) + 
-    xlab("ß Dominant all agents\n ß Secondary all agents = 0") + 
-  ylab("Segregation") +   
-   theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(),legend.text = element_text(size = 12),
-                      axis.title.y = (element_text(size = 12)), # element_blank(),  # 
-                      axis.title.x = (element_text(size = 12)), #   element_blank(), # 
-                      axis.text.x = (element_text(size = 11)),
-                      axis.text.y =  (element_text(size = 11)),
-                      plot.title=element_text(hjust = 0.5),  
-                      legend.margin=margin(0,2,0,0), panel.spacing = unit(0.8, "lines"), 
-                      strip.text.x = element_text(size = 15),  strip.text.y = element_text(size = 15),
-                      plot.caption = element_text(hjust= 0.5, size = 12)) +
-theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
-
-ggsave("diffsize80.jpg",plot = last_plot(),
-  device = NULL,
-  path = NULL,
-  scale = 1,
-  width = 5.5,
-  height = 5,
- # units = c("in", "cm", "mm"),
-  dpi = 300,
-  limitsize = TRUE)
-
-# +
-#  scale_shape_manual(values = c(16,15), guide = guide_legend(title="")) +
-
-```
-
-## Asymmetric dominant = secondary
-
-```{r asym_sens database, fig.pos="H",include=TRUE,fig.cap="Dominant = Secondary; Migrants change", echo=FALSE}
-
-# Change only in Migrants
-
-domsec_min <- read.csv("maj/sens_asym_min.csv")
-ID <- rep("min", length(domsec_min$run))
-domsec_min <- cbind(ID,domsec_min)
-
-domsec_maj <- read.csv("maj/sens_asym_maj.csv")
-ID <- rep("maj", length(domsec_min$run))
-domsec_maj <- cbind(ID,domsec_maj)
-
-dataset_maj <- rbind(domsec_min,domsec_maj)
-
-dominant_locals.labs <- c("ß Dominant Locals: 0", "ß Dominant Locals: 5","ß Dominant Locals: 10")
-names(dominant_locals.labs) <- c("0", "5", "10")
-circle_orange_labs <- c("20% Liberal Migrants", "50% Liberal Migrants","80% Liberal Migrants")
-names(circle_orange_labs) <- c("20", "50", "80")
-dominant_migrants.labs <- c("ß Dominant Migrants: 0", "ß Dominant Migrants: 5","ß Dominant Migrants: 10")
-names(dominant_migrants.labs) <- c("0", "5", "10")
-dominant_locals.labs <- c("ß Dominant Locals: 0", "ß Dominant Locals: 5","ß Dominant Locals: 10")
-names(dominant_locals.labs) <- c("0", "5", "10")
-
-```
-
-```{r asym_dom_min, fig.pos="H",include=TRUE,fig.cap="Sensitivity assymetry", echo=FALSE}
-
-## Comparison
-
-loc_0 <- dataset_maj  %>% filter(ID == "min") %>% filter(circle_orange == 50) %>% filter(dominant_locals == 0) 
-loc_5 <- dataset_maj  %>% filter(ID == "min") %>% filter(circle_orange == 50) %>% filter(dominant_locals == 5) 
-loc_10 <- dataset_maj  %>% filter(ID == "min") %>% filter(circle_orange == 50) %>% filter(dominant_locals == 10)
-
-df <- loc_10
-name_min <- paste0("loc_10",".jpg")
-
-df %>% gather(key = subgroup, value = Segra, eth_sqr_loc, eth_sqr_min, eth_crl_loc, eth_crl_min, val_sqr_loc,val_sqr_min,val_crl_loc, val_crl_min) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"ethnic seg." = c("eth_sqr_loc","eth_sqr_min","eth_crl_loc","eth_crl_min"), "value seg." = c("val_sqr_loc","val_sqr_min","val_crl_loc", "val_crl_min")), "ethnic seg."),`group` = fct_relevel(fct_collapse(subgroup, "liberal" = c("eth_crl_loc","eth_crl_min","val_crl_loc", "val_crl_min"), "conservative" = c("eth_sqr_loc","eth_sqr_min","val_sqr_loc","val_sqr_min")), "liberal"), `ethnia` = fct_relevel(fct_collapse(subgroup, "Locals:80% ethnic population | 50% liberal" = c("eth_sqr_loc","eth_crl_loc","val_sqr_loc","val_crl_loc"), "Migrants: 20% ethnic population | 50% liberal" = c("eth_sqr_min","eth_crl_min","val_sqr_min","val_crl_min")),"Locals:80% ethnic population | 50% liberal" ))  %>%
-
-  ggplot( aes(x = dominant_migrants, y = Segra, color = `segregation`, shape = `group`)) + geom_line() + geom_point(size = 3) +
-
-  scale_x_discrete(limits= seq(0,20 ,by = 1)) +
-
-  scale_y_continuous(limits=c(0,1), breaks = c(0,0.2,0.5,0.8,1)) +
-  geom_vline(xintercept = c(1,5,10,20), color = "red") +
-    geom_hline(yintercept = c(0.5), color = "red", linetype = 2) +
-      geom_hline(yintercept = c(0.8), color = "purple", linetype = 5) +
-      geom_hline(yintercept = c(0.2), color = "purple", linetype = 2) +
-  facet_wrap( ~ `ethnia`,
-             nrow =2 , dir = "v")  +
-
- scale_color_manual(values = c("purple","dark green"), guide = guide_legend(title= "")) + # ,nrow=2, byrow = TRUE)) +
- scale_shape_manual(values = c("circle","square"), guide = guide_legend(title= "")) + #,nrow=2, byrow = TRUE)) + 
-   ylab("Segregation") +   
-  xlab("ß Dominat Migrants\n ß secondary all agents:0") + 
-#  guides(color = FALSE, shape = FALSE) +
-  ggtitle(paste0("ß dominant locals: ", df$dominant_locals)) +
-  theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(),legend.text = element_text(size = 12),
-                      axis.title.y = (element_text(size = 12)), #     
-                      axis.title.x = (element_text(size = 12)), #   element_blank(),
-
-                     #  axis.title.y = element_blank(),
-                     #  axis.title.x = element_blank(),
-
-                      axis.text.x = (element_text(size = 11)),
-                      axis.text.y =  (element_text(size = 11)),
-                      plot.title=element_text(hjust = 0.5),  
-                      legend.margin=margin(0,2,0,0), panel.spacing = unit(0.8, "lines"), 
-                      strip.text.x = element_text(size = 15),  strip.text.y = element_text(size = 15),
-                      plot.caption = element_text(hjust= 0.5, size = 12)) +
-theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
-
-ggsave(name_min,plot = last_plot(),
-  device = NULL,
-  path = NULL,
-  scale = 1,
-  width = 5.5,
-  height = 5,
- # units = c("in", "cm", "mm"),
-  dpi = 300,
-  limitsize = TRUE)
-
-```
-
-```{r asym_dom_min_dislib, fig.pos="H",include=TRUE,fig.cap="Sensitivity assymetry minority, effect distribution liberal minority", echo=FALSE}
-
-loc_0 <- dataset_maj  %>% filter(ID == "min") %>% filter(circle_orange == 50) %>% filter(dominant_locals == 0) 
-loc_5 <- dataset_maj  %>% filter(ID == "min") %>% filter(circle_orange == 20|circle_orange == 50 | circle_orange == 80) %>% filter(dominant_locals == 5)
-loc_10 <- dataset_maj  %>% filter(ID == "min") %>% filter(circle_orange == 20|circle_orange == 50 | circle_orange == 80) %>% filter(dominant_locals == 10)
-
-df <- loc_10
-name_min <- paste0("loc_10","_dislib.jpg")
-
-df %>% gather(key = subgroup, value = Segra, eth_sqr_loc, eth_sqr_min, eth_crl_loc, eth_crl_min, val_sqr_loc,val_sqr_min,val_crl_loc, val_crl_min) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"ethnic seg." = c("eth_sqr_loc","eth_sqr_min","eth_crl_loc","eth_crl_min"), "value seg." = c("val_sqr_loc","val_sqr_min","val_crl_loc", "val_crl_min")), "ethnic seg."),`group` = fct_relevel(fct_collapse(subgroup, "liberal" = c("eth_crl_loc","eth_crl_min","val_crl_loc", "val_crl_min"), "conservative" = c("eth_sqr_loc","eth_sqr_min","val_sqr_loc","val_sqr_min")), "liberal"), `ethnia` = fct_relevel(fct_collapse(subgroup, "Locals:80% ethnic\n 50% liberal" = c("eth_sqr_loc","eth_crl_loc","val_sqr_loc","val_crl_loc"), "Migrants: 20% ethnic" = c("eth_sqr_min","eth_crl_min","val_sqr_min","val_crl_min")),"Locals:80% ethnic\n 50% liberal" ))  %>%
-
-  ggplot( aes(x = dominant_migrants, y = Segra, color = `segregation`, shape = `group`)) + geom_line() + geom_point(size = 3) +
-
-  scale_x_discrete(limits= seq(0,20 ,by = 1)) +
-
-  scale_y_continuous(limits=c(0,1), breaks = c(0,0.2,0.5,0.8,1)) +
-  geom_vline(xintercept = c(1,5,10,20), color = "red") +
-    geom_hline(yintercept = c(0.5), color = "red", linetype = 2) +
-      geom_hline(yintercept = c(0.8), color = "purple", linetype = 5) +
-      geom_hline(yintercept = c(0.2), color = "purple", linetype = 2) +
-  facet_grid( `ethnia` ~ circle_orange, labeller = labeller(circle_orange = circle_orange_labs)) +
-
- scale_color_manual(values = c("purple","dark green"), guide = guide_legend(title= "")) + # ,nrow=2, byrow = TRUE)) +
- scale_shape_manual(values = c("circle","square"), guide = guide_legend(title= "")) + #,nrow=2, byrow = TRUE)) + 
-   ylab("Segregation") +   
-  xlab("ß Dominat Migrants\n ß secondary all agents:0") + 
-# guides(color = FALSE, shape = FALSE) +
- ggtitle(paste0("ß dominant locals: ", df$dominant_locals)) +
-  theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(),legend.text = element_text(size = 12),
-                     axis.title.y = (element_text(size = 12)), #     
-                     axis.title.x = (element_text(size = 12)), #   element_blank(),
-
-                      #  axis.title.y = element_blank(),
-                      #  axis.title.x = element_blank(),
-
-                      axis.text.x = (element_text(size = 9)),
-                      axis.text.y =  (element_text(size = 9)),
-                      plot.title=element_text(hjust = 0.5),  
-                      legend.margin=margin(0,2,0,0), panel.spacing = unit(0.8, "lines"), 
-                      strip.text.x = element_text(size = 15),  strip.text.y = element_text(size = 15),
-                      plot.caption = element_text(hjust= 0.5, size = 12)) +
-theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
-
-ggsave(name_min,plot = last_plot(),
-  device = NULL,
-  path = NULL,
-  scale = 1.5,
-  width = 8, #7.3,
-  height = 4, #3.8,
- # units = c("in", "cm", "mm"),
-  dpi = 300,
-  limitsize = TRUE)
-
-```
-
-```{r asym_dom_maj, fig.pos="H",include=TRUE,fig.cap="Sensitivity assymetry majority locals", echo=FALSE}
-
-mig_0 <- dataset_maj  %>% filter(ID == "maj") %>% filter(circle_orange == 50) %>% filter(dominant_migrants == 0) 
-mig_5 <- dataset_maj  %>% filter(ID == "maj") %>% filter(circle_orange == 50) %>% filter(dominant_migrants == 5) 
-mig_10 <- dataset_maj  %>% filter(ID == "maj") %>% filter(circle_orange == 50) %>% filter(dominant_migrants == 10)
-
-dfm <- mig_5
-name_maj <- paste0("mig_5",".jpg")
-
-dfm %>% gather(key = subgroup, value = Segra, eth_sqr_loc, eth_sqr_min, eth_crl_loc, eth_crl_min, val_sqr_loc,val_sqr_min,val_crl_loc, val_crl_min) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"ethnic seg." = c("eth_sqr_loc","eth_sqr_min","eth_crl_loc","eth_crl_min"), "value seg." = c("val_sqr_loc","val_sqr_min","val_crl_loc", "val_crl_min")), "ethnic seg."), `group` = fct_relevel(fct_collapse(subgroup, "liberal" = c("eth_crl_loc","eth_crl_min","val_crl_loc", "val_crl_min"), "conservative" = c("eth_sqr_loc","eth_sqr_min","val_sqr_loc","val_sqr_min")), "liberal"),
-  `ethnia` = fct_relevel(fct_collapse(subgroup, "Locals:80% ethnic population | 50% liberal" = c("eth_sqr_loc","eth_crl_loc","val_sqr_loc","val_crl_loc"), "Migrants: 20% ethnic population | 50% liberal" = c("eth_sqr_min","eth_crl_min","val_sqr_min","val_crl_min")),"Locals:80% ethnic population | 50% liberal" ))  %>%
-
-  ggplot( aes(x = dominant_locals, y = Segra, color = `segregation`, shape = `group`)) + geom_line() + geom_point(size = 3) +
-
-  scale_x_discrete(limits= seq(0,20 ,by = 1)) +
-
-scale_y_continuous(limits=c(0,1), breaks = c(0,0.2,0.5,0.8,1)) +
-  geom_vline(xintercept = c(1,5,10,20), color = "red") +
-    geom_hline(yintercept = c(0.5), color = "red", linetype = 2) +
-      geom_hline(yintercept = c(0.8), color = "purple", linetype = 5) +
-      geom_hline(yintercept = c(0.2), color = "purple", linetype = 2) +
-  facet_wrap( ~ `ethnia`,
-             nrow =2 , dir = "v")  +
-
- scale_color_manual(values = c("purple","dark green"), guide = guide_legend(title= "")) + # ,nrow=2, byrow = TRUE)) +
- scale_shape_manual(values = c("circle","square"), guide = guide_legend(title= "")) + #,nrow=2, byrow = TRUE)) + 
-   ylab("Segregation") +   
-  xlab("ß Dominat Locals\n ß secondary all agents:0") + 
-# guides(color = FALSE, shape = FALSE) +
-  ggtitle(paste0("ß dominant migrants: ", dfm$dominant_migrants)) +
-  theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(),legend.text = element_text(size = 12),
-                     # axis.title.y = (element_text(size = 12)), #     
-                     #  axis.title.x = (element_text(size = 12)), #   element_blank(),
-
-                     axis.title.y = element_blank(),
-                      axis.title.x = element_blank(),
-                      axis.text.x = (element_text(size = 11)),
-                      axis.text.y =  (element_text(size = 11)),
-                      plot.title=element_text(hjust = 0.5),  
-                      legend.margin=margin(0,2,0,0), panel.spacing = unit(0.8, "lines"), 
-                      strip.text.x = element_text(size = 15),  strip.text.y = element_text(size = 15),
-                      plot.caption = element_text(hjust= 0.5, size = 12)) +
-theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
-
-ggsave(name_maj,plot = last_plot(),
-  device = NULL,
-  path = NULL,
-  scale = 1,
-  width = 5.5,
-  height = 5,
- # units = c("in", "cm", "mm"),
-  dpi = 300,
-  limitsize = TRUE)
-
-```
-
-```{r asym_dom_maj_dislib, fig.pos="H",include=TRUE,fig.cap="Sensitivity assymetry majority locals, effect liberal migrants distribution", echo=FALSE}
-
-# mig_0 <- dataset_maj  %>% filter(ID == "maj") %>% filter(circle_orange == 50) %>% filter(dominant_migrants == 0) 
-mig_5 <- dataset_maj  %>% filter(ID == "maj") %>% filter(circle_orange == 20 | circle_orange == 50 |circle_orange == 80) %>% filter(dominant_migrants == 5) 
-mig_10 <- dataset_maj  %>% filter(ID == "maj") %>% filter(circle_orange == 20 | circle_orange == 50 |circle_orange == 80) %>% filter(dominant_migrants == 10)
-
-dfm <- mig_5
-name_maj <- paste0("mig_5","_dislib.jpg")
-
-dfm %>% gather(key = subgroup, value = Segra, eth_sqr_loc, eth_sqr_min, eth_crl_loc, eth_crl_min, val_sqr_loc,val_sqr_min,val_crl_loc, val_crl_min) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"ethnic seg." = c("eth_sqr_loc","eth_sqr_min","eth_crl_loc","eth_crl_min"), "value seg." = c("val_sqr_loc","val_sqr_min","val_crl_loc", "val_crl_min")), "ethnic seg."),`group` = fct_relevel(fct_collapse(subgroup, "liberal" = c("eth_crl_loc","eth_crl_min","val_crl_loc", "val_crl_min"), "conservative" = c("eth_sqr_loc","eth_sqr_min","val_sqr_loc","val_sqr_min")), "liberal"), `ethnia` = fct_relevel(fct_collapse(subgroup, "Locals:80% ethnic\n 50% liberal" = c("eth_sqr_loc","eth_crl_loc","val_sqr_loc","val_crl_loc"), "Migrants: 20% ethnic" = c("eth_sqr_min","eth_crl_min","val_sqr_min","val_crl_min")),"Locals:80% ethnic\n 50% liberal" ))  %>%
-
-  ggplot( aes(x = dominant_locals, y = Segra, color = `segregation`, shape = `group`)) + geom_line() + geom_point(size = 3) +
-
-  scale_x_discrete(limits= seq(0,20 ,by = 1)) +
-
-scale_y_continuous(limits=c(0,1), breaks = c(0,0.2,0.5,0.8,1)) +
-  geom_vline(xintercept = c(1,5,10,20), color = "red") +
-    geom_hline(yintercept = c(0.5), color = "red", linetype = 2) +
-      geom_hline(yintercept = c(0.8), color = "purple", linetype = 5) +
-      geom_hline(yintercept = c(0.2), color = "purple", linetype = 2) +
-  facet_grid( `ethnia` ~ circle_orange, labeller = labeller(circle_orange = circle_orange_labs)) + 
- scale_color_manual(values = c("purple","dark green"), guide = guide_legend(title= "")) + # ,nrow=2, byrow = TRUE)) +
- scale_shape_manual(values = c("circle","square"), guide = guide_legend(title= "")) + #,nrow=2, byrow = TRUE)) + 
-   ylab("Segregation") +   
-  xlab("ß Dominat Locals\n ß secondary all agents:0") + 
-# guides(color = FALSE, shape = FALSE) +
-  ggtitle(paste0("ß dominant migrants: ", dfm$dominant_migrants)) +
-  theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(),legend.text = element_text(size = 12),
-                      axis.title.y = (element_text(size = 12)), #     
-                      axis.title.x = (element_text(size = 12)), #   element_blank(),
-
-                    # axis.title.y = element_blank(),
-                    #   axis.title.x = element_blank(),
-                      axis.text.x = (element_text(size = 11)),
-                      axis.text.y =  (element_text(size = 11)),
-                      plot.title=element_text(hjust = 0.5),  
-                      legend.margin=margin(0,2,0,0), panel.spacing = unit(0.8, "lines"), 
-                      strip.text.x = element_text(size = 15),  strip.text.y = element_text(size = 15),
-                      plot.caption = element_text(hjust= 0.5, size = 12)) +
-theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
-
-ggsave(name_maj, plot = last_plot(),
-  device = NULL,
-  path = NULL,
-  scale = 1.5,
-  width = 8,
-  height = 4,
- # units = c("in", "cm", "mm"),
-  dpi = 300,
-  limitsize = TRUE)
-
-```
-
-# Increase in ethnnic liberal
-
-```{r libethn database, fig.width= 7,fig.height= 6, fig.pos="H",include=TRUE,fig.cap="Increase in  ethnic liberal", echo=FALSE}
-
-hc_hc <- read.csv("maj/maj_min_20-20-table.csv", sep = ",", skip = 6)
-names(hc_hc) <- pull(read.csv("maj/leg_maj_sens.csv"))
-ID <- rep("hc_hc", length(hc_hc$run))
-hc_hc <- cbind(ID,hc_hc)
-
-hc_lc <- read.csv("maj/maj_min_20-5-table.csv", sep = ",", skip = 6)
-names(hc_lc) <- pull(read.csv("maj/leg_maj_sens.csv"))
-ID <- rep("hc_lc", length(hc_lc$run))
-hc_lc <- cbind(ID,hc_lc)
-
-lc_hc <- read.csv("maj/maj_min_5-20-table.csv", sep = ",", skip = 6)
-names(lc_hc) <- pull(read.csv("maj/leg_maj_sens.csv"))
-ID <- rep("lc_hc",length(lc_hc$run))
-lc_hc <- cbind(ID,lc_hc)
-
-lc_lc <- read.csv("maj/maj_min_5-5-table.csv", sep = ",", skip = 6)
-names(lc_lc) <- pull(read.csv("maj/leg_maj_sens.csv"))
-ID <- rep("lc_lc",length(lc_lc$run))
-lc_lc <- cbind(ID,lc_lc)
-
-df_eth_loc <- rbind(hc_hc,hc_lc,lc_hc,lc_lc)
-#rm(hc_hc,hc_lc,lc_hc,lc_lc)
-
-```
-
-# Final
-
-```{r rand50, fig.width= 8,fig.height= 7, fig.pos="H",include=TRUE,fig.cap="Individual comparison rand 50", echo=FALSE}
-
-eth_min_lib.labs <- c("ß Ethnic liberal migrants: 0", "ß Ethnic liberal migrants: 1", "ß Ethnic liberal migrants: 2","ß Ethnic liberal migrants: 3","ß Ethnic liberal migrants: 4","ß Ethnic liberal migrants: 5","ß Ethnic liberal migrants: 10","ß Ethnic liberal migrants: 15","ß Ethnic liberal migrants: 20")
-names(eth_min_lib.labs) <- c("0","1","2","3","4", "5","10","15","20")
-eth_loc_lib.labs <- c("ß Ethnic liberal locals: 0", "ß Ethnic liberal locals: 1", "ß Ethnic liberal locals: 2","ß Ethnic liberal locals: 3","ß Ethnic liberal locals: 4","ß Ethnic liberal locals: 5","ß Ethnic liberal locals: 10","ß Ethnic liberal locals: 15","ß Ethnic liberal locals: 20")
-names(eth_loc_lib.labs) <-  c("0","1","2","3","4", "5","10","15","20")
-
-# Intermediate randomness Migrants x-axys
-
- df_eth_loc  %>% filter(ID == "lc_hc") %>% filter(circle_orange == 50)  %>% filter(eth_loc_lib == 0 | eth_loc_lib == 1 | eth_loc_lib == 3 | eth_loc_lib == 5) %>% gather(key = subgroup, value = Segra, eth_sqr_loc, eth_sqr_min, eth_crl_loc, eth_crl_min, val_sqr_loc,val_sqr_min,val_crl_loc, val_crl_min) %>%mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"ethnic seg." = c("eth_sqr_loc","eth_sqr_min","eth_crl_loc","eth_crl_min"), "value seg." = c("val_sqr_loc","val_sqr_min","val_crl_loc", "val_crl_min")), "ethnic seg."), `group` = fct_relevel(fct_collapse(subgroup, "liberal" = c("eth_crl_loc","eth_crl_min","val_crl_loc", "val_crl_min"), "conservative" = c("eth_sqr_loc","eth_sqr_min","val_sqr_loc","val_sqr_min")), "liberal"),
-  `ethnia` = fct_relevel(fct_collapse(subgroup, "Locals:80% ethnic\n 50% liberal" = c("eth_sqr_loc","eth_crl_loc","val_sqr_loc","val_crl_loc"), "Migrants: 20% ethnic\n 50% liberal" = c("eth_sqr_min","eth_crl_min","val_sqr_min","val_crl_min")),"Locals:80% ethnic\n 50% liberal" ))  %>%
-
-  ggplot( aes(x = eth_min_lib, y = Segra, color = `segregation`, shape = `group` )) + geom_line() + geom_point(size = 3) +
-
-  scale_x_discrete(limits= c(0,1,2,3,4,5,10,15,20)) +
-
-  scale_y_continuous(limits=c(0,1), breaks = c(0,0.2,0.5,0.8,1)) +
-  geom_vline(xintercept = c(1,5,10,20), color = "red") +
-    geom_hline(yintercept = c(0.5), color = "red", linetype = 2) +
-      geom_hline(yintercept = c(0.8), color = "purple", linetype = 5) +
-      geom_hline(yintercept = c(0.2), color = "purple", linetype = 2) +
-  facet_grid(`ethnia` ~ eth_loc_lib, labeller = labeller(eth_loc_lib = eth_loc_lib.labs, circle_orange = circle_orange_labs)) +
-               #nrow =2 , dir = "v")  +
-
- scale_color_manual(values = c("purple","dark green"), guide = guide_legend(title= "")) + # ,nrow=2, byrow = TRUE)) +
- scale_shape_manual(values = c("circle","square"), guide = guide_legend(title= "")) + #,nrow=2, byrow = TRUE)) + 
-   ylab("Segregation") +   
-  xlab("Ethnic liberal migrants") + 
-#  guides(color = FALSE, shape = FALSE) +
-ggtitle("ß dominant migrants: 20\nß dominant locals: 5") +
-  theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(),legend.text = element_text(size = 12),
-                      axis.title.y =   (element_text(size = 12)), # element_blank(),  # 
-                      axis.title.x =  (element_text(size = 14)), #   element_blank(),  # 
-                      axis.text.x = (element_text(size = 10)),
-                      axis.text.y =  (element_text(size = 10)),
-                      plot.title=element_text(face="bold", size = 14),   
-                      legend.margin=margin(0,0,0,0), panel.spacing = unit(0.8, "lines"), 
-                      strip.text.x = element_text(size = 15),  strip.text.y = element_text(size = 15),
-                      plot.caption = element_text(hjust= 0.5, size = 12)) +
-theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
-
-ggsave("lc_hc5_min.jpg",last_plot(),
-  device = NULL,
-  path = NULL,
-  scale = 2,
-  width = 6,
-  height = 3,
- # units = ("in", "cm", "mm"),
-  dpi = 300,
-  limitsize = TRUE)
-
-# Intermediate randomness Locals x-axys
-
-df_eth_loc  %>% filter(ID == "hc_lc") %>% filter(circle_orange == 50)  %>% filter(eth_min_lib == 0 | eth_min_lib == 1 | eth_min_lib == 3 |   eth_min_lib == 5) %>% gather(key = subgroup, value = Segra, eth_sqr_loc, eth_sqr_min, eth_crl_loc, eth_crl_min, val_sqr_loc,val_sqr_min,val_crl_loc, val_crl_min) %>%mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"ethnic seg." = c("eth_sqr_loc","eth_sqr_min","eth_crl_loc","eth_crl_min"), "value seg." = c("val_sqr_loc","val_sqr_min","val_crl_loc", "val_crl_min")), "ethnic seg."), `group` = fct_relevel(fct_collapse(subgroup, "liberal" = c("eth_crl_loc","eth_crl_min","val_crl_loc", "val_crl_min"), "conservative" = c("eth_sqr_loc","eth_sqr_min","val_sqr_loc","val_sqr_min")), "liberal"),
-  `ethnia` = fct_relevel(fct_collapse(subgroup, "Locals:80% ethnic\n 50% liberal" = c("eth_sqr_loc","eth_crl_loc","val_sqr_loc","val_crl_loc"), "Migrants: 20% ethnic\n 50% liberal" = c("eth_sqr_min","eth_crl_min","val_sqr_min","val_crl_min")),"Locals:80% ethnic\n 50% liberal" ))  %>%
-
-  ggplot( aes(x = eth_loc_lib, y = Segra, color = `segregation`, shape = `group` )) + geom_line() + geom_point(size = 3) +
-
-  scale_x_discrete(limits= c(0,1,2,3,4,5,10,15,20)) +
-
-  scale_y_continuous(limits=c(0,1), breaks = c(0,0.2,0.5,0.8,1)) +
-  geom_vline(xintercept = c(1,5,10,20), color = "red") +
-    geom_hline(yintercept = c(0.5), color = "red", linetype = 2) +
-      geom_hline(yintercept = c(0.8), color = "purple", linetype = 5) +
-      geom_hline(yintercept = c(0.2), color = "purple", linetype = 2) +
-  facet_grid(`ethnia` ~ eth_min_lib, labeller = labeller(eth_min_lib = eth_min_lib.labs, circle_orange = circle_orange_labs)) +
-               #nrow =2 , dir = "v")  +
-
- scale_color_manual(values = c("purple","dark green"), guide = guide_legend(title= "")) + # ,nrow=2, byrow = TRUE)) +
- scale_shape_manual(values = c("circle","square"), guide = guide_legend(title= "")) + #,nrow=2, byrow = TRUE)) + 
-   ylab("Segregation") +   
-  xlab("ethnic liberal locals") + 
-# guides(color = FALSE, shape = FALSE) +
-xlab("Ethnic liberal locals") + 
-# guides(color = FALSE, shape = FALSE) +
-ggtitle("ß dominant locals: 20\nß dominant migrants: 5") +
-  theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(),legend.text = element_text(size = 12),
-                      axis.title.y =   (element_text(size = 12)), # element_blank(),  # 
-                      axis.title.x =  (element_text(size = 14)), #   element_blank(),  # 
-                      axis.text.x = (element_text(size = 10)),
-                      axis.text.y =  (element_text(size = 10)),
-                      plot.title=element_text(face="bold", size = 14),   
-                      legend.margin=margin(0,0,0,0), panel.spacing = unit(0.8, "lines"), 
-                      strip.text.x = element_text(size = 15),  strip.text.y = element_text(size = 15),
-                      plot.caption = element_text(hjust= 0.5, size = 12)) +
-theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
-
-# 
-# comb <- ggarrange(mig,loc, nrow =  2, common.legend = TRUE, legend = "bottom")
-# annotate_figure(comb, 
-#                # top = text_grob("Dominant ß: 5",  face = "bold", size = 12),
-#                left = text_grob("Segregation", rot = 90, size = 12),
-#                 bottom = text_grob("ß value conservative both group: 0", hjust = 1, x = 1, size = 12),
-#                 )
-
-ggsave("lc_hc5_maj.jpg",last_plot(),
-  device = NULL,
-  path = NULL,
-   scale = 2,
-  width = 6,
-  height = 3,
- # units = c("in", "cm", "mm"),
-  dpi = 300,
-  limitsize = TRUE)
-
-```
-
-```{r det50, fig.width= 8,fig.height= 7, fig.pos="H",include=TRUE,fig.cap="Individual comparison determinism beta 20", echo=FALSE}
-
-eth_min_lib.labs <- c("ß Ethnic liberal migrants: 0", "ß Ethnic liberal migrants: 1", "ß Ethnic liberal migrants: 2","ß Ethnic liberal migrants: 3","ß Ethnic liberal migrants: 4","ß Ethnic liberal migrants: 5","ß Ethnic liberal migrants: 10","ß Ethnic liberal migrants: 15","ß Ethnic liberal migrants: 20")
-names(eth_min_lib.labs) <- c("0","1","2","3","4", "5","10","15","20")
-eth_loc_lib.labs <- c("ß Ethnic liberal locals: 0", "ß Ethnic liberal locals: 1", "ß Ethnic liberal locals: 2","ß Ethnic liberal locals: 3","ß Ethnic liberal locals: 4","ß Ethnic liberal locals: 5","ß Ethnic liberal locals: 10","ß Ethnic liberal locals: 15","ß Ethnic liberal locals: 20")
-names(eth_loc_lib.labs) <-  c("0","1","2","3","4", "5","10","15","20")
-
-# Intermediate randomness Migrants x-axys
-
- df_eth_loc  %>% filter(ID == "hc_hc") %>% filter(circle_orange == 50)  %>% filter(eth_loc_lib == 0 | eth_loc_lib == 5 | eth_loc_lib == 10 | eth_loc_lib == 20) %>% gather(key = subgroup, value = Segra, eth_sqr_loc, eth_sqr_min, eth_crl_loc, eth_crl_min, val_sqr_loc,val_sqr_min,val_crl_loc, val_crl_min) %>%mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"ethnic seg." = c("eth_sqr_loc","eth_sqr_min","eth_crl_loc","eth_crl_min"), "value seg." = c("val_sqr_loc","val_sqr_min","val_crl_loc", "val_crl_min")), "ethnic seg."), `group` = fct_relevel(fct_collapse(subgroup, "liberal" = c("eth_crl_loc","eth_crl_min","val_crl_loc", "val_crl_min"), "conservative" = c("eth_sqr_loc","eth_sqr_min","val_sqr_loc","val_sqr_min")), "liberal"),
-  `ethnia` = fct_relevel(fct_collapse(subgroup, "Locals:80% ethnic\n 50% liberal" = c("eth_sqr_loc","eth_crl_loc","val_sqr_loc","val_crl_loc"), "Migrants: 20% ethnic\n 50% liberal" = c("eth_sqr_min","eth_crl_min","val_sqr_min","val_crl_min")),"Locals:80% ethnic\n 50% liberal" ))  %>%
-
-  ggplot( aes(x = eth_min_lib, y = Segra, color = `segregation`, shape = `group` )) + geom_line() + geom_point(size = 3) +
-
-  scale_x_discrete(limits= c(0,1,2,3,4,5,10,15,20)) +
-
-  scale_y_continuous(limits=c(0,1), breaks = c(0,0.2,0.5,0.8,1)) +
-  geom_vline(xintercept = c(1,5,10,20), color = "red") +
-    geom_hline(yintercept = c(0.5), color = "red", linetype = 2) +
-      geom_hline(yintercept = c(0.8), color = "purple", linetype = 5) +
-      geom_hline(yintercept = c(0.2), color = "purple", linetype = 2) +
-  facet_grid(`ethnia` ~ eth_loc_lib, labeller = labeller(eth_loc_lib = eth_loc_lib.labs, circle_orange = circle_orange_labs)) +
-               #nrow =2 , dir = "v")  +
-
- scale_color_manual(values = c("purple","dark green"), guide = guide_legend(title= "")) + # ,nrow=2, byrow = TRUE)) +
- scale_shape_manual(values = c("circle","square"), guide = guide_legend(title= "")) + #,nrow=2, byrow = TRUE)) + 
-   ylab("Segregation") +   
-  xlab("Ethnic liberal migrants") + 
-# guides(color = FALSE, shape = FALSE) +
-ggtitle("ß dominant migrants: 20\nß dominant locals: 20") +
-  theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(),legend.text = element_text(size = 12),
-                      axis.title.y =   (element_text(size = 12)), # element_blank(),  # 
-                      axis.title.x =  (element_text(size = 14)), #   element_blank(),  # 
-                      axis.text.x = (element_text(size = 10)),
-                      axis.text.y =  (element_text(size = 10)),
-                      plot.title=element_text(face="bold", size = 14),   
-                      legend.margin=margin(0,0,0,0), panel.spacing = unit(0.8, "lines"), 
-                      strip.text.x = element_text(size = 15),  strip.text.y = element_text(size = 15),
-                      plot.caption = element_text(hjust= 0.5, size = 12)) +
-theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
-
-ggsave("hc_hc5_min.jpg",last_plot(),
-  device = NULL,
-  path = NULL,
-  scale = 2,
-  width = 6,
-  height = 3,
- # units = ("in", "cm", "mm"),
-  dpi = 300,
-  limitsize = TRUE)
-
-# Intermediate randomness Locals x-axys
-
-df_eth_loc  %>% filter(ID == "hc_hc") %>% filter(circle_orange == 50)  %>%  filter(eth_min_lib == 0 | eth_min_lib == 5 | eth_min_lib == 10 | eth_min_lib == 20)  %>% gather(key = subgroup, value = Segra, eth_sqr_loc, eth_sqr_min, eth_crl_loc, eth_crl_min, val_sqr_loc,val_sqr_min,val_crl_loc, val_crl_min) %>%mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"ethnic seg." = c("eth_sqr_loc","eth_sqr_min","eth_crl_loc","eth_crl_min"), "value seg." = c("val_sqr_loc","val_sqr_min","val_crl_loc", "val_crl_min")), "ethnic seg."), `group` = fct_relevel(fct_collapse(subgroup, "liberal" = c("eth_crl_loc","eth_crl_min","val_crl_loc", "val_crl_min"), "conservative" = c("eth_sqr_loc","eth_sqr_min","val_sqr_loc","val_sqr_min")), "liberal"),
-  `ethnia` = fct_relevel(fct_collapse(subgroup, "Locals:80% ethnic\n 50% liberal" = c("eth_sqr_loc","eth_crl_loc","val_sqr_loc","val_crl_loc"), "Migrants: 20% ethnic\n 50% liberal" = c("eth_sqr_min","eth_crl_min","val_sqr_min","val_crl_min")),"Locals:80% ethnic\n 50% liberal" ))  %>%
-
-  ggplot( aes(x = eth_loc_lib, y = Segra, color = `segregation`, shape = `group` )) + geom_line() + geom_point(size = 3) +
-
-  scale_x_discrete(limits= c(0,1,2,3,4,5,10,15,20)) +
-
-  scale_y_continuous(limits=c(0,1), breaks = c(0,0.2,0.5,0.8,1)) +
-  geom_vline(xintercept = c(1,5,10,20), color = "red") +
-    geom_hline(yintercept = c(0.5), color = "red", linetype = 2) +
-      geom_hline(yintercept = c(0.8), color = "purple", linetype = 5) +
-      geom_hline(yintercept = c(0.2), color = "purple", linetype = 2) +
-  facet_grid(`ethnia` ~ eth_min_lib, labeller = labeller(eth_min_lib = eth_min_lib.labs, circle_orange = circle_orange_labs)) +
-               #nrow =2 , dir = "v")  +
-
- scale_color_manual(values = c("purple","dark green"), guide = guide_legend(title= "")) + # ,nrow=2, byrow = TRUE)) +
- scale_shape_manual(values = c("circle","square"), guide = guide_legend(title= "")) + #,nrow=2, byrow = TRUE)) + 
-   ylab("Segregation") +   
-  xlab("ethnic liberal locals") + 
-# guides(color = FALSE, shape = FALSE) +
-xlab("Ethnic liberal locals") + 
- guides(color = FALSE, shape = FALSE) +
-ggtitle("ß dominant locals: 20\nß dominant migrants: 20") +
-  theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(),legend.text = element_text(size = 12),
-                      axis.title.y =   (element_text(size = 12)), # element_blank(),  # 
-                      axis.title.x =  (element_text(size = 14)), #   element_blank(),  # 
-                      axis.text.x = (element_text(size = 10)),
-                      axis.text.y =  (element_text(size = 10)),
-                      plot.title=element_text(face="bold", size = 14),   
-                      legend.margin=margin(0,0,0,0), panel.spacing = unit(0.8, "lines"), 
-                      strip.text.x = element_text(size = 15),  strip.text.y = element_text(size = 15),
-                      plot.caption = element_text(hjust= 0.5, size = 12)) +
-theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
-
-ggsave("hc_hc5_maj.jpg",last_plot(),
-  device = NULL,
-  path = NULL,
-   scale = 2,
-  width = 6,
-  height = 3,
- # units = c("in", "cm", "mm"),
-  dpi = 300,
-  limitsize = TRUE)
-
-#######
-#######
-
-# Intermediate randomness Migrants x-axys
-
- df_eth_loc  %>% filter(ID == "lc_lc") %>% filter(circle_orange == 50)  %>% filter(eth_loc_lib == 0 | eth_loc_lib == 1 | eth_loc_lib == 3 | eth_loc_lib == 5) %>% gather(key = subgroup, value = Segra, eth_sqr_loc, eth_sqr_min, eth_crl_loc, eth_crl_min, val_sqr_loc,val_sqr_min,val_crl_loc, val_crl_min) %>%mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"ethnic seg." = c("eth_sqr_loc","eth_sqr_min","eth_crl_loc","eth_crl_min"), "value seg." = c("val_sqr_loc","val_sqr_min","val_crl_loc", "val_crl_min")), "ethnic seg."), `group` = fct_relevel(fct_collapse(subgroup, "liberal" = c("eth_crl_loc","eth_crl_min","val_crl_loc", "val_crl_min"), "conservative" = c("eth_sqr_loc","eth_sqr_min","val_sqr_loc","val_sqr_min")), "liberal"),
-  `ethnia` = fct_relevel(fct_collapse(subgroup, "Locals:80% ethnic\n 50% liberal" = c("eth_sqr_loc","eth_crl_loc","val_sqr_loc","val_crl_loc"), "Migrants: 20% ethnic\n 50% liberal" = c("eth_sqr_min","eth_crl_min","val_sqr_min","val_crl_min")),"Locals:80% ethnic\n 50% liberal" ))  %>%
-
-  ggplot( aes(x = eth_min_lib, y = Segra, color = `segregation`, shape = `group` )) + geom_line() + geom_point(size = 3) +
-
-  scale_x_discrete(limits= c(0,1,2,3,4,5)) +
-
-  scale_y_continuous(limits=c(0,1), breaks = c(0,0.2,0.5,0.8,1)) +
-  geom_vline(xintercept = c(1,5), color = "red") +
-    geom_hline(yintercept = c(0.5), color = "red", linetype = 2) +
-      geom_hline(yintercept = c(0.8), color = "purple", linetype = 5) +
-      geom_hline(yintercept = c(0.2), color = "purple", linetype = 2) +
-  facet_grid(`ethnia` ~ eth_loc_lib, labeller = labeller(eth_loc_lib = eth_loc_lib.labs, circle_orange = circle_orange_labs)) +
-               #nrow =2 , dir = "v")  +
-
- scale_color_manual(values = c("purple","dark green"), guide = guide_legend(title= "")) + # ,nrow=2, byrow = TRUE)) +
- scale_shape_manual(values = c("circle","square"), guide = guide_legend(title= "")) + #,nrow=2, byrow = TRUE)) + 
-   ylab("Segregation") +   
-  xlab("Ethnic liberal migrants") + 
-# guides(color = FALSE, shape = FALSE) +
-ggtitle("ß dominant migrants: 5\nß dominant locals: 5") +
-  theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(),legend.text = element_text(size = 12),
-                      axis.title.y =   (element_text(size = 12)), # element_blank(),  # 
-                      axis.title.x =  (element_text(size = 14)), #   element_blank(),  # 
-                      axis.text.x = (element_text(size = 10)),
-                      axis.text.y =  (element_text(size = 10)),
-                      plot.title=element_text(face="bold", size = 14),   
-                      legend.margin=margin(0,0,0,0), panel.spacing = unit(0.8, "lines"), 
-                      strip.text.x = element_text(size = 15),  strip.text.y = element_text(size = 15),
-                      plot.caption = element_text(hjust= 0.5, size = 12)) +
-theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
-
-ggsave("lc_lc5_min.jpg",last_plot(),
-  device = NULL,
-  path = NULL,
-  scale = 2,
-  width = 6,
-  height = 3,
- # units = ("in", "cm", "mm"),
-  dpi = 300,
-  limitsize = TRUE)
-
-# Intermediate randomness Locals x-axys
-
-df_eth_loc  %>% filter(ID == "lc_lc") %>% filter(circle_orange == 50)  %>%  filter(eth_min_lib == 0 | eth_min_lib == 1 | eth_min_lib == 3 | eth_min_lib == 5)  %>% gather(key = subgroup, value = Segra, eth_sqr_loc, eth_sqr_min, eth_crl_loc, eth_crl_min, val_sqr_loc,val_sqr_min,val_crl_loc, val_crl_min) %>%mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"ethnic seg." = c("eth_sqr_loc","eth_sqr_min","eth_crl_loc","eth_crl_min"), "value seg." = c("val_sqr_loc","val_sqr_min","val_crl_loc", "val_crl_min")), "ethnic seg."), `group` = fct_relevel(fct_collapse(subgroup, "liberal" = c("eth_crl_loc","eth_crl_min","val_crl_loc", "val_crl_min"), "conservative" = c("eth_sqr_loc","eth_sqr_min","val_sqr_loc","val_sqr_min")), "liberal"),
-  `ethnia` = fct_relevel(fct_collapse(subgroup, "Locals:80% ethnic\n 50% liberal" = c("eth_sqr_loc","eth_crl_loc","val_sqr_loc","val_crl_loc"), "Migrants: 20% ethnic\n 50% liberal" = c("eth_sqr_min","eth_crl_min","val_sqr_min","val_crl_min")),"Locals:80% ethnic\n 50% liberal" ))  %>%
-
-  ggplot( aes(x = eth_loc_lib, y = Segra, color = `segregation`, shape = `group` )) + geom_line() + geom_point(size = 3) +
-
-  scale_x_discrete(limits= c(0,1,2,3,4,5)) +
-
-  scale_y_continuous(limits=c(0,1), breaks = c(0,0.2,0.5,0.8,1)) +
-  geom_vline(xintercept = c(1,5), color = "red") +
-    geom_hline(yintercept = c(0.5), color = "red", linetype = 2) +
-      geom_hline(yintercept = c(0.8), color = "purple", linetype = 5) +
-      geom_hline(yintercept = c(0.2), color = "purple", linetype = 2) +
-  facet_grid(`ethnia` ~ eth_min_lib, labeller = labeller(eth_min_lib = eth_min_lib.labs, circle_orange = circle_orange_labs)) +
-               #nrow =2 , dir = "v")  +
-
- scale_color_manual(values = c("purple","dark green"), guide = guide_legend(title= "")) + # ,nrow=2, byrow = TRUE)) +
- scale_shape_manual(values = c("circle","square"), guide = guide_legend(title= "")) + #,nrow=2, byrow = TRUE)) + 
-   ylab("Segregation") +   
-  xlab("ethnic liberal locals") + 
-# guides(color = FALSE, shape = FALSE) +
-xlab("Ethnic liberal locals") + 
-# guides(color = FALSE, shape = FALSE) +
-ggtitle("ß dominant migrants: 5\nß dominant locals: 5") +
-  theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(),legend.text = element_text(size = 12),
-                      axis.title.y =   (element_text(size = 12)), # element_blank(),  # 
-                      axis.title.x =  (element_text(size = 14)), #   element_blank(),  # 
-                      axis.text.x = (element_text(size = 10)),
-                      axis.text.y =  (element_text(size = 10)),
-                      plot.title=element_text(face="bold", size = 14),   
-                      legend.margin=margin(0,0,0,0), panel.spacing = unit(0.8, "lines"), 
-                      strip.text.x = element_text(size = 15),  strip.text.y = element_text(size = 15),
-                      plot.caption = element_text(hjust= 0.5, size = 12)) +
-theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
-
-ggsave("lc_lc5_maj.jpg",last_plot(),
-  device = NULL,
-  path = NULL,
-   scale = 2,
-  width = 6,
-  height = 3,
- # units = c("in", "cm", "mm"),
-  dpi = 300,
-  limitsize = TRUE)
-
-##### RANDOM dislib
-
- df_eth_loc  %>% filter(ID == "lc_lc")   %>% filter(eth_loc_lib == 5) %>% gather(key = subgroup, value = Segra, eth_sqr_loc, eth_sqr_min, eth_crl_loc, eth_crl_min, val_sqr_loc,val_sqr_min,val_crl_loc, val_crl_min) %>%mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"ethnic seg." = c("eth_sqr_loc","eth_sqr_min","eth_crl_loc","eth_crl_min"), "value seg." = c("val_sqr_loc","val_sqr_min","val_crl_loc", "val_crl_min")), "ethnic seg."), `group` = fct_relevel(fct_collapse(subgroup, "liberal" = c("eth_crl_loc","eth_crl_min","val_crl_loc", "val_crl_min"), "conservative" = c("eth_sqr_loc","eth_sqr_min","val_sqr_loc","val_sqr_min")), "liberal"),
-  `ethnia` = fct_relevel(fct_collapse(subgroup, "Locals:80% ethnic\n 50% liberal" = c("eth_sqr_loc","eth_crl_loc","val_sqr_loc","val_crl_loc"), "Migrants: 20% ethnic" = c("eth_sqr_min","eth_crl_min","val_sqr_min","val_crl_min")),"Locals:80% ethnic\n 50% liberal" ))  %>%
-
-  ggplot( aes(x = eth_min_lib, y = Segra, color = `segregation`, shape = `group` )) + geom_line() + geom_point(size = 3) +
-
-  scale_x_discrete(limits= c(0,1,2,3,4,5)) +
-
-  scale_y_continuous(limits=c(0,1), breaks = c(0,0.2,0.5,0.8,1)) +
-  geom_vline(xintercept = c(1,5), color = "red") +
-    geom_hline(yintercept = c(0.5), color = "red", linetype = 2) +
-      geom_hline(yintercept = c(0.8), color = "purple", linetype = 5) +
-      geom_hline(yintercept = c(0.2), color = "purple", linetype = 2) +
-  facet_grid(`ethnia` ~ circle_orange, labeller = labeller(eth_loc_lib = eth_loc_lib.labs, circle_orange = circle_orange_labs)) +
-               #nrow =2 , dir = "v")  +
-
- scale_color_manual(values = c("purple","dark green"), guide = guide_legend(title= "")) + # ,nrow=2, byrow = TRUE)) +
- scale_shape_manual(values = c("circle","square"), guide = guide_legend(title= "")) + #,nrow=2, byrow = TRUE)) + 
- ylab("Segregation") +   
- xlab("ß ethnic liberal migrants") + 
-# guides(color = FALSE, shape = FALSE) +
-ggtitle("ß dominant migrants: 5; ß dominant locals: 5\nß ethnic liberal locals: 5") +
-  theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(),legend.text = element_text(size = 12),
-                      axis.title.y =   (element_text(size = 12)), # element_blank(),  # 
-                      axis.title.x =  (element_text(size = 14)), #   element_blank(),  # 
-                      axis.text.x = (element_text(size = 10)),
-                      axis.text.y =  (element_text(size = 10)),
-                      plot.title=element_text(face="bold", size = 14),   
-                      legend.margin=margin(0,0,0,0), panel.spacing = unit(0.8, "lines"), 
-                      strip.text.x = element_text(size = 15),  strip.text.y = element_text(size = 15),
-                      plot.caption = element_text(hjust= 0.5, size = 12)) +
-theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
-
-ggsave("lc_lc_dis_min.jpg",last_plot(),
-  device = NULL,
-  path = NULL,
-   scale = 2,
-  width = 5,
-  height = 3,
- # units = c("in", "cm", "mm"),
-  dpi = 300,
-  limitsize = TRUE)
-
-# maj
-
-df_eth_loc  %>% filter(ID == "lc_lc")   %>% filter(eth_min_lib == 5) %>% gather(key = subgroup, value = Segra, eth_sqr_loc, eth_sqr_min, eth_crl_loc, eth_crl_min, val_sqr_loc,val_sqr_min,val_crl_loc, val_crl_min) %>%mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"ethnic seg." = c("eth_sqr_loc","eth_sqr_min","eth_crl_loc","eth_crl_min"), "value seg." = c("val_sqr_loc","val_sqr_min","val_crl_loc", "val_crl_min")), "ethnic seg."), `group` = fct_relevel(fct_collapse(subgroup, "liberal" = c("eth_crl_loc","eth_crl_min","val_crl_loc", "val_crl_min"), "conservative" = c("eth_sqr_loc","eth_sqr_min","val_sqr_loc","val_sqr_min")), "liberal"),
-  `ethnia` = fct_relevel(fct_collapse(subgroup, "Locals:80% ethnic\n 50% liberal" = c("eth_sqr_loc","eth_crl_loc","val_sqr_loc","val_crl_loc"), "Migrants: 20% ethnic" = c("eth_sqr_min","eth_crl_min","val_sqr_min","val_crl_min")),"Locals:80% ethnic\n 50% liberal" ))  %>%
-
-  ggplot( aes(x = eth_loc_lib, y = Segra, color = `segregation`, shape = `group` )) + geom_line() + geom_point(size = 3) +
-
-  scale_x_discrete(limits= c(0,1,2,3,4,5,10,15,20)) +
-
-  scale_y_continuous(limits=c(0,1), breaks = c(0,0.2,0.5,0.8,1)) +
-  geom_vline(xintercept = c(1,5,10,20), color = "red") +
-    geom_hline(yintercept = c(0.5), color = "red", linetype = 2) +
-      geom_hline(yintercept = c(0.8), color = "purple", linetype = 5) +
-      geom_hline(yintercept = c(0.2), color = "purple", linetype = 2) +
-  facet_grid(`ethnia` ~ circle_orange, labeller = labeller(eth_loc_lib = eth_loc_lib.labs, circle_orange = circle_orange_labs)) +
-               #nrow =2 , dir = "v")  +
-
- scale_color_manual(values = c("purple","dark green"), guide = guide_legend(title= "")) + # ,nrow=2, byrow = TRUE)) +
- scale_shape_manual(values = c("circle","square"), guide = guide_legend(title= "")) + #,nrow=2, byrow = TRUE)) + 
- ylab("Segregation") +   
- xlab("ß ethnic liberal locals") + 
-# guides(color = FALSE, shape = FALSE) +
-ggtitle("ß dominant locals: 5; ß dominant migrants: 5\nß ethnic liberal migrants: 5") +
-  theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(),legend.text = element_text(size = 12),
-                      axis.title.y =   (element_text(size = 12)), # element_blank(),  # 
-                      axis.title.x =  (element_text(size = 14)), #   element_blank(),  # 
-                      axis.text.x = (element_text(size = 10)),
-                      axis.text.y =  (element_text(size = 10)),
-                      plot.title=element_text(face="bold", size = 14),   
-                      legend.margin=margin(0,0,0,0), panel.spacing = unit(0.8, "lines"), 
-                      strip.text.x = element_text(size = 15),  strip.text.y = element_text(size = 15),
-                      plot.caption = element_text(hjust= 0.5, size = 12)) +
-theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
-
-ggsave("lc_lc_dis_maj.jpg",last_plot(),
-  device = NULL,
-  path = NULL,
-   scale = 2,
-  width = 5,
-  height = 3,
- # units = c("in", "cm", "mm"),
-  dpi = 300,
-  limitsize = TRUE)
-
-```
-
-```{r comparison baseline asym, fig.width= 8,fig.height= 7, fig.pos="H",include=TRUE,fig.cap="50% lib migrant", echo=FALSE}
-
-eth_min_lib.labs <- c("ß Ethnic liberal migrants: 0", "ß Ethnic liberal migrants: 1", "ß Ethnic liberal migrants: 2","ß Ethnic liberal migrants: 3","ß Ethnic liberal migrants: 4","ß Ethnic liberal migrants: 5","ß Ethnic liberal migrants: 10","ß Ethnic liberal migrants: 15","ß Ethnic liberal migrants: 20")
-names(eth_min_lib.labs) <- c("0","1","2","3","4", "5","10","15","20")
-eth_loc_lib.labs <- c("ß Ethnic liberal locals: 0", "ß Ethnic liberal locals: 1", "ß Ethnic liberal locals: 2","ß Ethnic liberal locals: 3","ß Ethnic liberal locals: 4","ß Ethnic liberal locals: 5","ß Ethnic liberal locals: 10","ß Ethnic liberal locals: 15","ß Ethnic liberal locals: 20")
-names(eth_loc_lib.labs) <-  c("0","1","2","3","4", "5","10","15","20")
-
-lc_hc_dis_min <-  df_eth_loc  %>% filter(ID == "hc_lc")   %>% filter(eth_loc_lib == 20) %>% gather(key = subgroup, value = Segra, eth_sqr_loc, eth_sqr_min, eth_crl_loc, eth_crl_min, val_sqr_loc,val_sqr_min,val_crl_loc, val_crl_min) %>%mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"ethnic seg." = c("eth_sqr_loc","eth_sqr_min","eth_crl_loc","eth_crl_min"), "value seg." = c("val_sqr_loc","val_sqr_min","val_crl_loc", "val_crl_min")), "ethnic seg."), `group` = fct_relevel(fct_collapse(subgroup, "liberal" = c("eth_crl_loc","eth_crl_min","val_crl_loc", "val_crl_min"), "conservative" = c("eth_sqr_loc","eth_sqr_min","val_sqr_loc","val_sqr_min")), "liberal"),
-  `ethnia` = fct_relevel(fct_collapse(subgroup, "Locals:80% ethnic\n 50% liberal" = c("eth_sqr_loc","eth_crl_loc","val_sqr_loc","val_crl_loc"), "Migrants: 20% ethnic" = c("eth_sqr_min","eth_crl_min","val_sqr_min","val_crl_min")),"Locals:80% ethnic\n 50% liberal" ))  %>%
-
-  ggplot( aes(x = eth_min_lib, y = Segra, color = `segregation`, shape = `group` )) + geom_line() + geom_point(size = 3) +
-
-  scale_x_discrete(limits= c(0,1,2,3,4,5,10,15,20)) +
-
-  scale_y_continuous(limits=c(0,1), breaks = c(0,0.2,0.5,0.8,1)) +
-  geom_vline(xintercept = c(1,5,10,20), color = "red") +
-    geom_hline(yintercept = c(0.5), color = "red", linetype = 2) +
-      geom_hline(yintercept = c(0.8), color = "purple", linetype = 5) +
-      geom_hline(yintercept = c(0.2), color = "purple", linetype = 2) +
-  facet_grid(`ethnia` ~ circle_orange, labeller = labeller(eth_loc_lib = eth_loc_lib.labs, circle_orange = circle_orange_labs)) +
-               #nrow =2 , dir = "v")  +
-
- scale_color_manual(values = c("purple","dark green"), guide = guide_legend(title= "")) + # ,nrow=2, byrow = TRUE)) +
- scale_shape_manual(values = c("circle","square"), guide = guide_legend(title= "")) + #,nrow=2, byrow = TRUE)) + 
- ylab("Segregation") +   
- xlab("ß ethnic liberal migrants") + 
-# guides(color = FALSE, shape = FALSE) +
-ggtitle("ß dominant migrants: 20; ß dominant locals: 5\nß ethnic liberal locals: 5") +
-  theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(),legend.text = element_text(size = 12),
-                      axis.title.y =   (element_text(size = 12)), # element_blank(),  # 
-                      axis.title.x =  (element_text(size = 14)), #   element_blank(),  # 
-                      axis.text.x = (element_text(size = 10)),
-                      axis.text.y =  (element_text(size = 10)),
-                      plot.title=element_text(face="bold", size = 14),   
-                      legend.margin=margin(0,0,0,0), panel.spacing = unit(0.8, "lines"), 
-                      strip.text.x = element_text(size = 15),  strip.text.y = element_text(size = 15),
-                      plot.caption = element_text(hjust= 0.5, size = 12)) +
-theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
-
-ggsave("lc_hc_dis_min.jpg",lc_hc_dis_min,
-  device = NULL,
-  path = NULL,
-   scale = 2,
-  width = 5,
-  height = 3,
- # units = c("in", "cm", "mm"),
-  dpi = 300,
-  limitsize = TRUE)
-
-hc_lc_dis_maj <-  df_eth_loc  %>% filter(ID == "hc_lc")   %>% filter(eth_min_lib == 5) %>% gather(key = subgroup, value = Segra, eth_sqr_loc, eth_sqr_min, eth_crl_loc, eth_crl_min, val_sqr_loc,val_sqr_min,val_crl_loc, val_crl_min) %>%mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"ethnic seg." = c("eth_sqr_loc","eth_sqr_min","eth_crl_loc","eth_crl_min"), "value seg." = c("val_sqr_loc","val_sqr_min","val_crl_loc", "val_crl_min")), "ethnic seg."), `group` = fct_relevel(fct_collapse(subgroup, "liberal" = c("eth_crl_loc","eth_crl_min","val_crl_loc", "val_crl_min"), "conservative" = c("eth_sqr_loc","eth_sqr_min","val_sqr_loc","val_sqr_min")), "liberal"),
-  `ethnia` = fct_relevel(fct_collapse(subgroup, "Locals:80% ethnic\n 50% liberal" = c("eth_sqr_loc","eth_crl_loc","val_sqr_loc","val_crl_loc"), "Migrants: 20% ethnic" = c("eth_sqr_min","eth_crl_min","val_sqr_min","val_crl_min")),"Locals:80% ethnic\n 50% liberal" ))  %>%
-
-  ggplot( aes(x = eth_loc_lib, y = Segra, color = `segregation`, shape = `group` )) + geom_line() + geom_point(size = 3) +
-
-  scale_x_discrete(limits= c(0,1,2,3,4,5,10,15,20)) +
-
-  scale_y_continuous(limits=c(0,1), breaks = c(0,0.2,0.5,0.8,1)) +
-  geom_vline(xintercept = c(1,5,10,20), color = "red") +
-    geom_hline(yintercept = c(0.5), color = "red", linetype = 2) +
-      geom_hline(yintercept = c(0.8), color = "purple", linetype = 5) +
-      geom_hline(yintercept = c(0.2), color = "purple", linetype = 2) +
-  facet_grid(`ethnia` ~ circle_orange, labeller = labeller(eth_loc_lib = eth_loc_lib.labs, circle_orange = circle_orange_labs)) +
-               #nrow =2 , dir = "v")  +
-
- scale_color_manual(values = c("purple","dark green"), guide = guide_legend(title= "")) + # ,nrow=2, byrow = TRUE)) +
- scale_shape_manual(values = c("circle","square"), guide = guide_legend(title= "")) + #,nrow=2, byrow = TRUE)) + 
- ylab("Segregation") +   
- xlab("ß ethnic liberal locals") + 
-# guides(color = FALSE, shape = FALSE) +
-ggtitle("ß dominant locals: 20; ß dominant migrants: 5\nß ethnic liberal migrants: 5") +
-  theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(),legend.text = element_text(size = 12),
-                      axis.title.y =   (element_text(size = 12)), # element_blank(),  # 
-                      axis.title.x =  (element_text(size = 14)), #   element_blank(),  # 
-                      axis.text.x = (element_text(size = 10)),
-                      axis.text.y =  (element_text(size = 10)),
-                      plot.title=element_text(face="bold", size = 14),   
-                      legend.margin=margin(0,0,0,0), panel.spacing = unit(0.8, "lines"), 
-                      strip.text.x = element_text(size = 15),  strip.text.y = element_text(size = 15),
-                      plot.caption = element_text(hjust= 0.5, size = 12)) +
-theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
-
-ggsave("hc_lc_dis_maj.jpg",hc_lc_dis_maj,
-  device = NULL,
-  path = NULL,
-   scale = 2,
-  width = 5,
-  height = 3,
- # units = c("in", "cm", "mm"),
-  dpi = 300,
-  limitsize = TRUE)
-
-# Determinism
-
-hc_hc_dis_min <-  df_eth_loc  %>% filter(ID == "hc_hc")   %>% filter(eth_loc_lib == 20) %>% gather(key = subgroup, value = Segra, eth_sqr_loc, eth_sqr_min, eth_crl_loc, eth_crl_min, val_sqr_loc,val_sqr_min,val_crl_loc, val_crl_min) %>%mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"ethnic seg." = c("eth_sqr_loc","eth_sqr_min","eth_crl_loc","eth_crl_min"), "value seg." = c("val_sqr_loc","val_sqr_min","val_crl_loc", "val_crl_min")), "ethnic seg."), `group` = fct_relevel(fct_collapse(subgroup, "liberal" = c("eth_crl_loc","eth_crl_min","val_crl_loc", "val_crl_min"), "conservative" = c("eth_sqr_loc","eth_sqr_min","val_sqr_loc","val_sqr_min")), "liberal"),
-  `ethnia` = fct_relevel(fct_collapse(subgroup, "Locals:80% ethnic\n 50% liberal" = c("eth_sqr_loc","eth_crl_loc","val_sqr_loc","val_crl_loc"), "Migrants: 20% ethnic" = c("eth_sqr_min","eth_crl_min","val_sqr_min","val_crl_min")),"Locals:80% ethnic\n 50% liberal" ))  %>%
-
-  ggplot( aes(x = eth_min_lib, y = Segra, color = `segregation`, shape = `group` )) + geom_line() + geom_point(size = 3) +
-
-  scale_x_discrete(limits= c(0,1,2,3,4,5,10,15,20)) +
-
-  scale_y_continuous(limits=c(0,1), breaks = c(0,0.2,0.5,0.8,1)) +
-  geom_vline(xintercept = c(1,5,10,20), color = "red") +
-    geom_hline(yintercept = c(0.5), color = "red", linetype = 2) +
-      geom_hline(yintercept = c(0.8), color = "purple", linetype = 5) +
-      geom_hline(yintercept = c(0.2), color = "purple", linetype = 2) +
-  facet_grid(`ethnia` ~ circle_orange, labeller = labeller(eth_loc_lib = eth_loc_lib.labs, circle_orange = circle_orange_labs)) +
-               #nrow =2 , dir = "v")  +
-
- scale_color_manual(values = c("purple","dark green"), guide = guide_legend(title= "")) + # ,nrow=2, byrow = TRUE)) +
- scale_shape_manual(values = c("circle","square"), guide = guide_legend(title= "")) + #,nrow=2, byrow = TRUE)) + 
- ylab("Segregation") +   
- xlab("ß ethnic liberal migrants") + 
-guides(color = FALSE, shape = FALSE) +
-ggtitle("ß dominant migrants: 20; ß dominant locals: 20\nß ethnic liberal locals: 20") +
-  theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(),legend.text = element_text(size = 12),
-                      axis.title.y =   (element_text(size = 12)), # element_blank(),  # 
-                      axis.title.x =  (element_text(size = 14)), #   element_blank(),  # 
-                      axis.text.x = (element_text(size = 10)),
-                      axis.text.y =  (element_text(size = 10)),
-                      plot.title=element_text(face="bold", size = 14),   
-                      legend.margin=margin(0,0,0,0), panel.spacing = unit(0.8, "lines"), 
-                      strip.text.x = element_text(size = 15),  strip.text.y = element_text(size = 15),
-                      plot.caption = element_text(hjust= 0.5, size = 12)) +
-theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
-
-ggsave("hc_hc_dis_min.jpg",hc_hc_dis_min,
-  device = NULL,
-  path = NULL,
-   scale = 2,
-  width = 5,
-  height = 3,
- # units = c("in", "cm", "mm"),
-  dpi = 300,
-  limitsize = TRUE)
-
-hc_hc_dis_maj <-  df_eth_loc  %>% filter(ID == "hc_hc")   %>% filter(eth_min_lib == 20) %>% gather(key = subgroup, value = Segra, eth_sqr_loc, eth_sqr_min, eth_crl_loc, eth_crl_min, val_sqr_loc,val_sqr_min,val_crl_loc, val_crl_min) %>%mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"ethnic seg." = c("eth_sqr_loc","eth_sqr_min","eth_crl_loc","eth_crl_min"), "value seg." = c("val_sqr_loc","val_sqr_min","val_crl_loc", "val_crl_min")), "ethnic seg."), `group` = fct_relevel(fct_collapse(subgroup, "liberal" = c("eth_crl_loc","eth_crl_min","val_crl_loc", "val_crl_min"), "conservative" = c("eth_sqr_loc","eth_sqr_min","val_sqr_loc","val_sqr_min")), "liberal"),
-  `ethnia` = fct_relevel(fct_collapse(subgroup, "Locals:80% ethnic\n 50% liberal" = c("eth_sqr_loc","eth_crl_loc","val_sqr_loc","val_crl_loc"), "Migrants: 20% ethnic" = c("eth_sqr_min","eth_crl_min","val_sqr_min","val_crl_min")),"Locals:80% ethnic\n 50% liberal" ))  %>%
-
-  ggplot( aes(x = eth_loc_lib, y = Segra, color = `segregation`, shape = `group` )) + geom_line() + geom_point(size = 3) +
-
-  scale_x_discrete(limits= c(0,1,2,3,4,5,10,15,20)) +
-
-  scale_y_continuous(limits=c(0,1), breaks = c(0,0.2,0.5,0.8,1)) +
-  geom_vline(xintercept = c(1,5,10,20), color = "red") +
-    geom_hline(yintercept = c(0.5), color = "red", linetype = 2) +
-      geom_hline(yintercept = c(0.8), color = "purple", linetype = 5) +
-      geom_hline(yintercept = c(0.2), color = "purple", linetype = 2) +
-  facet_grid(`ethnia` ~ circle_orange, labeller = labeller(eth_loc_lib = eth_loc_lib.labs, circle_orange = circle_orange_labs)) +
-               #nrow =2 , dir = "v")  +
-
- scale_color_manual(values = c("purple","dark green"), guide = guide_legend(title= "")) + # ,nrow=2, byrow = TRUE)) +
- scale_shape_manual(values = c("circle","square"), guide = guide_legend(title= "")) + #,nrow=2, byrow = TRUE)) + 
- ylab("Segregation") +   
- xlab("ß ethnic liberal locals") + 
-# guides(color = FALSE, shape = FALSE) +
-ggtitle("ß dominant locals: 20; ß dominant migrants: 20\nß ethnic liberal migrants: 20") +
-  theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(),legend.text = element_text(size = 12),
-                      axis.title.y =   (element_text(size = 12)), # element_blank(),  # 
-                      axis.title.x =  (element_text(size = 14)), #   element_blank(),  # 
-                      axis.text.x = (element_text(size = 10)),
-                      axis.text.y =  (element_text(size = 10)),
-                      plot.title=element_text(face="bold", size = 14),   
-                      legend.margin=margin(0,0,0,0), panel.spacing = unit(0.8, "lines"), 
-                      strip.text.x = element_text(size = 15),  strip.text.y = element_text(size = 15),
-                      plot.caption = element_text(hjust= 0.5, size = 12)) +
-theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
-
-ggsave("hc_hc_dis_maj.jpg",hc_hc_dis_maj,
-  device = NULL,
-  path = NULL,
-   scale = 2,
-  width = 5,
-  height = 3,
- # units = c("in", "cm", "mm"),
-  dpi = 300,
-  limitsize = TRUE)
-```
-
-```{r rand20, fig.width= 8,fig.height= 7, fig.pos="H",include=TRUE,fig.cap="Individual comparison rand 20", echo=FALSE}
-
-eth_min_lib.labs <- c("ß Ethnic liberal migrants: 0", "ß Ethnic liberal migrants: 1", "ß Ethnic liberal migrants: 2","ß Ethnic liberal migrants: 3","ß Ethnic liberal migrants: 4","ß Ethnic liberal migrants: 5","ß Ethnic liberal migrants: 10","ß Ethnic liberal migrants: 15","ß Ethnic liberal migrants: 20")
-names(eth_min_lib.labs) <- c("0","1","2","3","4", "5","10","15","20")
-eth_loc_lib.labs <- c("ß Ethnic liberal locals: 0", "ß Ethnic liberal locals: 1", "ß Ethnic liberal locals: 2","ß Ethnic liberal locals: 3","ß Ethnic liberal locals: 4","ß Ethnic liberal locals: 5","ß Ethnic liberal locals: 10","ß Ethnic liberal locals: 15","ß Ethnic liberal locals: 20")
-names(eth_loc_lib.labs) <-  c("0","1","2","3","4", "5","10","15","20")
-
-# Intermediate randomness Migrants x-axys
-
- df_eth_loc  %>% filter(ID == "lc_hc") %>% filter(circle_orange == 20)  %>% filter(eth_loc_lib == 0 | eth_loc_lib == 1 | eth_loc_lib == 3 | eth_loc_lib == 5) %>% gather(key = subgroup, value = Segra, eth_sqr_loc, eth_sqr_min, eth_crl_loc, eth_crl_min, val_sqr_loc,val_sqr_min,val_crl_loc, val_crl_min) %>%mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"ethnic seg." = c("eth_sqr_loc","eth_sqr_min","eth_crl_loc","eth_crl_min"), "value seg." = c("val_sqr_loc","val_sqr_min","val_crl_loc", "val_crl_min")), "ethnic seg."), `group` = fct_relevel(fct_collapse(subgroup, "liberal" = c("eth_crl_loc","eth_crl_min","val_crl_loc", "val_crl_min"), "conservative" = c("eth_sqr_loc","eth_sqr_min","val_sqr_loc","val_sqr_min")), "liberal"),
-  `ethnia` = fct_relevel(fct_collapse(subgroup, "Locals:80% ethnic\n 50% liberal" = c("eth_sqr_loc","eth_crl_loc","val_sqr_loc","val_crl_loc"), "Migrants: 20% ethnic\n 20% liberal" = c("eth_sqr_min","eth_crl_min","val_sqr_min","val_crl_min")),"Locals:80% ethnic\n 50% liberal" ))  %>%
-
-  ggplot( aes(x = eth_min_lib, y = Segra, color = `segregation`, shape = `group` )) + geom_line() + geom_point(size = 3) +
-
-  scale_x_discrete(limits= c(0,1,2,3,4,5,10,15,20)) +
-
-  scale_y_continuous(limits=c(0,1), breaks = c(0,0.2,0.5,0.8,1)) +
-  geom_vline(xintercept = c(1,5,10,20), color = "red") +
-    geom_hline(yintercept = c(0.5), color = "red", linetype = 2) +
-      geom_hline(yintercept = c(0.8), color = "purple", linetype = 5) +
-      geom_hline(yintercept = c(0.2), color = "purple", linetype = 2) +
-  facet_grid(`ethnia` ~ eth_loc_lib, labeller = labeller(eth_loc_lib = eth_loc_lib.labs, circle_orange = circle_orange_labs)) +
-               #nrow =2 , dir = "v")  +
-
- scale_color_manual(values = c("purple","dark green"), guide = guide_legend(title= "")) + # ,nrow=2, byrow = TRUE)) +
- scale_shape_manual(values = c("circle","square"), guide = guide_legend(title= "")) + #,nrow=2, byrow = TRUE)) + 
-   ylab("Segregation") +   
-  xlab("Ethnic liberal migrants") + 
- guides(color = FALSE, shape = FALSE) +
-ggtitle("ß dominant migrants: 20\nß dominant locals: 5") +
-  theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(),legend.text = element_text(size = 12),
-                      axis.title.y =   (element_text(size = 12)), # element_blank(),  # 
-                      axis.title.x =  (element_text(size = 14)), #   element_blank(),  # 
-                      axis.text.x = (element_text(size = 10)),
-                      axis.text.y =  (element_text(size = 10)),
-                      plot.title=element_text(face="bold", size = 14),   
-                      legend.margin=margin(0,0,0,0), panel.spacing = unit(0.8, "lines"), 
-                      strip.text.x = element_text(size = 15),  strip.text.y = element_text(size = 15),
-                      plot.caption = element_text(hjust= 0.5, size = 12)) +
-theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
-
-ggsave("lc_hc2_min.jpg",last_plot(),
-  device = NULL,
-  path = NULL,
-  scale = 2,
-  width = 6,
-  height = 3,
- # units = ("in", "cm", "mm"),
-  dpi = 300,
-  limitsize = TRUE)
-
-# Intermediate randomness Locals x-axys
-
-df_eth_loc  %>% filter(ID == "hc_lc") %>% filter(circle_orange == 20)  %>% filter(eth_min_lib == 0 | eth_min_lib == 1 | eth_min_lib == 3 |   eth_min_lib == 5) %>% gather(key = subgroup, value = Segra, eth_sqr_loc, eth_sqr_min, eth_crl_loc, eth_crl_min, val_sqr_loc,val_sqr_min,val_crl_loc, val_crl_min) %>%mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"ethnic seg." = c("eth_sqr_loc","eth_sqr_min","eth_crl_loc","eth_crl_min"), "value seg." = c("val_sqr_loc","val_sqr_min","val_crl_loc", "val_crl_min")), "ethnic seg."), `group` = fct_relevel(fct_collapse(subgroup, "liberal" = c("eth_crl_loc","eth_crl_min","val_crl_loc", "val_crl_min"), "conservative" = c("eth_sqr_loc","eth_sqr_min","val_sqr_loc","val_sqr_min")), "liberal"),
-  `ethnia` = fct_relevel(fct_collapse(subgroup, "Locals:80% ethnic\n 50% liberal" = c("eth_sqr_loc","eth_crl_loc","val_sqr_loc","val_crl_loc"), "Migrants: 20% ethnic\n 20% liberal" = c("eth_sqr_min","eth_crl_min","val_sqr_min","val_crl_min")),"Locals:80% ethnic\n 50% liberal" ))  %>%
-
-  ggplot( aes(x = eth_loc_lib, y = Segra, color = `segregation`, shape = `group` )) + geom_line() + geom_point(size = 3) +
-
-  scale_x_discrete(limits= c(0,1,2,3,4,5,10,15,20)) +
-
-  scale_y_continuous(limits=c(0,1), breaks = c(0,0.2,0.5,0.8,1)) +
-  geom_vline(xintercept = c(1,5,10,20), color = "red") +
-    geom_hline(yintercept = c(0.5), color = "red", linetype = 2) +
-      geom_hline(yintercept = c(0.8), color = "purple", linetype = 5) +
-      geom_hline(yintercept = c(0.2), color = "purple", linetype = 2) +
-  facet_grid(`ethnia` ~ eth_min_lib, labeller = labeller(eth_min_lib = eth_min_lib.labs, circle_orange = circle_orange_labs)) +
-               #nrow =2 , dir = "v")  +
-
- scale_color_manual(values = c("purple","dark green"), guide = guide_legend(title= "")) + # ,nrow=2, byrow = TRUE)) +
- scale_shape_manual(values = c("circle","square"), guide = guide_legend(title= "")) + #,nrow=2, byrow = TRUE)) + 
-   ylab("Segregation") +   
-  xlab("ethnic liberal locals") + 
-# guides(color = FALSE, shape = FALSE) +
-xlab("Ethnic liberal locals") + 
-# guides(color = FALSE, shape = FALSE) +
-ggtitle("ß dominant locals: 20\nß dominant migrants: 5") +
-  theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(),legend.text = element_text(size = 12),
-                      axis.title.y =   (element_text(size = 12)), # element_blank(),  # 
-                      axis.title.x =  (element_text(size = 14)), #   element_blank(),  # 
-                      axis.text.x = (element_text(size = 10)),
-                      axis.text.y =  (element_text(size = 10)),
-                      plot.title=element_text(face="bold", size = 14),   
-                      legend.margin=margin(0,0,0,0), panel.spacing = unit(0.8, "lines"), 
-                      strip.text.x = element_text(size = 15),  strip.text.y = element_text(size = 15),
-                      plot.caption = element_text(hjust= 0.5, size = 12)) +
-theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
-
-# 
-# comb <- ggarrange(mig,loc, nrow =  2, common.legend = TRUE, legend = "bottom")
-# annotate_figure(comb, 
-#                # top = text_grob("Dominant ß: 5",  face = "bold", size = 12),
-#                left = text_grob("Segregation", rot = 90, size = 12),
-#                 bottom = text_grob("ß value conservative both group: 0", hjust = 1, x = 1, size = 12),
-#                 )
-
-ggsave("lc_hc2_maj.jpg",last_plot(),
-  device = NULL,
-  path = NULL,
-   scale = 2,
-  width = 6,
-  height = 3,
- # units = c("in", "cm", "mm"),
-  dpi = 300,
-  limitsize = TRUE)
-
-```
-
-```{r rand80, fig.width= 8,fig.height= 7, fig.pos="H",include=TRUE,fig.cap="Individual comparison rand 80", echo=FALSE}
-
-eth_min_lib.labs <- c("ß Ethnic liberal migrants: 0", "ß Ethnic liberal migrants: 1", "ß Ethnic liberal migrants: 2","ß Ethnic liberal migrants: 3","ß Ethnic liberal migrants: 4","ß Ethnic liberal migrants: 5","ß Ethnic liberal migrants: 10","ß Ethnic liberal migrants: 15","ß Ethnic liberal migrants: 20")
-names(eth_min_lib.labs) <- c("0","1","2","3","4", "5","10","15","20")
-eth_loc_lib.labs <- c("ß Ethnic liberal locals: 0", "ß Ethnic liberal locals: 1", "ß Ethnic liberal locals: 2","ß Ethnic liberal locals: 3","ß Ethnic liberal locals: 4","ß Ethnic liberal locals: 5","ß Ethnic liberal locals: 10","ß Ethnic liberal locals: 15","ß Ethnic liberal locals: 20")
-names(eth_loc_lib.labs) <-  c("0","1","2","3","4", "5","10","15","20")
-
-# Intermediate randomness Migrants x-axys
-
- df_eth_loc  %>% filter(ID == "lc_hc") %>% filter(circle_orange == 80)  %>% filter(eth_loc_lib == 0 | eth_loc_lib == 1 | eth_loc_lib == 3 | eth_loc_lib == 5) %>% gather(key = subgroup, value = Segra, eth_sqr_loc, eth_sqr_min, eth_crl_loc, eth_crl_min, val_sqr_loc,val_sqr_min,val_crl_loc, val_crl_min) %>%mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"ethnic seg." = c("eth_sqr_loc","eth_sqr_min","eth_crl_loc","eth_crl_min"), "value seg." = c("val_sqr_loc","val_sqr_min","val_crl_loc", "val_crl_min")), "ethnic seg."), `group` = fct_relevel(fct_collapse(subgroup, "liberal" = c("eth_crl_loc","eth_crl_min","val_crl_loc", "val_crl_min"), "conservative" = c("eth_sqr_loc","eth_sqr_min","val_sqr_loc","val_sqr_min")), "liberal"),
-  `ethnia` = fct_relevel(fct_collapse(subgroup, "Locals:80% ethnic\n 50% liberal" = c("eth_sqr_loc","eth_crl_loc","val_sqr_loc","val_crl_loc"), "Migrants: 20% ethnic\n 80% liberal" = c("eth_sqr_min","eth_crl_min","val_sqr_min","val_crl_min")),"Locals:80% ethnic\n 50% liberal" ))  %>%
-
-  ggplot( aes(x = eth_min_lib, y = Segra, color = `segregation`, shape = `group` )) + geom_line() + geom_point(size = 3) +
-
-  scale_x_discrete(limits= c(0,1,2,3,4,5,10,15,20)) +
-
-  scale_y_continuous(limits=c(0,1), breaks = c(0,0.2,0.5,0.8,1)) +
-  geom_vline(xintercept = c(1,5,10,20), color = "red") +
-    geom_hline(yintercept = c(0.5), color = "red", linetype = 2) +
-      geom_hline(yintercept = c(0.8), color = "purple", linetype = 5) +
-      geom_hline(yintercept = c(0.2), color = "purple", linetype = 2) +
-  facet_grid(`ethnia` ~ eth_loc_lib, labeller = labeller(eth_loc_lib = eth_loc_lib.labs, circle_orange = circle_orange_labs)) +
-               #nrow =2 , dir = "v")  +
-
- scale_color_manual(values = c("purple","dark green"), guide = guide_legend(title= "")) + # ,nrow=2, byrow = TRUE)) +
- scale_shape_manual(values = c("circle","square"), guide = guide_legend(title= "")) + #,nrow=2, byrow = TRUE)) + 
-   ylab("Segregation") +   
-  xlab("Ethnic liberal migrants") + 
- guides(color = FALSE, shape = FALSE) +
-ggtitle("ß dominant migrants: 20\nß dominant locals: 5") +
-  theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(),legend.text = element_text(size = 12),
-                      axis.title.y =   (element_text(size = 12)), # element_blank(),  # 
-                      axis.title.x =  (element_text(size = 14)), #   element_blank(),  # 
-                      axis.text.x = (element_text(size = 10)),
-                      axis.text.y =  (element_text(size = 10)),
-                      plot.title=element_text(face="bold", size = 14),   
-                      legend.margin=margin(0,0,0,0), panel.spacing = unit(0.8, "lines"), 
-                      strip.text.x = element_text(size = 15),  strip.text.y = element_text(size = 15),
-                      plot.caption = element_text(hjust= 0.5, size = 12)) +
-theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
-
-ggsave("lc_hc8_min.jpg",last_plot(),
-  device = NULL,
-  path = NULL,
-  scale = 2,
-  width = 6,
-  height = 3,
- # units = ("in", "cm", "mm"),
-  dpi = 300,
-  limitsize = TRUE)
-
-# Intermediate randomness Locals x-axys
-
-df_eth_loc  %>% filter(ID == "hc_lc") %>% filter(circle_orange == 80)  %>% filter(eth_min_lib == 0 | eth_min_lib == 1 | eth_min_lib == 3 |   eth_min_lib == 5) %>% gather(key = subgroup, value = Segra, eth_sqr_loc, eth_sqr_min, eth_crl_loc, eth_crl_min, val_sqr_loc,val_sqr_min,val_crl_loc, val_crl_min) %>%mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"ethnic seg." = c("eth_sqr_loc","eth_sqr_min","eth_crl_loc","eth_crl_min"), "value seg." = c("val_sqr_loc","val_sqr_min","val_crl_loc", "val_crl_min")), "ethnic seg."), `group` = fct_relevel(fct_collapse(subgroup, "liberal" = c("eth_crl_loc","eth_crl_min","val_crl_loc", "val_crl_min"), "conservative" = c("eth_sqr_loc","eth_sqr_min","val_sqr_loc","val_sqr_min")), "liberal"),
-  `ethnia` = fct_relevel(fct_collapse(subgroup, "Locals:80% ethnic\n 50% liberal" = c("eth_sqr_loc","eth_crl_loc","val_sqr_loc","val_crl_loc"), "Migrants: 20% ethnic\n 80% liberal" = c("eth_sqr_min","eth_crl_min","val_sqr_min","val_crl_min")),"Locals:80% ethnic\n 50% liberal" ))  %>%
-
-  ggplot( aes(x = eth_loc_lib, y = Segra, color = `segregation`, shape = `group` )) + geom_line() + geom_point(size = 3) +
-
-  scale_x_discrete(limits= c(0,1,2,3,4,5,10,15,20)) +
-
-  scale_y_continuous(limits=c(0,1), breaks = c(0,0.2,0.5,0.8,1)) +
-  geom_vline(xintercept = c(1,5,10,20), color = "red") +
-    geom_hline(yintercept = c(0.5), color = "red", linetype = 2) +
-      geom_hline(yintercept = c(0.8), color = "purple", linetype = 5) +
-      geom_hline(yintercept = c(0.2), color = "purple", linetype = 2) +
-  facet_grid(`ethnia` ~ eth_min_lib, labeller = labeller(eth_min_lib = eth_min_lib.labs, circle_orange = circle_orange_labs)) +
-               #nrow =2 , dir = "v")  +
-
- scale_color_manual(values = c("purple","dark green"), guide = guide_legend(title= "")) + # ,nrow=2, byrow = TRUE)) +
- scale_shape_manual(values = c("circle","square"), guide = guide_legend(title= "")) + #,nrow=2, byrow = TRUE)) + 
-   ylab("Segregation") +   
-  xlab("ethnic liberal locals") + 
-# guides(color = FALSE, shape = FALSE) +
-xlab("Ethnic liberal locals") + 
-# guides(color = FALSE, shape = FALSE) +
-ggtitle("ß dominant locals: 20\nß dominant migrants: 5") +
-  theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(),legend.text = element_text(size = 12),
-                      axis.title.y =   (element_text(size = 12)), # element_blank(),  # 
-                      axis.title.x =  (element_text(size = 14)), #   element_blank(),  # 
-                      axis.text.x = (element_text(size = 10)),
-                      axis.text.y =  (element_text(size = 10)),
-                      plot.title=element_text(face="bold", size = 14),   
-                      legend.margin=margin(0,0,0,0), panel.spacing = unit(0.8, "lines"), 
-                      strip.text.x = element_text(size = 15),  strip.text.y = element_text(size = 15),
-                      plot.caption = element_text(hjust= 0.5, size = 12)) +
-theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
-
-# 
-# comb <- ggarrange(mig,loc, nrow =  2, common.legend = TRUE, legend = "bottom")
-# annotate_figure(comb, 
-#                # top = text_grob("Dominant ß: 5",  face = "bold", size = 12),
-#                left = text_grob("Segregation", rot = 90, size = 12),
-#                 bottom = text_grob("ß value conservative both group: 0", hjust = 1, x = 1, size = 12),
-#                 )
-
-ggsave("lc_hc8_maj.jpg",last_plot(),
-  device = NULL,
-  path = NULL,
-   scale = 2,
-  width = 6,
-  height = 3,
- # units = c("in", "cm", "mm"),
-  dpi = 300,
-  limitsize = TRUE)
-
-```
-
-```{r det20, fig.width= 8,fig.height= 7, fig.pos="H",include=TRUE,fig.cap="Individual comparison determinism beta 20", echo=FALSE}
-
-eth_min_lib.labs <- c("ß Ethnic liberal migrants: 0", "ß Ethnic liberal migrants: 1", "ß Ethnic liberal migrants: 2","ß Ethnic liberal migrants: 3","ß Ethnic liberal migrants: 4","ß Ethnic liberal migrants: 5","ß Ethnic liberal migrants: 10","ß Ethnic liberal migrants: 15","ß Ethnic liberal migrants: 20")
-names(eth_min_lib.labs) <- c("0","1","2","3","4", "5","10","15","20")
-eth_loc_lib.labs <- c("ß Ethnic liberal locals: 0", "ß Ethnic liberal locals: 1", "ß Ethnic liberal locals: 2","ß Ethnic liberal locals: 3","ß Ethnic liberal locals: 4","ß Ethnic liberal locals: 5","ß Ethnic liberal locals: 10","ß Ethnic liberal locals: 15","ß Ethnic liberal locals: 20")
-names(eth_loc_lib.labs) <-  c("0","1","2","3","4", "5","10","15","20")
-
-# Intermediate randomness Migrants x-axys
-
- df_eth_loc  %>% filter(ID == "hc_hc") %>% filter(circle_orange == 20)  %>% filter(eth_loc_lib == 0 | eth_loc_lib == 5 | eth_loc_lib == 10 | eth_loc_lib == 20) %>% gather(key = subgroup, value = Segra, eth_sqr_loc, eth_sqr_min, eth_crl_loc, eth_crl_min, val_sqr_loc,val_sqr_min,val_crl_loc, val_crl_min) %>%mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"ethnic seg." = c("eth_sqr_loc","eth_sqr_min","eth_crl_loc","eth_crl_min"), "value seg." = c("val_sqr_loc","val_sqr_min","val_crl_loc", "val_crl_min")), "ethnic seg."), `group` = fct_relevel(fct_collapse(subgroup, "liberal" = c("eth_crl_loc","eth_crl_min","val_crl_loc", "val_crl_min"), "conservative" = c("eth_sqr_loc","eth_sqr_min","val_sqr_loc","val_sqr_min")), "liberal"),
-  `ethnia` = fct_relevel(fct_collapse(subgroup, "Locals:80% ethnic\n 50% liberal" = c("eth_sqr_loc","eth_crl_loc","val_sqr_loc","val_crl_loc"), "Migrants: 20% ethnic\n 20% liberal" = c("eth_sqr_min","eth_crl_min","val_sqr_min","val_crl_min")),"Locals:80% ethnic\n 50% liberal" ))  %>%
-
-  ggplot( aes(x = eth_min_lib, y = Segra, color = `segregation`, shape = `group` )) + geom_line() + geom_point(size = 3) +
-
-  scale_x_discrete(limits= c(0,1,2,3,4,5,10,15,20)) +
-
-  scale_y_continuous(limits=c(0,1), breaks = c(0,0.2,0.5,0.8,1)) +
-  geom_vline(xintercept = c(1,5,10,20), color = "red") +
-    geom_hline(yintercept = c(0.5), color = "red", linetype = 2) +
-      geom_hline(yintercept = c(0.8), color = "purple", linetype = 5) +
-      geom_hline(yintercept = c(0.2), color = "purple", linetype = 2) +
-  facet_grid(`ethnia` ~ eth_loc_lib, labeller = labeller(eth_loc_lib = eth_loc_lib.labs, circle_orange = circle_orange_labs)) +
-               #nrow =2 , dir = "v")  +
-
- scale_color_manual(values = c("purple","dark green"), guide = guide_legend(title= "")) + # ,nrow=2, byrow = TRUE)) +
- scale_shape_manual(values = c("circle","square"), guide = guide_legend(title= "")) + #,nrow=2, byrow = TRUE)) + 
-   ylab("Segregation") +   
-  xlab("Ethnic liberal migrants") + 
- guides(color = FALSE, shape = FALSE) +
-ggtitle("ß dominant migrants: 20\nß dominant locals: 20") +
-  theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(),legend.text = element_text(size = 12),
-                      axis.title.y =   (element_text(size = 12)), # element_blank(),  # 
-                      axis.title.x =  (element_text(size = 14)), #   element_blank(),  # 
-                      axis.text.x = (element_text(size = 10)),
-                      axis.text.y =  (element_text(size = 10)),
-                      plot.title=element_text(face="bold", size = 14),   
-                      legend.margin=margin(0,0,0,0), panel.spacing = unit(0.8, "lines"), 
-                      strip.text.x = element_text(size = 15),  strip.text.y = element_text(size = 15),
-                      plot.caption = element_text(hjust= 0.5, size = 12)) +
-theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
-
-ggsave("hc_hc2_min.jpg",last_plot(),
-  device = NULL,
-  path = NULL,
-  scale = 2,
-  width = 6,
-  height = 3,
- # units = ("in", "cm", "mm"),
-  dpi = 300,
-  limitsize = TRUE)
-
-# Intermediate randomness Locals x-axys
-
-df_eth_loc  %>% filter(ID == "hc_hc") %>% filter(circle_orange == 20)  %>% filter(eth_min_lib == 0 | eth_min_lib == 5 | eth_min_lib == 10 | eth_min_lib == 20) %>% gather(key = subgroup, value = Segra, eth_sqr_loc, eth_sqr_min, eth_crl_loc, eth_crl_min, val_sqr_loc,val_sqr_min,val_crl_loc, val_crl_min) %>%mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"ethnic seg." = c("eth_sqr_loc","eth_sqr_min","eth_crl_loc","eth_crl_min"), "value seg." = c("val_sqr_loc","val_sqr_min","val_crl_loc", "val_crl_min")), "ethnic seg."), `group` = fct_relevel(fct_collapse(subgroup, "liberal" = c("eth_crl_loc","eth_crl_min","val_crl_loc", "val_crl_min"), "conservative" = c("eth_sqr_loc","eth_sqr_min","val_sqr_loc","val_sqr_min")), "liberal"),
-  `ethnia` = fct_relevel(fct_collapse(subgroup, "Locals:80% ethnic\n 50% liberal" = c("eth_sqr_loc","eth_crl_loc","val_sqr_loc","val_crl_loc"), "Migrants: 20% ethnic\n 20% liberal" = c("eth_sqr_min","eth_crl_min","val_sqr_min","val_crl_min")),"Locals:80% ethnic\n 50% liberal" ))  %>%
-
-  ggplot( aes(x = eth_loc_lib, y = Segra, color = `segregation`, shape = `group` )) + geom_line() + geom_point(size = 3) +
-
-  scale_x_discrete(limits= c(0,1,2,3,4,5,10,15,20)) +
-
-  scale_y_continuous(limits=c(0,1), breaks = c(0,0.2,0.5,0.8,1)) +
-  geom_vline(xintercept = c(1,5,10,20), color = "red") +
-    geom_hline(yintercept = c(0.5), color = "red", linetype = 2) +
-      geom_hline(yintercept = c(0.8), color = "purple", linetype = 5) +
-      geom_hline(yintercept = c(0.2), color = "purple", linetype = 2) +
-  facet_grid(`ethnia` ~ eth_min_lib, labeller = labeller(eth_min_lib = eth_min_lib.labs, circle_orange = circle_orange_labs)) +
-               #nrow =2 , dir = "v")  +
-
- scale_color_manual(values = c("purple","dark green"), guide = guide_legend(title= "")) + # ,nrow=2, byrow = TRUE)) +
- scale_shape_manual(values = c("circle","square"), guide = guide_legend(title= "")) + #,nrow=2, byrow = TRUE)) + 
-   ylab("Segregation") +   
-  xlab("ethnic liberal locals") + 
-# guides(color = FALSE, shape = FALSE) +
-xlab("Ethnic liberal locals") + 
-# guides(color = FALSE, shape = FALSE) +
-ggtitle("ß dominant locals: 20\nß dominant migrants: 20") +
-  theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(),legend.text = element_text(size = 12),
-                      axis.title.y =   (element_text(size = 12)), # element_blank(),  # 
-                      axis.title.x =  (element_text(size = 14)), #   element_blank(),  # 
-                      axis.text.x = (element_text(size = 10)),
-                      axis.text.y =  (element_text(size = 10)),
-                      plot.title=element_text(face="bold", size = 14),   
-                      legend.margin=margin(0,0,0,0), panel.spacing = unit(0.8, "lines"), 
-                      strip.text.x = element_text(size = 15),  strip.text.y = element_text(size = 15),
-                      plot.caption = element_text(hjust= 0.5, size = 12)) +
-theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
-
-# 
-# comb <- ggarrange(mig,loc, nrow =  2, common.legend = TRUE, legend = "bottom")
-# annotate_figure(comb, 
-#                # top = text_grob("Dominant ß: 5",  face = "bold", size = 12),
-#                left = text_grob("Segregation", rot = 90, size = 12),
-#                 bottom = text_grob("ß value conservative both group: 0", hjust = 1, x = 1, size = 12),
-#                 )
-
-ggsave("hc_hc2_maj.jpg",last_plot(),
-  device = NULL,
-  path = NULL,
-   scale = 2,
-  width = 6,
-  height = 3,
- # units = c("in", "cm", "mm"),
-  dpi = 300,
-  limitsize = TRUE)
-
-```
-
-```{r det80, fig.width= 8,fig.height= 7, fig.pos="H",include=TRUE,fig.cap="Individual comparison determinism beta 20", echo=FALSE}
-
-eth_min_lib.labs <- c("ß Ethnic liberal migrants: 0", "ß Ethnic liberal migrants: 1", "ß Ethnic liberal migrants: 2","ß Ethnic liberal migrants: 3","ß Ethnic liberal migrants: 4","ß Ethnic liberal migrants: 5","ß Ethnic liberal migrants: 10","ß Ethnic liberal migrants: 15","ß Ethnic liberal migrants: 20")
-names(eth_min_lib.labs) <- c("0","1","2","3","4", "5","10","15","20")
-eth_loc_lib.labs <- c("ß Ethnic liberal locals: 0", "ß Ethnic liberal locals: 1", "ß Ethnic liberal locals: 2","ß Ethnic liberal locals: 3","ß Ethnic liberal locals: 4","ß Ethnic liberal locals: 5","ß Ethnic liberal locals: 10","ß Ethnic liberal locals: 15","ß Ethnic liberal locals: 20")
-names(eth_loc_lib.labs) <-  c("0","1","2","3","4", "5","10","15","20")
-
-# Intermediate randomness Migrants x-axys
-
- df_eth_loc  %>% filter(ID == "hc_hc") %>% filter(circle_orange == 80)  %>% filter(eth_loc_lib == 0 | eth_loc_lib == 5 | eth_loc_lib == 10 | eth_loc_lib == 20) %>% gather(key = subgroup, value = Segra, eth_sqr_loc, eth_sqr_min, eth_crl_loc, eth_crl_min, val_sqr_loc,val_sqr_min,val_crl_loc, val_crl_min) %>%mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"ethnic seg." = c("eth_sqr_loc","eth_sqr_min","eth_crl_loc","eth_crl_min"), "value seg." = c("val_sqr_loc","val_sqr_min","val_crl_loc", "val_crl_min")), "ethnic seg."), `group` = fct_relevel(fct_collapse(subgroup, "liberal" = c("eth_crl_loc","eth_crl_min","val_crl_loc", "val_crl_min"), "conservative" = c("eth_sqr_loc","eth_sqr_min","val_sqr_loc","val_sqr_min")), "liberal"),
-  `ethnia` = fct_relevel(fct_collapse(subgroup, "Locals:80% ethnic\n 50% liberal" = c("eth_sqr_loc","eth_crl_loc","val_sqr_loc","val_crl_loc"), "Migrants: 20% ethnic\n 80% liberal" = c("eth_sqr_min","eth_crl_min","val_sqr_min","val_crl_min")),"Locals:80% ethnic\n 50% liberal" ))  %>%
-
-  ggplot( aes(x = eth_min_lib, y = Segra, color = `segregation`, shape = `group` )) + geom_line() + geom_point(size = 3) +
-
-  scale_x_discrete(limits= c(0,1,2,3,4,5,10,15,20)) +
-
-  scale_y_continuous(limits=c(0,1), breaks = c(0,0.2,0.5,0.8,1)) +
-  geom_vline(xintercept = c(1,5,10,20), color = "red") +
-    geom_hline(yintercept = c(0.5), color = "red", linetype = 2) +
-      geom_hline(yintercept = c(0.8), color = "purple", linetype = 5) +
-      geom_hline(yintercept = c(0.2), color = "purple", linetype = 2) +
-  facet_grid(`ethnia` ~ eth_loc_lib, labeller = labeller(eth_loc_lib = eth_loc_lib.labs, circle_orange = circle_orange_labs)) +
-               #nrow =2 , dir = "v")  +
-
- scale_color_manual(values = c("purple","dark green"), guide = guide_legend(title= "")) + # ,nrow=2, byrow = TRUE)) +
- scale_shape_manual(values = c("circle","square"), guide = guide_legend(title= "")) + #,nrow=2, byrow = TRUE)) + 
-   ylab("Segregation") +   
-  xlab("Ethnic liberal migrants") + 
- guides(color = FALSE, shape = FALSE) +
-ggtitle("ß dominant migrants: 20\nß dominant locals: 20") +
-  theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(),legend.text = element_text(size = 12),
-                      axis.title.y =   (element_text(size = 12)), # element_blank(),  # 
-                      axis.title.x =  (element_text(size = 14)), #   element_blank(),  # 
-                      axis.text.x = (element_text(size = 10)),
-                      axis.text.y =  (element_text(size = 10)),
-                      plot.title=element_text(face="bold", size = 14),   
-                      legend.margin=margin(0,0,0,0), panel.spacing = unit(0.8, "lines"), 
-                      strip.text.x = element_text(size = 15),  strip.text.y = element_text(size = 15),
-                      plot.caption = element_text(hjust= 0.5, size = 12)) +
-theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
-
-ggsave("hc_hc8_min.jpg",last_plot(),
-  device = NULL,
-  path = NULL,
-  scale = 2,
-  width = 6,
-  height = 3,
- # units = ("in", "cm", "mm"),
-  dpi = 300,
-  limitsize = TRUE)
-
-# Intermediate randomness Locals x-axys
-
-hc_hc8_maj <- df_eth_loc  %>% filter(ID == "hc_hc") %>% filter(circle_orange == 80)  %>% filter(eth_min_lib == 0 | eth_min_lib == 5 | eth_min_lib == 10 | eth_min_lib == 20) %>% gather(key = subgroup, value = Segra, eth_sqr_loc, eth_sqr_min, eth_crl_loc, eth_crl_min, val_sqr_loc,val_sqr_min,val_crl_loc, val_crl_min) %>%mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"ethnic seg." = c("eth_sqr_loc","eth_sqr_min","eth_crl_loc","eth_crl_min"), "value seg." = c("val_sqr_loc","val_sqr_min","val_crl_loc", "val_crl_min")), "ethnic seg."), `group` = fct_relevel(fct_collapse(subgroup, "liberal" = c("eth_crl_loc","eth_crl_min","val_crl_loc", "val_crl_min"), "conservative" = c("eth_sqr_loc","eth_sqr_min","val_sqr_loc","val_sqr_min")), "liberal"),
-  `ethnia` = fct_relevel(fct_collapse(subgroup, "Locals:80% ethnic\n 50% liberal" = c("eth_sqr_loc","eth_crl_loc","val_sqr_loc","val_crl_loc"), "Migrants: 20% ethnic\n 80% liberal" = c("eth_sqr_min","eth_crl_min","val_sqr_min","val_crl_min")),"Locals:80% ethnic\n 50% liberal" ))  %>%
-
-  ggplot( aes(x = eth_loc_lib, y = Segra, color = `segregation`, shape = `group` )) + geom_line() + geom_point(size = 3) +
-
-  scale_x_discrete(limits= c(0,1,2,3,4,5,10,15,20)) +
-
-  scale_y_continuous(limits=c(0,1), breaks = c(0,0.2,0.5,0.8,1)) +
-  geom_vline(xintercept = c(1,5,10,20), color = "red") +
-    geom_hline(yintercept = c(0.5), color = "red", linetype = 2) +
-      geom_hline(yintercept = c(0.8), color = "purple", linetype = 5) +
-      geom_hline(yintercept = c(0.2), color = "purple", linetype = 2) +
-  facet_grid(`ethnia` ~ eth_min_lib, labeller = labeller(eth_min_lib = eth_min_lib.labs, circle_orange = circle_orange_labs)) +
-               #nrow =2 , dir = "v")  +
-
- scale_color_manual(values = c("purple","dark green"), guide = guide_legend(title= "")) + # ,nrow=2, byrow = TRUE)) +
- scale_shape_manual(values = c("circle","square"), guide = guide_legend(title= "")) + #,nrow=2, byrow = TRUE)) + 
-   ylab("Segregation") +   
-  xlab("ethnic liberal locals") + 
-# guides(color = FALSE, shape = FALSE) +
-xlab("Ethnic liberal locals") + 
-# guides(color = FALSE, shape = FALSE) +
-ggtitle("ß dominant locals: 20\nß dominant migrants: 20") +
-  theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(),legend.text = element_text(size = 12),
-                      axis.title.y =   (element_text(size = 12)), # element_blank(),  # 
-                      axis.title.x =  (element_text(size = 14)), #   element_blank(),  # 
-                      axis.text.x = (element_text(size = 10)),
-                      axis.text.y =  (element_text(size = 10)),
-                      plot.title=element_text(face="bold", size = 14),   
-                      legend.margin=margin(0,0,0,0), panel.spacing = unit(0.8, "lines"), 
-                      strip.text.x = element_text(size = 15),  strip.text.y = element_text(size = 15),
-                      plot.caption = element_text(hjust= 0.5, size = 12)) +
-theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm")) 
-# 
-# comb <- ggarrange(mig,loc, nrow =  2, common.legend = TRUE, legend = "bottom")
-# annotate_figure(comb, 
-#                # top = text_grob("Dominant ß: 5",  face = "bold", size = 12),
-#                left = text_grob("Segregation", rot = 90, size = 12),
-#                 bottom = text_grob("ß value conservative both group: 0", hjust = 1, x = 1, size = 12),
-#                 )
-
-ggsave("hc_hc8_maj.jpg",hc_hc8_maj,
-  device = NULL,
-  path = NULL,
-   scale = 2,
-  width = 6,
-  height = 3,
- # units = c("in", "cm", "mm"),
-  dpi = 300,
-  limitsize = TRUE)
-
-```
-
-# TRASH
-
-```{r rand50locals, fig.width= 8,fig.height= 7, fig.pos="H",include=TRUE,fig.cap="Individual comparison rand 50", echo=FALSE}
-
-eth_min_lib.labs <- c("ß Ethnic liberal migrants: 0", "ß Ethnic liberal migrants: 1", "ß Ethnic liberal migrants: 2","ß Ethnic liberal migrants: 3","ß Ethnic liberal migrants: 4","ß Ethnic liberal migrants: 5","ß Ethnic liberal migrants: 10","ß Ethnic liberal migrants: 15","ß Ethnic liberal migrants: 20")
-names(eth_min_lib.labs) <- c("0","1","2","3","4", "5","10","15","20")
-eth_loc_lib.labs <- c("ß Ethnic liberal locals: 0", "ß Ethnic liberal locals: 1", "ß Ethnic liberal locals: 2","ß Ethnic liberal locals: 3","ß Ethnic liberal locals: 4","ß Ethnic liberal locals: 5","ß Ethnic liberal locals: 10","ß Ethnic liberal locals: 15","ß Ethnic liberal locals: 20")
-names(eth_loc_lib.labs) <-  c("0","1","2","3","4", "5","10","15","20")
-
-# Intermediate randomness Migrants x-axys
-
- df_eth_loc  %>% filter(ID == "lc_hc") %>% filter(circle_orange == 50)  %>% filter(eth_min_lib == 0 | eth_min_lib == 5 | eth_min_lib == 10 | eth_min_lib == 20) %>% gather(key = subgroup, value = Segra, eth_sqr_loc, eth_sqr_min, eth_crl_loc, eth_crl_min, val_sqr_loc,val_sqr_min,val_crl_loc, val_crl_min) %>%mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"ethnic seg." = c("eth_sqr_loc","eth_sqr_min","eth_crl_loc","eth_crl_min"), "value seg." = c("val_sqr_loc","val_sqr_min","val_crl_loc", "val_crl_min")), "ethnic seg."), `group` = fct_relevel(fct_collapse(subgroup, "liberal" = c("eth_crl_loc","eth_crl_min","val_crl_loc", "val_crl_min"), "conservative" = c("eth_sqr_loc","eth_sqr_min","val_sqr_loc","val_sqr_min")), "liberal"),
-  `ethnia` = fct_relevel(fct_collapse(subgroup, "Locals:80% ethnic\n 50% liberal" = c("eth_sqr_loc","eth_crl_loc","val_sqr_loc","val_crl_loc"), "Migrants: 20% ethnic\n 50% liberal" = c("eth_sqr_min","eth_crl_min","val_sqr_min","val_crl_min")),"Locals:80% ethnic\n 50% liberal" ))  %>%
-
-  ggplot( aes(x = eth_loc_lib, y = Segra, color = `segregation`, shape = `group` )) + geom_line() + geom_point(size = 3) +
-
-  scale_x_discrete(limits= c(0,1,2,3,4,5,10,15,20)) +
-
-  scale_y_continuous(limits=c(0,1), breaks = c(0,0.2,0.5,0.8,1)) +
-  geom_vline(xintercept = c(1,5,10,20), color = "red") +
-    geom_hline(yintercept = c(0.5), color = "red", linetype = 2) +
-      geom_hline(yintercept = c(0.8), color = "purple", linetype = 5) +
-      geom_hline(yintercept = c(0.2), color = "purple", linetype = 2) +
-  facet_grid(`ethnia` ~ eth_min_lib, labeller = labeller(eth_min_lib = eth_min_lib.labs, circle_orange = circle_orange_labs)) +
-               #nrow =2 , dir = "v")  +
-
- scale_color_manual(values = c("purple","dark green"), guide = guide_legend(title= "")) + # ,nrow=2, byrow = TRUE)) +
- scale_shape_manual(values = c("circle","square"), guide = guide_legend(title= "")) + #,nrow=2, byrow = TRUE)) + 
-   ylab("Segregation") +   
-  xlab("Ethnic liberal locals") + 
-#  guides(color = FALSE, shape = FALSE) +
-ggtitle("ß dominant migrants: 20\nß dominant locals: 5") +
-  theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(),legend.text = element_text(size = 12),
-                      axis.title.y =   (element_text(size = 12)), # element_blank(),  # 
-                      axis.title.x =  (element_text(size = 14)), #   element_blank(),  # 
-                      axis.text.x = (element_text(size = 10)),
-                      axis.text.y =  (element_text(size = 10)),
-                      plot.title=element_text(face="bold", size = 14),   
-                      legend.margin=margin(0,0,0,0), panel.spacing = unit(0.8, "lines"), 
-                      strip.text.x = element_text(size = 15),  strip.text.y = element_text(size = 15),
-                      plot.caption = element_text(hjust= 0.5, size = 12)) +
-theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
-
-ggsave("lc_hc5_min.jpg",last_plot(),
-  device = NULL,
-  path = NULL,
-  scale = 2,
-  width = 6,
-  height = 3,
- # units = ("in", "cm", "mm"),
-  dpi = 300,
-  limitsize = TRUE)
-
-# Intermediate randomness Locals x-axys
-
-df_eth_loc  %>% filter(ID == "hc_lc") %>% filter(circle_orange == 50)  %>% filter(eth_min_lib == 0 | eth_min_lib == 1 | eth_min_lib == 3 |   eth_min_lib == 5) %>% gather(key = subgroup, value = Segra, eth_sqr_loc, eth_sqr_min, eth_crl_loc, eth_crl_min, val_sqr_loc,val_sqr_min,val_crl_loc, val_crl_min) %>%mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"ethnic seg." = c("eth_sqr_loc","eth_sqr_min","eth_crl_loc","eth_crl_min"), "value seg." = c("val_sqr_loc","val_sqr_min","val_crl_loc", "val_crl_min")), "ethnic seg."), `group` = fct_relevel(fct_collapse(subgroup, "liberal" = c("eth_crl_loc","eth_crl_min","val_crl_loc", "val_crl_min"), "conservative" = c("eth_sqr_loc","eth_sqr_min","val_sqr_loc","val_sqr_min")), "liberal"),
-  `ethnia` = fct_relevel(fct_collapse(subgroup, "Locals:80% ethnic\n 50% liberal" = c("eth_sqr_loc","eth_crl_loc","val_sqr_loc","val_crl_loc"), "Migrants: 20% ethnic\n 50% liberal" = c("eth_sqr_min","eth_crl_min","val_sqr_min","val_crl_min")),"Locals:80% ethnic\n 50% liberal" ))  %>%
-
-  ggplot( aes(x = eth_loc_lib, y = Segra, color = `segregation`, shape = `group` )) + geom_line() + geom_point(size = 3) +
-
-  scale_x_discrete(limits= c(0,1,2,3,4,5,10,15,20)) +
-
-  scale_y_continuous(limits=c(0,1), breaks = c(0,0.2,0.5,0.8,1)) +
-  geom_vline(xintercept = c(1,5,10,20), color = "red") +
-    geom_hline(yintercept = c(0.5), color = "red", linetype = 2) +
-      geom_hline(yintercept = c(0.8), color = "purple", linetype = 5) +
-      geom_hline(yintercept = c(0.2), color = "purple", linetype = 2) +
-  facet_grid(`ethnia` ~ eth_min_lib, labeller = labeller(eth_min_lib = eth_min_lib.labs, circle_orange = circle_orange_labs)) +
-               #nrow =2 , dir = "v")  +
-
- scale_color_manual(values = c("purple","dark green"), guide = guide_legend(title= "")) + # ,nrow=2, byrow = TRUE)) +
- scale_shape_manual(values = c("circle","square"), guide = guide_legend(title= "")) + #,nrow=2, byrow = TRUE)) + 
-   ylab("Segregation") +   
-  xlab("ethnic liberal locals") + 
-# guides(color = FALSE, shape = FALSE) +
-xlab("Ethnic liberal locals") + 
-# guides(color = FALSE, shape = FALSE) +
-ggtitle("ß dominant locals: 20\nß dominant migrants: 5") +
-  theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(),legend.text = element_text(size = 12),
-                      axis.title.y =   (element_text(size = 12)), # element_blank(),  # 
-                      axis.title.x =  (element_text(size = 14)), #   element_blank(),  # 
-                      axis.text.x = (element_text(size = 10)),
-                      axis.text.y =  (element_text(size = 10)),
-                      plot.title=element_text(face="bold", size = 14),   
-                      legend.margin=margin(0,0,0,0), panel.spacing = unit(0.8, "lines"), 
-                      strip.text.x = element_text(size = 15),  strip.text.y = element_text(size = 15),
-                      plot.caption = element_text(hjust= 0.5, size = 12)) +
-theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
-
-# 
-# comb <- ggarrange(mig,loc, nrow =  2, common.legend = TRUE, legend = "bottom")
-# annotate_figure(comb, 
-#                # top = text_grob("Dominant ß: 5",  face = "bold", size = 12),
-#                left = text_grob("Segregation", rot = 90, size = 12),
-#                 bottom = text_grob("ß value conservative both group: 0", hjust = 1, x = 1, size = 12),
-#                 )
-
-ggsave("lc_hc5_maj.jpg",last_plot(),
-  device = NULL,
-  path = NULL,
-   scale = 2,
-  width = 6,
-  height = 3,
- # units = c("in", "cm", "mm"),
-  dpi = 300,
-  limitsize = TRUE)
-
-```
--->
+print(etlib_min80,type = "latex", file = "latex/etlib_min80.tex" , include.rownames=FALSE, add.to.row = addtorow, include.colnames = FALSE, latex.environments = "center")
+
+```

### 2021-04-12 analysis.Rmd
Update analysis.Rmd
simplified image (no scatterplot)

@@
 
-# Change work directory in quotes
-setwd("C:/Users/rocpa/OneDrive/Desktop/AF2/exp12_2020/")
+# Add working directory, substitute * in quotes (leave "/" for folders output of images and latex, or tweak). If bug with output name "images/" or "latex/", delete them in the name of output
+
+setwd("C:/Users/rocpa/OneDrive/Desktop/AF/ethnic-value_multinomial-master/")
 
@@
 
-plotname <- "images/vllblc.jpg"
+plotname <- "images/vllblc.jpg"  # delete images/ if bug
 xlab_t <- "ß value liberal local"
 
-xvalues <- c(dataset_sa$de_sq_bl_mean,dataset_sa$de_cl_bl_mean,dataset_sa$de_sq_or_mean,dataset_sa$de_cl_or_mean,
-       dataset_sa$dv_sq_bl_mean,dataset_sa$dv_cl_bl_mean,dataset_sa$dv_sq_or_mean,dataset_sa$dv_cl_or_mean)
-
- expo_pic <-   ggplot(data = dataset_sa) + 
-  geom_point(aes(x = dataset_sa$de_sq_bl_mean, y = dataset_sa$et_sq_bl_mean),color = "black", fill = "blue", shape = 22, size = 5) +
-  geom_point(aes(x = dataset_sa$de_cl_bl_mean, y = dataset_sa$et_cl_bl_mean),color = "black",fill = "blue", shape = 21, size = 5) +
-  geom_point(aes(x = dataset_sa$de_sq_or_mean, y = dataset_sa$et_sq_or_mean),color = "black", fill = "orange", shape = 22, size = 5) +
-  geom_point(aes(x = dataset_sa$de_cl_or_mean, y = dataset_sa$et_cl_or_mean),color = "black", fill = "orange", shape = 21, size = 5) +
-
-  geom_point(aes(x = dataset_sa$dv_sq_bl_mean, y = dataset_sa$vl_sq_bl_mean),color = "black", fill = "blue", shape = 8, size = 5.1) + 
-   geom_point(aes(x = dataset_sa$dv_sq_bl_mean, y = dataset_sa$vl_sq_bl_mean),color = "black", fill = "blue", shape = 22, size = 5) +
-
-   geom_point(aes(x = dataset_sa$dv_cl_bl_mean, y = dataset_sa$vl_cl_bl_mean),color = "black",fill = "blue", shape = 8, size = 5.1) + 
-  geom_point(aes(x = dataset_sa$dv_cl_bl_mean, y = dataset_sa$vl_cl_bl_mean),color = "black",fill = "blue", shape = 21, size = 5) +
-
-    geom_point(aes(x = dataset_sa$dv_sq_or_mean, y = dataset_sa$vl_sq_or_mean),color = "black", fill = "orange", shape = 8, size = 5.1) +
-  geom_point(aes(x = dataset_sa$dv_sq_or_mean, y = dataset_sa$vl_sq_or_mean),color = "black", fill = "orange", shape = 22, size = 5) +
-
-  geom_point(aes(x = dataset_sa$dv_cl_or_mean, y = dataset_sa$vl_cl_or_mean),color = "black", fill = "orange", shape = 8, size = 5.1) +
-geom_point(aes(x = dataset_sa$dv_cl_or_mean, y = dataset_sa$vl_cl_or_mean),color = "black", fill = "orange", shape = 21, size = 5) +
-
- scale_x_continuous(limits = c(min(xvalues),max(xvalues)), breaks = seq(0,max(xvalues), by = 0.5)) + 
-  scale_y_continuous(breaks= seq(0,1,by=0.1)) + 
-  geom_vline(xintercept = 1, color = "red") +
-   xlab(expression(Exposure[correct])) + ylab("Exposure") +
-  theme_bw() + theme( 
-    axis.title.x = (element_text(size = 13)), axis.title.y = (element_text(size = 15)),
-    axis.text.x =  (element_text(size = 12)), axis.text.y =  (element_text(size = 15)), 
-    legend.title = element_text(size = 13),legend.position = "bottom", legend.text = element_text(size = 13),
-    plot.title=element_text(hjust = 0.5), plot.caption = element_text(hjust= 0.5, size = 11), plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
+# deleted scatterplot
+
+# xvalues <- c(dataset_sa$de_sq_bl_mean,dataset_sa$de_cl_bl_mean,dataset_sa$de_sq_or_mean,dataset_sa$de_cl_or_mean,
+#        dataset_sa$dv_sq_bl_mean,dataset_sa$dv_cl_bl_mean,dataset_sa$dv_sq_or_mean,dataset_sa$dv_cl_or_mean)
+# 
+#  expo_pic <-   ggplot(data = dataset_sa) + 
+#   geom_point(aes(x = dataset_sa$de_sq_bl_mean, y = dataset_sa$et_sq_bl_mean),color = "black", fill = "blue", shape = 22, size = 5) +
+#   geom_point(aes(x = dataset_sa$de_cl_bl_mean, y = dataset_sa$et_cl_bl_mean),color = "black",fill = "blue", shape = 21, size = 5) +
+#   geom_point(aes(x = dataset_sa$de_sq_or_mean, y = dataset_sa$et_sq_or_mean),color = "black", fill = "orange", shape = 22, size = 5) +
+#   geom_point(aes(x = dataset_sa$de_cl_or_mean, y = dataset_sa$et_cl_or_mean),color = "black", fill = "orange", shape = 21, size = 5) +
+# 
+#   geom_point(aes(x = dataset_sa$dv_sq_bl_mean, y = dataset_sa$vl_sq_bl_mean),color = "black", fill = "blue", shape = 8, size = 5.1) + 
+#    geom_point(aes(x = dataset_sa$dv_sq_bl_mean, y = dataset_sa$vl_sq_bl_mean),color = "black", fill = "blue", shape = 22, size = 5) + 
+#   
+#    geom_point(aes(x = dataset_sa$dv_cl_bl_mean, y = dataset_sa$vl_cl_bl_mean),color = "black",fill = "blue", shape = 8, size = 5.1) + 
+#   geom_point(aes(x = dataset_sa$dv_cl_bl_mean, y = dataset_sa$vl_cl_bl_mean),color = "black",fill = "blue", shape = 21, size = 5) + 
+#   
+#     geom_point(aes(x = dataset_sa$dv_sq_or_mean, y = dataset_sa$vl_sq_or_mean),color = "black", fill = "orange", shape = 8, size = 5.1) +
+#   geom_point(aes(x = dataset_sa$dv_sq_or_mean, y = dataset_sa$vl_sq_or_mean),color = "black", fill = "orange", shape = 22, size = 5) +
+#   
+#   geom_point(aes(x = dataset_sa$dv_cl_or_mean, y = dataset_sa$vl_cl_or_mean),color = "black", fill = "orange", shape = 8, size = 5.1) +
+# geom_point(aes(x = dataset_sa$dv_cl_or_mean, y = dataset_sa$vl_cl_or_mean),color = "black", fill = "orange", shape = 21, size = 5) +
+#   
+#  scale_x_continuous(limits = c(min(xvalues),max(xvalues)), breaks = seq(0,max(xvalues), by = 0.5)) + 
+#   scale_y_continuous(breaks= seq(0,1,by=0.1)) + 
+#   geom_vline(xintercept = 1, color = "red") +
+#    xlab(expression(Exposure[correct])) + ylab("Exposure") +
+#   theme_bw() + theme( 
+#     axis.title.x = (element_text(size = 13)), axis.title.y = (element_text(size = 15)),
+#     axis.text.x =  (element_text(size = 12)), axis.text.y =  (element_text(size = 15)), 
+#     legend.title = element_text(size = 13),legend.position = "bottom", legend.text = element_text(size = 13),
+#     plot.title=element_text(hjust = 0.5), plot.caption = element_text(hjust= 0.5, size = 11), plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
+#
 
@@
     strip.text = element_text(size=13),
-    legend.title = element_text(size = 13),legend.position = "bottom", legend.text = element_text(size = 14),
+    legend.title = element_text(size = 13),legend.position = "right", legend.text = element_text(size = 14),
     plot.title=element_text(hjust = 0.5), plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
@@
 #, plot.caption = element_text(hjust= 0.5, size = 11)
-ggpubr::ggarrange(prox_pic, expo_pic, common.legend = TRUE, legend = "bottom", widths = c(1.3,1))
+# ggpubr::ggarrange(prox_pic, expo_pic, common.legend = TRUE, legend = "bottom", widths = c(1.3,1))
 
@@
   scale = 1,
-  width = 12,
-  height = 9,
+  width = 7.5,
+  height = 7,
   units = c("in", "cm", "mm"),
@@
 
-plotname <- "images/vllbmn.jpg"
+plotname <- "images/vllbmn.jpg"  # delete images/ if bug
 xlab_t <- "ß value liberal minority"
 
-xvalues <- c(dataset_sa$de_sq_bl_mean,dataset_sa$de_cl_bl_mean,dataset_sa$de_sq_or_mean,dataset_sa$de_cl_or_mean,
-       dataset_sa$dv_sq_bl_mean,dataset_sa$dv_cl_bl_mean,dataset_sa$dv_sq_or_mean,dataset_sa$dv_cl_or_mean)
+# deleted scatterplot
+
+# xvalues <- c(dataset_sa$de_sq_bl_mean,dataset_sa$de_cl_bl_mean,dataset_sa$de_sq_or_mean,dataset_sa$de_cl_or_mean,
+       # dataset_sa$dv_sq_bl_mean,dataset_sa$dv_cl_bl_mean,dataset_sa$dv_sq_or_mean,dataset_sa$dv_cl_or_mean)
 
@@
 
- expo_pic <-   ggplot(data = dataset_sa) + 
-  geom_point(aes(x = dataset_sa$de_sq_bl_mean, y = dataset_sa$et_sq_bl_mean),color = "black", fill = "blue", shape = 22, size = 5) +
-  geom_point(aes(x = dataset_sa$de_cl_bl_mean, y = dataset_sa$et_cl_bl_mean),color = "black",fill = "blue", shape = 21, size = 5) +
-  geom_point(aes(x = dataset_sa$de_sq_or_mean, y = dataset_sa$et_sq_or_mean),color = "black", fill = "orange", shape = 22, size = 5) +
-  geom_point(aes(x = dataset_sa$de_cl_or_mean, y = dataset_sa$et_cl_or_mean),color = "black", fill = "orange", shape = 21, size = 5) +
-
-  geom_point(aes(x = dataset_sa$dv_sq_bl_mean, y = dataset_sa$vl_sq_bl_mean),color = "black", fill = "blue", shape = 8, size = 5.1) + 
-   geom_point(aes(x = dataset_sa$dv_sq_bl_mean, y = dataset_sa$vl_sq_bl_mean),color = "black", fill = "blue", shape = 22, size = 5) +
-
-   geom_point(aes(x = dataset_sa$dv_cl_bl_mean, y = dataset_sa$vl_cl_bl_mean),color = "black",fill = "blue", shape = 8, size = 5.1) + 
-  geom_point(aes(x = dataset_sa$dv_cl_bl_mean, y = dataset_sa$vl_cl_bl_mean),color = "black",fill = "blue", shape = 21, size = 5) +
-
-    geom_point(aes(x = dataset_sa$dv_sq_or_mean, y = dataset_sa$vl_sq_or_mean),color = "black", fill = "orange", shape = 8, size = 5.1) +
-  geom_point(aes(x = dataset_sa$dv_sq_or_mean, y = dataset_sa$vl_sq_or_mean),color = "black", fill = "orange", shape = 22, size = 5) +
-
-  geom_point(aes(x = dataset_sa$dv_cl_or_mean, y = dataset_sa$vl_cl_or_mean),color = "black", fill = "orange", shape = 8, size = 5.1) +
-geom_point(aes(x = dataset_sa$dv_cl_or_mean, y = dataset_sa$vl_cl_or_mean),color = "black", fill = "orange", shape = 21, size = 5) +
-
- scale_x_continuous(limits = c(min(xvalues),max(xvalues)), breaks = seq(0,max(xvalues), by = 0.5)) + 
-  scale_y_continuous(breaks= seq(0,1,by=0.1)) + 
-  geom_vline(xintercept = 1, color = "red") +
-   xlab(expression(Exposure[correct])) + ylab("Exposure") +
-  theme_bw() + theme( 
-    axis.title.x = (element_text(size = 13)), axis.title.y = (element_text(size = 15)),
-    axis.text.x =  (element_text(size = 12)), axis.text.y =  (element_text(size = 15)), 
-    legend.title = element_text(size = 13),legend.position = "bottom", legend.text = element_text(size = 13),
-    plot.title=element_text(hjust = 0.5), plot.caption = element_text(hjust= 0.5, size = 11), plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
+#  expo_pic <-   ggplot(data = dataset_sa) + 
+#   geom_point(aes(x = dataset_sa$de_sq_bl_mean, y = dataset_sa$et_sq_bl_mean),color = "black", fill = "blue", shape = 22, size = 5) +
+#   geom_point(aes(x = dataset_sa$de_cl_bl_mean, y = dataset_sa$et_cl_bl_mean),color = "black",fill = "blue", shape = 21, size = 5) +
+#   geom_point(aes(x = dataset_sa$de_sq_or_mean, y = dataset_sa$et_sq_or_mean),color = "black", fill = "orange", shape = 22, size = 5) +
+#   geom_point(aes(x = dataset_sa$de_cl_or_mean, y = dataset_sa$et_cl_or_mean),color = "black", fill = "orange", shape = 21, size = 5) +
+# 
+#   geom_point(aes(x = dataset_sa$dv_sq_bl_mean, y = dataset_sa$vl_sq_bl_mean),color = "black", fill = "blue", shape = 8, size = 5.1) + 
+#    geom_point(aes(x = dataset_sa$dv_sq_bl_mean, y = dataset_sa$vl_sq_bl_mean),color = "black", fill = "blue", shape = 22, size = 5) + 
+#   
+#    geom_point(aes(x = dataset_sa$dv_cl_bl_mean, y = dataset_sa$vl_cl_bl_mean),color = "black",fill = "blue", shape = 8, size = 5.1) + 
+#   geom_point(aes(x = dataset_sa$dv_cl_bl_mean, y = dataset_sa$vl_cl_bl_mean),color = "black",fill = "blue", shape = 21, size = 5) + 
+#   
+#     geom_point(aes(x = dataset_sa$dv_sq_or_mean, y = dataset_sa$vl_sq_or_mean),color = "black", fill = "orange", shape = 8, size = 5.1) +
+#   geom_point(aes(x = dataset_sa$dv_sq_or_mean, y = dataset_sa$vl_sq_or_mean),color = "black", fill = "orange", shape = 22, size = 5) +
+#   
+#   geom_point(aes(x = dataset_sa$dv_cl_or_mean, y = dataset_sa$vl_cl_or_mean),color = "black", fill = "orange", shape = 8, size = 5.1) +
+# geom_point(aes(x = dataset_sa$dv_cl_or_mean, y = dataset_sa$vl_cl_or_mean),color = "black", fill = "orange", shape = 21, size = 5) +
+#   
+#  scale_x_continuous(limits = c(min(xvalues),max(xvalues)), breaks = seq(0,max(xvalues), by = 0.5)) + 
+#   scale_y_continuous(breaks= seq(0,1,by=0.1)) + 
+#   geom_vline(xintercept = 1, color = "red") +
+#    xlab(expression(Exposure[correct])) + ylab("Exposure") +
+#   theme_bw() + theme( 
+#     axis.title.x = (element_text(size = 13)), axis.title.y = (element_text(size = 15)),
+#     axis.text.x =  (element_text(size = 12)), axis.text.y =  (element_text(size = 15)), 
+#     legend.title = element_text(size = 13),legend.position = "bottom", legend.text = element_text(size = 13),
+#     plot.title=element_text(hjust = 0.5), plot.caption = element_text(hjust= 0.5, size = 11), plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
 
@@
 
-plotname <- "images/et_libloc.jpg"
+plotname <- "images/et_libloc.jpg" # delete images/ if bug
 xlab_t <- "ß ethnic liberal local"
 
-xvalues <- c(etlib_df$de_sq_bl_mean,etlib_df$de_cl_bl_mean,etlib_df$de_sq_or_mean,etlib_df$de_cl_or_mean,
-       etlib_df$dv_sq_bl_mean,etlib_df$dv_cl_bl_mean,etlib_df$dv_sq_or_mean,etlib_df$dv_cl_or_mean)
-
- expo_pic <-   ggplot(data = etlib_df) + 
-  geom_point(aes(x = etlib_df$de_sq_bl_mean, y = etlib_df$et_sq_bl_mean),color = "black", fill = "blue", shape = 22, size = 5) +
-  geom_point(aes(x = etlib_df$de_cl_bl_mean, y = etlib_df$et_cl_bl_mean),color = "black",fill = "blue", shape = 21, size = 5) +
-  geom_point(aes(x = etlib_df$de_sq_or_mean, y = etlib_df$et_sq_or_mean),color = "black", fill = "orange", shape = 22, size = 5) +
-  geom_point(aes(x = etlib_df$de_cl_or_mean, y = etlib_df$et_cl_or_mean),color = "black", fill = "orange", shape = 21, size = 5) +
-
-  geom_point(aes(x = etlib_df$dv_sq_bl_mean, y = etlib_df$vl_sq_bl_mean),color = "black", fill = "blue", shape = 8, size = 5.1) + 
-   geom_point(aes(x = etlib_df$dv_sq_bl_mean, y = etlib_df$vl_sq_bl_mean),color = "black", fill = "blue", shape = 22, size = 5) +
-
-   geom_point(aes(x = etlib_df$dv_cl_bl_mean, y = etlib_df$vl_cl_bl_mean),color = "black",fill = "blue", shape = 8, size = 5.1) + 
-  geom_point(aes(x = etlib_df$dv_cl_bl_mean, y = etlib_df$vl_cl_bl_mean),color = "black",fill = "blue", shape = 21, size = 5) +
-
-    geom_point(aes(x = etlib_df$dv_sq_or_mean, y = etlib_df$vl_sq_or_mean),color = "black", fill = "orange", shape = 8, size = 5.1) +
-  geom_point(aes(x = etlib_df$dv_sq_or_mean, y = etlib_df$vl_sq_or_mean),color = "black", fill = "orange", shape = 22, size = 5) +
-
-  geom_point(aes(x = etlib_df$dv_cl_or_mean, y = etlib_df$vl_cl_or_mean),color = "black", fill = "orange", shape = 8, size = 5.1) +
-geom_point(aes(x = etlib_df$dv_cl_or_mean, y = etlib_df$vl_cl_or_mean),color = "black", fill = "orange", shape = 21, size = 5) +
-
- scale_x_continuous(limits = c(min(xvalues),max(xvalues)), breaks = seq(0,max(xvalues), by = 0.5)) + 
-  scale_y_continuous(breaks= seq(0,1,by=0.1)) + 
-  geom_vline(xintercept = 1, color = "red") +
-  xlab(expression(Exposure[correct])) +  + ylab("Exposure") +
-  theme_bw() + theme( 
-    axis.title.x = (element_text(size = 13)), axis.title.y = (element_text(size = 15)),
-    axis.text.x =  (element_text(size = 12)), axis.text.y =  (element_text(size = 15)), 
-    legend.title = element_text(size = 13),legend.position = "bottom", legend.text = element_text(size = 13),
-    plot.title=element_text(hjust = 0.5), plot.caption = element_text(hjust= 0.5, size = 11), plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
+# deleted scatterplot
+
+# xvalues <- c(etlib_df$de_sq_bl_mean,etlib_df$de_cl_bl_mean,etlib_df$de_sq_or_mean,etlib_df$de_cl_or_mean,
+#        etlib_df$dv_sq_bl_mean,etlib_df$dv_cl_bl_mean,etlib_df$dv_sq_or_mean,etlib_df$dv_cl_or_mean)
+# 
+#  expo_pic <-   ggplot(data = etlib_df) + 
+#   geom_point(aes(x = etlib_df$de_sq_bl_mean, y = etlib_df$et_sq_bl_mean),color = "black", fill = "blue", shape = 22, size = 5) +
+#   geom_point(aes(x = etlib_df$de_cl_bl_mean, y = etlib_df$et_cl_bl_mean),color = "black",fill = "blue", shape = 21, size = 5) +
+#   geom_point(aes(x = etlib_df$de_sq_or_mean, y = etlib_df$et_sq_or_mean),color = "black", fill = "orange", shape = 22, size = 5) +
+#   geom_point(aes(x = etlib_df$de_cl_or_mean, y = etlib_df$et_cl_or_mean),color = "black", fill = "orange", shape = 21, size = 5) +
+# 
+#   geom_point(aes(x = etlib_df$dv_sq_bl_mean, y = etlib_df$vl_sq_bl_mean),color = "black", fill = "blue", shape = 8, size = 5.1) + 
+#    geom_point(aes(x = etlib_df$dv_sq_bl_mean, y = etlib_df$vl_sq_bl_mean),color = "black", fill = "blue", shape = 22, size = 5) + 
+#   
+#    geom_point(aes(x = etlib_df$dv_cl_bl_mean, y = etlib_df$vl_cl_bl_mean),color = "black",fill = "blue", shape = 8, size = 5.1) + 
+#   geom_point(aes(x = etlib_df$dv_cl_bl_mean, y = etlib_df$vl_cl_bl_mean),color = "black",fill = "blue", shape = 21, size = 5) + 
+#   
+#     geom_point(aes(x = etlib_df$dv_sq_or_mean, y = etlib_df$vl_sq_or_mean),color = "black", fill = "orange", shape = 8, size = 5.1) +
+#   geom_point(aes(x = etlib_df$dv_sq_or_mean, y = etlib_df$vl_sq_or_mean),color = "black", fill = "orange", shape = 22, size = 5) +
+#   
+#   geom_point(aes(x = etlib_df$dv_cl_or_mean, y = etlib_df$vl_cl_or_mean),color = "black", fill = "orange", shape = 8, size = 5.1) +
+# geom_point(aes(x = etlib_df$dv_cl_or_mean, y = etlib_df$vl_cl_or_mean),color = "black", fill = "orange", shape = 21, size = 5) +
+#   
+#  scale_x_continuous(limits = c(min(xvalues),max(xvalues)), breaks = seq(0,max(xvalues), by = 0.5)) + 
+#   scale_y_continuous(breaks= seq(0,1,by=0.1)) + 
+#   geom_vline(xintercept = 1, color = "red") +
+#   xlab(expression(Exposure[correct])) +  + ylab("Exposure") +
+#   theme_bw() + theme( 
+#     axis.title.x = (element_text(size = 13)), axis.title.y = (element_text(size = 15)),
+#     axis.text.x =  (element_text(size = 12)), axis.text.y =  (element_text(size = 15)), 
+#     legend.title = element_text(size = 13),legend.position = "bottom", legend.text = element_text(size = 13),
+#     plot.title=element_text(hjust = 0.5), plot.caption = element_text(hjust= 0.5, size = 11), plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
+#
 
@@
 
-plotname <- "images/et_libmin.jpg"
+plotname <- "images/et_libmin.jpg" # delete images/ if bug
 xlab_t <- "ß ethnic liberal minority"
 
-xvalues <- c(etlib_df$de_sq_bl_mean,etlib_df$de_cl_bl_mean,etlib_df$de_sq_or_mean,etlib_df$de_cl_or_mean,
-       etlib_df$dv_sq_bl_mean,etlib_df$dv_cl_bl_mean,etlib_df$dv_sq_or_mean,etlib_df$dv_cl_or_mean)
-
- expo_pic <-   ggplot(data = etlib_df) + 
-  geom_point(aes(x = etlib_df$de_sq_bl_mean, y = etlib_df$et_sq_bl_mean),color = "black", fill = "blue", shape = 22, size = 5) +
-  geom_point(aes(x = etlib_df$de_cl_bl_mean, y = etlib_df$et_cl_bl_mean),color = "black",fill = "blue", shape = 21, size = 5) +
-  geom_point(aes(x = etlib_df$de_sq_or_mean, y = etlib_df$et_sq_or_mean),color = "black", fill = "orange", shape = 22, size = 5) +
-  geom_point(aes(x = etlib_df$de_cl_or_mean, y = etlib_df$et_cl_or_mean),color = "black", fill = "orange", shape = 21, size = 5) +
-
-  geom_point(aes(x = etlib_df$dv_sq_bl_mean, y = etlib_df$vl_sq_bl_mean),color = "black", fill = "blue", shape = 8, size = 5.1) + 
-   geom_point(aes(x = etlib_df$dv_sq_bl_mean, y = etlib_df$vl_sq_bl_mean),color = "black", fill = "blue", shape = 22, size = 5) +
-
-   geom_point(aes(x = etlib_df$dv_cl_bl_mean, y = etlib_df$vl_cl_bl_mean),color = "black",fill = "blue", shape = 8, size = 5.1) + 
-  geom_point(aes(x = etlib_df$dv_cl_bl_mean, y = etlib_df$vl_cl_bl_mean),color = "black",fill = "blue", shape = 21, size = 5) +
-
-    geom_point(aes(x = etlib_df$dv_sq_or_mean, y = etlib_df$vl_sq_or_mean),color = "black", fill = "orange", shape = 8, size = 5.1) +
-  geom_point(aes(x = etlib_df$dv_sq_or_mean, y = etlib_df$vl_sq_or_mean),color = "black", fill = "orange", shape = 22, size = 5) +
-
-  geom_point(aes(x = etlib_df$dv_cl_or_mean, y = etlib_df$vl_cl_or_mean),color = "black", fill = "orange", shape = 8, size = 5.1) +
-geom_point(aes(x = etlib_df$dv_cl_or_mean, y = etlib_df$vl_cl_or_mean),color = "black", fill = "orange", shape = 21, size = 5) +
-
- scale_x_continuous(limits = c(min(xvalues),max(xvalues)), breaks = seq(0,max(xvalues), by = 0.5)) + 
-  scale_y_continuous(breaks= seq(0,1,by=0.1)) + 
-  geom_vline(xintercept = 1, color = "red") +
-  xlab(expression(Exposure[correct])) + ylab("Exposure") +
-  theme_bw() + theme( 
-    axis.title.x = (element_text(size = 13)), axis.title.y = (element_text(size = 15)),
-    axis.text.x =  (element_text(size = 12)), axis.text.y =  (element_text(size = 15)), 
-    legend.title = element_text(size = 13),legend.position = "bottom", legend.text = element_text(size = 13),
-    plot.title=element_text(hjust = 0.5), plot.caption = element_text(hjust= 0.5, size = 11), plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
-
+# deleted scatterplot
+
+# xvalues <- c(etlib_df$de_sq_bl_mean,etlib_df$de_cl_bl_mean,etlib_df$de_sq_or_mean,etlib_df$de_cl_or_mean,
+#        etlib_df$dv_sq_bl_mean,etlib_df$dv_cl_bl_mean,etlib_df$dv_sq_or_mean,etlib_df$dv_cl_or_mean)
+# 
+#  expo_pic <-   ggplot(data = etlib_df) + 
+#   geom_point(aes(x = etlib_df$de_sq_bl_mean, y = etlib_df$et_sq_bl_mean),color = "black", fill = "blue", shape = 22, size = 5) +
+#   geom_point(aes(x = etlib_df$de_cl_bl_mean, y = etlib_df$et_cl_bl_mean),color = "black",fill = "blue", shape = 21, size = 5) +
+#   geom_point(aes(x = etlib_df$de_sq_or_mean, y = etlib_df$et_sq_or_mean),color = "black", fill = "orange", shape = 22, size = 5) +
+#   geom_point(aes(x = etlib_df$de_cl_or_mean, y = etlib_df$et_cl_or_mean),color = "black", fill = "orange", shape = 21, size = 5) +
+# 
+#   geom_point(aes(x = etlib_df$dv_sq_bl_mean, y = etlib_df$vl_sq_bl_mean),color = "black", fill = "blue", shape = 8, size = 5.1) + 
+#    geom_point(aes(x = etlib_df$dv_sq_bl_mean, y = etlib_df$vl_sq_bl_mean),color = "black", fill = "blue", shape = 22, size = 5) + 
+#   
+#    geom_point(aes(x = etlib_df$dv_cl_bl_mean, y = etlib_df$vl_cl_bl_mean),color = "black",fill = "blue", shape = 8, size = 5.1) + 
+#   geom_point(aes(x = etlib_df$dv_cl_bl_mean, y = etlib_df$vl_cl_bl_mean),color = "black",fill = "blue", shape = 21, size = 5) + 
+#   
+#     geom_point(aes(x = etlib_df$dv_sq_or_mean, y = etlib_df$vl_sq_or_mean),color = "black", fill = "orange", shape = 8, size = 5.1) +
+#   geom_point(aes(x = etlib_df$dv_sq_or_mean, y = etlib_df$vl_sq_or_mean),color = "black", fill = "orange", shape = 22, size = 5) +
+#   
+#   geom_point(aes(x = etlib_df$dv_cl_or_mean, y = etlib_df$vl_cl_or_mean),color = "black", fill = "orange", shape = 8, size = 5.1) +
+# geom_point(aes(x = etlib_df$dv_cl_or_mean, y = etlib_df$vl_cl_or_mean),color = "black", fill = "orange", shape = 21, size = 5) +
+#   
+#  scale_x_continuous(limits = c(min(xvalues),max(xvalues)), breaks = seq(0,max(xvalues), by = 0.5)) + 
+#   scale_y_continuous(breaks= seq(0,1,by=0.1)) + 
+#   geom_vline(xintercept = 1, color = "red") +
+#   xlab(expression(Exposure[correct])) + ylab("Exposure") +
+#   theme_bw() + theme( 
+#     axis.title.x = (element_text(size = 13)), axis.title.y = (element_text(size = 15)),
+#     axis.text.x =  (element_text(size = 12)), axis.text.y =  (element_text(size = 15)), 
+#     legend.title = element_text(size = 13),legend.position = "bottom", legend.text = element_text(size = 13),
+#     plot.title=element_text(hjust = 0.5), plot.caption = element_text(hjust= 0.5, size = 11), plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
+#  
+# 
 data_prox <- etlib_df  %>% gather(key= subgroup, value = Prox, de_sq_bl_mean, dv_sq_bl_mean, de_cl_bl_mean, dv_cl_bl_mean, de_sq_or_mean, dv_sq_or_mean, de_cl_or_mean, dv_cl_or_mean) %>% mutate(

### 2021-04-28 analysis.Rmd
del exposure index scatterplot

@@
 library(viridis)
+library(data.table)
 options(xtable.floating = FALSE)
@@
 
-# Add working directory, substitute * in quotes (leave "/" for folders output of images and latex, or tweak). If bug with output name "images/" or "latex/", delete them in the name of output
-
+# Set workind directory
 setwd("C:/Users/rocpa/OneDrive/Desktop/AF/ethnic-value_multinomial-master/")
@@
 asym_dom <- read.csv("df_asym_dom.csv",sep = ",")          # asymmetric conditions, baseline figure dominant preference
-dislib <- read.csv("df_dislib.csv", sep = ",")             # sensitivity to distribution of liberals
-sa_asym <- read.csv("df_sa_asym.csv",sep =",")             # sensitivity analysis, ethnic asymmetry
-etlib <- read.csv("df_etlib.csv",sep =",")                 # ethnic preference liberals, ethnic asymmetry
+dislib <- read.csv("df_dislib.csv", sep = ",")             # sensitivity to distribution of liberals, sensitivity analysis, ethnic asymmetry
+# etlib <- read.csv("df_etlib.csv",sep =",")                 # ethnic preference liberals, ethnic asymmetry
 asym_all <- read.csv("df_asym_all.csv",sep =",")           # baseline ethnic  asymmetry
+# sa_asym <- read.csv("df_sa_asym.csv",sep =",")  #  PREVIOUS version is saved on GITHUB !! CHECK IF WORTH IT
+
+# Checked for 90!
+sa_asym <- read.csv("sa_asym_90.csv",sep =",")      
+etlib <- read.csv("etlib_90.csv",sep =",")
+
+# dfloc <- read.csv("test_90/etlib_loc.csv",sep = ",", skip = 6)
+# dfmin <- read.csv("test_90/etlib_min.csv",sep = ",", skip = 6)
+# names(dfloc) <- pull(read.csv("test_90/legend_90.csv"))
+# names(dfmin) <- pull(read.csv("test_90/legend_90.csv"))
+# etlib <- select(etlib, - c(32:47))
+# IDloc <- "etlib_loc"
+# IDmn <- "etlib_min"
+# dfloc <- cbind(IDloc,dfloc)
+# dfmin <- cbind(IDmn,dfmin)
+# names(dfmin)[names(dfmin) == "IDmn"] <- "ID"
+# etlib <- rbind(etlib,dfmin)
+# write.csv(etlib,"etlib_90.csv",row.names=FALSE)
 
@@
 
-circle_orange.labs <- c("20% liberal minority", "50% liberal minority", "80% liberal minority")
-names(circle_orange.labs) <- c("20","50","80")
+circle_orange.labs <- c("20% liberal minority", "50% liberal minority", "80% liberal minority","10% liberal minority","90% liberal minority")
+names(circle_orange.labs) <- c("20","50","80","10","90")
 
@@
 # database filter
+sa_asym <- sa_asym %>% filter(circle_orange == 10 | circle_orange == 50 | circle_orange == 90)
 excl <- names(sa_asym) %in% c("run", "ID","density","step","eth_lib_loc","val_con_loc","eth_lib_min","val_con_min")
@@
 
-plotname <- "images/vllblc.jpg"  # delete images/ if bug
+plotname <- "vllblc.jpg"  # delete images/ if bug
 xlab_t <- "ß value liberal local"
-
-# deleted scatterplot
-
-# xvalues <- c(dataset_sa$de_sq_bl_mean,dataset_sa$de_cl_bl_mean,dataset_sa$de_sq_or_mean,dataset_sa$de_cl_or_mean,
-#        dataset_sa$dv_sq_bl_mean,dataset_sa$dv_cl_bl_mean,dataset_sa$dv_sq_or_mean,dataset_sa$dv_cl_or_mean)
-# 
-#  expo_pic <-   ggplot(data = dataset_sa) + 
-#   geom_point(aes(x = dataset_sa$de_sq_bl_mean, y = dataset_sa$et_sq_bl_mean),color = "black", fill = "blue", shape = 22, size = 5) +
-#   geom_point(aes(x = dataset_sa$de_cl_bl_mean, y = dataset_sa$et_cl_bl_mean),color = "black",fill = "blue", shape = 21, size = 5) +
-#   geom_point(aes(x = dataset_sa$de_sq_or_mean, y = dataset_sa$et_sq_or_mean),color = "black", fill = "orange", shape = 22, size = 5) +
-#   geom_point(aes(x = dataset_sa$de_cl_or_mean, y = dataset_sa$et_cl_or_mean),color = "black", fill = "orange", shape = 21, size = 5) +
-# 
-#   geom_point(aes(x = dataset_sa$dv_sq_bl_mean, y = dataset_sa$vl_sq_bl_mean),color = "black", fill = "blue", shape = 8, size = 5.1) + 
-#    geom_point(aes(x = dataset_sa$dv_sq_bl_mean, y = dataset_sa$vl_sq_bl_mean),color = "black", fill = "blue", shape = 22, size = 5) + 
-#   
-#    geom_point(aes(x = dataset_sa$dv_cl_bl_mean, y = dataset_sa$vl_cl_bl_mean),color = "black",fill = "blue", shape = 8, size = 5.1) + 
-#   geom_point(aes(x = dataset_sa$dv_cl_bl_mean, y = dataset_sa$vl_cl_bl_mean),color = "black",fill = "blue", shape = 21, size = 5) + 
-#   
-#     geom_point(aes(x = dataset_sa$dv_sq_or_mean, y = dataset_sa$vl_sq_or_mean),color = "black", fill = "orange", shape = 8, size = 5.1) +
-#   geom_point(aes(x = dataset_sa$dv_sq_or_mean, y = dataset_sa$vl_sq_or_mean),color = "black", fill = "orange", shape = 22, size = 5) +
-#   
-#   geom_point(aes(x = dataset_sa$dv_cl_or_mean, y = dataset_sa$vl_cl_or_mean),color = "black", fill = "orange", shape = 8, size = 5.1) +
-# geom_point(aes(x = dataset_sa$dv_cl_or_mean, y = dataset_sa$vl_cl_or_mean),color = "black", fill = "orange", shape = 21, size = 5) +
-#   
-#  scale_x_continuous(limits = c(min(xvalues),max(xvalues)), breaks = seq(0,max(xvalues), by = 0.5)) + 
-#   scale_y_continuous(breaks= seq(0,1,by=0.1)) + 
-#   geom_vline(xintercept = 1, color = "red") +
-#    xlab(expression(Exposure[correct])) + ylab("Exposure") +
-#   theme_bw() + theme( 
-#     axis.title.x = (element_text(size = 13)), axis.title.y = (element_text(size = 15)),
-#     axis.text.x =  (element_text(size = 12)), axis.text.y =  (element_text(size = 15)), 
-#     legend.title = element_text(size = 13),legend.position = "bottom", legend.text = element_text(size = 13),
-#     plot.title=element_text(hjust = 0.5), plot.caption = element_text(hjust= 0.5, size = 11), plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
-#
 
@@
     plot.title=element_text(hjust = 0.5), plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
-
-#, plot.caption = element_text(hjust= 0.5, size = 11)
-# ggpubr::ggarrange(prox_pic, expo_pic, common.legend = TRUE, legend = "bottom", widths = c(1.3,1))
 
@@
 
-plotname <- "images/vllbmn.jpg"  # delete images/ if bug
+plotname <- "vllbmn.jpg"  # delete images/ if bug
 xlab_t <- "ß value liberal minority"
-
-# deleted scatterplot
-
-# xvalues <- c(dataset_sa$de_sq_bl_mean,dataset_sa$de_cl_bl_mean,dataset_sa$de_sq_or_mean,dataset_sa$de_cl_or_mean,
-       # dataset_sa$dv_sq_bl_mean,dataset_sa$dv_cl_bl_mean,dataset_sa$dv_sq_or_mean,dataset_sa$dv_cl_or_mean)
-
-# ethnic exposure plot
-
-#  expo_pic <-   ggplot(data = dataset_sa) + 
-#   geom_point(aes(x = dataset_sa$de_sq_bl_mean, y = dataset_sa$et_sq_bl_mean),color = "black", fill = "blue", shape = 22, size = 5) +
-#   geom_point(aes(x = dataset_sa$de_cl_bl_mean, y = dataset_sa$et_cl_bl_mean),color = "black",fill = "blue", shape = 21, size = 5) +
-#   geom_point(aes(x = dataset_sa$de_sq_or_mean, y = dataset_sa$et_sq_or_mean),color = "black", fill = "orange", shape = 22, size = 5) +
-#   geom_point(aes(x = dataset_sa$de_cl_or_mean, y = dataset_sa$et_cl_or_mean),color = "black", fill = "orange", shape = 21, size = 5) +
-# 
-#   geom_point(aes(x = dataset_sa$dv_sq_bl_mean, y = dataset_sa$vl_sq_bl_mean),color = "black", fill = "blue", shape = 8, size = 5.1) + 
-#    geom_point(aes(x = dataset_sa$dv_sq_bl_mean, y = dataset_sa$vl_sq_bl_mean),color = "black", fill = "blue", shape = 22, size = 5) + 
-#   
-#    geom_point(aes(x = dataset_sa$dv_cl_bl_mean, y = dataset_sa$vl_cl_bl_mean),color = "black",fill = "blue", shape = 8, size = 5.1) + 
-#   geom_point(aes(x = dataset_sa$dv_cl_bl_mean, y = dataset_sa$vl_cl_bl_mean),color = "black",fill = "blue", shape = 21, size = 5) + 
-#   
-#     geom_point(aes(x = dataset_sa$dv_sq_or_mean, y = dataset_sa$vl_sq_or_mean),color = "black", fill = "orange", shape = 8, size = 5.1) +
-#   geom_point(aes(x = dataset_sa$dv_sq_or_mean, y = dataset_sa$vl_sq_or_mean),color = "black", fill = "orange", shape = 22, size = 5) +
-#   
-#   geom_point(aes(x = dataset_sa$dv_cl_or_mean, y = dataset_sa$vl_cl_or_mean),color = "black", fill = "orange", shape = 8, size = 5.1) +
-# geom_point(aes(x = dataset_sa$dv_cl_or_mean, y = dataset_sa$vl_cl_or_mean),color = "black", fill = "orange", shape = 21, size = 5) +
-#   
-#  scale_x_continuous(limits = c(min(xvalues),max(xvalues)), breaks = seq(0,max(xvalues), by = 0.5)) + 
-#   scale_y_continuous(breaks= seq(0,1,by=0.1)) + 
-#   geom_vline(xintercept = 1, color = "red") +
-#    xlab(expression(Exposure[correct])) + ylab("Exposure") +
-#   theme_bw() + theme( 
-#     axis.title.x = (element_text(size = 13)), axis.title.y = (element_text(size = 15)),
-#     axis.text.x =  (element_text(size = 12)), axis.text.y =  (element_text(size = 15)), 
-#     legend.title = element_text(size = 13),legend.position = "bottom", legend.text = element_text(size = 13),
-#     plot.title=element_text(hjust = 0.5), plot.caption = element_text(hjust= 0.5, size = 11), plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
 
@@
 # database filter
+etlib <- etlib %>% filter(circle_orange == 10 | circle_orange == 50 | circle_orange == 90)
+
 excl <- names(etlib) %in% c("run", "ID","density","step","eth_con_loc","eth_con_min","val_lib_loc","val_lib_min","val_con_loc","val_con_min")
@@
 
-plotname <- "images/et_libloc.jpg" # delete images/ if bug
+plotname <- "et_libloc.jpg" # delete images/ if bug
 xlab_t <- "ß ethnic liberal local"
@@
 
-plotname <- "images/et_libmin.jpg" # delete images/ if bug
+plotname <- "et_libmin.jpg" # delete images/ if bug
 xlab_t <- "ß ethnic liberal minority"
@@
 
-xvalues <- c(dataset_sa$de_sq_bl_mean,dataset_sa$de_cl_bl_mean,dataset_sa$de_sq_or_mean,dataset_sa$de_cl_or_mean,
-       dataset_sa$dv_sq_bl_mean,dataset_sa$dv_cl_bl_mean,dataset_sa$dv_sq_or_mean,dataset_sa$dv_cl_or_mean)
-
- expo_pic <-   ggplot(data = dataset_sa) + 
-  geom_point(aes(x = dataset_sa$de_sq_bl_mean, y = dataset_sa$et_sq_bl_mean),color = "black", fill = "blue", shape = 22, size = 5) +
-  geom_point(aes(x = dataset_sa$de_cl_bl_mean, y = dataset_sa$et_cl_bl_mean),color = "black",fill = "blue", shape = 21, size = 5) +
-  geom_point(aes(x = dataset_sa$de_sq_or_mean, y = dataset_sa$et_sq_or_mean),color = "black", fill = "orange", shape = 22, size = 5) +
-  geom_point(aes(x = dataset_sa$de_cl_or_mean, y = dataset_sa$et_cl_or_mean),color = "black", fill = "orange", shape = 21, size = 5) +
-
-  geom_point(aes(x = dataset_sa$dv_sq_bl_mean, y = dataset_sa$vl_sq_bl_mean),color = "black", fill = "blue", shape = 8, size = 5.1) + 
-   geom_point(aes(x = dataset_sa$dv_sq_bl_mean, y = dataset_sa$vl_sq_bl_mean),color = "black", fill = "blue", shape = 22, size = 5) +
-
-   geom_point(aes(x = dataset_sa$dv_cl_bl_mean, y = dataset_sa$vl_cl_bl_mean),color = "black",fill = "blue", shape = 8, size = 5.1) + 
-  geom_point(aes(x = dataset_sa$dv_cl_bl_mean, y = dataset_sa$vl_cl_bl_mean),color = "black",fill = "blue", shape = 21, size = 5) +
-
-    geom_point(aes(x = dataset_sa$dv_sq_or_mean, y = dataset_sa$vl_sq_or_mean),color = "black", fill = "orange", shape = 8, size = 5.1) +
-  geom_point(aes(x = dataset_sa$dv_sq_or_mean, y = dataset_sa$vl_sq_or_mean),color = "black", fill = "orange", shape = 22, size = 5) +
-
-  geom_point(aes(x = dataset_sa$dv_cl_or_mean, y = dataset_sa$vl_cl_or_mean),color = "black", fill = "orange", shape = 8, size = 5.1) +
-geom_point(aes(x = dataset_sa$dv_cl_or_mean, y = dataset_sa$vl_cl_or_mean),color = "black", fill = "orange", shape = 21, size = 5) +
-
- scale_x_continuous(limits = c(min(xvalues),max(xvalues)), breaks = seq(0,max(xvalues), by = 0.5)) + 
-  scale_y_continuous(breaks= seq(0,1,by=0.1)) + 
-  geom_vline(xintercept = 1, color = "red") +
-   xlab(expression(Exposure[correct])) + ylab("Exposure") +
-  theme_bw() + theme( 
-    axis.title.x = (element_text(size = 13)), axis.title.y = (element_text(size = 15)),
-    axis.text.x =  (element_text(size = 12)), axis.text.y =  (element_text(size = 15)), 
-    legend.title = element_text(size = 13),legend.position = "bottom", legend.text = element_text(size = 13),
-    plot.title=element_text(hjust = 0.5), plot.caption = element_text(hjust= 0.5, size = 11), plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
-
 data_prox <- dataset_sa  %>% gather(key= subgroup, value = Prox, de_sq_bl_mean, dv_sq_bl_mean, de_cl_bl_mean, dv_cl_bl_mean, de_sq_or_mean, dv_sq_or_mean, de_cl_or_mean, dv_cl_or_mean) %>% mutate(
@@
     plot.title=element_text(hjust = 0.5), plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))
-
-#, plot.caption = element_text(hjust= 0.5, size = 11)
-ggpubr::ggarrange(prox_pic, expo_pic, common.legend = TRUE, legend = "bottom", widths = c(1.3,1))
 
@@
 "liberal local & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD\\\\\n")
-print(tablerb_prox50,type = "latex", file = "latex/vllblc50.tex"  , include.rownames=FALSE, add.to.row = addtorow, include.colnames = FALSE, latex.environments = "center")
-
-df_vllblc20 <- dataset_sa %>%  filter(circle_orange == 20)
-tablerb_prox20 <- xtable(df_vllblc20[,c("val_lib_loc","de_sq_bl_mean","de_sq_bl_sd","de_cl_bl_mean","de_cl_bl_sd","de_sq_or_mean","de_sq_or_sd","de_cl_or_mean","de_cl_or_sd","dv_sq_bl_mean","dv_sq_bl_sd","dv_cl_bl_mean","dv_cl_bl_sd","dv_sq_or_mean","dv_sq_or_sd","dv_cl_or_mean","dv_cl_or_sd")], digits = 3)
-align(tablerb_prox20) <- "c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|"
-addtorow <- list()
-addtorow$pos <- list(0, 0,0,0,0)
-addtorow$command <- c("\\multicolumn{17}{|c|}{Ethnic Asymmetry, $20 \\%$ Liberal Migrants: Spatial Proximity}  \\\\\\hline\n",
+print(tablerb_prox50,type = "latex", file = "vllblc50.tex"  , include.rownames=FALSE, add.to.row = addtorow, include.colnames = FALSE, latex.environments = "center")
+
+df_vllblc10 <- dataset_sa %>%  filter(circle_orange == 10)
+tablerb_prox10 <- xtable(df_vllblc10[,c("val_lib_loc","de_sq_bl_mean","de_sq_bl_sd","de_cl_bl_mean","de_cl_bl_sd","de_sq_or_mean","de_sq_or_sd","de_cl_or_mean","de_cl_or_sd","dv_sq_bl_mean","dv_sq_bl_sd","dv_cl_bl_mean","dv_cl_bl_sd","dv_sq_or_mean","dv_sq_or_sd","dv_cl_or_mean","dv_cl_or_sd")], digits = 3)
+align(tablerb_prox10) <- "c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|"
+addtorow <- list()
+addtorow$pos <- list(0, 0,0,0,0)
+addtorow$command <- c("\\multicolumn{17}{|c|}{Ethnic Asymmetry, $10 \\%$ Liberal Migrants: Spatial Proximity}  \\\\\\hline\n",
    "Preference &  \\multicolumn{8}{|c|}{Ethnic Proximity} & \\multicolumn{8}{|c|}{Value Proximity}   \\\\\\hline\n",
@@
 "liberal local & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD\\\\\n")
-print(tablerb_prox20,type = "latex", file = "latex/vllblc20.tex" , include.rownames=FALSE, add.to.row = addtorow, include.colnames = FALSE, latex.environments = "center")
-
-df_vllblc80 <- dataset_sa %>%  filter(circle_orange == 80)
-tablerb_prox80 <- xtable(df_vllblc80[,c("val_lib_loc","de_sq_bl_mean","de_sq_bl_sd","de_cl_bl_mean","de_cl_bl_sd","de_sq_or_mean","de_sq_or_sd","de_cl_or_mean","de_cl_or_sd","dv_sq_bl_mean","dv_sq_bl_sd","dv_cl_bl_mean","dv_cl_bl_sd","dv_sq_or_mean","dv_sq_or_sd","dv_cl_or_mean","dv_cl_or_sd")], digits = 3)
-align(tablerb_prox80) <- "c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|"
-addtorow <- list()
-addtorow$pos <- list(0, 0,0,0,0)
-addtorow$command <- c("\\multicolumn{17}{|c|}{Ethnic Asymmetry, $80 \\%$ Liberal Migrants: Spatial Proximity}  \\\\\\hline\n",
+print(tablerb_prox10,type = "latex", file = "vllblc10.tex" , include.rownames=FALSE, add.to.row = addtorow, include.colnames = FALSE, latex.environments = "center")
+
+df_vllblc90 <- dataset_sa %>%  filter(circle_orange == 90)
+tablerb_prox90 <- xtable(df_vllblc90[,c("val_lib_loc","de_sq_bl_mean","de_sq_bl_sd","de_cl_bl_mean","de_cl_bl_sd","de_sq_or_mean","de_sq_or_sd","de_cl_or_mean","de_cl_or_sd","dv_sq_bl_mean","dv_sq_bl_sd","dv_cl_bl_mean","dv_cl_bl_sd","dv_sq_or_mean","dv_sq_or_sd","dv_cl_or_mean","dv_cl_or_sd")], digits = 3)
+align(tablerb_prox90) <- "c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|"
+addtorow <- list()
+addtorow$pos <- list(0, 0,0,0,0)
+addtorow$command <- c("\\multicolumn{17}{|c|}{Ethnic Asymmetry, $90 \\%$ Liberal Migrants: Spatial Proximity}  \\\\\\hline\n",
    "Preference &  \\multicolumn{8}{|c|}{Ethnic Proximity} & \\multicolumn{8}{|c|}{Value Proximity}   \\\\\\hline\n",
@@
 "liberal local & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD\\\\\n")
-print(tablerb_prox80,type = "latex", file = "latex/vllblc80.tex" , include.rownames=FALSE, add.to.row = addtorow, include.colnames = FALSE, latex.environments = "center")
+print(tablerb_prox90,type = "latex", file = "vllblc90.tex" , include.rownames=FALSE, add.to.row = addtorow, include.colnames = FALSE, latex.environments = "center")
 
@@
 "liberal minority & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD\\\\\n")
-print(tablerb_mn50,type = "latex", file = "latex/vllbmn50.tex"  , include.rownames=FALSE, add.to.row = addtorow, include.colnames = FALSE, latex.environments = "center")
-
-df_vllbmn20 <- dataset_sa %>%  filter(circle_orange == 20)
-tablerb_mn20 <- xtable(df_vllbmn20[,c("val_lib_min","de_sq_bl_mean","de_sq_bl_sd","de_cl_bl_mean","de_cl_bl_sd","de_sq_or_mean","de_sq_or_sd","de_cl_or_mean","de_cl_or_sd","dv_sq_bl_mean","dv_sq_bl_sd","dv_cl_bl_mean","dv_cl_bl_sd","dv_sq_or_mean","dv_sq_or_sd","dv_cl_or_mean","dv_cl_or_sd")], digits = 3)
+print(tablerb_mn50,type = "latex", file = "vllbmn50.tex"  , include.rownames=FALSE, add.to.row = addtorow, include.colnames = FALSE, latex.environments = "center")
+
+df_vllbmn10 <- dataset_sa %>%  filter(circle_orange == 10)
+tablerb_mn10 <- xtable(df_vllbmn10[,c("val_lib_min","de_sq_bl_mean","de_sq_bl_sd","de_cl_bl_mean","de_cl_bl_sd","de_sq_or_mean","de_sq_or_sd","de_cl_or_mean","de_cl_or_sd","dv_sq_bl_mean","dv_sq_bl_sd","dv_cl_bl_mean","dv_cl_bl_sd","dv_sq_or_mean","dv_sq_or_sd","dv_cl_or_mean","dv_cl_or_sd")], digits = 3)
 align(tablerb_mn20) <- "c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|"
@@
 addtorow$pos <- list(0, 0,0,0,0)
-addtorow$command <- c("\\multicolumn{17}{|c|}{Ethnic Asymmetry, $20 \\%$ Liberal Migrants: Spatial Proximity}  \\\\\\hline\n",
+addtorow$command <- c("\\multicolumn{17}{|c|}{Ethnic Asymmetry, $10 \\%$ Liberal Migrants: Spatial Proximity}  \\\\\\hline\n",
    "Preference &  \\multicolumn{8}{|c|}{Ethnic Proximity} & \\multicolumn{8}{|c|}{Value Proximity}   \\\\\\hline\n",
@@
 "liberal minority & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD\\\\\n")
-print(tablerb_mn20,type = "latex", file = "latex/vllbmn20.tex" , include.rownames=FALSE, add.to.row = addtorow, include.colnames = FALSE, latex.environments = "center")
-
-df_vllbmn80 <- dataset_sa %>%  filter(circle_orange == 80)
-tablerb_mn80 <- xtable(df_vllbmn80[,c("val_lib_min","de_sq_bl_mean","de_sq_bl_sd","de_cl_bl_mean","de_cl_bl_sd","de_sq_or_mean","de_sq_or_sd","de_cl_or_mean","de_cl_or_sd","dv_sq_bl_mean","dv_sq_bl_sd","dv_cl_bl_mean","dv_cl_bl_sd","dv_sq_or_mean","dv_sq_or_sd","dv_cl_or_mean","dv_cl_or_sd")], digits = 3)
-align(tablerb_mn80) <- "c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|"
-addtorow <- list()
-addtorow$pos <- list(0, 0,0,0,0)
-addtorow$command <- c("\\multicolumn{17}{|c|}{Ethnic Asymmetry, $80 \\%$ Liberal Migrants: Spatial Proximity}  \\\\\\hline\n",
+print(tablerb_mn10,type = "latex", file = "vllbmn10.tex" , include.rownames=FALSE, add.to.row = addtorow, include.colnames = FALSE, latex.environments = "center")
+
+df_vllbmn90 <- dataset_sa %>%  filter(circle_orange == 90)
+tablerb_mn90 <- xtable(df_vllbmn90[,c("val_lib_min","de_sq_bl_mean","de_sq_bl_sd","de_cl_bl_mean","de_cl_bl_sd","de_sq_or_mean","de_sq_or_sd","de_cl_or_mean","de_cl_or_sd","dv_sq_bl_mean","dv_sq_bl_sd","dv_cl_bl_mean","dv_cl_bl_sd","dv_sq_or_mean","dv_sq_or_sd","dv_cl_or_mean","dv_cl_or_sd")], digits = 3)
+align(tablerb_mn90) <- "c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|"
+addtorow <- list()
+addtorow$pos <- list(0, 0,0,0,0)
+addtorow$command <- c("\\multicolumn{17}{|c|}{Ethnic Asymmetry, $90 \\%$ Liberal Migrants: Spatial Proximity}  \\\\\\hline\n",
    "Preference &  \\multicolumn{8}{|c|}{Ethnic Proximity} & \\multicolumn{8}{|c|}{Value Proximity}   \\\\\\hline\n",
@@
 "liberal minority & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD\\\\\n")
-print(tablerb_mn80,type = "latex", file = "latex/vllbmn80.tex" , include.rownames=FALSE, add.to.row = addtorow, include.colnames = FALSE, latex.environments = "center")
+print(tablerb_mn90,type = "latex", file = "vllbmn90.tex" , include.rownames=FALSE, add.to.row = addtorow, include.colnames = FALSE, latex.environments = "center")
 
@@
 "liberal local & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD\\\\\n")
-print(etlib_loc50,type = "latex", file = "latex/etlib_loc50.tex"  , include.rownames=FALSE, add.to.row = addtorow, include.colnames = FALSE, latex.environments = "center")
-
-df_etlib_loc20 <- etlib_df %>%  filter(circle_orange == 20)
-etlib_loc20 <- xtable(df_etlib_loc20[,c("eth_lib_loc","de_sq_bl_mean","de_sq_bl_sd","de_cl_bl_mean","de_cl_bl_sd","de_sq_or_mean","de_sq_or_sd","de_cl_or_mean","de_cl_or_sd","dv_sq_bl_mean","dv_sq_bl_sd","dv_cl_bl_mean","dv_cl_bl_sd","dv_sq_or_mean","dv_sq_or_sd","dv_cl_or_mean","dv_cl_or_sd")], digits = 3)
-align(etlib_loc20) <- "c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|"
-addtorow <- list()
-addtorow$pos <- list(0, 0,0,0,0)
-addtorow$command <- c("\\multicolumn{17}{|c|}{Ethnic Asymmetry, $20 \\%$ Liberal Migrants: Spatial Proximity}  \\\\\\hline\n",
+print(etlib_loc50,type = "latex", file = "etlib_loc50.tex"  , include.rownames=FALSE, add.to.row = addtorow, include.colnames = FALSE, latex.environments = "center")
+
+df_etlib_loc10 <- etlib_df %>%  filter(circle_orange == 10)
+etlib_loc10 <- xtable(df_etlib_loc10[,c("eth_lib_loc","de_sq_bl_mean","de_sq_bl_sd","de_cl_bl_mean","de_cl_bl_sd","de_sq_or_mean","de_sq_or_sd","de_cl_or_mean","de_cl_or_sd","dv_sq_bl_mean","dv_sq_bl_sd","dv_cl_bl_mean","dv_cl_bl_sd","dv_sq_or_mean","dv_sq_or_sd","dv_cl_or_mean","dv_cl_or_sd")], digits = 3)
+align(etlib_loc10) <- "c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|"
+addtorow <- list()
+addtorow$pos <- list(0, 0,0,0,0)
+addtorow$command <- c("\\multicolumn{17}{|c|}{Ethnic Asymmetry, $10 \\%$ Liberal Migrants: Spatial Proximity}  \\\\\\hline\n",
    "Preference &  \\multicolumn{8}{|c|}{Ethnic Proximity} & \\multicolumn{8}{|c|}{Value Proximity}   \\\\\\hline\n",
@@
 "liberal local & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD\\\\\n")
-print(etlib_loc20,type = "latex", file = "latex/etlib_loc20.tex" , include.rownames=FALSE, add.to.row = addtorow, include.colnames = FALSE, latex.environments = "center")
-
-df_etlib_loc80 <- etlib_df %>%  filter(circle_orange == 80)
-etlib_loc80 <- xtable(df_etlib_loc80[,c("eth_lib_loc","de_sq_bl_mean","de_sq_bl_sd","de_cl_bl_mean","de_cl_bl_sd","de_sq_or_mean","de_sq_or_sd","de_cl_or_mean","de_cl_or_sd","dv_sq_bl_mean","dv_sq_bl_sd","dv_cl_bl_mean","dv_cl_bl_sd","dv_sq_or_mean","dv_sq_or_sd","dv_cl_or_mean","dv_cl_or_sd")], digits = 3)
-align(etlib_loc80) <- "c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|"
-addtorow <- list()
-addtorow$pos <- list(0, 0,0,0,0)
-addtorow$command <- c("\\multicolumn{17}{|c|}{Ethnic Asymmetry, $80 \\%$ Liberal Migrants: Spatial Proximity}  \\\\\\hline\n",
+print(etlib_loc10,type = "latex", file = "etlib_loc10.tex" , include.rownames=FALSE, add.to.row = addtorow, include.colnames = FALSE, latex.environments = "center")
+
+df_etlib_loc90 <- etlib_df %>%  filter(circle_orange == 90)
+etlib_loc90 <- xtable(df_etlib_loc90[,c("eth_lib_loc","de_sq_bl_mean","de_sq_bl_sd","de_cl_bl_mean","de_cl_bl_sd","de_sq_or_mean","de_sq_or_sd","de_cl_or_mean","de_cl_or_sd","dv_sq_bl_mean","dv_sq_bl_sd","dv_cl_bl_mean","dv_cl_bl_sd","dv_sq_or_mean","dv_sq_or_sd","dv_cl_or_mean","dv_cl_or_sd")], digits = 3)
+align(etlib_loc90) <- "c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|"
+addtorow <- list()
+addtorow$pos <- list(0, 0,0,0,0)
+addtorow$command <- c("\\multicolumn{17}{|c|}{Ethnic Asymmetry, $90 \\%$ Liberal Migrants: Spatial Proximity}  \\\\\\hline\n",
    "Preference &  \\multicolumn{8}{|c|}{Ethnic Proximity} & \\multicolumn{8}{|c|}{Value Proximity}   \\\\\\hline\n",
@@
 "liberal local & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD\\\\\n")
-print(etlib_loc80,type = "latex", file = "latex/etlib_loc80.tex" , include.rownames=FALSE, add.to.row = addtorow, include.colnames = FALSE, latex.environments = "center")
+print(etlib_loc90,type = "latex", file = "etlib_loc90.tex" , include.rownames=FALSE, add.to.row = addtorow, include.colnames = FALSE, latex.environments = "center")
 
@@
 "liberal minority & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD\\\\\n")
-print(etlib_min50,type = "latex", file = "latex/etlib_min50.tex"  , include.rownames=FALSE, add.to.row = addtorow, include.colnames = FALSE, latex.environments = "center")
-
-df_etlib_min20 <- etlib_df %>%  filter(circle_orange == 20)
-etlib_min20 <- xtable(df_etlib_min20[,c("eth_lib_min","de_sq_bl_mean","de_sq_bl_sd","de_cl_bl_mean","de_cl_bl_sd","de_sq_or_mean","de_sq_or_sd","de_cl_or_mean","de_cl_or_sd","dv_sq_bl_mean","dv_sq_bl_sd","dv_cl_bl_mean","dv_cl_bl_sd","dv_sq_or_mean","dv_sq_or_sd","dv_cl_or_mean","dv_cl_or_sd")], digits = 3)
-align(etlib_min20) <- "c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|"
-addtorow <- list()
-addtorow$pos <- list(0, 0,0,0,0)
-addtorow$command <- c("\\multicolumn{17}{|c|}{Ethnic Asymmetry, $20 \\%$ Liberal Migrants: Spatial Proximity}  \\\\\\hline\n",
+print(etlib_min50,type = "latex", file = "etlib_min50.tex"  , include.rownames=FALSE, add.to.row = addtorow, include.colnames = FALSE, latex.environments = "center")
+
+df_etlib_min10 <- etlib_df %>%  filter(circle_orange == 10)
+etlib_min10 <- xtable(df_etlib_min10[,c("eth_lib_min","de_sq_bl_mean","de_sq_bl_sd","de_cl_bl_mean","de_cl_bl_sd","de_sq_or_mean","de_sq_or_sd","de_cl_or_mean","de_cl_or_sd","dv_sq_bl_mean","dv_sq_bl_sd","dv_cl_bl_mean","dv_cl_bl_sd","dv_sq_or_mean","dv_sq_or_sd","dv_cl_or_mean","dv_cl_or_sd")], digits = 3)
+align(etlib_min10) <- "c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|"
+addtorow <- list()
+addtorow$pos <- list(0, 0,0,0,0)
+addtorow$command <- c("\\multicolumn{17}{|c|}{Ethnic Asymmetry, $10 \\%$ Liberal Migrants: Spatial Proximity}  \\\\\\hline\n",
    "Preference &  \\multicolumn{8}{|c|}{Ethnic Proximity} & \\multicolumn{8}{|c|}{Value Proximity}   \\\\\\hline\n",
@@
 "liberal minority & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD\\\\\n")
-print(etlib_min20,type = "latex", file = "latex/etlib_min20.tex" , include.rownames=FALSE, add.to.row = addtorow, include.colnames = FALSE, latex.environments = "center")
-
-df_etlib_min80 <- etlib_df %>%  filter(circle_orange == 80)
-etlib_min80 <- xtable(df_etlib_min80[,c("eth_lib_min","de_sq_bl_mean","de_sq_bl_sd","de_cl_bl_mean","de_cl_bl_sd","de_sq_or_mean","de_sq_or_sd","de_cl_or_mean","de_cl_or_sd","dv_sq_bl_mean","dv_sq_bl_sd","dv_cl_bl_mean","dv_cl_bl_sd","dv_sq_or_mean","dv_sq_or_sd","dv_cl_or_mean","dv_cl_or_sd")], digits = 3)
-align(etlib_min80) <- "c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|"
-addtorow <- list()
-addtorow$pos <- list(0, 0,0,0,0)
-addtorow$command <- c("\\multicolumn{17}{|c|}{Ethnic Asymmetry, $80 \\%$ Liberal Migrants: Spatial Proximity}  \\\\\\hline\n",
+print(etlib_min10,type = "latex", file = "etlib_min10.tex" , include.rownames=FALSE, add.to.row = addtorow, include.colnames = FALSE, latex.environments = "center")
+
+df_etlib_min90 <- etlib_df %>%  filter(circle_orange == 90)
+etlib_min90 <- xtable(df_etlib_min90[,c("eth_lib_min","de_sq_bl_mean","de_sq_bl_sd","de_cl_bl_mean","de_cl_bl_sd","de_sq_or_mean","de_sq_or_sd","de_cl_or_mean","de_cl_or_sd","dv_sq_bl_mean","dv_sq_bl_sd","dv_cl_bl_mean","dv_cl_bl_sd","dv_sq_or_mean","dv_sq_or_sd","dv_cl_or_mean","dv_cl_or_sd")], digits = 3)
+align(etlib_min90) <- "c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|"
+addtorow <- list()
+addtorow$pos <- list(0, 0,0,0,0)
+addtorow$command <- c("\\multicolumn{17}{|c|}{Ethnic Asymmetry, $90 \\%$ Liberal Migrants: Spatial Proximity}  \\\\\\hline\n",
    "Preference &  \\multicolumn{8}{|c|}{Ethnic Proximity} & \\multicolumn{8}{|c|}{Value Proximity}   \\\\\\hline\n",
@@
 "liberal minority & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD\\\\\n")
-print(etlib_min80,type = "latex", file = "latex/etlib_min80.tex" , include.rownames=FALSE, add.to.row = addtorow, include.colnames = FALSE, latex.environments = "center")
-
-```
+print(etlib_min90,type = "latex", file = "etlib_min90.tex" , include.rownames=FALSE, add.to.row = addtorow, include.colnames = FALSE, latex.environments = "center")
+
+```

### 2021-05-25 additional.Rmd
test 3D plot

---
title: "additional3D"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

setwd("C:/Users/rocpa/OneDrive/Desktop/AF/ethnic-value_multinomial-master/additional/")

library(dplyr)
library(ggplot2)
library(plotly)
library(scatterplot3d)
library(reshape)
library(reshape2)
library(tidyr)
library(forcats)
library(plot3D)

valueminority.labs <- c("ß value liberals minority: 0", "ß value liberals minority: 1", "ß value liberals minority: 7")
names(valueminority.labs) <- c("0","1","7")
valuemajority.labs <- c("ß value liberals majority: 0", "ß value liberals majority: 1", "ß value liberals majority: 7")
names(valuemajority.labs) <- c("0","1","7")
ethnicminority.labs <- c("ß ethnic liberals minority: 0", "ß ethnic liberals minority: 1", "ß ethnic liberals minority: 7")
names(ethnicminority.labs) <- c("0","1","7")
ethnicmajority.labs <- c("ß ethnic liberals majority: 0", "ß ethnic liberals majority: 1", "ß ethnic liberals majority: 7")
names(ethnicmajority.labs) <- c("0","1","7")

mech <- read.csv("mech_lib.csv",sep=",")
excl <- names(mech) %in% c("run", "density","step")
mech <- mech[!excl] %>% group_by(eth_con_loc, eth_con_min,eth_lib_loc,eth_lib_min,val_lib_loc,val_lib_min,val_con_loc,val_con_min,circle_orange,circle_blue,fraction_blue) %>% summarise_all(mean)

df_sec <- read.csv("df_secondary.csv",sep=",")
exclet <- names(df_sec) %in% c("run", "density","step")

df_sec <- df_sec[!exclet] %>% group_by(ID,RND,eth_con_loc,eth_con_min,eth_lib_loc,eth_lib_min,val_lib_loc,val_lib_min,val_con_loc,val_con_min,circle_orange,circle_blue,fraction_blue) %>% summarise_all(mean)

 df <- read.csv("3Dlowdom.csv",sep = ",",skip = 6)
df2 <- read.csv("3Dhighdom.csv",sep = ",",skip = 6)
leg <- read.csv("legend_sa_asym.csv",sep=";")[,1]
df_fin <- rbind(df,df2)
 names(df_fin)<- leg

# 
# df_t <- rbind(df_3D,df_fin)
# 
# 
# write.csv(df_t,"3D.csv",row.names = F)

df_3D <- read.csv("3D.csv",sep=",")
excl3D <- names(df_3D) %in% c("run", "density","step")
df_3D <- df_3D[!excl3D] %>% group_by(eth_con_loc, eth_con_min,eth_lib_loc,eth_lib_min,val_lib_loc,val_lib_min,val_con_loc,val_con_min,circle_orange,circle_blue,fraction_blue) %>% summarise_all(mean)

```

```{r asym_baseline, fig.cap="Fig. 8 orig", echo = FALSE}

asym_dom <- read.csv("df_asym_dom.csv",sep = ",")

excl <- names(asym_dom) %in% c("run", "density","step")
df <- asym_dom[!excl] %>% group_by(dominant,circle_orange,circle_blue,fraction_blue,secondary) %>% summarise_all(mean)

df <- df %>% filter(df$dominant <= 15) 
df <- df %>% filter(df$fraction_blue==50|df$fraction_blue==60|df$fraction_blue==80)

majcons <- ggplotly(ggplot(data = df) + geom_point(aes(x=dominant,y=dv_sq_bl, colour = vl_sq_bl),shape = "circle")  + geom_line(aes(x=dominant,y=dv_sq_bl, linetype = as.factor(fraction_blue))) +
           geom_point(aes(x=dominant,y=de_sq_bl, colour = et_sq_bl),shape="square") + geom_line(aes(x=dominant,y=de_sq_bl, linetype = as.factor(fraction_blue)))+ ggtitle("majcons"))

majlib <- ggplotly(ggplot(data = df) + geom_point(aes(x=dominant,y=dv_cl_bl, colour = vl_cl_bl),shape = "circle")  + geom_line(aes(x=dominant,y=dv_cl_bl, linetype = as.factor(fraction_blue))) +
           geom_point(aes(x=dominant,y=de_cl_bl, colour = et_cl_bl),shape="square") + geom_line(aes(x=dominant,y=de_cl_bl, linetype = as.factor(fraction_blue))) + ggtitle("majlib"))

mincons <- ggplotly(ggplot(data = df) + geom_point(aes(x=dominant,y=dv_sq_or, colour = vl_sq_or),shape = "circle")  + geom_line(aes(x=dominant,y=dv_sq_or, linetype = as.factor(fraction_blue))) +
           geom_point(aes(x=dominant,y=de_sq_or, colour = et_sq_or),shape="square") + geom_line(aes(x=dominant,y=de_sq_or, linetype = as.factor(fraction_blue))) + ggtitle("mincons"))

minlib <- ggplotly(ggplot(data = df) + geom_point(aes(x=dominant,y=dv_cl_or, colour = vl_cl_or),shape = "circle")  + geom_line(aes(x=dominant,y=dv_cl_or, linetype = as.factor(fraction_blue))) +
           geom_point(aes(x=dominant,y=de_cl_or, colour = et_cl_or),shape="square") + geom_line(aes(x=dominant,y=de_cl_or, linetype = as.factor(fraction_blue)))+ ggtitle("minlib"))

majcons
majlib
mincons
minlib

```

```{r sa_asym, fig.cap="Fig. 8 orig", echo = FALSE}

sa_asym <- read.csv("df_sa_asym.csv",sep = ",")

excl <- names(sa_asym) %in% c("run", "density","step")
df <- sa_asym[!excl] %>% group_by(eth_con_loc, eth_con_min,eth_lib_loc,eth_lib_min,val_lib_loc,val_lib_min,val_con_loc,val_con_min,circle_orange,circle_blue,fraction_blue) %>% summarise_all(mean)

df <- df %>% filter(eth_con_min==20 & eth_con_loc==20 & val_lib_min==20)
df <- df %>% filter(fraction_blue==50|fraction_blue==60|fraction_blue==80)
df <- df %>% filter(circle_orange==50)

dominant <- df$val_lib_loc

majcons <- ggplotly(ggplot(data = df) + geom_point(aes(x=dominant,y=dv_sq_bl, colour = vl_sq_bl),shape = "circle")  + geom_line(aes(x=dominant,y=dv_sq_bl, linetype = as.factor(fraction_blue))) +
           geom_point(aes(x=dominant,y=de_sq_bl, colour = et_sq_bl),shape="square") + geom_line(aes(x=dominant,y=de_sq_bl, linetype = as.factor(fraction_blue)))+ ggtitle("majcons"))

majlib <- ggplotly(ggplot(data = df) + geom_point(aes(x=dominant,y=dv_cl_bl, colour = vl_cl_bl),shape = "circle")  + geom_line(aes(x=dominant,y=dv_cl_bl, linetype = as.factor(fraction_blue))) +
           geom_point(aes(x=dominant,y=de_cl_bl, colour = et_cl_bl),shape="square") + geom_line(aes(x=dominant,y=de_cl_bl, linetype = as.factor(fraction_blue))) + ggtitle("majlib"))

mincons <- ggplotly(ggplot(data = df) + geom_point(aes(x=dominant,y=dv_sq_or, colour = vl_sq_or),shape = "circle")  + geom_line(aes(x=dominant,y=dv_sq_or, linetype = as.factor(fraction_blue))) +
           geom_point(aes(x=dominant,y=de_sq_or, colour = et_sq_or),shape="square") + geom_line(aes(x=dominant,y=de_sq_or, linetype = as.factor(fraction_blue))) + ggtitle("mincons"))

minlib <- ggplotly(ggplot(data = df) + geom_point(aes(x=dominant,y=dv_cl_or, colour = vl_cl_or),shape = "circle")  + geom_line(aes(x=dominant,y=dv_cl_or, linetype = as.factor(fraction_blue))) +
           geom_point(aes(x=dominant,y=de_cl_or, colour = et_cl_or),shape="square") + geom_line(aes(x=dominant,y=de_cl_or, linetype = as.factor(fraction_blue)))+ ggtitle("minlib"))

majcons
majlib
mincons
minlib

```

# Comparing beta majority over beta minority liberal

```{r by-product_cons_original, fig.cap="Effect of liberals majority vs minority on value segregation conservatives", echo = FALSE}

# ethnic and value segregation for each group in the annex

##### 
# By-product value of conservatives by value preference liberals

# Majority

mech_cons <- mech %>% filter(fraction_blue == 50 | fraction_blue == 80) %>%  filter(val_lib_min==0 | val_lib_min==1 |val_lib_min==7) %>% gather(key=ethnics, value=Clust, dv_sq_bl,dv_sq_or)

cons_maj <- ggplot(data = mech_cons, aes(x=val_lib_loc,y=Clust,color=  `ethnics`,linetype= as.factor(fraction_blue))) + geom_point(size=1.5, shape = "square") + geom_line() + 
  facet_wrap(~val_lib_min,dir="v",labeller = labeller(val_lib_min = valueminority.labs)) +
    scale_y_continuous(breaks= seq(0,2,by=0.25)) +
  xlab("ß value liberal majority") + ylab("Spatial clustering") +
  geom_hline(yintercept=1,color="red") +
  scale_color_manual(values=c("blue","darkorange"),labels=c("Majority","Minority"),name="Ethnicity") +
    scale_linetype_manual(values=c("solid","dashed"),labels=c("50%","80%"),name="% Majority") +
   guides(color  = guide_legend(order = 1), linetype = guide_legend(order = 2)) +
  theme_bw()

# Minority

mech_lib <- mech %>%  filter(fraction_blue == 50 | fraction_blue == 80) %>%  filter(val_lib_loc==0 | val_lib_loc==1 |val_lib_loc==7) %>% gather(key=ethnics, value=Cluste, dv_sq_bl,dv_sq_or)

cons_min <- ggplot(data = mech_lib, aes(x=val_lib_min,y=Cluste,color=  `ethnics`,linetype= as.factor(fraction_blue))) + geom_point(size=1.5, shape = "square") + geom_line() + 
  facet_wrap(~val_lib_loc,dir="v",labeller = labeller(val_lib_loc = valuemajority.labs)) +
  xlab("ß value liberal minority") + ylab("Spatial clustering") +
  scale_y_continuous(breaks= seq(0,2,by=0.25)) +
  geom_hline(yintercept=1,color="red") +
  scale_color_manual(values=c("blue","darkorange"),labels=c("Majority","Minority"),name="Ethnicity") +
    scale_linetype_manual(values=c("solid","dashed"),labels=c("50%","80%"),name="% Majority") +
   guides(color  = guide_legend(order = 1), linetype = guide_legend(order = 2)) +
 theme_bw()

ggplotly(cons_maj)
ggplotly(cons_min)

lib_cons <- ggpubr::ggarrange(cons_maj,cons_min, common.legend = TRUE, legend = "bottom")

ggsave("lib_cons.jpg",plot=lib_cons)

```

```{r by-product ethnic cons, fig.cap="Effect of liberals majority vs minority on ethnic segregation conservatives", echo = FALSE}
# Not interesting, goes in the annex

# ethnic and value segregation for each group in the annex

##### 
# By-product value of conservatives by value preference liberals

# Majority

mech_cons <- mech %>% filter(fraction_blue == 50 | fraction_blue == 80) %>%  filter(val_lib_min==0 | val_lib_min==1 |val_lib_min==7) %>% gather(key=ethnics, value=Clust, de_sq_bl,de_sq_or)

cons_maj_et <- ggplot(data = mech_cons, aes(x=val_lib_loc,y=Clust,color=  `ethnics`,linetype= as.factor(fraction_blue))) + geom_point(size=1.5, shape = "square") + geom_line() + 
  facet_wrap(~val_lib_min,dir="v",labeller = labeller(val_lib_min = valueminority.labs)) +
    scale_y_continuous(breaks= seq(0,5,by=0.5)) +
  xlab("ß value liberal majority") + ylab("Spatial clustering") +
  geom_hline(yintercept=1,color="red") +
  scale_color_manual(values=c("blue","darkorange"),labels=c("Majority","Minority"),name="Ethnicity") +
    scale_linetype_manual(values=c("solid","dashed"),labels=c("50%","80%"),name="% Majority") +
   guides(color  = guide_legend(order = 1), linetype = guide_legend(order = 2)) +
  theme_bw()

# Minority

mech_lib <- mech %>%  filter(fraction_blue == 50 | fraction_blue == 80) %>%  filter(val_lib_loc==0 | val_lib_loc==1 |val_lib_loc==7) %>% gather(key=ethnics, value=Cluste, de_sq_bl,de_sq_or)

cons_min_et <- ggplot(data = mech_lib, aes(x=val_lib_min,y=Cluste,color=  `ethnics`,linetype= as.factor(fraction_blue))) + geom_point(size=1.5, shape = "square") + geom_line() + 
  facet_wrap(~val_lib_loc,dir="v",labeller = labeller(val_lib_loc = valuemajority.labs)) +
  xlab("ß value liberal minority") + ylab("Spatial clustering") +
  scale_y_continuous(breaks= seq(0,5,by=0.5)) +
  geom_hline(yintercept=1,color="red") +
  scale_color_manual(values=c("blue","darkorange"),labels=c("Majority","Minority"),name="Ethnicity") +
    scale_linetype_manual(values=c("solid","dashed"),labels=c("50%","80%"),name="% Majority") +
   guides(color  = guide_legend(order = 1), linetype = guide_legend(order = 2)) +
 theme_bw()

ggplotly(cons_maj_et)
ggplotly(cons_min_et)

lib_cons_et <- ggpubr::ggarrange(cons_maj_et,cons_min_et, common.legend = TRUE, legend = "bottom")

#ggsave("lib_cons.jpg",plot=lib_cons)

```

```{r beta_maj, fig.cap="effect liberals one  dataset", echo = FALSE}

#####
# Ethnic and value of liberals above each other
mech_vlmj <- mech %>% filter(fraction_blue == 50 | fraction_blue == 80) %>%  filter(val_lib_min==0 | val_lib_min==1 |val_lib_min==7) %>% gather(key = segregation, value = Clustmj, de_cl_bl, dv_cl_bl)

librmj <- ggplot(data=mech_vlmj,aes(x=val_lib_loc,y = Clustmj,shape=`segregation`,linetype=as.factor(fraction_blue))) + 
  geom_point(size=1.5,color="blue") + geom_line(color="blue") +
facet_wrap(~val_lib_min,dir="v",labeller=labeller(val_lib_min=valueminority.labs)) +
  xlab("ß value liberals majority") + ylab("Spatial Clustering") +
  scale_y_continuous(breaks= seq(0,2,by=0.25)) +
  scale_linetype_manual(values=c("solid","dashed"),labels=c("50%","80%"),name="% Majority" ) +
  scale_shape_manual(values=c("square","circle"),labels=c("Ethnic","Value"),name="Segregation" ) +
 ggtitle("Liberals Majority") +
    geom_hline(yintercept=1,color="red") +
      theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

mech_vlmn <- mech %>%  filter(fraction_blue == 50 | fraction_blue == 80) %>%  filter(val_lib_loc==0 | val_lib_loc==1 |val_lib_loc==7) %>% gather(key = segregation, value = Clustmn, de_cl_or, dv_cl_or)

librmn <- ggplot(data=mech_vlmn,aes(x=val_lib_min,y = Clustmn,shape=`segregation`,linetype=as.factor(fraction_blue))) + 
  geom_point(size=1.5,color="orange") + geom_line(color="orange") +
facet_wrap(~val_lib_loc,dir="v",labeller=labeller(val_lib_loc=valuemajority.labs)) +
 scale_y_continuous(breaks= seq(0,2,by=0.25)) +
  xlab("ß value liberals minority") + ylab("Spatial Clustering") +
    scale_linetype_manual(values=c("solid","dashed"),labels=c("50%","80%"),name="% Majority") +
  scale_shape_manual(values=c("square","circle"),labels=c("Ethnic","Value"),name="Segregation") +
    geom_hline(yintercept=1,color="red") +
    guides(  linetype = guide_legend(order = 1), shape = guide_legend(order = 2)) +
 #  guides(color=FALSE) + 
    ggtitle("Liberals Minority") +
    geom_hline(yintercept=1,color="red") +
      theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

ggplotly(librmj)
ggplotly(librmn)

lib_lib <- ggpubr::ggarrange(librmj,librmn, common.legend = TRUE, legend = "bottom")

ggsave("lib_lib.jpg",plot=lib_lib)

```

```{r etlib_min, fig.cap="Ethnic preference majority or minority over liberals or conservatives minority", echo = FALSE}

excl <- names(df_etlib) %in% c("run", "density","step")
df_etlib <- df_etlib[!excl] %>% group_by(ID,eth_con_loc,eth_con_min,eth_lib_loc,eth_lib_min,val_lib_loc,val_lib_min,val_con_loc,val_con_min,circle_orange,circle_blue,fraction_blue) %>% summarise_all(mean)

## Majority

df_ethloc <- df_etlib %>% filter(ID == "etlib_loc") %>% filter(fraction_blue == 80) %>% gather(key = subgroup, value = Clustetmj, de_sq_or,dv_sq_or,de_cl_or,dv_cl_or) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"Ethnic" = c("de_sq_or","de_cl_or"), "Value" = c("dv_sq_or","dv_cl_or") ),"Ethnic"),
              `orientation` = fct_relevel(fct_collapse(subgroup,"Conservative" = c("de_sq_or","dv_sq_or"), "Liberal" = c("de_cl_or","dv_cl_or")), "Conservative"))

maj_min <- ggplot(data=df_ethloc,aes(x=eth_lib_loc,y = Clustetmj,linetype=`segregation`,shape = `orientation`)) + 
  geom_point(size=1.5,color="orange") + geom_line(color="orange") +
facet_wrap(~eth_lib_min,dir="v",labeller=labeller(eth_lib_min=ethnicminority.labs)) +
  xlab("ß ethnic liberals majority") + ylab("Spatial Clustering") +
  scale_y_continuous(breaks= seq(0,5,by=0.50)) +
  scale_linetype_manual(values=c("solid","dashed"),labels=c("Ethnic","Value"),name="Segregation" ) +
  scale_shape_manual(values=c("square","circle"),labels=c("Conservative","Liberal"),name="Orientation \n minority" ) +
 ggtitle("") +
    geom_hline(yintercept=1,color="red") +
      theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

ggplotly(maj_min)
   maj_min
## Minority

df_ethmin <- df_etlib %>% filter(ID == "etlib_min") %>% filter(fraction_blue == 80) %>% gather(key = subgroup, value = Clustetmn, de_sq_or,dv_sq_or,de_cl_or,dv_cl_or) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"Ethnic" = c("de_sq_or","de_cl_or"), "Value" = c("dv_sq_or","dv_cl_or") ),"Ethnic"),
              `orientation` = fct_relevel(fct_collapse(subgroup,"Conservative" = c("de_sq_or","dv_sq_or"), "Liberal" = c("de_cl_or","dv_cl_or")), "Conservative"))

min_min <- ggplot(data=df_ethmin,aes(x=eth_lib_min,y = Clustetmn,linetype=`segregation`,shape = `orientation`)) + 
  geom_point(size=1.5,color="orange") + geom_line(color="orange") +
facet_wrap(~eth_lib_loc,dir="v",labeller=labeller(eth_lib_loc=ethnicmajority.labs)) +
  xlab("ß ethnic liberals minority") + ylab("Spatial Clustering") +
  scale_y_continuous(breaks= seq(0,5,by=0.50)) +
  scale_linetype_manual(values=c("solid","dashed"),labels=c("Ethnic","Value"),name="Segregation" ) +
  scale_shape_manual(values=c("square","circle"),labels=c("Conservative","Liberal"),name="Orientation \n minority" ) +
 ggtitle("") +
    geom_hline(yintercept=1,color="red") +
      theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

ggplotly(min_min)
   min_min

eth_lib_min <- ggpubr::ggarrange(maj_min,min_min, common.legend = TRUE, legend = "bottom")

ggsave("eth_lib_min.jpg",plot=eth_lib_min)

```

```{r etlib_min_test fraction, fig.cap="Ethnic preference majority or minority over liberals or conservatives minority", echo = FALSE}

df_etlib <- read.csv("df_etlib.csv",sep=",")

excl <- names(df_etlib) %in% c("run", "density","step")
df_etlib <- df_etlib[!excl] %>% group_by(ID,eth_con_loc,eth_con_min,eth_lib_loc,eth_lib_min,val_lib_loc,val_lib_min,val_con_loc,val_con_min,circle_orange,circle_blue,fraction_blue) %>% summarise_all(mean)

## Majority

df_ethloc <- df_etlib %>% filter(ID == "etlib_loc") %>% filter(fraction_blue == 50 | fraction_blue == 80) %>% gather(key = subgroup, value = Clustetmj, de_sq_or,dv_sq_or,de_cl_or,dv_cl_or) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"Ethnic" = c("de_sq_or","de_cl_or"), "Value" = c("dv_sq_or","dv_cl_or") ),"Ethnic"),
              `orientation` = fct_relevel(fct_collapse(subgroup,"Conservative" = c("de_sq_or","dv_sq_or"), "Liberal" = c("de_cl_or","dv_cl_or")), "Conservative"))

df_ethloc <- df_etlib %>% filter(ID == "etlib_loc") %>% filter(fraction_blue == 50 | fraction_blue == 80) %>%  filter(eth_lib_min==0 | eth_lib_min==1 |eth_lib_min==7) %>% gather(key = segregation, value = Clustmj, de_cl_bl, dv_cl_bl)

librmj <- ggplot(data=df_ethloc,aes(x=eth_lib_loc,y = Clustmj,shape=`segregation`,linetype=as.factor(fraction_blue))) + 
  geom_point(size=1.5,color="blue") + geom_line(color="blue") +
facet_wrap(~eth_lib_min,dir="v",labeller=labeller(eth_lib_min=ethnicminority.labs)) +
  xlab("ß ethnic liberals majority") + ylab("Spatial Clustering") +
  scale_y_continuous(breaks= seq(0,2,by=0.25)) +
  scale_linetype_manual(values=c("solid","dashed"),labels=c("50%","80%"),name="% Majority" ) +
  scale_shape_manual(values=c("square","circle"),labels=c("Ethnic","Value"),name="Segregation" ) +
 ggtitle("Liberals Majority") +
    geom_hline(yintercept=1,color="red") +
      theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

df_etmin <- df_etlib %>% filter(ID == "etlib_min") %>% filter(fraction_blue == 50 | fraction_blue == 80) %>%  filter(eth_lib_loc==0 | eth_lib_loc==1 |eth_lib_loc==7) %>% gather(key = segregation, value = Clustmn, de_cl_or, dv_cl_or)

librmn <- ggplot(data=df_etmin,aes(x=eth_lib_min,y = Clustmn,shape=`segregation`,linetype=as.factor(fraction_blue))) + 
  geom_point(size=1.5,color="orange") + geom_line(color="orange") +
facet_wrap(~eth_lib_loc,dir="v",labeller=labeller(eth_lib_loc=ethnicmajority.labs)) +
 scale_y_continuous(breaks= seq(0,2,by=0.25)) +
  xlab("ß ethnic liberals minority") + ylab("Spatial Clustering") +
    scale_linetype_manual(values=c("solid","dashed"),labels=c("50%","80%"),name="% Majority") +
  scale_shape_manual(values=c("square","circle"),labels=c("Ethnic","Value"),name="Segregation") +
    geom_hline(yintercept=1,color="red") +
    guides(  linetype = guide_legend(order = 1), shape = guide_legend(order = 2)) +
 #  guides(color=FALSE) + 
    ggtitle("Liberals Minority") +
    geom_hline(yintercept=1,color="red") +
      theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

ggplotly(librmj)
ggplotly(librmn)

lib_lib_ethnic <- ggpubr::ggarrange(librmj,librmn, common.legend = TRUE, legend = "bottom")

# ggsave("lib_lib.jpg",plot=lib_lib)

```

```{r etlib_maj, fig.cap="Ethnic preference majority or minority over liberals or conservatives majority", echo = FALSE}

## Majority

df_ethloc_maj <- df_etlib %>% filter(ID == "etlib_loc") %>% filter(fraction_blue == 80) %>% gather(key = subgroup, value = Clustetmj, de_sq_bl,dv_sq_bl,de_cl_bl,dv_cl_bl) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"Ethnic" = c("de_sq_bl","de_cl_bl"), "Value" = c("dv_sq_bl","dv_cl_bl") ),"Ethnic"),
              `orientation` = fct_relevel(fct_collapse(subgroup,"Conservative" = c("de_sq_bl","dv_sq_bl"), "Liberal" = c("de_cl_bl","dv_cl_bl")), "Conservative"))

maj_maj <- ggplot(data=df_ethloc_maj,aes(x=eth_lib_loc,y = Clustetmj,linetype=`segregation`,shape = `orientation`)) + 
  geom_point(size=1.5,color="blue") + geom_line(color="blue") +
facet_wrap(~eth_lib_min,dir="v",labeller=labeller(eth_lib_min=ethnicminority.labs)) +
  xlab("ß ethnic liberals majority") + ylab("Spatial Clustering") +
  scale_y_continuous(breaks= seq(0,5,by=0.50)) +
  scale_linetype_manual(values=c("solid","dashed"),labels=c("Ethnic","Value"),name="Segregation" ) +
  scale_shape_manual(values=c("square","circle"),labels=c("Conservative","Liberal"),name="Orientation \n majority" ) +
 ggtitle("") +
    geom_hline(yintercept=1,color="red") +
      theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

ggplotly(maj_maj)
   maj_maj
## Minority

df_ethmin_maj <- df_etlib %>% filter(ID == "etlib_min") %>% filter(fraction_blue == 80) %>% gather(key = subgroup, value = Clustetmn, de_sq_bl,dv_sq_bl,de_cl_bl,dv_cl_bl) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"Ethnic" = c("de_sq_bl","de_cl_bl"), "Value" = c("dv_sq_bl","dv_cl_bl") ),"Ethnic"),
              `orientation` = fct_relevel(fct_collapse(subgroup,"Conservative" = c("de_sq_bl","dv_sq_bl"), "Liberal" = c("de_cl_bl","dv_cl_bl")), "Conservative"))

min_maj <- ggplot(data=df_ethmin_maj,aes(x=eth_lib_min,y = Clustetmn,linetype=`segregation`,shape = `orientation`)) + 
  geom_point(size=1.5,color="blue") + geom_line(color="blue") +
facet_wrap(~eth_lib_loc,dir="v",labeller=labeller(eth_lib_loc=ethnicmajority.labs)) +
  xlab("ß ethnic liberals minority") + ylab("Spatial Clustering") +
  scale_y_continuous(breaks= seq(0,5,by=0.50)) +
  scale_linetype_manual(values=c("solid","dashed"),labels=c("Ethnic","Value"),name="Segregation" ) +
  scale_shape_manual(values=c("square","circle"),labels=c("Conservative","Liberal"),name="Orientation \n majority" ) +
 ggtitle("") +
    geom_hline(yintercept=1,color="red") +
      theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

ggplotly(min_maj)
   min_maj

eth_lib_maj <- ggpubr::ggarrange(maj_maj,min_maj, common.legend = TRUE, legend = "bottom")

ggsave("eth_lib_maj.jpg",plot=eth_lib_maj)

```

```{r sec_not_rel, fig.cap="Value conservativess and ethnic liberal not primary", echo = FALSE}

df <- df_sec  %>%  gather(key= subgroup, value = Prox, de_sq_bl, dv_sq_bl, de_cl_bl, dv_cl_bl, de_sq_or, dv_sq_or, de_cl_or, dv_cl_or) %>% mutate(  `segregation` = fct_relevel(fct_collapse(subgroup,"ethnics" = c("de_sq_bl","de_cl_bl","de_sq_or","de_cl_or"), "values" = c("dv_sq_bl","dv_cl_bl","dv_sq_or","dv_cl_or")),"ethnics"),
 `orientation` = fct_relevel(fct_collapse(subgroup, "conservative" = c("de_sq_bl","dv_sq_bl","de_sq_or","dv_sq_or"), "liberal" = c("de_cl_bl","dv_cl_bl","de_cl_or","dv_cl_or")),"conservative" ), 
 `ethnia` = fct_relevel(fct_collapse(subgroup, "local" = c("de_sq_bl","dv_sq_bl","de_cl_bl","dv_cl_bl"),"minority" = c("de_sq_or","dv_sq_or","de_cl_or","dv_cl_or")), "local"))

dflow <- df %>% filter(ID == "valuecon_min" & fraction_blue == 80) %>% filter(RND == "low")
dfh <- df %>% filter(ID == "valuecon_min" & fraction_blue == 80) %>% filter(RND == "high")

low <- ggplot(data=dflow, aes(x=dflow$val_con_min,y=Prox, linetype = `segregation` , fill = `ethnia`,  shape = `orientation`))  +  geom_point(size= 1.5) +
  geom_line(aes(color = `ethnia`)) + 
  facet_wrap(~  dflow$val_con_loc) +
  ggtitle("Low randomness") + 
   scale_linetype_manual(values=c("solid","dashed"), labels = c("ethnic","value"), guide = guide_legend(title = "Segregation", order = 1)) +
  scale_fill_manual(values = c("blue","darkorange")) + 
 scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
  scale_shape_manual(values = c(22,21), guide = guide_legend(title="Value" ,override.aes = list(size = 3), order = 3)) +
  guides(fill  = FALSE)

high <- ggplot(data=dfh, aes(x=dfh$val_con_min,y=Prox, linetype = `segregation` , fill = `ethnia`,  shape = `orientation`))  +  geom_point(size= 1.5) +
  geom_line(aes(color = `ethnia`)) + 
  facet_wrap(~  dfh$val_con_loc) +
  ggtitle("High randomness") + 
   scale_linetype_manual(values=c("solid","dashed"), labels = c("ethnic","value"), guide = guide_legend(title = "Segregation", order = 1)) +
  scale_fill_manual(values = c("blue","darkorange")) + 
 scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
  scale_shape_manual(values = c(22,21), guide = guide_legend(title="Value" ,override.aes = list(size = 3), order = 3)) +
  guides(fill  = FALSE)

cmp <- ggpubr::ggarrange(low,high,common.legend = T)

```

```{r sec_test, fig.cap="Value conservativess and ethnic liberal not primary", echo = FALSE}

# pref <- names(df_sec) %in% c("eth_con_loc", "eth_con_min","val_loc_lib")

etlblc_high <- df_sec  %>% filter(fraction_blue == 80) %>% filter(ID == "etlib_loc", RND == "high", eth_lib_loc == 5 | eth_lib_loc == 0) %>% filter(eth_lib_min == 0) %>% gather(key = subgroup, value = Clus, de_sq_bl,dv_sq_bl,de_cl_bl,dv_cl_bl,de_sq_or,dv_sq_or,de_cl_or,dv_cl_or)

etlblc_high_pic <- ggplot(etlblc_high, aes(fill = as.factor(etlblc_high$eth_lib_loc), y= etlblc_high$Clus, x = etlblc_high$subgroup) ) + 
    geom_bar(position="dodge", stat="identity") +
  scale_fill_manual(values=c("red","blue")) +
  scale_y_continuous(limits= c(0,6),breaks=seq(0,6,by=0.5))

etlblc_low <- df_sec  %>% filter(fraction_blue == 80) %>% filter(ID == "etlib_loc", RND == "low", eth_lib_loc == 20 | eth_lib_loc == 0) %>% filter(eth_lib_min == 0) %>% gather(key = subgroup, value = Clus, de_sq_bl,dv_sq_bl,de_cl_bl,dv_cl_bl,de_sq_or,dv_sq_or,de_cl_or,dv_cl_or)

etlblc_low_pic <- ggplot(etlblc_low, aes(fill = as.factor(etlblc_low$eth_lib_loc), y= etlblc_low$Clus, x = etlblc_low$subgroup) ) + 
    geom_bar(position="dodge", stat="identity") +
  scale_fill_manual(values=c("red","blue")) +
  scale_y_continuous(limits= c(0,6),breaks=seq(0,6,by=0.5))

etlbmn_high <- df_sec  %>% filter(fraction_blue == 80) %>% filter(ID == "etlib_min", RND == "high", eth_lib_min == 5 | eth_lib_min == 0) %>% filter(eth_lib_loc == 0) %>% gather(key = subgroup, value = Clus, de_sq_bl,dv_sq_bl,de_cl_bl,dv_cl_bl,de_sq_or,dv_sq_or,de_cl_or,dv_cl_or)

etlbmn_high_pic <- ggplot(etlbmn_high, aes(fill = as.factor(etlbmn_high$eth_lib_min), y= etlbmn_high$Clus, x = etlbmn_high$subgroup) ) + 
    geom_bar(position="dodge", stat="identity") +
  scale_fill_manual(values=c("red","blue")) +
  scale_y_continuous(limits= c(0,6),breaks=seq(0,6,by=0.5))

etlbmn_low <- df_sec  %>% filter(fraction_blue == 80) %>% filter(ID == "etlib_min", RND == "low", eth_lib_min == 20 | eth_lib_min == 0) %>% filter(eth_lib_loc == 0) %>% gather(key = subgroup, value = Clus, de_sq_bl,dv_sq_bl,de_cl_bl,dv_cl_bl,de_sq_or,dv_sq_or,de_cl_or,dv_cl_or)

etlbmn_low_pic <- ggplot(etlbmn_low, aes(fill = as.factor(etlbmn_low$eth_lib_min), y= etlbmn_low$Clus, x = etlbmn_low$subgroup) ) + 
    geom_bar(position="dodge", stat="identity") +
  scale_fill_manual(values=c("red","blue")) +
  scale_y_continuous(limits= c(0,6),breaks=seq(0,6,by=0.5))

vlcnlc_low <- df_sec  %>% filter(fraction_blue == 80) %>% filter(ID == "valuecon_loc", RND == "low", val_con_loc == 20 | val_con_loc == 0) %>% filter(val_con_min == 0) %>% gather(key = subgroup, value = Clus, de_sq_bl,dv_sq_bl,de_cl_bl,dv_cl_bl,de_sq_or,dv_sq_or,de_cl_or,dv_cl_or)

vlcnlc_low_pic <- ggplot(vlcnlc_low, aes(fill = as.factor(vlcnlc_low$val_con_loc), y= vlcnlc_low$Clus, x = vlcnlc_low$subgroup) ) + 
    geom_bar(position="dodge", stat="identity") +
  scale_fill_manual(values=c("red","blue")) +
  scale_y_continuous(limits= c(0,6),breaks=seq(0,6,by=0.5))

vlcnlc_high <- df_sec  %>% filter(fraction_blue == 80) %>% filter(ID == "valuecon_loc", RND == "high", val_con_loc == 5 | val_con_loc == 0) %>% filter(val_con_min == 0) %>% gather(key = subgroup, value = Clus, de_sq_bl,dv_sq_bl,de_cl_bl,dv_cl_bl,de_sq_or,dv_sq_or,de_cl_or,dv_cl_or)

vlcnlc_high_pic <- ggplot(vlcnlc_high, aes(fill = as.factor(vlcnlc_high$val_con_loc), y= vlcnlc_high$Clus, x = vlcnlc_high$subgroup) ) + 
    geom_bar(position="dodge", stat="identity") +
  scale_fill_manual(values=c("red","blue")) +
  scale_y_continuous(limits= c(0,6),breaks=seq(0,6,by=0.5))

vlcnmn_low <- df_sec  %>% filter(fraction_blue == 80) %>% filter(ID == "valuecon_min", RND == "low", val_con_min == 20 | val_con_min == 0) %>% filter(val_con_loc == 0) %>% gather(key = subgroup, value = Clus, de_sq_bl,dv_sq_bl,de_cl_bl,dv_cl_bl,de_sq_or,dv_sq_or,de_cl_or,dv_cl_or)

vlcnmn_low_pic <- ggplot(vlcnmn_low, aes(fill = as.factor(vlcnmn_low$val_con_min), y= vlcnmn_low$Clus, x = vlcnmn_low$subgroup) ) + 
    geom_bar(position="dodge", stat="identity") +
  scale_fill_manual(values=c("red","blue")) +
  scale_y_continuous(limits= c(0,6),breaks=seq(0,6,by=0.5))

vlcnmn_high <- df_sec  %>% filter(fraction_blue == 80) %>% filter(ID == "valuecon_min", RND == "high", val_con_min == 5 | val_con_min == 0) %>% filter(val_con_loc == 0) %>% gather(key = subgroup, value = Clus, de_sq_bl,dv_sq_bl,de_cl_bl,dv_cl_bl,de_sq_or,dv_sq_or,de_cl_or,dv_cl_or)

vlcnmn_high_pic <- ggplot(vlcnmn_high, aes(fill = as.factor(vlcnmn_high$val_con_min), y= vlcnmn_high$Clus, x = vlcnmn_high$subgroup) ) + 
    geom_bar(position="dodge", stat="identity") +
  scale_fill_manual(values=c("red","blue")) +
  scale_y_continuous(limits= c(0,6),breaks=seq(0,6,by=0.5))

ggplotly(etlblc_high_pic)
ggplotly(etlblc_low_pic)
ggplotly(etlbmn_high_pic)
ggplotly(etlbmn_low_pic)
ggplotly(vlcnlc_low_pic)
ggplotly(vlcnlc_high_pic)
ggplotly(vlcnmn_low_pic)
ggplotly(vlcnmn_high_pic)

```

```{r 3D, fig.cap="3D pictures", echo = FALSE}

excl3D <- names(df_fin) %in% c("run", "density","step")
df_fin <- df_fin[!excl3D] %>% group_by(eth_con_loc, eth_con_min,eth_lib_loc,eth_lib_min,val_lib_loc,val_lib_min,val_con_loc,val_con_min,circle_orange,circle_blue,fraction_blue) %>% summarise_all(mean)

vars <- c("de_sq_bl","dv_sq_bl","et_sq_bl","vl_sq_bl")
df_sqbl <- cbind(df_fin[,1:11],df_fin[,vars]) %>% filter(val_lib_loc==5,val_lib_min==5,eth_con_loc == 5,eth_con_min == 5)
df_high <- cbind(df_fin[,1:11],df_fin[,vars]) %>% filter(val_lib_loc==20,val_lib_min==20,eth_con_loc == 20,eth_con_min == 20)

lowE <- plot_ly(df_sqbl)  %>%
  add_trace(x=df_sqbl$fraction_blue,y=df_sqbl$circle_orange,z=df_sqbl$de_sq_bl,
            scene = "scene1",
                                        name = "Ethnic",
                                       type="scatter3d",
                                       mode="markers",
                                     marker = list(cmin=0,cmax=1,
                                                   # colorscale = "Reds",
                                     colorscale =  list(
                                        c(0,'pink'),
                                        c(0.25,'red'),
                                        c(0.5,'green'),
                                        c(0.75,'blue'),
                                        c(1, 'purple')),
                                       color= df_sqbl$et_sq_bl, showscale = T)

            )  %>% 
  layout(showlegend = F,
         title="Ethnic",
         scene = list(
      xaxis = list(title = "Ethnic Ratio",range=seq(50,90,by=10),dtick=10),
      yaxis = list(title = "% Liberal Minority",autorange = "reversed"),
      zaxis = list(title = "Cluster")))

 lowV<- plot_ly(df_sqbl)  %>%   add_trace(x=df_sqbl$fraction_blue,y=df_sqbl$circle_orange,z=df_sqbl$dv_sq_bl,
                                          scene =  "scene2",
                                     name = "Value",
                                     type="scatter3d",
                                     mode="markers",
                                    marker = list(cmin=0,cmax=1,
                                                   # colorscale = "Reds",
                                     colorscale =  list(
                                        c(0,'pink'),
                                        c(0.25,'red'),
                                        c(0.5,'green'),
                                        c(0.75,'blue'),
                                        c(1, 'purple')),
                                       color= df_sqbl$et_sq_bl, showscale = T)

            )  %>% 
       layout(showlegend = T,
         title="",
         scene = list(
      xaxis = list(title = "Ethnic Ratio",range=seq(50,90,by=10),dtick=10),
      yaxis = list(title = "% Liberal Minority",autorange = "reversed"),
      zaxis = list(title = "Cluster")))

A <- subplot(lowE,lowV) %>% layout(annotations = list(
 list(x = 0.2 , y = 1 , text = "Ethnic", showarrow = F, xref='paper', yref='paper'),
  list(x = 0.8 , y = 1, text = "Value", showarrow = F, xref='paper', yref='paper'))
)

   ###

high <- plot_ly(df_high)  %>% add_trace(x=df_high$fraction_blue,y=df_high$circle_orange,z=df_high$de_sq_bl,color= df_high$et_sq_bl,
                                       type="scatter3d",
                                       mode="markers",
                                       marker = list( colorscale = 'Reds', showscale = T))  %>%
  add_trace(x=df_high$fraction_blue,y=df_high$circle_orange,z=df_high$dv_sq_bl,color= df_high$vl_sq_bl,
              type="scatter3d",
                                       mode="markers",
                                      marker = list( colorscale = 'Greens', showscale = TRUE))  %>%
  layout(legend = list(orientation = 'h'),
         title="high",
         scene = list(
      xaxis = list(title = "Ethnic Ratio",range=seq(50,90,by=10),dtick=10),
      yaxis = list(title = "% Liberal Minority",autorange = "reversed"),
      zaxis = list(title = "Cluster")))

low
high

```

```{r 3Dsimple, fig.cap="3D pictures", echo = FALSE}

excl3D <- names(df_fin) %in% c("run", "density","step")
df_fin <- df_fin[!excl3D] %>% group_by(eth_con_loc, eth_con_min,eth_lib_loc,eth_lib_min,val_lib_loc,val_lib_min,val_con_loc,val_con_min,circle_orange,circle_blue,fraction_blue) %>% summarise_all(mean)

vars <- c("de_sq_or","dv_sq_or","et_sq_or","vl_sq_or")
df_sqbl <- cbind(df_fin[,1:11],df_fin[,vars]) %>% filter(val_lib_loc==5,val_lib_min==5,eth_con_loc == 5,eth_con_min == 5)
df_high <- cbind(df_fin[,1:11],df_fin[,vars]) %>% filter(val_lib_loc==20,val_lib_min==20,eth_con_loc == 20,eth_con_min == 20)

low <- plot3D::scatter3D(x = df_sqbl$fraction_blue, y = df_sqbl$circle_orange, z = df_sqbl$de_sq_or, colvar = df_sqbl$et_sq_or, col = ramp.col (col = c("grey", "blue"), n = 100, alpha = 1), pch=20, cex= 2, phi = 0)

```

### Back

```{r to write 3D csv, delete}
# trd <- read.csv("vlmaj_ethrat_3D_1.csv",sep=",",skip = 6)
# trd2 <- read.csv("vlmaj_ethrat_3D_2.csv",sep=",",skip = 6)
# lgnd <- read.csv("legend_sa_asym.csv",sep=";")[,1]
# names(trd2) <- lgnd
# 
# trd_f <- rbind(trd,trd2)
# 
# trdmin <- read.csv("vlmin_ethrat_3D_1.csv",sep=",",skip = 6)
# trd2min <- read.csv("vlmin_ethrat_3D_2.csv",sep=",",skip = 6)
# names(trdmin) <- lgnd
# names(trd2min) <- lgnd
# 
# trdmin_f <- rbind(trdmin,trd2min)
# 
# etlib_mj <- read.csv("etlib_loc_3D_1.csv",sep=",",skip = 6)
# lget <- read.csv("legend_etlib.csv",sep=";")[,1]
# names(etlib_mj) <- lget
# 
# 
# order <- c("run","density","fraction_blue", "circle_blue","circle_orange" ,"eth_con_loc","val_lib_loc", "eth_con_min" , "val_lib_min" ,  "val_con_loc","eth_lib_loc","val_con_min" ,  "eth_lib_min",   "step"  , "et_sq_bl" , "et_cl_bl" ,"et_sq_or","et_cl_or","vl_sq_bl","vl_cl_bl","vl_sq_or","vl_cl_or","de_sq_bl","de_cl_bl","de_sq_or","de_cl_or","dv_sq_bl","dv_cl_bl","dv_sq_or","dv_cl_or")
# 
# etlib_mj <- etlib_mj[,order]
# 
# etlib_mj2 <- read.csv("etlib_loc_3D_2.csv",sep=",",skip = 6)
# names(etlib_mj2) <- lget
# 
# etlib_mj2 <- etlib_mj2[,order]
# 
# df <- rbind(trdmin_f,etlib_mj,etlib_mj2)
# 
# etmin <- read.csv("etlib_min_3D_1.csv",sep = ",",skip = 6)
# names(etmin) <- lget
# 
# etmin2 <- read.csv("etlib_min_3D_2.csv",sep = ",",skip = 6)
# names(etmin2) <- lget
# 
# etmin_all <- rbind(etmin,etmin2)
# 
# etmin_all <- etmin_all[,order]
# 
# df_f <- rbind(df,etmin_all)
# 
# write.csv(df_f,"3D.csv",row.names = F)
```

```{r beta_maj, fig.cap="x-axis value liberals maj vs min, each group", echo = FALSE}
#####
# effect on ethnic and value preference of conservatives

consmj_majlib <- ggplot(data=mech_cons) + geom_point(aes(x=mech_cons$val_lib_loc,y=mech_cons$de_sq_bl,color=mech_cons$et_sq_bl),shape=15)  + 
  geom_line(aes(x=mech_cons$val_lib_loc,y=mech_cons$de_sq_bl,linetype=as.factor(mech_cons$fraction_blue)),color="blue") +
   scale_color_gradient(low = "grey", high = "brown") +
geom_point(aes(x=mech_cons$val_lib_loc,y=mech_cons$dv_sq_bl,color=mech_cons$vl_sq_bl),shape =15) +
    geom_line(aes(x=mech_cons$val_lib_loc,y=mech_cons$dv_sq_bl,linetype=as.factor(mech_cons$fraction_blue)),color="darkorange") +
  facet_wrap(~mech_cons$val_lib_min,dir="v") +
  theme(legend.position = "bottom")

consmj_minlib <- ggplot(data=mech_lib) + geom_point(aes(x=mech_lib$val_lib_min,y=mech_lib$de_sq_bl,color=mech_lib$et_sq_bl),shape=15)  + 
  geom_line(aes(x=mech_lib$val_lib_min,y=mech_lib$de_sq_bl,linetype=as.factor(mech_lib$fraction_blue)),color="blue") +
   scale_color_gradient(low = "grey", high = "brown") +
geom_point(aes(x=mech_lib$val_lib_min,y=mech_lib$dv_sq_bl,color=mech_lib$vl_sq_bl),shape =15) +
    geom_line(aes(x=mech_lib$val_lib_min,y=mech_lib$dv_sq_bl,linetype=as.factor(mech_lib$fraction_blue)),color="darkorange") +
  facet_wrap(~mech_lib$val_lib_loc,dir="v") +
  theme(legend.position = "bottom")

ggplotly(consmj_majlib)
ggplotly(consmj_minlib)

ggpubr::ggarrange(consmj_majlib,consmj_minlib)

##

consmn_majlib <- ggplot(data=mech_cons) + geom_point(aes(x=mech_cons$val_lib_loc,y=mech_cons$de_sq_or,color=mech_cons$et_sq_or),shape=15)  + 
  geom_line(aes(x=mech_cons$val_lib_loc,y=mech_cons$de_sq_or,linetype=as.factor(mech_cons$fraction_blue)),color="blue") +
   scale_color_gradient(low = "grey", high = "brown") +
  scale_y_continuous(limits=c(0.5,5),breaks = seq(0,5,by=1)) +
geom_point(aes(x=mech_cons$val_lib_loc,y=mech_cons$dv_sq_or,color=mech_cons$vl_sq_or),shape =15) +
    geom_line(aes(x=mech_cons$val_lib_loc,y=mech_cons$dv_sq_or,linetype=as.factor(mech_cons$fraction_blue)),color="darkorange") +
  facet_wrap(~mech_cons$val_lib_min,dir="v") +
  theme(legend.position = "bottom")

consmn_minlib <- ggplot(data=mech_lib) + geom_point(aes(x=mech_lib$val_lib_min,y=mech_lib$de_sq_or,color=mech_lib$et_sq_or),shape=15)  + 
  geom_line(aes(x=mech_lib$val_lib_min,y=mech_lib$de_sq_or,linetype=as.factor(mech_lib$fraction_blue)),color="blue") +
   scale_color_gradient(low = "grey", high = "brown") +
   scale_y_continuous(limits=c(0.9,5),breaks = seq(0,5,by=1)) +
geom_point(aes(x=mech_lib$val_lib_min,y=mech_lib$dv_sq_or,color=mech_lib$vl_sq_or),shape =15) +
    geom_line(aes(x=mech_lib$val_lib_min,y=mech_lib$dv_sq_or,linetype=as.factor(mech_lib$fraction_blue)),color="darkorange") +
  facet_wrap(~mech_lib$val_lib_loc,dir="v") +
  theme(legend.position = "bottom")

ggplotly(consmn_majlib)
ggplotly(consmn_minlib)

ggpubr::ggarrange(consmn_majlib,consmn_minlib)

#####
#behavior liberals

libmj_maj <- ggplot(data=mech_cons) + geom_point(aes(x=mech_cons$val_lib_loc,y=mech_cons$de_cl_bl,color=mech_cons$et_cl_bl),shape="square")  + geom_line(aes(x=mech_cons$val_lib_loc,y=mech_cons$de_cl_bl,linetype=as.factor(mech_cons$fraction_blue)),color="blue") +
   scale_color_gradient(low = "grey", high = "brown") +
geom_point(aes(x=mech_cons$val_lib_loc,y=mech_cons$dv_cl_bl,color=mech_cons$vl_cl_bl),shape ="circle") +
    geom_line(aes(x=mech_cons$val_lib_loc,y=mech_cons$dv_cl_bl,linetype=as.factor(mech_cons$fraction_blue)),color="darkorange") +
  facet_wrap(~mech_cons$val_lib_min,dir="v") +
  theme(legend.position = "bottom")

libmj_min <-  ggplot(data=mech_lib) + geom_point(aes(x=mech_lib$val_lib_min,y=mech_lib$de_cl_bl,color=mech_lib$et_cl_bl),shape="square")  + 
  geom_line(aes(x=mech_lib$val_lib_min,y=mech_lib$de_cl_bl,linetype=as.factor(mech_lib$fraction_blue)),color="blue") +
   scale_color_gradient(low = "grey", high = "brown") +
geom_point(aes(x=mech_lib$val_lib_min,y=mech_lib$dv_cl_bl,color=mech_lib$vl_cl_bl),shape ="circle") +
    geom_line(aes(x=mech_lib$val_lib_min,y=mech_lib$dv_cl_bl,linetype=as.factor(mech_lib$fraction_blue)),color="darkorange") +
  facet_wrap(~mech_lib$val_lib_loc,dir="v") +
  theme(legend.position = "bottom")

ggplotly(libmj_maj)
ggplotly(libmj_min)

ggpubr::ggarrange(libmj_maj,libmj_min)

libmn_maj <- ggplot(data=mech_cons) + geom_point(aes(x=mech_cons$val_lib_loc,y=mech_cons$de_cl_or,color=mech_cons$et_cl_or),shape="square")  + geom_line(aes(x=mech_cons$val_lib_loc,y=mech_cons$de_cl_or,linetype=as.factor(mech_cons$fraction_blue)),color="blue") +
   scale_color_gradient(low = "grey", high = "brown") +
geom_point(aes(x=mech_cons$val_lib_loc,y=mech_cons$dv_cl_or,color=mech_cons$vl_cl_or),shape ="circle") +
    geom_line(aes(x=mech_cons$val_lib_loc,y=mech_cons$dv_cl_or,linetype=as.factor(mech_cons$fraction_blue)),color="darkorange") +
  facet_wrap(~mech_cons$val_lib_min,dir="v") +
  theme(legend.position = "bottom")

libmn_min <-  ggplot(data=mech_lib) + geom_point(aes(x=mech_lib$val_lib_min,y=mech_lib$de_cl_or,color=mech_lib$et_cl_or),shape="square")  + 
  geom_line(aes(x=mech_lib$val_lib_min,y=mech_lib$de_cl_or,linetype=as.factor(mech_lib$fraction_blue)),color="blue") +
   scale_color_gradient(low = "grey", high = "brown") +
geom_point(aes(x=mech_lib$val_lib_min,y=mech_lib$dv_cl_or,color=mech_lib$vl_cl_or),shape ="circle") +
    geom_line(aes(x=mech_lib$val_lib_min,y=mech_lib$dv_cl_or,linetype=as.factor(mech_lib$fraction_blue)),color="darkorange") +
  facet_wrap(~mech_lib$val_lib_loc,dir="v") +
  theme(legend.position = "bottom")

ggplotly(libmn_maj)
ggplotly(libmn_min)

ggpubr::ggarrange(libmj_maj,libmj_min)
ggpubr::ggarrange(libmn_maj,libmn_min)

#####
# too complicated

lib_loc <- ggplot(data=mech_cons) + geom_point(aes(x=mech_cons$val_lib_loc,y=mech_cons$dv_sq_bl,color=mech_cons$vl_sq_bl),shape=15)  + 
  geom_line(aes(x=mech_cons$val_lib_loc,y=mech_cons$dv_sq_bl,linetype=as.factor(mech_cons$val_lib_min)),color="blue") +
   scale_color_gradient(low = "grey", high = "brown") +
geom_point(aes(x=mech_cons$val_lib_loc,y=mech_cons$dv_sq_or,color=mech_cons$vl_sq_or),shape =15) +
    geom_line(aes(x=mech_cons$val_lib_loc,y=mech_cons$dv_sq_or,linetype=as.factor(mech_cons$val_lib_min)),color="darkorange") +
  facet_wrap(~mech_cons$fraction_blue,dir="v") +
  theme(legend.position = "bottom")

lib_min <- ggplot(data=mech_lib) + geom_point(aes(x=mech_lib$val_lib_min,y=mech_lib$dv_sq_bl,color=mech_lib$vl_sq_bl),shape=15)  + 
  geom_line(aes(x=mech_lib$val_lib_min,y=mech_lib$dv_sq_bl,linetype=as.factor(mech_lib$val_lib_loc)),color="blue") +
   scale_color_gradient(low = "grey", high = "brown") +
geom_point(aes(x=mech_lib$val_lib_min,y=mech_lib$dv_sq_or,color=mech_lib$vl_sq_or),shape =15) +
    geom_line(aes(x=mech_lib$val_lib_min,y=mech_lib$dv_sq_or,linetype=as.factor(mech_lib$val_lib_loc)),color="darkorange") +
  facet_wrap(~mech_lib$fraction_blue,dir="v") +
  theme(legend.position = "bottom")

ggplotly(lib_loc)
ggplotly(lib_min)
ggpubr::ggarrange(lib_loc,lib_min,common.legend = TRUE)

#####
# fraction: take 50 65 80, beta = 0, 1, 7

df_min <- read.csv("vlmin_ethrat_1.csv",sep = ",",skip = 6)
legend <- read.csv("legend_sa_asym.csv",sep = ";")
legend <- as.data.frame(legend[,-2])
names(df_min) <- pull(legend)

df_maj <- read.csv("vlmaj_ethrat_1.csv",sep = ",",skip = 6)
names(df_maj) <- pull(legend)

excl <- names(df_min) %in% c("run", "density","step")
df_min <- df_min[!excl] %>% group_by(eth_con_loc, eth_con_min,eth_lib_loc,eth_lib_min,val_lib_loc,val_lib_min,val_con_loc,val_con_min,circle_orange,circle_blue,fraction_blue) %>% summarise_all(mean)

excl <- names(df_maj) %in% c("run", "density","step")
df_maj <- df_maj[!excl] %>% group_by(eth_con_loc, eth_con_min,eth_lib_loc,eth_lib_min,val_lib_loc,val_lib_min,val_con_loc,val_con_min,circle_orange,circle_blue,fraction_blue) %>% summarise_all(mean)

df_min <- df_min %>% filter(eth_con_min==20 & eth_con_loc==20)
# df_min <- df_min %>% filter(fraction_blue==50 |  fraction_blue==80)
df_min <- df_min %>% filter(val_lib_loc == 0 | val_lib_loc == 1 |  val_lib_loc == 7 )

# val_lib_loc == 3 ||val_lib_loc == 7 |

df_maj <- df_maj %>% filter(eth_con_min==20 & eth_con_loc==20)
# df_maj <- df_maj %>% filter(fraction_blue==50 |  fraction_blue==80)
df_maj <- df_maj %>% filter(val_lib_min == 0 | val_lib_min == 1 |   val_lib_min == 7 )

#  val_lib_min == 3 | val_lib_min == 7

majcons_min <- ggplot(data = mech_lib) + geom_point(aes(x=val_lib_min,y=dv_sq_bl, colour = vl_sq_bl),shape = "circle",size=2)  + geom_line(aes(x=val_lib_min,y=dv_sq_bl, linetype = as.factor(val_lib_loc))) + facet_wrap(~mech_lib$fraction_blue) +
  # geom_point(aes(x=val_lib_min,y=de_sq_bl, colour = et_sq_bl),shape = "square",size=2)  + geom_line(aes(x=val_lib_min,y=de_sq_bl, linetype = as.factor(val_lib_loc))) + facet_wrap(~df_min$fraction_blue)  + 
  ggtitle("majcons over min")

majcons_maj <- ggplot(data = mech_cons) + geom_point(aes(x=val_lib_loc,y=dv_sq_bl, colour = vl_sq_bl),shape = "circle",size=2)  + geom_line(aes(x=val_lib_loc,y=dv_sq_bl, linetype = as.factor(val_lib_min))) + facet_wrap(~mech_cons$fraction_blue) +
 # geom_point(aes(x=val_lib_loc,y=de_sq_bl, colour = et_sq_bl),shape = "square",size=2)  + geom_line(aes(x=val_lib_loc,y=de_sq_bl, linetype = as.factor(val_lib_min))) + facet_wrap(~df_min$fraction_blue)  + 
  ggtitle("majcons over min")

mincons_min <- ggplot(data = df_min) + geom_point(aes(x=val_lib_min,y=dv_sq_or, colour = vl_sq_or),shape = "circle",size=2)  + geom_line(aes(x=val_lib_min,y=dv_sq_or, linetype = as.factor(val_lib_loc))) + facet_wrap(~df_min$fraction_blue) +
#   geom_point(aes(x=val_lib_min,y=de_sq_or, colour = et_sq_or),shape = "square",size=2)  + geom_line(aes(x=val_lib_min,y=de_sq_or, linetype = as.factor(val_lib_loc))) + facet_wrap(~df_min$fraction_blue) +
  ggtitle("mincons over min")

mincons_maj <- ggplot(data = df_maj) + geom_point(aes(x=val_lib_loc,y=dv_sq_or, colour = vl_sq_or),shape = "circle",size=2)  + geom_line(aes(x=val_lib_loc,y=dv_sq_or, linetype = as.factor(val_lib_min))) + facet_wrap(~df_maj$fraction_blue) + # geom_point(aes(x=val_lib_loc,y=de_sq_or, colour = et_sq_or),shape = "square",size=2)  + geom_line(aes(x=val_lib_loc,y=de_sq_or, linetype = as.factor(val_lib_min))) + facet_wrap(~df_maj$fraction_blue) +
  ggtitle("mincons over maj")

ggplotly(majcons_min)
ggplotly(majcons_maj)

ggplotly(mincons_min)
ggplotly(mincons_maj)

majlib_min <- ggplot(data = df_min) + geom_point(aes(x=val_lib_min,y=dv_cl_bl, colour = vl_cl_bl),shape = "circle",size=2)  + geom_line(aes(x=val_lib_min,y=dv_cl_bl, linetype = as.factor(val_lib_loc))) + facet_wrap(~df_min$fraction_blue)+ 
  # geom_point(aes(x=val_lib_min,y=de_cl_bl, colour = et_cl_bl),shape = "square",size=2)  + geom_line(aes(x=val_lib_min,y=de_cl_bl, linetype = as.factor(val_lib_loc))) + facet_wrap(~df_min$fraction_blue)+ 
 ggtitle("majlib over min")

majlib_maj <- ggplot(data = df_maj) + geom_point(aes(x=val_lib_loc,y=dv_cl_bl, colour = vl_cl_bl),shape = "circle",size=2)  + geom_line(aes(x=val_lib_loc,y=dv_cl_bl, linetype = as.factor(val_lib_min))) + facet_wrap(~df_maj$fraction_blue) +
  # geom_point(aes(x=val_lib_loc,y=de_cl_bl, colour = et_cl_bl),shape = "square",size=2)  + geom_line(aes(x=val_lib_loc,y=de_cl_bl, linetype = as.factor(val_lib_min))) + facet_wrap(~df_min$fraction_blue)+
 ggtitle("majlib over maj")

ggplotly(majlib_min)
ggplotly(majlib_maj)

minlib_min <- ggplot(data = df_min) + geom_point(aes(x=val_lib_min,y=dv_cl_or, colour = vl_cl_or),shape = "circle",size=2)  + geom_line(aes(x=val_lib_min,y=dv_cl_or, linetype = as.factor(val_lib_loc))) + facet_wrap(~df_min$fraction_blue)+ geom_point(aes(x=val_lib_min,y=de_cl_or, colour = et_cl_or),shape = "square",size=2)  + geom_line(aes(x=val_lib_min,y=de_cl_or, linetype = as.factor(val_lib_loc))) + facet_wrap(~df_min$fraction_blue)  +
  ggtitle("minlib over min")

minlib_maj <- ggplot(data = df_maj) + geom_point(aes(x=val_lib_loc,y=dv_cl_or, colour = vl_cl_or),shape = "circle",size=2)  + geom_line(aes(x=val_lib_loc,y=dv_cl_or, linetype = as.factor(val_lib_min))) + facet_wrap(~df_maj$fraction_blue) + geom_point(aes(x=val_lib_loc,y=de_cl_or, colour = et_cl_or),shape = "square",size=2)  + geom_line(aes(x=val_lib_loc,y=de_cl_or, linetype = as.factor(val_lib_min))) + facet_wrap(~df_maj$fraction_blue) +
  ggtitle("minlib over maj")

ggplotly(minlib_min)
ggplotly(minlib_maj)

```

```{r back}

# fraction: take 50 65 80, beta = 0, 1, 7

# vlmin1 <- read.csv("vlmin_ethrat_1.csv",sep = ",",skip = 6)
# legend <- read.csv("legend_sa_asym.csv",sep = ";")
# legend <- as.data.frame(legend[,-2])
# names(vlmin1) <- pull(legend)
# 
# vlmin2 <- read.csv("vlmin_ethrat_2.csv",sep = ",",skip = 6)
# names(vlmin2) <- pull(legend)
# 
# vlmaj1 <- read.csv("vlmaj_ethrat_1.csv",sep = ",",skip = 6)
# names(vlmaj1) <- pull(legend)
# 
# vlmaj2 <- read.csv("vlmaj_ethrat_2.csv",sep = ",",skip = 6)
# names(vlmaj2) <- pull(legend)
# 
# mech_lib <- rbind(vlmin1,vlmin2,vlmaj1,vlmaj2)
# write.csv(mech_lib,"mech_lib.csv",row.names = FALSE)

df_long <- df %>% gather(key= subgroup, value = Outcome, de_sq_bl, dv_sq_bl, de_cl_bl, dv_cl_bl, de_sq_or, dv_sq_or, de_cl_or, dv_cl_or
                         ) %>% mutate(

   # `measureseg` = fct_relevel(fct_collapse(subgroup,"exposure" = c("et_sq_bl", "vl_sq_bl", "et_cl_bl", "vl_cl_bl", "et_sq_or", "vl_sq_or", "et_cl_or", "vl_cl_or"), "clustering" = c("de_sq_bl", "dv_sq_bl", "de_cl_bl", "dv_cl_bl", "de_sq_or", "dv_sq_or", "de_cl_or", "dv_cl_or")),"exposure"),

  `segregation` = fct_relevel(fct_collapse(subgroup,"ethnics" = c("de_sq_bl","de_cl_bl","de_sq_or","de_cl_or" ), "values" = c("dv_sq_bl","dv_cl_bl","dv_sq_or","dv_cl_or" )),"ethnics"),

 `orientation` = fct_relevel(fct_collapse(subgroup, "conservative" = c("de_sq_bl","dv_sq_bl","de_sq_or","dv_sq_or"), "liberal" = c("de_cl_bl","dv_cl_bl","de_cl_or","dv_cl_or")),"conservative" ),

 `ethnia` = fct_relevel(fct_collapse(subgroup, "local" = c("de_sq_bl","dv_sq_bl","de_cl_bl","dv_cl_bl"),"minority" = c("de_sq_or","dv_sq_or","de_cl_or","dv_cl_or")), "local"),

 `groupp` = fct_relevel(fct_collapse(subgroup, "cons_maj" = c("de_sq_bl","dv_sq_bl"),"lib_maj"=c("de_cl_bl","dv_cl_bl"),"cons_min"=c("de_sq_or","dv_sq_or"),"lib_min"=c("de_cl_or","dv_cl_or")),"cons_maj")
  )

## df_long 2 measures

df_long <- df %>% gather(key= subgroup, value = Outcome, et_sq_bl, vl_sq_bl, et_cl_bl, vl_cl_bl, et_sq_or, vl_sq_or, et_cl_or, vl_cl_or,
                          de_sq_bl, dv_sq_bl, de_cl_bl, dv_cl_bl, de_sq_or, dv_sq_or, de_cl_or, dv_cl_or ) %>% mutate(

   `measureseg` = fct_relevel(fct_collapse(subgroup,"exposure" = c("et_sq_bl", "vl_sq_bl", "et_cl_bl", "vl_cl_bl", "et_sq_or", "vl_sq_or", "et_cl_or", "vl_cl_or"), "clustering" = c("de_sq_bl", "dv_sq_bl", "de_cl_bl", "dv_cl_bl", "de_sq_or", "dv_sq_or", "de_cl_or", "dv_cl_or")),"exposure"),

  `segregation` = fct_relevel(fct_collapse(subgroup,"ethnics" = c("et_sq_bl","et_cl_bl","et_sq_or","et_cl_or","de_sq_bl","de_cl_bl","de_sq_or", "de_cl_or" ), "values" = c("vl_sq_bl","vl_cl_bl","vl_sq_or","vl_cl_or","dv_sq_bl","dv_cl_bl","dv_sq_or","dv_cl_or" )),"ethnics"),

 `orientation` = fct_relevel(fct_collapse(subgroup, "conservative" = c("et_sq_bl","vl_sq_bl","et_sq_or","vl_sq_or","de_sq_bl", "dv_sq_bl", "de_sq_or", "dv_sq_or"), "liberal" = c("et_cl_bl","vl_cl_bl","et_cl_or","vl_cl_or","de_cl_bl", "dv_cl_bl","de_cl_or", "dv_cl_or")),"conservative" ), 
 `ethnia` = fct_relevel(fct_collapse(subgroup, "local" = c("et_sq_bl","vl_sq_bl","et_cl_bl","vl_cl_bl","de_sq_bl", "dv_sq_bl", "de_cl_bl", "dv_cl_bl"),"minority" = c("et_sq_or","vl_sq_or","et_cl_or","vl_cl_or","de_sq_or", "dv_sq_or", "de_cl_or", "dv_cl_or")), "local")
 )

## 3D plotly

dfcl <- df_long[which(df_long$measureseg=="clustering"),]

df_etsqbl<- df[,which((names(df) %in% c("fraction_blue","dominant","et_sq_bl")))]

a <- as.matrix(df$dominant)
class(a)

b <- as.matrix(df$fraction_blue)
z <- as.matrix(df$et_sq_bl)

diba <- data.matrix(df)
class(diba)

M <- mesh(seq(0, 6*pi, length.out = 50),seq(pi/3, pi, length.out = 50))
u <- M$x ; v <- M$y

x <- data.matrix(df$fraction_blue)
y <- data.matrix(df$dominant)
z <- data.matrix(df$et_sq_bl)

dfa <- df[which(df$dominant <= 15),]
#plot_ly(data=df, x=df$dominant, y=df$fraction_blue, z=df$de_sq_bl, color = df$et_sq_bl) +
  plot_ly(data=dfa) %>% 
    add_trace(x=dfa$dominant, y=dfa$fraction_blue, z=dfa$de_sq_or, color = dfa$et_sq_bl,type = 'scatter3d',mode = 'lines+markers', marker = list( symbol="square") ) %>% 
     add_trace(x=dfa$dominant, y=dfa$fraction_blue, z=dfa$de_sq_bl, color = dfa$et_sq_bl, type = 'scatter3d',mode = 'lines+markers') %>%
    #   add_trace(x=df$dominant, y=df$fraction_blue, z=df$de_cl_or, color = df$et_cl_or, type = 'scatter3d',mode = 'lines+markers') %>%
    #     add_trace(x=df$dominant, y=df$fraction_blue, z=df$de_cl_bl, color = df$et_cl_bl, type = 'scatter3d',mode = 'lines+markers') %>%

    layout(
  #  title = "Layout options in a 3d scatter plot",
    scene = list(
      xaxis = list(title = "dominant"),
      yaxis = list(title = "ethnic ratio"),
      zaxis = list(title = "cluster")
    ))

# plot for each subgroup, aesthetic: x-axis:beta, y-axis:spatial clustering, linetype  = fraction_blue, shape = type of segregation, bright = exposure

## make ggplot into plotly
x1 <- 1:100
x2 <- x1 + 100
x3 <- x2 + 100

x <-  c(x1, x2, x3)
y <- c(2*x1, 5*x2, -2*x3)

group <-  c(rep("A", length(x1)),
           rep("B", length(x2)),
           rep("C", length(x3)))

ds <- data.frame(x, y, group)

# Use the group aesthetic to ensure lines are drawn separately for each group
p <- ggplot(ds, aes(x, y)) +
  geom_line(aes(group = group, color = group), size = 2) +
  ggtitle("Group specific line chart")

fig <- ggplotly(p)

## regression fit to 3D

# data(mtcars)
# 
# mtcars$shape <- cut(mtcars$mpg,
#                     breaks = c(0,18, 26, 100),
#                     labels = c("square", "circle", "diamond"))
# mtcars$color <- cut(mtcars$mpg,
#                     breaks = c(0,18, 26, 100),
#                     labels = c("red", "yellow", "green"))
# 
# plot_ly(type = "scatter", data = mtcars, x = rownames(mtcars), y = mtcars$mpg,
#         mode = "markers", symbol = ~I(shape), color = ~I(color))

x <- data.matrix(df$dominant)
y <- data.matrix(df$fraction_blue)
z <- data.matrix(df$et_sq_bl)

fit <- lm(z ~ as.integer(x) + as.integer(y))
# predict values on regular xy grid
grid.lines = 100
x.pred <- seq(min(x), max(x), length.out = grid.lines)
y.pred <- seq(min(y), max(y), length.out = grid.lines)
xy <- expand.grid( x = x.pred, y = y.pred)
z.pred <- matrix(predict(fit, newdata = xy),
                 nrow = grid.lines, ncol = grid.lines)
# fitted points for droplines to surface
fitpoints <- predict(fit)
# scatter plot with regression plane
scatter3D(x, y, z, pch = 18, cex = 2,
    theta = 90, phi = 0, ticktype = "detailed",
    xlab = "dominant", ylab = "maj/min", zlab = "de_sq_mj",
    surf = list(x = x.pred, y = y.pred, z = z.pred,
    facets = NA, fit = fitpoints), main = "df")

```

### 2021-05-25 additional.Rmd
ok plotly

@@
             scene = "scene1",
-                                        name = "Ethnic",
+                                       # name = "Ethnic",
                                        type="scatter3d",
                                        mode="markers",
-                                     marker = list(cmin=0,cmax=1,
-                                                   # colorscale = "Reds",
-                                     colorscale =  list(
-                                        c(0,'pink'),
-                                        c(0.25,'red'),
-                                        c(0.5,'green'),
-                                        c(0.75,'blue'),
-                                        c(1, 'purple')),
-                                       color= df_sqbl$et_sq_bl, showscale = T)
+                                     marker = list(
+                                       #cmin=0,cmax=1,
+                                           colorscale = "Reds",
+                                     # colorscale =  list(
+                                     #    c(0,'pink'),
+                                     #    c(0.25,'red'),
+                                     #    c(0.5,'green'),
+                                     #    c(0.75,'blue'),
+                                     #    c(1, 'purple')),
+                                       color= df_sqbl$et_sq_bl, showscale =  T,
+                                     colorbar=list(title = "Ethnic \nExposure" ,y = 0.3, len = 0.5, yanchor='top'))
 
@@
   layout(showlegend = F,
-         title="Ethnic",
-         scene = list(
+         #title="Ethnic",
+         "scene1" = list(
       xaxis = list(title = "Ethnic Ratio",range=seq(50,90,by=10),dtick=10),
       yaxis = list(title = "% Liberal Minority",autorange = "reversed"),
-      zaxis = list(title = "Cluster")))
+      zaxis = list(title = "Ethnic Cluster")))
 
@@
                                           scene =  "scene2",
-                                     name = "Value",
+                                   #  name = "Value",
                                      type="scatter3d",
                                      mode="markers", 
-                                    marker = list(cmin=0,cmax=1,
+                                     marker = list( #cmin=0,cmax=1,
                                                    # colorscale = "Reds",
-                                     colorscale =  list(
-                                        c(0,'pink'),
-                                        c(0.25,'red'),
-                                        c(0.5,'green'),
-                                        c(0.75,'blue'),
-                                        c(1, 'purple')),
-                                       color= df_sqbl$et_sq_bl, showscale = T)
+                                     colorscale = "Blues",
+                                       # list(
+                                       #  c(0,'pink'),
+                                       #  c(0.25,'red'),
+                                       #  c(0.5,'green'),
+                                       #  c(0.75,'blue'),
+                                       #  c(1, 'purple'))
 
+                                    color= df_sqbl$et_sq_bl , showscale = T, reversescale=T,
+                                     colorbar=list(title = "Value  \nExposure", y = 0.3, len=0.5, yanchor='bottom'))
             )  %>% 
-       layout(showlegend = T,
-         title="",
-         scene = list(
+       layout(showlegend = F,
+         "scene2" = list(
       xaxis = list(title = "Ethnic Ratio",range=seq(50,90,by=10),dtick=10),
       yaxis = list(title = "% Liberal Minority",autorange = "reversed"),
-      zaxis = list(title = "Cluster")))
+      zaxis = list(title = "Value Cluster")))
 
-A <- subplot(lowE,lowV) %>% layout(annotations = list(
- list(x = 0.2 , y = 1 , text = "Ethnic", showarrow = F, xref='paper', yref='paper'),
-  list(x = 0.8 , y = 1, text = "Value", showarrow = F, xref='paper', yref='paper'))
+axx <- list(
+  title = "Ethnic Ratio"
 )
+
+axy <- list(
+  title = "% Liberal Minority"
+)
+
+axz <- list(
+  title = "Ethnic Cluster"
+)
+
+A <- subplot(lowE, lowV)  %>%
+
+  layout(title =  "Conservative Locals"
+)
+
+b <- subplot(
+  add_markers(plot_ly(x=df_sqbl$fraction_blue,y=df_sqbl$circle_orange,z=df_sqbl$de_sq_bl),color=df_sqbl$et_sq_bl) %>% colorbar(title= "Ethnic")
+
+)
+
+c <- subplot(
+  add_markers(plot_ly(x=df_sqbl$fraction_blue,y=df_sqbl$circle_orange,z=df_sqbl$dv_sq_bl),color=df_sqbl$vl_sq_bl) %>% colorbar(title = "Value")
+
+)
+
+A <- subplot(b,c)
 

### 2021-05-27 additional.Rmd
df 3D

--- 2021-05-25 additional.Rmd
@@
 
- df <- read.csv("3Dlowdom.csv",sep = ",",skip = 6)
-df2 <- read.csv("3Dhighdom.csv",sep = ",",skip = 6)
-leg <- read.csv("legend_sa_asym.csv",sep=";")[,1]
-df_fin <- rbind(df,df2)
- names(df_fin)<- leg
-
+#  df <- read.csv("3Dlowdom.csv",sep = ",",skip = 6)
+# df2 <- read.csv("3Dhighdom.csv",sep = ",",skip = 6)
+#  df3 <- read.csv("3Detlibhigh.csv",sep = ",",skip = 6)
+# df4 <- read.csv("3Detliblow.csv",sep = ",",skip = 6)
+# 
+# leg <- read.csv("legend_sa_asym.csv",sep=";")[,1]
+# df_fin <- rbind(df,df2,df3,df4)
+#  names(df_fin)<- leg
+# # 
+#   write.csv(df_fin,"3D.csv",row.names = F)
+#  
+#
+
+# excl3D <- names(df_fin) %in% c("run", "density","step")
+# df_fin <- df_fin[!excl3D] %>% group_by(eth_con_loc, eth_con_min,eth_lib_loc,eth_lib_min,val_lib_loc,val_lib_min,val_con_loc,val_con_min,circle_orange,circle_blue,fraction_blue) %>% summarise_all(mean)
 # 
@@
 
-excl3D <- names(df_fin) %in% c("run", "density","step")
-df_fin <- df_fin[!excl3D] %>% group_by(eth_con_loc, eth_con_min,eth_lib_loc,eth_lib_min,val_lib_loc,val_lib_min,val_con_loc,val_con_min,circle_orange,circle_blue,fraction_blue) %>% summarise_all(mean)
-
 vars <- c("de_sq_bl","dv_sq_bl","et_sq_bl","vl_sq_bl")
-df_sqbl <- cbind(df_fin[,1:11],df_fin[,vars]) %>% filter(val_lib_loc==5,val_lib_min==5,eth_con_loc == 5,eth_con_min == 5)
-df_high <- cbind(df_fin[,1:11],df_fin[,vars]) %>% filter(val_lib_loc==20,val_lib_min==20,eth_con_loc == 20,eth_con_min == 20)
-
-lowE <- plot_ly(df_sqbl)  %>%
-  add_trace(x=df_sqbl$fraction_blue,y=df_sqbl$circle_orange,z=df_sqbl$de_sq_bl,
+df_3D_low <- cbind(df_3D[,1:11],df_3D[,vars]) %>% filter(val_lib_loc==5,val_lib_min==5,eth_con_loc == 5,eth_con_min == 5,eth_lib_loc ==0,eth_lib_min==0)
+df_3D_high <- cbind(df_3D[,1:11],df_3D[,vars]) %>% filter(val_lib_loc==20,val_lib_min==20,eth_con_loc == 20,eth_con_min == 20,eth_lib_loc ==0,eth_lib_min==0)
+
+lowE <- plot_ly(df_3D_low)  %>%
+  add_trace(x=df_3D_low$fraction_blue,y=df_3D_low$circle_orange,z=df_3D_low$de_sq_bl,
             scene = "scene1",
-                                        name = "Ethnic",
+                                       # name = "Ethnic",
                                        type="scatter3d",
                                        mode="markers",
-                                     marker = list(cmin=0,cmax=1,
-                                                   # colorscale = "Reds",
-                                     colorscale =  list(
-                                        c(0,'pink'),
-                                        c(0.25,'red'),
-                                        c(0.5,'green'),
-                                        c(0.75,'blue'),
-                                        c(1, 'purple')),
-                                       color= df_sqbl$et_sq_bl, showscale = T)
+                                     marker = list(
+                                       #cmin=0,cmax=1,
+                                           colorscale = "Reds",
+                                     # colorscale =  list(
+                                     #    c(0,'pink'),
+                                     #    c(0.25,'red'),
+                                     #    c(0.5,'green'),
+                                     #    c(0.75,'blue'),
+                                     #    c(1, 'purple')),
+                                       color= df_3D_low$et_sq_bl, showscale =  T,
+                                     colorbar=list(title = "Ethnic \nExposure" ,x = -0.1,  len = 0.5, yanchor='bottom'))
 
@@
   layout(showlegend = F,
-         title="Ethnic",
-         scene = list(
+         #title="Ethnic",
+         "scene1" = list(
       xaxis = list(title = "Ethnic Ratio",range=seq(50,90,by=10),dtick=10),
       yaxis = list(title = "% Liberal Minority",autorange = "reversed"),
-      zaxis = list(title = "Cluster")))
-
- lowV<- plot_ly(df_sqbl)  %>%   add_trace(x=df_sqbl$fraction_blue,y=df_sqbl$circle_orange,z=df_sqbl$dv_sq_bl,
+      zaxis = list(title = "Ethnic Cluster")))
+
+ lowV<- plot_ly(df_3D_low)  %>%   add_trace(x=df_3D_low$fraction_blue,y=df_3D_low$circle_orange,z=df_3D_low$dv_sq_bl,
                                           scene =  "scene2",
-                                     name = "Value",
+                                   #  name = "Value",
                                      type="scatter3d",
                                      mode="markers", 
-                                    marker = list(cmin=0,cmax=1,
+                                     marker = list( #cmin=0,cmax=1,
                                                    # colorscale = "Reds",
-                                     colorscale =  list(
-                                        c(0,'pink'),
-                                        c(0.25,'red'),
-                                        c(0.5,'green'),
-                                        c(0.75,'blue'),
-                                        c(1, 'purple')),
-                                       color= df_sqbl$et_sq_bl, showscale = T)
-
+                                     colorscale = "Blues",
+                                       # list(
+                                       #  c(0,'pink'),
+                                       #  c(0.25,'red'),
+                                       #  c(0.5,'green'),
+                                       #  c(0.75,'blue'),
+                                       #  c(1, 'purple'))
+
+                                    color= df_3D_low$vl_sq_bl , showscale = T, reversescale=T,
+                                     colorbar=list(title = "Value  \nExposure", len=0.5, yanchor='bottom'))
             )  %>% 
-       layout(showlegend = T,
-         title="",
-         scene = list(
+       layout(showlegend = F,
+         "scene2" = list(
       xaxis = list(title = "Ethnic Ratio",range=seq(50,90,by=10),dtick=10),
       yaxis = list(title = "% Liberal Minority",autorange = "reversed"),
-      zaxis = list(title = "Cluster")))
-
-A <- subplot(lowE,lowV) %>% layout(annotations = list(
- list(x = 0.2 , y = 1 , text = "Ethnic", showarrow = F, xref='paper', yref='paper'),
-  list(x = 0.8 , y = 1, text = "Value", showarrow = F, xref='paper', yref='paper'))
-)
-
-   ###
-
-high <- plot_ly(df_high)  %>% add_trace(x=df_high$fraction_blue,y=df_high$circle_orange,z=df_high$de_sq_bl,color= df_high$et_sq_bl,
+      zaxis = list(title = "Value Cluster")))
+
+ highE <- plot_ly(df_3D_high)  %>%
+  add_trace(x=df_3D_high$fraction_blue,y=df_3D_high$circle_orange,z=df_3D_high$de_sq_bl,
+            scene = "scene3",
+                                       # name = "Ethnic",
                                        type="scatter3d",
                                        mode="markers",
-                                       marker = list( colorscale = 'Reds', showscale = T))  %>%
-  add_trace(x=df_high$fraction_blue,y=df_high$circle_orange,z=df_high$dv_sq_bl,color= df_high$vl_sq_bl,
+                                     marker = list(
+                                       #cmin=0,cmax=1,
+                                           colorscale = "Reds",
+                                     # colorscale =  list(
+                                     #    c(0,'pink'),
+                                     #    c(0.25,'red'),
+                                     #    c(0.5,'green'),
+                                     #    c(0.75,'blue'),
+                                     #    c(1, 'purple')),
+                                       color= df_3D_high$et_sq_bl, showscale =  T,
+                                     colorbar=list(title = "Ethnic \nExposure" ,x = -0.1,  len = 0.5, yanchor='top'))
+
+            )  %>% 
+  layout(showlegend = F,
+         #title="Ethnic",
+         "scene3" = list(
+      xaxis = list(title = "Ethnic Ratio",range=seq(50,90,by=10),dtick=10),
+      yaxis = list(title = "% Liberal Minority",autorange = "reversed"),
+      zaxis = list(title = "Ethnic Cluster")))
+
+ highV<- plot_ly(df_3D_high)  %>%   add_trace(x=df_3D_high$fraction_blue,y=df_3D_high$circle_orange,z=df_3D_high$dv_sq_bl,
+                                          scene =  "scene4",
+                                   #  name = "Value",
                                      type="scatter3d",
                                      mode="markers", 
-                                      marker = list( colorscale = 'Greens', showscale = TRUE))  %>%
-  layout(legend = list(orientation = 'h'),
-         title="high",
-         scene = list(
+                                     marker = list( #cmin=0,cmax=1,
+                                                   # colorscale = "Reds",
+                                     colorscale = "Blues",
+                                       # list(
+                                       #  c(0,'pink'),
+                                       #  c(0.25,'red'),
+                                       #  c(0.5,'green'),
+                                       #  c(0.75,'blue'),
+                                       #  c(1, 'purple'))
+
+                                    color= df_3D_high$vl_sq_bl , showscale = T, reversescale=T,
+                                     colorbar=list(title = "Value  \nExposure", len=0.5, yanchor='top'))
+            )  %>% 
+       layout(showlegend = F,
+         "scene4" = list(
       xaxis = list(title = "Ethnic Ratio",range=seq(50,90,by=10),dtick=10),
       yaxis = list(title = "% Liberal Minority",autorange = "reversed"),
-      zaxis = list(title = "Cluster")))
-
-low
-high
-
-```
-
-```{r 3Dsimple, fig.cap="3D pictures", echo = FALSE}
-
-excl3D <- names(df_fin) %in% c("run", "density","step")
-df_fin <- df_fin[!excl3D] %>% group_by(eth_con_loc, eth_con_min,eth_lib_loc,eth_lib_min,val_lib_loc,val_lib_min,val_con_loc,val_con_min,circle_orange,circle_blue,fraction_blue) %>% summarise_all(mean)
-
-vars <- c("de_sq_or","dv_sq_or","et_sq_or","vl_sq_or")
-df_sqbl <- cbind(df_fin[,1:11],df_fin[,vars]) %>% filter(val_lib_loc==5,val_lib_min==5,eth_con_loc == 5,eth_con_min == 5)
-df_high <- cbind(df_fin[,1:11],df_fin[,vars]) %>% filter(val_lib_loc==20,val_lib_min==20,eth_con_loc == 20,eth_con_min == 20)
-
-low <- plot3D::scatter3D(x = df_sqbl$fraction_blue, y = df_sqbl$circle_orange, z = df_sqbl$de_sq_or, colvar = df_sqbl$et_sq_or, col = ramp.col (col = c("grey", "blue"), n = 100, alpha = 1), pch=20, cex= 2, phi = 0)
+      zaxis = list(title = "Value Cluster")))
+
+A <- subplot(lowE, lowV,  highE, highV) %>%
+
+   layout(scene = list(domain=list(x=c(0,0.5),y=c(0.5,1)),zaxis = list(title = "Ethnic Cluster")),
+         scene2 = list(domain=list(x=c(0.5,1),y=c(0.5,1))),
+         scene3 = list(domain=list(x=c(0,0.5),y=c(0,0.5))),
+         scene4 = list(domain=list(x=c(0.5,1),y=c(0,0.5)))
+         ) %>%
+
+  layout(annotations = list(
+  text = "Conservative Locals",
+  font = list(size = 18),
+  xref = "paper",
+  yref = "paper",
+  yanchor = "bottom",
+  xanchor = "center",
+  align = "center",
+  x = 0.5,
+  y = 1,
+  showarrow = FALSE
+)
+
+) %>%
+  layout(annotations = list(
+  text = "High Randomness",
+  font = list(size = 15),
+  xref = "paper",
+  yref = "paper",
+  yanchor = "bottom",
+  xanchor = "center",
+  align = "center",
+  x = 0.5,
+  y = 0.5,
+  showarrow = FALSE
+))%>%
+  layout(annotations = list(
+  text = "Low Randomness",
+  font = list(size = 15),
+  xref = "paper",
+  yref = "paper",
+  yanchor = "bottom",
+  xanchor = "center",
+  align = "center",
+  x = 0.5,
+  y = 0,
+  showarrow = FALSE
+)
+
+)
 

### 2021-05-27 additional.Rmd
last reference additional asymmetric

--- 2021-05-25 additional.Rmd
@@
 df_sec <- df_sec[!exclet] %>% group_by(ID,RND,eth_con_loc,eth_con_min,eth_lib_loc,eth_lib_min,val_lib_loc,val_lib_min,val_con_loc,val_con_min,circle_orange,circle_blue,fraction_blue) %>% summarise_all(mean)
-
- df <- read.csv("3Dlowdom.csv",sep = ",",skip = 6)
-df2 <- read.csv("3Dhighdom.csv",sep = ",",skip = 6)
-leg <- read.csv("legend_sa_asym.csv",sep=";")[,1]
-df_fin <- rbind(df,df2)
- names(df_fin)<- leg
-
-# 
-# df_t <- rbind(df_3D,df_fin)
-# 
-# 
-# write.csv(df_t,"3D.csv",row.names = F)
 
@@
 
-excl3D <- names(df_fin) %in% c("run", "density","step")
-df_fin <- df_fin[!excl3D] %>% group_by(eth_con_loc, eth_con_min,eth_lib_loc,eth_lib_min,val_lib_loc,val_lib_min,val_con_loc,val_con_min,circle_orange,circle_blue,fraction_blue) %>% summarise_all(mean)
+df_3D_low <- df_3D %>% filter(val_lib_loc==5,val_lib_min==5,eth_con_loc == 5,eth_con_min == 5,eth_lib_loc ==0,eth_lib_min==0) 
+df_3D_high <- df_3D %>% filter(val_lib_loc==20,val_lib_min==20,eth_con_loc == 20,eth_con_min == 20,eth_lib_loc ==0,eth_lib_min==0)
 
-vars <- c("de_sq_bl","dv_sq_bl","et_sq_bl","vl_sq_bl")
-df_sqbl <- cbind(df_fin[,1:11],df_fin[,vars]) %>% filter(val_lib_loc==5,val_lib_min==5,eth_con_loc == 5,eth_con_min == 5)
-df_high <- cbind(df_fin[,1:11],df_fin[,vars]) %>% filter(val_lib_loc==20,val_lib_min==20,eth_con_loc == 20,eth_con_min == 20)
+xx <- ~fraction_blue
+yy <- ~circle_orange
+zz <- ~de_sq_or
+cols <- ~et_sq_or
+zzv <- ~dv_sq_or
+colsv <- ~vl_sq_or
+tt <- "Conservative Minority"
 
-lowE <- plot_ly(df_sqbl)  %>%
-  add_trace(x=df_sqbl$fraction_blue,y=df_sqbl$circle_orange,z=df_sqbl$de_sq_bl,
+D3 <- {
+lowE <- plot_ly(df_3D_low)  %>%
+  add_trace(x= xx,y= yy,z=zz,
             scene = "scene1",
-                                        name = "Ethnic",
             type="scatter3d",
              mode="markers",
-                                     marker = list(cmin=0,cmax=1,
-                                                   # colorscale = "Reds",
-                                     colorscale =  list(
-                                        c(0,'pink'),
-                                        c(0.25,'red'),
-                                        c(0.5,'green'),
-                                        c(0.75,'blue'),
-                                        c(1, 'purple')),
-                                       color= df_sqbl$et_sq_bl, showscale = T)
+             marker = list(
+             colorscale = "Reds",
+             color= cols, showscale =  T,
+             colorbar=list(title = "Ethnic \nExposure" ,x = -0.1,  len = 0.5, yanchor='bottom'))
 
@@
   layout(showlegend = F,
-         title="Ethnic",
-         scene = list(
+         #title="Ethnic",
+         "scene1" = list(
       xaxis = list(title = "Ethnic Ratio",range=seq(50,90,by=10),dtick=10),
-      yaxis = list(title = "% Liberal Minority",autorange = "reversed"),
-      zaxis = list(title = "Cluster")))
+      yaxis = list(title = "% Liberal Minority" ,autorange = "reversed"),
+      zaxis = list(title = "Ethnic Cluster")))
 
- lowV<- plot_ly(df_sqbl)  %>%   add_trace(x=df_sqbl$fraction_blue,y=df_sqbl$circle_orange,z=df_sqbl$dv_sq_bl,
+ lowV<- plot_ly(df_3D_low)  %>%   add_trace(x=xx,y=yy,z=zzv,
              scene =  "scene2",
-                                     name = "Value",
              type="scatter3d",
              mode="markers", 
-                                    marker = list(cmin=0,cmax=1,
-                                                   # colorscale = "Reds",
-                                     colorscale =  list(
-                                        c(0,'pink'),
-                                        c(0.25,'red'),
-                                        c(0.5,'green'),
-                                        c(0.75,'blue'),
-                                        c(1, 'purple')),
-                                       color= df_sqbl$et_sq_bl, showscale = T)
+             marker = list( 
+             colorscale = "Blues",
+             color= colsv , showscale = T, reversescale=T,
+             colorbar=list(title = "Value  \nExposure", len=0.5, yanchor='bottom'))
+            )  %>% 
+       layout(showlegend = F,
+         "scene2" = list(
+      xaxis = list(title = "Ethnic Ratio",range=seq(50,90,by=10),dtick=10),
+      yaxis = list(title = "% Liberal Minority"  ,autorange = "reversed"),
+      zaxis = list(title = "Value Cluster")))
+
+highE <- plot_ly(df_3D_high)  %>%
+  add_trace(x=xx,y=yy,z=zz,
+            scene = "scene3",
+            type="scatter3d",
+             mode="markers",
+             marker = list(
+             colorscale = "Reds",
+             color= cols, showscale =  T,
+             colorbar=list(title = "Ethnic \nExposure" ,x = -0.1,  len = 0.5, yanchor='top'))
 
             )  %>%
-       layout(showlegend = T,
-         title="",
-         scene = list(
+  layout(showlegend = F,
+         #title="Ethnic",
+         "scene3" = list(
       xaxis = list(title = "Ethnic Ratio",range=seq(50,90,by=10),dtick=10),
-      yaxis = list(title = "% Liberal Minority",autorange = "reversed"),
-      zaxis = list(title = "Cluster")))
+      yaxis = list(title = "% Liberal Minority" ,autorange = "reversed"),
+      zaxis = list(title = "Ethnic Cluster")))
 
-A <- subplot(lowE,lowV) %>% layout(annotations = list(
- list(x = 0.2 , y = 1 , text = "Ethnic", showarrow = F, xref='paper', yref='paper'),
-  list(x = 0.8 , y = 1, text = "Value", showarrow = F, xref='paper', yref='paper'))
+ highV<- plot_ly(df_3D_high)  %>%   
+    add_trace(x=xx,y=yy,z=zz,
+     scene =  "scene4",
+     type="scatter3d",
+     mode="markers", 
+     marker = list( 
+     colorscale = "Blues",
+     color= colsv , showscale = T, reversescale=T,
+      colorbar=list(title = "Value  \nExposure", len=0.5, yanchor='top'))
+            )  %>% 
+       layout(showlegend = F,
+         "scene4" = list(
+      xaxis = list(title = "Ethnic Ratio",range=seq(50,90,by=10),dtick=10),
+      yaxis = list(title = "% Liberal Minority"   ,autorange = "reversed"),
+      zaxis = list(title = "Value Cluster")))
+
+subplot(lowE, lowV,  highE, highV) %>%
+
+   layout(scene = list(domain=list(x=c(0,0.5),y=c(0.5,1)),zaxis = list(title = "Ethnic Cluster")),
+         scene2 = list(domain=list(x=c(0.5,1),y=c(0.5,1))),
+         scene3 = list(domain=list(x=c(0,0.5),y=c(0,0.5))),
+         scene4 = list(domain=list(x=c(0.5,1),y=c(0,0.5)))
+         ) %>%
+
+  layout(annotations = list(
+  text = tt,
+  font = list(size = 18),
+  xref = "paper",
+  yref = "paper",
+  yanchor = "bottom",
+  xanchor = "center",
+  align = "center",
+  x = 0.5,
+  y = 1,
+  showarrow = FALSE
 )
 
-   ###
+) %>%
+  layout(annotations = list(
+  text = "High Randomness",
+  font = list(size = 15),
+  xref = "paper",
+  yref = "paper",
+  yanchor = "bottom",
+  xanchor = "center",
+  align = "center",
+  x = 0.5,
+  y = 0.5,
+  showarrow = FALSE
+))%>%
+  layout(annotations = list(
+  text = "Low Randomness",
+  font = list(size = 15),
+  xref = "paper",
+  yref = "paper",
+  yanchor = "bottom",
+  xanchor = "center",
+  align = "center",
+  x = 0.5,
+  y = 0,
+  showarrow = FALSE
+)
 
-high <- plot_ly(df_high)  %>% add_trace(x=df_high$fraction_blue,y=df_high$circle_orange,z=df_high$de_sq_bl,color= df_high$et_sq_bl,
-                                       type="scatter3d",
-                                       mode="markers",
-                                       marker = list( colorscale = 'Reds', showscale = T))  %>%
-  add_trace(x=df_high$fraction_blue,y=df_high$circle_orange,z=df_high$dv_sq_bl,color= df_high$vl_sq_bl,
-              type="scatter3d",
-                                       mode="markers",
-                                      marker = list( colorscale = 'Greens', showscale = TRUE))  %>%
-  layout(legend = list(orientation = 'h'),
-         title="high",
-         scene = list(
-      xaxis = list(title = "Ethnic Ratio",range=seq(50,90,by=10),dtick=10),
-      yaxis = list(title = "% Liberal Minority",autorange = "reversed"),
-      zaxis = list(title = "Cluster")))
-
-low
-high
-
-```
-
-```{r 3Dsimple, fig.cap="3D pictures", echo = FALSE}
-
-excl3D <- names(df_fin) %in% c("run", "density","step")
-df_fin <- df_fin[!excl3D] %>% group_by(eth_con_loc, eth_con_min,eth_lib_loc,eth_lib_min,val_lib_loc,val_lib_min,val_con_loc,val_con_min,circle_orange,circle_blue,fraction_blue) %>% summarise_all(mean)
-
-vars <- c("de_sq_or","dv_sq_or","et_sq_or","vl_sq_or")
-df_sqbl <- cbind(df_fin[,1:11],df_fin[,vars]) %>% filter(val_lib_loc==5,val_lib_min==5,eth_con_loc == 5,eth_con_min == 5)
-df_high <- cbind(df_fin[,1:11],df_fin[,vars]) %>% filter(val_lib_loc==20,val_lib_min==20,eth_con_loc == 20,eth_con_min == 20)
-
-low <- plot3D::scatter3D(x = df_sqbl$fraction_blue, y = df_sqbl$circle_orange, z = df_sqbl$de_sq_or, colvar = df_sqbl$et_sq_or, col = ramp.col (col = c("grey", "blue"), n = 100, alpha = 1), pch=20, cex= 2, phi = 0)
+)
+}
 

### 2021-06-17 additional.Rmd
code to simplify and merge

@@
 exclet <- names(df_sec) %in% c("run", "density","step")
-
 df_sec <- df_sec[!exclet] %>% group_by(ID,RND,eth_con_loc,eth_con_min,eth_lib_loc,eth_lib_min,val_lib_loc,val_lib_min,val_con_loc,val_con_min,circle_orange,circle_blue,fraction_blue) %>% summarise_all(mean)
@@
 
-```
-
+df_etlib <- read.csv("df_etlib_all.csv",sep=",")
+excl <- names(df_etlib) %in% c("run", "density","step")
+df_etlib <- df_etlib[!excl] %>% group_by(ID,eth_con_loc,eth_con_min,eth_lib_loc,eth_lib_min,val_lib_loc,val_lib_min,val_con_loc,val_con_min,circle_orange,circle_blue,fraction_blue) %>% summarise_all(mean)
+
+df_3Do <- read.csv("3D_old.csv",sep=",")
+excl3D <- names(df_3Do) %in% c("run", "density","step")
+df_3Do <- df_3Do[!excl3D] %>% group_by(eth_con_loc, eth_con_min,eth_lib_loc,eth_lib_min,val_lib_loc,val_lib_min,val_con_loc,val_con_min,circle_orange,circle_blue,fraction_blue) %>% summarise_all(mean)
+
+```
+
+# Between the 2 baseline: decide!
 ```{r asym_baseline, fig.cap="Fig. 8 orig", echo = FALSE}
+# Effect of ethnic asymmetry: all beta dominant equal
 
@@
 
-df <- df %>% filter(df$dominant <= 15) 
-df <- df %>% filter(df$fraction_blue==50|df$fraction_blue==60|df$fraction_blue==80)
+# df <- df %>% filter(df$dominant <= 15) 
+# df <- df %>% filter(df$fraction_blue==50|df$fraction_blue==60|df$fraction_blue==80)
 
@@
 
+# Sensitivity to value liberal locals , while the others are keep 20
+
 sa_asym <- read.csv("df_sa_asym.csv",sep = ",")
@@
 
-majcons <- ggplotly(ggplot(data = df) + geom_point(aes(x=dominant,y=dv_sq_bl, colour = vl_sq_bl),shape = "circle")  + geom_line(aes(x=dominant,y=dv_sq_bl, linetype = as.factor(fraction_blue))) +
-           geom_point(aes(x=dominant,y=de_sq_bl, colour = et_sq_bl),shape="square") + geom_line(aes(x=dominant,y=de_sq_bl, linetype = as.factor(fraction_blue)))+ ggtitle("majcons"))
-
-majlib <- ggplotly(ggplot(data = df) + geom_point(aes(x=dominant,y=dv_cl_bl, colour = vl_cl_bl),shape = "circle")  + geom_line(aes(x=dominant,y=dv_cl_bl, linetype = as.factor(fraction_blue))) +
-           geom_point(aes(x=dominant,y=de_cl_bl, colour = et_cl_bl),shape="square") + geom_line(aes(x=dominant,y=de_cl_bl, linetype = as.factor(fraction_blue))) + ggtitle("majlib"))
-
-mincons <- ggplotly(ggplot(data = df) + geom_point(aes(x=dominant,y=dv_sq_or, colour = vl_sq_or),shape = "circle")  + geom_line(aes(x=dominant,y=dv_sq_or, linetype = as.factor(fraction_blue))) +
-           geom_point(aes(x=dominant,y=de_sq_or, colour = et_sq_or),shape="square") + geom_line(aes(x=dominant,y=de_sq_or, linetype = as.factor(fraction_blue))) + ggtitle("mincons"))
-
-minlib <- ggplotly(ggplot(data = df) + geom_point(aes(x=dominant,y=dv_cl_or, colour = vl_cl_or),shape = "circle")  + geom_line(aes(x=dominant,y=dv_cl_or, linetype = as.factor(fraction_blue))) +
-           geom_point(aes(x=dominant,y=de_cl_or, colour = et_cl_or),shape="square") + geom_line(aes(x=dominant,y=de_cl_or, linetype = as.factor(fraction_blue)))+ ggtitle("minlib"))
+majcons <-  ggplot(data = df) + geom_point(aes(x=dominant,y=dv_sq_bl, colour = vl_sq_bl),shape = "circle")  + geom_line(aes(x=dominant,y=dv_sq_bl, linetype = as.factor(fraction_blue))) +
+           geom_point(aes(x=dominant,y=de_sq_bl, colour = et_sq_bl),shape="square") + geom_line(aes(x=dominant,y=de_sq_bl, linetype = as.factor(fraction_blue)))+ ggtitle("majcons")
+
+majlib <-  ggplot(data = df) + geom_point(aes(x=dominant,y=dv_cl_bl, colour = vl_cl_bl),shape = "circle")  + geom_line(aes(x=dominant,y=dv_cl_bl, linetype = as.factor(fraction_blue))) +
+           geom_point(aes(x=dominant,y=de_cl_bl, colour = et_cl_bl),shape="square") + geom_line(aes(x=dominant,y=de_cl_bl, linetype = as.factor(fraction_blue))) + ggtitle("majlib")
+
+mincons <-  ggplot(data = df) + geom_point(aes(x=dominant,y=dv_sq_or, colour = vl_sq_or),shape = "circle")  + geom_line(aes(x=dominant,y=dv_sq_or, linetype = as.factor(fraction_blue))) +
+           geom_point(aes(x=dominant,y=de_sq_or, colour = et_sq_or),shape="square") + geom_line(aes(x=dominant,y=de_sq_or, linetype = as.factor(fraction_blue))) + ggtitle("mincons")
+
+minlib <-  ggplot(data = df) + geom_point(aes(x=dominant,y=dv_cl_or, colour = vl_cl_or),shape = "circle")  + geom_line(aes(x=dominant,y=dv_cl_or, linetype = as.factor(fraction_blue))) +
+           geom_point(aes(x=dominant,y=de_cl_or, colour = et_cl_or),shape="square") + geom_line(aes(x=dominant,y=de_cl_or, linetype = as.factor(fraction_blue)))+ ggtitle("minlib")
 
@@
 ```{r by-product_cons_original, fig.cap="Effect of liberals majority vs minority on value segregation conservatives", echo = FALSE}
-
+# It goes
 # ethnic and value segregation for each group in the annex
@@
 
-ggsave("lib_cons.jpg",plot=lib_cons)
-
-```
-
-```{r by-product ethnic cons, fig.cap="Effect of liberals majority vs minority on ethnic segregation conservatives", echo = FALSE}
-# Not interesting, goes in the annex
-
-# ethnic and value segregation for each group in the annex
-
-##### 
-# By-product value of conservatives by value preference liberals
-
-# Majority
-
-mech_cons <- mech %>% filter(fraction_blue == 50 | fraction_blue == 80) %>%  filter(val_lib_min==0 | val_lib_min==1 |val_lib_min==7) %>% gather(key=ethnics, value=Clust, de_sq_bl,de_sq_or)
-
-cons_maj_et <- ggplot(data = mech_cons, aes(x=val_lib_loc,y=Clust,color=  `ethnics`,linetype= as.factor(fraction_blue))) + geom_point(size=1.5, shape = "square") + geom_line() + 
-  facet_wrap(~val_lib_min,dir="v",labeller = labeller(val_lib_min = valueminority.labs)) +
-    scale_y_continuous(breaks= seq(0,5,by=0.5)) +
-  xlab("ß value liberal majority") + ylab("Spatial clustering") +
-  geom_hline(yintercept=1,color="red") +
-  scale_color_manual(values=c("blue","darkorange"),labels=c("Majority","Minority"),name="Ethnicity") +
-    scale_linetype_manual(values=c("solid","dashed"),labels=c("50%","80%"),name="% Majority") +
-   guides(color  = guide_legend(order = 1), linetype = guide_legend(order = 2)) +
-  theme_bw()
-
-# Minority
-
-mech_lib <- mech %>%  filter(fraction_blue == 50 | fraction_blue == 80) %>%  filter(val_lib_loc==0 | val_lib_loc==1 |val_lib_loc==7) %>% gather(key=ethnics, value=Cluste, de_sq_bl,de_sq_or)
-
-cons_min_et <- ggplot(data = mech_lib, aes(x=val_lib_min,y=Cluste,color=  `ethnics`,linetype= as.factor(fraction_blue))) + geom_point(size=1.5, shape = "square") + geom_line() + 
-  facet_wrap(~val_lib_loc,dir="v",labeller = labeller(val_lib_loc = valuemajority.labs)) +
-  xlab("ß value liberal minority") + ylab("Spatial clustering") +
-  scale_y_continuous(breaks= seq(0,5,by=0.5)) +
-  geom_hline(yintercept=1,color="red") +
-  scale_color_manual(values=c("blue","darkorange"),labels=c("Majority","Minority"),name="Ethnicity") +
-    scale_linetype_manual(values=c("solid","dashed"),labels=c("50%","80%"),name="% Majority") +
-   guides(color  = guide_legend(order = 1), linetype = guide_legend(order = 2)) +
- theme_bw()
-
-ggplotly(cons_maj_et)
-ggplotly(cons_min_et)
-
-lib_cons_et <- ggpubr::ggarrange(cons_maj_et,cons_min_et, common.legend = TRUE, legend = "bottom")
-
-#ggsave("lib_cons.jpg",plot=lib_cons)
-
+# ggsave("lib_cons.jpg",plot=lib_cons)
+ggpubr::annotate_figure(lib_cons,
+               top = "Effect of liberals majority vs minority on value segregation conservatives")
 ```
@@
 ```{r beta_maj, fig.cap="effect liberals one  dataset", echo = FALSE}
-
+# It goes
 #####
@@
     geom_hline(yintercept=1,color="red") +
+  guides(color = "black") +
       theme_bw() +
@@
 
-ggsave("lib_lib.jpg",plot=lib_lib)
-
-```
-
-```{r etlib_min, fig.cap="Ethnic preference majority or minority over liberals or conservatives minority", echo = FALSE}
-
-excl <- names(df_etlib) %in% c("run", "density","step")
-df_etlib <- df_etlib[!excl] %>% group_by(ID,eth_con_loc,eth_con_min,eth_lib_loc,eth_lib_min,val_lib_loc,val_lib_min,val_con_loc,val_con_min,circle_orange,circle_blue,fraction_blue) %>% summarise_all(mean)
-
-## Majority
-
-df_ethloc <- df_etlib %>% filter(ID == "etlib_loc") %>% filter(fraction_blue == 80) %>% gather(key = subgroup, value = Clustetmj, de_sq_or,dv_sq_or,de_cl_or,dv_cl_or) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"Ethnic" = c("de_sq_or","de_cl_or"), "Value" = c("dv_sq_or","dv_cl_or") ),"Ethnic"),
-              `orientation` = fct_relevel(fct_collapse(subgroup,"Conservative" = c("de_sq_or","dv_sq_or"), "Liberal" = c("de_cl_or","dv_cl_or")), "Conservative"))
-
-maj_min <- ggplot(data=df_ethloc,aes(x=eth_lib_loc,y = Clustetmj,linetype=`segregation`,shape = `orientation`)) + 
-  geom_point(size=1.5,color="orange") + geom_line(color="orange") +
-facet_wrap(~eth_lib_min,dir="v",labeller=labeller(eth_lib_min=ethnicminority.labs)) +
-  xlab("ß ethnic liberals majority") + ylab("Spatial Clustering") +
-  scale_y_continuous(breaks= seq(0,5,by=0.50)) +
-  scale_linetype_manual(values=c("solid","dashed"),labels=c("Ethnic","Value"),name="Segregation" ) +
-  scale_shape_manual(values=c("square","circle"),labels=c("Conservative","Liberal"),name="Orientation \n minority" ) +
- ggtitle("") +
-    geom_hline(yintercept=1,color="red") +
-      theme_bw() +
-  theme(plot.title = element_text(hjust = 0.5))
-
-ggplotly(maj_min)
-   maj_min
-## Minority
-
-df_ethmin <- df_etlib %>% filter(ID == "etlib_min") %>% filter(fraction_blue == 80) %>% gather(key = subgroup, value = Clustetmn, de_sq_or,dv_sq_or,de_cl_or,dv_cl_or) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"Ethnic" = c("de_sq_or","de_cl_or"), "Value" = c("dv_sq_or","dv_cl_or") ),"Ethnic"),
-              `orientation` = fct_relevel(fct_collapse(subgroup,"Conservative" = c("de_sq_or","dv_sq_or"), "Liberal" = c("de_cl_or","dv_cl_or")), "Conservative"))
-
-min_min <- ggplot(data=df_ethmin,aes(x=eth_lib_min,y = Clustetmn,linetype=`segregation`,shape = `orientation`)) + 
-  geom_point(size=1.5,color="orange") + geom_line(color="orange") +
-facet_wrap(~eth_lib_loc,dir="v",labeller=labeller(eth_lib_loc=ethnicmajority.labs)) +
-  xlab("ß ethnic liberals minority") + ylab("Spatial Clustering") +
-  scale_y_continuous(breaks= seq(0,5,by=0.50)) +
-  scale_linetype_manual(values=c("solid","dashed"),labels=c("Ethnic","Value"),name="Segregation" ) +
-  scale_shape_manual(values=c("square","circle"),labels=c("Conservative","Liberal"),name="Orientation \n minority" ) +
- ggtitle("") +
-    geom_hline(yintercept=1,color="red") +
-      theme_bw() +
-  theme(plot.title = element_text(hjust = 0.5))
-
-ggplotly(min_min)
-   min_min
-
-eth_lib_min <- ggpubr::ggarrange(maj_min,min_min, common.legend = TRUE, legend = "bottom")
-
-ggsave("eth_lib_min.jpg",plot=eth_lib_min)
-
-```
-
-```{r etlib_min_test fraction, fig.cap="Ethnic preference majority or minority over liberals or conservatives minority", echo = FALSE}
-
-df_etlib <- read.csv("df_etlib.csv",sep=",")
-
-excl <- names(df_etlib) %in% c("run", "density","step")
-df_etlib <- df_etlib[!excl] %>% group_by(ID,eth_con_loc,eth_con_min,eth_lib_loc,eth_lib_min,val_lib_loc,val_lib_min,val_con_loc,val_con_min,circle_orange,circle_blue,fraction_blue) %>% summarise_all(mean)
-
-## Majority
-
-df_ethloc <- df_etlib %>% filter(ID == "etlib_loc") %>% filter(fraction_blue == 50 | fraction_blue == 80) %>% gather(key = subgroup, value = Clustetmj, de_sq_or,dv_sq_or,de_cl_or,dv_cl_or) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"Ethnic" = c("de_sq_or","de_cl_or"), "Value" = c("dv_sq_or","dv_cl_or") ),"Ethnic"),
-              `orientation` = fct_relevel(fct_collapse(subgroup,"Conservative" = c("de_sq_or","dv_sq_or"), "Liberal" = c("de_cl_or","dv_cl_or")), "Conservative"))
-
-df_ethloc <- df_etlib %>% filter(ID == "etlib_loc") %>% filter(fraction_blue == 50 | fraction_blue == 80) %>%  filter(eth_lib_min==0 | eth_lib_min==1 |eth_lib_min==7) %>% gather(key = segregation, value = Clustmj, de_cl_bl, dv_cl_bl)
-
-librmj <- ggplot(data=df_ethloc,aes(x=eth_lib_loc,y = Clustmj,shape=`segregation`,linetype=as.factor(fraction_blue))) + 
-  geom_point(size=1.5,color="blue") + geom_line(color="blue") +
-facet_wrap(~eth_lib_min,dir="v",labeller=labeller(eth_lib_min=ethnicminority.labs)) +
-  xlab("ß ethnic liberals majority") + ylab("Spatial Clustering") +
-  scale_y_continuous(breaks= seq(0,2,by=0.25)) +
-  scale_linetype_manual(values=c("solid","dashed"),labels=c("50%","80%"),name="% Majority" ) +
-  scale_shape_manual(values=c("square","circle"),labels=c("Ethnic","Value"),name="Segregation" ) +
- ggtitle("Liberals Majority") +
-    geom_hline(yintercept=1,color="red") +
-      theme_bw() +
-  theme(plot.title = element_text(hjust = 0.5))
-
-df_etmin <- df_etlib %>% filter(ID == "etlib_min") %>% filter(fraction_blue == 50 | fraction_blue == 80) %>%  filter(eth_lib_loc==0 | eth_lib_loc==1 |eth_lib_loc==7) %>% gather(key = segregation, value = Clustmn, de_cl_or, dv_cl_or)
-
-librmn <- ggplot(data=df_etmin,aes(x=eth_lib_min,y = Clustmn,shape=`segregation`,linetype=as.factor(fraction_blue))) + 
-  geom_point(size=1.5,color="orange") + geom_line(color="orange") +
-facet_wrap(~eth_lib_loc,dir="v",labeller=labeller(eth_lib_loc=ethnicmajority.labs)) +
- scale_y_continuous(breaks= seq(0,2,by=0.25)) +
-  xlab("ß ethnic liberals minority") + ylab("Spatial Clustering") +
-    scale_linetype_manual(values=c("solid","dashed"),labels=c("50%","80%"),name="% Majority") +
-  scale_shape_manual(values=c("square","circle"),labels=c("Ethnic","Value"),name="Segregation") +
-    geom_hline(yintercept=1,color="red") +
-    guides(  linetype = guide_legend(order = 1), shape = guide_legend(order = 2)) +
- #  guides(color=FALSE) + 
-    ggtitle("Liberals Minority") +
-    geom_hline(yintercept=1,color="red") +
-      theme_bw() +
-  theme(plot.title = element_text(hjust = 0.5))
-
-ggplotly(librmj)
-ggplotly(librmn)
-
-lib_lib_ethnic <- ggpubr::ggarrange(librmj,librmn, common.legend = TRUE, legend = "bottom")
-
+lib_lib
 # ggsave("lib_lib.jpg",plot=lib_lib)
@@
 
-```{r etlib_maj, fig.cap="Ethnic preference majority or minority over liberals or conservatives majority", echo = FALSE}
-
-## Majority
-
-df_ethloc_maj <- df_etlib %>% filter(ID == "etlib_loc") %>% filter(fraction_blue == 80) %>% gather(key = subgroup, value = Clustetmj, de_sq_bl,dv_sq_bl,de_cl_bl,dv_cl_bl) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"Ethnic" = c("de_sq_bl","de_cl_bl"), "Value" = c("dv_sq_bl","dv_cl_bl") ),"Ethnic"),
-              `orientation` = fct_relevel(fct_collapse(subgroup,"Conservative" = c("de_sq_bl","dv_sq_bl"), "Liberal" = c("de_cl_bl","dv_cl_bl")), "Conservative"))
-
-maj_maj <- ggplot(data=df_ethloc_maj,aes(x=eth_lib_loc,y = Clustetmj,linetype=`segregation`,shape = `orientation`)) + 
-  geom_point(size=1.5,color="blue") + geom_line(color="blue") +
-facet_wrap(~eth_lib_min,dir="v",labeller=labeller(eth_lib_min=ethnicminority.labs)) +
-  xlab("ß ethnic liberals majority") + ylab("Spatial Clustering") +
-  scale_y_continuous(breaks= seq(0,5,by=0.50)) +
-  scale_linetype_manual(values=c("solid","dashed"),labels=c("Ethnic","Value"),name="Segregation" ) +
-  scale_shape_manual(values=c("square","circle"),labels=c("Conservative","Liberal"),name="Orientation \n majority" ) +
- ggtitle("") +
-    geom_hline(yintercept=1,color="red") +
-      theme_bw() +
-  theme(plot.title = element_text(hjust = 0.5))
-
-ggplotly(maj_maj)
-   maj_maj
-## Minority
-
-df_ethmin_maj <- df_etlib %>% filter(ID == "etlib_min") %>% filter(fraction_blue == 80) %>% gather(key = subgroup, value = Clustetmn, de_sq_bl,dv_sq_bl,de_cl_bl,dv_cl_bl) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"Ethnic" = c("de_sq_bl","de_cl_bl"), "Value" = c("dv_sq_bl","dv_cl_bl") ),"Ethnic"),
-              `orientation` = fct_relevel(fct_collapse(subgroup,"Conservative" = c("de_sq_bl","dv_sq_bl"), "Liberal" = c("de_cl_bl","dv_cl_bl")), "Conservative"))
-
-min_maj <- ggplot(data=df_ethmin_maj,aes(x=eth_lib_min,y = Clustetmn,linetype=`segregation`,shape = `orientation`)) + 
-  geom_point(size=1.5,color="blue") + geom_line(color="blue") +
-facet_wrap(~eth_lib_loc,dir="v",labeller=labeller(eth_lib_loc=ethnicmajority.labs)) +
-  xlab("ß ethnic liberals minority") + ylab("Spatial Clustering") +
-  scale_y_continuous(breaks= seq(0,5,by=0.50)) +
-  scale_linetype_manual(values=c("solid","dashed"),labels=c("Ethnic","Value"),name="Segregation" ) +
-  scale_shape_manual(values=c("square","circle"),labels=c("Conservative","Liberal"),name="Orientation \n majority" ) +
- ggtitle("") +
-    geom_hline(yintercept=1,color="red") +
-      theme_bw() +
-  theme(plot.title = element_text(hjust = 0.5))
-
-ggplotly(min_maj)
-   min_maj
-
-eth_lib_maj <- ggpubr::ggarrange(maj_maj,min_maj, common.legend = TRUE, legend = "bottom")
-
-ggsave("eth_lib_maj.jpg",plot=eth_lib_maj)
-
-```
-
-```{r sec_not_rel, fig.cap="Value conservativess and ethnic liberal not primary", echo = FALSE}
-
-df <- df_sec  %>%  gather(key= subgroup, value = Prox, de_sq_bl, dv_sq_bl, de_cl_bl, dv_cl_bl, de_sq_or, dv_sq_or, de_cl_or, dv_cl_or) %>% mutate(  `segregation` = fct_relevel(fct_collapse(subgroup,"ethnics" = c("de_sq_bl","de_cl_bl","de_sq_or","de_cl_or"), "values" = c("dv_sq_bl","dv_cl_bl","dv_sq_or","dv_cl_or")),"ethnics"),
- `orientation` = fct_relevel(fct_collapse(subgroup, "conservative" = c("de_sq_bl","dv_sq_bl","de_sq_or","dv_sq_or"), "liberal" = c("de_cl_bl","dv_cl_bl","de_cl_or","dv_cl_or")),"conservative" ), 
- `ethnia` = fct_relevel(fct_collapse(subgroup, "local" = c("de_sq_bl","dv_sq_bl","de_cl_bl","dv_cl_bl"),"minority" = c("de_sq_or","dv_sq_or","de_cl_or","dv_cl_or")), "local"))
-
-dflow <- df %>% filter(ID == "valuecon_min" & fraction_blue == 80) %>% filter(RND == "low")
-dfh <- df %>% filter(ID == "valuecon_min" & fraction_blue == 80) %>% filter(RND == "high")
-
-low <- ggplot(data=dflow, aes(x=dflow$val_con_min,y=Prox, linetype = `segregation` , fill = `ethnia`,  shape = `orientation`))  +  geom_point(size= 1.5) +
-  geom_line(aes(color = `ethnia`)) + 
-  facet_wrap(~  dflow$val_con_loc) +
-  ggtitle("Low randomness") + 
-   scale_linetype_manual(values=c("solid","dashed"), labels = c("ethnic","value"), guide = guide_legend(title = "Segregation", order = 1)) +
-  scale_fill_manual(values = c("blue","darkorange")) + 
- scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
-  scale_shape_manual(values = c(22,21), guide = guide_legend(title="Value" ,override.aes = list(size = 3), order = 3)) +
-  guides(fill  = FALSE)
-
-high <- ggplot(data=dfh, aes(x=dfh$val_con_min,y=Prox, linetype = `segregation` , fill = `ethnia`,  shape = `orientation`))  +  geom_point(size= 1.5) +
-  geom_line(aes(color = `ethnia`)) + 
-  facet_wrap(~  dfh$val_con_loc) +
-  ggtitle("High randomness") + 
-   scale_linetype_manual(values=c("solid","dashed"), labels = c("ethnic","value"), guide = guide_legend(title = "Segregation", order = 1)) +
-  scale_fill_manual(values = c("blue","darkorange")) + 
- scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
-  scale_shape_manual(values = c(22,21), guide = guide_legend(title="Value" ,override.aes = list(size = 3), order = 3)) +
-  guides(fill  = FALSE)
-
-cmp <- ggpubr::ggarrange(low,high,common.legend = T)
-
-```
-
-```{r sec_test, fig.cap="Value conservativess and ethnic liberal not primary", echo = FALSE}
-
-# pref <- names(df_sec) %in% c("eth_con_loc", "eth_con_min","val_loc_lib")
-
-etlblc_high <- df_sec  %>% filter(fraction_blue == 80) %>% filter(ID == "etlib_loc", RND == "high", eth_lib_loc == 5 | eth_lib_loc == 0) %>% filter(eth_lib_min == 0) %>% gather(key = subgroup, value = Clus, de_sq_bl,dv_sq_bl,de_cl_bl,dv_cl_bl,de_sq_or,dv_sq_or,de_cl_or,dv_cl_or)
-
-etlblc_high_pic <- ggplot(etlblc_high, aes(fill = as.factor(etlblc_high$eth_lib_loc), y= etlblc_high$Clus, x = etlblc_high$subgroup) ) + 
-    geom_bar(position="dodge", stat="identity") +
-  scale_fill_manual(values=c("red","blue")) +
-  scale_y_continuous(limits= c(0,6),breaks=seq(0,6,by=0.5))
-
-etlblc_low <- df_sec  %>% filter(fraction_blue == 80) %>% filter(ID == "etlib_loc", RND == "low", eth_lib_loc == 20 | eth_lib_loc == 0) %>% filter(eth_lib_min == 0) %>% gather(key = subgroup, value = Clus, de_sq_bl,dv_sq_bl,de_cl_bl,dv_cl_bl,de_sq_or,dv_sq_or,de_cl_or,dv_cl_or)
-
-etlblc_low_pic <- ggplot(etlblc_low, aes(fill = as.factor(etlblc_low$eth_lib_loc), y= etlblc_low$Clus, x = etlblc_low$subgroup) ) + 
-    geom_bar(position="dodge", stat="identity") +
-  scale_fill_manual(values=c("red","blue")) +
-  scale_y_continuous(limits= c(0,6),breaks=seq(0,6,by=0.5))
-
-etlbmn_high <- df_sec  %>% filter(fraction_blue == 80) %>% filter(ID == "etlib_min", RND == "high", eth_lib_min == 5 | eth_lib_min == 0) %>% filter(eth_lib_loc == 0) %>% gather(key = subgroup, value = Clus, de_sq_bl,dv_sq_bl,de_cl_bl,dv_cl_bl,de_sq_or,dv_sq_or,de_cl_or,dv_cl_or)
-
-etlbmn_high_pic <- ggplot(etlbmn_high, aes(fill = as.factor(etlbmn_high$eth_lib_min), y= etlbmn_high$Clus, x = etlbmn_high$subgroup) ) + 
-    geom_bar(position="dodge", stat="identity") +
-  scale_fill_manual(values=c("red","blue")) +
-  scale_y_continuous(limits= c(0,6),breaks=seq(0,6,by=0.5))
-
-etlbmn_low <- df_sec  %>% filter(fraction_blue == 80) %>% filter(ID == "etlib_min", RND == "low", eth_lib_min == 20 | eth_lib_min == 0) %>% filter(eth_lib_loc == 0) %>% gather(key = subgroup, value = Clus, de_sq_bl,dv_sq_bl,de_cl_bl,dv_cl_bl,de_sq_or,dv_sq_or,de_cl_or,dv_cl_or)
-
-etlbmn_low_pic <- ggplot(etlbmn_low, aes(fill = as.factor(etlbmn_low$eth_lib_min), y= etlbmn_low$Clus, x = etlbmn_low$subgroup) ) + 
-    geom_bar(position="dodge", stat="identity") +
-  scale_fill_manual(values=c("red","blue")) +
-  scale_y_continuous(limits= c(0,6),breaks=seq(0,6,by=0.5))
-
-vlcnlc_low <- df_sec  %>% filter(fraction_blue == 80) %>% filter(ID == "valuecon_loc", RND == "low", val_con_loc == 20 | val_con_loc == 0) %>% filter(val_con_min == 0) %>% gather(key = subgroup, value = Clus, de_sq_bl,dv_sq_bl,de_cl_bl,dv_cl_bl,de_sq_or,dv_sq_or,de_cl_or,dv_cl_or)
-
-vlcnlc_low_pic <- ggplot(vlcnlc_low, aes(fill = as.factor(vlcnlc_low$val_con_loc), y= vlcnlc_low$Clus, x = vlcnlc_low$subgroup) ) + 
-    geom_bar(position="dodge", stat="identity") +
-  scale_fill_manual(values=c("red","blue")) +
-  scale_y_continuous(limits= c(0,6),breaks=seq(0,6,by=0.5))
-
-vlcnlc_high <- df_sec  %>% filter(fraction_blue == 80) %>% filter(ID == "valuecon_loc", RND == "high", val_con_loc == 5 | val_con_loc == 0) %>% filter(val_con_min == 0) %>% gather(key = subgroup, value = Clus, de_sq_bl,dv_sq_bl,de_cl_bl,dv_cl_bl,de_sq_or,dv_sq_or,de_cl_or,dv_cl_or)
-
-vlcnlc_high_pic <- ggplot(vlcnlc_high, aes(fill = as.factor(vlcnlc_high$val_con_loc), y= vlcnlc_high$Clus, x = vlcnlc_high$subgroup) ) + 
-    geom_bar(position="dodge", stat="identity") +
-  scale_fill_manual(values=c("red","blue")) +
-  scale_y_continuous(limits= c(0,6),breaks=seq(0,6,by=0.5))
-
-vlcnmn_low <- df_sec  %>% filter(fraction_blue == 80) %>% filter(ID == "valuecon_min", RND == "low", val_con_min == 20 | val_con_min == 0) %>% filter(val_con_loc == 0) %>% gather(key = subgroup, value = Clus, de_sq_bl,dv_sq_bl,de_cl_bl,dv_cl_bl,de_sq_or,dv_sq_or,de_cl_or,dv_cl_or)
-
-vlcnmn_low_pic <- ggplot(vlcnmn_low, aes(fill = as.factor(vlcnmn_low$val_con_min), y= vlcnmn_low$Clus, x = vlcnmn_low$subgroup) ) + 
-    geom_bar(position="dodge", stat="identity") +
-  scale_fill_manual(values=c("red","blue")) +
-  scale_y_continuous(limits= c(0,6),breaks=seq(0,6,by=0.5))
-
-vlcnmn_high <- df_sec  %>% filter(fraction_blue == 80) %>% filter(ID == "valuecon_min", RND == "high", val_con_min == 5 | val_con_min == 0) %>% filter(val_con_loc == 0) %>% gather(key = subgroup, value = Clus, de_sq_bl,dv_sq_bl,de_cl_bl,dv_cl_bl,de_sq_or,dv_sq_or,de_cl_or,dv_cl_or)
-
-vlcnmn_high_pic <- ggplot(vlcnmn_high, aes(fill = as.factor(vlcnmn_high$val_con_min), y= vlcnmn_high$Clus, x = vlcnmn_high$subgroup) ) + 
-    geom_bar(position="dodge", stat="identity") +
-  scale_fill_manual(values=c("red","blue")) +
-  scale_y_continuous(limits= c(0,6),breaks=seq(0,6,by=0.5))
-
-ggplotly(etlblc_high_pic)
-ggplotly(etlblc_low_pic)
-ggplotly(etlbmn_high_pic)
-ggplotly(etlbmn_low_pic)
-ggplotly(vlcnlc_low_pic)
-ggplotly(vlcnlc_high_pic)
-ggplotly(vlcnmn_low_pic)
-ggplotly(vlcnmn_high_pic)
-
-```
-
-```{r 3D, fig.cap="3D pictures", echo = FALSE}
-
-df_3D_low <- df_3D %>% filter(val_lib_loc==5,val_lib_min==5,eth_con_loc == 5,eth_con_min == 5,eth_lib_loc ==0,eth_lib_min==0) 
-df_3D_high <- df_3D %>% filter(val_lib_loc==20,val_lib_min==20,eth_con_loc == 20,eth_con_min == 20,eth_lib_loc ==0,eth_lib_min==0)
+```{r 3D_table, fig.cap="Each grouptype, distribution liberals faceted by ethnic ratio", echo = FALSE}
+
+df_fin <- df_3D %>% mutate(RND = case_when(
+  val_lib_loc==5 & val_lib_min==5 & eth_con_loc == 5 & eth_con_min == 5 ~ "H",
+  val_lib_loc==20 & val_lib_min==20 & eth_con_loc == 20 & eth_con_min == 20 ~ "L"
+))
+
+cmj <- subset(df_fin, eth_lib_loc ==0 & eth_lib_min == 0) %>% gather(subgroup, Segra, de_sq_bl,dv_sq_bl) %>% ggplot(aes(x=circle_orange,y=Segra,shape = subgroup, color = RND)) + geom_point() + geom_line() +
+  scale_color_manual(values = c("green","purple"),labels = c("high","low"), guide = guide_legend(title = "Randomness")) + 
+  scale_shape_manual(values = c("square","circle"),labels = c("ethnic","Value"), guide = guide_legend(title = "Segregation")) + 
+ scale_x_discrete(limits = seq(10,90 ,by = 10)) +
+  facet_wrap(~ fraction_blue, nrow = 1) +
+  ggtitle("Conservative majority") +
+  theme_bw()
+
+lb <- subset(df_fin, eth_lib_loc ==0 & eth_lib_min == 0) %>% gather(subgroup, Segra, de_cl_bl,dv_cl_bl) %>% ggplot(aes(x=circle_orange,y=Segra,shape = subgroup, color = RND)) + geom_point() + geom_line() +
+  scale_color_manual(values = c("green","purple"),labels = c("high","low"), guide = guide_legend(title = "Randomness")) + 
+  scale_shape_manual(values = c("square","circle"),labels = c("ethnic","Value"), guide = guide_legend(title = "Segregation")) + 
+ scale_x_discrete(limits = seq(10,90 ,by = 10)) +
+  facet_wrap(~ fraction_blue, nrow = 1) +
+  ggtitle("Liberals majority") +
+  theme_bw()
+
+cm <- subset(df_fin, eth_lib_loc ==0 & eth_lib_min == 0) %>% gather(subgroup, Segra, de_sq_or,dv_sq_or) %>% ggplot(aes(x=circle_orange,y=Segra,shape = subgroup, color = RND)) + geom_point() + geom_line() +
+  scale_color_manual(values = c("green","purple"),labels = c("high","low"), guide = guide_legend(title = "Randomness")) + 
+  scale_shape_manual(values = c("square","circle"),labels = c("ethnic","Value"), guide = guide_legend(title = "Segregation")) + 
+ scale_x_discrete(limits = seq(10,90 ,by = 10)) +
+  facet_wrap(~ fraction_blue, nrow = 1) +
+  ggtitle("Conservative minority") +
+  theme_bw()
+
+lm <- subset(df_fin, eth_lib_loc ==0 & eth_lib_min == 0) %>% gather(subgroup, Segra, de_cl_or,dv_cl_or) %>% ggplot(aes(x=circle_orange,y=Segra,shape = subgroup, color = RND)) + geom_point() + geom_line() +
+  scale_color_manual(values = c("green","purple"),labels = c("high","low"), guide = guide_legend(title = "Randomness")) + 
+  scale_shape_manual(values = c("square","circle"),labels = c("ethnic","Value"), guide = guide_legend(title = "Segregation")) + 
+ scale_x_discrete(limits = seq(10,90 ,by = 10)) +
+  facet_wrap(~ fraction_blue, nrow = 1) +
+  ggtitle("Liberals minority") +
+  theme_bw()
+
+```
+
+# Increase ethnic
+
+We only look at the behavior of liberals, as conservatives have minimal consequence. Combining the two plots looked awful
+
+```{r et_liberals, fig.cap="OK Effect of ethnic liberals majority vs minority on liberals", echo = FALSE}
+
+# etlib_maj <- df_etlib %>% filter(fraction_blue == 50 | fraction_blue == 80) %>% filter(eth_con_loc == 20 & eth_con_min == 20) %>% filter(val_con_loc == 0 & val_con_min == 0) %>% filter(eth_lib_min == 0)
+
+etlib_maj <- df_sec %>% filter(fraction_blue == 50 | fraction_blue == 80)  %>% gather(key = subgroup, value = Clustetmj, de_cl_bl,dv_cl_bl,de_cl_or,dv_cl_or) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"Ethnic" = c("de_cl_bl","de_cl_or"), "Value" = c("dv_cl_bl","dv_cl_or") ),"Ethnic"),
+              `ethnicity` = fct_relevel(fct_collapse(subgroup,"Liberals Majority" = c("de_cl_bl","dv_cl_bl"), "Liberals Minority" = c("de_cl_or","dv_cl_or")), "Liberals Majority")) # %>% filter(eth_lib_min == 0)
+
+# data_maj = etlib_maj[which(etlib_maj$ID == "etlib_loc" & etlib_maj$eth_lib_min == 0),]
+
+libmaj <-  ggplot(data =  etlib_maj[which(etlib_maj$ID == "etlib_loc" & etlib_maj$eth_lib_min == 0 & etlib_maj$eth_con_loc == 20  & etlib_maj$eth_con_min == 20 & etlib_maj$val_con_loc ==0 & etlib_maj$val_con_min == 0),], aes(x= eth_lib_loc,y = Clustetmj,linetype= as.factor(fraction_blue), shape =`segregation`,color = `ethnicity`) ) +
+  geom_point(size=2) + geom_line() +
+  facet_wrap(~`ethnicity`, dir = "v") +
+   scale_color_manual(values = c("blue","orange"), name = "Ethnicity") +
+  scale_shape_manual(values = c("square","circle"), name = "Segregation") +
+   scale_linetype_manual(values = c("solid","dashed"), labels = c("50%","80%"), name = "% Majority") +
+  xlab("ß ethnic liberals majority") +
+  ylab("Spatial Clustering") +
+  labs(caption = "ß ethnic liberals minority = 0") + theme_bw() +
+  guides(color = FALSE) +
+  theme(plot.caption = element_text(hjust = 0.5))
+
+libmin <-  ggplot(data = etlib_maj[which(etlib_maj$ID == "etlib_min" & etlib_maj$eth_lib_loc == 0 & etlib_maj$eth_con_loc == 20  & etlib_maj$eth_con_min == 20 & etlib_maj$val_con_loc ==0 & etlib_maj$val_con_min == 0),], aes(x= eth_lib_min,y = Clustetmj,linetype= as.factor(fraction_blue), shape =`segregation`,color = `ethnicity`) ) +
+  geom_point(size=2) + geom_line() + 
+  facet_wrap(~`ethnicity`, dir = "v") +
+   scale_color_manual(values = c("blue","orange"), name = "Ethnicity") + 
+  scale_shape_manual(values = c("square","circle"), name = "Segregation") + 
+   scale_linetype_manual(values = c("solid","dashed"), labels = c("50%","80%"), name = "% Majority") +
+  xlab("ß ethnic liberals minority") +
+  ylab("Spatial Clustering") +
+  labs(caption = "ß ethnic liberals majority = 0") + theme_bw() +
+  guides(color = FALSE) +
+  theme(plot.caption = element_text(hjust = 0.5))
+
+ggpubr::ggarrange(libmaj,libmin, common.legend = TRUE, legend = "bottom")
+
+# high randomness
+
+# libmaj_h <-  ggplot(data =  etlib_maj[which(etlib_maj$ID == "etlib_loc" & etlib_maj$eth_lib_min == 0 & etlib_maj$eth_con_loc == 5  & etlib_maj$eth_con_min == 5 & etlib_maj$val_con_loc ==0 & etlib_maj$val_con_min == 0),], aes(x= eth_lib_loc,y = Clustetmj,linetype= as.factor(fraction_blue), shape =`segregation`,color = `ethnicity`) ) +
+#   geom_point(size=2) + geom_line() +
+#   facet_wrap(~`ethnicity`, dir = "v") +
+#    scale_color_manual(values = c("blue","orange"), name = "Ethnicity") +
+#   scale_shape_manual(values = c("square","circle"), name = "Segregation") +
+#    scale_linetype_manual(values = c("solid","dashed"), labels = c("50%","80%"), name = "% Majority") +
+#   xlab("ß ethnic liberals majority") +
+#   ylab("Spatial Clustering") +
+#   labs(caption = "ß ethnic liberals minority = 0") + theme_bw() +
+#   guides(color = FALSE) +
+#   theme(plot.caption = element_text(hjust = 0.5))
+# 
+# libmin_h <-  ggplot(data = etlib_maj[which(etlib_maj$ID == "etlib_min" & etlib_maj$eth_lib_loc == 0 & etlib_maj$eth_con_loc == 5  & etlib_maj$eth_con_min == 5 & etlib_maj$val_con_loc ==0 & etlib_maj$val_con_min == 0),], aes(x= eth_lib_min,y = Clustetmj,linetype= as.factor(fraction_blue), shape =`segregation`,color = `ethnicity`) ) +
+#   geom_point(size=2) + geom_line() + 
+#   facet_wrap(~`ethnicity`, dir = "v") +
+#    scale_color_manual(values = c("blue","orange"), name = "Ethnicity") + 
+#   scale_shape_manual(values = c("square","circle"), name = "Segregation") + 
+#    scale_linetype_manual(values = c("solid","dashed"), labels = c("50%","80%"), name = "% Majority") +
+#   xlab("ß ethnic liberals minority") +
+#   ylab("Spatial Clustering") +
+#   labs(caption = "ß ethnic liberals majority = 0") + theme_bw() +
+#   guides(color = FALSE) +
+#   theme(plot.caption = element_text(hjust = 0.5))
+# 
+# 
+# ggpubr::ggarrange(libmaj_h,libmin_h, common.legend = TRUE, legend = "bottom")
+
+```
+
+```{r Ethnic liberals, fig.cap="Each grouptype, distribution liberals faceted by ethnic ratio", echo = FALSE}
+
+df_fin <- df_3D %>% mutate(RND = case_when(
+  val_lib_loc==5 & val_lib_min==5 & eth_con_loc == 5 & eth_con_min == 5 ~ "H",
+  val_lib_loc==20 & val_lib_min==20 & eth_con_loc == 20 & eth_con_min == 20 ~ "L"
+))
+
+subset(df_fin, eth_lib_loc != 0 & eth_lib_min != 0) %>% gather(subgroup, Segra, de_sq_bl,dv_sq_bl) %>% ggplot(aes(x=circle_orange,y=Segra,shape = subgroup, color = RND)) + geom_point() + geom_line() +
+  scale_color_manual(values = c("green","purple"),labels = c("high","low"), guide = guide_legend(title = "Randomness")) + 
+  scale_shape_manual(values = c("square","circle"),labels = c("ethnic","Value"), guide = guide_legend(title = "Segregation")) + 
+ scale_x_discrete(limits = seq(10,90 ,by = 10)) +
+  facet_wrap(~ fraction_blue, nrow = 1) +
+  ggtitle("Conservative majority") +
+  theme_bw()
+
+subset(df_fin, eth_lib_loc != 0 & eth_lib_min != 0) %>% gather(subgroup, Segra, de_cl_bl,dv_cl_bl) %>% ggplot(aes(x=circle_orange,y=Segra,shape = subgroup, color = RND)) + geom_point() + geom_line() +
+  scale_color_manual(values = c("green","purple"),labels = c("high","low"), guide = guide_legend(title = "Randomness")) + 
+  scale_shape_manual(values = c("square","circle"),labels = c("ethnic","Value"), guide = guide_legend(title = "Segregation")) + 
+ scale_x_discrete(limits = seq(10,90 ,by = 10)) +
+  facet_wrap(~ fraction_blue, nrow = 1) +
+  ggtitle("Liberals majority") +
+  theme_bw()
+
+subset(df_fin, eth_lib_loc != 0 & eth_lib_min != 0)  %>% gather(subgroup, Segra, de_sq_or,dv_sq_or) %>% ggplot(aes(x=circle_orange,y=Segra,shape = subgroup, color = RND)) + geom_point() + geom_line() +
+  scale_color_manual(values = c("green","purple"),labels = c("high","low"), guide = guide_legend(title = "Randomness")) + 
+  scale_shape_manual(values = c("square","circle"),labels = c("ethnic","Value"), guide = guide_legend(title = "Segregation")) + 
+ scale_x_discrete(limits = seq(10,90 ,by = 10)) +
+  facet_wrap(~ fraction_blue, nrow = 1) +
+  ggtitle("Conservative minority") +
+  theme_bw()
+
+subset(df_fin, eth_lib_loc != 0 & eth_lib_min != 0) %>% gather(subgroup, Segra, de_cl_or,dv_cl_or) %>% ggplot(aes(x=circle_orange,y=Segra,shape = subgroup, color = RND)) + geom_point() + geom_line() +
+  scale_color_manual(values = c("green","purple"),labels = c("high","low"), guide = guide_legend(title = "Randomness")) + 
+  scale_shape_manual(values = c("square","circle"),labels = c("ethnic","Value"), guide = guide_legend(title = "Segregation")) + 
+ scale_x_discrete(limits = seq(10,90 ,by = 10)) +
+  facet_wrap(~ fraction_blue, nrow = 1) +
+  ggtitle("Liberals minority") +
+  theme_bw()
+
+```
+
+```{r Ethnic liberalsT, fig.cap="Each grouptype, distribution liberals faceted by ethnic ratio", echo = FALSE}
+
+df_fin <- df_3D %>% mutate(RND = case_when(
+  val_lib_loc==5 & val_lib_min==5 & eth_con_loc == 5 & eth_con_min == 5 ~ "H",
+  val_lib_loc==20 & val_lib_min==20 & eth_con_loc == 20 & eth_con_min == 20 ~ "L"
+))
+
+sb <- list(
+  as.data.frame(cbind((subset(df_fin, eth_lib_loc != 0 & eth_lib_min != 0) %>% gather(subgroup, Segra, de_sq_bl,dv_sq_bl)),t="Conservative Majority")),
+           as.data.frame(cbind((subset(df_fin, eth_lib_loc != 0 & eth_lib_min != 0) %>% gather(subgroup, Segra, de_cl_bl,dv_cl_bl)),t="Liberal Majority")),
+            as.data.frame(cbind((subset(df_fin, eth_lib_loc != 0 & eth_lib_min != 0)  %>% gather(subgroup, Segra, de_sq_or,dv_sq_or)),t="Conservative Minority")),
+           as.data.frame(cbind((subset(df_fin, eth_lib_loc != 0 & eth_lib_min != 0) %>% gather(subgroup, Segra, de_cl_or,dv_cl_or)),t="Liberal Minority"))
+           )
+
+for (i in sb) {
+
+pl <-  ggplot(i, aes(x=circle_orange,y=Segra,shape = subgroup, color = RND)) + geom_point() + geom_line() +
+  scale_color_manual(values = c("green","purple"),labels = c("high","low"), guide = guide_legend(title = "Randomness")) + 
+  scale_shape_manual(values = c("square","circle"),labels = c("ethnic","Value"), guide = guide_legend(title = "Segregation")) + 
+ scale_x_discrete(limits = seq(10,90 ,by = 10)) +
+  facet_wrap(~ fraction_blue, nrow = 1) +
+ ggtitle(i$t) +
+  theme_bw()
+
+plot(pl)
+
+}
+
+```
+
+```{r 3Dsec, fig.cap="Increase ethnic preference, 3D", echo = FALSE}
+
+sec_3D_high <- df_3D %>% filter(val_lib_loc==5,val_lib_min==5,eth_con_loc == 5,eth_con_min == 5,eth_lib_loc ==5,eth_lib_min==5) 
+sec_3D_low <- df_3D %>% filter(val_lib_loc==20,val_lib_min==20,eth_con_loc == 20,eth_con_min == 20,eth_lib_loc ==20,eth_lib_min==20)
 
@@
 
-D3 <- {
-lowE <- plot_ly(df_3D_low)  %>%
+D3_e <- {
+lowE_e <- plot_ly(sec_3D_high)  %>%
   add_trace(x= xx,y= yy,z=zz,
@@
 
- lowV<- plot_ly(df_3D_low)  %>%   add_trace(x=xx,y=yy,z=zzv,
+ lowV_e<- plot_ly(sec_3D_high)  %>%   add_trace(x=xx,y=yy,z=zzv,
              scene =  "scene2",
@@
 
-highE <- plot_ly(df_3D_high)  %>%
+highE_e <- plot_ly(sec_3D_low)  %>%
   add_trace(x=xx,y=yy,z=zz,
@@
 
- highV<- plot_ly(df_3D_high)  %>%   
+ highV_e<- plot_ly(sec_3D_low)  %>%   
     add_trace(x=xx,y=yy,z=zz,
@@
 
-subplot(lowE, lowV,  highE, highV) %>%
+subplot(lowE_e, lowV_e,  highE_e, highV_e) %>%
 
@@
 
+### Annex
+
+```{r by-product ethnic cons, fig.cap="Effect of liberals majority vs minority on ethnic segregation conservatives", echo = FALSE}
+# Not interesting, goes in the annex
+
+# ethnic and value segregation for each group in the annex
+
+##### 
+# By-product value of conservatives by value preference liberals
+
+# Majority
+
+mech_cons <- mech %>% filter(fraction_blue == 50 | fraction_blue == 80) %>%  filter(val_lib_min==0 | val_lib_min==1 |val_lib_min==7) %>% gather(key=ethnics, value=Clust, de_sq_bl,de_sq_or)
+
+cons_maj_et <- ggplot(data = mech_cons, aes(x=val_lib_loc,y=Clust,color=  `ethnics`,linetype= as.factor(fraction_blue))) + geom_point(size=1.5, shape = "square") + geom_line() + 
+  facet_wrap(~val_lib_min,dir="v",labeller = labeller(val_lib_min = valueminority.labs)) +
+    scale_y_continuous(breaks= seq(0,5,by=0.5)) +
+  xlab("ß value liberal majority") + ylab("Spatial clustering") +
+  geom_hline(yintercept=1,color="red") +
+  scale_color_manual(values=c("blue","darkorange"),labels=c("Majority","Minority"),name="Ethnicity") +
+    scale_linetype_manual(values=c("solid","dashed"),labels=c("50%","80%"),name="% Majority") +
+   guides(color  = guide_legend(order = 1), linetype = guide_legend(order = 2)) +
+  theme_bw()
+
+# Minority
+
+mech_lib <- mech %>%  filter(fraction_blue == 50 | fraction_blue == 80) %>%  filter(val_lib_loc==0 | val_lib_loc==1 |val_lib_loc==7) %>% gather(key=ethnics, value=Cluste, de_sq_bl,de_sq_or)
+
+cons_min_et <- ggplot(data = mech_lib, aes(x=val_lib_min,y=Cluste,color=  `ethnics`,linetype= as.factor(fraction_blue))) + geom_point(size=1.5, shape = "square") + geom_line() + 
+  facet_wrap(~val_lib_loc,dir="v",labeller = labeller(val_lib_loc = valuemajority.labs)) +
+  xlab("ß value liberal minority") + ylab("Spatial clustering") +
+  scale_y_continuous(breaks= seq(0,5,by=0.5)) +
+  geom_hline(yintercept=1,color="red") +
+  scale_color_manual(values=c("blue","darkorange"),labels=c("Majority","Minority"),name="Ethnicity") +
+    scale_linetype_manual(values=c("solid","dashed"),labels=c("50%","80%"),name="% Majority") +
+   guides(color  = guide_legend(order = 1), linetype = guide_legend(order = 2)) +
+ theme_bw()
+
+ggplotly(cons_maj_et)
+ggplotly(cons_min_et)
+
+lib_cons_et <- ggpubr::ggarrange(cons_maj_et,cons_min_et, common.legend = TRUE, legend = "bottom")
+lib_cons_et
+#ggsave("lib_cons.jpg",plot=lib_cons)
+
+ggpubr::annotate_figure(lib_cons_et,top = "Effect of liberals majority vs minority on ethnic segregation conservatives")
+
+```
+
+```{r et_liberals_con, fig.cap="OK Effect of ethnic liberals majority vs minority on liberals", echo = FALSE}
+
+# etlib_maj <- df_etlib %>% filter(fraction_blue == 50 | fraction_blue == 80) %>% filter(eth_con_loc == 20 & eth_con_min == 20) %>% filter(val_con_loc == 0 & val_con_min == 0) %>% filter(eth_lib_min == 0)
+
+etlib_maj <- df_sec %>% filter(fraction_blue == 50 | fraction_blue == 80)  %>% gather(key = subgroup, value = Clustetmj, de_sq_bl,dv_sq_bl,de_sq_or,dv_sq_or) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"Ethnic" = c("de_sq_bl","de_sq_or"), "Value" = c("dv_sq_bl","dv_sq_or") ),"Ethnic"),
+              `ethnicity` = fct_relevel(fct_collapse(subgroup,"Liberals Majority" = c("de_sq_bl","dv_sq_bl"), "Liberals Minority" = c("de_sq_or","dv_sq_or")), "Liberals Majority")) # %>% filter(eth_lib_min == 0)
+
+# data_maj = etlib_maj[which(etlib_maj$ID == "etlib_loc" & etlib_maj$eth_lib_min == 0),]
+
+libmaj <-  ggplot(data =  etlib_maj[which(etlib_maj$ID == "etlib_loc" & etlib_maj$eth_lib_min == 0 & etlib_maj$eth_con_loc == 20  & etlib_maj$eth_con_min == 20 & etlib_maj$val_con_loc ==0 & etlib_maj$val_con_min == 0),], aes(x= eth_lib_loc,y = Clustetmj,linetype= as.factor(fraction_blue), shape =`segregation`,color = `ethnicity`) ) +
+  geom_point(size=2) + geom_line() +
+  facet_wrap(~`ethnicity`, dir = "v") +
+   scale_color_manual(values = c("blue","orange"), name = "Ethnicity") +
+  scale_shape_manual(values = c("square","circle"), name = "Segregation") +
+   scale_linetype_manual(values = c("solid","dashed"), labels = c("50%","80%"), name = "% Majority") +
+  xlab("ß ethnic liberals majority") +
+  ylab("Spatial Clustering") +
+  labs(caption = "ß ethnic liberals minority = 0") + theme_bw() +
+  guides(color = FALSE) +
+  theme(plot.caption = element_text(hjust = 0.5))
+
+libmin <-  ggplot(data = etlib_maj[which(etlib_maj$ID == "etlib_min" & etlib_maj$eth_lib_loc == 0 & etlib_maj$eth_con_loc == 20  & etlib_maj$eth_con_min == 20 & etlib_maj$val_con_loc ==0 & etlib_maj$val_con_min == 0),], aes(x= eth_lib_min,y = Clustetmj,linetype= as.factor(fraction_blue), shape =`segregation`,color = `ethnicity`) ) +
+  geom_point(size=2) + geom_line() + 
+  facet_wrap(~`ethnicity`, dir = "v") +
+   scale_color_manual(values = c("blue","orange"), name = "Ethnicity") + 
+  scale_shape_manual(values = c("square","circle"), name = "Segregation") + 
+   scale_linetype_manual(values = c("solid","dashed"), labels = c("50%","80%"), name = "% Majority") +
+  xlab("ß ethnic liberals minority") +
+  ylab("Spatial Clustering") +
+  labs(caption = "ß ethnic liberals majority = 0") + theme_bw() +
+  guides(color = FALSE) +
+  theme(plot.caption = element_text(hjust = 0.5))
+
+ggpubr::ggarrange(libmaj,libmin, common.legend = TRUE, legend = "bottom")
+
+# high randomness
+
+# libmaj_h <-  ggplot(data =  etlib_maj[which(etlib_maj$ID == "etlib_loc" & etlib_maj$eth_lib_min == 0 & etlib_maj$eth_con_loc == 5  & etlib_maj$eth_con_min == 5 & etlib_maj$val_con_loc ==0 & etlib_maj$val_con_min == 0),], aes(x= eth_lib_loc,y = Clustetmj,linetype= as.factor(fraction_blue), shape =`segregation`,color = `ethnicity`) ) +
+#   geom_point(size=2) + geom_line() +
+#   facet_wrap(~`ethnicity`, dir = "v") +
+#    scale_color_manual(values = c("blue","orange"), name = "Ethnicity") +
+#   scale_shape_manual(values = c("square","circle"), name = "Segregation") +
+#    scale_linetype_manual(values = c("solid","dashed"), labels = c("50%","80%"), name = "% Majority") +
+#   xlab("ß ethnic liberals majority") +
+#   ylab("Spatial Clustering") +
+#   labs(caption = "ß ethnic liberals minority = 0") + theme_bw() +
+#   guides(color = FALSE) +
+#   theme(plot.caption = element_text(hjust = 0.5))
+# 
+# libmin_h <-  ggplot(data = etlib_maj[which(etlib_maj$ID == "etlib_min" & etlib_maj$eth_lib_loc == 0 & etlib_maj$eth_con_loc == 5  & etlib_maj$eth_con_min == 5 & etlib_maj$val_con_loc ==0 & etlib_maj$val_con_min == 0),], aes(x= eth_lib_min,y = Clustetmj,linetype= as.factor(fraction_blue), shape =`segregation`,color = `ethnicity`) ) +
+#   geom_point(size=2) + geom_line() + 
+#   facet_wrap(~`ethnicity`, dir = "v") +
+#    scale_color_manual(values = c("blue","orange"), name = "Ethnicity") + 
+#   scale_shape_manual(values = c("square","circle"), name = "Segregation") + 
+#    scale_linetype_manual(values = c("solid","dashed"), labels = c("50%","80%"), name = "% Majority") +
+#   xlab("ß ethnic liberals minority") +
+#   ylab("Spatial Clustering") +
+#   labs(caption = "ß ethnic liberals majority = 0") + theme_bw() +
+#   guides(color = FALSE) +
+#   theme(plot.caption = element_text(hjust = 0.5))
+# 
+# 
+# ggpubr::ggarrange(libmaj_h,libmin_h, common.legend = TRUE, legend = "bottom")
+
+```
+
 ### Back
+
+```{r sec_test, fig.cap="Keep it for annex: effect of liberals or conservatives secondary preference in low or high determinism", echo = FALSE}
+
+# pref <- names(df_sec) %in% c("eth_con_loc", "eth_con_min","val_loc_lib")
+
+etlblc_high <- df_sec  %>% filter(fraction_blue == 80) %>% filter(ID == "etlib_loc", RND == "high", eth_lib_loc == 5 | eth_lib_loc == 0) %>% filter(eth_lib_min == 0) %>% gather(key = subgroup, value = Clus, de_sq_bl,dv_sq_bl,de_cl_bl,dv_cl_bl,de_sq_or,dv_sq_or,de_cl_or,dv_cl_or)
+
+etlblc_high_pic <- ggplot(etlblc_high, aes(fill = as.factor(etlblc_high$eth_lib_loc), y= etlblc_high$Clus, x = etlblc_high$subgroup) ) + 
+    geom_bar(position="dodge", stat="identity") +
+  scale_fill_manual(values=c("red","blue")) +
+  scale_y_continuous(limits= c(0,6),breaks=seq(0,6,by=0.5))
+
+etlblc_low <- df_sec  %>% filter(fraction_blue == 80) %>% filter(ID == "etlib_loc", RND == "low", eth_lib_loc == 20 | eth_lib_loc == 0) %>% filter(eth_lib_min == 0) %>% gather(key = subgroup, value = Clus, de_sq_bl,dv_sq_bl,de_cl_bl,dv_cl_bl,de_sq_or,dv_sq_or,de_cl_or,dv_cl_or)
+
+etlblc_low_pic <- ggplot(etlblc_low, aes(fill = as.factor(etlblc_low$eth_lib_loc), y= etlblc_low$Clus, x = etlblc_low$subgroup) ) + 
+    geom_bar(position="dodge", stat="identity") +
+  scale_fill_manual(values=c("red","blue")) +
+  scale_y_continuous(limits= c(0,6),breaks=seq(0,6,by=0.5))
+
+etlbmn_high <- df_sec  %>% filter(fraction_blue == 80) %>% filter(ID == "etlib_min", RND == "high", eth_lib_min == 5 | eth_lib_min == 0) %>% filter(eth_lib_loc == 0) %>% gather(key = subgroup, value = Clus, de_sq_bl,dv_sq_bl,de_cl_bl,dv_cl_bl,de_sq_or,dv_sq_or,de_cl_or,dv_cl_or)
+
+etlbmn_high_pic <- ggplot(etlbmn_high, aes(fill = as.factor(etlbmn_high$eth_lib_min), y= etlbmn_high$Clus, x = etlbmn_high$subgroup) ) + 
+    geom_bar(position="dodge", stat="identity") +
+  scale_fill_manual(values=c("red","blue")) +
+  scale_y_continuous(limits= c(0,6),breaks=seq(0,6,by=0.5))
+
+etlbmn_low <- df_sec  %>% filter(fraction_blue == 80) %>% filter(ID == "etlib_min", RND == "low", eth_lib_min == 20 | eth_lib_min == 0) %>% filter(eth_lib_loc == 0) %>% gather(key = subgroup, value = Clus, de_sq_bl,dv_sq_bl,de_cl_bl,dv_cl_bl,de_sq_or,dv_sq_or,de_cl_or,dv_cl_or)
+
+etlbmn_low_pic <- ggplot(etlbmn_low, aes(fill = as.factor(etlbmn_low$eth_lib_min), y= etlbmn_low$Clus, x = etlbmn_low$subgroup) ) + 
+    geom_bar(position="dodge", stat="identity") +
+  scale_fill_manual(values=c("red","blue")) +
+  scale_y_continuous(limits= c(0,6),breaks=seq(0,6,by=0.5))
+
+vlcnlc_low <- df_sec  %>% filter(fraction_blue == 80) %>% filter(ID == "valuecon_loc", RND == "low", val_con_loc == 20 | val_con_loc == 0) %>% filter(val_con_min == 0) %>% gather(key = subgroup, value = Clus, de_sq_bl,dv_sq_bl,de_cl_bl,dv_cl_bl,de_sq_or,dv_sq_or,de_cl_or,dv_cl_or)
+
+vlcnlc_low_pic <- ggplot(vlcnlc_low, aes(fill = as.factor(vlcnlc_low$val_con_loc), y= vlcnlc_low$Clus, x = vlcnlc_low$subgroup) ) + 
+    geom_bar(position="dodge", stat="identity") +
+  scale_fill_manual(values=c("red","blue")) +
+  scale_y_continuous(limits= c(0,6),breaks=seq(0,6,by=0.5))
+
+vlcnlc_high <- df_sec  %>% filter(fraction_blue == 80) %>% filter(ID == "valuecon_loc", RND == "high", val_con_loc == 5 | val_con_loc == 0) %>% filter(val_con_min == 0) %>% gather(key = subgroup, value = Clus, de_sq_bl,dv_sq_bl,de_cl_bl,dv_cl_bl,de_sq_or,dv_sq_or,de_cl_or,dv_cl_or)
+
+vlcnlc_high_pic <- ggplot(vlcnlc_high, aes(fill = as.factor(vlcnlc_high$val_con_loc), y= vlcnlc_high$Clus, x = vlcnlc_high$subgroup) ) + 
+    geom_bar(position="dodge", stat="identity") +
+  scale_fill_manual(values=c("red","blue")) +
+  scale_y_continuous(limits= c(0,6),breaks=seq(0,6,by=0.5))
+
+vlcnmn_low <- df_sec  %>% filter(fraction_blue == 80) %>% filter(ID == "valuecon_min", RND == "low", val_con_min == 20 | val_con_min == 0) %>% filter(val_con_loc == 0) %>% gather(key = subgroup, value = Clus, de_sq_bl,dv_sq_bl,de_cl_bl,dv_cl_bl,de_sq_or,dv_sq_or,de_cl_or,dv_cl_or)
+
+vlcnmn_low_pic <- ggplot(vlcnmn_low, aes(fill = as.factor(vlcnmn_low$val_con_min), y= vlcnmn_low$Clus, x = vlcnmn_low$subgroup) ) + 
+    geom_bar(position="dodge", stat="identity") +
+  scale_fill_manual(values=c("red","blue")) +
+  scale_y_continuous(limits= c(0,6),breaks=seq(0,6,by=0.5))
+
+vlcnmn_high <- df_sec  %>% filter(fraction_blue == 80) %>% filter(ID == "valuecon_min", RND == "high", val_con_min == 5 | val_con_min == 0) %>% filter(val_con_loc == 0) %>% gather(key = subgroup, value = Clus, de_sq_bl,dv_sq_bl,de_cl_bl,dv_cl_bl,de_sq_or,dv_sq_or,de_cl_or,dv_cl_or)
+
+vlcnmn_high_pic <- ggplot(vlcnmn_high, aes(fill = as.factor(vlcnmn_high$val_con_min), y= vlcnmn_high$Clus, x = vlcnmn_high$subgroup) ) + 
+    geom_bar(position="dodge", stat="identity") +
+  scale_fill_manual(values=c("red","blue")) +
+  scale_y_continuous(limits= c(0,6),breaks=seq(0,6,by=0.5))
+
+# ggplotly(etlblc_high_pic)
+# ggplotly(etlblc_low_pic)
+# ggplotly(etlbmn_high_pic)
+# ggplotly(etlbmn_low_pic)
+# ggplotly(vlcnlc_low_pic)
+# ggplotly(vlcnlc_high_pic)
+# ggplotly(vlcnmn_low_pic)
+# ggplotly(vlcnmn_high_pic)
+
+etlblc_high_pic
+etlblc_low_pic
+etlbmn_high_pic
+etlbmn_low_pic
+vlcnlc_low_pic
+vlcnlc_high_pic
+vlcnmn_low_pic
+vlcnmn_high_pic
+
+```
+
+```{r et_lib_cons, fig.cap="NO Effect of ethnic liberals on conservatives", echo = FALSE}
+
+# etlib_maj <- df_etlib %>% filter(fraction_blue == 50 | fraction_blue == 80) %>% filter(eth_con_loc == 20 & eth_con_min == 20) %>% filter(val_con_loc == 0 & val_con_min == 0) %>% filter(eth_lib_min == 0)
+
+etlib_cons <- df_sec %>% filter(fraction_blue == 50 | fraction_blue == 80, val_con_loc ==0, val_con_min == 0 )  %>% gather(key = subgroup, value = Clustetmj, de_sq_bl,dv_sq_bl,de_sq_or,dv_sq_or) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"Ethnic" = c("de_sq_bl","de_sq_or"), "Value" = c("dv_sq_bl","dv_sq_or") ),"Ethnic"),
+              `ethnicity` = fct_relevel(fct_collapse(subgroup,"Conservatives Majority" = c("de_sq_bl","dv_sq_bl"), "Conservatives Minority" = c("de_sq_or","dv_sq_or")), "Conservatives Majority")) # %>% filter(eth_lib_min == 0)
+
+# data_maj = etlib_maj[which(etlib_maj$ID == "etlib_loc" & etlib_maj$eth_lib_min == 0),]
+
+conmaj <-  ggplot(data =  etlib_cons[which(etlib_cons$ID == "etlib_loc" & etlib_cons$eth_lib_min == 0 & etlib_cons$eth_con_loc == 20 & etlib_cons$eth_con_min == 20),], aes(x= eth_lib_loc,y = Clustetmj,linetype= as.factor(fraction_blue), shape =`segregation`,color = `ethnicity`) ) +
+  geom_point(size=2) + geom_line() +
+  facet_wrap(~`ethnicity`, dir = "v") +
+   scale_color_manual(values = c("blue","orange"), name = "Ethnicity") +
+  scale_shape_manual(values = c("square","circle"), name = "Segregation") +
+   scale_linetype_manual(values = c("solid","dashed"), labels = c("50%","80%"), name = "% Majority") +
+  xlab("ß ethnic liberals majority") +
+  ylab("Spatial Clustering") +
+  labs(caption = "ß ethnic liberals minority = 0") + theme_bw() +
+  guides(color = FALSE) +
+  theme(plot.caption = element_text(hjust = 0.5))
+
+conmin <-  ggplot(data = etlib_cons[which(etlib_cons$ID == "etlib_min" & etlib_cons$eth_lib_loc == 0 & etlib_cons$eth_con_loc == 20 &  etlib_cons$eth_con_min == 20),], aes(x= eth_lib_min,y = Clustetmj,linetype= as.factor(fraction_blue), shape =`segregation`,color = `ethnicity`) ) +
+  geom_point(size=2) + geom_line() + 
+  facet_wrap(~`ethnicity`, dir = "v") +
+   scale_color_manual(values = c("blue","orange"), name = "Ethnicity") + 
+  scale_shape_manual(values = c("square","circle"), name = "Segregation") + 
+   scale_linetype_manual(values = c("solid","dashed"), labels = c("50%","80%"), name = "% Majority") +
+  xlab("ß ethnic liberals minority") +
+  ylab("Spatial Clustering") +
+  labs(caption = "ß ethnic liberals majority = 0") + theme_bw() +
+  guides(color = FALSE) +
+  theme(plot.caption = element_text(hjust = 0.5))
+
+ggpubr::ggarrange(conmaj,conmin, common.legend = TRUE, legend = "bottom")
+
+# high randomness
+
+# conmaj_h <-  ggplot(data =  etlib_cons[which(etlib_cons$ID == "etlib_loc" & etlib_cons$eth_lib_min == 0 & etlib_cons$eth_con_loc == 5 & etlib_cons$eth_con_min == 5),], aes(x= eth_lib_loc,y = Clustetmj,linetype= as.factor(fraction_blue), shape =`segregation`,color = `ethnicity`) ) +
+#   geom_point(size=2) + geom_line() +
+#   facet_wrap(~`ethnicity`, dir = "v") +
+#    scale_color_manual(values = c("blue","orange"), name = "Ethnicity") +
+#   scale_shape_manual(values = c("square","circle"), name = "Segregation") +
+#    scale_linetype_manual(values = c("solid","dashed"), labels = c("50%","80%"), name = "% Majority") +
+#   xlab("ß ethnic liberals majority") +
+#   ylab("Spatial Clustering") +
+#   labs(caption = "ß ethnic liberals minority = 0") + theme_bw() +
+#   guides(color = FALSE) +
+#   theme(plot.caption = element_text(hjust = 0.5))
+# 
+# conmin_h <-  ggplot(data = etlib_cons[which(etlib_cons$ID == "etlib_min" & etlib_cons$eth_lib_loc == 0 & etlib_cons$eth_con_loc == 5 &  etlib_cons$eth_con_min == 5),], aes(x= eth_lib_min,y = Clustetmj,linetype= as.factor(fraction_blue), shape =`segregation`,color = `ethnicity`) ) +
+#   geom_point(size=2) + geom_line() + 
+#   facet_wrap(~`ethnicity`, dir = "v") +
+#    scale_color_manual(values = c("blue","orange"), name = "Ethnicity") + 
+#   scale_shape_manual(values = c("square","circle"), name = "Segregation") + 
+#    scale_linetype_manual(values = c("solid","dashed"), labels = c("50%","80%"), name = "% Majority") +
+#   xlab("ß ethnic liberals minority") +
+#   ylab("Spatial Clustering") +
+#   labs(caption = "ß ethnic liberals majority = 0") + theme_bw() +
+#   guides(color = FALSE) +
+#   theme(plot.caption = element_text(hjust = 0.5))
+#  
+# 
+# ggpubr::ggarrange(conmaj_h,conmin_h, common.legend = TRUE, legend = "bottom") 
+# 
+# ggplotly(conmaj)
+
+```
+
+### Delete
 
@@
 ```
+
+```{r 3D, fig.cap="3D pictures", echo = FALSE}
+
+df_3D_high <- df_3D %>% filter(val_lib_loc==5,val_lib_min==5,eth_con_loc == 5,eth_con_min == 5,eth_lib_loc ==0,eth_lib_min==0)
+df_3D_low <- df_3D %>% filter(val_lib_loc==20,val_lib_min==20,eth_con_loc == 20,eth_con_min == 20,eth_lib_loc ==0,eth_lib_min==0)
+
+xx <- ~fraction_blue
+yy <- ~circle_orange
+zz <- ~de_cl_or
+cols <- ~et_cl_or
+zzv <- ~dv_cl_or
+colsv <- ~vl_cl_or
+tt <- "Liberasl Minority"
+
+D3 <- {
+lowE <- plot_ly(df_3D_high)  %>%
+  add_trace(x= xx,y= yy,z=zz,
+            scene = "scene1",
+            type="scatter3d",
+             mode="markers",
+             marker = list(
+             colorscale = "Reds",
+             color= cols, showscale =  T,
+             colorbar=list(title = "Ethnic \nExposure" ,x = -0.1,  len = 0.5, yanchor='bottom'))
+
+            )  %>%
+  layout(showlegend = F,
+         #title="Ethnic",
+         "scene1" = list(
+      xaxis = list(title = "Ethnic Ratio",range=seq(50,90,by=10),dtick=10),
+      yaxis = list(title = "% Liberal Minority" ,autorange = "reversed"),
+      zaxis = list(title = "Ethnic Cluster")))
+
+ lowV<- plot_ly(df_3D_high)  %>%   add_trace(x=xx,y=yy,z=zzv,
+             scene =  "scene2",
+             type="scatter3d",
+             mode="markers",
+             marker = list(
+             colorscale = "Blues",
+             color= colsv , showscale = T, reversescale=T,
+             colorbar=list(title = "Value  \nExposure", len=0.5, yanchor='bottom'))
+            )  %>%
+       layout(showlegend = F,
+         "scene2" = list(
+      xaxis = list(title = "Ethnic Ratio",range=seq(50,90,by=10),dtick=10),
+      yaxis = list(title = "% Liberal Minority"  ,autorange = "reversed"),
+      zaxis = list(title = "Value Cluster")))
+
+highE <- plot_ly(df_3D_low)  %>%
+  add_trace(x=xx,y=yy,z=zz,
+            scene = "scene3",
+            type="scatter3d",
+             mode="markers",
+             marker = list(
+             colorscale = "Reds",
+             color= cols, showscale =  T,
+             colorbar=list(title = "Ethnic \nExposure" ,x = -0.1,  len = 0.5, yanchor='top'))
+
+            )  %>%
+  layout(showlegend = F,
+         #title="Ethnic",
+         "scene3" = list(
+      xaxis = list(title = "Ethnic Ratio",range=seq(50,90,by=10),dtick=10),
+      yaxis = list(title = "% Liberal Minority" ,autorange = "reversed"),
+      zaxis = list(title = "Ethnic Cluster")))
+
+ highV<- plot_ly(df_3D_low)  %>%
+    add_trace(x=xx,y=yy,z=zz,
+     scene =  "scene4",
+     type="scatter3d",
+     mode="markers",
+     marker = list(
+     colorscale = "Blues",
+     color= colsv , showscale = T, reversescale=T,
+      colorbar=list(title = "Value  \nExposure", len=0.5, yanchor='top'))
+            )  %>%
+       layout(showlegend = F,
+         "scene4" = list(
+      xaxis = list(title = "Ethnic Ratio",range=seq(50,90,by=10),dtick=10),
+      yaxis = list(title = "% Liberal Minority"   ,autorange = "reversed"),
+      zaxis = list(title = "Value Cluster")))
+
+subplot(lowE, lowV,  highE, highV) %>%
+
+   layout(scene = list(domain=list(x=c(0,0.5),y=c(0.5,1)),zaxis = list(title = "Ethnic Cluster")),
+         scene2 = list(domain=list(x=c(0.5,1),y=c(0.5,1))),
+         scene3 = list(domain=list(x=c(0,0.5),y=c(0,0.5))),
+         scene4 = list(domain=list(x=c(0.5,1),y=c(0,0.5)))
+         ) %>%
+
+  layout(annotations = list(
+  text = tt,
+  font = list(size = 18),
+  xref = "paper",
+  yref = "paper",
+  yanchor = "bottom",
+  xanchor = "center",
+  align = "center",
+  x = 0.5,
+  y = 1,
+  showarrow = FALSE
+)
+
+) %>%
+  layout(annotations = list(
+  text = "High Randomness",
+  font = list(size = 15),
+  xref = "paper",
+  yref = "paper",
+  yanchor = "bottom",
+  xanchor = "center",
+  align = "center",
+  x = 0.5,
+  y = 0.5,
+  showarrow = FALSE
+))%>%
+  layout(annotations = list(
+  text = "Low Randomness",
+  font = list(size = 15),
+  xref = "paper",
+  yref = "paper",
+  yanchor = "bottom",
+  xanchor = "center",
+  align = "center",
+  x = 0.5,
+  y = 0,
+  showarrow = FALSE
+)
+
+)
+}
+
+```

### 2021-06-29 additional.Rmd
Add files via upload

@@
 library(plot3D)
+library(xlsx)
 
@@
 names(ethnicmajority.labs) <- c("0","1","7")
+ethnicity.labs <- c("50% Majority", "60% Majority","70% Majority","80% Majority","90% Majority")
+names(ethnicity.labs) <- c("50","60","70","80","90")
 
@@
 mech <- mech[!excl] %>% group_by(eth_con_loc, eth_con_min,eth_lib_loc,eth_lib_min,val_lib_loc,val_lib_min,val_con_loc,val_con_min,circle_orange,circle_blue,fraction_blue) %>% summarise_all(mean)
-
-df_sec <- read.csv("df_secondary.csv",sep=",")
-exclet <- names(df_sec) %in% c("run", "density","step")
-df_sec <- df_sec[!exclet] %>% group_by(ID,RND,eth_con_loc,eth_con_min,eth_lib_loc,eth_lib_min,val_lib_loc,val_lib_min,val_con_loc,val_con_min,circle_orange,circle_blue,fraction_blue) %>% summarise_all(mean)
 
@@
 
+df_sec <- read.csv("df_secondary.csv",sep=",")
+exclet <- names(df_sec) %in% c("run", "density","step")
+df_sec <- df_sec[!exclet] %>% group_by(ID,RND,eth_con_loc,eth_con_min,eth_lib_loc,eth_lib_min,val_lib_loc,val_lib_min,val_con_loc,val_con_min,circle_orange,circle_blue,fraction_blue) %>% summarise_all(mean)
+
 df_3Do <- read.csv("3D_old.csv",sep=",")
@@
 
+# value_dominant_den <- read.csv("dom_sqr_2.csv",skip = 6,sep = ",")
+# leg <- read.csv("leg_value_dominant_den.csv",sep=";")
+# 
+# value_dominant_den$ID <- "square"
+# value_dominant_den2 <- read.csv("dom_crl_2.csv",skip = 6,sep = ",")
+# names(value_dominant_den2) <- leg[,1]
+# value_dominant_den2$ID <- "circle"
+# 
+# value_dominant_den <- rbind(value_dominant_den,value_dominant_den2)
+# 
+# write.csv(value_dominant_den,"value_dominant_den.csv",row.names = F)
+
+value_basic_den <- read.csv("value_basic_den.csv",sep = ",")
+excl <- names(value_basic_den) %in% c("run","density","step")
+value_basic_den <- value_basic_den[!excl] %>% group_by(ID,fraction_blue,circle_blue,circle_orange,circle,square) %>% summarise_all(mean)
+
+value_dominant_den <- read.csv("value_dominant_den.csv",sep = ",")
+excl <- names(value_dominant_den) %in% c("run","density","step")
+value_dominant_den <- value_dominant_den[!excl] %>% group_by(ID,fraction_blue,circle_blue,circle_orange,dominant_square,dominant_circle,secondary_square,secondary_circle) %>% summarise_all(mean)
+
+dv <- c("step",
+"et_sq",
+"et_cl",
+"vl_sq",
+"vl_cl",
+"et_sq_bl",
+"et_cl_bl",
+"et_sq_or",
+"et_cl_or",
+"vl_sq_bl",
+"vl_cl_bl",
+"vl_sq_or",
+"vl_cl_or",
+"den_sq_bl",
+"den_sq_or",
+"den_cl_bl",
+"den_cl_or",
+"den_sq",
+"den_cl",
+"de_sq_bl",
+"de_cl_bl",
+"de_sq_or",
+"de_cl_or",
+"dv_sq_bl",
+"dv_cl_bl",
+"dv_sq_or",
+"dv_cl_or")
 ```
 
-# Between the 2 baseline: decide!
+```{r test_val-eth, fig.cap= "Checking effect of lvalue liberal = ethnic liberal" echo =  FALSE}
+
+# equal size; liberals: value = ethnic
+
+df <- read.csv("val_eth_circle3.csv",skip=6,sep=",")
+lg <- read.csv("lg_val_eth_circle3.csv",sep =";")
+names(df) <- lg[,1]
+
+df <- df %>%  gather(key = subgroup, value = Segra, et_sq,vl_sq,et_cl,vl_cl,den_sq,den_cl)  %>% mutate(
+`outcome` = fct_relevel(fct_collapse(subgroup,"Ethnic Segregation" = c("et_sq","et_cl"), "Value Segregation" = c("vl_sq","vl_cl"), "Density" = c("den_sq","den_cl")),"Ethnic Segregation"), 
+`orientation` = fct_relevel(fct_collapse(subgroup,"Conservatives" = c("et_sq","vl_sq","den_sq"), "Liberals" = c("et_cl","vl_cl","den_cl")), "Conservatives"))
+
+df %>% filter(dominant_square == circle_both) %>% ggplot(aes(x= circle_both,y = Segra, color = `outcome`, shape = `orientation`)) + geom_point() + geom_line() +
+  scale_color_manual(values = c("green","gray","purple"), guide = guide_legend(title = "Outcome")) +
+  scale_shape_manual(values = c("square","circle"), guide = guide_legend(title = "Orientation"))  +
+  scale_y_continuous(limits=c(0.45,1), breaks=seq(0.5,1,by=0.1)) +
+  xlab("ß value liberals = ß ethnic liberals") +
+  ylab("Outcome") +
+  theme_bw()+
+  theme(legend.position = "bottom")
+
+```
+
+```{r test_val-maj, fig.cap= "Checking effect of value liberal = ethnic liberal majority" echo =  FALSE}
+
+# equal size; liberals: value = ethnic
+
+df <- read.csv("mj_val_eth.csv",skip=6,sep=",")
+lg <- read.csv("lg_mj_val_eth.csv",sep =";")
+names(df) <- lg[,1]
+
+df <- df %>%  gather(key = subgroup, value = Segra, de_sq_bl,dv_sq_bl,de_cl_bl,dv_cl_bl,de_sq_or,dv_sq_or,de_cl_or,dv_cl_or)  %>% mutate(
+`segregation` = fct_relevel(fct_collapse(subgroup,"Ethnic" = c("de_sq_bl","de_cl_bl","de_sq_or","de_cl_or"), "Value" = c("dv_sq_bl","dv_cl_bl","dv_sq_or","dv_cl_or")),"Ethnic"), 
+ `ethnicity` = fct_relevel(fct_collapse(subgroup, "Majority" = c("de_sq_bl","dv_cl_bl","de_cl_bl","dv_sq_bl"), "Minority" = c("de_sq_or","de_cl_or","dv_sq_or","dv_cl_or")), "Majority"),
+`orientation` = fct_relevel(fct_collapse(subgroup,"Conservatives" = c("de_sq_bl","dv_sq_bl","de_sq_or","dv_sq_or"), "Liberals" = c("de_cl_bl","dv_cl_bl","de_cl_or","dv_cl_or")), "Conservatives"), 
+`type` = fct_relevel(fct_collapse(subgroup,"Conservative Majority" = c("de_sq_bl","dv_sq_bl"),
+      "Liberals Majority" = c("de_cl_bl","dv_cl_bl"),
+      "Conservative Minority" = c("de_sq_or","dv_sq_or"),
+      "Liberals Minority" = c("de_cl_or","dv_cl_or")), "Conservative Majority"))
+
+df %>% filter(dominant_square == circle_mj) %>% ggplot(aes(x= circle_mj,y = Segra, color = `segregation`, shape = `orientation`)) + geom_point() + geom_line() +
+  scale_color_manual(values = c("green","purple"), guide = guide_legend(title = "Outcome")) +
+  scale_shape_manual(values = c("square","circle"), guide = guide_legend(title = "Orientation"))  +
+ # scale_y_continuous(limits=c(0.45,1), breaks=seq(0.5,1,by=0.1)) +
+  xlab("ß value liberals majority = ß ethnic liberals majority") +
+  ylab("Outcome") +
+  facet_wrap(~  `ethnicity` ) +
+  theme_bw()+
+  theme(legend.position = "bottom")
+
+```
+
+# Basic two preferences
+```{r dompref, echo = FALSE}
+
+value_dominant_den <- value_dominant_den %>%  gather(key = subgroup, value = Segra, et_sq,vl_sq,et_cl,vl_cl,den_sq,den_cl)  %>% mutate(
+`outcome` = fct_relevel(fct_collapse(subgroup,"Ethnic Segregation" = c("et_sq","et_cl"), "Value Segregation" = c("vl_sq","vl_cl"), "Density" = c("den_sq","den_cl")),"Ethnic Segregation"), 
+`orientation` = fct_relevel(fct_collapse(subgroup,"Conservatives" = c("et_sq","vl_sq","den_sq"), "Liberals" = c("et_cl","vl_cl","den_cl")), "Conservatives"))
+
+value_basic_den <- value_basic_den %>%  gather(key = subgroup, value = Segra, et_sq,vl_sq,et_cl,vl_cl,den_sq,den_cl)  %>% mutate(
+`outcome` = fct_relevel(fct_collapse(subgroup,"Ethnic Segregation" = c("et_sq","et_cl"), "Value Segregation" = c("vl_sq","vl_cl"), "Density" = c("den_sq","den_cl")),"Ethnic Segregation"), 
+`orientation` = fct_relevel(fct_collapse(subgroup,"Conservatives" = c("et_sq","vl_sq","den_sq"), "Liberals" = c("et_cl","vl_cl","den_cl")), "Conservatives"))
+
+lib_dom <- value_dominant_den %>% filter (ID == "circle") %>% ggplot(aes(x = dominant_circle, y = Segra, color = `outcome`, shape = `orientation` )) + geom_point(size = 2) + geom_line() +
+  scale_color_manual(values = c("green","gray","purple"), guide = guide_legend(title = "Outcome")) +
+  scale_shape_manual(values = c("square","circle"), guide = guide_legend(title = "Orientation"))  +
+  scale_y_continuous(limits=c(0.45,1), breaks=seq(0.5,1,by=0.1)) +
+  xlab("ß value liberals \nall other ß = 0") +
+  ylab("Outcome") +
+  theme_bw()
+
+lib_both <- value_basic_den %>% filter (ID == "circle") %>% ggplot(aes(x = circle, y = Segra, color = `outcome`, shape = `orientation` )) + geom_point(size = 2) + geom_line() +
+  scale_color_manual(values = c("green","gray","purple"), guide = guide_legend(title = "Outcome")) +
+  scale_shape_manual(values = c("square","circle"), guide = guide_legend(title = "Orientation"))  +
+   scale_y_continuous(limits=c(0.45,1), breaks=seq(0.5,1,by=0.1)) +
+  xlab("ß value liberals = ß ethnic liberals") +
+  ylab("Outcome") +
+  theme_bw()
+
+cons_dom <- value_dominant_den %>% filter (ID == "square" & dominant_circle == 0) %>% ggplot(aes(x = dominant_square, y = Segra, color = `outcome`, shape = `orientation` )) + geom_point(size = 2) + geom_line() +
+  scale_color_manual(values = c("green","gray","purple"), guide = guide_legend(title = "Outcome")) +
+  scale_shape_manual(values = c("square","circle"), guide = guide_legend(title = "Orientation"))  +
+     scale_y_continuous(limits=c(0.45,1), breaks=seq(0.5,1,by=0.1)) +
+  xlab("ß ethnic conservatives \nall other ß = 0") +
+  ylab("Outcome") +
+  theme_bw()
+
+cons_both <- value_basic_den %>% filter (ID == "square") %>% ggplot(aes(x = square, y = Segra, color = `outcome`, shape = `orientation` )) + geom_point(size = 2) + geom_line() +
+  scale_color_manual(values = c("green","gray","purple"), guide = guide_legend(title = "Outcome")) +
+  scale_shape_manual(values = c("square","circle"), guide = guide_legend(title = "Orientation"))  +
+    scale_y_continuous(limits=c(0.45,1), breaks=seq(0.5,1,by=0.1)) +
+  xlab("ß ethnic conservatives = ß value conservatives") +
+  ylab("Outcome") +
+  theme_bw()
+
+a <- ggpubr::ggarrange(lib_dom,cons_dom , common.legend = TRUE, legend = "bottom")
+b <- ggpubr::ggarrange(lib_both,cons_both, common.legend = TRUE, legend = "bottom")
+
+a
+b
+
+```
+
+# Baseline asymmetric: dominant due to ethnic ration
 ```{r asym_baseline, fig.cap="Fig. 8 orig", echo = FALSE}
@@
 excl <- names(asym_dom) %in% c("run", "density","step")
-df <- asym_dom[!excl] %>% group_by(dominant,circle_orange,circle_blue,fraction_blue,secondary) %>% summarise_all(mean)
+asym_dom <- asym_dom[!excl] %>% group_by(dominant,circle_orange,circle_blue,fraction_blue,secondary) %>% summarise_all(mean)
 
@@
 
-majcons <- ggplotly(ggplot(data = df) + geom_point(aes(x=dominant,y=dv_sq_bl, colour = vl_sq_bl),shape = "circle")  + geom_line(aes(x=dominant,y=dv_sq_bl, linetype = as.factor(fraction_blue))) +
-           geom_point(aes(x=dominant,y=de_sq_bl, colour = et_sq_bl),shape="square") + geom_line(aes(x=dominant,y=de_sq_bl, linetype = as.factor(fraction_blue)))+ ggtitle("majcons"))
+asym_dom <- asym_dom  %>% filter(fraction_blue == 50 | fraction_blue == 80) %>% gather(key = subgroup, value = Segra, de_sq_bl,dv_sq_bl,de_cl_bl,dv_cl_bl,de_sq_or,dv_sq_or,de_cl_or,dv_cl_or)  %>% mutate(
+`segregation` = fct_relevel(fct_collapse(subgroup,"Ethnic" = c("de_sq_bl","de_cl_bl","de_sq_or","de_cl_or"), "Value" = c("dv_sq_bl","dv_cl_bl","dv_sq_or","dv_cl_or")),"Ethnic"), 
+ `ethnicity` = fct_relevel(fct_collapse(subgroup, "Majority" = c("de_sq_bl","dv_cl_bl","de_cl_bl","dv_sq_bl"), "Minority" = c("de_sq_or","de_cl_or","dv_sq_or","dv_cl_or")), "Majority"),
+`orientation` = fct_relevel(fct_collapse(subgroup,"Conservatives" = c("de_sq_bl","dv_sq_bl","de_sq_or","dv_sq_or"), "Liberals" = c("de_cl_bl","dv_cl_bl","de_cl_or","dv_cl_or")), "Conservatives"), 
+`type` = fct_relevel(fct_collapse(subgroup,"Conservative Majority" = c("de_sq_bl","dv_sq_bl"),
+      "Liberals Majority" = c("de_cl_bl","dv_cl_bl"),
+      "Conservative Minority" = c("de_sq_or","dv_sq_or"),
+      "Liberals Minority" = c("de_cl_or","dv_cl_or")), "Conservative Majority"))
 
-majlib <- ggplotly(ggplot(data = df) + geom_point(aes(x=dominant,y=dv_cl_bl, colour = vl_cl_bl),shape = "circle")  + geom_line(aes(x=dominant,y=dv_cl_bl, linetype = as.factor(fraction_blue))) +
-           geom_point(aes(x=dominant,y=de_cl_bl, colour = et_cl_bl),shape="square") + geom_line(aes(x=dominant,y=de_cl_bl, linetype = as.factor(fraction_blue))) + ggtitle("majlib"))
-
-mincons <- ggplotly(ggplot(data = df) + geom_point(aes(x=dominant,y=dv_sq_or, colour = vl_sq_or),shape = "circle")  + geom_line(aes(x=dominant,y=dv_sq_or, linetype = as.factor(fraction_blue))) +
-           geom_point(aes(x=dominant,y=de_sq_or, colour = et_sq_or),shape="square") + geom_line(aes(x=dominant,y=de_sq_or, linetype = as.factor(fraction_blue))) + ggtitle("mincons"))
-
-minlib <- ggplotly(ggplot(data = df) + geom_point(aes(x=dominant,y=dv_cl_or, colour = vl_cl_or),shape = "circle")  + geom_line(aes(x=dominant,y=dv_cl_or, linetype = as.factor(fraction_blue))) +
-           geom_point(aes(x=dominant,y=de_cl_or, colour = et_cl_or),shape="square") + geom_line(aes(x=dominant,y=de_cl_or, linetype = as.factor(fraction_blue)))+ ggtitle("minlib"))
-
-majcons
-majlib
-mincons
-minlib
-
-```
-
-```{r sa_asym, fig.cap="Fig. 8 orig", echo = FALSE}
-
-# Sensitivity to value liberal locals , while the others are keep 20
-
-sa_asym <- read.csv("df_sa_asym.csv",sep = ",")
-
-excl <- names(sa_asym) %in% c("run", "density","step")
-df <- sa_asym[!excl] %>% group_by(eth_con_loc, eth_con_min,eth_lib_loc,eth_lib_min,val_lib_loc,val_lib_min,val_con_loc,val_con_min,circle_orange,circle_blue,fraction_blue) %>% summarise_all(mean)
-
-df <- df %>% filter(eth_con_min==20 & eth_con_loc==20 & val_lib_min==20)
-df <- df %>% filter(fraction_blue==50|fraction_blue==60|fraction_blue==80)
-df <- df %>% filter(circle_orange==50)
-
-dominant <- df$val_lib_loc
-
-majcons <-  ggplot(data = df) + geom_point(aes(x=dominant,y=dv_sq_bl, colour = vl_sq_bl),shape = "circle")  + geom_line(aes(x=dominant,y=dv_sq_bl, linetype = as.factor(fraction_blue))) +
-           geom_point(aes(x=dominant,y=de_sq_bl, colour = et_sq_bl),shape="square") + geom_line(aes(x=dominant,y=de_sq_bl, linetype = as.factor(fraction_blue)))+ ggtitle("majcons")
-
-majlib <-  ggplot(data = df) + geom_point(aes(x=dominant,y=dv_cl_bl, colour = vl_cl_bl),shape = "circle")  + geom_line(aes(x=dominant,y=dv_cl_bl, linetype = as.factor(fraction_blue))) +
-           geom_point(aes(x=dominant,y=de_cl_bl, colour = et_cl_bl),shape="square") + geom_line(aes(x=dominant,y=de_cl_bl, linetype = as.factor(fraction_blue))) + ggtitle("majlib")
-
-mincons <-  ggplot(data = df) + geom_point(aes(x=dominant,y=dv_sq_or, colour = vl_sq_or),shape = "circle")  + geom_line(aes(x=dominant,y=dv_sq_or, linetype = as.factor(fraction_blue))) +
-           geom_point(aes(x=dominant,y=de_sq_or, colour = et_sq_or),shape="square") + geom_line(aes(x=dominant,y=de_sq_or, linetype = as.factor(fraction_blue))) + ggtitle("mincons")
-
-minlib <-  ggplot(data = df) + geom_point(aes(x=dominant,y=dv_cl_or, colour = vl_cl_or),shape = "circle")  + geom_line(aes(x=dominant,y=dv_cl_or, linetype = as.factor(fraction_blue))) +
-           geom_point(aes(x=dominant,y=de_cl_or, colour = et_cl_or),shape="square") + geom_line(aes(x=dominant,y=de_cl_or, linetype = as.factor(fraction_blue)))+ ggtitle("minlib")
-
-majcons
-majlib
-mincons
-minlib
+ggplot(data = asym_dom, aes(x = dominant, y = Segra, color = `segregation`, linetype = as.factor(fraction_blue))) + geom_point() + geom_line() +
+  facet_wrap(~ `type`, nrow = 1) +
+  scale_color_manual(values = c("green","purple"),labels =  c("Ethnic","Value"),guide = guide_legend(title = "Segregation \ntype")) +
+   scale_linetype_manual(values = c("solid","dashed"),labels =  c("50 %","80 %"),guide = guide_legend(title = "% Majority")) +
+  ylab("Spatial Clustering") +
+  xlab("ß dominant") +
+  theme_bw() +
+ theme(legend.position = "bottom")
 
@@
 
-```{r 3D_table, fig.cap="Each grouptype, distribution liberals faceted by ethnic ratio", echo = FALSE}
+```{r lib_min, fig.cap="Each grouptype, distribution liberals faceted by ethnic ratio", echo = FALSE}
 
@@
   val_lib_loc==5 & val_lib_min==5 & eth_con_loc == 5 & eth_con_min == 5 ~ "H",
-  val_lib_loc==20 & val_lib_min==20 & eth_con_loc == 20 & eth_con_min == 20 ~ "L"
-))
+  val_lib_loc==20 & val_lib_min==20 & eth_con_loc == 20 & eth_con_min == 20 ~ "L"))
 
-cmj <- subset(df_fin, eth_lib_loc ==0 & eth_lib_min == 0) %>% gather(subgroup, Segra, de_sq_bl,dv_sq_bl) %>% ggplot(aes(x=circle_orange,y=Segra,shape = subgroup, color = RND)) + geom_point() + geom_line() +
+sb <- list(
+  as.data.frame(cbind((subset(df_fin, eth_lib_loc == 0 & eth_lib_min  ==  0) %>% gather(subgroup, Segra, de_sq_bl,dv_sq_bl)),t="Conservative Majority",tt = "cmj")),
+           as.data.frame(cbind((subset(df_fin, eth_lib_loc  ==  0 & eth_lib_min  ==  0) %>% gather(subgroup, Segra, de_cl_bl,dv_cl_bl)),t="Liberal Majority",tt = "lmj")),
+            as.data.frame(cbind((subset(df_fin, eth_lib_loc  ==  0 & eth_lib_min  ==  0)  %>% gather(subgroup, Segra, de_sq_or,dv_sq_or)),t="Conservative Minority",tt = "cmn")),
+           as.data.frame(cbind((subset(df_fin, eth_lib_loc  ==  0 & eth_lib_min  ==  0) %>% gather(subgroup, Segra, de_cl_or,dv_cl_or)),t="Liberal Minority",tt = "lmn")),
+
+   as.data.frame(cbind((subset(df_fin, eth_lib_loc != 0 &  eth_lib_min != 0) %>% gather(subgroup, Segra, de_sq_bl,dv_sq_bl)),t="Conservative Majority_et",tt = "cmj_et")),
+           as.data.frame(cbind((subset(df_fin,  eth_lib_loc != 0 &  eth_lib_min != 0) %>% gather(subgroup, Segra, de_cl_bl,dv_cl_bl)),t="Liberal Majority_et",tt = "lmj_et")),
+            as.data.frame(cbind((subset(df_fin,  eth_lib_loc != 0 &  eth_lib_min != 0)  %>% gather(subgroup, Segra, de_sq_or,dv_sq_or)),t="Conservative Minority_et",tt = "cmn_et")),
+           as.data.frame(cbind((subset(df_fin,  eth_lib_loc != 0 &  eth_lib_min != 0) %>% gather(subgroup, Segra, de_cl_or,dv_cl_or)),t="Liberal Minority_et",tt = "lmn_et"))
+           )
+
+for (i in sb) {
+pl <-  ggplot(i, aes(x=circle_orange,y=Segra,shape = subgroup, color = RND)) + geom_point() + geom_line() +
+  scale_shape_manual(values = c("square","circle"),labels = c("ethnic","Value"), guide = guide_legend(title = "Segregation", order = 1)) + 
     scale_color_manual(values = c("green","purple"),labels = c("high","low"), guide = guide_legend(title = "Randomness")) + 
-  scale_shape_manual(values = c("square","circle"),labels = c("ethnic","Value"), guide = guide_legend(title = "Segregation")) + 
  scale_x_discrete(limits = seq(10,90 ,by = 10)) +
-  facet_wrap(~ fraction_blue, nrow = 1) +
-  ggtitle("Conservative majority") +
-  theme_bw()
+  xlab("% Liberals Minority") +
+  ylab("Spatial Clustering") +
+  geom_hline(yintercept=1,color="red") +
+  facet_wrap(~ fraction_blue, nrow = 1, labeller = labeller(fraction_blue = ethnicity.labs)) +
+ ggtitle(i$t) +
+  theme_bw() +
+  theme(panel.spacing = unit(0.7, "lines"), legend.position = "bottom")
 
-lb <- subset(df_fin, eth_lib_loc ==0 & eth_lib_min == 0) %>% gather(subgroup, Segra, de_cl_bl,dv_cl_bl) %>% ggplot(aes(x=circle_orange,y=Segra,shape = subgroup, color = RND)) + geom_point() + geom_line() +
-  scale_color_manual(values = c("green","purple"),labels = c("high","low"), guide = guide_legend(title = "Randomness")) + 
-  scale_shape_manual(values = c("square","circle"),labels = c("ethnic","Value"), guide = guide_legend(title = "Segregation")) + 
- scale_x_discrete(limits = seq(10,90 ,by = 10)) +
-  facet_wrap(~ fraction_blue, nrow = 1) +
-  ggtitle("Liberals majority") +
-  theme_bw()
-
-cm <- subset(df_fin, eth_lib_loc ==0 & eth_lib_min == 0) %>% gather(subgroup, Segra, de_sq_or,dv_sq_or) %>% ggplot(aes(x=circle_orange,y=Segra,shape = subgroup, color = RND)) + geom_point() + geom_line() +
-  scale_color_manual(values = c("green","purple"),labels = c("high","low"), guide = guide_legend(title = "Randomness")) + 
-  scale_shape_manual(values = c("square","circle"),labels = c("ethnic","Value"), guide = guide_legend(title = "Segregation")) + 
- scale_x_discrete(limits = seq(10,90 ,by = 10)) +
-  facet_wrap(~ fraction_blue, nrow = 1) +
-  ggtitle("Conservative minority") +
-  theme_bw()
-
-lm <- subset(df_fin, eth_lib_loc ==0 & eth_lib_min == 0) %>% gather(subgroup, Segra, de_cl_or,dv_cl_or) %>% ggplot(aes(x=circle_orange,y=Segra,shape = subgroup, color = RND)) + geom_point() + geom_line() +
-  scale_color_manual(values = c("green","purple"),labels = c("high","low"), guide = guide_legend(title = "Randomness")) + 
-  scale_shape_manual(values = c("square","circle"),labels = c("ethnic","Value"), guide = guide_legend(title = "Segregation")) + 
- scale_x_discrete(limits = seq(10,90 ,by = 10)) +
-  facet_wrap(~ fraction_blue, nrow = 1) +
-  ggtitle("Liberals minority") +
-  theme_bw()
+plot(pl)
+nmn <- paste0(as.name(i$tt),".jpg")
+ggsave(nmn, pl,  path = "images")
+}
 
@@
 
+```{r OK Ethnic preference liberals, fig.cap= "Same preferences ethnic and value, liberals", echo =  FALSE}
+
+# equal size; liberals: value = ethnic
+
+df1 <- read.csv("et_mj.csv", skip=6)
+df2 <- read.csv("et_mj2.csv", skip=6)
+df3 <- read.csv("et_mn.csv", skip=6)
+df4 <- read.csv("et_mn2.csv", skip=6)
+
+df <- rbind(df3,df4)
+lg <- read.csv("lg_et_mj.csv", sep=";")[,1]
+
+names(df) <- lg
+
+excldf <- names(df) %in% c("run", "density","step")
+df <- df[!excldf]
+
+df <- df %>% group_by(fraction_blue,circle_blue,circle_orange,dominant,et_mj_on,et_mn_on) %>% summarise_all(mean)
+
+df <- df %>%  gather(key = subgroup, value = Segra, de_sq_bl,dv_sq_bl,de_cl_bl,dv_cl_bl,de_sq_or,dv_sq_or,de_cl_or,dv_cl_or)  %>% mutate(
+`segregation` = fct_relevel(fct_collapse(subgroup,"Ethnic" = c("de_sq_bl","de_cl_bl","de_sq_or","de_cl_or"), "Value" = c("dv_sq_bl","dv_cl_bl","dv_sq_or","dv_cl_or")),"Ethnic"), 
+ `ethnicity` = fct_relevel(fct_collapse(subgroup, "Majority" = c("de_sq_bl","dv_cl_bl","de_cl_bl","dv_sq_bl"), "Minority" = c("de_sq_or","de_cl_or","dv_sq_or","dv_cl_or")), "Majority"),
+`orientation` = fct_relevel(fct_collapse(subgroup,"Conservatives" = c("de_sq_bl","dv_sq_bl","de_sq_or","dv_sq_or"), "Liberals" = c("de_cl_bl","dv_cl_bl","de_cl_or","dv_cl_or")), "Conservatives"), 
+`type` = fct_relevel(fct_collapse(subgroup,"Conservative Majority" = c("de_sq_bl","dv_sq_bl"),
+      "Liberals Majority" = c("de_cl_bl","dv_cl_bl"),
+      "Conservative Minority" = c("de_sq_or","dv_sq_or"),
+      "Liberals Minority" = c("de_cl_or","dv_cl_or")), "Conservative Majority"))
+
+df %>% filter(et_mj_on == "false") %>% ggplot(aes(x= dominant,y = Segra, color = `segregation`, shape = `orientation`, linetype = et_mn_on)) + geom_point() + geom_line() +
+  scale_color_manual(values = c("green","purple"), guide = guide_legend(title = "Outcome")) +
+  scale_shape_manual(values = c("square","circle"), guide = guide_legend(title = "Orientation"))  +
+ # scale_y_continuous(limits=c(0.45,1), breaks=seq(0.5,1,by=0.1)) +
+  xlab("beta") +
+  ylab("Outcome") +
+  facet_wrap(~  `type` ) +
+  theme_bw()+
+  theme(legend.position = "bottom")
+
+```
+
+```{r determinism_area_X_ethnic_size, echo = FALSE}
+lg <-  read.csv("lg_etlib.csv",sep=";")[,1]
+etlb_bs <- read.csv("et_lib_fc_bothfalse.csv",sep=",",skip=6)
+names(etlb_bs) <- lg
+etlb_bs$ID <- "bsl"
+
+etlb_mj <- read.csv("et_lib_fc_mj.csv",sep=",",skip=6)
+names(etlb_mj) <- lg
+etlb_mj$ID <- "mj_et"
+
+etlb_mn <- read.csv("et_lib_fc_mn.csv",sep=",",skip=6)
+names(etlb_mn) <- lg
+etlb_mn$ID <- "mn_et"
+
+etlb <- rbind(etlb_bs,etlb_mj,etlb_mn) %>% group_by(density,fraction_blue,circle_blue,circle_orange,et_mn_on,et_mj_on,dominant,ID) %>% summarise_all(mean) %>%  gather(key = subgroup, value = Segra, de_sq_bl,dv_sq_bl,de_cl_bl,dv_cl_bl,de_sq_or,dv_sq_or,de_cl_or,dv_cl_or)  %>% mutate(
+`segregation` = fct_relevel(fct_collapse(subgroup,"Ethnic" = c("de_sq_bl","de_cl_bl","de_sq_or","de_cl_or"), "Value" = c("dv_sq_bl","dv_cl_bl","dv_sq_or","dv_cl_or")),"Ethnic"), 
+ `ethnicity` = fct_relevel(fct_collapse(subgroup, "Majority" = c("de_sq_bl","dv_cl_bl","de_cl_bl","dv_sq_bl"), "Minority" = c("de_sq_or","de_cl_or","dv_sq_or","dv_cl_or")), "Majority"),
+`orientation` = fct_relevel(fct_collapse(subgroup,"Conservatives" = c("de_sq_bl","dv_sq_bl","de_sq_or","dv_sq_or"), "Liberals" = c("de_cl_bl","dv_cl_bl","de_cl_or","dv_cl_or")), "Conservatives"), 
+`type` = fct_relevel(fct_collapse(subgroup,"Conservative Majority" = c("de_sq_bl","dv_sq_bl"),
+      "Liberals Majority" = c("de_cl_bl","dv_cl_bl"),
+      "Conservative Minority" = c("de_sq_or","dv_sq_or"),
+      "Liberals Minority" = c("de_cl_or","dv_cl_or")), "Conservative Majority"))
+
+etlb_df <- etlb %>% filter(fraction_blue == 50 | fraction_blue == 80)
+
+lmn <- ggplot(etlb_df[which(etlb_df$type  == "Liberals Minority"),],aes(x=dominant,y=Segra,  linetype = as.factor(ID) ,color= as.factor(`segregation`))) + geom_point(shape="square") + geom_line() +
+  facet_wrap(~ fraction_blue, scales = "free_y") +
+  theme_bw()
+
+cmj
+cmn
+
+lmj
+lmn
+
+pic_lm <- ggpubr::ggarrange(lmj,lmn, nrow = 2,  common.legend = T, legend = "bottom")
+
+pic_cm
+pic_lm
+
+```
+
 We only look at the behavior of liberals, as conservatives have minimal consequence. Combining the two plots looked awful
@@
 
-# etlib_maj <- df_etlib %>% filter(fraction_blue == 50 | fraction_blue == 80) %>% filter(eth_con_loc == 20 & eth_con_min == 20) %>% filter(val_con_loc == 0 & val_con_min == 0) %>% filter(eth_lib_min == 0)
-
 etlib_maj <- df_sec %>% filter(fraction_blue == 50 | fraction_blue == 80)  %>% gather(key = subgroup, value = Clustetmj, de_cl_bl,dv_cl_bl,de_cl_or,dv_cl_or) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"Ethnic" = c("de_cl_bl","de_cl_or"), "Value" = c("dv_cl_bl","dv_cl_or") ),"Ethnic"),
-              `ethnicity` = fct_relevel(fct_collapse(subgroup,"Liberals Majority" = c("de_cl_bl","dv_cl_bl"), "Liberals Minority" = c("de_cl_or","dv_cl_or")), "Liberals Majority")) # %>% filter(eth_lib_min == 0)
-
-# data_maj = etlib_maj[which(etlib_maj$ID == "etlib_loc" & etlib_maj$eth_lib_min == 0),]
+              `ethnicity` = fct_relevel(fct_collapse(subgroup,"Liberals Majority" = c("de_cl_bl","dv_cl_bl"), "Liberals Minority" = c("de_cl_or","dv_cl_or")), "Liberals Majority"))
 
@@
 
-ggpubr::ggarrange(libmaj,libmin, common.legend = TRUE, legend = "bottom")
+df_t <- df_sec %>% filter(fraction_blue == 80) %>% filter(val_lib_loc == 20 & eth_lib_loc == 20 & eth_con_loc == 20 & val_con_loc == 0 & val_con_min == 0 & eth_con_min == 5)
 
-# high randomness
+libmin <-  ggplot(data = etlib_maj[which(etlib_maj$ID == "etlib_min" & etlib_maj$eth_lib_loc == 7 & etlib_maj$eth_con_loc == 20  & etlib_maj$eth_con_min == 20 & etlib_maj$val_con_loc ==0 & etlib_maj$val_con_min == 0),], aes(x= eth_lib_min,y = Clustetmj,linetype= as.factor(fraction_blue), shape =`segregation`,color = `ethnicity`) ) +
+  geom_point(size=2) + geom_line() + 
+  facet_wrap(~`ethnicity`, dir = "v") +
+   scale_color_manual(values = c("blue","orange"), name = "Ethnicity") + 
+  scale_shape_manual(values = c("square","circle"), name = "Segregation") + 
+   scale_linetype_manual(values = c("solid","dashed"), labels = c("50%","80%"), name = "% Majority") +
+  xlab("ß ethnic liberals minority") +
+  ylab("Spatial Clustering") +
+  labs(caption = "ß ethnic liberals majority = 0") + theme_bw() +
+  guides(color = FALSE) +
+  theme(plot.caption = element_text(hjust = 0.5))
 
-# libmaj_h <-  ggplot(data =  etlib_maj[which(etlib_maj$ID == "etlib_loc" & etlib_maj$eth_lib_min == 0 & etlib_maj$eth_con_loc == 5  & etlib_maj$eth_con_min == 5 & etlib_maj$val_con_loc ==0 & etlib_maj$val_con_min == 0),], aes(x= eth_lib_loc,y = Clustetmj,linetype= as.factor(fraction_blue), shape =`segregation`,color = `ethnicity`) ) +
-#   geom_point(size=2) + geom_line() +
-#   facet_wrap(~`ethnicity`, dir = "v") +
-#    scale_color_manual(values = c("blue","orange"), name = "Ethnicity") +
-#   scale_shape_manual(values = c("square","circle"), name = "Segregation") +
-#    scale_linetype_manual(values = c("solid","dashed"), labels = c("50%","80%"), name = "% Majority") +
-#   xlab("ß ethnic liberals majority") +
-#   ylab("Spatial Clustering") +
-#   labs(caption = "ß ethnic liberals minority = 0") + theme_bw() +
-#   guides(color = FALSE) +
-#   theme(plot.caption = element_text(hjust = 0.5))
-# 
-# libmin_h <-  ggplot(data = etlib_maj[which(etlib_maj$ID == "etlib_min" & etlib_maj$eth_lib_loc == 0 & etlib_maj$eth_con_loc == 5  & etlib_maj$eth_con_min == 5 & etlib_maj$val_con_loc ==0 & etlib_maj$val_con_min == 0),], aes(x= eth_lib_min,y = Clustetmj,linetype= as.factor(fraction_blue), shape =`segregation`,color = `ethnicity`) ) +
-#   geom_point(size=2) + geom_line() + 
-#   facet_wrap(~`ethnicity`, dir = "v") +
-#    scale_color_manual(values = c("blue","orange"), name = "Ethnicity") + 
-#   scale_shape_manual(values = c("square","circle"), name = "Segregation") + 
-#    scale_linetype_manual(values = c("solid","dashed"), labels = c("50%","80%"), name = "% Majority") +
-#   xlab("ß ethnic liberals minority") +
-#   ylab("Spatial Clustering") +
-#   labs(caption = "ß ethnic liberals majority = 0") + theme_bw() +
-#   guides(color = FALSE) +
-#   theme(plot.caption = element_text(hjust = 0.5))
-# 
-# 
-# ggpubr::ggarrange(libmaj_h,libmin_h, common.legend = TRUE, legend = "bottom")
+eth_lib <-  ggpubr::ggarrange(libmaj,libmin, common.legend = TRUE, legend = "bottom")
 
-```
-
-```{r Ethnic liberals, fig.cap="Each grouptype, distribution liberals faceted by ethnic ratio", echo = FALSE}
-
-df_fin <- df_3D %>% mutate(RND = case_when(
-  val_lib_loc==5 & val_lib_min==5 & eth_con_loc == 5 & eth_con_min == 5 ~ "H",
-  val_lib_loc==20 & val_lib_min==20 & eth_con_loc == 20 & eth_con_min == 20 ~ "L"
-))
-
-subset(df_fin, eth_lib_loc != 0 & eth_lib_min != 0) %>% gather(subgroup, Segra, de_sq_bl,dv_sq_bl) %>% ggplot(aes(x=circle_orange,y=Segra,shape = subgroup, color = RND)) + geom_point() + geom_line() +
-  scale_color_manual(values = c("green","purple"),labels = c("high","low"), guide = guide_legend(title = "Randomness")) + 
-  scale_shape_manual(values = c("square","circle"),labels = c("ethnic","Value"), guide = guide_legend(title = "Segregation")) + 
- scale_x_discrete(limits = seq(10,90 ,by = 10)) +
-  facet_wrap(~ fraction_blue, nrow = 1) +
-  ggtitle("Conservative majority") +
-  theme_bw()
-
-subset(df_fin, eth_lib_loc != 0 & eth_lib_min != 0) %>% gather(subgroup, Segra, de_cl_bl,dv_cl_bl) %>% ggplot(aes(x=circle_orange,y=Segra,shape = subgroup, color = RND)) + geom_point() + geom_line() +
-  scale_color_manual(values = c("green","purple"),labels = c("high","low"), guide = guide_legend(title = "Randomness")) + 
-  scale_shape_manual(values = c("square","circle"),labels = c("ethnic","Value"), guide = guide_legend(title = "Segregation")) + 
- scale_x_discrete(limits = seq(10,90 ,by = 10)) +
-  facet_wrap(~ fraction_blue, nrow = 1) +
-  ggtitle("Liberals majority") +
-  theme_bw()
-
-subset(df_fin, eth_lib_loc != 0 & eth_lib_min != 0)  %>% gather(subgroup, Segra, de_sq_or,dv_sq_or) %>% ggplot(aes(x=circle_orange,y=Segra,shape = subgroup, color = RND)) + geom_point() + geom_line() +
-  scale_color_manual(values = c("green","purple"),labels = c("high","low"), guide = guide_legend(title = "Randomness")) + 
-  scale_shape_manual(values = c("square","circle"),labels = c("ethnic","Value"), guide = guide_legend(title = "Segregation")) + 
- scale_x_discrete(limits = seq(10,90 ,by = 10)) +
-  facet_wrap(~ fraction_blue, nrow = 1) +
-  ggtitle("Conservative minority") +
-  theme_bw()
-
-subset(df_fin, eth_lib_loc != 0 & eth_lib_min != 0) %>% gather(subgroup, Segra, de_cl_or,dv_cl_or) %>% ggplot(aes(x=circle_orange,y=Segra,shape = subgroup, color = RND)) + geom_point() + geom_line() +
-  scale_color_manual(values = c("green","purple"),labels = c("high","low"), guide = guide_legend(title = "Randomness")) + 
-  scale_shape_manual(values = c("square","circle"),labels = c("ethnic","Value"), guide = guide_legend(title = "Segregation")) + 
- scale_x_discrete(limits = seq(10,90 ,by = 10)) +
-  facet_wrap(~ fraction_blue, nrow = 1) +
-  ggtitle("Liberals minority") +
-  theme_bw()
-
-```
-
-```{r Ethnic liberalsT, fig.cap="Each grouptype, distribution liberals faceted by ethnic ratio", echo = FALSE}
-
-df_fin <- df_3D %>% mutate(RND = case_when(
-  val_lib_loc==5 & val_lib_min==5 & eth_con_loc == 5 & eth_con_min == 5 ~ "H",
-  val_lib_loc==20 & val_lib_min==20 & eth_con_loc == 20 & eth_con_min == 20 ~ "L"
-))
-
-sb <- list(
-  as.data.frame(cbind((subset(df_fin, eth_lib_loc != 0 & eth_lib_min != 0) %>% gather(subgroup, Segra, de_sq_bl,dv_sq_bl)),t="Conservative Majority")),
-           as.data.frame(cbind((subset(df_fin, eth_lib_loc != 0 & eth_lib_min != 0) %>% gather(subgroup, Segra, de_cl_bl,dv_cl_bl)),t="Liberal Majority")),
-            as.data.frame(cbind((subset(df_fin, eth_lib_loc != 0 & eth_lib_min != 0)  %>% gather(subgroup, Segra, de_sq_or,dv_sq_or)),t="Conservative Minority")),
-           as.data.frame(cbind((subset(df_fin, eth_lib_loc != 0 & eth_lib_min != 0) %>% gather(subgroup, Segra, de_cl_or,dv_cl_or)),t="Liberal Minority"))
-           )
-
-for (i in sb) {
-
-pl <-  ggplot(i, aes(x=circle_orange,y=Segra,shape = subgroup, color = RND)) + geom_point() + geom_line() +
-  scale_color_manual(values = c("green","purple"),labels = c("high","low"), guide = guide_legend(title = "Randomness")) + 
-  scale_shape_manual(values = c("square","circle"),labels = c("ethnic","Value"), guide = guide_legend(title = "Segregation")) + 
- scale_x_discrete(limits = seq(10,90 ,by = 10)) +
-  facet_wrap(~ fraction_blue, nrow = 1) +
- ggtitle(i$t) +
-  theme_bw()
-
-plot(pl)
-
-}
-
-```
-
-```{r 3Dsec, fig.cap="Increase ethnic preference, 3D", echo = FALSE}
-
-sec_3D_high <- df_3D %>% filter(val_lib_loc==5,val_lib_min==5,eth_con_loc == 5,eth_con_min == 5,eth_lib_loc ==5,eth_lib_min==5) 
-sec_3D_low <- df_3D %>% filter(val_lib_loc==20,val_lib_min==20,eth_con_loc == 20,eth_con_min == 20,eth_lib_loc ==20,eth_lib_min==20)
-
-xx <- ~fraction_blue
-yy <- ~circle_orange
-zz <- ~de_sq_or
-cols <- ~et_sq_or
-zzv <- ~dv_sq_or
-colsv <- ~vl_sq_or
-tt <- "Conservative Minority"
-
-D3_e <- {
-lowE_e <- plot_ly(sec_3D_high)  %>%
-  add_trace(x= xx,y= yy,z=zz,
-            scene = "scene1",
-            type="scatter3d",
-             mode="markers",
-             marker = list(
-             colorscale = "Reds",
-             color= cols, showscale =  T,
-             colorbar=list(title = "Ethnic \nExposure" ,x = -0.1,  len = 0.5, yanchor='bottom'))
-
-            )  %>%
-  layout(showlegend = F,
-         #title="Ethnic",
-         "scene1" = list(
-      xaxis = list(title = "Ethnic Ratio",range=seq(50,90,by=10),dtick=10),
-      yaxis = list(title = "% Liberal Minority" ,autorange = "reversed"),
-      zaxis = list(title = "Ethnic Cluster")))
-
- lowV_e<- plot_ly(sec_3D_high)  %>%   add_trace(x=xx,y=yy,z=zzv,
-             scene =  "scene2",
-             type="scatter3d",
-             mode="markers", 
-             marker = list( 
-             colorscale = "Blues",
-             color= colsv , showscale = T, reversescale=T,
-             colorbar=list(title = "Value  \nExposure", len=0.5, yanchor='bottom'))
-            )  %>% 
-       layout(showlegend = F,
-         "scene2" = list(
-      xaxis = list(title = "Ethnic Ratio",range=seq(50,90,by=10),dtick=10),
-      yaxis = list(title = "% Liberal Minority"  ,autorange = "reversed"),
-      zaxis = list(title = "Value Cluster")))
-
-highE_e <- plot_ly(sec_3D_low)  %>%
-  add_trace(x=xx,y=yy,z=zz,
-            scene = "scene3",
-            type="scatter3d",
-             mode="markers",
-             marker = list(
-             colorscale = "Reds",
-             color= cols, showscale =  T,
-             colorbar=list(title = "Ethnic \nExposure" ,x = -0.1,  len = 0.5, yanchor='top'))
-
-            )  %>%
-  layout(showlegend = F,
-         #title="Ethnic",
-         "scene3" = list(
-      xaxis = list(title = "Ethnic Ratio",range=seq(50,90,by=10),dtick=10),
-      yaxis = list(title = "% Liberal Minority" ,autorange = "reversed"),
-      zaxis = list(title = "Ethnic Cluster")))
-
- highV_e<- plot_ly(sec_3D_low)  %>%   
-    add_trace(x=xx,y=yy,z=zz,
-     scene =  "scene4",
-     type="scatter3d",
-     mode="markers", 
-     marker = list( 
-     colorscale = "Blues",
-     color= colsv , showscale = T, reversescale=T,
-      colorbar=list(title = "Value  \nExposure", len=0.5, yanchor='top'))
-            )  %>% 
-       layout(showlegend = F,
-         "scene4" = list(
-      xaxis = list(title = "Ethnic Ratio",range=seq(50,90,by=10),dtick=10),
-      yaxis = list(title = "% Liberal Minority"   ,autorange = "reversed"),
-      zaxis = list(title = "Value Cluster")))
-
-subplot(lowE_e, lowV_e,  highE_e, highV_e) %>%
-
-   layout(scene = list(domain=list(x=c(0,0.5),y=c(0.5,1)),zaxis = list(title = "Ethnic Cluster")),
-         scene2 = list(domain=list(x=c(0.5,1),y=c(0.5,1))),
-         scene3 = list(domain=list(x=c(0,0.5),y=c(0,0.5))),
-         scene4 = list(domain=list(x=c(0.5,1),y=c(0,0.5)))
-         ) %>%
-
-  layout(annotations = list(
-  text = tt,
-  font = list(size = 18),
-  xref = "paper",
-  yref = "paper",
-  yanchor = "bottom",
-  xanchor = "center",
-  align = "center",
-  x = 0.5,
-  y = 1,
-  showarrow = FALSE
-)
-
-) %>%
-  layout(annotations = list(
-  text = "High Randomness",
-  font = list(size = 15),
-  xref = "paper",
-  yref = "paper",
-  yanchor = "bottom",
-  xanchor = "center",
-  align = "center",
-  x = 0.5,
-  y = 0.5,
-  showarrow = FALSE
-))%>%
-  layout(annotations = list(
-  text = "Low Randomness",
-  font = list(size = 15),
-  xref = "paper",
-  yref = "paper",
-  yanchor = "bottom",
-  xanchor = "center",
-  align = "center",
-  x = 0.5,
-  y = 0,
-  showarrow = FALSE
-)
-
-)
-}
+ggsave( "eth_lib.jpg" , eth_lib,  path = "images")
 
@@
 etlib_maj <- df_sec %>% filter(fraction_blue == 50 | fraction_blue == 80)  %>% gather(key = subgroup, value = Clustetmj, de_sq_bl,dv_sq_bl,de_sq_or,dv_sq_or) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"Ethnic" = c("de_sq_bl","de_sq_or"), "Value" = c("dv_sq_bl","dv_sq_or") ),"Ethnic"),
-              `ethnicity` = fct_relevel(fct_collapse(subgroup,"Liberals Majority" = c("de_sq_bl","dv_sq_bl"), "Liberals Minority" = c("de_sq_or","dv_sq_or")), "Liberals Majority")) # %>% filter(eth_lib_min == 0)
+              `ethnicity` = fct_relevel(fct_collapse(subgroup,"Conservatives Majority" = c("de_sq_bl","dv_sq_bl"), "Conservatives Minority" = c("de_sq_or","dv_sq_or")), "Conservatives Majority")) # %>% filter(eth_lib_min == 0)
 
@@
 
-# high randomness
-
-# libmaj_h <-  ggplot(data =  etlib_maj[which(etlib_maj$ID == "etlib_loc" & etlib_maj$eth_lib_min == 0 & etlib_maj$eth_con_loc == 5  & etlib_maj$eth_con_min == 5 & etlib_maj$val_con_loc ==0 & etlib_maj$val_con_min == 0),], aes(x= eth_lib_loc,y = Clustetmj,linetype= as.factor(fraction_blue), shape =`segregation`,color = `ethnicity`) ) +
-#   geom_point(size=2) + geom_line() +
-#   facet_wrap(~`ethnicity`, dir = "v") +
-#    scale_color_manual(values = c("blue","orange"), name = "Ethnicity") +
-#   scale_shape_manual(values = c("square","circle"), name = "Segregation") +
-#    scale_linetype_manual(values = c("solid","dashed"), labels = c("50%","80%"), name = "% Majority") +
-#   xlab("ß ethnic liberals majority") +
-#   ylab("Spatial Clustering") +
-#   labs(caption = "ß ethnic liberals minority = 0") + theme_bw() +
-#   guides(color = FALSE) +
-#   theme(plot.caption = element_text(hjust = 0.5))
-# 
-# libmin_h <-  ggplot(data = etlib_maj[which(etlib_maj$ID == "etlib_min" & etlib_maj$eth_lib_loc == 0 & etlib_maj$eth_con_loc == 5  & etlib_maj$eth_con_min == 5 & etlib_maj$val_con_loc ==0 & etlib_maj$val_con_min == 0),], aes(x= eth_lib_min,y = Clustetmj,linetype= as.factor(fraction_blue), shape =`segregation`,color = `ethnicity`) ) +
-#   geom_point(size=2) + geom_line() + 
-#   facet_wrap(~`ethnicity`, dir = "v") +
-#    scale_color_manual(values = c("blue","orange"), name = "Ethnicity") + 
-#   scale_shape_manual(values = c("square","circle"), name = "Segregation") + 
-#    scale_linetype_manual(values = c("solid","dashed"), labels = c("50%","80%"), name = "% Majority") +
-#   xlab("ß ethnic liberals minority") +
-#   ylab("Spatial Clustering") +
-#   labs(caption = "ß ethnic liberals majority = 0") + theme_bw() +
-#   guides(color = FALSE) +
-#   theme(plot.caption = element_text(hjust = 0.5))
-# 
-# 
-# ggpubr::ggarrange(libmaj_h,libmin_h, common.legend = TRUE, legend = "bottom")
-
 ```
@@
 
-```{r sec_test, fig.cap="Keep it for annex: effect of liberals or conservatives secondary preference in low or high determinism", echo = FALSE}
+```{r sec_test, fig.cap="Secondary preference high and low randomness", echo = FALSE}
 
@@
 
-etlblc_high <- df_sec  %>% filter(fraction_blue == 80) %>% filter(ID == "etlib_loc", RND == "high", eth_lib_loc == 5 | eth_lib_loc == 0) %>% filter(eth_lib_min == 0) %>% gather(key = subgroup, value = Clus, de_sq_bl,dv_sq_bl,de_cl_bl,dv_cl_bl,de_sq_or,dv_sq_or,de_cl_or,dv_cl_or)
+# Value conservaties
 
-etlblc_high_pic <- ggplot(etlblc_high, aes(fill = as.factor(etlblc_high$eth_lib_loc), y= etlblc_high$Clus, x = etlblc_high$subgroup) ) + 
-    geom_bar(position="dodge", stat="identity") +
-  scale_fill_manual(values=c("red","blue")) +
-  scale_y_continuous(limits= c(0,6),breaks=seq(0,6,by=0.5))
+df_sec <-  df_sec  %>% gather(key = subgroup, value = Clus, de_sq_bl,dv_sq_bl,de_cl_bl,dv_cl_bl,de_sq_or,dv_sq_or,de_cl_or,dv_cl_or)  %>% mutate(
+          `segregation` = fct_relevel(fct_collapse(subgroup,"Ethnic" = c("de_sq_bl","de_cl_bl","de_sq_or","de_cl_or"), "Value" = c("dv_sq_bl","dv_cl_bl","dv_sq_or","dv_cl_or")),"Ethnic"), 
+          `ethnicity` = fct_relevel(fct_collapse(subgroup," Majority" = c("de_sq_bl","dv_cl_bl","de_cl_bl","dv_sq_bl"), "Minority" = c("de_sq_or","de_cl_or","dv_sq_or","dv_cl_or")), "Majority"),
+         `orientation` = fct_relevel(fct_collapse(subgroup,"Conservatives" = c("de_sq_bl","dv_sq_bl","de_sq_or","dv_sq_or"), "Liberals" = c("de_cl_bl","dv_cl_bl","de_cl_or","dv_cl_or")), "Conservatives")  )
 
-etlblc_low <- df_sec  %>% filter(fraction_blue == 80) %>% filter(ID == "etlib_loc", RND == "low", eth_lib_loc == 20 | eth_lib_loc == 0) %>% filter(eth_lib_min == 0) %>% gather(key = subgroup, value = Clus, de_sq_bl,dv_sq_bl,de_cl_bl,dv_cl_bl,de_sq_or,dv_sq_or,de_cl_or,dv_cl_or)
+df_sec_vlmjH<- df_sec  %>%  filter(fraction_blue == 80 & ID == "valuecon_loc" & val_con_min == 0 & RND == "high") %>% filter(val_con_loc == 0 |val_con_loc == 5) 
+df_sec_vlmjL <- df_sec  %>%  filter(fraction_blue == 80 & ID == "valuecon_loc" & val_con_min == 0 & RND == "low") %>% filter(val_con_loc == 0 |val_con_loc == 20)
 
-etlblc_low_pic <- ggplot(etlblc_low, aes(fill = as.factor(etlblc_low$eth_lib_loc), y= etlblc_low$Clus, x = etlblc_low$subgroup) ) + 
-    geom_bar(position="dodge", stat="identity") +
-  scale_fill_manual(values=c("red","blue")) +
-  scale_y_continuous(limits= c(0,6),breaks=seq(0,6,by=0.5))
+datas <- df_sec_vlmjH
+df_sec_vlmjH_p <- ggplot(datas, aes(x = val_con_loc,y = Clus, shape = `orientation` , color = `ethnicity` , linetype = `segregation`)) + geom_point() + geom_line() +
+  scale_x_discrete(limits= c(0,max(datas$val_con_loc)),breaks = c(0,max(datas$val_con_loc))) +
+  scale_y_continuous(breaks = seq(0,max(datas$Clus),by=0.5)) +
+  scale_shape_manual(values = c("square","circle"),labels = c("Conservatives","Liberals"), name= "Orientation")  +
+ scale_color_manual(values=c("blue","orange"),labels = c("Majority","Minority"), name= "Ethnicity")  + scale_linetype_manual(values=c("solid","dashed"),labels = c("Ethnic","Value"), name= "Segregation \ntype") +
+  ylab("Spatial Clustering") +
+  xlab("ß value Conservatives Majority") +
+  ggtitle(if (datas$RND == "high") {"High Randomness (dominant ß = 5)"}else{"Low Randomness (dominant ß = 20)"}) +
+  # ggtitle(if RND ="high"   "High Randomness (dominant ß = 5)") +
+  theme_bw()
 
-etlbmn_high <- df_sec  %>% filter(fraction_blue == 80) %>% filter(ID == "etlib_min", RND == "high", eth_lib_min == 5 | eth_lib_min == 0) %>% filter(eth_lib_loc == 0) %>% gather(key = subgroup, value = Clus, de_sq_bl,dv_sq_bl,de_cl_bl,dv_cl_bl,de_sq_or,dv_sq_or,de_cl_or,dv_cl_or)
+datas <- df_sec_vlmjL
+df_sec_vlmjL_p <-  ggplot(datas, aes(x = val_con_loc,y = Clus, shape = `orientation` , color = `ethnicity` , linetype = `segregation`)) + geom_point() + geom_line() +
+  scale_x_discrete(limits= c(0,max(datas$val_con_loc)),breaks = c(0,max(datas$val_con_loc))) +
+  scale_y_continuous(breaks = seq(0,max(datas$Clus),by=0.5)) +
+  scale_shape_manual(values = c("square","circle"),labels = c("Conservatives","Liberals"), name= "Orientation")  +
+ scale_color_manual(values=c("blue","orange"),labels = c("Majority","Minority"), name= "Ethnicity")  + scale_linetype_manual(values=c("solid","dashed"),labels = c("Ethnic","Value"), name= "Segregation \ntype") +
+  ylab("Spatial Clustering") +
+  xlab("ß value Conservatives Majority") +
+  ggtitle(if (datas$RND == "high") {"High Randomness (dominant ß = 5)"}else{"Low Randomness (dominant ß = 20)"}) +
+  # ggtitle(if RND ="high"   "High Randomness (dominant ß = 5)") +
+  theme_bw()
 
-etlbmn_high_pic <- ggplot(etlbmn_high, aes(fill = as.factor(etlbmn_high$eth_lib_min), y= etlbmn_high$Clus, x = etlbmn_high$subgroup) ) + 
-    geom_bar(position="dodge", stat="identity") +
-  scale_fill_manual(values=c("red","blue")) +
-  scale_y_continuous(limits= c(0,6),breaks=seq(0,6,by=0.5))
+df_sec_vlmnH<- df_sec  %>%  filter(fraction_blue == 80 & ID == "valuecon_min" & val_con_loc == 0 & RND == "high") %>% filter(val_con_min == 0 |val_con_min == 5) 
+df_sec_vlmnL <- df_sec  %>%  filter(fraction_blue == 80 & ID == "valuecon_min" & val_con_loc == 0 & RND == "low") %>% filter(val_con_min == 0 |val_con_min == 20)
 
-etlbmn_low <- df_sec  %>% filter(fraction_blue == 80) %>% filter(ID == "etlib_min", RND == "low", eth_lib_min == 20 | eth_lib_min == 0) %>% filter(eth_lib_loc == 0) %>% gather(key = subgroup, value = Clus, de_sq_bl,dv_sq_bl,de_cl_bl,dv_cl_bl,de_sq_or,dv_sq_or,de_cl_or,dv_cl_or)
+datas <- df_sec_vlmnH
+df_sec_vlmnH_p <-  ggplot(datas, aes(x = val_con_min,y = Clus, shape = `orientation` , color = `ethnicity` , linetype = `segregation`)) + geom_point() + geom_line() +
+  scale_x_discrete(limits= c(0,max(datas$val_con_min)),breaks = c(0,max(datas$val_con_min))) +
+  scale_y_continuous(breaks = seq(0,max(datas$Clus),by=0.5)) +
+  scale_shape_manual(values = c("square","circle"),labels = c("Conservatives","Liberals"), name= "Orientation")  +
+ scale_color_manual(values=c("blue","orange"),labels = c("Majority","Minority"), name= "Ethnicity")  + scale_linetype_manual(values=c("solid","dashed"),labels = c("Ethnic","Value"), name= "Segregation \ntype") +
+  ylab("Spatial Clustering") +
+  xlab("ß value Conservatives Minority") +
+  ggtitle(if (datas$RND == "high") {"High Randomness (dominant ß = 5)"}else{"Low Randomness (dominant ß = 20)"}) +
+  # ggtitle(if RND ="high"   "High Randomness (dominant ß = 5)") +
+  theme_bw()
 
-etlbmn_low_pic <- ggplot(etlbmn_low, aes(fill = as.factor(etlbmn_low$eth_lib_min), y= etlbmn_low$Clus, x = etlbmn_low$subgroup) ) + 
-    geom_bar(position="dodge", stat="identity") +
-  scale_fill_manual(values=c("red","blue")) +
-  scale_y_continuous(limits= c(0,6),breaks=seq(0,6,by=0.5))
+datas <- df_sec_vlmnL
+df_sec_vlmnL_p <-  ggplot(datas, aes(x = val_con_min,y = Clus, shape = `orientation` , color = `ethnicity` , linetype = `segregation`)) + geom_point() + geom_line() +
+  scale_x_discrete(limits= c(0,max(datas$val_con_min)),breaks = c(0,max(datas$val_con_min))) +
+  scale_y_continuous(breaks = seq(0,max(datas$Clus),by=0.5)) +
+  scale_shape_manual(values = c("square","circle"),labels = c("Conservatives","Liberals"), name= "Orientation")  +
+ scale_color_manual(values=c("blue","orange"),labels = c("Majority","Minority"), name= "Ethnicity")  + scale_linetype_manual(values=c("solid","dashed"),labels = c("Ethnic","Value"), name= "Segregation \ntype") +
+  ylab("Spatial Clustering") +
+  xlab("ß value Conservatives Minority") +
+  ggtitle(if (datas$RND == "high") {"High Randomness (dominant ß = 5)"}else{"Low Randomness (dominant ß = 20)"}) +
+  # ggtitle(if RND ="high"   "High Randomness (dominant ß = 5)") +
+  theme_bw()
 
-vlcnlc_low <- df_sec  %>% filter(fraction_blue == 80) %>% filter(ID == "valuecon_loc", RND == "low", val_con_loc == 20 | val_con_loc == 0) %>% filter(val_con_min == 0) %>% gather(key = subgroup, value = Clus, de_sq_bl,dv_sq_bl,de_cl_bl,dv_cl_bl,de_sq_or,dv_sq_or,de_cl_or,dv_cl_or)
+ggpubr::ggarrange(df_sec_vlmjH_p,df_sec_vlmjL_p,df_sec_vlmnH_p,df_sec_vlmnL_p, common.legend = TRUE, legend = "bottom")
 
-vlcnlc_low_pic <- ggplot(vlcnlc_low, aes(fill = as.factor(vlcnlc_low$val_con_loc), y= vlcnlc_low$Clus, x = vlcnlc_low$subgroup) ) + 
-    geom_bar(position="dodge", stat="identity") +
-  scale_fill_manual(values=c("red","blue")) +
-  scale_y_continuous(limits= c(0,6),breaks=seq(0,6,by=0.5))
+# Ethnic liberals
 
-vlcnlc_high <- df_sec  %>% filter(fraction_blue == 80) %>% filter(ID == "valuecon_loc", RND == "high", val_con_loc == 5 | val_con_loc == 0) %>% filter(val_con_min == 0) %>% gather(key = subgroup, value = Clus, de_sq_bl,dv_sq_bl,de_cl_bl,dv_cl_bl,de_sq_or,dv_sq_or,de_cl_or,dv_cl_or)
+df_sec <-  df_sec  %>% gather(key = subgroup, value = Clus, de_sq_bl,dv_sq_bl,de_cl_bl,dv_cl_bl,de_sq_or,dv_sq_or,de_cl_or,dv_cl_or)  %>% mutate(
+          `segregation` = fct_relevel(fct_collapse(subgroup,"Ethnic" = c("de_sq_bl","de_cl_bl","de_sq_or","de_cl_or"), "Value" = c("dv_sq_bl","dv_cl_bl","dv_sq_or","dv_cl_or")),"Ethnic"), 
+          `ethnicity` = fct_relevel(fct_collapse(subgroup," Majority" = c("de_sq_bl","dv_cl_bl","de_cl_bl","dv_sq_bl"), "Minority" = c("de_sq_or","de_cl_or","dv_sq_or","dv_cl_or")), "Majority"),
+         `orientation` = fct_relevel(fct_collapse(subgroup,"Conservatives" = c("de_sq_bl","dv_sq_bl","de_sq_or","dv_sq_or"), "Liberals" = c("de_cl_bl","dv_cl_bl","de_cl_or","dv_cl_or")), "Conservatives")  )
 
-vlcnlc_high_pic <- ggplot(vlcnlc_high, aes(fill = as.factor(vlcnlc_high$val_con_loc), y= vlcnlc_high$Clus, x = vlcnlc_high$subgroup) ) + 
-    geom_bar(position="dodge", stat="identity") +
-  scale_fill_manual(values=c("red","blue")) +
-  scale_y_continuous(limits= c(0,6),breaks=seq(0,6,by=0.5))
+df_sec_etmjH<- df_sec  %>%  filter(fraction_blue == 80 & ID == "etlib_loc" & eth_lib_min == 0 & RND == "high") %>% filter(eth_lib_loc == 0 |eth_lib_loc == 5) 
+df_sec_etmjL <- df_sec  %>%  filter(fraction_blue == 80 & ID == "etlib_loc" & eth_lib_min == 0 & RND == "low") %>% filter(eth_lib_loc == 0 |eth_lib_loc == 20)
 
-vlcnmn_low <- df_sec  %>% filter(fraction_blue == 80) %>% filter(ID == "valuecon_min", RND == "low", val_con_min == 20 | val_con_min == 0) %>% filter(val_con_loc == 0) %>% gather(key = subgroup, value = Clus, de_sq_bl,dv_sq_bl,de_cl_bl,dv_cl_bl,de_sq_or,dv_sq_or,de_cl_or,dv_cl_or)
+datas <- df_sec_etmjH
+df_sec_etmjH_p <- ggplot(datas, aes(x = eth_lib_loc,y = Clus, shape = `orientation` , color = `ethnicity` , linetype = `segregation`)) + geom_point() + geom_line() +
+  scale_x_discrete(limits= c(0,max(datas$eth_lib_loc)),breaks = c(0,max(datas$eth_lib_loc))) +
+  scale_y_continuous(breaks = seq(0,max(datas$Clus),by=0.5)) +
+  scale_shape_manual(values = c("square","circle"),labels = c("Conservatives","Liberals"), name= "Orientation")  +
+ scale_color_manual(values=c("blue","orange"),labels = c("Majority","Minority"), name= "Ethnicity")  + scale_linetype_manual(values=c("solid","dashed"),labels = c("Ethnic","Value"), name= "Segregation \ntype") +
+  ylab("Spatial Clustering") +
+  xlab("ß Ethnic Liberals Majority") +
+  ggtitle(if (datas$RND == "high") {"High Randomness (dominant ß = 5)"}else{"Low Randomness (dominant ß = 20)"}) +
+  # ggtitle(if RND ="high"   "High Randomness (dominant ß = 5)") +
+  theme_bw()
 
-vlcnmn_low_pic <- ggplot(vlcnmn_low, aes(fill = as.factor(vlcnmn_low$val_con_min), y= vlcnmn_low$Clus, x = vlcnmn_low$subgroup) ) + 
-    geom_bar(position="dodge", stat="identity") +
-  scale_fill_manual(values=c("red","blue")) +
-  scale_y_continuous(limits= c(0,6),breaks=seq(0,6,by=0.5))
+datas <- df_sec_etmjL
+df_sec_etmjL_p <-  ggplot(datas, aes(x = eth_lib_loc,y = Clus, shape = `orientation` , color = `ethnicity` , linetype = `segregation`)) + geom_point() + geom_line() +
+  scale_x_discrete(limits= c(0,max(datas$eth_lib_loc)),breaks = c(0,max(datas$eth_lib_loc))) +
+  scale_y_continuous(breaks = seq(0,max(datas$Clus),by=0.5)) +
+  scale_shape_manual(values = c("square","circle"),labels = c("Conservatives","Liberals"), name= "Orientation")  +
+ scale_color_manual(values=c("blue","orange"),labels = c("Majority","Minority"), name= "Ethnicity")  + scale_linetype_manual(values=c("solid","dashed"),labels = c("Ethnic","Value"), name= "Segregation \ntype") +
+  ylab("Spatial Clustering") +
+  xlab("ß Ethnic Liberals Majority") +
+  ggtitle(if (datas$RND == "high") {"High Randomness (dominant ß = 5)"}else{"Low Randomness (dominant ß = 20)"}) +
+  # ggtitle(if RND ="high"   "High Randomness (dominant ß = 5)") +
+  theme_bw()
 
-vlcnmn_high <- df_sec  %>% filter(fraction_blue == 80) %>% filter(ID == "valuecon_min", RND == "high", val_con_min == 5 | val_con_min == 0) %>% filter(val_con_loc == 0) %>% gather(key = subgroup, value = Clus, de_sq_bl,dv_sq_bl,de_cl_bl,dv_cl_bl,de_sq_or,dv_sq_or,de_cl_or,dv_cl_or)
+df_sec_etmnH<- df_sec  %>%  filter(fraction_blue == 80 & ID == "etlib_min" & eth_lib_loc == 0 & RND == "high") %>% filter(eth_lib_min == 0 |eth_lib_min == 5) 
+df_sec_etmnL <- df_sec  %>%  filter(fraction_blue == 80 & ID == "etlib_min" & eth_lib_loc == 0 & RND == "low") %>% filter(eth_lib_min == 0 |eth_lib_min == 20)
 
-vlcnmn_high_pic <- ggplot(vlcnmn_high, aes(fill = as.factor(vlcnmn_high$val_con_min), y= vlcnmn_high$Clus, x = vlcnmn_high$subgroup) ) + 
-    geom_bar(position="dodge", stat="identity") +
-  scale_fill_manual(values=c("red","blue")) +
-  scale_y_continuous(limits= c(0,6),breaks=seq(0,6,by=0.5))
+datas <- df_sec_etmnH
+df_sec_etmnH_p <-  ggplot(datas, aes(x = eth_lib_min,y = Clus, shape = `orientation` , color = `ethnicity` , linetype = `segregation`)) + geom_point() + geom_line() +
+  scale_x_discrete(limits= c(0,max(datas$eth_lib_min)),breaks = c(0,max(datas$eth_lib_min))) +
+  scale_y_continuous(breaks = seq(0,max(datas$Clus),by=0.5)) +
+  scale_shape_manual(values = c("square","circle"),labels = c("Conservatives","Liberals"), name= "Orientation")  +
+ scale_color_manual(values=c("blue","orange"),labels = c("Majority","Minority"), name= "Ethnicity")  + scale_linetype_manual(values=c("solid","dashed"),labels = c("Ethnic","Value"), name= "Segregation \ntype") +
+  ylab("Spatial Clustering") +
+  xlab("ß Ethnic Liberals Minority") +
+  ggtitle(if (datas$RND == "high") {"High Randomness (dominant ß = 5)"}else{"Low Randomness (dominant ß = 20)"}) +
+  # ggtitle(if RND ="high"   "High Randomness (dominant ß = 5)") +
+  theme_bw()
 
-# ggplotly(etlblc_high_pic)
-# ggplotly(etlblc_low_pic)
-# ggplotly(etlbmn_high_pic)
-# ggplotly(etlbmn_low_pic)
-# ggplotly(vlcnlc_low_pic)
-# ggplotly(vlcnlc_high_pic)
-# ggplotly(vlcnmn_low_pic)
-# ggplotly(vlcnmn_high_pic)
+datas <- df_sec_etmnL
+df_sec_etmnL_p <-  ggplot(datas, aes(x = eth_lib_min,y = Clus, shape = `orientation` , color = `ethnicity` , linetype = `segregation`)) + geom_point() + geom_line() +
+  scale_x_discrete(limits= c(0,max(datas$eth_lib_min)),breaks = c(0,max(datas$eth_lib_min))) +
+  scale_y_continuous(breaks = seq(0,max(datas$Clus),by=0.5)) +
+  scale_shape_manual(values = c("square","circle"),labels = c("Conservatives","Liberals"), name= "Orientation")  +
+ scale_color_manual(values=c("blue","orange"),labels = c("Majority","Minority"), name= "Ethnicity")  + scale_linetype_manual(values=c("solid","dashed"),labels = c("Ethnic","Value"), name= "Segregation \ntype") +
+  ylab("Spatial Clustering") +
+  xlab("ß Ethnic Liberals Minority") +
+  ggtitle(if (datas$RND == "high") {"High Randomness (dominant ß = 5)"}else{"Low Randomness (dominant ß = 20)"}) +
+  # ggtitle(if RND ="high"   "High Randomness (dominant ß = 5)") +
+  theme_bw()
 
-etlblc_high_pic
-etlblc_low_pic
-etlbmn_high_pic
-etlbmn_low_pic
-vlcnlc_low_pic
-vlcnlc_high_pic
-vlcnmn_low_pic
-vlcnmn_high_pic
-
+ggpubr::ggarrange(df_sec_etmjH_p,df_sec_etmjL_p,df_sec_etmnH_p,df_sec_etmnL_p, common.legend = TRUE, legend = "bottom")
 ```
@@
 
-# high randomness
-
-# conmaj_h <-  ggplot(data =  etlib_cons[which(etlib_cons$ID == "etlib_loc" & etlib_cons$eth_lib_min == 0 & etlib_cons$eth_con_loc == 5 & etlib_cons$eth_con_min == 5),], aes(x= eth_lib_loc,y = Clustetmj,linetype= as.factor(fraction_blue), shape =`segregation`,color = `ethnicity`) ) +
-#   geom_point(size=2) + geom_line() +
-#   facet_wrap(~`ethnicity`, dir = "v") +
-#    scale_color_manual(values = c("blue","orange"), name = "Ethnicity") +
-#   scale_shape_manual(values = c("square","circle"), name = "Segregation") +
-#    scale_linetype_manual(values = c("solid","dashed"), labels = c("50%","80%"), name = "% Majority") +
-#   xlab("ß ethnic liberals majority") +
-#   ylab("Spatial Clustering") +
-#   labs(caption = "ß ethnic liberals minority = 0") + theme_bw() +
-#   guides(color = FALSE) +
-#   theme(plot.caption = element_text(hjust = 0.5))
-# 
-# conmin_h <-  ggplot(data = etlib_cons[which(etlib_cons$ID == "etlib_min" & etlib_cons$eth_lib_loc == 0 & etlib_cons$eth_con_loc == 5 &  etlib_cons$eth_con_min == 5),], aes(x= eth_lib_min,y = Clustetmj,linetype= as.factor(fraction_blue), shape =`segregation`,color = `ethnicity`) ) +
-#   geom_point(size=2) + geom_line() + 
-#   facet_wrap(~`ethnicity`, dir = "v") +
-#    scale_color_manual(values = c("blue","orange"), name = "Ethnicity") + 
-#   scale_shape_manual(values = c("square","circle"), name = "Segregation") + 
-#    scale_linetype_manual(values = c("solid","dashed"), labels = c("50%","80%"), name = "% Majority") +
-#   xlab("ß ethnic liberals minority") +
-#   ylab("Spatial Clustering") +
-#   labs(caption = "ß ethnic liberals majority = 0") + theme_bw() +
-#   guides(color = FALSE) +
-#   theme(plot.caption = element_text(hjust = 0.5))
-#  
-# 
-# ggpubr::ggarrange(conmaj_h,conmin_h, common.legend = TRUE, legend = "bottom") 
-# 
-# ggplotly(conmaj)
-
 ```
-
-### Delete
-
-```{r to write 3D csv, delete}
-# trd <- read.csv("vlmaj_ethrat_3D_1.csv",sep=",",skip = 6)
-# trd2 <- read.csv("vlmaj_ethrat_3D_2.csv",sep=",",skip = 6)
-# lgnd <- read.csv("legend_sa_asym.csv",sep=";")[,1]
-# names(trd2) <- lgnd
-# 
-# trd_f <- rbind(trd,trd2)
-# 
-# trdmin <- read.csv("vlmin_ethrat_3D_1.csv",sep=",",skip = 6)
-# trd2min <- read.csv("vlmin_ethrat_3D_2.csv",sep=",",skip = 6)
-# names(trdmin) <- lgnd
-# names(trd2min) <- lgnd
-# 
-# trdmin_f <- rbind(trdmin,trd2min)
-# 
-# etlib_mj <- read.csv("etlib_loc_3D_1.csv",sep=",",skip = 6)
-# lget <- read.csv("legend_etlib.csv",sep=";")[,1]
-# names(etlib_mj) <- lget
-# 
-# 
-# order <- c("run","density","fraction_blue", "circle_blue","circle_orange" ,"eth_con_loc","val_lib_loc", "eth_con_min" , "val_lib_min" ,  "val_con_loc","eth_lib_loc","val_con_min" ,  "eth_lib_min",   "step"  , "et_sq_bl" , "et_cl_bl" ,"et_sq_or","et_cl_or","vl_sq_bl","vl_cl_bl","vl_sq_or","vl_cl_or","de_sq_bl","de_cl_bl","de_sq_or","de_cl_or","dv_sq_bl","dv_cl_bl","dv_sq_or","dv_cl_or")
-# 
-# etlib_mj <- etlib_mj[,order]
-# 
-# etlib_mj2 <- read.csv("etlib_loc_3D_2.csv",sep=",",skip = 6)
-# names(etlib_mj2) <- lget
-# 
-# etlib_mj2 <- etlib_mj2[,order]
-# 
-# df <- rbind(trdmin_f,etlib_mj,etlib_mj2)
-# 
-# etmin <- read.csv("etlib_min_3D_1.csv",sep = ",",skip = 6)
-# names(etmin) <- lget
-# 
-# etmin2 <- read.csv("etlib_min_3D_2.csv",sep = ",",skip = 6)
-# names(etmin2) <- lget
-# 
-# etmin_all <- rbind(etmin,etmin2)
-# 
-# etmin_all <- etmin_all[,order]
-# 
-# df_f <- rbind(df,etmin_all)
-# 
-# write.csv(df_f,"3D.csv",row.names = F)
-```
-
-```{r beta_maj, fig.cap="x-axis value liberals maj vs min, each group", echo = FALSE}
-#####
-# effect on ethnic and value preference of conservatives
-
-consmj_majlib <- ggplot(data=mech_cons) + geom_point(aes(x=mech_cons$val_lib_loc,y=mech_cons$de_sq_bl,color=mech_cons$et_sq_bl),shape=15)  + 
-  geom_line(aes(x=mech_cons$val_lib_loc,y=mech_cons$de_sq_bl,linetype=as.factor(mech_cons$fraction_blue)),color="blue") +
-   scale_color_gradient(low = "grey", high = "brown") +
-geom_point(aes(x=mech_cons$val_lib_loc,y=mech_cons$dv_sq_bl,color=mech_cons$vl_sq_bl),shape =15) +
-    geom_line(aes(x=mech_cons$val_lib_loc,y=mech_cons$dv_sq_bl,linetype=as.factor(mech_cons$fraction_blue)),color="darkorange") +
-  facet_wrap(~mech_cons$val_lib_min,dir="v") +
-  theme(legend.position = "bottom")
-
-consmj_minlib <- ggplot(data=mech_lib) + geom_point(aes(x=mech_lib$val_lib_min,y=mech_lib$de_sq_bl,color=mech_lib$et_sq_bl),shape=15)  + 
-  geom_line(aes(x=mech_lib$val_lib_min,y=mech_lib$de_sq_bl,linetype=as.factor(mech_lib$fraction_blue)),color="blue") +
-   scale_color_gradient(low = "grey", high = "brown") +
-geom_point(aes(x=mech_lib$val_lib_min,y=mech_lib$dv_sq_bl,color=mech_lib$vl_sq_bl),shape =15) +
-    geom_line(aes(x=mech_lib$val_lib_min,y=mech_lib$dv_sq_bl,linetype=as.factor(mech_lib$fraction_blue)),color="darkorange") +
-  facet_wrap(~mech_lib$val_lib_loc,dir="v") +
-  theme(legend.position = "bottom")
-
-ggplotly(consmj_majlib)
-ggplotly(consmj_minlib)
-
-ggpubr::ggarrange(consmj_majlib,consmj_minlib)
-
-##
-
-consmn_majlib <- ggplot(data=mech_cons) + geom_point(aes(x=mech_cons$val_lib_loc,y=mech_cons$de_sq_or,color=mech_cons$et_sq_or),shape=15)  + 
-  geom_line(aes(x=mech_cons$val_lib_loc,y=mech_cons$de_sq_or,linetype=as.factor(mech_cons$fraction_blue)),color="blue") +
-   scale_color_gradient(low = "grey", high = "brown") +
-  scale_y_continuous(limits=c(0.5,5),breaks = seq(0,5,by=1)) +
-geom_point(aes(x=mech_cons$val_lib_loc,y=mech_cons$dv_sq_or,color=mech_cons$vl_sq_or),shape =15) +
-    geom_line(aes(x=mech_cons$val_lib_loc,y=mech_cons$dv_sq_or,linetype=as.factor(mech_cons$fraction_blue)),color="darkorange") +
-  facet_wrap(~mech_cons$val_lib_min,dir="v") +
-  theme(legend.position = "bottom")
-
-consmn_minlib <- ggplot(data=mech_lib) + geom_point(aes(x=mech_lib$val_lib_min,y=mech_lib$de_sq_or,color=mech_lib$et_sq_or),shape=15)  + 
-  geom_line(aes(x=mech_lib$val_lib_min,y=mech_lib$de_sq_or,linetype=as.factor(mech_lib$fraction_blue)),color="blue") +
-   scale_color_gradient(low = "grey", high = "brown") +
-   scale_y_continuous(limits=c(0.9,5),breaks = seq(0,5,by=1)) +
-geom_point(aes(x=mech_lib$val_lib_min,y=mech_lib$dv_sq_or,color=mech_lib$vl_sq_or),shape =15) +
-    geom_line(aes(x=mech_lib$val_lib_min,y=mech_lib$dv_sq_or,linetype=as.factor(mech_lib$fraction_blue)),color="darkorange") +
-  facet_wrap(~mech_lib$val_lib_loc,dir="v") +
-  theme(legend.position = "bottom")
-
-ggplotly(consmn_majlib)
-ggplotly(consmn_minlib)
-
-ggpubr::ggarrange(consmn_majlib,consmn_minlib)
-
-#####
-#behavior liberals
-
-libmj_maj <- ggplot(data=mech_cons) + geom_point(aes(x=mech_cons$val_lib_loc,y=mech_cons$de_cl_bl,color=mech_cons$et_cl_bl),shape="square")  + geom_line(aes(x=mech_cons$val_lib_loc,y=mech_cons$de_cl_bl,linetype=as.factor(mech_cons$fraction_blue)),color="blue") +
-   scale_color_gradient(low = "grey", high = "brown") +
-geom_point(aes(x=mech_cons$val_lib_loc,y=mech_cons$dv_cl_bl,color=mech_cons$vl_cl_bl),shape ="circle") +
-    geom_line(aes(x=mech_cons$val_lib_loc,y=mech_cons$dv_cl_bl,linetype=as.factor(mech_cons$fraction_blue)),color="darkorange") +
-  facet_wrap(~mech_cons$val_lib_min,dir="v") +
-  theme(legend.position = "bottom")
-
-libmj_min <-  ggplot(data=mech_lib) + geom_point(aes(x=mech_lib$val_lib_min,y=mech_lib$de_cl_bl,color=mech_lib$et_cl_bl),shape="square")  + 
-  geom_line(aes(x=mech_lib$val_lib_min,y=mech_lib$de_cl_bl,linetype=as.factor(mech_lib$fraction_blue)),color="blue") +
-   scale_color_gradient(low = "grey", high = "brown") +
-geom_point(aes(x=mech_lib$val_lib_min,y=mech_lib$dv_cl_bl,color=mech_lib$vl_cl_bl),shape ="circle") +
-    geom_line(aes(x=mech_lib$val_lib_min,y=mech_lib$dv_cl_bl,linetype=as.factor(mech_lib$fraction_blue)),color="darkorange") +
-  facet_wrap(~mech_lib$val_lib_loc,dir="v") +
-  theme(legend.position = "bottom")
-
-ggplotly(libmj_maj)
-ggplotly(libmj_min)
-
-ggpubr::ggarrange(libmj_maj,libmj_min)
-
-libmn_maj <- ggplot(data=mech_cons) + geom_point(aes(x=mech_cons$val_lib_loc,y=mech_cons$de_cl_or,color=mech_cons$et_cl_or),shape="square")  + geom_line(aes(x=mech_cons$val_lib_loc,y=mech_cons$de_cl_or,linetype=as.factor(mech_cons$fraction_blue)),color="blue") +
-   scale_color_gradient(low = "grey", high = "brown") +
-geom_point(aes(x=mech_cons$val_lib_loc,y=mech_cons$dv_cl_or,color=mech_cons$vl_cl_or),shape ="circle") +
-    geom_line(aes(x=mech_cons$val_lib_loc,y=mech_cons$dv_cl_or,linetype=as.factor(mech_cons$fraction_blue)),color="darkorange") +
-  facet_wrap(~mech_cons$val_lib_min,dir="v") +
-  theme(legend.position = "bottom")
-
-libmn_min <-  ggplot(data=mech_lib) + geom_point(aes(x=mech_lib$val_lib_min,y=mech_lib$de_cl_or,color=mech_lib$et_cl_or),shape="square")  + 
-  geom_line(aes(x=mech_lib$val_lib_min,y=mech_lib$de_cl_or,linetype=as.factor(mech_lib$fraction_blue)),color="blue") +
-   scale_color_gradient(low = "grey", high = "brown") +
-geom_point(aes(x=mech_lib$val_lib_min,y=mech_lib$dv_cl_or,color=mech_lib$vl_cl_or),shape ="circle") +
-    geom_line(aes(x=mech_lib$val_lib_min,y=mech_lib$dv_cl_or,linetype=as.factor(mech_lib$fraction_blue)),color="darkorange") +
-  facet_wrap(~mech_lib$val_lib_loc,dir="v") +
-  theme(legend.position = "bottom")
-
-ggplotly(libmn_maj)
-ggplotly(libmn_min)
-
-ggpubr::ggarrange(libmj_maj,libmj_min)
-ggpubr::ggarrange(libmn_maj,libmn_min)
-
-#####
-# too complicated
-
-lib_loc <- ggplot(data=mech_cons) + geom_point(aes(x=mech_cons$val_lib_loc,y=mech_cons$dv_sq_bl,color=mech_cons$vl_sq_bl),shape=15)  + 
-  geom_line(aes(x=mech_cons$val_lib_loc,y=mech_cons$dv_sq_bl,linetype=as.factor(mech_cons$val_lib_min)),color="blue") +
-   scale_color_gradient(low = "grey", high = "brown") +
-geom_point(aes(x=mech_cons$val_lib_loc,y=mech_cons$dv_sq_or,color=mech_cons$vl_sq_or),shape =15) +
-    geom_line(aes(x=mech_cons$val_lib_loc,y=mech_cons$dv_sq_or,linetype=as.factor(mech_cons$val_lib_min)),color="darkorange") +
-  facet_wrap(~mech_cons$fraction_blue,dir="v") +
-  theme(legend.position = "bottom")
-
-lib_min <- ggplot(data=mech_lib) + geom_point(aes(x=mech_lib$val_lib_min,y=mech_lib$dv_sq_bl,color=mech_lib$vl_sq_bl),shape=15)  + 
-  geom_line(aes(x=mech_lib$val_lib_min,y=mech_lib$dv_sq_bl,linetype=as.factor(mech_lib$val_lib_loc)),color="blue") +
-   scale_color_gradient(low = "grey", high = "brown") +
-geom_point(aes(x=mech_lib$val_lib_min,y=mech_lib$dv_sq_or,color=mech_lib$vl_sq_or),shape =15) +
-    geom_line(aes(x=mech_lib$val_lib_min,y=mech_lib$dv_sq_or,linetype=as.factor(mech_lib$val_lib_loc)),color="darkorange") +
-  facet_wrap(~mech_lib$fraction_blue,dir="v") +
-  theme(legend.position = "bottom")
-
-ggplotly(lib_loc)
-ggplotly(lib_min)
-ggpubr::ggarrange(lib_loc,lib_min,common.legend = TRUE)
-
-#####
-# fraction: take 50 65 80, beta = 0, 1, 7
-
-df_min <- read.csv("vlmin_ethrat_1.csv",sep = ",",skip = 6)
-legend <- read.csv("legend_sa_asym.csv",sep = ";")
-legend <- as.data.frame(legend[,-2])
-names(df_min) <- pull(legend)
-
-df_maj <- read.csv("vlmaj_ethrat_1.csv",sep = ",",skip = 6)
-names(df_maj) <- pull(legend)
-
-excl <- names(df_min) %in% c("run", "density","step")
-df_min <- df_min[!excl] %>% group_by(eth_con_loc, eth_con_min,eth_lib_loc,eth_lib_min,val_lib_loc,val_lib_min,val_con_loc,val_con_min,circle_orange,circle_blue,fraction_blue) %>% summarise_all(mean)
-
-excl <- names(df_maj) %in% c("run", "density","step")
-df_maj <- df_maj[!excl] %>% group_by(eth_con_loc, eth_con_min,eth_lib_loc,eth_lib_min,val_lib_loc,val_lib_min,val_con_loc,val_con_min,circle_orange,circle_blue,fraction_blue) %>% summarise_all(mean)
-
-df_min <- df_min %>% filter(eth_con_min==20 & eth_con_loc==20)
-# df_min <- df_min %>% filter(fraction_blue==50 |  fraction_blue==80)
-df_min <- df_min %>% filter(val_lib_loc == 0 | val_lib_loc == 1 |  val_lib_loc == 7 )
-
-# val_lib_loc == 3 ||val_lib_loc == 7 |
-
-df_maj <- df_maj %>% filter(eth_con_min==20 & eth_con_loc==20)
-# df_maj <- df_maj %>% filter(fraction_blue==50 |  fraction_blue==80)
-df_maj <- df_maj %>% filter(val_lib_min == 0 | val_lib_min == 1 |   val_lib_min == 7 )
-
-#  val_lib_min == 3 | val_lib_min == 7
-
-majcons_min <- ggplot(data = mech_lib) + geom_point(aes(x=val_lib_min,y=dv_sq_bl, colour = vl_sq_bl),shape = "circle",size=2)  + geom_line(aes(x=val_lib_min,y=dv_sq_bl, linetype = as.factor(val_lib_loc))) + facet_wrap(~mech_lib$fraction_blue) +
-  # geom_point(aes(x=val_lib_min,y=de_sq_bl, colour = et_sq_bl),shape = "square",size=2)  + geom_line(aes(x=val_lib_min,y=de_sq_bl, linetype = as.factor(val_lib_loc))) + facet_wrap(~df_min$fraction_blue)  +
-  ggtitle("majcons over min")
-
-majcons_maj <- ggplot(data = mech_cons) + geom_point(aes(x=val_lib_loc,y=dv_sq_bl, colour = vl_sq_bl),shape = "circle",size=2)  + geom_line(aes(x=val_lib_loc,y=dv_sq_bl, linetype = as.factor(val_lib_min))) + facet_wrap(~mech_cons$fraction_blue) +
- # geom_point(aes(x=val_lib_loc,y=de_sq_bl, colour = et_sq_bl),shape = "square",size=2)  + geom_line(aes(x=val_lib_loc,y=de_sq_bl, linetype = as.factor(val_lib_min))) + facet_wrap(~df_min$fraction_blue)  +
-  ggtitle("majcons over min")
-
-mincons_min <- ggplot(data = df_min) + geom_point(aes(x=val_lib_min,y=dv_sq_or, colour = vl_sq_or),shape = "circle",size=2)  + geom_line(aes(x=val_lib_min,y=dv_sq_or, linetype = as.factor(val_lib_loc))) + facet_wrap(~df_min$fraction_blue) +
-#   geom_point(aes(x=val_lib_min,y=de_sq_or, colour = et_sq_or),shape = "square",size=2)  + geom_line(aes(x=val_lib_min,y=de_sq_or, linetype = as.factor(val_lib_loc))) + facet_wrap(~df_min$fraction_blue) +
-  ggtitle("mincons over min")
-
-mincons_maj <- ggplot(data = df_maj) + geom_point(aes(x=val_lib_loc,y=dv_sq_or, colour = vl_sq_or),shape = "circle",size=2)  + geom_line(aes(x=val_lib_loc,y=dv_sq_or, linetype = as.factor(val_lib_min))) + facet_wrap(~df_maj$fraction_blue) + # geom_point(aes(x=val_lib_loc,y=de_sq_or, colour = et_sq_or),shape = "square",size=2)  + geom_line(aes(x=val_lib_loc,y=de_sq_or, linetype = as.factor(val_lib_min))) + facet_wrap(~df_maj$fraction_blue) +
-  ggtitle("mincons over maj")
-
-ggplotly(majcons_min)
-ggplotly(majcons_maj)
-
-ggplotly(mincons_min)
-ggplotly(mincons_maj)
-
-majlib_min <- ggplot(data = df_min) + geom_point(aes(x=val_lib_min,y=dv_cl_bl, colour = vl_cl_bl),shape = "circle",size=2)  + geom_line(aes(x=val_lib_min,y=dv_cl_bl, linetype = as.factor(val_lib_loc))) + facet_wrap(~df_min$fraction_blue)+
-  # geom_point(aes(x=val_lib_min,y=de_cl_bl, colour = et_cl_bl),shape = "square",size=2)  + geom_line(aes(x=val_lib_min,y=de_cl_bl, linetype = as.factor(val_lib_loc))) + facet_wrap(~df_min$fraction_blue)+
- ggtitle("majlib over min")
-
-majlib_maj <- ggplot(data = df_maj) + geom_point(aes(x=val_lib_loc,y=dv_cl_bl, colour = vl_cl_bl),shape = "circle",size=2)  + geom_line(aes(x=val_lib_loc,y=dv_cl_bl, linetype = as.factor(val_lib_min))) + facet_wrap(~df_maj$fraction_blue) +
-  # geom_point(aes(x=val_lib_loc,y=de_cl_bl, colour = et_cl_bl),shape = "square",size=2)  + geom_line(aes(x=val_lib_loc,y=de_cl_bl, linetype = as.factor(val_lib_min))) + facet_wrap(~df_min$fraction_blue)+
- ggtitle("majlib over maj")
-
-ggplotly(majlib_min)
-ggplotly(majlib_maj)
-
-minlib_min <- ggplot(data = df_min) + geom_point(aes(x=val_lib_min,y=dv_cl_or, colour = vl_cl_or),shape = "circle",size=2)  + geom_line(aes(x=val_lib_min,y=dv_cl_or, linetype = as.factor(val_lib_loc))) + facet_wrap(~df_min$fraction_blue)+ geom_point(aes(x=val_lib_min,y=de_cl_or, colour = et_cl_or),shape = "square",size=2)  + geom_line(aes(x=val_lib_min,y=de_cl_or, linetype = as.factor(val_lib_loc))) + facet_wrap(~df_min$fraction_blue)  +
-  ggtitle("minlib over min")
-
-minlib_maj <- ggplot(data = df_maj) + geom_point(aes(x=val_lib_loc,y=dv_cl_or, colour = vl_cl_or),shape = "circle",size=2)  + geom_line(aes(x=val_lib_loc,y=dv_cl_or, linetype = as.factor(val_lib_min))) + facet_wrap(~df_maj$fraction_blue) + geom_point(aes(x=val_lib_loc,y=de_cl_or, colour = et_cl_or),shape = "square",size=2)  + geom_line(aes(x=val_lib_loc,y=de_cl_or, linetype = as.factor(val_lib_min))) + facet_wrap(~df_maj$fraction_blue) +
-  ggtitle("minlib over maj")
-
-ggplotly(minlib_min)
-ggplotly(minlib_maj)
-
-```
-
-```{r back}
-
-# fraction: take 50 65 80, beta = 0, 1, 7
-
-# vlmin1 <- read.csv("vlmin_ethrat_1.csv",sep = ",",skip = 6)
-# legend <- read.csv("legend_sa_asym.csv",sep = ";")
-# legend <- as.data.frame(legend[,-2])
-# names(vlmin1) <- pull(legend)
-# 
-# vlmin2 <- read.csv("vlmin_ethrat_2.csv",sep = ",",skip = 6)
-# names(vlmin2) <- pull(legend)
-# 
-# vlmaj1 <- read.csv("vlmaj_ethrat_1.csv",sep = ",",skip = 6)
-# names(vlmaj1) <- pull(legend)
-# 
-# vlmaj2 <- read.csv("vlmaj_ethrat_2.csv",sep = ",",skip = 6)
-# names(vlmaj2) <- pull(legend)
-# 
-# mech_lib <- rbind(vlmin1,vlmin2,vlmaj1,vlmaj2)
-# write.csv(mech_lib,"mech_lib.csv",row.names = FALSE)
-
-df_long <- df %>% gather(key= subgroup, value = Outcome, de_sq_bl, dv_sq_bl, de_cl_bl, dv_cl_bl, de_sq_or, dv_sq_or, de_cl_or, dv_cl_or
-                         ) %>% mutate(
-
-   # `measureseg` = fct_relevel(fct_collapse(subgroup,"exposure" = c("et_sq_bl", "vl_sq_bl", "et_cl_bl", "vl_cl_bl", "et_sq_or", "vl_sq_or", "et_cl_or", "vl_cl_or"), "clustering" = c("de_sq_bl", "dv_sq_bl", "de_cl_bl", "dv_cl_bl", "de_sq_or", "dv_sq_or", "de_cl_or", "dv_cl_or")),"exposure"),
-
-  `segregation` = fct_relevel(fct_collapse(subgroup,"ethnics" = c("de_sq_bl","de_cl_bl","de_sq_or","de_cl_or" ), "values" = c("dv_sq_bl","dv_cl_bl","dv_sq_or","dv_cl_or" )),"ethnics"),
-
- `orientation` = fct_relevel(fct_collapse(subgroup, "conservative" = c("de_sq_bl","dv_sq_bl","de_sq_or","dv_sq_or"), "liberal" = c("de_cl_bl","dv_cl_bl","de_cl_or","dv_cl_or")),"conservative" ),
-
- `ethnia` = fct_relevel(fct_collapse(subgroup, "local" = c("de_sq_bl","dv_sq_bl","de_cl_bl","dv_cl_bl"),"minority" = c("de_sq_or","dv_sq_or","de_cl_or","dv_cl_or")), "local"),
-
- `groupp` = fct_relevel(fct_collapse(subgroup, "cons_maj" = c("de_sq_bl","dv_sq_bl"),"lib_maj"=c("de_cl_bl","dv_cl_bl"),"cons_min"=c("de_sq_or","dv_sq_or"),"lib_min"=c("de_cl_or","dv_cl_or")),"cons_maj")
-  )
-
-## df_long 2 measures
-
-df_long <- df %>% gather(key= subgroup, value = Outcome, et_sq_bl, vl_sq_bl, et_cl_bl, vl_cl_bl, et_sq_or, vl_sq_or, et_cl_or, vl_cl_or,
-                          de_sq_bl, dv_sq_bl, de_cl_bl, dv_cl_bl, de_sq_or, dv_sq_or, de_cl_or, dv_cl_or ) %>% mutate(
-
-   `measureseg` = fct_relevel(fct_collapse(subgroup,"exposure" = c("et_sq_bl", "vl_sq_bl", "et_cl_bl", "vl_cl_bl", "et_sq_or", "vl_sq_or", "et_cl_or", "vl_cl_or"), "clustering" = c("de_sq_bl", "dv_sq_bl", "de_cl_bl", "dv_cl_bl", "de_sq_or", "dv_sq_or", "de_cl_or", "dv_cl_or")),"exposure"),
-
-  `segregation` = fct_relevel(fct_collapse(subgroup,"ethnics" = c("et_sq_bl","et_cl_bl","et_sq_or","et_cl_or","de_sq_bl","de_cl_bl","de_sq_or", "de_cl_or" ), "values" = c("vl_sq_bl","vl_cl_bl","vl_sq_or","vl_cl_or","dv_sq_bl","dv_cl_bl","dv_sq_or","dv_cl_or" )),"ethnics"),
-
- `orientation` = fct_relevel(fct_collapse(subgroup, "conservative" = c("et_sq_bl","vl_sq_bl","et_sq_or","vl_sq_or","de_sq_bl", "dv_sq_bl", "de_sq_or", "dv_sq_or"), "liberal" = c("et_cl_bl","vl_cl_bl","et_cl_or","vl_cl_or","de_cl_bl", "dv_cl_bl","de_cl_or", "dv_cl_or")),"conservative" ),
- `ethnia` = fct_relevel(fct_collapse(subgroup, "local" = c("et_sq_bl","vl_sq_bl","et_cl_bl","vl_cl_bl","de_sq_bl", "dv_sq_bl", "de_cl_bl", "dv_cl_bl"),"minority" = c("et_sq_or","vl_sq_or","et_cl_or","vl_cl_or","de_sq_or", "dv_sq_or", "de_cl_or", "dv_cl_or")), "local")
- )
-
-## 3D plotly
-
-dfcl <- df_long[which(df_long$measureseg=="clustering"),]
-
-df_etsqbl<- df[,which((names(df) %in% c("fraction_blue","dominant","et_sq_bl")))]
-
-a <- as.matrix(df$dominant)
-class(a)
-
-b <- as.matrix(df$fraction_blue)
-z <- as.matrix(df$et_sq_bl)
-
-diba <- data.matrix(df)
-class(diba)
-
-M <- mesh(seq(0, 6*pi, length.out = 50),seq(pi/3, pi, length.out = 50))
-u <- M$x ; v <- M$y
-
-x <- data.matrix(df$fraction_blue)
-y <- data.matrix(df$dominant)
-z <- data.matrix(df$et_sq_bl)
-
-dfa <- df[which(df$dominant <= 15),]
-#plot_ly(data=df, x=df$dominant, y=df$fraction_blue, z=df$de_sq_bl, color = df$et_sq_bl) +
-  plot_ly(data=dfa) %>% 
-    add_trace(x=dfa$dominant, y=dfa$fraction_blue, z=dfa$de_sq_or, color = dfa$et_sq_bl,type = 'scatter3d',mode = 'lines+markers', marker = list( symbol="square") ) %>% 
-     add_trace(x=dfa$dominant, y=dfa$fraction_blue, z=dfa$de_sq_bl, color = dfa$et_sq_bl, type = 'scatter3d',mode = 'lines+markers') %>%
-    #   add_trace(x=df$dominant, y=df$fraction_blue, z=df$de_cl_or, color = df$et_cl_or, type = 'scatter3d',mode = 'lines+markers') %>%
-    #     add_trace(x=df$dominant, y=df$fraction_blue, z=df$de_cl_bl, color = df$et_cl_bl, type = 'scatter3d',mode = 'lines+markers') %>%
-
-    layout(
-  #  title = "Layout options in a 3d scatter plot",
-    scene = list(
-      xaxis = list(title = "dominant"),
-      yaxis = list(title = "ethnic ratio"),
-      zaxis = list(title = "cluster")
-    ))
-
-# plot for each subgroup, aesthetic: x-axis:beta, y-axis:spatial clustering, linetype  = fraction_blue, shape = type of segregation, bright = exposure
-
-## make ggplot into plotly
-x1 <- 1:100
-x2 <- x1 + 100
-x3 <- x2 + 100
-
-x <-  c(x1, x2, x3)
-y <- c(2*x1, 5*x2, -2*x3)
-
-group <-  c(rep("A", length(x1)),
-           rep("B", length(x2)),
-           rep("C", length(x3)))
-
-ds <- data.frame(x, y, group)
-
-# Use the group aesthetic to ensure lines are drawn separately for each group
-p <- ggplot(ds, aes(x, y)) +
-  geom_line(aes(group = group, color = group), size = 2) +
-  ggtitle("Group specific line chart")
-
-fig <- ggplotly(p)
-
-## regression fit to 3D
-
-# data(mtcars)
-# 
-# mtcars$shape <- cut(mtcars$mpg,
-#                     breaks = c(0,18, 26, 100),
-#                     labels = c("square", "circle", "diamond"))
-# mtcars$color <- cut(mtcars$mpg,
-#                     breaks = c(0,18, 26, 100),
-#                     labels = c("red", "yellow", "green"))
-# 
-# plot_ly(type = "scatter", data = mtcars, x = rownames(mtcars), y = mtcars$mpg,
-#         mode = "markers", symbol = ~I(shape), color = ~I(color))
-
-x <- data.matrix(df$dominant)
-y <- data.matrix(df$fraction_blue)
-z <- data.matrix(df$et_sq_bl)
-
-fit <- lm(z ~ as.integer(x) + as.integer(y))
-# predict values on regular xy grid
-grid.lines = 100
-x.pred <- seq(min(x), max(x), length.out = grid.lines)
-y.pred <- seq(min(y), max(y), length.out = grid.lines)
-xy <- expand.grid( x = x.pred, y = y.pred)
-z.pred <- matrix(predict(fit, newdata = xy),
-                 nrow = grid.lines, ncol = grid.lines)
-# fitted points for droplines to surface
-fitpoints <- predict(fit)
-# scatter plot with regression plane
-scatter3D(x, y, z, pch = 18, cex = 2,
-    theta = 90, phi = 0, ticktype = "detailed",
-    xlab = "dominant", ylab = "maj/min", zlab = "de_sq_mj",
-    surf = list(x = x.pred, y = y.pred, z = z.pred,
-    facets = NA, fit = fitpoints), main = "df")
-
-```
-
-```{r 3D, fig.cap="3D pictures", echo = FALSE}
-
-df_3D_high <- df_3D %>% filter(val_lib_loc==5,val_lib_min==5,eth_con_loc == 5,eth_con_min == 5,eth_lib_loc ==0,eth_lib_min==0)
-df_3D_low <- df_3D %>% filter(val_lib_loc==20,val_lib_min==20,eth_con_loc == 20,eth_con_min == 20,eth_lib_loc ==0,eth_lib_min==0)
-
-xx <- ~fraction_blue
-yy <- ~circle_orange
-zz <- ~de_cl_or
-cols <- ~et_cl_or
-zzv <- ~dv_cl_or
-colsv <- ~vl_cl_or
-tt <- "Liberasl Minority"
-
-D3 <- {
-lowE <- plot_ly(df_3D_high)  %>%
-  add_trace(x= xx,y= yy,z=zz,
-            scene = "scene1",
-            type="scatter3d",
-             mode="markers",
-             marker = list(
-             colorscale = "Reds",
-             color= cols, showscale =  T,
-             colorbar=list(title = "Ethnic \nExposure" ,x = -0.1,  len = 0.5, yanchor='bottom'))
-
-            )  %>%
-  layout(showlegend = F,
-         #title="Ethnic",
-         "scene1" = list(
-      xaxis = list(title = "Ethnic Ratio",range=seq(50,90,by=10),dtick=10),
-      yaxis = list(title = "% Liberal Minority" ,autorange = "reversed"),
-      zaxis = list(title = "Ethnic Cluster")))
-
- lowV<- plot_ly(df_3D_high)  %>%   add_trace(x=xx,y=yy,z=zzv,
-             scene =  "scene2",
-             type="scatter3d",
-             mode="markers",
-             marker = list(
-             colorscale = "Blues",
-             color= colsv , showscale = T, reversescale=T,
-             colorbar=list(title = "Value  \nExposure", len=0.5, yanchor='bottom'))
-            )  %>%
-       layout(showlegend = F,
-         "scene2" = list(
-      xaxis = list(title = "Ethnic Ratio",range=seq(50,90,by=10),dtick=10),
-      yaxis = list(title = "% Liberal Minority"  ,autorange = "reversed"),
-      zaxis = list(title = "Value Cluster")))
-
-highE <- plot_ly(df_3D_low)  %>%
-  add_trace(x=xx,y=yy,z=zz,
-            scene = "scene3",
-            type="scatter3d",
-             mode="markers",
-             marker = list(
-             colorscale = "Reds",
-             color= cols, showscale =  T,
-             colorbar=list(title = "Ethnic \nExposure" ,x = -0.1,  len = 0.5, yanchor='top'))
-
-            )  %>%
-  layout(showlegend = F,
-         #title="Ethnic",
-         "scene3" = list(
-      xaxis = list(title = "Ethnic Ratio",range=seq(50,90,by=10),dtick=10),
-      yaxis = list(title = "% Liberal Minority" ,autorange = "reversed"),
-      zaxis = list(title = "Ethnic Cluster")))
-
- highV<- plot_ly(df_3D_low)  %>%
-    add_trace(x=xx,y=yy,z=zz,
-     scene =  "scene4",
-     type="scatter3d",
-     mode="markers",
-     marker = list(
-     colorscale = "Blues",
-     color= colsv , showscale = T, reversescale=T,
-      colorbar=list(title = "Value  \nExposure", len=0.5, yanchor='top'))
-            )  %>%
-       layout(showlegend = F,
-         "scene4" = list(
-      xaxis = list(title = "Ethnic Ratio",range=seq(50,90,by=10),dtick=10),
-      yaxis = list(title = "% Liberal Minority"   ,autorange = "reversed"),
-      zaxis = list(title = "Value Cluster")))
-
-subplot(lowE, lowV,  highE, highV) %>%
-
-   layout(scene = list(domain=list(x=c(0,0.5),y=c(0.5,1)),zaxis = list(title = "Ethnic Cluster")),
-         scene2 = list(domain=list(x=c(0.5,1),y=c(0.5,1))),
-         scene3 = list(domain=list(x=c(0,0.5),y=c(0,0.5))),
-         scene4 = list(domain=list(x=c(0.5,1),y=c(0,0.5)))
-         ) %>%
-
-  layout(annotations = list(
-  text = tt,
-  font = list(size = 18),
-  xref = "paper",
-  yref = "paper",
-  yanchor = "bottom",
-  xanchor = "center",
-  align = "center",
-  x = 0.5,
-  y = 1,
-  showarrow = FALSE
-)
-
-) %>%
-  layout(annotations = list(
-  text = "High Randomness",
-  font = list(size = 15),
-  xref = "paper",
-  yref = "paper",
-  yanchor = "bottom",
-  xanchor = "center",
-  align = "center",
-  x = 0.5,
-  y = 0.5,
-  showarrow = FALSE
-))%>%
-  layout(annotations = list(
-  text = "Low Randomness",
-  font = list(size = 15),
-  xref = "paper",
-  yref = "paper",
-  yanchor = "bottom",
-  xanchor = "center",
-  align = "center",
-  x = 0.5,
-  y = 0,
-  showarrow = FALSE
-)
-
-)
-}
-
-```

### 2021-07-07 additional.Rmd
final decisions

@@
 
+```{r combine majority}
+
+sens_vlmj1 <- read.csv("sens_vlmj.csv",skip=6,sep=",")
+names(sens_vlmj1) <- read.csv("lg_full.csv",sep=";")[,1]
+
+sens_vlmj2 <- read.csv("sens_vlmj2.csv",skip=6,sep=",")
+names(sens_vlmj2) <- read.csv("lg_full.csv",sep=";")[,1]
+
+sens_vlmj <- rbind(sens_vlmj1,sens_vlmj2)
+sens_vlmj$ID <- "mj"
+
+sens_vlmn <- read.csv("sens_vlmn.csv",skip = 6, sep= ",")
+names(sens_vlmn) <- read.csv("lg_full.csv",sep=";")[,1]
+sens_vlmn$ID <- "mn"
+
+sens_vl <- rbind(sens_vlmj,sens_vlmn)
+
+write.csv(sens_vl,"sens_vl.csv",row.names = F)
+
+sens_vl <- read.csv("sens_vl.csv",sep =",") %>% select(-c(run)) %>%
+  group_by(density,fraction_blue,circle_blue,circle_orange,eth_con_loc,eth_con_min,val_lib_loc,val_lib_min,eth_lib_loc,eth_lib_min,val_con_loc,val_con_min,ID) %>% summarise_all(mean) %>%  gather(key = subgroup, value = Segra, de_sq_bl,dv_sq_bl,de_cl_bl,dv_cl_bl,de_sq_or,dv_sq_or,de_cl_or,dv_cl_or)  %>% mutate(
+`segregation` = fct_relevel(fct_collapse(subgroup,"Ethnic" = c("de_sq_bl","de_cl_bl","de_sq_or","de_cl_or"), "Value" = c("dv_sq_bl","dv_cl_bl","dv_sq_or","dv_cl_or")),"Ethnic"), 
+ `ethnicity` = fct_relevel(fct_collapse(subgroup, "Majority" = c("de_sq_bl","dv_cl_bl","de_cl_bl","dv_sq_bl"), "Minority" = c("de_sq_or","de_cl_or","dv_sq_or","dv_cl_or")), "Majority"),
+`orientation` = fct_relevel(fct_collapse(subgroup,"Conservatives" = c("de_sq_bl","dv_sq_bl","de_sq_or","dv_sq_or"), "Liberals" = c("de_cl_bl","dv_cl_bl","de_cl_or","dv_cl_or")), "Conservatives"), 
+`type` = fct_relevel(fct_collapse(subgroup,"Conservative Majority" = c("de_sq_bl","dv_sq_bl"),
+      "Liberals Majority" = c("de_cl_bl","dv_cl_bl"),
+      "Conservative Minority" = c("de_sq_or","dv_sq_or"),
+      "Liberals Minority" = c("de_cl_or","dv_cl_or")), "Conservative Majority"))
+
+mj <- sens_vl %>% filter(ID == "mj") %>% filter(type == "Liberals Majority" | type == "Liberals Minority") %>% ggplot(aes(x=val_lib_loc,y=Segra, color = segregation, linetype = as.factor(val_lib_min))) + geom_point() + geom_line() +
+  facet_wrap(~ type)
+
+mj
+
+```
+
 # Increase ethnic
@@
 ```{r determinism_area_X_ethnic_size, echo = FALSE}
-lg <-  read.csv("lg_etlib.csv",sep=";")[,1]
-etlb_bs <- read.csv("et_lib_fc_bothfalse.csv",sep=",",skip=6)
-names(etlb_bs) <- lg
-etlb_bs$ID <- "bsl"
+# lg <-  read.csv("lg_etlib.csv",sep=";")[,1]
+# 
+# etlb_bs <- read.csv("et_lib_fc_bothfalse.csv",sep=",",skip=6)
+# names(etlb_bs) <- lg
+# etlb_bs$ID <- "bsl"
+# 
+# etlb_mj <- read.csv("et_lib_fc_mj.csv",sep=",",skip=6)
+# names(etlb_mj) <- lg
+# etlb_mj$ID <- "mj_et"
+# 
+# etlb_mn <- read.csv("et_lib_fc_mn.csv",sep=",",skip=6)
+# names(etlb_mn) <- lg
+# etlb_mn$ID <- "mn_et"
+# 
+# etlb_bs2 <- read.csv("et_lib_fc_bothfalse2.csv",sep=",",skip=6)
+# names(etlb_bs2) <- lg
+# etlb_bs2$ID <- "bsl"
+# 
+# etlb_mj2 <- read.csv("et_lib_fc_mj2.csv",sep=",",skip=6)
+# names(etlb_mj2) <- lg
+# etlb_mj2$ID <- "mj_et"
+# 
+# etlb_mn2 <- read.csv("et_lib_fc_mn2.csv",sep=",",skip=6)
+# names(etlb_mn2) <- lg
+# etlb_mn2$ID <- "mn_et"
+# 
+# etlb <- rbind(etlb_bs,etlb_mj,etlb_mn,etlb_bs2,etlb_mj2,etlb_mn2)
+# 
+# write.csv(etlb,"etlb.csv",row.names=F)
 
-etlb_mj <- read.csv("et_lib_fc_mj.csv",sep=",",skip=6)
-names(etlb_mj) <- lg
-etlb_mj$ID <- "mj_et"
-
-etlb_mn <- read.csv("et_lib_fc_mn.csv",sep=",",skip=6)
-names(etlb_mn) <- lg
-etlb_mn$ID <- "mn_et"
-
-etlb <- rbind(etlb_bs,etlb_mj,etlb_mn) %>% group_by(density,fraction_blue,circle_blue,circle_orange,et_mn_on,et_mj_on,dominant,ID) %>% summarise_all(mean) %>%  gather(key = subgroup, value = Segra, de_sq_bl,dv_sq_bl,de_cl_bl,dv_cl_bl,de_sq_or,dv_sq_or,de_cl_or,dv_cl_or)  %>% mutate(
+etlb <- read.csv("etlb.csv",sep=",") %>% select(-c(run)) %>%
+  group_by(density,fraction_blue,circle_blue,circle_orange,et_mn_on,et_mj_on,dominant,ID) %>% summarise_all(mean) %>%  gather(key = subgroup, value = Segra, de_sq_bl,dv_sq_bl,de_cl_bl,dv_cl_bl,de_sq_or,dv_sq_or,de_cl_or,dv_cl_or)  %>% mutate(
 `segregation` = fct_relevel(fct_collapse(subgroup,"Ethnic" = c("de_sq_bl","de_cl_bl","de_sq_or","de_cl_or"), "Value" = c("dv_sq_bl","dv_cl_bl","dv_sq_or","dv_cl_or")),"Ethnic"), 
@@
       "Conservative Minority" = c("de_sq_or","dv_sq_or"),
-      "Liberals Minority" = c("de_cl_or","dv_cl_or")), "Conservative Majority"))
+      "Liberals Minority" = c("de_cl_or","dv_cl_or")), "Conservative Majority")) %>% filter(fraction_blue == 50| fraction_blue == 80)
 
-etlb_df <- etlb %>% filter(fraction_blue == 50 | fraction_blue == 80)
+cl <- list(
+as.data.frame(cbind(subset(etlb, type == "Conservative Majority" | type == "Conservative Minority"), s = "conservatives")),
+as.data.frame(cbind(subset(etlb, type == "Liberals Majority" | type == "Liberals Minority"), s = "liberals"))
+)
 
-lmn <- ggplot(etlb_df[which(etlb_df$type  == "Liberals Minority"),],aes(x=dominant,y=Segra,  linetype = as.factor(ID) ,color= as.factor(`segregation`))) + geom_point(shape="square") + geom_line() +
-  facet_wrap(~ fraction_blue, scales = "free_y") +
-  theme_bw()
+for (i in cl) {
 
-cmj
-cmn
+  p <- ggplot(i, aes(dominant,y=Segra,color =`segregation`,linetype = as.factor(ID) )) +
+    geom_point(size = 1.5, shape = if(i$s == "conservatives"){"square"}else{"circle"}) +
+    geom_line() +
+    facet_wrap(type ~ fraction_blue,  scales = "free", labeller = labeller(fraction_blue = c("50" = "50% Majority", "80" = "80% Majority"))) + 
+    scale_color_manual(values = c("darkgreen","purple"), labels = c("Ethnic","Value"), guide_legend(title = "Segregation:")) +
+        scale_linetype_manual(values = c("solid","longdash","dotted"), labels = c("Baseline","Lib Maj","Lib Min"), guide_legend(title = "Beta Ethnic:")) +
+    ylab("Spatial Clustering") +
+    xlab("ß dominant") +
+    theme_bw() +
+    theme(legend.position = "bottom")
 
-lmj
-lmn
+  plot(p)
 
-pic_lm <- ggpubr::ggarrange(lmj,lmn, nrow = 2,  common.legend = T, legend = "bottom")
+  nm <- paste0(as.name(i$s),".jpg")
+  ggsave(nm,p,path = "images")
 
-pic_cm
-pic_lm
+}
 

### 2021-07-13 af2.Rmd
one file df, abm, analysis

--- 2021-07-07 additional.Rmd
@@
 
-setwd("C:/Users/rocpa/OneDrive/Desktop/AF/ethnic-value_multinomial-master/additional/")
+setwd("C:/Users/rocpa/OneDrive/Desktop/AF2/analysis")
 
@@
 
-valueminority.labs <- c("ß value liberals minority: 0", "ß value liberals minority: 1", "ß value liberals minority: 7")
-names(valueminority.labs) <- c("0","1","7")
-valuemajority.labs <- c("ß value liberals majority: 0", "ß value liberals majority: 1", "ß value liberals majority: 7")
-names(valuemajority.labs) <- c("0","1","7")
-ethnicminority.labs <- c("ß ethnic liberals minority: 0", "ß ethnic liberals minority: 1", "ß ethnic liberals minority: 7")
-names(ethnicminority.labs) <- c("0","1","7")
-ethnicmajority.labs <- c("ß ethnic liberals majority: 0", "ß ethnic liberals majority: 1", "ß ethnic liberals majority: 7")
-names(ethnicmajority.labs) <- c("0","1","7")
-ethnicity.labs <- c("50% Majority", "60% Majority","70% Majority","80% Majority","90% Majority")
-names(ethnicity.labs) <- c("50","60","70","80","90")
+# To combine dataframes
+# dfg <- function(x,id){
+# lg <- read.csv("code_dv.csv", sep = ";")
+# x <- rbind(read.csv(paste0(x,".csv"),sep = ",",skip = 6),read.csv(paste0(x,".csv"),sep = ",",skip = 6))
+# names(x) <- lg[,1]
+# x$ID <- id
+# as.data.frame(x)
+# }
+# 
+# bsl <- dfg("bsl_dom_sec","bsl")
+# bsl_dom <- dfg("bsl_dom","bsl_dom")
+# bsl_sec_cl <- dfg("bsl_dom_sec_circle","bsl_sec_cl")
+# bsl_sec_sq <- dfg("bsl_dom_sec_square","bsl_sec_sq")
+# sens_lib  <- dfg("sens_lib" ,"sens_lib")
+# sens_con  <- dfg( "sens_con" ,"sens_con")
+# bsl_lib_con   <- dfg("bsl_value_lib_con","bsl_lib_con")
+# bsl_con_lib  <- dfg("bsl_value_con_lib","bsl_con_lib")
+# hmp  <- dfg("bsl_dom_sec_htmp","hmp")
+# asm  <- dfg("asym_bsl_sec","asm")
+# asm_dom  <- dfg("asym_bsl_secno","asm_dom")
+# libmj  <- dfg("asym_libmj_mn","libmj")
+# libmn  <- dfg("asym_libmn_mj","libmn")
+# dislib  <- dfg("asym_dislib","dislib")
+# dislib_maj  <- dfg("asym_dislib_libmajL","dislib_maj")
+# dislib_min  <- dfg("asym_dislib_libminL","dislib_min")
+# etlib_bsl  <- dfg("asym_et_bsl","etlib_bsl")
+# etlib_maj  <- dfg("asym_et_mj","etlib_maj")
+# etlib_min  <- dfg("asym_et_mn","etlib_min")
+# dislibet_maj  <- dfg("asym_dislib_et_mj", "dislibet_maj")
+# dislibet_min  <- dfg("asym_dislib_et_mn","dislibet_min")
+# 
+# df_tot <- rbind(bsl,bsl_dom, bsl_sec_cl, bsl_sec_sq,sens_lib,sens_con,bsl_lib_con ,bsl_con_lib ,hmp,  asm , asm_dom , libmj , libmn  ,dislib , dislib_maj,dislib_min  ,etlib_bsl,etlib_maj ,etlib_min ,dislibet_maj ,dislibet_min)
+# 
+# 
+# write.csv(df_tot,"df_tot.csv",row.names = F)
 
-mech <- read.csv("mech_lib.csv",sep=",")
-excl <- names(mech) %in% c("run", "density","step")
-mech <- mech[!excl] %>% group_by(eth_con_loc, eth_con_min,eth_lib_loc,eth_lib_min,val_lib_loc,val_lib_min,val_con_loc,val_con_min,circle_orange,circle_blue,fraction_blue) %>% summarise_all(mean)
+df <- read.csv("df_tot.csv",sep =",")
 
-df_3D <- read.csv("3D.csv",sep=",")
-excl3D <- names(df_3D) %in% c("run", "density","step")
-df_3D <- df_3D[!excl3D] %>% group_by(eth_con_loc, eth_con_min,eth_lib_loc,eth_lib_min,val_lib_loc,val_lib_min,val_con_loc,val_con_min,circle_orange,circle_blue,fraction_blue) %>% summarise_all(mean)
+# 
+# 
+# 
+# 
+# df_3D <- read.csv("3D.csv",sep=",")
+# excl3D <- names(df_3D) %in% c("run", "density","step")
+# df_3D <- df_3D[!excl3D] %>% group_by(eth_con_loc, eth_con_min,eth_lib_loc,eth_lib_min,val_lib_loc,val_lib_min,val_con_loc,val_con_min,circle_orange,circle_blue,fraction_blue) %>% summarise_all(mean)
+# 
+# 
+# value_basic_den <- read.csv("value_basic_den.csv",sep = ",")
+# excl <- names(value_basic_den) %in% c("run","density","step")
+# value_basic_den <- value_basic_den[!excl] %>% group_by(ID,fraction_blue,circle_blue,circle_orange,circle,square) %>% summarise_all(mean)
+# 
+# 
+# value_dominant_den <- read.csv("value_dominant_den.csv",sep = ",")
+# excl <- names(value_dominant_den) %in% c("run","density","step")
+# value_dominant_den <- value_dominant_den[!excl] %>% group_by(ID,fraction_blue,circle_blue,circle_orange,dominant_square,dominant_circle,secondary_square,secondary_circle) %>% summarise_all(mean) 
+#
 
-df_etlib <- read.csv("df_etlib_all.csv",sep=",")
-excl <- names(df_etlib) %in% c("run", "density","step")
-df_etlib <- df_etlib[!excl] %>% group_by(ID,eth_con_loc,eth_con_min,eth_lib_loc,eth_lib_min,val_lib_loc,val_lib_min,val_con_loc,val_con_min,circle_orange,circle_blue,fraction_blue) %>% summarise_all(mean)
-
-df_sec <- read.csv("df_secondary.csv",sep=",")
-exclet <- names(df_sec) %in% c("run", "density","step")
-df_sec <- df_sec[!exclet] %>% group_by(ID,RND,eth_con_loc,eth_con_min,eth_lib_loc,eth_lib_min,val_lib_loc,val_lib_min,val_con_loc,val_con_min,circle_orange,circle_blue,fraction_blue) %>% summarise_all(mean)
-
-df_3Do <- read.csv("3D_old.csv",sep=",")
-excl3D <- names(df_3Do) %in% c("run", "density","step")
-df_3Do <- df_3Do[!excl3D] %>% group_by(eth_con_loc, eth_con_min,eth_lib_loc,eth_lib_min,val_lib_loc,val_lib_min,val_con_loc,val_con_min,circle_orange,circle_blue,fraction_blue) %>% summarise_all(mean)
-
-# value_dominant_den <- read.csv("dom_sqr_2.csv",skip = 6,sep = ",")
-# leg <- read.csv("leg_value_dominant_den.csv",sep=";")
-# 
-# value_dominant_den$ID <- "square"
-# value_dominant_den2 <- read.csv("dom_crl_2.csv",skip = 6,sep = ",")
-# names(value_dominant_den2) <- leg[,1]
-# value_dominant_den2$ID <- "circle"
-# 
-# value_dominant_den <- rbind(value_dominant_den,value_dominant_den2)
-# 
-# write.csv(value_dominant_den,"value_dominant_den.csv",row.names = F)
-
-value_basic_den <- read.csv("value_basic_den.csv",sep = ",")
-excl <- names(value_basic_den) %in% c("run","density","step")
-value_basic_den <- value_basic_den[!excl] %>% group_by(ID,fraction_blue,circle_blue,circle_orange,circle,square) %>% summarise_all(mean)
-
-value_dominant_den <- read.csv("value_dominant_den.csv",sep = ",")
-excl <- names(value_dominant_den) %in% c("run","density","step")
-value_dominant_den <- value_dominant_den[!excl] %>% group_by(ID,fraction_blue,circle_blue,circle_orange,dominant_square,dominant_circle,secondary_square,secondary_circle) %>% summarise_all(mean)
-
-dv <- c("step",
-"et_sq",
-"et_cl",
-"vl_sq",
-"vl_cl",
-"et_sq_bl",
-"et_cl_bl",
-"et_sq_or",
-"et_cl_or",
-"vl_sq_bl",
-"vl_cl_bl",
-"vl_sq_or",
-"vl_cl_or",
-"den_sq_bl",
-"den_sq_or",
-"den_cl_bl",
-"den_cl_or",
-"den_sq",
-"den_cl",
-"de_sq_bl",
-"de_cl_bl",
-"de_sq_or",
-"de_cl_or",
-"dv_sq_bl",
-"dv_cl_bl",
-"dv_sq_or",
-"dv_cl_or")
 ```
@@
   ylab("Outcome") +
-  theme_bw()+
-  theme(legend.position = "bottom")
-
-```
-
-```{r test_val-maj, fig.cap= "Checking effect of value liberal = ethnic liberal majority" echo =  FALSE}
-
-# equal size; liberals: value = ethnic
-
-df <- read.csv("mj_val_eth.csv",skip=6,sep=",")
-lg <- read.csv("lg_mj_val_eth.csv",sep =";")
-names(df) <- lg[,1]
-
-df <- df %>%  gather(key = subgroup, value = Segra, de_sq_bl,dv_sq_bl,de_cl_bl,dv_cl_bl,de_sq_or,dv_sq_or,de_cl_or,dv_cl_or)  %>% mutate(
-`segregation` = fct_relevel(fct_collapse(subgroup,"Ethnic" = c("de_sq_bl","de_cl_bl","de_sq_or","de_cl_or"), "Value" = c("dv_sq_bl","dv_cl_bl","dv_sq_or","dv_cl_or")),"Ethnic"), 
- `ethnicity` = fct_relevel(fct_collapse(subgroup, "Majority" = c("de_sq_bl","dv_cl_bl","de_cl_bl","dv_sq_bl"), "Minority" = c("de_sq_or","de_cl_or","dv_sq_or","dv_cl_or")), "Majority"),
-`orientation` = fct_relevel(fct_collapse(subgroup,"Conservatives" = c("de_sq_bl","dv_sq_bl","de_sq_or","dv_sq_or"), "Liberals" = c("de_cl_bl","dv_cl_bl","de_cl_or","dv_cl_or")), "Conservatives"), 
-`type` = fct_relevel(fct_collapse(subgroup,"Conservative Majority" = c("de_sq_bl","dv_sq_bl"),
-      "Liberals Majority" = c("de_cl_bl","dv_cl_bl"),
-      "Conservative Minority" = c("de_sq_or","dv_sq_or"),
-      "Liberals Minority" = c("de_cl_or","dv_cl_or")), "Conservative Majority"))
-
-df %>% filter(dominant_square == circle_mj) %>% ggplot(aes(x= circle_mj,y = Segra, color = `segregation`, shape = `orientation`)) + geom_point() + geom_line() +
-  scale_color_manual(values = c("green","purple"), guide = guide_legend(title = "Outcome")) +
-  scale_shape_manual(values = c("square","circle"), guide = guide_legend(title = "Orientation"))  +
- # scale_y_continuous(limits=c(0.45,1), breaks=seq(0.5,1,by=0.1)) +
-  xlab("ß value liberals majority = ß ethnic liberals majority") +
-  ylab("Outcome") +
-  facet_wrap(~  `ethnicity` ) +
   theme_bw()+
@@
 # Baseline asymmetric: dominant due to ethnic ration
+
 ```{r asym_baseline, fig.cap="Fig. 8 orig", echo = FALSE}
-# Effect of ethnic asymmetry: all beta dominant equal
 
@@
 
-# df <- df %>% filter(df$dominant <= 15) 
-# df <- df %>% filter(df$fraction_blue==50|df$fraction_blue==60|df$fraction_blue==80)
-
-asym_dom <- asym_dom  %>% filter(fraction_blue == 50 | fraction_blue == 80) %>% gather(key = subgroup, value = Segra, de_sq_bl,dv_sq_bl,de_cl_bl,dv_cl_bl,de_sq_or,dv_sq_or,de_cl_or,dv_cl_or)  %>% mutate(
+asym_dom <-  read.csv("df_asym_dom.csv",sep = ",") %>% select(-c(run,density,step)) %>% group_by(dominant,circle_orange,circle_blue,fraction_blue,secondary) %>% summarise_all(mean) %>% 
+  gather(key = subgroup, value = Segra, de_sq_bl,dv_sq_bl,de_cl_bl,dv_cl_bl,de_sq_or,dv_sq_or,de_cl_or,dv_cl_or)  %>% mutate(
 `segregation` = fct_relevel(fct_collapse(subgroup,"Ethnic" = c("de_sq_bl","de_cl_bl","de_sq_or","de_cl_or"), "Value" = c("dv_sq_bl","dv_cl_bl","dv_sq_or","dv_cl_or")),"Ethnic"), 
@@
       "Conservative Minority" = c("de_sq_or","dv_sq_or"),
-      "Liberals Minority" = c("de_cl_or","dv_cl_or")), "Conservative Majority"))
+      "Liberals Minority" = c("de_cl_or","dv_cl_or")), "Conservative Majority")) %>%
+  filter(fraction_blue == 50 | fraction_blue == 80)
 
-ggplot(data = asym_dom, aes(x = dominant, y = Segra, color = `segregation`, linetype = as.factor(fraction_blue))) + geom_point() + geom_line() +
-  facet_wrap(~ `type`, nrow = 1) +
-  scale_color_manual(values = c("green","purple"),labels =  c("Ethnic","Value"),guide = guide_legend(title = "Segregation \ntype")) +
+asym_dom <- ggplot(data = asym_dom, aes(x = dominant, y = Segra, color = `segregation`, linetype = as.factor(fraction_blue))) + geom_point(size = 1.5) + geom_line() +
+  facet_wrap(~ `type`, nrow = 1, scales= "free") +
+  scale_color_manual(values = c("dark green","purple"),labels =  c("Ethnic","Value"),guide = guide_legend(title = "Segregation")) +
    scale_linetype_manual(values = c("solid","dashed"),labels =  c("50 %","80 %"),guide = guide_legend(title = "% Majority")) +
@@
   xlab("ß dominant") +
+    geom_hline(yintercept=1,color="red") +
   theme_bw() +
  theme(legend.position = "bottom")
+
+ggsave("asym_dom.jpg",asym_dom, path = "images", width = 9, height = 4, dpi = 300)
 
@@
 
-```{r by-product_cons_original, fig.cap="Effect of liberals majority vs minority on value segregation conservatives", echo = FALSE}
-# It goes
-# ethnic and value segregation for each group in the annex
-
-##### 
-# By-product value of conservatives by value preference liberals
-
-# Majority
-
-mech_cons <- mech %>% filter(fraction_blue == 50 | fraction_blue == 80) %>%  filter(val_lib_min==0 | val_lib_min==1 |val_lib_min==7) %>% gather(key=ethnics, value=Clust, dv_sq_bl,dv_sq_or)
-
-cons_maj <- ggplot(data = mech_cons, aes(x=val_lib_loc,y=Clust,color=  `ethnics`,linetype= as.factor(fraction_blue))) + geom_point(size=1.5, shape = "square") + geom_line() + 
-  facet_wrap(~val_lib_min,dir="v",labeller = labeller(val_lib_min = valueminority.labs)) +
-    scale_y_continuous(breaks= seq(0,2,by=0.25)) +
-  xlab("ß value liberal majority") + ylab("Spatial clustering") +
-  geom_hline(yintercept=1,color="red") +
-  scale_color_manual(values=c("blue","darkorange"),labels=c("Majority","Minority"),name="Ethnicity") +
-    scale_linetype_manual(values=c("solid","dashed"),labels=c("50%","80%"),name="% Majority") +
-   guides(color  = guide_legend(order = 1), linetype = guide_legend(order = 2)) +
-  theme_bw()
-
-# Minority
-
-mech_lib <- mech %>%  filter(fraction_blue == 50 | fraction_blue == 80) %>%  filter(val_lib_loc==0 | val_lib_loc==1 |val_lib_loc==7) %>% gather(key=ethnics, value=Cluste, dv_sq_bl,dv_sq_or)
-
-cons_min <- ggplot(data = mech_lib, aes(x=val_lib_min,y=Cluste,color=  `ethnics`,linetype= as.factor(fraction_blue))) + geom_point(size=1.5, shape = "square") + geom_line() + 
-  facet_wrap(~val_lib_loc,dir="v",labeller = labeller(val_lib_loc = valuemajority.labs)) +
-  xlab("ß value liberal minority") + ylab("Spatial clustering") +
-  scale_y_continuous(breaks= seq(0,2,by=0.25)) +
-  geom_hline(yintercept=1,color="red") +
-  scale_color_manual(values=c("blue","darkorange"),labels=c("Majority","Minority"),name="Ethnicity") +
-    scale_linetype_manual(values=c("solid","dashed"),labels=c("50%","80%"),name="% Majority") +
-   guides(color  = guide_legend(order = 1), linetype = guide_legend(order = 2)) +
- theme_bw()
-
-ggplotly(cons_maj)
-ggplotly(cons_min)
-
-lib_cons <- ggpubr::ggarrange(cons_maj,cons_min, common.legend = TRUE, legend = "bottom")
-
-# ggsave("lib_cons.jpg",plot=lib_cons)
-ggpubr::annotate_figure(lib_cons,
-               top = "Effect of liberals majority vs minority on value segregation conservatives")
-```
-
-```{r beta_maj, fig.cap="effect liberals one  dataset", echo = FALSE}
-# It goes
-#####
-# Ethnic and value of liberals above each other
-mech_vlmj <- mech %>% filter(fraction_blue == 50 | fraction_blue == 80) %>%  filter(val_lib_min==0 | val_lib_min==1 |val_lib_min==7) %>% gather(key = segregation, value = Clustmj, de_cl_bl, dv_cl_bl)
-
-librmj <- ggplot(data=mech_vlmj,aes(x=val_lib_loc,y = Clustmj,shape=`segregation`,linetype=as.factor(fraction_blue))) + 
-  geom_point(size=1.5,color="blue") + geom_line(color="blue") +
-facet_wrap(~val_lib_min,dir="v",labeller=labeller(val_lib_min=valueminority.labs)) +
-  xlab("ß value liberals majority") + ylab("Spatial Clustering") +
-  scale_y_continuous(breaks= seq(0,2,by=0.25)) +
-  scale_linetype_manual(values=c("solid","dashed"),labels=c("50%","80%"),name="% Majority" ) +
-  scale_shape_manual(values=c("square","circle"),labels=c("Ethnic","Value"),name="Segregation" ) +
- ggtitle("Liberals Majority") +
-    geom_hline(yintercept=1,color="red") +
-  guides(color = "black") +
-      theme_bw() +
-  theme(plot.title = element_text(hjust = 0.5))
-
-mech_vlmn <- mech %>%  filter(fraction_blue == 50 | fraction_blue == 80) %>%  filter(val_lib_loc==0 | val_lib_loc==1 |val_lib_loc==7) %>% gather(key = segregation, value = Clustmn, de_cl_or, dv_cl_or)
-
-librmn <- ggplot(data=mech_vlmn,aes(x=val_lib_min,y = Clustmn,shape=`segregation`,linetype=as.factor(fraction_blue))) + 
-  geom_point(size=1.5,color="orange") + geom_line(color="orange") +
-facet_wrap(~val_lib_loc,dir="v",labeller=labeller(val_lib_loc=valuemajority.labs)) +
- scale_y_continuous(breaks= seq(0,2,by=0.25)) +
-  xlab("ß value liberals minority") + ylab("Spatial Clustering") +
-    scale_linetype_manual(values=c("solid","dashed"),labels=c("50%","80%"),name="% Majority") +
-  scale_shape_manual(values=c("square","circle"),labels=c("Ethnic","Value"),name="Segregation") +
-    geom_hline(yintercept=1,color="red") +
-    guides(  linetype = guide_legend(order = 1), shape = guide_legend(order = 2)) +
- #  guides(color=FALSE) + 
-    ggtitle("Liberals Minority") +
-    geom_hline(yintercept=1,color="red") +
-      theme_bw() +
-  theme(plot.title = element_text(hjust = 0.5))
-
-ggplotly(librmj)
-ggplotly(librmn)
-
-lib_lib <- ggpubr::ggarrange(librmj,librmn, common.legend = TRUE, legend = "bottom")
-
-lib_lib
-# ggsave("lib_lib.jpg",plot=lib_lib)
-
-```
-
-```{r lib_min, fig.cap="Each grouptype, distribution liberals faceted by ethnic ratio", echo = FALSE}
-
-df_fin <- df_3D %>% mutate(RND = case_when(
-  val_lib_loc==5 & val_lib_min==5 & eth_con_loc == 5 & eth_con_min == 5 ~ "H",
-  val_lib_loc==20 & val_lib_min==20 & eth_con_loc == 20 & eth_con_min == 20 ~ "L"))
-
-sb <- list(
-  as.data.frame(cbind((subset(df_fin, eth_lib_loc == 0 & eth_lib_min  ==  0) %>% gather(subgroup, Segra, de_sq_bl,dv_sq_bl)),t="Conservative Majority",tt = "cmj")),
-           as.data.frame(cbind((subset(df_fin, eth_lib_loc  ==  0 & eth_lib_min  ==  0) %>% gather(subgroup, Segra, de_cl_bl,dv_cl_bl)),t="Liberal Majority",tt = "lmj")),
-            as.data.frame(cbind((subset(df_fin, eth_lib_loc  ==  0 & eth_lib_min  ==  0)  %>% gather(subgroup, Segra, de_sq_or,dv_sq_or)),t="Conservative Minority",tt = "cmn")),
-           as.data.frame(cbind((subset(df_fin, eth_lib_loc  ==  0 & eth_lib_min  ==  0) %>% gather(subgroup, Segra, de_cl_or,dv_cl_or)),t="Liberal Minority",tt = "lmn")),
-
-   as.data.frame(cbind((subset(df_fin, eth_lib_loc != 0 &  eth_lib_min != 0) %>% gather(subgroup, Segra, de_sq_bl,dv_sq_bl)),t="Conservative Majority_et",tt = "cmj_et")),
-           as.data.frame(cbind((subset(df_fin,  eth_lib_loc != 0 &  eth_lib_min != 0) %>% gather(subgroup, Segra, de_cl_bl,dv_cl_bl)),t="Liberal Majority_et",tt = "lmj_et")),
-            as.data.frame(cbind((subset(df_fin,  eth_lib_loc != 0 &  eth_lib_min != 0)  %>% gather(subgroup, Segra, de_sq_or,dv_sq_or)),t="Conservative Minority_et",tt = "cmn_et")),
-           as.data.frame(cbind((subset(df_fin,  eth_lib_loc != 0 &  eth_lib_min != 0) %>% gather(subgroup, Segra, de_cl_or,dv_cl_or)),t="Liberal Minority_et",tt = "lmn_et"))
-           )
-
-for (i in sb) {
-pl <-  ggplot(i, aes(x=circle_orange,y=Segra,shape = subgroup, color = RND)) + geom_point() + geom_line() +
-  scale_shape_manual(values = c("square","circle"),labels = c("ethnic","Value"), guide = guide_legend(title = "Segregation", order = 1)) + 
-    scale_color_manual(values = c("green","purple"),labels = c("high","low"), guide = guide_legend(title = "Randomness")) + 
- scale_x_discrete(limits = seq(10,90 ,by = 10)) +
-  xlab("% Liberals Minority") +
-  ylab("Spatial Clustering") +
-  geom_hline(yintercept=1,color="red") +
-  facet_wrap(~ fraction_blue, nrow = 1, labeller = labeller(fraction_blue = ethnicity.labs)) +
- ggtitle(i$t) +
-  theme_bw() +
-  theme(panel.spacing = unit(0.7, "lines"), legend.position = "bottom")
-
-plot(pl)
-nmn <- paste0(as.name(i$tt),".jpg")
-ggsave(nmn, pl,  path = "images")
-}
-
-```
-
-```{r combine majority}
-
-sens_vlmj1 <- read.csv("sens_vlmj.csv",skip=6,sep=",")
-names(sens_vlmj1) <- read.csv("lg_full.csv",sep=";")[,1]
-
-sens_vlmj2 <- read.csv("sens_vlmj2.csv",skip=6,sep=",")
-names(sens_vlmj2) <- read.csv("lg_full.csv",sep=";")[,1]
-
-sens_vlmj <- rbind(sens_vlmj1,sens_vlmj2)
-sens_vlmj$ID <- "mj"
-
-sens_vlmn <- read.csv("sens_vlmn.csv",skip = 6, sep= ",")
-names(sens_vlmn) <- read.csv("lg_full.csv",sep=";")[,1]
-sens_vlmn$ID <- "mn"
-
-sens_vl <- rbind(sens_vlmj,sens_vlmn)
-
-write.csv(sens_vl,"sens_vl.csv",row.names = F)
+```{r plot asym}
 
@@
 
-mj <- sens_vl %>% filter(ID == "mj") %>% filter(type == "Liberals Majority" | type == "Liberals Minority") %>% ggplot(aes(x=val_lib_loc,y=Segra, color = segregation, linetype = as.factor(val_lib_min))) + geom_point() + geom_line() +
-  facet_wrap(~ type)
-
-mj
+asym.plot <- function(i){
+  suppressWarnings(
+ggplot(data = i, aes(x= if(i$ID == "mj"){i$val_lib_loc}else{i$val_lib_min}, y=Segra, color = segregation, linetype = as.factor(if (i$ID == "mj"){i$val_lib_min}else{i$val_lib_loc}))) + geom_point(size = 1.5) + geom_line() +
+  facet_wrap(~ type, scales = "free") +
+  scale_linetype_manual(values = c("solid","dotted","dashed"),labels = c("0","1","15"), guide = guide_legend(title = 
+   if (i$ID == "mj"){ "ß liberal minority"}else{ "ß liberal majority"})) +
+  scale_color_manual(values = c("dark green","purple"), labels =  c("ethnic","value"), guide = guide_legend(title = "Segregation")) +
+  xlab(if (i$ID == "mj"){ "ß liberal majority"}else{ "ß liberal minority"}) +
+  ylab("Spatial Clustering") +
+  geom_hline(yintercept=1,color="red") +
+  theme_bw() +
+  theme(legend.position="right")
+)
+}
 
@@
 
-# Increase ethnic
+```{r asym liberals}
 
-```{r OK Ethnic preference liberals, fig.cap= "Same preferences ethnic and value, liberals", echo =  FALSE}
+mnlib <- asym.plot( sens_vl %>%  filter( ID == "mn" & type == "Liberals Minority"))
+mjlib <- asym.plot(sens_vl %>%  filter( ID == "mj" & type == "Liberals Majority"))
 
-# equal size; liberals: value = ethnic
+asym_lib <- suppressWarnings( ggpubr::ggarrange(mnlib,mjlib,ncol=1,nrow=2))
 
-df1 <- read.csv("et_mj.csv", skip=6)
-df2 <- read.csv("et_mj2.csv", skip=6)
-df3 <- read.csv("et_mn.csv", skip=6)
-df4 <- read.csv("et_mn2.csv", skip=6)
+ggsave("asym_lib.jpg",asym_lib,path = "images")
 
-df <- rbind(df3,df4)
-lg <- read.csv("lg_et_mj.csv", sep=";")[,1]
+```
 
-names(df) <- lg
+```{r asym conservatives}
 
-excldf <- names(df) %in% c("run", "density","step")
-df <- df[!excldf]
+mncon <- asym.plot( sens_vl %>%  filter( type == "Conservative Majority" | type == "Conservative Minority") %>% filter(ID == "mn"))
+mjcon <- asym.plot(sens_vl %>%  filter( type == "Conservative Majority" | type == "Conservative Minority") %>% filter(ID == "mj"))
 
-df <- df %>% group_by(fraction_blue,circle_blue,circle_orange,dominant,et_mj_on,et_mn_on) %>% summarise_all(mean)
+asym_cons <- suppressWarnings( ggpubr::ggarrange(mncon,mjcon,ncol=1,nrow=2))
 
-df <- df %>%  gather(key = subgroup, value = Segra, de_sq_bl,dv_sq_bl,de_cl_bl,dv_cl_bl,de_sq_or,dv_sq_or,de_cl_or,dv_cl_or)  %>% mutate(
+ggsave("asym_cons.jpg",asym_cons,path = "images")
+
+```
+
+```{r asym dislib}
+
+dislib <- read.csv("dislib.csv",sep = ",") %>% select(-c(run)) %>%
+  group_by(density,fraction_blue,circle_blue,circle_orange,eth_con_loc,eth_con_min,val_lib_loc,val_lib_min,eth_lib_loc,eth_lib_min,val_con_loc,val_con_min,ID) %>% summarise_all(mean) %>%  gather(key = subgroup, value = Segra, de_sq_bl,dv_sq_bl,de_cl_bl,dv_cl_bl,de_sq_or,dv_sq_or,de_cl_or,dv_cl_or)  %>% mutate(
 `segregation` = fct_relevel(fct_collapse(subgroup,"Ethnic" = c("de_sq_bl","de_cl_bl","de_sq_or","de_cl_or"), "Value" = c("dv_sq_bl","dv_cl_bl","dv_sq_or","dv_cl_or")),"Ethnic"), 
@@
 
-df %>% filter(et_mj_on == "false") %>% ggplot(aes(x= dominant,y = Segra, color = `segregation`, shape = `orientation`, linetype = et_mn_on)) + geom_point() + geom_line() +
-  scale_color_manual(values = c("green","purple"), guide = guide_legend(title = "Outcome")) +
-  scale_shape_manual(values = c("square","circle"), guide = guide_legend(title = "Orientation"))  +
- # scale_y_continuous(limits=c(0.45,1), breaks=seq(0.5,1,by=0.1)) +
-  xlab("beta") +
-  ylab("Outcome") +
-  facet_wrap(~  `type` ) +
-  theme_bw()+
-  theme(legend.position = "bottom")
+ethnicity.labs <- c("50% Majority", "60% Majority","70% Majority","80% Majority","90% Majority")
+names(ethnicity.labs) <- c("50","60","70","80","90")
+
+st <- list(
+dislib %>% filter(type == "Conservative Majority"),
+dislib %>% filter(type == "Conservative Minority"),
+dislib %>% filter(type == "Liberals Majority"),
+dislib %>% filter(type == "Liberals Minority")
+
+)
+
+suppressWarnings(
+for (df in st) {
+
+pl <- ggplot(data = df, aes(x= circle_orange, y=Segra, color = segregation, linetype = as.factor(ID))) + geom_point(size=1.5) + geom_line() +
+  facet_wrap(~ fraction_blue, nrow=1, labeller = labeller(fraction_blue = ethnicity.labs)) +
+scale_linetype_manual(values = c(bsl = "solid", mj1 = "dashed", mn1 = "dotted"),labels = c("Basine (ß = 15)","ß liberal majority = 1","ß liberal minority = 1"), guide = guide_legend(title = "Dominant \nPreference:")) +
+  scale_color_manual(values = c("dark green","purple"), labels =  c("ethnic","value"), guide = guide_legend(title = "Segregation")) +
+  xlab("% Liberals Minority") +
+  ylab("Spatial Clustering") +
+   scale_x_discrete(limits = seq(10,90 ,by = 10)) +
+  geom_hline(yintercept=1,color="red") +
+  ggtitle(df$type) +
+  theme_bw() +
+  theme(panel.spacing = unit(0.7, "lines"),legend.position="bottom",legend.text=element_text(size=12))
+
+nmn <- c(if(df$type == "Conservative Majority"){"dislib_cn_mj"}, if(df$type == "Conservative Minority"){"dislib_cn_mn"},if(df$type == "Liberals Majority"){"dislib_lb_mj"},if(df$type == "Liberals Minority"){"dislib_lb_mn"})
+
+ggsave(paste0(nmn,".jpg"), pl,path = "images", width = 10, height = 6, dpi = 300)
+
+}
+
+)
 
@@
 
-```{r determinism_area_X_ethnic_size, echo = FALSE}
-# lg <-  read.csv("lg_etlib.csv",sep=";")[,1]
-# 
-# etlb_bs <- read.csv("et_lib_fc_bothfalse.csv",sep=",",skip=6)
-# names(etlb_bs) <- lg
-# etlb_bs$ID <- "bsl"
-# 
-# etlb_mj <- read.csv("et_lib_fc_mj.csv",sep=",",skip=6)
-# names(etlb_mj) <- lg
-# etlb_mj$ID <- "mj_et"
-# 
-# etlb_mn <- read.csv("et_lib_fc_mn.csv",sep=",",skip=6)
-# names(etlb_mn) <- lg
-# etlb_mn$ID <- "mn_et"
-# 
-# etlb_bs2 <- read.csv("et_lib_fc_bothfalse2.csv",sep=",",skip=6)
-# names(etlb_bs2) <- lg
-# etlb_bs2$ID <- "bsl"
-# 
-# etlb_mj2 <- read.csv("et_lib_fc_mj2.csv",sep=",",skip=6)
-# names(etlb_mj2) <- lg
-# etlb_mj2$ID <- "mj_et"
-# 
-# etlb_mn2 <- read.csv("et_lib_fc_mn2.csv",sep=",",skip=6)
-# names(etlb_mn2) <- lg
-# etlb_mn2$ID <- "mn_et"
-# 
-# etlb <- rbind(etlb_bs,etlb_mj,etlb_mn,etlb_bs2,etlb_mj2,etlb_mn2)
-# 
-# write.csv(etlb,"etlb.csv",row.names=F)
+# Increase ethnic liberal
+
+```{r ethnicliberal, echo = FALSE}
 
@@
 )
+
+suppressWarnings(
 
@@
 
-```
-
-We only look at the behavior of liberals, as conservatives have minimal consequence. Combining the two plots looked awful
-
-```{r et_liberals, fig.cap="OK Effect of ethnic liberals majority vs minority on liberals", echo = FALSE}
-
-etlib_maj <- df_sec %>% filter(fraction_blue == 50 | fraction_blue == 80)  %>% gather(key = subgroup, value = Clustetmj, de_cl_bl,dv_cl_bl,de_cl_or,dv_cl_or) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"Ethnic" = c("de_cl_bl","de_cl_or"), "Value" = c("dv_cl_bl","dv_cl_or") ),"Ethnic"),
-              `ethnicity` = fct_relevel(fct_collapse(subgroup,"Liberals Majority" = c("de_cl_bl","dv_cl_bl"), "Liberals Minority" = c("de_cl_or","dv_cl_or")), "Liberals Majority"))
-
-libmaj <-  ggplot(data =  etlib_maj[which(etlib_maj$ID == "etlib_loc" & etlib_maj$eth_lib_min == 0 & etlib_maj$eth_con_loc == 20  & etlib_maj$eth_con_min == 20 & etlib_maj$val_con_loc ==0 & etlib_maj$val_con_min == 0),], aes(x= eth_lib_loc,y = Clustetmj,linetype= as.factor(fraction_blue), shape =`segregation`,color = `ethnicity`) ) +
-  geom_point(size=2) + geom_line() +
-  facet_wrap(~`ethnicity`, dir = "v") +
-   scale_color_manual(values = c("blue","orange"), name = "Ethnicity") +
-  scale_shape_manual(values = c("square","circle"), name = "Segregation") +
-   scale_linetype_manual(values = c("solid","dashed"), labels = c("50%","80%"), name = "% Majority") +
-  xlab("ß ethnic liberals majority") +
-  ylab("Spatial Clustering") +
-  labs(caption = "ß ethnic liberals minority = 0") + theme_bw() +
-  guides(color = FALSE) +
-  theme(plot.caption = element_text(hjust = 0.5))
-
-libmin <-  ggplot(data = etlib_maj[which(etlib_maj$ID == "etlib_min" & etlib_maj$eth_lib_loc == 0 & etlib_maj$eth_con_loc == 20  & etlib_maj$eth_con_min == 20 & etlib_maj$val_con_loc ==0 & etlib_maj$val_con_min == 0),], aes(x= eth_lib_min,y = Clustetmj,linetype= as.factor(fraction_blue), shape =`segregation`,color = `ethnicity`) ) +
-  geom_point(size=2) + geom_line() + 
-  facet_wrap(~`ethnicity`, dir = "v") +
-   scale_color_manual(values = c("blue","orange"), name = "Ethnicity") + 
-  scale_shape_manual(values = c("square","circle"), name = "Segregation") + 
-   scale_linetype_manual(values = c("solid","dashed"), labels = c("50%","80%"), name = "% Majority") +
-  xlab("ß ethnic liberals minority") +
-  ylab("Spatial Clustering") +
-  labs(caption = "ß ethnic liberals majority = 0") + theme_bw() +
-  guides(color = FALSE) +
-  theme(plot.caption = element_text(hjust = 0.5))
-
-df_t <- df_sec %>% filter(fraction_blue == 80) %>% filter(val_lib_loc == 20 & eth_lib_loc == 20 & eth_con_loc == 20 & val_con_loc == 0 & val_con_min == 0 & eth_con_min == 5)
-
-libmin <-  ggplot(data = etlib_maj[which(etlib_maj$ID == "etlib_min" & etlib_maj$eth_lib_loc == 7 & etlib_maj$eth_con_loc == 20  & etlib_maj$eth_con_min == 20 & etlib_maj$val_con_loc ==0 & etlib_maj$val_con_min == 0),], aes(x= eth_lib_min,y = Clustetmj,linetype= as.factor(fraction_blue), shape =`segregation`,color = `ethnicity`) ) +
-  geom_point(size=2) + geom_line() + 
-  facet_wrap(~`ethnicity`, dir = "v") +
-   scale_color_manual(values = c("blue","orange"), name = "Ethnicity") + 
-  scale_shape_manual(values = c("square","circle"), name = "Segregation") + 
-   scale_linetype_manual(values = c("solid","dashed"), labels = c("50%","80%"), name = "% Majority") +
-  xlab("ß ethnic liberals minority") +
-  ylab("Spatial Clustering") +
-  labs(caption = "ß ethnic liberals majority = 0") + theme_bw() +
-  guides(color = FALSE) +
-  theme(plot.caption = element_text(hjust = 0.5))
-
-eth_lib <-  ggpubr::ggarrange(libmaj,libmin, common.legend = TRUE, legend = "bottom")
-
-ggsave( "eth_lib.jpg" , eth_lib,  path = "images")
+)
 
@@
 
-### Annex
+# Increase ethnic: distribution liberals
 
-```{r by-product ethnic cons, fig.cap="Effect of liberals majority vs minority on ethnic segregation conservatives", echo = FALSE}
-# Not interesting, goes in the annex
+```{r dislib_et}
 
-# ethnic and value segregation for each group in the annex
+dislib_et <- read.csv("dislib_et.csv",sep=",") %>% select(-c(run)) %>%
+  group_by(density,fraction_blue,circle_blue,circle_orange,et_mn_on,et_mj_on,dominant,ID) %>% summarise_all(mean) %>%  gather(key = subgroup, value = Segra, de_sq_bl,dv_sq_bl,de_cl_bl,dv_cl_bl,de_sq_or,dv_sq_or,de_cl_or,dv_cl_or)  %>% mutate(
+`segregation` = fct_relevel(fct_collapse(subgroup,"Ethnic" = c("de_sq_bl","de_cl_bl","de_sq_or","de_cl_or"), "Value" = c("dv_sq_bl","dv_cl_bl","dv_sq_or","dv_cl_or")),"Ethnic"), 
+ `ethnicity` = fct_relevel(fct_collapse(subgroup, "Majority" = c("de_sq_bl","dv_cl_bl","de_cl_bl","dv_sq_bl"), "Minority" = c("de_sq_or","de_cl_or","dv_sq_or","dv_cl_or")), "Majority"),
+`orientation` = fct_relevel(fct_collapse(subgroup,"Conservatives" = c("de_sq_bl","dv_sq_bl","de_sq_or","dv_sq_or"), "Liberals" = c("de_cl_bl","dv_cl_bl","de_cl_or","dv_cl_or")), "Conservatives"), 
+`type` = fct_relevel(fct_collapse(subgroup,"Conservative Majority" = c("de_sq_bl","dv_sq_bl"),
+      "Liberals Majority" = c("de_cl_bl","dv_cl_bl"),
+      "Conservative Minority" = c("de_sq_or","dv_sq_or"),
+      "Liberals Minority" = c("de_cl_or","dv_cl_or")), "Conservative Majority"))
 
-##### 
-# By-product value of conservatives by value preference liberals
+ethnicity.labs <- c("50% Majority", "60% Majority","70% Majority","80% Majority","90% Majority")
+names(ethnicity.labs) <- c("50","60","70","80","90")
 
-# Majority
+st <- list(
+dislib_et %>% filter(type == "Conservative Majority"),
+dislib_et %>% filter(type == "Conservative Minority"),
+dislib_et %>% filter(type == "Liberals Majority"),
+dislib_et %>% filter(type == "Liberals Minority")
 
-mech_cons <- mech %>% filter(fraction_blue == 50 | fraction_blue == 80) %>%  filter(val_lib_min==0 | val_lib_min==1 |val_lib_min==7) %>% gather(key=ethnics, value=Clust, de_sq_bl,de_sq_or)
+)
 
-cons_maj_et <- ggplot(data = mech_cons, aes(x=val_lib_loc,y=Clust,color=  `ethnics`,linetype= as.factor(fraction_blue))) + geom_point(size=1.5, shape = "square") + geom_line() + 
-  facet_wrap(~val_lib_min,dir="v",labeller = labeller(val_lib_min = valueminority.labs)) +
-    scale_y_continuous(breaks= seq(0,5,by=0.5)) +
-  xlab("ß value liberal majority") + ylab("Spatial clustering") +
+suppressWarnings(
+for (df in st) {
+
+pl <- ggplot(data = df, aes(x= circle_orange, y=Segra, color = segregation, linetype = as.factor(ID))) + geom_point(size=1.5) + geom_line() +
+  facet_wrap(~ fraction_blue, nrow=1, labeller = labeller(fraction_blue = ethnicity.labs)) +
+scale_linetype_manual(values = c(bsl = "solid", etmj = "dashed", etmn = "dotted"),labels = c("Basine (ß = 0)","ß liberal majority","ß liberal minority"), guide = guide_legend(title = "ß ethnic")) +
+  scale_color_manual(values = c("dark green","purple"), labels =  c("ethnic","value"), guide = guide_legend(title = "Segregation")) +
+  xlab("% Liberals Minority") +
+  ylab("Spatial Clustering") +
+   scale_x_discrete(limits = seq(10,90 ,by = 10)) +
   geom_hline(yintercept=1,color="red") +
-  scale_color_manual(values=c("blue","darkorange"),labels=c("Majority","Minority"),name="Ethnicity") +
-    scale_linetype_manual(values=c("solid","dashed"),labels=c("50%","80%"),name="% Majority") +
-   guides(color  = guide_legend(order = 1), linetype = guide_legend(order = 2)) +
-  theme_bw()
+  ggtitle(df$type) +
+  theme_bw() +
+  theme(panel.spacing = unit(0.7, "lines"),legend.position="bottom",legend.text=element_text(size=12))
 
-# Minority
+nmn <- c(if(df$type == "Conservative Majority"){"dislib_cn_mj_et"}, if(df$type == "Conservative Minority"){"dislib_cn_mn_et"},if(df$type == "Liberals Majority"){"dislib_lb_mj_et"},if(df$type == "Liberals Minority"){"dislib_lb_mn_et"})
 
-mech_lib <- mech %>%  filter(fraction_blue == 50 | fraction_blue == 80) %>%  filter(val_lib_loc==0 | val_lib_loc==1 |val_lib_loc==7) %>% gather(key=ethnics, value=Cluste, de_sq_bl,de_sq_or)
+ggsave(paste0(nmn,".jpg"), pl,path = "images", width = 10, height = 6, dpi = 300)
 
-cons_min_et <- ggplot(data = mech_lib, aes(x=val_lib_min,y=Cluste,color=  `ethnics`,linetype= as.factor(fraction_blue))) + geom_point(size=1.5, shape = "square") + geom_line() + 
-  facet_wrap(~val_lib_loc,dir="v",labeller = labeller(val_lib_loc = valuemajority.labs)) +
-  xlab("ß value liberal minority") + ylab("Spatial clustering") +
-  scale_y_continuous(breaks= seq(0,5,by=0.5)) +
-  geom_hline(yintercept=1,color="red") +
-  scale_color_manual(values=c("blue","darkorange"),labels=c("Majority","Minority"),name="Ethnicity") +
-    scale_linetype_manual(values=c("solid","dashed"),labels=c("50%","80%"),name="% Majority") +
-   guides(color  = guide_legend(order = 1), linetype = guide_legend(order = 2)) +
- theme_bw()
+}
 
-ggplotly(cons_maj_et)
-ggplotly(cons_min_et)
-
-lib_cons_et <- ggpubr::ggarrange(cons_maj_et,cons_min_et, common.legend = TRUE, legend = "bottom")
-lib_cons_et
-#ggsave("lib_cons.jpg",plot=lib_cons)
-
-ggpubr::annotate_figure(lib_cons_et,top = "Effect of liberals majority vs minority on ethnic segregation conservatives")
+)
 
 ```
-
-```{r et_liberals_con, fig.cap="OK Effect of ethnic liberals majority vs minority on liberals", echo = FALSE}
-
-# etlib_maj <- df_etlib %>% filter(fraction_blue == 50 | fraction_blue == 80) %>% filter(eth_con_loc == 20 & eth_con_min == 20) %>% filter(val_con_loc == 0 & val_con_min == 0) %>% filter(eth_lib_min == 0)
-
-etlib_maj <- df_sec %>% filter(fraction_blue == 50 | fraction_blue == 80)  %>% gather(key = subgroup, value = Clustetmj, de_sq_bl,dv_sq_bl,de_sq_or,dv_sq_or) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"Ethnic" = c("de_sq_bl","de_sq_or"), "Value" = c("dv_sq_bl","dv_sq_or") ),"Ethnic"),
-              `ethnicity` = fct_relevel(fct_collapse(subgroup,"Conservatives Majority" = c("de_sq_bl","dv_sq_bl"), "Conservatives Minority" = c("de_sq_or","dv_sq_or")), "Conservatives Majority")) # %>% filter(eth_lib_min == 0)
-
-# data_maj = etlib_maj[which(etlib_maj$ID == "etlib_loc" & etlib_maj$eth_lib_min == 0),]
-
-libmaj <-  ggplot(data =  etlib_maj[which(etlib_maj$ID == "etlib_loc" & etlib_maj$eth_lib_min == 0 & etlib_maj$eth_con_loc == 20  & etlib_maj$eth_con_min == 20 & etlib_maj$val_con_loc ==0 & etlib_maj$val_con_min == 0),], aes(x= eth_lib_loc,y = Clustetmj,linetype= as.factor(fraction_blue), shape =`segregation`,color = `ethnicity`) ) +
-  geom_point(size=2) + geom_line() +
-  facet_wrap(~`ethnicity`, dir = "v") +
-   scale_color_manual(values = c("blue","orange"), name = "Ethnicity") +
-  scale_shape_manual(values = c("square","circle"), name = "Segregation") +
-   scale_linetype_manual(values = c("solid","dashed"), labels = c("50%","80%"), name = "% Majority") +
-  xlab("ß ethnic liberals majority") +
-  ylab("Spatial Clustering") +
-  labs(caption = "ß ethnic liberals minority = 0") + theme_bw() +
-  guides(color = FALSE) +
-  theme(plot.caption = element_text(hjust = 0.5))
-
-libmin <-  ggplot(data = etlib_maj[which(etlib_maj$ID == "etlib_min" & etlib_maj$eth_lib_loc == 0 & etlib_maj$eth_con_loc == 20  & etlib_maj$eth_con_min == 20 & etlib_maj$val_con_loc ==0 & etlib_maj$val_con_min == 0),], aes(x= eth_lib_min,y = Clustetmj,linetype= as.factor(fraction_blue), shape =`segregation`,color = `ethnicity`) ) +
-  geom_point(size=2) + geom_line() + 
-  facet_wrap(~`ethnicity`, dir = "v") +
-   scale_color_manual(values = c("blue","orange"), name = "Ethnicity") + 
-  scale_shape_manual(values = c("square","circle"), name = "Segregation") + 
-   scale_linetype_manual(values = c("solid","dashed"), labels = c("50%","80%"), name = "% Majority") +
-  xlab("ß ethnic liberals minority") +
-  ylab("Spatial Clustering") +
-  labs(caption = "ß ethnic liberals majority = 0") + theme_bw() +
-  guides(color = FALSE) +
-  theme(plot.caption = element_text(hjust = 0.5))
-
-ggpubr::ggarrange(libmaj,libmin, common.legend = TRUE, legend = "bottom")
-
-```
-
-### Back
-
-```{r sec_test, fig.cap="Secondary preference high and low randomness", echo = FALSE}
-
-# pref <- names(df_sec) %in% c("eth_con_loc", "eth_con_min","val_loc_lib")
-
-# Value conservaties
-
-df_sec <-  df_sec  %>% gather(key = subgroup, value = Clus, de_sq_bl,dv_sq_bl,de_cl_bl,dv_cl_bl,de_sq_or,dv_sq_or,de_cl_or,dv_cl_or)  %>% mutate(
-          `segregation` = fct_relevel(fct_collapse(subgroup,"Ethnic" = c("de_sq_bl","de_cl_bl","de_sq_or","de_cl_or"), "Value" = c("dv_sq_bl","dv_cl_bl","dv_sq_or","dv_cl_or")),"Ethnic"), 
-          `ethnicity` = fct_relevel(fct_collapse(subgroup," Majority" = c("de_sq_bl","dv_cl_bl","de_cl_bl","dv_sq_bl"), "Minority" = c("de_sq_or","de_cl_or","dv_sq_or","dv_cl_or")), "Majority"),
-         `orientation` = fct_relevel(fct_collapse(subgroup,"Conservatives" = c("de_sq_bl","dv_sq_bl","de_sq_or","dv_sq_or"), "Liberals" = c("de_cl_bl","dv_cl_bl","de_cl_or","dv_cl_or")), "Conservatives")  )
-
-df_sec_vlmjH<- df_sec  %>%  filter(fraction_blue == 80 & ID == "valuecon_loc" & val_con_min == 0 & RND == "high") %>% filter(val_con_loc == 0 |val_con_loc == 5) 
-df_sec_vlmjL <- df_sec  %>%  filter(fraction_blue == 80 & ID == "valuecon_loc" & val_con_min == 0 & RND == "low") %>% filter(val_con_loc == 0 |val_con_loc == 20)
-
-datas <- df_sec_vlmjH
-df_sec_vlmjH_p <- ggplot(datas, aes(x = val_con_loc,y = Clus, shape = `orientation` , color = `ethnicity` , linetype = `segregation`)) + geom_point() + geom_line() +
-  scale_x_discrete(limits= c(0,max(datas$val_con_loc)),breaks = c(0,max(datas$val_con_loc))) +
-  scale_y_continuous(breaks = seq(0,max(datas$Clus),by=0.5)) +
-  scale_shape_manual(values = c("square","circle"),labels = c("Conservatives","Liberals"), name= "Orientation")  +
- scale_color_manual(values=c("blue","orange"),labels = c("Majority","Minority"), name= "Ethnicity")  + scale_linetype_manual(values=c("solid","dashed"),labels = c("Ethnic","Value"), name= "Segregation \ntype") +
-  ylab("Spatial Clustering") +
-  xlab("ß value Conservatives Majority") +
-  ggtitle(if (datas$RND == "high") {"High Randomness (dominant ß = 5)"}else{"Low Randomness (dominant ß = 20)"}) +
-  # ggtitle(if RND ="high"   "High Randomness (dominant ß = 5)") +
-  theme_bw()
-
-datas <- df_sec_vlmjL
-df_sec_vlmjL_p <-  ggplot(datas, aes(x = val_con_loc,y = Clus, shape = `orientation` , color = `ethnicity` , linetype = `segregation`)) + geom_point() + geom_line() +
-  scale_x_discrete(limits= c(0,max(datas$val_con_loc)),breaks = c(0,max(datas$val_con_loc))) +
-  scale_y_continuous(breaks = seq(0,max(datas$Clus),by=0.5)) +
-  scale_shape_manual(values = c("square","circle"),labels = c("Conservatives","Liberals"), name= "Orientation")  +
- scale_color_manual(values=c("blue","orange"),labels = c("Majority","Minority"), name= "Ethnicity")  + scale_linetype_manual(values=c("solid","dashed"),labels = c("Ethnic","Value"), name= "Segregation \ntype") +
-  ylab("Spatial Clustering") +
-  xlab("ß value Conservatives Majority") +
-  ggtitle(if (datas$RND == "high") {"High Randomness (dominant ß = 5)"}else{"Low Randomness (dominant ß = 20)"}) +
-  # ggtitle(if RND ="high"   "High Randomness (dominant ß = 5)") +
-  theme_bw()
-
-df_sec_vlmnH<- df_sec  %>%  filter(fraction_blue == 80 & ID == "valuecon_min" & val_con_loc == 0 & RND == "high") %>% filter(val_con_min == 0 |val_con_min == 5) 
-df_sec_vlmnL <- df_sec  %>%  filter(fraction_blue == 80 & ID == "valuecon_min" & val_con_loc == 0 & RND == "low") %>% filter(val_con_min == 0 |val_con_min == 20)
-
-datas <- df_sec_vlmnH
-df_sec_vlmnH_p <-  ggplot(datas, aes(x = val_con_min,y = Clus, shape = `orientation` , color = `ethnicity` , linetype = `segregation`)) + geom_point() + geom_line() +
-  scale_x_discrete(limits= c(0,max(datas$val_con_min)),breaks = c(0,max(datas$val_con_min))) +
-  scale_y_continuous(breaks = seq(0,max(datas$Clus),by=0.5)) +
-  scale_shape_manual(values = c("square","circle"),labels = c("Conservatives","Liberals"), name= "Orientation")  +
- scale_color_manual(values=c("blue","orange"),labels = c("Majority","Minority"), name= "Ethnicity")  + scale_linetype_manual(values=c("solid","dashed"),labels = c("Ethnic","Value"), name= "Segregation \ntype") +
-  ylab("Spatial Clustering") +
-  xlab("ß value Conservatives Minority") +
-  ggtitle(if (datas$RND == "high") {"High Randomness (dominant ß = 5)"}else{"Low Randomness (dominant ß = 20)"}) +
-  # ggtitle(if RND ="high"   "High Randomness (dominant ß = 5)") +
-  theme_bw()
-
-datas <- df_sec_vlmnL
-df_sec_vlmnL_p <-  ggplot(datas, aes(x = val_con_min,y = Clus, shape = `orientation` , color = `ethnicity` , linetype = `segregation`)) + geom_point() + geom_line() +
-  scale_x_discrete(limits= c(0,max(datas$val_con_min)),breaks = c(0,max(datas$val_con_min))) +
-  scale_y_continuous(breaks = seq(0,max(datas$Clus),by=0.5)) +
-  scale_shape_manual(values = c("square","circle"),labels = c("Conservatives","Liberals"), name= "Orientation")  +
- scale_color_manual(values=c("blue","orange"),labels = c("Majority","Minority"), name= "Ethnicity")  + scale_linetype_manual(values=c("solid","dashed"),labels = c("Ethnic","Value"), name= "Segregation \ntype") +
-  ylab("Spatial Clustering") +
-  xlab("ß value Conservatives Minority") +
-  ggtitle(if (datas$RND == "high") {"High Randomness (dominant ß = 5)"}else{"Low Randomness (dominant ß = 20)"}) +
-  # ggtitle(if RND ="high"   "High Randomness (dominant ß = 5)") +
-  theme_bw()
-
-ggpubr::ggarrange(df_sec_vlmjH_p,df_sec_vlmjL_p,df_sec_vlmnH_p,df_sec_vlmnL_p, common.legend = TRUE, legend = "bottom")
-
-# Ethnic liberals
-
-df_sec <-  df_sec  %>% gather(key = subgroup, value = Clus, de_sq_bl,dv_sq_bl,de_cl_bl,dv_cl_bl,de_sq_or,dv_sq_or,de_cl_or,dv_cl_or)  %>% mutate(
-          `segregation` = fct_relevel(fct_collapse(subgroup,"Ethnic" = c("de_sq_bl","de_cl_bl","de_sq_or","de_cl_or"), "Value" = c("dv_sq_bl","dv_cl_bl","dv_sq_or","dv_cl_or")),"Ethnic"), 
-          `ethnicity` = fct_relevel(fct_collapse(subgroup," Majority" = c("de_sq_bl","dv_cl_bl","de_cl_bl","dv_sq_bl"), "Minority" = c("de_sq_or","de_cl_or","dv_sq_or","dv_cl_or")), "Majority"),
-         `orientation` = fct_relevel(fct_collapse(subgroup,"Conservatives" = c("de_sq_bl","dv_sq_bl","de_sq_or","dv_sq_or"), "Liberals" = c("de_cl_bl","dv_cl_bl","de_cl_or","dv_cl_or")), "Conservatives")  )
-
-df_sec_etmjH<- df_sec  %>%  filter(fraction_blue == 80 & ID == "etlib_loc" & eth_lib_min == 0 & RND == "high") %>% filter(eth_lib_loc == 0 |eth_lib_loc == 5) 
-df_sec_etmjL <- df_sec  %>%  filter(fraction_blue == 80 & ID == "etlib_loc" & eth_lib_min == 0 & RND == "low") %>% filter(eth_lib_loc == 0 |eth_lib_loc == 20)
-
-datas <- df_sec_etmjH
-df_sec_etmjH_p <- ggplot(datas, aes(x = eth_lib_loc,y = Clus, shape = `orientation` , color = `ethnicity` , linetype = `segregation`)) + geom_point() + geom_line() +
-  scale_x_discrete(limits= c(0,max(datas$eth_lib_loc)),breaks = c(0,max(datas$eth_lib_loc))) +
-  scale_y_continuous(breaks = seq(0,max(datas$Clus),by=0.5)) +
-  scale_shape_manual(values = c("square","circle"),labels = c("Conservatives","Liberals"), name= "Orientation")  +
- scale_color_manual(values=c("blue","orange"),labels = c("Majority","Minority"), name= "Ethnicity")  + scale_linetype_manual(values=c("solid","dashed"),labels = c("Ethnic","Value"), name= "Segregation \ntype") +
-  ylab("Spatial Clustering") +
-  xlab("ß Ethnic Liberals Majority") +
-  ggtitle(if (datas$RND == "high") {"High Randomness (dominant ß = 5)"}else{"Low Randomness (dominant ß = 20)"}) +
-  # ggtitle(if RND ="high"   "High Randomness (dominant ß = 5)") +
-  theme_bw()
-
-datas <- df_sec_etmjL
-df_sec_etmjL_p <-  ggplot(datas, aes(x = eth_lib_loc,y = Clus, shape = `orientation` , color = `ethnicity` , linetype = `segregation`)) + geom_point() + geom_line() +
-  scale_x_discrete(limits= c(0,max(datas$eth_lib_loc)),breaks = c(0,max(datas$eth_lib_loc))) +
-  scale_y_continuous(breaks = seq(0,max(datas$Clus),by=0.5)) +
-  scale_shape_manual(values = c("square","circle"),labels = c("Conservatives","Liberals"), name= "Orientation")  +
- scale_color_manual(values=c("blue","orange"),labels = c("Majority","Minority"), name= "Ethnicity")  + scale_linetype_manual(values=c("solid","dashed"),labels = c("Ethnic","Value"), name= "Segregation \ntype") +
-  ylab("Spatial Clustering") +
-  xlab("ß Ethnic Liberals Majority") +
-  ggtitle(if (datas$RND == "high") {"High Randomness (dominant ß = 5)"}else{"Low Randomness (dominant ß = 20)"}) +
-  # ggtitle(if RND ="high"   "High Randomness (dominant ß = 5)") +
-  theme_bw()
-
-df_sec_etmnH<- df_sec  %>%  filter(fraction_blue == 80 & ID == "etlib_min" & eth_lib_loc == 0 & RND == "high") %>% filter(eth_lib_min == 0 |eth_lib_min == 5) 
-df_sec_etmnL <- df_sec  %>%  filter(fraction_blue == 80 & ID == "etlib_min" & eth_lib_loc == 0 & RND == "low") %>% filter(eth_lib_min == 0 |eth_lib_min == 20)
-
-datas <- df_sec_etmnH
-df_sec_etmnH_p <-  ggplot(datas, aes(x = eth_lib_min,y = Clus, shape = `orientation` , color = `ethnicity` , linetype = `segregation`)) + geom_point() + geom_line() +
-  scale_x_discrete(limits= c(0,max(datas$eth_lib_min)),breaks = c(0,max(datas$eth_lib_min))) +
-  scale_y_continuous(breaks = seq(0,max(datas$Clus),by=0.5)) +
-  scale_shape_manual(values = c("square","circle"),labels = c("Conservatives","Liberals"), name= "Orientation")  +
- scale_color_manual(values=c("blue","orange"),labels = c("Majority","Minority"), name= "Ethnicity")  + scale_linetype_manual(values=c("solid","dashed"),labels = c("Ethnic","Value"), name= "Segregation \ntype") +
-  ylab("Spatial Clustering") +
-  xlab("ß Ethnic Liberals Minority") +
-  ggtitle(if (datas$RND == "high") {"High Randomness (dominant ß = 5)"}else{"Low Randomness (dominant ß = 20)"}) +
-  # ggtitle(if RND ="high"   "High Randomness (dominant ß = 5)") +
-  theme_bw()
-
-datas <- df_sec_etmnL
-df_sec_etmnL_p <-  ggplot(datas, aes(x = eth_lib_min,y = Clus, shape = `orientation` , color = `ethnicity` , linetype = `segregation`)) + geom_point() + geom_line() +
-  scale_x_discrete(limits= c(0,max(datas$eth_lib_min)),breaks = c(0,max(datas$eth_lib_min))) +
-  scale_y_continuous(breaks = seq(0,max(datas$Clus),by=0.5)) +
-  scale_shape_manual(values = c("square","circle"),labels = c("Conservatives","Liberals"), name= "Orientation")  +
- scale_color_manual(values=c("blue","orange"),labels = c("Majority","Minority"), name= "Ethnicity")  + scale_linetype_manual(values=c("solid","dashed"),labels = c("Ethnic","Value"), name= "Segregation \ntype") +
-  ylab("Spatial Clustering") +
-  xlab("ß Ethnic Liberals Minority") +
-  ggtitle(if (datas$RND == "high") {"High Randomness (dominant ß = 5)"}else{"Low Randomness (dominant ß = 20)"}) +
-  # ggtitle(if RND ="high"   "High Randomness (dominant ß = 5)") +
-  theme_bw()
-
-ggpubr::ggarrange(df_sec_etmjH_p,df_sec_etmjL_p,df_sec_etmnH_p,df_sec_etmnL_p, common.legend = TRUE, legend = "bottom")
-```
-
-```{r et_lib_cons, fig.cap="NO Effect of ethnic liberals on conservatives", echo = FALSE}
-
-# etlib_maj <- df_etlib %>% filter(fraction_blue == 50 | fraction_blue == 80) %>% filter(eth_con_loc == 20 & eth_con_min == 20) %>% filter(val_con_loc == 0 & val_con_min == 0) %>% filter(eth_lib_min == 0)
-
-etlib_cons <- df_sec %>% filter(fraction_blue == 50 | fraction_blue == 80, val_con_loc ==0, val_con_min == 0 )  %>% gather(key = subgroup, value = Clustetmj, de_sq_bl,dv_sq_bl,de_sq_or,dv_sq_or) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"Ethnic" = c("de_sq_bl","de_sq_or"), "Value" = c("dv_sq_bl","dv_sq_or") ),"Ethnic"),
-              `ethnicity` = fct_relevel(fct_collapse(subgroup,"Conservatives Majority" = c("de_sq_bl","dv_sq_bl"), "Conservatives Minority" = c("de_sq_or","dv_sq_or")), "Conservatives Majority")) # %>% filter(eth_lib_min == 0)
-
-# data_maj = etlib_maj[which(etlib_maj$ID == "etlib_loc" & etlib_maj$eth_lib_min == 0),]
-
-conmaj <-  ggplot(data =  etlib_cons[which(etlib_cons$ID == "etlib_loc" & etlib_cons$eth_lib_min == 0 & etlib_cons$eth_con_loc == 20 & etlib_cons$eth_con_min == 20),], aes(x= eth_lib_loc,y = Clustetmj,linetype= as.factor(fraction_blue), shape =`segregation`,color = `ethnicity`) ) +
-  geom_point(size=2) + geom_line() +
-  facet_wrap(~`ethnicity`, dir = "v") +
-   scale_color_manual(values = c("blue","orange"), name = "Ethnicity") +
-  scale_shape_manual(values = c("square","circle"), name = "Segregation") +
-   scale_linetype_manual(values = c("solid","dashed"), labels = c("50%","80%"), name = "% Majority") +
-  xlab("ß ethnic liberals majority") +
-  ylab("Spatial Clustering") +
-  labs(caption = "ß ethnic liberals minority = 0") + theme_bw() +
-  guides(color = FALSE) +
-  theme(plot.caption = element_text(hjust = 0.5))
-
-conmin <-  ggplot(data = etlib_cons[which(etlib_cons$ID == "etlib_min" & etlib_cons$eth_lib_loc == 0 & etlib_cons$eth_con_loc == 20 &  etlib_cons$eth_con_min == 20),], aes(x= eth_lib_min,y = Clustetmj,linetype= as.factor(fraction_blue), shape =`segregation`,color = `ethnicity`) ) +
-  geom_point(size=2) + geom_line() + 
-  facet_wrap(~`ethnicity`, dir = "v") +
-   scale_color_manual(values = c("blue","orange"), name = "Ethnicity") + 
-  scale_shape_manual(values = c("square","circle"), name = "Segregation") + 
-   scale_linetype_manual(values = c("solid","dashed"), labels = c("50%","80%"), name = "% Majority") +
-  xlab("ß ethnic liberals minority") +
-  ylab("Spatial Clustering") +
-  labs(caption = "ß ethnic liberals majority = 0") + theme_bw() +
-  guides(color = FALSE) +
-  theme(plot.caption = element_text(hjust = 0.5))
-
-ggpubr::ggarrange(conmaj,conmin, common.legend = TRUE, legend = "bottom")
-
-```

### 2021-07-14 af2.Rmd
df

@@
  ---
-title: "additional3D"
+title: "af2"
 output: pdf_document
@@
 knitr::opts_chunk$set(echo = TRUE)
+
+#setwd("C:/Users/rocpa/OneDrive/Desktop/AF2/analysis")
 
@@
 
-df <- read.csv("df_tot.csv",sep =",")
+df <- read.csv("df_tot.csv",sep =",") %>% select(-c(run)) %>%
+  group_by(ID,density,majority,liberal_maj,liberal_min,beta_distribution,con_maj,con_min,lib_maj,lib_min,dominant,secondary,con_eth,lib_val,lib_eth,con_val,eth_con_maj,eth_con_min,eth_lib_maj,eth_lib_min,val_con_maj,val_con_min,val_lib_maj,val_lib_min,step) %>%
+  summarise_all(c("m"= mean,"sd"= sd)) %>%  
+  gather(key = group_bsl, value = Segra_bsl, et_cl_m,et_sq_m,vl_cl_m,vl_sq_m,den_cl_m,den_sq_m,
+         et_cl_sd,et_sq_sd,vl_cl_sd,vl_sq_sd,den_cl_sd,den_sq_sd
+         )  %>%
+  mutate(`outcome` = fct_relevel(fct_collapse(group_bsl,"Ethnic" = c("et_sq_m","et_cl_m","et_sq_sd","et_cl_sd"), "Value" = c("vl_sq_m","vl_cl_m","vl_sq_sd","vl_cl_sd"), "Density" = c("den_sq_m","den_cl_m","den_sq_sd","den_cl_sd")),"Ethnic"),
+`orientation` = fct_relevel(fct_collapse(group_bsl,"Conservatives" = c("et_sq_m","vl_sq_m","den_sq_m","et_sq_sd","vl_sq_sd","den_sq_sd"
+                                                                       ), "Liberals" = c("et_cl_m","vl_cl_m","den_cl_m", "et_cl_sd","vl_cl_sd","den_cl_sd")), "Conservatives"),
+`Stat` = fct_relevel(fct_collapse(group_bsl,"Mean" = c("et_cl_m","et_sq_m","vl_cl_m","vl_sq_m","den_cl_m","den_sq_m"), "SD" = c("et_cl_sd","et_sq_sd","vl_cl_sd","vl_sq_sd","den_cl_sd","den_sq_sd")),  "Mean")) %>%
+  gather(key = group_asm, value = Segra_asm, cls_et_sq_bl_m,cls_et_cl_bl_m,cls_et_sq_or_m,cls_et_cl_or_m,
+         cls_vl_sq_bl_m,cls_vl_cl_bl_m,cls_vl_sq_or_m,cls_vl_cl_or_m,
+         cls_den_sq_bl_m,cls_den_cl_bl_m,cls_den_sq_or_m,cls_den_cl_or_m,
+           et_sq_bl_m, et_cl_bl_m, et_sq_or_m, et_cl_or_m,
+           vl_sq_bl_m, vl_cl_bl_m, vl_sq_or_m, vl_cl_or_m,
+           den_sq_bl_m, den_cl_bl_m, den_sq_or_m, den_cl_or_m,
 
-# 
-# 
-# 
-# 
-# df_3D <- read.csv("3D.csv",sep=",")
-# excl3D <- names(df_3D) %in% c("run", "density","step")
-# df_3D <- df_3D[!excl3D] %>% group_by(eth_con_loc, eth_con_min,eth_lib_loc,eth_lib_min,val_lib_loc,val_lib_min,val_con_loc,val_con_min,circle_orange,circle_blue,fraction_blue) %>% summarise_all(mean)
-# 
-# 
-# value_basic_den <- read.csv("value_basic_den.csv",sep = ",")
-# excl <- names(value_basic_den) %in% c("run","density","step")
-# value_basic_den <- value_basic_den[!excl] %>% group_by(ID,fraction_blue,circle_blue,circle_orange,circle,square) %>% summarise_all(mean)
-# 
-# 
-# value_dominant_den <- read.csv("value_dominant_den.csv",sep = ",")
-# excl <- names(value_dominant_den) %in% c("run","density","step")
-# value_dominant_den <- value_dominant_den[!excl] %>% group_by(ID,fraction_blue,circle_blue,circle_orange,dominant_square,dominant_circle,secondary_square,secondary_circle) %>% summarise_all(mean) 
-#
+         cls_et_sq_bl_sd,cls_et_cl_bl_sd,cls_et_sq_or_sd,cls_et_cl_or_sd,
+         cls_vl_sq_bl_sd,cls_vl_cl_bl_sd,cls_vl_sq_or_sd,cls_vl_cl_or_sd,
+         cls_den_sq_bl_sd,cls_den_cl_bl_sd,cls_den_sq_or_sd,cls_den_cl_or_sd,
+           et_sq_bl_sd, et_cl_bl_sd, et_sq_or_sd, et_cl_or_sd,
+           vl_sq_bl_sd, vl_cl_bl_sd, vl_sq_or_sd, vl_cl_or_sd,
+           den_sq_bl_sd, den_cl_bl_sd, den_sq_or_sd, den_cl_or_sd
+
+         )%>% 
+  mutate(`outcome` = fct_relevel(fct_collapse(group_asm, 
+          "Ethnic" = c("cls_et_sq_bl_m","cls_et_cl_bl_m","cls_et_sq_or_m","cls_et_cl_or_m","et_sq_bl_m","et_cl_bl_m","et_sq_or_m","et_cl_or_m",
+                       "cls_et_sq_bl_sd","cls_et_cl_bl_sd","cls_et_sq_or_sd","cls_et_cl_or_sd","et_sq_bl_sd","et_cl_bl_sd","et_sq_or_sd","et_cl_or_sd"
+
+                       ),
+           "Value" = c( "cls_vl_sq_bl_m","cls_vl_cl_bl_m","cls_vl_sq_or_m","cls_vl_cl_or_m" ,"vl_sq_bl_m","vl_cl_bl_m","vl_sq_or_m","vl_cl_or_m",
+                        "cls_vl_sq_bl_sd","cls_vl_cl_bl_sd","cls_vl_sq_or_sd","cls_vl_cl_or_sd" ,"vl_sq_bl_sd","vl_cl_bl_sd","vl_sq_or_sd","vl_cl_or_sd"
+                        ),
+           "Density" = c("cls_den_sq_bl_m","cls_den_cl_bl_m","cls_den_sq_or_m","cls_den_cl_or_m","den_sq_bl_m","den_cl_bl_m","den_sq_or_m","den_cl_or_m",
+                         "cls_den_sq_bl_sd","cls_den_cl_bl_sd","cls_den_sq_or_sd","cls_den_cl_or_sd","den_sq_bl_sd","den_cl_bl_sd","den_sq_or_sd","den_cl_or_sd"
+                         )
+                                              ), "Ethnic"),
+
+         `type` = fct_relevel(fct_collapse(group_asm,
+            "Conservative Majority" = c("cls_et_sq_bl_m","cls_vl_sq_bl_m","cls_den_sq_bl_m", "et_sq_bl_m","vl_sq_bl_m","den_sq_bl_m",
+                          "cls_et_sq_bl_sd","cls_vl_sq_bl_sd","cls_den_sq_bl_sd", "et_sq_bl_sd","vl_sq_bl_sd","den_sq_bl_sd"              
+                                        ),
+            "Liberal Majority" = c("cls_et_cl_bl_m","cls_vl_cl_bl_m","cls_den_cl_bl_m",  "et_cl_bl_m","vl_cl_bl_m","den_cl_bl_m",
+                                   "cls_et_cl_bl_sd","cls_vl_cl_bl_sd","cls_den_cl_bl_sd",  "et_cl_bl_sd","vl_cl_bl_sd","den_cl_bl_sd"
+
+                                   ),
+             "Conservative Minority" = c("cls_et_sq_or_m","cls_vl_sq_or_m","cls_den_sq_or_m",  "et_sq_or_m","vl_sq_or_m","den_sq_or_m",
+                                         "cls_et_sq_or_sd","cls_vl_sq_or_sd","cls_den_sq_or_sd",  "et_sq_or_sd","vl_sq_or_sd","den_sq_or_sd"
+
+                                         ),
+             "Liberal Minority" = c("cls_et_cl_or_m","cls_vl_cl_or_m","cls_den_cl_or_m", "et_cl_or_m","vl_cl_or_m","den_cl_or_m",
+                                    "cls_et_cl_or_sd","cls_vl_cl_or_sd","cls_den_cl_or_sd", "et_cl_or_sd","vl_cl_or_sd","den_cl_or_sd"
+                                    )
+            ),"Conservative Majority" ),
+         `metric` = fct_relevel(fct_collapse(group_asm,
+            "Exposure" = c("et_sq_bl_m", "et_cl_bl_m", "et_sq_or_m", "et_cl_or_m", "vl_sq_bl_m", "vl_cl_bl_m", "vl_sq_or_m", "vl_cl_or_m", "den_sq_bl_m", "den_cl_bl_m",  "den_sq_or_m", "den_cl_or_m",
+                           "et_sq_bl_sd", "et_cl_bl_sd", "et_sq_or_sd", "et_cl_or_sd", "vl_sq_bl_sd", "vl_cl_bl_sd", "vl_sq_or_sd", "vl_cl_or_sd", "den_sq_bl_sd", "den_cl_bl_sd",  "den_sq_or_sd", "den_cl_or_sd"
+                           ),
+            "Cluster" = c("cls_et_sq_bl_m","cls_et_cl_bl_m","cls_et_sq_or_m","cls_et_cl_or_m", "cls_vl_sq_bl_m","cls_vl_cl_bl_m","cls_vl_sq_or_m","cls_vl_cl_or_m", "cls_den_sq_bl_m","cls_den_cl_bl_m","cls_den_sq_or_m","cls_den_cl_or_m",
+
+      "cls_et_sq_bl_sd","cls_et_cl_bl_sd","cls_et_sq_or_sd","cls_et_cl_or_sd", "cls_vl_sq_bl_sd","cls_vl_cl_bl_sd","cls_vl_sq_or_sd","cls_vl_cl_or_sd", "cls_den_sq_bl_sd","cls_den_cl_bl_sd","cls_den_sq_or_sd","cls_den_cl_or_sd"
+
+                          )), "Exposure"),
+      `Stat` = fct_relevel(fct_collapse(group_asm,
+                                        "Mean" = c("cls_et_sq_bl_m","cls_et_cl_bl_m","cls_et_sq_or_m","cls_et_cl_or_m",
+         "cls_vl_sq_bl_m","cls_vl_cl_bl_m","cls_vl_sq_or_m","cls_vl_cl_or_m",
+         "cls_den_sq_bl_m","cls_den_cl_bl_m","cls_den_sq_or_m","cls_den_cl_or_m",
+           "et_sq_bl_m", "et_cl_bl_m", "et_sq_or_m", "et_cl_or_m",
+           "vl_sq_bl_m", "vl_cl_bl_m", "vl_sq_or_m", "vl_cl_or_m",
+           "den_sq_bl_m", "den_cl_bl_m", "den_sq_or_m", "den_cl_or_m"),
+         "SD" = c("cls_et_sq_bl_sd","cls_et_cl_bl_sd","cls_et_sq_or_sd","cls_et_cl_or_sd",
+         "cls_vl_sq_bl_sd","cls_vl_cl_bl_sd","cls_vl_sq_or_sd","cls_vl_cl_or_sd",
+         "cls_den_sq_bl_sd","cls_den_cl_bl_sd","cls_den_sq_or_sd","cls_den_cl_or_sd",
+           "et_sq_bl_sd", "et_cl_bl_sd", "et_sq_or_sd", "et_cl_or_sd",
+           "vl_sq_bl_sd", "vl_cl_bl_sd", "vl_sq_or_sd", "vl_cl_or_sd",
+           "den_sq_bl_sd", "den_cl_bl_sd", "den_sq_or_sd", "den_cl_or_sd" )), "Mean"))
+
+# df <- read.csv("df_tot.csv",sep =",") %>% select(-c(run)) %>%
+#   group_by(ID,density,majority,liberal_maj,liberal_min,beta_distribution,con_maj,con_min,lib_maj,lib_min,dominant,secondary,con_eth,lib_val,lib_eth,con_val,eth_con_maj,eth_con_min,eth_lib_maj,eth_lib_min,val_con_maj,val_con_min,val_lib_maj,val_lib_min,step) %>% summarise_all(c("m"= mean,"sd"= sd)) %>%  gather(key = group_bsl, value = Segra_bsl, et_cl_m,et_sq_m,vl_cl_m,vl_sq_m,den_cl_m,den_sq_m)  %>%
+#   mutate(`outcome` = fct_relevel(fct_collapse(group_bsl,"Ethnic" = c("et_sq_m","et_cl_m"), "Value" = c("vl_sq_m","vl_cl_m"), "Density" = c("den_sq_m","den_cl_m")),"Ethnic"),
+# `orientation` = fct_relevel(fct_collapse(group_bsl,"Conservatives" = c("et_sq_m","vl_sq_m","den_sq_m"), "Liberals" = c("et_cl_m","vl_cl_m","den_cl_m")), "Conservatives") ) %>%
+#   gather(key = group_asm, value = Segra_asm, cls_et_sq_bl_m,cls_et_cl_bl_m,cls_et_sq_or_m,cls_et_cl_or_m,
+#          cls_vl_sq_bl_m,cls_vl_cl_bl_m,cls_vl_sq_or_m,cls_vl_cl_or_m,
+#          cls_den_sq_bl_m,cls_den_cl_bl_m,cls_den_sq_or_m,cls_den_cl_or_m)%>% 
+#   mutate(`outcome` = fct_relevel(fct_collapse(group_asm, "Ethnic" = c("cls_et_sq_bl_m","cls_et_cl_bl_m","cls_et_sq_or_m","cls_et_cl_or_m"),
+#                                               "Value" = c( "cls_vl_sq_bl_m","cls_vl_cl_bl_m","cls_vl_sq_or_m","cls_vl_cl_or_m"),
+#                                               "Density" = c("cls_den_sq_bl_m","cls_den_cl_bl_m","cls_den_sq_or_m","cls_den_cl_or_m")
+#                                               ), "Ethnic"),
+#          `outcome` = fct_relevel(fct_collapse(group_asm, "Conservative Majority" = c("cls_et_sq_bl_m","cls_vl_sq_bl_m","cls_den_sq_bl_m"),
+#                                               "Liberal Majority" = c("cls_et_cl_bl_m","cls_vl_cl_bl_m","cls_den_cl_bl_m"),
+#                                               "Conservative Minority" = c("cls_et_sq_or_m","cls_vl_sq_or_m","cls_den_sq_or_m"),
+#                                               "Liberal Minority" = c("cls_et_cl_or_m","cls_vl_cl_or_m","cls_den_cl_or_m")
+#             )))
 
